### 2018-04-02 selection_tutorial.Rmd
updating repository

---
title: "Tutorial: Calculating Selection"
output: html_notebook
---

```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
library(tidyverse)
library(cowplot) # pretty default ggplots
library(broom) # for tidying multiple linear models

## LOAD & MANAGE DATASET ----

gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number),
         Treatment.focus = as.character(Treatment.focus),
         Treatment = as.character(Treatment),
         Genotype = as.character(Genotype),
         Gall_Letter = as.character(Gall_Letter)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)))

# create a new dataset that compares phenotypic distributions before and after selection
galls_before <- mutate(gall_selection.df, Timing="Before")
galls_after <- filter(gall_selection.df, gall_survival == 1) %>% mutate(Timing = "After")

gall_diffs.df <- bind_rows(galls_before, galls_after)
```

Examine distributions of phenotypes
```{r}
size_means <- gall_selection.df %>%
  group_by(Treatment.focus) %>%
  summarise_at(vars(Gall_Height_mm, gall_survival), funs(mean))
size_means

gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm, fill=Treatment.focus)) +
  geom_density(alpha=0.5) +
  geom_vline(data=size_means, aes(xintercept=Gall_Height_mm, color=Treatment.focus), linetype="dotted")

# according to Shapiro-Wilk though, its non-normal (P < 0.05). 
# other transformations don't help, I think the raw distribution looks pretty good though
shapiro.test(gall_selection.df$Gall_Height_mm)
shapiro.test(sqrt(gall_selection.df$Gall_Height_mm))
shapiro.test(log(gall_selection.df$Gall_Height_mm))

## AGGREGATE DATA AT GALL LEVEL ----
# for analyzing the number of individuals per gall

agg_gall.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position, Gall_Number) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(log.gall_individuals = log(gall_individuals))

# I added a log-transformed 'gall individuals' because it helps normalize the distribution a bit
shapiro.test(agg_gall.level$gall_individuals)
shapiro.test(sqrt(agg_gall.level$gall_individuals))
shapiro.test(log(agg_gall.level$gall_individuals))

# calculate average number of individuals per gall in each treatment
indiv_means <- agg_gall.level %>%
  group_by(Treatment.focus) %>%
  summarise_at(vars(gall_individuals, log.gall_individuals, gall_survival), funs(mean))
indiv_means

agg_gall.level %>%
  ggplot(., aes(x=gall_individuals, fill=Treatment.focus)) +
  geom_histogram(position='identity', alpha=0.5, binwidth=1) +
  geom_vline(data=indiv_means, aes(xintercept=gall_individuals, color=Treatment.focus), linetype="dotted") +
  scale_x_continuous(breaks=c(1:10))

agg_gall.level %>%
  ggplot(., aes(x=log.gall_individuals, fill=Treatment.focus)) +
  geom_histogram(position='identity', alpha=0.5) +
  geom_vline(data=indiv_means, aes(xintercept=log.gall_individuals, color=Treatment.focus), linetype="dotted")

## AGGREGATE DATA AT TREE LEVEL ----
# for gall density analysis

agg_tree.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sqrt.Density_per_100_shoots = sqrt(Density_per_100_shoots))

# I added a square-root transformation to gall density because it makes the distribution more normal (but not quite)
shapiro.test(agg_tree.level$Density_per_100_shoots)
shapiro.test(sqrt(agg_tree.level$Density_per_100_shoots))
shapiro.test(log(agg_tree.level$Density_per_100_shoots+1))

# calculate the average gall density in each treatment
density_means <- agg_tree.level %>%
  group_by(Treatment.focus) %>%
  summarise_at(vars(Density_per_100_shoots, sqrt.Density_per_100_shoots, gall_survival), funs(mean))
density_means

# plot the distribution of gall density in each treatment
agg_tree.level %>%
  ggplot(., aes(x=Density_per_100_shoots, fill=Treatment.focus)) +
  geom_density(alpha=0.5) +
  geom_vline(data = density_means, aes(xintercept=Density_per_100_shoots, color=Treatment.focus), linetype="dotted")

# plot the distribution of sqrt(gall density) in each treatment
agg_tree.level %>%
  ggplot(., aes(x=sqrt.Density_per_100_shoots, fill=Treatment.focus)) +
  geom_density(alpha=0.5) +
  geom_vline(data = density_means, aes(xintercept=sqrt.Density_per_100_shoots, color=Treatment.focus), linetype="dotted")
```

```{r}
gall_selection.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control",
                                   gall_survival/filter(size_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(size_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

non_singular <- gall_selection.df %>%
  filter(Plant_Position %in% plants_manygalls) %>%
  group_by(Genotype, Treatment.focus, Plant_Position) %>%
  summarise_at(vars(gall_survival), mean) %>%
  filter(gall_survival > 0 & gall_survival < 1)

size.gradients_plant.level <- gall_selection.df %>%
  filter(Plant_Position %in% non_singular$Plant_Position) %>%
  group_by(Genotype, Treatment.focus, Plant_Position) %>%
  do(model = lm(I(gall_survival/mean(gall_survival)) ~ I(Gall_Height_mm-mean(Gall_Height_mm)), .)) %>%
  tidy(model) %>%
  filter(term != "(Intercept)")

size.gradients_plant.level
summary(lm(estimate ~ Genotype*Treatment.focus, data=size.gradients_plant.level, weights = std.error))
ggplot(size.gradients_plant.level, aes(x=Genotype, y=estimate, fill=Treatment.focus, size=std.error)) +
  geom_point()
```

Understanding the causes of selection in different environments is not straightforward.

The most straightforward way to measure selection is the *selection differential*, which corresponds to the difference in mean phenotype before vs. after selection: $$s=\bar{z}^*-\bar{z}$$.

```{r figure: gall size selection differential, echo=FALSE, message=FALSE, warning=FALSE}
size_means_diffs <- gall_diffs.df %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(Gall_Height_mm, gall_survival), funs(mean, var, sd)) 
size_means_diffs

size_differentials <- size_means_diffs %>%
  select(Timing, Treatment.focus, Gall_Height_mm_mean) %>%
  spread(Timing, Gall_Height_mm) %>%
  mutate(selection_differential = After - Before)
size_differentials

gall_diffs.df %>%
  ggplot(., aes(x=Gall_Height_mm, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data=size_means_diffs, aes(xintercept=Gall_Height_mm_mean, color=Timing), linetype="dashed") +
  facet_wrap(~Treatment.focus, ncol = 1)
```

We find that the selection differential on control trees ($s=$`r round(filter(size_differentials, Treatment.focus=="Control")$selection_differential,2)`) is 43% larger than on treatment trees ($s=$`r round(filter(size_differentials, Treatment.focus=="Ectoparasitoid exclusion")$selection_differential, 2)`).

We can also look at selection in another way. Let's plot the relationship between absolute fitness and the phenotype.
```{r figure: gall size linear regression, echo=FALSE, message=FALSE, warning=FALSE}
gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm - mean(Gall_Height_mm), y=gall_survival, color=Treatment.focus)) +
  geom_smooth(method="lm") +
  geom_jitter(height=0.05, shape=1) +
  geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

That's interesting, the slope of absolute fitness as a function of phenotype doesn't look all that different between treatments, but the differences in mean fitness are:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
size_lm <- lm(gall_survival ~ 
                Treatment.focus + 
                I(Gall_Height_mm - mean(Gall_Height_mm)) +  
                Treatment.focus:I(Gall_Height_mm - mean(Gall_Height_mm)), 
              data = gall_selection.df)
summary(size_lm)

size.gradient_lm <- lm(relative_fitness ~ 
                #Treatment.focus + 
                I(Gall_Height_mm - mean(Gall_Height_mm)) +  
                Treatment.focus:I(Gall_Height_mm - mean(Gall_Height_mm)), 
              data = gall_selection.df)
summary(size.gradient_lm)
```

This suggests that the difference in selection between the control and treatment trees is due to differences in fitness between treatments and NOT the relationship between phenotype and fitness. In case you don't believe me, let me convince you that we can recover the selection differentials from a linear model such as this. Note that another way we can define the selection differential is: $$s=\frac{Cov(W,z)}{\bar{W}}$$

where $$W$$ represents absolute fitness and $$z$$ represents the phenotype. In linear model, the regression coefficient $b$ corresponds to: $$b=\frac{Cov(W,z)}{Var(z)}$$

Thus, $$s=b\cdot\frac{Var(z)}{\bar{W}}$$

`r 0.081308*filter(size_means_diffs, Timing=="Before",Treatment.focus=="Control")$Gall_Height_mm_var/filter(size_means_diffs, Timing=="Before",Treatment.focus=="Control")$gall_survival_mean`

```{r figure: gall size logistic regression, echo=FALSE, message=FALSE, warning=FALSE}
binomial_smooth <- function(...) {
  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
}

gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm - mean(Gall_Height_mm), y=gall_survival, color=Treatment.focus)) +
  binomial_smooth() +
  geom_jitter(height=0.05, shape=1) +
  geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
indiv_lm <- lm(gall_survival ~ 
                Treatment.focus + 
                I(gall_individuals - mean(gall_individuals)) +  
                Treatment.focus:I(gall_individuals - mean(gall_individuals)), 
              data = agg_gall.level)
summary(indiv_lm)

agg_gall.level <- agg_gall.level %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control",
                                   gall_survival/filter(indiv_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(indiv_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

indiv.gradient_lm <- lm(relative_fitness ~ 
                #Treatment.focus + 
                I(gall_individuals - mean(gall_individuals)) +  
                Treatment.focus:I(gall_individuals - mean(gall_individuals)), 
              data = agg_gall.level)
summary(indiv.gradient_lm)
```

```{r figure: gall individuals logistic regression, echo=FALSE, message=FALSE, warning=FALSE}
agg_gall.level %>%
  ggplot(., aes(x=gall_individuals - mean(gall_individuals), y=gall_survival, color=Treatment.focus)) +
  binomial_smooth() +
  geom_jitter(height=0.05, shape=1) +
  #geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
density_lm <- lm(gall_survival ~ 
                Treatment.focus + 
                I(Density_per_100_shoots - mean(Density_per_100_shoots)) +  
                Treatment.focus:I(Density_per_100_shoots - mean(Density_per_100_shoots)), 
              data = agg_tree.level)
summary(density_lm)

agg_tree.level <- agg_tree.level %>%
  mutate(relative_fitness = ifelse(Treatment.focus=="Control",
                                   gall_survival/filter(density_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(density_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

density.gradient_lm <- lm(relative_fitness ~ 
                #Treatment.focus + 
                I(Density_per_100_shoots - mean(Density_per_100_shoots)) +  
                Treatment.focus:I(Density_per_100_shoots - mean(Density_per_100_shoots)), 
              data = agg_tree.level)
summary(density.gradient_lm)
```

```{r figure: gall individuals logistic regression, echo=FALSE, message=FALSE, warning=FALSE}
agg_tree.level %>%
  ggplot(., aes(x=Density_per_100_shoots - mean(Density_per_100_shoots), y=gall_survival, color=Treatment.focus)) +
  binomial_smooth() +
  geom_jitter(height=0.05, shape=1) +
  #geom_hline(data = size_means, aes(yintercept=gall_survival, color=Treatment.focus), linetype="dotted") +
  geom_vline(xintercept=0, color="grey")
```

Visually, we can estimate the selection differentials
```{r}
library(gsg)

# why are these different?
gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(moments = moments.differentials(z = .$Gall_Height_mm - mean(.$Gall_Height_mm), W = .$gall_survival, standardized = FALSE)) %>%
  tidy(moments)

control.diff <- moments.differentials(
  z = filter(gall_selection.df, Treatment.focus=="Control")$Gall_Height_mm,
  W = filter(gall_selection.df, Treatment.focus=="Control")$gall_survival, 
  standardized = FALSE
)
control.diff

treatment.diff <- moments.differentials(
  z = filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")$Gall_Height_mm,
  W = filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival, 
  standardized = FALSE
)
treatment.diff

```

## Calculating selection differentials

```{r}

size_lms <- gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(model = lm(gall_survival ~ I(Gall_Height_mm - mean(Gall_Height_mm)), .)) %>%
  tidy(model)
size_lms

summary(lm(gall_survival ~ I(Gall_Height_mm-mean(Gall_Height_mm)), data = filter(gall_selection.df, Treatment.focus=="Control")))

#size_vars <- gall_selection.df %>%
#  group_by(Treatment.focus) %>%
#  summarise_at(vars(Gall_Height_mm), funs(var,sd))
#size_vars

size_lms %>%
  select(Treatment.focus, term, estimate) %>%
  spread(term, estimate) %>%
  mutate(selection_differential = `I(Gall_Height_mm - mean(Gall_Height_mm))`/`(Intercept)`)

gall_selection.df %>%
  do(model = lm(gall_survival ~ I(Gall_Height_mm - mean(Gall_Height_mm))*Treatment.focus, .)) %>%
  tidy(model)

## calculating selection gradients
gall_selection.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus == "Control", 
                                   gall_survival/filter(size_means, Treatment.focus=="Control")$gall_survival,
                                   gall_survival/filter(size_means, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival))

gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm - mean(Gall_Height_mm), y=relative_fitness, color=Treatment.focus)) +
  geom_jitter(height=0.02) +
  geom_smooth(method="lm") + 
  geom_hline(yintercept=1, color="grey", linetype="dotted") +
  geom_vline(xintercept=0, color="grey")

size_gradients <- gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(model = lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), .)) %>%
  tidy(model)
size_gradients

summary(lm(relative_fitness ~ I(scale(Gall_Height_mm)), data = filter(gall_selection.df, Treatment.focus=="Control")))

# for standardized selection gradients
gall_selection.df %>%
  group_by(Treatment.focus) %>%
  do(model = lm(relative_fitness ~ I((Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm)), .)) %>%
  tidy(model)

cov12 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), cov(relative_fitness, Gall_Height_mm))
sd1 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), sd(Gall_Height_mm))
var1 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), var(Gall_Height_mm))
sd2 <- with(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), sd(relative_fitness))

cov12/var1
```

Unstandardized b coefficient is equal to Cov(x,y)/var(x).

$$b=\frac{Cov(x,y)}{Var(x)}$$

Standardized cofficient (Beta) is equal to Cov(x,y)/var(x)SD(x)/SD(y)

$$\beta=\frac{Cov(x,y)}{SD(x)SD(x)}\cdot\frac{SD(x)}{SD(y)}$$

$$w=\frac{W}{\hat{W}}$$

$$s=Cov(w,z)$$
also

$$s=\frac{Cov(W,z)}{\hat{W}}$$

Selection differentials can be calculated as the covariance between the phenotype and absolute fitness, cov(W,z), divided by mean fitness. If we additionally standardize the scale of the phenotype by dividing by its variance, then we also get the selection gradient.

Calculate the selection differentials (difference in means) before and after selection for each treatment.
```{r}
size_means <- gall_diffs.df %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(Gall_Height_mm), funs(mean)) %>%
  ungroup() 
size_means

size_diffs <- size_means %>%
  spread(Timing, Gall_Height_mm) %>%
  mutate(selection_differential = After - Before)
size_diffs

gall_diffs.df %>%
  ggplot(., aes(x=Gall_Height_mm, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = size_means, aes(xintercept=Gall_Height_mm, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

Calculate selection differentials for scaled and normalized traits
```{r}
sc.sqrt.size_means <- gall_diffs.df %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(sc.sqrt.Gall_Height_mm), funs(mean)) %>%
  ungroup() 
sc.sqrt.size_means

sc.sqrt.size_diffs <- sc.sqrt.size_means %>%
  spread(Timing, sc.sqrt.Gall_Height_mm) %>%
  mutate(selection_differential = After - Before)
sc.sqrt.size_diffs

gall_diffs.df %>%
  ggplot(., aes(x=sc.sqrt.Gall_Height_mm, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = sc.sqrt.size_means, aes(xintercept=sc.sqrt.Gall_Height_mm, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

```{r}

gall_selection.df %>%
  group_by(Treatment.focus) %>%
  summarise(covariance = cov(gall_survival, Gall_Height_mm),
            mean_fitness = mean(gall_survival)) %>%
  mutate(selection_differential = covariance/mean_fitness)

gall_selection.df %>%
  group_by(Treatment.focus) %>%
  summarise(covariance = cov(gall_survival, sc.sqrt.Gall_Height_mm),
            mean_fitness = mean(gall_survival)) %>%
  mutate(selection_differential = covariance/mean_fitness)

summary(lm(gall_survival ~ sc.sqrt.Gall_Height_mm, filter(gall_selection.df, Treatment.focus=="Control")))
summary(lm(gall_survival ~ sc.sqrt.Gall_Height_mm, filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))

summary(lm(relative_fitness ~ sc.sqrt.Gall_Height_mm, data=filter(size.rel_fitness.df, Treatment.focus=="Control")))
```

NOTE THAT THE SELECTION DIFFERENTIAL SHOULD CORRESPOND TO THE SELECTION GRADIENT?? (ACCORDING TO HUNTER ET AL 2018, EQN. 4)

Calculate selection gradients acting on gall size
```{r}
size.rel_fitness.df <- gall_selection.df %>%
  mutate(relative_fitness = ifelse(Treatment.focus == "Control", gall_survival/control.mean_fitness, gall_survival/treatment.mean_fitness))

size.rel_fitness.df %>%
  ggplot(., aes(x = Gall_Height_mm, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

size.rel_fitness.df %>%
  ggplot(., aes(x = sc.sqrt.Gall_Height_mm, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

size.rel_fitness.lm <- lm(relative_fitness ~ Gall_Height_mm + Gall_Height_mm:Treatment.focus, data=size.rel_fitness.df)
summary(size.rel_fitness.lm)

sc.sqrt.size.rel_fitness.lm <- lm(relative_fitness ~ sc.sqrt.Gall_Height_mm + sc.sqrt.Gall_Height_mm:Treatment.focus, data=size.rel_fitness.df)
summary(sc.sqrt.size.rel_fitness.lm) 
```

NEED TO CALCULATE SELECTION DIFFERENTIALS AT THE FINEST LEVEL, SINCE THAT IS WHERE SURVIVAL IS ZERO OR 1.

Calculate selection differentials for number of individuals per galls
```{r}
agg_gall.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position, Gall_Number) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sc.log.gall_individuals = as.numeric(scale(log(gall_individuals))))

agg_gall.diffs <- bind_rows(
  mutate(agg_gall.level, Timing = "Before"),
  mutate(filter(agg_gall.level, gall_survival == 1), Timing = "After")
)

indiv_means <- agg_gall.diffs %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(gall_individuals, sc.log.gall_individuals), mean, na.rm = TRUE) %>%
  ungroup() 
indiv_means

indiv_diffs <- indiv_means %>%
  select(Timing, Treatment.focus, gall_individuals) %>%
  spread(Timing, gall_individuals) %>%
  mutate(selection_differential = After - Before)
indiv_diffs

sc.log.indiv_diffs <- indiv_means %>%
  select(Timing, Treatment.focus, sc.log.gall_individuals) %>%
  spread(Timing, sc.log.gall_individuals) %>%
  mutate(selection_differential = After - Before)
sc.log.indiv_diffs

agg_gall.diffs %>%
  ggplot(., aes(x=gall_individuals, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = indiv_means, aes(xintercept=gall_individuals, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)

agg_gall.diffs %>%
  ggplot(., aes(x=sc.log.gall_individuals, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = indiv_means, aes(xintercept=sc.log.gall_individuals, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

Calculate selection gradients acting on number of individuals per gall
```{r}
agg_gall.control.mean_fit <- mean(filter(agg_gall.level, Treatment.focus=="Control")$gall_survival)
agg_gall.treatment.mean_fit <- mean(filter(agg_gall.level, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival)

agg_gall.level <- agg_gall.level %>%
  mutate(relative_fitness = ifelse(Treatment.focus == "Control", 
                                   gall_survival/agg_gall.control.mean_fit,
                                   gall_survival/agg_gall.treatment.mean_fit))

agg_gall.level %>%
  ggplot(., aes(x = gall_individuals, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

agg_gall.level %>%
  ggplot(., aes(x = sc.log.gall_individuals, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

indiv.gradient.lm <- lm(relative_fitness ~ gall_individuals + gall_individuals:Treatment.focus, agg_gall.level)
summary(indiv.gradient.lm)

sc.log.indiv.gradient.lm <- lm(relative_fitness ~ sc.log.gall_individuals + sc.log.gall_individuals:Treatment.focus, agg_gall.level)
summary(sc.log.indiv.gradient.lm)
```

Calculate selection differentials for gall density
```{r}
agg_tree.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sc.sqrt.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots))))

agg_tree.diffs <- bind_rows(
  mutate(agg_tree.level, Timing = "Before"),
  mutate(filter(agg_tree.level, gall_survival == 1), Timing = "After")
)

density_means <- gall_diffs.df %>%
  distinct(Plant_Position, Timing, Treatment.focus, Density_per_100_shoots) %>%
  group_by(Timing, Treatment.focus) %>%
  summarise_at(vars(Density_per_100_shoots), funs(mean)) %>%
  ungroup() 
density_means

density_diffs <- density_means %>%
  spread(Timing, Density_per_100_shoots) %>%
  mutate(selection_differential = After - Before)
density_diffs

gall_diffs.df %>%
  distinct(Plant_Position, Timing, Treatment.focus, Density_per_100_shoots) %>%
  ggplot(., aes(x=Density_per_100_shoots, fill=Timing)) +
  geom_density(alpha=0.5) +
  geom_vline(data = density_means, aes(xintercept=Density_per_100_shoots, color=Timing), linetype="dotted") +
  facet_wrap(~Treatment.focus, ncol=1)
```

Calculate selection gradients acting on gall density
```{r}
agg_tree.level <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype, Plant_Position) %>%
  summarise_at(vars(gall_survival, gall_individuals, Gall_Height_mm, Density_per_100_shoots), funs(mean)) %>%
  mutate(sc.sqrt.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots))))

agg_tree.control.mean_fit <- mean(filter(agg_tree.level, Treatment.focus=="Control")$gall_survival)
agg_tree.treatment.mean_fit <- mean(filter(agg_tree.level, Treatment.focus=="Ectoparasitoid exclusion")$gall_survival)

agg_tree.level <- agg_tree.level %>% 
  mutate(relative_fitness = ifelse(Treatment.focus=="Control", 
                                   gall_survival/agg_tree.control.mean_fit, 
                                   gall_survival/agg_tree.treatment.mean_fit))

agg_tree.level %>%
  ggplot(., aes(x = Density_per_100_shoots, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

agg_tree.level %>%
  ggplot(., aes(x = sc.sqrt.Density_per_100_shoots, y = relative_fitness, color=Treatment.focus)) +
  geom_jitter(shape=1, height = 0.02) +
  geom_hline(yintercept=1, linetype="dotted") +
  geom_smooth(method = "lm")

density.gradient.lm <- lm(relative_fitness ~ Density_per_100_shoots + Density_per_100_shoots:Treatment.focus, agg_tree.level)
summary(density.gradient.lm)

sc.sqrt.density.gradient.lm <- lm(relative_fitness ~ sc.sqrt.Density_per_100_shoots + sc.sqrt.Density_per_100_shoots:Treatment.focus, agg_tree.level)
summary(sc.sqrt.density.gradient.lm)
plot(sc.sqrt.density.gradient.lm) # not too bad
```

### 2018-04-02 gsg_models.R

@@ -1,33 +1,38 @@
 
 ## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-
+library(raster)
 library(tidyverse)
+library(FD)
 library(mgcv)
 library(gamm4) # for generalized additive mixed models #
 library(gsg)
+#library(lme4)
 library(cowplot) # pretty default ggplots
+#library(visreg) # quick visualizations of model outputs
+#library(brms)
+library(belg) # calculating configurational entropy of a 2D landscape
 
 #################   BE CAREFUL IN HOW DATA IS SUBSETTED !!! ###################
 
 ## LOAD & MANAGE DATASET ----
 
 gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.factor(Plant_Position),
-         Gall_Number = as.factor(Gall_Number),
-         Treatment.focus = as.factor(Treatment.focus),
-         Treatment = as.factor(Treatment),
-         Genotype = as.factor(Genotype),
-         Gall_Letter = as.factor(Gall_Letter)) %>%
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number),
+         Treatment.focus = as.character(Treatment.focus),
+         Treatment = as.character(Treatment),
+         Genotype = as.character(Genotype),
+         Gall_Letter = as.character(Gall_Letter)) %>%
   unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
   
   # subset data for analysis
   filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%          # eliminate unknown sources of mortality
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
   mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
          egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.Gall_Height_mm = as.numeric(scale(sqrt(Gall_Height_mm))),
-         sc.gall_individuals = as.numeric(scale(log(gall_individuals))),
-         sc.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots))))
+         sc.Gall_Height_mm = as.numeric(scale(Gall_Height_mm)), # sqrt()
[…]

### 2018-04-02 raster_entropy.R

@@ -1,0 +1,24 @@
+library(raster)
+
+# Example Data
+set.seed(1)
+r <- raster(matrix(sample(1:10, 100, replace=T), 10, 10))
+
+# Calculate a weights matrix, and reset elements to 0s and 1s 
+# rather than true weights
+fw <- focalWeight(r, 0.2, 'circle')
+fw <- ifelse(fw == 0, NA, 1)
+
+# Neighbourhood richness
+richness <- function(x, ...) {
+  length(unique(na.omit(x)))
+}
+richOut <- focal(r, fw, fun=richness, pad=T)
+
+# Neighbourhood Shannon Diversity Index
+shannon <- function(x, ...) {
+  cnts <- table(x)
+  cnts <- cnts / sum(cnts)
+  -sum(cnts * log(cnts))
+}
+shanOut <- focal(r, fw, fun=shannon, pad=T)

### 2018-04-09 supp_mat_complexity_selection.Rmd
working on supplementary material

---
title: "Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore"
author: Matt Barbour
output: html_notebook
---

Load dataset. This dataset is a subset that only includes larva that survive to pupation or turned into parasitoids. We omitted any data where larva mortality was unclear. This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
library(tidyverse)
library(cowplot) # pretty default ggplots
library(broom) # for tidying multiple linear models
library(mgcv) # generalized additive models
library(gsg) # calculating selection gradients

## LOAD & MANAGE DATASET ----

gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  # convert appropriate variables to characters instead of integers
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)))

## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
control_df <- gall_selection.df %>%
  filter(Treatment.focus == "Control") %>%
  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
         c.gall_individuals = gall_individuals - mean(gall_individuals),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))

treatment_df <- gall_selection.df %>%
  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
         c.gall_individuals = gall_individuals - mean(gall_individuals),
         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
```

```{r FUNCTIONS}
gam.plot <- function(gam.model, ...) {
  plot(gam.model, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
}

# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
# also, using 'refit.smooth = T' also generated some very skewed distributions
# the recipe below provided the most sensible estimates for my data
gradient.calc <- function(mod, phenotype, covariates = NULL) {
  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
                refit.smooth = F, 
                n.boot = 1000,
                se.method = 'boot.para',
                standardized = T)
} 
```

Choosing the level of model complexity. We used AIC to pair down the complexity of the model. For both the control and treatment plants, there is support for maintaing the linear interaction between gall size and the number of individuals per gall. In both cases, AIC suggest that the models lacking linear interaction terms were more parsimonious, so we subsequently analyzed selection gradients with these models.

```{r AIC MODEL COMPLEXITY}

## CONTROL PLANTS ----
gamm_full.control <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots) +
                                  c.Gall_Height_mm:c.gall_individuals + 
                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
                                  c.gall_individuals:c.Density_per_100_shoots,
                                data = control_df)
summary(gamm_full.control$gam)
summary(gamm_full.control$mer)

gamm_red.control <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots),
                                data = control_df)
summary(gamm_red.control$gam)
summary(gamm_red.control$mer)

AIC(gamm_full.control$mer, gamm_red.control$mer)

## TREATMENT PLANTS ----
gamm_full.treatment <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots) +
                                  c.Gall_Height_mm:c.gall_individuals + 
                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
                                  c.gall_individuals:c.Density_per_100_shoots,
                                data = treatment_df)
summary(gamm_full.treatment$gam)
summary(gamm_full.treatment$mer)

gamm_red.treatment <- gamm.model(gall_survival ~ 
                                  s(c.Gall_Height_mm) + 
                                  s(c.gall_individuals, k=9) + 
                                  s(c.Density_per_100_shoots),
                                data = treatment_df)
summary(gamm_red.treatment$gam)
summary(gamm_red.treatment$mer)

AIC(gamm_full.treatment$mer, gamm_red.treatment$mer)
```

```{r SELECTION GRADIENTS}

## GALL SIZE ----
sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
                                 phenotype = "c.Gall_Height_mm", 
                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                   phenotype = "c.Gall_Height_mm", 
                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))

## GALL INDIVIDUALS ----
sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
                                        phenotype = "c.gall_individuals", 
                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                          phenotype = "c.gall_individuals", 
                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))

## GALL DENSITY ----
sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
                                    phenotype = "c.Density_per_100_shoots", 
                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
                                      phenotype = "c.Density_per_100_shoots", 
                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))

## PRINT TABLE ----
rbind(
  mutate(sg.size_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.size_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.individuals_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.density_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.density_treatment$ests, Food_Web_Treatment = "Simple")
)

round(rbind(
  sg.size_control$ests,
  sg.size_treatment$ests,
  sg.individuals_control$ests,
  sg.individuals_treatment$ests,
  sg.density_control$ests,
  sg.density_treatment$ests
),3)

## BOOTSTRAPPED INTERVALS ----
bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
)

bootstrap_df %>%
  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
  geom_boxplot() +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~Selection_Type) +
  coord_flip() 
```

Another decision we had to make was whether to calculate selection gradients with GAM or GAMMs. The problem with calculating selection gradients with GAMM is that the selection gradients can vary among environmental contexts that are being modelled by random intercepts. Since we did not alter random slopes, this would just cause variation in the selection gradients around the mean value, which is what our model tries to estimate. Therefore, we felt our GAMM model accurately reflects the selection that is happening at the population-level.

GAM estimates of selection gradients differ from GAMM

```{r COMPARE GAM WITH GAMM}

## CONTROL PLANTS ----
gam_red.control <- gam(gall_survival ~
                         s(c.Gall_Height_mm) + 
                         s(c.gall_individuals, k=9) +
                         s(c.Density_per_100_shoots),
                       data = control_df, family = binomial(link = "logit"))
summary(gam_red.control)

gam.plot(gam_red.control)
gam.plot(gamm_red.control$gam)

## TREATMENT PLANTS ----
gam_red.treatment <- gam(gall_survival ~
                         s(c.Gall_Height_mm) + 
                         s(c.gall_individuals, k=9) +
                         s(c.Density_per_100_shoots),
                       data = treatment_df, family = binomial(link = "logit"))
summary(gam_red.treatment)

gam.plot(gam_red.treatment)
gam.plot(gamm_red.treatment$gam)

#### CALCULATE SELECTION GRADIENTS FROM GAM ----

## GALL SIZE ----
sg.gam.size_control <- gradient.calc(mod = gam_red.control, 
                                 phenotype = "c.Gall_Height_mm", 
                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
sg.gam.size_treatment <- gradient.calc(mod = gam_red.treatment, 
                                   phenotype = "c.Gall_Height_mm", 
                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))

## GALL INDIVIDUALS ----
sg.gam.individuals_control <- gradient.calc(mod = gam_red.control, 
                                        phenotype = "c.gall_individuals", 
                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
sg.gam.individuals_treatment <- gradient.calc(mod = gam_red.treatment, 
                                          phenotype = "c.gall_individuals", 
                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))

## GALL DENSITY ----
sg.gam.density_control <- gradient.calc(mod = gam_red.control, 
                                    phenotype = "c.Density_per_100_shoots", 
                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
sg.gam.density_treatment <- gradient.calc(mod = gam_red.treatment, 
                                      phenotype = "c.Density_per_100_shoots", 
                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))

## PRINT TABLE ----
rbind(
  mutate(sg.gam.size_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.gam.size_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.gam.individuals_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.gam.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
  mutate(sg.gam.density_control$ests, Food_Web_Treatment = "Complex"),
  mutate(sg.gam.density_treatment$ests, Food_Web_Treatment = "Simple")
)

round(rbind(
  sg.gam.size_control$ests,
  sg.gam.size_treatment$ests,
  sg.gam.individuals_control$ests,
  sg.gam.individuals_treatment$ests,
  sg.gam.density_control$ests,
  sg.gam.density_treatment$ests
),3)

## BOOTSTRAPPED INTERVALS ----
gam.bootstrap_df <- bind_rows(
  data.frame(Bootstrap_Estimates = sg.gam.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.gam.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.gam.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.gam.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.gam.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.gam.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.gam.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.gam.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.gam.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.gam.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
  data.frame(Bootstrap_Estimates = sg.gam.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
  data.frame(Bootstrap_Estimates = sg.gam.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
)

gam.bootstrap_df %>%
  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
  geom_boxplot() +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~Selection_Type) +
  coord_flip()

```

```{r}
size_models <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival ~ Gall_Height_mm, data = .)) %>%
  tidy(model) %>%
  ungroup()

size_models %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8)) +
  facet_wrap(~term, scales = "free_y")
```

```{r}
size.grad_models <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival/mean(gall_survival) ~ I(Gall_Height_mm - mean(Gall_Height_mm)), data = .)) %>%
  tidy(model) %>%
  ungroup()
size.grad_models

size.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_bar(stat="identity", position = "dodge") +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8))

size.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, position = "dodge", size=4) +
  geom_hline(yintercept=0, linetype="dotted")

summary(lm(estimate ~ Treatment.focus, data = filter(size.grad_models, term != "(Intercept)")))
```

### 2018-04-11 supp_mat_complexity_selection.Rmd
exploring effects of plant genotype on selection gradients.

@@
 library(gsg) # calculating selection gradients
+library(visreg)
 
@@
 
+Analyze separate models for absolute fitness as a function of gall size for each treatment and genotype combination. 
 ```{r}
@@
   group_by(Treatment.focus, Genotype) %>%
-  do(model = lm(gall_survival ~ Gall_Height_mm, data = .)) %>%
+  do(model = lm(gall_survival ~ I(Gall_Height_mm-mean(Gall_Height_mm)), data = .)) %>%
   tidy(model) %>%
@@
   ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
-  geom_bar(stat="identity", position = "dodge") +
   geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
-                width = 0.5, position = position_dodge(width = 0.8)) +
+                width = 0.5, position = position_dodge(width=0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted") +
   facet_wrap(~term, scales = "free_y")
@@
 ```{r}
+size.geno <- gall_selection.df %>%
+  group_by(Treatment.focus, Genotype) %>%
+  summarise_at(vars(Gall_Height_mm), funs(mean))
+size.geno
+
 size.grad_models <- gall_selection.df %>%
@@
   ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
-  geom_bar(stat="identity", position = "dodge") +
   geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
-                width = 0.5, position = position_dodge(width = 0.8))
+                width = 0.5, position = position_dodge(width = 0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted")
 
@@
   geom_line() +
-  geom_point(shape=21, position = "dodge", size=4) +
+  geom_point(shape=21, size=4) +
   geom_hline(yintercept=0, linetype="dotted")
 
-summary(lm(estimate ~ Treatment.focus, data = filter(size.grad_models, term != "(Intercept)")))
+gall_selection.df$c.Gall_Height_mm <- with(gall_selection.df, Gall_Height_mm - mean(Gall_Height_mm))
+
+size_GxE_lms <- lm(gall_survival ~ (c.Gall_Height_mm+Genotype+Treatment.focus)^2, data = gall_selection.df, contrast = list(Genotype = "contr.sum"))
+summary(size_GxE_lms)
+anova(size_GxE_lms)
+
+table(gall_selection.df$Genotype, gall_selection.df$Treatment.focus)
+
+test <- size.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  left_join(., size.geno)
+
+cor.test(test$estimate, test$Gall_Height_mm)
 ```
+
+```{r}
+gall_agg <- gall_selection.df %>%
+  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise_at(vars(gall_individuals, gall_survival), funs(mean)) %>%
+  ungroup() %>%
+  mutate(c.gall_individuals = gall_individuals - mean(gall_individuals))
+
+ind_models <- gall_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  do(model = lm(gall_survival ~ I(gall_individuals-mean(gall_individuals)), data = .)) %>%
+  tidy(model) %>%
+  ungroup()
+
+ind_models %>%
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
+                width = 0.5, position = position_dodge(width=0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted") +
+  facet_wrap(~term, scales = "free_y")
+
+ind.grad_models <- gall_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  do(model = lm(gall_survival/mean(gall_survival) ~ I(gall_individuals - mean(gall_individuals)), data = .)) %>%
+  tidy(model) %>%
+  ungroup()
+ind.grad_models
+
+ind.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
+                width = 0.5, position = position_dodge(width = 0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted") 
+```
+
+```{r}
+plant_agg <- gall_selection.df %>%
+  group_by(Genotype, Treatment.focus, Plant_Position) %>%
+  summarise_at(vars(Density_per_100_shoots, gall_survival), funs(mean)) %>%
+  ungroup() %>%
+  mutate(c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+
+density.grad_models <- plant_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  do(model = lm(gall_survival/mean(gall_survival) ~ I(Density_per_100_shoots - mean(Density_per_100_shoots)), data = .)) %>%
+  tidy(model) %>%
+  ungroup()
+density.grad_models
+
+density.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
+                width = 0.5, position = position_dodge(width = 0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted") 
+```
+
+```{r}
+gall_selection.df$c.gall_individuals <- with(gall_selection.df, gall_individuals - mean(gall_individuals))
+
+ind_GxE_lms <- lm(gall_survival ~ c.gall_individuals*Genotype*Treatment.focus, data = gall_selection.df, contrast = list(Genotype = "contr.sum"))
+summary(ind_GxE_lms)
+anova(ind_GxE_lms)
+```
+
+```{r}
+
+agg.ind_GxE_lms <- lm(gall_survival ~ (c.gall_individuals + Genotype + Treatment.focus)^2, data = gall_agg, contrast = list(Genotype = "contr.sum"))
+summary(agg.ind_GxE_lms)
+anova(agg.ind_GxE_lms)
+visreg(agg.ind_GxE_lms, xvar="c.gall_individuals", by="Treatment.focus")
+visreg(agg.ind_GxE_lms, xvar="c.gall_individuals", by="Genotype")
+```
+
+```{r}
+gall_selection.df$c.Density_per_100_shoots <- with(gall_selection.df, Density_per_100_shoots - mean(Density_per_100_shoots))
+
+density_GxE_lms <- lm(gall_survival ~ (c.Density_per_100_shoots + Genotype + Treatment.focus)^2, data = gall_selection.df, contrast = list(Genotype = "contr.sum"))
+summary(density_GxE_lms)
+anova(density_GxE_lms)
+```
+
+```{r}
+plant_agg <- gall_selection.df %>%
+  group_by(Genotype, Treatment.focus, Plant_Position) %>%
+  summarise_at(vars(Density_per_100_shoots, gall_survival), funs(mean)) %>%
+  ungroup() %>%
+  mutate(c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+
+agg.density_GxE_lms <- lm(gall_survival ~ c.Density_per_100_shoots*Genotype*Treatment.focus, data = plant_agg, contrast = list(Genotype = "contr.sum"))
+summary(agg.density_GxE_lms)
+anova(agg.density_GxE_lms)
+```
+
+```{r}
+multivar_GxE_lms <- lm(gall_survival ~ Genotype*Treatment.focus*c.Gall_Height_mm, data = gall_selection.df, contrast = list(Genotype = "contr.sum", Treatment.focus="contr.sum"))
+summary(multivar_GxE_lms)
+car::vif(multivar_GxE_lms)
+anova(multivar_GxE_lms)
+visreg(multivar_GxE_lms, xvar="c.Gall_Height_mm", by="Treatment.focus")
+visreg(multivar_GxE_lms, xvar="c.gall_individuals", by="Treatment.focus")
+visreg(multivar_GxE_lms, xvar="c.Density_per_100_shoots", by="Treatment.focus")
+visreg2d(multivar_GxE_lms, xvar="c.Density_per_100_shoots", yvar="c.gall_individuals")
+```
+
+```{r Piecewise SEM}
+library(lme4)
+library(lmerTest)
+library(piecewiseSEM)
+
+size_geno <- lm(Gall_Height_mm ~ Genotype, gall_selection.df, contrast = list(Genotype="contr.sum")) 
+summary(size_geno)
+sem.model.fits(size_geno)
+anova(size_geno)
+
+ind_geno <- lm(gall_individuals ~ Genotype, gall_selection.df, contrast = list(Genotype="contr.sum"))
+summary(ind_geno)
+sem.model.fits(ind_geno)
+anova(ind_geno)
+
+density_geno <- lmer(log(Density_per_100_shoots+1) ~ Genotype + (1|Plant_Position/Gall_Number/Gall_ID), gall_selection.df, contrast = list(Genotype="contr.sum"))
+summary(density_geno)
+sem.model.fits(density_geno)
+anova(density_geno)
+
+selection_grads <- lm(gall_survival ~ Treatment.focus*(Gall_Height_mm+gall_individuals+Density_per_100_shoots)^2, gall_selection.df)
+sem.model.fits(selection_grads)
+
+model.list <- list(size_geno, ind_geno, density_geno, selection_grads)
+
+sem.fit(model.list, gall_selection.df, corr.errors = c("Gall_Height_mm~~gall_individuals","Gall_Height_mm~~Density_per_100_shoots","gall_individuals~~Density_per_100_shoots"))
+```
+
+```{r}
+gall_selection.df %>%
+  ggplot(., aes(x=c.Gall_Height_mm, y=gall_survival, color=Genotype)) +
+  geom_smooth(method="lm") +
+  facet_wrap(~Treatment.focus)
+
+gall_agg %>%
+  ggplot(., aes(x=c.gall_individuals, y=gall_survival, color=Genotype)) +
+  geom_smooth(method="lm") +
+  facet_wrap(~Treatment.focus)
+
+plant_agg %>%
+  ggplot(., aes(x=c.Density_per_100_shoots, y=gall_survival, color=Genotype)) +
+  geom_smooth(method="lm") +
+  facet_wrap(~Treatment.focus)
+```

### 2018-04-13 supp_mat_complexity_selection.Rmd
exploring effects of plant genotype on selection gradients.

@@
 
-Analyze separate models for absolute fitness as a function of gall size for each treatment and genotype combination. 
+## What is the relative importance of plant genotype vs. food-web complexity in altering selection gradients?
+
+Gall Size
+```{r}
+# RELATIONSHIP BETWEEN ABSOLUTE FITNESS AND GALL SIZE ACROSS GENOTYPES AND TREATMENTS
+ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
+  geom_point(shape=1) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  #geom_smooth(method = "lm", formula = y ~ poly(x,2), color="red") +
+  facet_wrap(~Genotype, ncol=2)
+
+ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival/mean(gall_survival))) +
+  geom_point() + 
+  geom_smooth(method="lm", formula=y~poly(x,2))
+
+ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
+  geom_point() + 
+  geom_smooth(method="gam", formula=y~s(x), method.args = list(family=binomial(link="logit")))
+
+ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival)) +
+  geom_point() + 
+  geom_smooth(method="gam", formula=y~s(x), method.args = list(family=binomial(link="logit"))) +
+  facet_wrap(~Genotype)
+
+ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
+  geom_point() + 
+  geom_smooth(method="lm", formula=y~poly(x,2)) +
+  facet_wrap(~Genotype)
+
+## ESTIMATE DIRECTIONAL SELECTION GRADIENTS ON GALL SIZE FOR EACH PLANT GENOTYPE AND FOOD-WEB TREATMENT
+size.grad_models <- gall_selection.df %>%
+  group_by(Treatment.focus, Genotype) %>%
+  do(model = lm(gall_survival/mean(gall_survival) ~ I((Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm)), data = .)) %>%
+  tidy(model) %>%
+  ungroup()
+size.grad_models
+
+## PLOT VARIATION IN SELECTION GRADIENTS FOR GALL SIZE AMONG PLANT GENOTYPES AND FOOD-WEB TREATMENTS
+size.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
+                width = 0.5, position = position_dodge(width = 0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted")
+
+## PLOT IN A REACTION NORM STYLE
+size.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
+  geom_line() +
+  geom_point(shape=21, size=4) +
+  geom_hline(yintercept=0, linetype="dotted")
+
+mean_GxE <- gall_selection.df %>%
+  group_by(Treatment.focus, Genotype) %>%
+  summarise_at(vars(gall_survival, Gall_Height_mm), funs(mean))
+mean_GxE
+
+rel_fit_GxE <- c()
+c.GxE.Gall_Height_mm <- c()
+for(i in 1:dim(gall_selection.df)[1]){
+  rel_fit_GxE[i] <- gall_selection.df$gall_survival[i]/filter(mean_GxE,
+                                                          Treatment.focus==gall_selection.df$Treatment.focus[i],
+                                                          Genotype==gall_selection.df$Genotype[i])$gall_survival
+ # c.GxE.Gall_Height_mm <- gall_selection.df$Gall_Height_mm[i] - filter(mean_GxE,
+#                                                          Treatment.focus==gall_selection.df$Treatment.focus[i],
+#                                                          Genotype==gall_selection.df$Genotype[i])$Gall_Height_mm
+}
+gall_selection.df$rel_fit_GxE <- rel_fit_GxE
+#gall_selection.df$c.GxE.Gall_Height_mm <- c.GxE.Gall_Height_mm
+
+gall_selection.df$c.Gall_Height_mm <- gall_selection.df$Gall_Height_mm - mean(gall_selection.df$Gall_Height_mm)
+
+library(sjstats)
+rel_fit_GxE.lm <- lm(rel_fit_GxE ~ c.Gall_Height_mm + c.Gall_Height_mm:Genotype + c.Gall_Height_mm:Treatment.focus + c.Gall_Height_mm:Treatment.focus:Genotype, data = gall_selection.df, contrast = list(Genotype="contr.sum",Treatment.focus="contr.sum"))
+summary(rel_fit_GxE.lm)
+anova(rel_fit_GxE.lm)
+anova_stats(rel_fit_GxE.lm)
+
+## visual checks of regression model
+visreg(rel_fit_GxE.lm) # confirms that relativizing fitness across genotypes and treatments worked
+visreg(rel_fit_GxE.lm, xvar="c.Gall_Height_mm")
+visreg(rel_fit_GxE.lm, xvar="c.Gall_Height_mm", by="Genotype")
+visreg(rel_fit_GxE.lm, xvar="c.Gall_Height_mm", by="Treatment.focus")
+```
+
 ```{r}
@@
   facet_wrap(~term, scales = "free_y")
+
+size_models %>%
+  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
+  geom_line() +
+  geom_point(shape=21, size=4) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~term, scales = "free_y")
 ```
@@
 ```{r}
+
 size.geno <- gall_selection.df %>%
@@
 size.geno
-
-size.grad_models <- gall_selection.df %>%
-  group_by(Treatment.focus, Genotype) %>%
-  do(model = lm(gall_survival/mean(gall_survival) ~ I(Gall_Height_mm - mean(Gall_Height_mm)), data = .)) %>%
-  tidy(model) %>%
-  ungroup()
-size.grad_models
-
-size.grad_models %>%
-  filter(term != "(Intercept)") %>%
-  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
-  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
-                width = 0.5, position = position_dodge(width = 0.8)) +
-  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
-  geom_hline(yintercept = 0, linetype="dotted")
-
-size.grad_models %>%
-  filter(term != "(Intercept)") %>%
-  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
-  geom_line() +
-  geom_point(shape=21, size=4) +
-  geom_hline(yintercept=0, linetype="dotted")
-
-gall_selection.df$c.Gall_Height_mm <- with(gall_selection.df, Gall_Height_mm - mean(Gall_Height_mm))
-
-size_GxE_lms <- lm(gall_survival ~ (c.Gall_Height_mm+Genotype+Treatment.focus)^2, data = gall_selection.df, contrast = list(Genotype = "contr.sum"))
-summary(size_GxE_lms)
-anova(size_GxE_lms)
-
 table(gall_selection.df$Genotype, gall_selection.df$Treatment.focus)
@@
 
+ggplot(test, aes(x=Gall_Height_mm, y=estimate, fill=Genotype, size=1/std.error)) +
+  geom_point(shape=21) +
+  facet_wrap(~Treatment.focus)
+
 cor.test(test$estimate, test$Gall_Height_mm)
 ```
+
+Number of individuals per gall
 
@@
 
-ind_models <- gall_agg %>%
-  group_by(Treatment.focus, Genotype) %>%
-  do(model = lm(gall_survival ~ I(gall_individuals-mean(gall_individuals)), data = .)) %>%
-  tidy(model) %>%
-  ungroup()
+ggplot(gall_agg, aes(x=c.gall_individuals, y=gall_survival/mean(gall_survival))) +
+  geom_point() + 
+  geom_smooth(method="lm", formula=y~poly(x,2))
 
-ind_models %>%
-  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
-  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
-                width = 0.5, position = position_dodge(width=0.8)) +
-  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
-  geom_hline(yintercept = 0, linetype="dotted") +
-  facet_wrap(~term, scales = "free_y")
+ggplot(gall_agg, aes(x=c.gall_individuals, y=gall_survival, color=Treatment.focus)) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  #geom_smooth(method = "lm", formula = y ~ poly(x,2), color="red") +
+  facet_wrap(~Genotype, ncol=2)
+
+ggplot(gall_agg, aes(x=c.gall_individuals, y=gall_survival, color=Treatment.focus)) +
+  geom_point() + 
+  geom_smooth(method="gam", formula=y~s(x,k=9), method.args = list(family=binomial(link="logit")))
 
@@
   geom_hline(yintercept = 0, linetype="dotted")
+
+## PLOT IN A REACTION NORM STYLE
+ind.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
+  geom_line() +
+  geom_point(shape=21, size=4) +
+  geom_hline(yintercept=0, linetype="dotted")
+
+gall_mean_GxE <- gall_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  summarise_at(vars(gall_survival, gall_individuals), funs(mean))
+gall_mean_GxE
+
+gall_rel_fit_GxE <- c()
+for(i in 1:dim(gall_agg)[1]){
+  gall_rel_fit_GxE[i] <- gall_agg$gall_survival[i]/filter(gall_mean_GxE,
+                                                          Treatment.focus==gall_agg$Treatment.focus[i],
+                                                          Genotype==gall_agg$Genotype[i])$gall_survival
+}
+gall_agg$rel_fit_GxE <- gall_rel_fit_GxE
+
+gall_rel_fit_GxE.lm <- lm(rel_fit_GxE ~ c.gall_individuals + c.gall_individuals:Genotype + c.gall_individuals:Treatment.focus + c.gall_individuals:Treatment.focus:Genotype, data = gall_agg, contrast = list(Genotype="contr.sum",Treatment.focus="contr.sum"))
+summary(gall_rel_fit_GxE.lm)
+anova(gall_rel_fit_GxE.lm)
+anova_stats(gall_rel_fit_GxE.lm)
+
+## visual checks of regression model
+visreg(gall_rel_fit_GxE.lm) # confirms that relativizing fitness across genotypes and treatments worked
+visreg(gall_rel_fit_GxE.lm, xvar="c.gall_individuals")
+visreg(gall_rel_fit_GxE.lm, xvar="c.gall_individuals", by="Genotype")
+visreg(gall_rel_fit_GxE.lm, xvar="c.gall_individuals", by="Treatment.focus")
+```
+
+```{r}
+ind_models <- gall_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  do(model = lm(gall_survival ~ I(gall_individuals-mean(gall_individuals)), data = .)) %>%
+  tidy(model) %>%
+  ungroup()
+
+ind_models %>%
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
+                width = 0.5, position = position_dodge(width=0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted") +
+  facet_wrap(~term, scales = "free_y")
+
+ind_models %>%
+  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
+  geom_line() +
+  geom_point(shape=21, size=4) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~term, scales = "free_y")
+```
+
+```{r}
+ind.geno <- gall_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  summarise_at(vars(gall_individuals), funs(mean))
+ind.geno
+table(gall_agg$Genotype, gall_agg$Treatment.focus)
+
+test2 <- ind.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  left_join(., ind.geno)
+
+ggplot(test2, aes(x=gall_individuals, y=estimate, fill=Genotype, size=1/std.error)) +
+  geom_point(shape=21) +
+  facet_wrap(~Treatment.focus)
+
+cor.test(test2$estimate, test2$gall_individuals)
 ```
@@
 
+ggplot(plant_agg, aes(x=c.Density_per_100_shoots, y=gall_survival, color=Treatment.focus)) +
+  geom_smooth(method = "lm", formula = y ~ x) +
+  #geom_smooth(method = "lm", formula = y ~ poly(x,2), color="red") +
+  facet_wrap(~Genotype, ncol=2)
+
+ggplot(plant_agg, aes(x=c.Density_per_100_shoots, y=gall_survival/mean(gall_survival))) +
+  geom_point() + 
+  geom_smooth(method="gam", formula=y~s(x))
+  #geom_smooth(method="lm", formula=y~poly(x,2))
+
+ggplot(plant_agg, aes(x=c.Density_per_100_shoots, y=gall_survival, color=Treatment.focus)) +
+  geom_point() + 
+  geom_smooth(method="gam", formula=y~s(x), method.args = list(family=binomial(link="logit")))
+
 density.grad_models <- plant_agg %>%
-  group_by(Treatment.focus, Genotype) %>%
-  do(model = lm(gall_survival/mean(gall_survival) ~ I(Density_per_100_shoots - mean(Density_per_100_shoots)), data = .)) %>%
+  group_by(Treatment.focus, Genotype) %>% #  
+  do(model = lm(gall_survival/mean(gall_survival) ~ I((Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots)), data = .)) %>%
   tidy(model) %>%
@@
   filter(term != "(Intercept)") %>%
-  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) + # 
   geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
@@
   geom_hline(yintercept = 0, linetype="dotted")
+
+## PLOT IN A REACTION NORM STYLE
+density.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
+  geom_line() +
+  geom_point(shape=21, size=4) +
+  geom_hline(yintercept=0, linetype="dotted")
+
+plant_mean_GxE <- plant_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  summarise_at(vars(gall_survival, Density_per_100_shoots), funs(mean))
+plant_mean_GxE
+
+plant_rel_fit_GxE <- c()
+for(i in 1:dim(plant_agg)[1]){
+  plant_rel_fit_GxE[i] <- plant_agg$gall_survival[i]/filter(plant_mean_GxE,
+                                                          Treatment.focus==plant_agg$Treatment.focus[i],
+                                                          Genotype==plant_agg$Genotype[i])$gall_survival
+}
+plant_agg$rel_fit_GxE <- plant_rel_fit_GxE
+
+plant_rel_fit_GxE.lm <- lm(rel_fit_GxE ~ c.Density_per_100_shoots + c.Density_per_100_shoots:Genotype + c.Density_per_100_shoots:Treatment.focus + c.Density_per_100_shoots:Treatment.focus:Genotype, data = plant_agg, contrast = list(Genotype="contr.sum",Treatment.focus="contr.sum"))
+summary(plant_rel_fit_GxE.lm)
+anova(plant_rel_fit_GxE.lm)
+anova_stats(plant_rel_fit_GxE.lm)
+
+## visual checks of regression model
+visreg(plant_rel_fit_GxE.lm) # confirms that relativizing fitness across genotypes and treatments worked
+visreg(plant_rel_fit_GxE.lm, xvar="c.Density_per_100_shoots")
+visreg(plant_rel_fit_GxE.lm, xvar="c.Density_per_100_shoots", by="Genotype")
+visreg(plant_rel_fit_GxE.lm, xvar="c.Density_per_100_shoots", by="Treatment.focus")
 ```
+
+```{r}
+density_models <- plant_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  do(model = lm(gall_survival ~ I(Density_per_100_shoots-mean(Density_per_100_shoots)), data = .)) %>%
+  tidy(model) %>%
+  ungroup()
+
+density_models %>%
+  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
+  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
+                width = 0.5, position = position_dodge(width=0.8)) +
+  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
+  geom_hline(yintercept = 0, linetype="dotted") +
+  facet_wrap(~term, scales = "free_y")
+
+density_models %>%
+  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
+  geom_line() +
+  geom_point(shape=21, size=4) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~term, scales = "free_y")
+```
+
+```{r}
+density.geno <- plant_agg %>%
+  group_by(Treatment.focus, Genotype) %>%
+  summarise_at(vars(Density_per_100_shoots), funs(mean))
+density.geno
+table(plant_agg$Genotype, plant_agg$Treatment.focus)
+
+test3 <- density.grad_models %>%
+  filter(term != "(Intercept)") %>%
+  left_join(., density.geno)
+
+ggplot(test3, aes(x=Density_per_100_shoots, y=estimate, fill=Genotype, size=1/std.error)) +
+  geom_point(shape=21) +
+  facet_wrap(~Treatment.focus)
+
+cor.test(test3$estimate, test3$Density_per_100_shoots)
+```
+
+### old but will likely use much of this
+
+Analyze separate models for absolute fitness as a function of gall size for each treatment and genotype combination.
 

### 2018-04-14 McPeek_perspective.R
preliminary tests of applying McPeek perspective from Fig. 3.13 in his "Evolutionary Community Ecology" book to my data.

@@ -1,0 +1,157 @@
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+library(tidyverse)
+library(cowplot) # pretty default ggplots
+library(broom) # for tidying multiple linear models
+library(mgcv) # generalized additive models
+library(gsg) # calculating selection gradients
+library(visreg)
+library(viridis)
+
+## LOAD & MANAGE DATASET ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  # convert appropriate variables to characters instead of integers
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) 
+
+## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
+control_df <- gall_selection.df %>%
+  filter(Treatment.focus == "Control") %>%
+  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
+         c.gall_individuals = gall_individuals - mean(gall_individuals),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+
+treatment_df <- gall_selection.df %>%
+  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
+  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
+         c.gall_individuals = gall_individuals - mean(gall_individuals),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+
+
+## SUMMARIZE DATA AT TREE-LEVEL
+
+## CONTROL PLANTS
+control_tree <- control_df %>%
+  group_by(Genotype, Plant_Position) %>%
[…]

### 2018-04-16 McPeek_perspective.R
incorporating gall individuals into McPeek analysis.

@@ -1,9 +1,9 @@
 ## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
 library(tidyverse)
 library(cowplot) # pretty default ggplots
-library(broom) # for tidying multiple linear models
-library(mgcv) # generalized additive models
-library(gsg) # calculating selection gradients
+#library(broom) # for tidying multiple linear models
+#library(mgcv) # generalized additive models
+#library(gsg) # calculating selection gradients
 library(visreg)
 library(viridis)
 
@@ -23,27 +23,173 @@ gall_selection.df <- read_csv("gall_selection_data.csv") %>%
 
 ## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
 control_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Control") %>%
-  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  filter(Treatment.focus == "Control")
 
 treatment_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
-  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  filter(Treatment.focus == "Ectoparasitoid exclusion") 
 
-
-## SUMMARIZE DATA AT TREE-LEVEL
-
-## CONTROL PLANTS
-control_tree <- control_df %>%
-  group_by(Genotype, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_survival), funs(mean, n())) %>%
+# summarize each data set at tree-level
+all_tree <- gall_selection.df %>%
+  # summarise first at gall level
+  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean)) %>%
+  
+  # then summarise at the plant level
[…]

### 2018-05-02 McPeek_perspective.R
finding the best statistical approach

@@ -7,6 +7,9 @@ library(cowplot) # pretty default ggplots
 library(visreg)
 library(viridis)
 
+mean_log <- function(x) mean(log(x))
+var_log <- function(x) var(log(x))
+
 ## LOAD & MANAGE DATASET ----
 
 gall_selection.df <- read_csv("gall_selection_data.csv") %>%
@@ -36,7 +39,7 @@ all_tree <- gall_selection.df %>%
   
   # then summarise at the plant level
   group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, n())) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, mean_log, var_log, n())) %>%
   ungroup() %>%
   select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
   mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
@@ -50,7 +53,7 @@ control_tree <- control_df %>%
   
   # then summarise at the plant level
   group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, n())) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, n())) %>%
   ungroup() %>%
   select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
   mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
@@ -64,12 +67,32 @@ treatment_tree <- treatment_df %>%
   
   # then summarise at the plant level
   group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, n())) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, n())) %>%
   ungroup() %>%
   select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
[…]

### 2018-05-02 final_analysis.R

@@ -1,0 +1,274 @@
+
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+library(tidyverse)
+library(cowplot) # pretty default ggplots
+#library(broom) # for tidying multiple linear models
+#library(mgcv) # generalized additive models
+#library(gsg) # calculating selection gradients
+library(lme4)
+library(visreg)
+library(viridis)
+
+overdisp_fun <- function(model) {
+  ## number of variance parameters in 
+  ##   an n-by-n variance-covariance matrix
+  vpars <- function(m) {
+    nrow(m)*(nrow(m)+1)/2
+  }
+  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
+  rdf <- nrow(model.frame(model))-model.df
+  rp <- residuals(model,type="pearson")
+  Pearson.chisq <- sum(rp^2)
+  prat <- Pearson.chisq/rdf
+  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
+  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
+}
+
+## LOAD & MANAGE DATASET ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  # convert appropriate variables to characters instead of integers
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) 
+
+# summarize at gall-level for gall individuals
+all_gall <- gall_selection.df %>%
+  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise(gall_individuals = mean(gall_individuals)) %>%
+  group_by(Genotype, Treatment.focus, Plant_Position) %>%
+  summarise(gall_sample_size = n(),
+            gall_survival_mean.gall.level = mean(gall_survival), 
+            gall_individuals_mean = mean(gall_individuals),
[…]

### 2018-05-02 McPeek_perspective.R
updates to McPeek perspective

@@ -80,51 +80,106 @@ treatment_tree <- treatment_df %>%
 #  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
 #         c.Density_per_100_shoots_mean = Density_per_100_shoots_mean - mean(Density_per_100_shoots_mean))
 
+#### EXAMINE CORRELATIONS ----
+
+## gall size vs. individuals
+size.ind.corr.lm <- lm(c.gall_individuals_mean ~ c.Gall_Height_mm_mean*Treatment.focus, data = all_tree, contrasts=list(Treatment.focus="contr.sum"))
+summary(size.ind.corr.lm)
+visreg(size.ind.corr.lm, xvar="c.Gall_Height_mm_mean", by="Treatment.focus")
+
+## gall size vs. density
+size.dens.corr.lm <- lm(c.Density_per_100_shoots_mean ~ c.Gall_Height_mm_mean*Treatment.focus, data = all_tree, contrasts=list(Treatment.focus="contr.sum"))
+summary(size.dens.corr.lm)
+visreg(size.dens.corr.lm, xvar="c.Gall_Height_mm_mean", by="Treatment.focus")
+
+## gall individuals vs. density
+ind.dens.corr.lm <- lm(c.Density_per_100_shoots_mean ~ c.gall_individuals_mean*Treatment.focus, data = all_tree, contrasts=list(Treatment.focus="contr.sum"))
+summary(ind.dens.corr.lm)
+visreg(ind.dens.corr.lm, xvar="c.gall_individuals_mean", by="Treatment.focus")
+
+
 #### CONTROL - ECO-EVO FITNESS LANDSCAPE ANALYSES ----
 
-## Summary: In the complex food web, trait (evo) gradient is much more important than the 
-## abundance (eco) gradient in shaping the fitness landscape.
+## Summary: In the complex food web, trait (evo) gradient is much more important than either 
+## abundance (eco) gradient in shaping the fitness landscape. There are no statistical interactions
+## among these different gradients. Note that removing the one high density outlier permits tests
+## of statistical interactions since it greatly reduces multicollinearity. Including or excluding it though
+## does not change the qualitative conclusions
 
 # analysis
[…]

### 2018-05-02 supp_mat_complexity_selection.Rmd

--- 2018-04-09 supp_mat_complexity_selection.Rmd
@@
 ```{r FUNCTIONS}
+gamm.model <- function(formula, data) {
+  gamm4(formula, data, 
+        random = ~(1|Genotype/Plant_Position/Gall_Number),
+        family = binomial(link = logit))
+}
+
 gam.plot <- function(gam.model, ...) {
@@
 ## CONTROL PLANTS ----
-gam_red.control <- gam(gall_survival ~
+
+## Gall Height
+gam_red.control_size <- gam(gall_survival ~
                              s(c.Gall_Height_mm) + 
-                         s(c.gall_individuals, k=9) +
-                         s(c.Density_per_100_shoots),
+                             c.gall_individuals +
+                             c.Density_per_100_shoots,
                            data = control_df, family = binomial(link = "logit"))
@@
 
+## Gall individuals
+control_df_gall.level <- control_df %>%
+  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise(gall_survival_mean = mean(gall_survival),
+            gall_individuals = mean(gall_individuals),                 # note that there is no variance, it is the actual value
+            Gall_Height_mm_mean = mean(Gall_Height_mm),
+            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
+  ungroup() %>%
+  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
+         c.gall_individuals = gall_individuals - mean(gall_individuals),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
+
+gam_red.control_indiv <- gam(gall_survival_mean ~
+                              c.Gall_Height_mm_mean + 
+                              s(c.gall_individuals, k=9) +
+                              c.Density_per_100_shoots,
+                             data = control_df_gall.level, family = binomial(link = "logit")) # we didn't include weights because this would be correlated with the number of individuals per gall
+summary(gam_red.control_indiv)
+
+gam.plot(gam_red.control_indiv)
+gam.plot(gamm_red.control$gam)
+
+## Gall density
+control_df_plant.level <- control_df_gall.level %>%
+  group_by(Treatment.focus, Plant_Position) %>%
+  summarise(gall_survival_mean = mean(gall_survival_mean),
+            gall_sample_size = n(),
+            gall_individuals_mean = mean(gall_individuals),                 
+            Gall_Height_mm_mean = mean(Gall_Height_mm_mean),
+            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
+  ungroup() %>%
+  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
+         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
+
+gam_red.control_density <- gam(gall_survival_mean ~
+                                c.Gall_Height_mm_mean + 
+                                c.gall_individuals_mean +
+                                s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
+                             data = control_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
+summary(gam_red.control_density)
+
+gam.plot(gam_red.control_density)
+gam.plot(gamm_red.control$gam)
+
 ## TREATMENT PLANTS ----
-gam_red.treatment <- gam(gall_survival ~
+
+## Gall Height
+gam_red.treatment_size <- gam(gall_survival ~
                          s(c.Gall_Height_mm) + 
-                         s(c.gall_individuals, k=9) +
-                         s(c.Density_per_100_shoots),
+                         c.gall_individuals +
+                         c.Density_per_100_shoots,
                        data = treatment_df, family = binomial(link = "logit"))
@@
 gam.plot(gam_red.treatment)
+gam.plot(gamm_red.treatment$gam)
+
+## Gall individuals
+treatment_df_gall.level <- treatment_df %>%
+  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise(gall_survival_mean = mean(gall_survival),
+            gall_individuals = mean(gall_individuals),                 # note that there is no variance, it is the actual value
+            Gall_Height_mm_mean = mean(Gall_Height_mm),
+            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
+  ungroup() %>%
+  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
+         c.gall_individuals = gall_individuals - mean(gall_individuals),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
+
+gam_red.treatment_indiv <- gam(gall_survival_mean ~
+                              c.Gall_Height_mm_mean + 
+                              s(c.gall_individuals, k=9) +
+                              c.Density_per_100_shoots,
+                             data = treatment_df_gall.level, family = binomial(link = "logit"))
+summary(gam_red.treatment_indiv)
+
+gam.plot(gam_red.treatment_indiv)
+gam.plot(gamm_red.treatment$gam)
+
+## Gall density
+treatment_df_plant.level <- treatment_df_gall.level %>%
+  group_by(Treatment.focus, Plant_Position) %>%
+  summarise(gall_survival_mean = mean(gall_survival_mean),
+            gall_sample_size = n(),
+            gall_individuals_mean = mean(gall_individuals),                 
+            Gall_Height_mm_mean = mean(Gall_Height_mm_mean),
+            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
+  ungroup() %>%
+  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
+         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
+
+gam_red.treatment_density <- gam(gall_survival_mean ~
+                                c.Gall_Height_mm_mean + 
+                                c.gall_individuals_mean +
+                                s(c.Density_per_100_shoots),
+                             data = treatment_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
+summary(gam_red.treatment_density)
+
+gam.plot(gam_red.treatment_density)
 gam.plot(gamm_red.treatment$gam)
@@
 ```
-
-```{r}
-size_models <- gall_selection.df %>%
-  group_by(Treatment.focus, Genotype) %>%
-  do(model = lm(gall_survival ~ Gall_Height_mm, data = .)) %>%
-  tidy(model) %>%
-  ungroup()
-
-size_models %>%
-  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
-  geom_bar(stat="identity", position = "dodge") +
-  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
-                width = 0.5, position = position_dodge(width = 0.8)) +
-  facet_wrap(~term, scales = "free_y")
-```
-
-```{r}
-size.grad_models <- gall_selection.df %>%
-  group_by(Treatment.focus, Genotype) %>%
-  do(model = lm(gall_survival/mean(gall_survival) ~ I(Gall_Height_mm - mean(Gall_Height_mm)), data = .)) %>%
-  tidy(model) %>%
-  ungroup()
-size.grad_models
-
-size.grad_models %>%
-  filter(term != "(Intercept)") %>%
-  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
-  geom_bar(stat="identity", position = "dodge") +
-  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
-                width = 0.5, position = position_dodge(width = 0.8))
-
-size.grad_models %>%
-  filter(term != "(Intercept)") %>%
-  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
-  geom_line() +
-  geom_point(shape=21, position = "dodge", size=4) +
-  geom_hline(yintercept=0, linetype="dotted")
-
-summary(lm(estimate ~ Treatment.focus, data = filter(size.grad_models, term != "(Intercept)")))
-```

### 2018-05-02 GxE_effects.Rmd
exploring GxE effects on selection gradients.

---
title: "GxE Effects..."
output: html_notebook
---

Could be worth exploring....

## What is the relative importance of plant genotype vs. food-web complexity in altering selection gradients?

Gall Size
```{r}
# RELATIONSHIP BETWEEN ABSOLUTE FITNESS AND GALL SIZE ACROSS GENOTYPES AND TREATMENTS
ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
  geom_point(shape=1) +
  geom_smooth(method = "lm", formula = y ~ x) +
  #geom_smooth(method = "lm", formula = y ~ poly(x,2), color="red") +
  facet_wrap(~Genotype, ncol=2)

ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival/mean(gall_survival))) +
  geom_point() + 
  geom_smooth(method="lm", formula=y~poly(x,2))

ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
  geom_point() + 
  geom_smooth(method="gam", formula=y~s(x), method.args = list(family=binomial(link="logit")))

ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival)) +
  geom_point() + 
  geom_smooth(method="gam", formula=y~s(x), method.args = list(family=binomial(link="logit"))) +
  facet_wrap(~Genotype)

ggplot(gall_selection.df, aes(x=c.Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
  geom_point() + 
  geom_smooth(method="lm", formula=y~poly(x,2)) +
  facet_wrap(~Genotype)

## ESTIMATE DIRECTIONAL SELECTION GRADIENTS ON GALL SIZE FOR EACH PLANT GENOTYPE AND FOOD-WEB TREATMENT
size.grad_models <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival/mean(gall_survival) ~ I((Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm)), data = .)) %>%
  tidy(model) %>%
  ungroup()
size.grad_models

## PLOT VARIATION IN SELECTION GRADIENTS FOR GALL SIZE AMONG PLANT GENOTYPES AND FOOD-WEB TREATMENTS
size.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8)) +
  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
  geom_hline(yintercept = 0, linetype="dotted")

## PLOT IN A REACTION NORM STYLE
size.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, size=4) +
  geom_hline(yintercept=0, linetype="dotted")

mean_GxE <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  summarise_at(vars(gall_survival, Gall_Height_mm), funs(mean))
mean_GxE

rel_fit_GxE <- c()
c.GxE.Gall_Height_mm <- c()
for(i in 1:dim(gall_selection.df)[1]){
  rel_fit_GxE[i] <- gall_selection.df$gall_survival[i]/filter(mean_GxE,
                                                          Treatment.focus==gall_selection.df$Treatment.focus[i],
                                                          Genotype==gall_selection.df$Genotype[i])$gall_survival
 # c.GxE.Gall_Height_mm <- gall_selection.df$Gall_Height_mm[i] - filter(mean_GxE,
#                                                          Treatment.focus==gall_selection.df$Treatment.focus[i],
#                                                          Genotype==gall_selection.df$Genotype[i])$Gall_Height_mm
}
gall_selection.df$rel_fit_GxE <- rel_fit_GxE
#gall_selection.df$c.GxE.Gall_Height_mm <- c.GxE.Gall_Height_mm

gall_selection.df$c.Gall_Height_mm <- gall_selection.df$Gall_Height_mm - mean(gall_selection.df$Gall_Height_mm)

library(sjstats)
rel_fit_GxE.lm <- lm(rel_fit_GxE ~ c.Gall_Height_mm + c.Gall_Height_mm:Genotype + c.Gall_Height_mm:Treatment.focus + c.Gall_Height_mm:Treatment.focus:Genotype, data = gall_selection.df, contrast = list(Genotype="contr.sum",Treatment.focus="contr.sum"))
summary(rel_fit_GxE.lm)
anova(rel_fit_GxE.lm)
anova_stats(rel_fit_GxE.lm)

## visual checks of regression model
visreg(rel_fit_GxE.lm) # confirms that relativizing fitness across genotypes and treatments worked
visreg(rel_fit_GxE.lm, xvar="c.Gall_Height_mm")
visreg(rel_fit_GxE.lm, xvar="c.Gall_Height_mm", by="Genotype")
visreg(rel_fit_GxE.lm, xvar="c.Gall_Height_mm", by="Treatment.focus")
```

```{r}
size_models <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival ~ I(Gall_Height_mm-mean(Gall_Height_mm)), data = .)) %>%
  tidy(model) %>%
  ungroup()

size_models %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width=0.8)) +
  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
  geom_hline(yintercept = 0, linetype="dotted") +
  facet_wrap(~term, scales = "free_y")

size_models %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, size=4) +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~term, scales = "free_y")
```

```{r}

size.geno <- gall_selection.df %>%
  group_by(Treatment.focus, Genotype) %>%
  summarise_at(vars(Gall_Height_mm), funs(mean))
size.geno
table(gall_selection.df$Genotype, gall_selection.df$Treatment.focus)

test <- size.grad_models %>%
  filter(term != "(Intercept)") %>%
  left_join(., size.geno)

ggplot(test, aes(x=Gall_Height_mm, y=estimate, fill=Genotype, size=1/std.error)) +
  geom_point(shape=21) +
  facet_wrap(~Treatment.focus)

cor.test(test$estimate, test$Gall_Height_mm)
```

Number of individuals per gall

```{r}
gall_agg <- gall_selection.df %>%
  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
  summarise_at(vars(gall_individuals, gall_survival), funs(mean)) %>%
  ungroup() %>%
  mutate(c.gall_individuals = gall_individuals - mean(gall_individuals))

ggplot(gall_agg, aes(x=c.gall_individuals, y=gall_survival/mean(gall_survival))) +
  geom_point() + 
  geom_smooth(method="lm", formula=y~poly(x,2))

ggplot(gall_agg, aes(x=c.gall_individuals, y=gall_survival, color=Treatment.focus)) +
  geom_smooth(method = "lm", formula = y ~ x) +
  #geom_smooth(method = "lm", formula = y ~ poly(x,2), color="red") +
  facet_wrap(~Genotype, ncol=2)

ggplot(gall_agg, aes(x=c.gall_individuals, y=gall_survival, color=Treatment.focus)) +
  geom_point() + 
  geom_smooth(method="gam", formula=y~s(x,k=9), method.args = list(family=binomial(link="logit")))

ind.grad_models <- gall_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival/mean(gall_survival) ~ I(gall_individuals - mean(gall_individuals)), data = .)) %>%
  tidy(model) %>%
  ungroup()
ind.grad_models

ind.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8)) +
  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
  geom_hline(yintercept = 0, linetype="dotted")

## PLOT IN A REACTION NORM STYLE
ind.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, size=4) +
  geom_hline(yintercept=0, linetype="dotted")

gall_mean_GxE <- gall_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  summarise_at(vars(gall_survival, gall_individuals), funs(mean))
gall_mean_GxE

gall_rel_fit_GxE <- c()
for(i in 1:dim(gall_agg)[1]){
  gall_rel_fit_GxE[i] <- gall_agg$gall_survival[i]/filter(gall_mean_GxE,
                                                          Treatment.focus==gall_agg$Treatment.focus[i],
                                                          Genotype==gall_agg$Genotype[i])$gall_survival
}
gall_agg$rel_fit_GxE <- gall_rel_fit_GxE

gall_rel_fit_GxE.lm <- lm(rel_fit_GxE ~ c.gall_individuals + c.gall_individuals:Genotype + c.gall_individuals:Treatment.focus + c.gall_individuals:Treatment.focus:Genotype, data = gall_agg, contrast = list(Genotype="contr.sum",Treatment.focus="contr.sum"))
summary(gall_rel_fit_GxE.lm)
anova(gall_rel_fit_GxE.lm)
anova_stats(gall_rel_fit_GxE.lm)

## visual checks of regression model
visreg(gall_rel_fit_GxE.lm) # confirms that relativizing fitness across genotypes and treatments worked
visreg(gall_rel_fit_GxE.lm, xvar="c.gall_individuals")
visreg(gall_rel_fit_GxE.lm, xvar="c.gall_individuals", by="Genotype")
visreg(gall_rel_fit_GxE.lm, xvar="c.gall_individuals", by="Treatment.focus")
```

```{r}
ind_models <- gall_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival ~ I(gall_individuals-mean(gall_individuals)), data = .)) %>%
  tidy(model) %>%
  ungroup()

ind_models %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width=0.8)) +
  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
  geom_hline(yintercept = 0, linetype="dotted") +
  facet_wrap(~term, scales = "free_y")

ind_models %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, size=4) +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~term, scales = "free_y")
```

```{r}
ind.geno <- gall_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  summarise_at(vars(gall_individuals), funs(mean))
ind.geno
table(gall_agg$Genotype, gall_agg$Treatment.focus)

test2 <- ind.grad_models %>%
  filter(term != "(Intercept)") %>%
  left_join(., ind.geno)

ggplot(test2, aes(x=gall_individuals, y=estimate, fill=Genotype, size=1/std.error)) +
  geom_point(shape=21) +
  facet_wrap(~Treatment.focus)

cor.test(test2$estimate, test2$gall_individuals)
```

```{r}
plant_agg <- gall_selection.df %>%
  group_by(Genotype, Treatment.focus, Plant_Position) %>%
  summarise_at(vars(Density_per_100_shoots, gall_survival), funs(mean)) %>%
  ungroup() %>%
  mutate(c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))

ggplot(plant_agg, aes(x=c.Density_per_100_shoots, y=gall_survival, color=Treatment.focus)) +
  geom_smooth(method = "lm", formula = y ~ x) +
  #geom_smooth(method = "lm", formula = y ~ poly(x,2), color="red") +
  facet_wrap(~Genotype, ncol=2)

ggplot(plant_agg, aes(x=c.Density_per_100_shoots, y=gall_survival/mean(gall_survival))) +
  geom_point() + 
  geom_smooth(method="gam", formula=y~s(x))
  #geom_smooth(method="lm", formula=y~poly(x,2))

ggplot(plant_agg, aes(x=c.Density_per_100_shoots, y=gall_survival, color=Treatment.focus)) +
  geom_point() + 
  geom_smooth(method="gam", formula=y~s(x), method.args = list(family=binomial(link="logit")))

density.grad_models <- plant_agg %>%
  group_by(Treatment.focus, Genotype) %>% #  
  do(model = lm(gall_survival/mean(gall_survival) ~ I((Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots)), data = .)) %>%
  tidy(model) %>%
  ungroup()
density.grad_models

density.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) + # 
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width = 0.8)) +
  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
  geom_hline(yintercept = 0, linetype="dotted")

## PLOT IN A REACTION NORM STYLE
density.grad_models %>%
  filter(term != "(Intercept)") %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, size=4) +
  geom_hline(yintercept=0, linetype="dotted")

plant_mean_GxE <- plant_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  summarise_at(vars(gall_survival, Density_per_100_shoots), funs(mean))
plant_mean_GxE

plant_rel_fit_GxE <- c()
for(i in 1:dim(plant_agg)[1]){
  plant_rel_fit_GxE[i] <- plant_agg$gall_survival[i]/filter(plant_mean_GxE,
                                                          Treatment.focus==plant_agg$Treatment.focus[i],
                                                          Genotype==plant_agg$Genotype[i])$gall_survival
}
plant_agg$rel_fit_GxE <- plant_rel_fit_GxE

plant_rel_fit_GxE.lm <- lm(rel_fit_GxE ~ c.Density_per_100_shoots + c.Density_per_100_shoots:Genotype + c.Density_per_100_shoots:Treatment.focus + c.Density_per_100_shoots:Treatment.focus:Genotype, data = plant_agg, contrast = list(Genotype="contr.sum",Treatment.focus="contr.sum"))
summary(plant_rel_fit_GxE.lm)
anova(plant_rel_fit_GxE.lm)
anova_stats(plant_rel_fit_GxE.lm)

## visual checks of regression model
visreg(plant_rel_fit_GxE.lm) # confirms that relativizing fitness across genotypes and treatments worked
visreg(plant_rel_fit_GxE.lm, xvar="c.Density_per_100_shoots")
visreg(plant_rel_fit_GxE.lm, xvar="c.Density_per_100_shoots", by="Genotype")
visreg(plant_rel_fit_GxE.lm, xvar="c.Density_per_100_shoots", by="Treatment.focus")
```

```{r}
density_models <- plant_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  do(model = lm(gall_survival ~ I(Density_per_100_shoots-mean(Density_per_100_shoots)), data = .)) %>%
  tidy(model) %>%
  ungroup()

density_models %>%
  ggplot(., aes(x=Genotype, y=estimate, fill=Treatment.focus)) +
  geom_errorbar(aes(ymax = estimate + std.error, ymin = estimate - std.error), #, color=Treatment.focus
                width = 0.5, position = position_dodge(width=0.8)) +
  geom_point(shape=21, size = 2, position = position_dodge(width=0.8)) +
  geom_hline(yintercept = 0, linetype="dotted") +
  facet_wrap(~term, scales = "free_y")

density_models %>%
  ggplot(., aes(x=Treatment.focus, y=estimate, fill=Genotype, group=Genotype)) +
  geom_line() +
  geom_point(shape=21, size=4) +
  geom_hline(yintercept=0, linetype="dotted") +
  facet_wrap(~term, scales = "free_y")
```

```{r}
density.geno <- plant_agg %>%
  group_by(Treatment.focus, Genotype) %>%
  summarise_at(vars(Density_per_100_shoots), funs(mean))
density.geno
table(plant_agg$Genotype, plant_agg$Treatment.focus)

test3 <- density.grad_models %>%
  filter(term != "(Intercept)") %>%
  left_join(., density.geno)

ggplot(test3, aes(x=Density_per_100_shoots, y=estimate, fill=Genotype, size=1/std.error)) +
  geom_point(shape=21) +
  facet_wrap(~Treatment.focus)

cor.test(test3$estimate, test3$Density_per_100_shoots)
```

### old but will likely use much of this

Analyze separate models for absolute fitness as a function of gall size for each treatment and genotype combination.

```{r}
gall_selection.df$c.gall_individuals <- with(gall_selection.df, gall_individuals - mean(gall_individuals))

ind_GxE_lms <- lm(gall_survival ~ c.gall_individuals*Genotype*Treatment.focus, data = gall_selection.df, contrast = list(Genotype = "contr.sum"))
summary(ind_GxE_lms)
anova(ind_GxE_lms)
```

```{r}

agg.ind_GxE_lms <- lm(gall_survival ~ (c.gall_individuals + Genotype + Treatment.focus)^2, data = gall_agg, contrast = list(Genotype = "contr.sum"))
summary(agg.ind_GxE_lms)
anova(agg.ind_GxE_lms)
visreg(agg.ind_GxE_lms, xvar="c.gall_individuals", by="Treatment.focus")
visreg(agg.ind_GxE_lms, xvar="c.gall_individuals", by="Genotype")
```

```{r}
gall_selection.df$c.Density_per_100_shoots <- with(gall_selection.df, Density_per_100_shoots - mean(Density_per_100_shoots))

density_GxE_lms <- lm(gall_survival ~ (c.Density_per_100_shoots + Genotype + Treatment.focus)^2, data = gall_selection.df, contrast = list(Genotype = "contr.sum"))
summary(density_GxE_lms)
anova(density_GxE_lms)
```

```{r}
plant_agg <- gall_selection.df %>%
  group_by(Genotype, Treatment.focus, Plant_Position) %>%
  summarise_at(vars(Density_per_100_shoots, gall_survival), funs(mean)) %>%
  ungroup() %>%
  mutate(c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))

agg.density_GxE_lms <- lm(gall_survival ~ c.Density_per_100_shoots*Genotype*Treatment.focus, data = plant_agg, contrast = list(Genotype = "contr.sum"))
summary(agg.density_GxE_lms)
anova(agg.density_GxE_lms)
```

```{r}
multivar_GxE_lms <- lm(gall_survival ~ Genotype*Treatment.focus*c.Gall_Height_mm, data = gall_selection.df, contrast = list(Genotype = "contr.sum", Treatment.focus="contr.sum"))
summary(multivar_GxE_lms)
car::vif(multivar_GxE_lms)
anova(multivar_GxE_lms)
visreg(multivar_GxE_lms, xvar="c.Gall_Height_mm", by="Treatment.focus")
visreg(multivar_GxE_lms, xvar="c.gall_individuals", by="Treatment.focus")
visreg(multivar_GxE_lms, xvar="c.Density_per_100_shoots", by="Treatment.focus")
visreg2d(multivar_GxE_lms, xvar="c.Density_per_100_shoots", yvar="c.gall_individuals")
```

```{r Piecewise SEM}
library(lme4)
library(lmerTest)
library(piecewiseSEM)

size_geno <- lm(Gall_Height_mm ~ Genotype, gall_selection.df, contrast = list(Genotype="contr.sum")) 
summary(size_geno)
sem.model.fits(size_geno)
anova(size_geno)

ind_geno <- lm(gall_individuals ~ Genotype, gall_selection.df, contrast = list(Genotype="contr.sum"))
summary(ind_geno)
sem.model.fits(ind_geno)
anova(ind_geno)

density_geno <- lmer(log(Density_per_100_shoots+1) ~ Genotype + (1|Plant_Position/Gall_Number/Gall_ID), gall_selection.df, contrast = list(Genotype="contr.sum"))
summary(density_geno)
sem.model.fits(density_geno)
anova(density_geno)

selection_grads <- lm(gall_survival ~ Treatment.focus*(Gall_Height_mm+gall_individuals+Density_per_100_shoots)^2, gall_selection.df)
sem.model.fits(selection_grads)

model.list <- list(size_geno, ind_geno, density_geno, selection_grads)

sem.fit(model.list, gall_selection.df, corr.errors = c("Gall_Height_mm~~gall_individuals","Gall_Height_mm~~Density_per_100_shoots","gall_individuals~~Density_per_100_shoots"))
```

```{r}
gall_selection.df %>%
  ggplot(., aes(x=c.Gall_Height_mm, y=gall_survival, color=Genotype)) +
  geom_smooth(method="lm") +
  facet_wrap(~Treatment.focus)

gall_agg %>%
  ggplot(., aes(x=c.gall_individuals, y=gall_survival, color=Genotype)) +
  geom_smooth(method="lm") +
  facet_wrap(~Treatment.focus)

plant_agg %>%
  ggplot(., aes(x=c.Density_per_100_shoots, y=gall_survival, color=Genotype)) +
  geom_smooth(method="lm") +
  facet_wrap(~Treatment.focus)
```

### 2018-05-02 McPeek_perspective.R
need to fix...

@@ -7,6 +7,9 @@ library(cowplot) # pretty default ggplots
 library(visreg)
 library(viridis)
 
+mean_log <- function(x) mean(log(x))
+var_log <- function(x) var(log(x))
+
 ## LOAD & MANAGE DATASET ----
 
 gall_selection.df <- read_csv("gall_selection_data.csv") %>%
@@ -36,7 +39,7 @@ all_tree <- gall_selection.df %>%
   
   # then summarise at the plant level
   group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, n())) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, mean_log, var_log, n())) %>%
   ungroup() %>%
   select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
   mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
@@ -50,7 +53,7 @@ control_tree <- control_df %>%
   
   # then summarise at the plant level
   group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, n())) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, n())) %>%
   ungroup() %>%
   select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
   mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
@@ -64,12 +67,179 @@ treatment_tree <- treatment_df %>%
   
   # then summarise at the plant level
   group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, n())) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, n())) %>%
   ungroup() %>%
   select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
[…]

### 2018-05-02 supp_mat_complexity_selection.Rmd
playing around with adjust smooth to get sensical curves.

@@
                            data = control_df, family = binomial(link = "logit"))
-summary(gam_red.control)
+summary(gam_red.control_size)
 
-gam.plot(gam_red.control)
+gam.plot(gam_red.control_size)
 gam.plot(gamm_red.control$gam)
@@
 
+test.control_df_plant.level <- control_df %>%
+  group_by(Treatment.focus, Plant_Position) %>%
+  summarise(gall_survival_mean = mean(gall_survival),
+            gall_sample_size = n(),
+            gall_individuals_mean = mean(gall_individuals),                 
+            Gall_Height_mm_mean = mean(Gall_Height_mm),
+            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
+  ungroup() %>%
+  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
+         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+
 gam_red.control_density <- gam(gall_survival_mean ~
-                                c.Gall_Height_mm_mean + 
-                                c.gall_individuals_mean +
+                                s(c.Gall_Height_mm_mean) + 
+                                s(c.gall_individuals_mean, k=3) +
                                 s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
-                             data = control_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
+                             data = control_df_plant.level,
+                             family = binomial, #(link = "logit"), 
+                             weights = gall_sample_size) # weighting appears to alter the results...
 summary(gam_red.control_density)
+plot(gam_red.control_density, pages=1, residuals=TRUE)
+gam.check(gam_red.control_density)
+
+plot(lambda, gcvscore, type = "l") # or
+plot(log(lambda), gcvscore, type = "l")
 
@@
 gam.plot(gamm_red.control$gam)
+
+set.seed(1) 
+dat <- gamSim(1,n=400,scale=2)
+
+## fit a GAM with quite low `k'
+b<-gam(y~s(x0,k=6)+s(x1,k=6)+s(x2,k=6)+s(x3,k=6),data=dat)
+plot(b,pages=1,residuals=TRUE) ## hint of a problem in s(x2)
+gam.check(b)
 
@@
 gam_red.treatment_density <- gam(gall_survival_mean ~
-                                c.Gall_Height_mm_mean + 
-                                c.gall_individuals_mean +
+                                s(c.Gall_Height_mm_mean) + 
+                                s(c.gall_individuals_mean) +
                                 s(c.Density_per_100_shoots),
-                             data = treatment_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
+                             data = treatment_df_plant.level, family = binomial(link = "logit"))#, weights = gall_sample_size) # weighting appears to alter the results...
 summary(gam_red.treatment_density)

### 2018-05-03 supp_mat_complexity_selection.Rmd
created template for 2D fitness landscape plots.

--- 2018-05-02 supp_mat_complexity_selection.Rmd
@@
 library(mgcv) # generalized additive models
+library(gamm4) # generalized additive mixed-models
 library(gsg) # calculating selection gradients
 library(visreg)
+library(viridis) # for color palette
 
@@
   gamm4(formula, data, 
-        random = ~(1|Genotype/Plant_Position/Gall_Number),
+        random = ~(1|Plant_Position/Gall_Number), # Genotype/
         family = binomial(link = logit))
@@
                 standardized = T)
+}
+
+insect_FL <- function(mod, phenotype, covariates = NULL) {
+  fitness.landscape(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32,
+                    PI.method = 'boot.para',
+                    refit.smooth = F,
+                    PI.interval = c(0.025,0.975),
+                    plt.density = 100)
+}
+
+get_insect_FL.df <- function(FL){
+  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
+    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
+}
+
+ggplot_uniFL <- function(FL.df) {
+  ggplot(FL.df, aes(x = Var1, y = mean_fitness)) +
+    geom_line() + 
+    geom_ribbon(aes(ymin = lower_2.5, ymax = upper_97.5), alpha = 0.5)
 }
@@
                              s(c.Gall_Height_mm) + 
-                             c.gall_individuals +
-                             c.Density_per_100_shoots,
+                             s(c.gall_individuals, k=9) +
+                             s(c.Density_per_100_shoots),
                            data = control_df, family = binomial(link = "logit"))
-summary(gam_red.control)
+summary(gam_red.control_size)
 
-gam.plot(gam_red.control)
-gam.plot(gamm_red.control$gam)
+gam.plot(gam_red.control_size, pages=1)
+gam.plot(gamm_red.control$gam, pages=1)
 
@@
 gam_red.control_indiv <- gam(gall_survival_mean ~
-                              c.Gall_Height_mm_mean + 
+                              s(c.Gall_Height_mm_mean) + 
                               s(c.gall_individuals, k=9) +
-                              c.Density_per_100_shoots,
+                              s(c.Density_per_100_shoots),
                              data = control_df_gall.level, family = binomial(link = "logit")) # we didn't include weights because this would be correlated with the number of individuals per gall
@@
 
-gam.plot(gam_red.control_indiv)
-gam.plot(gamm_red.control$gam)
+gam.plot(gam_red.control_indiv, pages=1)
+gam.plot(gamm_red.control$gam, pages=1)
 
@@
          c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+
+#test.control_df_plant.level <- control_df %>%
+#  group_by(Treatment.focus, Plant_Position) %>%
+#  summarise(gall_survival_mean = mean(gall_survival),
+#            gall_sample_size = n(),
+#            gall_individuals_mean = mean(gall_individuals),                 
+#            Gall_Height_mm_mean = mean(Gall_Height_mm),
+#            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
+#  ungroup() %>%
+#  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
+#         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
+#         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
 
 gam_red.control_density <- gam(gall_survival_mean ~
-                                c.Gall_Height_mm_mean + 
-                                c.gall_individuals_mean +
-                                s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
-                             data = control_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
+                                s(c.Gall_Height_mm_mean) + 
+                                s(c.gall_individuals_mean, k=9) +
+                                s(c.Density_per_100_shoots, k=3),  # adjusting k value to avoid overfitting of Density   
+                             data = control_df_plant.level,
+                             family = binomial(link = "logit"), 
+                             weights = gall_sample_size) 
 summary(gam_red.control_density)
 
-gam.plot(gam_red.control_density)
-gam.plot(gamm_red.control$gam)
+gam.plot(gam_red.control_density, pages=1)
+gam.plot(gamm_red.control$gam, pages=1)
 
@@
                          s(c.Gall_Height_mm) + 
-                         c.gall_individuals +
-                         c.Density_per_100_shoots,
+                         s(c.gall_individuals, k=9) +
+                         s(c.Density_per_100_shoots),
                        data = treatment_df, family = binomial(link = "logit"))
-summary(gam_red.treatment)
+summary(gam_red.treatment_size)
 
-gam.plot(gam_red.treatment)
-gam.plot(gamm_red.treatment$gam)
+gam.plot(gam_red.treatment_size, pages=1)
+gam.plot(gamm_red.treatment$gam, pages=1)
 
@@
             Gall_Height_mm_mean = mean(Gall_Height_mm),
-            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
+            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember this is pseudo-replicated at the gall-level
   ungroup() %>%
@@
 gam_red.treatment_indiv <- gam(gall_survival_mean ~
-                              c.Gall_Height_mm_mean + 
+                              s(c.Gall_Height_mm_mean) + 
                               s(c.gall_individuals, k=9) +
-                              c.Density_per_100_shoots,
+                              s(c.Density_per_100_shoots),
                              data = treatment_df_gall.level, family = binomial(link = "logit"))
@@
 
-gam.plot(gam_red.treatment_indiv)
-gam.plot(gamm_red.treatment$gam)
+gam.plot(gam_red.treatment_indiv, pages=1)
+gam.plot(gamm_red.treatment$gam, pages=1)
 
@@
          c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
+         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
 
 gam_red.treatment_density <- gam(gall_survival_mean ~
-                                c.Gall_Height_mm_mean + 
-                                c.gall_individuals_mean +
+                                s(c.Gall_Height_mm_mean) + 
+                                s(c.gall_individuals_mean, k=9) +
                                 s(c.Density_per_100_shoots),
-                             data = treatment_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
+                             data = treatment_df_plant.level, family = binomial(link = "logit"), 
+                             weights = gall_sample_size) 
 summary(gam_red.treatment_density)
 
-gam.plot(gam_red.treatment_density)
-gam.plot(gamm_red.treatment$gam)
+gam.plot(gam_red.treatment_density, pages=1)
+gam.plot(gamm_red.treatment$gam, pages=1)
 
@@
 ## GALL SIZE ----
-sg.gam.size_control <- gradient.calc(mod = gam_red.control, 
+sg.gam.size_control <- gradient.calc(mod = gam_red.control_size, 
                                  phenotype = "c.Gall_Height_mm", 
                                  covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
-sg.gam.size_treatment <- gradient.calc(mod = gam_red.treatment, 
+sg.gam.size_treatment <- gradient.calc(mod = gam_red.treatment_size, 
                                    phenotype = "c.Gall_Height_mm", 
@@
 ## GALL INDIVIDUALS ----
-sg.gam.individuals_control <- gradient.calc(mod = gam_red.control, 
+sg.gam.individuals_control <- gradient.calc(mod = gam_red.control_indiv, 
                                         phenotype = "c.gall_individuals", 
-                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-sg.gam.individuals_treatment <- gradient.calc(mod = gam_red.treatment, 
+                                        covariates = c("c.Gall_Height_mm_mean","c.Density_per_100_shoots"))
+sg.gam.individuals_treatment <- gradient.calc(mod = gam_red.treatment_indiv, 
                                           phenotype = "c.gall_individuals", 
-                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+                                          covariates = c("c.Gall_Height_mm_mean","c.Density_per_100_shoots"))
 
 ## GALL DENSITY ----
-sg.gam.density_control <- gradient.calc(mod = gam_red.control, 
+sg.gam.density_control <- gradient.calc(mod = gam_red.control_density, 
                                     phenotype = "c.Density_per_100_shoots", 
-                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-sg.gam.density_treatment <- gradient.calc(mod = gam_red.treatment, 
+                                    covariates = c("c.gall_individuals_mean","c.Gall_Height_mm_mean"))
+sg.gam.density_treatment <- gradient.calc(mod = gam_red.treatment_density, 
                                       phenotype = "c.Density_per_100_shoots", 
-                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+                                      covariates = c("c.gall_individuals_mean","c.Gall_Height_mm_mean"))
 
@@
 ```
+
+```{r Fitness Landscapes}
+## GALL SIZE ----
+fl.size_control <- insect_FL(mod = gamm_red.control$gam, 
+                                 phenotype = "c.Gall_Height_mm", 
+                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+fl.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                   phenotype = "c.Gall_Height_mm", 
+                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+
+## GALL INDIVIDUALS ----
+fl.individuals_control <- insect_FL(mod = gamm_red.control$gam, 
+                                        phenotype = "c.gall_individuals", 
+                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+fl.individuals_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                          phenotype = "c.gall_individuals", 
+                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+
+## GALL DENSITY ----
+fl.density_control <- insect_FL(mod = gamm_red.control$gam, 
+                                    phenotype = "c.Density_per_100_shoots", 
+                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+fl.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                      phenotype = "c.Density_per_100_shoots", 
+                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+
+get_insect_FL.df(fl.size_control) %>%
+  ggplot_uniFL(.)
+
+get_insect_FL.df(fl.size_treatment) %>%
+  ggplot_uniFL(.)
+
+get_insect_FL.df(fl.individuals_control) %>%
+  ggplot_uniFL(.)
+
+get_insect_FL.df(fl.individuals_treatment) %>%
+  ggplot_uniFL(.)
+
+get_insect_FL.df(fl.density_control) %>%
+  ggplot_uniFL(.)
+
+get_insect_FL.df(fl.density_treatment) %>%
+  ggplot_uniFL(.)
+
+## Landscape
+fl.individuals.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
+                                              phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
+                                              covariates = c("c.Gall_Height_mm"))
+
+get_insect_FL.df(fl.individuals.x.density_control) %>%
+  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  geom_tile()
+
+fl.individuals.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                                phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
+                                                covariates = c("c.Gall_Height_mm"))
+get_insect_FL.df(fl.individuals.x.density_treatment) %>%
+  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  geom_tile()
+
+test <- bind_rows(mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment.focus="Simple"),
+          mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment.focus="Complex"))
+
+ggplot(test, aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  geom_raster() + 
+  facet_wrap(~Treatment.focus) +
+  scale_fill_viridis()
+```

### 2018-05-14 morgue_supp_mat.Rmd
create morgue for old ideas

--- 2018-05-03 supp_mat_complexity_selection.Rmd
@@
 ---
-title: "Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore"
-author: Matt Barbour
+title: "Morgue: Supplementary material"
 output: html_notebook
 ---
-
-Load dataset.
-This dataset is a subset that only includes larva that survive to pupation or turned into parasitoids.
-We omitted any data where larva mortality was unclear.
-This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
-```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-library(tidyverse)
-library(cowplot) # pretty default ggplots
-library(broom) # for tidying multiple linear models
-library(mgcv) # generalized additive models
-library(gamm4) # generalized additive mixed-models
-library(gsg) # calculating selection gradients
-library(visreg)
-library(viridis) # for color palette
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  # convert appropriate variables to characters instead of integers
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)))
-
-## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
-control_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Control") %>%
-  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
-
-treatment_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
-  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
-```
-
-```{r FUNCTIONS}
-gamm.model <- function(formula, data) {
-  gamm4(formula, data, 
-        random = ~(1|Plant_Position/Gall_Number), # Genotype/
-        family = binomial(link = logit))
-}
-
-gam.plot <- function(gam.model, ...) {
-  plot(gam.model, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
-}
-
-# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
-# also, using 'refit.smooth = T' also generated some very skewed distributions
-# the recipe below provided the most sensible estimates for my data
-gradient.calc <- function(mod, phenotype, covariates = NULL) {
-  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
-                refit.smooth = F, 
-                n.boot = 1000,
-                se.method = 'boot.para',
-                standardized = T)
-}
-
-insect_FL <- function(mod, phenotype, covariates = NULL) {
-  fitness.landscape(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32,
-                    PI.method = 'boot.para',
-                    refit.smooth = F,
-                    PI.interval = c(0.025,0.975),
-                    plt.density = 100)
-}
-
-get_insect_FL.df <- function(FL){
-  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
-    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
-}
-
-ggplot_uniFL <- function(FL.df) {
-  ggplot(FL.df, aes(x = Var1, y = mean_fitness)) +
-    geom_line() + 
-    geom_ribbon(aes(ymin = lower_2.5, ymax = upper_97.5), alpha = 0.5)
-}
-```
-
-Choosing the level of model complexity.
-We used AIC to pair down the complexity of the model.
-For both the control and treatment plants, there is support for maintaing the linear interaction between gall size and the number of individuals per gall.
-In both cases, AIC suggest that the models lacking linear interaction terms were more parsimonious, so we subsequently analyzed selection gradients with these models.
-
-```{r AIC MODEL COMPLEXITY}
-
-## CONTROL PLANTS ----
-gamm_full.control <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots) +
-                                  c.Gall_Height_mm:c.gall_individuals + 
-                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
-                                  c.gall_individuals:c.Density_per_100_shoots,
-                                data = control_df)
-summary(gamm_full.control$gam)
-summary(gamm_full.control$mer)
-
-gamm_red.control <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots),
-                                data = control_df)
-summary(gamm_red.control$gam)
-summary(gamm_red.control$mer)
-
-AIC(gamm_full.control$mer, gamm_red.control$mer)
-
-## TREATMENT PLANTS ----
-gamm_full.treatment <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots) +
-                                  c.Gall_Height_mm:c.gall_individuals + 
-                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
-                                  c.gall_individuals:c.Density_per_100_shoots,
-                                data = treatment_df)
-summary(gamm_full.treatment$gam)
-summary(gamm_full.treatment$mer)
-
-gamm_red.treatment <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots),
-                                data = treatment_df)
-summary(gamm_red.treatment$gam)
-summary(gamm_red.treatment$mer)
-
-AIC(gamm_full.treatment$mer, gamm_red.treatment$mer)
-```
-
-```{r SELECTION GRADIENTS}
-
-## GALL SIZE ----
-sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                 phenotype = "c.Gall_Height_mm", 
-                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
-sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                   phenotype = "c.Gall_Height_mm", 
-                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
-
-## GALL INDIVIDUALS ----
-sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                        phenotype = "c.gall_individuals", 
-                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                          phenotype = "c.gall_individuals", 
-                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-
-## GALL DENSITY ----
-sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                    phenotype = "c.Density_per_100_shoots", 
-                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                      phenotype = "c.Density_per_100_shoots", 
-                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-
-## PRINT TABLE ----
-rbind(
-  mutate(sg.size_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.size_treatment$ests, Food_Web_Treatment = "Simple"),
-  mutate(sg.individuals_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
-  mutate(sg.density_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.density_treatment$ests, Food_Web_Treatment = "Simple")
-)
-
-round(rbind(
-  sg.size_control$ests,
-  sg.size_treatment$ests,
-  sg.individuals_control$ests,
-  sg.individuals_treatment$ests,
-  sg.density_control$ests,
-  sg.density_treatment$ests
-),3)
-
-## BOOTSTRAPPED INTERVALS ----
-bootstrap_df <- bind_rows(
-  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
-)
-
-bootstrap_df %>%
-  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
-  geom_boxplot() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_Type) +
-  coord_flip() 
-```
-
-Another decision we had to make was whether to calculate selection gradients with GAM or GAMMs.
-The problem with calculating selection gradients with GAMM is that the selection gradients can vary among environmental contexts that are being modelled by random intercepts.
-Since we did not alter random slopes, this would just cause variation in the selection gradients around the mean value, which is what our model tries to estimate.
-Therefore, we felt our GAMM model accurately reflects the selection that is happening at the population-level.
 
@@
 ```
-
-```{r Fitness Landscapes}
-## GALL SIZE ----
-fl.size_control <- insect_FL(mod = gamm_red.control$gam, 
-                                 phenotype = "c.Gall_Height_mm", 
-                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
-fl.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                   phenotype = "c.Gall_Height_mm", 
-                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
-
-## GALL INDIVIDUALS ----
-fl.individuals_control <- insect_FL(mod = gamm_red.control$gam, 
-                                        phenotype = "c.gall_individuals", 
-                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-fl.individuals_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                          phenotype = "c.gall_individuals", 
-                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-
-## GALL DENSITY ----
-fl.density_control <- insect_FL(mod = gamm_red.control$gam, 
-                                    phenotype = "c.Density_per_100_shoots", 
-                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-fl.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                      phenotype = "c.Density_per_100_shoots", 
-                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-
-get_insect_FL.df(fl.size_control) %>%
-  ggplot_uniFL(.)
-
-get_insect_FL.df(fl.size_treatment) %>%
-  ggplot_uniFL(.)
-
-get_insect_FL.df(fl.individuals_control) %>%
-  ggplot_uniFL(.)
-
-get_insect_FL.df(fl.individuals_treatment) %>%
-  ggplot_uniFL(.)
-
-get_insect_FL.df(fl.density_control) %>%
-  ggplot_uniFL(.)
-
-get_insect_FL.df(fl.density_treatment) %>%
-  ggplot_uniFL(.)
-
-## Landscape
-fl.individuals.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
-                                              phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
-                                              covariates = c("c.Gall_Height_mm"))
-
-get_insect_FL.df(fl.individuals.x.density_control) %>%
-  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
-  geom_tile()
-
-fl.individuals.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                                phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
-                                                covariates = c("c.Gall_Height_mm"))
-get_insect_FL.df(fl.individuals.x.density_treatment) %>%
-  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
-  geom_tile()
-
-test <- bind_rows(mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment.focus="Simple"),
-          mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment.focus="Complex"))
-
-ggplot(test, aes(x=Var1, y=Var2, fill=mean_fitness)) +
-  geom_raster() + 
-  facet_wrap(~Treatment.focus) +
-  scale_fill_viridis()
-```

### 2018-05-14 supp_mat_complexity_selection.Rmd
update supp mat

--- 2018-05-02 supp_mat_complexity_selection.Rmd
@@
 
+```{r}
+sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                               phenotype = c("c.Gall_Height_mm", "c.gall_individuals"),
+                                               covariates = c("c.Density_per_100_shoots"))
+sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                                 phenotype = c("c.Gall_Height_mm", "c.gall_individuals"),
+                                                 covariates = c("c.Density_per_100_shoots"))
+sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                               phenotype = c("c.Gall_Height_mm", "c.Density_per_100_shoots"),
+                                               covariates = c("c.gall_individuals"))
+sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                                 phenotype = c("c.Gall_Height_mm","c.Density_per_100_shoots"),
+                                                 covariates = c("c.gall_individuals"))
+sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                                  phenotype = c("c.Density_per_100_shoots", "c.gall_individuals"),
+                                                  covariates = c("c.Gall_Height_mm"))
+sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                                    phenotype = c("c.Density_per_100_shoots", "c.gall_individuals"),
+                                                    covariates = c("c.Gall_Height_mm"))
+
+# note that while the means are always the same for each gradient calculation, the SE and p-values can be slightly different. I always reported the highest SE and highest P-value to be conservative
+bind_rows(data.frame(round(sg.size.x.individuals_control$ests,3), 
+                     gradients = rownames(sg.size.x.individuals_control$ests),
+                     treatment = "Complex"),
+          data.frame(round(sg.size.x.individuals_treatment$ests,3), 
+                     gradients = rownames(sg.size.x.individuals_treatment$ests),
+                     treatment = "Simple"),
+          data.frame(round(sg.size.x.density_control$ests,3), 
+                     gradients = rownames(sg.size.x.density_control$ests),
+                     treatment = "Complex"),
+          data.frame(round(sg.size.x.density_treatment$ests,3), 
+                     gradients = rownames(sg.size.x.density_treatment$ests),
+                     treatment = "Simple"),
+          data.frame(round(sg.density.x.individuals_control$ests,3), 
+                     gradients = rownames(sg.density.x.individuals_control$ests),
+                     treatment = "Complex"),
+          data.frame(round(sg.density.x.individuals_treatment$ests,3), 
+                     gradients = rownames(sg.density.x.individuals_treatment$ests),
+                     treatment = "Simple")) %>%
+  distinct %>%
+  arrange(gradients)
+
+```
+
 Another decision we had to make was whether to calculate selection gradients with GAM or GAMMs.
@@
 
-GAM estimates of selection gradients differ from GAMM
+Now we plot the fitness landscapes associated with different combinations of gall phenotypes.
+We restrict these plots to 1 SD above and below the mean trait value, as this contains the majority of phenotypes under selection.
+Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
+```{r Fitness Landscapes}
 
-```{r COMPARE GAM WITH GAMM}
+#### ESTIMATE FITNESS LANDSCAPES ----
 
-## CONTROL PLANTS ----
-
-## Gall Height
-gam_red.control_size <- gam(gall_survival ~
-                             s(c.Gall_Height_mm) + 
-                             c.gall_individuals +
-                             c.Density_per_100_shoots,
-                           data = control_df, family = binomial(link = "logit"))
-summary(gam_red.control)
-
-gam.plot(gam_red.control)
-gam.plot(gamm_red.control$gam)
-
-## Gall individuals
-control_df_gall.level <- control_df %>%
-  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
-  summarise(gall_survival_mean = mean(gall_survival),
-            gall_individuals = mean(gall_individuals),                 # note that there is no variance, it is the actual value
-            Gall_Height_mm_mean = mean(Gall_Height_mm),
-            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
-  ungroup() %>%
-  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
-
-gam_red.control_indiv <- gam(gall_survival_mean ~
-                              c.Gall_Height_mm_mean + 
-                              s(c.gall_individuals, k=9) +
-                              c.Density_per_100_shoots,
-                             data = control_df_gall.level, family = binomial(link = "logit")) # we didn't include weights because this would be correlated with the number of individuals per gall
-summary(gam_red.control_indiv)
-
-gam.plot(gam_red.control_indiv)
-gam.plot(gamm_red.control$gam)
-
-## Gall density
-control_df_plant.level <- control_df_gall.level %>%
-  group_by(Treatment.focus, Plant_Position) %>%
-  summarise(gall_survival_mean = mean(gall_survival_mean),
-            gall_sample_size = n(),
-            gall_individuals_mean = mean(gall_individuals),                 
-            Gall_Height_mm_mean = mean(Gall_Height_mm_mean),
-            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
-  ungroup() %>%
-  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
-         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
-
-gam_red.control_density <- gam(gall_survival_mean ~
-                                c.Gall_Height_mm_mean + 
-                                c.gall_individuals_mean +
-                                s(c.Density_per_100_shoots, k=3),   # do I adjust k to be consistent with mixed-effects model?
-                             data = control_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
-summary(gam_red.control_density)
-
-gam.plot(gam_red.control_density)
-gam.plot(gamm_red.control$gam)
-
-## TREATMENT PLANTS ----
-
-## Gall Height
-gam_red.treatment_size <- gam(gall_survival ~
-                         s(c.Gall_Height_mm) + 
-                         c.gall_individuals +
-                         c.Density_per_100_shoots,
-                       data = treatment_df, family = binomial(link = "logit"))
-summary(gam_red.treatment)
-
-gam.plot(gam_red.treatment)
-gam.plot(gamm_red.treatment$gam)
-
-## Gall individuals
-treatment_df_gall.level <- treatment_df %>%
-  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
-  summarise(gall_survival_mean = mean(gall_survival),
-            gall_individuals = mean(gall_individuals),                 # note that there is no variance, it is the actual value
-            Gall_Height_mm_mean = mean(Gall_Height_mm),
-            Density_per_100_shoots = mean(Density_per_100_shoots)) %>% # remember that this is pseudo-replicated at the gall-level
-  ungroup() %>%
-  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
-
-gam_red.treatment_indiv <- gam(gall_survival_mean ~
-                              c.Gall_Height_mm_mean + 
-                              s(c.gall_individuals, k=9) +
-                              c.Density_per_100_shoots,
-                             data = treatment_df_gall.level, family = binomial(link = "logit"))
-summary(gam_red.treatment_indiv)
-
-gam.plot(gam_red.treatment_indiv)
-gam.plot(gamm_red.treatment$gam)
-
-## Gall density
-treatment_df_plant.level <- treatment_df_gall.level %>%
-  group_by(Treatment.focus, Plant_Position) %>%
-  summarise(gall_survival_mean = mean(gall_survival_mean),
-            gall_sample_size = n(),
-            gall_individuals_mean = mean(gall_individuals),                 
-            Gall_Height_mm_mean = mean(Gall_Height_mm_mean),
-            Density_per_100_shoots = mean(Density_per_100_shoots)) %>%                # note that there is no variance, it is the actual value
-  ungroup() %>%
-  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
-         c.gall_individuals_mean = gall_individuals_mean - mean(gall_individuals_mean),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots)) # why is this giving zero values?
-
-gam_red.treatment_density <- gam(gall_survival_mean ~
-                                c.Gall_Height_mm_mean + 
-                                c.gall_individuals_mean +
-                                s(c.Density_per_100_shoots),
-                             data = treatment_df_plant.level, family = binomial(link = "logit"), weights = gall_sample_size) # weighting appears to alter the results...
-summary(gam_red.treatment_density)
-
-gam.plot(gam_red.treatment_density)
-gam.plot(gamm_red.treatment$gam)
-
-#### CALCULATE SELECTION GRADIENTS FROM GAM ----
-
-## GALL SIZE ----
-sg.gam.size_control <- gradient.calc(mod = gam_red.control, 
+## GALL SIZE
+fl.size_control <- insect_FL(mod = gamm_red.control$gam, 
                                  phenotype = "c.Gall_Height_mm", 
                                  covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
-sg.gam.size_treatment <- gradient.calc(mod = gam_red.treatment, 
+fl.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                    phenotype = "c.Gall_Height_mm", 
@@
 
-## GALL INDIVIDUALS ----
-sg.gam.individuals_control <- gradient.calc(mod = gam_red.control, 
+## GALL INDIVIDUALS
+fl.individuals_control <- insect_FL(mod = gamm_red.control$gam, 
                                         phenotype = "c.gall_individuals", 
                                         covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-sg.gam.individuals_treatment <- gradient.calc(mod = gam_red.treatment, 
+fl.individuals_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                           phenotype = "c.gall_individuals", 
@@
 
-## GALL DENSITY ----
-sg.gam.density_control <- gradient.calc(mod = gam_red.control, 
+## GALL DENSITY 
+fl.density_control <- insect_FL(mod = gamm_red.control$gam, 
                                     phenotype = "c.Density_per_100_shoots", 
                                     covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-sg.gam.density_treatment <- gradient.calc(mod = gam_red.treatment, 
+fl.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
                                       phenotype = "c.Density_per_100_shoots", 
@@
 
-## PRINT TABLE ----
-rbind(
-  mutate(sg.gam.size_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.gam.size_treatment$ests, Food_Web_Treatment = "Simple"),
-  mutate(sg.gam.individuals_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.gam.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
-  mutate(sg.gam.density_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.gam.density_treatment$ests, Food_Web_Treatment = "Simple")
-)
+## GALL INDIVIDUALS X DENSITY
+fl.individuals.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
+                                              phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
+                                              covariates = c("c.Gall_Height_mm"))
+fl.individuals.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                                phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
+                                                covariates = c("c.Gall_Height_mm"))
 
-round(rbind(
-  sg.gam.size_control$ests,
-  sg.gam.size_treatment$ests,
-  sg.gam.individuals_control$ests,
-  sg.gam.individuals_treatment$ests,
-  sg.gam.density_control$ests,
-  sg.gam.density_treatment$ests
-),3)
+## GALL INDIVIDUALS x SIZE
+fl.individuals.x.size_control <- insect_FL(mod = gamm_red.control$gam, 
+                                            phenotype = c("c.Gall_Height_mm","c.gall_individuals"), 
+                                            covariates = c("c.Density_per_100_shoots"))
+fl.individuals.x.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                             phenotype = c("c.Gall_Height_mm","c.gall_individuals"), 
+                                             covariates = c("c.Density_per_100_shoots"))
 
-## BOOTSTRAPPED INTERVALS ----
-gam.bootstrap_df <- bind_rows(
-  data.frame(Bootstrap_Estimates = sg.gam.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.gam.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.gam.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.gam.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.gam.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.gam.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.gam.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.gam.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.gam.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.gam.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.gam.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.gam.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
-)
+## GALL DENSITY X SIZE
+fl.size.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
+                                       phenotype = c("c.Density_per_100_shoots","c.Gall_Height_mm"), 
+                                       covariates = c("c.gall_individuals"))
+fl.size.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
+                                         phenotype = c("c.Density_per_100_shoots","c.Gall_Height_mm"), 
+                                         covariates = c("c.gall_individuals"))
 
-gam.bootstrap_df %>%
-  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
-  geom_boxplot() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_Type) +
-  coord_flip()
+#### PLOT FITNESS LANDSCAPES ----
 
+# Order: orange, light blue, green, yellow, dark blue, red, pink
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
+complex_color <- cbPalette[6]
+simple_color <- cbPalette[5]
+treatmeant_colors <- c(complex_color, simple_color)
+
+## 1-DIMENSIONAL
+uni_size <- bind_rows(mutate(get_insect_FL.df(fl.size_control), Treatment = "Complex"),
+          mutate(get_insect_FL.df(fl.size_treatment), Treatment = "Simple")) %>%
+  ggplot(.) +
+  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
+  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
+  ylab("Mean fitness") +
+  xlab("Mean gall size") +
+  scale_color_manual(values = treatmeant_colors) +
+  scale_fill_manual(values = treatmeant_colors) +
+  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))
+
+uni_clutch <- bind_rows(mutate(get_insect_FL.df(fl.individuals_control), Treatment = "Complex"),
+          mutate(get_insect_FL.df(fl.individuals_treatment), Treatment = "Simple")) %>%
+  ggplot(.) +
+  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
+  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
+  ylab("Mean fitness") +
+  xlab("Mean clutch size") +
+  scale_color_manual(values = treatmeant_colors) +
+  scale_fill_manual(values = treatmeant_colors) +
+  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))
+
+uni_pref <- bind_rows(mutate(get_insect_FL.df(fl.density_control), Treatment = "Complex"),
+          mutate(get_insect_FL.df(fl.density_treatment), Treatment = "Simple")) %>%
+  ggplot(.) +
+  geom_line(aes(x = Var1, y = mean_fitness, color=Treatment)) + 
+  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
+  ylab("Mean fitness") +
+  xlab("Mean female preference") +
+  scale_color_manual(values = treatmeant_colors) +
+  scale_fill_manual(values = treatmeant_colors) +
+  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits = c(0,1))
+
+uni_legend <- get_legend(uni_size)
+
+uni_plots <- plot_grid(uni_size + theme(legend.position = "none"), 
+                       uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       labels = "AUTO", nrow = 1, align='hv')
+plot_grid(uni_plots, uni_legend, ncol=2, rel_widths = c(3,0.3))
+
+## 2-DIMENSIONAL
+
+bind_rows(mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment="Simple"),
+          mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment="Complex")) %>%
+  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  geom_raster() + 
+  facet_wrap(~Treatment) +
+  scale_fill_viridis() +
+  xlab("Female preference") +
+  ylab("Clutch size")
+
+bind_rows(mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
+          mutate(get_insect_FL.df(fl.individuals.x.size_control), Treatment="Complex")) %>%
+  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  geom_raster() + 
+  facet_wrap(~Treatment) +
+  scale_fill_viridis() +
+  xlab("Clutch size") +
+  ylab("Gall size")
+
+bind_rows(mutate(get_insect_FL.df(fl.size.x.density_treatment), Treatment="Simple"),
+          mutate(get_insect_FL.df(fl.size.x.density_control), Treatment="Complex")) %>%
+  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  geom_raster() + 
+  facet_wrap(~Treatment) +
+  scale_fill_viridis() +
+  xlab("Gall size") +
+  ylab("Female preference")
 ```

### 2018-05-17 morgue_supp_mat.Rmd
working draft of code for analysis is finished.

@@
 ---
+
+ggplot_uniFL <- function(FL.df) {
+  ggplot(FL.df, aes(x = Var1, y = mean_fitness)) +
+    geom_line() + 
+    geom_ribbon(aes(ymin = lower_2.5, ymax = upper_97.5), alpha = 0.5)
+}
+
+```{r SELECTION GRADIENTS}
+
+## GALL SIZE ----
+sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                 phenotype = "c.Gall_Height_mm", 
+                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                   phenotype = "c.Gall_Height_mm", 
+                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+
+## GALL INDIVIDUALS ----
+sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                        phenotype = "c.gall_individuals", 
+                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                          phenotype = "c.gall_individuals", 
+                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+
+## GALL DENSITY ----
+sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                    phenotype = "c.Density_per_100_shoots", 
+                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                      phenotype = "c.Density_per_100_shoots", 
+                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+
+## PRINT TABLE ----
+rbind(
+  mutate(sg.size_control$ests, Food_Web_Treatment = "Complex"),
+  mutate(sg.size_treatment$ests, Food_Web_Treatment = "Simple"),
+  mutate(sg.individuals_control$ests, Food_Web_Treatment = "Complex"),
+  mutate(sg.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
+  mutate(sg.density_control$ests, Food_Web_Treatment = "Complex"),
+  mutate(sg.density_treatment$ests, Food_Web_Treatment = "Simple")
+)
+
+round(rbind(
+  sg.size_control$ests,
+  sg.size_treatment$ests,
+  sg.individuals_control$ests,
+  sg.individuals_treatment$ests,
+  sg.density_control$ests,
+  sg.density_treatment$ests
+),3)
+
+## BOOTSTRAPPED INTERVALS ----
+bootstrap_df <- bind_rows(
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
+)
+
+bootstrap_df %>%
+  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
+  geom_boxplot() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_Type) +
+  coord_flip() 
+```
 

### 2018-05-17 supp_mat_complexity_selection.Rmd
working draft of code for analysis is finished.

@@
 ```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
+
 ## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
@@
   filter(Treatment.focus == "Control") %>%
-  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
+         gall_individuals = gall_individuals - mean(gall_individuals),
+         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
 
@@
   filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
-  mutate(c.Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         c.gall_individuals = gall_individuals - mean(gall_individuals),
-         c.Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
+         gall_individuals = gall_individuals - mean(gall_individuals),
+         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
 ```
@@
   gamm4(formula, data, 
-        random = ~(1|Plant_Position/Gall_Number), # Genotype/
+        random = ~(1|Genotype/Plant_Position/Gall_Number), 
         family = binomial(link = logit))
@@
   gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
-                refit.smooth = F, 
+                refit.smooth = T, # F
                 n.boot = 1000,
-                se.method = 'boot.para',
+                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
                 standardized = T)
@@
 }
-
-ggplot_uniFL <- function(FL.df) {
-  ggplot(FL.df, aes(x = Var1, y = mean_fitness)) +
-    geom_line() + 
-    geom_ribbon(aes(ymin = lower_2.5, ymax = upper_97.5), alpha = 0.5)
-}
 ```
@@
 gamm_full.control <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots) +
-                                  c.Gall_Height_mm:c.gall_individuals + 
-                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
-                                  c.gall_individuals:c.Density_per_100_shoots,
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots + 
+                                  gall_individuals:Density_per_100_shoots,
                                 data = control_df)
@@
 gamm_red.control <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots),
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots),
                                 data = control_df)
@@
 gamm_full.treatment <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots) +
-                                  c.Gall_Height_mm:c.gall_individuals + 
-                                  c.Gall_Height_mm:c.Density_per_100_shoots + 
-                                  c.gall_individuals:c.Density_per_100_shoots,
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots + 
+                                  gall_individuals:Density_per_100_shoots,
                                 data = treatment_df)
@@
 gamm_red.treatment <- gamm.model(gall_survival ~ 
-                                  s(c.Gall_Height_mm) + 
-                                  s(c.gall_individuals, k=9) + 
-                                  s(c.Density_per_100_shoots),
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots),
                                 data = treatment_df)
@@
 ```
+Parametric bootstrapping: Currently reported results
 
-```{r SELECTION GRADIENTS}
+Case-wise bootstrapping: qualitative results match parametric bootstrapping.
 
-## GALL SIZE ----
+Posterior: qualitative results match parametric bootstrapping, except that non-linear selection on gall size in the complex food-web is no longer significant.
+
+Permutation: qualtiative results are consistent with parametric bootstrapping.
+Exceptions include: in the simple food-web, there is no evidence of non-linear selection for gall density or gall individuals.
+In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
+```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE}
+## Estimate directional, nonlinear, and correlational selection gradients
 sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                 phenotype = "c.Gall_Height_mm", 
-                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+                                 phenotype = "Gall_Height_mm", 
+                                 covariates = c("gall_individuals","Density_per_100_shoots"))
 sg.size_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                   phenotype = "c.Gall_Height_mm", 
-                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+                                   phenotype = "Gall_Height_mm", 
+                                   covariates = c("gall_individuals","Density_per_100_shoots"))
+sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                        phenotype = "gall_individuals", 
+                                        covariates = c("Gall_Height_mm","Density_per_100_shoots"))
+sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                          phenotype = "gall_individuals", 
+                                          covariates = c("Gall_Height_mm","Density_per_100_shoots"))
+sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                    phenotype = "Density_per_100_shoots", 
+                                    covariates = c("gall_individuals","Gall_Height_mm"))
+sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                      phenotype = "Density_per_100_shoots", 
+                                      covariates = c("gall_individuals","Gall_Height_mm"))
+sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                               phenotype = c("Gall_Height_mm", "gall_individuals"),
+                                               covariates = c("Density_per_100_shoots"))
+sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                                 phenotype = c("Gall_Height_mm", "gall_individuals"),
+                                                 covariates = c("Density_per_100_shoots"))
+sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                               phenotype = c("Gall_Height_mm", "Density_per_100_shoots"),
+                                               covariates = c("gall_individuals"))
+sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                                 phenotype = c("Gall_Height_mm","Density_per_100_shoots"),
+                                                 covariates = c("gall_individuals"))
+sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
+                                                  phenotype = c("Density_per_100_shoots", "gall_individuals"),
+                                                  covariates = c("Gall_Height_mm"))
+sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
+                                                    phenotype = c("Density_per_100_shoots", "gall_individuals"),
+                                                    covariates = c("Gall_Height_mm"))
 
-## GALL INDIVIDUALS ----
-sg.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                        phenotype = "c.gall_individuals", 
-                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
-sg.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                          phenotype = "c.gall_individuals", 
-                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+## Summarise the results
+sg.summary <- bind_rows(
+          data.frame(sg.size_control$ests, #round(,3), 
+                     gradients = rownames(sg.size_control$ests),
+                     treatment = "Complex"),
+          data.frame(sg.size_treatment$ests, #round(,3), 
+                     gradients = rownames(sg.size_treatment$ests),
+                     treatment = "Simple"),
+          data.frame(sg.individuals_control$ests, #round(,3), 
+                     gradients = rownames(sg.individuals_control$ests),
+                     treatment = "Complex"),
+          data.frame(sg.individuals_treatment$ests, #round(,3), 
+                     gradients = rownames(sg.individuals_treatment$ests),
+                     treatment = "Simple"),
+          data.frame(sg.density_control$ests, #round(,3), 
+                     gradients = rownames(sg.density_control$ests),
+                     treatment = "Complex"),
+          data.frame(sg.density_treatment$ests, #round(,3), 
+                     gradients = rownames(sg.density_treatment$ests),
+                     treatment = "Simple"),
+          data.frame(sg.size.x.individuals_control$ests, #round(,3), 
+                     gradients = rownames(sg.size.x.individuals_control$ests),
+                     treatment = "Complex")[5,],
+          data.frame(sg.size.x.individuals_treatment$ests, #round(,3), 
+                     gradients = rownames(sg.size.x.individuals_treatment$ests),
+                     treatment = "Simple")[5,],
+          data.frame(sg.size.x.density_control$ests, #round(,3), 
+                     gradients = rownames(sg.size.x.density_control$ests),
+                     treatment = "Complex")[5,],
+          data.frame(sg.size.x.density_treatment$ests, #round(,3), 
+                     gradients = rownames(sg.size.x.density_treatment$ests),
+                     treatment = "Simple")[5,],
+          data.frame(sg.density.x.individuals_control$ests, #round(,3), 
+                     gradients = rownames(sg.density.x.individuals_control$ests),
+                     treatment = "Complex")[5,],
+          data.frame(sg.density.x.individuals_treatment$ests, #round(,3), 
+                     gradients = rownames(sg.density.x.individuals_treatment$ests),
+                     treatment = "Simple")[5,])
 
-## GALL DENSITY ----
-sg.density_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                    phenotype = "c.Density_per_100_shoots", 
-                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
-sg.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                      phenotype = "c.Density_per_100_shoots", 
-                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+## Table of Estimates
+sg.table <- sg.summary %>%
+  mutate(plus_minus = "\u00B1", estimates = round(estimates, 4), SE = round(SE, 4)) %>%
+  unite(col = estimate_SE, from = c("estimates", "plus_minus", "SE"), sep="") %>%
+  select(-P.value) %>%
+  spread(treatment, estimate_SE)
+sg.table
+write_csv(sg.table, "sg.table.csv")
 
-## PRINT TABLE ----
-rbind(
-  mutate(sg.size_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.size_treatment$ests, Food_Web_Treatment = "Simple"),
-  mutate(sg.individuals_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.individuals_treatment$ests, Food_Web_Treatment = "Simple"),
-  mutate(sg.density_control$ests, Food_Web_Treatment = "Complex"),
-  mutate(sg.density_treatment$ests, Food_Web_Treatment = "Simple")
-)
+## Table of P-values
+sg.summary %>%
+  select(-estimates, -SE) %>%
+  spread(treatment, P.value)
+```
 
-round(rbind(
-  sg.size_control$ests,
-  sg.size_treatment$ests,
-  sg.individuals_control$ests,
-  sg.individuals_treatment$ests,
-  sg.density_control$ests,
-  sg.density_treatment$ests
-),3)
-
+```{r}
+hist(as.numeric(sg.density_control$boot[ ,1]))
 ## BOOTSTRAPPED INTERVALS ----
@@
   data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,1]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,2]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
   data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple")
+  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  # correlational
+  data.frame(Bootstrap_Estimates = as.numeric(sg.size.x.individuals_control$boot[ ,5]), Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size.x.individuals_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+    data.frame(Bootstrap_Estimates = sg.size.x.density_control$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size.x.density_treatment$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.density.x.individuals_control$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.density.x.individuals_treatment$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
 )
@@
 bootstrap_df %>%
+  #filter(Selection_Type == "Gamma") %>%
   ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
@@
   geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_Type) +
+  facet_wrap(~Selection_Type, scales = "free_x") +
   coord_flip() 
-```
-
-```{r}
-sg.size.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                               phenotype = c("c.Gall_Height_mm", "c.gall_individuals"),
-                                               covariates = c("c.Density_per_100_shoots"))
-sg.size.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                                 phenotype = c("c.Gall_Height_mm", "c.gall_individuals"),
-                                                 covariates = c("c.Density_per_100_shoots"))
-sg.size.x.density_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                               phenotype = c("c.Gall_Height_mm", "c.Density_per_100_shoots"),
-                                               covariates = c("c.gall_individuals"))
-sg.size.x.density_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                                 phenotype = c("c.Gall_Height_mm","c.Density_per_100_shoots"),
-                                                 covariates = c("c.gall_individuals"))
-sg.density.x.individuals_control <- gradient.calc(mod = gamm_red.control$gam, 
-                                                  phenotype = c("c.Density_per_100_shoots", "c.gall_individuals"),
-                                                  covariates = c("c.Gall_Height_mm"))
-sg.density.x.individuals_treatment <- gradient.calc(mod = gamm_red.treatment$gam, 
-                                                    phenotype = c("c.Density_per_100_shoots", "c.gall_individuals"),
-                                                    covariates = c("c.Gall_Height_mm"))
-
-# note that while the means are always the same for each gradient calculation, the SE and p-values can be slightly different. I always reported the highest SE and highest P-value to be conservative
-bind_rows(data.frame(round(sg.size.x.individuals_control$ests,3), 
-                     gradients = rownames(sg.size.x.individuals_control$ests),
-                     treatment = "Complex"),
-          data.frame(round(sg.size.x.individuals_treatment$ests,3), 
-                     gradients = rownames(sg.size.x.individuals_treatment$ests),
-                     treatment = "Simple"),
-          data.frame(round(sg.size.x.density_control$ests,3), 
-                     gradients = rownames(sg.size.x.density_control$ests),
-                     treatment = "Complex"),
-          data.frame(round(sg.size.x.density_treatment$ests,3), 
-                     gradients = rownames(sg.size.x.density_treatment$ests),
-                     treatment = "Simple"),
-          data.frame(round(sg.density.x.individuals_control$ests,3), 
-                     gradients = rownames(sg.density.x.individuals_control$ests),
-                     treatment = "Complex"),
-          data.frame(round(sg.density.x.individuals_treatment$ests,3), 
-                     gradients = rownames(sg.density.x.individuals_treatment$ests),
-                     treatment = "Simple")) %>%
-  distinct %>%
-  arrange(gradients)
-
 ```
@@
 fl.size_control <- insect_FL(mod = gamm_red.control$gam, 
-                                 phenotype = "c.Gall_Height_mm", 
-                                 covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+                                 phenotype = "Gall_Height_mm", 
+                                 covariates = c("gall_individuals","Density_per_100_shoots"))
 fl.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                   phenotype = "c.Gall_Height_mm", 
-                                   covariates = c("c.gall_individuals","c.Density_per_100_shoots"))
+                                   phenotype = "Gall_Height_mm", 
+                                   covariates = c("gall_individuals","Density_per_100_shoots"))
 
@@
 fl.individuals_control <- insect_FL(mod = gamm_red.control$gam, 
-                                        phenotype = "c.gall_individuals", 
-                                        covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+                                        phenotype = "gall_individuals", 
+                                        covariates = c("Gall_Height_mm","Density_per_100_shoots"))
 fl.individuals_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                          phenotype = "c.gall_individuals", 
-                                          covariates = c("c.Gall_Height_mm","c.Density_per_100_shoots"))
+                                          phenotype = "gall_individuals", 
+                                          covariates = c("Gall_Height_mm","Density_per_100_shoots"))
 
@@
 fl.density_control <- insect_FL(mod = gamm_red.control$gam, 
-                                    phenotype = "c.Density_per_100_shoots", 
-                                    covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+                                    phenotype = "Density_per_100_shoots", 
+                                    covariates = c("gall_individuals","Gall_Height_mm"))
 fl.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                      phenotype = "c.Density_per_100_shoots", 
-                                      covariates = c("c.gall_individuals","c.Gall_Height_mm"))
+                                      phenotype = "Density_per_100_shoots", 
+                                      covariates = c("gall_individuals","Gall_Height_mm"))
 
@@
 fl.individuals.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
-                                              phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
-                                              covariates = c("c.Gall_Height_mm"))
+                                              phenotype = c("Density_per_100_shoots","gall_individuals"), 
+                                              covariates = c("Gall_Height_mm"))
 fl.individuals.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                                phenotype = c("c.Density_per_100_shoots","c.gall_individuals"), 
-                                                covariates = c("c.Gall_Height_mm"))
+                                                phenotype = c("Density_per_100_shoots","gall_individuals"), 
+                                                covariates = c("Gall_Height_mm"))
 
@@
 fl.individuals.x.size_control <- insect_FL(mod = gamm_red.control$gam, 
-                                            phenotype = c("c.Gall_Height_mm","c.gall_individuals"), 
-                                            covariates = c("c.Density_per_100_shoots"))
+                                            phenotype = c("Gall_Height_mm","gall_individuals"), 
+                                            covariates = c("Density_per_100_shoots"))
 fl.individuals.x.size_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                             phenotype = c("c.Gall_Height_mm","c.gall_individuals"), 
-                                             covariates = c("c.Density_per_100_shoots"))
+                                             phenotype = c("Gall_Height_mm","gall_individuals"), 
+                                             covariates = c("Density_per_100_shoots"))
 
@@
 fl.size.x.density_control <- insect_FL(mod = gamm_red.control$gam, 
-                                       phenotype = c("c.Density_per_100_shoots","c.Gall_Height_mm"), 
-                                       covariates = c("c.gall_individuals"))
+                                       phenotype = c("Density_per_100_shoots","Gall_Height_mm"), 
+                                       covariates = c("gall_individuals"))
 fl.size.x.density_treatment <- insect_FL(mod = gamm_red.treatment$gam, 
-                                         phenotype = c("c.Density_per_100_shoots","c.Gall_Height_mm"), 
-                                         covariates = c("c.gall_individuals"))
+                                         phenotype = c("Density_per_100_shoots","Gall_Height_mm"), 
+                                         covariates = c("gall_individuals"))
 
@@
                                         axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       labels = "AUTO", nrow = 1, align='hv')
-plot_grid(uni_plots, uni_legend, ncol=2, rel_widths = c(3,0.3))
+                       labels = "AUTO", ncol = 4, align='hv')
+
+fitness_landscapes_1d <- ggdraw(uni_plots) + draw_grob(uni_legend, x = 0.8, y=0) #plot_grid(uni_plots, uni_legend, ncol=2, rel_widths = c(3,0.3))
+fitness_landscapes_1d
+save_plot("fitness_landscapes_1d.png", fitness_landscapes_1d, base_height=6, base_width = 8)
 
 ## 2-DIMENSIONAL
-
-bind_rows(mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment="Simple"),
-          mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment="Complex")) %>%
-  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
-  geom_raster() + 
-  facet_wrap(~Treatment) +
-  scale_fill_viridis() +
-  xlab("Female preference") +
-  ylab("Clutch size")
-
-bind_rows(mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
+clutch.x.size_2d <- bind_rows(
+  mutate(get_insect_FL.df(fl.individuals.x.size_treatment), Treatment="Simple"),
   mutate(get_insect_FL.df(fl.individuals.x.size_control), Treatment="Complex")) %>%
@@
   facet_wrap(~Treatment) +
-  scale_fill_viridis() +
-  xlab("Clutch size") +
-  ylab("Gall size")
+  scale_fill_viridis(name = "Mean fitness") +
+  xlab("Mean gall size") +
+  ylab("Mean clutch size")
 
-bind_rows(mutate(get_insect_FL.df(fl.size.x.density_treatment), Treatment="Simple"),
+size.x.pref_2d <- bind_rows(
+  mutate(get_insect_FL.df(fl.size.x.density_treatment), Treatment="Simple"),
   mutate(get_insect_FL.df(fl.size.x.density_control), Treatment="Complex")) %>%
-  ggplot(., aes(x=Var1, y=Var2, fill=mean_fitness)) +
+  ggplot(., aes(x=Var2, y=Var1, fill=mean_fitness)) +
   geom_raster() + 
   facet_wrap(~Treatment) +
-  scale_fill_viridis() +
-  xlab("Gall size") +
-  ylab("Female preference")
+  scale_fill_viridis(name = "Mean fitness") +
+  xlab("Mean gall size") +
+  ylab("Mean female preference")
+
+clutch.x.pref_2d <- bind_rows(
+  mutate(get_insect_FL.df(fl.individuals.x.density_treatment), Treatment="Simple"),
+  mutate(get_insect_FL.df(fl.individuals.x.density_control), Treatment="Complex")) %>%
+  ggplot(., aes(x=Var2, y=Var1, fill=mean_fitness)) +
+  geom_raster() + 
+  facet_wrap(~Treatment) +
+  scale_fill_viridis(name = "Mean fitness") +
+  xlab("Mean clutch size") +
+  ylab("Mean female preference")
+
+legend_2d <- get_legend(clutch.x.size_2d)
+
+landscape_plots <- plot_grid(size.x.pref_2d + theme(legend.position = "none", axis.title.x = element_blank()),
+                             clutch.x.pref_2d + theme(legend.position = "none", axis.title.y = element_blank()),
+                             clutch.x.size_2d + theme(legend.position = "none"), nrow=2, align="hv")
+fitness_landscapes_2d <- ggdraw(landscape_plots) + draw_grob(legend_2d, x = 0.7, y=-0.2)
+save_plot("fitness_landscapes_2d.png", fitness_landscapes_2d, base_height=6, base_width = 8)
 ```

### 2018-05-18 supp_mat_complexity_selection.Rmd
exploring alternative models

@@
   gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
-                refit.smooth = T, # F
+                refit.smooth = F,
                 n.boot = 1000,
@@
 ## CONTROL PLANTS ----
-gamm_full.control <- gamm.model(gall_survival ~ 
+gamm_red.control <- gamm.model(gall_survival ~ 
                                   s(Gall_Height_mm) + 
@@
 
-AIC(gamm_full.control$mer, gamm_red.control$mer)
+gamm_red.control.noG <- gamm4(gall_survival ~ 
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots),
+                                  random = ~(1|Plant_Position/Gall_Number), 
+                                  family = binomial(link = logit),
+                                data = control_df)
+summary(gamm_red.control.noG$gam)
+summary(gamm_red.control.noG$mer)
+
+glmm_full.control <- gamm.model(gall_survival ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots +
+                                  gall_individuals:Density_per_100_shoots,
+                                data = control_df)
+summary(glmm_full.control$gam)
+summary(glmm_full.control$mer)
+
+glmm_red.control <- gamm.model(gall_survival ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+                                data = control_df)
+summary(glmm_red.control$gam)
+summary(glmm_red.control$mer)
+
+lmm_red.control <- gamm4(gall_survival ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+                           random = ~(1|Plant_Position/Gall_Number),
+                                data = control_df, family=gaussian())
+summary(lmm_red.control$gam)
+summary(lmm_red.control$mer)
+
+AIC(gamm_full.control$mer, gamm_red.control$mer, gamm_red.control.noG$mer, glmm_full.control$mer, glmm_red.control$mer, lmm_red.control$mer)
 
 ## TREATMENT PLANTS ----
-gamm_full.treatment <- gamm.model(gall_survival ~ 
+gamm_red.treatment <- gamm.model(gall_survival ~ 
                                   s(Gall_Height_mm) + 
@@
 
-AIC(gamm_full.treatment$mer, gamm_red.treatment$mer)
+gamm_red.treatment.noG <- gamm4(gall_survival ~ 
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots),
+                                  random = ~(1|Plant_Position/Gall_Number), 
+                                  family = binomial(link = logit),
+                                data = treatment_df)
+summary(gamm_red.treatment.noG$gam)
+summary(gamm_red.treatment.noG$mer)
+
+glmm_full.treatment <- gamm.model(gall_survival ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots +
+                                  gall_individuals:Density_per_100_shoots,
+                                data = treatment_df)
+summary(glmm_full.treatment$gam)
+summary(glmm_full.treatment$mer)
+
+glmm_red.treatment <- gamm.model(gall_survival ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+                                data = treatment_df)
+summary(glmm_red.treatment$gam)
+summary(glmm_red.treatment$mer)
+
+lmm_red.treatment <- gamm4(gall_survival ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+                           random = ~(1|Plant_Position/Gall_Number),
+                                data = treatment_df, family=gaussian())
+summary(lmm_red.treatment$gam)
+summary(lmm_red.treatment$mer)
+
+AIC(gamm_full.treatment$mer, gamm_red.treatment$mer, gamm_red.treatment.noG$mer, glmm_full.treatment$mer, glmm_red.treatment$mer, lmm_red.treatment$mer)
+
+## Linear mixed-models
+lmm_full.control <- lmer(gall_survival/0.45 ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots +
+                                  gall_individuals:Density_per_100_shoots +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                                data = control_df)
+summary(lmm_full.control)
+car::Anova(lmm_full.control, test="F")
+visreg::visreg(lmm_full.control)
+
+lmm_full.treatment <- lmer(gall_survival/0.6 ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots +
+                                  gall_individuals:Density_per_100_shoots +
+                             (1|Genotype/Plant_Position/Gall_Number),
+                                data = treatment_df)
+summary(lmm_full.treatment)
+car::Anova(lmm_full.treatment, test="F")
+
+lmm_red.treatment <- lmer(gall_survival/0.6 ~ 
+                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
+                              (1|Genotype/Plant_Position/Gall_Number),
+                                data = treatment_df)
+summary(lmm_red.treatment)
+car::Anova(lmm_red.treatment, test="F")
+visreg::visreg(lmm_red.treatment)
+
+AIC(lmm_full.treatment, lmm_red.treatment)
+
+gall_selection.df$relative.fit <- with(gall_selection.df, ifelse(Treatment.focus=="Control", gall_survival/0.45, gall_survival/0.6))
+
+lmm_full <- lmer(relative.fit ~ poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) + 
+                                poly(Gall_Height_mm,2):Treatment.focus + 
+                                poly(gall_individuals,2):Treatment.focus + 
+                                poly(Density_per_100_shoots,2):Treatment.focus +
+                                (1|Genotype/Plant_Position/Gall_Number),
+                                data = gall_selection.df)
+summary(lmm_full)
+car::Anova(lmm_full, test="F")
+visreg::visreg(lmm_full, xvar="Gall_Height_mm", by="Treatment.focus")
+visreg::visreg(lmm_full, xvar="gall_individuals", by="Treatment.focus")
+visreg::visreg(lmm_full, xvar="Density_per_100_shoots", by="Treatment.focus")
 ```
@@
 ```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE}
+
 ## Estimate directional, nonlinear, and correlational selection gradients
@@
 sg.summary <- bind_rows(
-          data.frame(sg.size_control$ests, #round(,3), 
+          data.frame(sg.size_control$ests,  
                      gradients = rownames(sg.size_control$ests),
                      treatment = "Complex"),
-          data.frame(sg.size_treatment$ests, #round(,3), 
+          data.frame(sg.size_treatment$ests, 
                      gradients = rownames(sg.size_treatment$ests),
                      treatment = "Simple"),
-          data.frame(sg.individuals_control$ests, #round(,3), 
+          data.frame(sg.individuals_control$ests,  
                      gradients = rownames(sg.individuals_control$ests),
                      treatment = "Complex"),
-          data.frame(sg.individuals_treatment$ests, #round(,3), 
+          data.frame(sg.individuals_treatment$ests,  
                      gradients = rownames(sg.individuals_treatment$ests),
                      treatment = "Simple"),
-          data.frame(sg.density_control$ests, #round(,3), 
+          data.frame(sg.density_control$ests, 
                      gradients = rownames(sg.density_control$ests),
                      treatment = "Complex"),
-          data.frame(sg.density_treatment$ests, #round(,3), 
+          data.frame(sg.density_treatment$ests, 
                      gradients = rownames(sg.density_treatment$ests),
                      treatment = "Simple"),
-          data.frame(sg.size.x.individuals_control$ests, #round(,3), 
+          data.frame(sg.size.x.individuals_control$ests,  
                      gradients = rownames(sg.size.x.individuals_control$ests),
                      treatment = "Complex")[5,],
-          data.frame(sg.size.x.individuals_treatment$ests, #round(,3), 
+          data.frame(sg.size.x.individuals_treatment$ests,  
                      gradients = rownames(sg.size.x.individuals_treatment$ests),
                      treatment = "Simple")[5,],
-          data.frame(sg.size.x.density_control$ests, #round(,3), 
+          data.frame(sg.size.x.density_control$ests,  
                      gradients = rownames(sg.size.x.density_control$ests),
                      treatment = "Complex")[5,],
-          data.frame(sg.size.x.density_treatment$ests, #round(,3), 
+          data.frame(sg.size.x.density_treatment$ests,  
                      gradients = rownames(sg.size.x.density_treatment$ests),
                      treatment = "Simple")[5,],
-          data.frame(sg.density.x.individuals_control$ests, #round(,3), 
+          data.frame(sg.density.x.individuals_control$ests, 
                      gradients = rownames(sg.density.x.individuals_control$ests),
                      treatment = "Complex")[5,],
-          data.frame(sg.density.x.individuals_treatment$ests, #round(,3), 
+          data.frame(sg.density.x.individuals_treatment$ests, 
                      gradients = rownames(sg.density.x.individuals_treatment$ests),
@@
 ```{r}
-hist(as.numeric(sg.density_control$boot[ ,1]))
+
 ## BOOTSTRAPPED INTERVALS ----
 bootstrap_df <- bind_rows(
-  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "c.Gall_Height_mm", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "c.Gall_Height_mm", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "c.gall_individuals", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "c.gall_individuals", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,1]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = as.numeric(sg.density_control$boot[ ,2]), Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "c.Density_per_100_shoots", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.individuals_control$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.individuals_treatment$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,1], Phenotype = "Oviposition preference", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.density_control$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,1], Phenotype = "Oviposition preference", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.density_treatment$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
   # correlational
-  data.frame(Bootstrap_Estimates = as.numeric(sg.size.x.individuals_control$boot[ ,5]), Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size.x.individuals_control$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
   data.frame(Bootstrap_Estimates = sg.size.x.individuals_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
-    data.frame(Bootstrap_Estimates = sg.size.x.density_control$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.size.x.density_treatment$boot[ ,5], Phenotype = "Size,Preference", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
-  data.frame(Bootstrap_Estimates = sg.density.x.individuals_control$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
-  data.frame(Bootstrap_Estimates = sg.density.x.individuals_treatment$boot[ ,5], Phenotype = "Preference,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
+    data.frame(Bootstrap_Estimates = sg.size.x.density_control$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size.x.density_treatment$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.density.x.individuals_control$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.density.x.individuals_treatment$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
 )
@@
   coord_flip() 
+```
+
+Compare bootstrapped replicates across treatments, rather than comparing to zero.
+```{r}
+bootstrap_df %>%
+  filter(Phenotype == "Gall size", Selection_Type == "Beta") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+bootstrap_df %>%
+  filter(Phenotype == "Gall size", Selection_Type == "Gamma") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+bootstrap_df %>%
+  filter(Phenotype == "Clutch size", Selection_Type == "Beta") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+bootstrap_df %>%
+  filter(Phenotype == "Clutch size", Selection_Type == "Gamma") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+bootstrap_df %>%
+  filter(Phenotype == "Oviposition preference", Selection_Type == "Beta") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+bootstrap_df %>%
+  filter(Phenotype == "Oviposition preference", Selection_Type == "Gamma") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+bootstrap_df %>%
+  filter(Phenotype == "Size,Clutch", Selection_Type == "Correlational") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient > 0)/1000) # flipped sign
+
+bootstrap_df %>%
+  filter(Phenotype == "Size,Pref.", Selection_Type == "Correlational") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient > 0)/1000) # flipped sign
+
+bootstrap_df %>%
+  filter(Phenotype == "Pref.,Clutch", Selection_Type == "Correlational") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web_Treatment, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
 ```
@@
   geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
-  ylab("Mean fitness") +
-  xlab("Mean gall size") +
+  ylab("Population mean fitness") +
+  xlab("Mean gall size\n(mm)") +
   scale_color_manual(values = treatmeant_colors) +
@@
   geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
-  ylab("Mean fitness") +
-  xlab("Mean clutch size") +
+  ylab("Population mean fitness") +
+  xlab("Mean clutch size\n(no. of larva)") +
   scale_color_manual(values = treatmeant_colors) +
@@
   geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
-  ylab("Mean fitness") +
-  xlab("Mean female preference") +
+  ylab("Population mean fitness") +
+  xlab("Mean oviposition preference\n(larva per 100 shoots)") +
   scale_color_manual(values = treatmeant_colors) +
@@
   facet_wrap(~Treatment) +
-  scale_fill_viridis(name = "Mean fitness") +
-  xlab("Mean gall size") +
-  ylab("Mean clutch size")
+  scale_fill_viridis(name = "Population\nmean fitness") +
+  xlab("Mean gall size (mm)") +
+  ylab("Mean clutch size (no. larva)")
 
@@
   facet_wrap(~Treatment) +
-  scale_fill_viridis(name = "Mean fitness") +
-  xlab("Mean gall size") +
-  ylab("Mean female preference")
+  scale_fill_viridis(name = "Population\nmean fitness") +
+  xlab("Mean gall size (mm)") +
+  ylab("Mean oviposition preference (no. larva per 100 shoots)")
 
@@
   facet_wrap(~Treatment) +
-  scale_fill_viridis(name = "Mean fitness") +
-  xlab("Mean clutch size") +
-  ylab("Mean female preference")
+  scale_fill_viridis(name = "Population\nmean fitness") +
+  xlab("Mean clutch size (no. larva)") +
+  ylab("Mean oviposition preference (no. larva per 100 shoots)")
 

### 2018-05-31 supp_mat_complexity_selection.Rmd
updating model selection

@@
 }
+
+overdisp_fun <- function(model) {
+  ## number of variance parameters in 
+  ##   an n-by-n variance-covariance matrix
+  vpars <- function(m) {
+    nrow(m)*(nrow(m)+1)/2
+  }
+  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
+  rdf <- nrow(model.frame(model))-model.df
+  rp <- residuals(model,type="pearson")
+  Pearson.chisq <- sum(rp^2)
+  prat <- Pearson.chisq/rdf
+  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
+  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
+}
+```
+
+```{r}
+# convert treatment to factor to use as 'by' variable in gamm.model
+gall_selection.df <- gall_selection.df %>%
+  mutate(Treatment_contr.sum=factor(Treatment.focus), 
+         sc.gall_size = as.numeric(scale(Gall_Height_mm)),
+         sc.clutch_size = as.numeric(scale(gall_individuals)),
+         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
+contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
+# Inspect contrasts:
+contrasts(gall_selection.df$Treatment_contr.sum)
+
+## AIC MODEL SELECTION
+# Note that I use gamm4 to fit all models to maintain consistency
+
+## GAMM full
+m1 <- gamm.model(gall_survival ~ Treatment_contr.sum +
+                   s(sc.gall_size, by=Treatment_contr.sum) + 
+                   s(sc.clutch_size, by=Treatment_contr.sum) + 
+                   s(sc.female_preference, by=Treatment_contr.sum) + 
+                   sc.gall_size:sc.clutch_size + sc.gall_size:sc.clutch_size:Treatment_contr.sum +
+                   sc.gall_size:sc.female_preference + sc.gall_size:sc.female_preference:Treatment_contr.sum +                                 sc.clutch_size:sc.female_preference + sc.clutch_size:sc.female_preference:Treatment_contr.sum,
+                 data = gall_selection.df)
+summary(m1$gam); summary(m1$mer)
+
+gamm_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
+                             s(sc.gall_size) + 
+                             s(sc.clutch_size, by=Treatment_contr.sum) + 
+                             s(sc.female_preference, by=Treatment_contr.sum),
+                 data = gall_selection.df)
+summary(gamm_reduced$gam); summary(gamm_reduced$mer)
+
+gamm_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum +
+                             sc.gall_size + 
+                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
+                             s(sc.female_preference, by=Treatment_contr.sum),
+                 data = gall_selection.df)
+summary(gamm_reduced2$gam); summary(gamm_reduced2$mer)
+
+GLMM_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
+                             sc.gall_size + 
+                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
+                             sc.female_preference + sc.female_preference:Treatment_contr.sum,
+                            data = gall_selection.df)
+summary(GLMM_reduced$gam); summary(GLMM_reduced$mer)
+
+AIC(m1$mer, gamm_reduced$mer, gamm_reduced2$mer, GLMM_reduced$mer)
+
+glmer_reduced <- glmer(gall_survival ~ Treatment_contr.sum +
+                             sc.gall_size + 
+                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
+                             sc.female_preference + sc.female_preference:Treatment_contr.sum +
+                             (1|Genotype/Plant_Position/Gall_Number),
+                       family=binomial(link=logit),
+                       data = gall_selection.df, glmerControl(optimizer="bobyqa"))
+summary(glmer_reduced)
+overdisp_fun(glmer_reduced) # no evidence of overdispersion
+
+v <- visreg(fit, 'Days', 'Subject', re.form=(~Days|Subject), plot=FALSE)
+plot(v)
+plot(v, overlay=TRUE)
+
+test <- visreg(glmer_reduced, xvar=c("sc.gall_size"), by="Genotype", re.form=(~1|Genotype), plot=FALSE, 
+       scale="response", partial=TRUE, gg=TRUE, overlay=TRUE,
+       cond = list(sc.gall_size=0, sc.clutch_size=0, sc.female_preference=0))
+plot(test, partial=TRUE, overlay=TRUE)
+visreg(glmer_reduced, xvar=c("sc.gall_size"), scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
+visreg(glmer_reduced, xvar=c("sc.clutch_size"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
+visreg(glmer_reduced, xvar=c("sc.female_preference"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
+
+## GLMER full
+glmer_full <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
+                           Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
+                         data = gall_selection.df)
+summary(glmer_full$gam); summary(glmer_full$mer)
+round(vcov(glmer_full$mer), 2) # no evidence of correlations that would confound interpretations of statistical main and interaction effects.
+
+glmer_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) +
+                           I(sc.gall_size^2) + I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
+                         data = gall_selection.df)
+summary(glmer_reduced$gam); summary(glmer_reduced$mer, correlation=TRUE)
+visreg(glmer_reduced$gam, xvar="sc.gall_size", by="sc.clutch_size", scale="response")
+
+glmer_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum*sc.clutch_size + sc.gall_size + sc.female_preference +
+                               I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
+                         data = gall_selection.df)
+summary(glmer_reduced2$gam); summary(glmer_reduced2$mer)
+
+AIC(glmer_full$mer, glmer_reduced$mer, glmer_reduced2$mer)
+
+## LMER full
+m3 <- gamm4(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
+                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)),
+            family = gaussian(link=identity),
+            random = ~(1|Genotype/Plant_Position/Gall_Number),
+            data = gall_selection.df)
+
+AIC(m1$mer, m2$mer, m3$mer) # suggests that the GLMM is best
+
+## Do we need a model with interactions between traits?
+m4 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
+                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
+                 data = gall_selection.df)
+AIC(m2$mer, m4$mer) # AIC suggests not
+
+## Do we need a model with non-linear trait effects?
+m5 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
+                   (I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
+                 data = gall_selection.df)
+AIC(m4$mer, m5$mer) # 
+summary(m5$gam)
+summary(m5$mer)
+
+m6 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference), 
+                 data = gall_selection.df)
+AIC(m5$mer, m6$mer) 
 ```

### 2018-05-31 supp_mat_complexity_selection.Rmd
updating figures with relative fitness and bootstrapped confidence intervals.

@@
   filter(Treatment.focus == "Control") %>%
-  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         gall_individuals = gall_individuals - mean(gall_individuals),
-         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  mutate(sc.gall_size = (Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm),
+         sc.clutch_size = (gall_individuals - mean(gall_individuals))/sd(gall_individuals),
+         sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
 
@@
   filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
-  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         gall_individuals = gall_individuals - mean(gall_individuals),
-         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  mutate(sc.gall_size = (Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm),
+         sc.clutch_size = (gall_individuals - mean(gall_individuals))/sd(gall_individuals),
+         sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
 ```
@@
 }
+
+inverse_logit <- function(x) exp(x)/(1+exp(x))
 ```
@@
 AIC(m5$mer, m6$mer) 
+```
+
+```{r}
+
+## Control treatment
+Wbar_model_control <-  glmer(gall_survival ~ 1 + (1|Genotype/Plant_Position/Gall_Number),
+                         family=binomial(link=logit),
+                         data = control_df, glmerControl(optimizer="bobyqa"))
+Wbar_control <- inverse_logit(fixef(Wbar_model_control))
+
+glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         family=binomial(link=logit),
+                         data = control_df, glmerControl(optimizer="bobyqa"))
+summary(glmer_control)
+```
+
+```{r}
+
+## Ectoparasitoid exclusion treatment
+Wbar_model_treatment <-  glmer(gall_survival ~ 1 + (1|Genotype/Plant_Position/Gall_Number),
+                         family=binomial(link=logit),
+                         data = treatment_df, glmerControl(optimizer="bobyqa"))
+Wbar_treatment <- inverse_logit(fixef(Wbar_model_treatment))
+
+glmer_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         family=binomial(link=logit),
+                         data = treatment_df, glmerControl(optimizer="bobyqa"))
+summary(glmer_treatment)
+```
+
+```{r}
+distribution_female_preference <- distinct(.data=gall_selection.df, Plant_Position, Density_per_100_shoots)$Density_per_100_shoots 
+HPDinterval_female_preference <- coda::HPDinterval(coda::as.mcmc(scale(distribution_female_preference)), prob=0.95); HPDinterval_female_preference
+
+bind_rows(mutate(visreg(glmer_treatment, xvar="sc.female_preference", scale="response", plot=F)$fit, 
+                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
+          mutate(visreg(glmer_control, xvar="sc.female_preference", scale="response", plot=F)$fit, 
+                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
+  ggplot(., aes(x=sc.female_preference, y=`Relative fitness`, color=Treatment)) +
+  geom_line() +
+  scale_x_continuous(limits = c(HPDinterval_female_preference[1], HPDinterval_female_preference[2]))
+```
+
+```{r}
+distribution_clutch_size <- distinct(.data=gall_selection.df, Plant_Position, Gall_Number, gall_individuals)$gall_individuals
+HPDinterval_clutch_size <- coda::HPDinterval(coda::as.mcmc(scale(distribution_clutch_size)), prob=0.95); HPDinterval_clutch_size
+
+bind_rows(mutate(visreg(glmer_treatment, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
+                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
+          mutate(visreg(glmer_control, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
+                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
+  ggplot(., aes(x=sc.clutch_size, y=`Relative fitness`, color=Treatment)) +
+  geom_line() +
+  scale_x_continuous(limits = c(HPDinterval_clutch_size[1], HPDinterval_clutch_size[2]))
+```
+
+```{r}
+distribution_gall_size <- distinct(.data=gall_selection.df, Plant_Position, Gall_Number, Gall_Letter, Gall_Height_mm)$Gall_Height_mm
+HPDinterval_gall_size <- coda::HPDinterval(coda::as.mcmc(scale(distribution_gall_size)), prob=0.95); HPDinterval_gall_size
+
+predict_gall_size_df <- data.frame(sc.gall_size = seq(HPDinterval_gall_size[1], HPDinterval_gall_size[2], length.out=100),
+                                   sc.clutch_size = 0,
+                                   sc.female_preference = 0)
+model_matrix_gall_size <- model.matrix(~sc.gall_size + sc.clutch_size + sc.female_preference, predict_gall_size_df)
+
+# ref: https://www.r-bloggers.com/confidence-intervals-for-prediction-in-glmms/
+boot_treatment_gall_size <-bootMer(glmer_treatment, FUN = function(.) inverse_logit(model_matrix_gall_size %*% fixef(.)), nsim=200)
+se_treatment_gall_size <- apply(boot_treatment_gall_size$t, 2, function(x) x[order(x)])
+boot_lower <- se_treatment_gall_size[1, ]
+boot_upper <- se_treatment_gall_size[2, ]
+
+bind_rows(mutate(visreg(glmer_treatment, xvar="sc.gall_size", scale="response", plot=F)$fit, 
+                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
+          mutate(visreg(glmer_control, xvar="sc.gall_size", scale="response", plot=F)$fit, 
+                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
+  ggplot(., aes(x=sc.gall_size, y=`Relative fitness`, color=Treatment)) +
+  geom_line() +
+  geom_ribbon(aes(ymin=boot_lower, ymax=boot_upper)) +
+  scale_x_continuous(limits = c(HPDinterval_gall_size[1], HPDinterval_gall_size[2]))
 ```

### 2018-06-06 supp_mat_complexity_selection.Rmd
working on visualizations of fitness landscapes.

@@
 inverse_logit <- function(x) exp(x)/(1+exp(x))
+
+Beta_avg_grad <- function(logistic_model, mean_fitness) {
+  brackets <- predict(logistic_model, type = "response") * (1 - predict(logistic_model, type="response"))
+  gradient <- mean(brackets) * fixef(logistic_model) / mean_fitness 
+  return(gradient)
+}
 ```
@@
 ```{r}
+## Calculate directional selection gradients
+# following method of Janzen and Stern
+
+Beta_avg_grad <- function(.) {
+  mean_fitness <- inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
+  mean(brackets) * fixef(.)[-1] / mean_fitness 
+}
+
+```
+
+```{r}
 
 ## Control treatment
-Wbar_model_control <-  glmer(gall_survival ~ 1 + (1|Genotype/Plant_Position/Gall_Number),
-                         family=binomial(link=logit),
-                         data = control_df, glmerControl(optimizer="bobyqa"))
-Wbar_control <- inverse_logit(fixef(Wbar_model_control))
 
+# GLMM
 glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
@@
 summary(glmer_control)
+
+# Mean fitness
+Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+# Use parametric bootstrapping to get confidence intervals for selection gradients
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+
+data.frame(Beta_avg_grad = round(Beta_avg_grad(glmer_control),2),
+           lowerCI_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
+           upperCI_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2)) %>%
+  knitr::kable(.)
 ```
@@
 ## Ectoparasitoid exclusion treatment
-Wbar_model_treatment <-  glmer(gall_survival ~ 1 + (1|Genotype/Plant_Position/Gall_Number),
-                         family=binomial(link=logit),
-                         data = treatment_df, glmerControl(optimizer="bobyqa"))
-Wbar_treatment <- inverse_logit(fixef(Wbar_model_treatment))
 
+# GLMM
 glmer_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
@@
 summary(glmer_treatment)
+
+# Mean fitness
+Wbar_treatment <- inverse_logit(fixef(update(glmer_treatment, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+# Use parametric bootstrapping to get confidence intervals for selection gradients
+boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=10)
+
+data.frame(Beta_avg_grad = round(Beta_avg_grad(glmer_treatment),2),
+           lowerCI_2.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
+           upperCI_97.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2)) %>%
+  knitr::kable(.)
+```
+
+```{r}
+## Custom function to calculate relative fitness intervals for my models
+relative_fitness_intervals <- function(logistic_model, newdata, bootstraps){
+  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
+  model_null <- model.matrix(~1, newdata)
+
+  get_relative_fitness <- function(.) {
+  #mean_fitness <- mean(inverse_logit(model_null %*% fixef(.))) #fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
+  absolute_fitness #/ mean_fitness # mean(absolute_fitness) # 
+  }
+
+  get_bootstraps <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])
+
+  mean_fitness <- mean(get_relative_fitness(logistic_model))
+
+  return(data.frame(relative_fitness = get_relative_fitness(logistic_model)/mean_fitness,
+                    lower_2.5 = get_intervals[1, ]/mean_fitness,
+                    upper_97.5 = get_intervals[2, ]/mean_fitness,
+                    newdata))
+}
+```
+
+Illustrating the relationship between phenotype and mean fitness depends critically on the range of parameters shown.
+Perhaps this is what it is a good idea to show it based on the actual phenotypic distributions, or for 1 +/- SD
+
+```{r}
+RF_treatment_gall_size <- relative_fitness_intervals(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = seq(min(treatment_df$sc.gall_size),
+                        max(treatment_df$sc.gall_size),
+                        length.out = 100),
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=200)
+
+mean(RF_treatment_gall_size$relative_fitness)
+
+RF_control_gall_size <- relative_fitness_intervals(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = seq(min(control_df$sc.gall_size),
+                        max(control_df$sc.gall_size),
+                        length.out = 100),
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=200)
+
+mean(RF_control_gall_size$relative_fitness)
+
+bind_rows(mutate(RF_treatment_gall_size, Treatment = "Simple"),
+          mutate(RF_control_gall_size, Treatment = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness, color=Treatment, fill=Treatment)) +
+  geom_hline(yintercept=1, linetype="dotted") +
+  geom_line() +
+  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5)
+```
+
+```{r}
+RF_treatment_clutch_size <- relative_fitness_intervals(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(min(treatment_df$sc.clutch_size),
+                          max(treatment_df$sc.clutch_size),
+                          length.out = 100),
+     sc.female_preference = 0),
+  bootstraps=200)
+
+mean(RF_treatment_clutch_size$relative_fitness)
+
+RF_control_clutch_size <- relative_fitness_intervals(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(min(control_df$sc.clutch_size),
+                        max(control_df$sc.clutch_size),
+                        length.out = 100),
+     sc.female_preference = 0),
+  bootstraps=200)
+
+mean(RF_control_clutch_size$relative_fitness)
+
+bind_rows(mutate(RF_treatment_clutch_size, Treatment = "Simple"),
+          mutate(RF_control_clutch_size, Treatment = "Complex")) %>%
+  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, color=Treatment, fill=Treatment)) +
+  geom_hline(yintercept=1, linetype="dotted") +
+  geom_line() +
+  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5)
+```
+
+```{r}
+RF_treatment_female_preference <- relative_fitness_intervals(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0,
+     sc.female_preference = seq(min(treatment_df$sc.female_preference),
+                                max(treatment_df$sc.female_preference),
+                                length.out = 100)),
+  bootstraps=200)
+
+mean(RF_treatment_female_preference$relative_fitness)
+
+RF_control_female_preference <- relative_fitness_intervals(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0,
+     sc.female_preference = seq(min(control_df$sc.female_preference),
+                                max(control_df$sc.female_preference),
+                                length.out = 100)),
+  bootstraps=200)
+
+mean(RF_control_female_preference$relative_fitness)
+
+bind_rows(mutate(RF_treatment_female_preference, Treatment = "Simple"),
+          mutate(RF_control_female_preference, Treatment = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=relative_fitness, color=Treatment, fill=Treatment)) +
+  geom_hline(yintercept=1, linetype="dotted") +
+  geom_line() +
+  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5) +
 ```

### 2018-06-07 supp_mat_complexity_selection.Rmd
some early explorations of directly calculating derivatives

--- 2018-05-31 supp_mat_complexity_selection.Rmd
@@
 control_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Control") %>%
-  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         gall_individuals = gall_individuals - mean(gall_individuals),
-         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  filter(Treatment.focus == "Control") #%>%
+  #mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
+  #       gall_individuals = gall_individuals - mean(gall_individuals),
+  #       Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
 
 treatment_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
-  mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
-         gall_individuals = gall_individuals - mean(gall_individuals),
-         Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
+  filter(Treatment.focus == "Ectoparasitoid exclusion") #%>%
+  #mutate(Gall_Height_mm = Gall_Height_mm - mean(Gall_Height_mm),
+  #       gall_individuals = gall_individuals - mean(gall_individuals),
+  #       Density_per_100_shoots = Density_per_100_shoots - mean(Density_per_100_shoots))
 ```
 
+Custom functions to avoid repetitive code
 ```{r FUNCTIONS}
@@
 gam.plot <- function(gam.model, ...) {
-  plot(gam.model, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
+  plot(gam.model, se = TRUE, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
 }
@@
 }
-
-overdisp_fun <- function(model) {
-  ## number of variance parameters in 
-  ##   an n-by-n variance-covariance matrix
-  vpars <- function(m) {
-    nrow(m)*(nrow(m)+1)/2
-  }
-  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
-  rdf <- nrow(model.frame(model))-model.df
-  rp <- residuals(model,type="pearson")
-  Pearson.chisq <- sum(rp^2)
-  prat <- Pearson.chisq/rdf
-  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
-  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
-}
-```
-
-```{r}
-# convert treatment to factor to use as 'by' variable in gamm.model
-gall_selection.df <- gall_selection.df %>%
-  mutate(Treatment_contr.sum=factor(Treatment.focus), 
-         sc.gall_size = as.numeric(scale(Gall_Height_mm)),
-         sc.clutch_size = as.numeric(scale(gall_individuals)),
-         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
-contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
-# Inspect contrasts:
-contrasts(gall_selection.df$Treatment_contr.sum)
-
-## AIC MODEL SELECTION
-# Note that I use gamm4 to fit all models to maintain consistency
-
-## GAMM full
-m1 <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                   s(sc.gall_size, by=Treatment_contr.sum) + 
-                   s(sc.clutch_size, by=Treatment_contr.sum) + 
-                   s(sc.female_preference, by=Treatment_contr.sum) + 
-                   sc.gall_size:sc.clutch_size + sc.gall_size:sc.clutch_size:Treatment_contr.sum +
-                   sc.gall_size:sc.female_preference + sc.gall_size:sc.female_preference:Treatment_contr.sum +                                 sc.clutch_size:sc.female_preference + sc.clutch_size:sc.female_preference:Treatment_contr.sum,
-                 data = gall_selection.df)
-summary(m1$gam); summary(m1$mer)
-
-gamm_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                             s(sc.gall_size) + 
-                             s(sc.clutch_size, by=Treatment_contr.sum) + 
-                             s(sc.female_preference, by=Treatment_contr.sum),
-                 data = gall_selection.df)
-summary(gamm_reduced$gam); summary(gamm_reduced$mer)
-
-gamm_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                             sc.gall_size + 
-                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
-                             s(sc.female_preference, by=Treatment_contr.sum),
-                 data = gall_selection.df)
-summary(gamm_reduced2$gam); summary(gamm_reduced2$mer)
-
-GLMM_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                             sc.gall_size + 
-                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
-                             sc.female_preference + sc.female_preference:Treatment_contr.sum,
-                            data = gall_selection.df)
-summary(GLMM_reduced$gam); summary(GLMM_reduced$mer)
-
-AIC(m1$mer, gamm_reduced$mer, gamm_reduced2$mer, GLMM_reduced$mer)
-
-glmer_reduced <- glmer(gall_survival ~ Treatment_contr.sum +
-                             sc.gall_size + 
-                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
-                             sc.female_preference + sc.female_preference:Treatment_contr.sum +
-                             (1|Genotype/Plant_Position/Gall_Number),
-                       family=binomial(link=logit),
-                       data = gall_selection.df, glmerControl(optimizer="bobyqa"))
-summary(glmer_reduced)
-overdisp_fun(glmer_reduced) # no evidence of overdispersion
-
-v <- visreg(fit, 'Days', 'Subject', re.form=(~Days|Subject), plot=FALSE)
-plot(v)
-plot(v, overlay=TRUE)
-
-test <- visreg(glmer_reduced, xvar=c("sc.gall_size"), by="Genotype", re.form=(~1|Genotype), plot=FALSE, 
-       scale="response", partial=TRUE, gg=TRUE, overlay=TRUE,
-       cond = list(sc.gall_size=0, sc.clutch_size=0, sc.female_preference=0))
-plot(test, partial=TRUE, overlay=TRUE)
-visreg(glmer_reduced, xvar=c("sc.gall_size"), scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
-visreg(glmer_reduced, xvar=c("sc.clutch_size"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
-visreg(glmer_reduced, xvar=c("sc.female_preference"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
-
-## GLMER full
-glmer_full <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
-                           Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
-                         data = gall_selection.df)
-summary(glmer_full$gam); summary(glmer_full$mer)
-round(vcov(glmer_full$mer), 2) # no evidence of correlations that would confound interpretations of statistical main and interaction effects.
-
-glmer_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) +
-                           I(sc.gall_size^2) + I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
-                         data = gall_selection.df)
-summary(glmer_reduced$gam); summary(glmer_reduced$mer, correlation=TRUE)
-visreg(glmer_reduced$gam, xvar="sc.gall_size", by="sc.clutch_size", scale="response")
-
-glmer_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum*sc.clutch_size + sc.gall_size + sc.female_preference +
-                               I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
-                         data = gall_selection.df)
-summary(glmer_reduced2$gam); summary(glmer_reduced2$mer)
-
-AIC(glmer_full$mer, glmer_reduced$mer, glmer_reduced2$mer)
-
-## LMER full
-m3 <- gamm4(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
-                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)),
-            family = gaussian(link=identity),
-            random = ~(1|Genotype/Plant_Position/Gall_Number),
-            data = gall_selection.df)
-
-AIC(m1$mer, m2$mer, m3$mer) # suggests that the GLMM is best
-
-## Do we need a model with interactions between traits?
-m4 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
-                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
-                 data = gall_selection.df)
-AIC(m2$mer, m4$mer) # AIC suggests not
-
-## Do we need a model with non-linear trait effects?
-m5 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
-                   (I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
-                 data = gall_selection.df)
-AIC(m4$mer, m5$mer) # 
-summary(m5$gam)
-summary(m5$mer)
-
-m6 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference), 
-                 data = gall_selection.df)
-AIC(m5$mer, m6$mer) 
 ```
@@
 ## CONTROL PLANTS ----
-gamm_red.control <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots + 
-                                  gall_individuals:Density_per_100_shoots,
+gamm_full.control <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = control_df)
-summary(gamm_full.control$gam)
-summary(gamm_full.control$mer)
+summary(gamm_full.control$gam); summary(gamm_full.control$mer)
 
-gamm_red.control <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
+glmm_full.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = control_df)
-summary(gamm_red.control$gam)
-summary(gamm_red.control$mer)
+summary(glmm_full.control$gam); summary(glmm_full.control$mer)
 
-gamm_red.control.noG <- gamm4(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
-                                  random = ~(1|Plant_Position/Gall_Number), 
-                                  family = binomial(link = logit),
+gamm_red.control <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots),
                                 data = control_df)
-summary(gamm_red.control.noG$gam)
-summary(gamm_red.control.noG$mer)
+summary(gamm_red.control$gam); summary(gamm_red.control$mer)
 
-glmm_full.control <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots,
+glmm_quad.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2),
                                 data = control_df)
-summary(glmm_full.control$gam)
-summary(glmm_full.control$mer)
+summary(glmm_quad.control$gam); summary(glmm_quad.control$mer)
 
-glmm_red.control <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+glmm_lin.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
                                 data = control_df)
-summary(glmm_red.control$gam)
-summary(glmm_red.control$mer)
+summary(glmm_lin.control$gam); summary(glmm_lin.control$mer)
 
-lmm_red.control <- gamm4(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
-                           random = ~(1|Plant_Position/Gall_Number),
-                                data = control_df, family=gaussian())
-summary(lmm_red.control$gam)
-summary(lmm_red.control$mer)
+lmm_lin.control <- gamm4(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
+                          data = control_df,
+                          random = ~(1|Genotype/Plant_Position/Gall_Number), 
+                          family = gaussian(link = identity))
+summary(lmm_lin.control$gam); summary(lmm_lin.control$mer)
 
-AIC(gamm_full.control$mer, gamm_red.control$mer, gamm_red.control.noG$mer, glmm_full.control$mer, glmm_red.control$mer, lmm_red.control$mer)
+glmm_lin.red.control <- gamm.model(gall_survival ~ Gall_Height_mm,
+                                data = control_df)
+summary(glmm_lin.red.control$gam); summary(glmm_lin.red.control$mer)
+
+glmm_null.control <- gamm.model(gall_survival ~ 1,
+                                data = control_df)
+summary(glmm_null.control$gam); summary(glmm_null.control$mer)
+
+glmm_lin.red.noRE.control <- gamm4(gall_survival ~ Gall_Height_mm,
+                          data = control_df,
+                          random = ~(1|Gall_Number), 
+                          family = binomial(link = logit))
+summary(glmm_lin.red.noRE.control$gam); summary(glmm_lin.red.noRE.control$mer)
+
+AIC(gamm_full.control$mer, glmm_full.control$mer, gamm_red.control$mer, glmm_quad.control$mer, glmm_lin.control$mer, lmm_lin.control$mer, glmm_lin.red.control$mer, glmm_null.control$mer, glmm_lin.red.noRE.control$mer)
 
 ## TREATMENT PLANTS ----
-gamm_red.treatment <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots + 
-                                  gall_individuals:Density_per_100_shoots,
+gamm_full.treatment <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = treatment_df)
-summary(gamm_full.treatment$gam)
-summary(gamm_full.treatment$mer)
+summary(gamm_full.treatment$gam); summary(gamm_full.treatment$mer)
 
-gamm_red.treatment <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
+glmm_full.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = treatment_df)
-summary(gamm_red.treatment$gam)
-summary(gamm_red.treatment$mer)
+summary(glmm_full.treatment$gam); summary(glmm_full.treatment$mer)
 
-gamm_red.treatment.noG <- gamm4(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
-                                  random = ~(1|Plant_Position/Gall_Number), 
-                                  family = binomial(link = logit),
+gamm_red.treatment <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots),
                                 data = treatment_df)
-summary(gamm_red.treatment.noG$gam)
-summary(gamm_red.treatment.noG$mer)
+summary(gamm_red.treatment$gam); summary(gamm_red.treatment$mer)
 
-glmm_full.treatment <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots,
+glmm_quad.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2),
                                 data = treatment_df)
-summary(glmm_full.treatment$gam)
-summary(glmm_full.treatment$mer)
+summary(glmm_quad.treatment$gam); summary(glmm_quad.treatment$mer)
 
-glmm_red.treatment <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+glmm_lin.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
                                 data = treatment_df)
-summary(glmm_red.treatment$gam)
-summary(glmm_red.treatment$mer)
+summary(glmm_lin.treatment$gam); summary(glmm_lin.treatment$mer)
 
-lmm_red.treatment <- gamm4(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
-                           random = ~(1|Plant_Position/Gall_Number),
-                                data = treatment_df, family=gaussian())
-summary(lmm_red.treatment$gam)
-summary(lmm_red.treatment$mer)
+lmm_lin.treatment <- gamm4(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
+                          data = treatment_df,
+                          random = ~(1|Genotype/Plant_Position/Gall_Number), 
+                          family = gaussian(link = identity))
+summary(lmm_lin.treatment$gam); summary(lmm_lin.treatment$mer)
 
-AIC(gamm_full.treatment$mer, gamm_red.treatment$mer, gamm_red.treatment.noG$mer, glmm_full.treatment$mer, glmm_red.treatment$mer, lmm_red.treatment$mer)
+glmm_quad.red.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots + I(Density_per_100_shoots^2),
+                                data = treatment_df)
+summary(glmm_quad.red.treatment$gam); summary(glmm_quad.red.treatment$mer)
 
-## Linear mixed-models
-lmm_full.control <- lmer(gall_survival/0.45 ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots +
-                           (1|Genotype/Plant_Position/Gall_Number),
-                                data = control_df)
-summary(lmm_full.control)
-car::Anova(lmm_full.control, test="F")
-visreg::visreg(lmm_full.control)
+glmm_null.treatment <- gamm.model(gall_survival ~ 1,
+                                data = treatment_df)
+summary(glmm_null.treatment$gam); summary(glmm_null.treatment$mer)
 
-lmm_full.treatment <- lmer(gall_survival/0.6 ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots +
-                             (1|Genotype/Plant_Position/Gall_Number),
-                                data = treatment_df)
-summary(lmm_full.treatment)
-car::Anova(lmm_full.treatment, test="F")
+glmm_lin.red.noRE.treatment <- gamm4(gall_survival ~ Gall_Height_mm,
+                          data = treatment_df,
+                          random = ~(1|Gall_Number), 
+                          family = binomial(link = logit))
+summary(glmm_lin.red.noRE.treatment$gam); summary(glmm_lin.red.noRE.treatment$mer)
 
-lmm_red.treatment <- lmer(gall_survival/0.6 ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                              (1|Genotype/Plant_Position/Gall_Number),
-                                data = treatment_df)
-summary(lmm_red.treatment)
-car::Anova(lmm_red.treatment, test="F")
-visreg::visreg(lmm_red.treatment)
+AIC(gamm_full.treatment$mer, glmm_full.treatment$mer, gamm_red.treatment$mer, glmm_quad.treatment$mer, glmm_lin.treatment$mer, lmm_lin.treatment$mer, glmm_lin.red.treatment$mer, glmm_null.treatment$mer, glmm_lin.red.noRE.treatment$mer, glmm_quad.red.treatment$mer)
+```
 
-AIC(lmm_full.treatment, lmm_red.treatment)
+```{r}
+library(schoenberg)
+pointwise <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))})
+simultaneous <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))}, type = "simultaneous", seWithMean=TRUE)
 
-gall_selection.df$relative.fit <- with(gall_selection.df, ifelse(Treatment.focus=="Control", gall_survival/0.45, gall_survival/0.6))
+compare.confint <- bind_rows(mutate(pointwise, confint = "pointwise"), mutate(simultaneous, confint = "simultaneous")) 
+compare.confint$confint <- relevel(factor(compare.confint$confint), ref = "simultaneous")
 
-lmm_full <- lmer(relative.fit ~ poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) + 
-                                poly(Gall_Height_mm,2):Treatment.focus + 
-                                poly(gall_individuals,2):Treatment.focus + 
-                                poly(Density_per_100_shoots,2):Treatment.focus +
-                                (1|Genotype/Plant_Position/Gall_Number),
-                                data = gall_selection.df)
-summary(lmm_full)
-car::Anova(lmm_full, test="F")
-visreg::visreg(lmm_full, xvar="Gall_Height_mm", by="Treatment.focus")
-visreg::visreg(lmm_full, xvar="gall_individuals", by="Treatment.focus")
-visreg::visreg(lmm_full, xvar="Density_per_100_shoots", by="Treatment.focus")
+ggplot(compare.confint, aes(x=Gall_Height_mm)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper), alpha=0.25) +
+  geom_line(aes(y=est), color="black") +
+  facet_wrap(~confint)
+
+schluter <- gam.plot(gamm_red.control$gam)
+schluter
+
+gam.plot(glmm_lin.red.control$gam, all.terms=TRUE)
+test <- plot(glmm_lin.red.control$gam, all.terms=TRUE)
+gam.gradients(mod = glmm_lin.red.control$gam, phenotype = "Gall_Height_mm", se.method = "n")
+coef(glmm_lin.red.control$gam)
+
+# test derivative calculations
+control_df$Genotype <- factor(control_df$Genotype)
+control_df$Plant_Position <- factor(control_df$Plant_Position)
+control_df$Gall_Number <- factor(control_df$Gall_Number)
+A <- gam(gall_survival ~ s(Gall_Height_mm) + s(Plant_Position, bs="re") + s(Gall_Number, bs="re"), data = control_df, family=binomial(link=logit)) # random=~(1|Genotype/Plant_Position/Gall_Number),
+summary(A)
+
+head(control_df)
+A_withMean <- plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_withMean
+A_only <- plot(A, se = TRUE, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_only
+draw(A)
+
+# new data for prediction
+newDF <- with(control_df, data.frame(Gall_Height_mm = seq(min(Gall_Height_mm),max(Gall_Height_mm),length.out = 100)))
+# prediction of smoothed estimates at each unique year value
+# with standard error    
+B <- predict(A$gam,  newDF, type="response", se.fit=TRUE)
+B
+
+# finite difference approach to derivatives following
+# example from ?predict.gam
+
+eps <- 1e-7
+X0 <- predict(A, newDF, type = 'lpmatrix')
+X0 <- exp(X0)/(1+exp(X0))
+
+newDFeps_p <- newDF + eps
+
+X1 <- predict(A, newDFeps_p, type = 'lpmatrix')
+X1 <- exp(X1)/(1+exp(X1))
+# finite difference approximation of first derivative
+# the design matrix
+Xp <- (X0 - X1) / eps
+Xp
+# first derivative
+fd_d1 <- Xp %*% coef(A)
+fd_d1/mean_fit
+# second derivative
+newDFeps_m <- newDF - eps
+
+X_1 <- predict(A$gam, newDFeps_m, type = 'lpmatrix')
+# design matrix for second derivative
+Xpp <- (X1 + X_1 - 2*X0)  / eps^2
+# second derivative
+fd_d2 <- Xpp %*% coef(A$gam)
+
+exp(fd_d1) / ( 1+exp(fd_d1))  # type = "response"
+exp(fd_d2) / ( 1+exp(fd_d2))  # type = "response"
+
+mean(fd_d1)/mean_fit
+mean(fd_d2)/mean_fit
+
+gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
+
+coef(A)
+mean_fit <- mean(control_df$gall_survival)
+fderiv_size <- fderiv(A, newdata = data.frame(Gall_Height_mm = mean(control_df$Gall_Height_mm)), offset = mean_fit)
+test <- fderiv_size$derivatives$`s(Gall_Height_mm)`$deriv
+exp(test)/(1+exp(test))
+
+plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))})
+diff <- .Machine$double.eps^(1/3)
+predicts <- predict(A, newdata = data.frame(Gall_Height_mm = c(mean(control_df$Gall_Height_mm)-diff,mean(control_df$Gall_Height_mm)+diff)), type="lpmatrix")
+tests <- predicts %*% coef(A)
+exp(tests)/(1+exp(tests))
+t1 <- exp(predicts[2])/(1+exp(predicts[2]));t1
+t2 <- exp(predicts[1])/(1+exp(predicts[1]));t2
+((t1-t2)/(diff*2))/mean(control_df$gall_survival)
+gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
+
+	Wbar <- function(x, mod, phenotype,covariates) {
+    		new.d <- as.data.frame(mod$model[,c(phenotype,covariates)])
+    		names(new.d)<-c(phenotype,covariates)
+    		new.d2<-new.d
+    		for (i in 1:length(x)) {
+    		    new.d[,as.character(phenotype[i])] <-
+    		    new.d[,as.character(phenotype[i])]+x[i]
+    		}
+
+    		p <- predict.gam(
+			   object=mod,
+    	 	   newdata=new.d,
+    	 	   newdata.guaranteed=TRUE,
+    	 	   type="response"
+    		)
+    	return(mean(p))
+	}
+	as.data.frame(A$model[ ,"Gall_Height_mm"])
+	#mean(control_df$gall_survival)
+	Wbar(x=0, mod=A, phenotype="Gall_Height_mm", covariates=NULL)
+first.derivatives <- grad(f=Wbar, x=rep(0, 1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); first.derivatives
+denom <- Wbar(x=rep(0,1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); denom
+first.derivatives/denom
+pracma:::grad
+A$Vp
+A$coefficients
+A_withMean
 ```
+
 Parametric bootstrapping: Currently reported results

### 2018-06-07 AmNat_MS_template.tex
considering trying to write article in Rstudio...

\documentclass[11pt]{article}
\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
\usepackage[utf8]{inputenc}
\usepackage{lineno}
\usepackage{titlesec}
\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}

%%%%%%%%%%%%%%%%%%%%%
% Line numbering
%%%%%%%%%%%%%%%%%%%%%
%\usepackage{lineno}
% Please use line numbering with your initial submission and
% subsequent revisions. After acceptance, please turn line numbering
% off by adding percent signs to the lines %\usepackage{lineno} and
% to %\linenumbers{} and %\modulolinenumbers[3] below.

\title{Template and Guidelines for Using \LaTeX{} in \textit{The~American~Naturalist} }

% This version of the LaTeX template was last updated on
% January 11, 2018.

%%%%%%%%%%%%%%%%%%%%%
% Authorship
%%%%%%%%%%%%%%%%%%%%%
% Please remove authorship information while your paper is under review,
% unless you wish to waive your anonymity under double-blind review. You
% will need to add this information back in to your final files after
% acceptance.

\author{Owen E. Cook$^{1,\ast}$ \\ 
Generic H. Collaborator$^{2,\dag}$ \\ 
Additional Q. Expert$^{3}$}

\date{}

\begin{document}

\maketitle

\noindent{} 1. University of Chicago, Chicago, Illinois 60637;

\noindent{} 2. University of Toronto, Toronto, Ontario M5S 1A5, Canada;

\noindent{} 3. Middle Eastern Technical University, Çankaya, Ankara 06800, Turkey.

\noindent{} $\ast$ Corresponding author; e-mail: amnat@uchicago.edu.

\noindent{} $\dag$ Deceased.

\bigskip

\textit{Manuscript elements}: Figure~1, figure~2, table~1, online appendices~A and B (including figure~A1 and figure~A2). Figure~2 is to print in color.

\bigskip

\textit{Keywords}: Examples, model, template, guidelines.

\bigskip

\textit{Manuscript type}: Article. %Or e-article, note, e-note, natural history miscellany, e-natural history miscellany, comment, reply, invited symposium, or countdown to 150.

\bigskip

\noindent{\footnotesize Prepared using the suggested \LaTeX{} template for \textit{Am.\ Nat.}}

%\linenumbers{}
%\modulolinenumbers[3]

\newpage{}

\section*{Abstract}

Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed non risus. Suspendisse lectus tortor, dignissim sit amet, adipiscing nec, ultricies sed, dolor. Cras elementum ultrices diam.

\newpage{}

\section*{Introduction}

% The journal does not have numbered sections in the main portion of
% articles. Please refrain from using section references (à la
% section~\ref{section:CountingOwlEggs}), and refer to sections by name
% (e.g. section ``Counting Owl Eggs'').

The quick red fox jumps over the lazy brown dog. Furthermore, the quick brown fox jumps over the lazy red dog. In addition, the quick R\"{u}ppell's fox (\textit{Vulpes rueppellii}) jumps over the lazy golden retriever.

\section*{Methods}

Lorem ipsum (\citealt{Xiao2015}) ut velit mauris, egestas sed, gravida nec, ornare ut, mi. Aenean ut orci vel massa suscipit pulvinar. Nulla sollicitudin. Fusce varius, ligula non tempus aliquam, nunc turpis ullamcorper nibh, in tempus sapien eros vitae ligula.

\subsection*{The quickness of the fox}

Lorem ipsum nulla facilisi, despite the findings of \citet{LemKapEx07}. Etiam semper, orci sit amet facilisis interdum, tellus nunc consequat erat, quis viverra nisi diam ut metus. Pellentesque cursus, sapien malesuada euismod iaculis, mauris purus interdum diam, vel vestibulum justo enim vitae tellus. Nunc interdum lorem sit amet diam volutpat tristique. Quisque pulvinar ac metus commodo lacinia (\citealt{Ing11,Xiao2015}).

\subsubsection*{Third-order heading}

Usually two or three levels of heading will be all you need. Journal style even permits a fourth level in case you need it.

\paragraph*{Fourth-order heading}
The quick red fox jumps over the lazy brown dog in this paragraph as well.

\subsection*{The redness of the fox}

As \citet{Xiao2015} argued, phasellus porttitor eros et ante condimentum, eget facilisis orci condimentum. Nulla facilisi. Proin placerat elit blandit, euismod dolor nec, dapibus diam. Mauris posuere malesuada lacus, at elementum lacus auctor eu (fig~\ref{Fig:Jumps}A).

\section*{Results}

Lorem ipsum dolor sit amet. Aenean pulvinar malesuada commodo (see \citealt{DavisEtAl2011}; table~\ref{Table:Okapi}). Sed aliquet mauris odio, in tristique dui egestas a. Etiam eu malesuada quam. Suspendisse tincidunt eu erat sit amet vulputate. Duis at arcu et nisl dictum mattis. Maecenas vel cursus ante. Cras eleifend elit nec velit sollicitudin fermentum in ac mauris. Pellentesque rutrum magna vel elit maximus hendrerit.

\subsection*{The height of the jump}

Aenean eu pellentesque quam (fig.~\ref{Fig:OkapiHorn}). Nam pellentesque augue eu finibus lacinia. Nullam nec justo vitae odio imperdiet rhoncus vitae vitae quam. Pellentesque porttitor metus et lectus ornare, ac cursus urna efficitur (fig~\ref{Fig:Jumps}B).

\subsection*{The laziness of the dog}

Sed sit amet pharetra nisi (video~\ref{VideoExample}, fig.~\ref{Fig:AnotherFigure}). Praesent quis dolor in dolor molestie cursus et ac nisi. Vestibulum ante purus, semper eget est vitae, vehicula ornare nisl. Morbi efficitur euismod enim, nec feugiat tellus cursus eget. Donec mauris nibh, volutpat vehicula viverra at, iaculis congue sem. Praesent eget erat rhoncus erat sollicitudin volutpat.

If you have deposited data to Dryad, you should cite them somewhere in the main text (usually in the Methods or Results sections). A sentence like the following will do. All data are available in the Dryad Digital Repository (\citealt{CookEtAl2015}).

\section*{Discussion}

Nam pulvinar lorem at lorem ultrices, vel accumsan massa feugiat (\citealt{Ing11}). Proin tristique velit eget lacus iaculis, in pellentesque nulla varius. Phasellus sodales est odio, eu pulvinar magna pellentesque eu. Sed ut lobortis eros. Aliquam eget metus turpis. Sed et convallis lectus, id tincidunt enim. In porta nibh ut lacus feugiat, non consequat orci rhoncus. Morbi blandit at augue nec tempor. Sed fringilla ipsum ut justo viverra, ut euismod nisi gravida.

Curabitur non posuere augue, id suscipit orci. Nunc luctus accumsan aliquam. Cras egestas turpis vitae nisl vulputate interdum. Donec pellentesque libero egestas tortor pharetra laoreet. Phasellus facilisis auctor ligula, eu sollicitudin mi sagittis non.

\section*{Conclusion}

Duis pharetra enim at libero cursus, eu commodo mi vestibulum. Nullam eget velit nec lectus viverra sodales. Suspendisse egestas, eros at dictum tincidunt, mi orci laoreet libero, eget rutrum sapien arcu blandit odio.

%%%%%%%%%%%%%%%%%%%%%
% Acknowledgments
%%%%%%%%%%%%%%%%%%%%%
% You may wish to remove the Acknowledgments section while your paper 
% is under review (unless you wish to waive your anonymity under
% double-blind review) if the Acknowledgments reveal your identity.
% If you remove this section, you will need to add it back in to your
% final files after acceptance.

\section*{Acknowledgments}

OEC would like to thank the world. GHC is much indebted to the solar system. AQE was supported by a generous grant from the Milky Way (MW/01010/987654).

\newpage{}

\section*{Appendix A: Supplementary Figures}

% Please reset counters for the appendix (thus normally figure A1, 
% figure A2, table A1, etc.).

% In certain cases, it may be appropriate to have a PRINT appendix in
% addition to (or instead of) an online appendix. In this case, please 
% name the print appendix Appendix A, and any subsequent appendixes (if 
% there are any) should be named Online Appendix B, Online Appendix C,
% etc.

% Counters for each appendix should match the letter of that appendix.
% For example, tables in Appendix C should be numbered table C1, table C2,
% etc. This applies to tables, equations, and figures.

% It's better not to use the \appendix command, because we have some
% formatting peculiarities that \appendix conflicts with.

\renewcommand{\theequation}{A\arabic{equation}}
% redefine the command that creates the equation number.
\renewcommand{\thetable}{A\arabic{table}}
\setcounter{equation}{0}  % reset counter 
\setcounter{figure}{0}
\setcounter{table}{0}

\subsection*{Fox--dog encounters through the ages}

The quick red fox jumps over the lazy brown dog. The quick red fox has always jumped over the lazy brown dog. The quick red fox began jumping over the lazy brown dog in the 19th century and has never ceased from so jumping, as we shall see in figure~\ref{Fig:Jumps}. But there can be surprises (figure~\ref{Fig:JumpsOk}).

If the order and location of figures is not otherwise clear, feel free to include explanatory dummy text like this:

[Figure A1 goes here.]

[Figure A2 goes here.]

\subsection*{Further insights}

Tables in the appendices can appear in the appendix text (see table~\ref{Table:Rivers} for an example), unlike appendix figure legends which should be grouped at the end of the document together with the other figure legends.

\begin{table}[h]
\caption{Various rivers, cities, and animals}
\label{Table:Rivers}
\centering
\begin{tabular}{lll}\hline
River        & City        & Animal            \\ \hline
Chicago      & Chicago     & Raccoon           \\
Des Plaines  & Joliet      & Coyote            \\
Illinois     & Peoria      & Cardinal          \\
Kankakee     & Bourbonnais & White-tailed deer \\
Mississippi  & Galena      & Bald eagle        \\ \hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: See table~\ref{Table:Okapi} below for further table formatting hints.}
\end{table}

Lorem ipsum dolor sit amet, as we have seen in figures~\ref{Fig:Jumps} and \ref{Fig:JumpsOk}.

\newpage{}

\section*{Appendix B: Additional Methods}

\subsection*{Measuring the height of fox jumps without a meterstick}

Pellentesque ac nibh placerat, luctus lectus non, elementum mauris. 
Morbi odio velit, eleifend ut hendrerit vitae, consequat sit amet 
nulla. Pellentesque porttitor vitae nisl quis tempus. Pellentesque 
habitant morbi tristique senectus et netus et malesuada fames ac 
turpis egestas. Praesent ut nisi odio. Vivamus vel lorem gravida 
odio molestie volutpat condimentum et arcu.

\begin{equation}
{ \frac{1}{N_k-1} \sum \limits_{t=1}^{N_k} (M_{tjk} - \bar{M}_{jk})^2}
\end{equation}

\subsection*{Quantifying the brownness of the dog}

Pellentesque eu nulla odio (\citealt{Xiao2015,CookEtAl2015}). Nulla aliquam porta metus, quis malesuada orci faucibus quis. Suspendisse nunc magna, tristique sit amet sollicitudin nec, elementum et lacus. Sed vitae elementum mi. In hac habitasse platea dictumst. Etiam eu tortor elit. Sed ac tortor purus. Aliquam volutpat, odio sit amet posuere pretium, dolor ex interdum ante, sed luctus quam eros ac nulla.

\begin{equation}
{ (\sum \limits_{p=1}^P {n_{sp}})^{-1}\sum \limits_{p=1}^P {n_{sp}Q_{p}}}
\end{equation}

\newpage{}

%%%%%%%%%%%%%%%%%%%%%
% Bibliography
%%%%%%%%%%%%%%%%%%%%%
% You can either type your references following the examples below, or
% compile your BiBTeX database and paste the contents of your .bbl file
% here. The amnatnat.bst style file should work for this---but please
% let us know if you run into any hitches with it!
% The list below includes sample journal articles, book chapters, and
% Dryad references.

\begin{thebibliography}{}

\bibitem[{Cook et~al.(2015)Cook, Collaborator, and Expert}]{CookEtAl2015}
Cook, O.~E., G.~H. Collaborator, and A.~Q. Expert. 2015.
\newblock Data from: Template and guidelines for using \LaTeX{} in \textit{The American Naturalist}.
\newblock American Naturalist, Dryad Digital Repository, http://dx.doi.org/10.5061/dryad.XYZAB.

\bibitem[{Davis et~al.(2011)Davis, Brakora, and Lee}]{DavisEtAl2011}
Davis, E.~B., K.~A. Brakora, and A.~H. Lee. 2011.
\newblock Evolution of ruminant headgear: a review.
\newblock Proceedings of the Royal Society B 278:2857--2865.

\bibitem[{Inglis et~al.(2011)Inglis, Roberts, Gardner, and Buckling}]{Ing11}
Inglis, R.~F., P.~G. Roberts, A.~Gardner, and A.~Buckling. 2011.
\newblock Spite and the scale of competition in \textit{Pseudomonas
  aeruginosa}.
\newblock American Naturalist 178:276--285.

\bibitem[{Lemod\`{e}le et~al.(2007)Lemodele, Kapitelschreiber, and Exemplar}]{LemKapEx07}
Lemod\`{e}le, P.-Q., A.~B. Kapitelschreiber, and C.~D.~E. Exemplar. 2007.
\newblock An exemplary instance of chapters in books.
\newblock Pages 231--245 \emph{in} J.-P. \'{E}crivain and M.~A. Term\'{e}szettud\'{o}s, eds. Inspiring Instances of Brilliant Writing. Truth Pudding Press, Fond du Lac, WI.

\bibitem[{Xiao et~al.(2015)Xiao, McGlinn, and White}]{Xiao2015}
Xiao, X., D.~J. McGlinn, and E.~P. White. 2015.
\newblock A strong test of the maximum entropy theory of ecology.
\newblock American Naturalist 185:E705--E80.

\end{thebibliography}

\newpage{}

\section*{Tables}
\renewcommand{\thetable}{\arabic{table}}
\setcounter{table}{0}

\begin{table}[h]
\caption{Animals in various cities with equations}
\label{Table:Okapi}
\centering
\begin{tabular}{llc}\hline
Animal    & City         & Equation \\ \hline
Dog       & Springfield  & $x+y=z$ \\
Fox       & Indianapolis & $2x+2y=2z$ \\
Okapi$^a$ & Chicago      & $x-y<z$ \\
Badger    & Madison      & $x+2y>z$ \\ \hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: Table titles should be short. Further details should go in a `notes' area after the tabular environment, like this. $^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
\end{table}

\newpage{}

\section*{Figure legends}

\begin{figure}[h!]
%\includegraphics{horn-of-okapi}
\caption{Figure legends can be longer than the titles of tables. However, they should not be excessively long.}
\label{Fig:OkapiHorn}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%
% Videos
%%%%%%%%%%%%%%%%%%%%%
% If you have videos, journal style for them is similar to that for
% figures. You'll want to include a still image (such as a JPEG)
% to give your readers a preview of what the video looks like.

%%%%% Include the text below if you have videos

\renewcommand{\figurename}{Video} 
\setcounter{figure}{0}
% Thanks to Flo Debarre for the pro tip of putting
% \renewcommand{\figurename}{Video} before the Video legend and
% \renewcommand{\figurename}{Figure} after it!

\begin{figure}[h!]
%\includegraphics{VideoScreengrab.jpg}
\caption{Video legends can follow the same principles as figure legends. Counters should be set and reset so that videos and figures are enumerated separately.}
\label{VideoExample}
\end{figure}

\renewcommand{\figurename}{Figure}
\setcounter{figure}{1}

%%%%% Include the above if you have videos

\begin{figure}[h!]
%\includegraphics{elegance}
\caption{In this way, figure legends can be listed at the end of the document, with references that work, even though the graphic itself should be included for final files after acceptance. Instead, upload the relevant figure files separately to Editorial Manager; Editorial Manager should insert them at the end of the PDF automatically.}
\label{Fig:AnotherFigure}
\end{figure}

\subsection*{Online figure legends}

\renewcommand{\thefigure}{A\arabic{figure}}
\setcounter{figure}{0}

\begin{figure}[h!]
%\includegraphics{jumps20m}
\caption{\textit{A}, the quick red fox proceeding to jump 20~m straight into the air over not one, but several lazy dogs. \textit{B}, the quick red fox landing gracefully despite the skepticism of naysayers.}
\label{Fig:Jumps}
\end{figure}

\begin{figure}[h!]
%\includegraphics{jumps20m}
\caption{The quicker the red fox jumps, the likelier it is to land near an okapi. For further details, see \citet{LemKapEx07}.}
\label{Fig:JumpsOk}
\end{figure}

\renewcommand{\thefigure}{B\arabic{figure}}
\setcounter{figure}{0}

\end{document}

### 2018-06-07 manuscript.Rmd
considering trying to write article in Rstudio...

---
title: "Food-web complexity flattens the fitness landscape of an insect herbivore"
author: "Matthew A. Barbour"
date: "6/4/2018"
output: 
  pdf_document:
    template: AmNat_MS_template.tex
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. You can embed an R code chunk like this:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-06-07 supp_mat_complexity_selection.Rmd

--- 2018-06-06 supp_mat_complexity_selection.Rmd
@@
 
+Custom functions to avoid repetitive code
 ```{r FUNCTIONS}
@@
 ## CONTROL PLANTS ----
-gamm_red.control <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots + 
-                                  gall_individuals:Density_per_100_shoots,
+gamm_full.control <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = control_df)
-summary(gamm_full.control$gam)
-summary(gamm_full.control$mer)
-
-gamm_red.control <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
+summary(gamm_full.control$gam); summary(gamm_full.control$mer)
+
+glmm_full.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = control_df)
-summary(gamm_red.control$gam)
-summary(gamm_red.control$mer)
-
-gamm_red.control.noG <- gamm4(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
-                                  random = ~(1|Plant_Position/Gall_Number), 
-                                  family = binomial(link = logit),
+summary(glmm_full.control$gam); summary(glmm_full.control$mer)
+
+gamm_red.control <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots),
                                 data = control_df)
-summary(gamm_red.control.noG$gam)
-summary(gamm_red.control.noG$mer)
-
-glmm_full.control <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots,
+summary(gamm_red.control$gam); summary(gamm_red.control$mer)
+
+glmm_quad.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2),
                                 data = control_df)
-summary(glmm_full.control$gam)
-summary(glmm_full.control$mer)
-
-glmm_red.control <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+summary(glmm_quad.control$gam); summary(glmm_quad.control$mer)
+
+glmm_lin.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
                                 data = control_df)
-summary(glmm_red.control$gam)
-summary(glmm_red.control$mer)
-
-lmm_red.control <- gamm4(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
-                           random = ~(1|Plant_Position/Gall_Number),
-                                data = control_df, family=gaussian())
-summary(lmm_red.control$gam)
-summary(lmm_red.control$mer)
-
-AIC(gamm_full.control$mer, gamm_red.control$mer, gamm_red.control.noG$mer, glmm_full.control$mer, glmm_red.control$mer, lmm_red.control$mer)
+summary(glmm_lin.control$gam); summary(glmm_lin.control$mer)
+
+lmm_lin.control <- gamm4(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
+                          data = control_df,
+                          random = ~(1|Genotype/Plant_Position/Gall_Number), 
+                          family = gaussian(link = identity))
+summary(lmm_lin.control$gam); summary(lmm_lin.control$mer)
+
+glmm_lin.red.control <- gamm.model(gall_survival ~ Gall_Height_mm,
+                                data = control_df)
+summary(glmm_lin.red.control$gam); summary(glmm_lin.red.control$mer)
+
+glmm_null.control <- gamm.model(gall_survival ~ 1,
+                                data = control_df)
+summary(glmm_null.control$gam); summary(glmm_null.control$mer)
+
+glmm_lin.red.noRE.control <- gamm4(gall_survival ~ Gall_Height_mm,
+                          data = control_df,
+                          random = ~(1|Gall_Number), 
+                          family = binomial(link = logit))
+summary(glmm_lin.red.noRE.control$gam); summary(glmm_lin.red.noRE.control$mer)
+
+AIC(gamm_full.control$mer, glmm_full.control$mer, gamm_red.control$mer, glmm_quad.control$mer, glmm_lin.control$mer, lmm_lin.control$mer, glmm_lin.red.control$mer, glmm_null.control$mer, glmm_lin.red.noRE.control$mer)
 
 ## TREATMENT PLANTS ----
-gamm_red.treatment <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots + 
-                                  gall_individuals:Density_per_100_shoots,
+gamm_full.treatment <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = treatment_df)
-summary(gamm_full.treatment$gam)
-summary(gamm_full.treatment$mer)
-
-gamm_red.treatment <- gamm.model(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
+summary(gamm_full.treatment$gam); summary(gamm_full.treatment$mer)
+
+glmm_full.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2) +
+                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
                                 data = treatment_df)
-summary(gamm_red.treatment$gam)
-summary(gamm_red.treatment$mer)
-
-gamm_red.treatment.noG <- gamm4(gall_survival ~ 
-                                  s(Gall_Height_mm) + 
-                                  s(gall_individuals, k=9) + 
-                                  s(Density_per_100_shoots),
-                                  random = ~(1|Plant_Position/Gall_Number), 
-                                  family = binomial(link = logit),
+summary(glmm_full.treatment$gam); summary(glmm_full.treatment$mer)
+
+gamm_red.treatment <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots),
                                 data = treatment_df)
-summary(gamm_red.treatment.noG$gam)
-summary(gamm_red.treatment.noG$mer)
-
-glmm_full.treatment <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots,
+summary(gamm_red.treatment$gam); summary(gamm_red.treatment$mer)
+
+glmm_quad.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+                                  I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2),
                                 data = treatment_df)
-summary(glmm_full.treatment$gam)
-summary(glmm_full.treatment$mer)
-
-glmm_red.treatment <- gamm.model(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
+summary(glmm_quad.treatment$gam); summary(glmm_quad.treatment$mer)
+
+glmm_lin.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
                                 data = treatment_df)
-summary(glmm_red.treatment$gam)
-summary(glmm_red.treatment$mer)
-
-lmm_red.treatment <- gamm4(gall_survival ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2),
-                           random = ~(1|Plant_Position/Gall_Number),
-                                data = treatment_df, family=gaussian())
-summary(lmm_red.treatment$gam)
-summary(lmm_red.treatment$mer)
-
-AIC(gamm_full.treatment$mer, gamm_red.treatment$mer, gamm_red.treatment.noG$mer, glmm_full.treatment$mer, glmm_red.treatment$mer, lmm_red.treatment$mer)
-
-## Linear mixed-models
-lmm_full.control <- lmer(gall_survival/0.45 ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots +
-                           (1|Genotype/Plant_Position/Gall_Number),
-                                data = control_df)
-summary(lmm_full.control)
-car::Anova(lmm_full.control, test="F")
-visreg::visreg(lmm_full.control)
-
-lmm_full.treatment <- lmer(gall_survival/0.6 ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                                  Gall_Height_mm:gall_individuals + 
-                                  Gall_Height_mm:Density_per_100_shoots +
-                                  gall_individuals:Density_per_100_shoots +
-                             (1|Genotype/Plant_Position/Gall_Number),
+summary(glmm_lin.treatment$gam); summary(glmm_lin.treatment$mer)
+
+lmm_lin.treatment <- gamm4(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots,
+                          data = treatment_df,
+                          random = ~(1|Genotype/Plant_Position/Gall_Number), 
+                          family = gaussian(link = identity))
+summary(lmm_lin.treatment$gam); summary(lmm_lin.treatment$mer)
+
+glmm_quad.red.treatment <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots + I(Density_per_100_shoots^2),
                                 data = treatment_df)
-summary(lmm_full.treatment)
-car::Anova(lmm_full.treatment, test="F")
-
-lmm_red.treatment <- lmer(gall_survival/0.6 ~ 
-                                  poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) +
-                              (1|Genotype/Plant_Position/Gall_Number),
+summary(glmm_quad.red.treatment$gam); summary(glmm_quad.red.treatment$mer)
+
+glmm_null.treatment <- gamm.model(gall_survival ~ 1,
                                 data = treatment_df)
-summary(lmm_red.treatment)
-car::Anova(lmm_red.treatment, test="F")
-visreg::visreg(lmm_red.treatment)
-
-AIC(lmm_full.treatment, lmm_red.treatment)
-
-gall_selection.df$relative.fit <- with(gall_selection.df, ifelse(Treatment.focus=="Control", gall_survival/0.45, gall_survival/0.6))
-
-lmm_full <- lmer(relative.fit ~ poly(Gall_Height_mm,2) + poly(gall_individuals,2) + poly(Density_per_100_shoots,2) + 
-                                poly(Gall_Height_mm,2):Treatment.focus + 
-                                poly(gall_individuals,2):Treatment.focus + 
-                                poly(Density_per_100_shoots,2):Treatment.focus +
-                                (1|Genotype/Plant_Position/Gall_Number),
-                                data = gall_selection.df)
-summary(lmm_full)
-car::Anova(lmm_full, test="F")
-visreg::visreg(lmm_full, xvar="Gall_Height_mm", by="Treatment.focus")
-visreg::visreg(lmm_full, xvar="gall_individuals", by="Treatment.focus")
-visreg::visreg(lmm_full, xvar="Density_per_100_shoots", by="Treatment.focus")
-```
+summary(glmm_null.treatment$gam); summary(glmm_null.treatment$mer)
+
+glmm_lin.red.noRE.treatment <- gamm4(gall_survival ~ Gall_Height_mm,
+                          data = treatment_df,
+                          random = ~(1|Gall_Number), 
+                          family = binomial(link = logit))
+summary(glmm_lin.red.noRE.treatment$gam); summary(glmm_lin.red.noRE.treatment$mer)
+
+AIC(gamm_full.treatment$mer, glmm_full.treatment$mer, gamm_red.treatment$mer, glmm_quad.treatment$mer, glmm_lin.treatment$mer, lmm_lin.treatment$mer, glmm_lin.red.treatment$mer, glmm_null.treatment$mer, glmm_lin.red.noRE.treatment$mer, glmm_quad.red.treatment$mer)
+```
+
+```{r}
+library(schoenberg)
+pointwise <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))})
+simultaneous <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))}, type = "simultaneous", seWithMean=TRUE)
+
+compare.confint <- bind_rows(mutate(pointwise, confint = "pointwise"), mutate(simultaneous, confint = "simultaneous")) 
+compare.confint$confint <- relevel(factor(compare.confint$confint), ref = "simultaneous")
+
+ggplot(compare.confint, aes(x=Gall_Height_mm)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper), alpha=0.25) +
+  geom_line(aes(y=est), color="black") +
+  facet_wrap(~confint)
+
+schluter <- gam.plot(gamm_red.control$gam)
+schluter
+
+gam.plot(glmm_lin.red.control$gam, all.terms=TRUE)
+test <- plot(glmm_lin.red.control$gam, all.terms=TRUE)
+gam.gradients(mod = glmm_lin.red.control$gam, phenotype = "Gall_Height_mm", se.method = "n")
+coef(glmm_lin.red.control$gam)
+
+# test derivative calculations
+control_df$Genotype <- factor(control_df$Genotype)
+control_df$Plant_Position <- factor(control_df$Plant_Position)
+control_df$Gall_Number <- factor(control_df$Gall_Number)
+A <- gam(gall_survival ~ s(Gall_Height_mm) + s(Plant_Position, bs="re") + s(Gall_Number, bs="re"), data = control_df, family=binomial(link=logit)) # random=~(1|Genotype/Plant_Position/Gall_Number),
+summary(A)
+
+head(control_df)
+A_withMean <- plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_withMean
+A_only <- plot(A, se = TRUE, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_only
+draw(A)
+
+# new data for prediction
+newDF <- with(control_df, data.frame(Gall_Height_mm = seq(min(Gall_Height_mm),max(Gall_Height_mm),length.out = 100)))
+# prediction of smoothed estimates at each unique year value
+# with standard error    
+B <- predict(A$gam,  newDF, type="response", se.fit=TRUE)
+B
+
+# finite difference approach to derivatives following
+# example from ?predict.gam
+
+eps <- 1e-7
+X0 <- predict(A, newDF, type = 'lpmatrix')
+X0 <- exp(X0)/(1+exp(X0))
+
+newDFeps_p <- newDF + eps
+
+X1 <- predict(A, newDFeps_p, type = 'lpmatrix')
+X1 <- exp(X1)/(1+exp(X1))
+# finite difference approximation of first derivative
+# the design matrix
+Xp <- (X0 - X1) / eps
+Xp
+# first derivative
+fd_d1 <- Xp %*% coef(A)
+fd_d1/mean_fit
+# second derivative
+newDFeps_m <- newDF - eps
+
+X_1 <- predict(A$gam, newDFeps_m, type = 'lpmatrix')
+# design matrix for second derivative
+Xpp <- (X1 + X_1 - 2*X0)  / eps^2
+# second derivative
+fd_d2 <- Xpp %*% coef(A$gam)
+
+exp(fd_d1) / ( 1+exp(fd_d1))  # type = "response"
+exp(fd_d2) / ( 1+exp(fd_d2))  # type = "response"
+
+mean(fd_d1)/mean_fit
+mean(fd_d2)/mean_fit
+
+gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
+
+coef(A)
+mean_fit <- mean(control_df$gall_survival)
+fderiv_size <- fderiv(A, newdata = data.frame(Gall_Height_mm = mean(control_df$Gall_Height_mm)), offset = mean_fit)
+test <- fderiv_size$derivatives$`s(Gall_Height_mm)`$deriv
+exp(test)/(1+exp(test))
+
+plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))})
+diff <- .Machine$double.eps^(1/3)
+predicts <- predict(A, newdata = data.frame(Gall_Height_mm = c(mean(control_df$Gall_Height_mm)-diff,mean(control_df$Gall_Height_mm)+diff)), type="lpmatrix")
+tests <- predicts %*% coef(A)
+exp(tests)/(1+exp(tests))
+t1 <- exp(predicts[2])/(1+exp(predicts[2]));t1
+t2 <- exp(predicts[1])/(1+exp(predicts[1]));t2
+((t1-t2)/(diff*2))/mean(control_df$gall_survival)
+gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
+
+	Wbar <- function(x, mod, phenotype,covariates) {
+    		new.d <- as.data.frame(mod$model[,c(phenotype,covariates)])
+    		names(new.d)<-c(phenotype,covariates)
+    		new.d2<-new.d
+    		for (i in 1:length(x)) {
+    		    new.d[,as.character(phenotype[i])] <-
+    		    new.d[,as.character(phenotype[i])]+x[i]
+    		}
+
+    		p <- predict.gam(
+			   object=mod,
+    	 	   newdata=new.d,
+    	 	   newdata.guaranteed=TRUE,
+    	 	   type="response"
+    		)
+    	return(mean(p))
+	}
+	as.data.frame(A$model[ ,"Gall_Height_mm"])
+	#mean(control_df$gall_survival)
+	Wbar(x=0, mod=A, phenotype="Gall_Height_mm", covariates=NULL)
+first.derivatives <- grad(f=Wbar, x=rep(0, 1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); first.derivatives
+denom <- Wbar(x=rep(0,1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); denom
+first.derivatives/denom
+pracma:::grad
+A$Vp
+A$coefficients
+A_withMean
+```
+
 Parametric bootstrapping: Currently reported results

### 2018-06-07 supp_mat_complexity_selection.Rmd
considering going back to GAMM models for fitting, since the toolkit is available for everything in the 'gsg' package.

--- 2018-06-06 supp_mat_complexity_selection.Rmd
@@
 # Use parametric bootstrapping to get confidence intervals for selection gradients
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=200, parallel="multicore", ncpus=32)
 
@@
 # Use parametric bootstrapping to get confidence intervals for selection gradients
-boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=10)
+boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=200, parallel="multicore", ncpus=32)
 
@@
   model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
-  model_null <- model.matrix(~1, newdata)
-
-  get_relative_fitness <- function(.) {
-  #mean_fitness <- mean(inverse_logit(model_null %*% fixef(.))) #fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+  get_absolute_fitness <- function(.) {
   absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
-  absolute_fitness #/ mean_fitness # mean(absolute_fitness) # 
+  absolute_fitness 
   }
 
-  get_bootstraps <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+  get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
   get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])
 
-  mean_fitness <- mean(get_relative_fitness(logistic_model))
-
-  return(data.frame(relative_fitness = get_relative_fitness(logistic_model)/mean_fitness,
+  mean_fitness <- mean(get_absolute_fitness(logistic_model))
+
+  return(data.frame(relative_fitness = get_absolute_fitness(logistic_model)/mean_fitness,
                     lower_2.5 = get_intervals[1, ]/mean_fitness,
@@
 ```{r}
+HPD_50_treatment_size <- coda::HPDinterval(coda::as.mcmc(treatment_df$sc.gall_size), prob=0.5)
+HPD_50_control_size <- coda::HPDinterval(coda::as.mcmc(control_df$sc.gall_size), prob=0.5)
+
+HPD_95_treatment_size <- coda::HPDinterval(coda::as.mcmc(treatment_df$sc.gall_size), prob=0.95)
+HPD_95_control_size <- coda::HPDinterval(coda::as.mcmc(control_df$sc.gall_size), prob=0.95)
+
 RF_treatment_gall_size <- relative_fitness_intervals(
@@
   newdata = expand.grid(
-     sc.gall_size = seq(min(treatment_df$sc.gall_size),
-                        max(treatment_df$sc.gall_size),
-                        length.out = 100),
+     sc.gall_size = treatment_df$sc.gall_size, 
      sc.clutch_size = 0,
      sc.female_preference = 0),
-  bootstraps=200)
+  bootstraps=1000)
 
@@
   newdata = expand.grid(
-     sc.gall_size = seq(min(control_df$sc.gall_size),
-                        max(control_df$sc.gall_size),
-                        length.out = 100),
+     sc.gall_size = treatment_df$sc.gall_size,
      sc.clutch_size = 0,
      sc.female_preference = 0),
-  bootstraps=200)
+  bootstraps=1000)
 
 mean(RF_control_gall_size$relative_fitness)
+
+bind_rows(mutate(treatment_df, Treatment = "Simple"),
+          mutate(control_df, Treatment = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, color=Treatment, fill=Treatment)) +
+  geom_density(alpha=0.5)
 
@@
           mutate(RF_control_gall_size, Treatment = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=relative_fitness, color=Treatment, fill=Treatment)) +
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness)) +
   geom_hline(yintercept=1, linetype="dotted") +
-  geom_line() +
-  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5)
-```
-
-```{r}
+  geom_line(aes(color=Treatment), size=0.25) +
+  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5, fill=Treatment), alpha=0.25) +
+  geom_line(data = filter(mutate(RF_treatment_gall_size, Treatment = "Simple"), 
+                          between(sc.gall_size, HPD_95_treatment_size[1], HPD_95_treatment_size[2])),
+            aes(color=Treatment), size=1) +
+  geom_line(data = filter(mutate(RF_control_gall_size, Treatment = "Complex"), 
+                          between(sc.gall_size, HPD_95_control_size[1], HPD_95_control_size[2])), 
+            aes(color=Treatment), size=1) +
+    geom_line(data = filter(mutate(RF_treatment_gall_size, Treatment = "Simple"), 
+                          between(sc.gall_size, HPD_50_treatment_size[1], HPD_50_treatment_size[2])),
+            aes(color=Treatment), size=2.5) +
+  geom_line(data = filter(mutate(RF_control_gall_size, Treatment = "Complex"), 
+                          between(sc.gall_size, HPD_50_control_size[1], HPD_50_control_size[2])), 
+            aes(color=Treatment), size=2.5) +
+  ylab("Relative fitness") +
+  xlab("Gall size (mm)")
+```
+
+```{r}
+## Get Highest Posterior Density Intervals for clutch size phenotype
+
+# 50%
+HPD_50_treatment_clutch <- coda::HPDinterval(coda::as.mcmc(
+  distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.5)
+HPD_50_control_clutch <- coda::HPDinterval(coda::as.mcmc(
+  distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.5)
+
+# 95%
+HPD_95_treatment_clutch <- coda::HPDinterval(coda::as.mcmc(
+  distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.95)
+HPD_95_control_clutch <- coda::HPDinterval(coda::as.mcmc(
+  distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), prob=0.95)
+
 RF_treatment_clutch_size <- relative_fitness_intervals(
@@
      sc.gall_size = 0,
-     sc.clutch_size = seq(min(treatment_df$sc.clutch_size),
-                          max(treatment_df$sc.clutch_size),
-                          length.out = 100),
+     sc.clutch_size = distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
      sc.female_preference = 0),
-  bootstraps=200)
-
+  bootstraps=1000)
+
+# confirm that mean relative fitness = 1
 mean(RF_treatment_clutch_size$relative_fitness)
@@
      sc.gall_size = 0,
-     sc.clutch_size = seq(min(control_df$sc.clutch_size),
-                        max(control_df$sc.clutch_size),
-                        length.out = 100),
+     sc.clutch_size = distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
      sc.female_preference = 0),
-  bootstraps=200)
-
+  bootstraps=1000)
+
+# confirm that mean relative fitness = 1
 mean(RF_control_clutch_size$relative_fitness)
@@
           mutate(RF_control_clutch_size, Treatment = "Complex")) %>%
-  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, color=Treatment, fill=Treatment)) +
+  ggplot(., aes(x=sc.clutch_size, y=relative_fitness)) +
   geom_hline(yintercept=1, linetype="dotted") +
-  geom_line() +
-  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5)
-```
-
-```{r}
+  geom_line(aes(color=Treatment), size=0.25) +
+  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5, fill=Treatment), alpha=0.25) +
+  geom_line(data = filter(mutate(RF_treatment_clutch_size, Treatment = "Simple"), 
+                          between(sc.clutch_size, HPD_95_treatment_clutch[1], HPD_95_treatment_clutch[2])),
+            aes(color=Treatment), size=1) +
+  geom_line(data = filter(mutate(RF_control_clutch_size, Treatment = "Complex"), 
+                          between(sc.clutch_size, HPD_95_control_clutch[1], HPD_95_control_clutch[2])), 
+            aes(color=Treatment), size=1) +
+    geom_line(data = filter(mutate(RF_treatment_clutch_size, Treatment = "Simple"), 
+                          between(sc.clutch_size, HPD_50_treatment_clutch[1], HPD_50_treatment_clutch[2])),
+            aes(color=Treatment), size=2.5) +
+  geom_line(data = filter(mutate(RF_control_clutch_size, Treatment = "Complex"), 
+                          between(sc.clutch_size, HPD_50_control_clutch[1], HPD_50_control_clutch[2])), 
+            aes(color=Treatment), size=2.5) +
+  ylab("Relative fitness") +
+  xlab("Clutch size")
+```
+
+```{r}
+## Get Highest Posterior Density Intervals for clutch size phenotype
+
+# 50%
+HPD_50_treatment_preference <- coda::HPDinterval(coda::as.mcmc(
+  distinct(treatment_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.5)
+HPD_50_control_preference <- coda::HPDinterval(coda::as.mcmc(
+  distinct(control_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.5)
+
+# 95%
+HPD_95_treatment_preference <- coda::HPDinterval(coda::as.mcmc(
+  distinct(treatment_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.95)
+HPD_95_control_preference <- coda::HPDinterval(coda::as.mcmc(
+  distinct(control_df, Plant_Position, Gall_Number, sc.female_preference)$sc.female_preference), prob=0.95)
+
 RF_treatment_female_preference <- relative_fitness_intervals(
@@
      sc.clutch_size = 0,
-     sc.female_preference = seq(min(treatment_df$sc.female_preference),
-                                max(treatment_df$sc.female_preference),
-                                length.out = 100)),
-  bootstraps=200)
+     sc.female_preference = distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference), 
+  bootstraps=1000)
 
@@
      sc.clutch_size = 0,
-     sc.female_preference = seq(min(control_df$sc.female_preference),
-                                max(control_df$sc.female_preference),
-                                length.out = 100)),
-  bootstraps=200)
+     sc.female_preference = distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference), 
+  bootstraps=1000)
 
@@
           mutate(RF_control_female_preference, Treatment = "Complex")) %>%
-  ggplot(., aes(x=sc.female_preference, y=relative_fitness, color=Treatment, fill=Treatment)) +
+  ggplot(., aes(x=sc.female_preference, y=relative_fitness)) +
     geom_hline(yintercept=1, linetype="dotted") +
-  geom_line() +
-  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5), alpha=0.5) +
+  geom_line(aes(color=Treatment), size=0.25) +
+  geom_ribbon(aes(ymin=lower_2.5, ymax=upper_97.5, fill=Treatment), alpha=0.25) +
+  geom_line(data = filter(mutate(RF_treatment_female_preference, Treatment = "Simple"), 
+                          between(sc.female_preference, HPD_95_treatment_preference[1], HPD_95_treatment_preference[2])),
+            aes(color=Treatment), size=1) +
+  geom_line(data = filter(mutate(RF_control_female_preference, Treatment = "Complex"), 
+                          between(sc.female_preference, HPD_95_control_preference[1], HPD_95_control_preference[2])), 
+            aes(color=Treatment), size=1) +
+    geom_line(data = filter(mutate(RF_treatment_female_preference, Treatment = "Simple"), 
+                          between(sc.female_preference, HPD_50_treatment_preference[1], HPD_50_treatment_preference[2])),
+            aes(color=Treatment), size=2.5) +
+  geom_line(data = filter(mutate(RF_control_female_preference, Treatment = "Complex"), 
+                          between(sc.female_preference, HPD_50_control_preference[1], HPD_50_control_preference[2])), 
+            aes(color=Treatment), size=2.5) +
+  ylab("Relative fitness") +
+  xlab("Female preference")
+```
+
+```{r}
+RF_treatment_clutch_preference <- relative_fitness_intervals(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
+     sc.female_preference = distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference), 
+  bootstraps=100)
+
+mean(RF_treatment_clutch_preference$relative_fitness)
+
+RF_control_clutch_preference <- relative_fitness_intervals(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
+     sc.female_preference = distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference), 
+  bootstraps=100)
+
+mean(RF_control_clutch_preference$relative_fitness)
+
+bind_rows(mutate(RF_treatment_clutch_preference, Treatment="Simple"),
+          mutate(RF_control_clutch_preference, Treatment="Complex")) %>%
+  ggplot(., aes(x=sc.clutch_size, y=sc.female_preference, fill=relative_fitness)) +
+  geom_raster(size=2) + 
+  facet_wrap(~Treatment) +
+  scale_fill_viridis(name = "Relative fitness") +
+  xlab("Clutch size") +
+  ylab("Female preference")
+
+expand.grid(sc.gall_size = 0,
+     sc.clutch_size = distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size,
+     sc.female_preference = distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference) %>%
+  ggplot(., aes(x=sc.clutch_size, y=sc.female_preference)) +
+  geom_point(shape=21)
 ```
@@
 bind_rows(mutate(visreg(glmer_treatment, xvar="sc.female_preference", scale="response", plot=F)$fit, 
-                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
+                   Treatment="Simple", `Relative fitness` = visregFit/mean(visregFit)), 
           mutate(visreg(glmer_control, xvar="sc.female_preference", scale="response", plot=F)$fit, 
-                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
+                   Treatment="Complex", `Relative fitness` = visregFit/mean(visregFit))) %>%
   ggplot(., aes(x=sc.female_preference, y=`Relative fitness`, color=Treatment)) +
@@
 bind_rows(mutate(visreg(glmer_treatment, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
-                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
+                   Treatment="Simple", `Relative fitness` = visregFit/mean(visregFit)), 
           mutate(visreg(glmer_control, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
-                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
+                   Treatment="Complex", `Relative fitness` = visregFit/mean(visregFit))) %>%
   ggplot(., aes(x=sc.clutch_size, y=`Relative fitness`, color=Treatment)) +
@@
 
+```{r}
+gam.plot(gamm_red.control$gam, select="Gall_Height_mm")
+```
+
 Another decision we had to make was whether to calculate selection gradients with GAM or GAMMs.
@@
 
+control_mean_fitness <- mean(get_insect_FL.df(fl.size_control)$mean_fitness)
+treatment_mean_fitness <- mean(get_insect_FL.df(fl.size_treatment)$mean_fitness)
+
+bind_rows(mutate(get_insect_FL.df(fl.size_control), Treatment = "Complex"),
+          mutate(get_insect_FL.df(fl.size_treatment), Treatment = "Simple")) %>%
+  mutate(relative_fitness = ifelse(Treatment=="Complex", mean_fitness/control_mean_fitness, mean_fitness/treatment_mean_fitness),
+         lower_2.5 = ifelse(Treatment=="Complex", lower_2.5/control_mean_fitness, lower_2.5/treatment_mean_fitness),
+         upper_97.5 = ifelse(Treatment=="Complex", upper_97.5/control_mean_fitness, upper_97.5/treatment_mean_fitness)) %>%
+  ggplot(.) +
+  geom_line(aes(x = Var1, y = relative_fitness, color=Treatment)) + 
+  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
+  ylab("Relative fitness") +
+  xlab("Mean gall size\n(mm)") +
+  scale_color_manual(values = treatmeant_colors) +
+  scale_fill_manual(values = treatmeant_colors)
+
 uni_clutch <- bind_rows(mutate(get_insect_FL.df(fl.individuals_control), Treatment = "Complex"),
@@
 
+control_mean_fitness <- mean(get_insect_FL.df(fl.individuals_control)$mean_fitness)
+treatment_mean_fitness <- mean(get_insect_FL.df(fl.individuals_treatment)$mean_fitness)
+
+bind_rows(mutate(get_insect_FL.df(fl.individuals_control), Treatment = "Complex"),
+          mutate(get_insect_FL.df(fl.individuals_treatment), Treatment = "Simple")) %>%
+  mutate(relative_fitness = ifelse(Treatment=="Complex", mean_fitness/control_mean_fitness, mean_fitness/treatment_mean_fitness),
+         lower_2.5 = ifelse(Treatment=="Complex", lower_2.5/control_mean_fitness, lower_2.5/treatment_mean_fitness),
+         upper_97.5 = ifelse(Treatment=="Complex", upper_97.5/control_mean_fitness, upper_97.5/treatment_mean_fitness)) %>%
+  ggplot(.) +
+  geom_line(aes(x = Var1, y = relative_fitness, color=Treatment)) + 
+  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
+  ylab("Relative fitness") +
+  xlab("Mean gall individuals\n(mm)") +
+  scale_color_manual(values = treatmeant_colors) +
+  scale_fill_manual(values = treatmeant_colors)
+
 uni_pref <- bind_rows(mutate(get_insect_FL.df(fl.density_control), Treatment = "Complex"),
@@
 
+control_mean_fitness <- mean(get_insect_FL.df(fl.density_control)$mean_fitness)
+treatment_mean_fitness <- mean(get_insect_FL.df(fl.density_treatment)$mean_fitness)
+
+bind_rows(mutate(get_insect_FL.df(fl.density_control), Treatment = "Complex"),
+          mutate(get_insect_FL.df(fl.density_treatment), Treatment = "Simple")) %>%
+  mutate(relative_fitness = ifelse(Treatment=="Complex", mean_fitness/control_mean_fitness, mean_fitness/treatment_mean_fitness),
+         lower_2.5 = ifelse(Treatment=="Complex", lower_2.5/control_mean_fitness, lower_2.5/treatment_mean_fitness),
+         upper_97.5 = ifelse(Treatment=="Complex", upper_97.5/control_mean_fitness, upper_97.5/treatment_mean_fitness)) %>%
+  ggplot(.) +
+  geom_line(aes(x = Var1, y = relative_fitness, color=Treatment)) + 
+  geom_ribbon(aes(x = Var1, ymin = lower_2.5, ymax = upper_97.5, fill=Treatment), alpha = 0.25) +
+  ylab("Relative fitness") +
+  xlab("Mean gall density\n(mm)") +
+  scale_color_manual(values = treatmeant_colors) +
+  scale_fill_manual(values = treatmeant_colors)
+
 uni_legend <- get_legend(uni_size)

### 2018-06-08 supp_mat_complexity_selection.Rmd
reorganizing analyses

@@
 This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
-```{r Preliminaries, message=FALSE, warning=FALSE, include=FALSE}
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+```{r setup}
+knitr::opts_chunk$set(include = FALSE)
+
+## Load required libraries ----
 library(tidyverse)
@@
 
-## LOAD & MANAGE DATASET ----
+## Load and manage data ----
 
@@
 
-## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
+# convert treatment to factor to use as 'by' variable in generalized additive models
+gall_selection.df <- gall_selection.df %>%
+  mutate(Treatment_contr.sum=factor(Treatment.focus), 
+         sc.gall_size = as.numeric(scale(Gall_Height_mm)),
+         sc.clutch_size = as.numeric(scale(gall_individuals)),
+         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
+contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
+
+## Create separate datasets for quantifying selection gradients ----
 control_df <- gall_selection.df %>%
@@
          sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
-```
-
-Custom functions to avoid repetitive code
-```{r FUNCTIONS}
+
+## Custom functions to avoid repetitive code ----
 gamm.model <- function(formula, data) {
@@
 
-Beta_avg_grad <- function(logistic_model, mean_fitness) {
-  brackets <- predict(logistic_model, type = "response") * (1 - predict(logistic_model, type="response"))
-  gradient <- mean(brackets) * fixef(logistic_model) / mean_fitness 
-  return(gradient)
+#Beta_avg_grad <- function(logistic_model, mean_fitness) {
+#  brackets <- predict(logistic_model, type = "response") * (1 - predict(logistic_model, type="response"))
+#  gradient <- mean(brackets) * fixef(logistic_model) / mean_fitness 
+#  return(gradient)
+#}
+
+## Calculate directional selection gradients
+# following method of Janzen and Stern 1998, Evolution
+Beta_avg_grad <- function(.) {
+  mean_fitness <- inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
+  mean(brackets) * fixef(.)[-1] / mean_fitness 
 }
-```
-
-```{r}
-# convert treatment to factor to use as 'by' variable in gamm.model
-gall_selection.df <- gall_selection.df %>%
-  mutate(Treatment_contr.sum=factor(Treatment.focus), 
-         sc.gall_size = as.numeric(scale(Gall_Height_mm)),
-         sc.clutch_size = as.numeric(scale(gall_individuals)),
-         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
-contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
-# Inspect contrasts:
-contrasts(gall_selection.df$Treatment_contr.sum)
-
-## AIC MODEL SELECTION
-# Note that I use gamm4 to fit all models to maintain consistency
-
-## GAMM full
-m1 <- gamm.model(gall_survival ~ Treatment_contr.sum +
+
+## Calculate confidence intervals of relative fitness
+relative_fitness_intervals <- function(logistic_model, newdata, bootstraps){
+  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
+
+  get_absolute_fitness <- function(.) {
+  absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
+  absolute_fitness#/mean(absolute_fitness) 
+  }
+
+  get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+  browser()
+
+  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])
+
+  #mean_fitness <- mean(get_absolute_fitness(logistic_model))
+
+  return(data.frame(relative_fitness = get_absolute_fitness(logistic_model),#/mean_fitness,
+                    lower_2.5 = get_intervals[1, ],#/mean_fitness,
+                    upper_97.5 = get_intervals[2, ],#/mean_fitness,
+                    newdata))
+}
+```
+
+We used Aikaike Information Criteria (AIC)
+
+```{r AIC Model Selection}
+
+## GAMM 1: models the effect of food-web treatment on univariate and multivariate fitness landscapes ----
+GAMM_1 <- gamm.model(gall_survival ~ 
+                       Treatment_contr.sum +
                        s(sc.gall_size, by=Treatment_contr.sum) + 
@@
                      data = gall_selection.df)
-summary(m1$gam); summary(m1$mer)
-
-gamm_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                             s(sc.gall_size) + 
+# summary(GAMM_1$gam); summary(GAMM_1$mer)
+
+## GAMM 2: models the effect of food-web treatment on univariate, but not multivariate landscape ----
+GAMM_2 <- gamm.model(gall_survival ~ 
+                       Treatment_contr.sum +
+                       s(sc.gall_size, by=Treatment_contr.sum) + 
+                       s(sc.clutch_size, by=Treatment_contr.sum) + 
+                       s(sc.female_preference, by=Treatment_contr.sum) +
+                       sc.gall_size:sc.clutch_size + 
+                       sc.gall_size:sc.female_preference +                        
+                       sc.clutch_size:sc.female_preference,
+                     data = gall_selection.df)
+# summary(GAMM_2$gam); summary(GAMM_2$mer)
+
+## GAMM 3: models the effect of food-web treatment on univariate landscape ----
+GAMM_3 <- gamm.model(gall_survival ~ 
+                       Treatment_contr.sum +
+                       s(sc.gall_size, by=Treatment_contr.sum) + 
                        s(sc.clutch_size, by=Treatment_contr.sum) + 
@@
                       data = gall_selection.df)
-summary(gamm_reduced$gam); summary(gamm_reduced$mer)
-
-gamm_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                             sc.gall_size + 
-                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
-                             s(sc.female_preference, by=Treatment_contr.sum),
+# summary(GAMM_3$gam); summary(GAMM_3$mer)
+
+## GAMM 4: assumes that the food-web does not modify the fitness landscape 
+GAMM_4 <- gamm.model(gall_survival ~ 
+                       Treatment_contr.sum +
+                       s(sc.gall_size) + 
+                       s(sc.clutch_size) + 
+                       s(sc.female_preference),
                      data = gall_selection.df)
-summary(gamm_reduced2$gam); summary(gamm_reduced2$mer)
-
-GLMM_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum +
-                             sc.gall_size + 
+# summary(GAMM_4$gam); summary(GAMM_4$mer)
+
+## AIC Comparison of GAMMs
+knitr::kable(AIC(GAMM_1$mer, GAMM_2$mer, GAMM_3$mer, GAMM_4$mer))
+
+```
+
+AIC model comparison suggests that ....
+
+Now let's compare the best GAMMs to analog generalized linear mixed-models (GLMM).
+If these GLMMs have a lower AIC value than their respective GAMMs, then this suggests that there is only evidence of directional selection in our data.
+```{r}
+# Note that I still use gamm.model to allow for appropriate model comparisons
+
+## GLMM 3: only models the effect of food-web treatment on directional selection gradients ----
+GLMM_3 <- gamm.model(gall_survival ~ 
+                       Treatment_contr.sum +
+                       sc.gall_size + sc.gall_size:Treatment_contr.sum + 
                        sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
@@
                       data = gall_selection.df)
-summary(GLMM_reduced$gam); summary(GLMM_reduced$mer)
-
-AIC(m1$mer, gamm_reduced$mer, gamm_reduced2$mer, GLMM_reduced$mer)
-
-glmer_reduced <- glmer(gall_survival ~ Treatment_contr.sum +
+#summary(GLMM_3$gam); summary(GLMM_3$mer)
+
+## GLMM 4: only models the effect of food-web treatment on directional selection gradients ----
+GLMM_4 <- gamm.model(gall_survival ~ 
+                       Treatment_contr.sum +
                        sc.gall_size + 
-                             sc.clutch_size + sc.clutch_size:Treatment_contr.sum + 
-                             sc.female_preference + sc.female_preference:Treatment_contr.sum +
-                             (1|Genotype/Plant_Position/Gall_Number),
-                       family=binomial(link=logit),
-                       data = gall_selection.df, glmerControl(optimizer="bobyqa"))
-summary(glmer_reduced)
-overdisp_fun(glmer_reduced) # no evidence of overdispersion
-
-v <- visreg(fit, 'Days', 'Subject', re.form=(~Days|Subject), plot=FALSE)
-plot(v)
-plot(v, overlay=TRUE)
-
-test <- visreg(glmer_reduced, xvar=c("sc.gall_size"), by="Genotype", re.form=(~1|Genotype), plot=FALSE, 
-       scale="response", partial=TRUE, gg=TRUE, overlay=TRUE,
-       cond = list(sc.gall_size=0, sc.clutch_size=0, sc.female_preference=0))
-plot(test, partial=TRUE, overlay=TRUE)
-visreg(glmer_reduced, xvar=c("sc.gall_size"), scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
-visreg(glmer_reduced, xvar=c("sc.clutch_size"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
-visreg(glmer_reduced, xvar=c("sc.female_preference"), by="Treatment_contr.sum", scale="response", partial=TRUE, gg=TRUE, overlay=TRUE)
-
-## GLMER full
-glmer_full <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
-                           Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
+                       sc.clutch_size + 
+                       sc.female_preference,
                       data = gall_selection.df)
-summary(glmer_full$gam); summary(glmer_full$mer)
-round(vcov(glmer_full$mer), 2) # no evidence of correlations that would confound interpretations of statistical main and interaction effects.
-
-glmer_reduced <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) +
-                           I(sc.gall_size^2) + I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
-                         data = gall_selection.df)
-summary(glmer_reduced$gam); summary(glmer_reduced$mer, correlation=TRUE)
-visreg(glmer_reduced$gam, xvar="sc.gall_size", by="sc.clutch_size", scale="response")
-
-glmer_reduced2 <- gamm.model(gall_survival ~ Treatment_contr.sum*sc.clutch_size + sc.gall_size + sc.female_preference +
-                               I(sc.female_preference^2) + sc.gall_size:sc.clutch_size, 
-                         data = gall_selection.df)
-summary(glmer_reduced2$gam); summary(glmer_reduced2$mer)
-
-AIC(glmer_full$mer, glmer_reduced$mer, glmer_reduced2$mer)
-
-## LMER full
-m3 <- gamm4(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference)^2 +
-                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)),
-            family = gaussian(link=identity),
-            random = ~(1|Genotype/Plant_Position/Gall_Number),
-            data = gall_selection.df)
-
-AIC(m1$mer, m2$mer, m3$mer) # suggests that the GLMM is best
-
-## Do we need a model with interactions between traits?
-m4 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
-                   Treatment_contr.sum*(I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
-                 data = gall_selection.df)
-AIC(m2$mer, m4$mer) # AIC suggests not
-
-## Do we need a model with non-linear trait effects?
-m5 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference) + #^2 +
-                   (I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2)), 
-                 data = gall_selection.df)
-AIC(m4$mer, m5$mer) # 
-summary(m5$gam)
-summary(m5$mer)
-
-m6 <- gamm.model(gall_survival ~ Treatment_contr.sum*(sc.gall_size + sc.clutch_size + sc.female_preference), 
-                 data = gall_selection.df)
-AIC(m5$mer, m6$mer) 
-```
-
-```{r}
-## Calculate directional selection gradients
-# following method of Janzen and Stern
-
-Beta_avg_grad <- function(.) {
-  mean_fitness <- inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
-  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
-  mean(brackets) * fixef(.)[-1] / mean_fitness 
-}
-
-```
-
-```{r}
-
-## Control treatment
-
-# GLMM
+#summary(GLMM_4$gam); summary(GLMM_4$mer)
+
+knitr::kable(AIC(GAMM_3$mer, GLMM_3$mer, GAMM_4$mer, GLMM_4$mer)) 
+```
+
+It appears that the best predictive model is the GLMM that includes an effect of food-web treatment on directional selection gradients.
+Therefore, we continue by quantifying the effect of food-web treatment on directional selection gradients.
+
+The model selection procedure was useful for pairing down the complexity of our model.
+To actually quantify the directional selection gradients in each treatment though, we analyze each treatment separately.
+
+```{r Selection Gradients - Complex Food Web}
+# note that I've switched to using the lme4 package to analyzing the GLMM
+
+# GLMM ----
 glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
                            (1|Genotype/Plant_Position/Gall_Number),
-                         family=binomial(link=logit),
-                         data = control_df, glmerControl(optimizer="bobyqa"))
-summary(glmer_control)
-
-# Mean fitness
+                         data = control_df,
+                         family = binomial(link = logit), optimizer = "bobyqa")
+# summary(glmer_control)
+
+# Mean fitness ----
 Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
 
-# Use parametric bootstrapping to get confidence intervals for selection gradients
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=200, parallel="multicore", ncpus=32)
-
-data.frame(Beta_avg_grad = round(Beta_avg_grad(glmer_control),2),
-           lowerCI_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
-           upperCI_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2)) %>%
-  knitr::kable(.)
-```
-
-```{r}
-
-## Ectoparasitoid exclusion treatment
-
-# GLMM
+# Confidence intervals for selection gradients ----
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=1000, parallel="multicore", ncpus=32)
+
+## Summary ----
+summary_Beta_glmm_control <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Beta = round(Beta_avg_grad(glmer_control),3),
+  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)) 
+```
+
+```{r Selection Gradients - Simple Food Web}
+
+## GLMM ----
 glmer_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
                            (1|Genotype/Plant_Position/Gall_Number),
-                         family=binomial(link=logit),
-                         data = treatment_df, glmerControl(optimizer="bobyqa"))
-summary(glmer_treatment)
-
-# Mean fitness
+                         data = treatment_df,
+                         family = binomial(link = logit), optimizer = "bobyqa")
+# summary(glmer_treatment)
+
+## Mean fitness ----
 Wbar_treatment <- inverse_logit(fixef(update(glmer_treatment, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
 
-# Use parametric bootstrapping to get confidence intervals for selection gradients
-boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=200, parallel="multicore", ncpus=32)
-
-data.frame(Beta_avg_grad = round(Beta_avg_grad(glmer_treatment),2),
-           lowerCI_2.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
-           upperCI_97.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2)) %>%
+## Confidence intervals for selection gradients ----
+boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=1000, parallel="multicore", ncpus=32)
+
+## Summary ----
+summary_Beta_glmm_treatment <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Beta = round(Beta_avg_grad(glmer_treatment),2),
+  lower_2.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
+  upper_97.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2)) 
+```
+
+To ensure we are calculating these selection gradients correctly, we'll compare our results to those obtained from the *gsg* package developed by Michael Morrissey.
+```{r Check Gradient Calculations}
+
+## GAMM Control ----
+gamm_control <- gamm.model(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference,
+                             data = control_df)
+gsg_control <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GAMM",
+  Beta = round(c(gam.gradients(gamm_control$gam, 
+                         phenotype = "sc.gall_size", covariates = c("sc.clutch_size","sc.female_preference"), 
+                         se.method = "n")["B-sc.gall_size","estimates"],
+           gam.gradients(gamm_control$gam, 
+                         phenotype = "sc.clutch_size", covariates = c("sc.gall_size","sc.female_preference"), 
+                         se.method = "n")["B-sc.clutch","estimates"],
+           gam.gradients(gamm_control$gam, 
+                         phenotype = "sc.female_preference", covariates = c("sc.gall_size","sc.clutch_size"),
+                         se.method = "n")["B-sc.female_preference","estimates"]),3),
+  lower_2.5 = NA,
+  upper_97.5 = NA)
+
+## GAMM Treatment ----
+gamm_treatment <- gamm.model(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference,
+                             data = treatment_df)
+gsg_treatment <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Simple",
+  Model = "GAMM",
+  Beta = round(c(gam.gradients(gamm_treatment$gam, 
+                         phenotype = "sc.gall_size", covariates = c("sc.clutch_size","sc.female_preference"), 
+                         se.method = "n")["B-sc.gall_size","estimates"],
+           gam.gradients(gamm_treatment$gam, 
+                         phenotype = "sc.clutch_size", covariates = c("sc.gall_size","sc.female_preference"), 
+                         se.method = "n")["B-sc.clutch","estimates"],
+           gam.gradients(gamm_treatment$gam, 
+                         phenotype = "sc.female_preference", covariates = c("sc.gall_size","sc.clutch_size"),
+                         se.method = "n")["B-sc.female_preference","estimates"]),3),
+  lower_2.5 = NA,
+  upper_97.5 = NA)
+
+## Compare GAMM and GLMM estimates ----
+compare_Beta <- bind_rows(gsg_control, gsg_treatment, summary_Beta_glmm_control, summary_Beta_glmm_treatment) %>%
+  select(-lower_2.5, -upper_97.5) %>%
+  spread(Model, Beta)
+
+knitr::kable(compare_Beta)
+
+```
+
+The comparisons are quite close, but why should they differ at all?
+This suggests that my implementation of the Janzen and Stern 1998 method and Morrisey's are slightly different.
+Perhaps this is because Janzen and Stern relies on the coefficient to calculate the gradient, whereas Morrisey calculates it using the finite difference methods for partial derivatives...
+
+Now let's look at how the confidence intervals vary between the GLMM and GAMMs. Note that I now fit it with a spline function to allow gsg to calculate bootstrap intervals (it won't otherwise).
+
+```{r gsg Comparison}
+
+## Fit generalized additive mixed models ----
+gamm_control_2 <- gamm.model(gall_survival ~ s(sc.gall_size) + s(sc.clutch_size,k=9) + s(sc.female_preference),
+                             data = control_df)
+
+gamm_treatment_2 <- gamm.model(gall_survival ~ s(sc.gall_size) + s(sc.clutch_size,k=9) + s(sc.female_preference),
+                             data = treatment_df)
+
+## Estimate selection gradients ----
+sg.size_control <- gradient.calc(mod = gamm_control_2$gam, 
+                                 phenotype = "sc.gall_size", 
+                                 covariates = c("sc.clutch_size","sc.female_preference"))
+sg.size_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+                                   phenotype = "sc.gall_size", 
+                                   covariates = c("sc.clutch_size","sc.female_preference"))
+sg.clutch_control <- gradient.calc(mod = gamm_control_2$gam, 
+                                        phenotype = "sc.clutch_size", 
+                                        covariates = c("sc.gall_size","sc.female_preference"))
+sg.clutch_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+                                          phenotype = "sc.clutch_size", 
+                                          covariates = c("sc.gall_size","sc.female_preference"))
+sg.preference_control <- gradient.calc(mod = gamm_control_2$gam, 
+                                    phenotype = "sc.female_preference", 
+                                    covariates = c("sc.clutch_size","sc.gall_size"))
+sg.preference_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+                                      phenotype = "sc.female_preference", 
+                                      covariates = c("sc.clutch_size","sc.gall_size"))
+
+## Organize bootstrap estimates ----
+bootstrap_df <- bind_rows(
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], 
+             Phenotype = "Gall size", Selection_Type = "Beta", Food_Web = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], 
+             Phenotype = "Gall size", Selection_Type = "Beta", Food_Web = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.clutch_control$boot[ ,1], 
+             Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.clutch_treatment$boot[ ,1], 
+             Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.preference_control$boot[ ,1], 
+             Phenotype = "Female preference", Selection_Type = "Beta", Food_Web = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.preference_treatment$boot[ ,1], 
+             Phenotype = "Female preference", Selection_Type = "Beta", Food_Web = "Simple"))
+
+## Summarise bootstrap estimates ----
+gsg_gradients <- bootstrap_df %>%
+  group_by(Phenotype, Food_Web) %>%
+  summarise(Beta = round(mean(Bootstrap_Estimates),3),
+            lower_2.5 = round(quantile(Bootstrap_Estimates, probs = 0.025),3),
+            upper_97.5 = round(quantile(Bootstrap_Estimates, probs = 0.975),3)) %>%
+  mutate(Model = "gsg_GAMM")
+
+## Compare gsg GAMM and GLMM estimates of directional selection ----
+bind_rows(gsg_gradients, summary_Beta_glmm_control, summary_Beta_glmm_treatment) %>%
+  arrange(Phenotype, Food_Web, Model) %>%
+  mutate(absolute_range = upper_97.5 - lower_2.5) %>%
   knitr::kable(.)
@@
 
-```{r}
-## Custom function to calculate relative fitness intervals for my models
-relative_fitness_intervals <- function(logistic_model, newdata, bootstraps){
-  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
-
-  get_absolute_fitness <- function(.) {
-  absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
-  absolute_fitness 
-  }
-
-  get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
-  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])
-
-  mean_fitness <- mean(get_absolute_fitness(logistic_model))
-
-  return(data.frame(relative_fitness = get_absolute_fitness(logistic_model)/mean_fitness,
-                    lower_2.5 = get_intervals[1, ]/mean_fitness,
-                    upper_97.5 = get_intervals[2, ]/mean_fitness,
-                    newdata))
-}
+Both methods give the same qualitative results.
+However, range of the confidence intervals can be more than twice as large using my GLMM bootstrapping methods.
+Therefore, our reported intervals provide a conservative estimate.
+
+```{r Compare Selection Gradients across Treatments - GLMM}
+
+## Gather bootstrap data from GLMMs
+glmm_boostrap_df <- bind_rows(
+  data.frame(boot_Beta_treatment$t, ID = rep(1:dim(boot_Beta_treatment$t)[1]), Food_Web = "Simple"),
+  data.frame(boot_Beta_control$t, ID = rep(1:dim(boot_Beta_control$t)[1]), Food_Web = "Complex")
+)
+
+## Gall size ----
+select(glmm_boostrap_df, sc.gall_size, ID, Food_Web) %>%
+  spread(Food_Web, sc.gall_size) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/dim(glmm_boostrap_df)[1])
+
+## Clutch size ----
+select(glmm_boostrap_df, sc.clutch_size, ID, Food_Web) %>%
+  spread(Food_Web, sc.clutch_size) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/dim(glmm_boostrap_df)[1])
+
+## Female preference ----
+select(glmm_boostrap_df, sc.female_preference, ID, Food_Web) %>%
+  spread(Food_Web, sc.female_preference) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/dim(glmm_boostrap_df)[1])
+```
+
+We observe the same qualitative results with *gsg* GAMMs, except that the P-values are always lower.
+
+```{r Compare Selection Gradients across Treatments - gsg GAMM}
+
+## Gall size ----
+bootstrap_df %>%
+  filter(Phenotype == "Gall size", Selection_Type == "Beta") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+## Clutch size ----
+bootstrap_df %>%
+  filter(Phenotype == "Clutch size", Selection_Type == "Beta") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
+
+## Female preference ----
+bootstrap_df %>%
+  filter(Phenotype == "Female preference", Selection_Type == "Beta") %>%
+  mutate(ID = rep(1:1000,2)) %>%
+  spread(Food_Web, Bootstrap_Estimates) %>%
+  mutate(diff_gradient = Complex - Simple) %>%
+  summarise(p_value = sum(diff_gradient < 0)/1000)
 ```
@@
 
-```{r}
+```{r GLMM Univariate Landscapes, eval=FALSE}
+
+## Gall size ----
 HPD_50_treatment_size <- coda::HPDinterval(coda::as.mcmc(treatment_df$sc.gall_size), prob=0.5)
@@
      sc.female_preference = 0),
-  bootstraps=1000)
+  bootstraps=10)
 
@@
      sc.female_preference = 0),
-  bootstraps=1000)
+  bootstraps=100)
 
@@
   xlab("Gall size (mm)")
-```
-
-```{r}
+
+## Clutch size ----
+
 ## Get Highest Posterior Density Intervals for clutch size phenotype
@@
   xlab("Clutch size")
-```
-
-```{r}
-## Get Highest Posterior Density Intervals for clutch size phenotype
+
+## Female preference ----
+## Get Highest Posterior Density Intervals for female preference phenotype
 
@@
 
-```{r}
+```{r GLMM Multivariate Landscapes, eval=FALSE}
+
+## Clutch size x Female Preference ----
 RF_treatment_clutch_preference <- relative_fitness_intervals(
@@
 
-```{r}
-distribution_female_preference <- distinct(.data=gall_selection.df, Plant_Position, Density_per_100_shoots)$Density_per_100_shoots 
-HPDinterval_female_preference <- coda::HPDinterval(coda::as.mcmc(scale(distribution_female_preference)), prob=0.95); HPDinterval_female_preference
-
-bind_rows(mutate(visreg(glmer_treatment, xvar="sc.female_preference", scale="response", plot=F)$fit, 
-                   Treatment="Simple", `Relative fitness` = visregFit/mean(visregFit)), 
-          mutate(visreg(glmer_control, xvar="sc.female_preference", scale="response", plot=F)$fit, 
-                   Treatment="Complex", `Relative fitness` = visregFit/mean(visregFit))) %>%
-  ggplot(., aes(x=sc.female_preference, y=`Relative fitness`, color=Treatment)) +
-  geom_line() +
-  scale_x_continuous(limits = c(HPDinterval_female_preference[1], HPDinterval_female_preference[2]))
-```
-
-```{r}
-distribution_clutch_size <- distinct(.data=gall_selection.df, Plant_Position, Gall_Number, gall_individuals)$gall_individuals
-HPDinterval_clutch_size <- coda::HPDinterval(coda::as.mcmc(scale(distribution_clutch_size)), prob=0.95); HPDinterval_clutch_size
-
-bind_rows(mutate(visreg(glmer_treatment, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
-                   Treatment="Simple", `Relative fitness` = visregFit/mean(visregFit)), 
-          mutate(visreg(glmer_control, xvar="sc.clutch_size", scale="response", plot=F)$fit, 
-                   Treatment="Complex", `Relative fitness` = visregFit/mean(visregFit))) %>%
-  ggplot(., aes(x=sc.clutch_size, y=`Relative fitness`, color=Treatment)) +
-  geom_line() +
-  scale_x_continuous(limits = c(HPDinterval_clutch_size[1], HPDinterval_clutch_size[2]))
-```
-
-```{r}
-distribution_gall_size <- distinct(.data=gall_selection.df, Plant_Position, Gall_Number, Gall_Letter, Gall_Height_mm)$Gall_Height_mm
-HPDinterval_gall_size <- coda::HPDinterval(coda::as.mcmc(scale(distribution_gall_size)), prob=0.95); HPDinterval_gall_size
-
-predict_gall_size_df <- data.frame(sc.gall_size = seq(HPDinterval_gall_size[1], HPDinterval_gall_size[2], length.out=100),
-                                   sc.clutch_size = 0,
-                                   sc.female_preference = 0)
-model_matrix_gall_size <- model.matrix(~sc.gall_size + sc.clutch_size + sc.female_preference, predict_gall_size_df)
-
-# ref: https://www.r-bloggers.com/confidence-intervals-for-prediction-in-glmms/
-boot_treatment_gall_size <-bootMer(glmer_treatment, FUN = function(.) inverse_logit(model_matrix_gall_size %*% fixef(.)), nsim=200)
-se_treatment_gall_size <- apply(boot_treatment_gall_size$t, 2, function(x) x[order(x)])
-boot_lower <- se_treatment_gall_size[1, ]
-boot_upper <- se_treatment_gall_size[2, ]
-
-bind_rows(mutate(visreg(glmer_treatment, xvar="sc.gall_size", scale="response", plot=F)$fit, 
-                   Treatment="Simple", `Relative fitness` = visregFit/Wbar_treatment), 
-          mutate(visreg(glmer_control, xvar="sc.gall_size", scale="response", plot=F)$fit, 
-                   Treatment="Complex", `Relative fitness` = visregFit/Wbar_control)) %>%
-  ggplot(., aes(x=sc.gall_size, y=`Relative fitness`, color=Treatment)) +
-  geom_line() +
-  geom_ribbon(aes(ymin=boot_lower, ymax=boot_upper)) +
-  scale_x_continuous(limits = c(HPDinterval_gall_size[1], HPDinterval_gall_size[2]))
-```
-
 Choosing the level of model complexity.
@@
 
-```{r AIC MODEL COMPLEXITY}
+```{r AIC Model Selection v0.1, eval=FALSE}
 
 ## CONTROL PLANTS ----
-gamm_full.control <- gamm.model(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots) +
-                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
+gamm_full.control <- gamm.model(gall_survival ~ 
+                                  s(Gall_Height_mm) + 
+                                  s(gall_individuals, k=9) + 
+                                  s(Density_per_100_shoots) +
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots + 
+                                  gall_individuals:Density_per_100_shoots,
                                 data = control_df)
-summary(gamm_full.control$gam); summary(gamm_full.control$mer)
-
-glmm_full.control <- gamm.model(gall_survival ~ Gall_Height_mm + gall_individuals + Density_per_100_shoots +
+summary(gamm_full.control$gam)
+summary(gamm_full.control$mer)
+
+glmm_full.control <- gamm.model(gall_survival ~ 
+                                  Gall_Height_mm + 
+                                  gall_individuals + 
+                                  Density_per_100_shoots +
                                   I(Gall_Height_mm^2) + I(gall_individuals^2) + I(Density_per_100_shoots^2) +
-                                  Gall_Height_mm:gall_individuals + Gall_Height_mm:Density_per_100_shoots + gall_individuals:Density_per_100_shoots,
+                                  Gall_Height_mm:gall_individuals + 
+                                  Gall_Height_mm:Density_per_100_shoots + 
+                                  gall_individuals:Density_per_100_shoots,
                                 data = control_df)
@@
 
-```{r}
-library(schoenberg)
-pointwise <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))})
-simultaneous <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))}, type = "simultaneous", seWithMean=TRUE)
-
-compare.confint <- bind_rows(mutate(pointwise, confint = "pointwise"), mutate(simultaneous, confint = "simultaneous")) 
-compare.confint$confint <- relevel(factor(compare.confint$confint), ref = "simultaneous")
-
-ggplot(compare.confint, aes(x=Gall_Height_mm)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper), alpha=0.25) +
-  geom_line(aes(y=est), color="black") +
-  facet_wrap(~confint)
-
-schluter <- gam.plot(gamm_red.control$gam)
-schluter
-
-gam.plot(glmm_lin.red.control$gam, all.terms=TRUE)
-test <- plot(glmm_lin.red.control$gam, all.terms=TRUE)
-gam.gradients(mod = glmm_lin.red.control$gam, phenotype = "Gall_Height_mm", se.method = "n")
-coef(glmm_lin.red.control$gam)
-
-# test derivative calculations
-control_df$Genotype <- factor(control_df$Genotype)
-control_df$Plant_Position <- factor(control_df$Plant_Position)
-control_df$Gall_Number <- factor(control_df$Gall_Number)
-A <- gam(gall_survival ~ s(Gall_Height_mm) + s(Plant_Position, bs="re") + s(Gall_Number, bs="re"), data = control_df, family=binomial(link=logit)) # random=~(1|Genotype/Plant_Position/Gall_Number),
-summary(A)
-
-head(control_df)
-A_withMean <- plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_withMean
-A_only <- plot(A, se = TRUE, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_only
-draw(A)
-
-# new data for prediction
-newDF <- with(control_df, data.frame(Gall_Height_mm = seq(min(Gall_Height_mm),max(Gall_Height_mm),length.out = 100)))
-# prediction of smoothed estimates at each unique year value
-# with standard error    
-B <- predict(A$gam,  newDF, type="response", se.fit=TRUE)
-B
-
-# finite difference approach to derivatives following
-# example from ?predict.gam
-
-eps <- 1e-7
-X0 <- predict(A, newDF, type = 'lpmatrix')
-X0 <- exp(X0)/(1+exp(X0))
-
-newDFeps_p <- newDF + eps
-
-X1 <- predict(A, newDFeps_p, type = 'lpmatrix')
-X1 <- exp(X1)/(1+exp(X1))
-# finite difference approximation of first derivative
-# the design matrix
-Xp <- (X0 - X1) / eps
-Xp
-# first derivative
-fd_d1 <- Xp %*% coef(A)
-fd_d1/mean_fit
-# second derivative
-newDFeps_m <- newDF - eps
-
-X_1 <- predict(A$gam, newDFeps_m, type = 'lpmatrix')
-# design matrix for second derivative
-Xpp <- (X1 + X_1 - 2*X0)  / eps^2
-# second derivative
-fd_d2 <- Xpp %*% coef(A$gam)
-
-exp(fd_d1) / ( 1+exp(fd_d1))  # type = "response"
-exp(fd_d2) / ( 1+exp(fd_d2))  # type = "response"
-
-mean(fd_d1)/mean_fit
-mean(fd_d2)/mean_fit
-
-gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
-
-coef(A)
-mean_fit <- mean(control_df$gall_survival)
-fderiv_size <- fderiv(A, newdata = data.frame(Gall_Height_mm = mean(control_df$Gall_Height_mm)), offset = mean_fit)
-test <- fderiv_size$derivatives$`s(Gall_Height_mm)`$deriv
-exp(test)/(1+exp(test))
-
-plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))})
-diff <- .Machine$double.eps^(1/3)
-predicts <- predict(A, newdata = data.frame(Gall_Height_mm = c(mean(control_df$Gall_Height_mm)-diff,mean(control_df$Gall_Height_mm)+diff)), type="lpmatrix")
-tests <- predicts %*% coef(A)
-exp(tests)/(1+exp(tests))
-t1 <- exp(predicts[2])/(1+exp(predicts[2]));t1
-t2 <- exp(predicts[1])/(1+exp(predicts[1]));t2
-((t1-t2)/(diff*2))/mean(control_df$gall_survival)
-gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
-
-	Wbar <- function(x, mod, phenotype,covariates) {
-    		new.d <- as.data.frame(mod$model[,c(phenotype,covariates)])
-    		names(new.d)<-c(phenotype,covariates)
-    		new.d2<-new.d
-    		for (i in 1:length(x)) {
-    		    new.d[,as.character(phenotype[i])] <-
-    		    new.d[,as.character(phenotype[i])]+x[i]
-    		}
-
-    		p <- predict.gam(
-			   object=mod,
-    	 	   newdata=new.d,
-    	 	   newdata.guaranteed=TRUE,
-    	 	   type="response"
-    		)
-    	return(mean(p))
-	}
-	as.data.frame(A$model[ ,"Gall_Height_mm"])
-	#mean(control_df$gall_survival)
-	Wbar(x=0, mod=A, phenotype="Gall_Height_mm", covariates=NULL)
-first.derivatives <- grad(f=Wbar, x=rep(0, 1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); first.derivatives
-denom <- Wbar(x=rep(0,1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); denom
-first.derivatives/denom
-pracma:::grad
-A$Vp
-A$coefficients
-A_withMean
-```
-
 Parametric bootstrapping: Currently reported results
@@
 In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
-```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE}
-
-## Estimate directional, nonlinear, and correlational selection gradients
+```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE, eval=FALSE}
+
+## Estimate directional, nonlinear, and correlational selection gradients ----
 sg.size_control <- gradient.calc(mod = gamm_red.control$gam, 
@@
 
-## Summarise the results
+## Summarise the results ----
 sg.summary <- bind_rows(
@@
 
-## Table of Estimates
+## Table of Estimates ----
 sg.table <- sg.summary %>%
@@
 
-## Table of P-values
+## Table of P-values ----
 sg.summary %>%
@@
 
-```{r}
+```{r Selection Gradients - Bootstrapped Intervals, eval=FALSE}
 
@@
 Compare bootstrapped replicates across treatments, rather than comparing to zero.
-```{r}
+```{r Compare bootstrapped replicates across treatments, eval=FALSE}
 bootstrap_df %>%
@@
   summarise(p_value = sum(diff_gradient < 0)/1000)
-```
-
-```{r}
-gam.plot(gamm_red.control$gam, select="Gall_Height_mm")
 ```

### 2018-06-08 morgue_supp_mat.Rmd
adding some things I don't anticipate needing anymore

@@
 
+```{r gsg Comparison}
+
+## Fit generalized additive mixed models ----
+gamm_control_2 <- gamm.model(gall_survival ~ s(sc.gall_size) + s(sc.clutch_size,k=9) + s(sc.female_preference),
+                             data = control_df)
+
+gamm_treatment_2 <- gamm.model(gall_survival ~ s(sc.gall_size) + s(sc.clutch_size,k=9) + s(sc.female_preference),
+                             data = treatment_df)
+
+## Estimate directional, nonlinear, and correlational selection gradients ----
+sg.size_control <- gradient.calc(mod = gamm_control_2$gam, 
+                                 phenotype = "sc.gall_size", 
+                                 covariates = c("sc.clutch_size","sc.female_preference"))
+sg.size_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+                                   phenotype = "sc.gall_size", 
+                                   covariates = c("sc.clutch_size","sc.female_preference"))
+sg.clutch_control <- gradient.calc(mod = gamm_control_2$gam, 
+                                        phenotype = "sc.clutch_size", 
+                                        covariates = c("sc.gall_size","sc.female_preference"))
+sg.clutch_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+                                          phenotype = "sc.clutch_size", 
+                                          covariates = c("sc.gall_size","sc.female_preference"))
+sg.preference_control <- gradient.calc(mod = gamm_control_2$gam, 
+                                    phenotype = "sc.female_preference", 
+                                    covariates = c("sc.clutch_size","sc.gall_size"))
+sg.preference_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+                                      phenotype = "sc.female_preference", 
+                                      covariates = c("sc.clutch_size","sc.gall_size"))
+#sg.size.x.clutch_control <- gradient.calc(mod = gamm_control_2$gam, 
+#                                               phenotype = c("sc.gall_size", "sc.clutch_size"),
+#                                               covariates = c("sc.female_preference"))
+#sg.size.x.clutch_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+#                                                 phenotype = c("sc.gall_size", "sc.clutch_size"),
+#                                                 covariates = c("sc.female_preference"))
+#sg.size.x.preference_control <- gradient.calc(mod = gamm_control_2$gam, 
+#                                               phenotype = c("sc.gall_size", "sc.female_preference"),
+#                                               covariates = c("sc.clutch_size"))
+#sg.size.x.preference_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+#                                                 phenotype = c("sc.gall_size","sc.female_preference"),
+#                                                 covariates = c("sc.clutch_size"))
+#sg.preference.x.clutch_control <- gradient.calc(mod = gamm_control_2$gam, 
+#                                                  phenotype = c("sc.female_preference", "sc.clutch_size"),
+#                                                  covariates = c("sc.gall_size"))
+#sg.preference.x.clutch_treatment <- gradient.calc(mod = gamm_treatment_2$gam, 
+#                                                    phenotype = c("sc.female_preference", "sc.clutch_size"),
+#                                                    covariates = c("sc.gall_size"))
+
+## Summarise the results ----
+#sg.summary <- bind_rows(
+#          data.frame(sg.size_control$ests,  
+#                     gradients = rownames(sg.size_control$ests),
+#                     treatment = "Complex"),
+#          data.frame(sg.size_treatment$ests, 
+#                     gradients = rownames(sg.size_treatment$ests),
+#                     treatment = "Simple"),
+#          data.frame(sg.clutch_control$ests,  
+#                     gradients = rownames(sg.clutch_control$ests),
+#                     treatment = "Complex"),
+#          data.frame(sg.clutch_treatment$ests,  
+#                     gradients = rownames(sg.clutch_treatment$ests),
+#                     treatment = "Simple"),
+#          data.frame(sg.preference_control$ests, 
+#                     gradients = rownames(sg.preference_control$ests),
+#                     treatment = "Complex"),
+#          data.frame(sg.preference_treatment$ests, 
+#                     gradients = rownames(sg.preference_treatment$ests),
+#                     treatment = "Simple"))#,
+          #data.frame(sg.size.x.clutch_control$ests,  
+          #           gradients = rownames(sg.size.x.clutch_control$ests),
+          #           treatment = "Complex")[5,],
+          #data.frame(sg.size.x.clutch_treatment$ests,  
+          #           gradients = rownames(sg.size.x.clutch_treatment$ests),
+          #           treatment = "Simple")[5,],
+          #data.frame(sg.size.x.preference_control$ests,  
+          #           gradients = rownames(sg.size.x.preference_control$ests),
+          #           treatment = "Complex")[5,],
+          #data.frame(sg.size.x.preference_treatment$ests,  
+          #           gradients = rownames(sg.size.x.preference_treatment$ests),
+          #           treatment = "Simple")[5,],
+          #data.frame(sg.preference.x.clutch_control$ests, 
+          #           gradients = rownames(sg.preference.x.clutch_control$ests),
+          #           treatment = "Complex")[5,],
+          #data.frame(sg.preference.x.clutch_treatment$ests, 
+          #           gradients = rownames(sg.preference.x.clutch_treatment$ests),
+          #           treatment = "Simple")[5,])
+
+## Table of Estimates ----
+#sg.table <- sg.summary %>%
+#  mutate(plus_minus = "\u00B1", estimates = round(estimates, 4), SE = round(SE, 4)) %>%
+#  unite(col = estimate_SE, from = c("estimates", "plus_minus", "SE"), sep="") %>%
+#  select(-P.value) %>%
+#  spread(treatment, estimate_SE)
+#sg.table
+#write_csv(sg.table, "sg.table.csv")
+
+## Table of P-values ----
+#sg.summary %>%
+#  select(-estimates, -SE) %>%
+#  spread(treatment, P.value)
+
+## BOOTSTRAPPED INTERVALS ----
+bootstrap_df <- bind_rows(
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web = "Simple"),
+#  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.clutch_control$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.clutch_control$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.clutch_treatment$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web = "Simple"),
+#  data.frame(Bootstrap_Estimates = sg.clutch_treatment$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.preference_control$boot[ ,1], Phenotype = "Female preference", Selection_Type = "Beta", Food_Web = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.preference_control$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.preference_treatment$boot[ ,1], Phenotype = "Female preference", Selection_Type = "Beta", Food_Web = "Simple"))#,
+#  data.frame(Bootstrap_Estimates = sg.preference_treatment$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  # correlational
+#  data.frame(Bootstrap_Estimates = sg.size.x.clutch_control$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.size.x.clutch_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+#    data.frame(Bootstrap_Estimates = sg.size.x.preference_control$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.size.x.preference_treatment$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+#  data.frame(Bootstrap_Estimates = sg.preference.x.clutch_control$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.preference.x.clutch_treatment$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
+#)
+
+bootstrap_df %>%
+  #filter(Selection_Type == "Gamma") %>%
+  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web)) +
+  geom_boxplot() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_Type, scales = "free_x") +
+  coord_flip()
+
+gsg_gradients <- bootstrap_df %>%
+  group_by(Phenotype, Food_Web) %>%
+  summarise(Beta = round(mean(Bootstrap_Estimates),3),
+            lower_2.5 = round(quantile(Bootstrap_Estimates, probs = 0.025),3),
+            upper_97.5 = round(quantile(Bootstrap_Estimates, probs = 0.975),3)) %>%
+  mutate(Model = "gsg_GAMM")
+
+bind_rows(gsg_gradients, summary_Beta_glmm_control, summary_Beta_glmm_treatment) %>%
+  arrange(Phenotype, Food_Web, Model) %>%
+  mutate(absolute_range = upper_97.5 - lower_2.5) %>%
+  knitr::kable(.)
+```
+
+```{r} 
 ggplot_uniFL <- function(FL.df) {
@@
 }
+```
+
+```{r Selection Gradients - Bootstrapped Intervals, eval=FALSE}
+
+## BOOTSTRAPPED INTERVALS ----
+bootstrap_df <- bind_rows(
+  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.size_control$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,1], Phenotype = "Gall size", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+#  data.frame(Bootstrap_Estimates = sg.size_treatment$boot[ ,2], Phenotype = "Gall size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.clutch_control$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.clutch_control$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.clutch_treatment$boot[ ,1], Phenotype = "Clutch size", Selection_Type = "Beta", Food_Web_Treatment = "Simple"),
+#  data.frame(Bootstrap_Estimates = sg.clutch_treatment$boot[ ,2], Phenotype = "Clutch size", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  data.frame(Bootstrap_Estimates = sg.preference_control$boot[ ,1], Phenotype = "Female preference", Selection_Type = "Beta", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.preference_control$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Complex"),
+  data.frame(Bootstrap_Estimates = sg.preference_treatment$boot[ ,1], Phenotype = "Female preference", Selection_Type = "Beta", Food_Web_Treatment = "Simple"))#,
+#  data.frame(Bootstrap_Estimates = sg.preference_treatment$boot[ ,2], Phenotype = "Oviposition preference", Selection_Type = "Gamma", Food_Web_Treatment = "Simple"),
+  # correlational
+#  data.frame(Bootstrap_Estimates = sg.size.x.clutch_control$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.size.x.clutch_treatment$boot[ ,5], Phenotype = "Size,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+#    data.frame(Bootstrap_Estimates = sg.size.x.preference_control$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.size.x.preference_treatment$boot[ ,5], Phenotype = "Size,Pref.", Selection_Type = "Correlational", Food_Web_Treatment = "Simple"),
+#  data.frame(Bootstrap_Estimates = sg.preference.x.clutch_control$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Complex"),
+#  data.frame(Bootstrap_Estimates = sg.preference.x.clutch_treatment$boot[ ,5], Phenotype = "Pref.,Clutch", Selection_Type = "Correlational", Food_Web_Treatment = "Simple")
+#)
+
+bootstrap_df %>%
+  #filter(Selection_Type == "Gamma") %>%
+  ggplot(., aes(x=Phenotype, y=Bootstrap_Estimates, fill=Food_Web_Treatment)) +
+  geom_boxplot() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_Type, scales = "free_x") +
+  coord_flip()
+
+gsg_gradients <- bootstrap_df %>%
+  group_by(Phenotype, Food_Web_Treatment) %>%
+  summarise(Beta = round(mean(Bootstrap_Estimates),3),
+            lower_2.5 = round(quantile(Bootstrap_Estimates, probs = 0.025),3),
+            upper_97.5 = round(quantile(Bootstrap_Estimates, probs = 0.975),3))
+
+knitr::kable(gsg_gradients)
+```
+
+```{r}
+library(schoenberg)
+pointwise <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))})
+simultaneous <- confint(gamm_red.control$gam, parm = "Gall_Height_mm", trans = function(x) {exp(x)/(1+exp(x))}, type = "simultaneous", seWithMean=TRUE)
+
+compare.confint <- bind_rows(mutate(pointwise, confint = "pointwise"), mutate(simultaneous, confint = "simultaneous")) 
+compare.confint$confint <- relevel(factor(compare.confint$confint), ref = "simultaneous")
+
+ggplot(compare.confint, aes(x=Gall_Height_mm)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper), alpha=0.25) +
+  geom_line(aes(y=est), color="black") +
+  facet_wrap(~confint)
+
+schluter <- gam.plot(gamm_red.control$gam)
+schluter
+
+gam.plot(glmm_lin.red.control$gam, all.terms=TRUE)
+test <- plot(glmm_lin.red.control$gam, all.terms=TRUE)
+gam.gradients(mod = glmm_lin.red.control$gam, phenotype = "Gall_Height_mm", se.method = "n")
+coef(glmm_lin.red.control$gam)
+
+# test derivative calculations
+control_df$Genotype <- factor(control_df$Genotype)
+control_df$Plant_Position <- factor(control_df$Plant_Position)
+control_df$Gall_Number <- factor(control_df$Gall_Number)
+A <- gam(gall_survival ~ s(Gall_Height_mm) + s(Plant_Position, bs="re") + s(Gall_Number, bs="re"), data = control_df, family=binomial(link=logit)) # random=~(1|Genotype/Plant_Position/Gall_Number),
+summary(A)
+
+head(control_df)
+A_withMean <- plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_withMean
+A_only <- plot(A, se = TRUE, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))}); A_only
+draw(A)
+
+# new data for prediction
+newDF <- with(control_df, data.frame(Gall_Height_mm = seq(min(Gall_Height_mm),max(Gall_Height_mm),length.out = 100)))
+# prediction of smoothed estimates at each unique year value
+# with standard error    
+B <- predict(A$gam,  newDF, type="response", se.fit=TRUE)
+B
+
+# finite difference approach to derivatives following
+# example from ?predict.gam
+
+eps <- 1e-7
+X0 <- predict(A, newDF, type = 'lpmatrix')
+X0 <- exp(X0)/(1+exp(X0))
+
+newDFeps_p <- newDF + eps
+
+X1 <- predict(A, newDFeps_p, type = 'lpmatrix')
+X1 <- exp(X1)/(1+exp(X1))
+# finite difference approximation of first derivative
+# the design matrix
+Xp <- (X0 - X1) / eps
+Xp
+# first derivative
+fd_d1 <- Xp %*% coef(A)
+fd_d1/mean_fit
+# second derivative
+newDFeps_m <- newDF - eps
+
+X_1 <- predict(A$gam, newDFeps_m, type = 'lpmatrix')
+# design matrix for second derivative
+Xpp <- (X1 + X_1 - 2*X0)  / eps^2
+# second derivative
+fd_d2 <- Xpp %*% coef(A$gam)
+
+exp(fd_d1) / ( 1+exp(fd_d1))  # type = "response"
+exp(fd_d2) / ( 1+exp(fd_d2))  # type = "response"
+
+mean(fd_d1)/mean_fit
+mean(fd_d2)/mean_fit
+
+gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
+
+coef(A)
+mean_fit <- mean(control_df$gall_survival)
+fderiv_size <- fderiv(A, newdata = data.frame(Gall_Height_mm = mean(control_df$Gall_Height_mm)), offset = mean_fit)
+test <- fderiv_size$derivatives$`s(Gall_Height_mm)`$deriv
+exp(test)/(1+exp(test))
+
+plot(A, se = TRUE, seWithMean = T, shift = mean(predict(A)), trans = function(x) {exp(x)/(1+exp(x))})
+diff <- .Machine$double.eps^(1/3)
+predicts <- predict(A, newdata = data.frame(Gall_Height_mm = c(mean(control_df$Gall_Height_mm)-diff,mean(control_df$Gall_Height_mm)+diff)), type="lpmatrix")
+tests <- predicts %*% coef(A)
+exp(tests)/(1+exp(tests))
+t1 <- exp(predicts[2])/(1+exp(predicts[2]));t1
+t2 <- exp(predicts[1])/(1+exp(predicts[1]));t2
+((t1-t2)/(diff*2))/mean(control_df$gall_survival)
+gam.gradients(A, phenotype = "Gall_Height_mm", se.method="n", standardized = FALSE)
+
+	Wbar <- function(x, mod, phenotype,covariates) {
+    		new.d <- as.data.frame(mod$model[,c(phenotype,covariates)])
+    		names(new.d)<-c(phenotype,covariates)
+    		new.d2<-new.d
+    		for (i in 1:length(x)) {
+    		    new.d[,as.character(phenotype[i])] <-
+    		    new.d[,as.character(phenotype[i])]+x[i]
+    		}
+
+    		p <- predict.gam(
+			   object=mod,
+    	 	   newdata=new.d,
+    	 	   newdata.guaranteed=TRUE,
+    	 	   type="response"
+    		)
+    	return(mean(p))
+	}
+	as.data.frame(A$model[ ,"Gall_Height_mm"])
+	#mean(control_df$gall_survival)
+	Wbar(x=0, mod=A, phenotype="Gall_Height_mm", covariates=NULL)
+first.derivatives <- grad(f=Wbar, x=rep(0, 1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); first.derivatives
+denom <- Wbar(x=rep(0,1), mod=A, phenotype="Gall_Height_mm", covariates=NULL); denom
+first.derivatives/denom
+pracma:::grad
+A$Vp
+A$coefficients
+A_withMean
+```
 

### 2018-06-08 supp_mat_complexity_selection.Rmd
substantial progress in visualizing univariate fitness landscapes. Multivariate is next!

@@
 
-## Calculate confidence intervals of relative fitness
-relative_fitness_intervals <- function(logistic_model, newdata, bootstraps){
+## Bootstrap fitness estimates
+bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){
   model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
 
-  get_absolute_fitness <- function(.) {
-  absolute_fitness <- inverse_logit(model_matrix %*% fixef(.))
-  absolute_fitness#/mean(absolute_fitness) 
-  }
+  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))
 
   get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
-  browser()
-
-  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*0.025,0),round(bootstraps*0.975,0))])
-
-  #mean_fitness <- mean(get_absolute_fitness(logistic_model))
-
-  return(data.frame(relative_fitness = get_absolute_fitness(logistic_model),#/mean_fitness,
-                    lower_2.5 = get_intervals[1, ],#/mean_fitness,
-                    upper_97.5 = get_intervals[2, ],#/mean_fitness,
-                    newdata))
+
+  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  return(data.frame(newdata, 
+                    average = get_absolute_fitness(logistic_model), 
+                    lower = get_intervals[1, ],
+                    upper = get_intervals[2, ],
+                    t(get_bootstraps$t)))
 }
@@
 # Confidence intervals for selection gradients ----
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=1000, parallel="multicore", ncpus=32)
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
 
@@
 ## Confidence intervals for selection gradients ----
-boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=1000, parallel="multicore", ncpus=32)
+boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
 
@@
 Illustrating the relationship between phenotype and mean fitness depends critically on the range of parameters shown.
-Perhaps this is what it is a good idea to show it based on the actual phenotypic distributions, or for 1 +/- SD
+Perhaps this is what it is a good idea to show it based on the actual phenotypic distributions, or for 1 +/- SD.
+
+The reason why the intervals look so chunky is because I've used the actual phenotypic distributions rather than sampling evenly at high densities across the distribution.
+
+One interesting thing is that I don't believe the relative fitness intervals correspond to the absolute fitness intervals.
+This is likely because there can be a high absolute fitness, but the relative fitness might not change all that much...This means I need to figure out another way to plot these intervals.
+One easy way to do this would be to just return a list of two data frames, one that corresponds to absolute fitness and the other to relative fitness.
+This would be the easiest solution that would also remove a lot of redundancy in my code.
+
+```{r Gall Size Fitness Landscape}
+
+## Control ----
+RF_control_gall_size <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-2,2,length.out=1000), #sort(control_df$sc.gall_size),
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Treatment ----
+RF_treatment_gall_size <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-2,2,length.out=1000), #sort(treatment_df$sc.gall_size), 
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Spaghetti Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
+  group_by(ID, Food_Web) %>%
+  mutate(relative_fitness = fitness/mean(fitness)) %>%
+  ungroup() %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  group_by(Food_Web) %>%
+  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
+
+## Spaghetti Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
+
+```{r Clutch Size Fitness Landscapes}
+
+## Control ----
+RF_control_clutch_size <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = sort(distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), # note that these aren't unique
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Treatment ----
+RF_treatment_clutch_size <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = sort(distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), # note that these aren't unique
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Spaghetti Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.female_preference) %>%
+  gather(ID, fitness, -sc.clutch_size, -Food_Web) %>%
+  group_by(ID, Food_Web) %>%
+  mutate(relative_fitness = fitness/mean(fitness)) %>%
+  ungroup() %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Relative Fitness ----
+
+# unclear to me why the complex intervals are weird...
+bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+  group_by(Food_Web) %>%
+  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.clutch_size, y=relative_fitness)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
+
+## Spaghetti Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.female_preference) %>%
+  gather(ID, fitness, -sc.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.clutch_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.clutch_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
+
+```{r Female Preference Fitness Landscapes}
+
+## Control ----
+RF_control_female_preference <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0, 
+     sc.female_preference = sort(distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference)), 
+  bootstraps=100)
+
+## Treatment ----
+RF_treatment_female_preference <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0,
+     sc.female_preference = sort(distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference)), 
+  bootstraps=100)
+
+## Spaghetti Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.clutch_size) %>%
+  gather(ID, fitness, -sc.female_preference, -Food_Web) %>%
+  group_by(ID, Food_Web) %>%
+  mutate(relative_fitness = fitness/mean(fitness)) %>%
+  ungroup() %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Relative Fitness ----
+
+# unclear to me why the complex intervals are weird...
+bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+  group_by(Food_Web) %>%
+  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.female_preference, y=relative_fitness)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
+
+## Spaghetti Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.clutch_size) %>%
+  gather(ID, fitness, -sc.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.female_preference, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
 
@@
   newdata = expand.grid(
-     sc.gall_size = treatment_df$sc.gall_size, 
+     sc.gall_size = sort(treatment_df$sc.gall_size), 
      sc.clutch_size = 0,
@@
      sc.female_preference = 0),
-  bootstraps=100)
+  bootstraps=10)
 

### 2018-06-20 elsevier_test/elsevier_test.Rmd
drafting manuscript in Rstudio

---
title: Short Paper
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    footnote: Corresponding Author
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
abstract: |
  Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”. Given that the loss of biodiversity is simplifying the structure of ecological networks, there is a pressing need to answer the question: how does network complexity affect natural selection and the fitness landscape of associated species? To answer this question, we conducted a field experiment that manipulated the complexity of a food web associated with a galling insect herbivore. To maintain complex food webs, we allowed the entire community of natural enemies to attack insect galls on 64 plants in a common garden setting. To create simple food webs, we excluded a guild of three larval parasitoids by bagging galls on 64 different plants; therefore, mortality in this treatment was primarily due to a single egg parasitoid that attacks prior to gall formation. We then measured herbivore survival as a function of three key gall traits in each treatment. We found that more traits were under selection in the simple vs. complex food web. This occurred because different parasitoid species impose different selection pressures on gall traits, thereby minimizing relative fitness differences among insect galls with different phenotypes. Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change.

bibliography: mybibfile.bib
output: rticles::elsevier_article
---

_Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_

Introduction
============

Biological diversity -- from genes, to phenotypes, to species -- has fascinated evolutionary biologists for decades. However, the explicit context (i.e. ecological environment) is often abstracted and not examined in detail in studies of natural selection. Thus, we have a poor understanding of how biological diversity itself, imposes natural selection, and the potential feedbacks that may emerge.

In contrast, ecologists have begun to embrace the complexity of the natural world, and seeking to identify the complex networks of interactions that underlie community structure and ecosystem function. However, these studies have not examined how evolutionary processes feedback to shape the structure and evolution of these interaction networks.

We sought to bridge this gap through a field experiment that examines how food-web complexity alters the fitness landscape of species embedded within this food web.

Materials & Methods
===================

<!-- I. Give details about the study site, but not focusing on the genetic variation since this doesn't play much of a role in this manuscript. -->

To isolate the effects of coastal willow (\textit{S. hookeriana} Barratt ex Hooker) genetic variation on the plant-insect food web, we used a common garden experiment consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;'53"N, 124&deg;12'4"W) near Loleta, California, USA. Willow genotypes were collected from a single population of willows growing around Humboldt Bay. While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other [@Barbour2016-hz], suggesting that we can treat them as independent from one another. This common garden was planted in February 2009 with 25 clonal replicates (i.e. stem cuttings) of each willow genotype in a completely randomized design in two hectares of a former cattle pasture at HBNWR. Willows in our garden begin flowering in February and reach their peak growth in early August. During this study, willows had reached 2 - 4 m in height. Further details on the genotyping and planting of the common garden are available in (@Barbour2015-tp).

We conducted our study within a common garden consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA. Willow genotypes were collected from a single population of willows growing around Humboldt Bay. While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (Barbour et al. 2016), suggesting that we can treat them as independent from one another. This common garden was planted in February 2009 with 25 clonal replicates (i.e. stem cuttings) of each willow genotype in a completely randomized design in two hectares of a former cattle pasture at HBNWR. Willows in our garden begin flowering in February and reach their peak growth in early August. During this study, willows had reached 2 - 4 m in height. Further details on the genotyping and planting of the common garden are available in (Barbour et al. 2015). We conducted this experiment across 8 different plant genotypes that span the range of trait variation (Barbour et al. 2015).

<!-- II. Describe the food-web manipulation experiment -->

We setup our food-web manipulation soon after galls began developing on \textit{S. hookeriana} in early June of 2013. On treatment plants, we enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids). This treatment did not exclude the egg parasitoid \textit{Platygaster} sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). On control plants, we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack \textit{Iteomyia}. Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. In late August 2013, we collected marked and bagged galls from each plant. We placed galls in 30 mL transport vials and allowed them to complete development for 4 months at room temperature in the lab. We opened galls under a dissecting scope and determined whether larva survived to pupation, our measure of fitness, or were parasitized.

<!-- % III. Describe how we measured gall phenotypes -->

We collected data on three different phenotypes for each larva that have been shown to be important in our work (cite Barbour et al. 2016) and in other work with Cecidomyiid midges (CITE). First, we measured the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). Second, we counted the number of chambers in each gall, which is indicative of the number of larva per gall. All larva collected from the same gall were scored with the same 'number of larva per gall' phenotype. This trait is indicative of the clutch size of adult females.  %This trait likely reflects a combination of both larva feeding behavior as well as adult female preferences and clutch size (CITE Art Weis' work). 
Third, we estimated gall density as the number of larva per 100 shoots. We did this by counting the number of gall chambers on five randomly sampled branches per tree. To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant. All larva collected from the same plant were scored with the same gall density phenotype. This phenotype is indicative of the preference of female midges for particular plant traits (hereafter 'female preference').

<!-- % IV. Describe statistical analysis to test the effects of food-web complexity -->

We used generalized additive mixed models (GAMMs, cite Bolker et al. 2008) to test the effects of food-web complexity on the shape of fitness landscape. Larva survival (0 or 1) was our response variable and measure of fitness. We specified our food-web treatment, each gall trait, and all possible statistical interactions, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape. This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. We specified plant genotype, plant individual nested within genotype, and multi-chambered gall nested within plant individual, as random effects.

To account for the correlated structure of our gall phenotypes (female preference at plant-level; clutch size at gall-level; chamber size at chamber-level), we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.

From these GAMMs, we estimate selection gradients by assuming the mean value of our random effects (i.e. setting them to zero). This was appropriate for our analysis, since we were interested in estimating the fitness landscape, which is function of population mean fitness and mean trait values.

We used a spline-based semiparametric regression (Schluter 1988, Morrissey and Sakedra 2014). These analyses are desirable because they lead to inferences of the form of selection that make few \textit{a priori} assumptions (Schluter 1988), and can now be used to quantify standardized selection gradients (Morrissey and Sakrera 2014).

We then calculated selection gradients as the partial derivatives in absolute fitness (larva survival) with response to multivariate phenotype using the \textit{gsg} package in R (cite Morrissey and R project). We standardized phenotypes (mean=0, SD=1), so that first-order derivatives correspond to the intensity of directional selection ($\beta$\textsubscript{trait}), while second-order derivatives correspond to intensity of nonlinear ($\gamma$\textsubscript{trait}) and correlational selection ($\gamma$\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are thus comparable within this study as well as to others.

Our GLMMs are useful for testing the effects of food-web complexity on the fitness landscape within the context of our experimental design; however, coefficients from GLMMs cannot be easily converted into quantitative estimates of selection gradients (cite Morrissey's work). Therefore, for each treatment, we fit separate generalized additive models (GAMs) for gall traits that we identified as being under selection from our GLMMs. Estimating selection gradients from GAMs can give insight to both linear and non-linear selection gradients, which we assumed were all linear for our GLMMs, given the complexity of already fitting up to 4-way interactions in these models. For the number of larva per gall and gall density, we aggregated larva survival at the gall or plant level, respectively, to avoid pseudoreplication in our GAMs.

There are various bibliography styles available. You can select the
style of your choice in the preamble of this document. These styles are
Elsevier styles based on standard styles like Harvard and Vancouver.
Please use BibTeX to generate your bibliography and include DOIs
whenever available.

Here are two sample references: @Feynman1963118 [@Dirac1953888].

References {#references .unnumbered}
==========

### 2018-06-20 elsevier_test/elsevier_test.tex
drafting manuscript in Rstudio

--- 2018-06-20 elsevier_test/elsevier_test.Rmd
@@
----
-title: Short Paper
-author:
-  - name: Alice Anonymous
-    email: alice@example.com
-    affiliation: Some Institute of Technology
-    footnote: Corresponding Author
-  - name: Bob Security
-    email: bob@example.com
-    affiliation: Another University
-address:
-  - code: Some Institute of Technology
-    address: Department, Street, City, State, Zip
-  - code: Another University
-    address: Department, Street, City, State, Zip
-abstract: |
-  Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
-Given that the loss of biodiversity is simplifying the structure of ecological networks, there is a pressing need to answer the question: how does network complexity affect natural selection and the fitness landscape of associated species?
-To answer this question, we conducted a field experiment that manipulated the complexity of a food web associated with a galling insect herbivore.
-To maintain complex food webs, we allowed the entire community of natural enemies to attack insect galls on 64 plants in a common garden setting.
-To create simple food webs, we excluded a guild of three larval parasitoids by bagging galls on 64 different plants; therefore, mortality in this treatment was primarily due to a single egg parasitoid that attacks prior to gall formation.
-We then measured herbivore survival as a function of three key gall traits in each treatment.
-We found that more traits were under selection in the simple vs.
-complex food web.
-This occurred because different parasitoid species impose different selection pressures on gall traits, thereby minimizing relative fitness differences among insect galls with different phenotypes.
-Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change.
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
+\usepackage{lineno} % add
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 
-bibliography: mybibfile.bib
-output: rticles::elsevier_article
----
+\bibliographystyle{elsarticle-harv}
+\biboptions{sort&compress} % For natbib
+\usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
+%% Redefines the elsarticle footer
+%\makeatletter
+%\def\ps@pprintTitle{%
+% \let\@oddhead\@empty
+% \let\@evenhead\@empty
+% \def\@oddfoot{\it \hfill\today}%
+% \let\@evenfoot\@oddfoot}
+%\makeatother
 
-_Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_
+% A modified page layout
+\textwidth 6.75in
+\oddsidemargin -0.15in
+\evensidemargin -0.15in
+\textheight 9in
+\topmargin -0.5in
+%%%%%%%%%%%%%%%% end my additions to header
 
-Introduction
-============
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Short Paper},
+            colorlinks=true,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\setcounter{secnumdepth}{0}
+% Pandoc toggle for numbering sections (defaults to be off)
+\setcounter{secnumdepth}{0}
+% Pandoc header
 
-Biological diversity -- from genes, to phenotypes, to species -- has fascinated evolutionary biologists for decades.
-However, the explicit context (i.e.
-ecological environment) is often abstracted and not examined in detail in studies of natural selection.
-Thus, we have a poor understanding of how biological diversity itself, imposes natural selection, and the potential feedbacks that may emerge.
+\usepackage[nomarkers]{endfloat}
 
-In contrast, ecologists have begun to embrace the complexity of the natural world, and seeking to identify the complex networks of interactions that underlie community structure and ecosystem function.
-However, these studies have not examined how evolutionary processes feedback to shape the structure and evolution of these interaction networks.
+\begin{document}
+\begin{frontmatter}
 
-We sought to bridge this gap through a field experiment that examines how food-web complexity alters the fitness landscape of species embedded within this food web.
+  \title{Short Paper}
+    \author[Some Institute of Technology]{Alice Anonymous\corref{c1}}
+   \ead{alice@example.com} 
+   \cortext[c1]{Corresponding Author}
+    \author[Another University]{Bob Security}
+   \ead{bob@example.com}
 
-Materials & Methods
-===================
+      \address[Some Institute of Technology]{Department, Street, City, State, Zip}
+    \address[Another University]{Department, Street, City, State, Zip}
 
-<!-- I. Give details about the study site, but not focusing on the genetic variation since this doesn't play much of a role in this manuscript. -->
+  \begin{abstract}
+  Studies of natural selection and fitness landscapes usually treat the
+  network of interacting species as a ``black box''. Given that the loss
+  of biodiversity is simplifying the structure of ecological networks,
+  there is a pressing need to answer the question: how does network
+  complexity affect natural selection and the fitness landscape of
+  associated species? To answer this question, we conducted a field
+  experiment that manipulated the complexity of a food web associated with
+  a galling insect herbivore. To maintain complex food webs, we allowed
+  the entire community of natural enemies to attack insect galls on 64
+  plants in a common garden setting. To create simple food webs, we
+  excluded a guild of three larval parasitoids by bagging galls on 64
+  different plants; therefore, mortality in this treatment was primarily
+  due to a single egg parasitoid that attacks prior to gall formation. We
+  then measured herbivore survival as a function of three key gall traits
+  in each treatment. We found that more traits were under selection in the
+  simple vs.~complex food web. This occurred because different parasitoid
+  species impose different selection pressures on gall traits, thereby
+  minimizing relative fitness differences among insect galls with
+  different phenotypes. Our work suggests that more complex food webs
+  allow phenotypic variation to persist, which could facilitate subsequent
+  adaptive evolution to environmental change.
+  \end{abstract}
 
-To isolate the effects of coastal willow (\textit{S.
-hookeriana} Barratt ex Hooker) genetic variation on the plant-insect food web, we used a common garden experiment consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;'53"N, 124&deg;12'4"W) near Loleta, California, USA.
-Willow genotypes were collected from a single population of willows growing around Humboldt Bay.
-While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other [@Barbour2016-hz], suggesting that we can treat them as independent from one another.
-This common garden was planted in February 2009 with 25 clonal replicates (i.e.
-stem cuttings) of each willow genotype in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 2 - 4 m in height.
-Further details on the genotyping and planting of the common garden are available in (@Barbour2015-tp).
+ \end{frontmatter}
 
-We conducted our study within a common garden consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
-Willow genotypes were collected from a single population of willows growing around Humboldt Bay.
-While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (Barbour et al.
-2016), suggesting that we can treat them as independent from one another.
-This common garden was planted in February 2009 with 25 clonal replicates (i.e.
-stem cuttings) of each willow genotype in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 2 - 4 m in height.
-Further details on the genotyping and planting of the common garden are available in (Barbour et al.
-2015).
-We conducted this experiment across 8 different plant genotypes that span the range of trait variation (Barbour et al.
+\emph{Text based on elsarticle sample manuscript, see
+\url{http://www.elsevier.com/author-schemas/latex-instructions\#elsarticle}}
+
+\section{Introduction}\label{introduction}
+
+Biological diversity -- from genes, to phenotypes, to species -- has
+fascinated evolutionary biologists for decades. However, the explicit
+context (i.e.~ecological environment) is often abstracted and not
+examined in detail in studies of natural selection. Thus, we have a poor
+understanding of how biological diversity itself, imposes natural
+selection, and the potential feedbacks that may emerge.
+
+In contrast, ecologists have begun to embrace the complexity of the
+natural world, and seeking to identify the complex networks of
+interactions that underlie community structure and ecosystem function.
+However, these studies have not examined how evolutionary processes
+feedback to shape the structure and evolution of these interaction
+networks.
+
+We sought to bridge this gap through a field experiment that examines
+how food-web complexity alters the fitness landscape of species embedded
+within this food web.
+
+\section{Materials \& Methods}\label{materials-methods}
+
+To isolate the effects of coastal willow (\textit{S. hookeriana} Barratt
+ex Hooker) genetic variation on the plant-insect food web, we used a
+common garden experiment consisting of 26 different willow genotypes (13
+males; 13 females), located at Humboldt Bay National Wildlife Refuge
+(HBNWR) (40°'53``N, 124°12'4''W) near Loleta, California, USA. Willow
+genotypes were collected from a single population of willows growing
+around Humboldt Bay. While relatedness among these genotypes is unknown,
+their phenotypes in multivariate trait space are quite distinct from
+each other ({\textbf{???}}), suggesting that we can treat them as
+independent from one another. This common garden was planted in February
+2009 with 25 clonal replicates (i.e.~stem cuttings) of each willow
+genotype in a completely randomized design in two hectares of a former
+cattle pasture at HBNWR. Willows in our garden begin flowering in
+February and reach their peak growth in early August. During this study,
+willows had reached 2 - 4 m in height. Further details on the genotyping
+and planting of the common garden are available in (Barbour et al.
 2015).
 
-<!-- II. Describe the food-web manipulation experiment -->
+We conducted our study within a common garden consisting of 26 different
+willow genotypes (13 males; 13 females), located at Humboldt Bay
+National Wildlife Refuge (HBNWR) (40°40'53``N, 124°12'4''W) near Loleta,
+California, USA. Willow genotypes were collected from a single
+population of willows growing around Humboldt Bay. While relatedness
+among these genotypes is unknown, their phenotypes in multivariate trait
+space are quite distinct from each other (Barbour et al. 2016),
+suggesting that we can treat them as independent from one another. This
+common garden was planted in February 2009 with 25 clonal replicates
+(i.e.~stem cuttings) of each willow genotype in a completely randomized
+design in two hectares of a former cattle pasture at HBNWR. Willows in
+our garden begin flowering in February and reach their peak growth in
+early August. During this study, willows had reached 2 - 4 m in height.
+Further details on the genotyping and planting of the common garden are
+available in (Barbour et al. 2015). We conducted this experiment across
+8 different plant genotypes that span the range of trait variation
+(Barbour et al. 2015).
 
-We setup our food-web manipulation soon after galls began developing on \textit{S.
-hookeriana} in early June of 2013.
-On treatment plants, we enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
-This treatment did not exclude the egg parasitoid \textit{Platygaster} sp.
-which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE).
-On control plants, we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack \textit{Iteomyia}.
-Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
-In late August 2013, we collected marked and bagged galls from each plant.
-We placed galls in 30 mL transport vials and allowed them to complete development for 4 months at room temperature in the lab.
-We opened galls under a dissecting scope and determined whether larva survived to pupation, our measure of fitness, or were parasitized.
+We setup our food-web manipulation soon after galls began developing on
+\textit{S. hookeriana} in early June of 2013. On treatment plants, we
+enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to
+exclude three parasitoid species that attack during larva development
+(hereafter larval parasitoids). This treatment did not exclude the egg
+parasitoid \textit{Platygaster} sp. which attacks prior to gall
+initiation (note that in Cecidomyiid midges, larva initiate gall
+development CITE). On control plants, we used flagging tape to mark 14
+galled leaves per plant, allowing the full suite of parasitoids to
+attack \textit{Iteomyia}. Marking galls with flagging tape ensured that
+we compared control and treatment galls with similar phenology when we
+collected galls later in the season. In late August 2013, we collected
+marked and bagged galls from each plant. We placed galls in 30 mL
+transport vials and allowed them to complete development for 4 months at
+room temperature in the lab. We opened galls under a dissecting scope
+and determined whether larva survived to pupation, our measure of
+fitness, or were parasitized.
 
-<!-- % III. Describe how we measured gall phenotypes -->
-
-We collected data on three different phenotypes for each larva that have been shown to be important in our work (cite Barbour et al.
-2016) and in other work with Cecidomyiid midges (CITE).
-First, we measured the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
-Second, we counted the number of chambers in each gall, which is indicative of the number of larva per gall.
-All larva collected from the same gall were scored with the same 'number of larva per gall' phenotype.
-This trait is indicative of the clutch size of adult females.
-%This trait likely reflects a combination of both larva feeding behavior as well as adult female preferences and clutch size (CITE Art Weis' work).
-Third, we estimated gall density as the number of larva per 100 shoots.
-We did this by counting the number of gall chambers on five randomly sampled branches per tree.
-To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant.
-All larva collected from the same plant were scored with the same gall density phenotype.
-This phenotype is indicative of the preference of female midges for particular plant traits (hereafter 'female preference').
-
-<!-- % IV. Describe statistical analysis to test the effects of food-web complexity -->
+We collected data on three different phenotypes for each larva that have
+been shown to be important in our work (cite Barbour et al. 2016) and in
+other work with Cecidomyiid midges (CITE). First, we measured the size
+of each gall chamber to the nearest 0.01 mm at its maximum diameter
+(perpendicular to the direction of plant tissue growth). Second, we
+counted the number of chambers in each gall, which is indicative of the
+number of larva per gall. All larva collected from the same gall were
+scored with the same `number of larva per gall' phenotype. This trait is
+indicative of the clutch size of adult females. \%This trait likely
+reflects a combination of both larva feeding behavior as well as adult
+female preferences and clutch size (CITE Art Weis' work). Third, we
+estimated gall density as the number of larva per 100 shoots. We did
+this by counting the number of gall chambers on five randomly sampled
+branches per tree. To account for potential differences in the number of
+shoots per branch for each plant genotype (CITE other willow work), we
+then counted the number of shoots on the fifth branch to estimate the
+number of larva per 100 shoots for each plant. All larva collected from
+the same plant were scored with the same gall density phenotype. This
+phenotype is indicative of the preference of female midges for
+particular plant traits (hereafter `female preference').
 
 We used generalized additive mixed models (GAMMs, cite Bolker et al.
-2008) to test the effects of food-web complexity on the shape of fitness landscape.
-Larva survival (0 or 1) was our response variable and measure of fitness.
-We specified our food-web treatment, each gall trait, and all possible statistical interactions, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
-This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape.
-We specified plant genotype, plant individual nested within genotype, and multi-chambered gall nested within plant individual, as random effects.
+2008) to test the effects of food-web complexity on the shape of fitness
+landscape. Larva survival (0 or 1) was our response variable and measure
+of fitness. We specified our food-web treatment, each gall trait, and
+all possible statistical interactions, as fixed effects to fully explore
+the effects of food-web complexity on the fitness landscape. This
+analysis implicitly assumes that selection is linear, which we felt was
+a necessary trade-off for exploring the shape of the fitness landscape.
+We specified plant genotype, plant individual nested within genotype,
+and multi-chambered gall nested within plant individual, as random
+effects.
 
-To account for the correlated structure of our gall phenotypes (female preference at plant-level; clutch size at gall-level; chamber size at chamber-level), we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
+To account for the correlated structure of our gall phenotypes (female
+preference at plant-level; clutch size at gall-level; chamber size at
+chamber-level), we specified gall ID nested within plant ID nested
+within plant genotype as random intercepts in our statistical models.
 
-From these GAMMs, we estimate selection gradients by assuming the mean value of our random effects (i.e.
-setting them to zero).
-This was appropriate for our analysis, since we were interested in estimating the fitness landscape, which is function of population mean fitness and mean trait values.
+From these GAMMs, we estimate selection gradients by assuming the mean
+value of our random effects (i.e.~setting them to zero). This was
+appropriate for our analysis, since we were interested in estimating the
+fitness landscape, which is function of population mean fitness and mean
+trait values.
 
-We used a spline-based semiparametric regression (Schluter 1988, Morrissey and Sakedra 2014).
-These analyses are desirable because they lead to inferences of the form of selection that make few \textit{a priori} assumptions (Schluter 1988), and can now be used to quantify standardized selection gradients (Morrissey and Sakrera 2014).
+We used a spline-based semiparametric regression (Schluter 1988,
+Morrissey and Sakedra 2014). These analyses are desirable because they
+lead to inferences of the form of selection that make few
+\textit{a priori} assumptions (Schluter 1988), and can now be used to
+quantify standardized selection gradients (Morrissey and Sakrera 2014).
 
-We then calculated selection gradients as the partial derivatives in absolute fitness (larva survival) with response to multivariate phenotype using the \textit{gsg} package in R (cite Morrissey and R project).
-We standardized phenotypes (mean=0, SD=1), so that first-order derivatives correspond to the intensity of directional selection ($\beta$\textsubscript{trait}), while second-order derivatives correspond to intensity of nonlinear ($\gamma$\textsubscript{trait}) and correlational selection ($\gamma$\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are thus comparable within this study as well as to others.
+We then calculated selection gradients as the partial derivatives in
+absolute fitness (larva survival) with response to multivariate
+phenotype using the \textit{gsg} package in R (cite Morrissey and R
+project). We standardized phenotypes (mean=0, SD=1), so that first-order
+derivatives correspond to the intensity of directional selection
+(\(\beta\)\textsubscript{trait}), while second-order derivatives
+correspond to intensity of nonlinear (\(\gamma\)\textsubscript{trait})
+and correlational selection
+(\(\gamma\)\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are
+thus comparable within this study as well as to others.
 
-Our GLMMs are useful for testing the effects of food-web complexity on the fitness landscape within the context of our experimental design; however, coefficients from GLMMs cannot be easily converted into quantitative estimates of selection gradients (cite Morrissey's work).
-Therefore, for each treatment, we fit separate generalized additive models (GAMs) for gall traits that we identified as being under selection from our GLMMs.
-Estimating selection gradients from GAMs can give insight to both linear and non-linear selection gradients, which we assumed were all linear for our GLMMs, given the complexity of already fitting up to 4-way interactions in these models.
-For the number of larva per gall and gall density, we aggregated larva survival at the gall or plant level, respectively, to avoid pseudoreplication in our GAMs.
+Our GLMMs are useful for testing the effects of food-web complexity on
+the fitness landscape within the context of our experimental design;
+however, coefficients from GLMMs cannot be easily converted into
+quantitative estimates of selection gradients (cite Morrissey's work).
+Therefore, for each treatment, we fit separate generalized additive
+models (GAMs) for gall traits that we identified as being under
+selection from our GLMMs. Estimating selection gradients from GAMs can
+give insight to both linear and non-linear selection gradients, which we
+assumed were all linear for our GLMMs, given the complexity of already
+fitting up to 4-way interactions in these models. For the number of
+larva per gall and gall density, we aggregated larva survival at the
+gall or plant level, respectively, to avoid pseudoreplication in our
+GAMs.
 
@@
 Elsevier styles based on standard styles like Harvard and Vancouver.
-Please use BibTeX to generate your bibliography and include DOIs
+Please use BibTeX~to generate your bibliography and include DOIs
 whenever available.
 
-Here are two sample references: @Feynman1963118 [@Dirac1953888].
+Here are two sample references: ({\textbf{???}}; {\textbf{???}}).
 
-References {#references .unnumbered}
-==========
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
+
+\end{document}

### 2018-06-20 supp_mat_complexity_selection.Rmd

@@
 
+  # Absolute fitness
   get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))
 
-  get_bootstraps <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
-
-  get_intervals <- apply(get_bootstraps$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
-
-  return(data.frame(newdata, 
+  get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  absolute_fitness_df <- data.frame(newdata, 
                     average = get_absolute_fitness(logistic_model), 
-                    lower = get_intervals[1, ],
-                    upper = get_intervals[2, ],
-                    t(get_bootstraps$t)))
+                    lower = get_intervals_absolute_fitness[1, ],
+                    upper = get_intervals_absolute_fitness[2, ],
+                    t(get_bootstraps_absolute_fitness$t))
+
+  # Relative fitness
+  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))
+
+  get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  relative_fitness_df <- data.frame(newdata, 
+                    average = get_relative_fitness(logistic_model), 
+                    lower = get_intervals_relative_fitness[1, ],
+                    upper = get_intervals_relative_fitness[2, ],
+                    t(get_bootstraps_relative_fitness$t))
+  # Organize data
+  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
 }
@@
 
-```{r Gall Size Fitness Landscape}
+Okay, I solved the interval problem with relative fitness.
+Now I want to see if I can smooth up the 95% interval plots, by just plotting these 95% bootstrapped reps, shouldn't they be smooth lines?
+Is it something weird with geom_ribbon?
+
+```{r REVISED Gall Size Fitness Landscape}
+
+## Control ----
+RF_control_gall_size <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000), 
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Treatment ----
+RF_treatment_gall_size <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Spaghetti Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
+  #group_by(ID, Food_Web) %>%
+  #mutate(relative_fitness = fitness/mean(fitness)) %>%
+  #ungroup() %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
+  #group_by(Food_Web) %>%
+  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.gall_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+
+## Spaghetti Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
+
+```{r OLD Gall Size Fitness Landscape, eval=FALSE}
 
@@
      sc.gall_size = 0,
-     sc.clutch_size = sort(distinct(control_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), # note that these aren't unique
+     sc.clutch_size = seq(-1,1,length.out=1000),
      sc.female_preference = 0),
@@
      sc.gall_size = 0,
-     sc.clutch_size = sort(distinct(treatment_df, Plant_Position, Gall_Number, sc.clutch_size)$sc.clutch_size), # note that these aren't unique
+     sc.clutch_size = seq(-1,1,length.out=1000),
      sc.female_preference = 0),
@@
 ## Spaghetti Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
   select(-sc.gall_size, -sc.female_preference) %>%
-  gather(ID, fitness, -sc.clutch_size, -Food_Web) %>%
-  group_by(ID, Food_Web) %>%
-  mutate(relative_fitness = fitness/mean(fitness)) %>%
-  ungroup() %>%
+  gather(ID, relative_fitness, -sc.clutch_size, -Food_Web) %>%
+  #group_by(ID, Food_Web) %>%
+  #mutate(relative_fitness = fitness/mean(fitness)) %>%
+  #ungroup() %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
@@
 
-# unclear to me why the complex intervals are weird...
-bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
   group_by(Food_Web) %>%
-  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
-  ggplot(., aes(x=sc.clutch_size, y=relative_fitness)) +
+  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.clutch_size, y=average)) +
   geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
 
 ## Spaghetti Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
   select(-sc.gall_size, -sc.female_preference) %>%
-  gather(ID, fitness, -sc.clutch_size, -Food_Web) %>%
+  gather(ID, absolute_fitness, -sc.clutch_size, -Food_Web) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.clutch_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 ## Interval Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_clutch_size, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
   ggplot(., aes(x=sc.clutch_size, y=average)) +
@@
      sc.clutch_size = 0, 
-     sc.female_preference = sort(distinct(control_df, Plant_Position, sc.female_preference)$sc.female_preference)), 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
   bootstraps=100)
@@
      sc.clutch_size = 0,
-     sc.female_preference = sort(distinct(treatment_df, Plant_Position, sc.female_preference)$sc.female_preference)), 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
   bootstraps=100)
@@
 ## Spaghetti Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
   select(-sc.gall_size, -sc.clutch_size) %>%
-  gather(ID, fitness, -sc.female_preference, -Food_Web) %>%
-  group_by(ID, Food_Web) %>%
-  mutate(relative_fitness = fitness/mean(fitness)) %>%
-  ungroup() %>%
+  gather(ID, relative_fitness, -sc.female_preference, -Food_Web) %>%
+  #group_by(ID, Food_Web) %>%
+  #mutate(relative_fitness = fitness/mean(fitness)) %>%
+  #ungroup() %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
@@
 # unclear to me why the complex intervals are weird...
-bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
-  group_by(Food_Web) %>%
-  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
-  ggplot(., aes(x=sc.female_preference, y=relative_fitness)) +
+bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
+  #group_by(Food_Web) %>%
+  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.female_preference, y=average)) +
   geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
 
 ## Spaghetti Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
   select(-sc.gall_size, -sc.clutch_size) %>%
-  gather(ID, fitness, -sc.female_preference, -Food_Web) %>%
+  gather(ID, absolute_fitness, -sc.female_preference, -Food_Web) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.female_preference, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 ## Interval Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_female_preference, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference, Food_Web = "Complex")) %>%
+bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
   ggplot(., aes(x=sc.female_preference, y=average)) +

### 2018-06-21 elsevier_test/elsevier_test.Rmd
working on organization of intro

@@
 ---
-title: Short Paper
+title: Food-web complexity flattens the fitness landscape of an insect herbivore
 author:
-  - name: Alice Anonymous
-    email: alice@example.com
-    affiliation: Some Institute of Technology
+  - name: Matthew A. Barbour
+    email: matthew.barbour@ieu.uzh.ch
+    affiliation: Department of Evolutionary Biology and Environmental Studies, University of Zurich, Zurich, Switzerland
     footnote: Corresponding Author
-  - name: Bob Security
-    email: bob@example.com
+  - name: Jordi Bascompte
+    email: jordi.bascompte@ieu.uzh.ch
     affiliation: Another University
@@
 
+<!-- I. Community context can affect evolutionary change -->
+
 Biological diversity -- from genes, to phenotypes, to species -- has fascinated evolutionary biologists for decades.
-However, the explicit context (i.e.
-ecological environment) is often abstracted and not examined in detail in studies of natural selection.
-Thus, we have a poor understanding of how biological diversity itself, imposes natural selection, and the potential feedbacks that may emerge.
+
+Much of this biological diversity has been shaped by natural selection via trophic interactions, such as resource competition (cite charater displacement), mutualistic exchanges of resource (cite?
+), and predation (cite recent Heath and Stireman paper).
+
+NEED to recognize that evolutionary biologists have begun to explore how community context affects evolutionary change (work by Sharon Strauss, Casey terHorst, Lutz Becks, etc.).
+These results have begun to show interesting patterns whereby the composition of species in a community can alter the direction and strength of natural selection imposed on species embedded within these communities (cite).
+
+Put another way, these results have begun to show biological diversity, in terms of differences between species, can drive evolutionary change.
+
+While there is clear evidence for pairwise trophic interactions to drive evolution by natural selection, its unclear how biological diversity itself imposes natural selection and drives evolutionary change.
+
+<!-- II. Still unclear how biological diversity shapes evolutionary change -->
+
+Exploring the effects of biological diversity requires an explicit examination of the network structure of trophic interactions between species in a community.
+Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...); however, we are currently lacking experimental tests.
+
+<!-- II. Ecologists have incorporated community context -->
 
@@
 
+Results
+=======
+
+Discussion
+==========
+
+<!-- Feedbacks between biological diversity and evolutionary change -->
+
 There are various bibliography styles available. You can select the

### 2018-06-21 supp_mat_complexity_selection.Rmd
Revised plots of multivariate fitness landscapes for manuscript.

@@
 
+  if(is.null(bootstraps) == FALSE){
     get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
@@
                     t(get_bootstraps_absolute_fitness$t))
+  } else {
+    absolute_fitness_df <- data.frame(newdata, 
+                    average = get_absolute_fitness(logistic_model))
+  }
 
@@
 
+  if(is.null(bootstraps) == FALSE){
     get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
@@
                     t(get_bootstraps_relative_fitness$t))
+  } else {
+      relative_fitness_df <- data.frame(newdata, 
+                    average = get_relative_fitness(logistic_model))
+  }
+
   # Organize data
@@
   geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
+
+```{r Multivariate Landscapes}
+
+## Clutch size x Female preference ----
+
+# Control
+RF_control_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000), 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment
+RF_treatment_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+## Gall size x Clutch size ----
+
+# Control
+RF_control_size.x.clutch <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = seq(-1,1,length.out=1000), 
+     sc.female_preference = 0), 
+  bootstraps=NULL)
+
+# Treatment
+RF_treatment_size.x.clutch <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0), 
+  bootstraps=NULL)
+
+## Gall size x Female preference ----
+
+# Control
+RF_control_size.x.preference <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0, 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment
+RF_treatment_size.x.preference <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0,
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+## Relative fitness plots ----
+
+# Get range in relative fitness for accurate scaling across all plots
+RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
+          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
+          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+# Clutch x Preference
+RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+
+# Size x Clutch
+RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+
+# Size x Preference
+RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+
+# Get legend
+RF_landscape_legend <- get_legend(RF_plot_size.x.preference)
+
+# Format plots
+RF_landscape_plots <- plot_grid(
+  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
+  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
+  RF_plot_size.x.preference + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "AUTO")
+RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
+RF_landscape_2d
+save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
+
+## Absolute fitness landscapes ----
+AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
+          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
+          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+# Size x Preference
+AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Size x Clutch
+AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Clutch x Preference
+AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
+  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
+  AF_plot_size.x.preference + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "AUTO")
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
 ```

### 2018-06-21 supp_mat_complexity_selection.Rmd
created plots of selection gradients for manuscript. Also added .pdf versions of plots for presentations.

@@
 
-```{r REVISED Gall Size Fitness Landscape}
-
-## Control ----
+```{r Univariate Fitness Landscapes}
+## Gall size ----
+
+# Control
 RF_control_gall_size <- bootstrap_fitness(
@@
 
-## Treatment ----
+# Treatment
 RF_treatment_gall_size <- bootstrap_fitness(
@@
 
-## Spaghetti Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
+## Clutch size ----
+
+# Control
+RF_control_clutch_size <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0),
+  bootstraps=100)
+
+# Treatment 
+RF_treatment_clutch_size <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Female preference ----
+
+# Control 
+RF_control_female_preference <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0, 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=100)
+
+# Treatment
+RF_treatment_female_preference <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0,
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=100)
+
+## Relative fitness plots ----
+
+# Get range in relative fitness for accurate scaling across all plots
+RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
+          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
+          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, relative_fitness, -sc.gall_size) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  summarise(min = min(relative_fitness), max = max(relative_fitness))
+RF_gradient_scale <- c(0,0.5,1,1.5,2,2.5) # adjusted based on range
+
+# Color palette: order -> orange, light blue, green, yellow, dark blue, red, pink
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
+complex_color <- cbPalette[6]
+simple_color <- cbPalette[5]
+treatment_colors <- c(complex_color, simple_color)
+
+# Gall size    
+RF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
           mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
@@
   gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
-  #group_by(ID, Food_Web) %>%
-  #mutate(relative_fitness = fitness/mean(fitness)) %>%
-  #ungroup() %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
@@
   geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
-  #group_by(Food_Web) %>%
-  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
-  ggplot(., aes(x=sc.gall_size, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
-
-## Spaghetti Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Clutch size
+RF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.female_preference) %>%
+  gather(ID, relative_fitness, -sc.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Female preference 
+RF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.clutch_size) %>%
+  gather(ID, relative_fitness, -sc.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Get legend
+RF_uni_legend <- get_legend(RF_uni_size)
+
+# Make plots
+RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none"), 
+                       RF_uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       RF_uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       labels = "AUTO", ncol = 4, align='hv')
+
+RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
+RF_gradients
+save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
+save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
+
+## Absolute fitness plots ----
+
+# Get range in relative fitness for accurate scaling across all plots
+AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
+
+# Gall size 
+AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
           mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
@@
   geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
-```
-
-```{r OLD Gall Size Fitness Landscape, eval=FALSE}
-
-## Control ----
-RF_control_gall_size <- bootstrap_fitness(
-  logistic_model = glmer_control, 
-  newdata = expand.grid(
-     sc.gall_size = seq(-2,2,length.out=1000), #sort(control_df$sc.gall_size),
-     sc.clutch_size = 0,
-     sc.female_preference = 0),
-  bootstraps=100)
-
-## Treatment ----
-RF_treatment_gall_size <- bootstrap_fitness(
-  logistic_model = glmer_treatment, 
-  newdata = expand.grid(
-     sc.gall_size = seq(-2,2,length.out=1000), #sort(treatment_df$sc.gall_size), 
-     sc.clutch_size = 0,
-     sc.female_preference = 0),
-  bootstraps=100)
-
-## Spaghetti Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
-  select(-sc.clutch_size, -sc.female_preference) %>%
-  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
-  group_by(ID, Food_Web) %>%
-  mutate(relative_fitness = fitness/mean(fitness)) %>%
-  ungroup() %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
-  group_by(Food_Web) %>%
-  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
-  ggplot(., aes(x=sc.gall_size, y=relative_fitness)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
-
-## Spaghetti Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
-  select(-sc.clutch_size, -sc.female_preference) %>%
-  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
-```
-
-```{r Clutch Size Fitness Landscapes}
-
-## Control ----
-RF_control_clutch_size <- bootstrap_fitness(
-  logistic_model = glmer_control, 
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.clutch_size = seq(-1,1,length.out=1000),
-     sc.female_preference = 0),
-  bootstraps=100)
-
-## Treatment ----
-RF_treatment_clutch_size <- bootstrap_fitness(
-  logistic_model = glmer_treatment, 
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.clutch_size = seq(-1,1,length.out=1000),
-     sc.female_preference = 0),
-  bootstraps=100)
-
-## Spaghetti Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.female_preference) %>%
-  gather(ID, relative_fitness, -sc.clutch_size, -Food_Web) %>%
-  #group_by(ID, Food_Web) %>%
-  #mutate(relative_fitness = fitness/mean(fitness)) %>%
-  #ungroup() %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Relative Fitness ----
-
-bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
-  group_by(Food_Web) %>%
-  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
-  ggplot(., aes(x=sc.clutch_size, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
-
-## Spaghetti Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Clutch size
+AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
           mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
@@
   geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.clutch_size, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
-```
-
-```{r Female Preference Fitness Landscapes}
-
-## Control ----
-RF_control_female_preference <- bootstrap_fitness(
-  logistic_model = glmer_control, 
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.clutch_size = 0, 
-     sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=100)
-
-## Treatment ----
-RF_treatment_female_preference <- bootstrap_fitness(
-  logistic_model = glmer_treatment, 
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.clutch_size = 0,
-     sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=100)
-
-## Spaghetti Plot: Relative Fitness ----   
-bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.clutch_size) %>%
-  gather(ID, relative_fitness, -sc.female_preference, -Food_Web) %>%
-  #group_by(ID, Food_Web) %>%
-  #mutate(relative_fitness = fitness/mean(fitness)) %>%
-  #ungroup() %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Relative Fitness ----
-
-# unclear to me why the complex intervals are weird...
-bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
-  #group_by(Food_Web) %>%
-  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
-  ggplot(., aes(x=sc.female_preference, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
-
-## Spaghetti Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Female preference
+AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
           mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
@@
   geom_line() +
-  scale_alpha_manual(values=c(1,0.1)) +
-  scale_size_manual(values=c(1.5,0.25))
-
-## Interval Plot: Absolute Fitness ----   
-bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.female_preference, y=average)) +
-  geom_line(aes(color=Food_Web)) +
-  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Get legend
+AF_uni_legend <- get_legend(AF_uni_size)
+
+# Make plots
+AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
+                       AF_uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       AF_uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       labels = "AUTO", ncol = 4, align='hv')
+
+AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
+AF_gradients
+save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
+save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
 ```
@@
 save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
+save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
 
@@
 save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
+save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
 ```

### 2018-06-21 supp_mat_complexity_selection.Rmd
updated .Rmd to cache chunks so I don't have to rerun code that is unchanged.

@@
 
-```{r AIC Model Selection}
+```{r AIC Model Selection, cache=TRUE}
 
@@
 If these GLMMs have a lower AIC value than their respective GAMMs, then this suggests that there is only evidence of directional selection in our data.
-```{r}
+```{r GAMM vs GLMM, cache=TRUE}
 # Note that I still use gamm.model to allow for appropriate model comparisons
@@
 
-```{r Selection Gradients - Complex Food Web}
+```{r Selection Gradients - Complex Food Web, cache=TRUE}
 # note that I've switched to using the lme4 package to analyzing the GLMM
@@
 
-```{r Selection Gradients - Simple Food Web}
+```{r Selection Gradients - Simple Food Web, cache=TRUE}
 
@@
 To ensure we are calculating these selection gradients correctly, we'll compare our results to those obtained from the *gsg* package developed by Michael Morrissey.
-```{r Check Gradient Calculations}
+```{r Check Gradient Calculations, cache=TRUE}
 
@@
 
-```{r gsg Comparison}
+```{r gsg Comparison, cache=TRUE}
 
@@
 
-```{r Compare Selection Gradients across Treatments - GLMM}
+```{r Compare Selection Gradients across Treatments - GLMM, cache=TRUE}
 
@@
 
-```{r Compare Selection Gradients across Treatments - gsg GAMM}
+```{r Compare Selection Gradients across Treatments - gsg GAMM, cache=TRUE}
 
@@
 
-```{r Univariate Fitness Landscapes}
+```{r Univariate Fitness Landscapes, cache=TRUE}
 ## Gall size ----
@@
 
-```{r Multivariate Landscapes}
+```{r Multivariate Landscapes, cache=TRUE}
 
@@
 Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
-```{r Fitness Landscapes}
+```{r Fitness Landscapes, eval=FALSE}
 

### 2018-06-21 supp_mat_complexity_selection.Rmd
made .Rmd file knits .html efficiently
Former-commit-id: 87e02b4ec2fab993512768bd52398af43e95118e

@@
 ---
-title: "Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore"
-author: Matt Barbour
-output: html_notebook
+title: Supplementary Material for Food-web complexity alters the fitness landscape
+  of an insect herbivore
+author: "Matt Barbour"
+output:
+  html_document: default
+  html_notebook: default
 ---
@@
 This enabled us to focus on the selection pressures imposed by insect parasitoids rather than other sources.
-```{r setup}
-knitr::opts_chunk$set(include = FALSE)
+```{r setup, include=FALSE}
 
@@
 
-```{r AIC Model Selection, cache=TRUE}
+```{r AIC Model Selection, echo=TRUE, cache=TRUE}
 
@@
 
-```{r GLMM Univariate Landscapes, eval=FALSE}
+```{r GLMM Univariate Landscapes, eval=FALSE, include=FALSE}
 
@@
 
-```{r GLMM Multivariate Landscapes, eval=FALSE}
+```{r GLMM Multivariate Landscapes, eval=FALSE, include=FALSE}
 
@@
 
-```{r AIC Model Selection v0.1, eval=FALSE}
+```{r AIC Model Selection v0.1, eval=FALSE, include=FALSE}
 
@@
 In the complex food-web, there is only marginal evidence for non-linear selection acting on gall size, but there is evidence for correlational selection between gall size and the number of individuals per gall.
-```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE, eval=FALSE}
+```{r SELECTION GRADIENTS, echo=TRUE, warning=FALSE, eval=FALSE, include=FALSE}
 
@@
 
-```{r Selection Gradients - Bootstrapped Intervals, eval=FALSE}
+```{r Selection Gradients - Bootstrapped Intervals, eval=FALSE, include=FALSE}
 
@@
 Compare bootstrapped replicates across treatments, rather than comparing to zero.
-```{r Compare bootstrapped replicates across treatments, eval=FALSE}
+```{r Compare bootstrapped replicates across treatments, eval=FALSE, include=FALSE}
 bootstrap_df %>%
@@
 Therefore, this fitness landscape integrates information from the fitness function with information about distributions of phenotype, and has been suggested to be a more informative way to visualize the magnitude of natural selection.
-```{r Fitness Landscapes, eval=FALSE}
+```{r Fitness Landscapes, eval=FALSE, include=FALSE}
 

### 2018-06-21 elsevier_test/elsevier_test.Rmd
added GRC abstract to think about reframing the paper.
Former-commit-id: f447ab24724625427d952dae9067aee93b395039

@@
     address: Department, Street, City, State, Zip
-abstract: |
-  Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
+abstract: Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
 Given that the loss of biodiversity is simplifying the structure of ecological networks, there is a pressing need to answer the question: how does network complexity affect natural selection and the fitness landscape of associated species?
@@
 Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change.
+
+Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
+Similarly, fitness landscapes provide a mechanistic link between population and evolutionary ecology, as they describe the influence of natural selection on phenotypic variation.
+It remains unclear, however, how the network structure of species interactions shapes the fitness landscape.
+Understanding this relationship is likely key for developing a predictive ecology across scales of biological organization.
+To examine the relationship between network structure and the fitness landscape, we conducted a field experiment that manipulated the network of trophic interactions (simple vs.
+complex) influencing the fitness of an insect herbivore.
+We then quantified the fitness landscape of herbivores in each treatment by measuring herbivore survival as a function of multiple phenotypic traits.
+We found that more traits were under selection in the simple vs.
+complex trophic network.
+This occurred because different natural enemies impose different selection pressures on herbivore traits, thereby minimizing relative fitness differences among herbivore phenotypes in the complex network.
+Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change.
 

### 2018-06-21 supp_mat_complexity_selection.Rmd
removed fig files from code in order to get .rdb < 100 MB
Former-commit-id: 3f4044dab0ffc25f83fe0e7d6e03ce734c8d8778

@@
 RF_gradients
-save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
-save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
+#save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
+#save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
 
@@
 AF_gradients
-save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
-save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
+#save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
+#save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
 ```
@@
 RF_landscape_2d
-save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
-save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
 
@@
 AF_landscape_2d
-save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
 ```

### 2018-06-21 supp_mat_complexity_selection.Rmd
removed cached files to be able to push commit. I think I can avoid this if I simply split up the chunks into Relative and Absolute fitness.
Former-commit-id: 2d5ce108463a82db67374a2a6afd5d8431c597e2

@@
 RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
-RF_landscape_2d
+#RF_landscape_2d
 #save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
@@
 AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
+#AF_landscape_2d
 #save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)

### 2018-06-22 elsevier_test/elsevier_test.Rmd
added some text to intro, methods, and results.

@@
 
-We sought to bridge this gap through a field experiment that examines how food-web complexity alters the fitness landscape of species embedded within this food web.
+<!-- III. Generate expectations for how food-web complexity may alter selection gradients -->
+
+Food-web complexity may influence selection gradients in multiple ways.
+First, if more diverse predator communities are more efficient as suppressing prey densities (e.g.
+biodiversity-ecosystem fucntion; Ives 2005 Ecology Letters), then this will result in lower mean fitness.
+A reduction in mean fitness, all else equal, will intensify natural selection and thus could increase the rate of evolutionary change.
+Alternatively, if predators are functionally distinct, more diverse communities can reduce the strength of selection.
+This is because each predator has a different functional relationship between prey phenotype and the probability of an interaction.
+
+<!-- IV. Introduce study system -->
+
+Here, we conducted a field experiment to test the effect of food-web complexity on the fitness landscape of a species embedded within this food web.
+To do this, we used a common garden experiment with a host plant (*Salix hooeriana*), an abundant herbivore (*Iteomyia salicisverruca*), and the diverse community of insect parasitoids that attack it.
+Prior work in this system has shown that there is directional selection for larger galls, likely because larger galls provide more of a refuge from parasitoid attack.
+However, there is also evidence that different parasitoid species impose differential selection on gall phenotypes.
+
+<!-- IV. Relationship between entropy and fitness landscape 
+In more complex communities, there is greater uncertainty for an individual prey in which predator species will be imposing the trophic interaction. This also means the -->
 
@@
 
-We collected data on three different phenotypes for each larva that have been shown to be important in our work (cite Barbour et al.
-2016) and in other work with Cecidomyiid midges (CITE).
+We collected data on three different phenotypes for each larva that have been shown to be important in our work (@Barbour2016) and in other work with Cecidomyiid midges (@Weis1983, @Heath2018).
 First, we measured the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
-Second, we counted the number of chambers in each gall, which is indicative of the number of larva per gall.
-All larva collected from the same gall were scored with the same 'number of larva per gall' phenotype.
-This trait is indicative of the clutch size of adult females.
-%This trait likely reflects a combination of both larva feeding behavior as well as adult female preferences and clutch size (CITE Art Weis' work).
+Our previous work has shown that larger galls provide a refuge for larva from parasitoid attack (@Barbour2016).
+Second, we counted the number of chambers in each gall, which is indicative of the clutch size of adult female midges (@Weis1983).
+All larva collected from the same multi-chambered gall were scored with the same clutch size.
 Third, we estimated gall density as the number of larva per 100 shoots.
-We did this by counting the number of gall chambers on five randomly sampled branches per tree.
+We did this by summing the number of gall chambers for galls on five randomly sampled branches per tree.
 To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant.
@@
 This phenotype is indicative of the preference of female midges for particular plant traits (hereafter 'female preference').
+
+The measurement of insect densities on a plant is a commonly used index for measuring oviposition preference (@Gripenberg2010), although it is controversal (@Singer1986)
 
@@
 
+We used Aikaike Information Criteria to compare models that varied in complexity.
+This analysis enabled us to explore the appropriate complexity of the model to include for our analyses (i.e.
+include non-linear and correlational selection gradients and whether they varied with food-web treatment).
+
 Results
 =======
+
+We found that more phenotypic traits were under selection in the simple vs.
+complex food web.
+In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex Beta = ; simple Beta = )(Fig.
+2A).
+In complex food webs, there was no evidence of selection on clutch size ($\beta_{clutch}=$) or female preference ($\beta_{preference}=$)(orange lines in Fig.
+2B,C).
+In simple food webs, however, clutch size and female preference were under strong directional selection, with smaller clutch sizes and weaker preferences resulting in higher larval survival (blue lines in Fig.
+2B,C).
+These different selection pressures resulted in different adaptive landscapes in complex vs.
+simple food webs, with evidence for more rugged landscapes in the simple rather than the complex food web (Fig.
+3).
+Depending on the trait combinations used to create the landscape, we found that the ruggedness of the adaptive landscape ranged from 10\% higher (Fig.
+3A) to 274\% higher (Fig.
+3C) in the simple vs.
+complex food web.
+Our model comparison suggested that it was unnecessary to test for the effects of non-linear or correlational selection gradients (ref.
+supp.
+mat.).
 

### 2018-06-22 elsevier_test/elsevier_test.Rmd
tiny edit
updating methods section

@@
     address: Department, Street, City, State, Zip
-abstract: Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
+abstract: 
+  Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
 Given that the loss of biodiversity is simplifying the structure of ecological networks, there is a pressing need to answer the question: how does network complexity affect natural selection and the fitness landscape of associated species?
@@
 Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change.
-
 Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
@@
 
-Food-web complexity may influence selection gradients in multiple ways.
+Food-web complexity may influence selection gradients in at least two ways.
 First, if more diverse predator communities are more efficient as suppressing prey densities (e.g.
@@
 
-To isolate the effects of coastal willow (\textit{S.
+<!-- To isolate the effects of coastal willow (\textit{S.
 hookeriana} Barratt ex Hooker) genetic variation on the plant-insect food web, we used a common garden experiment consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;'53"N, 124&deg;12'4"W) near Loleta, California, USA.
@@
 During this study, willows had reached 2 - 4 m in height.
-Further details on the genotyping and planting of the common garden are available in (@Barbour2015-tp).
+Further details on the genotyping and planting of the common garden are available in (@Barbour2015).
+-->
 
-We conducted our study within a common garden consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
-Willow genotypes were collected from a single population of willows growing around Humboldt Bay.
-While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (Barbour et al.
-2016), suggesting that we can treat them as independent from one another.
-This common garden was planted in February 2009 with 25 clonal replicates (i.e.
-stem cuttings) of each willow genotype in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
+We conducted our study within a four-year old common garden of *Salix hookeriana* located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
+This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
+<!--While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (@Barbour2016), suggesting that we can treat them as independent from one another.--> Clonal replicates (stem cuttings) of each genotype were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
 Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 2 - 4 m in height.
-Further details on the genotyping and planting of the common garden are available in (Barbour et al.
-2015).
-We conducted this experiment across 8 different plant genotypes that span the range of trait variation (Barbour et al.
-2015).
+During this study, willows had reached 5 - 9m in height.
+Further details on the genotyping and planting of the common garden are available in (@Barbour2015).
 
@@
 
-We setup our food-web manipulation soon after galls began developing on \textit{S.
-hookeriana} in early June of 2013.
-On treatment plants, we enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
-This treatment did not exclude the egg parasitoid \textit{Platygaster} sp.
+We setup our food-web manipulation soon after galls began developing on *S.
+hookeriana* in early June of 2013.
+We manipulated gall exposure to parasitoids across 128 plants from 8 different plant genotypes that span the range of trait variation observed in this willow population (@Barbour2015).
+On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
+This treatment did not exclude the egg parasitoid *Platygaster* sp.
 which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE).
-On control plants, we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack \textit{Iteomyia}.
+On control plants, we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack *Iteomyia*.
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
-In late August 2013, we collected marked and bagged galls from each plant.
-We placed galls in 30 mL transport vials and allowed them to complete development for 4 months at room temperature in the lab.
-We opened galls under a dissecting scope and determined whether larva survived to pupation, our measure of fitness, or were parasitized.
+In late August, we collected marked and bagged galls from each plant.
+We placed galls into 30 mL vials and <!-- allowed them to complete development-->kept them in the lab for 4 months at room temperature.
+We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
 
@@
 First, we measured the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
-Our previous work has shown that larger galls provide a refuge for larva from parasitoid attack (@Barbour2016).
+Our previous work has shown that a larger gall diameter provides a refuge for larva from parasitoid attack (@Barbour2016).
 Second, we counted the number of chambers in each gall, which is indicative of the clutch size of adult female midges (@Weis1983).
 All larva collected from the same multi-chambered gall were scored with the same clutch size.
-Third, we estimated gall density as the number of larva per 100 shoots.
-We did this by summing the number of gall chambers for galls on five randomly sampled branches per tree.
+Third, we estimated gall density as the number of chambers per 100 shoots per plant.
+We did this by summing the number of chambers across all galls found on five randomly sampled branches per tree.
 To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant.
@@
 This phenotype is indicative of the preference of female midges for particular plant traits (hereafter 'female preference').
-
-The measurement of insect densities on a plant is a commonly used index for measuring oviposition preference (@Gripenberg2010), although it is controversal (@Singer1986)
+The measurement of insect densities on a plant is a commonly used index for measuring oviposition preference (@Gripenberg2010), although caution must be taken in inferring 'preference' (@Singer1986).
+This is because oviposition is a complex process and the number of individuals observed on plants in the field can be influenced by processes other than preference.
+While we recognize this, since our data comes from a randomized placement of genotypes and that we can still detect the presence of an individual even if it dies before development (empty chamber lacking an exit hole and without any evidence of larva or parasitoid).
+We cannot control for egg predation, although this likely plays a comparatively minor role in determining gall survival (@Hawkins1997).
 
 <!-- % IV. Describe statistical analysis to test the effects of food-web complexity -->
+
+To identify the appropriate level of model complexity for testing the effects of food-web complexity on the fitness landscapes, we compared models using Aikaike Information Criteria.
+The maximal complexity we explored was a generalized additive mixed model that fit cubic splines to each trait as well as linear interactions between a maximum of two traits as well as an interaction with food-web treatment.
+We then examined simpler models where
+
+<!--$$logit(E(W))=\mu+\beta_{diameter}+\beta_{clutch}+\beta_{preference}+$$
+$$logit(E(W))=\mu+treatment+s(diam):treat+s(clutch)+s(pref)+diam:cluch+diam:pref+clutch:pref+(1|Genotype/Plant/Gall)$$-->
+
+This analysis enabled us to explore the appropriate complexity of the model to include for our analyses (i.e.
+include non-linear and correlational selection gradients and whether they varied with food-web treatment).
 
@@
 
-To account for the correlated structure of our gall phenotypes (female preference at plant-level; clutch size at gall-level; chamber size at chamber-level), we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
+To quantify selection gradients, we fit separate statistical models to data from each food-web treatment.
+We used the method of @Janzen1998 to calculate selection gradients and used parametric bootstrapping to calculate their 95% confidence intervals (@Bolker2009).
+
+To account for the correlated structure of our gall phenotypes (oviposition preference at plant-level; clutch size at gall-level; gall diameter at chamber-level), we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
 
@@
 
-We used a spline-based semiparametric regression (Schluter 1988, Morrissey and Sakedra 2014).
+<!-- We used a spline-based semiparametric regression (Schluter 1988, Morrissey and Sakedra 2014).
 These analyses are desirable because they lead to inferences of the form of selection that make few \textit{a priori} assumptions (Schluter 1988), and can now be used to quantify standardized selection gradients (Morrissey and Sakrera 2014).
@@
 We standardized phenotypes (mean=0, SD=1), so that first-order derivatives correspond to the intensity of directional selection ($\beta$\textsubscript{trait}), while second-order derivatives correspond to intensity of nonlinear ($\gamma$\textsubscript{trait}) and correlational selection ($\gamma$\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are thus comparable within this study as well as to others.
+-->
 
-Our GLMMs are useful for testing the effects of food-web complexity on the fitness landscape within the context of our experimental design; however, coefficients from GLMMs cannot be easily converted into quantitative estimates of selection gradients (cite Morrissey's work).
+<!-- Our GLMMs are useful for testing the effects of food-web complexity on the fitness landscape within the context of our experimental design; however, coefficients from GLMMs cannot be easily converted into quantitative estimates of selection gradients (cite Morrissey's work).
 Therefore, for each treatment, we fit separate generalized additive models (GAMs) for gall traits that we identified as being under selection from our GLMMs.
@@
 For the number of larva per gall and gall density, we aggregated larva survival at the gall or plant level, respectively, to avoid pseudoreplication in our GAMs.
-
-We used Aikaike Information Criteria to compare models that varied in complexity.
-This analysis enabled us to explore the appropriate complexity of the model to include for our analyses (i.e.
-include non-linear and correlational selection gradients and whether they varied with food-web treatment).
+-->
 

### 2018-06-22 elsevier_test/elsevier_test.tex
updating methods section

@@
             pdfauthor={},
-            pdftitle={Short Paper},
+            pdftitle={Food-web complexity flattens the fitness landscape of an insect herbivore},
             colorlinks=true,
@@
 
-  \title{Short Paper}
-    \author[Some Institute of Technology]{Alice Anonymous\corref{c1}}
-   \ead{alice@example.com} 
+  \title{Food-web complexity flattens the fitness landscape of an insect
+herbivore}
+    \author[Department of Evolutionary Biology and Environmental Studies, University
+of Zurich, Zurich, Switzerland]{Matthew A. Barbour\corref{c1}}
+   \ead{matthew.barbour@ieu.uzh.ch} 
    \cortext[c1]{Corresponding Author}
-    \author[Another University]{Bob Security}
-   \ead{bob@example.com}
+    \author[Another University]{Jordi Bascompte}
+   \ead{jordi.bascompte@ieu.uzh.ch}
 
@@
   \begin{abstract}
-  Studies of natural selection and fitness landscapes usually treat the
-  network of interacting species as a ``black box''. Given that the loss
-  of biodiversity is simplifying the structure of ecological networks,
-  there is a pressing need to answer the question: how does network
-  complexity affect natural selection and the fitness landscape of
-  associated species? To answer this question, we conducted a field
-  experiment that manipulated the complexity of a food web associated with
-  a galling insect herbivore. To maintain complex food webs, we allowed
-  the entire community of natural enemies to attack insect galls on 64
-  plants in a common garden setting. To create simple food webs, we
-  excluded a guild of three larval parasitoids by bagging galls on 64
-  different plants; therefore, mortality in this treatment was primarily
-  due to a single egg parasitoid that attacks prior to gall formation. We
-  then measured herbivore survival as a function of three key gall traits
-  in each treatment. We found that more traits were under selection in the
-  simple vs.~complex food web. This occurred because different parasitoid
-  species impose different selection pressures on gall traits, thereby
-  minimizing relative fitness differences among insect galls with
-  different phenotypes. Our work suggests that more complex food webs
-  allow phenotypic variation to persist, which could facilitate subsequent
-  adaptive evolution to environmental change.
+  true
   \end{abstract}
@@
 Biological diversity -- from genes, to phenotypes, to species -- has
-fascinated evolutionary biologists for decades. However, the explicit
-context (i.e.~ecological environment) is often abstracted and not
-examined in detail in studies of natural selection. Thus, we have a poor
-understanding of how biological diversity itself, imposes natural
-selection, and the potential feedbacks that may emerge.
+fascinated evolutionary biologists for decades.
+
+Much of this biological diversity has been shaped by natural selection
+via trophic interactions, such as resource competition (cite charater
+displacement), mutualistic exchanges of resource (cite? ), and predation
+(cite recent Heath and Stireman paper).
+
+NEED to recognize that evolutionary biologists have begun to explore how
+community context affects evolutionary change (work by Sharon Strauss,
+Casey terHorst, Lutz Becks, etc.). These results have begun to show
+interesting patterns whereby the composition of species in a community
+can alter the direction and strength of natural selection imposed on
+species embedded within these communities (cite).
+
+Put another way, these results have begun to show biological diversity,
+in terms of differences between species, can drive evolutionary change.
+
+While there is clear evidence for pairwise trophic interactions to drive
+evolution by natural selection, its unclear how biological diversity
+itself imposes natural selection and drives evolutionary change.
+
+Exploring the effects of biological diversity requires an explicit
+examination of the network structure of trophic interactions between
+species in a community. Theoretical models have begun to examine how the
+network structure of species interactions drives evolutionary change
+(Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish
+guy\ldots{}); however, we are currently lacking experimental tests.
 
@@
 
-We sought to bridge this gap through a field experiment that examines
-how food-web complexity alters the fitness landscape of species embedded
-within this food web.
+Food-web complexity may influence selection gradients in at least two
+ways. First, if more diverse predator communities are more efficient as
+suppressing prey densities (e.g.~biodiversity-ecosystem fucntion; Ives
+2005 Ecology Letters), then this will result in lower mean fitness. A
+reduction in mean fitness, all else equal, will intensify natural
+selection and thus could increase the rate of evolutionary change.
+Alternatively, if predators are functionally distinct, more diverse
+communities can reduce the strength of selection. This is because each
+predator has a different functional relationship between prey phenotype
+and the probability of an interaction.
+
+Here, we conducted a field experiment to test the effect of food-web
+complexity on the fitness landscape of a species embedded within this
+food web. To do this, we used a common garden experiment with a host
+plant (\emph{Salix hooeriana}), an abundant herbivore (\emph{Iteomyia
+salicisverruca}), and the diverse community of insect parasitoids that
+attack it. Prior work in this system has shown that there is directional
+selection for larger galls, likely because larger galls provide more of
+a refuge from parasitoid attack. However, there is also evidence that
+different parasitoid species impose differential selection on gall
+phenotypes.
 
@@
 
-To isolate the effects of coastal willow (\textit{S. hookeriana} Barratt
-ex Hooker) genetic variation on the plant-insect food web, we used a
-common garden experiment consisting of 26 different willow genotypes (13
-males; 13 females), located at Humboldt Bay National Wildlife Refuge
-(HBNWR) (40°'53``N, 124°12'4''W) near Loleta, California, USA. Willow
-genotypes were collected from a single population of willows growing
-around Humboldt Bay. While relatedness among these genotypes is unknown,
-their phenotypes in multivariate trait space are quite distinct from
-each other ({\textbf{???}}), suggesting that we can treat them as
-independent from one another. This common garden was planted in February
-2009 with 25 clonal replicates (i.e.~stem cuttings) of each willow
-genotype in a completely randomized design in two hectares of a former
-cattle pasture at HBNWR. Willows in our garden begin flowering in
-February and reach their peak growth in early August. During this study,
-willows had reached 2 - 4 m in height. Further details on the genotyping
-and planting of the common garden are available in (Barbour et al.
-2015).
-
-We conducted our study within a common garden consisting of 26 different
-willow genotypes (13 males; 13 females), located at Humboldt Bay
-National Wildlife Refuge (HBNWR) (40°40'53``N, 124°12'4''W) near Loleta,
-California, USA. Willow genotypes were collected from a single
-population of willows growing around Humboldt Bay. While relatedness
-among these genotypes is unknown, their phenotypes in multivariate trait
-space are quite distinct from each other (Barbour et al. 2016),
-suggesting that we can treat them as independent from one another. This
-common garden was planted in February 2009 with 25 clonal replicates
-(i.e.~stem cuttings) of each willow genotype in a completely randomized
-design in two hectares of a former cattle pasture at HBNWR. Willows in
-our garden begin flowering in February and reach their peak growth in
-early August. During this study, willows had reached 2 - 4 m in height.
-Further details on the genotyping and planting of the common garden are
-available in (Barbour et al. 2015). We conducted this experiment across
-8 different plant genotypes that span the range of trait variation
-(Barbour et al. 2015).
+We conducted our study within a four-year old common garden of
+\emph{Salix hookeriana} located at Humboldt Bay National Wildlife Refuge
+(HBNWR) (40°40'53``N, 124°12'4''W) near Loleta, California, USA. This
+common garden consists of 26 different willow genotypes that were
+collected from a single population of willows growing around Humboldt
+Bay. Clonal replicates (stem cuttings) of each genotype were planted in
+a completely randomized design in two hectares of a former cattle
+pasture at HBNWR. Willows in our garden begin flowering in February and
+reach their peak growth in early August. During this study, willows had
+reached 5 - 9m in height. Further details on the genotyping and planting
+of the common garden are available in (Barbour et al. (2015)).
 
 We setup our food-web manipulation soon after galls began developing on
-\textit{S. hookeriana} in early June of 2013. On treatment plants, we
-enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to
-exclude three parasitoid species that attack during larva development
-(hereafter larval parasitoids). This treatment did not exclude the egg
-parasitoid \textit{Platygaster} sp. which attacks prior to gall
-initiation (note that in Cecidomyiid midges, larva initiate gall
+\emph{S. hookeriana} in early June of 2013. We manipulated gall exposure
+to parasitoids across 128 plants from 8 different plant genotypes that
+span the range of trait variation observed in this willow population
+(Barbour et al. (2015)). On treatment plants (8 replicates per
+genotype), we enclosed 14 galled leaves with organza bags (MANUFACTORER
+DETAILS) to exclude three parasitoid species that attack during larva
+development (hereafter larval parasitoids). This treatment did not
+exclude the egg parasitoid \emph{Platygaster} sp. which attacks prior to
+gall initiation (note that in Cecidomyiid midges, larva initiate gall
 development CITE). On control plants, we used flagging tape to mark 14
 galled leaves per plant, allowing the full suite of parasitoids to
-attack \textit{Iteomyia}. Marking galls with flagging tape ensured that
-we compared control and treatment galls with similar phenology when we
-collected galls later in the season. In late August 2013, we collected
-marked and bagged galls from each plant. We placed galls in 30 mL
-transport vials and allowed them to complete development for 4 months at
-room temperature in the lab. We opened galls under a dissecting scope
-and determined whether larva survived to pupation, our measure of
-fitness, or were parasitized.
+attack \emph{Iteomyia}. Marking galls with flagging tape ensured that we
+compared control and treatment galls with similar phenology when we
+collected galls later in the season. In late August, we collected marked
+and bagged galls from each plant. We placed galls into 30 mL vials and
+kept them in the lab for 4 months at room temperature. We then opened
+galls under a dissecting scope and determined whether larva survived to
+pupation (our measure of fitness) or were parasitized.
 
 We collected data on three different phenotypes for each larva that have
-been shown to be important in our work (cite Barbour et al. 2016) and in
-other work with Cecidomyiid midges (CITE). First, we measured the size
-of each gall chamber to the nearest 0.01 mm at its maximum diameter
-(perpendicular to the direction of plant tissue growth). Second, we
-counted the number of chambers in each gall, which is indicative of the
-number of larva per gall. All larva collected from the same gall were
-scored with the same `number of larva per gall' phenotype. This trait is
-indicative of the clutch size of adult females. \%This trait likely
-reflects a combination of both larva feeding behavior as well as adult
-female preferences and clutch size (CITE Art Weis' work). Third, we
-estimated gall density as the number of larva per 100 shoots. We did
-this by counting the number of gall chambers on five randomly sampled
-branches per tree. To account for potential differences in the number of
-shoots per branch for each plant genotype (CITE other willow work), we
-then counted the number of shoots on the fifth branch to estimate the
-number of larva per 100 shoots for each plant. All larva collected from
-the same plant were scored with the same gall density phenotype. This
-phenotype is indicative of the preference of female midges for
-particular plant traits (hereafter `female preference').
+been shown to be important in our work (Barbour et al. (2016)) and in
+other work with Cecidomyiid midges (Weis, Price, and Lynch (1983),
+Heath, Abbot, and Stireman (2018)). First, we measured the size of each
+gall chamber to the nearest 0.01 mm at its maximum diameter
+(perpendicular to the direction of plant tissue growth). Our previous
+work has shown that a larger gall diameter provides a refuge for larva
+from parasitoid attack (Barbour et al. (2016)). Second, we counted the
+number of chambers in each gall, which is indicative of the clutch size
+of adult female midges (Weis, Price, and Lynch (1983)). All larva
+collected from the same multi-chambered gall were scored with the same
+clutch size. Third, we estimated gall density as the number of chambers
+per 100 shoots per plant. We did this by summing the number of chambers
+across all galls found on five randomly sampled branches per tree. To
+account for potential differences in the number of shoots per branch for
+each plant genotype (CITE other willow work), we then counted the number
+of shoots on the fifth branch to estimate the number of larva per 100
+shoots for each plant. All larva collected from the same plant were
+scored with the same gall density phenotype. This phenotype is
+indicative of the preference of female midges for particular plant
+traits (hereafter `female preference'). The measurement of insect
+densities on a plant is a commonly used index for measuring oviposition
+preference (Gripenberg et al. (2010)), although caution must be taken in
+inferring `preference' (Singer (1986)). This is because oviposition is a
+complex process and the number of individuals observed on plants in the
+field can be influenced by processes other than preference. While we
+recognize this, since our data comes from a randomized placement of
+genotypes and that we can still detect the presence of an individual
+even if it dies before development (empty chamber lacking an exit hole
+and without any evidence of larva or parasitoid). We cannot control for
+egg predation, although this likely plays a comparatively minor role in
+determining gall survival (Hawkins, Cornell, and Hochberg (1997)).
+
+To identify the appropriate level of model complexity for testing the
+effects of food-web complexity on the fitness landscapes, we compared
+models using Aikaike Information Criteria. The maximal complexity we
+explored was a generalized additive mixed model that fit cubic splines
+to each trait as well as linear interactions between a maximum of two
+traits as well as an interaction with food-web treatment. We then
+examined simpler models where
+
+This analysis enabled us to explore the appropriate complexity of the
+model to include for our analyses (i.e.~include non-linear and
+correlational selection gradients and whether they varied with food-web
+treatment).
 
@@
 
-To account for the correlated structure of our gall phenotypes (female
-preference at plant-level; clutch size at gall-level; chamber size at
-chamber-level), we specified gall ID nested within plant ID nested
-within plant genotype as random intercepts in our statistical models.
+To quantify selection gradients, we fit separate statistical models to
+data from each food-web treatment. We used the method of Frederic J
+Janzen and Hal S Stearn (1998) to calculate selection gradients and used
+parametric bootstrapping to calculate their 95\% confidence intervals
+(Bolker et al. (2009)).
+
+To account for the correlated structure of our gall phenotypes
+(oviposition preference at plant-level; clutch size at gall-level; gall
+diameter at chamber-level), we specified gall ID nested within plant ID
+nested within plant genotype as random intercepts in our statistical
+models.
 
@@
 
-We used a spline-based semiparametric regression (Schluter 1988,
-Morrissey and Sakedra 2014). These analyses are desirable because they
-lead to inferences of the form of selection that make few
-\textit{a priori} assumptions (Schluter 1988), and can now be used to
-quantify standardized selection gradients (Morrissey and Sakrera 2014).
+\section{Results}\label{results}
 
-We then calculated selection gradients as the partial derivatives in
-absolute fitness (larva survival) with response to multivariate
-phenotype using the \textit{gsg} package in R (cite Morrissey and R
-project). We standardized phenotypes (mean=0, SD=1), so that first-order
-derivatives correspond to the intensity of directional selection
-(\(\beta\)\textsubscript{trait}), while second-order derivatives
-correspond to intensity of nonlinear (\(\gamma\)\textsubscript{trait})
-and correlational selection
-(\(\gamma\)\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are
-thus comparable within this study as well as to others.
+We found that more phenotypic traits were under selection in the simple
+vs.~complex food web. In both complex and simple food webs, gall
+diameter was under strong directional selection, with larger galls
+resulting in higher larval survival (complex Beta = ; simple Beta =
+)(Fig. 2A). In complex food webs, there was no evidence of selection on
+clutch size (\(\beta_{clutch}=\)) or female preference
+(\(\beta_{preference}=\))(orange lines in Fig. 2B,C). In simple food
+webs, however, clutch size and female preference were under strong
+directional selection, with smaller clutch sizes and weaker preferences
+resulting in higher larval survival (blue lines in Fig. 2B,C). These
+different selection pressures resulted in different adaptive landscapes
+in complex vs.~simple food webs, with evidence for more rugged
+landscapes in the simple rather than the complex food web (Fig. 3).
+Depending on the trait combinations used to create the landscape, we
+found that the ruggedness of the adaptive landscape ranged from 10\%
+higher (Fig. 3A) to 274\% higher (Fig. 3C) in the simple vs.~complex
+food web. Our model comparison suggested that it was unnecessary to test
+for the effects of non-linear or correlational selection gradients (ref.
+supp. mat.).
 
-Our GLMMs are useful for testing the effects of food-web complexity on
-the fitness landscape within the context of our experimental design;
-however, coefficients from GLMMs cannot be easily converted into
-quantitative estimates of selection gradients (cite Morrissey's work).
-Therefore, for each treatment, we fit separate generalized additive
-models (GAMs) for gall traits that we identified as being under
-selection from our GLMMs. Estimating selection gradients from GAMs can
-give insight to both linear and non-linear selection gradients, which we
-assumed were all linear for our GLMMs, given the complexity of already
-fitting up to 4-way interactions in these models. For the number of
-larva per gall and gall density, we aggregated larva survival at the
-gall or plant level, respectively, to avoid pseudoreplication in our
-GAMs.
+\section{Discussion}\label{discussion}
 
@@
 
+\hypertarget{refs}{}
+\hypertarget{ref-Barbour2016}{}
+Barbour, Matthew A, Miguel A Fortuna, Jordi Bascompte, Joshua R
+Nicholson, Riitta Julkunen-Tiitto, Erik S Jules, and Gregory M
+Crutsinger. 2016. ``Genetic Specificity of a Plant--insect Food Web:
+Implications for Linking Genetic Variation to Network Complexity.''
+\emph{Proceedings of the National Academy of Sciences} 113 (8). National
+Acad Sciences: 2128--33.
+
+\hypertarget{ref-Barbour2015}{}
+Barbour, Matthew A, Mariano A Rodriguez-Cabal, Elizabeth T Wu, Riitta
+Julkunen-Tiitto, Carol E Ritland, Allyson E Miscampbell, Erik S Jules,
+and Gregory M Crutsinger. 2015. ``Multiple Plant Traits Shape the
+Genetic Basis of Herbivore Community Assembly.'' \emph{Funct. Ecol.} 29
+(8): 995--1006.
+
+\hypertarget{ref-Bolker2009}{}
+Bolker, Benjamin M, Mollie E Brooks, Connie J Clark, Shane W Geange,
+John R Poulsen, M Henry H Stevens, and Jada-Simone S White. 2009.
+``Generalized Linear Mixed Models: A Practical Guide for Ecology and
+Evolution.'' \emph{Trends Ecol. Evol.} 24 (3): 127--35.
+
+\hypertarget{ref-Janzen1998}{}
+Frederic J Janzen and Hal S Stearn. 1998. ``Logistic Regression for
+Empirical Studies of Multivariate Selection.'' \emph{Evolution} 52 (6):
+1564--71.
+
+\hypertarget{ref-Gripenberg2010}{}
+Gripenberg, Sofia, Peter J Mayhew, Mark Parnell, and Tomas Roslin. 2010.
+``A Meta-Analysis of Preference-Performance Relationships in
+Phytophagous Insects.'' \emph{Ecol. Lett.} 13 (3): 383--93.
+
+\hypertarget{ref-Hawkins1997}{}
+Hawkins, Bradford A, Howard V Cornell, and Michael E Hochberg. 1997.
+``Predators, Parasitoids, and Pathogens as Mortality Agents in
+Phytophagous Insect Populations.'' \emph{Ecology} 78 (7). Ecological
+Society of America: 2145--52.
+
+\hypertarget{ref-Heath2018}{}
+Heath, Jeremy J, Patrick Abbot, and John O Stireman 3rd. 2018.
+``Adaptive Divergence in a Defense Symbiosis Driven from the Top down.''
+\emph{Am. Nat.} 192 (1): E21--E36.
+
+\hypertarget{ref-Singer1986}{}
+Singer, Michael C. 1986. ``The Definition and Measurement of Oviposition
+Preference in Plant-Feeding Insects.'' In \emph{Insect-Plant
+Interactions}, edited by James R Miller and Thomas A Miller, 65--94. New
+York, NY: Springer New York.
+
+\hypertarget{ref-Weis1983}{}
+Weis, Arthur E, Peter W Price, and Michael Lynch. 1983. ``Selective
+Pressures on Clutch Size in the Gall Maker Asteromyia Carbonifera.''
+\emph{Ecology} 64 (4). Ecological Society of America: 688--95.
+
 \end{document}

### 2018-06-24 elsevier_test/elsevier_test.Rmd
more finalized version of study site, food-web manipulation, and measuring gall phenotypes sections of Methods.

@@
 
+## Study Site
+
 <!-- I. Give details about the study site, but not focusing on the genetic variation since this doesn't play much of a role in this manuscript. -->
 
-<!-- To isolate the effects of coastal willow (\textit{S.
-hookeriana} Barratt ex Hooker) genetic variation on the plant-insect food web, we used a common garden experiment consisting of 26 different willow genotypes (13 males; 13 females), located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;'53"N, 124&deg;12'4"W) near Loleta, California, USA.
-Willow genotypes were collected from a single population of willows growing around Humboldt Bay.
-While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other [@Barbour2016-hz], suggesting that we can treat them as independent from one another.
-This common garden was planted in February 2009 with 25 clonal replicates (i.e.
-stem cuttings) of each willow genotype in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 2 - 4 m in height.
-Further details on the genotyping and planting of the common garden are available in (@Barbour2015).
--->
-
-We conducted our study within a four-year old common garden of *Salix hookeriana* located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
+We conducted our study within a four-year old common garden of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
 This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-<!--While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (@Barbour2016), suggesting that we can treat them as independent from one another.--> Clonal replicates (stem cuttings) of each genotype were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
+<!--While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (@Barbour2016), suggesting that we can treat them as independent from one another.--> Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
 Willows in our garden begin flowering in February and reach their peak growth in early August.
 During this study, willows had reached 5 - 9m in height.
-Further details on the genotyping and planting of the common garden are available in (@Barbour2015).
+Further details on the genotyping and planting of the common garden are available in @Barbour2015.
+
+## Food-Web Manipulation
 
@@
 
-We setup our food-web manipulation soon after galls began developing on *S.
-hookeriana* in early June of 2013.
-We manipulated gall exposure to parasitoids across 128 plants from 8 different plant genotypes that span the range of trait variation observed in this willow population (@Barbour2015).
+We setup our food-web manipulation across 128 plants soon after galls began developing on *S. hookeriana* in early June of 2013. 
+These 128 plants came from eight different plant genotypes, spanning the range of trait variation observed in this willow population (@Barbour2015). 
 On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
-This treatment did not exclude the egg parasitoid *Platygaster* sp.
-which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE).
-On control plants, we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack *Iteomyia*.
+This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
+On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack *Iteomyia*. 
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
-In late August, we collected marked and bagged galls from each plant.
-We placed galls into 30 mL vials and <!-- allowed them to complete development-->kept them in the lab for 4 months at room temperature.
+Our food-web manipulation altered the average number of trophic interactions that *Iteomyia* was exposed to from BLANK on control plants to BLANK on treatment plants. 
+Thus, we refer to galls on control plants as being exposed to a 'complex' food web, whereas galls on treatment plants were exposed to a 'simple' food web.
+In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and <!-- allowed them to complete development--> kept them in the lab for 4 months at room temperature.
 We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
+
+## Measuring Gall Traits
 
@@
 
-We collected data on three different phenotypes for each larva that have been shown to be important in our work (@Barbour2016) and in other work with Cecidomyiid midges (@Weis1983, @Heath2018).
-First, we measured the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
+We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018). 
+First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). 
 Our previous work has shown that a larger gall diameter provides a refuge for larva from parasitoid attack (@Barbour2016).
-Second, we counted the number of chambers in each gall, which is indicative of the clutch size of adult female midges (@Weis1983).
+<!-- Consider whether it is important to make the distinction that diameter was measured at the multi-chambered gall level in previous work -->
+Second, we measured the clutch size of adult female midges by counting the number of chambers in each gall (@Weis1983). 
 All larva collected from the same multi-chambered gall were scored with the same clutch size. 
-Third, we estimated gall density as the number of chambers per 100 shoots per plant.
-We did this by summing the number of chambers across all galls found on five randomly sampled branches per tree.
-To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant.
-All larva collected from the same plant were scored with the same gall density phenotype.
-This phenotype is indicative of the preference of female midges for particular plant traits (hereafter 'female preference').
-The measurement of insect densities on a plant is a commonly used index for measuring oviposition preference (@Gripenberg2010), although caution must be taken in inferring 'preference' (@Singer1986).
-This is because oviposition is a complex process and the number of individuals observed on plants in the field can be influenced by processes other than preference.
-While we recognize this, since our data comes from a randomized placement of genotypes and that we can still detect the presence of an individual even if it dies before development (empty chamber lacking an exit hole and without any evidence of larva or parasitoid).
-We cannot control for egg predation, although this likely plays a comparatively minor role in determining gall survival (@Hawkins1997).
+Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant.
+The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010), although caution must be taken in inferring 'preference' (@Singer1986).
+This is because larval densities can be influenced by processes other than preference. 
+For example, if an ovipositing female is not exposed to the full spectrum of plant types (in this case genotypes), then it is difficult to infer whether patterns of larval densities are actually due to <!--dispersal limitation or-->preference.
+Also, observed larval densities could be influenced by egg predation.
+While we recognize these limitations, a couple of aspects of our study system likely alleviate these limitations. 
+For example, since our data comes from a randomized placement of willow genotypes in a common garden, there is no consistent bias in which willow genotypes that females are exposed to while searching for oviposition sites.
+Although we cannot control for egg predation, this source of mortality appears to play comparatively minor role in determining the mortality of galling insects (@Hawkins1997).
+<!-- and that we can still detect the presence of an individual even if it dies before development (empty chamber lacking an exit hole and without any evidence of larva or parasitoid).
+-->
+To quantify female preference (gall density), we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
+We converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
+<!-- To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant.-->
+All larva collected from the same plant were scored with the same female preference.
+
+## Statistical Analyses
 
@@
 
+<!-- Consider exploring whether there is a linear or non-linear relationship between food-web complexity and the strength of selection.
+I think I could do this simply by calculating the index of food-web complexity measured on each plant.
+Perhaps it would also be good to measure to calculate the selection gradient observed on each plant -->
+
 We found that more phenotypic traits were under selection in the simple vs.

### 2018-06-24 elsevier_test/elsevier_test.tex
more finalized version of study site, food-web manipulation, and measuring gall phenotypes sections of Methods.

@@
 
-We conducted our study within a four-year old common garden of
-\emph{Salix hookeriana} located at Humboldt Bay National Wildlife Refuge
-(HBNWR) (40°40'53``N, 124°12'4''W) near Loleta, California, USA. This
-common garden consists of 26 different willow genotypes that were
-collected from a single population of willows growing around Humboldt
-Bay. Clonal replicates (stem cuttings) of each genotype were planted in
-a completely randomized design in two hectares of a former cattle
-pasture at HBNWR. Willows in our garden begin flowering in February and
-reach their peak growth in early August. During this study, willows had
-reached 5 - 9m in height. Further details on the genotyping and planting
-of the common garden are available in (Barbour et al. (2015)).
+\subsection{Study Site}\label{study-site}
 
-We setup our food-web manipulation soon after galls began developing on
-\emph{S. hookeriana} in early June of 2013. We manipulated gall exposure
-to parasitoids across 128 plants from 8 different plant genotypes that
-span the range of trait variation observed in this willow population
-(Barbour et al. (2015)). On treatment plants (8 replicates per
-genotype), we enclosed 14 galled leaves with organza bags (MANUFACTORER
-DETAILS) to exclude three parasitoid species that attack during larva
-development (hereafter larval parasitoids). This treatment did not
-exclude the egg parasitoid \emph{Platygaster} sp. which attacks prior to
-gall initiation (note that in Cecidomyiid midges, larva initiate gall
-development CITE). On control plants, we used flagging tape to mark 14
+We conducted our study within a four-year old common garden of coastal
+willow (\emph{Salix hookeriana}) located at Humboldt Bay National
+Wildlife Refuge (HBNWR) (40°40'53``N, 124°12'4''W) near Loleta,
+California, USA. This common garden consists of 26 different willow
+genotypes that were collected from a single population of willows
+growing around Humboldt Bay. Stem cuttings of each genotype (25
+replicates per genotypes) were planted in a completely randomized design
+in two hectares of a former cattle pasture at HBNWR. Willows in our
+garden begin flowering in February and reach their peak growth in early
+August. During this study, willows had reached 5 - 9m in height. Further
+details on the genotyping and planting of the common garden are
+available in Barbour et al. (2015).
+
+\subsection{Food-Web Manipulation}\label{food-web-manipulation}
+
+We setup our food-web manipulation across 128 plants soon after galls
+began developing on \emph{S. hookeriana} in early June of 2013. These
+128 plants came from eight different plant genotypes, spanning the range
+of trait variation observed in this willow population (Barbour et al.
+(2015)). On treatment plants (8 replicates per genotype), we enclosed 14
+galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three
+parasitoid species that attack during larva development (hereafter
+larval parasitoids). This treatment did not exclude the egg parasitoid
+\emph{Platygaster} sp. which attacks prior to gall initiation (note that
+in Cecidomyiid midges, larva initiate gall development CITE). On control
+plants (8 replicates per genotype), we used flagging tape to mark 14
 galled leaves per plant, allowing the full suite of parasitoids to
@@
 compared control and treatment galls with similar phenology when we
-collected galls later in the season. In late August, we collected marked
-and bagged galls from each plant. We placed galls into 30 mL vials and
-kept them in the lab for 4 months at room temperature. We then opened
-galls under a dissecting scope and determined whether larva survived to
-pupation (our measure of fitness) or were parasitized.
+collected galls later in the season. Our food-web manipulation altered
+the average number of trophic interactions that \emph{Iteomyia} was
+exposed to from BLANK on control plants to BLANK on treatment plants.
+Thus, we refer to galls on control plants as being exposed to a
+`complex' food web, whereas galls on treatment plants were exposed to a
+`simple' food web. In late August, we collected marked and bagged galls
+from each plant, placed them into 30 mL vials and kept them in the lab
+for 4 months at room temperature. We then opened galls under a
+dissecting scope and determined whether larva survived to pupation (our
+measure of fitness) or were parasitized.
 
-We collected data on three different phenotypes for each larva that have
-been shown to be important in our work (Barbour et al. (2016)) and in
-other work with Cecidomyiid midges (Weis, Price, and Lynch (1983),
-Heath, Abbot, and Stireman (2018)). First, we measured the size of each
-gall chamber to the nearest 0.01 mm at its maximum diameter
-(perpendicular to the direction of plant tissue growth). Our previous
-work has shown that a larger gall diameter provides a refuge for larva
-from parasitoid attack (Barbour et al. (2016)). Second, we counted the
-number of chambers in each gall, which is indicative of the clutch size
-of adult female midges (Weis, Price, and Lynch (1983)). All larva
+\subsection{Measuring Gall Traits}\label{measuring-gall-traits}
+
+We collected data on three different traits that we anticipated would
+experience selection based on our previous work (Barbour et al. (2016))
+and others work with Cecidomyiid midges (Weis, Price, and Lynch (1983),
+Heath, Abbot, and Stireman (2018)). First, we measured gall diameter as
+the size of each gall chamber to the nearest 0.01 mm at its maximum
+diameter (perpendicular to the direction of plant tissue growth). Our
+previous work has shown that a larger gall diameter provides a refuge
+for larva from parasitoid attack (Barbour et al. (2016)). Second, we
+measured the clutch size of adult female midges by counting the number
+of chambers in each gall (Weis, Price, and Lynch (1983)). All larva
 collected from the same multi-chambered gall were scored with the same
-clutch size. Third, we estimated gall density as the number of chambers
-per 100 shoots per plant. We did this by summing the number of chambers
-across all galls found on five randomly sampled branches per tree. To
-account for potential differences in the number of shoots per branch for
-each plant genotype (CITE other willow work), we then counted the number
-of shoots on the fifth branch to estimate the number of larva per 100
-shoots for each plant. All larva collected from the same plant were
-scored with the same gall density phenotype. This phenotype is
-indicative of the preference of female midges for particular plant
-traits (hereafter `female preference'). The measurement of insect
-densities on a plant is a commonly used index for measuring oviposition
-preference (Gripenberg et al. (2010)), although caution must be taken in
-inferring `preference' (Singer (1986)). This is because oviposition is a
-complex process and the number of individuals observed on plants in the
-field can be influenced by processes other than preference. While we
-recognize this, since our data comes from a randomized placement of
-genotypes and that we can still detect the presence of an individual
-even if it dies before development (empty chamber lacking an exit hole
-and without any evidence of larva or parasitoid). We cannot control for
-egg predation, although this likely plays a comparatively minor role in
-determining gall survival (Hawkins, Cornell, and Hochberg (1997)).
+clutch size. Third, we measured female preference for oviposition
+(egg-laying) sites as the density of larva observed on a plant. The
+measurement of larval densities on plants in the field is a commonly
+used index for measuring oviposition preference (Gripenberg et al.
+(2010)), although caution must be taken in inferring `preference'
+(Singer (1986)). This is because larval densities can be influenced by
+processes other than preference. For example, if an ovipositing female
+is not exposed to the full spectrum of plant types (in this case
+genotypes), then it is difficult to infer whether patterns of larval
+densities are actually due to preference. Also, observed larval
+densities could be influenced by egg predation.\\
+While we recognize these limitations, a couple of aspects of our study
+system likely alleviate these limitations. For example, since our data
+comes from a randomized placement of willow genotypes in a common
+garden, there is no consistent bias in which willow genotypes that
+females are exposed to while searching for oviposition sites. Although
+we cannot control for egg predation, this source of mortality appears to
+play comparatively minor role in determining the mortality of galling
+insects (Hawkins, Cornell, and Hochberg (1997)). To quantify female
+preference (gall density), we randomly sampled five branches per tree
+and summed the number of individual gall chambers observed. We converted
+these counts to a measure of gall density per 100 shoots by counting the
+number of shoots on the last branch we sampled. All larva collected from
+the same plant were scored with the same female preference.
+
+\subsection{Statistical Analyses}\label{statistical-analyses}
 

### 2018-06-24 elsevier_test/elsevier_test.Rmd
fine tuning statistical methods section

@@
 
-To identify the appropriate level of model complexity for testing the effects of food-web complexity on the fitness landscapes, we compared models using Aikaike Information Criteria. 
-The maximal complexity we explored was a generalized additive mixed model that fit cubic splines to each trait as well as linear interactions between a maximum of two traits as well as an interaction with food-web treatment.
-We then examined simpler models where
+To characterize the shape of the fitness landscape, we quantified selection gradients acting on each trait in simple vs.
+complex food webs.
+We did this by fitting separate statistical models to data from each food-web treatment.
+We used generalized linear mixed models (GLMMs, @Bolker2009) with larval survival (0 or 1) as our response variable and measure of fitness.
+We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait, as fixed effects in the statistical models.
+To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
+Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
+setting them to zero) to estimate selection gradients.
+We then used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), nonlinear ($\gamma_{z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
+To test whether selection gradients differed between treatments, we used our bootstrapped estimates to calculate the probability that selection gradients in the simple food web were larger/smaller than in the complex food web (i.e.
+the p-value).
 
@@
 
-This analysis enabled us to explore the appropriate complexity of the model to include for our analyses (i.e.
-include non-linear and correlational selection gradients and whether they varied with food-web treatment).
-
-We used generalized additive mixed models (GAMMs, cite Bolker et al.
-2008) to test the effects of food-web complexity on the shape of fitness landscape.
+<!-- We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
 Larva survival (0 or 1) was our response variable and measure of fitness. 
-We specified our food-web treatment, each gall trait, and all possible statistical interactions, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
+<!-- Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients. -->
+<!-- We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
 This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. 
-We specified plant genotype, plant individual nested within genotype, and multi-chambered gall nested within plant individual, as random effects.
-
-To quantify selection gradients, we fit separate statistical models to data from each food-web treatment.
-We used the method of @Janzen1998 to calculate selection gradients and used parametric bootstrapping to calculate their 95% confidence intervals (@Bolker2009).
-
-To account for the correlated structure of our gall phenotypes (oviposition preference at plant-level; clutch size at gall-level; gall diameter at chamber-level), we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
-
-From these GAMMs, we estimate selection gradients by assuming the mean value of our random effects (i.e.
-setting them to zero).
-This was appropriate for our analysis, since we were interested in estimating the fitness landscape, which is function of population mean fitness and mean trait values.
+To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
+<!-- To identify the appropriate level of model complexity for testing the effects of food-web complexity on the fitness landscapes, we compared models using Aikaike Information Criteria. 
+The maximal complexity we explored was a generalized additive mixed model that fit cubic splines to each trait as well as linear interactions between a maximum of two traits as well as an interaction with food-web treatment.
+-->
 

### 2018-06-24 elsevier_test/elsevier_test.tex
fine tuning statistical methods section

@@
 
-To identify the appropriate level of model complexity for testing the
-effects of food-web complexity on the fitness landscapes, we compared
-models using Aikaike Information Criteria. The maximal complexity we
-explored was a generalized additive mixed model that fit cubic splines
-to each trait as well as linear interactions between a maximum of two
-traits as well as an interaction with food-web treatment. We then
-examined simpler models where
-
-This analysis enabled us to explore the appropriate complexity of the
-model to include for our analyses (i.e.~include non-linear and
-correlational selection gradients and whether they varied with food-web
-treatment).
-
-We used generalized additive mixed models (GAMMs, cite Bolker et al.
-2008) to test the effects of food-web complexity on the shape of fitness
-landscape. Larva survival (0 or 1) was our response variable and measure
-of fitness. We specified our food-web treatment, each gall trait, and
-all possible statistical interactions, as fixed effects to fully explore
-the effects of food-web complexity on the fitness landscape. This
-analysis implicitly assumes that selection is linear, which we felt was
-a necessary trade-off for exploring the shape of the fitness landscape.
-We specified plant genotype, plant individual nested within genotype,
-and multi-chambered gall nested within plant individual, as random
-effects.
-
-To quantify selection gradients, we fit separate statistical models to
-data from each food-web treatment. We used the method of Frederic J
-Janzen and Hal S Stearn (1998) to calculate selection gradients and used
-parametric bootstrapping to calculate their 95\% confidence intervals
-(Bolker et al. (2009)).
-
-To account for the correlated structure of our gall phenotypes
-(oviposition preference at plant-level; clutch size at gall-level; gall
-diameter at chamber-level), we specified gall ID nested within plant ID
-nested within plant genotype as random intercepts in our statistical
-models.
-
-From these GAMMs, we estimate selection gradients by assuming the mean
-value of our random effects (i.e.~setting them to zero). This was
-appropriate for our analysis, since we were interested in estimating the
-fitness landscape, which is function of population mean fitness and mean
-trait values.
+To characterize the shape of the fitness landscape, we quantified
+selection gradients acting on each trait in simple vs.~complex food
+webs. We did this by fitting separate statistical models to data from
+each food-web treatment. We used generalized linear mixed models (GLMMs,
+Bolker et al. (2009)) with larval survival (0 or 1) as our response
+variable and measure of fitness. We specified linear and quadratic terms
+for each gall trait as well as linear interaction terms between each
+gall trait, as fixed effects in the statistical models. To account for
+the correlated structure of clutch size (gall level) and female
+preference (plant level) as well as any other independent effects of
+willow genotype on larval survival, we specified gall ID nested within
+plant ID nested within plant genotype as random intercepts in our
+statistical models. Since we were interested in characterizing the
+fitness landscape -- the relationship between mean trait values and
+population mean fitness -- we assumed the mean value of our random
+effects (i.e.~setting them to zero) to estimate selection gradients. We
+then used the method of Frederic J Janzen and Hal S Stearn (1998) to
+calculate directional (\(\beta_{z_i}\)), nonlinear (\(\gamma_{z_i}\)),
+and correlational (\(\gamma_{z_i,z_j}\)) selection gradients and used
+parametric bootstrapping (1000 replicates) to calculate their 95\%
+confidence intervals (Bolker et al. (2009)). To test whether selection
+gradients differed between treatments, we used our bootstrapped
+estimates to calculate the probability that selection gradients in the
+simple food web were larger/smaller than in the complex food web
+(i.e.~the p-value).
 

### 2018-06-29 elsevier_test/elsevier_test.Rmd
adding code directly to file.

@@
 _Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_
+
+```{r setup, include=FALSE}
+
+## Load required libraries ----
+library(tidyverse)
+library(cowplot) # pretty default ggplots
+library(broom) # for tidying multiple linear models
+library(mgcv) # generalized additive models
+library(gamm4) # generalized additive mixed-models
+library(gsg) # calculating selection gradients
+library(visreg)
+library(viridis) # for color palette
+
+## Load and manage data ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  # convert appropriate variables to characters instead of integers
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)))
+
+# convert treatment to factor to use as 'by' variable in generalized additive models
+gall_selection.df <- gall_selection.df %>%
+  mutate(Treatment_contr.sum=factor(Treatment.focus), 
+         sc.gall_size = as.numeric(scale(Gall_Height_mm)),
+         sc.clutch_size = as.numeric(scale(gall_individuals)),
+         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
+contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
+
+## Create separate datasets for quantifying selection gradients ----
+control_df <- gall_selection.df %>%
+  filter(Treatment.focus == "Control") %>%
+  mutate(sc.gall_size = (Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm),
+         sc.clutch_size = (gall_individuals - mean(gall_individuals))/sd(gall_individuals),
+         sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
+
+treatment_df <- gall_selection.df %>%
+  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
+  mutate(sc.gall_size = (Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm),
+         sc.clutch_size = (gall_individuals - mean(gall_individuals))/sd(gall_individuals),
+         sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
+
+## Custom functions to avoid repetitive code ----
+gamm.model <- function(formula, data) {
+  gamm4(formula, data, 
+        random = ~(1|Genotype/Plant_Position/Gall_Number), 
+        family = binomial(link = logit))
+}
+
+gam.plot <- function(gam.model, ...) {
+  plot(gam.model, se = TRUE, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
+}
+
+# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
+# also, using 'refit.smooth = T' also generated some very skewed distributions
+# the recipe below provided the most sensible estimates for my data
+gradient.calc <- function(mod, phenotype, covariates = NULL) {
+  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
+                refit.smooth = F,
+                n.boot = 1000,
+                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
+                standardized = T)
+}
+
+insect_FL <- function(mod, phenotype, covariates = NULL) {
+  fitness.landscape(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32,
+                    PI.method = 'boot.para',
+                    refit.smooth = F,
+                    PI.interval = c(0.025,0.975),
+                    plt.density = 100)
+}
+
+get_insect_FL.df <- function(FL){
+  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
+    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
+}
+
+overdisp_fun <- function(model) {
+  ## number of variance parameters in 
+  ##   an n-by-n variance-covariance matrix
+  vpars <- function(m) {
+    nrow(m)*(nrow(m)+1)/2
+  }
+  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
+  rdf <- nrow(model.frame(model))-model.df
+  rp <- residuals(model,type="pearson")
+  Pearson.chisq <- sum(rp^2)
+  prat <- Pearson.chisq/rdf
+  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
+  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
+}
+
+inverse_logit <- function(x) exp(x)/(1+exp(x))
+
+#Beta_avg_grad <- function(logistic_model, mean_fitness) {
+#  brackets <- predict(logistic_model, type = "response") * (1 - predict(logistic_model, type="response"))
+#  gradient <- mean(brackets) * fixef(logistic_model) / mean_fitness 
+#  return(gradient)
+#}
+
+## Calculate directional selection gradients
+# following method of Janzen and Stern 1998, Evolution
+Beta_avg_grad <- function(.) {
+  mean_fitness <- inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
+  mean(brackets) * fixef(.)[-1] / mean_fitness 
+}
+
+## Bootstrap fitness estimates
+bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){
+  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
+
+  # Absolute fitness
+  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))
+
+  if(is.null(bootstraps) == FALSE){
+    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  absolute_fitness_df <- data.frame(newdata, 
+                    average = get_absolute_fitness(logistic_model), 
+                    lower = get_intervals_absolute_fitness[1, ],
+                    upper = get_intervals_absolute_fitness[2, ],
+                    t(get_bootstraps_absolute_fitness$t))
+  } else {
+    absolute_fitness_df <- data.frame(newdata, 
+                    average = get_absolute_fitness(logistic_model))
+  }
+
+  # Relative fitness
+  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))
+
+  if(is.null(bootstraps) == FALSE){
+    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  relative_fitness_df <- data.frame(newdata, 
+                    average = get_relative_fitness(logistic_model), 
+                    lower = get_intervals_relative_fitness[1, ],
+                    upper = get_intervals_relative_fitness[2, ],
+                    t(get_bootstraps_relative_fitness$t))
+  } else {
+      relative_fitness_df <- data.frame(newdata, 
+                    average = get_relative_fitness(logistic_model))
+  }
+
+  # Organize data
+  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
+}
+```
 
@@
 the p-value).
+All analyses and visualizations were conducted in R.
+
+```{r Selection Gradients - Complex Food Web, cache=TRUE}
+# note that I've switched to using the lme4 package to analyzing the GLMM
+
+# GLMM ----
+glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
+                         sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = control_df,
+                         family = binomial(link = logit), optimizer = "bobyqa")
+# summary(glmer_control)
+
+# Mean fitness ----
+Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+# Confidence intervals for selection gradients ----
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+
+## Summary ----
+summary_Beta_glmm_control <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Beta = round(Beta_avg_grad(glmer_control),3),
+  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+summary_Beta_glmm_control
+```
+
+```{r Selection Gradients - Simple Food Web, cache=TRUE}
+
+## GLMM ----
+glmer_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
+                         sc.gall_size:sc.clutch_size + 
+                          sc.gall_size:sc.female_preference + 
+                           sc.clutch_size:sc.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = treatment_df,
+                         family = binomial(link = logit), optimizer = "bobyqa")
+summary(glmer_treatment)
+
+## Mean fitness ----
+Wbar_treatment <- inverse_logit(fixef(update(glmer_treatment, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+## Confidence intervals for selection gradients ----
+boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+
+## Summary ----
+summary_Beta_glmm_treatment <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Beta = round(Beta_avg_grad(glmer_treatment),2),
+  lower_2.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
+  upper_97.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2))
+
+summary_Beta_glmm_treatment
+```
 

### 2018-06-29 elsevier_test/elsevier_test.Rmd
working on intro structure

@@
 
+<!-- Alternative intro, "the fitness landscape as the unifying concept between ecology and evolutionary biology "-->
+
 <!-- I. Community context can affect evolutionary change -->
@@
 Biological diversity -- from genes, to phenotypes, to species -- has fascinated evolutionary biologists for decades.
+<!-- need to improve this instead of just saying its fascinated a small group of people --> Much of this biological diversity has been shaped by natural selection via trophic interactions, such as resource competition (@Schluter2000), mutualistic exchanges of resource (@Jordano1987), and predation (@Abrams2000).
+While there is clear evidence for pairwise trophic interactions to drive evolution by natural selection, we also know that many species are embedded within complex networks of interacting species.
+<!-- need to make the link to multiple traits and the adaptive landscape here --> Nevertheless, the dynamics of natural selection in species-rich communities remains poorly explored (@McPeek2017).
 
-Much of this biological diversity has been shaped by natural selection via trophic interactions, such as resource competition (cite charater displacement), mutualistic exchanges of resource (cite?
-), and predation (cite recent Heath and Stireman paper).
+More recently, researchers have begun to explore how the community context drives evolutionary change (@McPeek2017; @TerHorst2018).
 
@@
 
-Put another way, these results have begun to show biological diversity, in terms of differences between species, can drive evolutionary change.
-
-While there is clear evidence for pairwise trophic interactions to drive evolution by natural selection, its unclear how biological diversity itself imposes natural selection and drives evolutionary change.
+In other words, these results have begun to illustrate show how biological diversity, in terms of differences between species, can shape evolution.
+Nevertheless, predicting the how the composition of species in a community requires moving beyond a description of community composition.
+simply knowing the composition of species in a community will
 
@@
 
-Exploring the effects of biological diversity requires an explicit examination of the network structure of trophic interactions between species in a community.
-Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...); however, we are currently lacking experimental tests.
+Predicting the effects of biological diversity on requires an explicit examination of the network structure of trophic interactions between species in a community.
+Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests.
 
@@
 
-In contrast, ecologists have begun to embrace the complexity of the natural world, and seeking to identify the complex networks of interactions that underlie community structure and ecosystem function.
+<!-- In contrast, ecologists have begun to embrace the complexity of the natural world, and seeking to identify the complex networks of interactions that underlie community structure and ecosystem function.
 However, these studies have not examined how evolutionary processes feedback to shape the structure and evolution of these interaction networks.
+-->
 
@@
 
-Food-web complexity may influence selection gradients in at least two ways.
-First, if more diverse predator communities are more efficient as suppressing prey densities (e.g.
+Food-web complexity can shape the fitness landscape in at least two ways.
+First, if more diverse predator communities are more efficient at suppressing prey densities (e.g.
 biodiversity-ecosystem fucntion; Ives 2005 Ecology Letters), then this will result in lower mean fitness.
-A reduction in mean fitness, all else equal, will intensify natural selection and thus could increase the rate of evolutionary change.
+A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018) and thus could speed up the rate of evolutionary change.
 Alternatively, if predators are functionally distinct, more diverse communities can reduce the strength of selection.
@@
 
-Here, we conducted a field experiment to test the effect of food-web complexity on the fitness landscape of a species embedded within this food web.
+Here, we conducted a field experiment to test the effect of network complexity on the fitness landscape of a constituent species.
 To do this, we used a common garden experiment with a host plant (*Salix hooeriana*), an abundant herbivore (*Iteomyia salicisverruca*), and the diverse community of insect parasitoids that attack it.

### 2018-07-01 elsevier_test/elsevier_test.Rmd
working on intro. close to a solid draft.

@@
 
+> *There is a much more insidious kind of extinction: the extinction of ecological interactions.* 
+> *(Janzen, D.H. 1974. The deflowering of Central America. Natural History. 83:48–53).*
+
 Introduction
@@
 
+<!-- I. Evolutionary dynamics in species-rich communities remains unclear, especially in the field -->
+
+Biological diversity -- from genes, to phenotypes, to species -- has and continues to be shaped by the interplay between ecological and evolutionary processes.
+<!-- need to improve this instead of just saying its fascinated a small group of people -->
+Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (@Schluter2000), mutualisms (@Jordano1987), and predation (@Abrams2000).
+While there is clear evidence that pairwise interactions can drive evolution, we also know that most species interact with multiple species in an ecological community.
+<!-- are embedded within species-rich communities.--> <!-- complex networks of interacting species.
+<!-- need to make the link to multiple traits and the adaptive landscape here --> <!-- Somthing about the this work remaining eminently theoretical -->
+Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--> is challenging and eminently theoretical (@McPeek2017, Nuismer paper, Guimeras paper, also McGill paper about biodiversity effects on evolution).
+<!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
+I think it would be useful to show that there is some field and lab experiments demonstrating that community context can alter evolutionary trajectories -->
+Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
+
+<!-- Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests of how changes in network structure will alter the dynamics of natural selection in the field.
+-->
+
+<!-- II. Linking species loss to changes in network complexity -->
+
+Predicting the evolutionary consequences of biodiversity loss first requires an understanding of the concommitant change in the network structure of species interactions.<!-- the relationship between the network structure of a community and the fitness landscape of its constituent species.-->
+Knowing the interaction network is crucial because the loss of biodiversity, in and of itself, will not alter evolution -- it is the associated loss of ecological interactions that will affect evolutionary change (@Janzen1974).
+For a network of directly connected species, we would expect that the loss of species to result in a loss of network complexity.<!-- Need to formalize this logic more, because the loss of a specialist species in a highly generalist food web, would actually increase network complexity...
+Maybe I need to focus on the node/species level property -->
+Network complexity is a property that describes the diversity of interactions in an ecological community (@Banasek-Richter2009). 
+Thus, all else equal, species loss will decrease the diversity of interactions, resulting in a more simple network.
+<!-- Explicitly linking network complexity to the fitness landscape, however, is ultimately needed to predict the evolutionary consequences of biodiversity loss.
+-->
+
+<!-- III. Linking changes in network complexity to the fitness landscape -->
+Predicting how a change in network complexity will alter evolution also requires an understanding of the relationship between network structure and the adaptive landscape. 
+The adaptive landscape (i.e.
+fitness landscape or selective surface) describes the relationship between the average trait value of a population and its average fitness (cite Arnold).
+<!-- Need to make the transition between network and trophic complexity -->
+For a trophic network, such as a food web, changes in network complexity can shape the adaptive landscape of constituent species in at least two ways. 
+First, if a more diverse community of consumers is more efficient at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population. 
+A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018) and thus could speed up the rate of evolutionary change. 
+On the other hand, if consumers are functionally distinct, then more diverse communities can dampen the strength of selection. 
+This is because each consumer has a different functional relationship with resource traits. 
+In addition, there is a reduced probability in interacting with a specific consumer species in a more diverse community.
+Thus, a more diverse consumer community may impose more diffuse selection across the adaptive landscape. <!--and the probability of an interaction.-->
+<!-- Consider linking to a reduced probability of interacting with any one species in the community, which would dampen the selection pressures acting on a given phenotype, also, if predators impose selection on different parts of a prey phenotype, then these selection pressures may even cancel each other out -->
+
+<!-- IV. Summarize our plans to tackle this problem -->
+
+Here, we provide a quantitative test of how the loss of species diversity -- and concomittant loss of network complexity -- shapes the adaptive landscape of a consitutent species in a natural community.
+<!-- Here, we conducted a field experiment to test how changes in network complexity would shape the fitness landscape of a constituent species. -->
+We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on the insect herbivore, *Iteomyia salicisverruca*. 
+The larva of this herbivore species induces tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006). 
+Prior work with this study system has shown that there is directional selection for larger galls, likely because larger galls provide a refuge from parasitoid attack (@Barbour2016). 
+However, there is also evidence that each parasitoid species imposes differential selection on gall traits (@Barbour2016). <!-- Need a sentence to wrap it up--> 
+<!-- Taken together, our study seeks to provide one of the first quantitative tests of how the loss of species diversity -- and concomittant loss of network complexity -- shapes the fitness landscape of associated species.
+-->
+Taken together, our aim is to provide evidence for how the simplification of natural communities affects the adaptive<!--process--> potential of constituent species.
+
 <!-- Alternative intro, "the fitness landscape as the unifying concept between ecology and evolutionary biology "-->
 
-<!-- I. Community context can affect evolutionary change -->
+<!-- Although often used solely as a metaphor, the fitness landscape explicitly links ecology and evolutionary biology. -->
+<!-- Fitness landscapes provide a quantitative framework for unifying evolutionary biology and ecology.
+Alternatively described as the 'adaptive landscape' or 'selective surface', evolutionary biologists have traditionally used the fitness landscape to describe how changes in the mean values of a trait or multiple traits can alter population mean fitness.
+Less appreciated is the fact that ecologists have similarly been studying the fitness landscape of species but through the lense of population dynamics.
+study how changes in population abundances of interacting species shapes the fitness landscape (@McPeek2017).
+This is because per capita population growth rate is equivalent to population mean fitness (cite Lande ; @McPeek2017).
+-->
 
-Biological diversity -- from genes, to phenotypes, to species -- has fascinated evolutionary biologists for decades.
-<!-- need to improve this instead of just saying its fascinated a small group of people --> Much of this biological diversity has been shaped by natural selection via trophic interactions, such as resource competition (@Schluter2000), mutualistic exchanges of resource (@Jordano1987), and predation (@Abrams2000).
-While there is clear evidence for pairwise trophic interactions to drive evolution by natural selection, we also know that many species are embedded within complex networks of interacting species.
-<!-- need to make the link to multiple traits and the adaptive landscape here --> Nevertheless, the dynamics of natural selection in species-rich communities remains poorly explored (@McPeek2017).
+<!-- Therefore, understanding the feedbacks between ecological and evolutionary dynamics requires an assessment of how the community context shapes the fitness landscape.
 
-More recently, researchers have begun to explore how the community context drives evolutionary change (@McPeek2017; @TerHorst2018).
-
-NEED to recognize that evolutionary biologists have begun to explore how community context affects evolutionary change (work by Sharon Strauss, Casey terHorst, Lutz Becks, etc.).
-These results have begun to show interesting patterns whereby the composition of species in a community can alter the direction and strength of natural selection imposed on species embedded within these communities (cite).
-
-In other words, these results have begun to illustrate show how biological diversity, in terms of differences between species, can shape evolution.
-Nevertheless, predicting the how the composition of species in a community requires moving beyond a description of community composition.
-simply knowing the composition of species in a community will
-
-<!-- II. Still unclear how biological diversity shapes evolutionary change -->
-
-Predicting the effects of biological diversity on requires an explicit examination of the network structure of trophic interactions between species in a community.
-Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests.
+We are in the midst of the lost of biological diversity; yet it remains unclear how the loss of biological diversity will alter evolutionary change within species. In order to predict how -->
 
@@
 
-Food-web complexity can shape the fitness landscape in at least two ways.
+<!-- Food-web complexity can shape the fitness landscape in at least two ways.
 First, if more diverse predator communities are more efficient at suppressing prey densities (e.g.
@@
 This is because each predator has a different functional relationship between prey phenotype and the probability of an interaction.
-
-<!-- IV. Introduce study system -->
-
-Here, we conducted a field experiment to test the effect of network complexity on the fitness landscape of a constituent species.
-To do this, we used a common garden experiment with a host plant (*Salix hooeriana*), an abundant herbivore (*Iteomyia salicisverruca*), and the diverse community of insect parasitoids that attack it.
-Prior work in this system has shown that there is directional selection for larger galls, likely because larger galls provide more of a refuge from parasitoid attack.
-However, there is also evidence that different parasitoid species impose differential selection on gall phenotypes.
+-->
 
@@
 
-```{r Selection Gradients - Complex Food Web, cache=TRUE}
+```{r Selection Gradients - Complex Food Web, cache=TRUE, eval=FALSE}
 # note that I've switched to using the lme4 package to analyzing the GLMM
@@
 
-```{r Selection Gradients - Simple Food Web, cache=TRUE}
+```{r Selection Gradients - Simple Food Web, cache=TRUE, eval=FALSE}
 
@@
 
-We found that more phenotypic traits were under selection in the simple vs.
-complex food web.
-In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex Beta = ; simple Beta = )(Fig.
-2A).
-In complex food webs, there was no evidence of selection on clutch size ($\beta_{clutch}=$) or female preference ($\beta_{preference}=$)(orange lines in Fig.
-2B,C).
+We found that more phenotypic traits were under selection in the simple vs. complex food web. 
+In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex Beta = ; simple Beta = )(Fig. 2A). 
+In complex food webs, there was no evidence of selection on clutch size ($\beta_{clutch}=$) or female preference ($\beta_{preference}=$)(orange lines in Fig. 2B,C). 
 In simple food webs, however, clutch size and female preference were under strong directional selection, with smaller clutch sizes and weaker preferences resulting in higher larval survival (blue lines in Fig.
@@
 complex food web.
-Our model comparison suggested that it was unnecessary to test for the effects of non-linear or correlational selection gradients (ref.
-supp.
-mat.).
+Our model comparison suggested that it was unnecessary to test for the effects of non-linear or correlational selection gradients (ref. supp. mat.).
 
@@
 <!-- Feedbacks between biological diversity and evolutionary change -->
+
+More recently, researchers have begun to explore how the community context drives evolutionary change (@McPeek2017; @TerHorst2018).
+
+NEED to recognize that evolutionary biologists have begun to explore how community context affects evolutionary change (work by Sharon Strauss, Casey terHorst, Lutz Becks, etc.).
+These results have begun to show interesting patterns whereby the composition of species in a community can alter the direction and strength of natural selection imposed on species embedded within these communities (cite).
+
+In other words, these results have begun to illustrate show how biological diversity, in terms of differences between species, can shape evolution.
+Nevertheless, predicting the how the composition of species in a community requires moving beyond a description of community composition.
+simply knowing the composition of species in a community will
 

### 2018-07-01 elsevier_test/elsevier_test.tex
adding code directly to file.
working on intro. close to a solid draft.

@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
 \ifxetex
@@
 
+\begin{quote}
+\emph{There is a much more insidious kind of extinction: the extinction
+of ecological interactions.} \emph{(Janzen, D.H. 1974. The deflowering
+of Central America. Natural History. 83:48--53).}
+\end{quote}
+
 \section{Introduction}\label{introduction}
 
-Biological diversity -- from genes, to phenotypes, to species -- has
-fascinated evolutionary biologists for decades.
+Biological diversity -- from genes, to phenotypes, to species -- has and
+continues to be shaped by the interplay between ecological and
+evolutionary processes. Much of this biological diversity has been
+molded by natural selection arising from species interactions, such as
+resource competition (Schluter (2000)), mutualisms (Jordano (1987)), and
+predation (Abrams (2000)). While there is clear evidence that pairwise
+interactions can drive evolution, we also know that most species
+interact with multiple species in an ecological community. Understanding
+how evolutionary dynamics unfold in a community context is challenging
+and eminently theoretical (({\textbf{???}}), Nuismer paper, Guimeras
+paper, also McGill paper about biodiversity effects on evolution). Given
+the rapid loss of species diversity we are experiencing throughout the
+world (cite), we are in urgent need of work that makes and tests
+predictions for how the loss of species will affect the evolutionary
+process in natural communities.
 
-Much of this biological diversity has been shaped by natural selection
-via trophic interactions, such as resource competition (cite charater
-displacement), mutualistic exchanges of resource (cite? ), and predation
-(cite recent Heath and Stireman paper).
+Predicting the evolutionary consequences of biodiversity loss first
+requires an understanding of the concommitant change in the network
+structure of species interactions. Knowing the interaction network is
+crucial because the loss of biodiversity, in and of itself, will not
+alter evolution -- it is the associated loss of ecological interactions
+that will affect evolutionary change (Janzen (1974)). For a network of
+directly connected species, we would expect that the loss of species to
+result in a loss of network complexity. Network complexity is a property
+that describes the diversity of interactions in an ecological community
+(Banasek-Richter et al. (2009)). Thus, all else equal, species loss will
+decrease the diversity of interactions, resulting in a more simple
+network.
 
-NEED to recognize that evolutionary biologists have begun to explore how
-community context affects evolutionary change (work by Sharon Strauss,
-Casey terHorst, Lutz Becks, etc.). These results have begun to show
-interesting patterns whereby the composition of species in a community
-can alter the direction and strength of natural selection imposed on
-species embedded within these communities (cite).
+Predicting how a change in network complexity will alter evolution also
+requires an understanding of the relationship between network structure
+and the adaptive landscape. The adaptive landscape (i.e.~fitness
+landscape or selective surface) describes the relationship between the
+average trait value of a population and its average fitness (cite
+Arnold). For a trophic network, such as a food web, changes in network
+complexity can shape the adaptive landscape of constituent species in at
+least two ways. First, if a more diverse community of consumers is more
+efficient at suppressing resource densities (Ives, Cardinale, and Snyder
+(2005)), then this will result in lower mean fitness of the resource
+population. A reduction in mean fitness, all else equal, will intensify
+natural selection (Hunter et al. (2018)) and thus could speed up the
+rate of evolutionary change. On the other hand, if consumers are
+functionally distinct, then more diverse communities can dampen the
+strength of selection. This is because each consumer has a different
+functional relationship with resource traits. In addition, there is a
+reduced probability in interacting with a specific consumer species in a
+more diverse community. Thus, a more diverse consumer community may
+impose more diffuse selection across the adaptive landscape.
 
-Put another way, these results have begun to show biological diversity,
-in terms of differences between species, can drive evolutionary change.
-
-While there is clear evidence for pairwise trophic interactions to drive
-evolution by natural selection, its unclear how biological diversity
-itself imposes natural selection and drives evolutionary change.
-
-Exploring the effects of biological diversity requires an explicit
-examination of the network structure of trophic interactions between
-species in a community. Theoretical models have begun to examine how the
-network structure of species interactions drives evolutionary change
-(Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish
-guy\ldots{}); however, we are currently lacking experimental tests.
-
-In contrast, ecologists have begun to embrace the complexity of the
-natural world, and seeking to identify the complex networks of
-interactions that underlie community structure and ecosystem function.
-However, these studies have not examined how evolutionary processes
-feedback to shape the structure and evolution of these interaction
-networks.
-
-Food-web complexity may influence selection gradients in at least two
-ways. First, if more diverse predator communities are more efficient as
-suppressing prey densities (e.g.~biodiversity-ecosystem fucntion; Ives
-2005 Ecology Letters), then this will result in lower mean fitness. A
-reduction in mean fitness, all else equal, will intensify natural
-selection and thus could increase the rate of evolutionary change.
-Alternatively, if predators are functionally distinct, more diverse
-communities can reduce the strength of selection. This is because each
-predator has a different functional relationship between prey phenotype
-and the probability of an interaction.
-
-Here, we conducted a field experiment to test the effect of food-web
-complexity on the fitness landscape of a species embedded within this
-food web. To do this, we used a common garden experiment with a host
-plant (\emph{Salix hooeriana}), an abundant herbivore (\emph{Iteomyia
-salicisverruca}), and the diverse community of insect parasitoids that
-attack it. Prior work in this system has shown that there is directional
-selection for larger galls, likely because larger galls provide more of
-a refuge from parasitoid attack. However, there is also evidence that
-different parasitoid species impose differential selection on gall
-phenotypes.
+Here, we provide a quantitative test of how the loss of species
+diversity -- and concomittant loss of network complexity -- shapes the
+adaptive landscape of a consitutent species in a natural community. We
+conducted a field experiment that manipulated the diversity of insect
+parasitoids that were able to impose selection on the insect herbivore,
+\emph{Iteomyia salicisverruca}. The larva of this herbivore species
+induces tooth-shaped galls when they feed on the developing leaves of
+willow trees (\emph{Salix} sp., Russo (2006)). Prior work with this
+study system has shown that there is directional selection for larger
+galls, likely because larger galls provide a refuge from parasitoid
+attack (Barbour et al. (2016)). However, there is also evidence that
+each parasitoid species imposes differential selection on gall traits
+(Barbour et al. (2016)). Taken together, our aim is to provide evidence
+for how the simplification of natural communities affects the adaptive
+potential of constituent species.
 
@@
 and others work with Cecidomyiid midges (Weis, Price, and Lynch (1983),
-Heath, Abbot, and Stireman (2018)). First, we measured gall diameter as
-the size of each gall chamber to the nearest 0.01 mm at its maximum
-diameter (perpendicular to the direction of plant tissue growth). Our
-previous work has shown that a larger gall diameter provides a refuge
-for larva from parasitoid attack (Barbour et al. (2016)). Second, we
-measured the clutch size of adult female midges by counting the number
-of chambers in each gall (Weis, Price, and Lynch (1983)). All larva
-collected from the same multi-chambered gall were scored with the same
-clutch size. Third, we measured female preference for oviposition
-(egg-laying) sites as the density of larva observed on a plant. The
-measurement of larval densities on plants in the field is a commonly
-used index for measuring oviposition preference (Gripenberg et al.
-(2010)), although caution must be taken in inferring `preference'
+J. J. Heath, Abbot, and Stireman (2018)). First, we measured gall
+diameter as the size of each gall chamber to the nearest 0.01 mm at its
+maximum diameter (perpendicular to the direction of plant tissue
+growth). Our previous work has shown that a larger gall diameter
+provides a refuge for larva from parasitoid attack (Barbour et al.
+(2016)). Second, we measured the clutch size of adult female midges by
+counting the number of chambers in each gall (Weis, Price, and Lynch
+(1983)). All larva collected from the same multi-chambered gall were
+scored with the same clutch size. Third, we measured female preference
+for oviposition (egg-laying) sites as the density of larva observed on a
+plant. The measurement of larval densities on plants in the field is a
+commonly used index for measuring oviposition preference (Gripenberg et
+al. (2010)), although caution must be taken in inferring `preference'
 (Singer (1986)). This is because larval densities can be influenced by
@@
 simple food web were larger/smaller than in the complex food web
-(i.e.~the p-value).
+(i.e.~the p-value). All analyses and visualizations were conducted in R.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{# note that I've switched to using the lme4 package to analyzing the GLMM}
+
+\CommentTok{# GLMM ----}
+\NormalTok{glmer_control <-}\StringTok{ }\KeywordTok{glmer}\NormalTok{(gall_survival }\OperatorTok{~}\StringTok{ }\NormalTok{sc.gall_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.female_preference }\OperatorTok{+}
+\StringTok{                         }\KeywordTok{I}\NormalTok{(sc.gall_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.clutch_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.female_preference}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}
+\StringTok{                         }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}
+\StringTok{                           }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{Genotype}\OperatorTok{/}\NormalTok{Plant_Position}\OperatorTok{/}\NormalTok{Gall_Number),}
+                         \DataTypeTok{data =}\NormalTok{ control_df,}
+                         \DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\DataTypeTok{link =}\NormalTok{ logit), }\DataTypeTok{optimizer =} \StringTok{"bobyqa"}\NormalTok{)}
+\CommentTok{# summary(glmer_control)}
+
+\CommentTok{# Mean fitness ----}
+\NormalTok{Wbar_control <-}\StringTok{ }\KeywordTok{inverse_logit}\NormalTok{(}\KeywordTok{fixef}\NormalTok{(}\KeywordTok{update}\NormalTok{(glmer_control, .}\OperatorTok{~}\NormalTok{.
+}\OperatorTok{-}\NormalTok{sc.gall_size }\OperatorTok{-}\NormalTok{sc.clutch_size }\OperatorTok{-}\NormalTok{sc.female_preference)))}
+
+\CommentTok{# Confidence intervals for selection gradients ----}
+\NormalTok{boot_Beta_control <-}\StringTok{ }\KeywordTok{bootMer}\NormalTok{(glmer_control, }\DataTypeTok{FUN =}\NormalTok{ Beta_avg_grad, }\DataTypeTok{nsim=}\DecValTok{100}\NormalTok{, }\DataTypeTok{parallel=}\StringTok{"multicore"}\NormalTok{, }\DataTypeTok{ncpus=}\DecValTok{32}\NormalTok{)}
+
+\NormalTok{## Summary ----}
+\NormalTok{summary_Beta_glmm_control <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall size"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Complex"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Beta =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(glmer_control),}\DecValTok{3}\NormalTok{),}
+  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{),}
+  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)) }
+
+\NormalTok{summary_Beta_glmm_control}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{## GLMM ----}
+\NormalTok{glmer_treatment <-}\StringTok{ }\KeywordTok{glmer}\NormalTok{(gall_survival }\OperatorTok{~}\StringTok{ }\NormalTok{sc.gall_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.female_preference }\OperatorTok{+}
+\StringTok{                         }\KeywordTok{I}\NormalTok{(sc.gall_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.clutch_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.female_preference}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}
+\StringTok{                         }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }
+\StringTok{                          }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}\StringTok{ }
+\StringTok{                           }\NormalTok{sc.clutch_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}
+\StringTok{                           }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{Genotype}\OperatorTok{/}\NormalTok{Plant_Position}\OperatorTok{/}\NormalTok{Gall_Number),}
+                         \DataTypeTok{data =}\NormalTok{ treatment_df,}
+                         \DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\DataTypeTok{link =}\NormalTok{ logit), }\DataTypeTok{optimizer =} \StringTok{"bobyqa"}\NormalTok{)}
+\KeywordTok{summary}\NormalTok{(glmer_treatment)}
+
+\NormalTok{## Mean fitness ----}
+\NormalTok{Wbar_treatment <-}\StringTok{ }\KeywordTok{inverse_logit}\NormalTok{(}\KeywordTok{fixef}\NormalTok{(}\KeywordTok{update}\NormalTok{(glmer_treatment, .}\OperatorTok{~}\NormalTok{.
+}\OperatorTok{-}\NormalTok{sc.gall_size }\OperatorTok{-}\NormalTok{sc.clutch_size }\OperatorTok{-}\NormalTok{sc.female_preference)))}
+
+\NormalTok{## Confidence intervals for selection gradients ----}
+\NormalTok{boot_Beta_treatment <-}\StringTok{ }\KeywordTok{bootMer}\NormalTok{(glmer_treatment, }\DataTypeTok{FUN =}\NormalTok{ Beta_avg_grad, }\DataTypeTok{nsim=}\DecValTok{100}\NormalTok{, }\DataTypeTok{parallel=}\StringTok{"multicore"}\NormalTok{, }\DataTypeTok{ncpus=}\DecValTok{32}\NormalTok{)}
+
+\NormalTok{## Summary ----}
+\NormalTok{summary_Beta_glmm_treatment <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall size"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Simple"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Beta =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(glmer_treatment),}\DecValTok{2}\NormalTok{),}
+  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{2}\NormalTok{),}
+  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{2}\NormalTok{)) }
+
+\NormalTok{summary_Beta_glmm_treatment}
+\end{Highlighting}
+\end{Shaded}
 
@@
 
+More recently, researchers have begun to explore how the community
+context drives evolutionary change (({\textbf{???}}); terHorst et al.
+(2018)).
+
+NEED to recognize that evolutionary biologists have begun to explore how
+community context affects evolutionary change (work by Sharon Strauss,
+Casey terHorst, Lutz Becks, etc.). These results have begun to show
+interesting patterns whereby the composition of species in a community
+can alter the direction and strength of natural selection imposed on
+species embedded within these communities (cite).
+
+In other words, these results have begun to illustrate show how
+biological diversity, in terms of differences between species, can shape
+evolution. Nevertheless, predicting the how the composition of species
+in a community requires moving beyond a description of community
+composition. simply knowing the composition of species in a community
+will
+
 There are various bibliography styles available. You can select the
@@
 \hypertarget{refs}{}
+\hypertarget{ref-Abrams2000}{}
+Abrams, Peter A. 2000. ``The Evolution of Predator-Prey Interactions:
+Theory and Evidence.'' \emph{Annu. Rev. Ecol. Syst.} 31. Annual Reviews:
+79--105.
+
+\hypertarget{ref-Banasek-Richter2009}{}
+Banasek-Richter, Carolin, Louis-Félix Bersier, Marie-France Cattin,
+Richard Baltensperger, Jean-Pierre Gabriel, Yves Merz, Robert E
+Ulanowicz, et al. 2009. ``Complexity in Quantitative Food Webs.''
+\emph{Ecology} 90 (6): 1470--7.
+
 \hypertarget{ref-Barbour2016}{}
@@
 
+\hypertarget{ref-Hunter2018}{}
+Hunter, Darren C, Josephine M Pemberton, Jill G Pilkington, and Michael
+B Morrissey. 2018. ``Quantification and Decomposition of
+Environment-Selection Relationships.'' \emph{Evolution}, March.
+
+\hypertarget{ref-Ives2005}{}
+Ives, Anthony R, Bradley J Cardinale, and William E Snyder. 2005. ``A
+Synthesis of Subdisciplines: Predator--prey Interactions, and
+Biodiversity and Ecosystem Functioning.'' \emph{Ecol. Lett.} 8 (1).
+Blackwell Science Ltd: 102--16.
+
+\hypertarget{ref-Janzen1974}{}
+Janzen, Daniel. 1974. ``The Deflowering of Central America.''
+\emph{Natural History} 83 (January): 49--53.
+
+\hypertarget{ref-Jordano1987}{}
+Jordano, Pedro. 1987. ``Patterns of Mutualistic Interactions in
+Pollination and Seed Dispersal: Connectance, Dependence Asymmetries, and
+Coevolution.'' \emph{Am. Nat.} 129 (5): 657--77.
+
+\hypertarget{ref-Russo2006}{}
+Russo, Ron. 2006. \emph{Field Guide to Plant Galls of California and
+Other Western States}. 1st ed. University of California Press.
+
+\hypertarget{ref-Schluter2000}{}
+Schluter, Dolph. 2000. ``Ecological Character Displacement in Adaptive
+Radiation.'' \emph{Am. Nat.} 156 (S4): S4--S16.
+
 \hypertarget{ref-Singer1986}{}
@@
 York, NY: Springer New York.
+
+\hypertarget{ref-TerHorst2018}{}
+terHorst, Casey P, Peter C Zee, Katy D Heath, Thomas E Miller, Abigail I
+Pastore, Swati Patel, Sebastian J Schreiber, Michael J Wade, and Matthew
+R Walsh. 2018. ``Evolution in a Community Context: Trait Responses to
+Multiple Species Interactions*.'' \emph{Am. Nat.}, January. University
+of Chicago PressChicago, IL.
 

### 2018-07-02 elsevier_test/elsevier_test.Rmd
updating plots and analyses in ms

@@
 library(viridis) # for color palette
+library(lme4) # for generalized linear mixed models
 
@@
 ## Custom functions to avoid repetitive code ----
-gamm.model <- function(formula, data) {
-  gamm4(formula, data, 
-        random = ~(1|Genotype/Plant_Position/Gall_Number), 
-        family = binomial(link = logit))
-}
 
-gam.plot <- function(gam.model, ...) {
-  plot(gam.model, se = TRUE, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
-}
-
-# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
-# also, using 'refit.smooth = T' also generated some very skewed distributions
-# the recipe below provided the most sensible estimates for my data
-gradient.calc <- function(mod, phenotype, covariates = NULL) {
-  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
-                refit.smooth = F,
-                n.boot = 1000,
-                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
-                standardized = T)
-}
-
-insect_FL <- function(mod, phenotype, covariates = NULL) {
-  fitness.landscape(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32,
-                    PI.method = 'boot.para',
-                    refit.smooth = F,
-                    PI.interval = c(0.025,0.975),
-                    plt.density = 100)
-}
-
-get_insect_FL.df <- function(FL){
-  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
-    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
-}
-
+## Test for overdispersion
 overdisp_fun <- function(model) {
@@
 
+## Transform logit to probability
 inverse_logit <- function(x) exp(x)/(1+exp(x))
 
-#Beta_avg_grad <- function(logistic_model, mean_fitness) {
-#  brackets <- predict(logistic_model, type = "response") * (1 - predict(logistic_model, type="response"))
-#  gradient <- mean(brackets) * fixef(logistic_model) / mean_fitness 
-#  return(gradient)
-#}
-
-## Calculate directional selection gradients
-# following method of Janzen and Stern 1998, Evolution
+## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
 Beta_avg_grad <- function(.) {
@@
 ## Bootstrap fitness estimates
-bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){
-  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
+bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
+  model_matrix <- model.matrix(formula(fixed_effects), newdata)
 
@@
 }
+
+## Number of bootstrap replicates ----
+n_boots_analysis <- 50
+n_boots_plots <- 50
 ```
@@
 <!-- need to make the link to multiple traits and the adaptive landscape here --> <!-- Somthing about the this work remaining eminently theoretical -->
-Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--> is challenging and eminently theoretical (@McPeek2017, Nuismer paper, Guimeras paper, also McGill paper about biodiversity effects on evolution).
+Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--> is challenging and eminently theoretical (@McPeek2017, @De_Mazancourt2008, @Guimaraes2017, @Nuismer2013).
 <!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
@@
 
-Predicting the evolutionary consequences of biodiversity loss first requires an understanding of the concommitant change in the network structure of species interactions.<!-- the relationship between the network structure of a community and the fitness landscape of its constituent species.-->
+Predicting the evolutionary consequences of species loss first requires an understanding of the concommitant change in the species-interaction networks.<!-- the relationship between the network structure of a community and the fitness landscape of its constituent species.-->
 Knowing the interaction network is crucial because the loss of biodiversity, in and of itself, will not alter evolution -- it is the associated loss of ecological interactions that will affect evolutionary change (@Janzen1974).
@@
 We used generalized linear mixed models (GLMMs, @Bolker2009) with larval survival (0 or 1) as our response variable and measure of fitness.
-We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait, as fixed effects in the statistical models.
+We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
 To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
@@
 setting them to zero) to estimate selection gradients.
-We then used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), nonlinear ($\gamma_{z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
+We then used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
 To test whether selection gradients differed between treatments, we used our bootstrapped estimates to calculate the probability that selection gradients in the simple food web were larger/smaller than in the complex food web (i.e.
 the p-value).
-All analyses and visualizations were conducted in R.
+All analyses and visualizations were conducted in R (@R2018).
 
-```{r Selection Gradients - Complex Food Web, cache=TRUE, eval=FALSE}
+```{r Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
 # note that I've switched to using the lme4 package to analyzing the GLMM
 
-# GLMM ----
-glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
-                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
-                         sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference +
+# Directional selection ----
+beta_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
                            (1|Genotype/Plant_Position/Gall_Number),
                          data = control_df,
-                         family = binomial(link = logit), optimizer = "bobyqa")
-# summary(glmer_control)
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+summary(beta_control)
+overdisp_fun(beta_control)
+
+# Quadratic selection ----
+quad_control <- update(beta_control, .~. + I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2))
+
+summary(quad_control)
+overdisp_fun(quad_control)
+
+# Correlational selection ----
+corr_control <- update(quad_control, .~. + sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference)
+
+summary(corr_control)
+overdisp_fun(corr_control)
 
 # Mean fitness ----
-Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+Wbar_control <- inverse_logit(fixef(update(beta_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
 
-# Confidence intervals for selection gradients ----
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+# Confidence intervals ----
+boot_beta_control <- bootMer(beta_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_quad_control <- bootMer(quad_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_corr_control <- bootMer(corr_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
 
-## Summary ----
-summary_Beta_glmm_control <- data.frame(
-  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+```{r Selection Gradients - Simple Food Web, cache=TRUE, include=FALSE}
+
+# Directional selection ----
+beta_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = treatment_df,
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+summary(beta_treatment)
+overdisp_fun(beta_treatment)
+
+# Quadratic selection ----
+quad_treatment <- update(beta_treatment, .~. + I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2))
+
+summary(quad_treatment)
+overdisp_fun(quad_treatment)
+
+# Correlational selection ----
+corr_treatment <- update(quad_treatment, .~. + sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference)
+
+summary(corr_treatment)
+overdisp_fun(corr_treatment)
+
+# Mean fitness ----
+Wbar_treatment <- inverse_logit(fixef(update(beta_treatment, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+# Confidence intervals ----
+boot_beta_treatment <- bootMer(beta_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_quad_treatment <- bootMer(quad_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_corr_treatment <- bootMer(corr_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Table of Selection Gradients, echo=FALSE, message=FALSE, warning=FALSE}
+
+## Summarize Control Selection Gradients ----
+summary_beta_control <- data.frame(
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
   Food_Web = "Complex",
   Model = "GLMM",
-  Beta = round(Beta_avg_grad(glmer_control),3),
-  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_control),3),
+  lower_2.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
 
-summary_Beta_glmm_control
-```
+# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)
+summary_quad_control <- data.frame(
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Quadratic",
+  Estimate = 2*round(Beta_avg_grad(quad_control),3)[-c(1:3)],
+  lower_2.5 = 2*round(apply(boot_quad_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:3)],
+  upper_97.5 = 2*round(apply(boot_quad_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:3)])
 
-```{r Selection Gradients - Simple Food Web, cache=TRUE, eval=FALSE}
+summary_corr_control <- data.frame(
+  Phenotype = c("Diam,Clutch", "Diam,Pref", "Clutch,Pref"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Correlational",
+  Estimate = round(Beta_avg_grad(corr_control),3)[-c(1:6)],
+  lower_2.5 = round(apply(boot_corr_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:6)],
+  upper_97.5 = round(apply(boot_corr_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:6)])
 
-## GLMM ----
-glmer_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
-                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
-                         sc.gall_size:sc.clutch_size + 
-                          sc.gall_size:sc.female_preference + 
-                           sc.clutch_size:sc.female_preference +
-                           (1|Genotype/Plant_Position/Gall_Number),
-                         data = treatment_df,
-                         family = binomial(link = logit), optimizer = "bobyqa")
-summary(glmer_treatment)
-
-## Mean fitness ----
-Wbar_treatment <- inverse_logit(fixef(update(glmer_treatment, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
-
-## Confidence intervals for selection gradients ----
-boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
-
-## Summary ----
-summary_Beta_glmm_treatment <- data.frame(
+## Summarize Treatment Selection Gradients ----
+summary_beta_treatment <- data.frame(
   Phenotype = c("Gall size", "Clutch size", "Female preference"),
@@
   Model = "GLMM",
-  Beta = round(Beta_avg_grad(glmer_treatment),2),
-  lower_2.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
-  upper_97.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2))
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_treatment),3),
+  lower_2.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
 
-summary_Beta_glmm_treatment
+# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)
+summary_quad_treatment <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Type = "Quadratic",
+  Estimate = 2*round(Beta_avg_grad(quad_treatment),3)[-c(1:3)],
+  lower_2.5 = 2*round(apply(boot_quad_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:3)],
+  upper_97.5 = 2*round(apply(boot_quad_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:3)])
+
+summary_corr_treatment <- data.frame(
+  Phenotype = c("Diam,Clutch", "Diam,Pref", "Clutch,Pref"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Type = "Correlational",
+  Estimate = round(Beta_avg_grad(corr_treatment),3)[-c(1:6)],
+  lower_2.5 = round(apply(boot_corr_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:6)],
+  upper_97.5 = round(apply(boot_corr_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:6)])
+
+bind_rows(summary_beta_control, summary_beta_treatment)
+bind_rows(summary_quad_control, summary_quad_treatment)
+bind_rows(summary_corr_control, summary_corr_treatment)
 ```
@@
 
+BREAK UP INTO INDIVIDUAL PIECES: E.G. GALL SIZE. THIS SHOULD BE SMALL ENOUGH TO ALLOW CACHING
+
+```{r Get Univariate Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
+## Gall size ----
+
+# Control
+RF_control_gall_size <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000), 
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+# Treatment
+RF_treatment_gall_size <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Clutch size ----
+
+# Control
+RF_control_clutch_size <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0),
+  bootstraps=100)
+
+# Treatment 
+RF_treatment_clutch_size <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Female preference ----
+
+# Control 
+RF_control_female_preference <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0, 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=100)
+
+# Treatment
+RF_treatment_female_preference <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = 0,
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=100)
+```
+
+```{r Plot Univariate Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
+## Relative fitness plots ----
+
+# Get range in relative fitness for accurate scaling across all plots
+RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
+          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
+          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, relative_fitness, -sc.gall_size) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  summarise(min = min(relative_fitness), max = max(relative_fitness))
+RF_gradient_scale <- c(0,0.5,1,1.5,2,2.5) # adjusted based on range
+
+# Color palette: order -> orange, light blue, green, yellow, dark blue, red, pink
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
+complex_color <- cbPalette[6]
+simple_color <- cbPalette[5]
+treatment_colors <- c(complex_color, simple_color)
+
+# Gall size    
+RF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Clutch size
+RF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.female_preference) %>%
+  gather(ID, relative_fitness, -sc.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Female preference 
+RF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.clutch_size) %>%
+  gather(ID, relative_fitness, -sc.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Get legend
+RF_uni_legend <- get_legend(RF_uni_size)
+
+# Make plots
+RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none"), 
+                       RF_uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       RF_uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       labels = "AUTO", ncol = 4, align='hv')
+
+RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
+RF_gradients
+#save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
+#save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
+```
+
+```{r Get Multivariate Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
+
+## Clutch size x Female preference ----
+
+# Control
+RF_control_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000), 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment
+RF_treatment_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+## Gall size x Clutch size ----
+
+# Control
+RF_control_size.x.clutch <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = seq(-1,1,length.out=1000), 
+     sc.female_preference = 0), 
+  bootstraps=NULL)
+
+# Treatment
+RF_treatment_size.x.clutch <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0), 
+  bootstraps=NULL)
+
+## Gall size x Female preference ----
+
+# Control
+RF_control_size.x.preference <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0, 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment
+RF_treatment_size.x.preference <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0,
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+```
+
+```{r Plot Multivariate Fitness Landscape, echo=FALSE, message=FALSE, warning=FALSE}
+
+## Relative fitness plots ----
+
+# Get range in relative fitness for accurate scaling across all plots
+RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
+          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
+          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+# Clutch x Preference
+RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+
+# Size x Clutch
+RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+
+# Size x Preference
+RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+
+# Get legend
+RF_landscape_legend <- get_legend(RF_plot_size.x.preference)
+
+# Format plots
+RF_landscape_plots <- plot_grid(
+  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
+  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
+  RF_plot_size.x.preference + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "AUTO")
+RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
+RF_landscape_2d
+#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
+```
+
+```{r AIC Model Comparison, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
+
+# Control ----
+AIC(beta_control, quad_control, corr_control)
+
+glm.beta_control <- glm(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference, data=control_df, family=binomial(link=logit))
+
+beta_control.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                                   (1|Gall_Number),
+                                 data = control_df,
+                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+AIC(beta_control, glm.beta_control)
+AIC(beta_control, beta_control.REonlyGallID)
+overdisp_fun(beta_control)
+
+# Treatment ----
+AIC(beta_treatment, quad_treatment, corr_treatment)
+
+glm.beta_treatment <- glm(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference, data=treatment_df, family=binomial(link=logit))
+
+beta_treatment.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                                   (1|Genotype/Plant_Position),
+                                 data = treatment_df,
+                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+overdisp_fun(beta_treatment)
+
+AIC(beta_treatment, glm.beta_treatment)
+AIC(beta_treatment, beta_treatment.REonlyGallID)
+anova(beta_treatment, beta_treatment.REonlyGallID)
+anova(beta_treatment, glm.beta_treatment)
+```
+
 Discussion
@@
 ==========
+
+```{r Univariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
+## Absolute fitness plots ----
+
+# Get range in relative fitness for accurate scaling across all plots
+AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
+
+# Gall size 
+AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Clutch size
+AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Female preference
+AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.clutch_size) %>%
+  gather(ID, absolute_fitness, -sc.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Get legend
+AF_uni_legend <- get_legend(AF_uni_size)
+
+# Make plots
+AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
+                       AF_uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       AF_uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       labels = "AUTO", ncol = 4, align='hv')
+
+AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
+AF_gradients
+#save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
+#save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
+```
+
+```{r Multivariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
+
+## Absolute fitness landscapes ----
+AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
+          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
+          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+# Size x Preference
+AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Size x Clutch
+AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Clutch x Preference
+AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
+  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
+  AF_plot_size.x.preference + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "AUTO")
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
+```
+
+```{r OLD GAMM comparison, eval=FALSE, include=FALSE}
+gamm_control <- gamm.model(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
+                         sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference, 
+                         data = control_df)
+summary(gamm_control$gam)
+
+gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.clutch_size"), covariates = c("sc.female_preference"), se.method="none")
+gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.female_preference"), covariates = c("sc.clutch_size"), se.method="none")
+gam.gradients(gamm_control$gam, phenotype=c("sc.clutch_size","sc.female_preference"), covariates = c("sc.gall_size"), se.method="none")
+
+AIC(corr_control, gamm_control$mer)
+```
+
+```{r OLD Selection Gradients - Complex Food Web, eval=FALSE, include=FALSE}
+# note that I've switched to using the lme4 package to analyzing the GLMM
+
+# GLMM ----
+glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
+                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
+                         sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = control_df,
+                         family = binomial(link = logit), optimizer = "bobyqa")
+summary(glmer_control)
+
+# Mean fitness ----
+Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+
+# Confidence intervals for selection gradients ----
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+
+## Summary ----
+summary_Beta_glmm_control <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Beta = round(Beta_avg_grad(glmer_control),3),
+  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+summary_Beta_glmm_control
+```

### 2018-07-02 elsevier_test/elsevier_test.tex
updating plots and analyses in ms

@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
+\usepackage{graphicx}
+% We will generate all images so they have a width \maxwidth. This means
+% that they will get their normal width if they fit onto the page, but
+% are scaled down if they would overflow the margins.
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
+\else\Gin@nat@width\fi}
+\makeatother
+\let\Oldincludegraphics\includegraphics
+\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
 \ifxetex
@@
 how evolutionary dynamics unfold in a community context is challenging
-and eminently theoretical (({\textbf{???}}), Nuismer paper, Guimeras
-paper, also McGill paper about biodiversity effects on evolution). Given
-the rapid loss of species diversity we are experiencing throughout the
-world (cite), we are in urgent need of work that makes and tests
-predictions for how the loss of species will affect the evolutionary
-process in natural communities.
+and eminently theoretical (Mcpeek (2017), Mazancourt, Johnson, and
+Barraclough (2008), Guimarães et al. (2017), Nuismer, Jordano, and
+Bascompte (2013)). Given the rapid loss of species diversity we are
+experiencing throughout the world (cite), we are in urgent need of work
+that makes and tests predictions for how the loss of species will affect
+the evolutionary process in natural communities.
 
-Predicting the evolutionary consequences of biodiversity loss first
-requires an understanding of the concommitant change in the network
-structure of species interactions. Knowing the interaction network is
-crucial because the loss of biodiversity, in and of itself, will not
-alter evolution -- it is the associated loss of ecological interactions
-that will affect evolutionary change (Janzen (1974)). For a network of
-directly connected species, we would expect that the loss of species to
-result in a loss of network complexity. Network complexity is a property
-that describes the diversity of interactions in an ecological community
-(Banasek-Richter et al. (2009)). Thus, all else equal, species loss will
-decrease the diversity of interactions, resulting in a more simple
-network.
+Predicting the evolutionary consequences of species loss first requires
+an understanding of the concommitant change in the species-interaction
+networks. Knowing the interaction network is crucial because the loss of
+biodiversity, in and of itself, will not alter evolution -- it is the
+associated loss of ecological interactions that will affect evolutionary
+change (Janzen (1974)). For a network of directly connected species, we
+would expect that the loss of species to result in a loss of network
+complexity. Network complexity is a property that describes the
+diversity of interactions in an ecological community (Banasek-Richter et
+al. (2009)). Thus, all else equal, species loss will decrease the
+diversity of interactions, resulting in a more simple network.
 
@@
 for each gall trait as well as linear interaction terms between each
-gall trait, as fixed effects in the statistical models. To account for
+gall trait as fixed effects in the statistical models. To account for
 the correlated structure of clutch size (gall level) and female
@@
 then used the method of Frederic J Janzen and Hal S Stearn (1998) to
-calculate directional (\(\beta_{z_i}\)), nonlinear (\(\gamma_{z_i}\)),
+calculate directional (\(\beta_{z_i}\)), quadratic (\(\gamma_{z_i}\)),
 and correlational (\(\gamma_{z_i,z_j}\)) selection gradients and used
@@
 simple food web were larger/smaller than in the complex food web
-(i.e.~the p-value). All analyses and visualizations were conducted in R.
+(i.e.~the p-value). All analyses and visualizations were conducted in R
+(R Core Team (2018)).
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{# note that I've switched to using the lme4 package to analyzing the GLMM}
+\begin{verbatim}
+##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
+## 1     Gall diameter  Complex  GLMM Beta    0.555     0.426      0.683
+## 2       Clutch size  Complex  GLMM Beta    0.036    -0.090      0.169
+## 3 Female preference  Complex  GLMM Beta    0.003    -0.185      0.131
+## 4         Gall size   Simple  GLMM Beta    0.289     0.208      0.339
+## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.010
+## 6 Female preference   Simple  GLMM Beta   -0.204    -0.291     -0.097
+\end{verbatim}
 
-\CommentTok{# GLMM ----}
-\NormalTok{glmer_control <-}\StringTok{ }\KeywordTok{glmer}\NormalTok{(gall_survival }\OperatorTok{~}\StringTok{ }\NormalTok{sc.gall_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.female_preference }\OperatorTok{+}
-\StringTok{                         }\KeywordTok{I}\NormalTok{(sc.gall_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.clutch_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.female_preference}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}
-\StringTok{                         }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}
-\StringTok{                           }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{Genotype}\OperatorTok{/}\NormalTok{Plant_Position}\OperatorTok{/}\NormalTok{Gall_Number),}
-                         \DataTypeTok{data =}\NormalTok{ control_df,}
-                         \DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\DataTypeTok{link =}\NormalTok{ logit), }\DataTypeTok{optimizer =} \StringTok{"bobyqa"}\NormalTok{)}
-\CommentTok{# summary(glmer_control)}
+\begin{verbatim}
+##           Phenotype Food_Web Model      Type Estimate lower_2.5 upper_97.5
+## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.084      0.164
+## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.232      0.260
+## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.098      0.154
+## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.104      0.236
+## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.170
+## 6 Female preference   Simple  GLMM Quadratic    0.204     0.078      0.408
+\end{verbatim}
 
-\CommentTok{# Mean fitness ----}
-\NormalTok{Wbar_control <-}\StringTok{ }\KeywordTok{inverse_logit}\NormalTok{(}\KeywordTok{fixef}\NormalTok{(}\KeywordTok{update}\NormalTok{(glmer_control, .}\OperatorTok{~}\NormalTok{.
-}\OperatorTok{-}\NormalTok{sc.gall_size }\OperatorTok{-}\NormalTok{sc.clutch_size }\OperatorTok{-}\NormalTok{sc.female_preference)))}
-
-\CommentTok{# Confidence intervals for selection gradients ----}
-\NormalTok{boot_Beta_control <-}\StringTok{ }\KeywordTok{bootMer}\NormalTok{(glmer_control, }\DataTypeTok{FUN =}\NormalTok{ Beta_avg_grad, }\DataTypeTok{nsim=}\DecValTok{100}\NormalTok{, }\DataTypeTok{parallel=}\StringTok{"multicore"}\NormalTok{, }\DataTypeTok{ncpus=}\DecValTok{32}\NormalTok{)}
-
-\NormalTok{## Summary ----}
-\NormalTok{summary_Beta_glmm_control <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
-  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall size"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
-  \DataTypeTok{Food_Web =} \StringTok{"Complex"}\NormalTok{,}
-  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
-  \DataTypeTok{Beta =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(glmer_control),}\DecValTok{3}\NormalTok{),}
-  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{),}
-  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)) }
-
-\NormalTok{summary_Beta_glmm_control}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\NormalTok{## GLMM ----}
-\NormalTok{glmer_treatment <-}\StringTok{ }\KeywordTok{glmer}\NormalTok{(gall_survival }\OperatorTok{~}\StringTok{ }\NormalTok{sc.gall_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }\NormalTok{sc.female_preference }\OperatorTok{+}
-\StringTok{                         }\KeywordTok{I}\NormalTok{(sc.gall_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.clutch_size}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}\StringTok{ }\KeywordTok{I}\NormalTok{(sc.female_preference}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{+}
-\StringTok{                         }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.clutch_size }\OperatorTok{+}\StringTok{ }
-\StringTok{                          }\NormalTok{sc.gall_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}\StringTok{ }
-\StringTok{                           }\NormalTok{sc.clutch_size}\OperatorTok{:}\NormalTok{sc.female_preference }\OperatorTok{+}
-\StringTok{                           }\NormalTok{(}\DecValTok{1}\OperatorTok{|}\NormalTok{Genotype}\OperatorTok{/}\NormalTok{Plant_Position}\OperatorTok{/}\NormalTok{Gall_Number),}
-                         \DataTypeTok{data =}\NormalTok{ treatment_df,}
-                         \DataTypeTok{family =} \KeywordTok{binomial}\NormalTok{(}\DataTypeTok{link =}\NormalTok{ logit), }\DataTypeTok{optimizer =} \StringTok{"bobyqa"}\NormalTok{)}
-\KeywordTok{summary}\NormalTok{(glmer_treatment)}
-
-\NormalTok{## Mean fitness ----}
-\NormalTok{Wbar_treatment <-}\StringTok{ }\KeywordTok{inverse_logit}\NormalTok{(}\KeywordTok{fixef}\NormalTok{(}\KeywordTok{update}\NormalTok{(glmer_treatment, .}\OperatorTok{~}\NormalTok{.
-}\OperatorTok{-}\NormalTok{sc.gall_size }\OperatorTok{-}\NormalTok{sc.clutch_size }\OperatorTok{-}\NormalTok{sc.female_preference)))}
-
-\NormalTok{## Confidence intervals for selection gradients ----}
-\NormalTok{boot_Beta_treatment <-}\StringTok{ }\KeywordTok{bootMer}\NormalTok{(glmer_treatment, }\DataTypeTok{FUN =}\NormalTok{ Beta_avg_grad, }\DataTypeTok{nsim=}\DecValTok{100}\NormalTok{, }\DataTypeTok{parallel=}\StringTok{"multicore"}\NormalTok{, }\DataTypeTok{ncpus=}\DecValTok{32}\NormalTok{)}
-
-\NormalTok{## Summary ----}
-\NormalTok{summary_Beta_glmm_treatment <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
-  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall size"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
-  \DataTypeTok{Food_Web =} \StringTok{"Simple"}\NormalTok{,}
-  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
-  \DataTypeTok{Beta =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(glmer_treatment),}\DecValTok{2}\NormalTok{),}
-  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{2}\NormalTok{),}
-  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_Beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{2}\NormalTok{)) }
-
-\NormalTok{summary_Beta_glmm_treatment}
-\end{Highlighting}
-\end{Shaded}
+\begin{verbatim}
+##     Phenotype Food_Web Model          Type Estimate lower_2.5 upper_97.5
+## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.145      0.055
+## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.302      0.165
+## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.079      0.120
+## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.161      0.048
+## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.052      0.093
+## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.167      0.085
+\end{verbatim}
 
@@
 
+BREAK UP INTO INDIVIDUAL PIECES: E.G. GALL SIZE. THIS SHOULD BE SMALL
+ENOUGH TO ALLOW CACHING
+
+\includegraphics{elsevier_test_files/figure-latex/Plot Univariate Landscapes-1.pdf}
+
+\includegraphics{elsevier_test_files/figure-latex/Plot Multivariate Fitness Landscape-1.pdf}
+
+\begin{verbatim}
+##              df      AIC
+## beta_control  7 809.1027
+## quad_control 10 814.3022
+## corr_control 13 817.6910
+\end{verbatim}
+
+\begin{verbatim}
+##                  df      AIC
+## beta_control      7 809.1027
+## glm.beta_control  4 881.0152
+\end{verbatim}
+
+\begin{verbatim}
+##                           df      AIC
+## beta_control               7 809.1027
+## beta_control.REonlyGallID  5 816.4817
+\end{verbatim}
+
+\begin{verbatim}
+##       chisq       ratio         rdf           p 
+## 349.7811634   0.5025591 696.0000000   1.0000000
+\end{verbatim}
+
+\begin{verbatim}
+##                df      AIC
+## beta_treatment  7 619.1030
+## quad_treatment 10 620.1640
+## corr_treatment 13 622.3247
+\end{verbatim}
+
+\begin{verbatim}
+##       chisq       ratio         rdf           p 
+## 190.3351784   0.3215121 592.0000000   1.0000000
+\end{verbatim}
+
+\begin{verbatim}
+##                    df      AIC
+## beta_treatment      7 619.1030
+## glm.beta_treatment  4 712.4146
+\end{verbatim}
+
+\begin{verbatim}
+##                             df      AIC
+## beta_treatment               7 619.1030
+## beta_treatment.REonlyGallID  6 669.5617
+\end{verbatim}
+
+\begin{verbatim}
+## Data: treatment_df
+## Models:
+## beta_treatment.REonlyGallID: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
+## beta_treatment.REonlyGallID:     (1 | Genotype/Plant_Position)
+## beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
+## beta_treatment:     (1 | Genotype/Plant_Position/Gall_Number)
+##                             Df    AIC    BIC  logLik deviance  Chisq
+## beta_treatment.REonlyGallID  6 669.56 695.93 -328.78   657.56       
+## beta_treatment               7 619.10 649.87 -302.55   605.10 52.459
+##                             Chi Df Pr(>Chisq)    
+## beta_treatment.REonlyGallID                      
+## beta_treatment                   1  4.394e-13 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+
+\begin{verbatim}
+## Data: treatment_df
+## Models:
+## glm.beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference
+## beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
+## beta_treatment:     (1 | Genotype/Plant_Position/Gall_Number)
+##                    Df    AIC    BIC  logLik deviance  Chisq Chi Df
+## glm.beta_treatment  4 712.41 730.00 -352.21   704.41              
+## beta_treatment      7 619.10 649.87 -302.55   605.10 99.311      3
+##                    Pr(>Chisq)    
+## glm.beta_treatment               
+## beta_treatment      < 2.2e-16 ***
+## ---
+## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
+\end{verbatim}
+
 \section{Discussion}\label{discussion}
@@
 More recently, researchers have begun to explore how the community
-context drives evolutionary change (({\textbf{???}}); terHorst et al.
+context drives evolutionary change (Mcpeek (2017); terHorst et al.
 (2018)).
@@
 \addcontentsline{toc}{section}{References}
+
+\includegraphics{elsevier_test_files/figure-latex/Univariate Absolute Fitness Landscapes-1.pdf}
+
+\includegraphics{elsevier_test_files/figure-latex/Multivariate Absolute Fitness Landscapes-1.pdf}
 
@@
 
+\hypertarget{ref-Guimaraes2017}{}
+Guimarães, Paulo R, Jr, Mathias M Pires, Pedro Jordano, Jordi Bascompte,
+and John N Thompson. 2017. ``Indirect Effects Drive Coevolution in
+Mutualistic Networks.'' \emph{Nature} 550 (7677): 511--14.
+
 \hypertarget{ref-Hawkins1997}{}
@@
 
+\hypertarget{ref-De_Mazancourt2008}{}
+Mazancourt, C de, E Johnson, and T G Barraclough. 2008. ``Biodiversity
+Inhibits Species' Evolutionary Responses to Changing Environments.''
+\emph{Ecol. Lett.} 11 (4): 380--88.
+
+\hypertarget{ref-McPeek2017}{}
+Mcpeek, Mark A. 2017. \emph{Evolutionary Community Ecology}. Princeton
+University Press.
+
+\hypertarget{ref-Nuismer2013}{}
+Nuismer, Scott L, Pedro Jordano, and Jordi Bascompte. 2013.
+``Coevolution and the Architecture of Mutualistic Networks.''
+\emph{Evolution} 67 (2): 338--54.
+
+\hypertarget{ref-R2018}{}
+R Core Team. 2018. \emph{R: A Language and Environment for Statistical
+Computing}. Vienna, Austria: R Foundation for Statistical Computing.
+\url{https://www.R-project.org/}.
+
 \hypertarget{ref-Russo2006}{}

### 2018-07-04 elsevier_test/elsevier_test.Rmd
broke chunks into sizes less than 100 MB. enhanced plot aesthetics.

@@
 n_boots_plots <- 50
+
 ```
@@
 
+```{r Figure 1, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*."}
+knitr::include_graphics("complex_simple_foodwebs_compressed.pdf")
+```
+
 Results
@@
 
-BREAK UP INTO INDIVIDUAL PIECES: E.G. GALL SIZE. THIS SHOULD BE SMALL ENOUGH TO ALLOW CACHING
-
-```{r Get Univariate Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
-## Gall size ----
-
-# Control
+```{r Get Gall Diameter Relative Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
 RF_control_gall_size <- bootstrap_fitness(
@@
      sc.female_preference = 0),
-  bootstraps=100)
-
-# Treatment
+  bootstraps=n_boots_plots)
+
+# Treatment ----
 RF_treatment_gall_size <- bootstrap_fitness(
@@
      sc.female_preference = 0),
-  bootstraps=100)
-
-## Clutch size ----
-
-# Control
+  bootstraps=n_boots_plots)
+```
+
+```{r Get Clutch Size Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
 RF_control_clutch_size <- bootstrap_fitness(
@@
      sc.female_preference = 0),
-  bootstraps=100)
-
-# Treatment 
+  bootstraps=n_boots_plots)
+
+# Treatment ----
 RF_treatment_clutch_size <- bootstrap_fitness(
@@
      sc.female_preference = 0),
-  bootstraps=100)
-
-## Female preference ----
-
-# Control 
+  bootstraps=n_boots_plots)
+```
+
+```{r Get Female Preference Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
 RF_control_female_preference <- bootstrap_fitness(
@@
      sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=100)
-
-# Treatment
+  bootstraps=n_boots_plots)
+
+# Treatment ----
 RF_treatment_female_preference <- bootstrap_fitness(
@@
      sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=100)
-```
-
-```{r Plot Univariate Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
-## Relative fitness plots ----
-
-# Get range in relative fitness for accurate scaling across all plots
+  bootstraps=n_boots_plots)
+
+```
+
+```{r Get Clutch Size x Female Preference Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000), 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment ----
+RF_treatment_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_size.x.clutch <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = seq(-1,1,length.out=1000), 
+     sc.female_preference = 0), 
+  bootstraps=NULL)
+
+# Treatment ----
+RF_treatment_size.x.clutch <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = seq(-1,1,length.out=1000),
+     sc.female_preference = 0), 
+  bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_size.x.preference <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0, 
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment ----
+RF_treatment_size.x.preference <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.clutch_size = 0,
+     sc.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+```
+
+```{r Fitness Landscape Plot Helpers, include=FALSE, cache=TRUE}
+
+## Color palette ----
+
+# order -> orange, light blue, green, yellow, dark blue, red, pink
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
+complex_color <- cbPalette[6]
+simple_color <- cbPalette[5]
+treatment_colors <- c(complex_color, simple_color)
+
+## Scale relative fitness across plots ----
+
+# 1D
 RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
@@
   summarise(min = min(relative_fitness), max = max(relative_fitness))
-RF_gradient_scale <- c(0,0.5,1,1.5,2,2.5) # adjusted based on range
-
-# Color palette: order -> orange, light blue, green, yellow, dark blue, red, pink
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
-complex_color <- cbPalette[6]
-simple_color <- cbPalette[5]
-treatment_colors <- c(complex_color, simple_color)
-
-# Gall size    
+RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
+
+# 2D
+RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
+          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
+          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+## Scale absolute fitness across plots ----
+
+# 1D
+AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
+
+# 2D
+AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
+          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
+          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+```
+
+```{r Plot Univariate Landscapes, include=FALSE, cache=TRUE}
+
+# Gall Diameter ----   
 RF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
@@
   scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SDs)") +
+  xlab("Gall diameter (SD)") +
   ylab("Relative fitness") +
   scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-
-# Clutch size
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)), labels = RF_gradient_scale) +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1))
+
+# Clutch size ----
 RF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
@@
   scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
+  xlab("Clutch size (SD)") +
   ylab("Relative fitness") +
   scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-
-# Female preference 
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)), labels = RF_gradient_scale) +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1))
+
+# Female preference ----
 RF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
@@
   scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
+  xlab("Female preference (SD)") +
   ylab("Relative fitness") +
   scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+  scale_y_continuous(breaks = RF_gradient_scale, limits = c(min(RF_gradient_scale), max(RF_gradient_scale)), labels = RF_gradient_scale) +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1))
+```
+
+```{r Figure 2 Univariate Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients."}
 
@@
 # Make plots
-RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none"), 
+RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none",
+                                              axis.text.x = element_text(size=10),
+                                              axis.title.x = element_text(size=11)), 
                        RF_uni_clutch + theme(legend.position = "none", 
-                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                                          axis.title.y = element_blank(), axis.text.y = element_blank(),
+                                          axis.text.x = element_text(size=10),
+                                          axis.title.x = element_text(size=11)),
                        RF_uni_pref + theme(legend.position = "none", 
-                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       labels = "AUTO", ncol = 4, align='hv')
+                                        axis.title.y = element_blank(), axis.text.y = element_blank(),
+                                        axis.text.x = element_text(size=10),
+                                        axis.title.x = element_text(size=11)),
+                       labels = "AUTO", ncol = 3, align='hv')
 
 RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
-RF_gradients
+#RF_gradients
+RF_uni_plots
 #save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
@@
 
-```{r Get Multivariate Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
-
-## Clutch size x Female preference ----
-
-# Control
-RF_control_clutch.x.preference <- bootstrap_fitness(
-  logistic_model = beta_control, 
-  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.clutch_size = seq(-1,1,length.out=1000), 
-     sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-
-# Treatment
-RF_treatment_clutch.x.preference <- bootstrap_fitness(
-  logistic_model = beta_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.clutch_size = seq(-1,1,length.out=1000),
-     sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-
-## Gall size x Clutch size ----
-
-# Control
-RF_control_size.x.clutch <- bootstrap_fitness(
-  logistic_model = beta_control, 
-  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.clutch_size = seq(-1,1,length.out=1000), 
-     sc.female_preference = 0), 
-  bootstraps=NULL)
-
-# Treatment
-RF_treatment_size.x.clutch <- bootstrap_fitness(
-  logistic_model = beta_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.clutch_size = seq(-1,1,length.out=1000),
-     sc.female_preference = 0), 
-  bootstraps=NULL)
-
-## Gall size x Female preference ----
-
-# Control
-RF_control_size.x.preference <- bootstrap_fitness(
-  logistic_model = beta_control, 
-  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.clutch_size = 0, 
-     sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-
-# Treatment
-RF_treatment_size.x.preference <- bootstrap_fitness(
-  logistic_model = beta_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.clutch_size + sc.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.clutch_size = 0,
-     sc.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-```
-
-```{r Plot Multivariate Fitness Landscape, echo=FALSE, message=FALSE, warning=FALSE}
-
-## Relative fitness plots ----
-
-# Get range in relative fitness for accurate scaling across all plots
-RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
-          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
-          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
-  summarise(min = min(average), max = max(average))
-
-# Clutch x Preference
+---
+
+```{r Plot Multivariate Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Clutch x Preference ----
 RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
@@
   facet_wrap(~Food_Web) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
+  xlab("Female preference (SD)") +
+  ylab("Clutch size (SD)") +
   #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
-
-# Size x Clutch
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
+
+# Size x Clutch ----
 RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
@@
   facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
+  xlab("Gall diameter (SD)") +
+  ylab("Clutch size (SD)") +
   #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
-
-# Size x Preference
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
+
+# Size x Preference ----
 RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
@@
   facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Female preference (SDs)") +
+  xlab("Gall diameter (SD)") +
+  ylab("Female preference (SD)") +
   #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness")
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
+```
+
+```{r Figure 3 Multivariate Landscapes, echo=FALSE, fig.cap="Relative fitness landscapes of gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C).
+Note that traits for all plots range 1 SD below and above the mean (=0)."}
 
 # Get legend
-RF_landscape_legend <- get_legend(RF_plot_size.x.preference)
+RF_landscape_legend <- get_legend((RF_plot_size.x.preference + theme(legend.title = element_text(size=12), legend.text=element_text(size=10))))
 
@@
 RF_landscape_plots <- plot_grid(
-  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
-  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
-  RF_plot_size.x.preference + theme(legend.position = "none"), 
+  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)),
+  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank(), axis.text = element_text(size=9), axis.text.y = element_blank(), axis.title = element_text(size=11), strip.text = element_text(size=11)),
+  RF_plot_size.x.preference + theme(legend.position = "none", axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)), 
   nrow=2, align="hv", labels = "AUTO")
@@
 
+---
+
 ```{r AIC Model Comparison, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}
@@
 ## Absolute fitness plots ----
-
-# Get range in relative fitness for accurate scaling across all plots
-AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
 
@@
   scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+```
+
+```{r Figure S1 Univariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
 
@@
 ```{r Multivariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
-
-## Absolute fitness landscapes ----
-AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
-          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
-          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
-  summarise(min = min(average), max = max(average))
 
@@
   scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-
+```
+
+```{r Figure S2 Multivariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
 # Get legend

### 2018-07-04 elsevier_test/elsevier_test.tex
broke chunks into sizes less than 100 MB. enhanced plot aesthetics.

@@
 ##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
-## 1     Gall diameter  Complex  GLMM Beta    0.555     0.426      0.683
-## 2       Clutch size  Complex  GLMM Beta    0.036    -0.090      0.169
-## 3 Female preference  Complex  GLMM Beta    0.003    -0.185      0.131
-## 4         Gall size   Simple  GLMM Beta    0.289     0.208      0.339
-## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.010
-## 6 Female preference   Simple  GLMM Beta   -0.204    -0.291     -0.097
+## 1     Gall diameter  Complex  GLMM Beta    0.555     0.432      0.642
+## 2       Clutch size  Complex  GLMM Beta    0.036    -0.075      0.177
+## 3 Female preference  Complex  GLMM Beta    0.003    -0.228      0.148
+## 4         Gall size   Simple  GLMM Beta    0.289     0.220      0.357
+## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.001
+## 6 Female preference   Simple  GLMM Beta   -0.204    -0.273     -0.119
 \end{verbatim}
@@
 ##           Phenotype Food_Web Model      Type Estimate lower_2.5 upper_97.5
-## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.084      0.164
-## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.232      0.260
-## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.098      0.154
-## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.104      0.236
-## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.170
-## 6 Female preference   Simple  GLMM Quadratic    0.204     0.078      0.408
+## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.052      0.218
+## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.186      0.254
+## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.078      0.146
+## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.078      0.266
+## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.156
+## 6 Female preference   Simple  GLMM Quadratic    0.204    -0.008      0.446
 \end{verbatim}
@@
 ##     Phenotype Food_Web Model          Type Estimate lower_2.5 upper_97.5
-## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.145      0.055
-## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.302      0.165
-## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.079      0.120
-## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.161      0.048
-## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.052      0.093
-## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.167      0.085
+## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.085      0.076
+## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.274      0.074
+## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.109      0.063
+## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.215      0.029
+## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.064      0.097
+## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.156      0.045
 \end{verbatim}
+
+\begin{figure}[htbp]
+\centering
+\includegraphics{complex_simple_foodwebs_compressed.pdf}
+\caption{Illustrations of complex (A) and simple (B) food webs
+associated with the insect herbivore, \emph{Iteomyia salicisverruca}.}
+\end{figure}
 
@@
 
-BREAK UP INTO INDIVIDUAL PIECES: E.G. GALL SIZE. THIS SHOULD BE SMALL
-ENOUGH TO ALLOW CACHING
+\begin{figure}[htbp]
+\centering
+\includegraphics{elsevier_test_files/figure-latex/Figure 2 Univariate Landscapes-1.pdf}
+\caption{Selection gradients acting on gall traits in complex vs.~simple
+food webs. Each panel corresponds to a different gall trait: gall
+diameter (A); clutch size (B); and female preference (C). Solid lines
+represent the estimated gradients in complex (orange) and simple (blue)
+food webs. Transparent lines represent bootstrapped replicates (n=100)
+to show the uncertainty in estimated gradients.}
+\end{figure}
 
-\includegraphics{elsevier_test_files/figure-latex/Plot Univariate Landscapes-1.pdf}
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
-\includegraphics{elsevier_test_files/figure-latex/Plot Multivariate Fitness Landscape-1.pdf}
+\begin{figure}[htbp]
+\centering
+\includegraphics{elsevier_test_files/figure-latex/Figure 3 Multivariate Landscapes-1.pdf}
+\caption{Relative fitness landscapes of gall traits in complex
+vs.~simple food webs. Each panel corresponds to a different combination
+of traits: clutch size and gall diameter (A); clutch size and female
+preference (B); female preference and gall diameter (C). Note that
+traits for all plots range 1 SD below and above the mean (=0).}
+\end{figure}
+
+\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
 
@@
 
-\includegraphics{elsevier_test_files/figure-latex/Univariate Absolute Fitness Landscapes-1.pdf}
+\includegraphics{elsevier_test_files/figure-latex/Figure S1 Univariate Absolute Fitness Landscapes-1.pdf}
 
-\includegraphics{elsevier_test_files/figure-latex/Multivariate Absolute Fitness Landscapes-1.pdf}
+\includegraphics{elsevier_test_files/figure-latex/Figure S2 Multivariate Absolute Fitness Landscapes-1.pdf}
 

### 2018-07-06 GRC_2018.Rmd
testing reveal.js presentation

--- 2018-06-07 manuscript.Rmd
@@
 ---
-title: "Food-web complexity flattens the fitness landscape of an insect herbivore"
-author: "Matthew A. Barbour"
-date: "6/4/2018"
+title: "From ecosystems to genes: an experimental test of how network structure affects the fitness landscape"
 output: 
-  pdf_document:
-    template: AmNat_MS_template.tex
+  revealjs::revealjs_presentation:
+    theme: white
+    transition: fade
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
-```
+# R Markdown
 
-## R Markdown
-
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
 
 When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
 
-```{r cars}
+## Slide with Bullets
+
+- Bullet 1
+- Bullet 2
+- Bullet 3
+
+## Slide with R Code and Output
+
+```{r}
 summary(cars)
@@
 
-## Including Plots
+## Slide with Plot
 
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r, echo=FALSE}
+plot(cars)
 ```
-
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

### 2018-09-20 assessing viability of species specific responses.Rmd
many many changes

---
title: "playground"
author: "Matt Barbour"
date: "7/22/2018"
output: html_document
---

The abundance of specific parasitoid species was too low to try to tease apart species specific effects on the selection gradients. This was likely due to the less than ideal environment for rearing which made it difficult to determine which parasitoid species were associated with a specific gall, but we could determine whether Platy was because they stayed within the gall and weren't found outside of it.
```{r setup, include=FALSE}

## Load required libraries ----
library(tidyverse)

## Load and manage data ----

gall_selection_ALL.df <- read_csv("gall_selection_data_ALL.csv") %>%
  # convert appropriate variables to characters instead of integers
  mutate(Plant_Position = as.character(Plant_Position),
         Gall_Number = as.character(Gall_Number)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

  # subset data for analysis
  filter(phenology == "early", Location == "tree",
         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) %>%
  mutate(Eulo = eulo.female + eulo.male + exit_none_eulo.female + eulo.us, # no Eulo? only came from unknown galls?
         Meso = exit_none_meso.male + exit_none_meso.female + exit_none_meso.us + meso.female + meso.male + meso.us,
         Tory = exit_none_tory.male + exit_none_tory.female + exit_none_tory.us + tory.female + tory.male + tory.us)

summary(gall_selection_ALL.df)
table(gall_selection_ALL.df$platy)
table(gall_selection_ALL.df$Meso)
table(gall_selection_ALL.df$Tory)
table(gall_selection_ALL.df$ectos)
```

### 2018-09-20 elsevier_test/elsevier_test.Rmd
many many changes

--- 2018-07-01 elsevier_test/elsevier_test.Rmd
@@
 ---
-title: Food-web complexity flattens the fitness landscape of an insect herbivore
+title: Food-web complexity alters the fitness landscape of an insect herbivore
 author:
@@
     email: matthew.barbour@ieu.uzh.ch
-    affiliation: Department of Evolutionary Biology and Environmental Studies, University of Zurich, Zurich, Switzerland
+    affiliation: a,b
     footnote: Corresponding Author
+  - name: Christopher J. Greyson-Gaito
+    affiliation: a,c
+  - name: Arezoo Sootodeh
+    affiliation: a
+  - name: Brendan Locke
+    affiliation: d
   - name: Jordi Bascompte
-    email: jordi.bascompte@ieu.uzh.ch
-    affiliation: Another University
+    affiliation: b
 address:
-  - code: Some Institute of Technology
-    address: Department, Street, City, State, Zip
-  - code: Another University
-    address: Department, Street, City, State, Zip
-abstract: 
-  Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
+  - code: a
+    address: University of British Columbia, Department of Zoology, 6270 University Blvd., Vancouver, BC, V6T 1Z4, Canada
+  - code: b
+    address: University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, Zurich, 8057, Switzerland
+  - code: c
+    address: University of Guelph, Department of Integrative Biology, 50 Stone Rd. East, Guelph, ONT, N1G 2W1, Canada
+  - code: d
+    address: Humboldt State University, Department of Biological Sciences, 1 Harpst St., Arcata, CA, 95521, USA
+abstract: "Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
 Given that     the loss of biodiversity is simplifying the structure of ecological networks, there is a pressing need to answer the question: how does network complexity affect natural selection and the fitness landscape of associated species?
@@
 This occurred because different parasitoid species impose different selection pressures on gall traits, thereby minimizing relative fitness differences among insect galls with different phenotypes.
-Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change.
-Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
+Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change."
+
+bibliography: mybibfile.bib
+output: rticles::elsevier_article
+---
+
+<!-- Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
 Similarly, fitness landscapes provide a mechanistic link between population and evolutionary ecology, as they describe the influence of natural selection on phenotypic variation.
@@
 This occurred because different natural enemies impose different selection pressures on herbivore traits, thereby minimizing relative fitness differences among herbivore phenotypes in the complex network.
-Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change.
-
-bibliography: mybibfile.bib
-output: rticles::elsevier_article
----
-
-_Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_
+Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change.-->
 
@@
 library(cowplot) # pretty default ggplots
-library(broom) # for tidying multiple linear models
+#library(broom) # for tidying multiple linear models
 library(mgcv) # generalized additive models
-library(gamm4) # generalized additive mixed-models
+#library(gamm4) # generalized additive mixed-models
 library(gsg) # calculating selection gradients
-library(visreg)
+#library(visreg)
 library(viridis) # for color palette
+library(lme4) # for generalized linear mixed models
 
@@
   mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)))
-
-# convert treatment to factor to use as 'by' variable in generalized additive models
-gall_selection.df <- gall_selection.df %>%
-  mutate(Treatment_contr.sum=factor(Treatment.focus), 
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
          sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
          sc.clutch_size = as.numeric(scale(gall_individuals)), 
-         sc.female_preference = as.numeric(scale(Density_per_100_shoots)))
-contrasts(gall_selection.df$Treatment_contr.sum) <- 'contr.sum'
+         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
+         sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
+         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
 
@@
 control_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Control") %>%
-  mutate(sc.gall_size = (Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm),
-         sc.clutch_size = (gall_individuals - mean(gall_individuals))/sd(gall_individuals),
-         sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
+  filter(Treatment.focus == "Control") #%>%
+  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
+  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
+  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
+  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
+  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
 
 treatment_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Ectoparasitoid exclusion") %>%
-  mutate(sc.gall_size = (Gall_Height_mm - mean(Gall_Height_mm))/sd(Gall_Height_mm),
-         sc.clutch_size = (gall_individuals - mean(gall_individuals))/sd(gall_individuals),
-         sc.female_preference = (Density_per_100_shoots - mean(Density_per_100_shoots))/sd(Density_per_100_shoots))
+  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
+  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
+  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
+  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
+  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+
+mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.
 
 ## Custom functions to avoid repetitive code ----
-gamm.model <- function(formula, data) {
-  gamm4(formula, data, 
-        random = ~(1|Genotype/Plant_Position/Gall_Number), 
-        family = binomial(link = logit))
-}
 
-gam.plot <- function(gam.model, ...) {
-  plot(gam.model, se = TRUE, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
-}
-
-# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
-# also, using 'refit.smooth = T' also generated some very skewed distributions
-# the recipe below provided the most sensible estimates for my data
-gradient.calc <- function(mod, phenotype, covariates = NULL) {
-  gam.gradients(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32, 
-                refit.smooth = F,
-                n.boot = 1000,
-                se.method = 'boot.para', #'posterior', #'boot.para', #'permute', 'boot.case'#  
-                standardized = T)
-}
-
-insect_FL <- function(mod, phenotype, covariates = NULL) {
-  fitness.landscape(mod, phenotype, covariates, parallel = 'multicore', ncpus = 32,
-                    PI.method = 'boot.para',
-                    refit.smooth = F,
-                    PI.interval = c(0.025,0.975),
-                    plt.density = 100)
-}
-
-get_insect_FL.df <- function(FL){
-  data.frame(mean_fitness = FL$Wbar, FL$points, t(FL$WbarPI)) %>%
-    mutate(lower_2.5 = X2.5., upper_97.5 = X97.5.)
-}
-
+## Test for overdispersion
 overdisp_fun <- function(model) {
@@
 
+## Transform logit to probability
 inverse_logit <- function(x) exp(x)/(1+exp(x))
 
-#Beta_avg_grad <- function(logistic_model, mean_fitness) {
-#  brackets <- predict(logistic_model, type = "response") * (1 - predict(logistic_model, type="response"))
-#  gradient <- mean(brackets) * fixef(logistic_model) / mean_fitness 
-#  return(gradient)
-#}
-
-## Calculate directional selection gradients
-# following method of Janzen and Stern 1998, Evolution
+## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
 Beta_avg_grad <- function(.) {
-  mean_fitness <- inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  mean_fitness <- mean(predict(., type = "response")) #inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
   brackets <- predict(., type = "response") * (1 - predict(., type="response"))
@@
 
+## Calculate intensity/opportunity for selection
+intensity_of_selection <- function(.) {
+  mean_fitness <- mean(predict(., type = "response")) # inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  relative_fitness <- predict(., type = "response") / mean_fitness 
+  var(relative_fitness)
+}
+
 ## Bootstrap fitness estimates
-bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){
-  model_matrix <- model.matrix(~ sc.gall_size + sc.clutch_size + sc.female_preference, newdata)
+bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
+  model_matrix <- model.matrix(formula(fixed_effects), newdata)
 
@@
 }
+
+## Number of bootstrap replicates
+n_boots_analysis <- 1000
+n_boots_plots <- 100
+
 ```
 
-> *There is a much more insidious kind of extinction: the extinction of ecological interactions.* 
-> *(Janzen, D.H. 1974. The deflowering of Central America. Natural History. 83:48–53).*
+AIC comparison suggests gam is better than quadratic approximation; however, I'm worried that the GAM model is overfitting.
+I feel like the quadratic approximation, while not providing the best fit, will still preven the model from overfitting.
+
+Now the question is: normal glm vs. mixed-model? Maybe I need to answer, why not the mixed model?
+
+- There is no theory developed for them. 
+- Relative fitness occurs at different hierarchical levels instead of the level of the sampled population.
+- Less straightforward.
+
+Mixed-models are also good for modeling heterogeneity, but if I'm interested in a general population level, then maybe I don't have to worry about that. 
+```{r GAM, include=F}
+control_gam <- gam(gall_survival ~ s(sc.gall_size) + s(sc.log.clutch_size, k=9) + s(sc.log1p.female_preference), control_df, family=binomial(link=logit))
+plot(control_gam, trans = inverse_logit)
+
+treatment_gam <- gam(gall_survival ~ s(sc.gall_size) + s(sc.log.clutch_size, k=9) + s(sc.log1p.female_preference), treatment_df, family=binomial(link=logit))
+plot(treatment_gam, trans = inverse_logit)
+
+control_gam_quad <- gam(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2), control_df, family=binomial(link=logit))
+
+treatment_gam_quad <- gam(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2), treatment_df, family=binomial(link=logit))
+
+AIC(control_gam, control_gam_quad)
+AIC(treatment_gam, treatment_gam_quad)
+
+hist(gall_selection.df$sc.gall_size)
+hist(gall_selection.df$sc.log.clutch_size)
+hist(gall_selection.df$sc.log1p.female_preference)
+
+control_glm <- glm(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, control_df, family=quasibinomial())#family=binomial(link=logit))
+summary(control_glm)
+visreg::visreg(control_glm, scale = "response")
+
+treatment_glm <- glm(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, treatment_df, family=quasibinomial())#family=binomial(link=logit))
+summary(treatment_glm)
+
+visreg::visreg(control_glm, scale = "response")
+visreg::visreg(treatment_glm, scale = "response")
+
+test_glm <- glm(gall_survival ~ Treatment.focus*(sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference), gall_selection.df, family=quasibinomial())#family=binomial(link=logit))
+summary(test_glm)
+
+visreg::visreg2d(test_glm, xvar="sc.gall_size", yvar="sc.log.clutch_size", scale="response")
+```
+
+```{r, Cryptic effects of parasitism on gall morphology, include=F}
+# how does this analysis compare to Heath?
+# does it make sense to look for the interaction?
+
+control_gall_size <- lmer(sc.gall_size ~ gall_survival +
+                           (1|Genotype:Plant_Position:Gall_Number),
+                         data = control_df)
+summary(control_gall_size)
+visreg::visreg(control_gall_size, xvar="gall_survival")
+
+piecewiseSEM::rsquared(control_gall_size)
+
+flip.control_gall_size <- lmer(gall_survival ~ sc.gall_size +
+                           (1|Genotype:Plant_Position:Gall_Number),
+                         data = control_df)
+summary(flip.control_gall_size)
+visreg::visreg(flip.control_gall_size, xvar="sc.gall_size")
+
+lm.control_gall_size <- lm(Gall_Height_mm ~ gall_survival,
+                         data = control_df)
+summary(lm.control_gall_size)
+visreg::visreg(lm.control_gall_size, xvar="gall_survival")
+
+lmer.control_gall_size <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype:Plant_Position:Gall_Number),
+                         data = control_df)
+summary(lmer.control_gall_size)
+visreg::visreg(lmer.control_gall_size, xvar="gall_survival")
+
+lmer.control_gall_size_2 <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype/Plant_Position/Gall_Number),
+                         data = control_df)
+summary(lmer.control_gall_size_2)
+visreg::visreg(lmer.control_gall_size_2, xvar="gall_survival")
+
+piecewiseSEM::rsquared(flip.control_gall_size)
+
+treatment_gall_size <- lmer(sc.gall_size ~ gall_survival +
+                           (1|Genotype:Plant_Position:Gall_Number),
+                         data = treatment_df)
+summary(treatment_gall_size)
+visreg::visreg(treatment_gall_size, xvar="gall_survival")
+
+lm.treatment_gall_size <- lm(Gall_Height_mm ~ gall_survival,
+                         data = treatment_df)
+summary(lm.treatment_gall_size)
+visreg::visreg(lm.treatment_gall_size, xvar="gall_survival")
+
+lmer.treatment_gall_size <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype:Plant_Position:Gall_Number),
+                         data = treatment_df)
+summary(lmer.treatment_gall_size)
+visreg::visreg(lmer.treatment_gall_size, xvar="gall_survival")
+
+lmer.treatment_gall_size_2 <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype/Plant_Position/Gall_Number),
+                         data = treatment_df)
+summary(lmer.treatment_gall_size_2)
+visreg::visreg(lmer.treatment_gall_size_2, xvar="gall_survival")
+
+piecewiseSEM::rsquared(lmer.treatment_gall_size_2)
+
+lmer.treatment_sc.gall_size_2 <- lmer(sc.gall_size ~ gall_survival + sc.clutch_size + sc.female_preference + (1|Genotype/Plant_Position/Gall_Number),
+                         data = treatment_df)
+summary(lmer.treatment_sc.gall_size_2)
+
+lm.treatment_sc.gall_size <- lm(sc.gall_size ~ gall_survival,
+                         data = treatment_df)
+summary(lm.treatment_sc.gall_size)
+
+summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2), data=treatment_df))
+summary(lmer(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + (1|Genotype/Plant_Position/Gall_Number), data=treatment_df))
+
+summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) , data=control_df))
+summary(lmer(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + (1|Genotype/Plant_Position/Gall_Number), data=control_df))
+
+pair_control <- control_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  group_by(Gall_Number, gall_survival) %>%
+  summarise(mean_gall_size = mean(sc.gall_size)) %>%
+  spread(gall_survival, mean_gall_size) %>%
+  mutate(diff = `1` - `0`)
+summary(pair_control$diff)
+length(pair_control$diff)
+
+t.test(pair_control$`1`, pair_control$`0`, paired = T)
+
+pair_treatment <- treatment_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  group_by(Gall_Number, gall_survival) %>%
+  summarise(mean_gall_size = mean(sc.gall_size)) %>%
+  spread(gall_survival, mean_gall_size) %>%
+  mutate(diff = `1` - `0`)
+summary(pair_treatment$diff)
+length(pair_treatment$diff)
+pair_treatment
+
+t.test(pair_treatment$`1`, pair_treatment$`0`, paired = T)
+
+pair_control_ectos <- control_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(ectos)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  group_by(Gall_Number, gall_survival) %>%
+  summarise(mean_gall_size = mean(sc.gall_size)) %>%
+  spread(gall_survival, mean_gall_size) %>%
+  mutate(diff = `1` - `0`)
+summary(pair_control_ectos$diff)
+length(pair_control_ectos$diff)
+
+t.test(pair_control_ectos$`1`, pair_control_ectos$`0`, paired = T)
+
+pair_control_platy <- control_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(egg_parasitoid)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  group_by(Gall_Number, gall_survival) %>%
+  summarise(mean_gall_size = mean(sc.gall_size)) %>%
+  spread(gall_survival, mean_gall_size) %>%
+  mutate(diff = `1` - `0`)
+summary(pair_control_platy$diff)
+length(pair_control_platy$diff)
+
+t.test(pair_control_platy$`1`, pair_control_platy$`0`, paired = T)
+
+gsg::moments.differentials(z=control_df$sc.gall_size, W = control_df$gall_survival)
+gsg::moments.differentials(z=treatment_df$sc.gall_size, W = treatment_df$gall_survival)
+
+summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size, control_df))
+summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size, treatment_df))
+
+test_control_df <- bind_rows(mutate(control_df, type = 0), mutate(filter(control_df, gall_survival == 1), type = 1))
+summary(lm(sc.gall_size ~ type, test_control_df)) # virtually the same as above
+
+test_treatment_df <- bind_rows(mutate(treatment_df, type = 0), mutate(filter(treatment_df, gall_survival == 1), type = 1))
+summary(lm(sc.gall_size ~ type, test_treatment_df)) # virtually the same as above
+
+# can also look at it this way and just look at the mean difference before and after selection
+test_control_df %>%
+  group_by(type) %>%
+  summarise(mean_gall_size = mean(sc.gall_size))
+
+test_treatment_df %>%
+  group_by(type) %>%
+  summarise(mean_gall_size = mean(sc.gall_size))
+
+# does this enable me to estimate the confounding effect of parasitism on gall size? 
+# Note that the intercept is no longer centered on zero...
+summary(lmer(sc.gall_size ~ type + (1|Genotype/Plant_Position/Gall_Number), test_control_df))
+summary(lmer(sc.gall_size ~ type + (1|Genotype/Plant_Position/Gall_Number), test_treatment_df))
+
+moments_control_df <- control_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  group_by(Gall_Number, gall_survival) %>%
+  summarise(mean_gall_size = mean(sc.gall_size))
+
+gsg::moments.differentials(z=moments_control_df$mean_gall_size, W=moments_control_df$gall_survival) # does this mean anything?
+
+moments_treatment_df <- treatment_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  group_by(Gall_Number, gall_survival) %>%
+  summarise(mean_gall_size = mean(sc.gall_size))
+
+gsg::moments.differentials(z=moments_treatment_df$mean_gall_size, W=moments_treatment_df$gall_survival)
+
+### MOST PROMISING ANALYSIS THUS FAR THAT MAY ENABLE ME TO ASSESS THE BIAS OF PARASITISM ON OBSERVED SELECTION GRADIENTS.
+test_again_control <- control_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
+  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
+  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
+
+hist(test_again_control$diff_gall_size)
+t.test(test_again_control$survive_mean_gall_size, test_again_control$all_mean_gall_size, paired = T)
+
+test_ectos_control <- control_df %>%
+  filter(pupa > 0 | ectos > 0) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
+  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
+  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
+
+hist(test_ectos_control$diff_gall_size)
+t.test(test_ectos_control$survive_mean_gall_size, test_ectos_control$all_mean_gall_size, paired = T)
+
+test_platy_control <- control_df %>%
+  filter(pupa > 0 | egg_parasitoid > 0) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
+  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
+  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
+
+hist(test_platy_control$diff_gall_size)
+t.test(test_platy_control$survive_mean_gall_size, test_platy_control$all_mean_gall_size, paired = T)
+
+test_again_treatment <- treatment_df %>%
+  #filter(gall_individuals==2) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  #filter(mean_survival == 0.5) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
+  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
+  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
+  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
+
+hist(test_again_treatment$diff_gall_size)
+t.test(test_again_treatment$survive_mean_gall_size, test_again_treatment$all_mean_gall_size, paired = T)
+```
+
+```{r Calculate Mean and SD of Gall Traits at Different Scales, include=F, eval=F}
+
+## Calculate mean and SD of gall traits at different scales ----
+summary.individual_level <- gall_selection.df %>%
+  group_by(Treatment.focus) %>%
+  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean, sd), na.rm = TRUE) %>%
+  mutate(Level = "Individual")
+
+mean.gall_size.control <- filter(summary.individual_level, Treatment.focus == "Control")$Gall_Height_mm_mean
+sd.gall_size.control <- filter(summary.individual_level, Treatment.focus == "Control")$Gall_Height_mm_sd
+mean.gall_size.treatment <- filter(summary.individual_level, Treatment.focus == "Ectoparasitoid exclusion")$Gall_Height_mm_mean
+sd.gall_size.treatment <- filter(summary.individual_level, Treatment.focus == "Ectoparasitoid exclusion")$Gall_Height_mm_sd
+
+summary.gall_level <- gall_selection.df %>%
+  group_by(Treatment.focus, Gall_Number) %>%
+  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean), na.rm = TRUE) %>%
+  group_by(Treatment.focus) %>%
+  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean, sd), na.rm = TRUE) %>%
+  mutate(Level = "Gall")
+
+mean.clutch_size.control <- filter(summary.gall_level, Treatment.focus == "Control")$gall_individuals_mean
+sd.clutch_size.control <- filter(summary.gall_level, Treatment.focus == "Control")$gall_individuals_sd
+mean.clutch_size.treatment <- filter(summary.gall_level, Treatment.focus == "Ectoparasitoid exclusion")$gall_individuals_mean
+sd.clutch_size.treatment <- filter(summary.gall_level, Treatment.focus == "Ectoparasitoid exclusion")$gall_individuals_sd
+
+summary.plant_level <- gall_selection.df %>%
+  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean), na.rm = TRUE) %>%
+  group_by(Treatment.focus, Plant_Position) %>%
+  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean), na.rm = TRUE) %>%
+  group_by(Treatment.focus) %>%
+  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean, sd), na.rm = TRUE) %>%
+  mutate(Level = "Plant")
+
+mean.female_preference.control <- filter(summary.plant_level, Treatment.focus == "Control")$Density_per_100_shoots_mean
+sd.female_preference.control <- filter(summary.plant_level, Treatment.focus == "Control")$Density_per_100_shoots_sd
+mean.female_preference.treatment <- filter(summary.plant_level, Treatment.focus == "Ectoparasitoid exclusion")$Density_per_100_shoots_mean
+sd.female_preference.treatment <- filter(summary.plant_level, Treatment.focus == "Ectoparasitoid exclusion")$Density_per_100_shoots_sd
+
+summary.gall_traits <- bind_rows(summary.individual_level, summary.gall_level, summary.plant_level)
+```
+
+<!-- > *There is a much more insidious kind of extinction: the extinction of ecological interactions.* 
+> *(Janzen, D.H. 1974. The deflowering of Central America. Natural History. 83:48–53).* -->
 
@@
 
+<!-- I. Fitness Landscape as a unifying framework for evolution and ecology at the population-level -->
+
+The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
+The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
+Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$.
+In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
+For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
+density-dependence, CITE Foundational and current work).
+In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
+Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
+
+Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
+Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
+This has provided an effective framework for predicting how changes in the biotic environment (e.g.
+density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
+At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
+However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
+Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
+Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
+
+Here, we integrate species-interaction networks and the fitness landscape to empirically test how changes in the biotic environment -- network of species interactions -- affect the dynamics of natural selection.
+Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (*Iteomyia salicisverruca*)(Fig.
+1).
+The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006).
+These galls provide protection from generalist predators (e.g.
+ants, spiders), thus the network of interacting parasitoids provides a realistic representation of the biotic environment this insect herbivore is experiencing.
+Therefore, our manipulation of parasitoid diversity alters the diversity of interactions, or food-web complexity, that this insect herbivore experiences.
+
+<!--Prior work with this study system has shown that there is directional selection for larger galls, likely because larger galls provide a refuge from parasitoid attack (@Barbour2016). 
+However, there is also evidence that each parasitoid species imposes differential selection on gall traits (@Barbour2016).-->
+
+Changes in food-web complexity could influence a resource population's fitness landscape in at least two ways.
+First, if a more diverse community of consumers is more effective at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population.
+A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018).
+On the other hand, if consumers impose different selection pressures on resource traits, then more diverse communities could dampen the strength of selection acting on a given trait.
+This is because a greater diversity in selection pressures is equivalent to greater uncertainty in the selective environment.
+Thus, a more diverse consumer community may relax the net selection pressures acting on resource traits.
+Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the fitness landscape of a resource population.
+
 <!-- I. Evolutionary dynamics in species-rich communities remains unclear, especially in the field -->
 
-Biological diversity -- from genes, to phenotypes, to species -- has and continues to be shaped by the interplay between ecological and evolutionary processes.
+<!-- Biological diversity -- from genes, to phenotypes, to species -- has and continues to be shaped by the interplay between ecological and evolutionary processes.
 <!-- need to improve this instead of just saying its fascinated a small group of people -->
-Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (@Schluter2000), mutualisms (@Jordano1987), and predation (@Abrams2000).
+<!-- Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (@Schluter2000), mutualisms (@Jordano1987), and predation (@Abrams2000).
 While there is clear evidence that pairwise interactions can drive evolution, we also know that most species interact with multiple species in an ecological community.
@@
 <!-- need to make the link to multiple traits and the adaptive landscape here --> <!-- Somthing about the this work remaining eminently theoretical -->
-Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--> is challenging and eminently theoretical (@McPeek2017, Nuismer paper, Guimeras paper, also McGill paper about biodiversity effects on evolution).
+<!-- Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--><!--  is challenging and eminently theoretical (@McPeek2017, @De_Mazancourt2008, @Guimaraes2017, @Nuismer2013).
 <!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
 I think it would be useful to show that there is some field and lab experiments demonstrating that community context can alter evolutionary trajectories -->
-Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
+<!-- Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
 
@@
 These 128 plants came from eight different plant genotypes, spanning the range of trait variation observed in this willow population (@Barbour2015). 
-On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
+On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
 This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
@@
 
-To characterize the shape of the fitness landscape, we quantified selection gradients acting on each trait in simple vs.
-complex food webs.
-We did this by fitting separate statistical models to data from each food-web treatment.
+To characterize the shape of the fitness landscape in simple and complex food webs, we fit separate statistical models to quantify individual selection surfaces acting on each trait. 
 We used generalized linear mixed models (GLMMs, @Bolker2009) with larval survival (0 or 1) as our response variable and measure of fitness. 
-We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait, as fixed effects in the statistical models.
+In our full model, we specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models. 
 To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
@@
 setting them to zero) to estimate selection gradients.
-We then used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), nonlinear ($\gamma_{z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
+We then used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
+We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
 To test whether selection gradients differed between treatments, we used our bootstrapped estimates to calculate the probability that selection gradients in the simple food web were larger/smaller than in the complex food web (i.e.
 the p-value).
-All analyses and visualizations were conducted in R.
+Together, we had survival estimates for 1,306 larva, 607 galls, 111 plants, and 8 plant genotypes.
+We report estimated selection gradients and the 95% confidence intervals in parentheses.
+All analyses and visualizations were conducted in R (@R2018).
 
-```{r Selection Gradients - Complex Food Web, cache=TRUE, eval=FALSE}
+```{r Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
 # note that I've switched to using the lme4 package to analyzing the GLMM
 
-# GLMM ----
-glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
-                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
-                         sc.gall_size:sc.clutch_size + sc.gall_size:sc.female_preference + sc.clutch_size:sc.female_preference +
+# Directional selection ----
+beta_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
                            (1|Genotype/Plant_Position/Gall_Number),
                          data = control_df,
-                         family = binomial(link = logit), optimizer = "bobyqa")
-# summary(glmer_control)
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+summary(beta_control)
+overdisp_fun(beta_control)
+
+intensity_of_selection(beta_control)
+
+# Quadratic selection ----
+quad_control <- update(beta_control, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
+
+summary(quad_control)
+overdisp_fun(quad_control)
+
+# Correlational selection ----
+corr_control <- update(quad_control, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
+
+summary(corr_control)
+overdisp_fun(corr_control)
 
 # Mean fitness ----
-Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+Wbar_control <- inverse_logit(fixef(update(beta_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
 
-# Confidence intervals for selection gradients ----
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+# Confidence intervals ----
+boot_beta_control <- bootMer(beta_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_quad_control <- bootMer(quad_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_corr_control <- bootMer(corr_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
 
-## Summary ----
-summary_Beta_glmm_control <- data.frame(
-  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+```{r Selection Gradients - Simple Food Web, cache=TRUE, include=FALSE}
+
+# Directional selection ----
+beta_treatment <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = treatment_df,
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+summary(beta_treatment)
+overdisp_fun(beta_treatment)
+
+intensity_of_selection(beta_treatment)
+
+# Quadratic selection ----
+quad_treatment <- update(beta_treatment, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
+
+summary(quad_treatment)
+overdisp_fun(quad_treatment)
+
+# Correlational selection ----
+corr_treatment <- update(quad_treatment, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
+
+summary(corr_treatment)
+overdisp_fun(corr_treatment)
+
+# Mean fitness ----
+Wbar_treatment <- inverse_logit(fixef(update(beta_treatment, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
+
+# Confidence intervals ----
+boot_beta_treatment <- bootMer(beta_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_quad_treatment <- bootMer(quad_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_corr_treatment <- bootMer(corr_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Larval Parasitoids Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
+# note that I've switched to using the lme4 package to analyzing the GLMM
+
+ectoptoid_control_df <- filter(control_df,  ectos > 0 | pupa > 0) %>%
+  mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)),
+         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))),
+         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+
+# Directional selection ----
+beta_ectoptoid_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = ectoptoid_control_df,
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+summary(beta_ectoptoid_control)
+overdisp_fun(beta_ectoptoid_control)
+
+intensity_of_selection(beta_ectoptoid_control)
+
+#vcov.merMod(beta_ectoptoid_control)
+
+# Quadratic selection ----
+quad_ectoptoid_control <- update(beta_ectoptoid_control, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
+
+summary(quad_ectoptoid_control)
+overdisp_fun(quad_ectoptoid_control)
+
+# Correlational selection ----
+corr_ectoptoid_control <- update(quad_ectoptoid_control, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
+
+summary(corr_ectoptoid_control)
+overdisp_fun(corr_ectoptoid_control)
+
+# Mean fitness ----
+Wbar_ectoptoid_control <- inverse_logit(fixef(update(beta_ectoptoid_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
+
+# Confidence intervals ----
+boot_beta_ectoptoid_control <- bootMer(beta_ectoptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_quad_ectoptoid_control <- bootMer(quad_ectoptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_corr_ectoptoid_control <- bootMer(corr_ectoptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Egg Parasitoids Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
+# note that I've switched to using the lme4 package to analyzing the GLMM
+
+eggptoid_control_df <- filter(control_df,  platy > 0 | pupa > 0) %>%
+  mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)),
+         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))),
+         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+
+# Directional selection ----
+beta_eggptoid_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = eggptoid_control_df,
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+summary(beta_eggptoid_control)
+overdisp_fun(beta_eggptoid_control)
+
+intensity_of_selection(beta_eggptoid_control)
+
+#vcov.merMod(beta_eggptoid_control)
+
+# Quadratic selection ----
+quad_eggptoid_control <- update(beta_eggptoid_control, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
+
+summary(quad_eggptoid_control)
+overdisp_fun(quad_eggptoid_control)
+
+# Correlational selection ----
+corr_eggptoid_control <- update(quad_eggptoid_control, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
+
+summary(corr_eggptoid_control)
+overdisp_fun(corr_eggptoid_control)
+
+# Mean fitness ----
+Wbar_eggptoid_control <- inverse_logit(fixef(update(beta_eggptoid_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
+
+# Confidence intervals ----
+boot_beta_eggptoid_control <- bootMer(beta_eggptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_quad_eggptoid_control <- bootMer(quad_eggptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_corr_eggptoid_control <- bootMer(corr_eggptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Mortality, include=F}
+# 8-10% mortality induced by intraguild predators
+mean(control_df$platy)
+mean(treatment_df$platy)
+mean(eggptoid_control_df$platy)
+
+# Gall mortality to Platy
+1 - mean(treatment_df$pupa)
+
+# Gall mortality to Ectos
+
+# Platy mortality to intraguild predation
+mean(treatment_df$platy) - mean(control_df$platy)
+
+mean(control_df$ectos)
+mean(treatment_df$ectos)
+mean(ectoptoid_control_df$ectos)
+
+mean(control_df$pupa)
+mean(treatment_df$pupa)
+mean(eggptoid_control_df$pupa)
+mean(ectoptoid_control_df$pupa)
+```
+
+```{r Partition Selection Gradients in Complex Food Web, include=F}
+summary_beta_treatment <- data.frame(
+  Ptoids = "All",
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_treatment),3),
+  lower_2.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+summary_beta_control <- data.frame(
+  Ptoids = "All",
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
   Food_Web = "Complex",
   Model = "GLMM",
-  Beta = round(Beta_avg_grad(glmer_control),3),
-  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_control),3),
+  lower_2.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
 
-summary_Beta_glmm_control
+summary_beta_ectoptoid_control <- data.frame(
+  Ptoids = "Ectos",
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_ectoptoid_control),3),
+  lower_2.5 = round(apply(boot_beta_ectoptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_ectoptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+summary_beta_eggtpoid_control <- data.frame(
+  Ptoids = "Egg",
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_eggptoid_control),3),
+  lower_2.5 = round(apply(boot_beta_eggptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_eggptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+bind_rows(summary_beta_treatment, summary_beta_control, summary_beta_ectoptoid_control, summary_beta_eggtpoid_control) %>%
+  arrange(Phenotype)
 ```
 
-```{r Selection Gradients - Simple Food Web, cache=TRUE, eval=FALSE}
+```{r include=FALSE}
+mean_log1p <- function(x) mean(log1p(x), na.rm=T)
+sd_na.rm <- function(x) sd(log1p(x), na.rm=T)
 
-## GLMM ----
-glmer_treatment <- glmer(gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference +
-                         I(sc.gall_size^2) + I(sc.clutch_size^2) + I(sc.female_preference^2) +
-                         sc.gall_size:sc.clutch_size + 
-                          sc.gall_size:sc.female_preference + 
-                           sc.clutch_size:sc.female_preference +
-                           (1|Genotype/Plant_Position/Gall_Number),
-                         data = treatment_df,
-                         family = binomial(link = logit), optimizer = "bobyqa")
-summary(glmer_treatment)
+## Platygaster
+platy_trait_control <- filter(control_df, platy > 0) %>%
+  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
 
-## Mean fitness ----
-Wbar_treatment <- inverse_logit(fixef(update(glmer_treatment, .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+platy_trait_treatmeant <- filter(treatment_df, platy > 0) %>%
+  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
 
-## Confidence intervals for selection gradients ----
-boot_Beta_treatment <- bootMer(glmer_treatment, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+bind_rows(platy_trait_control, platy_trait_treatmeant)
 
-## Summary ----
-summary_Beta_glmm_treatment <- data.frame(
-  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+(platy_trait_treatmeant$Gall_Height_mm_mean_log1p - platy_trait_control$Gall_Height_mm_mean_log1p)/platy_trait_control$Gall_Height_mm_sd_na.rm
+
+(platy_trait_treatmeant$gall_individuals_mean_log1p - platy_trait_control$gall_individuals_mean_log1p)/platy_trait_control$gall_individuals_sd_na.rm
+
+(platy_trait_treatmeant$Density_per_100_shoots_mean_log1p - platy_trait_control$Density_per_100_shoots_mean_log1p)/platy_trait_control$Density_per_100_shoots_sd_na.rm
+
+## Pupa
+pupa_trait_control <- filter(control_df, pupa > 0) %>%
+  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
+
+pupa_trait_treatmeant <- filter(treatment_df, pupa > 0) %>%
+  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
+
+bind_rows(pupa_trait_control, pupa_trait_treatmeant)
+
+(pupa_trait_treatmeant$Gall_Height_mm_mean_log1p - pupa_trait_control$Gall_Height_mm_mean_log1p)/pupa_trait_control$Gall_Height_mm_sd_na.rm
+
+(pupa_trait_treatmeant$gall_individuals_mean_log1p - pupa_trait_control$gall_individuals_mean_log1p)/pupa_trait_control$gall_individuals_sd_na.rm
+
+(pupa_trait_treatmeant$Density_per_100_shoots_mean_log1p - pupa_trait_control$Density_per_100_shoots_mean_log1p)/pupa_trait_control$Density_per_100_shoots_sd_na.rm
+```
+
+```{r Table of Selection Gradients}
+
+## Summarize Control Selection Gradients ----
+summary_beta_control <- data.frame(
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_control),3),
+  lower_2.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)
+summary_quad_control <- data.frame(
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Quadratic",
+  Estimate = 2*round(Beta_avg_grad(quad_control),3)[-c(1:3)],
+  lower_2.5 = 2*round(apply(boot_quad_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:3)],
+  upper_97.5 = 2*round(apply(boot_quad_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:3)])
+
+summary_corr_control <- data.frame(
+  Phenotype = c("Diam,Clutch", "Diam,Pref", "Clutch,Pref"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Type = "Correlational",
+  Estimate = round(Beta_avg_grad(corr_control),3)[-c(1:6)],
+  lower_2.5 = round(apply(boot_corr_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:6)],
+  upper_97.5 = round(apply(boot_corr_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:6)])
+
+## Summarize Treatment Selection Gradients ----
+summary_beta_treatment <- data.frame(
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
   Food_Web = "Simple",
   Model = "GLMM",
-  Beta = round(Beta_avg_grad(glmer_treatment),2),
-  lower_2.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),2),
-  upper_97.5 = round(apply(boot_Beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),2))
+  Type = "Beta",
+  Estimate = round(Beta_avg_grad(beta_treatment),3),
+  lower_2.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
 
-summary_Beta_glmm_treatment
+# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)
+summary_quad_treatment <- data.frame(
+  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Type = "Quadratic",
+  Estimate = 2*round(Beta_avg_grad(quad_treatment),3)[-c(1:3)],
+  lower_2.5 = 2*round(apply(boot_quad_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:3)],
+  upper_97.5 = 2*round(apply(boot_quad_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:3)])
+
+summary_corr_treatment <- data.frame(
+  Phenotype = c("Diam,Clutch", "Diam,Pref", "Clutch,Pref"),
+  Food_Web = "Simple",
+  Model = "GLMM",
+  Type = "Correlational",
+  Estimate = round(Beta_avg_grad(corr_treatment),3)[-c(1:6)],
+  lower_2.5 = round(apply(boot_corr_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:6)],
+  upper_97.5 = round(apply(boot_corr_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:6)])
+
+bind_rows(summary_beta_control, summary_beta_treatment) %>% arrange(Phenotype)
+bind_rows(summary_quad_control, summary_quad_treatment) %>% arrange(Phenotype)
+bind_rows(summary_corr_control, summary_corr_treatment) %>% arrange(Phenotype)
 ```
@@
 
+```{r Figure 1, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
+Black arrows denote 'who-eats-whom' in this network of trophic interactions."}
+knitr::include_graphics("complex_simple_foodwebs_compressed.pdf")
+```
+
 Results
@@
 Perhaps it would also be good to measure to calculate the selection gradient observed on each plant -->
+Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
+In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$ 
+`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`
+; simple $\beta_{diam}=$
+`r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`
+)(Fig. \ref{fig:Univariate_Landscapes}A). 
+In simple food webs, both clutch size and female preference experience directional selection, with smaller clutch sizes ($\beta_{clutch}=$
+`r paste0(filter(summary_beta_treatment, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Clutch size")$upper_97.5,"]")`
+and weaker preferences ($\beta_{pref}=$
+`r paste0(filter(summary_beta_treatment, Phenotype=="Female preference")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Female preference")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Female preference")$upper_97.5,"]")`
+) resulting in higher larval survival (blue lines in Fig. \ref{fig:Univariate_Landscapes}B,C).
+In contrast, there was no evidence of selection on clutch size ($\beta_{clutch}=$
+`r paste0(filter(summary_beta_control, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_control, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Clutch size")$upper_97.5,"]")`
+) or female preference ($\beta_{pref}=$
+`r paste0(filter(summary_beta_control, Phenotype=="Female preference")$Estimate," [",filter(summary_beta_control, Phenotype=="Female preference")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Female preference")$upper_97.5,"]")`
+) in complex food webs (orange lines in Fig.
+\ref{fig:Univariate_Landscapes}B,C).
+The absence of selection on clutch size and female preference was likely a result of conflicting selection pressures imposed by each guild of parasitoids due to their different functional relationships with gall traits.
+Together, these different patterns of selection resulted in an ideal combination of traits having higher fitness in the simple food web (large diameter, smaller clutches, weaker preference), whereas there was a larger combination of trait values that had equal fitness in the complex food web (Fig.
+\ref{fig:Multivariate_Landscapes}).
+We did not find any strong evidence for nonlinear or correlational selection gradients acting on gall traits in either food-web treatment.
+The second major pattern was that the overall intensity of selection was stronger in the complex vs.
+simple food web.
+This result appeared to be driven by selection on gall diameter in the complex food web, which was more than
+`r round(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate/filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate,1)`
+$\times$ larger than any other selection gradient in our analyses.
 
-We found that more phenotypic traits were under selection in the simple vs. complex food web. 
-In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex Beta = ; simple Beta = )(Fig. 2A). 
-In complex food webs, there was no evidence of selection on clutch size ($\beta_{clutch}=$) or female preference ($\beta_{preference}=$)(orange lines in Fig. 2B,C). 
-In simple food webs, however, clutch size and female preference were under strong directional selection, with smaller clutch sizes and weaker preferences resulting in higher larval survival (blue lines in Fig.
-2B,C).
-These different selection pressures resulted in different adaptive landscapes in complex vs.
-simple food webs, with evidence for more rugged landscapes in the simple rather than the complex food web (Fig.
-3).
-Depending on the trait combinations used to create the landscape, we found that the ruggedness of the adaptive landscape ranged from 10\% higher (Fig.
-3A) to 274\% higher (Fig.
-3C) in the simple vs.
-complex food web.
-Our model comparison suggested that it was unnecessary to test for the effects of non-linear or correlational selection gradients (ref. supp. mat.).
+```{r Get Gall Diameter Relative Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_gall_size <- bootstrap_fitness(
+  logistic_model = quad_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000), 
+     sc.log.clutch_size = 0,
+     sc.log1p.female_preference = 0),
+  bootstraps=n_boots_plots)
+
+# Treatment ----
+RF_treatment_gall_size <- bootstrap_fitness(
+  logistic_model = quad_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.log.clutch_size = 0,
+     sc.log1p.female_preference = 0),
+  bootstraps=n_boots_plots)
+```
+
+```{r Get Clutch Size Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_clutch_size <- bootstrap_fitness(
+  logistic_model = quad_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.log.clutch_size = seq(-1,1,length.out=1000),
+     sc.log1p.female_preference = 0),
+  bootstraps=n_boots_plots)
+
+# Treatment ----
+RF_treatment_clutch_size <- bootstrap_fitness(
+  logistic_model = quad_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.log.clutch_size = seq(-1,1,length.out=1000),
+     sc.log1p.female_preference = 0),
+  bootstraps=n_boots_plots)
+```
+
+```{r Get Female Preference Fitness Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_female_preference <- bootstrap_fitness(
+  logistic_model = quad_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.log.clutch_size = 0, 
+     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=n_boots_plots)
+
+# Treatment ----
+RF_treatment_female_preference <- bootstrap_fitness(
+  logistic_model = quad_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.log.clutch_size = 0,
+     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=n_boots_plots)
+
+```
+
+```{r Get Clutch Size x Female Preference Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = corr_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.log.clutch_size = seq(-1,1,length.out=1000), 
+     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment ----
+RF_treatment_clutch.x.preference <- bootstrap_fitness(
+  logistic_model = corr_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = 0,
+     sc.log.clutch_size = seq(-1,1,length.out=1000),
+     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_size.x.clutch <- bootstrap_fitness(
+  logistic_model = corr_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.log.clutch_size = seq(-1,1,length.out=1000), 
+     sc.log1p.female_preference = 0), 
+  bootstraps=NULL)
+
+# Treatment ----
+RF_treatment_size.x.clutch <- bootstrap_fitness(
+  logistic_model = corr_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.log.clutch_size = seq(-1,1,length.out=1000),
+     sc.log1p.female_preference = 0), 
+  bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, cache=TRUE}
+
+# Control ----
+RF_control_size.x.preference <- bootstrap_fitness(
+  logistic_model = corr_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.log.clutch_size = 0, 
+     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+
+# Treatment ----
+RF_treatment_size.x.preference <- bootstrap_fitness(
+  logistic_model = corr_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=1000),
+     sc.log.clutch_size = 0,
+     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  bootstraps=NULL)
+```
+
+```{r Fitness Landscape Plot Helpers, include=FALSE, cache=TRUE}
+
+## Color palette ----
+
+# order -> orange, light blue, green, yellow, dark blue, red, pink
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
+complex_color <- cbPalette[6] # 1
+simple_color <- cbPalette[5] # 2
+treatment_colors <- c(complex_color, simple_color)
+
+## Scale relative fitness across plots ----
+
+# 1D
+RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
+          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
+          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
+  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
+  gather(ID, relative_fitness, -sc.gall_size) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  summarise(min = min(relative_fitness), max = max(relative_fitness))
+RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
+
+# 2D
+RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
+          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
+          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+## Scale absolute fitness across plots ----
+
+# 1D
+AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
+
+# 2D
+AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
+          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
+          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+```
+
+```{r Plot Univariate Landscapes, include=FALSE, cache=TRUE}
+uni_breaks <- c(0.1,0.5,1)
+
+# Gall size 
+AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Population mean fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+#AF_uni_size
+  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
+
+# Clutch size
+AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.log1p.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.log.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Population mean fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
+
+# Female preference
+AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.log.clutch_size) %>%
+  gather(ID, absolute_fitness, -sc.log1p.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log1p.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Population mean fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
+```
+
+```{r Univariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
+Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
+
+# Get legend
+AF_uni_legend <- get_legend(AF_uni_size)
+
+# Make plots
+AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none", 
+                                              axis.text.x = element_text(size=10),
+                                              axis.title.x = element_text(size=11)), 
+                       AF_uni_clutch + theme(legend.position = "none",
+                                             axis.title.y = element_blank(), 
+                                             axis.text.y = element_blank(),
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                       AF_uni_pref + theme(legend.position = "none", 
+                                           axis.title.y = element_blank(), 
+                                           axis.text.y = element_blank(), 
+                                           axis.text.x = element_text(size=10),
+                                           axis.title.x = element_text(size=11)),
+                       labels = "AUTO", ncol = 3, align='hv')
+
+AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
+AF_gradients
+#AF_uni_plots
+# save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
+```
+
+```{r Plot Multivariate Fitness Landscape, include=FALSE, cache=TRUE}
+
+my_breaks <- c(0.2,0.4,0.6,0.8)
+
+# Size x Preference
+AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
+
+# Size x Clutch
+AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
+
+# Clutch x Preference
+AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max), 
+```
+
+```{r Multivariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C).
+Note that traits for all plots range 1 SD below and above the mean (=0)."}
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
+  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
+  AF_plot_size.x.preference + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "AUTO")
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
+```
+
+```{r AIC Model Comparison, include=FALSE, cache=TRUE}
+
+# Control ----
+AIC(beta_control, quad_control, corr_control)
+
+glm.beta_control <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=control_df, family=binomial(link=logit))
+
+beta_control.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                                   (1|Gall_Number),
+                                 data = control_df,
+                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+AIC(beta_control, glm.beta_control)
+AIC(beta_control, beta_control.REonlyGallID)
+overdisp_fun(beta_control)
+
+# Treatment ----
+AIC(beta_treatment, quad_treatment, corr_treatment)
+
+glm.beta_treatment <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=treatment_df, family=binomial(link=logit))
+
+beta_treatment.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                                   (1|Genotype/Plant_Position),
+                                 data = treatment_df,
+                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+overdisp_fun(beta_treatment)
+
+AIC(beta_treatment, glm.beta_treatment)
+AIC(beta_treatment, beta_treatment.REonlyGallID)
+anova(beta_treatment, beta_treatment.REonlyGallID)
+anova(beta_treatment, glm.beta_treatment)
+```
 
@@
 
-<!-- Feedbacks between biological diversity and evolutionary change -->
+<!-- Summary -->
+
+Our key finding was that the adaptive landscape was less constrained in the complex vs.
+simple food web.
+These fewer constraints arise from conflicting selection pressures imposed by different parasitoid guilds, resulting in fewer traits under selection in the complex food web.
+At the same time, we observed an overall greater intensity of selection in the complex food web, suggesting that trait evolution can be faster in complex vs.
+simple food webs.
+Our observation that natural selection was more constrained and less intense in simple vs.
+complex food webs suggests that the loss of biodiversity could constrain the adaptive potential of interacting species by reducing genetic and phenotypic variation in multiple traits.
+
+<!-- Selective constraints result -->
+
+Current theory suggests that when the number of selective constrains is less than the number of genetic constraints (i.e.
+some genetically variable traits are selective neutral), there are multiple positions on the landscape that confer equal fitness (Lande 1981; Lande and Arnold 1985).
+In this scenario, trait differences between populations may simply be due to neutral processes (e.g.
+genetic drift and mutation) moving trait values of the population.
+For our system, we currently lack quantitative estimates of genetic variation in our traits, although work with other species of galling insects has shown that gall diameter (Abramhson, Heath's work), clutch size (look to Weiss' work), and oviposition preference (Abrahmson's work?) are genetically variable.
+We encourage others to examine how changes in community context will alter selection on multiple traits.
+
+<!-- Intensity of selection result -->
+
+One interesting result of our work was that the overall intensity of selection appeared to be larger in complex food webs.
+This result was driven by the large selection gradient acting on gall diameter in complex vs.
+simple food webs.
+This difference in selection intensity is likely not driven by a difference in the ecological relationship between gall diameter and parasitoid attack (i.e.
+slope), but actually a result of the lower mean fitness of *Iteomyia* in the complex food web.
+This lower mean fitness is not surprising ---we excluded an entire guild of parasitoids from attacking the insect.
+But this more intense selection pressure may simply represent a transient dynamic.
+This is because we would expect the egg-parasitoid *Platygaster* to increase in abundance over time once its intraguild predator has been removed.
+While our results suggest that this wouldn't affect the slope of the relationship, the higher abundance of the egg parasitoid would likely reduce the mean fitness of *Iteomyia*, thus increasing the selection gradient acting on gall diameter closer to what we observed in the complex food web.
+We don't expect it to fully compensate, given that the larval parasitoids exhibit a different functional relationship with gall traits, and thus we expect a more diverse community of primary parasitoids to generally impose greater parasitism pressure, a factor that appears to be a general trend in parasitoid community (Hawkins citation) and likely for other consumers (Ives and Cardinale Ecology Letters).
+
+<!-- Quantifying indirect effects of food-web complexity -->
+
+Our study focused on quantifying the direct effects of changes in network complexity on the fitness landscape; however, changes in network complexity may have pervasive indirect effects via coevolution or by initiating evolutionary cascades.
+In our system, we observed that excluding the guild of larval parasitoids altered selection on both the basal resource (*Iteomyia*) and the intraguild prey (*Platygaster*).
+GIVE DETAILS AND SUGGEST A POTENTIAL EVOLUTIONARY CASCADE.
+
+<!-- Generality of effects of food-web complexity -->
+
+Our study manipulated food-web complexity and examined changes in the fitness landscape of species embedded within this network.
+However, other studies have also examined, at least theoretically, how changes in the diversity of competitive communities affects evolution.
+These studies have generally suggested that the diversity of competitors may actually constrain the adaptive landscape, a finding that stands in contrast to our results.
+NEED TO REVIEW THESE PAPERS TO SEE HOW ITS DIFFERENT.
+
+<!-- Conclusion -->
+
+We suggest that by explicitly focusing on network structure, we can predict how changes in biodiversity will affect the adaptive potential of constituent species.
+A network allows a powerful representation of the 'community context', lending predictive power to how changes in network structure (either due to loss of species or links), will alter natural selection and consequently evolutionary change.
+Our results also suggest that losing biodiversity may not just have consequences at the community level, but also population-level consequences that may actually constrain adaptation to changing environments.
+This argues that changes in network complexity may not only affect the robustness of communities, but also that of constituent populations to future environmental change.
+
+<!-- 
+From Arnold Am Nat 1992 Constrains on phenotypic evolution
+ Evolutionary models with constant adaptive landscapes and G-matrices pro-
+ vide some generalizations about the effects of selective constraints. First, the
+ phenotypic mean of the population tends to evolve in an uphill direction on the
+ adaptive landscape (Lande 1979). When selection is frequency-independent and
+ the landscape is Gaussian, the population mean equilibrates on an adaptive peak.
+ Burger (1986), however, modeled evolution on a landscape that was an ascending
+ ridge with increasingly steep flanks. He found that the population would equili-
+ brate on the ridge crest when stabilizing selection reached a critical level. Second,
+ frequency-dependent selection generally causes the population to equilibrate
+ some distance downslope from an adaptive peak (Lande 1976b, 1980b). Finally,
+ when the number of selective constraints is less than the number of genetic con-
+ straints so that some genetically variable traits are selectively neutral, there is a
+ collection of possible equilibrium points (a line, plane, or hyperplane) rather than
+ a single equilibrium point (Lande 1981; Lande and Arnold 1985). In the case of
+ mating preferences and sexually selected traits, for example, the evolutionary
+ outcome is changed dramatically depending on whether selection acts on mating
+ preferences (Arnold 1987; Pomiankowski et al. 1991).
+
+I. Feedbacks between biological diversity and evolutionary change
 
@@
 Here are two sample references: @Feynman1963118 [@Dirac1953888].
+-->
 
@@
 ==========
+
+```{r Univariate Absolute Fitness Landscapes, include=FALSE}
+## Absolute fitness plots ----
+
+# Gall size 
+AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Clutch size
+AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.log1p.female_preference) %>%
+  gather(ID, absolute_fitness, -sc.log.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+
+# Female preference
+AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.log.clutch_size) %>%
+  gather(ID, absolute_fitness, -sc.log1p.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log1p.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Absolute fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
+```
+
+```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE}
+
+# Get legend
+AF_uni_legend <- get_legend(AF_uni_size)
+
+# Make plots
+AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
+                       AF_uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       AF_uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
+                       labels = "AUTO", ncol = 4, align='hv')
+
+AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
+AF_gradients
+#save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
+#save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
+```
+
+```{r Multivariate Absolute Fitness Landscapes, include=FALSE}
+
+# Size x Preference
+AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Size x Clutch
+AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+
+# Clutch x Preference
+AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
+```
+
+```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE}
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
+  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
+  AF_plot_size.x.preference + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "AUTO")
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
+```
+
+```{r OLD GAMM comparison, eval=FALSE, include=FALSE}
+gamm_control <- gamm.model(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, 
+                         data = control_df)
+summary(gamm_control$gam)
+
+gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log.clutch_size"), covariates = c("sc.log1p.female_preference"), se.method="none")
+gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log1p.female_preference"), covariates = c("sc.log.clutch_size"), se.method="none")
+gam.gradients(gamm_control$gam, phenotype=c("sc.log.clutch_size","sc.log1p.female_preference"), covariates = c("sc.gall_size"), se.method="none")
+
+AIC(corr_control, gamm_control$mer)
+```
+
+```{r OLD Selection Gradients - Complex Food Web, eval=FALSE, include=FALSE}
+# note that I've switched to using the lme4 package to analyzing the GLMM
+
+# GLMM ----
+glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = control_df,
+                         family = binomial(link = logit), optimizer = "bobyqa")
+summary(glmer_control)
+
+# Mean fitness ----
+Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
+
+# Confidence intervals for selection gradients ----
+boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
+
+## Summary ----
+summary_Beta_glmm_control <- data.frame(
+  Phenotype = c("Gall size", "Clutch size", "Female preference"),
+  Food_Web = "Complex",
+  Model = "GLMM",
+  Beta = round(Beta_avg_grad(glmer_control),3),
+  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
+  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
+
+summary_Beta_glmm_control
+```
+
+```{r Get 3D, include=FALSE, eval=FALSE}
+# note that length.out=10 now
+library(FD)
+
+# Control ----
+RF_control_3D <- bootstrap_fitness(
+  logistic_model = beta_control, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=10),
+     sc.log.clutch_size = seq(-1,1,length.out=10),
+     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
+  bootstraps=NULL)
+mean(RF_control_3D$relative_fitness$average)
+
+control_traits <- RF_control_3D$relative_fitness %>%
+  filter(average < 1) %>%
+  select(-average) %>%
+  mutate(Treatment = "Control")
+
+FD_control <- dbFD(control_traits)
+
+FD_control
+
+# Treatment ----
+RF_treatment_3D <- bootstrap_fitness(
+  logistic_model = beta_treatment, 
+  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
+  newdata = expand.grid(
+     sc.gall_size = seq(-1,1,length.out=10),
+     sc.log.clutch_size = seq(-1,1,length.out=10),
+     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
+  bootstraps=NULL)
+mean(RF_treatment_3D$relative_fitness$average)
+
+treatment_traits <- RF_treatment_3D$relative_fitness %>%
+  filter(average < 1) %>%
+  select(-average) %>%
+  mutate(Treatment = "Treatment")
+
+FD_treatment <- dbFD(treatment_traits)
+
+bind_rows(
+  data.frame(FD_control),
+  data.frame(FD_treatment)
+)
+
+library(vegan)
+all_traits <- bind_rows(control_traits, treatment_traits)
+
+dim(control_traits)
+dim(treatment_traits)
+
+traits_betadisper <- betadisper(d = vegdist(select(all_traits, -Treatment), method = "euclidean"), group = all_traits$Treatment)
+boxplot(traits_betadisper)
+
+ggplot(all_traits, aes(x=sc.gall_size, y=sc.log1p.female_preference, color=Treatment)) +
+  geom_jitter(width=0.05, size = 2)
+
+ggplot(all_traits, aes(x=sc.gall_size, y=sc.log.clutch_size, color=Treatment)) +
+  geom_jitter(width=0.05, size=2)
+
+ggplot(all_traits, aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, color=Treatment)) +
+  geom_jitter(width=0.05, size=2)
+
+##
+
+control_traits <- RF_control_3D$relative_fitness %>%
+  mutate(Treatment = "Control", average_cut = cut(average, breaks = c(0,0.9,1.1,2)))
+control_traits$average_cut
+
+treatment_traits <-RF_treatment_3D$relative_fitness %>%
+  mutate(Treatment = "Treatment", average_cut = cut(average, breaks = c(0,0.9,1.1,2)))
+
+all_traits <- bind_rows(control_traits, treatment_traits)
+table(all_traits$Treatment, all_traits$average_cut)
+
+ggplot(all_traits, aes(x=average, fill=Treatment)) +
+  geom_density(alpha=0.2) +
+  xlab("Relative fitness")
+
+data.frame(control = var(control_traits$average), treatment = var(treatment_traits$average))
+#all_traits %>%
+#  filter(average > 1) %>%
+#  ggplot(., aes(x=average, color=Treatment)) + geom_density()
+
+##
+
+#control_traits <- RF_control_3D$relative_fitness %>%
+#  mutate(Treatment = "Control", abund = average*100)
+
+#treatment_traits <-RF_treatment_3D$relative_fitness %>%
+#  mutate(Treatment = "Treatment", abund = average*100)
+
+#all_traits <- bind_rows(control_traits, treatment_traits)
+
+#library(MASS)
+#all_traits %>%
+#  ggplot(., aes(x=sc.log.clutch_size, y=sc.log1p.female_preference)) +
+#  geom_point() +
+#  stat_density_2d(aes(fill = stat(level)), geom = "polygon")
+```
+
+```{r Plot Univariate Landscapes OLD, include=FALSE, cache=TRUE, eval=FALSE}
+
+# Gall Diameter ----   
+RF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
+  gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall diameter (SD)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Clutch size ----
+RF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.log1p.female_preference) %>%
+  gather(ID, relative_fitness, -sc.log.clutch_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SD)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+
+# Female preference ----
+RF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
+  select(-sc.gall_size, -sc.log.clutch_size) %>%
+  gather(ID, relative_fitness, -sc.log1p.female_preference, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log1p.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  geom_hline(yintercept = 1, linetype = "dotted") +
+  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SD)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
+```
+
+```{r Figure 2 Univariate Landscapes OLD, echo=FALSE, eval=FALSE}
+
+# Get legend
+RF_uni_legend <- get_legend(RF_uni_size)
+
+# Make plots
+RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none",
+                                              axis.text.x = element_text(size=10),
+                                              axis.title.x = element_text(size=11)), 
+                       RF_uni_clutch + theme(legend.position = "none", 
+                                          axis.title.y = element_blank(), axis.text.y = element_blank(),
+                                          axis.text.x = element_text(size=10),
+                                          axis.title.x = element_text(size=11)),
+                       RF_uni_pref + theme(legend.position = "none", 
+                                        axis.title.y = element_blank(), axis.text.y = element_blank(),
+                                        axis.text.x = element_text(size=10),
+                                        axis.title.x = element_text(size=11)),
+                       labels = "AUTO", ncol = 3, align='hv')
+
+RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
+#RF_gradients
+RF_uni_plots
+#save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
+#save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
+```
+
+```{r Plot Multivariate Fitness Landscape OLD, include=FALSE, cache=TRUE, eval=FALSE}
+
+# Clutch x Preference ----
+RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch.x.preference$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Female preference (SD)") +
+  ylab("Clutch size (SD)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
+
+# Size x Clutch ----
+RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.clutch$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SD)") +
+  ylab("Clutch size (SD)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
+
+# Size x Preference ----
+RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_size.x.preference$relative_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
+  geom_raster() +
+  facet_wrap(~Food_Web) +
+  xlab("Gall diameter (SD)") +
+  ylab("Female preference (SD)") +
+  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
+  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
+```
+
+```{r Figure 3 Multivariate Landscapes OLD, echo=FALSE, eval=FALSE}
+
+# Get legend
+RF_landscape_legend <- get_legend((RF_plot_size.x.preference + theme(legend.title = element_text(size=12), legend.text=element_text(size=10))))
+
+# Format plots
+RF_landscape_plots <- plot_grid(
+  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)),
+  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank(), axis.text = element_text(size=9), axis.text.y = element_blank(), axis.title = element_text(size=11), strip.text = element_text(size=11)),
+  RF_plot_size.x.preference + theme(legend.position = "none", axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)), 
+  nrow=2, align="hv", labels = "AUTO")
+RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
+RF_landscape_2d
+#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
+```

### 2018-09-20 elsevier_test/elsevier_test.tex
many many changes

@@
 \IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
 \usepackage{graphicx}
@@
             pdfauthor={},
-            pdftitle={Food-web complexity flattens the fitness landscape of an insect herbivore},
+            pdftitle={Food-web complexity alters the fitness landscape of an insect herbivore},
             colorlinks=true,
@@
 
-  \title{Food-web complexity flattens the fitness landscape of an insect
-herbivore}
-    \author[Department of Evolutionary Biology and Environmental Studies, University
-of Zurich, Zurich, Switzerland]{Matthew A. Barbour\corref{c1}}
+  \title{Food-web complexity alters the fitness landscape of an insect herbivore}
+    \author[a,b]{Matthew A. Barbour\corref{c1}}
    \ead{matthew.barbour@ieu.uzh.ch} 
    \cortext[c1]{Corresponding Author}
-    \author[Another University]{Jordi Bascompte}
-   \ead{jordi.bascompte@ieu.uzh.ch}
+    \author[a,c]{Christopher J. Greyson-Gaito}
 
-      \address[Some Institute of Technology]{Department, Street, City, State, Zip}
-    \address[Another University]{Department, Street, City, State, Zip}
+    \author[a]{Arezoo Sootodeh}
+
+    \author[d]{Brendan Locke}
+
+    \author[b]{Jordi Bascompte}
+
+      \address[a]{University of British Columbia, Department of Zoology, 6270 University
+Blvd., Vancouver, BC, V6T 1Z4, Canada}
+    \address[b]{University of Zurich, Department of Evolutionary Biology and
+Environmental Studies, Winterthurerstrasse 190, Zurich, 8057,
+Switzerland}
+    \address[c]{University of Guelph, Department of Integrative Biology, 50 Stone Rd.
+East, Guelph, ONT, N1G 2W1, Canada}
+    \address[d]{Humboldt State University, Department of Biological Sciences, 1 Harpst
+St., Arcata, CA, 95521, USA}
 
   \begin{abstract}
-  true
+  Studies of natural selection and fitness landscapes usually treat the
+  network of interacting species as a ``black box''. Given that the loss
+  of biodiversity is simplifying the structure of ecological networks,
+  there is a pressing need to answer the question: how does network
+  complexity affect natural selection and the fitness landscape of
+  associated species? To answer this question, we conducted a field
+  experiment that manipulated the complexity of a food web associated with
+  a galling insect herbivore. To maintain complex food webs, we allowed
+  the entire community of natural enemies to attack insect galls on 64
+  plants in a common garden setting. To create simple food webs, we
+  excluded a guild of three larval parasitoids by bagging galls on 64
+  different plants; therefore, mortality in this treatment was primarily
+  due to a single egg parasitoid that attacks prior to gall formation. We
+  then measured herbivore survival as a function of three key gall traits
+  in each treatment. We found that more traits were under selection in the
+  simple vs.~complex food web. This occurred because different parasitoid
+  species impose different selection pressures on gall traits, thereby
+  minimizing relative fitness differences among insect galls with
+  different phenotypes. Our work suggests that more complex food webs
+  allow phenotypic variation to persist, which could facilitate subsequent
+  adaptive evolution to environmental change.
   \end{abstract}
@@
  \end{frontmatter}
-
-\emph{Text based on elsarticle sample manuscript, see
-\url{http://www.elsevier.com/author-schemas/latex-instructions\#elsarticle}}
-
-\begin{quote}
-\emph{There is a much more insidious kind of extinction: the extinction
-of ecological interactions.} \emph{(Janzen, D.H. 1974. The deflowering
-of Central America. Natural History. 83:48--53).}
-\end{quote}
 
@@
 (2015)). On treatment plants (8 replicates per genotype), we enclosed 14
-galled leaves with organza bags (MANUFACTORER DETAILS) to exclude three
-parasitoid species that attack during larva development (hereafter
-larval parasitoids). This treatment did not exclude the egg parasitoid
-\emph{Platygaster} sp. which attacks prior to gall initiation (note that
-in Cecidomyiid midges, larva initiate gall development CITE). On control
-plants (8 replicates per genotype), we used flagging tape to mark 14
-galled leaves per plant, allowing the full suite of parasitoids to
-attack \emph{Iteomyia}. Marking galls with flagging tape ensured that we
-compared control and treatment galls with similar phenology when we
-collected galls later in the season. Our food-web manipulation altered
-the average number of trophic interactions that \emph{Iteomyia} was
-exposed to from BLANK on control plants to BLANK on treatment plants.
-Thus, we refer to galls on control plants as being exposed to a
-`complex' food web, whereas galls on treatment plants were exposed to a
-`simple' food web. In late August, we collected marked and bagged galls
-from each plant, placed them into 30 mL vials and kept them in the lab
-for 4 months at room temperature. We then opened galls under a
-dissecting scope and determined whether larva survived to pupation (our
-measure of fitness) or were parasitized.
+galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI,
+USA) to exclude three parasitoid species that attack during larva
+development (hereafter larval parasitoids). This treatment did not
+exclude the egg parasitoid \emph{Platygaster} sp. which attacks prior to
+gall initiation (note that in Cecidomyiid midges, larva initiate gall
+development CITE). On control plants (8 replicates per genotype), we
+used flagging tape to mark 14 galled leaves per plant, allowing the full
+suite of parasitoids to attack \emph{Iteomyia}. Marking galls with
+flagging tape ensured that we compared control and treatment galls with
+similar phenology when we collected galls later in the season. Our
+food-web manipulation altered the average number of trophic interactions
+that \emph{Iteomyia} was exposed to from BLANK on control plants to
+BLANK on treatment plants. Thus, we refer to galls on control plants as
+being exposed to a `complex' food web, whereas galls on treatment plants
+were exposed to a `simple' food web. In late August, we collected marked
+and bagged galls from each plant, placed them into 30 mL vials and kept
+them in the lab for 4 months at room temperature. We then opened galls
+under a dissecting scope and determined whether larva survived to
+pupation (our measure of fitness) or were parasitized.
 
@@
 and others work with Cecidomyiid midges (Weis, Price, and Lynch (1983),
-J. J. Heath, Abbot, and Stireman (2018)). First, we measured gall
-diameter as the size of each gall chamber to the nearest 0.01 mm at its
-maximum diameter (perpendicular to the direction of plant tissue
-growth). Our previous work has shown that a larger gall diameter
-provides a refuge for larva from parasitoid attack (Barbour et al.
-(2016)). Second, we measured the clutch size of adult female midges by
-counting the number of chambers in each gall (Weis, Price, and Lynch
-(1983)). All larva collected from the same multi-chambered gall were
-scored with the same clutch size. Third, we measured female preference
-for oviposition (egg-laying) sites as the density of larva observed on a
-plant. The measurement of larval densities on plants in the field is a
-commonly used index for measuring oviposition preference (Gripenberg et
-al. (2010)), although caution must be taken in inferring `preference'
+Heath, Abbot, and Stireman (2018)). First, we measured gall diameter as
+the size of each gall chamber to the nearest 0.01 mm at its maximum
+diameter (perpendicular to the direction of plant tissue growth). Our
+previous work has shown that a larger gall diameter provides a refuge
+for larva from parasitoid attack (Barbour et al. (2016)). Second, we
+measured the clutch size of adult female midges by counting the number
+of chambers in each gall (Weis, Price, and Lynch (1983)). All larva
+collected from the same multi-chambered gall were scored with the same
+clutch size. Third, we measured female preference for oviposition
+(egg-laying) sites as the density of larva observed on a plant. The
+measurement of larval densities on plants in the field is a commonly
+used index for measuring oviposition preference (Gripenberg et al.
+(2010)), although caution must be taken in inferring `preference'
 (Singer (1986)). This is because larval densities can be influenced by
@@
 
-To characterize the shape of the fitness landscape, we quantified
-selection gradients acting on each trait in simple vs.~complex food
-webs. We did this by fitting separate statistical models to data from
-each food-web treatment. We used generalized linear mixed models (GLMMs,
-Bolker et al. (2009)) with larval survival (0 or 1) as our response
-variable and measure of fitness. We specified linear and quadratic terms
-for each gall trait as well as linear interaction terms between each
-gall trait as fixed effects in the statistical models. To account for
-the correlated structure of clutch size (gall level) and female
-preference (plant level) as well as any other independent effects of
-willow genotype on larval survival, we specified gall ID nested within
-plant ID nested within plant genotype as random intercepts in our
-statistical models. Since we were interested in characterizing the
-fitness landscape -- the relationship between mean trait values and
-population mean fitness -- we assumed the mean value of our random
-effects (i.e.~setting them to zero) to estimate selection gradients. We
-then used the method of Frederic J Janzen and Hal S Stearn (1998) to
-calculate directional (\(\beta_{z_i}\)), quadratic (\(\gamma_{z_i}\)),
-and correlational (\(\gamma_{z_i,z_j}\)) selection gradients and used
-parametric bootstrapping (1000 replicates) to calculate their 95\%
-confidence intervals (Bolker et al. (2009)). To test whether selection
+To characterize the shape of the fitness landscape in simple and complex
+food webs, we fit separate statistical models to quantify individual
+selection surfaces acting on each trait. We used generalized linear
+mixed models (GLMMs, Bolker et al. (2009)) with larval survival (0 or 1)
+as our response variable and measure of fitness. In our full model, we
+specified linear and quadratic terms for each gall trait as well as
+linear interaction terms between each gall trait as fixed effects in the
+statistical models. To account for the correlated structure of clutch
+size (gall level) and female preference (plant level) as well as any
+other independent effects of willow genotype on larval survival, we
+specified gall ID nested within plant ID nested within plant genotype as
+random intercepts in our statistical models. Since we were interested in
+characterizing the fitness landscape -- the relationship between mean
+trait values and population mean fitness -- we assumed the mean value of
+our random effects (i.e.~setting them to zero) to estimate selection
+gradients. We then used the method of Frederic J Janzen and Hal S Stearn
+(1998) to calculate directional (\(\beta_{z_i}\)), quadratic
+(\(\gamma_{z_i}\)), and correlational (\(\gamma_{z_i,z_j}\)) selection
+gradients and used parametric bootstrapping (1000 replicates) to
+calculate their 95\% confidence intervals (Bolker et al. (2009)). We
+estimated directional selection gradients by excluding quadratic terms
+and statistical interactions in the model. To test whether selection
 gradients differed between treatments, we used our bootstrapped
@@
 simple food web were larger/smaller than in the complex food web
-(i.e.~the p-value). All analyses and visualizations were conducted in R
-(R Core Team (2018)).
+(i.e.~the p-value). Together, we had survival estimates for 1,306 larva,
+607 galls, 111 plants, and 8 plant genotypes. We report estimated
+selection gradients and the 95\% confidence intervals in parentheses.
+All analyses and visualizations were conducted in R (R Core Team
+(2018)).
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\NormalTok{## Summarize Control Selection Gradients ----}
+\NormalTok{summary_beta_control <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall diameter"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Complex"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Type =} \StringTok{"Beta"}\NormalTok{,}
+  \DataTypeTok{Estimate =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(beta_control),}\DecValTok{3}\NormalTok{),}
+  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{),}
+  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_beta_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)) }
+
+\CommentTok{# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)}
+\NormalTok{summary_quad_control <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall diameter"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Complex"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Type =} \StringTok{"Quadratic"}\NormalTok{,}
+  \DataTypeTok{Estimate =} \DecValTok{2}\OperatorTok{*}\KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(quad_control),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{3}\NormalTok{)],}
+  \DataTypeTok{lower_2.5 =} \DecValTok{2}\OperatorTok{*}\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_quad_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{3}\NormalTok{)],}
+  \DataTypeTok{upper_97.5 =} \DecValTok{2}\OperatorTok{*}\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_quad_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{3}\NormalTok{)]) }
+
+\NormalTok{summary_corr_control <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Diam,Clutch"}\NormalTok{, }\StringTok{"Diam,Pref"}\NormalTok{, }\StringTok{"Clutch,Pref"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Complex"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Type =} \StringTok{"Correlational"}\NormalTok{,}
+  \DataTypeTok{Estimate =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(corr_control),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{)],}
+  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_corr_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{)],}
+  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_corr_control}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{)]) }
+
+\NormalTok{## Summarize Treatment Selection Gradients ----}
+\NormalTok{summary_beta_treatment <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall diameter"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Simple"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Type =} \StringTok{"Beta"}\NormalTok{,}
+  \DataTypeTok{Estimate =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(beta_treatment),}\DecValTok{3}\NormalTok{),}
+  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{),}
+  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_beta_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)) }
+
+\CommentTok{# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)}
+\NormalTok{summary_quad_treatment <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Gall diameter"}\NormalTok{, }\StringTok{"Clutch size"}\NormalTok{, }\StringTok{"Female preference"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Simple"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Type =} \StringTok{"Quadratic"}\NormalTok{,}
+  \DataTypeTok{Estimate =} \DecValTok{2}\OperatorTok{*}\KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(quad_treatment),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{3}\NormalTok{)],}
+  \DataTypeTok{lower_2.5 =} \DecValTok{2}\OperatorTok{*}\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_quad_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{3}\NormalTok{)],}
+  \DataTypeTok{upper_97.5 =} \DecValTok{2}\OperatorTok{*}\KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_quad_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{3}\NormalTok{)]) }
+
+\NormalTok{summary_corr_treatment <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}
+  \DataTypeTok{Phenotype =} \KeywordTok{c}\NormalTok{(}\StringTok{"Diam,Clutch"}\NormalTok{, }\StringTok{"Diam,Pref"}\NormalTok{, }\StringTok{"Clutch,Pref"}\NormalTok{),}
+  \DataTypeTok{Food_Web =} \StringTok{"Simple"}\NormalTok{,}
+  \DataTypeTok{Model =} \StringTok{"GLMM"}\NormalTok{,}
+  \DataTypeTok{Type =} \StringTok{"Correlational"}\NormalTok{,}
+  \DataTypeTok{Estimate =} \KeywordTok{round}\NormalTok{(}\KeywordTok{Beta_avg_grad}\NormalTok{(corr_treatment),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{)],}
+  \DataTypeTok{lower_2.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_corr_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.025}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{)],}
+  \DataTypeTok{upper_97.5 =} \KeywordTok{round}\NormalTok{(}\KeywordTok{apply}\NormalTok{(boot_corr_treatment}\OperatorTok{$}\NormalTok{t, }\DecValTok{2}\NormalTok{, }\DataTypeTok{FUN =} \ControlFlowTok{function}\NormalTok{(bootstraps) }\KeywordTok{quantile}\NormalTok{(bootstraps, }\FloatTok{0.975}\NormalTok{)),}\DecValTok{3}\NormalTok{)[}\OperatorTok{-}\KeywordTok{c}\NormalTok{(}\DecValTok{1}\OperatorTok{:}\DecValTok{6}\NormalTok{)]) }
+
+\KeywordTok{bind_rows}\NormalTok{(summary_beta_control, summary_beta_treatment) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{arrange}\NormalTok{(Phenotype)}
+\end{Highlighting}
+\end{Shaded}
 
 \begin{verbatim}
-##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
-## 1     Gall diameter  Complex  GLMM Beta    0.555     0.432      0.642
-## 2       Clutch size  Complex  GLMM Beta    0.036    -0.075      0.177
-## 3 Female preference  Complex  GLMM Beta    0.003    -0.228      0.148
-## 4         Gall size   Simple  GLMM Beta    0.289     0.220      0.357
-## 5       Clutch size   Simple  GLMM Beta   -0.102    -0.190     -0.001
-## 6 Female preference   Simple  GLMM Beta   -0.204    -0.273     -0.119
+## Warning in bind_rows_(x, .id): Unequal factor levels: coercing to character
+\end{verbatim}
+
+\begin{verbatim}
+## Warning in bind_rows_(x, .id): binding character and factor vector,
+## coercing into character vector
+
+## Warning in bind_rows_(x, .id): binding character and factor vector,
+## coercing into character vector
 \end{verbatim}
@@
 ##           Phenotype Food_Web Model Type Estimate lower_2.5 upper_97.5
-## 1     Gall diameter  Complex  GLMM Quadratic    0.050    -0.052      0.218
-## 2       Clutch size  Complex  GLMM Quadratic    0.000    -0.186      0.254
-## 3 Female preference  Complex  GLMM Quadratic    0.032    -0.078      0.146
-## 4         Gall size   Simple  GLMM Quadratic    0.090    -0.078      0.266
-## 5       Clutch size   Simple  GLMM Quadratic    0.032    -0.070      0.156
-## 6 Female preference   Simple  GLMM Quadratic    0.204    -0.008      0.446
+## 1       Clutch size  Complex  GLMM Beta    0.043    -0.044      0.106
+## 2       Clutch size   Simple  GLMM Beta   -0.091    -0.243     -0.012
+## 3 Female preference  Complex  GLMM Beta   -0.093    -0.246      0.051
+## 4 Female preference   Simple  GLMM Beta   -0.232    -0.906     -0.362
+## 5     Gall diameter  Complex  GLMM Beta    0.442     0.418      0.604
+## 6     Gall diameter   Simple  GLMM Beta    0.328     0.191      0.319
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{bind_rows}\NormalTok{(summary_quad_control, summary_quad_treatment) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{arrange}\NormalTok{(Phenotype)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning in bind_rows_(x, .id): Unequal factor levels: coercing to character
+
+## Warning in bind_rows_(x, .id): binding character and factor vector,
+## coercing into character vector
+
+## Warning in bind_rows_(x, .id): binding character and factor vector,
+## coercing into character vector
 \end{verbatim}
@@
 ##           Phenotype Food_Web Model      Type Estimate lower_2.5 upper_97.5
-## 1 Diam,Clutch  Complex  GLMM Correlational   -0.028    -0.085      0.076
-## 2   Diam,Pref  Complex  GLMM Correlational   -0.104    -0.274      0.074
-## 3 Clutch,Pref  Complex  GLMM Correlational    0.004    -0.109      0.063
-## 4 Diam,Clutch   Simple  GLMM Correlational   -0.106    -0.215      0.029
-## 5   Diam,Pref   Simple  GLMM Correlational    0.003    -0.064      0.097
-## 6 Clutch,Pref   Simple  GLMM Correlational   -0.021    -0.156      0.045
+## 1       Clutch size  Complex  GLMM Quadratic   -0.056    -0.228      0.118
+## 2       Clutch size   Simple  GLMM Quadratic   -0.110    -0.440      0.094
+## 3 Female preference  Complex  GLMM Quadratic    0.180     0.028      0.276
+## 4 Female preference   Simple  GLMM Quadratic   -0.076    -0.548      0.266
+## 5     Gall diameter  Complex  GLMM Quadratic    0.066    -0.070      0.188
+## 6     Gall diameter   Simple  GLMM Quadratic    0.064    -0.122      0.232
 \end{verbatim}
 
-\begin{figure}[htbp]
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{bind_rows}\NormalTok{(summary_corr_control, summary_corr_treatment) }\OperatorTok{%>%}\StringTok{ }\KeywordTok{arrange}\NormalTok{(Phenotype)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Warning in bind_rows_(x, .id): Unequal factor levels: coercing to character
+
+## Warning in bind_rows_(x, .id): binding character and factor vector,
+## coercing into character vector
+
+## Warning in bind_rows_(x, .id): binding character and factor vector,
+## coercing into character vector
+\end{verbatim}
+
+\begin{verbatim}
+##     Phenotype Food_Web Model          Type Estimate lower_2.5 upper_97.5
+## 1 Clutch,Pref  Complex  GLMM Correlational    0.041    -0.054      0.142
+## 2 Clutch,Pref   Simple  GLMM Correlational    0.006    -0.110      0.119
+## 3 Diam,Clutch  Complex  GLMM Correlational   -0.044    -0.144      0.060
+## 4 Diam,Clutch   Simple  GLMM Correlational   -0.093    -0.278      0.009
+## 5   Diam,Pref  Complex  GLMM Correlational   -0.105    -0.245      0.008
+## 6   Diam,Pref   Simple  GLMM Correlational   -0.012    -0.114      0.114
+\end{verbatim}
+
+\begin{figure}
 \centering
@@
 \caption{Illustrations of complex (A) and simple (B) food webs
-associated with the insect herbivore, \emph{Iteomyia salicisverruca}.}
+associated with the insect herbivore, \emph{Iteomyia salicisverruca}.
+Black arrows denote `who-eats-whom' in this network of trophic
+interactions.}
 \end{figure}
@@
 
-We found that more phenotypic traits were under selection in the simple
-vs.~complex food web. In both complex and simple food webs, gall
-diameter was under strong directional selection, with larger galls
-resulting in higher larval survival (complex Beta = ; simple Beta =
-)(Fig. 2A). In complex food webs, there was no evidence of selection on
-clutch size (\(\beta_{clutch}=\)) or female preference
-(\(\beta_{preference}=\))(orange lines in Fig. 2B,C). In simple food
-webs, however, clutch size and female preference were under strong
-directional selection, with smaller clutch sizes and weaker preferences
-resulting in higher larval survival (blue lines in Fig. 2B,C). These
-different selection pressures resulted in different adaptive landscapes
-in complex vs.~simple food webs, with evidence for more rugged
-landscapes in the simple rather than the complex food web (Fig. 3).
-Depending on the trait combinations used to create the landscape, we
-found that the ruggedness of the adaptive landscape ranged from 10\%
-higher (Fig. 3A) to 274\% higher (Fig. 3C) in the simple vs.~complex
-food web. Our model comparison suggested that it was unnecessary to test
-for the effects of non-linear or correlational selection gradients (ref.
-supp. mat.).
+Two key patterns emerged from our analyses. First, fewer phenotypic
+traits were under selection in the complex vs.~simple food web. In both
+complex and simple food webs, gall diameter was under strong directional
+selection, with larger galls resulting in higher larval survival
+(complex \(\beta_{diam}=\) 0.442 {[}0.418,0.604{]} ; simple
+\(\beta_{diam}=\) 0.328 {[}0.191,0.319{]} )(Fig.
+\ref{fig:Univariate_Landscapes}A). In simple food webs, both clutch size
+and female preference experience directional selection, with smaller
+clutch sizes (\(\beta_{clutch}=\) -0.091 {[}-0.243,-0.012{]} and weaker
+preferences (\(\beta_{pref}=\) -0.232 {[}-0.906,-0.362{]} ) resulting in
+higher larval survival (blue lines in Fig.
+\ref{fig:Univariate_Landscapes}B,C). In contrast, there was no evidence
+of selection on clutch size (\(\beta_{clutch}=\) 0.043
+{[}-0.044,0.106{]} ) or female preference (\(\beta_{pref}=\) -0.093
+{[}-0.246,0.051{]} ) in complex food webs (orange lines in Fig.
+\ref{fig:Univariate_Landscapes}B,C). The absence of selection on clutch
+size and female preference was likely a result of conflicting selection
+pressures imposed by each guild of parasitoids due to their different
+functional relationships with gall traits. Together, these different
+patterns of selection resulted in an ideal combination of traits having
+higher fitness in the simple food web (large diameter, smaller clutches,
+weaker preference), whereas there was a larger combination of trait
+values that had equal fitness in the complex food web (Fig.
+\ref{fig:Multivariate_Landscapes}). We did not find any strong evidence
+for nonlinear or correlational selection gradients acting on gall traits
+in either food-web treatment. The second major pattern was that the
+overall intensity of selection was stronger in the complex vs.~simple
+food web. This result appeared to be driven by selection on gall
+diameter in the complex food web, which was more than 1.3 \(\times\)
+larger than any other selection gradient in our analyses.
 
-\begin{figure}[htbp]
+\begin{figure}
 \centering
-\includegraphics{elsevier_test_files/figure-latex/Figure 2 Univariate Landscapes-1.pdf}
-\caption{Selection gradients acting on gall traits in complex vs.~simple
-food webs. Each panel corresponds to a different gall trait: gall
-diameter (A); clutch size (B); and female preference (C). Solid lines
-represent the estimated gradients in complex (orange) and simple (blue)
-food webs. Transparent lines represent bootstrapped replicates (n=100)
-to show the uncertainty in estimated gradients.}
+\includegraphics{elsevier_test_files/figure-latex/Univariate_Landscapes-1.pdf}
+\caption{\label{fig:Univariate_Landscapes}Selection gradients acting on
+gall traits in complex vs.~simple food webs. Each panel corresponds to a
+different gall trait: gall diameter (A); clutch size (B); and female
+preference (C). Solid lines represent the estimated gradients in complex
+(orange) and simple (blue) food webs. Transparent lines represent
+bootstrapped replicates (n=100) to show the uncertainty in estimated
+gradients. Note that only 100 bootstraps are displayed here, but that
+inferences are based on 1,000 bootstrapped samples.}
 \end{figure}
 
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-\begin{figure}[htbp]
+\begin{figure}
 \centering
-\includegraphics{elsevier_test_files/figure-latex/Figure 3 Multivariate Landscapes-1.pdf}
-\caption{Relative fitness landscapes of gall traits in complex
-vs.~simple food webs. Each panel corresponds to a different combination
-of traits: clutch size and gall diameter (A); clutch size and female
-preference (B); female preference and gall diameter (C). Note that
-traits for all plots range 1 SD below and above the mean (=0).}
+\includegraphics{elsevier_test_files/figure-latex/Multivariate_Landscapes-1.pdf}
+\caption{\label{fig:Multivariate_Landscapes}Fitness landscapes of gall
+traits in complex vs.~simple food webs. Each panel corresponds to a
+different combination of traits: clutch size and gall diameter (A);
+clutch size and female preference (B); female preference and gall
+diameter (C). Note that traits for all plots range 1 SD below and above
+the mean (=0).}
 \end{figure}
-
-\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}
-
-\begin{verbatim}
-##              df      AIC
-## beta_control  7 809.1027
-## quad_control 10 814.3022
-## corr_control 13 817.6910
-\end{verbatim}
-
-\begin{verbatim}
-##                  df      AIC
-## beta_control      7 809.1027
-## glm.beta_control  4 881.0152
-\end{verbatim}
-
-\begin{verbatim}
-##                           df      AIC
-## beta_control               7 809.1027
-## beta_control.REonlyGallID  5 816.4817
-\end{verbatim}
-
-\begin{verbatim}
-##       chisq       ratio         rdf           p 
-## 349.7811634   0.5025591 696.0000000   1.0000000
-\end{verbatim}
-
-\begin{verbatim}
-##                df      AIC
-## beta_treatment  7 619.1030
-## quad_treatment 10 620.1640
-## corr_treatment 13 622.3247
-\end{verbatim}
-
-\begin{verbatim}
-##       chisq       ratio         rdf           p 
-## 190.3351784   0.3215121 592.0000000   1.0000000
-\end{verbatim}
-
-\begin{verbatim}
-##                    df      AIC
-## beta_treatment      7 619.1030
-## glm.beta_treatment  4 712.4146
-\end{verbatim}
-
-\begin{verbatim}
-##                             df      AIC
-## beta_treatment               7 619.1030
-## beta_treatment.REonlyGallID  6 669.5617
-\end{verbatim}
-
-\begin{verbatim}
-## Data: treatment_df
-## Models:
-## beta_treatment.REonlyGallID: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
-## beta_treatment.REonlyGallID:     (1 | Genotype/Plant_Position)
-## beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
-## beta_treatment:     (1 | Genotype/Plant_Position/Gall_Number)
-##                             Df    AIC    BIC  logLik deviance  Chisq
-## beta_treatment.REonlyGallID  6 669.56 695.93 -328.78   657.56       
-## beta_treatment               7 619.10 649.87 -302.55   605.10 52.459
-##                             Chi Df Pr(>Chisq)    
-## beta_treatment.REonlyGallID                      
-## beta_treatment                   1  4.394e-13 ***
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-\end{verbatim}
-
-\begin{verbatim}
-## Data: treatment_df
-## Models:
-## glm.beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference
-## beta_treatment: gall_survival ~ sc.gall_size + sc.clutch_size + sc.female_preference + 
-## beta_treatment:     (1 | Genotype/Plant_Position/Gall_Number)
-##                    Df    AIC    BIC  logLik deviance  Chisq Chi Df
-## glm.beta_treatment  4 712.41 730.00 -352.21   704.41              
-## beta_treatment      7 619.10 649.87 -302.55   605.10 99.311      3
-##                    Pr(>Chisq)    
-## glm.beta_treatment               
-## beta_treatment      < 2.2e-16 ***
-## ---
-## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
-\end{verbatim}
 
@@
 
-More recently, researchers have begun to explore how the community
-context drives evolutionary change (Mcpeek (2017); terHorst et al.
-(2018)).
+Our key finding was that the adaptive landscape was less constrained in
+the complex vs.~simple food web. These fewer constraints arise from
+conflicting selection pressures imposed by different parasitoid guilds,
+resulting in fewer traits under selection in the complex food web. At
+the same time, we observed an overall greater intensity of selection in
+the complex food web, suggesting that trait evolution can be faster in
+complex vs.~simple food webs. Our observation that natural selection was
+more constrained and less intense in simple vs.~complex food webs
+suggests that the loss of biodiversity could constrain the adaptive
+potential of interacting species by reducing genetic and phenotypic
+variation in multiple traits.
 
-NEED to recognize that evolutionary biologists have begun to explore how
-community context affects evolutionary change (work by Sharon Strauss,
-Casey terHorst, Lutz Becks, etc.). These results have begun to show
-interesting patterns whereby the composition of species in a community
-can alter the direction and strength of natural selection imposed on
-species embedded within these communities (cite).
+Current theory suggests that when the number of selective constrains is
+less than the number of genetic constraints (i.e.~some genetically
+variable traits are selective neutral), there are multiple positions on
+the landscape that confer equal fitness (Lande 1981; Lande and Arnold
+1985). In this scenario, trait differences between populations may
+simply be due to neutral processes (e.g.~genetic drift and mutation)
+moving trait values of the population. For our system, we currently lack
+quantitative estimates of genetic variation in our traits, although work
+with other species of galling insects has shown that gall diameter
+(Abramhson, Heath's work), clutch size (look to Weiss' work), and
+oviposition preference (Abrahmson's work?) are genetically variable. We
+encourage others to examine how changes in community context will alter
+selection on multiple traits.
 
-In other words, these results have begun to illustrate show how
-biological diversity, in terms of differences between species, can shape
-evolution. Nevertheless, predicting the how the composition of species
-in a community requires moving beyond a description of community
-composition. simply knowing the composition of species in a community
-will
+One interesting result of our work was that the overall intensity of
+selection appeared to be larger in complex food webs. This result was
+driven by the large selection gradient acting on gall diameter in
+complex vs.~simple food webs. This difference in selection intensity is
+likely not driven by a difference in the ecological relationship between
+gall diameter and parasitoid attack (i.e.~slope), but actually a result
+of the lower mean fitness of \emph{Iteomyia} in the complex food web.
+This lower mean fitness is not surprising ---we excluded an entire guild
+of parasitoids from attacking the insect. But this more intense
+selection pressure may simply represent a transient dynamic. This is
+because we would expect the egg-parasitoid \emph{Platygaster} to
+increase in abundance over time once its intraguild predator has been
+removed. While our results suggest that this wouldn't affect the slope
+of the relationship, the higher abundance of the egg parasitoid would
+likely reduce the mean fitness of \emph{Iteomyia}, thus increasing the
+selection gradient acting on gall diameter closer to what we observed in
+the complex food web. We don't expect it to fully compensate, given that
+the larval parasitoids exhibit a different functional relationship with
+gall traits, and thus we expect a more diverse community of primary
+parasitoids to generally impose greater parasitism pressure, a factor
+that appears to be a general trend in parasitoid community (Hawkins
+citation) and likely for other consumers (Ives and Cardinale Ecology
+Letters).
 
-There are various bibliography styles available. You can select the
-style of your choice in the preamble of this document. These styles are
-Elsevier styles based on standard styles like Harvard and Vancouver.
-Please use BibTeX~to generate your bibliography and include DOIs
-whenever available.
+Our study focused on quantifying the direct effects of changes in
+network complexity on the fitness landscape; however, changes in network
+complexity may have pervasive indirect effects via coevolution or by
+initiating evolutionary cascades. In our system, we observed that
+excluding the guild of larval parasitoids altered selection on both the
+basal resource (\emph{Iteomyia}) and the intraguild prey
+(\emph{Platygaster}). GIVE DETAILS AND SUGGEST A POTENTIAL EVOLUTIONARY
+CASCADE.
 
-Here are two sample references: ({\textbf{???}}; {\textbf{???}}).
+Our study manipulated food-web complexity and examined changes in the
+fitness landscape of species embedded within this network. However,
+other studies have also examined, at least theoretically, how changes in
+the diversity of competitive communities affects evolution. These
+studies have generally suggested that the diversity of competitors may
+actually constrain the adaptive landscape, a finding that stands in
+contrast to our results. NEED TO REVIEW THESE PAPERS TO SEE HOW ITS
+DIFFERENT.
+
+We suggest that by explicitly focusing on network structure, we can
+predict how changes in biodiversity will affect the adaptive potential
+of constituent species. A network allows a powerful representation of
+the `community context', lending predictive power to how changes in
+network structure (either due to loss of species or links), will alter
+natural selection and consequently evolutionary change. Our results also
+suggest that losing biodiversity may not just have consequences at the
+community level, but also population-level consequences that may
+actually constrain adaptation to changing environments. This argues that
+changes in network complexity may not only affect the robustness of
+communities, but also that of constituent populations to future
+environmental change.
 
@@
 \addcontentsline{toc}{section}{References}
-
-\includegraphics{elsevier_test_files/figure-latex/Figure S1 Univariate Absolute Fitness Landscapes-1.pdf}
-
-\includegraphics{elsevier_test_files/figure-latex/Figure S2 Multivariate Absolute Fitness Landscapes-1.pdf}
 
@@
 
-\hypertarget{ref-TerHorst2018}{}
-terHorst, Casey P, Peter C Zee, Katy D Heath, Thomas E Miller, Abigail I
-Pastore, Swati Patel, Sebastian J Schreiber, Michael J Wade, and Matthew
-R Walsh. 2018. ``Evolution in a Community Context: Trait Responses to
-Multiple Species Interactions*.'' \emph{Am. Nat.}, January. University
-of Chicago PressChicago, IL.
-
 \hypertarget{ref-Weis1983}{}

### 2018-09-20 ms_complexity_selection.Rmd
many many changes

--- 2018-09-20 elsevier_test/elsevier_test.Rmd
@@
 ---
-title: Food-web complexity alters the fitness landscape of an insect herbivore
+title: Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore 
 author:
@@
     address: Humboldt State University, Department of Biological Sciences, 1 Harpst St., Arcata, CA, 95521, USA
-abstract: "Studies of natural selection and fitness landscapes usually treat the network of interacting species as a “black box”.
-Given that     the loss of biodiversity is simplifying the structure of ecological networks, there is a pressing need to answer the question: how does network complexity affect natural selection and the fitness landscape of associated species?
-To answer this question, we conducted a field experiment that manipulated the complexity of a food web associated with a galling insect herbivore.
-To maintain complex food webs, we allowed the entire community of natural enemies to attack insect galls on 64 plants in a common garden setting.
-To create simple food webs, we excluded a guild of three larval parasitoids by bagging galls on 64 different plants; therefore, mortality in this treatment was primarily due to a single egg parasitoid that attacks prior to gall formation.
-We then measured herbivore survival as a function of three key gall traits in each treatment.
-We found that more traits were under selection in the simple vs.
-complex food web.
-This occurred because different parasitoid species impose different selection pressures on gall traits, thereby minimizing relative fitness differences among insect galls with different phenotypes.
-Our work suggests that more complex food webs allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution to environmental change."
-
-bibliography: mybibfile.bib
-output: rticles::elsevier_article
----
-
-<!-- Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
+abstract: "Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
 Similarly, fitness landscapes provide a mechanistic link between population and evolutionary ecology, as they describe the influence of natural selection on phenotypic variation.
@@
 This occurred because different natural enemies impose different selection pressures on herbivore traits, thereby minimizing relative fitness differences among herbivore phenotypes in the complex network.
-Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change.-->
+Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change."
+
+bibliography: mybibfile.bib
+output: rticles::elsevier_article
+---
 
@@
 ## Load required libraries ----
-library(tidyverse)
+library(car)        # for homogeneity of variance test
+library(tidyverse)  # for managing data
 library(cowplot)    # pretty default ggplots
-#library(broom) # for tidying multiple linear models
-library(mgcv) # generalized additive models
-#library(gamm4) # generalized additive mixed-models
-library(gsg) # calculating selection gradients
-#library(visreg)
+library(broom)      # for tidying multiple linear models
+library(visreg)     # for quick visualizations of model effects
 library(viridis)    # for color palette
 library(lme4)       # for generalized linear mixed models
+library(piecewiseSEM) # for calculating model R-square
+library(latex2exp)  # using Latex notation for axes labels
 
@@
          platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
+         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
          egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
-         sc.clutch_size = as.numeric(scale(gall_individuals)), 
-         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
-         sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
-         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
+         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
+         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots)))) 
+dim(gall_selection.df)
+
+table(gall_selection.df$Treatment.focus, gall_selection.df$ectos)
 
 ## Create separate datasets for quantifying selection gradients ----
-control_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Control") #%>%
+#control_df <- gall_selection.df %>%
+#  filter(Treatment.focus == "Control") #%>%
   #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
@@
   #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
-
-treatment_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+#dim(control_df)
+
+#treatment_df <- gall_selection.df %>%
+#  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+#dim(treatment_df)
   #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
@@
 
-mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.
+#mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.
 
@@
 
+## Test for multicollinearity (from: https://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/)
+vif.mer <- function (fit) {
+    ## adapted from rms::vif
+
+    v <- vcov(fit)
+    nam <- names(fixef(fit))
+
+    ## exclude intercepts
+    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
+    if (ns > 0) {
+        v <- v[-(1:ns), -(1:ns), drop = FALSE]
+        nam <- nam[-(1:ns)]
+    }
+
+    d <- diag(v)^0.5
+    v <- diag(solve(v/(d %o% d)))
+    names(v) <- nam
+    v
+}
+
 ## Transform logit to probability
@@
 Beta_avg_grad <- function(.) {
-  mean_fitness <- mean(predict(., type = "response")) #inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  mean_fitness <- mean(predict(., type = "response")) 
   brackets <- predict(., type = "response") * (1 - predict(., type="response"))
-  mean(brackets) * fixef(.)[-1] / mean_fitness 
+  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
 }
@@
   var(relative_fitness)
+}
+
+## Compute the matrix describing the curvature of the fitness landscape
+curvature_fitness.landscape <- function(gammas, # matrix of nonlinear and correlational selection gradients 
+                                        betas){ # vector of directional selection gradients
+  gammas - betas %*% t(betas)
 }
@@
 ## Number of bootstrap replicates
-n_boots_analysis <- 1000
+n_boots_analysis <- 30 #1000
 n_boots_plots <- 100
@@
 ```
-
-AIC comparison suggests gam is better than quadratic approximation; however, I'm worried that the GAM model is overfitting.
-I feel like the quadratic approximation, while not providing the best fit, will still preven the model from overfitting.
-
-Now the question is: normal glm vs. mixed-model? Maybe I need to answer, why not the mixed model?
-
-- There is no theory developed for them. 
-- Relative fitness occurs at different hierarchical levels instead of the level of the sampled population.
-- Less straightforward.
-
-Mixed-models are also good for modeling heterogeneity, but if I'm interested in a general population level, then maybe I don't have to worry about that. 
-```{r GAM, include=F}
-control_gam <- gam(gall_survival ~ s(sc.gall_size) + s(sc.log.clutch_size, k=9) + s(sc.log1p.female_preference), control_df, family=binomial(link=logit))
-plot(control_gam, trans = inverse_logit)
-
-treatment_gam <- gam(gall_survival ~ s(sc.gall_size) + s(sc.log.clutch_size, k=9) + s(sc.log1p.female_preference), treatment_df, family=binomial(link=logit))
-plot(treatment_gam, trans = inverse_logit)
-
-control_gam_quad <- gam(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2), control_df, family=binomial(link=logit))
-
-treatment_gam_quad <- gam(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2), treatment_df, family=binomial(link=logit))
-
-AIC(control_gam, control_gam_quad)
-AIC(treatment_gam, treatment_gam_quad)
-
-hist(gall_selection.df$sc.gall_size)
-hist(gall_selection.df$sc.log.clutch_size)
-hist(gall_selection.df$sc.log1p.female_preference)
-
-control_glm <- glm(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, control_df, family=quasibinomial())#family=binomial(link=logit))
-summary(control_glm)
-visreg::visreg(control_glm, scale = "response")
-
-treatment_glm <- glm(gall_survival ~ sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, treatment_df, family=quasibinomial())#family=binomial(link=logit))
-summary(treatment_glm)
-
-visreg::visreg(control_glm, scale = "response")
-visreg::visreg(treatment_glm, scale = "response")
-
-test_glm <- glm(gall_survival ~ Treatment.focus*(sc.gall_size + I(sc.gall_size^2) + sc.log.clutch_size + I(sc.log.clutch_size^2) + sc.log1p.female_preference + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference), gall_selection.df, family=quasibinomial())#family=binomial(link=logit))
-summary(test_glm)
-
-visreg::visreg2d(test_glm, xvar="sc.gall_size", yvar="sc.log.clutch_size", scale="response")
-```
-
-```{r, Cryptic effects of parasitism on gall morphology, include=F}
-# how does this analysis compare to Heath?
-# does it make sense to look for the interaction?
-
-control_gall_size <- lmer(sc.gall_size ~ gall_survival +
-                           (1|Genotype:Plant_Position:Gall_Number),
-                         data = control_df)
-summary(control_gall_size)
-visreg::visreg(control_gall_size, xvar="gall_survival")
-
-piecewiseSEM::rsquared(control_gall_size)
-
-flip.control_gall_size <- lmer(gall_survival ~ sc.gall_size +
-                           (1|Genotype:Plant_Position:Gall_Number),
-                         data = control_df)
-summary(flip.control_gall_size)
-visreg::visreg(flip.control_gall_size, xvar="sc.gall_size")
-
-lm.control_gall_size <- lm(Gall_Height_mm ~ gall_survival,
-                         data = control_df)
-summary(lm.control_gall_size)
-visreg::visreg(lm.control_gall_size, xvar="gall_survival")
-
-lmer.control_gall_size <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype:Plant_Position:Gall_Number),
-                         data = control_df)
-summary(lmer.control_gall_size)
-visreg::visreg(lmer.control_gall_size, xvar="gall_survival")
-
-lmer.control_gall_size_2 <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype/Plant_Position/Gall_Number),
-                         data = control_df)
-summary(lmer.control_gall_size_2)
-visreg::visreg(lmer.control_gall_size_2, xvar="gall_survival")
-
-piecewiseSEM::rsquared(flip.control_gall_size)
-
-treatment_gall_size <- lmer(sc.gall_size ~ gall_survival +
-                           (1|Genotype:Plant_Position:Gall_Number),
-                         data = treatment_df)
-summary(treatment_gall_size)
-visreg::visreg(treatment_gall_size, xvar="gall_survival")
-
-lm.treatment_gall_size <- lm(Gall_Height_mm ~ gall_survival,
-                         data = treatment_df)
-summary(lm.treatment_gall_size)
-visreg::visreg(lm.treatment_gall_size, xvar="gall_survival")
-
-lmer.treatment_gall_size <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype:Plant_Position:Gall_Number),
-                         data = treatment_df)
-summary(lmer.treatment_gall_size)
-visreg::visreg(lmer.treatment_gall_size, xvar="gall_survival")
-
-lmer.treatment_gall_size_2 <- lmer(Gall_Height_mm ~ gall_survival + (1|Genotype/Plant_Position/Gall_Number),
-                         data = treatment_df)
-summary(lmer.treatment_gall_size_2)
-visreg::visreg(lmer.treatment_gall_size_2, xvar="gall_survival")
-
-piecewiseSEM::rsquared(lmer.treatment_gall_size_2)
-
-lmer.treatment_sc.gall_size_2 <- lmer(sc.gall_size ~ gall_survival + sc.clutch_size + sc.female_preference + (1|Genotype/Plant_Position/Gall_Number),
-                         data = treatment_df)
-summary(lmer.treatment_sc.gall_size_2)
-
-lm.treatment_sc.gall_size <- lm(sc.gall_size ~ gall_survival,
-                         data = treatment_df)
-summary(lm.treatment_sc.gall_size)
-
-summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2), data=treatment_df))
-summary(lmer(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + (1|Genotype/Plant_Position/Gall_Number), data=treatment_df))
-
-summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) , data=control_df))
-summary(lmer(gall_survival/mean(gall_survival) ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + (1|Genotype/Plant_Position/Gall_Number), data=control_df))
-
-pair_control <- control_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  group_by(Gall_Number, gall_survival) %>%
-  summarise(mean_gall_size = mean(sc.gall_size)) %>%
-  spread(gall_survival, mean_gall_size) %>%
-  mutate(diff = `1` - `0`)
-summary(pair_control$diff)
-length(pair_control$diff)
-
-t.test(pair_control$`1`, pair_control$`0`, paired = T)
-
-pair_treatment <- treatment_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  group_by(Gall_Number, gall_survival) %>%
-  summarise(mean_gall_size = mean(sc.gall_size)) %>%
-  spread(gall_survival, mean_gall_size) %>%
-  mutate(diff = `1` - `0`)
-summary(pair_treatment$diff)
-length(pair_treatment$diff)
-pair_treatment
-
-t.test(pair_treatment$`1`, pair_treatment$`0`, paired = T)
-
-pair_control_ectos <- control_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(ectos)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  group_by(Gall_Number, gall_survival) %>%
-  summarise(mean_gall_size = mean(sc.gall_size)) %>%
-  spread(gall_survival, mean_gall_size) %>%
-  mutate(diff = `1` - `0`)
-summary(pair_control_ectos$diff)
-length(pair_control_ectos$diff)
-
-t.test(pair_control_ectos$`1`, pair_control_ectos$`0`, paired = T)
-
-pair_control_platy <- control_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(egg_parasitoid)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  group_by(Gall_Number, gall_survival) %>%
-  summarise(mean_gall_size = mean(sc.gall_size)) %>%
-  spread(gall_survival, mean_gall_size) %>%
-  mutate(diff = `1` - `0`)
-summary(pair_control_platy$diff)
-length(pair_control_platy$diff)
-
-t.test(pair_control_platy$`1`, pair_control_platy$`0`, paired = T)
-
-gsg::moments.differentials(z=control_df$sc.gall_size, W = control_df$gall_survival)
-gsg::moments.differentials(z=treatment_df$sc.gall_size, W = treatment_df$gall_survival)
-
-summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size, control_df))
-summary(lm(gall_survival/mean(gall_survival) ~ sc.gall_size, treatment_df))
-
-test_control_df <- bind_rows(mutate(control_df, type = 0), mutate(filter(control_df, gall_survival == 1), type = 1))
-summary(lm(sc.gall_size ~ type, test_control_df)) # virtually the same as above
-
-test_treatment_df <- bind_rows(mutate(treatment_df, type = 0), mutate(filter(treatment_df, gall_survival == 1), type = 1))
-summary(lm(sc.gall_size ~ type, test_treatment_df)) # virtually the same as above
-
-# can also look at it this way and just look at the mean difference before and after selection
-test_control_df %>%
-  group_by(type) %>%
-  summarise(mean_gall_size = mean(sc.gall_size))
-
-test_treatment_df %>%
-  group_by(type) %>%
-  summarise(mean_gall_size = mean(sc.gall_size))
-
-# does this enable me to estimate the confounding effect of parasitism on gall size? 
-# Note that the intercept is no longer centered on zero...
-summary(lmer(sc.gall_size ~ type + (1|Genotype/Plant_Position/Gall_Number), test_control_df))
-summary(lmer(sc.gall_size ~ type + (1|Genotype/Plant_Position/Gall_Number), test_treatment_df))
-
-moments_control_df <- control_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  group_by(Gall_Number, gall_survival) %>%
-  summarise(mean_gall_size = mean(sc.gall_size))
-
-gsg::moments.differentials(z=moments_control_df$mean_gall_size, W=moments_control_df$gall_survival) # does this mean anything?
-
-moments_treatment_df <- treatment_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  group_by(Gall_Number, gall_survival) %>%
-  summarise(mean_gall_size = mean(sc.gall_size))
-
-gsg::moments.differentials(z=moments_treatment_df$mean_gall_size, W=moments_treatment_df$gall_survival)
-
-### MOST PROMISING ANALYSIS THUS FAR THAT MAY ENABLE ME TO ASSESS THE BIAS OF PARASITISM ON OBSERVED SELECTION GRADIENTS.
-test_again_control <- control_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
-  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
-  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
-
-hist(test_again_control$diff_gall_size)
-t.test(test_again_control$survive_mean_gall_size, test_again_control$all_mean_gall_size, paired = T)
-
-test_ectos_control <- control_df %>%
-  filter(pupa > 0 | ectos > 0) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
-  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
-  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
-
-hist(test_ectos_control$diff_gall_size)
-t.test(test_ectos_control$survive_mean_gall_size, test_ectos_control$all_mean_gall_size, paired = T)
-
-test_platy_control <- control_df %>%
-  filter(pupa > 0 | egg_parasitoid > 0) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
-  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
-  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
-
-hist(test_platy_control$diff_gall_size)
-t.test(test_platy_control$survive_mean_gall_size, test_platy_control$all_mean_gall_size, paired = T)
-
-test_again_treatment <- treatment_df %>%
-  #filter(gall_individuals==2) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  #filter(mean_survival == 0.5) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.gall_size) %>%
-  mutate(all_mean_gall_size = mean(sc.gall_size)) %>%
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_gall_size = mean(sc.gall_size)) %>%
-  distinct(Gall_Number, all_mean_gall_size, survive_mean_gall_size) %>%
-  mutate(diff_gall_size = survive_mean_gall_size - all_mean_gall_size)  # all of these represent selection differentials at the gall level
-
-hist(test_again_treatment$diff_gall_size)
-t.test(test_again_treatment$survive_mean_gall_size, test_again_treatment$all_mean_gall_size, paired = T)
-```
-
-```{r Calculate Mean and SD of Gall Traits at Different Scales, include=F, eval=F}
-
-## Calculate mean and SD of gall traits at different scales ----
-summary.individual_level <- gall_selection.df %>%
-  group_by(Treatment.focus) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean, sd), na.rm = TRUE) %>%
-  mutate(Level = "Individual")
-
-mean.gall_size.control <- filter(summary.individual_level, Treatment.focus == "Control")$Gall_Height_mm_mean
-sd.gall_size.control <- filter(summary.individual_level, Treatment.focus == "Control")$Gall_Height_mm_sd
-mean.gall_size.treatment <- filter(summary.individual_level, Treatment.focus == "Ectoparasitoid exclusion")$Gall_Height_mm_mean
-sd.gall_size.treatment <- filter(summary.individual_level, Treatment.focus == "Ectoparasitoid exclusion")$Gall_Height_mm_sd
-
-summary.gall_level <- gall_selection.df %>%
-  group_by(Treatment.focus, Gall_Number) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean), na.rm = TRUE) %>%
-  group_by(Treatment.focus) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean, sd), na.rm = TRUE) %>%
-  mutate(Level = "Gall")
-
-mean.clutch_size.control <- filter(summary.gall_level, Treatment.focus == "Control")$gall_individuals_mean
-sd.clutch_size.control <- filter(summary.gall_level, Treatment.focus == "Control")$gall_individuals_sd
-mean.clutch_size.treatment <- filter(summary.gall_level, Treatment.focus == "Ectoparasitoid exclusion")$gall_individuals_mean
-sd.clutch_size.treatment <- filter(summary.gall_level, Treatment.focus == "Ectoparasitoid exclusion")$gall_individuals_sd
-
-summary.plant_level <- gall_selection.df %>%
-  group_by(Treatment.focus, Plant_Position, Gall_Number) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean), na.rm = TRUE) %>%
-  group_by(Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean), na.rm = TRUE) %>%
-  group_by(Treatment.focus) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), funs(mean, sd), na.rm = TRUE) %>%
-  mutate(Level = "Plant")
-
-mean.female_preference.control <- filter(summary.plant_level, Treatment.focus == "Control")$Density_per_100_shoots_mean
-sd.female_preference.control <- filter(summary.plant_level, Treatment.focus == "Control")$Density_per_100_shoots_sd
-mean.female_preference.treatment <- filter(summary.plant_level, Treatment.focus == "Ectoparasitoid exclusion")$Density_per_100_shoots_mean
-sd.female_preference.treatment <- filter(summary.plant_level, Treatment.focus == "Ectoparasitoid exclusion")$Density_per_100_shoots_sd
-
-summary.gall_traits <- bind_rows(summary.individual_level, summary.gall_level, summary.plant_level)
-```
-
-<!-- > *There is a much more insidious kind of extinction: the extinction of ecological interactions.* 
-> *(Janzen, D.H. 1974. The deflowering of Central America. Natural History. 83:48–53).* -->
 
@@
 ============
-
-<!-- I. Fitness Landscape as a unifying framework for evolution and ecology at the population-level -->
 
@@
 
-<!--Prior work with this study system has shown that there is directional selection for larger galls, likely because larger galls provide a refuge from parasitoid attack (@Barbour2016). 
-However, there is also evidence that each parasitoid species imposes differential selection on gall traits (@Barbour2016).-->
-
 Changes in food-web complexity could influence a resource population's fitness landscape in at least two ways.
@@
 
-<!-- I. Evolutionary dynamics in species-rich communities remains unclear, especially in the field -->
-
-<!-- Biological diversity -- from genes, to phenotypes, to species -- has and continues to be shaped by the interplay between ecological and evolutionary processes.
-<!-- need to improve this instead of just saying its fascinated a small group of people -->
-<!-- Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (@Schluter2000), mutualisms (@Jordano1987), and predation (@Abrams2000).
-While there is clear evidence that pairwise interactions can drive evolution, we also know that most species interact with multiple species in an ecological community.
-<!-- are embedded within species-rich communities.--> <!-- complex networks of interacting species.
-<!-- need to make the link to multiple traits and the adaptive landscape here --> <!-- Somthing about the this work remaining eminently theoretical -->
-<!-- Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--><!--  is challenging and eminently theoretical (@McPeek2017, @De_Mazancourt2008, @Guimaraes2017, @Nuismer2013).
-<!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
-I think it would be useful to show that there is some field and lab experiments demonstrating that community context can alter evolutionary trajectories -->
-<!-- Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
-
-<!-- Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests of how changes in network structure will alter the dynamics of natural selection in the field.
--->
-
-<!-- II. Linking species loss to changes in network complexity -->
-
-Predicting the evolutionary consequences of species loss first requires an understanding of the concommitant change in the species-interaction networks.<!-- the relationship between the network structure of a community and the fitness landscape of its constituent species.-->
-Knowing the interaction network is crucial because the loss of biodiversity, in and of itself, will not alter evolution -- it is the associated loss of ecological interactions that will affect evolutionary change (@Janzen1974).
-For a network of directly connected species, we would expect that the loss of species to result in a loss of network complexity.<!-- Need to formalize this logic more, because the loss of a specialist species in a highly generalist food web, would actually increase network complexity...
-Maybe I need to focus on the node/species level property -->
-Network complexity is a property that describes the diversity of interactions in an ecological community (@Banasek-Richter2009). 
-Thus, all else equal, species loss will decrease the diversity of interactions, resulting in a more simple network.
-<!-- Explicitly linking network complexity to the fitness landscape, however, is ultimately needed to predict the evolutionary consequences of biodiversity loss.
--->
-
-<!-- III. Linking changes in network complexity to the fitness landscape -->
-Predicting how a change in network complexity will alter evolution also requires an understanding of the relationship between network structure and the adaptive landscape. 
-The adaptive landscape (i.e.
-fitness landscape or selective surface) describes the relationship between the average trait value of a population and its average fitness (cite Arnold).
-<!-- Need to make the transition between network and trophic complexity -->
-For a trophic network, such as a food web, changes in network complexity can shape the adaptive landscape of constituent species in at least two ways. 
-First, if a more diverse community of consumers is more efficient at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population. 
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018) and thus could speed up the rate of evolutionary change. 
-On the other hand, if consumers are functionally distinct, then more diverse communities can dampen the strength of selection. 
-This is because each consumer has a different functional relationship with resource traits. 
-In addition, there is a reduced probability in interacting with a specific consumer species in a more diverse community.
-Thus, a more diverse consumer community may impose more diffuse selection across the adaptive landscape. <!--and the probability of an interaction.-->
-<!-- Consider linking to a reduced probability of interacting with any one species in the community, which would dampen the selection pressures acting on a given phenotype, also, if predators impose selection on different parts of a prey phenotype, then these selection pressures may even cancel each other out -->
-
-<!-- IV. Summarize our plans to tackle this problem -->
-
-Here, we provide a quantitative test of how the loss of species diversity -- and concomittant loss of network complexity -- shapes the adaptive landscape of a consitutent species in a natural community.
-<!-- Here, we conducted a field experiment to test how changes in network complexity would shape the fitness landscape of a constituent species. -->
-We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on the insect herbivore, *Iteomyia salicisverruca*. 
-The larva of this herbivore species induces tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006). 
-Prior work with this study system has shown that there is directional selection for larger galls, likely because larger galls provide a refuge from parasitoid attack (@Barbour2016). 
-However, there is also evidence that each parasitoid species imposes differential selection on gall traits (@Barbour2016). <!-- Need a sentence to wrap it up--> 
-<!-- Taken together, our study seeks to provide one of the first quantitative tests of how the loss of species diversity -- and concomittant loss of network complexity -- shapes the fitness landscape of associated species.
--->
-Taken together, our aim is to provide evidence for how the simplification of natural communities affects the adaptive<!--process--> potential of constituent species.
-
-<!-- Alternative intro, "the fitness landscape as the unifying concept between ecology and evolutionary biology "-->
-
-<!-- Although often used solely as a metaphor, the fitness landscape explicitly links ecology and evolutionary biology. -->
-<!-- Fitness landscapes provide a quantitative framework for unifying evolutionary biology and ecology.
-Alternatively described as the 'adaptive landscape' or 'selective surface', evolutionary biologists have traditionally used the fitness landscape to describe how changes in the mean values of a trait or multiple traits can alter population mean fitness.
-Less appreciated is the fact that ecologists have similarly been studying the fitness landscape of species but through the lense of population dynamics.
-study how changes in population abundances of interacting species shapes the fitness landscape (@McPeek2017).
-This is because per capita population growth rate is equivalent to population mean fitness (cite Lande ; @McPeek2017).
--->
-
-<!-- Therefore, understanding the feedbacks between ecological and evolutionary dynamics requires an assessment of how the community context shapes the fitness landscape.
-
-We are in the midst of the lost of biological diversity; yet it remains unclear how the loss of biological diversity will alter evolutionary change within species. In order to predict how -->
-
-<!-- II. Ecologists have incorporated community context -->
-
-<!-- In contrast, ecologists have begun to embrace the complexity of the natural world, and seeking to identify the complex networks of interactions that underlie community structure and ecosystem function.
-However, these studies have not examined how evolutionary processes feedback to shape the structure and evolution of these interaction networks.
--->
-
-<!-- III. Generate expectations for how food-web complexity may alter selection gradients -->
-
-<!-- Food-web complexity can shape the fitness landscape in at least two ways.
-First, if more diverse predator communities are more efficient at suppressing prey densities (e.g.
-biodiversity-ecosystem fucntion; Ives 2005 Ecology Letters), then this will result in lower mean fitness.
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018) and thus could speed up the rate of evolutionary change.
-Alternatively, if predators are functionally distinct, more diverse communities can reduce the strength of selection.
-This is because each predator has a different functional relationship between prey phenotype and the probability of an interaction.
--->
-
-<!-- IV. Relationship between entropy and fitness landscape 
-In more complex communities, there is greater uncertainty for an individual prey in which predator species will be imposing the trophic interaction. This also means the -->
-
 Materials & Methods
@@
 
-<!-- I. Give details about the study site, but not focusing on the genetic variation since this doesn't play much of a role in this manuscript. -->
-
 We conducted our study within a four-year old common garden of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
 This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-<!--While relatedness among these genotypes is unknown, their phenotypes in multivariate trait space are quite distinct from each other (@Barbour2016), suggesting that we can treat them as independent from one another.--> Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
+Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
 Willows in our garden begin flowering in February and reach their peak growth in early August.
@@
 ## Food-Web Manipulation
-
-<!-- II. Describe the food-web manipulation experiment -->
 
@@
 This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
-On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant, allowing the full suite of parasitoids to attack *Iteomyia*. 
+On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack *Iteomyia*. 
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
@@
 We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
+Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (*Platygaster* sp.), or was parasitized by a larval parasitoid.
+For the food-web treatment that excluded parasitoids, we further restricted our data by removing any instances of parasitism by a larval parasitoid.
+This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
+Together, we had survival estimates for 1,306 larva from 607 galls, 111 plants, and 8 plant genotypes.
 
 ## Measuring Gall Traits
-
-<!-- % III. Describe how we measured gall phenotypes -->
 
@@
 All larva collected from the same multi-chambered gall were scored with the same clutch size. 
-Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant.
-The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010), although caution must be taken in inferring 'preference' (@Singer1986).
-This is because larval densities can be influenced by processes other than preference. 
-For example, if an ovipositing female is not exposed to the full spectrum of plant types (in this case genotypes), then it is difficult to infer whether patterns of larval densities are actually due to <!--dispersal limitation or-->preference.
-Also, observed larval densities could be influenced by egg predation.
-While we recognize these limitations, a couple of aspects of our study system likely alleviate these limitations. 
+Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant in an independent survey.
+Specifically, we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
+We then converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
+All larva collected from the same plant were scored with the same female preference.
+The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010); however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference (@Singer1986).
+Fortunately, a couple of features of our study system suggest that larval density on a plant may be a good proxy for female preference.
 For example, since our data comes from a randomized placement of willow genotypes in a common garden, there is no consistent bias in which willow genotypes that females are exposed to while searching for oviposition sites.
-Although we cannot control for egg predation, this source of mortality appears to play comparatively minor role in determining the mortality of galling insects (@Hawkins1997).
-<!-- and that we can still detect the presence of an individual even if it dies before development (empty chamber lacking an exit hole and without any evidence of larva or parasitoid).
--->
-To quantify female preference (gall density), we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
-We converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
-<!-- To account for potential differences in the number of shoots per branch for each plant genotype (CITE other willow work), we then counted the number of shoots on the fifth branch to estimate the number of larva per 100 shoots for each plant.-->
-All larva collected from the same plant were scored with the same female preference.
-
-## Statistical Analyses
-
-<!-- % IV. Describe statistical analysis to test the effects of food-web complexity -->
-
-To characterize the shape of the fitness landscape in simple and complex food webs, we fit separate statistical models to quantify individual selection surfaces acting on each trait. 
-We used generalized linear mixed models (GLMMs, @Bolker2009) with larval survival (0 or 1) as our response variable and measure of fitness. 
-In our full model, we specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models. 
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
+Also, egg predation is a minor source of mortality for galling insects in general (@Hawkins1997), thus we do not expect any prior egg predation to bias our estimates of observed larval densities.
+
+### Quantifying the Fitness Landscape
+
+To characterize the shape of the fitness landscape in simple and complex food webs, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
+We used a binomial error distribution (logit link function) since larval survival (0 or 1) was our response variable and measure of fitness.
+We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
+To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
 Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
 setting them to zero) to estimate selection gradients.
-We then used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
+Also, the fitness landscape assumes that traits distributions are multivariate normal.
+To better meet this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
+We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
+We used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
 We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
-To test whether selection gradients differed between treatments, we used our bootstrapped estimates to calculate the probability that selection gradients in the simple food web were larger/smaller than in the complex food web (i.e.
-the p-value).
-Together, we had survival estimates for 1,306 larva, 607 galls, 111 plants, and 8 plant genotypes.
-We report estimated selection gradients and the 95% confidence intervals in parentheses.
+Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value as this contains the majority of the trait distribution that selection is acting on.
+
+Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits.
+Any influence on trait expression would bias selection gradients acting on those traits.
+In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
+Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
+To estimate this bias, we subset our data to only include galls where there was variation in larval survival (1 > survival > 0) within the same gall.
+We then calculated "apparent" selection differentials for each gall by comparing the average chamber diameter of all larva (before "selection") to the average chamber diameter of surviving larva and analyzed separate one-sample t-tests for each food-web treatment.
+This analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
+In general, we found that our estimates of directional selection on chamber diameter were positively biased (Appendix).
+In other words, our analyses were overestimating the magnitude of selection acting on gall diameter.
+Therefore, we adjusted our estimates of directional selection on chamber diameter ($\beta_{diam}$) by subtracting the biased selection differentials.
+Note that selection gradients and selection differentials for chamber diameter were virtually the same (Appendix).
+
+### Quantifying Selective Constraints
+
+The strength and pattern of selective constraints can be measured as the slope and curvature of the fitness landscape (Arnold 1992).
+
+We can translate selection surfaces of individuals to the fitness landscape of a population
+
+To characterize the net effects of food-web complexity on the slope and curvature of *Iteomyia*'s fitness landscape, we took advantage of existing theory that links selection surfaces of individuals to the fitness landscape of the population (Phillips & Arnold 1998, Arnold 2003).
+Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
+$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
+whereas the curvature of the fitness landscape is a function of the directional, nonlinear, and correlational selection gradients: 
+$$\text{Curvature} = \gamma - \beta \beta^T$$
+where \gamma represents the matrix of nonlinear and correlational selection gradients:
+$$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
+Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
+Assuming that there is additive genetic variance and covariance between these traits under selection, then the slope and curvature of the fitness landscape give insight to how the population's mean trait value will change in the next generation as well as how additive genetic variance and covariance changes within a generation.
+
+While making quantitative predictions about trait evolution requires knowledge of the additive genetic variance and covariance of these traits, the slope and curvature of the fitness landscape still give qualitative insight to the evolutionary trajectory of a population.
+
+If we assume that there is additive genetic variance and covariance between these traits, then the matrix describing the curvature of the fitness landscape gives qualitative insight to the selective constraints acting on the population.
+For example, the diagonal of the curvature matrix dictates (qualitatively) whether the additive genetic variance in each trait will increase ($+$), decrease ($-$), or stay the same ($0$).
+Similarly, the off-diagonal of the curvature matrix dictates whether selection favors trait integration (positive covariance), a tradeoff (negative covariance), or no change in genetic covariance.
+In other words, we can get qualitative insight to how food-web complexity influences constraints on the fitness landscape by counting the number of negative sign values along the diagnoal (which imply a decrease in additive genetic variance) and the number of positive or negative signs along the off diagonal (which imply changes in additive genetic covariance that lead to either trait integration or tradeoffs).
+
 All analyses and visualizations were conducted in R (@R2018).
 
-```{r Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
-# note that I've switched to using the lme4 package to analyzing the GLMM
-
-# Directional selection ----
-beta_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+```{r Effects of food-web complexity on absolute fitness, cache=TRUE, include=FALSE}
+
+## Fit GLMMs
+null_glmer <- glmer(gall_survival ~ 1 +
                       (1|Genotype/Plant_Position/Gall_Number),
-                         data = control_df,
+                    data = gall_selection.df,
                     family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-summary(beta_control)
-overdisp_fun(beta_control)
-
-intensity_of_selection(beta_control)
-
-# Quadratic selection ----
-quad_control <- update(beta_control, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
-
-summary(quad_control)
-overdisp_fun(quad_control)
-
-# Correlational selection ----
-corr_control <- update(quad_control, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
-
-summary(corr_control)
-overdisp_fun(corr_control)
-
-# Mean fitness ----
-Wbar_control <- inverse_logit(fixef(update(beta_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
-
-# Confidence intervals ----
-boot_beta_control <- bootMer(beta_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_quad_control <- bootMer(quad_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_corr_control <- bootMer(corr_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-```
-
-```{r Selection Gradients - Simple Food Web, cache=TRUE, include=FALSE}
-
-# Directional selection ----
-beta_treatment <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+
+trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + #sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
+                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
                       (1|Genotype/Plant_Position/Gall_Number),
-                         data = treatment_df,
+                    data = gall_selection.df,
                     family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
 
-summary(beta_treatment)
-overdisp_fun(beta_treatment)
-
-intensity_of_selection(beta_treatment)
-
-# Quadratic selection ----
-quad_treatment <- update(beta_treatment, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
-
-summary(quad_treatment)
-overdisp_fun(quad_treatment)
-
-# Correlational selection ----
-corr_treatment <- update(quad_treatment, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
-
-summary(corr_treatment)
-overdisp_fun(corr_treatment)
-
-# Mean fitness ----
-Wbar_treatment <- inverse_logit(fixef(update(beta_treatment, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
-
-# Confidence intervals ----
-boot_beta_treatment <- bootMer(beta_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_quad_treatment <- bootMer(quad_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_corr_treatment <- bootMer(corr_treatment, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-```
-
-```{r Larval Parasitoids Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
-# note that I've switched to using the lme4 package to analyzing the GLMM
-
-ectoptoid_control_df <- filter(control_df,  ectos > 0 | pupa > 0) %>%
-  mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)),
-         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))),
-         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
-
-# Directional selection ----
-beta_ectoptoid_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+foodweb_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +
+                         Foodweb*(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
                          (1|Genotype/Plant_Position/Gall_Number),
-                         data = ectoptoid_control_df,
+                       data = gall_selection.df,
                        family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
 
-summary(beta_ectoptoid_control)
-overdisp_fun(beta_ectoptoid_control)
-
-intensity_of_selection(beta_ectoptoid_control)
-
-#vcov.merMod(beta_ectoptoid_control)
-
-# Quadratic selection ----
-quad_ectoptoid_control <- update(beta_ectoptoid_control, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
-
-summary(quad_ectoptoid_control)
-overdisp_fun(quad_ectoptoid_control)
-
-# Correlational selection ----
-corr_ectoptoid_control <- update(quad_ectoptoid_control, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
-
-summary(corr_ectoptoid_control)
-overdisp_fun(corr_ectoptoid_control)
-
-# Mean fitness ----
-Wbar_ectoptoid_control <- inverse_logit(fixef(update(beta_ectoptoid_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
-
-# Confidence intervals ----
-boot_beta_ectoptoid_control <- bootMer(beta_ectoptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_quad_ectoptoid_control <- bootMer(quad_ectoptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_corr_ectoptoid_control <- bootMer(corr_ectoptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-```
-
-```{r Egg Parasitoids Selection Gradients - Complex Food Web, cache=TRUE, include=FALSE}
-# note that I've switched to using the lme4 package to analyzing the GLMM
-
-eggptoid_control_df <- filter(control_df,  platy > 0 | pupa > 0) %>%
-  mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)),
-         sc.log.clutch_size = as.numeric(scale(log(gall_individuals))),
-         sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
-
-# Directional selection ----
-beta_eggptoid_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+## Test for overdispersion
+overdisp_fun(null_glmer)     # no evidence
+overdisp_fun(trait_glmer)    # no evidence
+overdisp_fun(foodweb_glmer)  # no evidence
+
+## Test for multicollinearity
+vif.mer(trait_glmer)
+vif.mer(foodweb_glmer)
+
+## Compare statistical summaries of each model
+summary(null_glmer)
+summary(trait_glmer)
+summary(foodweb_glmer)
+
+rsquared(trait_glmer, method="delta")
+rsquared(foodweb_glmer, method="delta")
+
+## Test statistical significance of effects ----
+
+# Overall, there is clear evidence that food-web treatment alters absolute fitness
+anova(null_glmer, trait_glmer, foodweb_glmer, test = "Chisq")
+
+## Parse out mechanisms of food-web effects ----
+foodweb_glmer_beta <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
                          (1|Genotype/Plant_Position/Gall_Number),
-                         data = eggptoid_control_df,
+                       data = gall_selection.df,
                        family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-summary(beta_eggptoid_control)
-overdisp_fun(beta_eggptoid_control)
-
-intensity_of_selection(beta_eggptoid_control)
-
-#vcov.merMod(beta_eggptoid_control)
-
-# Quadratic selection ----
-quad_eggptoid_control <- update(beta_eggptoid_control, .~. + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2))
-
-summary(quad_eggptoid_control)
-overdisp_fun(quad_eggptoid_control)
-
-# Correlational selection ----
-corr_eggptoid_control <- update(quad_eggptoid_control, .~. + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference)
-
-summary(corr_eggptoid_control)
-overdisp_fun(corr_eggptoid_control)
-
-# Mean fitness ----
-Wbar_eggptoid_control <- inverse_logit(fixef(update(beta_eggptoid_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
-
-# Confidence intervals ----
-boot_beta_eggptoid_control <- bootMer(beta_eggptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_quad_eggptoid_control <- bootMer(quad_eggptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-boot_corr_eggptoid_control <- bootMer(corr_eggptoid_control, FUN = Beta_avg_grad, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+test <- tidy(foodweb_glmer_beta, confint=T) %>%
+  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
+                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
+  select(-group)
+data.frame(term = test[,1], round(test[,-1],3))
+
+# Use drop1 to test highest order effects and visreg to visualize the effects
+# Use update to remove highest order effects from more complex models.
+
+# Evidence that food-web treatment alters nonlinear selection acting on female preference.
+Appears to be evidence for disruptive selection in complex food web, but a lack of nonlinear selection in the simple food web.
+drop1(foodweb_glmer, test="Chisq")
+summary(foodweb_glmer)
+visreg::visreg(foodweb_glmer, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
+
+foodweb_glmer_TEST <- update(foodweb_glmer, .~.
+-Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+vif.mer(foodweb_glmer_TEST)
+
+# Evidence of nonlinear selection acting on gall size. No evidence of disruptive selection.
+foodweb_glmer_2 <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
+drop1(foodweb_glmer_2, test="Chisq") 
+summary(foodweb_glmer_2)
+visreg::visreg(foodweb_glmer_2, xvar="sc.Diam", scale = "response")
+
+# Evidence of food-web treatment altering directional selection on clutch size; marginal evidence of correlational selection acting on gall size and clutch size.
+foodweb_glmer_3 <- update(foodweb_glmer_2, .~.
+-I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+drop1(foodweb_glmer_3, test="Chisq") 
+summary(foodweb_glmer_3)
+visreg::visreg(foodweb_glmer_3, xvar="sc.log.Clutch", by="Foodweb", scale="response")
+visreg::visreg(foodweb_glmer_3, xvar="sc.Diam", by="sc.log.Clutch", scale="response")
+visreg::visreg(foodweb_glmer_3, xvar="sc.log.Clutch", by="sc.Diam", scale="response") # a different perspective
+
+# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; evidence of directional selection acting on female preference
+foodweb_glmer_4 <- update(foodweb_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
+drop1(foodweb_glmer_4, test="Chisq") 
+summary(foodweb_glmer_4)
+visreg::visreg(foodweb_glmer_4, xvar="Foodweb", scale="response")
+visreg::visreg(foodweb_glmer_4, xvar="sc.Diam", scale="response")
+visreg::visreg(foodweb_glmer_4, xvar="sc.log1p.Pref", scale="response")
+```
+
+I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
+
+```{r REVISED Get Selection Gradients for GLMER}
+
+## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
+complex_mean_fitness <- mean(complex_predict)
+
+simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
+simple_mean_fitness <- mean(simple_predict)
+
+# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
+alt_predict <- predict(foodweb_glmer_beta, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
+alt_mean_fitness <- mean(alt_predict)
+complex_mean_brackets - alt_mean_brackets
+complex_mean_fitness - alt_mean_fitness
+
+# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
+# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
+foodweb_tidy_betas <- tidy(foodweb_glmer_beta, conf.int=T) %>%
+  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
+                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
+  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
+         Selection_form = c(NA,NA,rep("Directional",6)),
+         Multiplier = rep(1,8))
+
+foodweb_tidy_gammas <- tidy(foodweb_glmer, conf.int=T) %>%
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
+                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
+  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
+         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
+         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))
+
+get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
+  mutate(alpha = estimate, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = p.value) %>%
+  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
+
+complex_alphas <- filter(get_alphas, Foodweb == "Complex"); complex_alphas
+simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
+
+coefs_gradients <- data.frame(Variable = complex_alphas$term, 
+           a_complex = complex_alphas$alpha,
+           a_complex_2.5 = complex_alphas$alpha_2.5,
+           a_complex_97.5 = complex_alphas$alpha_97.5,
+           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
+           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
+           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5,
+           Selection_form = complex_alphas$Selection_form,                # doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier
+           Multiplier = complex_alphas$Multiplier) %>%                     
+  mutate(b_complex = complex_mean_brackets * a_complex / complex_mean_fitness * Multiplier,
+         b_complex_2.5 = complex_mean_brackets * a_complex_2.5 / complex_mean_fitness * Multiplier,
+         b_complex_97.5 = complex_mean_brackets * a_complex_97.5 / complex_mean_fitness * Multiplier,
+         b_simple = simple_mean_brackets * a_simple / simple_mean_fitness * Multiplier,
+         b_simple_2.5 = simple_mean_brackets * a_simple_2.5 / simple_mean_fitness * Multiplier,
+         b_simple_97.5 = simple_mean_brackets * a_simple_97.5 / simple_mean_fitness * Multiplier)
+
+bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5, Selection_form), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
+  ylab("Regression coefficient")
+
+## Modify to be directional, nonlinear, then correlational with legend in 4th area.
+## Modify so that axes have gamma and beta with the trait as a subscript
+bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5, Selection_form), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
+  ylab("Selection gradient")
+
+```
+
+```{r Get Selection Gradients for GLMER}
+
+## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
+complex_mean_fitness <- mean(complex_predict)
+
+simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
+simple_mean_fitness <- mean(simple_predict)
+
+# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
+alt_predict <- predict(foodweb_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
+alt_mean_fitness <- mean(alt_predict)
+complex_mean_brackets - alt_mean_brackets
+complex_mean_fitness - alt_mean_fitness
+
+# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
+# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
+foodweb_tidy_4 <- tidy(foodweb_glmer_4, conf.int=T) %>%
+  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log1p.Pref")) %>%
+  mutate(Foodweb = c("Complex","Simple","Common","Common"),
+         Selection_form = c(NA,NA,"Directional","Directional"),
+         Multiplier = c(1,1,1,1))
+
+foodweb_tidy_3 <- tidy(foodweb_glmer_3, conf.int=T) %>%
+  filter(term %in% c("sc.log.Clutch","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch")) %>%
+  mutate(Foodweb = c("Complex","Common","Common","Common","Simple"),
+         Selection_form = c("Directional","Correlational","Correlational","Correlational","Directional"),
+         Multiplier = c(1,1,1,1,1))
+
+foodweb_tidy_2 <- tidy(foodweb_glmer_2, conf.int=T) %>%
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref")) %>%
+  mutate(Foodweb = c("Common","Common","Common"),
+         Selection_form = c("Nonlinear","Nonlinear","Correlational"),
+         Multiplier = c(2,2,1))
+
+foodweb_tidy <- tidy(foodweb_glmer, conf.int=T) %>%
+  filter(term %in% c("I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)")) %>%
+  mutate(Foodweb = c("Complex","Simple"),
+         Selection_form = c("Nonlinear","Nonlinear"),
+         Multiplier = c(2,2))
+
+get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
+  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
+  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
+
+complex_alphas <- filter(get_alphas, Foodweb == "Complex"); complex_alphas
+simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
+common_alphas <- filter(get_alphas, Foodweb == "Common"); common_alphas
+
+## NEED TO DUPLICATE COMMON COEFFICIENTS, AS THIS WILL MAKE IT EASIEST TO KEEP THE SAME CODE AND CALCULATE SELECTION GRADIENTS
+
+# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
+coefs_gradients.complex_simple <- data.frame(Variable = complex_alphas$term, 
+           a_complex = complex_alphas$alpha,
+           a_complex_2.5 = complex_alphas$alpha_2.5,
+           a_complex_97.5 = complex_alphas$alpha_97.5,
+           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
+           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
+           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5,
+           Selection_form = complex_alphas$Selection_form,                # doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier
+           Multiplier = complex_alphas$Multiplier) %>%                     
+  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3) * Multiplier,
+         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3) * Multiplier,
+         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3) * Multiplier,
+         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3) * Multiplier,
+         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3) * Multiplier,
+         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3) * Multiplier)
+
+# duplicate common alpha coefficients for complex and simple food webs
+coefs_gradients.common <- data.frame(Variable = common_alphas$term, 
+           a_complex = common_alphas$alpha,
+           a_complex_2.5 = common_alphas$alpha_2.5,
+           a_complex_97.5 = common_alphas$alpha_97.5,
+           a_simple = common_alphas$alpha,        
+           a_simple_2.5 = common_alphas$alpha_2.5, 
+           a_simple_97.5 = common_alphas$alpha_97.5,
+           Selection_form = common_alphas$Selection_form,
+           Multiplier = common_alphas$Multiplier) %>% 
+  # for the selection gradients though, calculate them on the scale of relative fitness for each food-web treatment
+  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3) * Multiplier,
+         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3) * Multiplier,
+         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3) * Multiplier,
+         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3) * Multiplier,
+         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3) * Multiplier,
+         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3) * Multiplier)
+
+coefs_gradients <- bind_rows(coefs_gradients.complex_simple, coefs_gradients.common)
+
+bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  ylab("Regression coefficient")
+
+## Modify to be directional, nonlinear, then correlational with legend in 4th area.
+## Modify so that axes have gamma and beta with the trait as a subscript
+bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5, Selection_form), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
+  ylab("Selection gradient")
+
+```
+
+```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE}
+p<-ggplot(data=x, aes(x=y, y=x)) +
+geom_errorbar(aes(ymin=x-ci, ymax=x+ci)) +
+scale_x_discrete(breaks=c("label1","label2"),
+               labels = lapply(sprintf('$\\alpha^\\beta$'), TeX)
+p
+```
+
+What's the rationale for this test?
+First, we focus on galls where there is evidence of both survival and parasitism within the gall.
+The idea is that galls from the same clutch should be similar in size, therefore, any selection on diameter would be apparent.
+If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection gradient to be the result of confounding factors.
+Note that this is likely overestimates the effect of the confounding factor, since we are assuming that any heterogeneity in gall size (for this dataset) is due to a confounding effect of parasitism on gall diameter.
+Then, we can just subtract this value from the observed covariance between gall diameter and larval survival to adjust for the confounding effects of parasitism.
+This analysis should be relegated to the supplement.
+
+Would we expect any confounding effects on nonlinear selection?
+```{r Confounding effects of parasitism on gall size}
+## paired t-test approach. Weakness is that it only calculates the selection differential rather than the gradient, which is more meaningful for multivariate trait evolution
+pair_df <- gall_selection.df %>%
+  group_by(Foodweb, Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Foodweb, Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
+  # calculate mean phenotype at gall level (before selection)
+  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
+  # then filter surviving galls and calculate the mean phenotype (after selection)
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
+  # only retain distinct data points and calculate the difference (selection differential)
+  distinct(Foodweb, Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
+  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
+t.test(diff_sc.Diam ~ Foodweb, pair_df)
+t.test(pair_df$survive_mean_sc.Diam, pair_df$all_mean_sc.Diam, paired = T)
+
+complex_pair_df <- gall_selection.df %>%
+  filter(Foodweb=="Complex") %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
+  # calculate mean phenotype at gall level (before selection)
+  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
+  # then filter surviving galls and calculate the mean phenotype (after selection)
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
+  # only retain distinct data points and calculate the difference (selection differential)
+  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
+  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
+t.test(complex_pair_df$survive_mean_sc.Diam, complex_pair_df$all_mean_sc.Diam, paired = T)
+
+ectos_pair_df <- gall_selection.df %>%
+  filter(Foodweb=="Complex" & platy < 1) %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
+  # calculate mean phenotype at gall level (before selection)
+  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
+  # then filter surviving galls and calculate the mean phenotype (after selection)
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
+  # only retain distinct data points and calculate the difference (selection differential)
+  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
+  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
+t.test(ectos_pair_df$survive_mean_sc.Diam, ectos_pair_df$all_mean_sc.Diam, paired = T)
+
+simple_pair_df <- gall_selection.df %>%
+  filter(Foodweb=="Simple") %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
+  # calculate mean phenotype at gall level (before selection)
+  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
+  # then filter surviving galls and calculate the mean phenotype (after selection)
+  filter(gall_survival == 1) %>%
+  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
+  # only retain distinct data points and calculate the difference (selection differential)
+  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
+  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
+t.test(simple_pair_df$survive_mean_sc.Diam, simple_pair_df$all_mean_sc.Diam, paired = T)
+
+## selection gradient approach
+confounding_df <- gall_selection.df %>%
+  group_by(Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1)
+
+confounding_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
+                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
+                         (1|Genotype/Plant_Position/Gall_Number),
+                       data = confounding_df,
+                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+summary(confounding_glmer)
+
+## Replicate GLMM tests but with this confounding factor dataset ----
+
+# No effects
+drop1(confounding_glmer, test="Chisq")
+summary(confounding_glmer)
+
+# No effects on nonlinear selection acting on gall diameter, but also there is not much evidence for any effects.
+confounding_glmer_2 <- update(confounding_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
+drop1(confounding_glmer_2, test="Chisq") 
+summary(confounding_glmer_2)
+
+# Evidence of food-web treatment altering directional selection on clutch size; marginal evidence of correlational selection acting on gall size and clutch size.
+confounding_glmer_3 <- update(confounding_glmer_2, .~.
+-I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+drop1(confounding_glmer_3, test="Chisq") 
+summary(confounding_glmer_3)
+
+# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; evidence of directional selection acting on female preference
+confounding_glmer_4 <- update(confounding_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
+drop1(confounding_glmer_4, test="Chisq") 
+summary(confounding_glmer_4)
+
+fixef(foodweb_glmer_4)["sc.Diam"] - fixef(confounding_glmer_4)["sc.Diam"]
+
+confounding_predict <- predict(foodweb_glmer, type="response") # not subsetting the data to complex or simple food webs, since we didn't find a difference in this subset
+confounding_mean_brackets <- mean(confounding_predict * (1 - confounding_predict))
+confounding_mean_fitness <- mean(confounding_predict)
+
+# alternatively, this suggest that we are overestimating the selection gradient by this much...
+round(confounding_mean_brackets * fixef(confounding_glmer_4)["sc.Diam"] / confounding_mean_fitness, 3)
+
+diam_glmer <- glmer(gall_survival ~ Foodweb + sc.Diam +
+                         (1|Genotype/Plant_Position/Gall_Number),
+                       data = gall_selection.df,
+                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+# note that the selection gradient and differential are virtually the same for gall diameter, given the similarity in their alpha coefficients.
+fixef(diam_glmer)["sc.Diam"]
+fixef(foodweb_glmer_4)["sc.Diam"]
+
+# selection differentials
+round(complex_mean_brackets * fixef(diam_glmer)["sc.Diam"] / complex_mean_fitness, 3)
+round(simple_mean_brackets * fixef(diam_glmer)["sc.Diam"] / simple_mean_fitness, 3)
+```
+
+Appears to be selection for Platygaster to attack larva at high densities in more complex food webs (and a decrease in the variance).
+This may be a result of the poorer searching ability of parasitoids at very high gall densities, potentially due to saturation.
+This suggests that the fitness landscape may be dynamic because these selective effects (assuming there is heritable variation in the egg parasitoid) will change the following year.
+This could be an important discussion point to take into account for future work.
+This is different from simply altering the strength of selection, which will occur as species move along the fitness landscape, but this result suggests that the nature of the fitness landscape may actually be changing.
+For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
+```{r Selection on Platygaster Traits}
+platy_selection_df <- gall_selection.df %>%
+  filter(egg_parasitoid > 0) 
+platy_selection_df$Foodweb <- relevel(factor(platy_selection_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids
+
+platy_Diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), platy_selection_df)
+summary(platy_Diam)
+Anova(platy_Diam, test.statistic = "F")
+
+platy_Clutch <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), platy_selection_df)
+summary(platy_Clutch)
+Anova(platy_Clutch, test.statistic = "F")
+
+platy_Pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), platy_selection_df)
+summary(platy_Pref)
+Anova(platy_Pref, test.statistic = "F")
+
+## Test whether food-web complexity influences nonlinear selection with Levene's test for homogeneity of variance between groups
+# Note that this result should be interepreted cautiously since we cannot account for non-independence due to plant genotype, plant ID, or gall ID
+leveneTest(sc.Diam ~ Foodweb, platy_selection_df)
+leveneTest(sc.log.Clutch ~ Foodweb, platy_selection_df)
+leveneTest(sc.log1p.Pref ~ Foodweb, platy_selection_df)
+
+ggplot(platy_selection_df, aes(x=Foodweb, y=sc.Diam)) +
+  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
+  stat_summary(fun.y="mean", geom="point", color="black", size=3)
+
+ggplot(platy_selection_df, aes(x=Foodweb, y=sc.log.Clutch)) +
+  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
+  stat_summary(fun.y="mean", geom="point", color="black", size=3)
+
+ggplot(platy_selection_df, aes(x=Foodweb, y=sc.log1p.Pref)) +
+  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
+  stat_summary(fun.y="mean", geom="point", color="black", size=3)
+```
+
+## Table for Alpha regression coefficients
+\begin{table}[]
+\begin{tabular}{lcc}
+                                                                           \\ \hline
+                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
+\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
+$Diam$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Clutch$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Pref$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Diam^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Clutch^2$             & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Pref^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Diam:Clutch$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Diam:Pref$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$Clutch:Pref$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]              \\ \hline
+\end{tabular}
+\end{table}
+
+## Table for Iteomyia selection gradients
+\begin{table}[]
+\begin{tabular}{lcc}
+                                                                                  \\ \hline
+                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
+\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
+$\beta_{Diam}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\beta_{Clutch}$                  & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\beta_{Pref}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\gamma_{Diam,Diam}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\gamma_{Clutch,Clutch}$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\gamma_{Pref,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\gamma_{Diam,Clutch}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\gamma_{Diam,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
+$\gamma_{Clutch,Pref}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]           \\ \hline
+\end{tabular}
+\end{table}
+
+## Table for bias
+\begin{table}[]
+\begin{tabular}{lc}
+                                                                  \\ \hline
+\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
+Complex (All)                 & `r ` [`r `-`r `]  \\
+Complex (Larval guild)        & `r ` [`r `-`r `]  \\
+Simple (\textit{Platygaster}) & `r ` [`r `-`r `]                  \\ \hline
+\end{tabular}
+\end{table}
+
+## Table for Platygaster selection
+\begin{table}[]
+\begin{tabular}{lc}
+                                                                  \\ \hline
+\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
+$s_{Diam}$                      & `r ` [`r `-`r `]  \\
+$s_{Clutch}$                    & `r ` [`r `-`r `]  \\
+$s_{Pref}$                      & `r ` [`r `-`r `]  \\ 
+$s_{Diam,Diam}$                 & `r ` [`r `-`r `]  \\
+$s_{Clutch,Clutch}$             & `r ` [`r `-`r `]  \\
+$s_{Pref,Pref}$                 & `r ` [`r `-`r `]                \\ \hline
+\end{tabular}
+\end{table}
+
+```{r DUPLICATE for bootstrap test}
+
+## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
+complex_mean_fitness <- mean(complex_predict)
+
+simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
+simple_mean_fitness <- mean(simple_predict)
+
+# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
+alt_predict <- predict(foodweb_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
+alt_mean_fitness <- mean(alt_predict)
+complex_mean_brackets - alt_mean_brackets
+complex_mean_fitness - alt_mean_fitness
+
+foodweb_tidy_4 <- filter(tidy(bootMer(foodweb_glmer_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
+foodweb_tidy_3 <- filter(tidy(bootMer(foodweb_glmer_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
+                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
+                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
+foodweb_tidy_2 <- filter(tidy(bootMer(foodweb_glmer_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
+                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
+foodweb_tidy <- filter(tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
+                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
+                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
+                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
+## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs.
+This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
+#foodweb_tidy_4 <- filter(tidy(foodweb_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
+#foodweb_tidy_3 <- filter(tidy(foodweb_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
+#foodweb_tidy_2 <- filter(tidy(foodweb_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
+#foodweb_tidy <- filter(tidy(foodweb_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
+
+get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
+  mutate(alpha = round(statistic, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3)) %>%
+  select(term, alpha, alpha_2.5, alpha_97.5)
+
+complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
+simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
+
+# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
+coefs_gradients <- data.frame(Variable = complex_alphas$term, 
+           a_complex = complex_alphas$alpha,
+           a_complex_2.5 = complex_alphas$alpha_2.5,
+           a_complex_97.5 = complex_alphas$alpha_97.5,
+           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
+           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
+           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
+  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
+         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
+         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
+         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
+         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
+         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3))
+
+bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted")
+
+bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted")
+
+```
+
+Note that equation 3 in Phillips and Arnold 1998 is good justification for why quadratic selection cofficients should be multiplied by two (but not correlational ones?)
+
+The G-matrix is essentially a scalar.
+For my data, since there is no correlational selection, it doesn't matter if there is genetic covariance between the traits, as this will not effect the change in genetic covariances within a generation (because there is no selection).
+Also, the G_matrix does not qualitatively alter the conclusions that there will be a decrease in additive genetic variance in gall diameter due to the strong directional selection; however, there will be an increase in the additive genetic variance in female preference.
+Since this is an experiment, we can assume that the G-matrix is the same between treatments
+
+Remember that the diagonals refer to additive genetic CO-variances.
+Thus, positive or negative values for delta_G give insight to whether selection will act to integrate traits (positive covariance) or create trade-offs (negative covariance).
+
+Assuming that there is positive additive genetic variance and co-variance in these traits (i.e.
+all values of G-matrix are positive), then the curvature of the fitness landscape can give insight to qualitative changes in the G matrix.
+This is because the G-matrix acts as a scalar of changes in the fitness landscape.
+
+```{r Slope and Curvature of Fitness Landscape, include=FALSE}
+betas <- c(-0.5,-0.5,0.5)
+gammas_matrix <- matrix(c(-0.1, 0.0, 0.0,
+                          0.0, -0.1, 0.0,
+                          0.0, 0.0, -0.1), 
+                        nrow=3, byrow=T)
+
+## G-matrix ----
+# (1) Asssume equal additive genetic variance for all three traits
+# (2) Assume no additive genetic covariance
+# The first assumption may not be realistic, but violations of this assumption will not qualitatively alter our inferences about whether additive genetic variance will increase or decrease.
+Qualitative changes in additive genetic variance is only determined by the curvature of the fitness landscape.
+Violations of this assumption will only affect the rate of phenotypic evolution and magnitude of change in genetic variance.
+# The second assumption may also not be realistic; however, it will not affect our results because we found no evidence of correlational selection (therefore, there can be no change in genetic covariance).
+G_matrix <- matrix(c(1.0, 1.0, 1.0,
+                     1.0, 1.0, 1.0,
+                     1.0, 1.0, 1.0),
+                   nrow=3, byrow=T)
+
+# Equation 1 from Phillips and Arnold 1989, Evolution
+delta_z <- G_matrix %*% betas
+data.frame(trait = c("diam","clutch","pref"),
+           delta_z = delta_z)
+
+# Equation 2 from Phillips and Arnold 1989, Evolution
+delta_G <- G_matrix * (gammas_matrix - betas %*% t(betas)) * G_matrix
+delta_G
+```
+
+$$\text{Slope}_{complex} = \beta_{complex} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.4 \\ 0 \\ -0.3 \end{pmatrix}$$
+$$\text{Slope}_{simple} = \beta_{simple} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.3 \\ -0.2 \\ -0.3 \end{pmatrix}$$
+$$\gamma_{complex} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&-0.3 \end{pmatrix}$$
+$$\gamma_{simple} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
+$$\text{Curvature} = \gamma - \beta \beta^T$$
+$$\text{Curvature}_{complex} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
+$$\text{Curvature}_{simple} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
+
+```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE}
+
+## Fit GLMM
+
+platyecto_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
+                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
+                         (1|Genotype/Plant_Position/Gall_Number),
+                       data = filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1), # exclude cases of egg-parasitism from Complex food web
+                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+## Test for overdispersion
+overdisp_fun(platyecto_glmer) # no evidence
+
+## Compare statistical summaries of each model
+summary(platyecto_glmer)
+piecewiseSEM::rsquared(platyecto_glmer)
+
+## Parse out mechanisms of food-web effects ----
+# Use drop1 to test highest order effects and visreg to visualize the effects
+
+# Marginal evidence that larval parasitoids are the drivers of nonlinear selection acting on female preference (disruptive selection)
+drop1(platyecto_glmer, test="Chisq")
+summary(platyecto_glmer)
+visreg::visreg(platyecto_glmer, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
+
+# Marginal evidence of nonlinear selection acting on gall size. Marginal evidence of correlational selection acting on all traits.
+platyecto_glmer_2 <- update(platyecto_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
+drop1(platyecto_glmer_2, test="Chisq") 
+visreg::visreg(platyecto_glmer_2, xvar="sc.Diam", scale = "response") 
+# plot 3-way interaction?
+
+# Evidence of food-web treatment altering directional selection on clutch size
+platyecto_glmer_3 <- update(platyecto_glmer_2, .~.
+-I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+drop1(platyecto_glmer_3, test="Chisq") 
+summary(platyecto_glmer_3)
+visreg::visreg(platyecto_glmer_3, xvar="sc.log.Clutch", by="Foodweb", scale="response") # conflicting selection have net null effects in complex food web
+
+# No evidence of clear fitness effects of platy vs.
+ectos on absolute fitness; evidence of directional selection acting on gall size; no evidence of directional selection on clutch size (in complex food web); evidence of directional selection acting on female preference
+platyecto_glmer_4 <- update(platyecto_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
+drop1(platyecto_glmer_4, test="Chisq") 
+summary(platyecto_glmer_4)
+visreg::visreg(platyecto_glmer_4, xvar="Foodweb", scale="response")
+visreg::visreg(platyecto_glmer_4, xvar="sc.Diam", scale="response")
+visreg::visreg(platyecto_glmer_4, xvar="sc.log.Clutch", scale="response")
+visreg::visreg(platyecto_glmer_4, xvar="sc.log1p.Pref", scale="response")
+```
+
+```{r For platy ecto comparison}
+## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+complex_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
+complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
+complex_mean_fitness <- mean(complex_predict)
+
+simple_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
+simple_mean_fitness <- mean(simple_predict)
+
+# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
+alt_predict <- predict(platyecto_glmer_2, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
+alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
+alt_mean_fitness <- mean(alt_predict)
+complex_mean_brackets - alt_mean_brackets
+complex_mean_fitness - alt_mean_fitness
+
+platyecto_tidy_4 <- filter(tidy(platyecto_glmer_4, conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
+platyecto_tidy_3 <- filter(tidy(platyecto_glmer_3, conf.int=T), 
+                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
+                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
+platyecto_tidy_2 <- filter(tidy(platyecto_glmer_2, conf.int=T), 
+                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
+platyecto_tidy <- filter(tidy(platyecto_glmer, conf.int=T), 
+                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
+                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
+                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
+## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs.
+This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
+#platyecto_tidy_4 <- filter(tidy(platyecto_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
+#platyecto_tidy_3 <- filter(tidy(platyecto_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
+#platyecto_tidy_2 <- filter(tidy(platyecto_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
+#platyecto_tidy <- filter(tidy(platyecto_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
+
+get_alphas <- bind_rows(platyecto_tidy_4, platyecto_tidy_3, platyecto_tidy_2, platyecto_tidy) %>% 
+  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
+  select(term, alpha, alpha_2.5, alpha_97.5, P)
+
+complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
+simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
+
+# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
+coefs_gradients <- data.frame(Variable = complex_alphas$term, 
+           a_complex = complex_alphas$alpha,
+           a_complex_2.5 = complex_alphas$alpha_2.5,
+           a_complex_97.5 = complex_alphas$alpha_97.5,
+           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
+           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
+           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
+  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
+         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
+         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
+         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
+         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
+         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3)) %>%
+  filter(Variable != "(Intercept)")
+
+select(coefs_gradients, Variable, a_complex:a_simple_97.5)
+select(coefs_gradients, Variable, b_complex:b_simple_97.5)
+
+bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted")
+
+bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
+  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
+  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted")
+
+inverse_logit(complex_alphas$alpha[1]) - complex_mean_fitness # small difference in mean fitness estimates compared to intercept in complex food web
+inverse_logit(complex_alphas$alpha[1] + simple_alphas$alpha[1]) - simple_mean_fitness # larger difference in mean fitness estimates from intercept in simple food web, unclear why...perhaps because the mean phenotypes don't match up as nicely?
+```
+
+```{r}
+## Calculating same coefficients as for simple vs. complex food web
+
+## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+ecto_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex" & platy < 1), type="response")
+ecto_mean_brackets <- mean(ecto_predict * (1 - ecto_predict))
+ecto_mean_fitness <- mean(ecto_predict)
+
+platy_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+platy_mean_brackets <- mean(platy_predict * (1 - platy_predict))
+platy_mean_fitness <- mean(platy_predict)
+
+# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
+alt_predict <- predict(platyecto_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex" & platy < 1), type="response")
+alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
+alt_mean_fitness <- mean(alt_predict)
+ecto_mean_brackets - alt_mean_brackets
+ecto_mean_fitness - alt_mean_fitness
+
+# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
+# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
+platyecto_tidy_4 <- tidy(platyecto_glmer_4, conf.int=T) %>%
+  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log1p.Pref")) %>%
+  mutate(platyecto = c("ecto","platy","Common","Common"),
+         Selection_form = c(NA,NA,"Directional","Directional"),
+         Multiplier = c(1,1,1,1))
+
+platyecto_tidy_3 <- tidy(platyecto_glmer_3, conf.int=T) %>%
+  filter(term %in% c("sc.log.Clutch","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch")) %>%
+  mutate(platyecto = c("ecto","Common","Common","Common","platy"),
+         Selection_form = c("Directional","Correlational","Correlational","Correlational","Directional"),
+         Multiplier = c(1,1,1,1,1))
+
+platyecto_tidy_2 <- tidy(platyecto_glmer_2, conf.int=T) %>%
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref")) %>%
+  mutate(platyecto = c("Common","Common","Common"),
+         Selection_form = c("Nonlinear","Nonlinear","Correlational"),
+         Multiplier = c(2,2,1))
+
+platyecto_tidy <- tidy(platyecto_glmer, conf.int=T) %>%
+  filter(term %in% c("I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)")) %>%
+  mutate(platyecto = c("ecto","platy"),
+         Selection_form = c("Nonlinear","Nonlinear"),
+         Multiplier = c(2,2))
+
+get_platyecto_alphas <- bind_rows(platyecto_tidy_4, platyecto_tidy_3, platyecto_tidy_2, platyecto_tidy) %>% 
+  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
+  select(term, platyecto, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
+
+ecto_alphas <- filter(get_platyecto_alphas, platyecto == "ecto"); ecto_alphas
+platy_alphas <- filter(get_platyecto_alphas, platyecto == "platy"); platy_alphas
+common_platyecto_alphas <- filter(get_platyecto_alphas, platyecto == "Common"); common_platyecto_alphas
+
+coefs_gradients.ecto_platy <- data.frame(Variable = ecto_alphas$term, 
+           a_ecto = ecto_alphas$alpha,
+           a_ecto_2.5 = ecto_alphas$alpha_2.5,
+           a_ecto_97.5 = ecto_alphas$alpha_97.5,
+           a_platy = ecto_alphas$alpha + platy_alphas$alpha,        # the baseline is the coefficient in the ecto food web, therefore we simply add the corresponding coefficients from the platy food web to get the coefficients on the same scale as the ecto web
+           a_platy_2.5 = ecto_alphas$alpha + platy_alphas$alpha_2.5, # same addition process for confidence intervals
+           a_platy_97.5 = ecto_alphas$alpha + platy_alphas$alpha_97.5,
+           Selection_form = ecto_alphas$Selection_form,                # doesn't matter whether platy_ or ecto_alphas is chosen for Selection_form or Multiplier
+           Multiplier = ecto_alphas$Multiplier) %>%                     
+  mutate(b_ecto = round(ecto_mean_brackets * a_ecto / ecto_mean_fitness, 3) * Multiplier,
+         b_ecto_2.5 = round(ecto_mean_brackets * a_ecto_2.5 / ecto_mean_fitness, 3) * Multiplier,
+         b_ecto_97.5 = round(ecto_mean_brackets * a_ecto_97.5 / ecto_mean_fitness, 3) * Multiplier,
+         b_platy = round(platy_mean_brackets * a_platy / platy_mean_fitness, 3) * Multiplier,
+         b_platy_2.5 = round(platy_mean_brackets * a_platy_2.5 / platy_mean_fitness, 3) * Multiplier,
+         b_platy_97.5 = round(platy_mean_brackets * a_platy_97.5 / platy_mean_fitness, 3) * Multiplier)
+
+coefs_gradients.ecto_platy.common <- data.frame(Variable = common_platyecto_alphas$term, 
+           a_ecto = common_platyecto_alphas$alpha,
+           a_ecto_2.5 = common_platyecto_alphas$alpha_2.5,
+           a_ecto_97.5 = common_platyecto_alphas$alpha_97.5,
+           a_platy = common_platyecto_alphas$alpha,        
+           a_platy_2.5 = common_platyecto_alphas$alpha_2.5, 
+           a_platy_97.5 = common_platyecto_alphas$alpha_97.5,
+           Selection_form = common_platyecto_alphas$Selection_form,
+           Multiplier = common_platyecto_alphas$Multiplier) %>% 
+  # for the selection gradients though, calculate them on the scale of relative fitness for each food-web treatment
+  mutate(b_ecto = round(ecto_mean_brackets * a_ecto / ecto_mean_fitness, 3) * Multiplier,
+         b_ecto_2.5 = round(ecto_mean_brackets * a_ecto_2.5 / ecto_mean_fitness, 3) * Multiplier,
+         b_ecto_97.5 = round(ecto_mean_brackets * a_ecto_97.5 / ecto_mean_fitness, 3) * Multiplier,
+         b_platy = round(platy_mean_brackets * a_platy / platy_mean_fitness, 3) * Multiplier,
+         b_platy_2.5 = round(platy_mean_brackets * a_platy_2.5 / platy_mean_fitness, 3) * Multiplier,
+         b_platy_97.5 = round(platy_mean_brackets * a_platy_97.5 / platy_mean_fitness, 3) * Multiplier)
+
+coefs_gradients.ecto_platy <- bind_rows(coefs_gradients.ecto_platy, coefs_gradients.ecto_platy.common)
+
+bind_rows(mutate(select(coefs_gradients.ecto_platy, Variable, a=a_ecto, a_2.5=a_ecto_2.5, a_97.5=a_ecto_97.5), platyecto = "ecto"),
+          mutate(select(coefs_gradients.ecto_platy, Variable, a=a_platy, a_2.5=a_platy_2.5, a_97.5=a_platy_97.5), platyecto = "platy")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=platyecto, color=platyecto)) +
+  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  ylab("Regression coefficient")
+
+## Modify to be directional, nonlinear, then correlational with legend in 4th area.
+## Modify so that axes have gamma and beta with the trait as a subscript
+bind_rows(mutate(select(coefs_gradients.ecto_platy, Variable, b=b_ecto, b_2.5=b_ecto_2.5, b_97.5=b_ecto_97.5, Selection_form), platyecto = "ecto"),
+          mutate(select(coefs_gradients.ecto_platy, Variable, b=b_platy, b_2.5=b_platy_2.5, b_97.5=b_platy_97.5, Selection_form), platyecto = "platy")) %>%
+  filter(Variable != "(Intercept)") %>%
+  ggplot(., aes(x = Variable, fill=platyecto, color=platyecto)) +
+  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
+  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
+  ylab("Selection gradient")
+```
+
+Compared to the GLM, the GLMM gives the same inferences about the effect of food-web treatment.
+The main difference was that there was stronger evidence of correlational selection, but no evidence that this correlational selection varied among food-web treatments.
+Still, this stronger evidence for correlational selection should be interpreted with caution since the GLM does not account for the non-indepedence of these fitness estimates.
+```{r Compare GLMM to GLM}
+## Fit GLMs. Dispersion parameter was ~1, so I just used a binomial model. 
+null_glm <- glm(gall_survival ~ sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
+                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2),
+                    data = gall_selection.df,
+                    family = binomial(link = logit))
+
+foodweb_glm <- glm(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
+                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)),
+                       data = gall_selection.df,
+                       family = binomial(link = logit))
+
+## Compare statistical summaries of each model
+summary(null_glm)
+summary(foodweb_glm)
+piecewiseSEM::rsquared(null_glm)
+piecewiseSEM::rsquared(foodweb_glm)
+
+## Test statistical significance of effects ----
+
+# Overall, there is clear evidence that food-web treatment alters absolute fitness
+anova(null_glm, foodweb_glm, test = "Chisq")
+
+## Parse out mechanisms of food-web effects ----
+# Use drop1 to test highest order effects and visreg to visualize the effects
+
+# Evidence that food-web treatment alters nonlinear selection acting on female preference. Appears to be evidence for disruptive selection in complex food web.
+# Unique to GLM: marginal evidence for food-web treatment altering nonlinear selection on clutch size
+drop1(foodweb_glm, test="Chisq")
+visreg::visreg(foodweb_glm, xvar="sc.log1p.Pref", by="Foodweb", scale = "response") 
+visreg::visreg(foodweb_glm, xvar="sc.log.Clutch", by="Foodweb", scale = "response")
+
+# Evidence of nonlinear selection acting on gall size. No evidence of disruptive selection.
+# No unique effects in the glm
+foodweb_glm_2 <- update(foodweb_glm, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
+drop1(foodweb_glm_2, test="Chisq") 
+visreg::visreg(foodweb_glm_2, xvar="sc.Diam", scale = "response")
+
+# Evidence of food-web treatment altering directional selection on clutch size
+# Unique to GLM: there is stronger support for correlational selection acting on gall size and clutch size; also, there is evidence for correlational selection acting on clutch size and female preference.
+foodweb_glm_3 <- update(foodweb_glm_2, .~.
+-I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+drop1(foodweb_glm_3, test="Chisq") 
+visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="Foodweb", scale="response")
+visreg::visreg(foodweb_glm_3, xvar="sc.Diam", by="sc.log.Clutch", scale="response")
+visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="sc.Diam", scale="response") # a different perspective
+visreg::visreg(foodweb_glm_3, xvar="sc.log1p.Pref", by="sc.log.Clutch", scale="response")
+visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="sc.log1p.Pref", scale="response")
+
+# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; no evidence of directional selection on clutch size (in complex food web); evidence of directional selection acting on female preference
+# No unique effects in the glm
+foodweb_glm_4 <- update(foodweb_glm_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
+drop1(foodweb_glm_4, test="Chisq") 
+visreg::visreg(foodweb_glm_4, xvar="Foodweb", scale="response")
+visreg::visreg(foodweb_glm_4, xvar="sc.Diam", scale="response")
+visreg::visreg(foodweb_glm_4, xvar="sc.log.Clutch", scale="response")
+visreg::visreg(foodweb_glm_4, xvar="sc.log1p.Pref", scale="response")
+```
+
+```{r Get Selection Gradients for GLM}
+complex_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
+complex_mean_fitness <- mean(complex_predict)
+
+simple_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
+simple_mean_fitness <- mean(simple_predict)
+
+foodweb_tidy_4 <- filter(tidy(foodweb_glm_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
+foodweb_tidy_3 <- filter(tidy(foodweb_glm_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
+foodweb_tidy_2 <- filter(tidy(foodweb_glm_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
+foodweb_tidy <- filter(tidy(foodweb_glm), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
+
+get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
+  mutate(alpha = round(estimate, 3), alpha_SE = round(std.error, 3), P = round(p.value, 3)) %>%
+  select(term, alpha, alpha_SE, P)
+
+complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
+simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
+
+# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
+data.frame(Variable = complex_alphas$term, 
+           alpha_complex = complex_alphas$alpha, 
+           alpha_simple = complex_alphas$alpha + simple_alphas$alpha) %>% # add the corresponding coefficients to get the coefficients on the same scale as the complex web)
+  mutate(beta_complex = round(complex_mean_brackets * alpha_complex / complex_mean_fitness, 3),
+         beta_simple = round(simple_mean_brackets * alpha_simple / simple_mean_fitness, 3)) %>%
+  filter(Variable != "(Intercept)")
+
+inverse_logit(complex_alphas$alpha[1]) - complex_mean_fitness # small difference in mean fitness estimates compared to intercept in complex food web
+inverse_logit(complex_alphas$alpha[1] + simple_alphas$alpha[1]) - simple_mean_fitness # larger difference in mean fitness estimates from intercept in simple food web, unclear why...perhaps because the mean phenotypes don't match up as nicely?
 ```
@@
 mean(ectoptoid_control_df$pupa)
-```
-
-```{r Partition Selection Gradients in Complex Food Web, include=F}
-summary_beta_treatment <- data.frame(
-  Ptoids = "All",
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Simple",
-  Model = "GLMM",
-  Type = "Beta",
-  Estimate = round(Beta_avg_grad(beta_treatment),3),
-  lower_2.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-summary_beta_control <- data.frame(
-  Ptoids = "All",
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Type = "Beta",
-  Estimate = round(Beta_avg_grad(beta_control),3),
-  lower_2.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-summary_beta_ectoptoid_control <- data.frame(
-  Ptoids = "Ectos",
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Type = "Beta",
-  Estimate = round(Beta_avg_grad(beta_ectoptoid_control),3),
-  lower_2.5 = round(apply(boot_beta_ectoptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_beta_ectoptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-summary_beta_eggtpoid_control <- data.frame(
-  Ptoids = "Egg",
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Type = "Beta",
-  Estimate = round(Beta_avg_grad(beta_eggptoid_control),3),
-  lower_2.5 = round(apply(boot_beta_eggptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_beta_eggptoid_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-bind_rows(summary_beta_treatment, summary_beta_control, summary_beta_ectoptoid_control, summary_beta_eggtpoid_control) %>%
-  arrange(Phenotype)
-```
-
-```{r include=FALSE}
-mean_log1p <- function(x) mean(log1p(x), na.rm=T)
-sd_na.rm <- function(x) sd(log1p(x), na.rm=T)
-
-## Platygaster
-platy_trait_control <- filter(control_df, platy > 0) %>%
-  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
-
-platy_trait_treatmeant <- filter(treatment_df, platy > 0) %>%
-  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
-
-bind_rows(platy_trait_control, platy_trait_treatmeant)
-
-(platy_trait_treatmeant$Gall_Height_mm_mean_log1p - platy_trait_control$Gall_Height_mm_mean_log1p)/platy_trait_control$Gall_Height_mm_sd_na.rm
-
-(platy_trait_treatmeant$gall_individuals_mean_log1p - platy_trait_control$gall_individuals_mean_log1p)/platy_trait_control$gall_individuals_sd_na.rm
-
-(platy_trait_treatmeant$Density_per_100_shoots_mean_log1p - platy_trait_control$Density_per_100_shoots_mean_log1p)/platy_trait_control$Density_per_100_shoots_sd_na.rm
-
-## Pupa
-pupa_trait_control <- filter(control_df, pupa > 0) %>%
-  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
-
-pupa_trait_treatmeant <- filter(treatment_df, pupa > 0) %>%
-  summarise_at(vars("Gall_Height_mm","gall_individuals","Density_per_100_shoots"), funs(mean_log1p, sd_na.rm))
-
-bind_rows(pupa_trait_control, pupa_trait_treatmeant)
-
-(pupa_trait_treatmeant$Gall_Height_mm_mean_log1p - pupa_trait_control$Gall_Height_mm_mean_log1p)/pupa_trait_control$Gall_Height_mm_sd_na.rm
-
-(pupa_trait_treatmeant$gall_individuals_mean_log1p - pupa_trait_control$gall_individuals_mean_log1p)/pupa_trait_control$gall_individuals_sd_na.rm
-
-(pupa_trait_treatmeant$Density_per_100_shoots_mean_log1p - pupa_trait_control$Density_per_100_shoots_mean_log1p)/pupa_trait_control$Density_per_100_shoots_sd_na.rm
-```
-
-```{r Table of Selection Gradients}
-
-## Summarize Control Selection Gradients ----
-summary_beta_control <- data.frame(
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Type = "Beta",
-  Estimate = round(Beta_avg_grad(beta_control),3),
-  lower_2.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)
-summary_quad_control <- data.frame(
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Type = "Quadratic",
-  Estimate = 2*round(Beta_avg_grad(quad_control),3)[-c(1:3)],
-  lower_2.5 = 2*round(apply(boot_quad_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:3)],
-  upper_97.5 = 2*round(apply(boot_quad_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:3)])
-
-summary_corr_control <- data.frame(
-  Phenotype = c("Diam,Clutch", "Diam,Pref", "Clutch,Pref"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Type = "Correlational",
-  Estimate = round(Beta_avg_grad(corr_control),3)[-c(1:6)],
-  lower_2.5 = round(apply(boot_corr_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:6)],
-  upper_97.5 = round(apply(boot_corr_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:6)])
-
-## Summarize Treatment Selection Gradients ----
-summary_beta_treatment <- data.frame(
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Simple",
-  Model = "GLMM",
-  Type = "Beta",
-  Estimate = round(Beta_avg_grad(beta_treatment),3),
-  lower_2.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_beta_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-# doubled quadratic estimates to make comparable to directional selection gradients (Stinchcombe et al. 2008, Evolution)
-summary_quad_treatment <- data.frame(
-  Phenotype = c("Gall diameter", "Clutch size", "Female preference"),
-  Food_Web = "Simple",
-  Model = "GLMM",
-  Type = "Quadratic",
-  Estimate = 2*round(Beta_avg_grad(quad_treatment),3)[-c(1:3)],
-  lower_2.5 = 2*round(apply(boot_quad_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:3)],
-  upper_97.5 = 2*round(apply(boot_quad_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:3)])
-
-summary_corr_treatment <- data.frame(
-  Phenotype = c("Diam,Clutch", "Diam,Pref", "Clutch,Pref"),
-  Food_Web = "Simple",
-  Model = "GLMM",
-  Type = "Correlational",
-  Estimate = round(Beta_avg_grad(corr_treatment),3)[-c(1:6)],
-  lower_2.5 = round(apply(boot_corr_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3)[-c(1:6)],
-  upper_97.5 = round(apply(boot_corr_treatment$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3)[-c(1:6)])
-
-bind_rows(summary_beta_control, summary_beta_treatment) %>% arrange(Phenotype)
-bind_rows(summary_quad_control, summary_quad_treatment) %>% arrange(Phenotype)
-bind_rows(summary_corr_control, summary_corr_treatment) %>% arrange(Phenotype)
 ```
@@
 
-<!-- Consider exploring whether there is a linear or non-linear relationship between food-web complexity and the strength of selection.
-I think I could do this simply by calculating the index of food-web complexity measured on each plant.
-Perhaps it would also be good to measure to calculate the selection gradient observed on each plant -->
+We found that changes in food-web complexity fundamentally altered the shape of *Iteomyia*'s fitness landscape (statistical test for trait vs. food-web*traits).
+
+For example, there was directional selection for larger gall diameter in both complex and simple food webs, but the magnitude of the selection gradient was X-fold higher in the complex food web.
+The steeper selection gradient in the complex food web was not a result of stronger covariance between gall diameter and larval survival, but a result of average larval survival being X-fold lower in the complex food web.
+
+We observed directional selection for smaller clutch sizes in the simple food web, but no evidence of selection on this trait in the complex food web.
+The absence of selection in the complex food web appeared to be a result of conflicting selection pressures imposed by the egg parasitoid *Platygaster* and the guild of larval parasitoids (statistical test focus on egg vs.
+larval parasitoids).
+Specifically, larval parasitoids actually impose directional selection for larger clutch sizes (selection gradient), but the net effect is no selection when both parasitoid guilds are present.
+
+We found evidence of disruptive selection acting on female preference in the complex food web, but no evidence of nonlinear selection on this trait in the simple food web.
+Similar to clutch size, these differences in nonlinear selection appeared to be due to different selection pressures imposed by egg and larval parasitoids.
+
+**Characterizing the slope and curvature of the fitness landscape**
+
+**Old**
 Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
-In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$ 
-`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`
-; simple $\beta_{diam}=$
-`r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`
-)(Fig. \ref{fig:Univariate_Landscapes}A). 
+In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`; simple $\beta_{diam}=$ `r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`)(Fig.
+\ref{fig:Univariate_Landscapes}A).
+
+In the complex food web, we found that there was no selection acting on clutch size
+
 In simple food webs, both clutch size and female preference experience directional selection, with smaller clutch sizes ($\beta_{clutch}=$

### 2018-09-20 revising_dataset.R

@@ -18,7 +18,7 @@ library(cowplot) # for clean multi-panel plots
 ## read in data frames ----
 
 # parasitism data
-vLG.df <- read.csv("MBGalls/VLGCollect2013.csv") %>% tbl_df
+vLG.df <- read.csv("VLGCollect2013.csv") %>% tbl_df
 
 # plant information
 plant.info <- read.csv("Willow Garden Positions.csv") %>%
@@ -139,6 +139,14 @@ write_csv(ind.tree.data, "gall_selection_data.csv")
 table(ind.tree.data$Treatment.focus, ind.tree.data$Treatment)
 table(ind.tree.data$Treatment, ind.tree.data$Location) # note that there aren't any situations with "marked" ground galls, which makes this comparison difficult.
 table(ind.tree.data$Treatment, ind.tree.data$phenology)
+
+ind.tree.data.ALL <- IGP.df.ind.galln %>%
+  ungroup() %>%
+  filter(Gall_Number != "unk") %>%
+  #select(Treatment.focus, Treatment, Location, phenology, Genotype, Plant_Position, Gall_Number:Density_per_100_shoots, gall_individuals,
+  #       platy, pupa, ectos, platy.ectos, none.none, total) %>%
+  droplevels.data.frame() 
+write_csv(ind.tree.data.ALL, "gall_selection_data_ALL.csv")
 
 ######################## EVERYTHING BELOW IS OLD, BUT MAYBE USEFUL ##########################################
 

### 2018-09-20 ms_complexity_selection.Rmd
updated global tests of GLMMs

@@
 
-## Fit GLMMs
+## FIT GLMMs ---
+
+# Null Model
 null_glmer <- glmer(gall_survival ~ 1 +
@@
 
-trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + #sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
+# Model assuming no effect of food-web treatment
+trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + 
                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
@@
 
+# Model allowing for an effect of food-web treatment
 foodweb_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +
@@
 
-## Test for overdispersion
-overdisp_fun(null_glmer)     # no evidence
-overdisp_fun(trait_glmer)    # no evidence
-overdisp_fun(foodweb_glmer)  # no evidence
-
-## Test for multicollinearity
-vif.mer(trait_glmer)
-vif.mer(foodweb_glmer)
-
-## Compare statistical summaries of each model
-summary(null_glmer)
-summary(trait_glmer)
-summary(foodweb_glmer)
-
-rsquared(trait_glmer, method="delta")
-rsquared(foodweb_glmer, method="delta")
+## STATISTICAL TESTS ----
+
+# There is clear evidence that the traits we have measured influence larva survival
+anova(null_glmer, trait_glmer, test="Chisq")
+rsquared(list(null_glmer, trait_glmer))
+
+# There is also clear evidence that our food-web treatment altered natural selection
+anova(trait_glmer, foodweb_glmer)
+rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment
+
+## EVALUATING MODEL ASSUMPTIONS ---
+
+# There is no evidence of overdispersion
+overdisp_fun(foodweb_glmer)
+
+# There are no clear patterns in the distribution of the residuals (= good)
+visreg(foodweb_glmer)
 
@@
 anova(null_glmer, trait_glmer, foodweb_glmer, test = "Chisq") 
-
-## Parse out mechanisms of food-web effects ----
-foodweb_glmer_beta <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-test <- tidy(foodweb_glmer_beta, confint=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
-  select(-group)
-data.frame(term = test[,1], round(test[,-1],3))
-
-# Use drop1 to test highest order effects and visreg to visualize the effects
-# Use update to remove highest order effects from more complex models.
-
-# Evidence that food-web treatment alters nonlinear selection acting on female preference.
-Appears to be evidence for disruptive selection in complex food web, but a lack of nonlinear selection in the simple food web.
-drop1(foodweb_glmer, test="Chisq")
-summary(foodweb_glmer)
-visreg::visreg(foodweb_glmer, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
-
-foodweb_glmer_TEST <- update(foodweb_glmer, .~.
--Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-vif.mer(foodweb_glmer_TEST)
-
-# Evidence of nonlinear selection acting on gall size. No evidence of disruptive selection.
-foodweb_glmer_2 <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(foodweb_glmer_2, test="Chisq") 
-summary(foodweb_glmer_2)
-visreg::visreg(foodweb_glmer_2, xvar="sc.Diam", scale = "response")
-
-# Evidence of food-web treatment altering directional selection on clutch size; marginal evidence of correlational selection acting on gall size and clutch size.
-foodweb_glmer_3 <- update(foodweb_glmer_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(foodweb_glmer_3, test="Chisq") 
-summary(foodweb_glmer_3)
-visreg::visreg(foodweb_glmer_3, xvar="sc.log.Clutch", by="Foodweb", scale="response")
-visreg::visreg(foodweb_glmer_3, xvar="sc.Diam", by="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glmer_3, xvar="sc.log.Clutch", by="sc.Diam", scale="response") # a different perspective
-
-# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; evidence of directional selection acting on female preference
-foodweb_glmer_4 <- update(foodweb_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(foodweb_glmer_4, test="Chisq") 
-summary(foodweb_glmer_4)
-visreg::visreg(foodweb_glmer_4, xvar="Foodweb", scale="response")
-visreg::visreg(foodweb_glmer_4, xvar="sc.Diam", scale="response")
-visreg::visreg(foodweb_glmer_4, xvar="sc.log1p.Pref", scale="response")
 ```

### 2018-09-20 ms_complexity_selection.Rmd
updated coefficient estimates from full model. Need to revise so that coefficients that are not influenced by food web do not receive separate estimates.

@@
 
+I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
+
 ```{r Effects of food-web complexity on absolute fitness, cache=TRUE, include=FALSE}
@@
 
+# Model excluding quadratic and trait:trait interactions. This is necessary for accurately estimating directional selection gradients (Betas, Lande and Arnold 1983)
+betas_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
+                         (1|Genotype/Plant_Position/Gall_Number),
+                       data = gall_selection.df,
+                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
 ## STATISTICAL TESTS ----
@@
 # There is also clear evidence that our food-web treatment altered natural selection
-anova(trait_glmer, foodweb_glmer)
+foodweb_test <- tidy(anova(trait_glmer, foodweb_glmer, test="Chisq"))
 rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment
@@
 visreg(foodweb_glmer)
-
-## Test statistical significance of effects ----
-
-# Overall, there is clear evidence that food-web treatment alters absolute fitness
-anova(null_glmer, trait_glmer, foodweb_glmer, test = "Chisq") 
-```
-
-I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
-
-```{r REVISED Get Selection Gradients for GLMER}
-
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+```
+
+```{r Get Selection Gradients for GLMER}
+
+## METHOD OF JANZEN AND STERN 1998 ----
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
 complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
@@
 
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(foodweb_glmer_beta, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
+alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
 alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
 alt_mean_fitness <- mean(alt_predict)
-complex_mean_brackets - alt_mean_brackets
-complex_mean_fitness - alt_mean_fitness
-
-# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
-# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
-foodweb_tidy_betas <- tidy(foodweb_glmer_beta, conf.int=T) %>%
+test_mean_brackets <- complex_mean_brackets
+test_mean_fitness <- complex_mean_fitness
+test_mean_brackets - alt_mean_brackets # virtually the same
+test_mean_fitness - alt_mean_fitness # virtually the same
+
+# Tidy data for beta terms
+foodweb_tidy_betas <- tidy(betas_glmer, conf.int=T) %>%
   filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
@@
 
+# Tidy data for gamma terms.
+Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al.
+2008)
 foodweb_tidy_gammas <- tidy(foodweb_glmer, conf.int=T) %>%
@@
 
+# Combine and tidy the regression (alpha) coefficients
 get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
@@
 
-We found that changes in food-web complexity fundamentally altered the shape of *Iteomyia*'s fitness landscape (statistical test for trait vs. food-web*traits).
+We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ($\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).
 

### 2018-09-21 manuscript/manuscript.tex
getting organized

--- 2018-06-07 AmNat_MS_template.tex
@@
 
-\title{Template and Guidelines for Using \LaTeX{} in \textit{The~American~Naturalist} }
+\title{Phenotypic evolution is less constrained in complex food webs}
 
@@
 
-\author{Owen E. Cook$^{1,\ast}$ \\ 
-Generic H. Collaborator$^{2,\dag}$ \\ 
-Additional Q. Expert$^{3}$}
+\author{Matthew A. Barbour$^{1,2,\ast}$ \\ 
+Christopher J. Greyson-Gaito$^{1,3}$ \\ 
+Arezoo Sootodeh$^{3}$ \\
+Brendan Lock$^{4} \\
+Jordi Bascompte$^{2}}
 
@@
 
-\noindent{} 1. University of Chicago, Chicago, Illinois 60637;
+\noindent{} 1. University of British Columbia, Department of Zoology, Vancouver, British Columbia V6T 1Z4, Canada;
 
-\noindent{} 2. University of Toronto, Toronto, Ontario M5S 1A5, Canada;
+\noindent{} 2. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;
 
-\noindent{} 3. Middle Eastern Technical University, Çankaya, Ankara 06800, Turkey.
+\noindent{} 3. University of Guelph, Department of Integrative Biology, Guelph, Ontario N1G 2W1, Canada;
 
-\noindent{} $\ast$ Corresponding author; e-mail: amnat@uchicago.edu.
+\noindent{} 3. Humboldt State University, Department of Biological Sciences, Arcata, California 95521, USA.
 
-\noindent{} $\dag$ Deceased.
+\noindent{} $\ast$ Corresponding author; e-mail: matthew.barbour@ieu.uzh.ch.
 

### 2018-09-21 temporary_morgue/Am_Nat_Template.Rnw
getting organized

--- 2018-06-07 AmNat_MS_template.tex
@@
 \begin{document}
+\SweaveOpts{concordance=TRUE}
 
@@
 Mauris posuere malesuada lacus, at elementum lacus auctor eu (fig~\ref{Fig:Jumps}A).
+
+<<echo=FALSE>>=
+## Load required libraries ----
+library(car)        # for homogeneity of variance test
+library(tidyverse)  # for managing data
+library(cowplot)    # pretty default ggplots
+library(broom)      # for tidying multiple linear models
+library(visreg)     # for quick visualizations of model effects
+library(viridis)    # for color palette
+library(lme4)       # for generalized linear mixed models
+library(piecewiseSEM) # for calculating model R-square
+library(latex2exp)  # using Latex notation for axes labels
+
+## Load and manage data ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  # convert appropriate variables to characters instead of integers
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
+         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
+         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
+         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
+         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots)))) 
+dim(gall_selection.df)
+
+table(gall_selection.df$Treatment.focus, gall_selection.df$ectos)
+
+## Create separate datasets for quantifying selection gradients ----
+#control_df <- gall_selection.df %>%
+#  filter(Treatment.focus == "Control") #%>%
+  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
+  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
+  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
+  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
+  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+#dim(control_df)
+
+#treatment_df <- gall_selection.df %>%
+#  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+#dim(treatment_df)
+  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
+  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
+  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
+  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
+  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+
+#mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.
+
+## Custom functions to avoid repetitive code ----
+
+## Test for overdispersion
+overdisp_fun <- function(model) {
+  ## number of variance parameters in 
+  ##   an n-by-n variance-covariance matrix
+  vpars <- function(m) {
+    nrow(m)*(nrow(m)+1)/2
+  }
+  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
+  rdf <- nrow(model.frame(model))-model.df
+  rp <- residuals(model,type="pearson")
+  Pearson.chisq <- sum(rp^2)
+  prat <- Pearson.chisq/rdf
+  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
+  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
+}
+
+## Test for multicollinearity (from: https://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/)
+vif.mer <- function (fit) {
+    ## adapted from rms::vif
+
+    v <- vcov(fit)
+    nam <- names(fixef(fit))
+
+    ## exclude intercepts
+    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
+    if (ns > 0) {
+        v <- v[-(1:ns), -(1:ns), drop = FALSE]
+        nam <- nam[-(1:ns)]
+    }
+
+    d <- diag(v)^0.5
+    v <- diag(solve(v/(d %o% d)))
+    names(v) <- nam
+    v
+}
+
+## Transform logit to probability
+inverse_logit <- function(x) exp(x)/(1+exp(x))
+
+## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
+Beta_avg_grad <- function(.) {
+  mean_fitness <- mean(predict(., type = "response")) 
+  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
+  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
+}
+
+## Calculate intensity/opportunity for selection
+intensity_of_selection <- function(.) {
+  mean_fitness <- mean(predict(., type = "response")) # inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
+  relative_fitness <- predict(., type = "response") / mean_fitness 
+  var(relative_fitness)
+}
+
+## Compute the matrix describing the curvature of the fitness landscape
+curvature_fitness.landscape <- function(gammas, # matrix of nonlinear and correlational selection gradients 
+                                        betas){ # vector of directional selection gradients
+  gammas - betas %*% t(betas)
+}
+
+## Bootstrap fitness estimates
+bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
+  model_matrix <- model.matrix(formula(fixed_effects), newdata)
+
+  # Absolute fitness
+  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))
+
+  if(is.null(bootstraps) == FALSE){
+    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  absolute_fitness_df <- data.frame(newdata, 
+                    average = get_absolute_fitness(logistic_model), 
+                    lower = get_intervals_absolute_fitness[1, ],
+                    upper = get_intervals_absolute_fitness[2, ],
+                    t(get_bootstraps_absolute_fitness$t))
+  } else {
+    absolute_fitness_df <- data.frame(newdata, 
+                    average = get_absolute_fitness(logistic_model))
+  }
+
+  # Relative fitness
+  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))
+
+  if(is.null(bootstraps) == FALSE){
+    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+
+  relative_fitness_df <- data.frame(newdata, 
+                    average = get_relative_fitness(logistic_model), 
+                    lower = get_intervals_relative_fitness[1, ],
+                    upper = get_intervals_relative_fitness[2, ],
+                    t(get_bootstraps_relative_fitness$t))
+  } else {
+      relative_fitness_df <- data.frame(newdata, 
+                    average = get_relative_fitness(logistic_model))
+  }
+
+  # Organize data
+  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
+}
+
+## Number of bootstrap replicates
+n_boots_analysis <- 30
+n_boots_plots <- 100
+@
+
+bootstraps $=Sexpr{sqrt(2)}$
 

### 2018-09-21 temporary_morgue/Appendix_complexity_selection/Appendix_complexity_selection.Rmd
getting organized

---
title: Short Paper
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    footnote: Corresponding Author
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
abstract: |
  This is the abstract.

  It consists of two paragraphs.

journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: mybibfile.bib
output: rticles::elsevier_article
---

_Text based on elsarticle sample manuscript, see [http://www.elsevier.com/author-schemas/latex-instructions#elsarticle](http://www.elsevier.com/author-schemas/latex-instructions#elsarticle)_

## Exploring Multicollinearity

```{r Exploring Multicollinearity}

predictor_df <- gall_selection.df %>%
  mutate(sc.Diam_2 = sc.Diam^2, sc.log.Clutch_2 = sc.log.Clutch^2, sc.log1p.Pref_2 = sc.log1p.Pref^2,
         sc.Diam_sc.log.Clutch = sc.Diam*sc.log.Clutch, sc.Diam_sc.log1p.Pref = sc.Diam*sc.log1p.Pref, sc.log.Clutch_sc.log1p.Pref = sc.log.Clutch*sc.log1p.Pref) %>%
  select(Foodweb, sc.Diam, sc.log.Clutch, sc.log1p.Pref, sc.Diam_2:sc.log.Clutch_sc.log1p.Pref)

predictor_df_2 <- gall_selection.df %>%
  mutate(sc.Diam = poly(sc.Diam,2)[,1], sc.log.Clutch = poly(sc.log.Clutch,2)[,1], sc.log1p.Pref = poly(sc.log1p.Pref,2)[,1],
         sc.Diam_2 = poly(sc.Diam,2)[,2], sc.log.Clutch_2 = poly(sc.log.Clutch,2)[,2], sc.log1p.Pref_2 = poly(sc.log1p.Pref,2)[,2],
         sc.Diam_sc.log.Clutch = sc.Diam*sc.log.Clutch, sc.Diam_sc.log1p.Pref = sc.Diam*sc.log1p.Pref, sc.log.Clutch_sc.log1p.Pref = sc.log.Clutch*sc.log1p.Pref) %>%
  select(Foodweb, sc.Diam, sc.log.Clutch, sc.log1p.Pref, sc.Diam_2:sc.log.Clutch_sc.log1p.Pref)

GGally::ggpairs(predictor_df, mapping = aes(color = Foodweb), 
                columns = c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","sc.Diam_2","sc.log.Clutch_2","sc.log1p.Pref_2"),
                columnLabels = c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2"),
                lower = list(continuous = "smooth"),
                diag = NULL)

GGally::ggpairs(predictor_df_2, mapping = aes(color = Foodweb), 
                columns = c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","sc.Diam_2","sc.log.Clutch_2","sc.log1p.Pref_2"),
                columnLabels = c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2"),
                lower = list(continuous = "smooth"),
                diag = NULL)

## Inspect correlations among predictors for nonlinear selection coefficients
GGally::ggpairs(predictor_df, mapping = aes(color = Foodweb), 
                columns = c("sc.Diam_2","sc.log.Clutch_2","sc.log1p.Pref_2","sc.Diam_sc.log.Clutch","sc.Diam_sc.log1p.Pref","sc.log.Clutch_sc.log1p.Pref"),
                columnLabels = c("Diam^2","Clutch^2","Pref^2","Diam,Clutch","Diam,Pref","Clutch,Pref"),
                lower = list(continuous = "smooth"),
                diag = NULL)
GGally::ggpairs(predictor_df_2, mapping = aes(color = Foodweb), 
                columns = c("sc.Diam_2","sc.log.Clutch_2","sc.log1p.Pref_2","sc.Diam_sc.log.Clutch","sc.Diam_sc.log1p.Pref","sc.log.Clutch_sc.log1p.Pref"),
                columnLabels = c("Diam^2","Clutch^2","Pref^2","Diam,Clutch","Diam,Pref","Clutch,Pref"),
                lower = list(continuous = "smooth"),
                diag = NULL)

GGally::ggpairs(predictor_df, mapping = aes(color = Foodweb), 
                columns = c("sc.Diam","sc.log.Clutch","sc.log1p.Pref_2","sc.Diam_sc.log.Clutch","sc.Diam_sc.log1p.Pref","sc.log.Clutch_sc.log1p.Pref"),
                columnLabels = c("Diam","Clutch","Pref","Diam,Clutch","Diam,Pref","Clutch,Pref"),
                lower = list(continuous = "smooth"),
                diag = NULL)
GGally::ggpairs(predictor_df_2, mapping = aes(color = Foodweb), 
                columns = c("sc.Diam","sc.log.Clutch","sc.log1p.Pref_2","sc.Diam_sc.log.Clutch","sc.Diam_sc.log1p.Pref","sc.log.Clutch_sc.log1p.Pref"),
                columnLabels = c("Diam","Clutch","Pref","Diam,Clutch","Diam,Pref","Clutch,Pref"),
                lower = list(continuous = "smooth"),
                diag = NULL)

ggplot(gall_selection.df, aes(x=Gall_Height_mm, y=Gall_Height_mm^2)) + geom_point() + geom_smooth(method="lm")
ggplot(gall_selection.df, aes(x=sc.Diam, y=sc.Diam^2, color=Foodweb)) + geom_point() + geom_smooth(method="lm")
ggplot(gall_selection.df, aes(x=sc.Diam, y=poly(sc.Diam,2)[,2], color=Foodweb)) + geom_point() + geom_smooth(method="lm")
ggplot(gall_selection.df, aes(x=sc.log.Clutch, y=sc.log.Clutch^2, color=Foodweb)) + geom_point() + geom_smooth(method="lm")
ggplot(gall_selection.df, aes(x=sc.log1p.Pref, y=sc.log1p.Pref^2, color=Foodweb)) + geom_point() + geom_smooth(method="lm")
ggplot(gall_selection.df, aes(x=sc.log1p.Pref, y=poly(sc.log1p.Pref,2)[,2], color=Foodweb)) + geom_point() + geom_smooth(method="lm") + scale_x_continuous(limits = c(-2.5,1))
ggplot(filter(gall_selection.df, Density_per_100_shoots > 0), aes(x=sc.log1p.Pref, y=sc.log1p.Pref^2, color=Foodweb)) + geom_point() + geom_smooth(method="lm")

hist(gall_selection.df$sc.log1p.Pref)

poly(gall_selection.df$sc.Diam,2)
```

## Table of means and sd of traits used in these analyses

```{r Table of Means and SD of Phenotypic Traits}
trait_table <- gall_selection.df %>%
  transmute(Diam = Gall_Height_mm, Clutch = gall_individuals, ln.Clutch = log(Clutch),
            Pref = Density_per_100_shoots, ln1p.Pref = log1p(Pref)) %>%
  summarise_all(funs(mean, sd)) %>%
  t(.) %>%
  data.frame(Value = .[,1], Trait = rownames(.)) %>%
  separate(Trait, into = c("Trait","Statistic"), sep="_") %>%
  select(Trait, Statistic, Value) %>%
  spread(key = Statistic, value = Value)

traits <- data.frame(trait_table, row.names = trait_table$Trait) %>% .[,-1] %>% round(.,2)
traits
```

\begin{table}[]
\begin{tabular}{lc}
                                                                              \\ \hline
\textbf{Trait}                                   & \textbf{Mean $\pm$ SD}     \\ \hline
\textbf{Chamber diameter}                        & `r traits["Diam","mean"]`$\pm$`r traits["Diam","sd"]`  \\
Clutch size                                      & `r traits["Clutch","mean"]`$\pm$`r traits["Clutch","sd"]`  \\
\boldmath$\ln(\textbf{Clutch size})$             & `r traits["ln.Clutch","mean"]`$\pm$`r traits["ln.Clutch","sd"]`  \\
Female preference                                & `r traits["Pref","mean"]`$\pm$`r traits["Pref","sd"]`  \\ 
\boldmath$\ln(1 + \textbf{Female preference})$   & `r traits["ln1p.Pref","mean"]`$\pm$`r traits["ln1p.Pref","sd"]`            \\ \hline
\end{tabular}
\end{table}

### 2018-09-21 temporary_morgue/GRC_2018.Rmd
getting organized

---
title: "From ecosystems to genes: an experimental test of how network structure affects the fitness landscape"
output: 
  revealjs::revealjs_presentation:
    theme: default
    transition: fade
    self_contained: true

---

# Scaling From Genes to Ecosystems

Insert figure I've made before, thinking about how genes scale up to affect the structure of species-interaction networks.

# Framework for Linking Ecosystems to Genes?

Image flipping network structure to affecting a species to visualize how network structure could contrain or facilitate phenotypic and genetic change

At the same time, I think it's equally important to start thinking about how network structure feedsback to constrain or facilitate evolutionary change. This is what I want to spend my time discussing today

# Fitness Landscape Unifies Ecology & Evolution

```{r McPeek Fig 1, out.width = "400px"}
knitr::include_graphics("McPeek_Fig_1.png")
```

Discuss why I think is the unifying concept for ecology and evolutionary biology

# Inferring the Fitness Landscape

$$w = z$$

Nice theory that links individual selection surfaces to the fitness landscape (Arnold 2003)

We can then use standard tools to estimate the local shape of the fitness landscape. e.g. Slope = Beta (same as selective surface); Curvature is equal to Gamm - Beta*Transpose(Beta)

# Willow Garden

```{r Garden pic, echo=FALSE, out.width = "400px"}
knitr::include_graphics("willow_garden_2011-enhanced-1226.jpeg")
```

Common garden was located at Humboldt Bay National Wildlife Refuge in northern California, and it consisted of 26 genotypes that were sampled from the local willow population.

# Experimental Manipulation of Network Structure

Photos illustrating how I manipulated the food web and what the resulting community looks like.

# Measuring Gall Phenotypes

1. Gall Diameter (mm)
2. Clutch size (no. larva per gall)
3. Oviposition preference (no. larva per 100 shoots)

Include an image next to these to illustrate what each of these phenotypes mean. Use the image that has the arrows pointing to measurment of gall diameter and to individual larva

# Quantifying the Fitness Landscape

# Absolute Fitness

```{r Univariate Landscapes}
library(qwraps2)
library(cowplot)

lazyload_cache_dir("elsevier_test/elsevier_test_cache/latex")

# Get legend
RF_uni_legend <- get_legend(RF_uni_size)

# Make plots
RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none",
                                              axis.text.x = element_text(size=10),
                                              axis.title.x = element_text(size=11)), 
                       RF_uni_clutch + theme(legend.position = "none", 
                                          axis.title.y = element_blank(), axis.text.y = element_blank(),
                                          axis.text.x = element_text(size=10),
                                          axis.title.x = element_text(size=11)),
                       RF_uni_pref + theme(legend.position = "none", 
                                        axis.title.y = element_blank(), axis.text.y = element_blank(),
                                        axis.text.x = element_text(size=10),
                                        axis.title.x = element_text(size=11)),
                       labels = "AUTO", ncol = 3, align='hv')

RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
RF_gradients
#RF_uni_plots
```

First draw attention to the mean differences and then to the slopes (the different components)

Build up each of the figures

```{r}
library(qwraps2)
library(cowplot)
library(tidyverse)

lazyload_cache_dir("elsevier_test/elsevier_test_cache/latex")

uni_breaks <- c(0.1,0.5,1)

# Gall size 
AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.clutch_size, -sc.female_preference) %>%
  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Gall diameter (SDs)") +
  ylab("Population mean fitness") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
  coord_cartesian(ylim=c(0.07,1))
#AF_uni_size
  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")

# Clutch size
AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.female_preference) %>%
  gather(ID, absolute_fitness, -sc.clutch_size, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Clutch size (SDs)") +
  ylab("Population mean fitness") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
  coord_cartesian(ylim=c(0.07,1))
  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")

# Female preference
AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
  select(-sc.gall_size, -sc.clutch_size) %>%
  gather(ID, absolute_fitness, -sc.female_preference, -Food_Web) %>%
  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
  ggplot(., aes(x=sc.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
  geom_line() +
  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
  xlab("Female preference (SDs)") +
  ylab("Population mean fitness") +
  scale_color_manual(values = treatment_colors, name = "Food web") +
  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
  coord_cartesian(ylim=c(0.07,1))
  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")

# Get legend
AF_uni_legend <- get_legend(AF_uni_size)

# Make plots
AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
                       AF_uni_clutch + theme(legend.position = "none", 
                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
                       AF_uni_pref + theme(legend.position = "none", 
                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
                       labels = "AUTO", ncol = 3, align='hv')

#AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
#AF_gradients
AF_uni_plots
save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
```

```{r Multivariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
library(viridis)

lazyload_cache_dir("elsevier_test/elsevier_test_cache/latex")

my_breaks <- c(0.2,0.4,0.6,0.8)

# Size x Preference
AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Female preference (SDs)") +
  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),

# Size x Clutch
AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Gall diameter (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),

# Clutch x Preference
AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
  geom_raster() +
  facet_wrap(~Food_Web) +
  xlab("Female preference (SDs)") +
  ylab("Clutch size (SDs)") +
  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),

# Get legend
AF_landscape_legend <- get_legend(AF_plot_size.x.preference)

# Format plots
AF_landscape_plots <- plot_grid(
  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
  AF_plot_size.x.preference + theme(legend.position = "none"), 
  nrow=2, align="hv", labels = "AUTO")
AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
AF_landscape_2d
#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
```

# Relative Fitness

- Univariate landscapes

Now show the same univariate plots but with the relative fitness on the y-axis.

First put the absolute landscape next to relative fitness to show the link between the two, then show the rest of the landscapes.

# Multivariate Perspective

Here is a different representation of these univariate landscapes.

Describe the axes for the figures.

# Conclusions

- Natural selection is stronger, yet less constrained in the complex food web.

# Open Questions

-

# Note

in presentation for GRC - emphasize also that the opportunity for selection is X% higher in the complex vs. simple environment, although that may be an artifact of the study (excluding parasitoids reduced mean fitness, which is likely why selection on gall diameter is twice as much).

### 2018-09-21 temporary_morgue/GRC_2018_test.Rmd
getting organized

--- 2018-09-21 temporary_morgue/GRC_2018.Rmd
@@
 ---
-title: "From ecosystems to genes: an experimental test of how network structure affects the fitness landscape"
+title: "**From Ecosystems to Genes**: Experimental Test of how Network Structure Shapes the Fitness Landscape"
 output: 
   revealjs::revealjs_presentation:
-    theme: default
     transition: fade
-    self_contained: true
-
+    self_contained: false
+    reveal_plugins: ["notes"]
 ---
 
-# Scaling From Genes to Ecosystems
+## Scaling from Genes to Ecosystems
 
@@
 
-# Framework for Linking Ecosystems to Genes?
+^Note: Blah blah blah
 
-Image flipping network structure to affecting a species to visualize how network structure could contrain or facilitate phenotypic and genetic change
+## Slide with Bullets
 
-At the same time, I think it's equally important to start thinking about how network structure feedsback to constrain or facilitate evolutionary change.
-This is what I want to spend my time discussing today
+```{r Slide with Bullets Header}
+cat("
+<style>
+h1 {
+   color: red;
+}
+</style>
+")
+```
 
-# Fitness Landscape Unifies Ecology & Evolution
+- Bullet 1
+- Bullet 2
+- Bullet 3
 
-```{r McPeek Fig 1, out.width = "400px"}
+## Slide with R Code and Output
+
+```{r}
+summary(cars)
+```
+
+## Slide with Plot
+
+```{r, echo=FALSE}
+plot(cars)
+```
+
+## Fitness Landscape Unifies Ecology & Evolution
+
+```{r McPeek Fig 1, out.width = "400px", echo=FALSE}
 knitr::include_graphics("McPeek_Fig_1.png")
@@
 
-# Inferring the Fitness Landscape
+## Univariate
 
-$$w = z$$
-
-Nice theory that links individual selection surfaces to the fitness landscape (Arnold 2003)
-
-We can then use standard tools to estimate the local shape of the fitness landscape. e.g. Slope = Beta (same as selective surface); Curvature is equal to Gamm - Beta*Transpose(Beta)
-
-# Willow Garden
-
-```{r Garden pic, echo=FALSE, out.width = "400px"}
-knitr::include_graphics("willow_garden_2011-enhanced-1226.jpeg")
-```
-
-Common garden was located at Humboldt Bay National Wildlife Refuge in northern California, and it consisted of 26 genotypes that were sampled from the local willow population.
-
-# Experimental Manipulation of Network Structure
-
-Photos illustrating how I manipulated the food web and what the resulting community looks like.
-
-# Measuring Gall Phenotypes
-
-1. Gall Diameter (mm)
-2. Clutch size (no. larva per gall)
-3. Oviposition preference (no. larva per 100 shoots)
-
-Include an image next to these to illustrate what each of these phenotypes mean. Use the image that has the arrows pointing to measurment of gall diameter and to individual larva
-
-# Quantifying the Fitness Landscape
-
-# Absolute Fitness
-
-```{r Univariate Landscapes}
+```{r Univariate Landscapes, echo=FALSE, message=FALSE}
 library(qwraps2)
@@
 ```
-
-First draw attention to the mean differences and then to the slopes (the different components)
-
-Build up each of the figures
-
-```{r}
-library(qwraps2)
-library(cowplot)
-library(tidyverse)
-
-lazyload_cache_dir("elsevier_test/elsevier_test_cache/latex")
-
-uni_breaks <- c(0.1,0.5,1)
-
-# Gall size 
-AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.clutch_size, -sc.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Population mean fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-#AF_uni_size
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Clutch size
-AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.clutch_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Population mean fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Female preference
-AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.clutch_size) %>%
-  gather(ID, absolute_fitness, -sc.female_preference, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
-  ylab("Population mean fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Get legend
-AF_uni_legend <- get_legend(AF_uni_size)
-
-# Make plots
-AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
-                       AF_uni_clutch + theme(legend.position = "none", 
-                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       AF_uni_pref + theme(legend.position = "none", 
-                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       labels = "AUTO", ncol = 3, align='hv')
-
-#AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
-#AF_gradients
-AF_uni_plots
-save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
-```
-
-```{r Multivariate Absolute Fitness Landscapes, echo=FALSE, message=FALSE, warning=FALSE}
-library(viridis)
-
-lazyload_cache_dir("elsevier_test/elsevier_test_cache/latex")
-
-my_breaks <- c(0.2,0.4,0.6,0.8)
-
-# Size x Preference
-AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.female_preference, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Female preference (SDs)") +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
-
-# Size x Clutch
-AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
-
-# Clutch x Preference
-AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.female_preference, y=sc.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
-
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
-  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
-  AF_plot_size.x.preference + theme(legend.position = "none"), 
-  nrow=2, align="hv", labels = "AUTO")
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
-```
-
-# Relative Fitness
-
-- Univariate landscapes
-
-Now show the same univariate plots but with the relative fitness on the y-axis.
-
-First put the absolute landscape next to relative fitness to show the link between the two, then show the rest of the landscapes.
-
-# Multivariate Perspective
-
-Here is a different representation of these univariate landscapes.
-
-Describe the axes for the figures.
-
-# Conclusions
-
-- Natural selection is stronger, yet less constrained in the complex food web.
-
-# Open Questions
-
--
-
-# Note
-
-in presentation for GRC - emphasize also that the opportunity for selection is X% higher in the complex vs.
-simple environment, although that may be an artifact of the study (excluding parasitoids reduced mean fitness, which is likely why selection on gall diameter is twice as much).

### 2018-09-21 temporary_morgue/Manuscript/Manuscript.Rmd
getting organized

--- 2018-09-20 ms_complexity_selection.Rmd
@@
 ---
-title: Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore 
+title: Phenotypic evolution is less constrained in complex food webs
 author:
@@
     address: Humboldt State University, Department of Biological Sciences, 1 Harpst St., Arcata, CA, 95521, USA
-abstract: "Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
-Similarly, fitness landscapes provide a mechanistic link between population and evolutionary ecology, as they describe the influence of natural selection on phenotypic variation.
-It remains unclear, however, how the network structure of species interactions shapes the fitness landscape.
-Understanding this relationship is likely key for developing a predictive ecology across scales of biological organization.
-To examine the relationship between network structure and the fitness landscape, we conducted a field experiment that manipulated the network of trophic interactions (simple vs.
-complex) influencing the fitness of an insect herbivore.
-We then quantified the fitness landscape of herbivores in each treatment by measuring herbivore survival as a function of multiple phenotypic traits.
-We found that more traits were under selection in the simple vs.
-complex trophic network.
-This occurred because different natural enemies impose different selection pressures on herbivore traits, thereby minimizing relative fitness differences among herbivore phenotypes in the complex network.
-Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change."
-
+abstract: |
+  This is the abstract.
+
+  It consists of two paragraphs.
+
+journal: "An awesome journal"
+date: "`r Sys.Date()`"
 bibliography: mybibfile.bib
@@
 ## Number of bootstrap replicates
-n_boots_analysis <- 30 #1000
+n_boots_analysis <- 30
 n_boots_plots <- 100
@@
 Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
+
+```{r LATEX NEED TO CHECK two, eval=FALSE, include=FALSE}
 $$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
@@
 $$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
+```
+
 Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
@@
 anova(null_glmer, trait_glmer, test="Chisq")
-rsquared(list(null_glmer, trait_glmer))
 
@@
 
-```{r Get Selection Gradients for GLMER}
+```{r Get Selection Gradients for GLMER, include=FALSE}
 
@@
 
-```{r Get Selection Gradients for GLMER}
-
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
+```{r Parametric Bootstrapping of Regression Coefficients and Selection Gradients, cache=TRUE, include=FALSE}
+
+## DUPLICATE ABOVE EXCEPT MODIFY FOR BOOTMER
+
+## METHOD OF JANZEN AND STERN 1998 ----
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
 complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
@@
 
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(foodweb_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
+alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
 alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
 alt_mean_fitness <- mean(alt_predict)
-complex_mean_brackets - alt_mean_brackets
-complex_mean_fitness - alt_mean_fitness
-
-# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
-# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
-foodweb_tidy_4 <- tidy(foodweb_glmer_4, conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log1p.Pref")) %>%
-  mutate(Foodweb = c("Complex","Simple","Common","Common"),
-         Selection_form = c(NA,NA,"Directional","Directional"),
-         Multiplier = c(1,1,1,1))
-
-foodweb_tidy_3 <- tidy(foodweb_glmer_3, conf.int=T) %>%
-  filter(term %in% c("sc.log.Clutch","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch")) %>%
-  mutate(Foodweb = c("Complex","Common","Common","Common","Simple"),
-         Selection_form = c("Directional","Correlational","Correlational","Correlational","Directional"),
-         Multiplier = c(1,1,1,1,1))
-
-foodweb_tidy_2 <- tidy(foodweb_glmer_2, conf.int=T) %>%
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c("Common","Common","Common"),
-         Selection_form = c("Nonlinear","Nonlinear","Correlational"),
-         Multiplier = c(2,2,1))
-
-foodweb_tidy <- tidy(foodweb_glmer, conf.int=T) %>%
-  filter(term %in% c("I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)")) %>%
-  mutate(Foodweb = c("Complex","Simple"),
-         Selection_form = c("Nonlinear","Nonlinear"),
-         Multiplier = c(2,2))
-
-get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
+test_mean_brackets <- complex_mean_brackets
+test_mean_fitness <- complex_mean_fitness
+test_mean_brackets - alt_mean_brackets # virtually the same
+test_mean_fitness - alt_mean_fitness # virtually the same
+
+# Tidy data for beta terms
+foodweb_tidy_betas <- tidy(bootMer(betas_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T) %>%
+  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
+                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
+  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
+         Selection_form = c(NA,NA,rep("Directional",6)),
+         Multiplier = rep(1,8))
+
+# Tidy data for gamma terms.
+Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al.
+2008)
+foodweb_tidy_gammas <- tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T) %>%
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
+                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
+  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
+         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
+         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))
+
+# Combine and tidy the regression (alpha) coefficients
+get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
+  mutate(alpha = statistic, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = ifelse(conf.low*conf.high > 0, "<0.05","NS")) %>% # change 'alpha = estimate' to 'alpha = statistic' for bootstrap.
+Multiply confidence intervals to determine whether the cofficient is signficantly different from zero.
   select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
@@
 simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
-common_alphas <- filter(get_alphas, Foodweb == "Common"); common_alphas
-
-## NEED TO DUPLICATE COMMON COEFFICIENTS, AS THIS WILL MAKE IT EASIEST TO KEEP THE SAME CODE AND CALCULATE SELECTION GRADIENTS
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-coefs_gradients.complex_simple <- data.frame(Variable = complex_alphas$term, 
+
+coefs_gradients <- data.frame(Variable = complex_alphas$term, 
            a_complex = complex_alphas$alpha,
@@
            Multiplier = complex_alphas$Multiplier) %>%                     
-  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3) * Multiplier,
-         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3) * Multiplier,
-         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3) * Multiplier,
-         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3) * Multiplier,
-         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3) * Multiplier,
-         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3) * Multiplier)
-
-# duplicate common alpha coefficients for complex and simple food webs
-coefs_gradients.common <- data.frame(Variable = common_alphas$term, 
-           a_complex = common_alphas$alpha,
-           a_complex_2.5 = common_alphas$alpha_2.5,
-           a_complex_97.5 = common_alphas$alpha_97.5,
-           a_simple = common_alphas$alpha,        
-           a_simple_2.5 = common_alphas$alpha_2.5, 
-           a_simple_97.5 = common_alphas$alpha_97.5,
-           Selection_form = common_alphas$Selection_form,
-           Multiplier = common_alphas$Multiplier) %>% 
-  # for the selection gradients though, calculate them on the scale of relative fitness for each food-web treatment
-  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3) * Multiplier,
-         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3) * Multiplier,
-         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3) * Multiplier,
-         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3) * Multiplier,
-         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3) * Multiplier,
-         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3) * Multiplier)
-
-coefs_gradients <- bind_rows(coefs_gradients.complex_simple, coefs_gradients.common)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
+  mutate(b_complex = complex_mean_brackets * a_complex / complex_mean_fitness * Multiplier,
+         b_complex_2.5 = complex_mean_brackets * a_complex_2.5 / complex_mean_fitness * Multiplier,
+         b_complex_97.5 = complex_mean_brackets * a_complex_97.5 / complex_mean_fitness * Multiplier,
+         b_simple = simple_mean_brackets * a_simple / simple_mean_fitness * Multiplier,
+         b_simple_2.5 = simple_mean_brackets * a_simple_2.5 / simple_mean_fitness * Multiplier,
+         b_simple_97.5 = simple_mean_brackets * a_simple_97.5 / simple_mean_fitness * Multiplier)
+
+bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5, Selection_form), Foodweb = "Complex"),
+          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
   filter(Variable != "(Intercept)") %>%
@@
   geom_hline(yintercept=0, linetype="dotted") +
+  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
   ylab("Regression coefficient")
@@
 
-```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE}
-p<-ggplot(data=x, aes(x=y, y=x)) +
-geom_errorbar(aes(ymin=x-ci, ymax=x+ci)) +
-scale_x_discrete(breaks=c("label1","label2"),
-               labels = lapply(sprintf('$\\alpha^\\beta$'), TeX)
-p
-```
-
-What's the rationale for this test?
-First, we focus on galls where there is evidence of both survival and parasitism within the gall.
-The idea is that galls from the same clutch should be similar in size, therefore, any selection on diameter would be apparent.
-If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection gradient to be the result of confounding factors.
-Note that this is likely overestimates the effect of the confounding factor, since we are assuming that any heterogeneity in gall size (for this dataset) is due to a confounding effect of parasitism on gall diameter.
-Then, we can just subtract this value from the observed covariance between gall diameter and larval survival to adjust for the confounding effects of parasitism.
-This analysis should be relegated to the supplement.
-
-Would we expect any confounding effects on nonlinear selection?
-```{r Confounding effects of parasitism on gall size}
-## paired t-test approach. Weakness is that it only calculates the selection differential rather than the gradient, which is more meaningful for multivariate trait evolution
-pair_df <- gall_selection.df %>%
-  group_by(Foodweb, Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Foodweb, Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Foodweb, Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(diff_sc.Diam ~ Foodweb, pair_df)
-t.test(pair_df$survive_mean_sc.Diam, pair_df$all_mean_sc.Diam, paired = T)
-
-complex_pair_df <- gall_selection.df %>%
-  filter(Foodweb=="Complex") %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(complex_pair_df$survive_mean_sc.Diam, complex_pair_df$all_mean_sc.Diam, paired = T)
-
-ectos_pair_df <- gall_selection.df %>%
-  filter(Foodweb=="Complex" & platy < 1) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(ectos_pair_df$survive_mean_sc.Diam, ectos_pair_df$all_mean_sc.Diam, paired = T)
-
-simple_pair_df <- gall_selection.df %>%
-  filter(Foodweb=="Simple") %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(simple_pair_df$survive_mean_sc.Diam, simple_pair_df$all_mean_sc.Diam, paired = T)
-
-## selection gradient approach
-confounding_df <- gall_selection.df %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1)
-
-confounding_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
-                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = confounding_df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-summary(confounding_glmer)
-
-## Replicate GLMM tests but with this confounding factor dataset ----
-
-# No effects
-drop1(confounding_glmer, test="Chisq")
-summary(confounding_glmer)
-
-# No effects on nonlinear selection acting on gall diameter, but also there is not much evidence for any effects.
-confounding_glmer_2 <- update(confounding_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(confounding_glmer_2, test="Chisq") 
-summary(confounding_glmer_2)
-
-# Evidence of food-web treatment altering directional selection on clutch size; marginal evidence of correlational selection acting on gall size and clutch size.
-confounding_glmer_3 <- update(confounding_glmer_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(confounding_glmer_3, test="Chisq") 
-summary(confounding_glmer_3)
-
-# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; evidence of directional selection acting on female preference
-confounding_glmer_4 <- update(confounding_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(confounding_glmer_4, test="Chisq") 
-summary(confounding_glmer_4)
-
-fixef(foodweb_glmer_4)["sc.Diam"] - fixef(confounding_glmer_4)["sc.Diam"]
-
-confounding_predict <- predict(foodweb_glmer, type="response") # not subsetting the data to complex or simple food webs, since we didn't find a difference in this subset
-confounding_mean_brackets <- mean(confounding_predict * (1 - confounding_predict))
-confounding_mean_fitness <- mean(confounding_predict)
-
-# alternatively, this suggest that we are overestimating the selection gradient by this much...
-round(confounding_mean_brackets * fixef(confounding_glmer_4)["sc.Diam"] / confounding_mean_fitness, 3)
-
-diam_glmer <- glmer(gall_survival ~ Foodweb + sc.Diam +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-# note that the selection gradient and differential are virtually the same for gall diameter, given the similarity in their alpha coefficients.
-fixef(diam_glmer)["sc.Diam"]
-fixef(foodweb_glmer_4)["sc.Diam"]
-
-# selection differentials
-round(complex_mean_brackets * fixef(diam_glmer)["sc.Diam"] / complex_mean_fitness, 3)
-round(simple_mean_brackets * fixef(diam_glmer)["sc.Diam"] / simple_mean_fitness, 3)
-```
-
-Appears to be selection for Platygaster to attack larva at high densities in more complex food webs (and a decrease in the variance).
-This may be a result of the poorer searching ability of parasitoids at very high gall densities, potentially due to saturation.
-This suggests that the fitness landscape may be dynamic because these selective effects (assuming there is heritable variation in the egg parasitoid) will change the following year.
-This could be an important discussion point to take into account for future work.
-This is different from simply altering the strength of selection, which will occur as species move along the fitness landscape, but this result suggests that the nature of the fitness landscape may actually be changing.
-For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
-```{r Selection on Platygaster Traits}
-platy_selection_df <- gall_selection.df %>%
-  filter(egg_parasitoid > 0) 
-platy_selection_df$Foodweb <- relevel(factor(platy_selection_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids
-
-platy_Diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), platy_selection_df)
-summary(platy_Diam)
-Anova(platy_Diam, test.statistic = "F")
-
-platy_Clutch <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), platy_selection_df)
-summary(platy_Clutch)
-Anova(platy_Clutch, test.statistic = "F")
-
-platy_Pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), platy_selection_df)
-summary(platy_Pref)
-Anova(platy_Pref, test.statistic = "F")
-
-## Test whether food-web complexity influences nonlinear selection with Levene's test for homogeneity of variance between groups
-# Note that this result should be interepreted cautiously since we cannot account for non-independence due to plant genotype, plant ID, or gall ID
-leveneTest(sc.Diam ~ Foodweb, platy_selection_df)
-leveneTest(sc.log.Clutch ~ Foodweb, platy_selection_df)
-leveneTest(sc.log1p.Pref ~ Foodweb, platy_selection_df)
-
-ggplot(platy_selection_df, aes(x=Foodweb, y=sc.Diam)) +
-  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
-  stat_summary(fun.y="mean", geom="point", color="black", size=3)
-
-ggplot(platy_selection_df, aes(x=Foodweb, y=sc.log.Clutch)) +
-  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
-  stat_summary(fun.y="mean", geom="point", color="black", size=3)
-
-ggplot(platy_selection_df, aes(x=Foodweb, y=sc.log1p.Pref)) +
-  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
-  stat_summary(fun.y="mean", geom="point", color="black", size=3)
-```
-
-## Table for Alpha regression coefficients
-\begin{table}[]
-\begin{tabular}{lcc}
-                                                                           \\ \hline
-                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
-$Diam$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Clutch$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Pref$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Diam^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Clutch^2$             & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Pref^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Diam:Clutch$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Diam:Pref$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Clutch:Pref$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]              \\ \hline
-\end{tabular}
-\end{table}
-
-## Table for Iteomyia selection gradients
-\begin{table}[]
-\begin{tabular}{lcc}
-                                                                                  \\ \hline
-                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
-$\beta_{Diam}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\beta_{Clutch}$                  & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\beta_{Pref}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Diam,Diam}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Clutch,Clutch}$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Pref,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Diam,Clutch}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Diam,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Clutch,Pref}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]           \\ \hline
-\end{tabular}
-\end{table}
-
-## Table for bias
-\begin{table}[]
-\begin{tabular}{lc}
-                                                                  \\ \hline
-\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
-Complex (All)                 & `r ` [`r `-`r `]  \\
-Complex (Larval guild)        & `r ` [`r `-`r `]  \\
-Simple (\textit{Platygaster}) & `r ` [`r `-`r `]                  \\ \hline
-\end{tabular}
-\end{table}
-
-## Table for Platygaster selection
-\begin{table}[]
-\begin{tabular}{lc}
-                                                                  \\ \hline
-\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
-$s_{Diam}$                      & `r ` [`r `-`r `]  \\
-$s_{Clutch}$                    & `r ` [`r `-`r `]  \\
-$s_{Pref}$                      & `r ` [`r `-`r `]  \\ 
-$s_{Diam,Diam}$                 & `r ` [`r `-`r `]  \\
-$s_{Clutch,Clutch}$             & `r ` [`r `-`r `]  \\
-$s_{Pref,Pref}$                 & `r ` [`r `-`r `]                \\ \hline
-\end{tabular}
-\end{table}
-
-```{r DUPLICATE for bootstrap test}
-
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
-complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(foodweb_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-complex_mean_brackets - alt_mean_brackets
-complex_mean_fitness - alt_mean_fitness
-
-foodweb_tidy_4 <- filter(tidy(bootMer(foodweb_glmer_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
-foodweb_tidy_3 <- filter(tidy(bootMer(foodweb_glmer_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
-                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-foodweb_tidy_2 <- filter(tidy(bootMer(foodweb_glmer_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
-                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-foodweb_tidy <- filter(tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
-                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
-                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs.
-This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
-#foodweb_tidy_4 <- filter(tidy(foodweb_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
-#foodweb_tidy_3 <- filter(tidy(foodweb_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-#foodweb_tidy_2 <- filter(tidy(foodweb_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-#foodweb_tidy <- filter(tidy(foodweb_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-
-get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
-  mutate(alpha = round(statistic, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3)) %>%
-  select(term, alpha, alpha_2.5, alpha_97.5)
-
-complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
-simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
-  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
-         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
-         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
-         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
-         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
-         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3))
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-```
-
-Note that equation 3 in Phillips and Arnold 1998 is good justification for why quadratic selection cofficients should be multiplied by two (but not correlational ones?)
-
-The G-matrix is essentially a scalar.
-For my data, since there is no correlational selection, it doesn't matter if there is genetic covariance between the traits, as this will not effect the change in genetic covariances within a generation (because there is no selection).
-Also, the G_matrix does not qualitatively alter the conclusions that there will be a decrease in additive genetic variance in gall diameter due to the strong directional selection; however, there will be an increase in the additive genetic variance in female preference.
-Since this is an experiment, we can assume that the G-matrix is the same between treatments
-
-Remember that the diagonals refer to additive genetic CO-variances.
-Thus, positive or negative values for delta_G give insight to whether selection will act to integrate traits (positive covariance) or create trade-offs (negative covariance).
-
-Assuming that there is positive additive genetic variance and co-variance in these traits (i.e.
-all values of G-matrix are positive), then the curvature of the fitness landscape can give insight to qualitative changes in the G matrix.
-This is because the G-matrix acts as a scalar of changes in the fitness landscape.
-
-```{r Slope and Curvature of Fitness Landscape, include=FALSE}
-betas <- c(-0.5,-0.5,0.5)
-gammas_matrix <- matrix(c(-0.1, 0.0, 0.0,
-                          0.0, -0.1, 0.0,
-                          0.0, 0.0, -0.1), 
-                        nrow=3, byrow=T)
-
-## G-matrix ----
-# (1) Asssume equal additive genetic variance for all three traits
-# (2) Assume no additive genetic covariance
-# The first assumption may not be realistic, but violations of this assumption will not qualitatively alter our inferences about whether additive genetic variance will increase or decrease.
-Qualitative changes in additive genetic variance is only determined by the curvature of the fitness landscape.
-Violations of this assumption will only affect the rate of phenotypic evolution and magnitude of change in genetic variance.
-# The second assumption may also not be realistic; however, it will not affect our results because we found no evidence of correlational selection (therefore, there can be no change in genetic covariance).
-G_matrix <- matrix(c(1.0, 1.0, 1.0,
-                     1.0, 1.0, 1.0,
-                     1.0, 1.0, 1.0),
-                   nrow=3, byrow=T)
-
-# Equation 1 from Phillips and Arnold 1989, Evolution
-delta_z <- G_matrix %*% betas
-data.frame(trait = c("diam","clutch","pref"),
-           delta_z = delta_z)
-
-# Equation 2 from Phillips and Arnold 1989, Evolution
-delta_G <- G_matrix * (gammas_matrix - betas %*% t(betas)) * G_matrix
-delta_G
-```
-
-$$\text{Slope}_{complex} = \beta_{complex} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.4 \\ 0 \\ -0.3 \end{pmatrix}$$
-$$\text{Slope}_{simple} = \beta_{simple} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.3 \\ -0.2 \\ -0.3 \end{pmatrix}$$
-$$\gamma_{complex} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&-0.3 \end{pmatrix}$$
-$$\gamma_{simple} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-$$\text{Curvature} = \gamma - \beta \beta^T$$
-$$\text{Curvature}_{complex} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-$$\text{Curvature}_{simple} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-
-```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE}
-
-## Fit GLMM
-
-platyecto_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
-                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1), # exclude cases of egg-parasitism from Complex food web
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-## Test for overdispersion
-overdisp_fun(platyecto_glmer) # no evidence
-
-## Compare statistical summaries of each model
-summary(platyecto_glmer)
-piecewiseSEM::rsquared(platyecto_glmer)
-
-## Parse out mechanisms of food-web effects ----
-# Use drop1 to test highest order effects and visreg to visualize the effects
-
-# Marginal evidence that larval parasitoids are the drivers of nonlinear selection acting on female preference (disruptive selection)
-drop1(platyecto_glmer, test="Chisq")
-summary(platyecto_glmer)
-visreg::visreg(platyecto_glmer, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
-
-# Marginal evidence of nonlinear selection acting on gall size. Marginal evidence of correlational selection acting on all traits.
-platyecto_glmer_2 <- update(platyecto_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(platyecto_glmer_2, test="Chisq") 
-visreg::visreg(platyecto_glmer_2, xvar="sc.Diam", scale = "response") 
-# plot 3-way interaction?
-
-# Evidence of food-web treatment altering directional selection on clutch size
-platyecto_glmer_3 <- update(platyecto_glmer_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(platyecto_glmer_3, test="Chisq") 
-summary(platyecto_glmer_3)
-visreg::visreg(platyecto_glmer_3, xvar="sc.log.Clutch", by="Foodweb", scale="response") # conflicting selection have net null effects in complex food web
-
-# No evidence of clear fitness effects of platy vs.
-ectos on absolute fitness; evidence of directional selection acting on gall size; no evidence of directional selection on clutch size (in complex food web); evidence of directional selection acting on female preference
-platyecto_glmer_4 <- update(platyecto_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(platyecto_glmer_4, test="Chisq") 
-summary(platyecto_glmer_4)
-visreg::visreg(platyecto_glmer_4, xvar="Foodweb", scale="response")
-visreg::visreg(platyecto_glmer_4, xvar="sc.Diam", scale="response")
-visreg::visreg(platyecto_glmer_4, xvar="sc.log.Clutch", scale="response")
-visreg::visreg(platyecto_glmer_4, xvar="sc.log1p.Pref", scale="response")
-```
-
-```{r For platy ecto comparison}
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
-complex_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(platyecto_glmer_2, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-complex_mean_brackets - alt_mean_brackets
-complex_mean_fitness - alt_mean_fitness
-
-platyecto_tidy_4 <- filter(tidy(platyecto_glmer_4, conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
-platyecto_tidy_3 <- filter(tidy(platyecto_glmer_3, conf.int=T), 
-                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-platyecto_tidy_2 <- filter(tidy(platyecto_glmer_2, conf.int=T), 
-                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-platyecto_tidy <- filter(tidy(platyecto_glmer, conf.int=T), 
-                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
-                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs.
-This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
-#platyecto_tidy_4 <- filter(tidy(platyecto_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
-#platyecto_tidy_3 <- filter(tidy(platyecto_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-#platyecto_tidy_2 <- filter(tidy(platyecto_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-#platyecto_tidy <- filter(tidy(platyecto_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-
-get_alphas <- bind_rows(platyecto_tidy_4, platyecto_tidy_3, platyecto_tidy_2, platyecto_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
-  select(term, alpha, alpha_2.5, alpha_97.5, P)
-
-complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
-simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
-  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
-         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
-         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
-         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
-         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
-         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3)) %>%
-  filter(Variable != "(Intercept)")
-
-select(coefs_gradients, Variable, a_complex:a_simple_97.5)
-select(coefs_gradients, Variable, b_complex:b_simple_97.5)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-inverse_logit(complex_alphas$alpha[1]) - complex_mean_fitness # small difference in mean fitness estimates compared to intercept in complex food web
-inverse_logit(complex_alphas$alpha[1] + simple_alphas$alpha[1]) - simple_mean_fitness # larger difference in mean fitness estimates from intercept in simple food web, unclear why...perhaps because the mean phenotypes don't match up as nicely?
-```
-
-```{r}
-## Calculating same coefficients as for simple vs. complex food web
-
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
-ecto_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex" & platy < 1), type="response")
-ecto_mean_brackets <- mean(ecto_predict * (1 - ecto_predict))
-ecto_mean_fitness <- mean(ecto_predict)
-
-platy_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-platy_mean_brackets <- mean(platy_predict * (1 - platy_predict))
-platy_mean_fitness <- mean(platy_predict)
-
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(platyecto_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex" & platy < 1), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-ecto_mean_brackets - alt_mean_brackets
-ecto_mean_fitness - alt_mean_fitness
-
-# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
-# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
-platyecto_tidy_4 <- tidy(platyecto_glmer_4, conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log1p.Pref")) %>%
-  mutate(platyecto = c("ecto","platy","Common","Common"),
-         Selection_form = c(NA,NA,"Directional","Directional"),
-         Multiplier = c(1,1,1,1))
-
-platyecto_tidy_3 <- tidy(platyecto_glmer_3, conf.int=T) %>%
-  filter(term %in% c("sc.log.Clutch","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch")) %>%
-  mutate(platyecto = c("ecto","Common","Common","Common","platy"),
-         Selection_form = c("Directional","Correlational","Correlational","Correlational","Directional"),
-         Multiplier = c(1,1,1,1,1))
-
-platyecto_tidy_2 <- tidy(platyecto_glmer_2, conf.int=T) %>%
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(platyecto = c("Common","Common","Common"),
-         Selection_form = c("Nonlinear","Nonlinear","Correlational"),
-         Multiplier = c(2,2,1))
-
-platyecto_tidy <- tidy(platyecto_glmer, conf.int=T) %>%
-  filter(term %in% c("I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)")) %>%
-  mutate(platyecto = c("ecto","platy"),
-         Selection_form = c("Nonlinear","Nonlinear"),
-         Multiplier = c(2,2))
-
-get_platyecto_alphas <- bind_rows(platyecto_tidy_4, platyecto_tidy_3, platyecto_tidy_2, platyecto_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
-  select(term, platyecto, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
-
-ecto_alphas <- filter(get_platyecto_alphas, platyecto == "ecto"); ecto_alphas
-platy_alphas <- filter(get_platyecto_alphas, platyecto == "platy"); platy_alphas
-common_platyecto_alphas <- filter(get_platyecto_alphas, platyecto == "Common"); common_platyecto_alphas
-
-coefs_gradients.ecto_platy <- data.frame(Variable = ecto_alphas$term, 
-           a_ecto = ecto_alphas$alpha,
-           a_ecto_2.5 = ecto_alphas$alpha_2.5,
-           a_ecto_97.5 = ecto_alphas$alpha_97.5,
-           a_platy = ecto_alphas$alpha + platy_alphas$alpha,        # the baseline is the coefficient in the ecto food web, therefore we simply add the corresponding coefficients from the platy food web to get the coefficients on the same scale as the ecto web
-           a_platy_2.5 = ecto_alphas$alpha + platy_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_platy_97.5 = ecto_alphas$alpha + platy_alphas$alpha_97.5,
-           Selection_form = ecto_alphas$Selection_form,                # doesn't matter whether platy_ or ecto_alphas is chosen for Selection_form or Multiplier
-           Multiplier = ecto_alphas$Multiplier) %>%                     
-  mutate(b_ecto = round(ecto_mean_brackets * a_ecto / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_2.5 = round(ecto_mean_brackets * a_ecto_2.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_97.5 = round(ecto_mean_brackets * a_ecto_97.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_platy = round(platy_mean_brackets * a_platy / platy_mean_fitness, 3) * Multiplier,
-         b_platy_2.5 = round(platy_mean_brackets * a_platy_2.5 / platy_mean_fitness, 3) * Multiplier,
-         b_platy_97.5 = round(platy_mean_brackets * a_platy_97.5 / platy_mean_fitness, 3) * Multiplier)
-
-coefs_gradients.ecto_platy.common <- data.frame(Variable = common_platyecto_alphas$term, 
-           a_ecto = common_platyecto_alphas$alpha,
-           a_ecto_2.5 = common_platyecto_alphas$alpha_2.5,
-           a_ecto_97.5 = common_platyecto_alphas$alpha_97.5,
-           a_platy = common_platyecto_alphas$alpha,        
-           a_platy_2.5 = common_platyecto_alphas$alpha_2.5, 
-           a_platy_97.5 = common_platyecto_alphas$alpha_97.5,
-           Selection_form = common_platyecto_alphas$Selection_form,
-           Multiplier = common_platyecto_alphas$Multiplier) %>% 
-  # for the selection gradients though, calculate them on the scale of relative fitness for each food-web treatment
-  mutate(b_ecto = round(ecto_mean_brackets * a_ecto / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_2.5 = round(ecto_mean_brackets * a_ecto_2.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_97.5 = round(ecto_mean_brackets * a_ecto_97.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_platy = round(platy_mean_brackets * a_platy / platy_mean_fitness, 3) * Multiplier,
-         b_platy_2.5 = round(platy_mean_brackets * a_platy_2.5 / platy_mean_fitness, 3) * Multiplier,
-         b_platy_97.5 = round(platy_mean_brackets * a_platy_97.5 / platy_mean_fitness, 3) * Multiplier)
-
-coefs_gradients.ecto_platy <- bind_rows(coefs_gradients.ecto_platy, coefs_gradients.ecto_platy.common)
-
-bind_rows(mutate(select(coefs_gradients.ecto_platy, Variable, a=a_ecto, a_2.5=a_ecto_2.5, a_97.5=a_ecto_97.5), platyecto = "ecto"),
-          mutate(select(coefs_gradients.ecto_platy, Variable, a=a_platy, a_2.5=a_platy_2.5, a_97.5=a_platy_97.5), platyecto = "platy")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=platyecto, color=platyecto)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  ylab("Regression coefficient")
-
-## Modify to be directional, nonlinear, then correlational with legend in 4th area.
-## Modify so that axes have gamma and beta with the trait as a subscript
-bind_rows(mutate(select(coefs_gradients.ecto_platy, Variable, b=b_ecto, b_2.5=b_ecto_2.5, b_97.5=b_ecto_97.5, Selection_form), platyecto = "ecto"),
-          mutate(select(coefs_gradients.ecto_platy, Variable, b=b_platy, b_2.5=b_platy_2.5, b_97.5=b_platy_97.5, Selection_form), platyecto = "platy")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=platyecto, color=platyecto)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Selection gradient")
-```
-
-Compared to the GLM, the GLMM gives the same inferences about the effect of food-web treatment.
-The main difference was that there was stronger evidence of correlational selection, but no evidence that this correlational selection varied among food-web treatments.
-Still, this stronger evidence for correlational selection should be interpreted with caution since the GLM does not account for the non-indepedence of these fitness estimates.
-```{r Compare GLMM to GLM}
-## Fit GLMs. Dispersion parameter was ~1, so I just used a binomial model. 
-null_glm <- glm(gall_survival ~ sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
-                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2),
-                    data = gall_selection.df,
-                    family = binomial(link = logit))
-
-foodweb_glm <- glm(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
-                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)),
-                       data = gall_selection.df,
-                       family = binomial(link = logit))
-
-## Compare statistical summaries of each model
-summary(null_glm)
-summary(foodweb_glm)
-piecewiseSEM::rsquared(null_glm)
-piecewiseSEM::rsquared(foodweb_glm)
-
-## Test statistical significance of effects ----
-
-# Overall, there is clear evidence that food-web treatment alters absolute fitness
-anova(null_glm, foodweb_glm, test = "Chisq")
-
-## Parse out mechanisms of food-web effects ----
-# Use drop1 to test highest order effects and visreg to visualize the effects
-
-# Evidence that food-web treatment alters nonlinear selection acting on female preference. Appears to be evidence for disruptive selection in complex food web.
-# Unique to GLM: marginal evidence for food-web treatment altering nonlinear selection on clutch size
-drop1(foodweb_glm, test="Chisq")
-visreg::visreg(foodweb_glm, xvar="sc.log1p.Pref", by="Foodweb", scale = "response") 
-visreg::visreg(foodweb_glm, xvar="sc.log.Clutch", by="Foodweb", scale = "response")
-
-# Evidence of nonlinear selection acting on gall size. No evidence of disruptive selection.
-# No unique effects in the glm
-foodweb_glm_2 <- update(foodweb_glm, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(foodweb_glm_2, test="Chisq") 
-visreg::visreg(foodweb_glm_2, xvar="sc.Diam", scale = "response")
-
-# Evidence of food-web treatment altering directional selection on clutch size
-# Unique to GLM: there is stronger support for correlational selection acting on gall size and clutch size; also, there is evidence for correlational selection acting on clutch size and female preference.
-foodweb_glm_3 <- update(foodweb_glm_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(foodweb_glm_3, test="Chisq") 
-visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="Foodweb", scale="response")
-visreg::visreg(foodweb_glm_3, xvar="sc.Diam", by="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="sc.Diam", scale="response") # a different perspective
-visreg::visreg(foodweb_glm_3, xvar="sc.log1p.Pref", by="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="sc.log1p.Pref", scale="response")
-
-# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; no evidence of directional selection on clutch size (in complex food web); evidence of directional selection acting on female preference
-# No unique effects in the glm
-foodweb_glm_4 <- update(foodweb_glm_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(foodweb_glm_4, test="Chisq") 
-visreg::visreg(foodweb_glm_4, xvar="Foodweb", scale="response")
-visreg::visreg(foodweb_glm_4, xvar="sc.Diam", scale="response")
-visreg::visreg(foodweb_glm_4, xvar="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glm_4, xvar="sc.log1p.Pref", scale="response")
-```
-
-```{r Get Selection Gradients for GLM}
-complex_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-foodweb_tidy_4 <- filter(tidy(foodweb_glm_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
-foodweb_tidy_3 <- filter(tidy(foodweb_glm_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-foodweb_tidy_2 <- filter(tidy(foodweb_glm_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-foodweb_tidy <- filter(tidy(foodweb_glm), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-
-get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_SE = round(std.error, 3), P = round(p.value, 3)) %>%
-  select(term, alpha, alpha_SE, P)
-
-complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
-simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-data.frame(Variable = complex_alphas$term, 
-           alpha_complex = complex_alphas$alpha, 
-           alpha_simple = complex_alphas$alpha + simple_alphas$alpha) %>% # add the corresponding coefficients to get the coefficients on the same scale as the complex web)
-  mutate(beta_complex = round(complex_mean_brackets * alpha_complex / complex_mean_fitness, 3),
-         beta_simple = round(simple_mean_brackets * alpha_simple / simple_mean_fitness, 3)) %>%
-  filter(Variable != "(Intercept)")
-
-inverse_logit(complex_alphas$alpha[1]) - complex_mean_fitness # small difference in mean fitness estimates compared to intercept in complex food web
-inverse_logit(complex_alphas$alpha[1] + simple_alphas$alpha[1]) - simple_mean_fitness # larger difference in mean fitness estimates from intercept in simple food web, unclear why...perhaps because the mean phenotypes don't match up as nicely?
-```
-
-```{r Mortality, include=F}
-# 8-10% mortality induced by intraguild predators
-mean(control_df$platy)
-mean(treatment_df$platy)
-mean(eggptoid_control_df$platy)
-
-# Gall mortality to Platy
-1 - mean(treatment_df$pupa)
-
-# Gall mortality to Ectos
-
-# Platy mortality to intraguild predation
-mean(treatment_df$platy) - mean(control_df$platy)
-
-mean(control_df$ectos)
-mean(treatment_df$ectos)
-mean(ectoptoid_control_df$ectos)
-
-mean(control_df$pupa)
-mean(treatment_df$pupa)
-mean(eggptoid_control_df$pupa)
-mean(ectoptoid_control_df$pupa)
-```
-
-<!--$$logit(E(W))=\mu+\beta_{diameter}+\beta_{clutch}+\beta_{preference}+$$
-$$logit(E(W))=\mu+treatment+s(diam):treat+s(clutch)+s(pref)+diam:cluch+diam:pref+clutch:pref+(1|Genotype/Plant/Gall)$$-->
-
-<!-- We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
-Larva survival (0 or 1) was our response variable and measure of fitness. 
-<!-- Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients. -->
-<!-- We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
-This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. 
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
-<!-- To identify the appropriate level of model complexity for testing the effects of food-web complexity on the fitness landscapes, we compared models using Aikaike Information Criteria. 
-The maximal complexity we explored was a generalized additive mixed model that fit cubic splines to each trait as well as linear interactions between a maximum of two traits as well as an interaction with food-web treatment.
--->
-
-<!-- We used a spline-based semiparametric regression (Schluter 1988, Morrissey and Sakedra 2014).
-These analyses are desirable because they lead to inferences of the form of selection that make few \textit{a priori} assumptions (Schluter 1988), and can now be used to quantify standardized selection gradients (Morrissey and Sakrera 2014).
-
-We then calculated selection gradients as the partial derivatives in absolute fitness (larva survival) with response to multivariate phenotype using the \textit{gsg} package in R (cite Morrissey and R project).
-We standardized phenotypes (mean=0, SD=1), so that first-order derivatives correspond to the intensity of directional selection ($\beta$\textsubscript{trait}), while second-order derivatives correspond to intensity of nonlinear ($\gamma$\textsubscript{trait}) and correlational selection ($\gamma$\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are thus comparable within this study as well as to others.
--->
-
-<!-- Our GLMMs are useful for testing the effects of food-web complexity on the fitness landscape within the context of our experimental design; however, coefficients from GLMMs cannot be easily converted into quantitative estimates of selection gradients (cite Morrissey's work).
-Therefore, for each treatment, we fit separate generalized additive models (GAMs) for gall traits that we identified as being under selection from our GLMMs.
-Estimating selection gradients from GAMs can give insight to both linear and non-linear selection gradients, which we assumed were all linear for our GLMMs, given the complexity of already fitting up to 4-way interactions in these models.
-For the number of larva per gall and gall density, we aggregated larva survival at the gall or plant level, respectively, to avoid pseudoreplication in our GAMs.
--->
-
-```{r Figure 1, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
-Black arrows denote 'who-eats-whom' in this network of trophic interactions."}
-knitr::include_graphics("complex_simple_foodwebs_compressed.pdf")
-```
-
-Results
-=======
-
-We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ($\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).
-
-For example, there was directional selection for larger gall diameter in both complex and simple food webs, but the magnitude of the selection gradient was X-fold higher in the complex food web.
-The steeper selection gradient in the complex food web was not a result of stronger covariance between gall diameter and larval survival, but a result of average larval survival being X-fold lower in the complex food web.
-
-We observed directional selection for smaller clutch sizes in the simple food web, but no evidence of selection on this trait in the complex food web.
-The absence of selection in the complex food web appeared to be a result of conflicting selection pressures imposed by the egg parasitoid *Platygaster* and the guild of larval parasitoids (statistical test focus on egg vs.
-larval parasitoids).
-Specifically, larval parasitoids actually impose directional selection for larger clutch sizes (selection gradient), but the net effect is no selection when both parasitoid guilds are present.
-
-We found evidence of disruptive selection acting on female preference in the complex food web, but no evidence of nonlinear selection on this trait in the simple food web.
-Similar to clutch size, these differences in nonlinear selection appeared to be due to different selection pressures imposed by egg and larval parasitoids.
-
-**Characterizing the slope and curvature of the fitness landscape**
-
-**Old**
-Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
-In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`; simple $\beta_{diam}=$ `r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`)(Fig.
-\ref{fig:Univariate_Landscapes}A).
-
-In the complex food web, we found that there was no selection acting on clutch size
-
-In simple food webs, both clutch size and female preference experience directional selection, with smaller clutch sizes ($\beta_{clutch}=$
-`r paste0(filter(summary_beta_treatment, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Clutch size")$upper_97.5,"]")`
-and weaker preferences ($\beta_{pref}=$
-`r paste0(filter(summary_beta_treatment, Phenotype=="Female preference")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Female preference")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Female preference")$upper_97.5,"]")`
-) resulting in higher larval survival (blue lines in Fig. \ref{fig:Univariate_Landscapes}B,C).
-In contrast, there was no evidence of selection on clutch size ($\beta_{clutch}=$
-`r paste0(filter(summary_beta_control, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_control, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Clutch size")$upper_97.5,"]")`
-) or female preference ($\beta_{pref}=$
-`r paste0(filter(summary_beta_control, Phenotype=="Female preference")$Estimate," [",filter(summary_beta_control, Phenotype=="Female preference")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Female preference")$upper_97.5,"]")`
-) in complex food webs (orange lines in Fig.
-\ref{fig:Univariate_Landscapes}B,C).
-The absence of selection on clutch size and female preference was likely a result of conflicting selection pressures imposed by each guild of parasitoids due to their different functional relationships with gall traits.
-Together, these different patterns of selection resulted in an ideal combination of traits having higher fitness in the simple food web (large diameter, smaller clutches, weaker preference), whereas there was a larger combination of trait values that had equal fitness in the complex food web (Fig.
-\ref{fig:Multivariate_Landscapes}).
-We did not find any strong evidence for nonlinear or correlational selection gradients acting on gall traits in either food-web treatment.
-The second major pattern was that the overall intensity of selection was stronger in the complex vs.
-simple food web.
-This result appeared to be driven by selection on gall diameter in the complex food web, which was more than
-`r round(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate/filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate,1)`
-$\times$ larger than any other selection gradient in our analyses.
-
-```{r Get Gall Diameter Relative Fitness Landscape, include=FALSE, cache=TRUE}
-
-# Control ----
-RF_control_gall_size <- bootstrap_fitness(
-  logistic_model = quad_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000), 
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = 0),
-  bootstraps=n_boots_plots)
-
-# Treatment ----
-RF_treatment_gall_size <- bootstrap_fitness(
-  logistic_model = quad_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = 0),
-  bootstraps=n_boots_plots)
-```
-
-```{r Get Clutch Size Fitness Landscape, include=FALSE, cache=TRUE}
-
-# Control ----
-RF_control_clutch_size <- bootstrap_fitness(
-  logistic_model = quad_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = 0),
-  bootstraps=n_boots_plots)
-
-# Treatment ----
-RF_treatment_clutch_size <- bootstrap_fitness(
-  logistic_model = quad_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = 0),
-  bootstraps=n_boots_plots)
-```
-
-```{r Get Female Preference Fitness Landscape, include=FALSE, cache=TRUE}
-
-# Control ----
-RF_control_female_preference <- bootstrap_fitness(
-  logistic_model = quad_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = 0, 
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=n_boots_plots)
-
-# Treatment ----
-RF_treatment_female_preference <- bootstrap_fitness(
-  logistic_model = quad_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=n_boots_plots)
-
-```
-
-```{r Get Clutch Size x Female Preference Landscape, include=FALSE, cache=TRUE}
-
-# Control ----
-RF_control_clutch.x.preference <- bootstrap_fitness(
-  logistic_model = corr_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000), 
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-
-# Treatment ----
-RF_treatment_clutch.x.preference <- bootstrap_fitness(
-  logistic_model = corr_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, cache=TRUE}
-
-# Control ----
-RF_control_size.x.clutch <- bootstrap_fitness(
-  logistic_model = corr_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = seq(-1,1,length.out=1000), 
-     sc.log1p.female_preference = 0), 
-  bootstraps=NULL)
-
-# Treatment ----
-RF_treatment_size.x.clutch <- bootstrap_fitness(
-  logistic_model = corr_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = 0), 
-  bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, cache=TRUE}
-
-# Control ----
-RF_control_size.x.preference <- bootstrap_fitness(
-  logistic_model = corr_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = 0, 
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-
-# Treatment ----
-RF_treatment_size.x.preference <- bootstrap_fitness(
-  logistic_model = corr_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-```
-
-```{r Fitness Landscape Plot Helpers, include=FALSE, cache=TRUE}
-
-## Color palette ----
-
-# order -> orange, light blue, green, yellow, dark blue, red, pink
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
-complex_color <- cbPalette[6] # 1
-simple_color <- cbPalette[5] # 2
-treatment_colors <- c(complex_color, simple_color)
-
-## Scale relative fitness across plots ----
-
-# 1D
-RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
-          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
-          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, relative_fitness, -sc.gall_size) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  summarise(min = min(relative_fitness), max = max(relative_fitness))
-RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
-
-# 2D
-RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
-          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
-          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
-  summarise(min = min(average), max = max(average))
-
-## Scale absolute fitness across plots ----
-
-# 1D
-AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
-
-# 2D
-AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
-          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
-          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
-  summarise(min = min(average), max = max(average))
-```
-
-```{r Plot Univariate Landscapes, include=FALSE, cache=TRUE}
-uni_breaks <- c(0.1,0.5,1)
-
-# Gall size 
-AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Population mean fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-#AF_uni_size
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Clutch size
-AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.log.clutch_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Population mean fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Female preference
-AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log.clutch_size) %>%
-  gather(ID, absolute_fitness, -sc.log1p.female_preference, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
-  ylab("Population mean fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-```
-
-```{r Univariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C).
-Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
-Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
-
-# Get legend
-AF_uni_legend <- get_legend(AF_uni_size)
-
-# Make plots
-AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none", 
-                                              axis.text.x = element_text(size=10),
-                                              axis.title.x = element_text(size=11)), 
-                       AF_uni_clutch + theme(legend.position = "none",
-                                             axis.title.y = element_blank(), 
-                                             axis.text.y = element_blank(),
-                                             axis.text.x = element_text(size=10),
-                                             axis.title.x = element_text(size=11)),
-                       AF_uni_pref + theme(legend.position = "none", 
-                                           axis.title.y = element_blank(), 
-                                           axis.text.y = element_blank(), 
-                                           axis.text.x = element_text(size=10),
-                                           axis.title.x = element_text(size=11)),
-                       labels = "AUTO", ncol = 3, align='hv')
-
-AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
-AF_gradients
-#AF_uni_plots
-# save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
-```
-
-```{r Plot Multivariate Fitness Landscape, include=FALSE, cache=TRUE}
-
-my_breaks <- c(0.2,0.4,0.6,0.8)
-
-# Size x Preference
-AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Female preference (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
-
-# Size x Clutch
-AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
-
-# Clutch x Preference
-AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max), 
-```
-
-```{r Multivariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C).
-Note that traits for all plots range 1 SD below and above the mean (=0)."}
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
-  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
-  AF_plot_size.x.preference + theme(legend.position = "none"), 
-  nrow=2, align="hv", labels = "AUTO")
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
-```
-
-```{r AIC Model Comparison, include=FALSE, cache=TRUE}
-
-# Control ----
-AIC(beta_control, quad_control, corr_control)
-
-glm.beta_control <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=control_df, family=binomial(link=logit))
-
-beta_control.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                                   (1|Gall_Number),
-                                 data = control_df,
-                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-AIC(beta_control, glm.beta_control)
-AIC(beta_control, beta_control.REonlyGallID)
-overdisp_fun(beta_control)
-
-# Treatment ----
-AIC(beta_treatment, quad_treatment, corr_treatment)
-
-glm.beta_treatment <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=treatment_df, family=binomial(link=logit))
-
-beta_treatment.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                                   (1|Genotype/Plant_Position),
-                                 data = treatment_df,
-                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-overdisp_fun(beta_treatment)
-
-AIC(beta_treatment, glm.beta_treatment)
-AIC(beta_treatment, beta_treatment.REonlyGallID)
-anova(beta_treatment, beta_treatment.REonlyGallID)
-anova(beta_treatment, glm.beta_treatment)
-```
-
-Discussion
-==========
-
-<!-- Summary -->
-
-Our key finding was that the adaptive landscape was less constrained in the complex vs.
-simple food web.
-These fewer constraints arise from conflicting selection pressures imposed by different parasitoid guilds, resulting in fewer traits under selection in the complex food web.
-At the same time, we observed an overall greater intensity of selection in the complex food web, suggesting that trait evolution can be faster in complex vs.
-simple food webs.
-Our observation that natural selection was more constrained and less intense in simple vs.
-complex food webs suggests that the loss of biodiversity could constrain the adaptive potential of interacting species by reducing genetic and phenotypic variation in multiple traits.
-
-<!-- Selective constraints result -->
-
-Current theory suggests that when the number of selective constrains is less than the number of genetic constraints (i.e.
-some genetically variable traits are selective neutral), there are multiple positions on the landscape that confer equal fitness (Lande 1981; Lande and Arnold 1985).
-In this scenario, trait differences between populations may simply be due to neutral processes (e.g.
-genetic drift and mutation) moving trait values of the population.
-For our system, we currently lack quantitative estimates of genetic variation in our traits, although work with other species of galling insects has shown that gall diameter (Abramhson, Heath's work), clutch size (look to Weiss' work), and oviposition preference (Abrahmson's work?) are genetically variable.
-We encourage others to examine how changes in community context will alter selection on multiple traits.
-
-<!-- Intensity of selection result -->
-
-One interesting result of our work was that the overall intensity of selection appeared to be larger in complex food webs.
-This result was driven by the large selection gradient acting on gall diameter in complex vs.
-simple food webs.
-This difference in selection intensity is likely not driven by a difference in the ecological relationship between gall diameter and parasitoid attack (i.e.
-slope), but actually a result of the lower mean fitness of *Iteomyia* in the complex food web.
-This lower mean fitness is not surprising ---we excluded an entire guild of parasitoids from attacking the insect.
-But this more intense selection pressure may simply represent a transient dynamic.
-This is because we would expect the egg-parasitoid *Platygaster* to increase in abundance over time once its intraguild predator has been removed.
-While our results suggest that this wouldn't affect the slope of the relationship, the higher abundance of the egg parasitoid would likely reduce the mean fitness of *Iteomyia*, thus increasing the selection gradient acting on gall diameter closer to what we observed in the complex food web.
-We don't expect it to fully compensate, given that the larval parasitoids exhibit a different functional relationship with gall traits, and thus we expect a more diverse community of primary parasitoids to generally impose greater parasitism pressure, a factor that appears to be a general trend in parasitoid community (Hawkins citation) and likely for other consumers (Ives and Cardinale Ecology Letters).
-
-<!-- Quantifying indirect effects of food-web complexity -->
-
-Our study focused on quantifying the direct effects of changes in network complexity on the fitness landscape; however, changes in network complexity may have pervasive indirect effects via coevolution or by initiating evolutionary cascades.
-In our system, we observed that excluding the guild of larval parasitoids altered selection on both the basal resource (*Iteomyia*) and the intraguild prey (*Platygaster*).
-GIVE DETAILS AND SUGGEST A POTENTIAL EVOLUTIONARY CASCADE.
-
-<!-- Generality of effects of food-web complexity -->
-
-Our study manipulated food-web complexity and examined changes in the fitness landscape of species embedded within this network.
-However, other studies have also examined, at least theoretically, how changes in the diversity of competitive communities affects evolution.
-These studies have generally suggested that the diversity of competitors may actually constrain the adaptive landscape, a finding that stands in contrast to our results.
-NEED TO REVIEW THESE PAPERS TO SEE HOW ITS DIFFERENT.
-
-<!-- Conclusion -->
-
-We suggest that by explicitly focusing on network structure, we can predict how changes in biodiversity will affect the adaptive potential of constituent species.
-A network allows a powerful representation of the 'community context', lending predictive power to how changes in network structure (either due to loss of species or links), will alter natural selection and consequently evolutionary change.
-Our results also suggest that losing biodiversity may not just have consequences at the community level, but also population-level consequences that may actually constrain adaptation to changing environments.
-This argues that changes in network complexity may not only affect the robustness of communities, but also that of constituent populations to future environmental change.
-
-<!-- 
-From Arnold Am Nat 1992 Constrains on phenotypic evolution
- Evolutionary models with constant adaptive landscapes and G-matrices pro-
- vide some generalizations about the effects of selective constraints. First, the
- phenotypic mean of the population tends to evolve in an uphill direction on the
- adaptive landscape (Lande 1979). When selection is frequency-independent and
- the landscape is Gaussian, the population mean equilibrates on an adaptive peak.
- Burger (1986), however, modeled evolution on a landscape that was an ascending
- ridge with increasingly steep flanks. He found that the population would equili-
- brate on the ridge crest when stabilizing selection reached a critical level. Second,
- frequency-dependent selection generally causes the population to equilibrate
- some distance downslope from an adaptive peak (Lande 1976b, 1980b). Finally,
- when the number of selective constraints is less than the number of genetic con-
- straints so that some genetically variable traits are selectively neutral, there is a
- collection of possible equilibrium points (a line, plane, or hyperplane) rather than
- a single equilibrium point (Lande 1981; Lande and Arnold 1985). In the case of
- mating preferences and sexually selected traits, for example, the evolutionary
- outcome is changed dramatically depending on whether selection acts on mating
- preferences (Arnold 1987; Pomiankowski et al. 1991).
-
-I. Feedbacks between biological diversity and evolutionary change
-
-More recently, researchers have begun to explore how the community context drives evolutionary change (@McPeek2017; @TerHorst2018).
-
-NEED to recognize that evolutionary biologists have begun to explore how community context affects evolutionary change (work by Sharon Strauss, Casey terHorst, Lutz Becks, etc.).
-These results have begun to show interesting patterns whereby the composition of species in a community can alter the direction and strength of natural selection imposed on species embedded within these communities (cite).
-
-In other words, these results have begun to illustrate show how biological diversity, in terms of differences between species, can shape evolution.
-Nevertheless, predicting the how the composition of species in a community requires moving beyond a description of community composition.
-simply knowing the composition of species in a community will
-
-There are various bibliography styles available. You can select the
-style of your choice in the preamble of this document. These styles are
-Elsevier styles based on standard styles like Harvard and Vancouver.
-Please use BibTeX to generate your bibliography and include DOIs
-whenever available.
-
-Here are two sample references: @Feynman1963118 [@Dirac1953888].
--->
-
 References {#references .unnumbered}
 ==========
-
-```{r Univariate Absolute Fitness Landscapes, include=FALSE}
-## Absolute fitness plots ----
-
-# Gall size 
-AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Absolute fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
-
-# Clutch size
-AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.log.clutch_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Absolute fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
-
-# Female preference
-AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log.clutch_size) %>%
-  gather(ID, absolute_fitness, -sc.log1p.female_preference, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
-  ylab("Absolute fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
-```
-
-```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE}
-
-# Get legend
-AF_uni_legend <- get_legend(AF_uni_size)
-
-# Make plots
-AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
-                       AF_uni_clutch + theme(legend.position = "none", 
-                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       AF_uni_pref + theme(legend.position = "none", 
-                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       labels = "AUTO", ncol = 4, align='hv')
-
-AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
-AF_gradients
-#save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
-#save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
-```
-
-```{r Multivariate Absolute Fitness Landscapes, include=FALSE}
-
-# Size x Preference
-AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Female preference (SDs)") +
-  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-
-# Size x Clutch
-AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-
-# Clutch x Preference
-AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-```
-
-```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE}
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
-  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
-  AF_plot_size.x.preference + theme(legend.position = "none"), 
-  nrow=2, align="hv", labels = "AUTO")
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
-```
-
-```{r OLD GAMM comparison, eval=FALSE, include=FALSE}
-gamm_control <- gamm.model(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
-                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, 
-                         data = control_df)
-summary(gamm_control$gam)
-
-gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log.clutch_size"), covariates = c("sc.log1p.female_preference"), se.method="none")
-gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log1p.female_preference"), covariates = c("sc.log.clutch_size"), se.method="none")
-gam.gradients(gamm_control$gam, phenotype=c("sc.log.clutch_size","sc.log1p.female_preference"), covariates = c("sc.gall_size"), se.method="none")
-
-AIC(corr_control, gamm_control$mer)
-```
-
-```{r OLD Selection Gradients - Complex Food Web, eval=FALSE, include=FALSE}
-# note that I've switched to using the lme4 package to analyzing the GLMM
-
-# GLMM ----
-glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
-                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
-                           (1|Genotype/Plant_Position/Gall_Number),
-                         data = control_df,
-                         family = binomial(link = logit), optimizer = "bobyqa")
-summary(glmer_control)
-
-# Mean fitness ----
-Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
-
-# Confidence intervals for selection gradients ----
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
-
-## Summary ----
-summary_Beta_glmm_control <- data.frame(
-  Phenotype = c("Gall size", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Beta = round(Beta_avg_grad(glmer_control),3),
-  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-summary_Beta_glmm_control
-```
-
-```{r Get 3D, include=FALSE, eval=FALSE}
-# note that length.out=10 now
-library(FD)
-
-# Control ----
-RF_control_3D <- bootstrap_fitness(
-  logistic_model = beta_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=10),
-     sc.log.clutch_size = seq(-1,1,length.out=10),
-     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
-  bootstraps=NULL)
-mean(RF_control_3D$relative_fitness$average)
-
-control_traits <- RF_control_3D$relative_fitness %>%
-  filter(average < 1) %>%
-  select(-average) %>%
-  mutate(Treatment = "Control")
-
-FD_control <- dbFD(control_traits)
-
-FD_control
-
-# Treatment ----
-RF_treatment_3D <- bootstrap_fitness(
-  logistic_model = beta_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=10),
-     sc.log.clutch_size = seq(-1,1,length.out=10),
-     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
-  bootstraps=NULL)
-mean(RF_treatment_3D$relative_fitness$average)
-
-treatment_traits <- RF_treatment_3D$relative_fitness %>%
-  filter(average < 1) %>%
-  select(-average) %>%
-  mutate(Treatment = "Treatment")
-
-FD_treatment <- dbFD(treatment_traits)
-
-bind_rows(
-  data.frame(FD_control),
-  data.frame(FD_treatment)
-)
-
-library(vegan)
-all_traits <- bind_rows(control_traits, treatment_traits)
-
-dim(control_traits)
-dim(treatment_traits)
-
-traits_betadisper <- betadisper(d = vegdist(select(all_traits, -Treatment), method = "euclidean"), group = all_traits$Treatment)
-boxplot(traits_betadisper)
-
-ggplot(all_traits, aes(x=sc.gall_size, y=sc.log1p.female_preference, color=Treatment)) +
-  geom_jitter(width=0.05, size = 2)
-
-ggplot(all_traits, aes(x=sc.gall_size, y=sc.log.clutch_size, color=Treatment)) +
-  geom_jitter(width=0.05, size=2)
-
-ggplot(all_traits, aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, color=Treatment)) +
-  geom_jitter(width=0.05, size=2)
-
-##
-
-control_traits <- RF_control_3D$relative_fitness %>%
-  mutate(Treatment = "Control", average_cut = cut(average, breaks = c(0,0.9,1.1,2)))
-control_traits$average_cut
-
-treatment_traits <-RF_treatment_3D$relative_fitness %>%
-  mutate(Treatment = "Treatment", average_cut = cut(average, breaks = c(0,0.9,1.1,2)))
-
-all_traits <- bind_rows(control_traits, treatment_traits)
-table(all_traits$Treatment, all_traits$average_cut)
-
-ggplot(all_traits, aes(x=average, fill=Treatment)) +
-  geom_density(alpha=0.2) +
-  xlab("Relative fitness")
-
-data.frame(control = var(control_traits$average), treatment = var(treatment_traits$average))
-#all_traits %>%
-#  filter(average > 1) %>%
-#  ggplot(., aes(x=average, color=Treatment)) + geom_density()
-
-##
-
-#control_traits <- RF_control_3D$relative_fitness %>%
-#  mutate(Treatment = "Control", abund = average*100)
-
-#treatment_traits <-RF_treatment_3D$relative_fitness %>%
-#  mutate(Treatment = "Treatment", abund = average*100)
-
-#all_traits <- bind_rows(control_traits, treatment_traits)
-
-#library(MASS)
-#all_traits %>%
-#  ggplot(., aes(x=sc.log.clutch_size, y=sc.log1p.female_preference)) +
-#  geom_point() +
-#  stat_density_2d(aes(fill = stat(level)), geom = "polygon")
-```
-
-```{r Plot Univariate Landscapes OLD, include=FALSE, cache=TRUE, eval=FALSE}
-
-# Gall Diameter ----   
-RF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  geom_hline(yintercept = 1, linetype = "dotted") +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SD)") +
-  ylab("Relative fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-
-# Clutch size ----
-RF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log1p.female_preference) %>%
-  gather(ID, relative_fitness, -sc.log.clutch_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  geom_hline(yintercept = 1, linetype = "dotted") +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SD)") +
-  ylab("Relative fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-
-# Female preference ----
-RF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log.clutch_size) %>%
-  gather(ID, relative_fitness, -sc.log1p.female_preference, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  geom_hline(yintercept = 1, linetype = "dotted") +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SD)") +
-  ylab("Relative fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-```
-
-```{r Figure 2 Univariate Landscapes OLD, echo=FALSE, eval=FALSE}
-
-# Get legend
-RF_uni_legend <- get_legend(RF_uni_size)
-
-# Make plots
-RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none",
-                                              axis.text.x = element_text(size=10),
-                                              axis.title.x = element_text(size=11)), 
-                       RF_uni_clutch + theme(legend.position = "none", 
-                                          axis.title.y = element_blank(), axis.text.y = element_blank(),
-                                          axis.text.x = element_text(size=10),
-                                          axis.title.x = element_text(size=11)),
-                       RF_uni_pref + theme(legend.position = "none", 
-                                        axis.title.y = element_blank(), axis.text.y = element_blank(),
-                                        axis.text.x = element_text(size=10),
-                                        axis.title.x = element_text(size=11)),
-                       labels = "AUTO", ncol = 3, align='hv')
-
-RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
-#RF_gradients
-RF_uni_plots
-#save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
-#save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
-```
-
-```{r Plot Multivariate Fitness Landscape OLD, include=FALSE, cache=TRUE, eval=FALSE}
-
-# Clutch x Preference ----
-RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$relative_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Female preference (SD)") +
-  ylab("Clutch size (SD)") +
-  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
-
-# Size x Clutch ----
-RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$relative_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SD)") +
-  ylab("Clutch size (SD)") +
-  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
-
-# Size x Preference ----
-RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$relative_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SD)") +
-  ylab("Female preference (SD)") +
-  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
-```
-
-```{r Figure 3 Multivariate Landscapes OLD, echo=FALSE, eval=FALSE}
-
-# Get legend
-RF_landscape_legend <- get_legend((RF_plot_size.x.preference + theme(legend.title = element_text(size=12), legend.text=element_text(size=10))))
-
-# Format plots
-RF_landscape_plots <- plot_grid(
-  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)),
-  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank(), axis.text = element_text(size=9), axis.text.y = element_blank(), axis.title = element_text(size=11), strip.text = element_text(size=11)),
-  RF_plot_size.x.preference + theme(legend.position = "none", axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)), 
-  nrow=2, align="hv", labels = "AUTO")
-RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
-RF_landscape_2d
-#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
-```

### 2018-09-21 temporary_morgue/Manuscript/Manuscript.tex
getting organized

--- 2018-09-21 temporary_morgue/Manuscript/Manuscript.Rmd
@@
----
-title: Phenotypic evolution is less constrained in complex food webs
-author:
-  - name: Matthew A. Barbour
-    email: matthew.barbour@ieu.uzh.ch
-    affiliation: a,b
-    footnote: Corresponding Author
-  - name: Christopher J. Greyson-Gaito
-    affiliation: a,c
-  - name: Arezoo Sootodeh
-    affiliation: a
-  - name: Brendan Locke
-    affiliation: d
-  - name: Jordi Bascompte
-    affiliation: b
-address:
-  - code: a
-    address: University of British Columbia, Department of Zoology, 6270 University Blvd., Vancouver, BC, V6T 1Z4, Canada
-  - code: b
-    address: University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, Zurich, 8057, Switzerland
-  - code: c
-    address: University of Guelph, Department of Integrative Biology, 50 Stone Rd. East, Guelph, ONT, N1G 2W1, Canada
-  - code: d
-    address: Humboldt State University, Department of Biological Sciences, 1 Harpst St., Arcata, CA, 95521, USA
-abstract: |
+\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
+%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
+\usepackage[hyphens]{url}
+
+  \journal{An awesome journal} % Sets Journal name
+
+\usepackage{lineno} % add
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+
+\bibliographystyle{elsarticle-harv}
+\biboptions{sort&compress} % For natbib
+\usepackage{graphicx}
+\usepackage{booktabs} % book-quality tables
+%%%%%%%%%%%%%%%% end my additions to header
+
+\usepackage[T1]{fontenc}
+\usepackage{lmodern}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \usepackage{fontspec}
+  \ifxetex
+    \usepackage{xltxtra,xunicode}
+  \fi
+  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
+  \newcommand{\euro}{€}
+\fi
+% use microtype if available
+\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
+\ifxetex
+  \usepackage[setpagesize=false, % page size defined by xetex
+              unicode=false, % unicode breaks when used with xetex
+              xetex]{hyperref}
+\else
+  \usepackage[unicode=true]{hyperref}
+\fi
+\hypersetup{breaklinks=true,
+            bookmarks=true,
+            pdfauthor={},
+            pdftitle={Phenotypic evolution is less constrained in complex food webs},
+            colorlinks=true,
+            urlcolor=blue,
+            linkcolor=magenta,
+            pdfborder={0 0 0}}
+\urlstyle{same}  % don't use monospace font for urls
+
+\setcounter{secnumdepth}{0}
+% Pandoc toggle for numbering sections (defaults to be off)
+\setcounter{secnumdepth}{0}
+% Pandoc header
+
+\begin{document}
+\begin{frontmatter}
+
+  \title{Phenotypic evolution is less constrained in complex food webs}
+    \author[a,b]{Matthew A. Barbour\corref{c1}}
+   \ead{matthew.barbour@ieu.uzh.ch} 
+   \cortext[c1]{Corresponding Author}
+    \author[a,c]{Christopher J. Greyson-Gaito}
+
+    \author[a]{Arezoo Sootodeh}
+
+    \author[d]{Brendan Locke}
+
+    \author[b]{Jordi Bascompte}
+
+      \address[a]{University of British Columbia, Department of Zoology, 6270 University
+Blvd., Vancouver, BC, V6T 1Z4, Canada}
+    \address[b]{University of Zurich, Department of Evolutionary Biology and
+Environmental Studies, Winterthurerstrasse 190, Zurich, 8057,
+Switzerland}
+    \address[c]{University of Guelph, Department of Integrative Biology, 50 Stone Rd.
+East, Guelph, ONT, N1G 2W1, Canada}
+    \address[d]{Humboldt State University, Department of Biological Sciences, 1 Harpst
+St., Arcata, CA, 95521, USA}
+
+  \begin{abstract}
   This is the abstract.
@@
   It consists of two paragraphs.
+  \end{abstract}
 
-journal: "An awesome journal"
-date: "`r Sys.Date()`"
-bibliography: mybibfile.bib
-output: rticles::elsevier_article
----
+ \end{frontmatter}
 
-```{r setup, include=FALSE}
+\section{Introduction}\label{introduction}
 
-## Load required libraries ----
-library(car)        # for homogeneity of variance test
-library(tidyverse)  # for managing data
-library(cowplot)    # pretty default ggplots
-library(broom)      # for tidying multiple linear models
-library(visreg)     # for quick visualizations of model effects
-library(viridis)    # for color palette
-library(lme4)       # for generalized linear mixed models
-library(piecewiseSEM) # for calculating model R-square
-library(latex2exp)  # using Latex notation for axes labels
+The fitness landscape provides a unifying framework for linking the
+ecology and evolution of populations (Lande 2007; McPeek 2017). The
+average fitness of a population is a common currency in ecology and
+evolution, but usually goes by different names in each field. Ecologists
+refer to it as per-capita population growth rate (\(dN/Ndt\)), whereas
+evolutionary biologists call it the natural log of population mean
+fitness (\(ln(\bar W_N)\). In addition to having different names,
+ecologists and evolutionary biologists have typically focused on
+different processes that shape the fitness landscape. For example,
+population ecologists have long studied the effect of a population's
+density on its per-capita growth rate (i.e.~density-dependence, CITE
+Foundational and current work). In contrast, evolutionary biologists
+have focused on how the mean trait value of a population influences its
+average fitness, as this describes the direction and magnitude of
+natural selection (CITE foundational and current work). Therefore, the
+fitness landscape describes the joint ecological and evolutionary
+dynamics of a population in a given environment.
 
-## Load and manage data ----
+Community ecologists have extended the ecological side of the fitness
+landscape by incorporating network theory. Species-interaction networks,
+such as a food web describing who eats whom, provide an explicit
+representation of the biotic environment as they describe the
+interdependency of populations within an ecological community. This has
+provided an effective framework for predicting how changes in the biotic
+environment (e.g.~density of directly and indirectly connected species)
+will impact population dynamics within species-rich communities. At the
+same time, evolutionary biologists have long recognized that changes in
+the biotic environment can alter the dynamics of natural selection.
+However, the biotic environment in which populations are evolving often
+remains a bit of a ``black box'' that's labelled by a general ecological
+process such as competition, predation, or mutualism. Because of this,
+it remains difficult to predict how changes in the biotic environment
+will affect the direction and magnitude of natural selection. Such
+predictions are urgently needed given the rapid changes in the biotic
+environment that most populations are currently experiencing throughout
+the world.
 
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  # convert appropriate variables to characters instead of integers
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+Here, we integrate species-interaction networks and the fitness
+landscape to empirically test how changes in the biotic environment --
+network of species interactions -- affect the dynamics of natural
+selection. Specifically, we conducted a field experiment that
+manipulated the diversity of insect parasitoids that were able to impose
+selection on an abundant insect herbivore (\emph{Iteomyia
+salicisverruca})(Fig. 1). The larva of this herbivore species induce
+tooth-shaped galls when they feed on the developing leaves of willow
+trees (\emph{Salix} sp., ({\textbf{???}})). These galls provide
+protection from generalist predators (e.g.~ants, spiders), thus the
+network of interacting parasitoids provides a realistic representation
+of the biotic environment this insect herbivore is experiencing.
+Therefore, our manipulation of parasitoid diversity alters the diversity
+of interactions, or food-web complexity, that this insect herbivore
+experiences.
 
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
-  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
-         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
-         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
-         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots)))) 
-dim(gall_selection.df)
+Changes in food-web complexity could influence a resource population's
+fitness landscape in at least two ways. First, if a more diverse
+community of consumers is more effective at suppressing resource
+densities (({\textbf{???}})), then this will result in lower mean
+fitness of the resource population. A reduction in mean fitness, all
+else equal, will intensify natural selection (({\textbf{???}})). On the
+other hand, if consumers impose different selection pressures on
+resource traits, then more diverse communities could dampen the strength
+of selection acting on a given trait. This is because a greater
+diversity in selection pressures is equivalent to greater uncertainty in
+the selective environment. Thus, a more diverse consumer community may
+relax the net selection pressures acting on resource traits. Here, we
+evaluate these hypothesized relationships through an experimental test
+of how changes in food-web complexity alters the fitness landscape of a
+resource population.
 
-table(gall_selection.df$Treatment.focus, gall_selection.df$ectos)
+\section{Materials \& Methods}\label{materials-methods}
 
-## Create separate datasets for quantifying selection gradients ----
-#control_df <- gall_selection.df %>%
-#  filter(Treatment.focus == "Control") #%>%
-  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
-  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
-  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
-  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
-  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
-#dim(control_df)
+\subsection{Study Site}\label{study-site}
 
-#treatment_df <- gall_selection.df %>%
-#  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
-#dim(treatment_df)
-  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
-  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
-  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
-  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
-  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+We conducted our study within a four-year old common garden of coastal
+willow (\emph{Salix hookeriana}) located at Humboldt Bay National
+Wildlife Refuge (HBNWR) (40°40'53``N, 124°12'4''W) near Loleta,
+California, USA. This common garden consists of 26 different willow
+genotypes that were collected from a single population of willows
+growing around Humboldt Bay. Stem cuttings of each genotype (25
+replicates per genotypes) were planted in a completely randomized design
+in two hectares of a former cattle pasture at HBNWR. Willows in our
+garden begin flowering in February and reach their peak growth in early
+August. During this study, willows had reached 5 - 9m in height. Further
+details on the genotyping and planting of the common garden are
+available in ({\textbf{???}}).
 
-#mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.
+\subsection{Food-Web Manipulation}\label{food-web-manipulation}
 
-## Custom functions to avoid repetitive code ----
+We setup our food-web manipulation across 128 plants soon after galls
+began developing on \emph{S. hookeriana} in early June of 2013. These
+128 plants came from eight different plant genotypes, spanning the range
+of trait variation observed in this willow population
+(({\textbf{???}})). On treatment plants (8 replicates per genotype), we
+enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant
+Prairie, WI, USA) to exclude three parasitoid species that attack during
+larva development (hereafter larval parasitoids). This treatment did not
+exclude the egg parasitoid \emph{Platygaster} sp. which attacks prior to
+gall initiation (note that in Cecidomyiid midges, larva initiate gall
+development CITE). On control plants (8 replicates per genotype), we
+used flagging tape to mark 14 galled leaves per plant
+(\textasciitilde{}30 larva), allowing the full suite of parasitoids to
+attack \emph{Iteomyia}. Marking galls with flagging tape ensured that we
+compared control and treatment galls with similar phenology when we
+collected galls later in the season. Our food-web manipulation altered
+the average number of trophic interactions that \emph{Iteomyia} was
+exposed to from BLANK on control plants to BLANK on treatment plants.
+Thus, we refer to galls on control plants as being exposed to a
+`complex' food web, whereas galls on treatment plants were exposed to a
+`simple' food web. In late August, we collected marked and bagged galls
+from each plant, placed them into 30 mL vials and kept them in the lab
+for 4 months at room temperature. We then opened galls under a
+dissecting scope and determined whether larva survived to pupation (our
+measure of fitness) or were parasitized. Since we were interested in
+selection imposed by interactions with parasitoids, we restricted our
+data to larva that either survived to pupation, was parasitized by an
+egg parasitoid (\emph{Platygaster} sp.), or was parasitized by a larval
+parasitoid. For the food-web treatment that excluded parasitoids, we
+further restricted our data by removing any instances of parasitism by a
+larval parasitoid. This represented less than 3\% of the observations in
+this food-web treatment and allowed us to focus our inferences of
+selection on those imposed by the egg parasitoid.\\
+Together, we had survival estimates for 1,306 larva from 607 galls, 111
+plants, and 8 plant genotypes.
 
-## Test for overdispersion
-overdisp_fun <- function(model) {
-  ## number of variance parameters in 
-  ##   an n-by-n variance-covariance matrix
-  vpars <- function(m) {
-    nrow(m)*(nrow(m)+1)/2
-  }
-  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
-  rdf <- nrow(model.frame(model))-model.df
-  rp <- residuals(model,type="pearson")
-  Pearson.chisq <- sum(rp^2)
-  prat <- Pearson.chisq/rdf
-  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
-  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
-}
+\subsection{Measuring Gall Traits}\label{measuring-gall-traits}
 
-## Test for multicollinearity (from: https://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/)
-vif.mer <- function (fit) {
-    ## adapted from rms::vif
+We collected data on three different traits that we anticipated would
+experience selection based on our previous work (({\textbf{???}})) and
+others work with Cecidomyiid midges (({\textbf{???}}),
+({\textbf{???}})). First, we measured gall diameter as the size of each
+gall chamber to the nearest 0.01 mm at its maximum diameter
+(perpendicular to the direction of plant tissue growth). Our previous
+work has shown that a larger gall diameter provides a refuge for larva
+from parasitoid attack (({\textbf{???}})). Second, we measured the
+clutch size of adult female midges by counting the number of chambers in
+each gall (({\textbf{???}})). All larva collected from the same
+multi-chambered gall were scored with the same clutch size. Third, we
+measured female preference for oviposition (egg-laying) sites as the
+density of larva observed on a plant in an independent survey.
+Specifically, we randomly sampled five branches per tree and summed the
+number of individual gall chambers observed. We then converted these
+counts to a measure of gall density per 100 shoots by counting the
+number of shoots on the last branch we sampled. All larva collected from
+the same plant were scored with the same female preference. The
+measurement of larval densities on plants in the field is a commonly
+used index for measuring oviposition preference (({\textbf{???}}));
+however, caution must be taken in inferring `preference' as larval
+densities can be influenced by processes other than preference
+(({\textbf{???}})). Fortunately, a couple of features of our study
+system suggest that larval density on a plant may be a good proxy for
+female preference. For example, since our data comes from a randomized
+placement of willow genotypes in a common garden, there is no consistent
+bias in which willow genotypes that females are exposed to while
+searching for oviposition sites. Also, egg predation is a minor source
+of mortality for galling insects in general (({\textbf{???}})), thus we
+do not expect any prior egg predation to bias our estimates of observed
+larval densities.
 
-    v <- vcov(fit)
-    nam <- names(fixef(fit))
+\subsubsection{Quantifying the Fitness
+Landscape}\label{quantifying-the-fitness-landscape}
 
-    ## exclude intercepts
-    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
-    if (ns > 0) {
-        v <- v[-(1:ns), -(1:ns), drop = FALSE]
-        nam <- nam[-(1:ns)]
-    }
+To characterize the shape of the fitness landscape in simple and complex
+food webs, we first used a generalized linear mixed model to quantify
+selection surfaces on individual traits. We used a binomial error
+distribution (logit link function) since larval survival (0 or 1) was
+our response variable and measure of fitness. We specified linear and
+quadratic terms for each gall trait as well as linear interaction terms
+between each gall trait as fixed effects in the statistical models. To
+account for the correlated structure of clutch size (gall level) and
+female preference (plant level) as well as any independent effects of
+willow genotype on larval survival, we specified gall ID nested within
+plant ID nested within plant genotype as random effects. Since we were
+interested in characterizing the fitness landscape -- the relationship
+between mean trait values and population mean fitness -- we assumed the
+mean value of our random effects (i.e.~setting them to zero) to estimate
+selection gradients. Also, the fitness landscape assumes that traits
+distributions are multivariate normal. To better meet this assumption,
+we log-transformed clutch size and added a small constant (1) to female
+preference before log transforming, since our surveys occassionaly
+estimated zero larval densities. We then scaled all phenotypic traits to
+mean=0 and SD=1 in order to calculate standardized selection gradients
+that were comparable across traits and with other studies of natural
+selection. We used the method of ({\textbf{???}}) to calculate
+directional (\(\beta_{z_i}\)), quadratic (\(\gamma_{z_i,z_i}\)), and
+correlational (\(\gamma_{z_i,z_j}\)) selection gradients and used
+parametric bootstrapping (1000 replicates) to calculate their 95\%
+confidence intervals (({\textbf{???}})). We estimated directional
+selection gradients by excluding quadratic terms and statistical
+interactions in the model. Note that for visualizing the fitness
+landscape we restrict trait axes to \(\pm 1\) SD of the mean trait value
+as this contains the majority of the trait distribution that selection
+is acting on.
 
-    d <- diag(v)^0.5
-    v <- diag(solve(v/(d %o% d)))
-    names(v) <- nam
-    v
-}
+Rather than imposing selection, parasitoids may themselves influence the
+expression of herbivore traits. Any influence on trait expression would
+bias selection gradients acting on those traits. In our system, it was
+plausible that parasitoids may influence chamber growth by promoting
+larval feeding (cite), speeding up larva development (cite), or killing
+larva before they complete their development (cite). Therefore, our
+estimates of selection on chamber diameter may be positively or
+negatively biased. To estimate this bias, we subset our data to only
+include galls where there was variation in larval survival (1
+\textgreater{} survival \textgreater{} 0) within the same gall. We then
+calculated ``apparent'' selection differentials for each gall by
+comparing the average chamber diameter of all larva (before
+``selection'') to the average chamber diameter of surviving larva and
+analyzed separate one-sample t-tests for each food-web treatment. This
+analysis is based on the assumption that larva within each gall come
+from the same clutch and therefore should have similar chamber diameters
+regardless of whether they are parasitized. In general, we found that
+our estimates of directional selection on chamber diameter were
+positively biased (Appendix). In other words, our analyses were
+overestimating the magnitude of selection acting on gall diameter.
+Therefore, we adjusted our estimates of directional selection on chamber
+diameter (\(\beta_{diam}\)) by subtracting the biased selection
+differentials. Note that selection gradients and selection differentials
+for chamber diameter were virtually the same (Appendix).
 
-## Transform logit to probability
-inverse_logit <- function(x) exp(x)/(1+exp(x))
+\subsubsection{Quantifying Selective
+Constraints}\label{quantifying-selective-constraints}
 
-## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
-Beta_avg_grad <- function(.) {
-  mean_fitness <- mean(predict(., type = "response")) 
-  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
-  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
-}
+The strength and pattern of selective constraints can be measured as the
+slope and curvature of the fitness landscape (Arnold 1992).
 
-## Calculate intensity/opportunity for selection
-intensity_of_selection <- function(.) {
-  mean_fitness <- mean(predict(., type = "response")) # inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
-  relative_fitness <- predict(., type = "response") / mean_fitness 
-  var(relative_fitness)
-}
+We can translate selection surfaces of individuals to the fitness
+landscape of a population
 
-## Compute the matrix describing the curvature of the fitness landscape
-curvature_fitness.landscape <- function(gammas, # matrix of nonlinear and correlational selection gradients 
-                                        betas){ # vector of directional selection gradients
-  gammas - betas %*% t(betas)
-}
+To characterize the net effects of food-web complexity on the slope and
+curvature of \emph{Iteomyia}'s fitness landscape, we took advantage of
+existing theory that links selection surfaces of individuals to the
+fitness landscape of the population (Phillips \& Arnold 1998, Arnold
+2003). Specifically, the slope of the fitness landscape corresponds to
+the column vector of directional selection gradients:
 
-## Bootstrap fitness estimates
-bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
-  model_matrix <- model.matrix(formula(fixed_effects), newdata)
+Note that we ommitted the upper triangle of the matrix for clarity since
+it is simply the reflection of the lower triangle. Assuming that there
+is additive genetic variance and covariance between these traits under
+selection, then the slope and curvature of the fitness landscape give
+insight to how the population's mean trait value will change in the next
+generation as well as how additive genetic variance and covariance
+changes within a generation.
 
-  # Absolute fitness
-  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))
+While making quantitative predictions about trait evolution requires
+knowledge of the additive genetic variance and covariance of these
+traits, the slope and curvature of the fitness landscape still give
+qualitative insight to the evolutionary trajectory of a population.
 
-  if(is.null(bootstraps) == FALSE){
-    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+If we assume that there is additive genetic variance and covariance
+between these traits, then the matrix describing the curvature of the
+fitness landscape gives qualitative insight to the selective constraints
+acting on the population. For example, the diagonal of the curvature
+matrix dictates (qualitatively) whether the additive genetic variance in
+each trait will increase (\(+\)), decrease (\(-\)), or stay the same
+(\(0\)). Similarly, the off-diagonal of the curvature matrix dictates
+whether selection favors trait integration (positive covariance), a
+tradeoff (negative covariance), or no change in genetic covariance. In
+other words, we can get qualitative insight to how food-web complexity
+influences constraints on the fitness landscape by counting the number
+of negative sign values along the diagnoal (which imply a decrease in
+additive genetic variance) and the number of positive or negative signs
+along the off diagonal (which imply changes in additive genetic
+covariance that lead to either trait integration or tradeoffs).
 
-   get_intervals_absolute_fitness <- apply(get_bootstraps_absolute_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
+All analyses and visualizations were conducted in R (({\textbf{???}})).
 
-  absolute_fitness_df <- data.frame(newdata, 
-                    average = get_absolute_fitness(logistic_model), 
-                    lower = get_intervals_absolute_fitness[1, ],
-                    upper = get_intervals_absolute_fitness[2, ],
-                    t(get_bootstraps_absolute_fitness$t))
-  } else {
-    absolute_fitness_df <- data.frame(newdata, 
-                    average = get_absolute_fitness(logistic_model))
-  }
+I need to go back to estimate a common alpha coefficient if the
+treatments do not differ from each other.
 
-  # Relative fitness
-  get_relative_fitness <- function(.) get_absolute_fitness(.)/mean(get_absolute_fitness(.))
+\section*{References}\label{references}
+\addcontentsline{toc}{section}{References}
 
-  if(is.null(bootstraps) == FALSE){
-    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
-
-  get_intervals_relative_fitness <- apply(get_bootstraps_relative_fitness$t, 2, function(x) x[order(x)][c(round(bootstraps*intervals[1],0),round(bootstraps*intervals[2],0))])
-
-  relative_fitness_df <- data.frame(newdata, 
-                    average = get_relative_fitness(logistic_model), 
-                    lower = get_intervals_relative_fitness[1, ],
-                    upper = get_intervals_relative_fitness[2, ],
-                    t(get_bootstraps_relative_fitness$t))
-  } else {
-      relative_fitness_df <- data.frame(newdata, 
-                    average = get_relative_fitness(logistic_model))
-  }
-
-  # Organize data
-  return(list(absolute_fitness = absolute_fitness_df, relative_fitness = relative_fitness_df))
-}
-
-## Number of bootstrap replicates
-n_boots_analysis <- 30
-n_boots_plots <- 100
-
-```
-
-Introduction
-============
-
-The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
-The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
-Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$.
-In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
-For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
-density-dependence, CITE Foundational and current work).
-In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
-Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
-
-Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
-Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
-This has provided an effective framework for predicting how changes in the biotic environment (e.g.
-density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
-At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
-However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
-Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
-Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
-
-Here, we integrate species-interaction networks and the fitness landscape to empirically test how changes in the biotic environment -- network of species interactions -- affect the dynamics of natural selection.
-Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (*Iteomyia salicisverruca*)(Fig.
-1).
-The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006).
-These galls provide protection from generalist predators (e.g.
-ants, spiders), thus the network of interacting parasitoids provides a realistic representation of the biotic environment this insect herbivore is experiencing.
-Therefore, our manipulation of parasitoid diversity alters the diversity of interactions, or food-web complexity, that this insect herbivore experiences.
-
-Changes in food-web complexity could influence a resource population's fitness landscape in at least two ways.
-First, if a more diverse community of consumers is more effective at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population.
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018).
-On the other hand, if consumers impose different selection pressures on resource traits, then more diverse communities could dampen the strength of selection acting on a given trait.
-This is because a greater diversity in selection pressures is equivalent to greater uncertainty in the selective environment.
-Thus, a more diverse consumer community may relax the net selection pressures acting on resource traits.
-Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the fitness landscape of a resource population.
-
-Materials & Methods
-===================
-
-## Study Site
-
-We conducted our study within a four-year old common garden of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
-This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 5 - 9m in height.
-Further details on the genotyping and planting of the common garden are available in @Barbour2015.
-
-## Food-Web Manipulation
-
-We setup our food-web manipulation across 128 plants soon after galls began developing on *S. hookeriana* in early June of 2013. 
-These 128 plants came from eight different plant genotypes, spanning the range of trait variation observed in this willow population (@Barbour2015). 
-On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
-This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
-On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack *Iteomyia*. 
-Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
-Our food-web manipulation altered the average number of trophic interactions that *Iteomyia* was exposed to from BLANK on control plants to BLANK on treatment plants. 
-Thus, we refer to galls on control plants as being exposed to a 'complex' food web, whereas galls on treatment plants were exposed to a 'simple' food web.
-In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and <!-- allowed them to complete development--> kept them in the lab for 4 months at room temperature.
-We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (*Platygaster* sp.), or was parasitized by a larval parasitoid.
-For the food-web treatment that excluded parasitoids, we further restricted our data by removing any instances of parasitism by a larval parasitoid.
-This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
-Together, we had survival estimates for 1,306 larva from 607 galls, 111 plants, and 8 plant genotypes.
-
-## Measuring Gall Traits
-
-We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018). 
-First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). 
-Our previous work has shown that a larger gall diameter provides a refuge for larva from parasitoid attack (@Barbour2016).
-<!-- Consider whether it is important to make the distinction that diameter was measured at the multi-chambered gall level in previous work -->
-Second, we measured the clutch size of adult female midges by counting the number of chambers in each gall (@Weis1983). 
-All larva collected from the same multi-chambered gall were scored with the same clutch size. 
-Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant in an independent survey.
-Specifically, we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
-We then converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
-All larva collected from the same plant were scored with the same female preference.
-The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010); however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference (@Singer1986).
-Fortunately, a couple of features of our study system suggest that larval density on a plant may be a good proxy for female preference.
-For example, since our data comes from a randomized placement of willow genotypes in a common garden, there is no consistent bias in which willow genotypes that females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general (@Hawkins1997), thus we do not expect any prior egg predation to bias our estimates of observed larval densities.
-
-### Quantifying the Fitness Landscape
-
-To characterize the shape of the fitness landscape in simple and complex food webs, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
-We used a binomial error distribution (logit link function) since larval survival (0 or 1) was our response variable and measure of fitness.
-We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
-Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
-setting them to zero) to estimate selection gradients.
-Also, the fitness landscape assumes that traits distributions are multivariate normal.
-To better meet this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
-We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
-We used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
-We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
-Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value as this contains the majority of the trait distribution that selection is acting on.
-
-Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits.
-Any influence on trait expression would bias selection gradients acting on those traits.
-In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
-Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
-To estimate this bias, we subset our data to only include galls where there was variation in larval survival (1 > survival > 0) within the same gall.
-We then calculated "apparent" selection differentials for each gall by comparing the average chamber diameter of all larva (before "selection") to the average chamber diameter of surviving larva and analyzed separate one-sample t-tests for each food-web treatment.
-This analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
-In general, we found that our estimates of directional selection on chamber diameter were positively biased (Appendix).
-In other words, our analyses were overestimating the magnitude of selection acting on gall diameter.
-Therefore, we adjusted our estimates of directional selection on chamber diameter ($\beta_{diam}$) by subtracting the biased selection differentials.
-Note that selection gradients and selection differentials for chamber diameter were virtually the same (Appendix).
-
-### Quantifying Selective Constraints
-
-The strength and pattern of selective constraints can be measured as the slope and curvature of the fitness landscape (Arnold 1992).
-
-We can translate selection surfaces of individuals to the fitness landscape of a population
-
-To characterize the net effects of food-web complexity on the slope and curvature of *Iteomyia*'s fitness landscape, we took advantage of existing theory that links selection surfaces of individuals to the fitness landscape of the population (Phillips & Arnold 1998, Arnold 2003).
-Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
-
-```{r LATEX NEED TO CHECK two, eval=FALSE, include=FALSE}
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
-whereas the curvature of the fitness landscape is a function of the directional, nonlinear, and correlational selection gradients: 
-$$\text{Curvature} = \gamma - \beta \beta^T$$
-where \gamma represents the matrix of nonlinear and correlational selection gradients:
-$$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
-```
-
-Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
-Assuming that there is additive genetic variance and covariance between these traits under selection, then the slope and curvature of the fitness landscape give insight to how the population's mean trait value will change in the next generation as well as how additive genetic variance and covariance changes within a generation.
-
-While making quantitative predictions about trait evolution requires knowledge of the additive genetic variance and covariance of these traits, the slope and curvature of the fitness landscape still give qualitative insight to the evolutionary trajectory of a population.
-
-If we assume that there is additive genetic variance and covariance between these traits, then the matrix describing the curvature of the fitness landscape gives qualitative insight to the selective constraints acting on the population.
-For example, the diagonal of the curvature matrix dictates (qualitatively) whether the additive genetic variance in each trait will increase ($+$), decrease ($-$), or stay the same ($0$).
-Similarly, the off-diagonal of the curvature matrix dictates whether selection favors trait integration (positive covariance), a tradeoff (negative covariance), or no change in genetic covariance.
-In other words, we can get qualitative insight to how food-web complexity influences constraints on the fitness landscape by counting the number of negative sign values along the diagnoal (which imply a decrease in additive genetic variance) and the number of positive or negative signs along the off diagonal (which imply changes in additive genetic covariance that lead to either trait integration or tradeoffs).
-
-All analyses and visualizations were conducted in R (@R2018).
-
-I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
-
-```{r Effects of food-web complexity on absolute fitness, cache=TRUE, include=FALSE}
-
-## FIT GLMMs ---
-
-# Null Model
-null_glmer <- glmer(gall_survival ~ 1 +
-                      (1|Genotype/Plant_Position/Gall_Number),
-                    data = gall_selection.df,
-                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-# Model assuming no effect of food-web treatment
-trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + 
-                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
-                      (1|Genotype/Plant_Position/Gall_Number),
-                    data = gall_selection.df,
-                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-# Model allowing for an effect of food-web treatment
-foodweb_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +
-                         Foodweb*(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-# Model excluding quadratic and trait:trait interactions. This is necessary for accurately estimating directional selection gradients (Betas, Lande and Arnold 1983)
-betas_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-## STATISTICAL TESTS ----
-
-# There is clear evidence that the traits we have measured influence larva survival
-anova(null_glmer, trait_glmer, test="Chisq")
-
-# There is also clear evidence that our food-web treatment altered natural selection
-foodweb_test <- tidy(anova(trait_glmer, foodweb_glmer, test="Chisq"))
-rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment
-
-## EVALUATING MODEL ASSUMPTIONS ---
-
-# There is no evidence of overdispersion
-overdisp_fun(foodweb_glmer)
-
-# There are no clear patterns in the distribution of the residuals (= good)
-visreg(foodweb_glmer)
-```
-
-```{r Get Selection Gradients for GLMER, include=FALSE}
-
-## METHOD OF JANZEN AND STERN 1998 ----
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
-alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-test_mean_brackets <- complex_mean_brackets
-test_mean_fitness <- complex_mean_fitness
-test_mean_brackets - alt_mean_brackets # virtually the same
-test_mean_fitness - alt_mean_fitness # virtually the same
-
-# Tidy data for beta terms
-foodweb_tidy_betas <- tidy(betas_glmer, conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
-         Selection_form = c(NA,NA,rep("Directional",6)),
-         Multiplier = rep(1,8))
-
-# Tidy data for gamma terms.
-Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al.
-2008)
-foodweb_tidy_gammas <- tidy(foodweb_glmer, conf.int=T) %>%
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
-         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
-         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))
-
-# Combine and tidy the regression (alpha) coefficients
-get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
-  mutate(alpha = estimate, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = p.value) %>%
-  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
-
-complex_alphas <- filter(get_alphas, Foodweb == "Complex"); complex_alphas
-simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
-
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5,
-           Selection_form = complex_alphas$Selection_form,                # doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier
-           Multiplier = complex_alphas$Multiplier) %>%                     
-  mutate(b_complex = complex_mean_brackets * a_complex / complex_mean_fitness * Multiplier,
-         b_complex_2.5 = complex_mean_brackets * a_complex_2.5 / complex_mean_fitness * Multiplier,
-         b_complex_97.5 = complex_mean_brackets * a_complex_97.5 / complex_mean_fitness * Multiplier,
-         b_simple = simple_mean_brackets * a_simple / simple_mean_fitness * Multiplier,
-         b_simple_2.5 = simple_mean_brackets * a_simple_2.5 / simple_mean_fitness * Multiplier,
-         b_simple_97.5 = simple_mean_brackets * a_simple_97.5 / simple_mean_fitness * Multiplier)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Regression coefficient")
-
-## Modify to be directional, nonlinear, then correlational with legend in 4th area.
-## Modify so that axes have gamma and beta with the trait as a subscript
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Selection gradient")
-
-```
-
-```{r Parametric Bootstrapping of Regression Coefficients and Selection Gradients, cache=TRUE, include=FALSE}
-
-## DUPLICATE ABOVE EXCEPT MODIFY FOR BOOTMER
-
-## METHOD OF JANZEN AND STERN 1998 ----
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
-alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-test_mean_brackets <- complex_mean_brackets
-test_mean_fitness <- complex_mean_fitness
-test_mean_brackets - alt_mean_brackets # virtually the same
-test_mean_fitness - alt_mean_fitness # virtually the same
-
-# Tidy data for beta terms
-foodweb_tidy_betas <- tidy(bootMer(betas_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
-         Selection_form = c(NA,NA,rep("Directional",6)),
-         Multiplier = rep(1,8))
-
-# Tidy data for gamma terms.
-Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al.
-2008)
-foodweb_tidy_gammas <- tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T) %>%
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
-         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
-         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))
-
-# Combine and tidy the regression (alpha) coefficients
-get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
-  mutate(alpha = statistic, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = ifelse(conf.low*conf.high > 0, "<0.05","NS")) %>% # change 'alpha = estimate' to 'alpha = statistic' for bootstrap.
-Multiply confidence intervals to determine whether the cofficient is signficantly different from zero.
-  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
-
-complex_alphas <- filter(get_alphas, Foodweb == "Complex"); complex_alphas
-simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
-
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5,
-           Selection_form = complex_alphas$Selection_form,                # doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier
-           Multiplier = complex_alphas$Multiplier) %>%                     
-  mutate(b_complex = complex_mean_brackets * a_complex / complex_mean_fitness * Multiplier,
-         b_complex_2.5 = complex_mean_brackets * a_complex_2.5 / complex_mean_fitness * Multiplier,
-         b_complex_97.5 = complex_mean_brackets * a_complex_97.5 / complex_mean_fitness * Multiplier,
-         b_simple = simple_mean_brackets * a_simple / simple_mean_fitness * Multiplier,
-         b_simple_2.5 = simple_mean_brackets * a_simple_2.5 / simple_mean_fitness * Multiplier,
-         b_simple_97.5 = simple_mean_brackets * a_simple_97.5 / simple_mean_fitness * Multiplier)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Regression coefficient")
-
-## Modify to be directional, nonlinear, then correlational with legend in 4th area.
-## Modify so that axes have gamma and beta with the trait as a subscript
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Selection gradient")
-
-```
-
-References {#references .unnumbered}
-==========
+\end{document}

### 2018-09-21 temporary_morgue/Test/Test.tex
getting organized

% !TeX program = pdfLaTeX
\documentclass[smallextended]{svjour3}       % onecolumn (second format)
%\documentclass[twocolumn]{svjour3}          % twocolumn
%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[utf8]{inputenc}

\usepackage[hyphens]{url} % not crucial - just used below for the URL
\usepackage{hyperref}
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
% \journalname{myjournal}
%

%% load any required packages here

\begin{document}

\title{Title here \thanks{Grants or other notes about the article that should go on the front page
should be placed here. General acknowledgments should be placed at the
end of the article.} }
 \subtitle{Do you have a subtitle? If so, write it here}

    \titlerunning{Short form of title (if too long for head)}

\author{  Äüthör 1 \and  Âuthóř 2 \and  }

    \authorrunning{ Short form of author list if too long for running head }

\institute{
        Äüthör 1 \at
     Department of YYY, University of XXX \\
     \email{\href{mailto:abc@def}{\nolinkurl{abc@def}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Âuthóř 2 \at
     Department of ZZZ, University of WWW \\
     \email{\href{mailto:djf@wef}{\nolinkurl{djf@wef}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

\date{Received: date / Accepted: date}
% The correct dates will be entered by the editor

\maketitle

\begin{abstract}
The text of your abstract. 150 -- 250 words.
\\
\keywords{
        key \and
        dictionary \and
        word \and
    }

    \subclass{
                    MSC code 1 \and
                    MSC code 2 \and
            }

\end{abstract}

\def\spacingset#1{\renewcommand{\baselinestretch}%
{#1}\small\normalsize} \spacingset{1}

\section{Introduction}\label{intro}

Your text comes here. Separate text sections with

\section{Section title}\label{sec:1}

Text with citations by Galyardt (2014), (Mislevy 2006).

\subsection{Subsection title}\label{sec:2}

as required. Don't forget to give each section and subsection a unique
label (see Sect. \ref{sec:1}).

\paragraph{Paragraph headings}\label{paragraph-headings}

Use paragraph headings as needed.

\begin{align}
a^2+b^2=c^2
\end{align}

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Galyardt14mmm}{}
Galyardt, April. 2014. ``Interpreting Mixed Membership Models:
Implications of Erosheva's Representation Theorem.'' In \emph{Handbook
of Mixed Membership Models}, edited by Edoardo M. Airoldi, David Blei,
Elena Erosheva, and Stephen E. Fienberg. Chapman; Hall.

\hypertarget{ref-Mislevy06Cog}{}
Mislevy, Robert. 2006. ``Cognitive Psychology and Educational
Assessment.'' In \emph{Educational Assessment}, edited by Robert L.
Brennan. American Council on Education; Praeger Publishers.

\bibliographystyle{spbasic}
\bibliography{bibliography.bib}

\end{document}

### 2018-09-21 temporary_morgue/To_Do.Rmd
getting organized

---
title: "To_Do"
author: "Matt Barbour"
date: "8/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Updated

> Population all tables with R-code to make output reproducible

> Decide whether to include 3-way interaction and update models appropriately. Right now, I'm thinking I shouldn't, because it doesn't jive with estimating the gamma matrix and consequences for the curvature of the fitness landscape.

> Duplicate coefficient estimates for bootstrapped models.

> Put statistical analyses in the supplement to show that there was no differences in phenotypes among the food-web treatments.

> Consider a different way to subset the data: convert all estimates of "surviving" ectoparasitism to gall survival, even though this may include estimates of platygaster parasitism.

> Need a graph showing the conflicting selection pressure imposed on clutch size and oviposition preference in the complex food web.

> Consider calculate difference between curvature matrix of complex and simple food webs to describe the change in curvature

----

> look for uncompressed version of "complex_simple_foodwebs.pdf" on Ruthie or my Macbook

> Use standard regression model to determine significant differences in selection gradients.

> Log-transform predictor variables in order to get a best approximation of the fitness landscape. I can use AIC to justify or reject this idea.

> Add a 3-way trait interaction term to test for these higher-order effects.

> Standardize trait values at the level of the whole data set.

> Calculate selection differentials and estimate how much I may have overestimated the effects of selection on gall diameter.

> Test for differences in trait values among treatments to dispell this idea as a factor driving differences in my selection gradients.

> Change position of figure legend for univariate plots (try placing middle-top with 3 plots across.)

> Get bootstrapped estimates of selection intensity and compare between treatments/

> Fix axis labels on plots (change to mean fitness and trait values)

> Fix size of axis text on plots.

> Modify color of figures for illustration of simple and complex food webs and make uncompressed.

> Conduct an analysis that looks at the selection gradients imposed by each guild of parasitoids and visualizes it.

> Spend 10 min. trying to figure out how to double-space the manuscript.

> Tidy repo

> Draft Discussion

> Calculate selection gradients acting on Platygaster. This will enable me to have a discussion about potential indirect evolutionary cascades occuring via changes in network complexity.

### 2018-09-21 temporary_morgue/gall_report.Rmd
getting organized

---
title: "Distributions of gall phenotypes"
author: "Matt Barbour"
date: "January 29, 2018"
output:
  html_document: default
  html_notebook: default
---

```{r load libraries, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse)
library(cowplot)
library(GGally)
```

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Function to return points and geom_smooth allow for the method to be changed
my_fn <- function(data, mapping, method="lm", ...){
      p <- ggplot(data = data, mapping = mapping) + 
      geom_point(shape = 1) + 
      geom_smooth(method=method, ...)
      p
    }
```

```{r load data, message=FALSE, warning=FALSE, include=FALSE}
gall_selection.df <- read_csv("gall_selection_data.csv") %>%
  mutate(Plant_Position = as.factor(Plant_Position),
         Gall_Number = as.factor(Gall_Number),
         Treatment.focus = as.factor(Treatment.focus),
         Treatment = as.factor(Treatment),
         Location = as.factor(Location),
         phenology = as.factor(phenology),
         Genotype = as.factor(Genotype),
         Gall_Letter = as.factor(Gall_Letter)) %>%
  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%

  # subset data for analysis
  filter(phenology == "early", Location == "tree") %>%
  mutate(gall_survival = ifelse(pupa > 0, 1, 0),
         platy_bin = ifelse(platy > 0, 1,0),
         ectos_bin = ifelse(ectos > 0, 1,0))
```

<br>

Here is what the distributions look like for the three gall phenotypes I measured. Sample size (n) corresponds to independent observations (e.g. individual-level for gall size, gall-level for number of individuals, plant-level for density). Dotted lines correspond to the mean phenotype. I plotted number of individuals as a histogram because its distribution is more discrete.
```{r trait distributions, echo=FALSE, message=FALSE, warning=FALSE}
size <- gall_selection.df %>%
  ggplot(., aes(x=Gall_Height_mm)) + geom_density(fill="grey", alpha=0.5) + 
  geom_vline(xintercept = mean(gall_selection.df$Gall_Height_mm), linetype="dotted") +
  geom_text(x=15, y=0.15, label=paste("n=",length(gall_selection.df$Gall_Height_mm))) +
  xlab("Gall size (mm)")

indiv <- gall_selection.df %>%
  distinct(Gall_Number, gall_individuals) %>%
  ggplot(., aes(x=gall_individuals)) + geom_histogram() + 
  geom_vline(xintercept = mean(distinct(gall_selection.df, Gall_Number, gall_individuals)$gall_individuals), linetype="dotted") + 
  scale_x_continuous(breaks=1:10, labels=1:10) + 
  geom_text(x=5, y=200, label=paste("n=",length(distinct(gall_selection.df, Gall_Number, gall_individuals)$gall_individuals))) +
  xlab("Individuals per gall")

dens <- gall_selection.df %>%
  distinct(Plant_Position, Density_per_100_shoots) %>%
  ggplot(., aes(x=Density_per_100_shoots)) + geom_density(fill="grey", alpha=0.5) + 
  geom_vline(xintercept = mean(distinct(gall_selection.df, Plant_Position, Density_per_100_shoots)$Density_per_100_shoots), linetype="dotted") +
  geom_text(x=50, y=0.02, label=paste("n=",length(distinct(gall_selection.df, Plant_Position, Density_per_100_shoots)$Density_per_100_shoots))) +
  xlab("Density (individuals/100 shoots)")

size
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
indiv
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
dens
```

<br>

Below, I've plotted the correlations among these traits. Note that all data points are at the individual-level (n = 1714). 
```{r phenotypic correlations, echo=FALSE, message=FALSE, warning=FALSE}
gall_selection.df %>% 
  select(Size = Gall_Height_mm, Individuals = gall_individuals, Density = Density_per_100_shoots) %>%
  ggpairs(., lower = list(continuous=wrap(my_fn, method="lm")))
```

<br>

These phenotypes also vary substantially among plant genotypes. The boxplots below show the median (black bar), 25th - 75th percentiles (IQR, box edges), 1.5 x IQR (whiskers), and outliers (points).

```{r phenotypes by genotype, echo=FALSE, message=FALSE, warning=FALSE}
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")

size.geno <- gall_selection.df %>%
  ggplot(., aes(x=Genotype, y=Gall_Height_mm, fill=Genotype)) + geom_boxplot(outlier.shape = 1, show.legend = F) +
  scale_fill_manual(values=cbPalette) +
  ylab("Gall size (mm)")

indiv.geno <- gall_selection.df %>%
  distinct(Genotype, Gall_Number, gall_individuals) %>%
  ggplot(., aes(x=Genotype, y=gall_individuals, fill=Genotype)) + geom_boxplot(outlier.shape = 1, show.legend = F) +
  scale_fill_manual(values=cbPalette) +
  ylab("Individuals per gall")

dens.geno <- gall_selection.df %>%
  distinct(Genotype, Plant_Position, Density_per_100_shoots) %>%
  ggplot(., aes(x=Genotype, y=Density_per_100_shoots, fill=Genotype)) + geom_boxplot(outlier.shape = 1, show.legend = F) +
  scale_fill_manual(values=cbPalette) +
  ylab("Density (individuals/100 shoots)")

size.geno

#plot_selection <- bind_rows(mutate(gall_selection.df, Selection = "Before selection"),
#                            mutate(filter(gall_selection.df, gall_survival == 1), Selection = "After selection"))
#plot_selection$Selection <- factor(plot_selection$Selection, levels = c("Before selection", "After selection"))
#plot_selection$Treatment.focus_lab <- factor(plot_selection$Treatment.focus, levels = c("Control", "Ectoparasitoid exclusion"), labels=c("Complex","Simple"))
#selection.summary <- group_by(plot_selection, Treatment.focus_lab, Selection) %>% 
#  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), mean, na.rm=TRUE)

#size_plot <- ggplot(plot_selection, aes(x=Gall_Height_mm)) + 
#  geom_density(fill="grey", alpha=0.5) + 
#  geom_vline(data = selection.summary, aes(xintercept = Gall_Height_mm), linetype="dotted") +
#  facet_grid(Selection ~ Treatment.focus_lab)

#size.genotype_plot <- ggplot(plot_selection, aes(x=Genotype, y=Gall_Height_mm, fill=Selection)) + geom_boxplot() + #facet_wrap(~Treatment.focus_lab, ncol=1)

#plot_grid(size_plot, size.genotype_plot, ncol = 1)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
indiv.geno
```

```{r, echo=FALSE, message=FALSE, warning=FALSE}
dens.geno
```

### 2018-09-21 temporary_morgue/morgue_supp_mat.Rmd
getting organized

--- 2018-06-08 morgue_supp_mat.Rmd
@@
 ---
+
+```{r Interval plots of univariate landscapes}
+## Interval Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
+  #group_by(Food_Web) %>%
+  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.gall_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+
+## Interval Plot: Relative Fitness ----
+
+bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
+  group_by(Food_Web) %>%
+  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.clutch_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.clutch_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+
+## Interval Plot: Relative Fitness ----
+
+# unclear to me why the complex intervals are weird...
+bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
+  #group_by(Food_Web) %>%
+  #mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.female_preference, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.female_preference, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
+
+```{r OLD Gall Size Fitness Landscape, eval=FALSE}
+
+## Control ----
+RF_control_gall_size <- bootstrap_fitness(
+  logistic_model = glmer_control, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-2,2,length.out=1000), #sort(control_df$sc.gall_size),
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Treatment ----
+RF_treatment_gall_size <- bootstrap_fitness(
+  logistic_model = glmer_treatment, 
+  newdata = expand.grid(
+     sc.gall_size = seq(-2,2,length.out=1000), #sort(treatment_df$sc.gall_size), 
+     sc.clutch_size = 0,
+     sc.female_preference = 0),
+  bootstraps=100)
+
+## Spaghetti Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
+  group_by(ID, Food_Web) %>%
+  mutate(relative_fitness = fitness/mean(fitness)) %>%
+  ungroup() %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Relative Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  group_by(Food_Web) %>%
+  mutate(relative_fitness = average/mean(average), lower_RF = lower/mean(lower), upper_RF = upper/mean(upper)) %>%
+  ggplot(., aes(x=sc.gall_size, y=relative_fitness)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower_RF, ymax=upper_RF, fill=Food_Web), alpha=0.25)
+
+## Spaghetti Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  select(-sc.clutch_size, -sc.female_preference) %>%
+  gather(ID, fitness, -sc.gall_size, -Food_Web) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.gall_size, y=fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.1)) +
+  scale_size_manual(values=c(1.5,0.25))
+
+## Interval Plot: Absolute Fitness ----   
+bind_rows(mutate(RF_treatment_gall_size, Food_Web = "Simple"), 
+          mutate(RF_control_gall_size, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.gall_size, y=average)) +
+  geom_line(aes(color=Food_Web)) +
+  geom_ribbon(aes(ymin=lower, ymax=upper, fill=Food_Web), alpha=0.25)
+```
 

### 2018-09-21 temporary_morgue/ms_complexity_selection.Rmd
getting organized

--- 2018-09-20 ms_complexity_selection.Rmd
@@
 visreg(foodweb_glmer)
+```
+
+```{r Model Modification}
+
+# In terms of the gammas, there was only evidence that food-web treatment altered nonlinear selection on preference
+summary(foodweb_glmer)
+
+# Therefore, we refit a model that only included this effect of food-web treatment on the gamma coefficients
+foodweb_glmer_revised <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+
+# Note that we still observe that food-web treatment alters nonlinear selection on female preference
+# There is also now marginal evidence for nonlinear selection on diameter as well as correlational selection between diameter and clutch (Diam:Clutch) and between diameter and preference (Diam:Pref).
+summary(foodweb_glmer_revised)
+
+summary(betas_glmer)
+
+betas_glmer_revised <- update(betas_glmer, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
+summary(betas_glmer_revised)
+
+foodweb_glmer_revised_again <- update(foodweb_glmer_revised, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
+summary(foodweb_glmer_revised_again)
 ```
@@
 
-```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE}
+```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE, eval=FALSE}
+## NOT WORKING
+
+library(latex2exp)
+data.frame(x=1:10,y=1:10)
 p<-ggplot(data=x, aes(x=y, y=x)) +
@@
 Would we expect any confounding effects on nonlinear selection?
-```{r Confounding effects of parasitism on gall size}
+```{r Confounding effects of parasitism on gall size, include=FALSE, eval=FALSE}
 ## paired t-test approach. Weakness is that it only calculates the selection differential rather than the gradient, which is more meaningful for multivariate trait evolution
@@
 For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
-```{r Selection on Platygaster Traits}
+```{r Selection on Platygaster Traits, include=FALSE, eval=FALSE}
 platy_selection_df <- gall_selection.df %>%
@@
 
-```{r DUPLICATE for bootstrap test}
-
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
-complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(foodweb_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-complex_mean_brackets - alt_mean_brackets
-complex_mean_fitness - alt_mean_fitness
-
-foodweb_tidy_4 <- filter(tidy(bootMer(foodweb_glmer_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
-foodweb_tidy_3 <- filter(tidy(bootMer(foodweb_glmer_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
-                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-foodweb_tidy_2 <- filter(tidy(bootMer(foodweb_glmer_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
-                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-foodweb_tidy <- filter(tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T), 
-                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
-                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs.
-This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
-#foodweb_tidy_4 <- filter(tidy(foodweb_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
-#foodweb_tidy_3 <- filter(tidy(foodweb_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-#foodweb_tidy_2 <- filter(tidy(foodweb_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-#foodweb_tidy <- filter(tidy(foodweb_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-
-get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
-  mutate(alpha = round(statistic, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3)) %>%
-  select(term, alpha, alpha_2.5, alpha_97.5)
-
-complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
-simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
-  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
-         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
-         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
-         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
-         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
-         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3))
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-```
-
 Note that equation 3 in Phillips and Arnold 1998 is good justification for why quadratic selection cofficients should be multiplied by two (but not correlational ones?)
@@
 
-```{r Slope and Curvature of Fitness Landscape, include=FALSE}
+```{r Slope and Curvature of Fitness Landscape, include=FALSE, eval=FALSE}
 betas <- c(-0.5,-0.5,0.5)
@@
 
+```{r LATEX NEED TO CHECK, eval=FALSE, include=FALSE}
 $$\text{Slope}_{complex} = \beta_{complex} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.4 \\ 0 \\ -0.3 \end{pmatrix}$$
@@
 $$\text{Curvature}_{simple} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-
-```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE}
+```
+
+```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE, eval=FALSE}
 
@@
 
-```{r For platy ecto comparison}
+```{r For platy ecto comparison, include=FALSE, eval=FALSE}
 ## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
@@
 
-```{r}
+```{r include=FALSE, eval=FALSE}
 ## Calculating same coefficients as for simple vs. complex food web
@@
 Still, this stronger evidence for correlational selection should be interpreted with caution since the GLM does not account for the non-indepedence of these fitness estimates.
-```{r Compare GLMM to GLM}
+```{r Compare GLMM to GLM, include=FALSE, eval=FALSE}
 ## Fit GLMs. Dispersion parameter was ~1, so I just used a binomial model. 
@@
 
-```{r Get Selection Gradients for GLM}
+```{r Get Selection Gradients for GLM, include=FALSE, eval=FALSE}
 complex_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
@@
 
-```{r Mortality, include=F}
+```{r Mortality, include=FALSE, eval=FALSE}
 # 8-10% mortality induced by intraguild predators
@@
 
-```{r Figure 1, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
+```{r Figure 1, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
 Black arrows denote 'who-eats-whom' in this network of trophic interactions."}
@@
 
-We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ($\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).
+We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ().
 
@@
 **Old**
+
+```{r OLD TEXT, include=FALSE, eval=FALSE}
+$\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).
+
 Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
@@
 
-```{r Get Gall Diameter Relative Fitness Landscape, include=FALSE, cache=TRUE}
+-->
+```
+
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE, eval=FALSE}
 
@@
 
-```{r Get Clutch Size Fitness Landscape, include=FALSE, cache=TRUE}
+```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE, eval=FALSE}
 
@@
 
-```{r Get Female Preference Fitness Landscape, include=FALSE, cache=TRUE}
+```{r Get Female Preference Fitness Landscape, include=FALSE, eval=FALSE}
 
@@
 
-```{r Get Clutch Size x Female Preference Landscape, include=FALSE, cache=TRUE}
+```{r Get Clutch Size x Female Preference Landscape, include=FALSE, eval=FALSE}
 
@@
 
-```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, cache=TRUE}
+```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, eval=FALSE}
 
@@
 
-```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, cache=TRUE}
+```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, eval=FALSE}
 
@@
 
-```{r Fitness Landscape Plot Helpers, include=FALSE, cache=TRUE}
+```{r Fitness Landscape Plot Helpers, include=FALSE, eval=FALSE}
 
@@
 
-```{r Plot Univariate Landscapes, include=FALSE, cache=TRUE}
+```{r Plot Univariate Landscapes, include=FALSE, eval=FALSE}
 uni_breaks <- c(0.1,0.5,1)
@@
 
-```{r Univariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs.
+```{r Univariate_Landscapes, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs.
 simple food webs.
@@
 
-```{r Plot Multivariate Fitness Landscape, include=FALSE, cache=TRUE}
+```{r Plot Multivariate Fitness Landscape, include=FALSE, eval=FALSE}
 
@@
 
-```{r Multivariate_Landscapes, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs.
+```{r Multivariate_Landscapes, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs.
 simple food webs.
@@
 #save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
-```
-
-```{r AIC Model Comparison, include=FALSE, cache=TRUE}
-
-# Control ----
-AIC(beta_control, quad_control, corr_control)
-
-glm.beta_control <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=control_df, family=binomial(link=logit))
-
-beta_control.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                                   (1|Gall_Number),
-                                 data = control_df,
-                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-AIC(beta_control, glm.beta_control)
-AIC(beta_control, beta_control.REonlyGallID)
-overdisp_fun(beta_control)
-
-# Treatment ----
-AIC(beta_treatment, quad_treatment, corr_treatment)
-
-glm.beta_treatment <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data=treatment_df, family=binomial(link=logit))
-
-beta_treatment.REonlyGallID <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                                   (1|Genotype/Plant_Position),
-                                 data = treatment_df,
-                                 family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-overdisp_fun(beta_treatment)
-
-AIC(beta_treatment, glm.beta_treatment)
-AIC(beta_treatment, beta_treatment.REonlyGallID)
-anova(beta_treatment, beta_treatment.REonlyGallID)
-anova(beta_treatment, glm.beta_treatment)
 ```
@@
 
-```{r Univariate Absolute Fitness Landscapes, include=FALSE}
+```{r Univariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
 ## Absolute fitness plots ----
@@
 
-```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE}
+```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
 
@@
 
-```{r Multivariate Absolute Fitness Landscapes, include=FALSE}
+```{r Multivariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
 
@@
 
-```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE}
+```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
 # Get legend
@@
 ```
-
-```{r OLD GAMM comparison, eval=FALSE, include=FALSE}
-gamm_control <- gamm.model(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
-                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference, 
-                         data = control_df)
-summary(gamm_control$gam)
-
-gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log.clutch_size"), covariates = c("sc.log1p.female_preference"), se.method="none")
-gam.gradients(gamm_control$gam, phenotype=c("sc.gall_size","sc.log1p.female_preference"), covariates = c("sc.log.clutch_size"), se.method="none")
-gam.gradients(gamm_control$gam, phenotype=c("sc.log.clutch_size","sc.log1p.female_preference"), covariates = c("sc.gall_size"), se.method="none")
-
-AIC(corr_control, gamm_control$mer)
-```
-
-```{r OLD Selection Gradients - Complex Food Web, eval=FALSE, include=FALSE}
-# note that I've switched to using the lme4 package to analyzing the GLMM
-
-# GLMM ----
-glmer_control <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
-                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
-                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
-                           (1|Genotype/Plant_Position/Gall_Number),
-                         data = control_df,
-                         family = binomial(link = logit), optimizer = "bobyqa")
-summary(glmer_control)
-
-# Mean fitness ----
-Wbar_control <- inverse_logit(fixef(update(glmer_control, .~. -sc.gall_size -sc.log.clutch_size -sc.log1p.female_preference)))
-
-# Confidence intervals for selection gradients ----
-boot_Beta_control <- bootMer(glmer_control, FUN = Beta_avg_grad, nsim=100, parallel="multicore", ncpus=32)
-
-## Summary ----
-summary_Beta_glmm_control <- data.frame(
-  Phenotype = c("Gall size", "Clutch size", "Female preference"),
-  Food_Web = "Complex",
-  Model = "GLMM",
-  Beta = round(Beta_avg_grad(glmer_control),3),
-  lower_2.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.025)),3),
-  upper_97.5 = round(apply(boot_Beta_control$t, 2, FUN = function(bootstraps) quantile(bootstraps, 0.975)),3))
-
-summary_Beta_glmm_control
-```
-
-```{r Get 3D, include=FALSE, eval=FALSE}
-# note that length.out=10 now
-library(FD)
-
-# Control ----
-RF_control_3D <- bootstrap_fitness(
-  logistic_model = beta_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=10),
-     sc.log.clutch_size = seq(-1,1,length.out=10),
-     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
-  bootstraps=NULL)
-mean(RF_control_3D$relative_fitness$average)
-
-control_traits <- RF_control_3D$relative_fitness %>%
-  filter(average < 1) %>%
-  select(-average) %>%
-  mutate(Treatment = "Control")
-
-FD_control <- dbFD(control_traits)
-
-FD_control
-
-# Treatment ----
-RF_treatment_3D <- bootstrap_fitness(
-  logistic_model = beta_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=10),
-     sc.log.clutch_size = seq(-1,1,length.out=10),
-     sc.log1p.female_preference = seq(-1,1,length.out=10)), 
-  bootstraps=NULL)
-mean(RF_treatment_3D$relative_fitness$average)
-
-treatment_traits <- RF_treatment_3D$relative_fitness %>%
-  filter(average < 1) %>%
-  select(-average) %>%
-  mutate(Treatment = "Treatment")
-
-FD_treatment <- dbFD(treatment_traits)
-
-bind_rows(
-  data.frame(FD_control),
-  data.frame(FD_treatment)
-)
-
-library(vegan)
-all_traits <- bind_rows(control_traits, treatment_traits)
-
-dim(control_traits)
-dim(treatment_traits)
-
-traits_betadisper <- betadisper(d = vegdist(select(all_traits, -Treatment), method = "euclidean"), group = all_traits$Treatment)
-boxplot(traits_betadisper)
-
-ggplot(all_traits, aes(x=sc.gall_size, y=sc.log1p.female_preference, color=Treatment)) +
-  geom_jitter(width=0.05, size = 2)
-
-ggplot(all_traits, aes(x=sc.gall_size, y=sc.log.clutch_size, color=Treatment)) +
-  geom_jitter(width=0.05, size=2)
-
-ggplot(all_traits, aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, color=Treatment)) +
-  geom_jitter(width=0.05, size=2)
-
-##
-
-control_traits <- RF_control_3D$relative_fitness %>%
-  mutate(Treatment = "Control", average_cut = cut(average, breaks = c(0,0.9,1.1,2)))
-control_traits$average_cut
-
-treatment_traits <-RF_treatment_3D$relative_fitness %>%
-  mutate(Treatment = "Treatment", average_cut = cut(average, breaks = c(0,0.9,1.1,2)))
-
-all_traits <- bind_rows(control_traits, treatment_traits)
-table(all_traits$Treatment, all_traits$average_cut)
-
-ggplot(all_traits, aes(x=average, fill=Treatment)) +
-  geom_density(alpha=0.2) +
-  xlab("Relative fitness")
-
-data.frame(control = var(control_traits$average), treatment = var(treatment_traits$average))
-#all_traits %>%
-#  filter(average > 1) %>%
-#  ggplot(., aes(x=average, color=Treatment)) + geom_density()
-
-##
-
-#control_traits <- RF_control_3D$relative_fitness %>%
-#  mutate(Treatment = "Control", abund = average*100)
-
-#treatment_traits <-RF_treatment_3D$relative_fitness %>%
-#  mutate(Treatment = "Treatment", abund = average*100)
-
-#all_traits <- bind_rows(control_traits, treatment_traits)
-
-#library(MASS)
-#all_traits %>%
-#  ggplot(., aes(x=sc.log.clutch_size, y=sc.log1p.female_preference)) +
-#  geom_point() +
-#  stat_density_2d(aes(fill = stat(level)), geom = "polygon")
-```
-
-```{r Plot Univariate Landscapes OLD, include=FALSE, cache=TRUE, eval=FALSE}
-
-# Gall Diameter ----   
-RF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, relative_fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  geom_hline(yintercept = 1, linetype = "dotted") +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SD)") +
-  ylab("Relative fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-
-# Clutch size ----
-RF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log1p.female_preference) %>%
-  gather(ID, relative_fitness, -sc.log.clutch_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.clutch_size, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  geom_hline(yintercept = 1, linetype = "dotted") +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SD)") +
-  ylab("Relative fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-
-# Female preference ----
-RF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$relative_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log.clutch_size) %>%
-  gather(ID, relative_fitness, -sc.log1p.female_preference, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.female_preference, y=relative_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  geom_hline(yintercept = 1, linetype = "dotted") +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SD)") +
-  ylab("Relative fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = RF_gradient_scale, labels = RF_gradient_scale) +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  coord_cartesian(ylim = c(min(RF_gradient_scale), max(RF_gradient_scale)))
-```
-
-```{r Figure 2 Univariate Landscapes OLD, echo=FALSE, eval=FALSE}
-
-# Get legend
-RF_uni_legend <- get_legend(RF_uni_size)
-
-# Make plots
-RF_uni_plots <- plot_grid(RF_uni_size + theme(legend.position = "none",
-                                              axis.text.x = element_text(size=10),
-                                              axis.title.x = element_text(size=11)), 
-                       RF_uni_clutch + theme(legend.position = "none", 
-                                          axis.title.y = element_blank(), axis.text.y = element_blank(),
-                                          axis.text.x = element_text(size=10),
-                                          axis.title.x = element_text(size=11)),
-                       RF_uni_pref + theme(legend.position = "none", 
-                                        axis.title.y = element_blank(), axis.text.y = element_blank(),
-                                        axis.text.x = element_text(size=10),
-                                        axis.title.x = element_text(size=11)),
-                       labels = "AUTO", ncol = 3, align='hv')
-
-RF_gradients <- ggdraw(RF_uni_plots) + draw_grob(RF_uni_legend, x = 0.8, y=0)
-#RF_gradients
-RF_uni_plots
-#save_plot("RF_gradients.png", RF_gradients, base_height=6, base_width = 8)
-#save_plot("RF_gradients.pdf", RF_gradients, base_height=6, base_width = 8)
-```
-
-```{r Plot Multivariate Fitness Landscape OLD, include=FALSE, cache=TRUE, eval=FALSE}
-
-# Clutch x Preference ----
-RF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$relative_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Female preference (SD)") +
-  ylab("Clutch size (SD)") +
-  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
-
-# Size x Clutch ----
-RF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$relative_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SD)") +
-  ylab("Clutch size (SD)") +
-  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
-
-# Size x Preference ----
-RF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$relative_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$relative_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SD)") +
-  ylab("Female preference (SD)") +
-  #scale_fill_gradient2(midpoint=1, limits = c(RF_range$min, RF_range$max))
-  scale_fill_viridis(limits = c(RF_range$min, RF_range$max), name = "Relative fitness") + 
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1))
-```
-
-```{r Figure 3 Multivariate Landscapes OLD, echo=FALSE, eval=FALSE}
-
-# Get legend
-RF_landscape_legend <- get_legend((RF_plot_size.x.preference + theme(legend.title = element_text(size=12), legend.text=element_text(size=10))))
-
-# Format plots
-RF_landscape_plots <- plot_grid(
-  RF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank(), axis.text.x = element_blank(), axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)),
-  RF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank(), axis.text = element_text(size=9), axis.text.y = element_blank(), axis.title = element_text(size=11), strip.text = element_text(size=11)),
-  RF_plot_size.x.preference + theme(legend.position = "none", axis.text = element_text(size=9), axis.title = element_text(size=11), strip.text = element_text(size=11)), 
-  nrow=2, align="hv", labels = "AUTO")
-RF_landscape_2d <- ggdraw(RF_landscape_plots) + draw_grob(RF_landscape_legend, x = 0.7, y=-0.2)
-RF_landscape_2d
-#save_plot("RF_landscapes_2d.png", RF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("RF_landscapes_2d.pdf", RF_landscape_2d, base_height=6, base_width = 8)
-```

### 2018-09-21 temporary_morgue/ms_complexity_selection.tex
getting organized

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

\usepackage{lineno} % add
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\bibliographystyle{elsarticle-harv}
\biboptions{sort&compress} % For natbib
\usepackage{graphicx}
\usepackage{booktabs} % book-quality tables
%%%%%%%%%%%%%%%% end my additions to header

\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \usepackage{fontspec}
  \ifxetex
    \usepackage{xltxtra,xunicode}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{color}
\usepackage{fancyvrb}
\newcommand{\VerbBar}{|}
\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
% Add ',fontsize=\small' for more characters per line
\usepackage{framed}
\definecolor{shadecolor}{RGB}{248,248,248}
\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
\newcommand{\ImportTok}[1]{#1}
\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
\newcommand{\BuiltInTok}[1]{#1}
\newcommand{\ExtensionTok}[1]{#1}
\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
\newcommand{\RegionMarkerTok}[1]{#1}
\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
\newcommand{\NormalTok}[1]{#1}
\usepackage{graphicx}
% We will generate all images so they have a width \maxwidth. This means
% that they will get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
\else\Gin@nat@width\fi}
\makeatother
\let\Oldincludegraphics\includegraphics
\renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=\maxwidth]{#1}}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore},
            colorlinks=true,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls

\setcounter{secnumdepth}{0}
% Pandoc toggle for numbering sections (defaults to be off)
\setcounter{secnumdepth}{0}
% Pandoc header

\begin{document}
\begin{frontmatter}

  \title{Phenotypic evolution is less constrained in complex food webs or
Food-web complexity alters the fitness landscape of an insect herbivore}
    \author[a,b]{Matthew A. Barbour\corref{c1}}
   \ead{matthew.barbour@ieu.uzh.ch} 
   \cortext[c1]{Corresponding Author}
    \author[a,c]{Christopher J. Greyson-Gaito}

    \author[a]{Arezoo Sootodeh}

    \author[d]{Brendan Locke}

    \author[b]{Jordi Bascompte}

      \address[a]{University of British Columbia, Department of Zoology, 6270 University
Blvd., Vancouver, BC, V6T 1Z4, Canada}
    \address[b]{University of Zurich, Department of Evolutionary Biology and
Environmental Studies, Winterthurerstrasse 190, Zurich, 8057,
Switzerland}
    \address[c]{University of Guelph, Department of Integrative Biology, 50 Stone Rd.
East, Guelph, ONT, N1G 2W1, Canada}
    \address[d]{Humboldt State University, Department of Biological Sciences, 1 Harpst
St., Arcata, CA, 95521, USA}

  \begin{abstract}
  Species-interaction networks provide a mechanistic link between
  community and population ecology, as they describe who interacts with
  whom in a community. Similarly, fitness landscapes provide a mechanistic
  link between population and evolutionary ecology, as they describe the
  influence of natural selection on phenotypic variation. It remains
  unclear, however, how the network structure of species interactions
  shapes the fitness landscape. Understanding this relationship is likely
  key for developing a predictive ecology across scales of biological
  organization. To examine the relationship between network structure and
  the fitness landscape, we conducted a field experiment that manipulated
  the network of trophic interactions (simple vs.~complex) influencing the
  fitness of an insect herbivore. We then quantified the fitness landscape
  of herbivores in each treatment by measuring herbivore survival as a
  function of multiple phenotypic traits. We found that more traits were
  under selection in the simple vs.~complex trophic network. This occurred
  because different natural enemies impose different selection pressures
  on herbivore traits, thereby minimizing relative fitness differences
  among herbivore phenotypes in the complex network. Our work suggests
  that more complex trophic networks allow phenotypic variation to
  persist, which could facilitate subsequent adaptive evolution of
  populations to environmental change.
  \end{abstract}

 \end{frontmatter}

\section{Introduction}\label{introduction}

The fitness landscape provides a unifying framework for linking the
ecology and evolution of populations (Lande 2007; McPeek 2017). The
average fitness of a population is a common currency in ecology and
evolution, but usually goes by different names in each field. Ecologists
refer to it as per-capita population growth rate (\(dN/Ndt\)), whereas
evolutionary biologists call it the natural log of population mean
fitness (\(ln(\bar W_N)\). In addition to having different names,
ecologists and evolutionary biologists have typically focused on
different processes that shape the fitness landscape. For example,
population ecologists have long studied the effect of a population's
density on its per-capita growth rate (i.e.~density-dependence, CITE
Foundational and current work). In contrast, evolutionary biologists
have focused on how the mean trait value of a population influences its
average fitness, as this describes the direction and magnitude of
natural selection (CITE foundational and current work). Therefore, the
fitness landscape describes the joint ecological and evolutionary
dynamics of a population in a given environment.

Community ecologists have extended the ecological side of the fitness
landscape by incorporating network theory. Species-interaction networks,
such as a food web describing who eats whom, provide an explicit
representation of the biotic environment as they describe the
interdependency of populations within an ecological community. This has
provided an effective framework for predicting how changes in the biotic
environment (e.g.~density of directly and indirectly connected species)
will impact population dynamics within species-rich communities. At the
same time, evolutionary biologists have long recognized that changes in
the biotic environment can alter the dynamics of natural selection.
However, the biotic environment in which populations are evolving often
remains a bit of a ``black box'' that's labelled by a general ecological
process such as competition, predation, or mutualism. Because of this,
it remains difficult to predict how changes in the biotic environment
will affect the direction and magnitude of natural selection. Such
predictions are urgently needed given the rapid changes in the biotic
environment that most populations are currently experiencing throughout
the world.

Here, we integrate species-interaction networks and the fitness
landscape to empirically test how changes in the biotic environment --
network of species interactions -- affect the dynamics of natural
selection. Specifically, we conducted a field experiment that
manipulated the diversity of insect parasitoids that were able to impose
selection on an abundant insect herbivore (\emph{Iteomyia
salicisverruca})(Fig. 1). The larva of this herbivore species induce
tooth-shaped galls when they feed on the developing leaves of willow
trees (\emph{Salix} sp., Russo (2006)). These galls provide protection
from generalist predators (e.g.~ants, spiders), thus the network of
interacting parasitoids provides a realistic representation of the
biotic environment this insect herbivore is experiencing. Therefore, our
manipulation of parasitoid diversity alters the diversity of
interactions, or food-web complexity, that this insect herbivore
experiences.

Changes in food-web complexity could influence a resource population's
fitness landscape in at least two ways. First, if a more diverse
community of consumers is more effective at suppressing resource
densities (Ives, Cardinale, and Snyder (2005)), then this will result in
lower mean fitness of the resource population. A reduction in mean
fitness, all else equal, will intensify natural selection (Hunter et al.
(2018)). On the other hand, if consumers impose different selection
pressures on resource traits, then more diverse communities could dampen
the strength of selection acting on a given trait. This is because a
greater diversity in selection pressures is equivalent to greater
uncertainty in the selective environment. Thus, a more diverse consumer
community may relax the net selection pressures acting on resource
traits. Here, we evaluate these hypothesized relationships through an
experimental test of how changes in food-web complexity alters the
fitness landscape of a resource population.

\section{Materials \& Methods}\label{materials-methods}

\subsection{Study Site}\label{study-site}

We conducted our study within a four-year old common garden of coastal
willow (\emph{Salix hookeriana}) located at Humboldt Bay National
Wildlife Refuge (HBNWR) (40°40'53``N, 124°12'4''W) near Loleta,
California, USA. This common garden consists of 26 different willow
genotypes that were collected from a single population of willows
growing around Humboldt Bay. Stem cuttings of each genotype (25
replicates per genotypes) were planted in a completely randomized design
in two hectares of a former cattle pasture at HBNWR. Willows in our
garden begin flowering in February and reach their peak growth in early
August. During this study, willows had reached 5 - 9m in height. Further
details on the genotyping and planting of the common garden are
available in Barbour et al. (2015).

\subsection{Food-Web Manipulation}\label{food-web-manipulation}

We setup our food-web manipulation across 128 plants soon after galls
began developing on \emph{S. hookeriana} in early June of 2013. These
128 plants came from eight different plant genotypes, spanning the range
of trait variation observed in this willow population (Barbour et al.
(2015)). On treatment plants (8 replicates per genotype), we enclosed 14
galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI,
USA) to exclude three parasitoid species that attack during larva
development (hereafter larval parasitoids). This treatment did not
exclude the egg parasitoid \emph{Platygaster} sp. which attacks prior to
gall initiation (note that in Cecidomyiid midges, larva initiate gall
development CITE). On control plants (8 replicates per genotype), we
used flagging tape to mark 14 galled leaves per plant
(\textasciitilde{}30 larva), allowing the full suite of parasitoids to
attack \emph{Iteomyia}. Marking galls with flagging tape ensured that we
compared control and treatment galls with similar phenology when we
collected galls later in the season. Our food-web manipulation altered
the average number of trophic interactions that \emph{Iteomyia} was
exposed to from BLANK on control plants to BLANK on treatment plants.
Thus, we refer to galls on control plants as being exposed to a
`complex' food web, whereas galls on treatment plants were exposed to a
`simple' food web. In late August, we collected marked and bagged galls
from each plant, placed them into 30 mL vials and kept them in the lab
for 4 months at room temperature. We then opened galls under a
dissecting scope and determined whether larva survived to pupation (our
measure of fitness) or were parasitized. Since we were interested in
selection imposed by interactions with parasitoids, we restricted our
data to larva that either survived to pupation, was parasitized by an
egg parasitoid (\emph{Platygaster} sp.), or was parasitized by a larval
parasitoid. For the food-web treatment that excluded parasitoids, we
further restricted our data by removing any instances of parasitism by a
larval parasitoid. This represented less than 3\% of the observations in
this food-web treatment and allowed us to focus our inferences of
selection on those imposed by the egg parasitoid.\\
Together, we had survival estimates for 1,306 larva from 607 galls, 111
plants, and 8 plant genotypes.

\subsection{Measuring Gall Traits}\label{measuring-gall-traits}

We collected data on three different traits that we anticipated would
experience selection based on our previous work (Barbour et al. (2016))
and others work with Cecidomyiid midges (Weis, Price, and Lynch (1983),
Heath, Abbot, and Stireman (2018)). First, we measured gall diameter as
the size of each gall chamber to the nearest 0.01 mm at its maximum
diameter (perpendicular to the direction of plant tissue growth). Our
previous work has shown that a larger gall diameter provides a refuge
for larva from parasitoid attack (Barbour et al. (2016)). Second, we
measured the clutch size of adult female midges by counting the number
of chambers in each gall (Weis, Price, and Lynch (1983)). All larva
collected from the same multi-chambered gall were scored with the same
clutch size. Third, we measured female preference for oviposition
(egg-laying) sites as the density of larva observed on a plant in an
independent survey. Specifically, we randomly sampled five branches per
tree and summed the number of individual gall chambers observed. We then
converted these counts to a measure of gall density per 100 shoots by
counting the number of shoots on the last branch we sampled. All larva
collected from the same plant were scored with the same female
preference. The measurement of larval densities on plants in the field
is a commonly used index for measuring oviposition preference
(Gripenberg et al. (2010)); however, caution must be taken in inferring
`preference' as larval densities can be influenced by processes other
than preference (Singer (1986)). Fortunately, a couple of features of
our study system suggest that larval density on a plant may be a good
proxy for female preference. For example, since our data comes from a
randomized placement of willow genotypes in a common garden, there is no
consistent bias in which willow genotypes that females are exposed to
while searching for oviposition sites. Also, egg predation is a minor
source of mortality for galling insects in general (Hawkins, Cornell,
and Hochberg (1997)), thus we do not expect any prior egg predation to
bias our estimates of observed larval densities.

\subsubsection{Quantifying the Fitness
Landscape}\label{quantifying-the-fitness-landscape}

To characterize the shape of the fitness landscape in simple and complex
food webs, we first used a generalized linear mixed model to quantify
selection surfaces on individual traits. We used a binomial error
distribution (logit link function) since larval survival (0 or 1) was
our response variable and measure of fitness. We specified linear and
quadratic terms for each gall trait as well as linear interaction terms
between each gall trait as fixed effects in the statistical models. To
account for the correlated structure of clutch size (gall level) and
female preference (plant level) as well as any independent effects of
willow genotype on larval survival, we specified gall ID nested within
plant ID nested within plant genotype as random effects. Since we were
interested in characterizing the fitness landscape -- the relationship
between mean trait values and population mean fitness -- we assumed the
mean value of our random effects (i.e.~setting them to zero) to estimate
selection gradients. Also, the fitness landscape assumes that traits
distributions are multivariate normal. To better meet this assumption,
we log-transformed clutch size and added a small constant (1) to female
preference before log transforming, since our surveys occassionaly
estimated zero larval densities. We then scaled all phenotypic traits to
mean=0 and SD=1 in order to calculate standardized selection gradients
that were comparable across traits and with other studies of natural
selection. We used the method of Frederic J Janzen and Hal S Stearn
(1998) to calculate directional (\(\beta_{z_i}\)), quadratic
(\(\gamma_{z_i,z_i}\)), and correlational (\(\gamma_{z_i,z_j}\))
selection gradients and used parametric bootstrapping (1000 replicates)
to calculate their 95\% confidence intervals (Bolker et al. (2009)). We
estimated directional selection gradients by excluding quadratic terms
and statistical interactions in the model. Note that for visualizing the
fitness landscape we restrict trait axes to \(\pm 1\) SD of the mean
trait value as this contains the majority of the trait distribution that
selection is acting on.

Rather than imposing selection, parasitoids may themselves influence the
expression of herbivore traits. Any influence on trait expression would
bias selection gradients acting on those traits. In our system, it was
plausible that parasitoids may influence chamber growth by promoting
larval feeding (cite), speeding up larva development (cite), or killing
larva before they complete their development (cite). Therefore, our
estimates of selection on chamber diameter may be positively or
negatively biased. To estimate this bias, we subset our data to only
include galls where there was variation in larval survival (1
\textgreater{} survival \textgreater{} 0) within the same gall. We then
calculated ``apparent'' selection differentials for each gall by
comparing the average chamber diameter of all larva (before
``selection'') to the average chamber diameter of surviving larva and
analyzed separate one-sample t-tests for each food-web treatment. This
analysis is based on the assumption that larva within each gall come
from the same clutch and therefore should have similar chamber diameters
regardless of whether they are parasitized. In general, we found that
our estimates of directional selection on chamber diameter were
positively biased (Appendix). In other words, our analyses were
overestimating the magnitude of selection acting on gall diameter.
Therefore, we adjusted our estimates of directional selection on chamber
diameter (\(\beta_{diam}\)) by subtracting the biased selection
differentials. Note that selection gradients and selection differentials
for chamber diameter were virtually the same (Appendix).

\subsubsection{Quantifying Selective
Constraints}\label{quantifying-selective-constraints}

The strength and pattern of selective constraints can be measured as the
slope and curvature of the fitness landscape (Arnold 1992).

We can translate selection surfaces of individuals to the fitness
landscape of a population

To characterize the net effects of food-web complexity on the slope and
curvature of \emph{Iteomyia}'s fitness landscape, we took advantage of
existing theory that links selection surfaces of individuals to the
fitness landscape of the population (Phillips \& Arnold 1998, Arnold
2003). Specifically, the slope of the fitness landscape corresponds to
the column vector of directional selection gradients:

Note that we ommitted the upper triangle of the matrix for clarity since
it is simply the reflection of the lower triangle. Assuming that there
is additive genetic variance and covariance between these traits under
selection, then the slope and curvature of the fitness landscape give
insight to how the population's mean trait value will change in the next
generation as well as how additive genetic variance and covariance
changes within a generation.

While making quantitative predictions about trait evolution requires
knowledge of the additive genetic variance and covariance of these
traits, the slope and curvature of the fitness landscape still give
qualitative insight to the evolutionary trajectory of a population.

If we assume that there is additive genetic variance and covariance
between these traits, then the matrix describing the curvature of the
fitness landscape gives qualitative insight to the selective constraints
acting on the population. For example, the diagonal of the curvature
matrix dictates (qualitatively) whether the additive genetic variance in
each trait will increase (\(+\)), decrease (\(-\)), or stay the same
(\(0\)). Similarly, the off-diagonal of the curvature matrix dictates
whether selection favors trait integration (positive covariance), a
tradeoff (negative covariance), or no change in genetic covariance. In
other words, we can get qualitative insight to how food-web complexity
influences constraints on the fitness landscape by counting the number
of negative sign values along the diagnoal (which imply a decrease in
additive genetic variance) and the number of positive or negative signs
along the off diagonal (which imply changes in additive genetic
covariance that lead to either trait integration or tradeoffs).

All analyses and visualizations were conducted in R (R Core Team
(2018)).

I need to go back to estimate a common alpha coefficient if the
treatments do not differ from each other.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# In terms of the gammas, there was only evidence that food-web treatment altered nonlinear selection on preference}
\KeywordTok{summary}\NormalTok{(foodweb_glmer)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## gall_survival ~ Foodweb * (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +  
##     Foodweb * (I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +  
##     (1 | Genotype/Plant_Position/Gall_Number)
##    Data: gall_selection.df
## Control: glmerControl(optimizer = "bobyqa")
## 
##      AIC      BIC   logLik deviance df.resid 
##   1399.5   1518.1   -676.7   1353.5     1262 
## 
## Scaled residuals: 
##      Min       1Q   Median       3Q      Max 
## -2.43637 -0.39448  0.08166  0.40662  2.61308 
## 
## Random effects:
##  Groups                                Name        Variance Std.Dev.
##  Gall_Number:(Plant_Position:Genotype) (Intercept) 4.2727   2.0671  
##  Plant_Position:Genotype               (Intercept) 0.6336   0.7960  
##  Genotype                              (Intercept) 0.2006   0.4479  
## Number of obs: 1285, groups:  
## Gall_Number:(Plant_Position:Genotype), 613; Plant_Position:Genotype, 111; Genotype, 8
## 
## Fixed effects:
##                                           Estimate Std. Error z value
## (Intercept)                               -0.69685    0.37782  -1.844
## FoodwebSimple                              1.75956    0.55810   3.153
## sc.Diam                                    1.65436    0.23584   7.015
## sc.log.Clutch                              0.06403    0.23937   0.267
## sc.log1p.Pref                             -0.54297    0.34148  -1.590
## I(sc.Diam^2)                               0.21368    0.14705   1.453
## I(sc.log.Clutch^2)                        -0.07400    0.17650  -0.419
## I(sc.log1p.Pref^2)                         0.70082    0.31013   2.260
## sc.Diam:sc.log.Clutch                     -0.15314    0.19274  -0.795
## sc.Diam:sc.log1p.Pref                     -0.53040    0.27222  -1.948
## sc.log.Clutch:sc.log1p.Pref                0.16936    0.27787   0.609
## FoodwebSimple:sc.Diam                     -0.11621    0.31148  -0.373
## FoodwebSimple:sc.log.Clutch               -0.88569    0.36150  -2.450
## FoodwebSimple:sc.log1p.Pref               -0.60782    0.47939  -1.268
## FoodwebSimple:I(sc.Diam^2)                 0.05600    0.22934   0.244
## FoodwebSimple:I(sc.log.Clutch^2)          -0.21967    0.25755  -0.853
## FoodwebSimple:I(sc.log1p.Pref^2)          -0.88444    0.39493  -2.239
## FoodwebSimple:sc.Diam:sc.log.Clutch       -0.24383    0.28475  -0.856
## FoodwebSimple:sc.Diam:sc.log1p.Pref        0.38979    0.34340   1.135
## FoodwebSimple:sc.log.Clutch:sc.log1p.Pref -0.10381    0.33455  -0.310
##                                           Pr(>|z|)    
## (Intercept)                                0.06513 .  
## FoodwebSimple                              0.00162 ** 
## sc.Diam                                    2.3e-12 ***
## sc.log.Clutch                              0.78909    
## sc.log1p.Pref                              0.11183    
## I(sc.Diam^2)                               0.14618    
## I(sc.log.Clutch^2)                         0.67503    
## I(sc.log1p.Pref^2)                         0.02384 *  
## sc.Diam:sc.log.Clutch                      0.42688    
## sc.Diam:sc.log1p.Pref                      0.05136 .  
## sc.log.Clutch:sc.log1p.Pref                0.54220    
## FoodwebSimple:sc.Diam                      0.70909    
## FoodwebSimple:sc.log.Clutch                0.01429 *  
## FoodwebSimple:sc.log1p.Pref                0.20484    
## FoodwebSimple:I(sc.Diam^2)                 0.80710    
## FoodwebSimple:I(sc.log.Clutch^2)           0.39370    
## FoodwebSimple:I(sc.log1p.Pref^2)           0.02513 *  
## FoodwebSimple:sc.Diam:sc.log.Clutch        0.39184    
## FoodwebSimple:sc.Diam:sc.log1p.Pref        0.25634    
## FoodwebSimple:sc.log.Clutch:sc.log1p.Pref  0.75634    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{verbatim}
## 
## Correlation matrix not shown by default, as p = 20 > 12.
## Use print(x, correlation=TRUE)  or
##     vcov(x)        if you need it
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Therefore, we refit a model that only included this effect of food-web treatment on the gamma coefficients}
\NormalTok{foodweb_glmer_revised <-}\StringTok{ }\KeywordTok{update}\NormalTok{(foodweb_glmer, .}\OperatorTok{~}\NormalTok{. }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\KeywordTok{I}\NormalTok{(sc.Diam}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\KeywordTok{I}\NormalTok{(sc.log.Clutch}\OperatorTok{^}\DecValTok{2}\NormalTok{) }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.Diam}\OperatorTok{:}\NormalTok{sc.log.Clutch }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.Diam}\OperatorTok{:}\NormalTok{sc.log1p.Pref }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.log.Clutch}\OperatorTok{:}\NormalTok{sc.log1p.Pref)}

\CommentTok{# Note that we still observe that food-web treatment alters nonlinear selection on female preference}
\CommentTok{# There is also now marginal evidence for nonlinear selection on diameter as well as correlational selection between diameter and clutch (Diam:Clutch) and between diameter and preference (Diam:Pref).}
\KeywordTok{summary}\NormalTok{(foodweb_glmer_revised)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.log1p.Pref +  
##     I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +  
##     (1 | Genotype/Plant_Position/Gall_Number) + sc.Diam:sc.log.Clutch +  
##     sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref + Foodweb:sc.Diam +  
##     Foodweb:sc.log.Clutch + Foodweb:sc.log1p.Pref + Foodweb:I(sc.log1p.Pref^2)
##    Data: gall_selection.df
## Control: glmerControl(optimizer = "bobyqa")
## 
##      AIC      BIC   logLik deviance df.resid 
##   1392.6   1485.5   -678.3   1356.6     1267 
## 
## Scaled residuals: 
##      Min       1Q   Median       3Q      Max 
## -2.56786 -0.39417  0.08248  0.40532  2.54775 
## 
## Random effects:
##  Groups                                Name        Variance Std.Dev.
##  Gall_Number:(Plant_Position:Genotype) (Intercept) 4.2062   2.0509  
##  Plant_Position:Genotype               (Intercept) 0.6052   0.7780  
##  Genotype                              (Intercept) 0.2062   0.4541  
## Number of obs: 1285, groups:  
## Gall_Number:(Plant_Position:Genotype), 613; Plant_Position:Genotype, 111; Genotype, 8
## 
## Fixed effects:
##                                   Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                      -0.588297   0.355456  -1.655   0.0979 .  
## FoodwebSimple                     1.577451   0.479441   3.290   0.0010 ** 
## sc.Diam                           1.585657   0.217494   7.291 3.09e-13 ***
## sc.log.Clutch                     0.009263   0.208112   0.045   0.9645    
## sc.log1p.Pref                    -0.524039   0.331334  -1.582   0.1137    
## I(sc.Diam^2)                      0.211654   0.110801   1.910   0.0561 .  
## I(sc.log.Clutch^2)               -0.167620   0.127219  -1.318   0.1876    
## I(sc.log1p.Pref^2)                0.646133   0.296141   2.182   0.0291 *  
## sc.Diam:sc.log.Clutch            -0.257952   0.140800  -1.832   0.0669 .  
## sc.Diam:sc.log1p.Pref            -0.273306   0.160883  -1.699   0.0894 .  
## sc.log.Clutch:sc.log1p.Pref       0.125058   0.151556   0.825   0.4093    
## FoodwebSimple:sc.Diam            -0.050583   0.291165  -0.174   0.8621    
## FoodwebSimple:sc.log.Clutch      -0.700008   0.295920  -2.366   0.0180 *  
## FoodwebSimple:sc.log1p.Pref      -0.611523   0.461851  -1.324   0.1855    
## FoodwebSimple:I(sc.log1p.Pref^2) -0.828557   0.382344  -2.167   0.0302 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{verbatim}
## 
## Correlation matrix not shown by default, as p = 15 > 12.
## Use print(x, correlation=TRUE)  or
##     vcov(x)        if you need it
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{summary}\NormalTok{(betas_glmer)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## gall_survival ~ Foodweb * (sc.Diam + sc.log.Clutch + sc.log1p.Pref) +  
##     (1 | Genotype/Plant_Position/Gall_Number)
##    Data: gall_selection.df
## Control: glmerControl(optimizer = "bobyqa")
## 
##      AIC      BIC   logLik deviance df.resid 
##   1394.0   1450.7   -686.0   1372.0     1274 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -2.2378 -0.3985  0.1132  0.3910  2.7651 
## 
## Random effects:
##  Groups                                Name        Variance Std.Dev.
##  Gall_Number:(Plant_Position:Genotype) (Intercept) 4.4523   2.1100  
##  Plant_Position:Genotype               (Intercept) 0.6350   0.7969  
##  Genotype                              (Intercept) 0.2966   0.5446  
## Number of obs: 1285, groups:  
## Gall_Number:(Plant_Position:Genotype), 613; Plant_Position:Genotype, 111; Genotype, 8
## 
## Fixed effects:
##                             Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                 -0.26211    0.30437  -0.861  0.38915    
## FoodwebSimple                1.07015    0.35648   3.002  0.00268 ** 
## sc.Diam                      1.53362    0.20976   7.311 2.64e-13 ***
## sc.log.Clutch                0.20562    0.19224   1.070  0.28480    
## sc.log1p.Pref               -0.67099    0.33534  -2.001  0.04540 *  
## FoodwebSimple:sc.Diam        0.02185    0.28368   0.077  0.93861    
## FoodwebSimple:sc.log.Clutch -0.70280    0.28710  -2.448  0.01437 *  
## FoodwebSimple:sc.log1p.Pref -0.15620    0.37677  -0.415  0.67845    
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) FdwbSm sc.Dim sc.l.C sc.1.P FdS:.D FS:..C
## FoodwebSmpl -0.505                                          
## sc.Diam     -0.002  0.100                                   
## sc.lg.Cltch  0.138 -0.088 -0.140                            
## sc.lg1p.Prf -0.215  0.181 -0.117 -0.081                     
## FdwbSmpl:.D -0.035  0.121 -0.525  0.167  0.061              
## FdwbSmp:..C -0.080  0.195  0.051 -0.682  0.069 -0.206       
## FdwbSm:.1.P  0.191 -0.119  0.042  0.020 -0.772 -0.092  0.025
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{betas_glmer_revised <-}\StringTok{ }\KeywordTok{update}\NormalTok{(betas_glmer, .}\OperatorTok{~}\NormalTok{. }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.Diam }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.log1p.Pref)}
\KeywordTok{summary}\NormalTok{(betas_glmer_revised)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.log1p.Pref +  
##     (1 | Genotype/Plant_Position/Gall_Number) + Foodweb:sc.log.Clutch
##    Data: gall_selection.df
## Control: glmerControl(optimizer = "bobyqa")
## 
##      AIC      BIC   logLik deviance df.resid 
##   1390.1   1436.6   -686.1   1372.1     1276 
## 
## Scaled residuals: 
##     Min      1Q  Median      3Q     Max 
## -2.2674 -0.3980  0.1138  0.3907  2.7868 
## 
## Random effects:
##  Groups                                Name        Variance Std.Dev.
##  Gall_Number:(Plant_Position:Genotype) (Intercept) 4.4391   2.1069  
##  Plant_Position:Genotype               (Intercept) 0.6320   0.7950  
##  Genotype                              (Intercept) 0.2961   0.5441  
## Number of obs: 1285, groups:  
## Gall_Number:(Plant_Position:Genotype), 613; Plant_Position:Genotype, 111; Genotype, 8
## 
## Fixed effects:
##                             Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                  -0.2381     0.2984  -0.798 0.425022    
## FoodwebSimple                 1.0519     0.3512   2.995 0.002744 ** 
## sc.Diam                       1.5430     0.1782   8.657  < 2e-16 ***
## sc.log.Clutch                 0.2062     0.1892   1.090 0.275618    
## sc.log1p.Pref                -0.7793     0.2120  -3.676 0.000237 ***
## FoodwebSimple:sc.log.Clutch  -0.6983     0.2805  -2.490 0.012792 *  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 
## Correlation of Fixed Effects:
##             (Intr) FdwbSm sc.Dim sc.l.C sc.1.P
## FoodwebSmpl -0.496                            
## sc.Diam     -0.023  0.193                     
## sc.lg.Cltch  0.142 -0.107 -0.061              
## sc.lg1p.Prf -0.109  0.143 -0.169 -0.100       
## FdwbSmp:..C -0.093  0.228 -0.070 -0.671  0.138
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{foodweb_glmer_revised_again <-}\StringTok{ }\KeywordTok{update}\NormalTok{(foodweb_glmer_revised, .}\OperatorTok{~}\NormalTok{. }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.Diam }\OperatorTok{-}\NormalTok{Foodweb}\OperatorTok{:}\NormalTok{sc.log1p.Pref)}
\KeywordTok{summary}\NormalTok{(foodweb_glmer_revised_again)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Generalized linear mixed model fit by maximum likelihood (Laplace
##   Approximation) [glmerMod]
##  Family: binomial  ( logit )
## Formula: 
## gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.log1p.Pref +  
##     I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +  
##     (1 | Genotype/Plant_Position/Gall_Number) + sc.Diam:sc.log.Clutch +  
##     sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref + Foodweb:sc.log.Clutch +  
##     Foodweb:I(sc.log1p.Pref^2)
##    Data: gall_selection.df
## Control: glmerControl(optimizer = "bobyqa")
## 
##      AIC      BIC   logLik deviance df.resid 
##   1390.5   1473.0   -679.2   1358.5     1269 
## 
## Scaled residuals: 
##      Min       1Q   Median       3Q      Max 
## -2.54938 -0.39242  0.08266  0.39760  2.57612 
## 
## Random effects:
##  Groups                                Name        Variance Std.Dev.
##  Gall_Number:(Plant_Position:Genotype) (Intercept) 4.2426   2.0598  
##  Plant_Position:Genotype               (Intercept) 0.6433   0.8021  
##  Genotype                              (Intercept) 0.2027   0.4502  
## Number of obs: 1285, groups:  
## Gall_Number:(Plant_Position:Genotype), 613; Plant_Position:Genotype, 111; Genotype, 8
## 
## Fixed effects:
##                                  Estimate Std. Error z value Pr(>|z|)    
## (Intercept)                      -0.50735    0.34880  -1.455  0.14579    
## FoodwebSimple                     1.31940    0.43004   3.068  0.00215 ** 
## sc.Diam                           1.57197    0.18409   8.539  < 2e-16 ***
## sc.log.Clutch                     0.02541    0.20704   0.123  0.90232    
## sc.log1p.Pref                    -0.81032    0.25766  -3.145  0.00166 ** 
## I(sc.Diam^2)                      0.21338    0.11085   1.925  0.05424 .  
## I(sc.log.Clutch^2)               -0.16136    0.12748  -1.266  0.20561    
## I(sc.log1p.Pref^2)                0.60114    0.29750   2.021  0.04332 *  
## sc.Diam:sc.log.Clutch            -0.24864    0.14046  -1.770  0.07669 .  
## sc.Diam:sc.log1p.Pref            -0.25261    0.15951  -1.584  0.11326    
## sc.log.Clutch:sc.log1p.Pref       0.12585    0.15240   0.826  0.40892    
## FoodwebSimple:sc.log.Clutch      -0.72888    0.29353  -2.483  0.01302 *  
## FoodwebSimple:I(sc.log1p.Pref^2) -0.59758    0.34290  -1.743  0.08138 .  
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\begin{verbatim}
## 
## Correlation matrix not shown by default, as p = 13 > 12.
## Use print(x, correlation=TRUE)  or
##     vcov(x)        if you need it
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{## METHOD OF JANZEN AND STERN 1998 ----}

\CommentTok{# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")}
\NormalTok{complex_predict <-}\StringTok{ }\KeywordTok{predict}\NormalTok{(foodweb_glmer, }\DataTypeTok{newdata=}\KeywordTok{filter}\NormalTok{(gall_selection.df, Foodweb}\OperatorTok{==}\StringTok{"Complex"}\NormalTok{), }\DataTypeTok{type=}\StringTok{"response"}\NormalTok{)}
\NormalTok{complex_mean_brackets <-}\StringTok{ }\KeywordTok{mean}\NormalTok{(complex_predict }\OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{complex_predict))}
\NormalTok{complex_mean_fitness <-}\StringTok{ }\KeywordTok{mean}\NormalTok{(complex_predict)}

\NormalTok{simple_predict <-}\StringTok{ }\KeywordTok{predict}\NormalTok{(foodweb_glmer, }\DataTypeTok{newdata=}\KeywordTok{filter}\NormalTok{(gall_selection.df, Foodweb}\OperatorTok{==}\StringTok{"Simple"}\NormalTok{), }\DataTypeTok{type=}\StringTok{"response"}\NormalTok{)}
\NormalTok{simple_mean_brackets <-}\StringTok{ }\KeywordTok{mean}\NormalTok{(simple_predict }\OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{simple_predict))}
\NormalTok{simple_mean_fitness <-}\StringTok{ }\KeywordTok{mean}\NormalTok{(simple_predict)}

\CommentTok{# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter }
\NormalTok{alt_predict <-}\StringTok{ }\KeywordTok{predict}\NormalTok{(betas_glmer, }\DataTypeTok{newdata=}\KeywordTok{filter}\NormalTok{(gall_selection.df, Foodweb}\OperatorTok{==}\StringTok{"Complex"}\NormalTok{), }\DataTypeTok{type=}\StringTok{"response"}\NormalTok{)}
\NormalTok{alt_mean_brackets <-}\StringTok{ }\KeywordTok{mean}\NormalTok{(alt_predict }\OperatorTok{*}\StringTok{ }\NormalTok{(}\DecValTok{1} \OperatorTok{-}\StringTok{ }\NormalTok{alt_predict))}
\NormalTok{alt_mean_fitness <-}\StringTok{ }\KeywordTok{mean}\NormalTok{(alt_predict)}
\NormalTok{test_mean_brackets <-}\StringTok{ }\NormalTok{complex_mean_brackets}
\NormalTok{test_mean_fitness <-}\StringTok{ }\NormalTok{complex_mean_fitness}
\NormalTok{test_mean_brackets }\OperatorTok{-}\StringTok{ }\NormalTok{alt_mean_brackets }\CommentTok{# virtually the same}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 8.652519e-05
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{test_mean_fitness }\OperatorTok{-}\StringTok{ }\NormalTok{alt_mean_fitness }\CommentTok{# virtually the same}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## [1] 0.0001767182
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Tidy data for beta terms}
\NormalTok{foodweb_tidy_betas <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(betas_glmer, }\DataTypeTok{conf.int=}\NormalTok{T) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(term }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"(Intercept)"}\NormalTok{,}\StringTok{"FoodwebSimple"}\NormalTok{,}\StringTok{"sc.Diam"}\NormalTok{,}\StringTok{"sc.log.Clutch"}\NormalTok{,}\StringTok{"sc.log1p.Pref"}\NormalTok{,}
                     \StringTok{"FoodwebSimple:sc.Diam"}\NormalTok{,}\StringTok{"FoodwebSimple:sc.log.Clutch"}\NormalTok{,}\StringTok{"FoodwebSimple:sc.log1p.Pref"}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Foodweb =} \KeywordTok{c}\NormalTok{(}\StringTok{"Complex"}\NormalTok{,}\StringTok{"Simple"}\NormalTok{,}\KeywordTok{rep}\NormalTok{(}\StringTok{"Complex"}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\StringTok{"Simple"}\NormalTok{,}\DecValTok{3}\NormalTok{)),}
         \DataTypeTok{Selection_form =} \KeywordTok{c}\NormalTok{(}\OtherTok{NA}\NormalTok{,}\OtherTok{NA}\NormalTok{,}\KeywordTok{rep}\NormalTok{(}\StringTok{"Directional"}\NormalTok{,}\DecValTok{6}\NormalTok{)),}
         \DataTypeTok{Multiplier =} \KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{8}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in bind_rows_(x, .id): binding factor and character vector,
## coercing into character vector
\end{verbatim}

\begin{verbatim}
## Warning in bind_rows_(x, .id): binding character and factor vector,
## coercing into character vector
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Tidy data for gamma terms. Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al. 2008)}
\NormalTok{foodweb_tidy_gammas <-}\StringTok{ }\KeywordTok{tidy}\NormalTok{(foodweb_glmer, }\DataTypeTok{conf.int=}\NormalTok{T) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(term }\OperatorTok{%in%}\StringTok{ }\KeywordTok{c}\NormalTok{(}\StringTok{"I(sc.Diam^2)"}\NormalTok{,}\StringTok{"I(sc.log.Clutch^2)"}\NormalTok{,}\StringTok{"I(sc.log1p.Pref^2)"}\NormalTok{,}
                     \StringTok{"sc.Diam:sc.log.Clutch"}\NormalTok{,}\StringTok{"sc.Diam:sc.log1p.Pref"}\NormalTok{,}\StringTok{"sc.log.Clutch:sc.log1p.Pref"}\NormalTok{,}
                     \StringTok{"FoodwebSimple:I(sc.Diam^2)"}\NormalTok{,}\StringTok{"FoodwebSimple:I(sc.log.Clutch^2)"}\NormalTok{,}\StringTok{"FoodwebSimple:I(sc.log1p.Pref^2)"}\NormalTok{,}
                     \StringTok{"FoodwebSimple:sc.Diam:sc.log.Clutch"}\NormalTok{,}\StringTok{"FoodwebSimple:sc.Diam:sc.log1p.Pref"}\NormalTok{,}\StringTok{"FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Foodweb =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"Complex"}\NormalTok{,}\DecValTok{6}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\StringTok{"Simple"}\NormalTok{,}\DecValTok{6}\NormalTok{)),}
         \DataTypeTok{Selection_form =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\StringTok{"Nonlinear"}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\StringTok{"Correlational"}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\StringTok{"Nonlinear"}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\StringTok{"Correlational"}\NormalTok{,}\DecValTok{3}\NormalTok{)),}
         \DataTypeTok{Multiplier =} \KeywordTok{c}\NormalTok{(}\KeywordTok{rep}\NormalTok{(}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\DecValTok{2}\NormalTok{,}\DecValTok{3}\NormalTok{),}\KeywordTok{rep}\NormalTok{(}\DecValTok{1}\NormalTok{,}\DecValTok{3}\NormalTok{)))}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## Warning in bind_rows_(x, .id): binding factor and character vector,
## coercing into character vector

## Warning in bind_rows_(x, .id): binding character and factor vector,
## coercing into character vector
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# Combine and tidy the regression (alpha) coefficients}
\NormalTok{get_alphas <-}\StringTok{ }\KeywordTok{bind_rows}\NormalTok{(foodweb_tidy_betas, foodweb_tidy_gammas) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{alpha =}\NormalTok{ estimate, }\DataTypeTok{alpha_2.5 =}\NormalTok{ conf.low, }\DataTypeTok{alpha_97.5 =}\NormalTok{ conf.high, }\DataTypeTok{P =}\NormalTok{ p.value) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{select}\NormalTok{(term, Foodweb, alpha, alpha_}\FloatTok{2.5}\NormalTok{, alpha_}\FloatTok{97.5}\NormalTok{, P, Selection_form, Multiplier)}

\NormalTok{complex_alphas <-}\StringTok{ }\KeywordTok{filter}\NormalTok{(get_alphas, Foodweb }\OperatorTok{==}\StringTok{ "Complex"}\NormalTok{); complex_alphas}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 8
##    term  Foodweb   alpha alpha_2.5 alpha_97.5        P Selection_form
##    <chr> <chr>     <dbl>     <dbl>      <dbl>    <dbl> <chr>         
##  1 (Int~ Complex -0.262    -0.859     0.334   3.89e- 1 <NA>          
##  2 sc.D~ Complex  1.53      1.12      1.94    2.64e-13 Directional   
##  3 sc.l~ Complex  0.206    -0.171     0.582   2.85e- 1 Directional   
##  4 sc.l~ Complex -0.671    -1.33     -0.0137  4.54e- 2 Directional   
##  5 I(sc~ Complex  0.214    -0.0745    0.502   1.46e- 1 Nonlinear     
##  6 I(sc~ Complex -0.0740   -0.420     0.272   6.75e- 1 Nonlinear     
##  7 I(sc~ Complex  0.701     0.0930    1.31    2.38e- 2 Nonlinear     
##  8 sc.D~ Complex -0.153    -0.531     0.225   4.27e- 1 Correlational 
##  9 sc.D~ Complex -0.530    -1.06      0.00314 5.14e- 2 Correlational 
## 10 sc.l~ Complex  0.169    -0.375     0.714   5.42e- 1 Correlational 
## # ... with 1 more variable: Multiplier <dbl>
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{simple_alphas <-}\StringTok{ }\KeywordTok{filter}\NormalTok{(get_alphas, Foodweb }\OperatorTok{==}\StringTok{ "Simple"}\NormalTok{); simple_alphas}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 10 x 8
##    term  Foodweb   alpha alpha_2.5 alpha_97.5       P Selection_form
##    <chr> <chr>     <dbl>     <dbl>      <dbl>   <dbl> <chr>         
##  1 Food~ Simple   1.07       0.371      1.77  0.00268 <NA>          
##  2 Food~ Simple   0.0218    -0.534      0.578 0.939   Directional   
##  3 Food~ Simple  -0.703     -1.27      -0.140 0.0144  Directional   
##  4 Food~ Simple  -0.156     -0.895      0.582 0.678   Directional   
##  5 Food~ Simple   0.0560    -0.393      0.505 0.807   Nonlinear     
##  6 Food~ Simple  -0.220     -0.724      0.285 0.394   Nonlinear     
##  7 Food~ Simple  -0.884     -1.66      -0.110 0.0251  Nonlinear     
##  8 Food~ Simple  -0.244     -0.802      0.314 0.392   Correlational 
##  9 Food~ Simple   0.390     -0.283      1.06  0.256   Correlational 
## 10 Food~ Simple  -0.104     -0.760      0.552 0.756   Correlational 
## # ... with 1 more variable: Multiplier <dbl>
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{coefs_gradients <-}\StringTok{ }\KeywordTok{data.frame}\NormalTok{(}\DataTypeTok{Variable =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{term, }
           \DataTypeTok{a_complex =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{alpha,}
           \DataTypeTok{a_complex_2.5 =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{alpha_}\FloatTok{2.5}\NormalTok{,}
           \DataTypeTok{a_complex_97.5 =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{alpha_}\FloatTok{97.5}\NormalTok{,}
           \DataTypeTok{a_simple =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{alpha }\OperatorTok{+}\StringTok{ }\NormalTok{simple_alphas}\OperatorTok{$}\NormalTok{alpha,        }\CommentTok{# the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web}
           \DataTypeTok{a_simple_2.5 =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{alpha }\OperatorTok{+}\StringTok{ }\NormalTok{simple_alphas}\OperatorTok{$}\NormalTok{alpha_}\FloatTok{2.5}\NormalTok{, }\CommentTok{# same addition process for confidence intervals}
           \DataTypeTok{a_simple_97.5 =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{alpha }\OperatorTok{+}\StringTok{ }\NormalTok{simple_alphas}\OperatorTok{$}\NormalTok{alpha_}\FloatTok{97.5}\NormalTok{,}
           \DataTypeTok{Selection_form =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{Selection_form,                }\CommentTok{# doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier}
           \DataTypeTok{Multiplier =}\NormalTok{ complex_alphas}\OperatorTok{$}\NormalTok{Multiplier) }\OperatorTok{%>%}\StringTok{                     }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{b_complex =}\NormalTok{ complex_mean_brackets }\OperatorTok{*}\StringTok{ }\NormalTok{a_complex }\OperatorTok{/}\StringTok{ }\NormalTok{complex_mean_fitness }\OperatorTok{*}\StringTok{ }\NormalTok{Multiplier,}
         \DataTypeTok{b_complex_2.5 =}\NormalTok{ complex_mean_brackets }\OperatorTok{*}\StringTok{ }\NormalTok{a_complex_}\FloatTok{2.5} \OperatorTok{/}\StringTok{ }\NormalTok{complex_mean_fitness }\OperatorTok{*}\StringTok{ }\NormalTok{Multiplier,}
         \DataTypeTok{b_complex_97.5 =}\NormalTok{ complex_mean_brackets }\OperatorTok{*}\StringTok{ }\NormalTok{a_complex_}\FloatTok{97.5} \OperatorTok{/}\StringTok{ }\NormalTok{complex_mean_fitness }\OperatorTok{*}\StringTok{ }\NormalTok{Multiplier,}
         \DataTypeTok{b_simple =}\NormalTok{ simple_mean_brackets }\OperatorTok{*}\StringTok{ }\NormalTok{a_simple }\OperatorTok{/}\StringTok{ }\NormalTok{simple_mean_fitness }\OperatorTok{*}\StringTok{ }\NormalTok{Multiplier,}
         \DataTypeTok{b_simple_2.5 =}\NormalTok{ simple_mean_brackets }\OperatorTok{*}\StringTok{ }\NormalTok{a_simple_}\FloatTok{2.5} \OperatorTok{/}\StringTok{ }\NormalTok{simple_mean_fitness }\OperatorTok{*}\StringTok{ }\NormalTok{Multiplier,}
         \DataTypeTok{b_simple_97.5 =}\NormalTok{ simple_mean_brackets }\OperatorTok{*}\StringTok{ }\NormalTok{a_simple_}\FloatTok{97.5} \OperatorTok{/}\StringTok{ }\NormalTok{simple_mean_fitness }\OperatorTok{*}\StringTok{ }\NormalTok{Multiplier) }

\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{mutate}\NormalTok{(}\KeywordTok{select}\NormalTok{(coefs_gradients, Variable, }\DataTypeTok{a=}\NormalTok{a_complex, }\DataTypeTok{a_2.5=}\NormalTok{a_complex_}\FloatTok{2.5}\NormalTok{, }\DataTypeTok{a_97.5=}\NormalTok{a_complex_}\FloatTok{97.5}\NormalTok{, Selection_form), }\DataTypeTok{Foodweb =} \StringTok{"Complex"}\NormalTok{),}
          \KeywordTok{mutate}\NormalTok{(}\KeywordTok{select}\NormalTok{(coefs_gradients, Variable, }\DataTypeTok{a=}\NormalTok{a_simple, }\DataTypeTok{a_2.5=}\NormalTok{a_simple_}\FloatTok{2.5}\NormalTok{, }\DataTypeTok{a_97.5=}\NormalTok{a_simple_}\FloatTok{97.5}\NormalTok{, Selection_form), }\DataTypeTok{Foodweb =} \StringTok{"Simple"}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(Variable }\OperatorTok{!=}\StringTok{ "(Intercept)"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(., }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ Variable, }\DataTypeTok{fill=}\NormalTok{Foodweb, }\DataTypeTok{color=}\NormalTok{Foodweb)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{y=}\NormalTok{a), }\DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width=}\FloatTok{0.5}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_errorbar}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymax =}\NormalTok{ a_}\FloatTok{97.5}\NormalTok{, }\DataTypeTok{ymin =}\NormalTok{ a_}\FloatTok{2.5}\NormalTok{), }\DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width=}\FloatTok{0.5}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_flip}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_hline}\NormalTok{(}\DataTypeTok{yintercept=}\DecValTok{0}\NormalTok{, }\DataTypeTok{linetype=}\StringTok{"dotted"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\NormalTok{Selection_form, }\DataTypeTok{nrow=}\DecValTok{2}\NormalTok{, }\DataTypeTok{scales =} \StringTok{"free_y"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Regression coefficient"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{ms_complexity_selection_files/figure-latex/Get Selection Gradients for GLMER-1.pdf}

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{## Modify to be directional, nonlinear, then correlational with legend in 4th area.}
\NormalTok{## Modify so that axes have gamma and beta with the trait as a subscript}
\KeywordTok{bind_rows}\NormalTok{(}\KeywordTok{mutate}\NormalTok{(}\KeywordTok{select}\NormalTok{(coefs_gradients, Variable, }\DataTypeTok{b=}\NormalTok{b_complex, }\DataTypeTok{b_2.5=}\NormalTok{b_complex_}\FloatTok{2.5}\NormalTok{, }\DataTypeTok{b_97.5=}\NormalTok{b_complex_}\FloatTok{97.5}\NormalTok{, Selection_form), }\DataTypeTok{Foodweb =} \StringTok{"Complex"}\NormalTok{),}
          \KeywordTok{mutate}\NormalTok{(}\KeywordTok{select}\NormalTok{(coefs_gradients, Variable, }\DataTypeTok{b=}\NormalTok{b_simple, }\DataTypeTok{b_2.5=}\NormalTok{b_simple_}\FloatTok{2.5}\NormalTok{, }\DataTypeTok{b_97.5=}\NormalTok{b_simple_}\FloatTok{97.5}\NormalTok{, Selection_form), }\DataTypeTok{Foodweb =} \StringTok{"Simple"}\NormalTok{)) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{filter}\NormalTok{(Variable }\OperatorTok{!=}\StringTok{ "(Intercept)"}\NormalTok{) }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{ggplot}\NormalTok{(., }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ Variable, }\DataTypeTok{fill=}\NormalTok{Foodweb, }\DataTypeTok{color=}\NormalTok{Foodweb)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_point}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{y=}\NormalTok{b), }\DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width=}\FloatTok{0.5}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_errorbar}\NormalTok{(}\KeywordTok{aes}\NormalTok{(}\DataTypeTok{ymax =}\NormalTok{ b_}\FloatTok{97.5}\NormalTok{, }\DataTypeTok{ymin =}\NormalTok{ b_}\FloatTok{2.5}\NormalTok{), }\DataTypeTok{position =} \KeywordTok{position_dodge}\NormalTok{(}\DataTypeTok{width=}\FloatTok{0.5}\NormalTok{)) }\OperatorTok{+}
\StringTok{  }\KeywordTok{coord_flip}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_hline}\NormalTok{(}\DataTypeTok{yintercept=}\DecValTok{0}\NormalTok{, }\DataTypeTok{linetype=}\StringTok{"dotted"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{facet_wrap}\NormalTok{(}\OperatorTok{~}\NormalTok{Selection_form, }\DataTypeTok{nrow=}\DecValTok{2}\NormalTok{, }\DataTypeTok{scales =} \StringTok{"free_y"}\NormalTok{) }\OperatorTok{+}
\StringTok{  }\KeywordTok{ylab}\NormalTok{(}\StringTok{"Selection gradient"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\includegraphics{ms_complexity_selection_files/figure-latex/Get Selection Gradients for GLMER-2.pdf}

What's the rationale for this test? First, we focus on galls where there
is evidence of both survival and parasitism within the gall. The idea is
that galls from the same clutch should be similar in size, therefore,
any selection on diameter would be apparent. If we assume that this is
all due to the effect of parasitism on larval development, truncating
gall diameter, then we can consider this new selection gradient to be
the result of confounding factors. Note that this is likely
overestimates the effect of the confounding factor, since we are
assuming that any heterogeneity in gall size (for this dataset) is due
to a confounding effect of parasitism on gall diameter. Then, we can
just subtract this value from the observed covariance between gall
diameter and larval survival to adjust for the confounding effects of
parasitism. This analysis should be relegated to the supplement.

Would we expect any confounding effects on nonlinear selection?

Appears to be selection for Platygaster to attack larva at high
densities in more complex food webs (and a decrease in the variance).
This may be a result of the poorer searching ability of parasitoids at
very high gall densities, potentially due to saturation. This suggests
that the fitness landscape may be dynamic because these selective
effects (assuming there is heritable variation in the egg parasitoid)
will change the following year. This could be an important discussion
point to take into account for future work. This is different from
simply altering the strength of selection, which will occur as species
move along the fitness landscape, but this result suggests that the
nature of the fitness landscape may actually be changing. For example,
larval parasitoids could be driving selection on Platygaster to be very
efficient at foraging, which will dampen once this pressure is removed,
and then could also dampen the selection acting on the galling
herbivore.

\subsection{Table for Alpha regression
coefficients}\label{table-for-alpha-regression-coefficients}

\begin{table}[]
\begin{tabular}{lcc}
                                                                           \\ \hline
                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
$Diam$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Clutch$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Pref$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Diam^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Clutch^2$             & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Pref^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Diam:Clutch$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Diam:Pref$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$Clutch:Pref$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]              \\ \hline
\end{tabular}
\end{table}

\subsection{Table for Iteomyia selection
gradients}\label{table-for-iteomyia-selection-gradients}

\begin{table}[]
\begin{tabular}{lcc}
                                                                                  \\ \hline
                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
$\beta_{Diam}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\beta_{Clutch}$                  & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\beta_{Pref}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\gamma_{Diam,Diam}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\gamma_{Clutch,Clutch}$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\gamma_{Pref,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\gamma_{Diam,Clutch}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\gamma_{Diam,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
$\gamma_{Clutch,Pref}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]           \\ \hline
\end{tabular}
\end{table}

\subsection{Table for bias}\label{table-for-bias}

\begin{table}[]
\begin{tabular}{lc}
                                                                  \\ \hline
\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
Complex (All)                 & `r ` [`r `-`r `]  \\
Complex (Larval guild)        & `r ` [`r `-`r `]  \\
Simple (\textit{Platygaster}) & `r ` [`r `-`r `]                  \\ \hline
\end{tabular}
\end{table}

\subsection{Table for Platygaster
selection}\label{table-for-platygaster-selection}

\begin{table}[]
\begin{tabular}{lc}
                                                                  \\ \hline
\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
$s_{Diam}$                      & `r ` [`r `-`r `]  \\
$s_{Clutch}$                    & `r ` [`r `-`r `]  \\
$s_{Pref}$                      & `r ` [`r `-`r `]  \\ 
$s_{Diam,Diam}$                 & `r ` [`r `-`r `]  \\
$s_{Clutch,Clutch}$             & `r ` [`r `-`r `]  \\
$s_{Pref,Pref}$                 & `r ` [`r `-`r `]                \\ \hline
\end{tabular}
\end{table}

Note that equation 3 in Phillips and Arnold 1998 is good justification
for why quadratic selection cofficients should be multiplied by two (but
not correlational ones?)

The G-matrix is essentially a scalar. For my data, since there is no
correlational selection, it doesn't matter if there is genetic
covariance between the traits, as this will not effect the change in
genetic covariances within a generation (because there is no selection).
Also, the G\_matrix does not qualitatively alter the conclusions that
there will be a decrease in additive genetic variance in gall diameter
due to the strong directional selection; however, there will be an
increase in the additive genetic variance in female preference. Since
this is an experiment, we can assume that the G-matrix is the same
between treatments

Remember that the diagonals refer to additive genetic CO-variances.
Thus, positive or negative values for delta\_G give insight to whether
selection will act to integrate traits (positive covariance) or create
trade-offs (negative covariance).

Assuming that there is positive additive genetic variance and
co-variance in these traits (i.e.~all values of G-matrix are positive),
then the curvature of the fitness landscape can give insight to
qualitative changes in the G matrix. This is because the G-matrix acts
as a scalar of changes in the fitness landscape.

Compared to the GLM, the GLMM gives the same inferences about the effect
of food-web treatment. The main difference was that there was stronger
evidence of correlational selection, but no evidence that this
correlational selection varied among food-web treatments. Still, this
stronger evidence for correlational selection should be interpreted with
caution since the GLM does not account for the non-indepedence of these
fitness estimates.

\section{Results}\label{results}

We found that changes in food-web complexity altered the shape of
\emph{Iteomyia}'s fitness landscape ().

For example, there was directional selection for larger gall diameter in
both complex and simple food webs, but the magnitude of the selection
gradient was X-fold higher in the complex food web. The steeper
selection gradient in the complex food web was not a result of stronger
covariance between gall diameter and larval survival, but a result of
average larval survival being X-fold lower in the complex food web.

We observed directional selection for smaller clutch sizes in the simple
food web, but no evidence of selection on this trait in the complex food
web. The absence of selection in the complex food web appeared to be a
result of conflicting selection pressures imposed by the egg parasitoid
\emph{Platygaster} and the guild of larval parasitoids (statistical test
focus on egg vs.~larval parasitoids). Specifically, larval parasitoids
actually impose directional selection for larger clutch sizes (selection
gradient), but the net effect is no selection when both parasitoid
guilds are present.

We found evidence of disruptive selection acting on female preference in
the complex food web, but no evidence of nonlinear selection on this
trait in the simple food web. Similar to clutch size, these differences
in nonlinear selection appeared to be due to different selection
pressures imposed by egg and larval parasitoids.

\textbf{Characterizing the slope and curvature of the fitness landscape}

\textbf{Old}

\section{Discussion}\label{discussion}

Our key finding was that the adaptive landscape was less constrained in
the complex vs.~simple food web. These fewer constraints arise from
conflicting selection pressures imposed by different parasitoid guilds,
resulting in fewer traits under selection in the complex food web. At
the same time, we observed an overall greater intensity of selection in
the complex food web, suggesting that trait evolution can be faster in
complex vs.~simple food webs. Our observation that natural selection was
more constrained and less intense in simple vs.~complex food webs
suggests that the loss of biodiversity could constrain the adaptive
potential of interacting species by reducing genetic and phenotypic
variation in multiple traits.

Current theory suggests that when the number of selective constrains is
less than the number of genetic constraints (i.e.~some genetically
variable traits are selective neutral), there are multiple positions on
the landscape that confer equal fitness (Lande 1981; Lande and Arnold
1985). In this scenario, trait differences between populations may
simply be due to neutral processes (e.g.~genetic drift and mutation)
moving trait values of the population. For our system, we currently lack
quantitative estimates of genetic variation in our traits, although work
with other species of galling insects has shown that gall diameter
(Abramhson, Heath's work), clutch size (look to Weiss' work), and
oviposition preference (Abrahmson's work?) are genetically variable. We
encourage others to examine how changes in community context will alter
selection on multiple traits.

One interesting result of our work was that the overall intensity of
selection appeared to be larger in complex food webs. This result was
driven by the large selection gradient acting on gall diameter in
complex vs.~simple food webs. This difference in selection intensity is
likely not driven by a difference in the ecological relationship between
gall diameter and parasitoid attack (i.e.~slope), but actually a result
of the lower mean fitness of \emph{Iteomyia} in the complex food web.
This lower mean fitness is not surprising ---we excluded an entire guild
of parasitoids from attacking the insect. But this more intense
selection pressure may simply represent a transient dynamic. This is
because we would expect the egg-parasitoid \emph{Platygaster} to
increase in abundance over time once its intraguild predator has been
removed. While our results suggest that this wouldn't affect the slope
of the relationship, the higher abundance of the egg parasitoid would
likely reduce the mean fitness of \emph{Iteomyia}, thus increasing the
selection gradient acting on gall diameter closer to what we observed in
the complex food web. We don't expect it to fully compensate, given that
the larval parasitoids exhibit a different functional relationship with
gall traits, and thus we expect a more diverse community of primary
parasitoids to generally impose greater parasitism pressure, a factor
that appears to be a general trend in parasitoid community (Hawkins
citation) and likely for other consumers (Ives and Cardinale Ecology
Letters).

Our study focused on quantifying the direct effects of changes in
network complexity on the fitness landscape; however, changes in network
complexity may have pervasive indirect effects via coevolution or by
initiating evolutionary cascades. In our system, we observed that
excluding the guild of larval parasitoids altered selection on both the
basal resource (\emph{Iteomyia}) and the intraguild prey
(\emph{Platygaster}). GIVE DETAILS AND SUGGEST A POTENTIAL EVOLUTIONARY
CASCADE.

Our study manipulated food-web complexity and examined changes in the
fitness landscape of species embedded within this network. However,
other studies have also examined, at least theoretically, how changes in
the diversity of competitive communities affects evolution. These
studies have generally suggested that the diversity of competitors may
actually constrain the adaptive landscape, a finding that stands in
contrast to our results. NEED TO REVIEW THESE PAPERS TO SEE HOW ITS
DIFFERENT.

We suggest that by explicitly focusing on network structure, we can
predict how changes in biodiversity will affect the adaptive potential
of constituent species. A network allows a powerful representation of
the `community context', lending predictive power to how changes in
network structure (either due to loss of species or links), will alter
natural selection and consequently evolutionary change. Our results also
suggest that losing biodiversity may not just have consequences at the
community level, but also population-level consequences that may
actually constrain adaptation to changing environments. This argues that
changes in network complexity may not only affect the robustness of
communities, but also that of constituent populations to future
environmental change.

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\hypertarget{ref-Barbour2016}{}
Barbour, Matthew A, Miguel A Fortuna, Jordi Bascompte, Joshua R
Nicholson, Riitta Julkunen-Tiitto, Erik S Jules, and Gregory M
Crutsinger. 2016. ``Genetic Specificity of a Plant--insect Food Web:
Implications for Linking Genetic Variation to Network Complexity.''
\emph{Proceedings of the National Academy of Sciences} 113 (8). National
Acad Sciences: 2128--33.

\hypertarget{ref-Barbour2015}{}
Barbour, Matthew A, Mariano A Rodriguez-Cabal, Elizabeth T Wu, Riitta
Julkunen-Tiitto, Carol E Ritland, Allyson E Miscampbell, Erik S Jules,
and Gregory M Crutsinger. 2015. ``Multiple Plant Traits Shape the
Genetic Basis of Herbivore Community Assembly.'' \emph{Funct. Ecol.} 29
(8): 995--1006.

\hypertarget{ref-Bolker2009}{}
Bolker, Benjamin M, Mollie E Brooks, Connie J Clark, Shane W Geange,
John R Poulsen, M Henry H Stevens, and Jada-Simone S White. 2009.
``Generalized Linear Mixed Models: A Practical Guide for Ecology and
Evolution.'' \emph{Trends Ecol. Evol.} 24 (3): 127--35.

\hypertarget{ref-Janzen1998}{}
Frederic J Janzen and Hal S Stearn. 1998. ``Logistic Regression for
Empirical Studies of Multivariate Selection.'' \emph{Evolution} 52 (6):
1564--71.

\hypertarget{ref-Gripenberg2010}{}
Gripenberg, Sofia, Peter J Mayhew, Mark Parnell, and Tomas Roslin. 2010.
``A Meta-Analysis of Preference-Performance Relationships in
Phytophagous Insects.'' \emph{Ecol. Lett.} 13 (3): 383--93.

\hypertarget{ref-Hawkins1997}{}
Hawkins, Bradford A, Howard V Cornell, and Michael E Hochberg. 1997.
``Predators, Parasitoids, and Pathogens as Mortality Agents in
Phytophagous Insect Populations.'' \emph{Ecology} 78 (7). Ecological
Society of America: 2145--52.

\hypertarget{ref-Heath2018}{}
Heath, Jeremy J, Patrick Abbot, and John O Stireman 3rd. 2018.
``Adaptive Divergence in a Defense Symbiosis Driven from the Top down.''
\emph{Am. Nat.} 192 (1): E21--E36.

\hypertarget{ref-Hunter2018}{}
Hunter, Darren C, Josephine M Pemberton, Jill G Pilkington, and Michael
B Morrissey. 2018. ``Quantification and Decomposition of
Environment-Selection Relationships.'' \emph{Evolution}, March.

\hypertarget{ref-Ives2005}{}
Ives, Anthony R, Bradley J Cardinale, and William E Snyder. 2005. ``A
Synthesis of Subdisciplines: Predator--prey Interactions, and
Biodiversity and Ecosystem Functioning.'' \emph{Ecol. Lett.} 8 (1).
Blackwell Science Ltd: 102--16.

\hypertarget{ref-R2018}{}
R Core Team. 2018. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\hypertarget{ref-Russo2006}{}
Russo, Ron. 2006. \emph{Field Guide to Plant Galls of California and
Other Western States}. 1st ed. University of California Press.

\hypertarget{ref-Singer1986}{}
Singer, Michael C. 1986. ``The Definition and Measurement of Oviposition
Preference in Plant-Feeding Insects.'' In \emph{Insect-Plant
Interactions}, edited by James R Miller and Thomas A Miller, 65--94. New
York, NY: Springer New York.

\hypertarget{ref-Weis1983}{}
Weis, Arthur E, Peter W Price, and Michael Lynch. 1983. ``Selective
Pressures on Clutch Size in the Gall Maker Asteromyia Carbonifera.''
\emph{Ecology} 64 (4). Ecological Society of America: 688--95.

\end{document}

### 2018-09-21 temporary_morgue/ms_complexity_selection_OLD.Rmd
getting organized

--- 2018-09-20 elsevier_test/elsevier_test.Rmd
@@
          platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
   mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
@@
          sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots)))) 
+dim(gall_selection.df)
 
@@
   #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
+dim(control_df)
 
@@
   filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+dim(treatment_df)
   #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
@@
   brackets <- predict(., type = "response") * (1 - predict(., type="response"))
-  mean(brackets) * fixef(.)[-1] / mean_fitness 
+  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
 }
@@
 
-<!-- > *There is a much more insidious kind of extinction: the extinction of ecological interactions.* 
-> *(Janzen, D.H. 1974. The deflowering of Central America. Natural History. 83:48–53).* -->
+So what did I learn this morning?
+I believe I can reliably estimate selection gradients from a full model by taking care in how I transform the data.
+This means that I use the data from each treatment to actually calculate the selection coefficients on the scale of relative fitness.
+```{r}
+hist(gall_selection.df$sc.gall_size)
+mean(gall_selection.df$sc.gall_size)
+sd(gall_selection.df$sc.gall_size)
+hist(rnorm(n = length(gall_selection.df$sc.gall_size), mean = 0, sd = 1))
+bind_rows(data.frame(phenotype = gall_selection.df$sc.gall_size, type = "real"), data.frame(phenotype = rnorm(n = length(gall_selection.df$sc.gall_size), mean = 0, sd = 1), type="sim")) %>%
+  ggplot(., aes(x=phenotype, fill=type)) + geom_density(alpha=0.25) # this is about as normally distributed as can be...
+
+base_glm <- glm(gall_survival ~ sc.gall_size, gall_selection.df, family=binomial(link="logit"))
+inverse_logit(coef(base_glm))
+mean(gall_selection.df$gall_survival)
+
+main_glm <- glm(gall_survival ~ Treatment.focus + sc.gall_size, gall_selection.df, family=binomial(link="logit"))
+summary(main_glm)
+inverse_logit(coef(main_glm))
+gall_selection.df %>% group_by(Treatment.focus) %>% summarise(mean_fitness = mean(gall_survival))
+
+inter_glm <- glm(gall_survival ~ Treatment.focus*sc.gall_size, gall_selection.df, family=binomial(link="logit"))
+summary(inter_glm)
+
+inter_rev_glm <- glm(gall_survival ~ Treatment.focus*sc.gall_size, mutate(gall_selection.df, Treatment.focus=relevel(as.factor(Treatment.focus), ref="Ectoparasitoid exclusion")), family=binomial(link="logit"))
+summary(inter_rev_glm)
+
+mean(predict(base_glm, type="response"))
+mean(gall_selection.df$gall_survival)
+
+mean(predict(base_glm, type="response")*(1-predict(base_glm, type="response")))*coef(base_glm)/mean(predict(base_glm, type="response"))
+mean(predict(main_glm, type="response")*(1-predict(main_glm, type="response")))*coef(main_glm)[3]/0.4551920
+mean(predict(inter_glm, type="response")*(1-predict(inter_glm, type="response")))*coef(inter_glm)[3]/0.4551920
+mean(predict(inter_glm, type="response")*(1-predict(inter_glm, type="response")))*(coef(inter_glm)[3]+coef(inter_glm)[4])/0.6168385
+mean(predict(inter_rev_glm, type="response")*(1-predict(inter_rev_glm, type="response")))*coef(inter_rev_glm)[3]/0.6168385
+mean(predict(inter_rev_glm, type="response")*(1-predict(inter_rev_glm, type="response")))*(coef(inter_rev_glm)[3]+coef(inter_rev_glm)[4])/0.4551920
+
+# now one of the questions is, do you use the mean of the "brackets" for the entire distribution, or just for the particular treatment?
+
+mean(control_df$gall_survival)
+mean(predict(glm(gall_survival ~ 1, control_df, family=binomial(link="logit")), type="response"))
+mean(predict(glmer(gall_survival ~ 1 + (1|Genotype), control_df, family=binomial(link="logit")), type="response"))
+mean(predict(glmer(gall_survival ~ 1 + (1|Genotype)+(1|Plant_Position), control_df, family=binomial(link="logit")), type="response"))
+mean(predict(glmer(gall_survival ~ 1 + (1|Genotype)+(1|Plant_Position) + (1|Gall_Number), control_df, family=binomial(link="logit")), type="response"))
+
+test_glmer <- glmer(gall_survival ~ Treatment.focus*sc.gall_size + (1|Genotype)+(1|Plant_Position) + (1|Gall_Number), gall_selection.df, family=binomial(link="logit"))
+summary(test_glmer)
+summary(inter_glm)
+mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Control"), type="response")*(1-predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Control"), type="response")))*fixef(test_glmer)[3]/mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Control"), type="response"))
+mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), type="response")*(1-predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), type="response")))*(fixef(test_glmer)[3]+fixef(test_glmer)[4])/mean(predict(test_glmer, newdata=filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"), type="response"))
+
+piecewiseSEM::rsquared(test_glmer)
+piecewiseSEM::rsquared(glmer(gall_survival ~ Treatment.focus*sc.gall_size + (1|Genotype), gall_selection.df, family=binomial(link="logit")))
+
+# the exact same, because of my coding structure
+summary(glmer(gall_survival ~ 1 + (1|Genotype)+(1|Plant_Position) + (1|Gall_Number), control_df, family=binomial(link="logit")))
+summary(glmer(gall_survival ~ 1 + (1|Genotype/Plant_Position/Gall_Number), control_df, family=binomial(link="logit")))
+```
 
@@
 Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the fitness landscape of a resource population.
-
-<!-- I. Evolutionary dynamics in species-rich communities remains unclear, especially in the field -->
-
-<!-- Biological diversity -- from genes, to phenotypes, to species -- has and continues to be shaped by the interplay between ecological and evolutionary processes.
-<!-- need to improve this instead of just saying its fascinated a small group of people -->
-<!-- Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (@Schluter2000), mutualisms (@Jordano1987), and predation (@Abrams2000).
-While there is clear evidence that pairwise interactions can drive evolution, we also know that most species interact with multiple species in an ecological community.
-<!-- are embedded within species-rich communities.--> <!-- complex networks of interacting species.
-<!-- need to make the link to multiple traits and the adaptive landscape here --> <!-- Somthing about the this work remaining eminently theoretical -->
-<!-- Understanding how evolutionary dynamics unfold in a community context<!-- when moving beyond pairwise interactions--><!-- in more species-rich communities--><!--  is challenging and eminently theoretical (@McPeek2017, @De_Mazancourt2008, @Guimaraes2017, @Nuismer2013).
-<!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
-I think it would be useful to show that there is some field and lab experiments demonstrating that community context can alter evolutionary trajectories -->
-<!-- Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
-
-<!-- Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests of how changes in network structure will alter the dynamics of natural selection in the field.
--->
-
-<!-- II. Linking species loss to changes in network complexity -->
-
-Predicting the evolutionary consequences of species loss first requires an understanding of the concommitant change in the species-interaction networks.<!-- the relationship between the network structure of a community and the fitness landscape of its constituent species.-->
-Knowing the interaction network is crucial because the loss of biodiversity, in and of itself, will not alter evolution -- it is the associated loss of ecological interactions that will affect evolutionary change (@Janzen1974).
-For a network of directly connected species, we would expect that the loss of species to result in a loss of network complexity.<!-- Need to formalize this logic more, because the loss of a specialist species in a highly generalist food web, would actually increase network complexity...
-Maybe I need to focus on the node/species level property -->
-Network complexity is a property that describes the diversity of interactions in an ecological community (@Banasek-Richter2009). 
-Thus, all else equal, species loss will decrease the diversity of interactions, resulting in a more simple network.
-<!-- Explicitly linking network complexity to the fitness landscape, however, is ultimately needed to predict the evolutionary consequences of biodiversity loss.
--->
-
-<!-- III. Linking changes in network complexity to the fitness landscape -->
-Predicting how a change in network complexity will alter evolution also requires an understanding of the relationship between network structure and the adaptive landscape. 
-The adaptive landscape (i.e.
-fitness landscape or selective surface) describes the relationship between the average trait value of a population and its average fitness (cite Arnold).
-<!-- Need to make the transition between network and trophic complexity -->
-For a trophic network, such as a food web, changes in network complexity can shape the adaptive landscape of constituent species in at least two ways. 
-First, if a more diverse community of consumers is more efficient at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population. 
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018) and thus could speed up the rate of evolutionary change. 
-On the other hand, if consumers are functionally distinct, then more diverse communities can dampen the strength of selection. 
-This is because each consumer has a different functional relationship with resource traits. 
-In addition, there is a reduced probability in interacting with a specific consumer species in a more diverse community.
-Thus, a more diverse consumer community may impose more diffuse selection across the adaptive landscape. <!--and the probability of an interaction.-->
-<!-- Consider linking to a reduced probability of interacting with any one species in the community, which would dampen the selection pressures acting on a given phenotype, also, if predators impose selection on different parts of a prey phenotype, then these selection pressures may even cancel each other out -->
-
-<!-- IV. Summarize our plans to tackle this problem -->
-
-Here, we provide a quantitative test of how the loss of species diversity -- and concomittant loss of network complexity -- shapes the adaptive landscape of a consitutent species in a natural community.
-<!-- Here, we conducted a field experiment to test how changes in network complexity would shape the fitness landscape of a constituent species. -->
-We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on the insect herbivore, *Iteomyia salicisverruca*. 
-The larva of this herbivore species induces tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006). 
-Prior work with this study system has shown that there is directional selection for larger galls, likely because larger galls provide a refuge from parasitoid attack (@Barbour2016). 
-However, there is also evidence that each parasitoid species imposes differential selection on gall traits (@Barbour2016). <!-- Need a sentence to wrap it up--> 
-<!-- Taken together, our study seeks to provide one of the first quantitative tests of how the loss of species diversity -- and concomittant loss of network complexity -- shapes the fitness landscape of associated species.
--->
-Taken together, our aim is to provide evidence for how the simplification of natural communities affects the adaptive<!--process--> potential of constituent species.
-
-<!-- Alternative intro, "the fitness landscape as the unifying concept between ecology and evolutionary biology "-->
-
-<!-- Although often used solely as a metaphor, the fitness landscape explicitly links ecology and evolutionary biology. -->
-<!-- Fitness landscapes provide a quantitative framework for unifying evolutionary biology and ecology.
-Alternatively described as the 'adaptive landscape' or 'selective surface', evolutionary biologists have traditionally used the fitness landscape to describe how changes in the mean values of a trait or multiple traits can alter population mean fitness.
-Less appreciated is the fact that ecologists have similarly been studying the fitness landscape of species but through the lense of population dynamics.
-study how changes in population abundances of interacting species shapes the fitness landscape (@McPeek2017).
-This is because per capita population growth rate is equivalent to population mean fitness (cite Lande ; @McPeek2017).
--->
-
-<!-- Therefore, understanding the feedbacks between ecological and evolutionary dynamics requires an assessment of how the community context shapes the fitness landscape.
-
-We are in the midst of the lost of biological diversity; yet it remains unclear how the loss of biological diversity will alter evolutionary change within species. In order to predict how -->
-
-<!-- II. Ecologists have incorporated community context -->
-
-<!-- In contrast, ecologists have begun to embrace the complexity of the natural world, and seeking to identify the complex networks of interactions that underlie community structure and ecosystem function.
-However, these studies have not examined how evolutionary processes feedback to shape the structure and evolution of these interaction networks.
--->
-
-<!-- III. Generate expectations for how food-web complexity may alter selection gradients -->
-
-<!-- Food-web complexity can shape the fitness landscape in at least two ways.
-First, if more diverse predator communities are more efficient at suppressing prey densities (e.g.
-biodiversity-ecosystem fucntion; Ives 2005 Ecology Letters), then this will result in lower mean fitness.
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018) and thus could speed up the rate of evolutionary change.
-Alternatively, if predators are functionally distinct, more diverse communities can reduce the strength of selection.
-This is because each predator has a different functional relationship between prey phenotype and the probability of an interaction.
--->
-
-<!-- IV. Relationship between entropy and fitness landscape 
-In more complex communities, there is greater uncertainty for an individual prey in which predator species will be imposing the trophic interaction. This also means the -->
 
@@
 All analyses and visualizations were conducted in R (@R2018).
+
+```{r Effects of food-web complexity on components of natural selection, cache=TRUE, include=FALSE}
+
+## Fit GLMM
+null_glmer <- glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
+                         sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = gall_selection.df,
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"), na.action = "na.fail")
+
+foodweb_glmer <- glmer(gall_survival ~ Treatment.focus*(sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
+                         sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference) +
+                           (1|Genotype/Plant_Position/Gall_Number),
+                         data = gall_selection.df,
+                         family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"), na.action = "na.fail")
+
+## Test for overdispersion
+overdisp_fun(null_glmer)    # no evidence
+overdisp_fun(foodweb_glmer) # no evidence
+
+## Compare statistical summaries of each model
+summary(null_glmer)
+summary(foodweb_glmer)
+
+round(cov2cor(vcov(foodweb_glmer)),2)
+
+## Test statistical significance of effects
+anova(null_glmer, foodweb_glmer, test = "Chisq") # evidence that food-web treatment alters the components of natural selection
+
+## Use drop1 to parse out which effects are determining the differences in selection between treatments.
+drop1(foodweb_glmer, test="Chisq") # marginal effect of food-web treatment on nonlinear selection acting on female preference
+
+drop1(update(foodweb_glmer, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # nonlinear selection acting on gall size in complex food web
+
+drop1(update(foodweb_glmer, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # marginal effect of correlational selection on gall size and clutch size in the complex food web; food-web treatment altered directional selection on clutch size
+
+drop1(update(foodweb_glmer, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference), test="Chisq") # strong effect of food-web treatment on absolute fitness; directional selection acting on gall size in complex food web; no directional selection acting on clutch size in the complex food web; directional selection acting on female preference in the complex food web.
+
+summary(update(foodweb_glmer, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference))
+```
+
+It appears that the mixed-effects model qualtiatively alters my conclusions when I compare the results of the full data set to the subset.
+Why is this?
+Perhaps it "learns" more from the random effects in the large dataset because it also accounts for the different treatments?
+```{r Something funny with mixed effects}
+summary(glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = treatment_df, family = binomial(link = logit)))
+summary(glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = control_df, family = binomial(link = logit)))
+summary(glm(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = gall_selection.df, family = binomial(link = logit)))
+summary(glm(gall_survival ~ Treatment.focus*(sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference), data = gall_selection.df, family = binomial(link = logit)))
+
+control_test <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = control_df, family = binomial(link = logit))
+ggplot(data.frame(resids = resid(control_test), Genotype = control_df$Genotype), aes(x=Genotype, y=resids)) +
+  geom_boxplot()
+summary(lm(resids ~ Genotype, data.frame(resids = resid(control_test), Genotype = control_df$Genotype)))
+anova(lm(resids ~ Genotype, data.frame(resids = resid(control_test), Genotype = control_df$Genotype)))
+
+treatment_test <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference, data = treatment_df, family = binomial(link = logit))
+ggplot(data.frame(resids = resid(treatment_test), Genotype = treatment_df$Genotype), aes(x=Genotype, y=resids)) +
+  geom_boxplot()
+summary(lm(resids ~ Genotype, data.frame(resids = resid(treatment_test), Genotype = treatment_df$Genotype)))
+anova(lm(resids ~ Genotype, data.frame(resids = resid(treatment_test), Genotype = treatment_df$Genotype)))
+
+summary(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (Treatment.focus|Genotype) + (1|Plant_Position/Gall_Number), data = gall_selection.df, family = binomial(link = logit)))
+
+anova(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")),
+      glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")), test="Chisq")
+
+anova(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")),
+      glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (sc.log1p.female_preference|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")), test="Chisq")
+
+summary(glmer(gall_survival ~ Treatment.focus + sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference|Genotype) + (1|Plant_Position) + (1|Gall_Number), data = gall_selection.df, family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa")))
+
+summary(glmer(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + (1|Genotype) + (1|Plant_Position/Gall_Number), data = control_df, family = binomial(link = logit)))
+
+with(gall_selection.df, table(Genotype, Treatment.focus))
+```
+
+```{r}
+foodweb_glm <- glm(gall_survival ~ Treatment.focus*(sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                         I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                         sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference +
+                         sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference),
+                         data = gall_selection.df,
+                         family = binomial(link = logit), na.action = "na.fail")
+
+## Compare statistical summaries of each model
+summary(foodweb_glm)
+
+## Use drop1 to parse out which effects are determining the differences in selection between treatments.
+drop1(foodweb_glm, test="Chisq") # marginal effect of food-web treatment on nonlinear selection acting on female preference
+
+drop1(update(foodweb_glm, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # nonlinear selection acting on gall size in complex food web
+
+drop1(update(foodweb_glm, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq") # marginal effect of correlational selection on gall size and clutch size in the complex food web; food-web treatment altered directional selection on clutch size
+
+drop1(update(foodweb_glm, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference), test="Chisq") # strong effect of food-web treatment on absolute fitness; directional selection acting on gall size in complex food web; no directional selection acting on clutch size in the complex food web; directional selection acting on female preference in the complex food web.
+
+summary(update(foodweb_glm, .~.
+-Treatment.focus:I(sc.gall_size^2) -Treatment.focus:I(sc.log.clutch_size^2) -Treatment.focus:I(sc.log1p.female_preference^2) -Treatment.focus:sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size:sc.log.clutch_size -Treatment.focus:sc.gall_size:sc.log1p.female_preference -Treatment.focus:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.gall_size:sc.log1p.female_preference -sc.log.clutch_size:sc.log1p.female_preference -Treatment.focus:sc.gall_size -Treatment.focus:sc.log.clutch_size -Treatment.focus:sc.log1p.female_preference))
+
+```
+
+```{r}
+glm_control <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                     I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                     sc.gall_size:sc.log.clutch_size + sc.log.clutch_size:sc.log1p.female_preference + sc.gall_size:sc.log1p.female_preference + sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference, data = control_df, family = binomial(link = logit))
+drop1(glm_control, test="Chisq")
+drop1(update(glm_control, .~. -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq")
+drop1(update(glm_control, .~.
+-I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log1p.female_preference), test="Chisq")
+
+glm_treatment <- glm(gall_survival ~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference +
+                     I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) +
+                     sc.gall_size:sc.log.clutch_size + sc.log.clutch_size:sc.log1p.female_preference + sc.gall_size:sc.log1p.female_preference + sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference, data = treatment_df, family = binomial(link = logit))
+drop1(glm_treatment, test="Chisq")
+drop1(update(glm_treatment, .~. -I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference), test="Chisq")
+drop1(update(glm_treatment, .~.
+-I(sc.gall_size^2) -I(sc.log.clutch_size^2) -I(sc.log1p.female_preference^2) -sc.gall_size:sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log.clutch_size -sc.log.clutch_size:sc.log1p.female_preference -sc.gall_size:sc.log1p.female_preference), test="Chisq")
+```
 

### 2018-09-21 temporary_morgue/selection_tutorial.Rmd
getting organized

--- 2018-04-02 selection_tutorial.Rmd
@@
 ---
-title: "Tutorial: Calculating Selection"
+title: "Tutorial: Quantifying Natural Selection"
 output: html_notebook
@@
 library(cowplot) # pretty default ggplots
-library(broom) # for tidying multiple linear models
+#library(broom) # for tidying multiple linear models
 
@@
 ```
+
+Evolution by natural selection requires three basic ingredients: (1) variation in phenotypes; (2) variation in fitness; and (3) heritabile phenotypic variation.
+Although heritability is a key component to predicting evolutionary change, we can ignore it if we just focus on quantifying natural selection, which requires just the first two ingredients.
+
+Perhaps the easiest way to quantify natural selection is by calculating the *selection differential* ($s$), which corresponds to the change in mean phenotype ($z$) after selection: $$s=\bar{z}^*-\bar{z}$$.
+For my galling insects, this is straightforward to measure.
+I calculate the mean phenotype of all galls and compare it to the mean phenotype of surviving insects.
+Below is an example with gall size:
+
+```{r figure: gall size selection differential, echo=FALSE, message=FALSE, warning=FALSE}
+size_means_diffs <- gall_diffs.df %>%
+  group_by(Timing, Treatment.focus) %>%
+  summarise_at(vars(Gall_Height_mm, gall_survival), funs(mean, var, sd))
+
+sd_size_before <- filter(size_means_diffs, Treatment.focus=="Control", Timing=="Before")$Gall_Height_mm_var
+
+size_differentials <- size_means_diffs %>%
+  select(Timing, Treatment.focus, Gall_Height_mm_mean) %>%
+  spread(Timing, Gall_Height_mm_mean) %>%
+  mutate(selection_differential = After - Before)
+
+s_size <- filter(size_differentials, Treatment.focus=="Control")$selection_differential
+sc_s_size <- s_size/sd_size_before
+
+gall_diffs.df %>%
+  filter(Treatment.focus == "Control") %>%
+  ggplot(., aes(x=Gall_Height_mm, fill=Timing)) +
+  geom_density(alpha=0.5) +
+  geom_vline(data=filter(size_means_diffs, Treatment.focus=="Control"), aes(xintercept=Gall_Height_mm_mean, color=Timing), linetype="dashed") #+
+  #facet_wrap(~Treatment.focus, ncol = 1)
+```
+
+Here, the $s=0.83$.
+Note that this selection differential is unstandardized.
+This makes it difficult to compare the strength of selection acting on different phenotypes both within and across studies.
+We can calculate the standardized selection differential as: $$S'=\frac{S}{\sigma_z}$$
+
+For gall size, $S'=0.18$.
+
+There is another way that we can express and visualize selection differentials, name as the covariance between phenotype and relative fitness: $$S=cov(w,z)$$
+
+where relative fitness is calculated as absolute fitness ($W$) divided by the mean fitness of the population: $$w=\frac{W}{\bar{W}}$$
+
+Let's visualize what this looks like with the gall data:
+
+```{r}
+W_bar_control <- filter(size_means_diffs, Treatment.focus=="Control", Timing=="Before")$gall_survival_mean
+control_df <- gall_selection.df %>%
+  filter(Treatment.focus=="Control") %>%
+  mutate(relative_fitness = gall_survival/W_bar_control)
+
+with(control_df, cov(relative_fitness, Gall_Height_mm))
+
+summary(lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), control_df))
+
+0.83/sd(control_df$Gall_Height_mm) # standardized selection differential
+0.83/var(control_df$Gall_Height_mm) # selection gradient
+
+ggplot(control_df, aes(x=Gall_Height_mm, y=relative_fitness)) +
+  geom_jitter(height=0.1, shape=1) +
+  geom_smooth(method="lm") +
+  geom_hline(yintercept=1, linetype="dotted", color="grey") +
+  geom_vline(xintercept=filter(size_means_diffs, Treatment.focus=="Control", Timing=="Before")$Gall_Height_mm_mean, 
+             linetype="dotted", color="grey")
+```
+
+This gives us the same estimate of selection differential as before.
+
+## Calculating selection in different environments
+
+```{r}
+
+# (1) calculate relative fitness for each environment separately
+W_bar_treatment <- filter(size_means_diffs, Treatment.focus=="Ectoparasitoid exclusion", Timing=="Before")$gall_survival_mean; W_bar_treatment
+
+gall_selection.df <- gall_selection.df %>%
+  mutate(relative_fitness = ifelse(Treatment.focus=="Control", gall_survival/W_bar_control, gall_survival/W_bar_treatment))
+
+ggplot(gall_selection.df, aes(x=Gall_Height_mm, y=relative_fitness, color=Treatment.focus)) +
+  geom_jitter(height=0.1, shape=1) +
+  geom_smooth(method="lm") +
+  geom_hline(yintercept=1, linetype="dotted", color="grey") +
+  geom_vline(data = filter(size_means_diffs, Timing=="Before"), aes(xintercept=Gall_Height_mm_mean, color=Treatment.focus), linetype="dotted")
+```
+
+Let's dissect this a bit further...
+
+```{r}
+ggplot(gall_selection.df, aes(x=Gall_Height_mm, y=gall_survival, color=Treatment.focus)) +
+  geom_jitter(height=0.05, shape=1) +
+  geom_smooth(method="lm") +
+  #geom_hline(yintercept=1, linetype="dotted", color="grey") +
+  geom_vline(data = filter(size_means_diffs, Timing=="Before"), aes(xintercept=Gall_Height_mm_mean, color=Treatment.focus), linetype="dotted") +
+  scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1))
+
+summary(lm(gall_survival ~ Treatment.focus*I(Gall_Height_mm - mean(Gall_Height_mm)), gall_selection.df))
+```
+
+Interesting.
+So there doesn't appear to be a difference in the relationship between gall survival and gall size between treatments.
+Therefore, the differences in selection gradients between treatments is due to differences in relative fitness between environments.
+
+So where do I go from here?
+In my view, the differences in relative fitness are an experimental artifact of the reduction in parasitoid diversity, and therefore, there hasn't been a chance for the parasitoid in the simple community to compensate in terms of its abundance over multiple generations and make up for the differences in relative fitness.
+
+Some exploratory analyses:
+
+```{r}
+with(control_df, cov(relative_fitness, Gall_Height_mm))
+
+summary(lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), control_df))
+
+with(control_df, cov(relative_fitness, gall_individuals))
+
+# adding gall individuals
+summary(lm(relative_fitness ~ 
+             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
+             I(gall_individuals - mean(gall_individuals)), 
+           control_df))
+
+# adding gall density
+summary(lm(relative_fitness ~ 
+             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
+             I(gall_individuals - mean(gall_individuals)) +
+             I(Density_per_100_shoots - mean(Density_per_100_shoots)),
+           control_df))
+
+## treatment focus
+summary(lm(relative_fitness ~ I(Gall_Height_mm - mean(Gall_Height_mm)), 
+           filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))
+
+summary(lm(relative_fitness ~ 
+             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
+             I(gall_individuals - mean(gall_individuals)), 
+           filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))
+
+summary(lm(relative_fitness ~ 
+             I(Gall_Height_mm - mean(Gall_Height_mm)) + 
+             I(gall_individuals - mean(gall_individuals)) +
+             I(Density_per_100_shoots - mean(Density_per_100_shoots)),
+           filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")))
+
+## with treatment variable
+summary(lm(relative_fitness_adj ~ 
+             I(Gall_Height_mm - mean(Gall_Height_mm)) + Treatment.focus:I(Gall_Height_mm - mean(Gall_Height_mm)) +
+             I(gall_individuals - mean(gall_individuals)) + Treatment.focus:I(gall_individuals - mean(gall_individuals)) +
+             I(Density_per_100_shoots - mean(Density_per_100_shoots)) + Treatment.focus:I(Density_per_100_shoots - mean(Density_per_100_shoots)),
+           gall_selection.df))
+
+W_bar_platy_control <- mean(filter(gall_selection.df, Treatment.focus=="Control")$egg_parasitoid)
+W_bar_platy_treatment <- mean(filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion")$egg_parasitoid)
+
+W_bar_treatment_adj <- W_bar_treatment - (W_bar_platy_treatment - W_bar_platy_control); W_bar_treatment_adj
+
+gall_selection.df <- gall_selection.df %>%
+  mutate(relative_fitness_adj = ifelse(Treatment.focus=="Control", gall_survival/W_bar_control, gall_survival/W_bar_treatment_adj))
+
+summary(lm(relative_fitness_adj ~ 
+             scale(Gall_Height_mm) + Treatment.focus:scale(Gall_Height_mm) +
+             scale(gall_individuals) + Treatment.focus:scale(gall_individuals) +
+             scale(Density_per_100_shoots) + Treatment.focus:scale(Density_per_100_shoots),
+           gall_selection.df))
+
+summary(lm(relative_fitness ~ 
+             scale(Gall_Height_mm) + Treatment.focus:scale(Gall_Height_mm) +
+             scale(gall_individuals) + Treatment.focus:scale(gall_individuals) +
+             scale(Density_per_100_shoots) + Treatment.focus:scale(Density_per_100_shoots),
+           gall_selection.df))
+```
+
+GSG package
+```{r}
+library(gsg)
+library(mgcv)
+library(visreg)
+
+# experimenting with boot.case gave bootstrapped distributions that weren't centered near the model mean estimate.
+# also, using 'refit.smooth = T' also generated some very skewed distributions
+# the recipe below provided the most sensible estimates for my data
+gradient.calc <- function(mod, phenotype, covariates = NULL) {
+  gam.gradients(mod, phenotype, covariates, #parallel = 'multicore', ncpus = 32, 
+                refit.smooth = F, 
+                se.method = 'boot.para',
+                standardized = T)
+}
+
+gam.size.control <- gam(gall_survival ~ s(Gall_Height_mm), data = filter(gall_selection.df, Treatment.focus=="Control"))
+summary(gam.size.control)
+visreg(gam.size.control)
+
+gradient.calc(gam.size.control, phenotype = "Gall_Height_mm")$ests
+
+gam.size.treatment <- gam(gall_survival ~ s(Gall_Height_mm) + s(gall_individuals, k=9) + s(Density_per_100_shoots), data = filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion"))
+summary(gam.size.treatment)
+visreg(gam.size.treatment)
+
+gradient.calc(gam.size.treatment, phenotype = "Gall_Height_mm", covariates = c("gall_individuals","Density_per_100_shoots"))$ests
+
+```
+
+Does the theory require multivariate normal phenotypes?
 
@@
 The most straightforward way to measure selection is the *selection differential*, which corresponds to the difference in mean phenotype before vs. after selection: $$s=\bar{z}^*-\bar{z}$$.
-
-```{r figure: gall size selection differential, echo=FALSE, message=FALSE, warning=FALSE}
-size_means_diffs <- gall_diffs.df %>%
-  group_by(Timing, Treatment.focus) %>%
-  summarise_at(vars(Gall_Height_mm, gall_survival), funs(mean, var, sd)) 
-size_means_diffs
-
-size_differentials <- size_means_diffs %>%
-  select(Timing, Treatment.focus, Gall_Height_mm_mean) %>%
-  spread(Timing, Gall_Height_mm) %>%
-  mutate(selection_differential = After - Before)
-size_differentials
-
-gall_diffs.df %>%
-  ggplot(., aes(x=Gall_Height_mm, fill=Timing)) +
-  geom_density(alpha=0.5) +
-  geom_vline(data=size_means_diffs, aes(xintercept=Gall_Height_mm_mean, color=Timing), linetype="dashed") +
-  facet_wrap(~Treatment.focus, ncol = 1)
-```
 

### 2018-09-21 temporary_morgue/supp_mat_complexity_selection.Rmd
getting organized

--- 2018-06-21 supp_mat_complexity_selection.Rmd
@@
 ---
+
+ADD A SECTION WITH AIC SHOWING THAT ITS BETTER TO USE A MODEL WITH TRANSFORMED VARIABLES, AND IT HELPS MEET THE ASSUMPTIONS OF THE FITNESS LANDSCAPE ANALYSIS.
 
@@
 }
+```
+
+```{r}
+length(unique(gall_selection.df$Genotype)) # 8 plant genotypes
+length(unique(gall_selection.df$Plant_Position)) # 111 plants
+length(unique(gall_selection.df$Gall_Number)) # 614 galls
+length(unique(gall_selection.df$Gall_ID)) # 1302 larva
 ```
@@
 ```
+
+<!--stackedit_data:
+eyJoaXN0b3J5IjpbLTEzMzk3NTQwOTNdfQ==
+-->

### 2018-09-21 exploratory_analyses.R

@@ -1,421 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES ----
-library(tidyverse)
-library(cowplot)
-
-## LOAD DATASET ----
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.factor(Plant_Position),
-         Gall_Number = as.factor(Gall_Number),
-         Treatment.focus = as.factor(Treatment.focus),
-         Treatment = as.factor(Treatment),
-         Location = as.factor(Location),
-         phenology = as.factor(phenology),
-         Genotype = as.factor(Genotype),
-         Gall_Letter = as.factor(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree") %>%
-  mutate(gall_survival = ifelse(pupa > 0, 1, 0),
-         platy_bin = ifelse(platy > 0, 1,0),
-         ectos_bin = ifelse(ectos > 0, 1,0))
-
-## EXPLORATORY PLOTS ----
-
-# Plot helpers
-binomial_smooth <- function(...) {
-  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
-}
-
-# explored gam smoothers but they were way too curvy to be informative.
-#gam_smooth <- function(...) {
-#  geom_smooth(method = "gam", method.args = list(family = "binomial"), formula = y ~ s(x))
-#}
-
-viridis6 <- function() {
-  # colours taken from the viridis package
-  c("#440154", "#414487", "#2A788E", "#22A884", "#7AD151", "#FDE725")
-}
-
-dodge <- position_jitterdodge(jitter.width = 0.25, jitter.height = 0, dodge.width = 0.5)
-
-
-## EXPLORING EFFECT OF GENOTYPE ON GALL PHENOTYPES, SURVIVAL, AND PARASITOID RESPONSES ----
-
-# Gall Density
-gall_selection.df %>%
-  group_by(Treatment.focus, Genotype, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots), mean) %>%
-  ggplot(., aes(x = Genotype, y = Density_per_100_shoots, group = Treatment.focus, color = Treatment.focus)) + 
-  geom_jitter(alpha = 0.5, position = dodge) + 
[…]

### 2018-09-21 gam_lm_models.R

@@ -1,240 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-library(mgcv)
-library(gsg)
-library(tidyverse)
-library(cowplot) # pretty default ggplots
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number),
-         Treatment.focus = as.character(Treatment.focus),
-         Treatment = as.character(Treatment),
-         Genotype = as.character(Genotype),
-         Gall_Letter = as.character(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.Gall_Height_mm = as.numeric(scale(Gall_Height_mm)), 
-         sc.gall_individuals = as.numeric(scale(gall_individuals)), 
-         sc.Density_per_100_shoots = as.numeric(scale(Density_per_100_shoots))) 
-
-# aggregate data at gall-level
-
-gall_agg.df <- gall_selection.df %>% 
-  group_by(Treatment.focus, Gall_Number) %>%
-  summarise(prop_survival = mean(gall_survival), # effectively a proportion
-            gall_survival = sum(gall_survival),
-            gall_trials = n(),
-            max.Gall_Height_mm = max(Gall_Height_mm), # taking max to be consistent with prior work
-            gall_individuals = mean(gall_individuals), # all the same number, chose mean for convenience
-            Density_per_100_shoots = mean(Density_per_100_shoots)) # all the same, chose mean for convenience
-
-control_agg.df <- filter(gall_agg.df, Treatment.focus == "Control") %>%
-  mutate(sc.max.Gall_Height_mm = as.numeric(scale(max.Gall_Height_mm)),
-         sc.gall_individuals = as.numeric(scale(gall_individuals)),
[…]

### 2018-09-21 gppr.R

@@ -1,97 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-
-library(tidyverse)
-#library(mgcv)
-#library(gamm4) # for generalized additive mixed models #
-library(gsg)
-library(cowplot) # pretty default ggplots
-library(lme4)
-
-#################   BE CAREFUL IN HOW DATA IS SUBSETTED !!! ###################
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.factor(Plant_Position),
-         Gall_Number = as.factor(Gall_Number),
-         Treatment.focus = as.factor(Treatment.focus),
-         Treatment = as.factor(Treatment),
-         Genotype = as.factor(Genotype),
-         Gall_Letter = as.factor(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%          # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.Gall_Height_mm = as.numeric(scale((Gall_Height_mm))),
-         sc.gall_individuals = as.numeric(scale((gall_individuals))),
-         sc.Density_per_100_shoots = as.numeric(scale((Density_per_100_shoots))))
-
-
-landscape <- glmer(gall_survival ~ sc.Gall_Height_mm*sc.gall_individuals*sc.Density_per_100_shoots*Treatment.focus +
-                     (1|Genotype/Plant_Position/Gall_Number), data = gall_selection.df, family=binomial(link=logit), 
-                   control = glmerControl(optimizer = "bobyqa"), contrasts = list(Treatment.focus="contr.sum"))
-summary(landscape)
-library(visreg)
-visreg(landscape)
-visreg(landscape, xvar = "sc.gall_individuals", by = "Treatment.focus")
-visreg(landscape, xvar = "sc.Density_per_100_shoots", by = "Treatment.focus")
-
[…]

### 2018-09-21 gsg_gradient_pvalue_errors.R

@@ -1,43 +1,0 @@
-## REPRODUCIBLE EXAMPLE OF POTENTIAL ERROR 
-## IN CALCULATION OF BOOT-STRAPPED P-VALUES
-## Matt Barbour, 1 Dec. 2017
-
-## FOLLOWING THE EXAMPLE IN GAM.GRADIENTS HELP FILE ----
-
-# simulated data (stabilizing selection)
-z<-rnorm(200,0,2)
-W<-rpois(200,exp(1-0.3*z^2))
-d<-as.data.frame(list(W=W,z=z))
-
-# characterize the fitness function
-library(mgcv)
-library(gsg)
-ff<-gam(W~s(z),family='poisson',data=d)
-
-# derive selection gradients
-gradients <- gam.gradients(mod=ff,phenotype="z",se.method='boot.para',standardized=FALSE)
-
-# I'm an idiot. The current method is correct.
-hist(gradients$boot[ ,1])
-abline(v = gradients$ests[1,1])
-
-## CURRENT METHOD ----
-# Bootstrapped estimates are compared to zero, not the observed estimate.
-
-# B-z: P = 0.934
-2*min(sum((gradients$boot[ ,1]>0)+0), sum((gradients$boot[ ,1]<0)+0))/length(gradients$boot[ ,2])
-gradients$ests$P.value[1]
-
-# G-z: P = 0.000
-2*min(sum((gradients$boot[ ,2]>0)+0), sum((gradients$boot[ ,2]<0)+0))/length(gradients$boot[ ,2])
-gradients$ests$P.value[2]
-
-## PROPOSED ALTERNATIVE ----
-# Bootstrapped estimates need to be compared to the observed estimate, not zero.
-
-# P = 0.746
-2*min(sum(gradients$boot[ ,1]>gradients$ests$estimates[1]), sum(gradients$boot[ ,1]<gradients$ests$estimates[1]))/length(gppr.size_indiv$boot[ ,1])
-
-# P = 0.574
-2*min(sum(gradients$boot[ ,2]>gradients$ests$estimates[2]), sum(gradients$boot[ ,2]<gradients$ests$estimates[2]))/length(gppr.size_indiv$boot[ ,2])
-

### 2018-09-21 phenotypic_responses.R

@@ -1,89 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-
-library(tidyverse)
-library(mgcv)
-library(gamm4) # for generalized additive mixed models #
-library(gsg)
-library(cowplot) # pretty default ggplots
-
-#################   BE CAREFUL IN HOW DATA IS SUBSETTED !!! ###################
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.factor(Plant_Position),
-         Gall_Number = as.factor(Gall_Number),
-         Treatment.focus = as.factor(Treatment.focus),
-         Treatment = as.factor(Treatment),
-         Genotype = as.factor(Genotype),
-         Gall_Letter = as.factor(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%          # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.Gall_Height_mm = as.numeric(scale(sqrt(Gall_Height_mm))),
-         sc.gall_individuals = as.numeric(scale(log(gall_individuals))),
-         sc.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots))))
-
-filter(gall_selection.df, pupa == 1) %>%
-  group_by(Treatment.focus) %>%
-  summarise_at(vars(sc_Gall_Height_mm, sc_gall_individuals, sc_Density_per_100_shoots), funs(mean,sd)) %>%
-  data.frame()
-
-
-filter(gall_selection.df, pupa == 1) %>%
-  ggplot(., aes(x=Gall_Height_mm, fill=Treatment.focus)) + geom_density(alpha=0.5)
-
-
-## EXPLORE WITH PHENOTYPES AS THE RESPONSE ----
-
-#test.control <- filter(gall_selection.df, Treatment.focus == "Control") %>%
-#  mutate(selection = "before") %>%
[…]

### 2018-09-21 revising_dataset.R

@@ -1,737 +1,0 @@
-## Notes ----
-# Restrict analysis to ground, tree, bag, mark, nomark, nobag galls only.
-# Focus: Want to determine whether the proportion of galls parasitized by Platygaster varies among willow genotypes and bagging treatment. If Platygaster parasitism is higher in bagged galls, then this is evidence of intraguild predation. This may also depend on willow genotype.
-# I don't expect there to be a difference between mark/nomark (paired on same willows), as this would indicate that marking the galls may have affected the foraging behavior of parasitoids. However, an effect could also mean that differences in phenology affect parasitism.
-# I do expect that Platygaster parasitism will be higher in bag vs. no-bag galls (paired on same willows) as well as higher in bag vs. mark/nomark galls. This will indicate evidence of intraguild predation.
-# I expect there to be a difference between no-bag and nomark galls, because no-bag galls were on trees with highly reduced gall densities. If previous work is correct, there may be higher ectoparasitism rates on these no-bag galls.
-# I don't expect a different in Platygaster parasitism between ground vs. tree galls. Note that I only bag and nomark galls have both ground and tree galls, therefore I should restrict my comparison to these ones.
-
-## source functions and other general details ----
-
-cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") # color-blind palette with grey
-
-## load libraries ----
-library(tidyverse)
-#library(lme4)
-library(cowplot) # for clean multi-panel plots
-
-## read in data frames ----
-
-# parasitism data
-vLG.df <- read.csv("VLGCollect2013.csv") %>% tbl_df
-
-# plant information
-plant.info <- read.csv("Willow Garden Positions.csv") %>%
-  tbl_df %>%
-  select(Row = Row.., Plant_Position = Plant.Position, Genotype, Gender) %>%
-  mutate(Plant_Position = as.character(Plant_Position))
-
-# upload gall density survey
-density <- read.csv("Density_Surveys_Gall_Parasitoid_Bagging_Experiment.csv", skip=1) %>%
-  tbl_df %>%
[…]

### 2018-09-21 temporary_morgue/Fontant_TED_index.R

@@ -1,0 +1,173 @@
+######################################################################################
+# Function to compute trait evenness index TED (Fontana et al. 2015)                 
+#                                                                                     
+# It requires R libraries 'geozoo', 'flexmix' and 'geometry'                                                              #                                                
+# input:                                                                             
+# - data frame 'traits': every row represents an individual, every column a trait    
+# - NA are not allowed                                                                         
+# - ADVICE: it is generally meaningful to standardise trait values (mean=0 and sd=1)
+######################################################################################
+
+
+
+#####################
+##    TED index    ##
+#####################
+# comparison between sample and an assemblage of equidistant points (with the same number of individuals)
+
+library(geozoo)
+library(flexmix)
+library(geometry)
+
+
+#############################
+# List of possible REFERENCES
+#############################
+
+# Open biggest sample
+# Change filename to name of file with maximum points
+control.survivors <- filter(gall_selection.df, Treatment.focus=="Control", gall_survival==1) %>% 
+  select(Plant_Position, sc.Gall_Height_mm, sc.gall_individuals, sc.Density_per_100_shoots)
+nrow(control.survivors)
+
+treatment.survivors <- filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion", gall_survival==1) %>% 
+  select(Plant_Position, sc.Gall_Height_mm, sc.gall_individuals, sc.Density_per_100_shoots)
+nrow(treatment.survivors)
+
+traits.max <- treatment.survivors[,-1] #read.csv("File_with_maximum_points.csv",sep=",",header=T)
+
+# Define maximum number of points (max1) and number of traits under consideration (dim1)
+# Alternatively, it is possible to manually define max1 and dim1!!
+max1 <- nrow(traits.max)
+dim1 <- ncol(traits.max)
+
+ref.matrix<-matrix(ncol=2,nrow=max1)
+if (dim1 == 1) {
+  i=0.9 } else { i=1.9 }
+n <- 0
+rows1<-0
[…]

### 2018-09-21 temporary_morgue/McPeek_perspective.R

@@ -1,0 +1,628 @@
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+library(tidyverse)
+library(cowplot) # pretty default ggplots
+#library(broom) # for tidying multiple linear models
+#library(mgcv) # generalized additive models
+#library(gsg) # calculating selection gradients
+library(visreg)
+library(viridis)
+
+mean_log <- function(x) mean(log(x))
+var_log <- function(x) var(log(x))
+
+## LOAD & MANAGE DATASET ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  # convert appropriate variables to characters instead of integers
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) 
+
+## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
+control_df <- gall_selection.df %>%
+  filter(Treatment.focus == "Control")
+
+treatment_df <- gall_selection.df %>%
+  filter(Treatment.focus == "Ectoparasitoid exclusion") 
+
+# summarize each data set at tree-level
+all_tree <- gall_selection.df %>%
+  # summarise first at gall level
+  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean)) %>%
+  
+  # then summarise at the plant level
+  group_by(Genotype, Treatment.focus, Plant_Position) %>%
+  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, mean_log, var_log, n())) %>%
+  ungroup() %>%
+  select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
+  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
[…]

### 2018-09-21 temporary_morgue/brms_gradients.R

@@ -1,0 +1,50 @@
+
+predict(control.major.brm, summary = T)[ ,"Estimate"]
+control.major.gam$gam$model
+
+## TEST FUNCTION FOR CALCULATING GRADIENTS WITH BRMS
+
+Wbar <- function(x, mod, phenotype,covariates) {
+  new.d <- as.data.frame(mod$data[,c(phenotype,covariates)])
+  names(new.d)<-c(phenotype,covariates)
+  new.d2<-new.d
+  for (i in 1:length(x)) {
+    new.d[,as.character(phenotype[i])] <-
+      new.d[,as.character(phenotype[i])]+x[i]
+  }
+  
+  p <- predict(
+    object=mod,
+    newdata=new.d,
+    #newdata.guaranteed=TRUE,
+    type="response"
+  )[ ,"Estimate"]
+  return(mean(p))
+}
+
+gradients <- function(m, phenotype, covariates) {
+  nTraits = length(phenotype)
+  first.derivatives <- grad(func=Wbar, x=rep(0, nTraits), 
+                            mod=m, phenotype=phenotype, covariates=covariates)
+  second.derivatives <- hessian(func=Wbar, x=rep(0, nTraits), 
+                                mod=m, phenotype=phenotype, covariates=covariates)
+  denom <- Wbar(x=rep(0,nTraits), mod=m, phenotype=phenotype,
+                covariates=covariates)
+  
+  beta <- first.derivatives  / denom
+  gamma <- second.derivatives / denom
+  
+  #if(standardized){
+  #  sds<-apply(as.matrix(mod$model[,phenotype]),2,sd)
+  #  beta<-beta*sds
+  #  gamma<-gamma*outer(sds,sds)
+  #}
+  return( list(
+    beta  = beta,
+    gamma = gamma
+  ))
+}
+library(numDeriv)
+gradients(m = control.major.brm, phenotype = "term1", covariates = NULL)
+
+# well the first round didn't work...

### 2018-09-21 temporary_morgue/exploratory_analyses.R

@@ -1,0 +1,421 @@
+
+## LOAD REQUIRED LIBRARIES ----
+library(tidyverse)
+library(cowplot)
+
+## LOAD DATASET ----
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  mutate(Plant_Position = as.factor(Plant_Position),
+         Gall_Number = as.factor(Gall_Number),
+         Treatment.focus = as.factor(Treatment.focus),
+         Treatment = as.factor(Treatment),
+         Location = as.factor(Location),
+         phenology = as.factor(phenology),
+         Genotype = as.factor(Genotype),
+         Gall_Letter = as.factor(Gall_Letter)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree") %>%
+  mutate(gall_survival = ifelse(pupa > 0, 1, 0),
+         platy_bin = ifelse(platy > 0, 1,0),
+         ectos_bin = ifelse(ectos > 0, 1,0))
+
+## EXPLORATORY PLOTS ----
+
+# Plot helpers
+binomial_smooth <- function(...) {
+  geom_smooth(method = "glm", method.args = list(family = "binomial"), ...)
+}
+
+# explored gam smoothers but they were way too curvy to be informative.
+#gam_smooth <- function(...) {
+#  geom_smooth(method = "gam", method.args = list(family = "binomial"), formula = y ~ s(x))
+#}
+
+viridis6 <- function() {
+  # colours taken from the viridis package
+  c("#440154", "#414487", "#2A788E", "#22A884", "#7AD151", "#FDE725")
+}
+
+dodge <- position_jitterdodge(jitter.width = 0.25, jitter.height = 0, dodge.width = 0.5)
+
+
+## EXPLORING EFFECT OF GENOTYPE ON GALL PHENOTYPES, SURVIVAL, AND PARASITOID RESPONSES ----
+
+# Gall Density
+gall_selection.df %>%
+  group_by(Treatment.focus, Genotype, Plant_Position) %>%
+  summarise_at(vars(Density_per_100_shoots), mean) %>%
+  ggplot(., aes(x = Genotype, y = Density_per_100_shoots, group = Treatment.focus, color = Treatment.focus)) + 
+  geom_jitter(alpha = 0.5, position = dodge) + 
[…]

### 2018-09-21 temporary_morgue/gam_lm_models.R

@@ -1,0 +1,240 @@
+
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+library(mgcv)
+library(gsg)
+library(tidyverse)
+library(cowplot) # pretty default ggplots
+
+## LOAD & MANAGE DATASET ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number),
+         Treatment.focus = as.character(Treatment.focus),
+         Treatment = as.character(Treatment),
+         Genotype = as.character(Genotype),
+         Gall_Letter = as.character(Gall_Letter)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
+         sc.Gall_Height_mm = as.numeric(scale(Gall_Height_mm)), 
+         sc.gall_individuals = as.numeric(scale(gall_individuals)), 
+         sc.Density_per_100_shoots = as.numeric(scale(Density_per_100_shoots))) 
+
+# aggregate data at gall-level
+
+gall_agg.df <- gall_selection.df %>% 
+  group_by(Treatment.focus, Gall_Number) %>%
+  summarise(prop_survival = mean(gall_survival), # effectively a proportion
+            gall_survival = sum(gall_survival),
+            gall_trials = n(),
+            max.Gall_Height_mm = max(Gall_Height_mm), # taking max to be consistent with prior work
+            gall_individuals = mean(gall_individuals), # all the same number, chose mean for convenience
+            Density_per_100_shoots = mean(Density_per_100_shoots)) # all the same, chose mean for convenience
+
+control_agg.df <- filter(gall_agg.df, Treatment.focus == "Control") %>%
+  mutate(sc.max.Gall_Height_mm = as.numeric(scale(max.Gall_Height_mm)),
+         sc.gall_individuals = as.numeric(scale(gall_individuals)),
[…]

### 2018-09-21 temporary_morgue/gsg_gradient_pvalue_errors.R

@@ -1,0 +1,43 @@
+## REPRODUCIBLE EXAMPLE OF POTENTIAL ERROR 
+## IN CALCULATION OF BOOT-STRAPPED P-VALUES
+## Matt Barbour, 1 Dec. 2017
+
+## FOLLOWING THE EXAMPLE IN GAM.GRADIENTS HELP FILE ----
+
+# simulated data (stabilizing selection)
+z<-rnorm(200,0,2)
+W<-rpois(200,exp(1-0.3*z^2))
+d<-as.data.frame(list(W=W,z=z))
+
+# characterize the fitness function
+library(mgcv)
+library(gsg)
+ff<-gam(W~s(z),family='poisson',data=d)
+
+# derive selection gradients
+gradients <- gam.gradients(mod=ff,phenotype="z",se.method='boot.para',standardized=FALSE)
+
+# I'm an idiot. The current method is correct.
+hist(gradients$boot[ ,1])
+abline(v = gradients$ests[1,1])
+
+## CURRENT METHOD ----
+# Bootstrapped estimates are compared to zero, not the observed estimate.
+
+# B-z: P = 0.934
+2*min(sum((gradients$boot[ ,1]>0)+0), sum((gradients$boot[ ,1]<0)+0))/length(gradients$boot[ ,2])
+gradients$ests$P.value[1]
+
+# G-z: P = 0.000
+2*min(sum((gradients$boot[ ,2]>0)+0), sum((gradients$boot[ ,2]<0)+0))/length(gradients$boot[ ,2])
+gradients$ests$P.value[2]
+
+## PROPOSED ALTERNATIVE ----
+# Bootstrapped estimates need to be compared to the observed estimate, not zero.
+
+# P = 0.746
+2*min(sum(gradients$boot[ ,1]>gradients$ests$estimates[1]), sum(gradients$boot[ ,1]<gradients$ests$estimates[1]))/length(gppr.size_indiv$boot[ ,1])
+
+# P = 0.574
+2*min(sum(gradients$boot[ ,2]>gradients$ests$estimates[2]), sum(gradients$boot[ ,2]<gradients$ests$estimates[2]))/length(gppr.size_indiv$boot[ ,2])
+

### 2018-09-21 temporary_morgue/gsg_models.R

@@ -1,0 +1,1140 @@
+
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+library(raster)
+library(tidyverse)
+library(FD)
+library(mgcv)
+library(gamm4) # for generalized additive mixed models #
+library(gsg)
+#library(lme4)
+library(cowplot) # pretty default ggplots
+#library(visreg) # quick visualizations of model outputs
+#library(brms)
+library(belg) # calculating configurational entropy of a 2D landscape
+
+#################   BE CAREFUL IN HOW DATA IS SUBSETTED !!! ###################
+
+## LOAD & MANAGE DATASET ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number),
+         Treatment.focus = as.character(Treatment.focus),
+         Treatment = as.character(Treatment),
+         Genotype = as.character(Genotype),
+         Gall_Letter = as.character(Gall_Letter)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
+         sc.Gall_Height_mm = as.numeric(scale(Gall_Height_mm)), # sqrt()
+         sc.gall_individuals = as.numeric(scale(gall_individuals)), # log()
+         sc.Density_per_100_shoots = as.numeric(scale(Density_per_100_shoots))) # sqrt()
+
+## GENERALIZED ADDITIVE MIXED MODELS + GENERALIZED PROJECTION PURSUIT REGRESSION ----
+
+gamm.model <- function(formula, data) {
+  gamm4(formula, data, 
+        random = ~(1|Genotype/Plant_Position/Gall_Number),
+        family = binomial(link = logit))
+}
+
+gamm.plot <- function(gamm.model, ...) {
+  plot(gamm.model$gam, seWithMean = T, shift = mean(predict(gamm.model$gam)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
+}
+
[…]

### 2018-09-21 temporary_morgue/hierarchical_models.R

@@ -1,0 +1,93 @@
+
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+library(tidyverse)
+library(brms)
+library(cowplot)
+library(bayesplot)
+
+options(mc.cores = parallel::detectCores()) # use all available cores
+
+## LOAD DATASET ----
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  mutate(Plant_Position = as.factor(Plant_Position),
+            Gall_Number = as.factor(Gall_Number),
+            Treatment.focus = as.factor(Treatment.focus),
+            Treatment = as.factor(Treatment),
+            Genotype = as.factor(Genotype),
+            Gall_Letter = as.factor(Gall_Letter)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%     # eliminate unknown sources of mortality
+  mutate(gall_survival = ifelse(pupa > 0, 1, 0))
+
+## EXPLORE DISTRIBUTIONS OF PHENOTYPIC TRAITS.
+# important implications for selection gradient analysis
+
+trans.ind <- log(gall_selection.df$gall_individuals) # closes transformation to normality
+hist(trans.ind)
+qqnorm(trans.ind)
+qqline(trans.ind, col = "red")
+shapiro.test(trans.ind)
+
+trans.size <- gall_selection.df$Gall_Height_mm # no transformation needed
+hist(trans.size)
+qqnorm(trans.size)
+qqline(trans.size, col = "red") 
+shapiro.test(trans.size) # doesn't pass the test though
+
+trans.density <- sqrt(gall_selection.df$Density_per_100_shoots) # sqrt is the closest
+hist(trans.density)
+qqnorm(trans.density)
+qqline(trans.density, col = "red") 
+shapiro.test(trans.density)
+
+gall_selection.df <- mutate(gall_selection.df,
+                            sc.size = scale(Gall_Height_mm),
+                            sc.log.ind = scale(log(gall_individuals)),
+                            sc.sqrt.density = scale(sqrt(Density_per_100_shoots)))
+
+## SPECIFYING PRIORS ----
+
+uninf_priors <- c(set_prior("normal(0,1)", class = "b"), set_prior("normal(0,2)", class = "sd")) # generic, weakly informative priors
+
+## BAYESIAN MODEL ---- 
+
[…]

### 2018-09-21 temporary_morgue/morgue.R

@@ -1,0 +1,753 @@
+
+
+## EXPLORE DISTRIBUTIONS ----
+ggplot(gall_selection.df, aes(x = Gall_Height_mm)) + geom_histogram() + scale_x_sqrt()
+summary(gall_selection.df$Gall_Height_mm)
+summary(sqrt(gall_selection.df$Gall_Height_mm)) # most symmetric distribution around median and mean.
+summary(log(gall_selection.df$Gall_Height_mm))
+
+gall_selection.df %>%
+  distinct(Genotype, Plant_Position, Gall_Number, gall_individuals) %>% # avoids pseudo replication
+  ggplot(., aes(x = gall_individuals)) + geom_histogram() + scale_x_log10()
+summary(gall_selection.df$gall_individuals)
+summary(sqrt(gall_selection.df$gall_individuals))
+summary(log(gall_selection.df$gall_individuals)) # most symmetric distribution around median and mean.
+
+gall_selection.df %>%
+  distinct(Genotype, Plant_Position, Density_per_100_shoots) %>% # avoids pseudo replication
+  ggplot(., aes(x = sqrt(Density_per_100_shoots))) + geom_histogram() # more normal, except for low values
+summary(gall_selection.df$Density_per_100_shoots)
+summary(sqrt(gall_selection.df$Density_per_100_shoots)) # most symmetric distribution around median and mean
+summary(log(gall_selection.df$Density_per_100_shoots+1))
+
+gall_selection.df <- mutate(gall_selection.df,
+                            sc.sqrt.size = scale(sqrt(Gall_Height_mm)),
+                            sc.log.indiv = scale(log(gall_individuals)),
+                            sc.sqrt.density = scale(sqrt(Density_per_100_shoots)))
+
+# correlations among predictors are virtually absent, except for between gall size and gall density
+car::scatterplotMatrix(select(gall_selection.df, sc.sqrt.size, sc.log.indiv, sc.sqrt.density)) # closer correspondence between loess and linear fits
[…]

### 2018-09-21 temporary_morgue/phenotypic_responses.R

@@ -1,0 +1,89 @@
+
+## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
+
+library(tidyverse)
+library(mgcv)
+library(gamm4) # for generalized additive mixed models #
+library(gsg)
+library(cowplot) # pretty default ggplots
+
+#################   BE CAREFUL IN HOW DATA IS SUBSETTED !!! ###################
+
+## LOAD & MANAGE DATASET ----
+
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+  mutate(Plant_Position = as.factor(Plant_Position),
+         Gall_Number = as.factor(Gall_Number),
+         Treatment.focus = as.factor(Treatment.focus),
+         Treatment = as.factor(Treatment),
+         Genotype = as.factor(Genotype),
+         Gall_Letter = as.factor(Gall_Letter)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+  
+  # subset data for analysis
+  filter(phenology == "early", Location == "tree",
+         platy > 0 | ectos > 0 | pupa > 0) %>%          # eliminate unknown sources of mortality
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
+         sc.Gall_Height_mm = as.numeric(scale(sqrt(Gall_Height_mm))),
+         sc.gall_individuals = as.numeric(scale(log(gall_individuals))),
+         sc.Density_per_100_shoots = as.numeric(scale(sqrt(Density_per_100_shoots))))
+
+filter(gall_selection.df, pupa == 1) %>%
+  group_by(Treatment.focus) %>%
+  summarise_at(vars(sc_Gall_Height_mm, sc_gall_individuals, sc_Density_per_100_shoots), funs(mean,sd)) %>%
+  data.frame()
+
+
+filter(gall_selection.df, pupa == 1) %>%
+  ggplot(., aes(x=Gall_Height_mm, fill=Treatment.focus)) + geom_density(alpha=0.5)
+
+
+## EXPLORE WITH PHENOTYPES AS THE RESPONSE ----
+
+#test.control <- filter(gall_selection.df, Treatment.focus == "Control") %>%
+#  mutate(selection = "before") %>%
[…]

### 2018-09-21 temporary_morgue/revising_dataset.R

@@ -1,0 +1,737 @@
+## Notes ----
+# Restrict analysis to ground, tree, bag, mark, nomark, nobag galls only.
+# Focus: Want to determine whether the proportion of galls parasitized by Platygaster varies among willow genotypes and bagging treatment. If Platygaster parasitism is higher in bagged galls, then this is evidence of intraguild predation. This may also depend on willow genotype.
+# I don't expect there to be a difference between mark/nomark (paired on same willows), as this would indicate that marking the galls may have affected the foraging behavior of parasitoids. However, an effect could also mean that differences in phenology affect parasitism.
+# I do expect that Platygaster parasitism will be higher in bag vs. no-bag galls (paired on same willows) as well as higher in bag vs. mark/nomark galls. This will indicate evidence of intraguild predation.
+# I expect there to be a difference between no-bag and nomark galls, because no-bag galls were on trees with highly reduced gall densities. If previous work is correct, there may be higher ectoparasitism rates on these no-bag galls.
+# I don't expect a different in Platygaster parasitism between ground vs. tree galls. Note that I only bag and nomark galls have both ground and tree galls, therefore I should restrict my comparison to these ones.
+
+## source functions and other general details ----
+
+cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7") # color-blind palette with grey
+
+## load libraries ----
+library(tidyverse)
+#library(lme4)
+library(cowplot) # for clean multi-panel plots
+
+## read in data frames ----
+
+# parasitism data
+vLG.df <- read.csv("VLGCollect2013.csv") %>% tbl_df
+
+# plant information
+plant.info <- read.csv("Willow Garden Positions.csv") %>%
+  tbl_df %>%
+  select(Row = Row.., Plant_Position = Plant.Position, Genotype, Gender) %>%
+  mutate(Plant_Position = as.character(Plant_Position))
+
+# upload gall density survey
+density <- read.csv("Density_Surveys_Gall_Parasitoid_Bagging_Experiment.csv", skip=1) %>%
+  tbl_df %>%
[…]

### 2018-09-21 temporary_morgue/specifying_priors.R

@@ -1,0 +1,143 @@
+
+library(RCurl)
+library(tidyverse)
+
+gall_network_2012 <-read.csv(text=getURL("https://raw.githubusercontent.com/mabarbour/Genotype_Networks/master/raw_data_management/data/gall_network_data.csv"), header = T)
+
+vLG_network <- gall_network_2012 %>%
+  filter(gall.sp == "vLG") %>%
+  distinct(Genotype, plant.position, gall.id.nest, g.height, shootEst.all, shootEst.no18, gall_contents, value) %>%
+  spread(gall_contents, value, fill = 0)
+
+vLG_network$total <- rowSums(select(vLG_network, Eulo.fem:vLG.pupa))
+vLG_network$ectos <- rowSums(select(vLG_network, Eulo.fem, Eulo.mal, Mesopol, Ptero.2, Tory.fem, Tory.mal))
+
+vLG_counts <- vLG_network %>%
+  group_by(Genotype, plant.position) %>%
+  summarise_at(vars(total), sum) %>%
+  rename(vLG_count = total)
+
+vLG_network <- left_join(vLG_network, vLG_counts) %>%
+  mutate(Density_per_100_shoots = vLG_count/shootEst.all*100)
+
+## EXPLORATORY PLOTS ----
+density.cut.2012 <- quantile(vLG_network$Density_per_100_shoots, probs = c(0,0.33,0.66,1), include.lowest = TRUE)
+vLG_network %>%
+  mutate(density.cut = cut(Density_per_100_shoots, density.cut.2012)) %>%
+  ggplot(., aes(x = g.height, y = vLG.pupa/total, weight = total)) +
+  geom_point(alpha = 0.5, aes(size = total)) +
+  binomial_smooth(formula = y ~ x) + facet_wrap(~density.cut)
+  
+
+## CONTINUED ----
+
+hist(vLG_network$g.height)
+hist(sqrt(vLG_network$g.height))
+
+hist(vLG_network$Density_per_100_shoots)
+hist(sqrt(vLG_network$Density_per_100_shoots))
+
+vLG_network <- mutate(vLG_network,
+                      sc.sqrt.size = (sqrt(g.height) - mean(sqrt(g.height), na.rm = T))/sd(sqrt(g.height), na.rm = T),
+                      sc.size = (g.height - mean(g.height, na.rm = T))/sd(g.height, na.rm = T),
[…]

### 2018-09-21 manuscript/manuscript.tex
added skeleton of text and tables to the manuscript

@@
 
-The quick red fox jumps over the lazy brown dog.
-Furthermore, the quick brown fox jumps over the lazy red dog.
-In addition, the quick R\"{u}ppell's fox (\textit{Vulpes rueppellii}) jumps over the lazy golden retriever.
+The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
+The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
+Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$).
+In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
+For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
+density-dependence, CITE Foundational and current work).
+In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
+Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
+
+Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
+Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
+This has provided an effective framework for predicting how changes in the biotic environment (e.g.
+density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
+At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
+However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
+Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
+Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
+
+Here, we integrate species-interaction networks and the fitness landscape to empirically test how changes in the biotic environment -- network of species interactions -- affect the dynamics of natural selection.
+Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (*Iteomyia salicisverruca*)(Fig.
+1).
+The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006).
+These galls provide protection from generalist predators (e.g.
+ants, spiders), thus the network of interacting parasitoids provides a realistic representation of the biotic environment this insect herbivore is experiencing.
+Therefore, our manipulation of parasitoid diversity alters the diversity of interactions, or food-web complexity, that this insect herbivore experiences.
+
+Changes in food-web complexity could influence a resource population's fitness landscape in at least two ways.
+First, if a more diverse community of consumers is more effective at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population.
+A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018).
+On the other hand, if consumers impose different selection pressures on resource traits, then more diverse communities could dampen the strength of selection acting on a given trait.
+This is because a greater diversity in selection pressures is equivalent to greater uncertainty in the selective environment.
+Thus, a more diverse consumer community may relax the net selection pressures acting on resource traits.
+Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the fitness landscape of a resource population.
 
@@
 
-Lorem ipsum (\citealt{Xiao2015}) ut velit mauris, egestas sed, gravida nec, ornare ut, mi.
-Aenean ut orci vel massa suscipit pulvinar.
-Nulla sollicitudin.
-Fusce varius, ligula non tempus aliquam, nunc turpis ullamcorper nibh, in tempus sapien eros vitae ligula.
+\subsection*{Study Site}
 
-\subsection*{The quickness of the fox}
+We conducted our study within a four-year old common garden of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
+This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
+Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
+Willows in our garden begin flowering in February and reach their peak growth in early August.
+During this study, willows had reached 5 - 9m in height.
+Further details on the genotyping and planting of the common garden are available in @Barbour2015.
 
-Lorem ipsum nulla facilisi, despite the findings of \citet{LemKapEx07}.
-Etiam semper, orci sit amet facilisis interdum, tellus nunc consequat erat, quis viverra nisi diam ut metus.
-Pellentesque cursus, sapien malesuada euismod iaculis, mauris purus interdum diam, vel vestibulum justo enim vitae tellus.
-Nunc interdum lorem sit amet diam volutpat tristique.
-Quisque pulvinar ac metus commodo lacinia (\citealt{Ing11,Xiao2015}).
+\subsection*{Food-web Manipulation}
 
-\subsubsection*{Third-order heading}
+We setup our food-web manipulation across 128 plants soon after galls began developing on *S. hookeriana* in early June of 2013. 
+These 128 plants came from eight different plant genotypes, spanning the range of trait variation observed in this willow population (@Barbour2015). 
+On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
+This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
+On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack *Iteomyia*. 
+Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
+Our food-web manipulation altered the average number of trophic interactions that *Iteomyia* was exposed to from BLANK on control plants to BLANK on treatment plants. 
+Thus, we refer to galls on control plants as being exposed to a 'complex' food web, whereas galls on treatment plants were exposed to a 'simple' food web.
+In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and <!-- allowed them to complete development--> kept them in the lab for 4 months at room temperature.
+We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
+Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (*Platygaster* sp.), or was parasitized by a larval parasitoid.
+For the food-web treatment that excluded parasitoids, we further restricted our data by removing any instances of parasitism by a larval parasitoid.
+This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
+Together, we had survival estimates for 1,306 larva from 607 galls, 111 plants, and 8 plant genotypes.
 
-Usually two or three levels of heading will be all you need. Journal style even permits a fourth level in case you need it.
+\subsection*{Measuring Gall Traits}
 
-\paragraph*{Fourth-order heading}
-The quick red fox jumps over the lazy brown dog in this paragraph as well.
+We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018). 
+First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). 
+Our previous work has shown that a larger gall diameter provides a refuge for larva from parasitoid attack (@Barbour2016).
+<!-- Consider whether it is important to make the distinction that diameter was measured at the multi-chambered gall level in previous work -->
+Second, we measured the clutch size of adult female midges by counting the number of chambers in each gall (@Weis1983). 
+All larva collected from the same multi-chambered gall were scored with the same clutch size. 
+Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant in an independent survey.
+Specifically, we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
+We then converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
+All larva collected from the same plant were scored with the same female preference.
+The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010); however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference (@Singer1986).
+Fortunately, a couple of features of our study system suggest that larval density on a plant may be a good proxy for female preference.
+For example, since our data comes from a randomized placement of willow genotypes in a common garden, there is no consistent bias in which willow genotypes that females are exposed to while searching for oviposition sites.
+Also, egg predation is a minor source of mortality for galling insects in general (@Hawkins1997), thus we do not expect any prior egg predation to bias our estimates of observed larval densities.
 
-\subsection*{The redness of the fox}
+\subsection*{Quantifying the Fitness Landscape}
 
-As \citet{Xiao2015} argued, phasellus porttitor eros et ante condimentum, eget facilisis orci condimentum.
-Nulla facilisi.
-Proin placerat elit blandit, euismod dolor nec, dapibus diam.
-Mauris posuere malesuada lacus, at elementum lacus auctor eu (fig~\ref{Fig:Jumps}A).
+To characterize the shape of the fitness landscape in simple and complex food webs, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
+We used a binomial error distribution (logit link function) since larval survival (0 or 1) was our response variable and measure of fitness.
+We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
+To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
+Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
+setting them to zero) to estimate selection gradients.
+Also, the fitness landscape assumes that traits distributions are multivariate normal.
+To better meet this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
+We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
+We used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95\% confidence intervals (@Bolker2009).
+We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
+Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value as this contains the majority of the trait distribution that selection is acting on.
+
+Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits.
+Any influence on trait expression would bias selection gradients acting on those traits.
+In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
+Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
+To estimate this bias, we subset our data to only include galls where there was variation in larval survival (1 > survival > 0) within the same gall.
+We then calculated "apparent" selection differentials for each gall by comparing the average chamber diameter of all larva (before "selection") to the average chamber diameter of surviving larva and analyzed separate one-sample t-tests for each food-web treatment.
+This analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
+In general, we found that our estimates of directional selection on chamber diameter were positively biased (Appendix).
+In other words, our analyses were overestimating the magnitude of selection acting on gall diameter.
+Therefore, we adjusted our estimates of directional selection on chamber diameter ($\beta_{diam}$) by subtracting the biased selection differentials.
+Note that selection gradients and selection differentials for chamber diameter were virtually the same (Appendix).
+
+\subsection*{Quantifying Selective Constraints}
+
+The strength and pattern of selective constraints can be measured as the slope and curvature of the fitness landscape (Arnold 1992).
+
+We can translate selection surfaces of individuals to the fitness landscape of a population
+
+To characterize the net effects of food-web complexity on the slope and curvature of *Iteomyia*'s fitness landscape, we took advantage of existing theory that links selection surfaces of individuals to the fitness landscape of the population (Phillips & Arnold 1998, Arnold 2003).
+Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
+
+$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
+whereas the curvature of the fitness landscape is a function of the directional, nonlinear, and correlational selection gradients: 
+$$\text{Curvature} = \gamma - \beta \beta^T$$
+where \gamma represents the matrix of nonlinear and correlational selection gradients:
+$$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
+
+Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
+Assuming that there is additive genetic variance and covariance between these traits under selection, then the slope and curvature of the fitness landscape give insight to how the population's mean trait value will change in the next generation as well as how additive genetic variance and covariance changes within a generation.
+
+While making quantitative predictions about trait evolution requires knowledge of the additive genetic variance and covariance of these traits, the slope and curvature of the fitness landscape still give qualitative insight to the evolutionary trajectory of a population.
+
+If we assume that there is additive genetic variance and covariance between these traits, then the matrix describing the curvature of the fitness landscape gives qualitative insight to the selective constraints acting on the population.
+For example, the diagonal of the curvature matrix dictates (qualitatively) whether the additive genetic variance in each trait will increase ($+$), decrease ($-$), or stay the same ($0$).
+Similarly, the off-diagonal of the curvature matrix dictates whether selection favors trait integration (positive covariance), a tradeoff (negative covariance), or no change in genetic covariance.
+In other words, we can get qualitative insight to how food-web complexity influences constraints on the fitness landscape by counting the number of negative sign values along the diagnoal (which imply a decrease in additive genetic variance) and the number of positive or negative signs along the off diagonal (which imply changes in additive genetic covariance that lead to either trait integration or tradeoffs).
+
+All analyses and visualizations were conducted in R (@R2018).
+
+I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
 
@@
 
-Lorem ipsum dolor sit amet.
-Aenean pulvinar malesuada commodo (see \citealt{DavisEtAl2011}; table~\ref{Table:Okapi}).
-Sed aliquet mauris odio, in tristique dui egestas a.
-Etiam eu malesuada quam.
-Suspendisse tincidunt eu erat sit amet vulputate.
-Duis at arcu et nisl dictum mattis.
-Maecenas vel cursus ante.
-Cras eleifend elit nec velit sollicitudin fermentum in ac mauris.
-Pellentesque rutrum magna vel elit maximus hendrerit.
-
-\subsection*{The height of the jump}
-
-Aenean eu pellentesque quam (fig.~\ref{Fig:OkapiHorn}).
-Nam pellentesque augue eu finibus lacinia.
-Nullam nec justo vitae odio imperdiet rhoncus vitae vitae quam.
-Pellentesque porttitor metus et lectus ornare, ac cursus urna efficitur (fig~\ref{Fig:Jumps}B).
-
-\subsection*{The laziness of the dog}
-
-Sed sit amet pharetra nisi (video~\ref{VideoExample}, fig.~\ref{Fig:AnotherFigure}).
-Praesent quis dolor in dolor molestie cursus et ac nisi.
-Vestibulum ante purus, semper eget est vitae, vehicula ornare nisl.
-Morbi efficitur euismod enim, nec feugiat tellus cursus eget.
-Donec mauris nibh, volutpat vehicula viverra at, iaculis congue sem.
-Praesent eget erat rhoncus erat sollicitudin volutpat.
-
-If you have deposited data to Dryad, you should cite them somewhere in the main text (usually in the Methods or Results sections).
-A sentence like the following will do.
-All data are available in the Dryad Digital Repository (\citealt{CookEtAl2015}).
-
 \section*{Discussion}
 
-Nam pulvinar lorem at lorem ultrices, vel accumsan massa feugiat (\citealt{Ing11}).
-Proin tristique velit eget lacus iaculis, in pellentesque nulla varius.
-Phasellus sodales est odio, eu pulvinar magna pellentesque eu.
-Sed ut lobortis eros.
-Aliquam eget metus turpis.
-Sed et convallis lectus, id tincidunt enim.
-In porta nibh ut lacus feugiat, non consequat orci rhoncus.
-Morbi blandit at augue nec tempor.
-Sed fringilla ipsum ut justo viverra, ut euismod nisi gravida.
-
-Curabitur non posuere augue, id suscipit orci.
-Nunc luctus accumsan aliquam.
-Cras egestas turpis vitae nisl vulputate interdum.
-Donec pellentesque libero egestas tortor pharetra laoreet.
-Phasellus facilisis auctor ligula, eu sollicitudin mi sagittis non.
-
 \section*{Conclusion}
-
-Duis pharetra enim at libero cursus, eu commodo mi vestibulum.
-Nullam eget velit nec lectus viverra sodales.
-Suspendisse egestas, eros at dictum tincidunt, mi orci laoreet libero, eget rutrum sapien arcu blandit odio.
 
@@
 \section*{Acknowledgments}
-
-OEC would like to thank the world. GHC is much indebted to the solar system. AQE was supported by a generous grant from the Milky Way (MW/01010/987654).
 
@@
 \begin{table}[h]
-\caption{Animals in various cities with equations}
-\label{Table:Okapi}
+\caption{Table for Alpha Regression coefficients}
+\label{Table:Alphas}
 \centering
-\begin{tabular}{llc}\hline
-Animal    & City         & Equation \\ \hline
-Dog       & Springfield  & $x+y=z$ \\
-Fox       & Indianapolis & $2x+2y=2z$ \\
-Okapi$^a$ & Chicago      & $x-y<z$ \\
-Badger    & Madison      & $x+2y>z$ \\ \hline
+\begin{tabular}{lcc}
+                                                                           \\ \hline
+                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
+\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
+$Diam$                 &  [ - ] &  [ - ] \\
+$Clutch$               &  [ - ] &  [ - ] \\
+$Pref$                 &  [ - ] &  [ - ] \\
+$Diam^2$               &  [ - ] &  [ - ] \\
+$Clutch^2$             &  [ - ] &  [ - ] \\
+$Pref^2$               &  [ - ] &  [ - ] \\
+$Diam:Clutch$          &  [ - ] &  [ - ] \\
+$Diam:Pref$            &  [ - ] &  [ - ] \\
+$Clutch:Pref$          &  [ - ] &  [ - ]              \\ \hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Table titles should be short.
+Further details should go in a `notes' area after the tabular environment, like this.
+$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
+\end{table}
+
+\newpage{}
+
+\begin{table}[h]
+\caption{Table for \textit{Iteomyia} Selection Gradients}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lcc}
+                                                                                  \\ \hline
+                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
+\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
+$\beta_{Diam}$                    &  [ - ] &  [ - ] \\
+$\beta_{Clutch}$                  &  [ - ] &  [ - ] \\
+$\beta_{Pref}$                    &  [ - ] &  [ - ] \\
+$\gamma_{Diam,Diam}$              &  [ - ] &  [ - ] \\
+$\gamma_{Clutch,Clutch}$          &  [ - ] &  [ - ] \\
+$\gamma_{Pref,Pref}$              &  [ - ] &  [ - ] \\
+$\gamma_{Diam,Clutch}$            &  [ - ] &  [ - ] \\
+$\gamma_{Diam,Pref}$              &  [ - ] &  [ - ] \\
+$\gamma_{Clutch,Pref}$            &  [ - ] &  [ - ]            \\ \hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Table titles should be short.
+Further details should go in a `notes' area after the tabular environment, like this.
+$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
+\end{table}
+
+\newpage{}
+
+\begin{table}[h]
+\caption{Table for bias}
+\label{Table:Bias}
+\centering
+\begin{tabular}{lc}
+                                                                  \\ \hline
+\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
+Complex (All)                 &  [ - ] \\
+Complex (Larval guild)        &  [ - ] \\
+Simple (\textit{Platygaster}) &  [ - ]                  \\ \hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Table titles should be short.
+Further details should go in a `notes' area after the tabular environment, like this.
+$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
+\end{table}
+
+\newpage{}
+
+\begin{table}[h]
+\caption{Table for \textit{Platygaster} Selection Differentials}
+\label{Table:PlatySelection}
+\centering
+\begin{tabular}{lc}
+                                                                  \\ \hline
+\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
+$s_{Diam}$                      &  [ - ] \\
+$s_{Clutch}$                    &  [ - ] \\
+$s_{Pref}$                      &  [ - ] \\ 
+$s_{Diam,Diam}$                 &  [ - ] \\
+$s_{Clutch,Clutch}$             &  [ - ] \\
+$s_{Pref,Pref}$                 &  [ - ]                \\ \hline
 \end{tabular}

### 2018-09-25 analyses/reproduce_analyses.Rmd
lots of progress in analysis

--- 2018-09-21 temporary_morgue/ms_complexity_selection.Rmd
@@
 ---
-title: Phenotypic evolution is less constrained in complex food webs or Food-web complexity alters the fitness landscape of an insect herbivore 
-author:
-  - name: Matthew A. Barbour
-    email: matthew.barbour@ieu.uzh.ch
-    affiliation: a,b
-    footnote: Corresponding Author
-  - name: Christopher J. Greyson-Gaito
-    affiliation: a,c
-  - name: Arezoo Sootodeh
-    affiliation: a
-  - name: Brendan Locke
-    affiliation: d
-  - name: Jordi Bascompte
-    affiliation: b
-address:
-  - code: a
-    address: University of British Columbia, Department of Zoology, 6270 University Blvd., Vancouver, BC, V6T 1Z4, Canada
-  - code: b
-    address: University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, Zurich, 8057, Switzerland
-  - code: c
-    address: University of Guelph, Department of Integrative Biology, 50 Stone Rd. East, Guelph, ONT, N1G 2W1, Canada
-  - code: d
-    address: Humboldt State University, Department of Biological Sciences, 1 Harpst St., Arcata, CA, 95521, USA
-abstract: "Species-interaction networks provide a mechanistic link between community and population ecology, as they describe who interacts with whom in a community.
-Similarly, fitness landscapes provide a mechanistic link between population and evolutionary ecology, as they describe the influence of natural selection on phenotypic variation.
-It remains unclear, however, how the network structure of species interactions shapes the fitness landscape.
-Understanding this relationship is likely key for developing a predictive ecology across scales of biological organization.
-To examine the relationship between network structure and the fitness landscape, we conducted a field experiment that manipulated the network of trophic interactions (simple vs.
-complex) influencing the fitness of an insect herbivore.
-We then quantified the fitness landscape of herbivores in each treatment by measuring herbivore survival as a function of multiple phenotypic traits.
-We found that more traits were under selection in the simple vs.
-complex trophic network.
-This occurred because different natural enemies impose different selection pressures on herbivore traits, thereby minimizing relative fitness differences among herbivore phenotypes in the complex network.
-Our work suggests that more complex trophic networks allow phenotypic variation to persist, which could facilitate subsequent adaptive evolution of populations to environmental change."
-
-bibliography: mybibfile.bib
-output: rticles::elsevier_article
+title: "Reproducing Analyses for Phenotypic evolution is less constrained in complex
+  food webs"
+author: "Matthew A. Barbour"
+date: "`r Sys.Date()`"
+output:
+  prettydoc::html_pretty:
+    theme: architect
+    highlight: github
 ---
@@
 library(latex2exp)  # using Latex notation for axes labels
+library(kableExtra)
+library(stringr)
 
@@
 
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
+gall_selection.df <- read_csv("../data/gall_selection_data.csv") %>%
   # convert appropriate variables to characters instead of integers
@@
          sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
-         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots)))) 
-dim(gall_selection.df)
-
-table(gall_selection.df$Treatment.focus, gall_selection.df$ectos)
-
-## Create separate datasets for quantifying selection gradients ----
-#control_df <- gall_selection.df %>%
-#  filter(Treatment.focus == "Control") #%>%
-  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
-  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
-  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
-  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
-  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
-#dim(control_df)
-
-#treatment_df <- gall_selection.df %>%
-#  filter(Treatment.focus == "Ectoparasitoid exclusion", ectos < 1) #%>%  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
-#dim(treatment_df)
-  #mutate(sc.gall_size = as.numeric(scale(Gall_Height_mm)), 
-  #       sc.clutch_size = as.numeric(scale(gall_individuals)), 
-  #       sc.log.clutch_size = as.numeric(scale(log(gall_individuals))), 
-  #       sc.female_preference = as.numeric(scale(Density_per_100_shoots)),
-  #       sc.log1p.female_preference = as.numeric(scale(log1p(Density_per_100_shoots))))
-
-#mean(filter(gall_selection.df, Treatment.focus == "Ectoparasitoid exclusion")$ectos) # less than 3% of larva were parasitized by an ectoparasitoid in the exclusion experiment.
+         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots))),
+         sc.DiamPoly1 = poly(sc.Diam,2)[,1],
+         sc.DiamPoly2 = poly(sc.Diam,2)[,2],
+         sc.log.ClutchPoly1 = poly(sc.log.Clutch,2)[,1],
+         sc.log.ClutchPoly2 = poly(sc.log.Clutch,2)[,2],
+         sc.log1p.PrefPoly1 = poly(sc.log1p.Pref,2)[,1],
+         sc.log1p.PrefPoly2 = poly(sc.log1p.Pref,2)[,2])
 
 ## Custom functions to avoid repetitive code ----
-
-## Test for overdispersion
-overdisp_fun <- function(model) {
-  ## number of variance parameters in 
-  ##   an n-by-n variance-covariance matrix
-  vpars <- function(m) {
-    nrow(m)*(nrow(m)+1)/2
-  }
-  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
-  rdf <- nrow(model.frame(model))-model.df
-  rp <- residuals(model,type="pearson")
-  Pearson.chisq <- sum(rp^2)
-  prat <- Pearson.chisq/rdf
-  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
-  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
-}
-
-## Test for multicollinearity (from: https://jonlefcheck.net/2012/12/28/dealing-with-multicollinearity-using-variance-inflation-factors/)
-vif.mer <- function (fit) {
-    ## adapted from rms::vif
-
-    v <- vcov(fit)
-    nam <- names(fixef(fit))
-
-    ## exclude intercepts
-    ns <- sum(1 * (nam == "Intercept" | nam == "(Intercept)"))
-    if (ns > 0) {
-        v <- v[-(1:ns), -(1:ns), drop = FALSE]
-        nam <- nam[-(1:ns)]
-    }
-
-    d <- diag(v)^0.5
-    v <- diag(solve(v/(d %o% d)))
-    names(v) <- nam
-    v
-}
 
@@
 inverse_logit <- function(x) exp(x)/(1+exp(x))
-
-## Calculate selection gradients following method of Janzen and Stern 1998, Evolution
-Beta_avg_grad <- function(.) {
-  mean_fitness <- mean(predict(., type = "response")) 
-  brackets <- predict(., type = "response") * (1 - predict(., type="response"))
-  mean(brackets) * fixef(.)[-1] / mean_fitness ## need to divide by mean fitness to put on relative fitness scale.
-}
-
-## Calculate intensity/opportunity for selection
-intensity_of_selection <- function(.) {
-  mean_fitness <- mean(predict(., type = "response")) # inverse_logit(fixef(update(., .~. -sc.gall_size -sc.clutch_size -sc.female_preference)))
-  relative_fitness <- predict(., type = "response") / mean_fitness 
-  var(relative_fitness)
-}
 
@@
 ## Bootstrap fitness estimates
-bootstrap_fitness <- function(logistic_model, fixed_effects, newdata, bootstraps, intervals=c(0.025,0.975)){
-  model_matrix <- model.matrix(formula(fixed_effects), newdata)
+bootstrap_fitness <- function(logistic_model, #fixed_effects, 
+                              newdata, bootstraps, intervals=c(0.025,0.975)){
+  #model_matrix <- model.matrix(formula(fixed_effects), newdata)
 
   # Absolute fitness
-  get_absolute_fitness <- function(.) inverse_logit(model_matrix %*% fixef(.))
+  get_absolute_fitness <- function(.) predict(., newdata=newdata, type="response", re.form=~0) #inverse_logit(model_matrix %*% fixef(.))
 
@@
 ## Number of bootstrap replicates
-n_boots_analysis <- 30
+n_boots_analysis <- 1000
 n_boots_plots <- 100
 
-```
-
-Introduction
-============
-
-The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
-The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
-Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$.
-In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
-For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
-density-dependence, CITE Foundational and current work).
-In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
-Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
-
-Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
-Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
-This has provided an effective framework for predicting how changes in the biotic environment (e.g.
-density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
-At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
-However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
-Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
-Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
-
-Here, we integrate species-interaction networks and the fitness landscape to empirically test how changes in the biotic environment -- network of species interactions -- affect the dynamics of natural selection.
-Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (*Iteomyia salicisverruca*)(Fig.
-1).
-The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006).
-These galls provide protection from generalist predators (e.g.
-ants, spiders), thus the network of interacting parasitoids provides a realistic representation of the biotic environment this insect herbivore is experiencing.
-Therefore, our manipulation of parasitoid diversity alters the diversity of interactions, or food-web complexity, that this insect herbivore experiences.
-
-Changes in food-web complexity could influence a resource population's fitness landscape in at least two ways.
-First, if a more diverse community of consumers is more effective at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population.
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018).
-On the other hand, if consumers impose different selection pressures on resource traits, then more diverse communities could dampen the strength of selection acting on a given trait.
-This is because a greater diversity in selection pressures is equivalent to greater uncertainty in the selective environment.
-Thus, a more diverse consumer community may relax the net selection pressures acting on resource traits.
-Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the fitness landscape of a resource population.
-
-Materials & Methods
-===================
-
-## Study Site
-
-We conducted our study within a four-year old common garden of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
-This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 5 - 9m in height.
-Further details on the genotyping and planting of the common garden are available in @Barbour2015.
-
-## Food-Web Manipulation
-
-We setup our food-web manipulation across 128 plants soon after galls began developing on *S. hookeriana* in early June of 2013. 
-These 128 plants came from eight different plant genotypes, spanning the range of trait variation observed in this willow population (@Barbour2015). 
-On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
-This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
-On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack *Iteomyia*. 
-Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
-Our food-web manipulation altered the average number of trophic interactions that *Iteomyia* was exposed to from BLANK on control plants to BLANK on treatment plants. 
-Thus, we refer to galls on control plants as being exposed to a 'complex' food web, whereas galls on treatment plants were exposed to a 'simple' food web.
-In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and <!-- allowed them to complete development--> kept them in the lab for 4 months at room temperature.
-We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (*Platygaster* sp.), or was parasitized by a larval parasitoid.
-For the food-web treatment that excluded parasitoids, we further restricted our data by removing any instances of parasitism by a larval parasitoid.
-This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
-Together, we had survival estimates for 1,306 larva from 607 galls, 111 plants, and 8 plant genotypes.
-
-## Measuring Gall Traits
-
-We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018). 
-First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). 
-Our previous work has shown that a larger gall diameter provides a refuge for larva from parasitoid attack (@Barbour2016).
-<!-- Consider whether it is important to make the distinction that diameter was measured at the multi-chambered gall level in previous work -->
-Second, we measured the clutch size of adult female midges by counting the number of chambers in each gall (@Weis1983). 
-All larva collected from the same multi-chambered gall were scored with the same clutch size. 
-Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant in an independent survey.
-Specifically, we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
-We then converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
-All larva collected from the same plant were scored with the same female preference.
-The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010); however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference (@Singer1986).
-Fortunately, a couple of features of our study system suggest that larval density on a plant may be a good proxy for female preference.
-For example, since our data comes from a randomized placement of willow genotypes in a common garden, there is no consistent bias in which willow genotypes that females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general (@Hawkins1997), thus we do not expect any prior egg predation to bias our estimates of observed larval densities.
-
-### Quantifying the Fitness Landscape
-
-To characterize the shape of the fitness landscape in simple and complex food webs, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
-We used a binomial error distribution (logit link function) since larval survival (0 or 1) was our response variable and measure of fitness.
-We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
-Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
-setting them to zero) to estimate selection gradients.
-Also, the fitness landscape assumes that traits distributions are multivariate normal.
-To better meet this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
-We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
-We used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95% confidence intervals (@Bolker2009).
-We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
-Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value as this contains the majority of the trait distribution that selection is acting on.
-
-Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits.
-Any influence on trait expression would bias selection gradients acting on those traits.
-In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
-Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
-To estimate this bias, we subset our data to only include galls where there was variation in larval survival (1 > survival > 0) within the same gall.
-We then calculated "apparent" selection differentials for each gall by comparing the average chamber diameter of all larva (before "selection") to the average chamber diameter of surviving larva and analyzed separate one-sample t-tests for each food-web treatment.
-This analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
-In general, we found that our estimates of directional selection on chamber diameter were positively biased (Appendix).
-In other words, our analyses were overestimating the magnitude of selection acting on gall diameter.
-Therefore, we adjusted our estimates of directional selection on chamber diameter ($\beta_{diam}$) by subtracting the biased selection differentials.
-Note that selection gradients and selection differentials for chamber diameter were virtually the same (Appendix).
-
-### Quantifying Selective Constraints
-
-The strength and pattern of selective constraints can be measured as the slope and curvature of the fitness landscape (Arnold 1992).
-
-We can translate selection surfaces of individuals to the fitness landscape of a population
-
-To characterize the net effects of food-web complexity on the slope and curvature of *Iteomyia*'s fitness landscape, we took advantage of existing theory that links selection surfaces of individuals to the fitness landscape of the population (Phillips & Arnold 1998, Arnold 2003).
-Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
-
-```{r LATEX NEED TO CHECK two, eval=FALSE, include=FALSE}
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
-whereas the curvature of the fitness landscape is a function of the directional, nonlinear, and correlational selection gradients: 
-$$\text{Curvature} = \gamma - \beta \beta^T$$
-where \gamma represents the matrix of nonlinear and correlational selection gradients:
-$$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
-```
-
-Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
-Assuming that there is additive genetic variance and covariance between these traits under selection, then the slope and curvature of the fitness landscape give insight to how the population's mean trait value will change in the next generation as well as how additive genetic variance and covariance changes within a generation.
-
-While making quantitative predictions about trait evolution requires knowledge of the additive genetic variance and covariance of these traits, the slope and curvature of the fitness landscape still give qualitative insight to the evolutionary trajectory of a population.
-
-If we assume that there is additive genetic variance and covariance between these traits, then the matrix describing the curvature of the fitness landscape gives qualitative insight to the selective constraints acting on the population.
-For example, the diagonal of the curvature matrix dictates (qualitatively) whether the additive genetic variance in each trait will increase ($+$), decrease ($-$), or stay the same ($0$).
-Similarly, the off-diagonal of the curvature matrix dictates whether selection favors trait integration (positive covariance), a tradeoff (negative covariance), or no change in genetic covariance.
-In other words, we can get qualitative insight to how food-web complexity influences constraints on the fitness landscape by counting the number of negative sign values along the diagnoal (which imply a decrease in additive genetic variance) and the number of positive or negative signs along the off diagonal (which imply changes in additive genetic covariance that lead to either trait integration or tradeoffs).
-
-All analyses and visualizations were conducted in R (@R2018).
-
-I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
-
-```{r Effects of food-web complexity on absolute fitness, cache=TRUE, include=FALSE}
-
-## FIT GLMMs ---
-
-# Null Model
-null_glmer <- glmer(gall_survival ~ 1 +
+## Color palette
+
+# order -> orange, light blue, green, yellow, dark blue, red, pink
+cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
+complex_color <- cbPalette[6] # 1
+simple_color <- cbPalette[5] # 2
+treatment_colors <- c(complex_color, simple_color)
+
+```
+
+# Effect of Food-Web Treatment on Larval Survival
+
+First we fit the full generalized linear mixed model to our data.
+This will enable us to evaluate whether there is any evidence that food-web treatment alters nonlinear selection on gall phenotypic variation.
+Note that we are not interested in directional selection yet, because we need to remove the nonlinear terms to evaluate its effects ([Lande and Arnold 1983](https://doi.org/10.1111/j.1558-5646.1983.tb00236.x)).
+
+```{r Model 1, cache=TRUE}
+model_1 <- glmer(
+  gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.log1p.Pref +
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
+    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref +
+    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref) +
     (1|Genotype/Plant_Position/Gall_Number),
@@
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-# Model assuming no effect of food-web treatment
-trait_glmer <- glmer(gall_survival ~ (sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 + 
-                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
-                      (1|Genotype/Plant_Position/Gall_Number),
-                    data = gall_selection.df,
-                    family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-# Model allowing for an effect of food-web treatment
-foodweb_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref)^2 +
-                         Foodweb*(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-# Model excluding quadratic and trait:trait interactions. This is necessary for accurately estimating directional selection gradients (Betas, Lande and Arnold 1983)
-betas_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-## STATISTICAL TESTS ----
-
-# There is clear evidence that the traits we have measured influence larva survival
-anova(null_glmer, trait_glmer, test="Chisq")
-
-# There is also clear evidence that our food-web treatment altered natural selection
-foodweb_test <- tidy(anova(trait_glmer, foodweb_glmer, test="Chisq"))
-rsquared(list(trait_glmer, foodweb_glmer), method="delta") # 3-4% increase in amount of variance explained when including effect of food-web treatment
-
-## EVALUATING MODEL ASSUMPTIONS ---
-
-# There is no evidence of overdispersion
-overdisp_fun(foodweb_glmer)
-
-# There are no clear patterns in the distribution of the residuals (= good)
-visreg(foodweb_glmer)
-```
-
-```{r Model Modification}
-
-# In terms of the gammas, there was only evidence that food-web treatment altered nonlinear selection on preference
-summary(foodweb_glmer)
-
-# Therefore, we refit a model that only included this effect of food-web treatment on the gamma coefficients
-foodweb_glmer_revised <- update(foodweb_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-
-# Note that we still observe that food-web treatment alters nonlinear selection on female preference
-# There is also now marginal evidence for nonlinear selection on diameter as well as correlational selection between diameter and clutch (Diam:Clutch) and between diameter and preference (Diam:Pref).
-summary(foodweb_glmer_revised)
-
-summary(betas_glmer)
-
-betas_glmer_revised <- update(betas_glmer, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
-summary(betas_glmer_revised)
-
-foodweb_glmer_revised_again <- update(foodweb_glmer_revised, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
-summary(foodweb_glmer_revised_again)
-```
-
-```{r Get Selection Gradients for GLMER}
-
-## METHOD OF JANZEN AND STERN 1998 ----
+```
+
+We use parametric bootstrapping (n=`r n_boots_analysis`) to evaluate the statistical significance of the effect of food-web treatment on nonlinear terms (i.e.
+Foodweb:trait^2 or Foodweb:trait_1:trait_2).
+Food-web treatment does influence the quadratic effect of of female preference on larva survival.
+None of the other terms statistically differ from zero.
+
+```{r Bootstrap Model 1, cache=TRUE, include=FALSE}
+boot_model_1 <- bootMer(model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_1 <- tidy(boot_model_1, conf.int=T) %>% 
+  # filter terms that only matter for this analysis
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
+                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) 
+```
+
+```{r Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE}
+plot_model_1 <- tidy_model_1 %>%
+  mutate(Food_web = ifelse(grepl("FoodwebSimple", .$term)==TRUE,"Simple","Complex")) %>%
+  filter(Food_web == "Simple")
+
+plot_model_1$term_plot <- factor(plot_model_1$term,
+                                levels=c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"),
+                                ordered=TRUE)
+
+plot_model_1 %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(plot_model_1$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+Therefore, we are going to drop them from the model.
+Note that we are still fitting the full curvature of the fitness landscape, but that we aren't allowing some aspects of it to vary between food-web treatments (since there was no evidence for it)
+
+```{r Model 2, cache=TRUE}
+
+# Remove non-signficiant effect of food-web treatment on quadratic and trait_i:trait_j interactions
+
+model_2 <- update(model_1, 
+                  .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2)
+                  -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+```
+
+```{r Bootstrap Model 2, cache=TRUE, include=FALSE}
+
+boot_model_2 <- bootMer(model_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_2 <- tidy(model_2, conf.int=T) %>% 
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                     "FoodwebSimple:I(sc.log1p.Pref^2)")) 
+```
+
+This represents our nonlinear regression coefficients.
+
+```{r Plot Nonlinear Terms, echo=FALSE}
+tidy_model_2$term_plot <- factor(tidy_model_2$term,
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            ordered = TRUE)
+
+tidy_model_2 %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(tidy_model_2$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.log1p.Pref^2)* indicates that food-web treatment alters quadractic selection on female preference; however, this coefficient is not useful for actually calculating the selection gradient.
+To do this, we refit a model so rather than estimating the change in slope (currently), it will actually estimate the slope.
+See [Schielzeth 2010](https://doi.org/10.1111/j.2041-210X.2010.00012.x) for a detailed explanation of this approach.
+```{r Adjust Model 2 for Slopes}
+model_2_adj <- update(model_2, .~. -I(sc.log1p.Pref^2))
+```
+
+```{r Boot Adjusted Model 2 for accurate slope estimates}
+boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_2_adj <- tidy(model_2_adj, conf.int=T) %>% 
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"))
+```
+
+Importantly we see now that although quadratic selection varies between treatments, it is not different from zero in the simple food web.
+
+```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE}
+tidy_model_2_adj$term_plot <- factor(tidy_model_2_adj$term,
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            ordered = TRUE)
+
+tidy_model_2_adj %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(tidy_model_2_adj$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+Now we fit a reduced model to assess the effects of whether food-web treatments alters components of directional selection
+
+```{r Fit Model 3, cache=TRUE}
+model_3 <- update(model_2, 
+                  .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -Foodweb:I(sc.log1p.Pref^2) 
+                  -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref)
+```
+
+We then use parametric bootstrapping to test whether food-web treatment alters the linear relationship between each trait and larva survival.
+
+```{r Bootstrap Model 3, cache=TRUE, include=FALSE}
+boot_model_3 <- bootMer(model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_3 <- tidy(boot_model_3, conf.int=T) 
+```
+
+```{r Plot Model 3, echo=FALSE}
+plot_model_3 <- tidy_model_3 %>%
+  mutate(Food_web = ifelse(grepl("FoodwebSimple:", .$term)==TRUE,"Simple","Complex")) %>%
+  filter(Food_web == "Simple")
+
+plot_model_3$term_ord <- factor(plot_model_3$term, 
+                                levels=c("FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"),
+                                ordered = TRUE)
+plot_model_3 %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(limits=rev(levels(plot_model_3$term_ord))) +
+  ylab("Coefficient (logit scale)")
+```
+
+There is clear evidence that food-web treatment alters the linear effect of clutch size on larva survival, but it has no effect on chamber diameter or female preference.
+Therefore, we fit a reduced model that removes these non-significant effects:
+
+```{r Fit Model 4}
+model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
+```
+
+This reduced model returns the same qualitative result as before.
+Specifically, that the linear effect of clutch size depends on food-web treatment.
+Note also that larval survival is significantly higher in the simple food web compared to the complex food web (dotted line).
+These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
+
+```{r Bootstrap Model 4, cache=TRUE, include=FALSE}
+boot_model_4 <- bootMer(model_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_4 <- tidy(boot_model_4, conf.int=T) 
+```
+
+```{r Plot Model 4, echo=FALSE}
+tidy_model_4$term_plot <- factor(tidy_model_4$term, 
+                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
+                                ordered = TRUE)
+
+plot_model_4 <- tidy_model_4 %>%
+  filter(term != "(Intercept)") %>%
+  droplevels()
+
+plot_model_4 %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(plot_model_4$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+As we did with model 2, we refit the model by removing the slope term so that we can fit different slopes for each interaction term.
+```{r Fit Model 4 adjusted for estimating clutch slopes}
+model_4_adj <- update(model_4, .~. -sc.log.Clutch)
+```
+
+```{r Bootstrap adjusted model 4, cache=TRUE, include=FALSE}
+boot_model_4_adj <- bootMer(model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_4_adj <- tidy(boot_model_4_adj, conf.int=T) 
+```
+
+```{r Plot adjusted model 4, echo=FALSE}
+tidy_model_4_adj$term_plot <- factor(tidy_model_4_adj$term, 
+                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
+                                ordered = TRUE)
+
+plot_model_4_adj <- tidy_model_4_adj %>%
+  filter(term != "(Intercept)") %>%
+  droplevels()
+
+plot_model_4_adj %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(plot_model_4_adj$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+So, for plotting the results, we are going to use the focused nonlinear model.
+This provides the best representation of the fitness landscape (although we can't use it to assess to quantify the effects of directional selection.
+
+Note that while there is no evidence to let the slopes vary among treatments, there is a clear effect of food web treatment on fitness.
+This could influence estimates of selection by magnifying them in the complex vs.
+simple food web.
+
+So to calculate the selection gradients, we used Janzen and Stern's method to transform the regression coefficients.
+
+Basically, I need to just multiply all of the coefficients by the simple and complex fitness. Except, however, for I(sc.log1p.Pref) and sc.log.Clutch. Here, we need the different coefficients.
+
+# Selection Gradients
+
+We used the method of [Janzen and Stern (1998)](https://doi.org/10.1111/j.1558-5646.1998.tb02237.x) to calculate selection gradients.
+Specifically, we first multiply each regression coefficient (and confidence interval) by the average of $W(z)[1-W(z)]$, where $W(z)$ corresponds to the predicted absolute fitness of an individual (in this case 1 if the larva survived, 0 if not) given its multivariate phenotype ($z$).
+We then divided this value by the mean absolute fitness ($\bar W$) so our results are in terms of relative fitness ($w$).
+Note that we doubled all quadratic selection gradients ($\gamma_{z_i,z_i}) to put them on the same scale as the directional and correlational selection gradients (detailed explanation in [Stinchcombe et al.
+2008](https://doi.org/10.1111/j.1558-5646.2008.00449.x)).
+
+```{r Organize and Transform Coefficients, include=FALSE}
+tidy_coefs <- bind_rows(
+  select(tidy_model_2_adj, term, estimate, conf.low, conf.high), 
+  select(tidy_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
+  filter(term != "(Intercept)", term != "FoodwebSimple") # remove main effects
+
+# Tidy common coefficients
+tidy_common_coefs <- tidy_coefs %>%
+  filter(term!="FoodwebComplex:I(sc.log1p.Pref^2)", term!="FoodwebSimple:I(sc.log1p.Pref^2)",
+         term!="FoodwebComplex:sc.log.Clutch",term!="FoodwebSimple:sc.log.Clutch")
+
+# Tidy unique coefficients to each food-web
+complex_quad_pref <- filter(tidy_coefs, term %in% "FoodwebComplex:I(sc.log1p.Pref^2)")
+complex_quad_pref$term <- "I(sc.log1p.Pref^2)"
+simple_quad_pref <- filter(tidy_coefs, term %in% "FoodwebSimple:I(sc.log1p.Pref^2)")
+simple_quad_pref$term <- "I(sc.log1p.Pref^2)"
+
+complex_clutch <- filter(tidy_coefs, term %in% "FoodwebComplex:sc.log.Clutch")
+complex_clutch$term <- "sc.log.Clutch"
+simple_clutch <- filter(tidy_coefs, term %in% "FoodwebSimple:sc.log.Clutch")
+simple_clutch$term <- "sc.log.Clutch"
+```
+
+```{r Calculate Selection Gradients, include=FALSE}
 
 # Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+complex_predict <- predict(model_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
 complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
@@
 
-simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+simple_predict <- predict(model_2, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
 simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
@@
 
-# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
-alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+# Double-check that using a different model (e.g.
+model_4) doesn't influence estimes of mean "brackets" and mean fitness.
+Below, I test this using the "Complex" food-web treatment as an example, but it doesn't matter
+alt_predict <- predict(model_4, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
 alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
@@
 
-# Tidy data for beta terms
-foodweb_tidy_betas <- tidy(betas_glmer, conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
-         Selection_form = c(NA,NA,rep("Directional",6)),
-         Multiplier = rep(1,8))
-
-# Tidy data for gamma terms.
-Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al.
+tidy_simple_grads <- bind_rows(tidy_common_coefs, simple_quad_pref, simple_clutch) %>%
+  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
 2008)
-foodweb_tidy_gammas <- tidy(foodweb_glmer, conf.int=T) %>%
+  transmute(term=term,
+            gradient = simple_mean_brackets * estimate / simple_mean_fitness * Multiplier,
+            `2.5%` = simple_mean_brackets * conf.low / simple_mean_fitness * Multiplier,
+            `97.5%` = simple_mean_brackets * conf.high / simple_mean_fitness * Multiplier)
+
+tidy_complex_grads <- bind_rows(tidy_common_coefs, complex_quad_pref, complex_clutch) %>%
+    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
+2008)
+  transmute(term=term,
+            gradient = complex_mean_brackets * estimate / complex_mean_fitness * Multiplier,
+            `2.5%` = complex_mean_brackets * conf.low / complex_mean_fitness * Multiplier,
+            `97.5%` = complex_mean_brackets * conf.high / complex_mean_fitness * Multiplier)
+
+selection_gradients <- bind_rows(
+  mutate(tidy_simple_grads, `Food web`="Simple"),
+  mutate(tidy_complex_grads, `Food web`="Complex")) #%>%
+  #mutate(Type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic", ifelse(grepl(":", .$term)==TRUE, "Correlational", "Directional")))
+```
+
+```{r Table of Selection Gradients, echo=FALSE}
+selection_gradients$term_ord <- factor(selection_gradients$term, 
+                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
+                                   ordered = TRUE)
+
+selection_gradients_table <- selection_gradients %>%
+  transmute(Term=term_ord, `Food web`, Gradient=round(gradient,2), `2.5%`=round(`2.5%`,2), `97.5%`=round(`97.5%`,2)) %>% 
+  arrange(Term)
+
+knitr::kable(selection_gradients_table, caption = "Table of Selection Gradients")
+```
+
+```{r Plot of Selection Gradients, echo=FALSE}
+selection_gradients %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(selection_gradients$term_ord))) +
+  ylab("Selection Gradient") +
+  scale_fill_manual(values=treatment_colors) +
+  scale_color_manual(values=treatment_colors)
+```
+
+## Contributions of larval parasitoids to selection gradients
+
+To identify the mechanisms by which food-web treatment altered selection gradients, we refit our models so that the complex food-web treatment only contained cases of parasitisms from larval parasitoids.
+Therefore, these analyses identify the unique contribution of each parasitoid guild to the selection gradients (egg parasitoid from simple food web; larval parasitoid from complex food web).
+Note that cases of larval parasitism may have been initially parasitized by an egg parasitoid.
+
+We restrict our model analyses to those where we observed different effects of food-web treatment on larval survival from the prior analyses (i.e. model 2 and model 4).
+
+```{r Egg vs. Larval Parasitoids Model, cache=TRUE}
+
+# excludes cases of egg-parasitism from Complex food web
+egg.vs.larval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1) %>% 
+  mutate(Foodweb = ifelse(Foodweb == "Simple", "Egg", "Larval"))
+
+egg.larval_model_2 <- update(model_2, data=egg.vs.larval_df)
+```
+
+```{r Bootstrap Egg vs. Larval Parasitoid Model 2, cache=TRUE, include=FALSE}
+
+boot_egg.larval_model_2 <- bootMer(egg.larval_model_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_egg.larval_model_2 <- tidy(egg.larval_model_2, conf.int=T) %>% 
   filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
                      "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
-         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
-         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))
-
-# Combine and tidy the regression (alpha) coefficients
-get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
-  mutate(alpha = estimate, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = p.value) %>%
-  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
-
-complex_alphas <- filter(get_alphas, Foodweb == "Complex"); complex_alphas
-simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
-
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5,
-           Selection_form = complex_alphas$Selection_form,                # doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier
-           Multiplier = complex_alphas$Multiplier) %>%                     
-  mutate(b_complex = complex_mean_brackets * a_complex / complex_mean_fitness * Multiplier,
-         b_complex_2.5 = complex_mean_brackets * a_complex_2.5 / complex_mean_fitness * Multiplier,
-         b_complex_97.5 = complex_mean_brackets * a_complex_97.5 / complex_mean_fitness * Multiplier,
-         b_simple = simple_mean_brackets * a_simple / simple_mean_fitness * Multiplier,
-         b_simple_2.5 = simple_mean_brackets * a_simple_2.5 / simple_mean_fitness * Multiplier,
-         b_simple_97.5 = simple_mean_brackets * a_simple_97.5 / simple_mean_fitness * Multiplier)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+                     "FoodwebLarval:I(sc.log1p.Pref^2)")) 
+```
+
+This represents our nonlinear regression coefficients.
+
+```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE}
+tidy_egg.larval_model_2$term_plot <- factor(tidy_egg.larval_model_2$term,
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            ordered = TRUE)
+
+tidy_egg.larval_model_2 %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+   geom_point(aes(y=estimate), size=3, shape=21, fill="grey") +
   coord_flip() +
   geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Regression coefficient")
-
-## Modify to be directional, nonlinear, then correlational with legend in 4th area.
-## Modify so that axes have gamma and beta with the trait as a subscript
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  scale_x_discrete(name="", limits = rev(levels(tidy_egg.larval_model_2$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+ To put all of the coefficients on the same scale, we refit it as we did in the food-web treatment
+```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE}
+egg.larval_model_2_adj <- update(model_2_adj, data=egg.vs.larval_df)
+```
+
+```{r Bootstrap Egg vs. Larval Parasitoid adjusted Model 2, cache=TRUE, include=FALSE}
+
+boot_egg.larval_model_2_adj <- bootMer(egg.larval_model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_egg.larval_model_2_adj <- tidy(egg.larval_model_2_adj, conf.int=T) %>% 
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref")) 
+```
+
+This represents our nonlinear regression coefficients.
+
+```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE}
+tidy_egg.larval_model_2_adj$term_plot <- factor(tidy_egg.larval_model_2_adj$term,
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            ordered = TRUE)
+
+tidy_egg.larval_model_2_adj %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+   geom_point(aes(y=estimate), size=3, shape=21, fill="grey") +
   coord_flip() +
   geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Selection gradient")
-
-```
-
-```{r Parametric Bootstrapping of Regression Coefficients and Selection Gradients, cache=TRUE, include=FALSE}
-
-## DUPLICATE ABOVE EXCEPT MODIFY FOR BOOTMER
-
-## METHOD OF JANZEN AND STERN 1998 ----
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-complex_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# Double-check that using the Beta-only model doesn't influence estimes of mean "brackets" and mean fitness. Using Complex food web as an example, but it doesn't matter 
-alt_predict <- predict(betas_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-test_mean_brackets <- complex_mean_brackets
-test_mean_fitness <- complex_mean_fitness
-test_mean_brackets - alt_mean_brackets # virtually the same
-test_mean_fitness - alt_mean_fitness # virtually the same
-
-# Tidy data for beta terms
-foodweb_tidy_betas <- tidy(bootMer(betas_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c("Complex","Simple",rep("Complex",3),rep("Simple",3)),
-         Selection_form = c(NA,NA,rep("Directional",6)),
-         Multiplier = rep(1,8))
-
-# Tidy data for gamma terms.
-Note that we multiply quadratic (nonlinear) selection coefficients by 2 so they are on the same scale as other coefficients (detailed explanation in Stinchcombe et al.
-2008)
-foodweb_tidy_gammas <- tidy(bootMer(foodweb_glmer, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32), conf.int=T) %>%
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(Foodweb = c(rep("Complex",6),rep("Simple",6)),
-         Selection_form = c(rep("Nonlinear",3),rep("Correlational",3),rep("Nonlinear",3),rep("Correlational",3)),
-         Multiplier = c(rep(2,3),rep(1,3),rep(2,3),rep(1,3)))
-
-# Combine and tidy the regression (alpha) coefficients
-get_alphas <- bind_rows(foodweb_tidy_betas, foodweb_tidy_gammas) %>% 
-  mutate(alpha = statistic, alpha_2.5 = conf.low, alpha_97.5 = conf.high, P = ifelse(conf.low*conf.high > 0, "<0.05","NS")) %>% # change 'alpha = estimate' to 'alpha = statistic' for bootstrap.
-Multiply confidence intervals to determine whether the cofficient is signficantly different from zero.
-  select(term, Foodweb, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
-
-complex_alphas <- filter(get_alphas, Foodweb == "Complex"); complex_alphas
-simple_alphas <- filter(get_alphas, Foodweb == "Simple"); simple_alphas
-
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5,
-           Selection_form = complex_alphas$Selection_form,                # doesn't matter whether simple_ or complex_alphas is chosen for Selection_form or Multiplier
-           Multiplier = complex_alphas$Multiplier) %>%                     
-  mutate(b_complex = complex_mean_brackets * a_complex / complex_mean_fitness * Multiplier,
-         b_complex_2.5 = complex_mean_brackets * a_complex_2.5 / complex_mean_fitness * Multiplier,
-         b_complex_97.5 = complex_mean_brackets * a_complex_97.5 / complex_mean_fitness * Multiplier,
-         b_simple = simple_mean_brackets * a_simple / simple_mean_fitness * Multiplier,
-         b_simple_2.5 = simple_mean_brackets * a_simple_2.5 / simple_mean_fitness * Multiplier,
-         b_simple_97.5 = simple_mean_brackets * a_simple_97.5 / simple_mean_fitness * Multiplier)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
+  scale_x_discrete(name="", limits = rev(levels(tidy_egg.larval_model_2_adj$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+Now we assess their contribution to the effect of food-web treatment on the linear terms.
+
+```{r Fit Egg vs. Larval Parasitoid Model 4}
+egg.larval_model_4 <- update(model_4, data=egg.vs.larval_df)
+```
+
+This reduced model returns the same qualitative result as before.
+Specifically, that the linear effect of clutch size depends on food-web treatment.
+Note also that larval survival is significantly higher in the simple food web compared to the complex food web (dotted line).
+These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
+
+```{r Bootstrap Egg vs. Larval Parasitoid Model 4, cache=TRUE, include=FALSE}
+boot_egg.larval_model_4 <- bootMer(egg.larval_model_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_egg.larval_model_4 <- tidy(boot_egg.larval_model_4, conf.int=T) 
+```
+
+Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
+```{r Plot Egg vs. Larval Parasitoid Model 4, echo=FALSE}
+tidy_egg.larval_model_4$term_ord <- factor(tidy_egg.larval_model_4$term, 
+                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.log1p.Pref"),
+                                ordered = TRUE)
+
+plot_egg.larval_model_4 <- tidy_egg.larval_model_4 %>%
+  filter(term != "(Intercept)") %>%
+  droplevels()
+
+plot_egg.larval_model_4 %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
   coord_flip() +
   geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Regression coefficient")
-
-## Modify to be directional, nonlinear, then correlational with legend in 4th area.
-## Modify so that axes have gamma and beta with the trait as a subscript
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5, Selection_form), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5, Selection_form), Foodweb = "Simple")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
+  scale_x_discrete(name="", limits = rev(levels(plot_egg.larval_model_4$term_ord))) +
+  ylab("Coefficient (logit scale)")
+```
+
+```{r Fit Egg vs. Larval Parasitoid adjusted Model 4}
+egg.larval_model_4_adj <- update(model_4_adj, data=egg.vs.larval_df)
+```
+
+This reduced model returns the same qualitative result as before.
+Specifically, that the linear effect of clutch size depends on food-web treatment.
+Note also that larval survival is significantly higher in the simple food web compared to the complex food web (dotted line).
+These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
+
+```{r Bootstrap Egg vs. Larval Parasitoid adjuted Model 4, cache=TRUE, include=FALSE}
+boot_egg.larval_model_4_adj <- bootMer(egg.larval_model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_egg.larval_model_4_adj <- tidy(boot_egg.larval_model_4_adj, conf.int=T) 
+```
+
+Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
+```{r Plot Egg vs. Larval Parasitoid adjusted Model 4, echo=FALSE}
+tidy_egg.larval_model_4_adj$term_ord <- factor(tidy_egg.larval_model_4_adj$term, 
+                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","FoodwebEgg:sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.log1p.Pref"),
+                                ordered = TRUE)
+
+plot_egg.larval_model_4_adj <- tidy_egg.larval_model_4_adj %>%
+  filter(term != "(Intercept)") %>%
+  droplevels()
+
+plot_egg.larval_model_4_adj %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
   coord_flip() +
   geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Selection gradient")
-
-```
-
-```{r Code Chunk to demonstrate use of latex2exp package, include=FALSE, eval=FALSE}
-## NOT WORKING
-
-library(latex2exp)
-data.frame(x=1:10,y=1:10)
-p<-ggplot(data=x, aes(x=y, y=x)) +
-geom_errorbar(aes(ymin=x-ci, ymax=x+ci)) +
-scale_x_discrete(breaks=c("label1","label2"),
-               labels = lapply(sprintf('$\\alpha^\\beta$'), TeX)
-p
-```
-
-What's the rationale for this test?
-First, we focus on galls where there is evidence of both survival and parasitism within the gall.
-The idea is that galls from the same clutch should be similar in size, therefore, any selection on diameter would be apparent.
-If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection gradient to be the result of confounding factors.
-Note that this is likely overestimates the effect of the confounding factor, since we are assuming that any heterogeneity in gall size (for this dataset) is due to a confounding effect of parasitism on gall diameter.
-Then, we can just subtract this value from the observed covariance between gall diameter and larval survival to adjust for the confounding effects of parasitism.
-This analysis should be relegated to the supplement.
-
-Would we expect any confounding effects on nonlinear selection?
+  scale_x_discrete(name="", limits = rev(levels(plot_egg.larval_model_4_adj$term_ord))) +
+  ylab("Coefficient (logit scale)")
+```
+
+## CALCULATE SELECTION GRADIENTS FOR EGG VS. LARVAL PARASITOIDS
+
+```{r Organize and Transform egg vs. larval parasitoid Coefficients, include=FALSE}
+tidy_egg.larval_coefs <- bind_rows(
+  select(tidy_egg.larval_model_2_adj, term, estimate, conf.low, conf.high), 
+  select(tidy_egg.larval_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
+  filter(term != "(Intercept)", term != "FoodwebLarval") # remove main effects
+
+# Tidy common coefficients
+tidy_egg.larval_common_coefs <- tidy_egg.larval_coefs %>%
+  filter(term!="FoodwebEgg:I(sc.log1p.Pref^2)", term!="FoodwebLarval:I(sc.log1p.Pref^2)",
+         term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")
+
+# Tidy unique coefficients to each food-web
+egg_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebEgg:I(sc.log1p.Pref^2)")
+egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
+larval_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebLarval:I(sc.log1p.Pref^2)")
+larval_quad_pref$term <- "I(sc.log1p.Pref^2)"
+
+egg_clutch <- filter(tidy_egg.larval_coefs, term %in% "FoodwebEgg:sc.log.Clutch")
+egg_clutch$term <- "sc.log.Clutch"
+larval_clutch <- filter(tidy_egg.larval_coefs, term %in% "FoodwebLarval:sc.log.Clutch")
+larval_clutch$term <- "sc.log.Clutch"
+```
+
+```{r Calculate Egg vs. larval parasitoid Selection Gradients, include=FALSE}
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
+larval_predict <- predict(egg.larval_model_2, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
+larval_mean_brackets <- mean(larval_predict * (1 - larval_predict))
+larval_mean_fitness <- mean(larval_predict)
+
+egg_predict <- predict(egg.larval_model_2, newdata=filter(egg.vs.larval_df, Foodweb=="Egg"), type="response")
+egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
+egg_mean_fitness <- mean(egg_predict)
+
+# Double-check that using a different model (e.g.
+egg.larval_model_4) doesn't influence estimes of mean "brackets" and mean fitness.
+Using "Complex" food-web treatment as an example, but it doesn't matter
+alt_egg.larval_predict <- predict(egg.larval_model_4, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
+alt_egg.larval_mean_brackets <- mean(alt_egg.larval_predict * (1 - alt_egg.larval_predict))
+alt_egg.larval_mean_fitness <- mean(alt_egg.larval_predict)
+test_egg.larval_mean_brackets <- larval_mean_brackets
+test_egg.larval_mean_fitness <- larval_mean_fitness
+test_egg.larval_mean_brackets - alt_egg.larval_mean_brackets # virtually the same
+test_egg.larval_mean_fitness - alt_egg.larval_mean_fitness # virtually the same
+
+tidy_egg_grads <- bind_rows(tidy_egg.larval_common_coefs, egg_quad_pref, egg_clutch) %>%
+  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
+2008)
+  transmute(term=term,
+            gradient = egg_mean_brackets * estimate / egg_mean_fitness * Multiplier,
+            `2.5%` = egg_mean_brackets * conf.low / egg_mean_fitness * Multiplier,
+            `97.5%` = egg_mean_brackets * conf.high / egg_mean_fitness * Multiplier)
+
+tidy_larval_grads <- bind_rows(tidy_egg.larval_common_coefs, larval_quad_pref, larval_clutch) %>%
+    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
+2008)
+  transmute(term=term,
+            gradient = larval_mean_brackets * estimate / larval_mean_fitness * Multiplier,
+            `2.5%` = larval_mean_brackets * conf.low / larval_mean_fitness * Multiplier,
+            `97.5%` = larval_mean_brackets * conf.high / larval_mean_fitness * Multiplier)
+
+egg.larval_selection_gradients <- bind_rows(
+  mutate(tidy_egg_grads, `Food web`="Egg"),
+  mutate(tidy_larval_grads, `Food web`="Larval")) #%>%
+  #mutate(Type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic", ifelse(grepl(":", .$term)==TRUE, "Correlational", "Directional")))
+```
+
+```{r Table of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE}
+egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
+                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
+                                   ordered = TRUE)
+
+egg.larval_selection_gradients_table <- egg.larval_selection_gradients %>%
+  transmute(Term=term_ord, Parasitoid=`Food web`, Gradient=round(gradient,2), `2.5%`=round(`2.5%`,2), `97.5%`=round(`97.5%`,2)) %>% 
+  arrange(Term)
+
+knitr::kable(egg.larval_selection_gradients_table, caption = "Table of Egg vs. Larval Parasitoid Selection Gradients")
+```
+
+```{r Plot of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE}
+egg.larval_selection_gradients %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(egg.larval_selection_gradients$term_ord))) +
+  ylab("Selection Gradient") +
+  scale_fill_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) +
+  scale_color_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) 
+```
+
+# Quantifying biased selection on chamber diameter
+
+We quantified biased selection on chamber diameter in the following way.
+First, we focus on multi-chambered galls where there is evidence of both survival and parasitism.
+The idea is that galls from the same clutch should be similar in size; therefore, any selection on diameter would be apparent.
+If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection differential to be the result of confounding factors.
+Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism.
+
+We calculated the bias in selection differential on chamber diameter by calculating the difference in mean chamber diameter before (i.e.
+all larva within the same gall) and after selection (only surviving larva).
+We then used a one-sample t-test to determine whether the selection differential was significantly different from zero.
+We conducted separate t-tests for each food-web treatment.
+
+We can then subtract this "biased selection differential" from the observed directional selection gradient on chamber diameter to adjust for the confounding effects of parasitism.
+
+```{r New approach for biased selection, include=FALSE}
+biased_df <- gall_selection.df %>%
+  group_by(Foodweb, Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1)
+
+summary(update(model_1, data=biased_df)) # no clear effects here...
+summary(update(model_2, data=biased_df)) # seeing the bias here, but its still not what we actually assess the differences on
+summary(update(model_3, data=biased_df)) # we're going to focus on diameter since that's our focus now. It doesn't appear that the slope differes between food-web treatments
+biased.diam_model_4 <- update(model_4, data=biased_df)
+summary(biased.diam_model_4) # looks like the bias in our sc.Diam coefficient is 0.35
+
+bias.adj_complex_predict <- predict(biased.diam_model_4, newdata=filter(biased_df, Foodweb=="Complex"), type="response")
+bias.adj_complex_mean_brackets <- mean(bias.adj_complex_predict * (1 - bias.adj_complex_predict))
+bias.adj_complex_mean_fitness <- mean(bias.adj_complex_predict)
+
+bias.adj_simple_predict <- predict(biased.diam_model_4, newdata=filter(biased_df, Foodweb=="Simple"), type="response")
+bias.adj_simple_mean_brackets <- mean(bias.adj_simple_predict * (1 - bias.adj_simple_predict))
+bias.adj_simple_mean_fitness <- mean(bias.adj_simple_predict)
+
+# convert to selection gradient
+bias.adj_sc.Diam_complex <- bias.adj_complex_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_complex_mean_fitness * 1 # 0.11
+bias.adj_sc.Diam_simple <- bias.adj_simple_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_simple_mean_fitness * 1 # 0.07
+
+# This analysis suggests that there is a little bias, but not too much. 
+```
+
+```{r Redo selection gradients}
+bias.adj_selection_gradients <- mutate(selection_gradients, adjusted = "No") %>%
+  # add bias adjusted directional selection gradient for Diameter in complex food-web
+  add_row(term="sc.Diam", 
+          gradient = complex_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$estimate - fixef(biased.diam_model_4)["sc.Diam"]) / complex_mean_fitness, 
+          `2.5%` = complex_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.low - fixef(biased.diam_model_4)["sc.Diam"]) / complex_mean_fitness, 
+          `97.5%` = complex_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.high - fixef(biased.diam_model_4)["sc.Diam"]) / complex_mean_fitness, 
+          `Food web` = "Complex", 
+          term_ord = "Diam", 
+          adjusted="Yes") %>%
+  # add bias adjusted directional selection gradient for Diameter in simple food-web
+  add_row(term="sc.Diam", 
+          gradient = simple_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$estimate - fixef(biased.diam_model_4)["sc.Diam"]) / simple_mean_fitness, 
+          `2.5%` = simple_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.low - fixef(biased.diam_model_4)["sc.Diam"]) / simple_mean_fitness, 
+          `97.5%` = simple_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.high - fixef(biased.diam_model_4)["sc.Diam"]) / simple_mean_fitness, 
+          `Food web` = "Simple", 
+          term_ord = "Diam", 
+          adjusted="Yes")
+```
+
+```{r Plot of bias adjusted Selection Gradients, echo=FALSE}
+bias.adj_selection_gradients %>%
+  ggplot(., aes(x=term_ord, shape=adjusted)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=1)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=1)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(bias.adj_selection_gradients$term_ord))) +
+  ylab("Selection Gradient") +
+  scale_fill_manual(values=treatment_colors) +
+  scale_color_manual(values=treatment_colors) +
+  scale_shape_manual(name="Bias\nadjusted", values=c(21,23))
+```
+
 ```{r Confounding effects of parasitism on gall size, include=FALSE, eval=FALSE}
@@
 
+## Selection on the egg parasitoid *Platygaster*
+
+We cannot calculate selection on the egg parasitoids *Platygaster* with the same method as we did for the herbivore *Iteomyia*.
+This is because the unique biology of host-parasitoid interactions enables us to determine whether the host (herbivore) has survived or not.
+With the egg parasitoid, we only have a record of the gall it was found in.
+But, we can take advantage of our treatment which excludes the guild of larval parasitoids.
+Specifically, we can compare the mean gall phenotype that egg parasitoids are reared from in the absence of larval parasitoids ("before" selection) to the mean gall phenotype in the presence of larval parasitoids ("after" selection).
+Therefore, we can use this cross-sectional data to quantify directional and quadratic selection differentials acting on the gall phenotypes.
+In essence, the gall phenotype becomes the extended phenotype of the egg parasitoid, since its attributes can influence the egg parasitoid's survival to its intraguild predator (larval parasitoid).
+
+To quantify the selection differential acting on the egg parasitoid, we used separate linear mixed models with the gall phenotype as the response variable, food-web treatment as the fixed effect, and then the same suite of random effects as for our primary analyses of *Iteomyia* survival (i.e.
+gall ID, nested within plant ID, nested within plant genotype).
+
+We found no evidence of directional or quadratic selection on either chamber diameter or clutch size; however, we observed positive directional selection on *Iteomyia* female preference as well stabilizing selection on preference.
+
 Appears to be selection for Platygaster to attack larva at high densities in more complex food webs (and a decrease in the variance).
@@
 ```
-
-## Table for Alpha regression coefficients
-\begin{table}[]
-\begin{tabular}{lcc}
-                                                                           \\ \hline
-                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
-$Diam$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Clutch$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Pref$                 & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Diam^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Clutch^2$             & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Pref^2$               & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Diam:Clutch$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Diam:Pref$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$Clutch:Pref$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]              \\ \hline
-\end{tabular}
-\end{table}
-
-## Table for Iteomyia selection gradients
-\begin{table}[]
-\begin{tabular}{lcc}
-                                                                                  \\ \hline
-                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
-$\beta_{Diam}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\beta_{Clutch}$                  & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\beta_{Pref}$                    & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Diam,Diam}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Clutch,Clutch}$          & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Pref,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Diam,Clutch}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Diam,Pref}$              & `r ` [`r `-`r `] & `r ` [`r `-`r `]  \\
-$\gamma_{Clutch,Pref}$            & `r ` [`r `-`r `] & `r ` [`r `-`r `]           \\ \hline
-\end{tabular}
-\end{table}
-
-## Table for bias
-\begin{table}[]
-\begin{tabular}{lc}
-                                                                  \\ \hline
-\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
-Complex (All)                 & `r ` [`r `-`r `]  \\
-Complex (Larval guild)        & `r ` [`r `-`r `]  \\
-Simple (\textit{Platygaster}) & `r ` [`r `-`r `]                  \\ \hline
-\end{tabular}
-\end{table}
-
-## Table for Platygaster selection
-\begin{table}[]
-\begin{tabular}{lc}
-                                                                  \\ \hline
-\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
-$s_{Diam}$                      & `r ` [`r `-`r `]  \\
-$s_{Clutch}$                    & `r ` [`r `-`r `]  \\
-$s_{Pref}$                      & `r ` [`r `-`r `]  \\ 
-$s_{Diam,Diam}$                 & `r ` [`r `-`r `]  \\
-$s_{Clutch,Clutch}$             & `r ` [`r `-`r `]  \\
-$s_{Pref,Pref}$                 & `r ` [`r `-`r `]                \\ \hline
-\end{tabular}
-\end{table}
 
@@
 ```
-
-Results
-=======
-
-We found that changes in food-web complexity altered the shape of *Iteomyia*'s fitness landscape ().
-
-For example, there was directional selection for larger gall diameter in both complex and simple food webs, but the magnitude of the selection gradient was X-fold higher in the complex food web.
-The steeper selection gradient in the complex food web was not a result of stronger covariance between gall diameter and larval survival, but a result of average larval survival being X-fold lower in the complex food web.
-
-We observed directional selection for smaller clutch sizes in the simple food web, but no evidence of selection on this trait in the complex food web.
-The absence of selection in the complex food web appeared to be a result of conflicting selection pressures imposed by the egg parasitoid *Platygaster* and the guild of larval parasitoids (statistical test focus on egg vs.
-larval parasitoids).
-Specifically, larval parasitoids actually impose directional selection for larger clutch sizes (selection gradient), but the net effect is no selection when both parasitoid guilds are present.
-
-We found evidence of disruptive selection acting on female preference in the complex food web, but no evidence of nonlinear selection on this trait in the simple food web.
-Similar to clutch size, these differences in nonlinear selection appeared to be due to different selection pressures imposed by egg and larval parasitoids.
-
-**Characterizing the slope and curvature of the fitness landscape**
-
-**Old**
 
@@
 
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE, eval=FALSE}
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0))
+
+RF_Diam <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Diam,
+  bootstraps=n_boots_plots)
 
 # Control ----
-RF_control_gall_size <- bootstrap_fitness(
-  logistic_model = quad_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000), 
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = 0),
+#RF_control_gall_size <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = seq(-1,1,length.out=1000), 
+#     sc.log.clutch_size = 0,
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+
+# Treatment ----
+#RF_treatment_gall_size <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = seq(-1,1,length.out=1000),
+#     sc.log.clutch_size = 0,
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+```
+
+```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE}
+newdata_Clutch <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0))
+
+RF_Clutch <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Clutch,
   bootstraps=n_boots_plots)
 
+# Control ----
+#RF_control_clutch_size <- bootstrap_fitness(
+#  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000),
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+
 # Treatment ----
-RF_treatment_gall_size <- bootstrap_fitness(
-  logistic_model = quad_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = 0),
+#RF_treatment_clutch_size <- bootstrap_fitness(
+#  logistic_model = model_2, #quad_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000),
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+```
+
+```{r Get Female Preference Fitness Landscape, cache=TRUE, include=FALSE}
+
+newdata_Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
+
+RF_Pref <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Pref,
   bootstraps=n_boots_plots)
-```
-
-```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE, eval=FALSE}
 
 # Control ----
-RF_control_clutch_size <- bootstrap_fitness(
-  logistic_model = quad_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = 0),
-  bootstraps=n_boots_plots)
+#RF_control_female_preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = 0, 
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=n_boots_plots)
 
 # Treatment ----
-RF_treatment_clutch_size <- bootstrap_fitness(
-  logistic_model = quad_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = 0),
-  bootstraps=n_boots_plots)
-```
-
-```{r Get Female Preference Fitness Landscape, include=FALSE, eval=FALSE}
+#RF_treatment_female_preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = 0,
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=n_boots_plots)
+
+```
+
+```{r Get Clutch Size x Female Preference Landscape, cache=TRUE, include=FALSE}
+
+newdata_Clutch.Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)))
+
+RF_Clutch.Pref <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Clutch.Pref,
+  bootstraps=NULL)
 
 # Control ----
-RF_control_female_preference <- bootstrap_fitness(
-  logistic_model = quad_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = 0, 
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=n_boots_plots)
+#RF_control_clutch.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000), 
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=NULL)
 
 # Treatment ----
-RF_treatment_female_preference <- bootstrap_fitness(
-  logistic_model = quad_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=n_boots_plots)
-
-```
-
-```{r Get Clutch Size x Female Preference Landscape, include=FALSE, eval=FALSE}
+#RF_treatment_clutch.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000),
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam.Clutch <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref=0))
+
+RF_Diam.Clutch <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Diam.Clutch,
+  bootstraps=NULL)
 
 # Control ----
-RF_control_clutch.x.preference <- bootstrap_fitness(
-  logistic_model = corr_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000), 
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#RF_control_size.x.clutch <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+ # newdata = expand.grid(
+  #   sc.gall_size = seq(-1,1,length.out=1000),
+   #  sc.log.clutch_size = seq(-1,1,length.out=1000), 
+    # sc.log1p.female_preference = 0), 
+  #bootstraps=NULL)
+
+# Treatment ----
+#RF_treatment_size.x.clutch <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+ # newdata = expand.grid(
+  #   sc.gall_size = seq(-1,1,length.out=1000),
+   #  sc.log.clutch_size = seq(-1,1,length.out=1000),
+    # sc.log1p.female_preference = 0), 
+  #bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Female Preference Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam.Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
+
+RF_Diam.Pref <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Diam.Pref,
   bootstraps=NULL)
 
+# Control ----
+#RF_control_size.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+#  newdata = expand.grid(
+ #    sc.gall_size = seq(-1,1,length.out=1000),
+  #   sc.log.clutch_size = 0, 
+   #  sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  ##bootstraps=NULL)
+
 # Treatment ----
-RF_treatment_clutch.x.preference <- bootstrap_fitness(
-  logistic_model = corr_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = 0,
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Clutch Size Landscape, include=FALSE, eval=FALSE}
-
-# Control ----
-RF_control_size.x.clutch <- bootstrap_fitness(
-  logistic_model = corr_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = seq(-1,1,length.out=1000), 
-     sc.log1p.female_preference = 0), 
-  bootstraps=NULL)
-
-# Treatment ----
-RF_treatment_size.x.clutch <- bootstrap_fitness(
-  logistic_model = corr_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = seq(-1,1,length.out=1000),
-     sc.log1p.female_preference = 0), 
-  bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Female Preference Landscape, include=FALSE, eval=FALSE}
-
-# Control ----
-RF_control_size.x.preference <- bootstrap_fitness(
-  logistic_model = corr_control, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = 0, 
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-
-# Treatment ----
-RF_treatment_size.x.preference <- bootstrap_fitness(
-  logistic_model = corr_treatment, 
-  fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-  newdata = expand.grid(
-     sc.gall_size = seq(-1,1,length.out=1000),
-     sc.log.clutch_size = 0,
-     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  bootstraps=NULL)
-```
-
-```{r Fitness Landscape Plot Helpers, include=FALSE, eval=FALSE}
-
-## Color palette ----
-
-# order -> orange, light blue, green, yellow, dark blue, red, pink
-cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
-complex_color <- cbPalette[6] # 1
-simple_color <- cbPalette[5] # 2
-treatment_colors <- c(complex_color, simple_color)
+#RF_treatment_size.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+ # newdata = expand.grid(
+  #   sc.gall_size = seq(-1,1,length.out=1000),
+   #  sc.log.clutch_size = 0,
+    # sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  #bootstraps=NULL)
+```
+
+```{r Fitness Landscape Plot Helpers, include=FALSE}
 
@@
 # 1D
-RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
-          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
-          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, relative_fitness, -sc.gall_size) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  summarise(min = min(relative_fitness), max = max(relative_fitness))
-RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
+#RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
+#          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
+#          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
+#  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
+#  gather(ID, relative_fitness, -sc.gall_size) %>%
+#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+#  summarise(min = min(relative_fitness), max = max(relative_fitness))
+#RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
 
 # 2D
-RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
-          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
-          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
-  summarise(min = min(average), max = max(average))
+#RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
+#          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
+#          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
+#  summarise(min = min(average), max = max(average))
 
@@
 # 2D
-AF_range <- bind_rows(RF_treatment_clutch.x.preference$absolute_fitness, RF_control_clutch.x.preference$absolute_fitness,
-          RF_treatment_size.x.clutch$absolute_fitness, RF_control_size.x.clutch$absolute_fitness,
-          RF_treatment_size.x.preference$absolute_fitness, RF_control_size.x.preference$absolute_fitness) %>%
+AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
   summarise(min = min(average), max = max(average))
@@
 
-```{r Plot Univariate Landscapes, include=FALSE, eval=FALSE}
-uni_breaks <- c(0.1,0.5,1)
+```{r Plot Univariate Landscapes, include=FALSE}
+uni_breaks <- c(0.1,0.5,1.0)
 
 # Gall size 
-AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
+AF_uni_Diam <- RF_Diam$absolute_fitness %>% #bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.log.Clutch, -sc.log1p.Pref) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
   scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Population mean fitness") +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Mean larva survival") +
   scale_color_manual(values = treatment_colors, name = "Food web") +
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
+  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
 #AF_uni_size
@@
 # Clutch size
-AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.log.clutch_size, -Food_Web) %>%
+AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% #bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.Diam, -sc.log1p.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
   xlab("Clutch size (SDs)") +
-  ylab("Population mean fitness") +
+  ylab("Mean larva survival") +
   scale_color_manual(values = treatment_colors, name = "Food web") +
@@
   scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
+  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
   #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
@@
 # Female preference
-AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log.clutch_size) %>%
-  gather(ID, absolute_fitness, -sc.log1p.female_preference, -Food_Web) %>%
+AF_uni_Pref <- RF_Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.log1p.Pref, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.log1p.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
   xlab("Female preference (SDs)") +
-  ylab("Population mean fitness") +
+  ylab("Mean larva survival") +
   scale_color_manual(values = treatment_colors, name = "Food web") +
@@
 
-```{r Univariate_Landscapes, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Univariate_Landscapes}Selection gradients acting on gall traits in complex vs.
+```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
 simple food webs.
@@
 # Get legend
-AF_uni_legend <- get_legend(AF_uni_size)
+AF_uni_legend <- get_legend(AF_uni_Diam)
 
 # Make plots
-AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none", 
+AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none", 
                                               axis.text.x = element_text(size=10),
                                               axis.title.x = element_text(size=11)), 
-                       AF_uni_clutch + theme(legend.position = "none",
+                       AF_uni_Clutch + theme(legend.position = "none",
                                              axis.title.y = element_blank(), 
-                                             axis.text.y = element_blank(),
+                                             #axis.text.y = element_blank(),
                                              axis.text.x = element_text(size=10),
                                              axis.title.x = element_text(size=11)),
-                       AF_uni_pref + theme(legend.position = "none", 
+                       AF_uni_Pref + theme(legend.position = "none", 
                                            axis.title.y = element_blank(), 
-                                           axis.text.y = element_blank(), 
+                                           #axis.text.y = element_blank(), 
                                            axis.text.x = element_text(size=10),
@@
 
-AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
+AF_gradients <- plot_grid(AF_uni_plots, AF_uni_legend, ncol = 2, rel_widths = c(1,0.2)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
 AF_gradients
@@
 # save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
-```
-
-```{r Plot Multivariate Fitness Landscape, include=FALSE, eval=FALSE}
+#save_plot("../figures/fitness_landscapes_1D.png", AF_gradients)#, base_height=6, base_width = 8)
+```
+
+```{r Plot Multivariate Fitness Landscape, include=FALSE}
 
@@
 # Size x Preference
-AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
+AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.Diam, y=sc.log1p.Pref, fill=average)) +
   geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
+  facet_wrap(~Foodweb) +
+  xlab("Chamber diameter (SDs)") +
   ylab("Female preference (SDs)") +
@@
   scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
+  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
 
 # Size x Clutch
-AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
+AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% #bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch, fill=average)) +
   geom_raster() +
-  facet_wrap(~Food_Web) +
+  facet_wrap(~Foodweb) +
   xlab("Gall diameter (SDs)") +
@@
   scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max),
+  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
 
 # Clutch x Preference
-AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
+AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
+         # mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
+  ggplot(., aes(x=sc.log1p.Pref, y=sc.log.Clutch, fill=average)) +
   geom_raster() +
-  facet_wrap(~Food_Web) +
+  facet_wrap(~Foodweb) +
   xlab("Female preference (SDs)") +
@@
   scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Population\nmean fitness", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(0.1,1)) # limits = c(AF_range$min, AF_range$max), 
-```
-
-```{r Multivariate_Landscapes, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Multivariate_Landscapes}Fitness landscapes of gall traits in complex vs.
+  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#, 
+```
+
+```{r Multivariate-Fitness-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
 simple food webs.
@@
 # Get legend
-AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
+AF_landscape_legend <- get_legend(AF_plot_Diam.Pref)
 
@@
 AF_landscape_plots <- plot_grid(
-  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
-  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
-  AF_plot_size.x.preference + theme(legend.position = "none"), 
+  AF_plot_Diam.Clutch + theme(legend.position = "none", 
+                              axis.title.y = element_text(size=11),
+                              axis.title.x = element_blank(),
+                              axis.text = element_text(size=10)),
+  AF_plot_Clutch.Pref + theme(legend.position = "none", 
+                              axis.title.y = element_blank(), 
+                              axis.text = element_text(size=10), 
+                              axis.title.x = element_text(size=11)),
+  AF_plot_Diam.Pref + theme(legend.position = "none", 
+                            axis.text = element_text(size=10),
+                            axis.title = element_text(size=11)), 
   nrow=2, align="hv", labels = "AUTO")
@@
 #save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("FL_2D.pdf", AF_landscape_2d, base_height=6, base_width = 8)
-```
-
-Discussion
-==========
-
-<!-- Summary -->
-
-Our key finding was that the adaptive landscape was less constrained in the complex vs.
-simple food web.
-These fewer constraints arise from conflicting selection pressures imposed by different parasitoid guilds, resulting in fewer traits under selection in the complex food web.
-At the same time, we observed an overall greater intensity of selection in the complex food web, suggesting that trait evolution can be faster in complex vs.
-simple food webs.
-Our observation that natural selection was more constrained and less intense in simple vs.
-complex food webs suggests that the loss of biodiversity could constrain the adaptive potential of interacting species by reducing genetic and phenotypic variation in multiple traits.
-
-<!-- Selective constraints result -->
-
-Current theory suggests that when the number of selective constrains is less than the number of genetic constraints (i.e.
-some genetically variable traits are selective neutral), there are multiple positions on the landscape that confer equal fitness (Lande 1981; Lande and Arnold 1985).
-In this scenario, trait differences between populations may simply be due to neutral processes (e.g.
-genetic drift and mutation) moving trait values of the population.
-For our system, we currently lack quantitative estimates of genetic variation in our traits, although work with other species of galling insects has shown that gall diameter (Abramhson, Heath's work), clutch size (look to Weiss' work), and oviposition preference (Abrahmson's work?) are genetically variable.
-We encourage others to examine how changes in community context will alter selection on multiple traits.
-
-<!-- Intensity of selection result -->
-
-One interesting result of our work was that the overall intensity of selection appeared to be larger in complex food webs.
-This result was driven by the large selection gradient acting on gall diameter in complex vs.
-simple food webs.
-This difference in selection intensity is likely not driven by a difference in the ecological relationship between gall diameter and parasitoid attack (i.e.
-slope), but actually a result of the lower mean fitness of *Iteomyia* in the complex food web.
-This lower mean fitness is not surprising ---we excluded an entire guild of parasitoids from attacking the insect.
-But this more intense selection pressure may simply represent a transient dynamic.
-This is because we would expect the egg-parasitoid *Platygaster* to increase in abundance over time once its intraguild predator has been removed.
-While our results suggest that this wouldn't affect the slope of the relationship, the higher abundance of the egg parasitoid would likely reduce the mean fitness of *Iteomyia*, thus increasing the selection gradient acting on gall diameter closer to what we observed in the complex food web.
-We don't expect it to fully compensate, given that the larval parasitoids exhibit a different functional relationship with gall traits, and thus we expect a more diverse community of primary parasitoids to generally impose greater parasitism pressure, a factor that appears to be a general trend in parasitoid community (Hawkins citation) and likely for other consumers (Ives and Cardinale Ecology Letters).
-
-<!-- Quantifying indirect effects of food-web complexity -->
-
-Our study focused on quantifying the direct effects of changes in network complexity on the fitness landscape; however, changes in network complexity may have pervasive indirect effects via coevolution or by initiating evolutionary cascades.
-In our system, we observed that excluding the guild of larval parasitoids altered selection on both the basal resource (*Iteomyia*) and the intraguild prey (*Platygaster*).
-GIVE DETAILS AND SUGGEST A POTENTIAL EVOLUTIONARY CASCADE.
-
-<!-- Generality of effects of food-web complexity -->
-
-Our study manipulated food-web complexity and examined changes in the fitness landscape of species embedded within this network.
-However, other studies have also examined, at least theoretically, how changes in the diversity of competitive communities affects evolution.
-These studies have generally suggested that the diversity of competitors may actually constrain the adaptive landscape, a finding that stands in contrast to our results.
-NEED TO REVIEW THESE PAPERS TO SEE HOW ITS DIFFERENT.
-
-<!-- Conclusion -->
-
-We suggest that by explicitly focusing on network structure, we can predict how changes in biodiversity will affect the adaptive potential of constituent species.
-A network allows a powerful representation of the 'community context', lending predictive power to how changes in network structure (either due to loss of species or links), will alter natural selection and consequently evolutionary change.
-Our results also suggest that losing biodiversity may not just have consequences at the community level, but also population-level consequences that may actually constrain adaptation to changing environments.
-This argues that changes in network complexity may not only affect the robustness of communities, but also that of constituent populations to future environmental change.
-
-<!-- 
-From Arnold Am Nat 1992 Constrains on phenotypic evolution
- Evolutionary models with constant adaptive landscapes and G-matrices pro-
- vide some generalizations about the effects of selective constraints. First, the
- phenotypic mean of the population tends to evolve in an uphill direction on the
- adaptive landscape (Lande 1979). When selection is frequency-independent and
- the landscape is Gaussian, the population mean equilibrates on an adaptive peak.
- Burger (1986), however, modeled evolution on a landscape that was an ascending
- ridge with increasingly steep flanks. He found that the population would equili-
- brate on the ridge crest when stabilizing selection reached a critical level. Second,
- frequency-dependent selection generally causes the population to equilibrate
- some distance downslope from an adaptive peak (Lande 1976b, 1980b). Finally,
- when the number of selective constraints is less than the number of genetic con-
- straints so that some genetically variable traits are selectively neutral, there is a
- collection of possible equilibrium points (a line, plane, or hyperplane) rather than
- a single equilibrium point (Lande 1981; Lande and Arnold 1985). In the case of
- mating preferences and sexually selected traits, for example, the evolutionary
- outcome is changed dramatically depending on whether selection acts on mating
- preferences (Arnold 1987; Pomiankowski et al. 1991).
-
-I. Feedbacks between biological diversity and evolutionary change
-
-More recently, researchers have begun to explore how the community context drives evolutionary change (@McPeek2017; @TerHorst2018).
-
-NEED to recognize that evolutionary biologists have begun to explore how community context affects evolutionary change (work by Sharon Strauss, Casey terHorst, Lutz Becks, etc.).
-These results have begun to show interesting patterns whereby the composition of species in a community can alter the direction and strength of natural selection imposed on species embedded within these communities (cite).
-
-In other words, these results have begun to illustrate show how biological diversity, in terms of differences between species, can shape evolution.
-Nevertheless, predicting the how the composition of species in a community requires moving beyond a description of community composition.
-simply knowing the composition of species in a community will
-
-There are various bibliography styles available. You can select the
-style of your choice in the preamble of this document. These styles are
-Elsevier styles based on standard styles like Harvard and Vancouver.
-Please use BibTeX to generate your bibliography and include DOIs
-whenever available.
-
-Here are two sample references: @Feynman1963118 [@Dirac1953888].
--->
-
-References {#references .unnumbered}
-==========
-
-```{r Univariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
-## Absolute fitness plots ----
-
-# Gall size 
-AF_uni_size <- bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.gall_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.gall_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Absolute fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
-
-# Clutch size
-AF_uni_clutch <- bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log1p.female_preference) %>%
-  gather(ID, absolute_fitness, -sc.log.clutch_size, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.clutch_size, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Absolute fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
-
-# Female preference
-AF_uni_pref <- bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.gall_size, -sc.log.clutch_size) %>%
-  gather(ID, absolute_fitness, -sc.log1p.female_preference, -Food_Web) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.female_preference, y=absolute_fitness, group=interaction(ID,Food_Web), color=Food_Web, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.1), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
-  ylab("Absolute fitness") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)))
-```
-
-```{r Figure S1 Univariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
-
-# Get legend
-AF_uni_legend <- get_legend(AF_uni_size)
-
-# Make plots
-AF_uni_plots <- plot_grid(AF_uni_size + theme(legend.position = "none"), 
-                       AF_uni_clutch + theme(legend.position = "none", 
-                                          axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       AF_uni_pref + theme(legend.position = "none", 
-                                        axis.title.y = element_blank(), axis.text.y = element_blank()),
-                       labels = "AUTO", ncol = 4, align='hv')
-
-AF_gradients <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.8, y=0)
-AF_gradients
-#save_plot("AF_gradients.png", AF_gradients, base_height=6, base_width = 8)
-#save_plot("AF_gradients.pdf", AF_gradients, base_height=6, base_width = 8)
-```
-
-```{r Multivariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
-
-# Size x Preference
-AF_plot_size.x.preference <- bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log1p.female_preference, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Female preference (SDs)") +
-  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-
-# Size x Clutch
-AF_plot_size.x.clutch <- bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.gall_size, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-
-# Clutch x Preference
-AF_plot_clutch.x.preference <- bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.female_preference, y=sc.log.clutch_size, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Food_Web) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_fill_viridis(limits = c(AF_range$min, AF_range$max), name = "Absolute fitness")
-```
-
-```{r Figure S2 Multivariate Absolute Fitness Landscapes, include=FALSE, eval=FALSE}
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_size.x.preference)
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_size.x.clutch + theme(legend.position = "none", axis.title.x = element_blank()),
-  AF_plot_clutch.x.preference + theme(legend.position = "none", axis.title.y = element_blank()),
-  AF_plot_size.x.preference + theme(legend.position = "none"), 
-  nrow=2, align="hv", labels = "AUTO")
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("AF_landscapes_2d.pdf", AF_landscape_2d, base_height=6, base_width = 8)
-```
+#save_plot("../figures/fitness_landscapes_2D.png", AF_landscape_2d)#, base_height=6, base_width = 8)
+```

### 2018-09-25 manuscript/manuscript.tex
lots of progress in analysis

@@
 \usepackage[sc]{mathpazo} %Like Palatino with extensive math support
+\usepackage{graphicx} % for organizing figures
 \usepackage{fullpage}
@@
 \begin{table}[h]
-\caption{Table for Alpha Regression coefficients}
-\label{Table:Alphas}
-\centering
-\begin{tabular}{lcc}
-                                                                           \\ \hline
-                       & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-\textbf{Coefficient}   & \textbf{Complex} & \textbf{Simple}                \\ \hline
-$Diam$                 &  [ - ] &  [ - ] \\
-$Clutch$               &  [ - ] &  [ - ] \\
-$Pref$                 &  [ - ] &  [ - ] \\
-$Diam^2$               &  [ - ] &  [ - ] \\
-$Clutch^2$             &  [ - ] &  [ - ] \\
-$Pref^2$               &  [ - ] &  [ - ] \\
-$Diam:Clutch$          &  [ - ] &  [ - ] \\
-$Diam:Pref$            &  [ - ] &  [ - ] \\
-$Clutch:Pref$          &  [ - ] &  [ - ]              \\ \hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Table titles should be short.
-Further details should go in a `notes' area after the tabular environment, like this.
-$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
-\end{table}
-
-\newpage{}
-
-\begin{table}[h]
 \caption{Table for \textit{Iteomyia} Selection Gradients}
@@
 \textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
-$\beta_{Diam}$                    &  [ - ] &  [ - ] \\
-$\beta_{Clutch}$                  &  [ - ] &  [ - ] \\
-$\beta_{Pref}$                    &  [ - ] &  [ - ] \\
-$\gamma_{Diam,Diam}$              &  [ - ] &  [ - ] \\
-$\gamma_{Clutch,Clutch}$          &  [ - ] &  [ - ] \\
-$\gamma_{Pref,Pref}$              &  [ - ] &  [ - ] \\
-$\gamma_{Diam,Clutch}$            &  [ - ] &  [ - ] \\
-$\gamma_{Diam,Pref}$              &  [ - ] &  [ - ] \\
-$\gamma_{Clutch,Pref}$            &  [ - ] &  [ - ]            \\ \hline
+$\beta_{Diam}$                    & 0.47 [0.36-0.58] & 0.29 [0.23,0.37] \\
+$\beta_{Clutch}$                  & 0.06 [-0.04,0.17] & -0.13 [-0.25,-0.04] \\
+$\beta_{Pref}$                    & -0.24 [-0.36,-0.11] & -0.15 [-0.23,-0.07] \\
+$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
+$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.04] & -0.06 [-0.16,0.02] \\
+$\gamma_{Pref,Pref}$              & 0.39 [0.02,0.81] & -0.32 [-0.63,-0.03] \\
+$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.01] \\
+$\gamma_{Diam,Pref}$              & -0.08 [-0.19,0.02] & -0.05 [-0.12,0.01] \\
+$\gamma_{Clutch,Pref}$            & 0.04 [-0.06,0.13] & 0.02 [-0.04,0.08]            \\ \hline
 \end{tabular}
@@
 
+%Path relative to the main .tex file 
+\graphicspath{ {../analyses/reproduce_analyses_files/figure-html/} }
+
 \begin{figure}[h!]
-%\includegraphics{horn-of-okapi}
-\caption{Figure legends can be longer than the titles of tables. However, they should not be excessively long.}
-\label{Fig:OkapiHorn}
+\includegraphics{Univariate-Fitness-Landscapes-1.png}
+\caption{Selection gradients acting on \texit{Iteomyia} traits in complex vs.
+simple food webs.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); clutch size (B); and female preference (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
+Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples.}
+\label{Fig:FL_1D}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics{Multivariate-Fitness-Landscapes-1.png}
+\caption{Fitness landscapes of gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and chamber diameter (A); clutch size and female preference (B); female preference and chamber diameter (C).
+Note that traits for all plots range 1 SD below and above the mean (=0).}
+\label{Fig:FL_2D}
 \end{figure}

### 2018-09-25 analyses/reproduce_analyses.Rmd
removed paired t-test approach for quantifying bias in selection on gall diameter. I'm favoring a different approach that is aligned with the analyses I'm doing for selection gradients.

@@
   scale_shape_manual(name="Bias\nadjusted", values=c(21,23))
-```
-
-```{r Confounding effects of parasitism on gall size, include=FALSE, eval=FALSE}
-## paired t-test approach. Weakness is that it only calculates the selection differential rather than the gradient, which is more meaningful for multivariate trait evolution
-pair_df <- gall_selection.df %>%
-  group_by(Foodweb, Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Foodweb, Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Foodweb, Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(diff_sc.Diam ~ Foodweb, pair_df)
-t.test(pair_df$survive_mean_sc.Diam, pair_df$all_mean_sc.Diam, paired = T)
-
-complex_pair_df <- gall_selection.df %>%
-  filter(Foodweb=="Complex") %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(complex_pair_df$survive_mean_sc.Diam, complex_pair_df$all_mean_sc.Diam, paired = T)
-
-ectos_pair_df <- gall_selection.df %>%
-  filter(Foodweb=="Complex" & platy < 1) %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(ectos_pair_df$survive_mean_sc.Diam, ectos_pair_df$all_mean_sc.Diam, paired = T)
-
-simple_pair_df <- gall_selection.df %>%
-  filter(Foodweb=="Simple") %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  select(Gall_Number, mean_survival, gall_survival, sc.Diam) %>%
-  # calculate mean phenotype at gall level (before selection)
-  mutate(all_mean_sc.Diam = mean(sc.Diam)) %>%
-  # then filter surviving galls and calculate the mean phenotype (after selection)
-  filter(gall_survival == 1) %>%
-  mutate(survive_mean_sc.Diam = mean(sc.Diam)) %>%
-  # only retain distinct data points and calculate the difference (selection differential)
-  distinct(Gall_Number, all_mean_sc.Diam, survive_mean_sc.Diam) %>%
-  mutate(diff_sc.Diam = survive_mean_sc.Diam - all_mean_sc.Diam)
-t.test(simple_pair_df$survive_mean_sc.Diam, simple_pair_df$all_mean_sc.Diam, paired = T)
-
-## selection gradient approach
-confounding_df <- gall_selection.df %>%
-  group_by(Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1)
-
-confounding_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
-                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = confounding_df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-summary(confounding_glmer)
-
-## Replicate GLMM tests but with this confounding factor dataset ----
-
-# No effects
-drop1(confounding_glmer, test="Chisq")
-summary(confounding_glmer)
-
-# No effects on nonlinear selection acting on gall diameter, but also there is not much evidence for any effects.
-confounding_glmer_2 <- update(confounding_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(confounding_glmer_2, test="Chisq") 
-summary(confounding_glmer_2)
-
-# Evidence of food-web treatment altering directional selection on clutch size; marginal evidence of correlational selection acting on gall size and clutch size.
-confounding_glmer_3 <- update(confounding_glmer_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(confounding_glmer_3, test="Chisq") 
-summary(confounding_glmer_3)
-
-# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; evidence of directional selection acting on female preference
-confounding_glmer_4 <- update(confounding_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(confounding_glmer_4, test="Chisq") 
-summary(confounding_glmer_4)
-
-fixef(foodweb_glmer_4)["sc.Diam"] - fixef(confounding_glmer_4)["sc.Diam"]
-
-confounding_predict <- predict(foodweb_glmer, type="response") # not subsetting the data to complex or simple food webs, since we didn't find a difference in this subset
-confounding_mean_brackets <- mean(confounding_predict * (1 - confounding_predict))
-confounding_mean_fitness <- mean(confounding_predict)
-
-# alternatively, this suggest that we are overestimating the selection gradient by this much...
-round(confounding_mean_brackets * fixef(confounding_glmer_4)["sc.Diam"] / confounding_mean_fitness, 3)
-
-diam_glmer <- glmer(gall_survival ~ Foodweb + sc.Diam +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = gall_selection.df,
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-# note that the selection gradient and differential are virtually the same for gall diameter, given the similarity in their alpha coefficients.
-fixef(diam_glmer)["sc.Diam"]
-fixef(foodweb_glmer_4)["sc.Diam"]
-
-# selection differentials
-round(complex_mean_brackets * fixef(diam_glmer)["sc.Diam"] / complex_mean_fitness, 3)
-round(simple_mean_brackets * fixef(diam_glmer)["sc.Diam"] / simple_mean_fitness, 3)
 ```

### 2018-10-08 To_Do.Rmd
update of current analyses

---
title: "To_Do"
author: "Matt Barbour"
date: "8/1/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Top Priority

> Decide on which target journal to submit to.

> Output regression stats for the absence of an effect of food-web on larval survival for chamber diameter and female preference.

> Update model_4 to give separate effects of food-web complexity on larval survival.

> Translate required data and figures to main manuscript.

> Write, write, write!!!

## Lower Priority

> if I want to include host plant effects, I need to exclude chamber diameter as a phenotype under selection by the plant. including it would further confound selection on Chamber diameter since none-none larva are found in smaller galls.

> Filter to get G-matrices at the end of each simulation, then compare differences in how the selective environment alters the evolvability of those populations.

> Put statistical analyses in the supplement to show that there was no differences in phenotypes among the food-web treatments.

> Modify color of figures for illustration of simple and complex food webs and make uncompressed.

### 2018-10-08 analyses/reproduce_analyses.Rmd
update of current analyses

@@
 ## Load required libraries ----
+library(evolqg) # need to load before dplyr
 library(car)        # for homogeneity of variance test
@@
 library(stringr)
+library(MVN)        # assessing multivariate normality assumption
 
@@
          sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
-         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots))),
-         sc.DiamPoly1 = poly(sc.Diam,2)[,1],
-         sc.DiamPoly2 = poly(sc.Diam,2)[,2],
-         sc.log.ClutchPoly1 = poly(sc.log.Clutch,2)[,1],
-         sc.log.ClutchPoly2 = poly(sc.log.Clutch,2)[,2],
-         sc.log1p.PrefPoly1 = poly(sc.log1p.Pref,2)[,1],
-         sc.log1p.PrefPoly2 = poly(sc.log1p.Pref,2)[,2])
+         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots))))
 
@@
 inverse_logit <- function(x) exp(x)/(1+exp(x))
-
-## Compute the matrix describing the curvature of the fitness landscape
-curvature_fitness.landscape <- function(gammas, # matrix of nonlinear and correlational selection gradients 
-                                        betas){ # vector of directional selection gradients
-  gammas - betas %*% t(betas)
-}
 
@@
 
+## Predicting evolutionary dynamics 
+evolutionary_dynamics <- function (betas,    # one-column matrix of directional selection gradients
+                                   gammas,   # matrix of nonlinear selection gradients
+                                   G_0,      # initial G-matrix
+                                   z_0,      # one-column matrix of initial trait values
+                                   t) {       # evolutionary time steps 
+    # Equation 2 from Phillips and Arnold 1989, Evolution
+    G <- rep(list(G_0), t) 
+    for (i in 1:t) G[[i + 1]] <- {
+      G[[i]] + G[[i]] %*% (gammas - betas %*% t(betas)) %*% G[[i]] # may need to add mutation/recombination matrix (see Phillips and Arnold 1989)
+    }
+
+    # Equation 1 from Phillips and Arnold 1989, Evolution
+    z <- rep(list(z_0), t) 
+    for (i in 1:t) z[[i + 1]] <- {
+        z[[i]] + G[[i]] %*% betas
+    }
+    return(list(z=z,G=G))
+}
+
+## Number of evolutionary time steps for simulation
+n_evo_sims <- 200 # 1000
+
+## Tidy up evolutionary simulations
+tidy_evo_sims <- function(evo_sims) {
+  tidy_sim <- data.frame(matrix(unlist(evo_sims$z), ncol=3, byrow=T)) %>% 
+    transmute(Time=1:length(evo_sims$z), Diam=round(X1,2), Clutch=round(X2,2), Pref=round(X3,2)) %>%
+    filter(Diam < 1, Diam > -1, Clutch < 1, Clutch > -1, Pref < 1, Pref > -1)
+
+  return(tidy_sim)
+}
+
 ## Color palette
@@
 
+```
+
+# Evaluating assumption of multivariate normality
+
+We used graphical checks to evaluate whether our transformations of traits resulted in a multivariate normal distribution.
+As you can see from the multivariate qq-plot, it seems reasonable that our data approximates a multivariate normal distribution.
+Of course, statistical tests suggest otherwise.
+But as an example of how silly these tests can be, look at the distribution of gall diameter.
+It is the closest ecological variable I've ever seen that is normally distributed, yet a Shapiro-Wilks test says otherwise.
+
+```{r MVN Assumption, echo=FALSE}
+
+mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.log1p.Pref), multivariatePlot = "qq", univariatePlot = "histogram")
+
+# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.log1p.Pref), multivariatePlot = "qq")
+
+mvn_assumption$univariateNormality[1, ]
 ```
@@
 
-```{r Boot Adjusted Model 2 for accurate slope estimates}
+```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE}
 boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Fit Model 4}
+```{r Fit Model 4, cache=TRUE}
 model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
@@
 As we did with model 2, we refit the model by removing the slope term so that we can fit different slopes for each interaction term. 
-```{r Fit Model 4 adjusted for estimating clutch slopes}
+```{r Fit Model 4 adjusted for estimating clutch slopes, cache=TRUE}
 model_4_adj <- update(model_4, .~. -sc.log.Clutch)
@@
 
-```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE}
+```{r Plot effect of Egg vs. Larval Parasitoid adjusted Model 2, echo=FALSE}
 tidy_egg.larval_model_2_adj$term_plot <- factor(tidy_egg.larval_model_2_adj$term,
@@
 
-```{r Fit Egg vs. Larval Parasitoid Model 4}
+```{r Fit Egg vs. Larval Parasitoid Model 4, cache=TRUE}
 egg.larval_model_4 <- update(model_4, data=egg.vs.larval_df)
@@
 
-```{r Fit Egg vs. Larval Parasitoid adjusted Model 4}
+```{r Fit Egg vs. Larval Parasitoid adjusted Model 4, cache=TRUE}
 egg.larval_model_4_adj <- update(model_4_adj, data=egg.vs.larval_df)
@@
 
-```{r Redo selection gradients}
+```{r Redo selection gradients, include=FALSE}
 bias.adj_selection_gradients <- mutate(selection_gradients, adjusted = "No") %>%
@@
 For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
-```{r Selection on Platygaster Traits, include=FALSE, eval=FALSE}
+```{r Selection on Platygaster Traits, cache=TRUE}
+
+## Subset the data to analyse change in gall phenotypes associated with Platygaster
 platy_selection_df <- gall_selection.df %>%
@@
 
+## Linear mixed models of linear selection differentials (change in mean phenotype)
 platy_Diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), platy_selection_df)
-summary(platy_Diam)
-Anova(platy_Diam, test.statistic = "F")
 
 platy_Clutch <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), platy_selection_df)
-summary(platy_Clutch)
-Anova(platy_Clutch, test.statistic = "F")
 
 platy_Pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), platy_selection_df)
-summary(platy_Pref)
-Anova(platy_Pref, test.statistic = "F")
-
-## Test whether food-web complexity influences nonlinear selection with Levene's test for homogeneity of variance between groups
+
+## Levene's test for quadratic selection differentials (change in phenotypic variance)
 # Note that this result should be interepreted cautiously since we cannot account for non-independence due to plant genotype, plant ID, or gall ID
-leveneTest(sc.Diam ~ Foodweb, platy_selection_df)
-leveneTest(sc.log.Clutch ~ Foodweb, platy_selection_df)
-leveneTest(sc.log1p.Pref ~ Foodweb, platy_selection_df)
-
-ggplot(platy_selection_df, aes(x=Foodweb, y=sc.Diam)) +
-  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
-  stat_summary(fun.y="mean", geom="point", color="black", size=3)
-
-ggplot(platy_selection_df, aes(x=Foodweb, y=sc.log.Clutch)) +
-  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
-  stat_summary(fun.y="mean", geom="point", color="black", size=3)
-
-ggplot(platy_selection_df, aes(x=Foodweb, y=sc.log1p.Pref)) +
-  stat_summary(fun="mean_cl_boot", geom="errorbar", color="red", width=0.1) +
-  stat_summary(fun.y="mean", geom="point", color="black", size=3)
+platy_Diam_levene <- leveneTest(sc.Diam ~ Foodweb, platy_selection_df)
+platy_Clutch_levene <- leveneTest(sc.log.Clutch ~ Foodweb, platy_selection_df)
+platy_Pref_levene <- leveneTest(sc.log1p.Pref ~ Foodweb, platy_selection_df)
+```
+
+```{r Plot models of Platygaster selection differentials, echo=FALSE}
+visreg_platy_Diam <- visreg(platy_Diam, xvar="Foodweb", gg=TRUE) + ylab("Chamber diameter (SD)") + xlab("")
+visreg_platy_Clutch <- visreg(platy_Clutch, xvar="Foodweb", gg=TRUE) + ylab("Clutch size (SD)") + xlab("")
+visreg_platy_Pref <- visreg(platy_Pref, xvar="Foodweb", gg=TRUE) + ylab("Female preference (SD)") + xlab("")
+
+plot_grid(visreg_platy_Diam, visreg_platy_Clutch, visreg_platy_Pref, align="hv", ncol=3)
+```
+
+```{r Calculate Selection Differentials for Platygaster, cache=TRUE, include=FALSE}
+
+## Calculation linear selection differentials
+boot_platy_Diam <- bootMer(platy_Diam, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+tidy_platy_Diam <- tidy(boot_platy_Diam, conf.int=T) %>% filter(term=="FoodwebComplex") %>% mutate(term="Diam")
+
+boot_platy_Clutch <- bootMer(platy_Clutch, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+tidy_platy_Clutch <- tidy(boot_platy_Clutch, conf.int=T) %>% filter(term=="FoodwebComplex") %>% mutate(term="Clutch")
+
+boot_platy_Pref <- bootMer(platy_Pref, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+tidy_platy_Pref <- tidy(boot_platy_Pref, conf.int=T) %>% filter(term=="FoodwebComplex") %>% mutate(term="Pref")
+
+platy_linear_selection <- bind_rows(tidy_platy_Diam, tidy_platy_Clutch, tidy_platy_Pref) %>% select(Term=term, Estimate=statistic, `2.5%`=conf.low, `97.5%`=conf.high)
+platy_linear_selection$Significance <- c("NS","NS","P < 0.05")
+
+## Calculate quadratic selection differentials
+# statistical significance is based on Levene's test of homogeneity of variances
+platy_quadratic_selection <- platy_selection_df %>%
+  group_by(Foodweb) %>%
+  summarise_at(c("sc.Diam","sc.log.Clutch","sc.log1p.Pref"), var) %>%
+  gather(key = Term, value = Variance, -Foodweb) %>%
+  spread(Foodweb, Variance) %>%
+  mutate(Estimate = Complex - Simple) %>%
+  select(Term, Estimate)
+platy_quadratic_selection$Term <- c("Diam^2","Pref^2","Clutch^2")
+platy_quadratic_selection$Significance <- c("NS","P < 0.05","NS")
+```
+
+```{r Table of Platygaster selection differentials, echo=FALSE}
+platy_selection_differentials <- bind_rows(platy_linear_selection, platy_quadratic_selection)
+
+knitr::kable(platy_selection_differentials, caption="Table of selection differentials acting on the egg parasitoid Platygaster")
+```
+
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0))
+
+RF_Diam <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Diam,
+  bootstraps=n_boots_plots)
+
+# Control ----
+#RF_control_gall_size <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = seq(-1,1,length.out=1000), 
+#     sc.log.clutch_size = 0,
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+
+# Treatment ----
+#RF_treatment_gall_size <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = seq(-1,1,length.out=1000),
+#     sc.log.clutch_size = 0,
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+```
+
+```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE}
+newdata_Clutch <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0))
+
+RF_Clutch <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Clutch,
+  bootstraps=n_boots_plots)
+
+# Control ----
+#RF_control_clutch_size <- bootstrap_fitness(
+#  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000),
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+
+# Treatment ----
+#RF_treatment_clutch_size <- bootstrap_fitness(
+#  logistic_model = model_2, #quad_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000),
+#     sc.log1p.female_preference = 0),
+#  bootstraps=n_boots_plots)
+```
+
+```{r Get Female Preference Fitness Landscape, cache=TRUE, include=FALSE}
+
+newdata_Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
+
+RF_Pref <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Pref,
+  bootstraps=n_boots_plots)
+
+# Control ----
+#RF_control_female_preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = 0, 
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=n_boots_plots)
+
+# Treatment ----
+#RF_treatment_female_preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = 0,
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=n_boots_plots)
+
+```
+
+```{r Get Clutch Size x Female Preference Landscape, cache=TRUE, include=FALSE}
+
+newdata_Clutch.Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)))
+
+RF_Clutch.Pref <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Clutch.Pref,
+  bootstraps=NULL)
+
+# Control ----
+#RF_control_clutch.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000), 
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=NULL)
+
+# Treatment ----
+#RF_treatment_clutch.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+#  newdata = expand.grid(
+#     sc.gall_size = 0,
+#     sc.log.clutch_size = seq(-1,1,length.out=1000),
+#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+#  bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam.Clutch <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref=0))
+
+RF_Diam.Clutch <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Diam.Clutch,
+  bootstraps=NULL)
+
+# Control ----
+#RF_control_size.x.clutch <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+ # newdata = expand.grid(
+  #   sc.gall_size = seq(-1,1,length.out=1000),
+   #  sc.log.clutch_size = seq(-1,1,length.out=1000), 
+    # sc.log1p.female_preference = 0), 
+  #bootstraps=NULL)
+
+# Treatment ----
+#RF_treatment_size.x.clutch <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+ # newdata = expand.grid(
+  #   sc.gall_size = seq(-1,1,length.out=1000),
+   #  sc.log.clutch_size = seq(-1,1,length.out=1000),
+    # sc.log1p.female_preference = 0), 
+  #bootstraps=NULL)
+```
+
+```{r Get Gall Diameter x Female Preference Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam.Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
+
+RF_Diam.Pref <- bootstrap_fitness(
+  logistic_model = model_2, #quad_control, 
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  newdata = newdata_Diam.Pref,
+  bootstraps=NULL)
+
+# Control ----
+#RF_control_size.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+#  newdata = expand.grid(
+ #    sc.gall_size = seq(-1,1,length.out=1000),
+  #   sc.log.clutch_size = 0, 
+   #  sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  ##bootstraps=NULL)
+
+# Treatment ----
+#RF_treatment_size.x.preference <- bootstrap_fitness(
+#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
+  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
+ # newdata = expand.grid(
+  #   sc.gall_size = seq(-1,1,length.out=1000),
+   #  sc.log.clutch_size = 0,
+    # sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
+  #bootstraps=NULL)
+```
+
+```{r Fitness Landscape Plot Helpers, include=FALSE}
+
+## Scale relative fitness across plots ----
+
+# 1D
+#RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
+#          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
+#          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
+#  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
+#  gather(ID, relative_fitness, -sc.gall_size) %>%
+#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+#  summarise(min = min(relative_fitness), max = max(relative_fitness))
+#RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
+
+# 2D
+#RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
+#          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
+#          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
+#  summarise(min = min(average), max = max(average))
+
+## Scale absolute fitness across plots ----
+
+# 1D
+AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
+
+# 2D
+AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+```
+
+```{r Plot Univariate Landscapes, include=FALSE}
+uni_breaks <- c(0.1,0.5,1.0)
+
+# Gall size 
+AF_uni_Diam <- RF_Diam$absolute_fitness %>% #bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.log.Clutch, -sc.log1p.Pref) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Mean larva survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
+  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
+#AF_uni_size
+  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
+
+# Clutch size
+AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% #bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.Diam, -sc.log1p.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Mean larva survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
+  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
+
+# Female preference
+AF_uni_Pref <- RF_Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
+          #mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.log1p.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log1p.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Female preference (SDs)") +
+  ylab("Mean larva survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
+  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
+```
+
+```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
+Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
+
+# Get legend
+AF_uni_legend <- get_legend(AF_uni_Diam)
+
+# Make plots
+AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none", 
+                                              axis.text.x = element_text(size=10),
+                                              axis.title.x = element_text(size=11)), 
+                       AF_uni_Clutch + theme(legend.position = "none",
+                                             axis.title.y = element_blank(), 
+                                             #axis.text.y = element_blank(),
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                       AF_uni_Pref + theme(legend.position = "none", 
+                                           axis.title.y = element_blank(), 
+                                           #axis.text.y = element_blank(), 
+                                           axis.text.x = element_text(size=10),
+                                           axis.title.x = element_text(size=11)),
+                       labels = "AUTO", ncol = 3, align='hv')
+
+AF_gradients <- plot_grid(AF_uni_plots, AF_uni_legend, ncol = 2, rel_widths = c(1,0.2)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
+AF_gradients
+#AF_uni_plots
+# save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
+#save_plot("../figures/fitness_landscapes_1D.png", AF_gradients)#, base_height=6, base_width = 8)
+```
+
+```{r Plot Multivariate Fitness Landscape, include=FALSE}
+
+my_breaks <- c(0.2,0.4,0.6,0.8)
+
+# Size x Clutch
+AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
+  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
+  geom_raster(aes(fill=average)) +
+  facet_wrap(~Foodweb) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
+
+# Size x Preference
+AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
+  ggplot(., aes(x=sc.Diam, y=sc.log1p.Pref)) +
+  geom_raster(aes(fill=average)) +
+  facet_wrap(~Foodweb) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Female preference (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
+
+# Clutch x Preference
+AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
+  ggplot(., aes(x=sc.log1p.Pref, y=sc.log.Clutch)) +
+  geom_raster(aes(fill=average)) +
+  facet_wrap(~Foodweb) +
+  xlab("Female preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) 
+```
+
+```{r Multivariate-Fitness-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C).
+Note that traits for all plots range 1 SD below and above the mean (=0)."}
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_Diam.Pref)
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_Diam.Clutch + theme(legend.position = "none", 
+                              axis.title.y = element_text(size=11),
+                              axis.title.x = element_blank(),
+                              axis.text = element_text(size=10)),
+  AF_plot_Clutch.Pref + theme(legend.position = "none", 
+                              axis.title.y = element_blank(), 
+                              axis.text = element_text(size=10), 
+                              axis.title.x = element_text(size=11)),
+  AF_plot_Diam.Pref + theme(legend.position = "none", 
+                            axis.text = element_text(size=10),
+                            axis.title = element_text(size=11)), 
+  nrow=2, align="hv", labels = "AUTO")
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
+#save_plot("../figures/fitness_landscapes_2D.png", AF_landscape_2d)#, base_height=6, base_width = 8)
 ```
@@
 
-```{r Slope and Curvature of Fitness Landscape, include=FALSE, eval=FALSE}
-betas <- c(-0.5,-0.5,0.5)
-gammas_matrix <- matrix(c(-0.1, 0.0, 0.0,
-                          0.0, -0.1, 0.0,
-                          0.0, 0.0, -0.1), 
-                        nrow=3, byrow=T)
-
-## G-matrix ----
-# (1) Asssume equal additive genetic variance for all three traits
-# (2) Assume no additive genetic covariance
-# The first assumption may not be realistic, but violations of this assumption will not qualitatively alter our inferences about whether additive genetic variance will increase or decrease.
-Qualitative changes in additive genetic variance is only determined by the curvature of the fitness landscape.
-Violations of this assumption will only affect the rate of phenotypic evolution and magnitude of change in genetic variance.
-# The second assumption may also not be realistic; however, it will not affect our results because we found no evidence of correlational selection (therefore, there can be no change in genetic covariance).
-G_matrix <- matrix(c(1.0, 1.0, 1.0,
-                     1.0, 1.0, 1.0,
-                     1.0, 1.0, 1.0),
-                   nrow=3, byrow=T)
-
-# Equation 1 from Phillips and Arnold 1989, Evolution
-delta_z <- G_matrix %*% betas
-data.frame(trait = c("diam","clutch","pref"),
-           delta_z = delta_z)
-
-# Equation 2 from Phillips and Arnold 1989, Evolution
-delta_G <- G_matrix * (gammas_matrix - betas %*% t(betas)) * G_matrix
-delta_G
-```
-
-```{r LATEX NEED TO CHECK, eval=FALSE, include=FALSE}
-$$\text{Slope}_{complex} = \beta_{complex} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.4 \\ 0 \\ -0.3 \end{pmatrix}$$
-$$\text{Slope}_{simple} = \beta_{simple} = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} = \begin{pmatrix} 0.3 \\ -0.2 \\ -0.3 \end{pmatrix}$$
-$$\gamma_{complex} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&-0.3 \end{pmatrix}$$
-$$\gamma_{simple} = \begin{pmatrix} \gamma_{diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref} \end{pmatrix} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-$$\text{Curvature} = \gamma - \beta \beta^T$$
-$$\text{Curvature}_{complex} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-$$\text{Curvature}_{simple} = \begin{pmatrix} 0.1&& \\ 0&0& \\ 0&0&0 \end{pmatrix}$$
-```
-
-```{r Effects of platy vs. ecto on absolute fitness, cache=TRUE, include=FALSE, eval=FALSE}
-
-## Fit GLMM
-
-platyecto_glmer <- glmer(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
-                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-                         (1|Genotype/Plant_Position/Gall_Number),
-                       data = filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1), # exclude cases of egg-parasitism from Complex food web
-                       family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-## Test for overdispersion
-overdisp_fun(platyecto_glmer) # no evidence
-
-## Compare statistical summaries of each model
-summary(platyecto_glmer)
-piecewiseSEM::rsquared(platyecto_glmer)
-
-## Parse out mechanisms of food-web effects ----
-# Use drop1 to test highest order effects and visreg to visualize the effects
-
-# Marginal evidence that larval parasitoids are the drivers of nonlinear selection acting on female preference (disruptive selection)
-drop1(platyecto_glmer, test="Chisq")
-summary(platyecto_glmer)
-visreg::visreg(platyecto_glmer, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
-
-# Marginal evidence of nonlinear selection acting on gall size. Marginal evidence of correlational selection acting on all traits.
-platyecto_glmer_2 <- update(platyecto_glmer, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(platyecto_glmer_2, test="Chisq") 
-visreg::visreg(platyecto_glmer_2, xvar="sc.Diam", scale = "response") 
-# plot 3-way interaction?
-
-# Evidence of food-web treatment altering directional selection on clutch size
-platyecto_glmer_3 <- update(platyecto_glmer_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(platyecto_glmer_3, test="Chisq") 
-summary(platyecto_glmer_3)
-visreg::visreg(platyecto_glmer_3, xvar="sc.log.Clutch", by="Foodweb", scale="response") # conflicting selection have net null effects in complex food web
-
-# No evidence of clear fitness effects of platy vs.
-ectos on absolute fitness; evidence of directional selection acting on gall size; no evidence of directional selection on clutch size (in complex food web); evidence of directional selection acting on female preference
-platyecto_glmer_4 <- update(platyecto_glmer_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(platyecto_glmer_4, test="Chisq") 
-summary(platyecto_glmer_4)
-visreg::visreg(platyecto_glmer_4, xvar="Foodweb", scale="response")
-visreg::visreg(platyecto_glmer_4, xvar="sc.Diam", scale="response")
-visreg::visreg(platyecto_glmer_4, xvar="sc.log.Clutch", scale="response")
-visreg::visreg(platyecto_glmer_4, xvar="sc.log1p.Pref", scale="response")
-```
-
-```{r For platy ecto comparison, include=FALSE, eval=FALSE}
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
-complex_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(platyecto_glmer_2, newdata=filter(gall_selection.df, Foodweb == "Complex" & platy < 1), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-complex_mean_brackets - alt_mean_brackets
-complex_mean_fitness - alt_mean_fitness
-
-platyecto_tidy_4 <- filter(tidy(platyecto_glmer_4, conf.int=T), term %in% c("(Intercept)","FoodwebSimple"))
-platyecto_tidy_3 <- filter(tidy(platyecto_glmer_3, conf.int=T), 
-                         term %in% c("sc.Diam","sc.log.Clutch","sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-platyecto_tidy_2 <- filter(tidy(platyecto_glmer_2, conf.int=T), 
-                         term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-platyecto_tidy <- filter(tidy(platyecto_glmer, conf.int=T), 
-                       term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                                   "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                                   "sc.Diam:sc.log.Clutch:sc.log1p.Pref",
-                                   "FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-## These alphas aren't the appropriate comparison, this is because when there is no interaction term, then the average is taken across all of the food webs.
-This is okay for testing the statistical significance, but not appropriate when I want to actually compare the magnitudes of the alphas and betas
-#platyecto_tidy_4 <- filter(tidy(platyecto_glmer_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
-#platyecto_tidy_3 <- filter(tidy(platyecto_glmer_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-#platyecto_tidy_2 <- filter(tidy(platyecto_glmer_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-#platyecto_tidy <- filter(tidy(platyecto_glmer), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-
-get_alphas <- bind_rows(platyecto_tidy_4, platyecto_tidy_3, platyecto_tidy_2, platyecto_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
-  select(term, alpha, alpha_2.5, alpha_97.5, P)
-
-complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
-simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-coefs_gradients <- data.frame(Variable = complex_alphas$term, 
-           a_complex = complex_alphas$alpha,
-           a_complex_2.5 = complex_alphas$alpha_2.5,
-           a_complex_97.5 = complex_alphas$alpha_97.5,
-           a_simple = complex_alphas$alpha + simple_alphas$alpha,        # the baseline is the coefficient in the complex food web, therefore we simply add the corresponding coefficients from the simple food web to get the coefficients on the same scale as the complex web
-           a_simple_2.5 = complex_alphas$alpha + simple_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_simple_97.5 = complex_alphas$alpha + simple_alphas$alpha_97.5) %>% 
-  mutate(b_complex = round(complex_mean_brackets * a_complex / complex_mean_fitness, 3),
-         b_complex_2.5 = round(complex_mean_brackets * a_complex_2.5 / complex_mean_fitness, 3),
-         b_complex_97.5 = round(complex_mean_brackets * a_complex_97.5 / complex_mean_fitness, 3),
-         b_simple = round(simple_mean_brackets * a_simple / simple_mean_fitness, 3),
-         b_simple_2.5 = round(simple_mean_brackets * a_simple_2.5 / simple_mean_fitness, 3),
-         b_simple_97.5 = round(simple_mean_brackets * a_simple_97.5 / simple_mean_fitness, 3)) %>%
-  filter(Variable != "(Intercept)")
-
-select(coefs_gradients, Variable, a_complex:a_simple_97.5)
-select(coefs_gradients, Variable, b_complex:b_simple_97.5)
-
-bind_rows(mutate(select(coefs_gradients, Variable, a=a_complex, a_2.5=a_complex_2.5, a_97.5=a_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, a=a_simple, a_2.5=a_simple_2.5, a_97.5=a_simple_97.5), Foodweb = "Simple")) %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-bind_rows(mutate(select(coefs_gradients, Variable, b=b_complex, b_2.5=b_complex_2.5, b_97.5=b_complex_97.5), Foodweb = "Complex"),
-          mutate(select(coefs_gradients, Variable, b=b_simple, b_2.5=b_simple_2.5, b_97.5=b_simple_97.5), Foodweb = "Simple")) %>%
-  ggplot(., aes(x = Variable, fill=Foodweb, color=Foodweb)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted")
-
-inverse_logit(complex_alphas$alpha[1]) - complex_mean_fitness # small difference in mean fitness estimates compared to intercept in complex food web
-inverse_logit(complex_alphas$alpha[1] + simple_alphas$alpha[1]) - simple_mean_fitness # larger difference in mean fitness estimates from intercept in simple food web, unclear why...perhaps because the mean phenotypes don't match up as nicely?
-```
-
-```{r include=FALSE, eval=FALSE}
-## Calculating same coefficients as for simple vs. complex food web
-
-## Estimate mean fitness and mean brackets (ref: Janzen and Stern 1998)
-ecto_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Complex" & platy < 1), type="response")
-ecto_mean_brackets <- mean(ecto_predict * (1 - ecto_predict))
-ecto_mean_fitness <- mean(ecto_predict)
-
-platy_predict <- predict(platyecto_glmer, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-platy_mean_brackets <- mean(platy_predict * (1 - platy_predict))
-platy_mean_fitness <- mean(platy_predict)
-
-# test whether using alternative models influences estimes of mean "brackets" and mean fitness 
-alt_predict <- predict(platyecto_glmer_2, newdata=filter(gall_selection.df, Foodweb=="Complex" & platy < 1), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-ecto_mean_brackets - alt_mean_brackets
-ecto_mean_fitness - alt_mean_fitness
-
-# Altering so that coefficients that differed between food webs are reported, but ones that weren't are simply reported as there baselines.
-# Added multiplier column so that quadratic (nonlinear) selection coefficients can be multiplied by 2 for fair comparison
-platyecto_tidy_4 <- tidy(platyecto_glmer_4, conf.int=T) %>%
-  filter(term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log1p.Pref")) %>%
-  mutate(platyecto = c("ecto","platy","Common","Common"),
-         Selection_form = c(NA,NA,"Directional","Directional"),
-         Multiplier = c(1,1,1,1))
-
-platyecto_tidy_3 <- tidy(platyecto_glmer_3, conf.int=T) %>%
-  filter(term %in% c("sc.log.Clutch","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch")) %>%
-  mutate(platyecto = c("ecto","Common","Common","Common","platy"),
-         Selection_form = c("Directional","Correlational","Correlational","Correlational","Directional"),
-         Multiplier = c(1,1,1,1,1))
-
-platyecto_tidy_2 <- tidy(platyecto_glmer_2, conf.int=T) %>%
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref")) %>%
-  mutate(platyecto = c("Common","Common","Common"),
-         Selection_form = c("Nonlinear","Nonlinear","Correlational"),
-         Multiplier = c(2,2,1))
-
-platyecto_tidy <- tidy(platyecto_glmer, conf.int=T) %>%
-  filter(term %in% c("I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)")) %>%
-  mutate(platyecto = c("ecto","platy"),
-         Selection_form = c("Nonlinear","Nonlinear"),
-         Multiplier = c(2,2))
-
-get_platyecto_alphas <- bind_rows(platyecto_tidy_4, platyecto_tidy_3, platyecto_tidy_2, platyecto_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_2.5 = round(conf.low, 3), alpha_97.5 = round(conf.high, 3), P = round(p.value, 3)) %>%
-  select(term, platyecto, alpha, alpha_2.5, alpha_97.5, P, Selection_form, Multiplier)
-
-ecto_alphas <- filter(get_platyecto_alphas, platyecto == "ecto"); ecto_alphas
-platy_alphas <- filter(get_platyecto_alphas, platyecto == "platy"); platy_alphas
-common_platyecto_alphas <- filter(get_platyecto_alphas, platyecto == "Common"); common_platyecto_alphas
-
-coefs_gradients.ecto_platy <- data.frame(Variable = ecto_alphas$term, 
-           a_ecto = ecto_alphas$alpha,
-           a_ecto_2.5 = ecto_alphas$alpha_2.5,
-           a_ecto_97.5 = ecto_alphas$alpha_97.5,
-           a_platy = ecto_alphas$alpha + platy_alphas$alpha,        # the baseline is the coefficient in the ecto food web, therefore we simply add the corresponding coefficients from the platy food web to get the coefficients on the same scale as the ecto web
-           a_platy_2.5 = ecto_alphas$alpha + platy_alphas$alpha_2.5, # same addition process for confidence intervals
-           a_platy_97.5 = ecto_alphas$alpha + platy_alphas$alpha_97.5,
-           Selection_form = ecto_alphas$Selection_form,                # doesn't matter whether platy_ or ecto_alphas is chosen for Selection_form or Multiplier
-           Multiplier = ecto_alphas$Multiplier) %>%                     
-  mutate(b_ecto = round(ecto_mean_brackets * a_ecto / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_2.5 = round(ecto_mean_brackets * a_ecto_2.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_97.5 = round(ecto_mean_brackets * a_ecto_97.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_platy = round(platy_mean_brackets * a_platy / platy_mean_fitness, 3) * Multiplier,
-         b_platy_2.5 = round(platy_mean_brackets * a_platy_2.5 / platy_mean_fitness, 3) * Multiplier,
-         b_platy_97.5 = round(platy_mean_brackets * a_platy_97.5 / platy_mean_fitness, 3) * Multiplier)
-
-coefs_gradients.ecto_platy.common <- data.frame(Variable = common_platyecto_alphas$term, 
-           a_ecto = common_platyecto_alphas$alpha,
-           a_ecto_2.5 = common_platyecto_alphas$alpha_2.5,
-           a_ecto_97.5 = common_platyecto_alphas$alpha_97.5,
-           a_platy = common_platyecto_alphas$alpha,        
-           a_platy_2.5 = common_platyecto_alphas$alpha_2.5, 
-           a_platy_97.5 = common_platyecto_alphas$alpha_97.5,
-           Selection_form = common_platyecto_alphas$Selection_form,
-           Multiplier = common_platyecto_alphas$Multiplier) %>% 
-  # for the selection gradients though, calculate them on the scale of relative fitness for each food-web treatment
-  mutate(b_ecto = round(ecto_mean_brackets * a_ecto / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_2.5 = round(ecto_mean_brackets * a_ecto_2.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_ecto_97.5 = round(ecto_mean_brackets * a_ecto_97.5 / ecto_mean_fitness, 3) * Multiplier,
-         b_platy = round(platy_mean_brackets * a_platy / platy_mean_fitness, 3) * Multiplier,
-         b_platy_2.5 = round(platy_mean_brackets * a_platy_2.5 / platy_mean_fitness, 3) * Multiplier,
-         b_platy_97.5 = round(platy_mean_brackets * a_platy_97.5 / platy_mean_fitness, 3) * Multiplier)
-
-coefs_gradients.ecto_platy <- bind_rows(coefs_gradients.ecto_platy, coefs_gradients.ecto_platy.common)
-
-bind_rows(mutate(select(coefs_gradients.ecto_platy, Variable, a=a_ecto, a_2.5=a_ecto_2.5, a_97.5=a_ecto_97.5), platyecto = "ecto"),
-          mutate(select(coefs_gradients.ecto_platy, Variable, a=a_platy, a_2.5=a_platy_2.5, a_97.5=a_platy_97.5), platyecto = "platy")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=platyecto, color=platyecto)) +
-  geom_point(aes(y=a), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = a_97.5, ymin = a_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  ylab("Regression coefficient")
-
-## Modify to be directional, nonlinear, then correlational with legend in 4th area.
-## Modify so that axes have gamma and beta with the trait as a subscript
-bind_rows(mutate(select(coefs_gradients.ecto_platy, Variable, b=b_ecto, b_2.5=b_ecto_2.5, b_97.5=b_ecto_97.5, Selection_form), platyecto = "ecto"),
-          mutate(select(coefs_gradients.ecto_platy, Variable, b=b_platy, b_2.5=b_platy_2.5, b_97.5=b_platy_97.5, Selection_form), platyecto = "platy")) %>%
-  filter(Variable != "(Intercept)") %>%
-  ggplot(., aes(x = Variable, fill=platyecto, color=platyecto)) +
-  geom_point(aes(y=b), position = position_dodge(width=0.5)) +
-  geom_errorbar(aes(ymax = b_97.5, ymin = b_2.5), position = position_dodge(width=0.5)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  facet_wrap(~Selection_form, nrow=2, scales = "free_y") +
-  ylab("Selection gradient")
-```
-
-Compared to the GLM, the GLMM gives the same inferences about the effect of food-web treatment.
-The main difference was that there was stronger evidence of correlational selection, but no evidence that this correlational selection varied among food-web treatments.
-Still, this stronger evidence for correlational selection should be interpreted with caution since the GLM does not account for the non-indepedence of these fitness estimates.
-```{r Compare GLMM to GLM, include=FALSE, eval=FALSE}
-## Fit GLMs. Dispersion parameter was ~1, so I just used a binomial model. 
-null_glm <- glm(gall_survival ~ sc.Diam*sc.log.Clutch*sc.log1p.Pref + 
-                      I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2),
-                    data = gall_selection.df,
-                    family = binomial(link = logit))
-
-foodweb_glm <- glm(gall_survival ~ Foodweb*(sc.Diam*sc.log.Clutch*sc.log1p.Pref +
-                         I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)),
-                       data = gall_selection.df,
-                       family = binomial(link = logit))
-
-## Compare statistical summaries of each model
-summary(null_glm)
-summary(foodweb_glm)
-piecewiseSEM::rsquared(null_glm)
-piecewiseSEM::rsquared(foodweb_glm)
-
-## Test statistical significance of effects ----
-
-# Overall, there is clear evidence that food-web treatment alters absolute fitness
-anova(null_glm, foodweb_glm, test = "Chisq")
-
-## Parse out mechanisms of food-web effects ----
-# Use drop1 to test highest order effects and visreg to visualize the effects
-
-# Evidence that food-web treatment alters nonlinear selection acting on female preference. Appears to be evidence for disruptive selection in complex food web.
-# Unique to GLM: marginal evidence for food-web treatment altering nonlinear selection on clutch size
-drop1(foodweb_glm, test="Chisq")
-visreg::visreg(foodweb_glm, xvar="sc.log1p.Pref", by="Foodweb", scale = "response") 
-visreg::visreg(foodweb_glm, xvar="sc.log.Clutch", by="Foodweb", scale = "response")
-
-# Evidence of nonlinear selection acting on gall size. No evidence of disruptive selection.
-# No unique effects in the glm
-foodweb_glm_2 <- update(foodweb_glm, .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.log1p.Pref^2) -Foodweb:sc.Diam:sc.log.Clutch:sc.log1p.Pref)
-drop1(foodweb_glm_2, test="Chisq") 
-visreg::visreg(foodweb_glm_2, xvar="sc.Diam", scale = "response")
-
-# Evidence of food-web treatment altering directional selection on clutch size
-# Unique to GLM: there is stronger support for correlational selection acting on gall size and clutch size; also, there is evidence for correlational selection acting on clutch size and female preference.
-foodweb_glm_3 <- update(foodweb_glm_2, .~.
--I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -sc.Diam:sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
-drop1(foodweb_glm_3, test="Chisq") 
-visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="Foodweb", scale="response")
-visreg::visreg(foodweb_glm_3, xvar="sc.Diam", by="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="sc.Diam", scale="response") # a different perspective
-visreg::visreg(foodweb_glm_3, xvar="sc.log1p.Pref", by="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glm_3, xvar="sc.log.Clutch", by="sc.log1p.Pref", scale="response")
-
-# Evidence that food-web treatment alters absolute fitness; evidence of directional selection acting on gall size; no evidence of directional selection on clutch size (in complex food web); evidence of directional selection acting on female preference
-# No unique effects in the glm
-foodweb_glm_4 <- update(foodweb_glm_3, .~. -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref -Foodweb:sc.Diam -Foodweb:sc.log.Clutch -Foodweb:sc.log1p.Pref)
-drop1(foodweb_glm_4, test="Chisq") 
-visreg::visreg(foodweb_glm_4, xvar="Foodweb", scale="response")
-visreg::visreg(foodweb_glm_4, xvar="sc.Diam", scale="response")
-visreg::visreg(foodweb_glm_4, xvar="sc.log.Clutch", scale="response")
-visreg::visreg(foodweb_glm_4, xvar="sc.log1p.Pref", scale="response")
-```
-
-```{r Get Selection Gradients for GLM, include=FALSE, eval=FALSE}
-complex_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(foodweb_glm, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-foodweb_tidy_4 <- filter(tidy(foodweb_glm_4), term %in% c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","sc.log1p.Pref"))
-foodweb_tidy_3 <- filter(tidy(foodweb_glm_3), term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"))
-foodweb_tidy_2 <- filter(tidy(foodweb_glm_2), term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch:sc.log1p.Pref","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"))
-foodweb_tidy <- filter(tidy(foodweb_glm), term %in% c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch:sc.log1p.Pref"))
-
-get_alphas <- bind_rows(foodweb_tidy_4, foodweb_tidy_3, foodweb_tidy_2, foodweb_tidy) %>% 
-  mutate(alpha = round(estimate, 3), alpha_SE = round(std.error, 3), P = round(p.value, 3)) %>%
-  select(term, alpha, alpha_SE, P)
-
-complex_alphas <- filter(get_alphas, !grepl("FoodwebSimple", term))
-simple_alphas <- filter(get_alphas, grepl("FoodwebSimple", term))
-
-# remember that the selection gradients need to be multiplied by 2 for quadratic gradients.
-data.frame(Variable = complex_alphas$term, 
-           alpha_complex = complex_alphas$alpha, 
-           alpha_simple = complex_alphas$alpha + simple_alphas$alpha) %>% # add the corresponding coefficients to get the coefficients on the same scale as the complex web)
-  mutate(beta_complex = round(complex_mean_brackets * alpha_complex / complex_mean_fitness, 3),
-         beta_simple = round(simple_mean_brackets * alpha_simple / simple_mean_fitness, 3)) %>%
-  filter(Variable != "(Intercept)")
-
-inverse_logit(complex_alphas$alpha[1]) - complex_mean_fitness # small difference in mean fitness estimates compared to intercept in complex food web
-inverse_logit(complex_alphas$alpha[1] + simple_alphas$alpha[1]) - simple_mean_fitness # larger difference in mean fitness estimates from intercept in simple food web, unclear why...perhaps because the mean phenotypes don't match up as nicely?
+Create a simple rule. If the confidence interval of the selection gradient overlaps zero, then I set it to zero. Otherwise, I set it to our best estimate of the gradient
+
+```{r Slope and Curvature of the Adaptive Landscape, include=FALSE}
+
+## Create beta-matrix for complex food-web treatment
+complex_betas_df <- bias.adj_selection_gradients %>%
+  filter(`Food web`=="Complex", term_ord %in% c("Pref","Clutch") | term_ord == "Diam" & adjusted=="Yes") %>% 
+  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
+rownames(complex_betas_df) <- complex_betas_df$term_ord
+
+complex_betas <- matrix(nrow = 3, ncol = 1, dimnames = list(c("Diam","Clutch","Pref"), c("")))
+complex_betas["Diam",] <- ifelse(complex_betas_df["Diam","low"]*complex_betas_df["Diam","high"] > 0, 
+                                        complex_betas_df["Diam","gradient"], 0)
+complex_betas["Clutch",] <- ifelse(complex_betas_df["Clutch","low"]*complex_betas_df["Clutch","high"] > 0,
+                                            complex_betas_df["Clutch","gradient"], 0)
+complex_betas["Pref",] <- ifelse(complex_betas_df["Pref","low"]*complex_betas_df["Pref","high"] > 0,
+                                        complex_betas_df["Pref","gradient"], 0)
+complex_betas <- round(complex_betas, 2)
+
+## Create gamma-matrix for complex food-web treatment
+complex_gammas_df <- bias.adj_selection_gradients %>%
+  filter(`Food web`=="Complex", term_ord %in% c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref")) %>% 
+  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
+rownames(complex_gammas_df) <- complex_gammas_df$term_ord
+
+complex_gammas <- matrix(nrow = 3, ncol = 3, dimnames = list(c("Diam","Clutch","Pref"), c("Diam","Clutch","Pref")))
+complex_gammas["Diam","Diam"] <- ifelse(complex_gammas_df["Diam^2","low"]*complex_gammas_df["Diam^2","high"] > 0, 
+                                        complex_gammas_df["Diam^2","gradient"], 0)
+complex_gammas["Clutch","Clutch"] <- ifelse(complex_gammas_df["Clutch^2","low"]*complex_gammas_df["Clutch^2","high"] > 0,
+                                            complex_gammas_df["Clutch^2","gradient"], 0)
+complex_gammas["Pref","Pref"] <- ifelse(complex_gammas_df["Pref^2","low"]*complex_gammas_df["Pref^2","high"] > 0,
+                                        complex_gammas_df["Pref^2","gradient"], 0)
+complex_gammas["Diam","Clutch"] <- ifelse(complex_gammas_df["Diam:Clutch","low"]*complex_gammas_df["Diam:Clutch","high"] > 0,
+                                          complex_gammas_df["Diam:Clutch","gradient"], 0)
+complex_gammas["Clutch","Diam"] <- complex_gammas["Diam","Clutch"]
+complex_gammas["Diam","Pref"] <- ifelse(complex_gammas_df["Diam:Pref","low"]*complex_gammas_df["Diam:Pref","high"] > 0,
+                                            complex_gammas_df["Diam:Pref","gradient"], 0)
+complex_gammas["Pref","Diam"] <- complex_gammas["Diam","Pref"]
+complex_gammas["Clutch","Pref"] <- ifelse(complex_gammas_df["Clutch:Pref","low"]*complex_gammas_df["Clutch:Pref","high"] > 0, 
+                                        complex_gammas_df["Clutch:Pref","gradient"], 0)
+complex_gammas["Pref","Clutch"] <- complex_gammas["Clutch","Pref"]
+complex_gammas <- round(complex_gammas, 2)
+
+## Create matrix of Betas in simple food-web treatment
+simple_betas_df <- bias.adj_selection_gradients %>%
+  filter(`Food web`=="Simple", term_ord %in% c("Pref","Clutch") | term_ord == "Diam" & adjusted=="Yes") %>% 
+  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
+rownames(simple_betas_df) <- simple_betas_df$term_ord
+
+simple_betas <- matrix(nrow = 3, ncol = 1, dimnames = list(c("Diam","Clutch","Pref"), c("")))
+simple_betas["Diam",] <- ifelse(simple_betas_df["Diam","low"]*simple_betas_df["Diam","high"] > 0, 
+                                        simple_betas_df["Diam","gradient"], 0)
+simple_betas["Clutch",] <- ifelse(simple_betas_df["Clutch","low"]*simple_betas_df["Clutch","high"] > 0,
+                                            simple_betas_df["Clutch","gradient"], 0)
+simple_betas["Pref",] <- ifelse(simple_betas_df["Pref","low"]*simple_betas_df["Pref","high"] > 0,
+                                        simple_betas_df["Pref","gradient"], 0)
+simple_betas <- round(simple_betas, 2)
+
+## Create gamma-matrix for simple food-web treatment
+simple_gammas_df <- bias.adj_selection_gradients %>%
+  filter(`Food web`=="Simple", term_ord %in% c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref")) %>% 
+  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
+rownames(simple_gammas_df) <- simple_gammas_df$term_ord
+
+simple_gammas <- matrix(nrow = 3, ncol = 3, dimnames = list(c("Diam","Clutch","Pref"), c("Diam","Clutch","Pref")))
+simple_gammas["Diam","Diam"] <- ifelse(simple_gammas_df["Diam^2","low"]*simple_gammas_df["Diam^2","high"] > 0, 
+                                        simple_gammas_df["Diam^2","gradient"], 0)
+simple_gammas["Clutch","Clutch"] <- ifelse(simple_gammas_df["Clutch^2","low"]*simple_gammas_df["Clutch^2","high"] > 0,
+                                            simple_gammas_df["Clutch^2","gradient"], 0)
+simple_gammas["Pref","Pref"] <- ifelse(simple_gammas_df["Pref^2","low"]*simple_gammas_df["Pref^2","high"] > 0,
+                                        simple_gammas_df["Pref^2","gradient"], 0)
+simple_gammas["Diam","Clutch"] <- ifelse(simple_gammas_df["Diam:Clutch","low"]*simple_gammas_df["Diam:Clutch","high"] > 0,
+                                          simple_gammas_df["Diam:Clutch","gradient"], 0)
+simple_gammas["Clutch","Diam"] <- simple_gammas["Diam","Clutch"]
+simple_gammas["Diam","Pref"] <- ifelse(simple_gammas_df["Diam:Pref","low"]*simple_gammas_df["Diam:Pref","high"] > 0,
+                                            simple_gammas_df["Diam:Pref","gradient"], 0)
+simple_gammas["Pref","Diam"] <- simple_gammas["Diam","Pref"]
+simple_gammas["Clutch","Pref"] <- ifelse(simple_gammas_df["Clutch:Pref","low"]*simple_gammas_df["Clutch:Pref","high"] > 0, 
+                                        simple_gammas_df["Clutch:Pref","gradient"], 0)
+simple_gammas["Pref","Clutch"] <- simple_gammas["Clutch","Pref"]
+simple_gammas <- round(simple_gammas, 2)
+
+## Calculate Curvature of the Fitness landscape
+complex_curvature <- complex_gammas - complex_betas %*% t(complex_betas)
+simple_curvature <- simple_gammas - simple_betas %*% t(simple_betas)
+```
+
+## Slope of adaptive landscape
+
+$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix}$$
+
+$$\text{Slope}_{complex} = \begin{pmatrix} `r complex_betas["Diam", ]` \\ `r complex_betas["Clutch", ]` \\ `r complex_betas["Pref", ]` \end{pmatrix}$$
+$$\text{Slope}_{simple} =  \begin{pmatrix} `r simple_betas["Diam", ]` \\ `r simple_betas["Clutch", ]` \\ `r simple_betas["Pref", ]` \end{pmatrix}$$
+
+## Curvature of adaptive landscape
+
+$$\text{Curvature} = \gamma - \beta \beta^\text{T}$$
+
+$$\gamma = \begin{pmatrix} \gamma_{diam} & \gamma_{diam,clutch} & \gamma_{diam,pref} \\ \gamma_{clutch,diam} & \gamma_{clutch} & \gamma_{clutch,pref} \\ \gamma_{pref,diam} & \gamma_{pref,clutch} &\gamma_{pref} \end{pmatrix}$$
+$$\gamma_{complex} = \begin{pmatrix} `r complex_gammas["Diam","Diam"]` & `r complex_gammas["Diam","Clutch"]` & `r complex_gammas["Diam","Pref"]` \\  `r complex_gammas["Clutch","Diam"]` & `r complex_gammas["Clutch","Clutch"]` & `r complex_gammas["Clutch","Pref"]` \\  `r complex_gammas["Pref","Diam"]` & `r complex_gammas["Pref","Clutch"]` & `r complex_gammas["Pref","Pref"]` \end{pmatrix}$$
+$$\gamma_{simple} = \begin{pmatrix} `r simple_gammas["Diam","Diam"]` & `r simple_gammas["Diam","Clutch"]` & `r simple_gammas["Diam","Pref"]` \\  `r simple_gammas["Clutch","Diam"]` & `r simple_gammas["Clutch","Clutch"]` & `r simple_gammas["Clutch","Pref"]` \\  `r simple_gammas["Pref","Diam"]` & `r simple_gammas["Pref","Clutch"]` & `r simple_gammas["Pref","Pref"]` \end{pmatrix}$$
+
+$$\text{Curvature}_{complex} = \begin{pmatrix} `r complex_curvature["Diam","Diam"]` & `r complex_curvature["Diam","Clutch"]` & `r complex_curvature["Diam","Pref"]` \\  `r complex_curvature["Clutch","Diam"]` & `r complex_curvature["Clutch","Clutch"]` & `r complex_curvature["Clutch","Pref"]` \\  `r complex_curvature["Pref","Diam"]` & `r complex_curvature["Pref","Clutch"]` & `r complex_curvature["Pref","Pref"]` \end{pmatrix}$$
+
+$$\text{Curvature}_{simple} = \begin{pmatrix} `r simple_curvature["Diam","Diam"]` & `r simple_curvature["Diam","Clutch"]` & `r simple_curvature["Diam","Pref"]` \\  `r simple_curvature["Clutch","Diam"]` & `r simple_curvature["Clutch","Clutch"]` & `r simple_curvature["Clutch","Pref"]` \\  `r simple_curvature["Pref","Diam"]` & `r simple_curvature["Pref","Clutch"]` & `r simple_curvature["Pref","Pref"]` \end{pmatrix}$$
+
+## Observed phenotypic variance-covariance matrix
+
+```{r Observe P matrix}
+
+## setup P-matrix
+P_matrix <- matrix(1, nrow=3, ncol=3, dimnames = list(c("Diam","Clutch","Pref"),c("Diam","Clutch","Pref")))
+
+## confirm that variance of phenotypic traits = 1
+P_matrix["Diam","Diam"] <- var(gall_selection.df$sc.Diam)
+P_matrix["Clutch","Clutch"] <- var(gall_selection.df$sc.log.Clutch)
+P_matrix["Pref","Pref"] <- var(gall_selection.df$sc.log1p.Pref)
+
+## calculate covariance between phenotypic traits
+P_matrix["Diam","Clutch"] <- with(gall_selection.df, cov(sc.Diam, sc.log.Clutch))
+P_matrix["Clutch","Diam"] <- P_matrix["Diam","Clutch"]
+
+P_matrix["Diam","Pref"] <- with(gall_selection.df, cov(sc.Diam, sc.log1p.Pref))
+P_matrix["Pref","Diam"] <- P_matrix["Diam","Pref"]
+
+P_matrix["Clutch","Pref"] <- with(gall_selection.df, cov(sc.log.Clutch, sc.log1p.Pref))
+P_matrix["Pref","Clutch"] <- P_matrix["Clutch","Pref"]
+
+heritability <- 0.3 # since all traits are scaled to SD (and variance)=1, then a narrow-sense heritability of 0.3 (which is reasonable) corresponds to an additive genetic variance of 0.3 (Vg = h2 * Vp)
+
+G_matrix <- P_matrix * heritability
+```
+
+$$\text{P} = \begin{pmatrix} `r round(P_matrix["Diam","Diam"],2)` & `r round(P_matrix["Diam","Clutch"],2)` & `r round(P_matrix["Diam","Pref"],2)` \\  `r round(P_matrix["Clutch","Diam"],2)` & `r round(P_matrix["Clutch","Clutch"],2)` & `r round(P_matrix["Clutch","Pref"],2)` \\  `r round(P_matrix["Pref","Diam"],2)` & `r round(P_matrix["Pref","Clutch"],2)` & `r round(P_matrix["Pref","Pref"],2)` \end{pmatrix}$$
+Note that the variance of each phenotypic trait is standardized to 1.
+If we assume that each phenotypic trait has a narrow-sense heritability ($h^2$) of `r heritability`, then the additive genetic variance of each trait is equal to its narrow-sense heritability.
+The resulting G-matrix is:
+
+$$\text{G} = \begin{pmatrix} `r round(G_matrix["Diam","Diam"],2)` & `r round(G_matrix["Diam","Clutch"],2)` & `r round(G_matrix["Diam","Pref"],2)` \\  `r round(G_matrix["Clutch","Diam"],2)` & `r round(G_matrix["Clutch","Clutch"],2)` & `r round(G_matrix["Clutch","Pref"],2)` \\  `r round(G_matrix["Pref","Diam"],2)` & `r round(G_matrix["Pref","Clutch"],2)` & `r round(G_matrix["Pref","Pref"],2)` \end{pmatrix}$$
+```{r Change in G-matrices, include=FALSE}
+complex_G_matrix <- G_matrix + G_matrix %*% complex_curvature %*% G_matrix
+simple_G_matrix <- G_matrix + G_matrix %*% simple_curvature %*% G_matrix
+```
+
+# Change in complex G-matrix
+
+$$\text{G}_{complex} = \begin{pmatrix} `r round(complex_G_matrix["Diam","Diam"],3)` & `r round(complex_G_matrix["Diam","Clutch"],3)` & `r round(complex_G_matrix["Diam","Pref"],3)` \\  `r round(complex_G_matrix["Clutch","Diam"],3)` & `r round(complex_G_matrix["Clutch","Clutch"],3)` & `r round(complex_G_matrix["Clutch","Pref"],3)` \\  `r round(complex_G_matrix["Pref","Diam"],3)` & `r round(complex_G_matrix["Pref","Clutch"],3)` & `r round(complex_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
+
+# Change in simple G-matrix
+
+$$\text{G}_{simple} = \begin{pmatrix} `r round(simple_G_matrix["Diam","Diam"],3)` & `r round(simple_G_matrix["Diam","Clutch"],3)` & `r round(simple_G_matrix["Diam","Pref"],3)` \\  `r round(simple_G_matrix["Clutch","Diam"],3)` & `r round(simple_G_matrix["Clutch","Clutch"],3)` & `r round(simple_G_matrix["Clutch","Pref"],3)` \\  `r round(simple_G_matrix["Pref","Diam"],3)` & `r round(simple_G_matrix["Pref","Clutch"],3)` & `r round(simple_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
+
+```{r Evo dynamics derived from observed phenotypic variance-covariance, include=FALSE}
+
+# initial trait values
+z_initial <- matrix(0, nrow=3, ncol=1, dimnames = list(c("Diam","Clutch","Pref")))
+
+# checks to see whether disruptive selection on preference is driving the relationship
+alt_complex_gammas <- complex_gammas
+alt_complex_gammas["Pref","Pref"] <- 0
+
+# basically, controls for differences in mean fitness
+alt_simple_betas <- complex_betas 
+alt_simple_betas["Clutch", ] <- simple_betas["Clutch", ] * simple_mean_fitness / complex_mean_fitness # best estimate on complex mean fitness scale, need to confirm...
+
+# simulate evolutionary dynamics
+complex_evo_dynamics <- evolutionary_dynamics(betas = complex_betas, 
+                                              gammas = complex_gammas, 
+                                              G_0 = G_matrix,
+                                              z_0 = z_initial,
+                                              t = n_evo_sims)
+
+simple_evo_dynamics <- evolutionary_dynamics(betas = simple_betas, 
+                                             gammas = simple_gammas, 
+                                             G_0 = G_matrix,
+                                             z_0 = z_initial,
+                                             t = n_evo_sims)
+
+## Tidy simulations
+complex_z_feasible <- mutate(tidy_evo_sims(complex_evo_dynamics), Foodweb="Complex")
+
+simple_z_feasible <- mutate(tidy_evo_sims(simple_evo_dynamics), Foodweb="Simple")
+```
+
+```{r altered parameters}
+complex_betas
+```
+
+## Walk across the adaptive landscape
+
+```{r Evo-Sim-Hyp-G, echo=FALSE, fig.cap="Evolutionary simulation of a hypothetical G-matrix"}
+
+# Make plots
+evosim_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
+  geom_line(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Clutch)) +
+  geom_point(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Clutch))
+
+evosim_AF_plot_Clutch.Pref <- AF_plot_Clutch.Pref +
+  geom_line(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Pref, y=Clutch)) +
+  geom_point(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Pref, y=Clutch))
+
+evosim_AF_plot_Diam.Pref <-  AF_plot_Diam.Pref +
+  geom_line(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Pref)) +
+  geom_point(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Pref))
+
+# Get legend
+evosim_AF_landscape_legend <- get_legend(evosim_AF_plot_Diam.Pref)
+
+# Format plots
+evosim_AF_landscape_plots <- plot_grid(
+  evosim_AF_plot_Diam.Clutch + theme(legend.position = "none", 
+                              axis.title.y = element_text(size=11),
+                              axis.title.x = element_blank(),
+                              axis.text = element_text(size=10)),
+ evosim_AF_plot_Clutch.Pref + theme(legend.position = "none", 
+                              axis.title.y = element_blank(), 
+                              axis.text = element_text(size=10), 
+                              axis.title.x = element_text(size=11)),
+  evosim_AF_plot_Diam.Pref + theme(legend.position = "none", 
+                            axis.text = element_text(size=10),
+                            axis.title = element_text(size=11)), 
+  nrow=2, align="hv", labels = "AUTO")
+evosim_AF_landscape_2d <- ggdraw(evosim_AF_landscape_plots) + draw_grob(evosim_AF_landscape_legend, x = 0.7, y=-0.2)
+evosim_AF_landscape_2d
+```
+
+## Compare evolvabilities of hypothetical G-matrix over time
+
+Since my covariance is standardized, it should be okay to calculate the mean squared correlation as an overall measure of trait integration.
+
+```{r Compare changes in hypothetical G-matric over time, echo=FALSE}
+last(complex_z_feasible$Time)/last(simple_z_feasible$Time)
+
+complex_evolvability <- c()
+complex_conditional.evolvability <- c()
+complex_constraints <- c()
+complex_autonomy <- c()
+complex_MeanSquaredCorrelation <- c()
+for(i in 1:last(complex_z_feasible$Time)){
+  complex_evolvability[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["evolvability"] 
+  complex_conditional.evolvability[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["conditional.evolvability"]
+  complex_constraints[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["constraints"]
+  complex_autonomy[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["autonomy"]
+  complex_MeanSquaredCorrelation[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["MeanSquaredCorrelation"]
+}
+
+simple_evolvability <- c()
+simple_conditional.evolvability <- c()
+simple_constraints <- c()
+simple_autonomy <- c()
+simple_MeanSquaredCorrelation <- c()
+for(i in 1:last(simple_z_feasible$Time)){
+  simple_evolvability[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["evolvability"] 
+  simple_conditional.evolvability[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["conditional.evolvability"]
+  simple_constraints[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["constraints"] 
+  simple_autonomy[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["autonomy"]
+  simple_MeanSquaredCorrelation[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["MeanSquaredCorrelation"]
+}
+
+gather_G_matrix_data <- bind_rows(
+  data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", 
+             evolvability=complex_evolvability,
+             conditional.evolvability=complex_conditional.evolvability,
+             constraints=complex_constraints,
+             autonomy=complex_autonomy,
+             MeanSquaredCorrelation=complex_MeanSquaredCorrelation),
+  data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple",
+             evolvability=simple_evolvability,
+             conditional.evolvability=simple_conditional.evolvability,
+             constraints=simple_constraints,
+             autonomy=simple_autonomy,
+             MeanSquaredCorrelation=simple_MeanSquaredCorrelation)) %>%
+  gather(key=G_metric, value=value, -Time, -Foodweb)
+
+gather_G_matrix_data %>%
+  ggplot(., aes(x=Time, y=value, color=Foodweb)) +
+  geom_point() +
+  geom_line() +
+  scale_color_manual(values=treatment_colors) +
+  facet_wrap(~G_metric, ncol=2, scales = "free_y")
+
+#bind_rows(data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", conditional.evolvability=complex_conditional.evolvability),
+#          data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple", conditional.evolvability=simple_conditional.evolvability)) %>%
+#  ggplot(., aes(x=Time, y=conditional.evolvability, color=Foodweb)) +
+#  geom_point() +
+#  geom_line() +
+#  scale_color_manual(values=treatment_colors)
+
+#bind_rows(data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", constraints=complex_constraints),
+#          data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple", constraints=simple_constraints)) %>%
+#  ggplot(., aes(x=Time, y=constraints, color=Foodweb)) +
+#  geom_point() +
+#  geom_line() +
+#  scale_color_manual(values=treatment_colors)
+
+#bind_rows(data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", autonomy=complex_autonomy),
+#          data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple", autonomy=simple_autonomy)) %>%
+#  ggplot(., aes(x=Time, y=autonomy, color=Foodweb)) +
+#  geom_point() +
+#  geom_line() +
+#  scale_color_manual(values=treatment_colors)
+```
+
+## More walks across the adaptive landscape
+
+```{r Generate random G matrices and simulate Evo Dynamics, include=FALSE}
+
+## Define the maximum additive genetic variance
+max_add_G <- 0.5
+
+## Number of G-matrix simulations
+n_G_sims <- 200 # 1000
+
+## Simulate G-matrices
+
+## ALTERNATIVE APPROACH: RandomMatrix(num.traits=3, num.matrices = 1, min.var=0, max.var=0.5)
+
+# additive genetic variance is sampled from a random uniform distribution and varies between 0 and max_add_G
+# additive genetic covariances can be positive or negative with a maximum absolute value determined by the product of additive genetic variances.
+sim_G <- list()
+for(i in 1:n_G_sims){
+  sim_G[[i]] <- diag(x = runif(n=3, min = 0, max = max_add_G), nrow = 3)
+  sim_G[[i]][1,2] <- runif(n=1, min=-(sim_G[[i]][1,1]*sim_G[[i]][2,2]), max=(sim_G[[i]][1,1]*sim_G[[i]][2,2]))
+  sim_G[[i]][2,1] <- sim_G[[i]][1,2]
+  sim_G[[i]][1,3] <- runif(n=1, min=-(sim_G[[i]][1,1]*sim_G[[i]][3,3]), max=(sim_G[[i]][1,1]*sim_G[[i]][3,3]))
+  sim_G[[i]][3,1] <- sim_G[[i]][1,3]
+  sim_G[[i]][2,3] <- runif(n=1, min=-(sim_G[[i]][2,2]*sim_G[[i]][3,3]), max=(sim_G[[i]][2,2]*sim_G[[i]][3,3]))
+  sim_G[[i]][3,2] <- sim_G[[i]][2,3]
+}
+
+## Simulations for complex food-web treatment
+complex_evo_sims <- lapply(X = sim_G, FUN = function(x) evolutionary_dynamics(betas = complex_betas, # test_betas, #
+                                                                              gammas = complex_gammas, # test_gammas, #
+                                                                              G_0 = x, z_0 = z_initial, t = n_evo_sims))
+
+tidy_complex_sims <- lapply(X = complex_evo_sims, FUN = tidy_evo_sims)
+
+tidier_complex_sims <- list()
+for(i in 1:length(tidy_complex_sims)){
+  tidier_complex_sims[[i]] <- mutate(tidy_complex_sims[[i]], simulation = i, Foodweb="Complex")
+}
+
+tidiest_complex_sims <- bind_rows(tidier_complex_sims)
+
+## Simulations for simple food-web treatment
+simple_evo_sims <- lapply(X = sim_G, FUN = function(x) evolutionary_dynamics(betas = simple_betas, # simple_betas
+                                                                             gammas = simple_gammas, # test_gammas, #
+                                                                             G_0 = x, z_0 = z_initial, t = n_evo_sims))
+
+tidy_simple_sims <- lapply(X = simple_evo_sims, FUN = tidy_evo_sims)
+
+tidier_simple_sims <- list()
+for(i in 1:length(tidy_simple_sims)){
+  tidier_simple_sims[[i]] <- mutate(tidy_simple_sims[[i]], simulation = i, Foodweb="Simple")
+}
+
+tidiest_simple_sims <- bind_rows(tidier_simple_sims)
+
+## Combine evolutionary simulations for plotting
+combine_tidied_evo_sims <- bind_rows(tidiest_complex_sims, tidiest_simple_sims)
+
+sims_to_subsample <- sample(unique(combine_tidied_evo_sims$simulation), 100)
+
+sub_tidied_evo_sims <- combine_tidied_evo_sims %>% filter(simulation %in% sims_to_subsample) # subsample 100 for plotting
+```
+
+```{r Plot evo sims of many G-matrices, include=FALSE}
+evosim.manyG_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
+  geom_line(data=sub_tidied_evo_sims, aes(x=Diam, y=Clutch, group=simulation), alpha=0.1)
+
+evosim.manyG_AF_plot_Clutch.Pref <- AF_plot_Clutch.Pref +
+  geom_line(data=sub_tidied_evo_sims, aes(x=Pref, y=Clutch, group=simulation), alpha=0.1)
+
+evosim.manyG_AF_plot_Diam.Pref <-  AF_plot_Diam.Pref +
+  geom_line(data=sub_tidied_evo_sims, aes(x=Diam, y=Pref, group=simulation), alpha=0.1)
+```
+
+```{r Evo-Sim-Many-G, echo=FALSE, fig.cap="Evolutionary simulation of a range of G-matrices"}
+# Get legend
+evosim.manyG_AF_landscape_legend <- get_legend(evosim.manyG_AF_plot_Diam.Pref)
+
+# Format plots
+evosim.manyG_AF_landscape_plots <- plot_grid(
+  evosim.manyG_AF_plot_Diam.Clutch + theme(legend.position = "none", 
+                              axis.title.y = element_text(size=11),
+                              axis.title.x = element_blank(),
+                              axis.text = element_text(size=10)),
+ evosim.manyG_AF_plot_Clutch.Pref + theme(legend.position = "none", 
+                              axis.title.y = element_blank(), 
+                              axis.text = element_text(size=10), 
+                              axis.title.x = element_text(size=11)),
+  evosim.manyG_AF_plot_Diam.Pref + theme(legend.position = "none", 
+                            axis.text = element_text(size=10),
+                            axis.title = element_text(size=11)), 
+  nrow=2, align="hv", labels = "AUTO")
+evosim.manyG_AF_landscape_2d <- ggdraw(evosim.manyG_AF_landscape_plots) + draw_grob(evosim.manyG_AF_landscape_legend, x = 0.7, y=-0.2)
+evosim.manyG_AF_landscape_2d
+```
+
+## Multivariate trait differences
+
+```{r Multivariate trait differences, include=FALSE, eval=FALSE}
+library(vegan)
+
+multivariate_trait_evolution <- combine_tidied_evo_sims %>%
+  group_by(simulation, Foodweb) %>%
+  summarise_at(vars(Diam, Clutch, Pref), funs(last)) %>%
+  ungroup()
+
+multivariate_trait_evolution %>%
+  group_by(Foodweb) %>%
+  summarise_at(vars(Diam, Clutch, Pref), funs(mean, sd))
+
+multivariate_trait_distance <- vegdist(x = select(multivariate_trait_evolution, Diam, Clutch, Pref), method = "euclidean")
+# multivariate_traits <- adonis(multivariate_trait_distance ~ Foodweb, data = multivariate_trait_evolution)
+
+trait_disper <- betadisper(d = multivariate_trait_distance, group = multivariate_trait_evolution$Foodweb)
+anova(trait_disper)
+plot(trait_disper)
+boxplot(trait_disper)
+```
+
+## How does the adaptive landscape influence the rate of evolution?
+
+Here we are going to see how fast it took for the *Iteomyia* to hit the edge of the adaptive landscape across many different G-matrices.
+```{r Rate of phenotypic evolution, include=FALSE}
+evo_sim_duration <-combine_tidied_evo_sims %>%
+  group_by(simulation, Foodweb) %>%
+  summarise_at(vars(Time), funs(last))
+
+which(evo_sim_duration$Time == n_evo_sims) # note that a boundary was hit on the adaptive landscape for all simulations prior to the simulation duration
+
+evo_sim_duration %>%
+  ggplot(., aes(x=Foodweb, y=Time, group=simulation)) +
+  geom_point() + 
+  geom_line() +
+  scale_y_log10() +
+  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
+
+# only 10 times out of 500 simulations where it took longer to hit the boundary in the complex food web (so in general, its faster)
+spread(evo_sim_duration, Foodweb, Time) %>%
+  filter(Complex > Simple)
+
+wide_evo_sim_duration <- spread(evo_sim_duration, Foodweb, Time) %>%
+  mutate(Diff = Simple - Complex, Diff.Percent = Diff/Complex, Diff.Fold = Simple/Complex)
+
+round(mean(wide_evo_sim_duration$Diff.Fold),1)
+```
+
+In general, *Iteomyia* hit the edge of the adaptive landscape faster in the complex vs. simple food web.
+
+```{r Intuition about evolvability, eval=FALSE}
+base_matrix <- matrix(c(1,0,0,
+                        0,1,0,
+                        0,0,1), nrow=3, ncol=3)
+base_G <- 0.5
+
+G_1 <- base_G*base_matrix
+MeanMatrixStatistics(G_1)
+G_2 <- G_1
+G_2[2,1] <- -G_1[1,1]*G_1[2,2]
+G_2[1,2] <- G_2[2,1]
+MeanMatrixStatistics(G_2)
+G_3 <- G_2
+G_3[3,1] <- -G_2[1,1]*G_2[3,3]
+G_3[1,3] <- G_3[3,1]
+MeanMatrixStatistics(G_3)
+G_4 <- G_3
+G_4[3,2] <- -G_3[2,2]*G_3[3,3]
+G_4[2,3] <- G_4[3,2]
+MeanMatrixStatistics(G_4)
+
+G_5 <- base_G*base_matrix
+MeanMatrixStatistics(G_5)
+G_6 <- G_5
+G_6[2,1] <- G_5[1,1]*G_5[2,2]
+G_6[1,2] <- G_6[2,1]
+MeanMatrixStatistics(G_6)
+G_7 <- G_6
+G_7[3,1] <- G_6[1,1]*G_6[3,3]
+G_7[1,3] <- G_7[3,1]
+MeanMatrixStatistics(G_7)
+G_8 <- G_7
+G_8[3,2] <- G_7[2,2]*G_7[3,3]
+G_8[2,3] <- G_8[3,2]
+MeanMatrixStatistics(G_8)
+
+bind_rows(MeanMatrixStatistics(G_1), MeanMatrixStatistics(G_2), MeanMatrixStatistics(G_3), #MeanMatrixStatistics(G_4),
+          MeanMatrixStatistics(G_5), MeanMatrixStatistics(G_6), MeanMatrixStatistics(G_7), MeanMatrixStatistics(G_8)) %>%
+  mutate(G_name = c(1:3,5:8), base_G = base_G) %>%
+  select(G_name, evolvability, conditional.evolvability, autonomy, constraints)
+```
+
+```{r Intuition about matrix multiplication, eval=FALSE}
+
+beta <- matrix(c(0.2,0,0.1), nrow = 3)
+- (beta %*% t(beta)) # decrease in genetic covariance between traits 1 and 3
+
+beta2 <- matrix(c(0.2,0,-0.1), nrow = 3)
+- (beta2 %*% t(beta2)) # increase in genetic covariance between traits 1 and 3
+
+cov.test <- matrix(1, nrow = 3, ncol=3)*0.5
+cov.test[2,1] <- cov.test[1,1]*cov.test[2,2]
+cov.test[1,2] <- cov.test[2,1]
+cov.test[3,1] <- cov.test[1,1]*cov.test[3,3]
+cov.test[1,3] <- cov.test[3,1]
+cov.test[2,3] <- cov.test[3,3]*cov.test[2,2]
+cov.test[3,2] <- cov.test[2,3]
+
+sim_data <- MASS::mvrnorm(n=10, mu=rep(0,3), Sigma=cov.test)
+plot(sim_data[,1] ~ sim_data[,2])
+```
+
+```{r Compare evolvabilities at end of simulation, echo=FALSE}
+
+complex_G_end <- list()
+simple_G_end <- list()
+for(i in 1:n_evo_sims){ #n_evo_sims
+
+  complex_time_end <- filter(evo_sim_duration, Foodweb=="Complex", simulation == i)$Time
+  simple_time_end <- filter(evo_sim_duration, Foodweb=="Simple", simulation == i)$Time
+
+  if(isSymmetric(complex_evo_sims[[i]]$G[[complex_time_end]])==TRUE){
+    complex_G_end[[i]] <- data.frame(t(MeanMatrixStatistics(complex_evo_sims[[i]]$G[[complex_time_end]]))) %>% select(evolvability, conditional.evolvability, autonomy, constraints, MeanSquaredCorrelation)
+  } else {complex_G_end[[i]] <- data.frame(evolvability=NA, conditional.evolvability=NA, autonomy=NA, constraints=NA, MeanSquaredCorrelation=NA)}
+
+  if(isSymmetric(simple_evo_sims[[i]]$G[[simple_time_end]])==TRUE){
+    simple_G_end[[i]] <- data.frame(t(MeanMatrixStatistics(simple_evo_sims[[i]]$G[[simple_time_end]]))) %>% select(evolvability, conditional.evolvability, autonomy, constraints, MeanSquaredCorrelation)
+  } else {simple_G_end[[i]] <- data.frame(evolvability=NA, conditional.evolvability=NA, autonomy=NA, constraints=NA, MeanSquaredCorrelation=NA)}
+}
+
+tidy_G_matrix_stats <- bind_rows(
+  mutate(bind_rows(complex_G_end), sim = 1:n_evo_sims, Foodweb="Complex"),
+  mutate(bind_rows(simple_G_end), sim = 1:n_evo_sims, Foodweb="Simple")) %>%
+  gather(key=G_metric, value=value, -sim, -Foodweb)
+
+tidy_G_matrix_stats %>%
+  ggplot(., aes(x=Foodweb, y=value, group=sim)) +
+  geom_point() + 
+  geom_line() +
+  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb)) +
+  facet_wrap(~G_metric, ncol=2, scales="free_y")
+
+#tidy_G_matrix_stats %>%
+#  ggplot(., aes(x=Foodweb, y=evolvability, group=sim)) +
+#  geom_point() + 
+#  geom_line() +
+#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
+
+#tidy_G_matrix_stats %>%
+#  ggplot(., aes(x=Foodweb, y=conditional.evolvability, group=sim)) +
+#  geom_point() + 
+#  geom_line() +
+#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
+
+#tidy_G_matrix_stats %>%
+#  ggplot(., aes(x=Foodweb, y=autonomy, group=sim)) +
+#  geom_point() + 
+#  geom_line() +
+#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
+
+#tidy_G_matrix_stats %>%
+#  ggplot(., aes(x=Foodweb, y=constraints, group=sim)) +
+#  geom_point() + 
+#  geom_line() +
+#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
+
+#evolvability_stats <- tidy_G_matrix_stats %>%
+#  select(sim, Foodweb, evolvability) %>%
+#  spread(Foodweb, evolvability) %>%
+#  mutate(Diff.mag = Complex/Simple)
+
+#mean(evolvability_stats$Diff.mag, na.rm=T) # Resulting G-matrix is 2x more evolvable in complex vs. simple food web.
 ```
@@
 To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
-<!-- To identify the appropriate level of model complexity for testing the effects of food-web complexity on the fitness landscapes, we compared models using Aikaike Information Criteria. 
-The maximal complexity we explored was a generalized additive mixed model that fit cubic splines to each trait as well as linear interactions between a maximum of two traits as well as an interaction with food-web treatment.
--->
-
-<!-- We used a spline-based semiparametric regression (Schluter 1988, Morrissey and Sakedra 2014).
-These analyses are desirable because they lead to inferences of the form of selection that make few \textit{a priori} assumptions (Schluter 1988), and can now be used to quantify standardized selection gradients (Morrissey and Sakrera 2014).
-
-We then calculated selection gradients as the partial derivatives in absolute fitness (larva survival) with response to multivariate phenotype using the \textit{gsg} package in R (cite Morrissey and R project).
-We standardized phenotypes (mean=0, SD=1), so that first-order derivatives correspond to the intensity of directional selection ($\beta$\textsubscript{trait}), while second-order derivatives correspond to intensity of nonlinear ($\gamma$\textsubscript{trait}) and correlational selection ($\gamma$\textsubscript{trait$_i$,}\textsubscript{trait$_j$}) and are thus comparable within this study as well as to others.
--->
-
-<!-- Our GLMMs are useful for testing the effects of food-web complexity on the fitness landscape within the context of our experimental design; however, coefficients from GLMMs cannot be easily converted into quantitative estimates of selection gradients (cite Morrissey's work).
-Therefore, for each treatment, we fit separate generalized additive models (GAMs) for gall traits that we identified as being under selection from our GLMMs.
-Estimating selection gradients from GAMs can give insight to both linear and non-linear selection gradients, which we assumed were all linear for our GLMMs, given the complexity of already fitting up to 4-way interactions in these models.
-For the number of larva per gall and gall density, we aggregated larva survival at the gall or plant level, respectively, to avoid pseudoreplication in our GAMs.
--->
-
-```{r Figure 1, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
-Black arrows denote 'who-eats-whom' in this network of trophic interactions."}
-knitr::include_graphics("complex_simple_foodwebs_compressed.pdf")
-```
 
@@
 ```
-
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE}
-
-newdata_Diam <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0))
-
-RF_Diam <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
-  newdata = newdata_Diam,
-  bootstraps=n_boots_plots)
-
-# Control ----
-#RF_control_gall_size <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = seq(-1,1,length.out=1000), 
-#     sc.log.clutch_size = 0,
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-
-# Treatment ----
-#RF_treatment_gall_size <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = seq(-1,1,length.out=1000),
-#     sc.log.clutch_size = 0,
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-```
-
-```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE}
-newdata_Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0))
-
-RF_Clutch <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
-  newdata = newdata_Clutch,
-  bootstraps=n_boots_plots)
-
-# Control ----
-#RF_control_clutch_size <- bootstrap_fitness(
-#  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000),
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-
-# Treatment ----
-#RF_treatment_clutch_size <- bootstrap_fitness(
-#  logistic_model = model_2, #quad_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000),
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-```
-
-```{r Get Female Preference Fitness Landscape, cache=TRUE, include=FALSE}
-
-newdata_Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
-
-RF_Pref <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
-  newdata = newdata_Pref,
-  bootstraps=n_boots_plots)
-
-# Control ----
-#RF_control_female_preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = 0, 
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=n_boots_plots)
-
-# Treatment ----
-#RF_treatment_female_preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = 0,
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=n_boots_plots)
-
-```
-
-```{r Get Clutch Size x Female Preference Landscape, cache=TRUE, include=FALSE}
-
-newdata_Clutch.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)))
-
-RF_Clutch.Pref <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
-  newdata = newdata_Clutch.Pref,
-  bootstraps=NULL)
-
-# Control ----
-#RF_control_clutch.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000), 
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=NULL)
-
-# Treatment ----
-#RF_treatment_clutch.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000),
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, include=FALSE}
-
-newdata_Diam.Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref=0))
-
-RF_Diam.Clutch <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
-  newdata = newdata_Diam.Clutch,
-  bootstraps=NULL)
-
-# Control ----
-#RF_control_size.x.clutch <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
- # newdata = expand.grid(
-  #   sc.gall_size = seq(-1,1,length.out=1000),
-   #  sc.log.clutch_size = seq(-1,1,length.out=1000), 
-    # sc.log1p.female_preference = 0), 
-  #bootstraps=NULL)
-
-# Treatment ----
-#RF_treatment_size.x.clutch <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
- # newdata = expand.grid(
-  #   sc.gall_size = seq(-1,1,length.out=1000),
-   #  sc.log.clutch_size = seq(-1,1,length.out=1000),
-    # sc.log1p.female_preference = 0), 
-  #bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Female Preference Landscape, cache=TRUE, include=FALSE}
-
-newdata_Diam.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
-
-RF_Diam.Pref <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
-  newdata = newdata_Diam.Pref,
-  bootstraps=NULL)
-
-# Control ----
-#RF_control_size.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-#  newdata = expand.grid(
- #    sc.gall_size = seq(-1,1,length.out=1000),
-  #   sc.log.clutch_size = 0, 
-   #  sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  ##bootstraps=NULL)
-
-# Treatment ----
-#RF_treatment_size.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
- # newdata = expand.grid(
-  #   sc.gall_size = seq(-1,1,length.out=1000),
-   #  sc.log.clutch_size = 0,
-    # sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  #bootstraps=NULL)
-```
-
-```{r Fitness Landscape Plot Helpers, include=FALSE}
-
-## Scale relative fitness across plots ----
-
-# 1D
-#RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
-#          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
-#          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
-#  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-#  gather(ID, relative_fitness, -sc.gall_size) %>%
-#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-#  summarise(min = min(relative_fitness), max = max(relative_fitness))
-#RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
-
-# 2D
-#RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
-#          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
-#          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
-#  summarise(min = min(average), max = max(average))
-
-## Scale absolute fitness across plots ----
-
-# 1D
-AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
-
-# 2D
-AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
-  summarise(min = min(average), max = max(average))
-```
-
-```{r Plot Univariate Landscapes, include=FALSE}
-uni_breaks <- c(0.1,0.5,1.0)
-
-# Gall size 
-AF_uni_Diam <- RF_Diam$absolute_fitness %>% #bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.Clutch, -sc.log1p.Pref) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Chamber diameter (SDs)") +
-  ylab("Mean larva survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
-  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
-#AF_uni_size
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Clutch size
-AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% #bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.Diam, -sc.log1p.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Mean larva survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Female preference
-AF_uni_Pref <- RF_Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.log1p.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
-  ylab("Mean larva survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-```
-
-```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C).
-Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
-Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
-
-# Get legend
-AF_uni_legend <- get_legend(AF_uni_Diam)
-
-# Make plots
-AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none", 
-                                              axis.text.x = element_text(size=10),
-                                              axis.title.x = element_text(size=11)), 
-                       AF_uni_Clutch + theme(legend.position = "none",
-                                             axis.title.y = element_blank(), 
-                                             #axis.text.y = element_blank(),
-                                             axis.text.x = element_text(size=10),
-                                             axis.title.x = element_text(size=11)),
-                       AF_uni_Pref + theme(legend.position = "none", 
-                                           axis.title.y = element_blank(), 
-                                           #axis.text.y = element_blank(), 
-                                           axis.text.x = element_text(size=10),
-                                           axis.title.x = element_text(size=11)),
-                       labels = "AUTO", ncol = 3, align='hv')
-
-AF_gradients <- plot_grid(AF_uni_plots, AF_uni_legend, ncol = 2, rel_widths = c(1,0.2)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
-AF_gradients
-#AF_uni_plots
-# save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
-#save_plot("../figures/fitness_landscapes_1D.png", AF_gradients)#, base_height=6, base_width = 8)
-```
-
-```{r Plot Multivariate Fitness Landscape, include=FALSE}
-
-my_breaks <- c(0.2,0.4,0.6,0.8)
-
-# Size x Preference
-AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_size.x.preference$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_size.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.Diam, y=sc.log1p.Pref, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Foodweb) +
-  xlab("Chamber diameter (SDs)") +
-  ylab("Female preference (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
-
-# Size x Clutch
-AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% #bind_rows(mutate(RF_treatment_size.x.clutch$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_size.x.clutch$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Foodweb) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
-
-# Clutch x Preference
-AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_clutch.x.preference$absolute_fitness, Food_Web = "Simple"), 
-         # mutate(RF_control_clutch.x.preference$absolute_fitness, Food_Web = "Complex")) %>%
-  ggplot(., aes(x=sc.log1p.Pref, y=sc.log.Clutch, fill=average)) +
-  geom_raster() +
-  facet_wrap(~Foodweb) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#, 
-```
-
-```{r Multivariate-Fitness-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C).
-Note that traits for all plots range 1 SD below and above the mean (=0)."}
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_Diam.Pref)
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_Diam.Clutch + theme(legend.position = "none", 
-                              axis.title.y = element_text(size=11),
-                              axis.title.x = element_blank(),
-                              axis.text = element_text(size=10)),
-  AF_plot_Clutch.Pref + theme(legend.position = "none", 
-                              axis.title.y = element_blank(), 
-                              axis.text = element_text(size=10), 
-                              axis.title.x = element_text(size=11)),
-  AF_plot_Diam.Pref + theme(legend.position = "none", 
-                            axis.text = element_text(size=10),
-                            axis.title = element_text(size=11)), 
-  nrow=2, align="hv", labels = "AUTO")
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("../figures/fitness_landscapes_2D.png", AF_landscape_2d)#, base_height=6, base_width = 8)
-```

### 2018-10-08 manuscript/manuscript.tex
update of current analyses

@@
 \usepackage[sc]{mathpazo} %Like Palatino with extensive math support
-\usepackage{graphicx} % for organizing figures
 \usepackage{fullpage}
@@
 \titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
+
+% Added packages
+\usepackage{amsmath} % for matrices
+\usepackage{graphicx} % for organizing figures
 
@@
 
-The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
-The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
-Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$).
-In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
-For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
-density-dependence, CITE Foundational and current work).
-In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
-Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
+% I. Adaptive landscape is a powerful framework for understanding the evolution of biological diversity (or phenotypic evolution).
 
-Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
-Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
-This has provided an effective framework for predicting how changes in the biotic environment (e.g.
-density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
-At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
-However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
-Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
-Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
+The adaptive landscape provides a powerful framework for understanding and predicting the evolution of biological diversity \textemdash from genes, to phenotypes, to species (Wright and Simpson).
+More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection (Lande 1979, Arnold papers).
+In particular, the shape of the adaptive landscape represents the presence and strength of different selection pressures imposed by the environment (Arnold's work).
+Species interactions often play a key role in defining the selective environment, as evidenced by the influence of resource competition (Schluter 2000), mutualisms (Jordano 1987), and predation (Abrams 2000) on the evolution of biological diversity.
+Although there is clear evidence that pairwise interactions shape the adaptive landscape, we also know that most species interact with multiple species in an ecological community.
+Understanding how the adaptive landscape is shaped by community context represents a major challenge for both empiricists and theoreticians given the diversity of selection pressures that a population is likely to experience in a natural ecological community.
 
-Here, we integrate species-interaction networks and the fitness landscape to empirically test how changes in the biotic environment -- network of species interactions -- affect the dynamics of natural selection.
-Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (*Iteomyia salicisverruca*)(Fig.
+% II. Species-interaction networks provide an explicit representation of the community context that populations are embedded within.
+
+Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the community context.
+These networks describe the interdependency of species within an ecological community, providing an effective framework for predicting how changes in the density of directly and indirectly connected species will impact other species, and in turn, community dynamics.
+Despite the importance of species-interaction networks for predicting ecological dynamics, these networks often lack quantitative information on how species interactions influence natural selection.
+Consequently, it is unclear how species-interaction networks shape the adaptive landscape, creating a major hurdle in our current ability to predict how changes in community context will affect phenotypic evolution.
+
+% III. Here we combine these frameworks to predict how changes in community context will affect phenotypic evolution. (empirically?)
+
+Here, we integrate species-interaction networks and the adaptive landscape to predict how changes in network structure will affect phenotypic evolution.
+We did this by first conducting a field experiment to characterize the effect of network structure on the adaptive landscape of a constituent species.
+We then used a mathematical model to simulate how changes in network structure altered phenotypic evolution.
+Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (\textit{Iteomyia salicisverruca})(Fig.
 1).
-The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (*Salix* sp., @Russo2006).
+The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (\textit{Salix} sp., @Russo2006).
 These galls provide protection from generalist predators (e.g.
@@
 Therefore, our manipulation of parasitoid diversity alters the diversity of interactions, or food-web complexity, that this insect herbivore experiences.
+
+% IV. Lay out predictions for how changes in network structure influence the adaptive landscape.
 
@@
 
+% Confronting this challenge is important now more than ever before, given the rapid changes we are witnessing in the diversity and composition of local communities (cite global change papers).
+
+% Natural selection is inherently an ecological process, describing how the environment changes phenotypic distributions of a population due to differences in fitness. %within a generation
+
+%At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
+However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
+Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
+Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
+
+% For example, the Lande equation ($\delta z=G\beta$) predicts the evolutionary trajectory of phenotypes ($\delta z$) as a function of directional selection gradients ($\beta$) and the additive genetic variance and covariance between these phenotypes (G-matrix, $G$).
+Similarly, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$).
+also shapes the G-matrix, which ultimately determines the ...
+.
+Importantly, the components of this theoretical framework can be est quantities that predict evolutionary change can all be estimated empirically
+
+% People have often studied pairwise species interactions.
+There is also tantalizing evidence that community context can alter natural selection on phenotypic distributions, but predicting these changes remains difficult.
+This is because work hasn't explicitly embodied the environment (which a network can).
+
+% Key part here is environment, which a food web or species-interaction network can provide an explicit representation of (i.e. community context).
+
+% Biological diversity \textemdash from genes, to phenotypes, to species \textemdash has and continues to be shaped by the interplay between ecological and evolutionary processes.
+Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (Schluter 2000), mutualisms (Jordano 1987), and predation (Abrams 2000).
+While there is clear evidence that pairwise interactions can drive evolution, we also know that most species interact with multiple species in an ecological community.
+Understanding and predicting how evolutionary dynamics unfold in a community context represents a major challenge both empirically and theoretically, given the diversity of selection pressures that a population is likely to experience in an ecological community.
+Answering this question also has important applications, especially given the rapid changes we are witnessing in the diversity and composition of local communities (cite global change papers).
+
+% is a key challenge and predicting how changes in ecological communities is challenging and eminently theoretical (@McPeek2017, @De_Mazancourt2008, @Guimaraes2017, @Nuismer2013).
+
+%<!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
+I think it would be useful to show that there is some field and lab experiments demonstrating that community context can alter evolutionary trajectories -->
+%<!-- Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
+
+%<!-- Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests of how changes in network structure will alter the dynamics of natural selection in the field.
+-->
+
+% The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
+The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
+Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$).
+In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
+For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
+density-dependence, CITE Foundational and current work).
+In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
+Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
+
+% Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
+Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
+This has provided an effective framework for predicting how changes in the biotic environment (e.g.
+density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
+At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
+However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
+Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
+Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
+
 \section*{Methods}
@@
 
-We conducted our study within a four-year old common garden of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40&deg;40'53"N, 124&deg;12'4"W) near Loleta, California, USA.
+We conducted our study within a four-year old common garden of coastal willow (\textit{Salix hookeriana}) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40\textdegree 40'53"N, 124\textdegree 12'4"W) near Loleta, California, USA.
 This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
@@
 This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
-On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack *Iteomyia*. 
+On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack \textit{Iteomyia}. 
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
-Our food-web manipulation altered the average number of trophic interactions that *Iteomyia* was exposed to from BLANK on control plants to BLANK on treatment plants. 
+Our food-web manipulation altered the average number of trophic interactions that \textit{Iteomyia} was exposed to from BLANK on control plants to BLANK on treatment plants. 
 Thus, we refer to galls on control plants as being exposed to a 'complex' food web, whereas galls on treatment plants were exposed to a 'simple' food web.
-In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and <!-- allowed them to complete development--> kept them in the lab for 4 months at room temperature.
+In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature. 
 We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (*Platygaster* sp.), or was parasitized by a larval parasitoid.
+Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (\textit{Platygaster} sp.), or was parasitized by a larval parasitoid.
 For the food-web treatment that excluded parasitoids, we further restricted our data by removing any instances of parasitism by a larval parasitoid.
@@
 
-We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018). 
+We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018) (\citealt{Heath2018}).
 First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). 
@@
 We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
-Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value as this contains the majority of the trait distribution that selection is acting on.
+Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
+This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean trait values of the population (Arnold 2001, Morrissey 2009).
 
@@
 
+\subsection*{Simulating Phenotypic Evolution}
+
+We used the method proposed by Hansen and Houle (2008) to characterize the evolvability of the G-matrices resulting from different adaptive landscapes.
+Their index of evolvability is theoretically linked to the theory underlying G matrices and adaptive landscapes, and describes the ability of a population to evolve in the direction of selection when stabilizing selection is absent.
+
+% Hansen and Houle 2008
+%Alternatively, but not
+%inconsistently, evolvability can be viewed in a quantitative
+%genetics context as a short-term ability to respond to
+%directional selection (Houle, 1992), which depends on
+%standing additive genetic variation in the traits under
+%selection and on the autonomy of this genetic variation
+%from other traits under stabilizing selection (Hansen
+%et al., 2003a, b; Hansen, 2003; Hansen & Houle, 2004)
+
 \section*{Results}
 
+\subsection*{Shape of the adaptive landscape}
+
+The shape of the adaptive landscape is described by its slope ($\beta$) and curvature ($\gamma - \beta \beta^\text{T}$).
+We found that food-web complexity altered the slope of the adaptive landscape in two key ways.
+First, there were fewer traits under directional selection in the complex (2 of 3) vs.
+simple food web (3 of 3).
+For example, across both food-web treatments there was directional selection for larger gall chambers and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
+In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
+The absence of selection on clutch size in the complex food web appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
+For example, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (\beta_{diam}=0.12 [0.04,0.21]).
+
+The second key effect of food-web complexity was to steepen the slope of the adaptive landscape (i.e.
+increase strength of selection).
+For example, the magnitude of directional selection in complex vs.
+simple food webs was ~60\% higher for both chamber diameter and female preference.
+This result was not due to any difference in the relationship between larva survival and gall phenotype (INSERT REGRESSION ANALYSIS), but was a result of the fact that average larval survival was lower in complex (INSERT MEAN PROBABILITY OF SURVIVAL) vs.
+simple food webs (INSERT MEAN PROBABILITY OF SURVIVAL).
+Remember that the selection gradient can be expressed as the covariance between absolute fitness ($W$) and individual phenotype ($z$) divided by mean fitness ($\bar W$).
+Therefore, lower survival, and thus mean fitness, will always increase the strength of selection.
+
+Unlike the slope, the curvature of the adaptive landscape is influenced by directional ($\beta$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
+Our food-web treatment did not appear to alter correlational selection, and there was no strong evidence that any of these selection gradients differed from zero (table~\ref{Table:Gradients}).
+Similarly, our food-web treatment did not appear to influence quadratic selection on chamber diameter or clutch size, and there was no strong evidence that these selection gradients differed from zero (table~\ref{Table:Gradients}).
+In contrast, our food-web treatment did alter quadratic selection acting on female preference.
+Specifically, we found evidence for disruptive selection (selection for extreme phenotypes) in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
+
+The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes genetic variation ($\Delta \text{G}$) within a generation.
+
+In the simple food web, we found that the adaptive landscape acted to decrease additive genetic variance in all three traits (diagonals of matrix).
+
+$$\text{Curvature}_{simple} = \begin{pmatrix} -0.05 & 0.02 & 0.03 \\  0.02 & -0.01 & -0.01 \\  0.03 & -0.01 & -0.02 \end{pmatrix}$$
+
+In contrast, we found the adaptive landscape in the complex food web only decreased the additive genetic variance in one of the three traits (chamber diameter).
+
+\text{Curvature}_{complex} = \begin{pmatrix} -0.13 & 0 & 0.9 \\ 0 & 0 & 0 \\ 0.09 & 0 & 0.33 \end{pmatrix}
+
+In the complex food web, we found that the adaptive landscape  We found that the adaptive landscape complex food web,
+
+We found that there were fewer selective constraints influence *Iteomyia* in the complex vs. the simple food-web treatment. Specifically, the curvature of the complex food-web was described as:
+
+whereas the curvature of the simple food-web is summarized by the following matrix:
+
+Specifically, we found that simple food webs would result in a decrease in additive genetic variance for all phenotypic traits (matrix diagonals) within a generation, wherease in the complex food web, we only found that one trait (chamber diameter), would experience a decrease in additive genetic variance (albeit large).
+Any non-zero for the off diagonals is evidence of constraints.
+In the simple food-web, we found evidence of constraints on each additive genetic covariance, albeit small, whereas for the complex food-web, we only observed a constraint on the covariance between chamber diameter and female preference (favoring trait intergration).
+Taken together, we observe constrains on 2 of 6 trait variances and covariances in the complex food web, whereas 6 of 6 trait variances and covariances were constrained in the simple food web.
+
+Our two dimensional surfaces are likely representative given the fact that there is no strong evidence of correlational selection (Phillips and Arnold 1989, Evolution)
+
+\subsection*{Phenotypic evolution is less constrained in the complex food web}
+
+% of the adaptive landscape describe its shape and therefore the direction and magnitude of phenotypic ($\Delta \text{z}$) and genetic change ($\Delta \text{G}$).
+
+Three key patterns emerged from our simulations of phenotypic evolution.
+The first was that phenotypic evolution was faster in complex vs.
+simple food webs.
+Specifically, it took \textit{Iteomyia} twice as long to hit the boundary of the adaptive landscape in the simple vs.
+complex food web.
+This pattern was driven by the fact that the absolute strength of selection was larger in complex vs.
+simple food webs, as we no longer observed this strong difference if we standardized all selection gradients by average larval survival measured in the complex food web (Appendix).
+
+The second key pattern we observed was that phenotypic evolution was less constrained in complex compared to simple food webs.
+
+Finally, we found that the adaptive landscape in the complex food web enhanced the evolvability of \textit{Iteomyia} compared to the simple food web.
+
+Food-web complexity fundamentally altered the shape of the adaptive landscape. For example,
+
+Across both food-web treatments, there was no clear evidence of correlational selection between (Table 1).
+
+We observed disruptive selection on female preference in the complex, but no evidence of any nonlinear selection the simple food web.
+This disruptive selection was likely driven by a different functional response of larval parasitoids to female preference.
+For example, when we subset our data to focus on differences between larval and egg parasitoids, we found that there was a trend for larval parasitoids to impose disruptive selection (\gamma_{pref,pref}=0.22 [-0.06,0.49]).
+
+In both complex and simple food webs, chamber diameter was under strong directional selection with larger galls resulting in higher larval survival (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
+
+In general, if there was evidence of selection, then the magnitude of selection was always greater in complex vs.
+simple food webs.
+These steeper selection gradients were simply due to the fact that average larval survival was lower in complex food webs.
+
 \section*{Discussion}
+
+Our key finding was that phenotypic evolution was less constrained for a species that was embedded within a complex food web compared to a simple one. These
+
+Two key patterns emerged from our study.
+First, selection was stronger and thus the potential speed of evolution in complex compared to simple food webs.
+Second, the adaptive landscape was less constrained in the complex vs.
+the simple food web.
 
@@
 
-\begin{thebibliography}{}
-
-\bibitem[{Cook et~al.(2015)Cook, Collaborator, and Expert}]{CookEtAl2015}
-Cook, O.~E., G.~H. Collaborator, and A.~Q. Expert. 2015.
-\newblock Data from: Template and guidelines for using \LaTeX{} in \textit{The American Naturalist}.
-\newblock American Naturalist, Dryad Digital Repository, http://dx.doi.org/10.5061/dryad.XYZAB.
-
-\bibitem[{Davis et~al.(2011)Davis, Brakora, and Lee}]{DavisEtAl2011}
-Davis, E.~B., K.~A. Brakora, and A.~H. Lee. 2011.
-\newblock Evolution of ruminant headgear: a review.
-\newblock Proceedings of the Royal Society B 278:2857--2865.
-
-\bibitem[{Inglis et~al.(2011)Inglis, Roberts, Gardner, and Buckling}]{Ing11}
-Inglis, R.~F., P.~G. Roberts, A.~Gardner, and A.~Buckling. 2011.
-\newblock Spite and the scale of competition in \textit{Pseudomonas
-  aeruginosa}.
-\newblock American Naturalist 178:276--285.
-
-\bibitem[{Lemod\`{e}le et~al.(2007)Lemodele, Kapitelschreiber, and Exemplar}]{LemKapEx07}
-Lemod\`{e}le, P.-Q., A.~B. Kapitelschreiber, and C.~D.~E. Exemplar. 2007.
-\newblock An exemplary instance of chapters in books.
-\newblock Pages 231--245 \emph{in} J.-P. \'{E}crivain and M.~A. Term\'{e}szettud\'{o}s, eds. Inspiring Instances of Brilliant Writing. Truth Pudding Press, Fond du Lac, WI.
-
-\bibitem[{Xiao et~al.(2015)Xiao, McGlinn, and White}]{Xiao2015}
-Xiao, X., D.~J. McGlinn, and E.~P. White. 2015.
-\newblock A strong test of the maximum entropy theory of ecology.
-\newblock American Naturalist 185:E705--E80.
-
-\end{thebibliography}
+\bibliographystyle{amnat}
+\bibliography{bibliography}
 
@@
 \textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
-$\beta_{Diam}$                    & 0.47 [0.36-0.58] & 0.29 [0.23,0.37] \\
-$\beta_{Clutch}$                  & 0.06 [-0.04,0.17] & -0.13 [-0.25,-0.04] \\
-$\beta_{Pref}$                    & -0.24 [-0.36,-0.11] & -0.15 [-0.23,-0.07] \\
+$\beta_{Diam}$                    & 0.47 [0.36,0.59] & 0.29 [0.23,0.37] \\
+$\beta_{Clutch}$                  & 0.06 [-0.05,0.19] & -0.09 [-0.17,-0.02] \\
+$\beta_{Pref}$                    & -0.24 [-0.38,-0.11] & -0.15 [-0.24,-0.07] \\
 $\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
-$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.04] & -0.06 [-0.16,0.02] \\
-$\gamma_{Pref,Pref}$              & 0.39 [0.02,0.81] & -0.32 [-0.63,-0.03] \\
-$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.01] \\
-$\gamma_{Diam,Pref}$              & -0.08 [-0.19,0.02] & -0.05 [-0.12,0.01] \\
-$\gamma_{Clutch,Pref}$            & 0.04 [-0.06,0.13] & 0.02 [-0.04,0.08]            \\ \hline
+$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.05] & -0.06 [-0.16,0.03] \\
+$\gamma_{Pref,Pref}$              & 0.39 [0.04,0.74] & -0.07 [-0.25,0.11] \\
+$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.00] \\
+$\gamma_{Diam,Pref}$              & -0.08 [-0.18,0.01] & -0.05 [-0.11,0.01] \\
+$\gamma_{Clutch,Pref}$            & 0.04 [-0.05,0.13] & 0.02 [-0.03,0.08]            \\ \hline
 \end{tabular}
@@
 \textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
-$s_{Diam}$                      &  [ - ] \\
-$s_{Clutch}$                    &  [ - ] \\
-$s_{Pref}$                      &  [ - ] \\ 
-$s_{Diam,Diam}$                 &  [ - ] \\
-$s_{Clutch,Clutch}$             &  [ - ] \\
-$s_{Pref,Pref}$                 &  [ - ]                \\ \hline
+$s_{Diam}$                      & 0.06 [-0.14,0.27] \\
+$s_{Clutch}$                    & 0.20 [-0.10,0.51] \\
+$s_{Pref}$                      & 0.20 [0.07,0.33 \\ 
+$s_{Diam,Diam}$                 & -0.11 \\
+$s_{Clutch,Clutch}$             & -0.91 \\
+$s_{Pref,Pref}$                 & -0.24                \\ \hline
 \end{tabular}

### 2018-10-08 manuscript/manuscript.tex
removed results related to phenotypic evolution, plus some other changes.

@@
 Here, we integrate species-interaction networks and the adaptive landscape to predict how changes in network structure will affect phenotypic evolution.
-We did this by first conducting a field experiment to characterize the effect of network structure on the adaptive landscape of a constituent species.
-We then used a mathematical model to simulate how changes in network structure altered phenotypic evolution.
+We did this by conducting a field experiment to characterize the effect of network structure on the adaptive landscape of a constituent species.
 Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (\textit{Iteomyia salicisverruca})(Fig.
@@
 
-Changes in food-web complexity could influence a resource population's fitness landscape in at least two ways.
+Changes in food-web complexity could influence a resource population's adaptive landscape in at least two ways.
 First, if a more diverse community of consumers is more effective at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population.
@@
 Thus, a more diverse consumer community may relax the net selection pressures acting on resource traits.
-Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the fitness landscape of a resource population.
+Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the adaptive landscape of a resource population.
 
@@
 
+If we only retain non-zero selection gradients, then we can
+
+Our two dimensional surfaces are likely representative given the fact that there is no strong evidence of correlational selection (Phillips and Arnold 1989, Evolution)
+
 \subsection*{Simulating Phenotypic Evolution}
@@
 simple food webs was ~60\% higher for both chamber diameter and female preference.
-This result was not due to any difference in the relationship between larva survival and gall phenotype (INSERT REGRESSION ANALYSIS), but was a result of the fact that average larval survival was lower in complex (INSERT MEAN PROBABILITY OF SURVIVAL) vs.
-simple food webs (INSERT MEAN PROBABILITY OF SURVIVAL).
+This result was not due to any difference in the relationship between larva survival and gall phenotype (Simple:coef_{Diam}=0.02 [-0.56,0.6]; Simple:coef_{Pref}=-0.16 [-0.83,0.61]), but was a result of the fact that average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs.
+simple food webs (0.69 [0.54,0.80]).
 Remember that the selection gradient can be expressed as the covariance between absolute fitness ($W$) and individual phenotype ($z$) divided by mean fitness ($\bar W$).
@@
 Unlike the slope, the curvature of the adaptive landscape is influenced by directional ($\beta$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
-Our food-web treatment did not appear to alter correlational selection, and there was no strong evidence that any of these selection gradients differed from zero (table~\ref{Table:Gradients}).
-Similarly, our food-web treatment did not appear to influence quadratic selection on chamber diameter or clutch size, and there was no strong evidence that these selection gradients differed from zero (table~\ref{Table:Gradients}).
+Our food-web treatment did not appear to alter correlational selection and there was no strong evidence that any of these selection gradients differed from zero (table~\ref{Table:Gradients}).
+Similarly, our food-web treatment did not appear to influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (table~\ref{Table:Gradients}).
 In contrast, our food-web treatment did alter quadratic selection acting on female preference.
@@
 The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes genetic variation ($\Delta \text{G}$) within a generation.
-
-In the simple food web, we found that the adaptive landscape acted to decrease additive genetic variance in all three traits (diagonals of matrix).
+In the simple food web, the curvature of the adaptive landscape had the following structure:
 
@@
 
-In contrast, we found the adaptive landscape in the complex food web only decreased the additive genetic variance in one of the three traits (chamber diameter).
+The negative values along the diagonal of this matrix suggests that the simple food web acted to decrease additive genetic variance in all three traits.
+The presence of non-zero values off the diagonal indicates that simple food web favors trait integration of all three phenotypic traits.
+
+In the complex food web, the curvature of the adaptive landscape had the following structure:
 
@@
 
-In the complex food web, we found that the adaptive landscape  We found that the adaptive landscape complex food web,
-
-We found that there were fewer selective constraints influence *Iteomyia* in the complex vs. the simple food-web treatment. Specifically, the curvature of the complex food-web was described as:
-
-whereas the curvature of the simple food-web is summarized by the following matrix:
+In contrast to the simple food web, we only observed a decrease in additive genetic variance for chamber diameter ($\Delta \text{G}_{Diam}=-0.13$) in the complex food web.
+The complex food web did not act to change additive genetic variance in clutch size, and actually acted to increase additive genetic variance in female preference ($\Delta \text{G}_{Diam,Diam}=\text{G}_{Diam,Diam}(0.33)\text{G}_{Diam,Diam}+\text{U}_{Diam,Diam}$).
+Along the off diagonal, we found that the complex food web favored trait integration between chamber diameter and female preference.
+In other words, the adaptive landscape did not act to constrain the pattern of trait integration between clutch size and the other phenotypic traits.
 
@@
 Taken together, we observe constrains on 2 of 6 trait variances and covariances in the complex food web, whereas 6 of 6 trait variances and covariances were constrained in the simple food web.
-
-Our two dimensional surfaces are likely representative given the fact that there is no strong evidence of correlational selection (Phillips and Arnold 1989, Evolution)
-
-\subsection*{Phenotypic evolution is less constrained in the complex food web}
-
-% of the adaptive landscape describe its shape and therefore the direction and magnitude of phenotypic ($\Delta \text{z}$) and genetic change ($\Delta \text{G}$).
-
-Three key patterns emerged from our simulations of phenotypic evolution.
-The first was that phenotypic evolution was faster in complex vs.
-simple food webs.
-Specifically, it took \textit{Iteomyia} twice as long to hit the boundary of the adaptive landscape in the simple vs.
-complex food web.
-This pattern was driven by the fact that the absolute strength of selection was larger in complex vs.
-simple food webs, as we no longer observed this strong difference if we standardized all selection gradients by average larval survival measured in the complex food web (Appendix).
-
-The second key pattern we observed was that phenotypic evolution was less constrained in complex compared to simple food webs.
-
-Finally, we found that the adaptive landscape in the complex food web enhanced the evolvability of \textit{Iteomyia} compared to the simple food web.
-
-Food-web complexity fundamentally altered the shape of the adaptive landscape. For example,
-
-Across both food-web treatments, there was no clear evidence of correlational selection between (Table 1).
-
-We observed disruptive selection on female preference in the complex, but no evidence of any nonlinear selection the simple food web.
-This disruptive selection was likely driven by a different functional response of larval parasitoids to female preference.
-For example, when we subset our data to focus on differences between larval and egg parasitoids, we found that there was a trend for larval parasitoids to impose disruptive selection (\gamma_{pref,pref}=0.22 [-0.06,0.49]).
-
-In both complex and simple food webs, chamber diameter was under strong directional selection with larger galls resulting in higher larval survival (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
-
-In general, if there was evidence of selection, then the magnitude of selection was always greater in complex vs.
-simple food webs.
-These steeper selection gradients were simply due to the fact that average larval survival was lower in complex food webs.
 

### 2018-10-15 manuscript/manuscript.tex
update manuscript

@@
 \usepackage{graphicx} % for organizing figures
+\usepackage{lmodern} % for tilde
+\usepackage[T1]{fontenc} % for tilde
 
@@
 
-\title{Phenotypic evolution is less constrained in complex food webs}
+\title{TBD}
+% 1. Populations experience fewer selective constraints in complex food webs
+% 2. Complex food webs impose fewer selective constraints on linked populations
+% 3. Food-web complexity reduces selective constraints on an insect herbivore
+% 4. Phenotypic evolution is less constrained in complex food webs
 
@@
 Arezoo Sootodeh$^{3}$ \\
-Brendan Lock$^{4} \\
+Brendan Locke$^{4} \\
 Jordi Bascompte$^{2}}
@@
 
-\textit{Manuscript elements}: Figure~1, figure~2, table~1, online appendices~A and B (including figure~A1 and figure~A2). Figure~2 is to print in color.
+\textit{Manuscript elements}: Figure~1, figure~2, figure~3. All figures should be printed in color.
 
@@
 
-\textit{Keywords}: Examples, model, template, guidelines.
+\textit{Keywords}: Adaptive landscape, host-parasitoid, natural selection, G-matrix.
 
@@
 
+The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes additive genetic (co)variances ($\Delta \text{G}$) within a generation.
+Specifically, the diagonals of the curvature matrix describe the effect of the adaptive landscape on additive genetic variance within a generation; therefore, any negative values along the diagonal are evidence of selective constraints.
+The off-diagonals of the curvature matrix describe the effect of the adaptive landscape on additive genetic covariances within a generation; therefore, any non-zero values are evidence of selective constraints as they favor trait integration.
+
 \subsection*{Simulating Phenotypic Evolution}
@@
 
-\subsection*{Shape of the adaptive landscape}
+\subsection*{Slope of the adaptive landscape}
 
-The shape of the adaptive landscape is described by its slope ($\beta$) and curvature ($\gamma - \beta \beta^\text{T}$).
-We found that food-web complexity altered the slope of the adaptive landscape in two key ways.
+We found that food-web complexity altered the slope of the adaptive landscape ($\beta$) in two key ways.
 First, there were fewer traits under directional selection in the complex (2 of 3) vs.
 simple food web (3 of 3).
-For example, across both food-web treatments there was directional selection for larger gall chambers and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
-In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
+For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
+In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
 The absence of selection on clutch size in the complex food web appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
-For example, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (\beta_{diam}=0.12 [0.04,0.21]).
+Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (fig.~\ref{Fig:LABEL}).
 
@@
 For example, the magnitude of directional selection in complex vs.
-simple food webs was ~60\% higher for both chamber diameter and female preference.
-This result was not due to any difference in the relationship between larva survival and gall phenotype (Simple:coef_{Diam}=0.02 [-0.56,0.6]; Simple:coef_{Pref}=-0.16 [-0.83,0.61]), but was a result of the fact that average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs.
+simple food webs was \textasciitilde 60\% higher for both chamber diameter and female preference (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
+This result was not due to any difference in the relationship between larva survival and gall phenotype ($\textrm{Simple:coef}_{Diam}=0.02 \ [-0.56,0.60]$; $\textrm{Simple:coef}_{Pref}=-0.16 \ [-0.83,0.61]$), but was due to the fact that the average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs.
 simple food webs (0.69 [0.54,0.80]).
-Remember that the selection gradient can be expressed as the covariance between absolute fitness ($W$) and individual phenotype ($z$) divided by mean fitness ($\bar W$).
-Therefore, lower survival, and thus mean fitness, will always increase the strength of selection.
+%Note that although the selection gradient is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, it can be rewritten as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$.
+This alternative expression makes clear that lower survival, and thus mean fitness, will always increase the strength of selection.
 
-Unlike the slope, the curvature of the adaptive landscape is influenced by directional ($\beta$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
-Our food-web treatment did not appear to alter correlational selection and there was no strong evidence that any of these selection gradients differed from zero (table~\ref{Table:Gradients}).
-Similarly, our food-web treatment did not appear to influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (table~\ref{Table:Gradients}).
+\subsection*{Curvature of the adaptive landscape}
+
+Unlike the slope, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$) is influenced by directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
+Our food-web treatment did not appear to alter correlational selection for any combination of traits and there was no strong evidence that any of these selection gradients differed from zero (fig.~\ref{Fig:LABEL}).
+Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (fig.~\ref{Fig:LABEL}).
 In contrast, our food-web treatment did alter quadratic selection acting on female preference.
-Specifically, we found evidence for disruptive selection (selection for extreme phenotypes) in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:FL_1D}; table~\ref{Table:Gradients}).
+Specifically, we found evidence for disruptive selection in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
+Disruptive selection in the complex food web appeared to be due to the presence of larval parasitoids enhancing the relative fitness of larva occuring on either low or high density trees (fig.~\ref{Fig:LABEL}).
 
-The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes genetic variation ($\Delta \text{G}$) within a generation.
-In the simple food web, the curvature of the adaptive landscape had the following structure:
+We can quantify the curvature ($C$) of the adaptive landscape by subtracting the matrix of directional selection gradients ($\beta \beta^\text{T}$) from the matrix of quadratic and correlational selection gradients ($\gamma$):
 
-$$\text{Curvature}_{simple} = \begin{pmatrix} -0.05 & 0.02 & 0.03 \\  0.02 & -0.01 & -0.01 \\  0.03 & -0.01 & -0.02 \end{pmatrix}$$
+$$C = \begin{pmatrix} C_{Diam,Diam} &  &  \\  C_{Clutch,Diam} & C_{Clutch,Clutch} &  \\  C_{Pref,Diam} & C_{Pref,Clutch} & C_{Pref,Pref} \end{pmatrix}$$
 
-The negative values along the diagonal of this matrix suggests that the simple food web acted to decrease additive genetic variance in all three traits.
-The presence of non-zero values off the diagonal indicates that simple food web favors trait integration of all three phenotypic traits.
+We omit the upper triangle of the matrix for clarity, because it is a mirror image of the lower triangle.
+Each component of this matrix describes how the adaptive landscape changes additive genetic (co)variances in phenotypic traits within a generation.
+To empirically estimate the curvature, we only retained nonzero selection gradients (i.e.
+95\% CI does not overlap with zero).
+We found that the curvature of the adaptive landscape in the complex and simple food web exhibited the following structures:
 
-In the complex food web, the curvature of the adaptive landscape had the following structure:
+$$C_{Complex} = \begin{pmatrix} -0.13 &  &  \\ 0 & 0 &  \\ 0.09 & 0 & 0.33 \end{pmatrix}$$
 
-\text{Curvature}_{complex} = \begin{pmatrix} -0.13 & 0 & 0.9 \\ 0 & 0 & 0 \\ 0.09 & 0 & 0.33 \end{pmatrix}
+$$C_{Simple} = \begin{pmatrix} -0.05 &  &  \\  0.02 & -0.01 &  \\  0.03 & -0.01 & -0.02 \end{pmatrix}$$
 
-In contrast to the simple food web, we only observed a decrease in additive genetic variance for chamber diameter ($\Delta \text{G}_{Diam}=-0.13$) in the complex food web.
-The complex food web did not act to change additive genetic variance in clutch size, and actually acted to increase additive genetic variance in female preference ($\Delta \text{G}_{Diam,Diam}=\text{G}_{Diam,Diam}(0.33)\text{G}_{Diam,Diam}+\text{U}_{Diam,Diam}$).
-Along the off diagonal, we found that the complex food web favored trait integration between chamber diameter and female preference.
-In other words, the adaptive landscape did not act to constrain the pattern of trait integration between clutch size and the other phenotypic traits.
-
-Specifically, we found that simple food webs would result in a decrease in additive genetic variance for all phenotypic traits (matrix diagonals) within a generation, wherease in the complex food web, we only found that one trait (chamber diameter), would experience a decrease in additive genetic variance (albeit large).
-Any non-zero for the off diagonals is evidence of constraints.
-In the simple food-web, we found evidence of constraints on each additive genetic covariance, albeit small, whereas for the complex food-web, we only observed a constraint on the covariance between chamber diameter and female preference (favoring trait intergration).
-Taken together, we observe constrains on 2 of 6 trait variances and covariances in the complex food web, whereas 6 of 6 trait variances and covariances were constrained in the simple food web.
+Comparing these matrices, we find evidence of selective constraints acting on 2 of 6 trait (co)variances in the complex food web, whereas 6 of 6 trait (co)variances experience selective constraints in the simple food web.
+Specifically, we found that simple food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the complex food web.
+For genetic covariances, we found that the simple food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.~\ref{Fig:FL_2D}).
+In contrast, the complex food web only constrained genetic covariance by favoring integration between chamber diameter and female preference (fig.~\ref{Fig:FL_2D}).
 
@@
 
-\section*{Appendix A: Supplementary Figures}
-
-% Please reset counters for the appendix (thus normally figure A1, 
-% figure A2, table A1, etc.).
-
-% In certain cases, it may be appropriate to have a PRINT appendix in
-% addition to (or instead of) an online appendix. In this case, please 
-% name the print appendix Appendix A, and any subsequent appendixes (if 
-% there are any) should be named Online Appendix B, Online Appendix C,
-% etc.
-
-% Counters for each appendix should match the letter of that appendix.
-% For example, tables in Appendix C should be numbered table C1, table C2,
-% etc. This applies to tables, equations, and figures.
-
-% It's better not to use the \appendix command, because we have some
-% formatting peculiarities that \appendix conflicts with.
-
-\renewcommand{\theequation}{A\arabic{equation}}
-% redefine the command that creates the equation number.
-\renewcommand{\thetable}{A\arabic{table}}
-\setcounter{equation}{0}  % reset counter 
-\setcounter{figure}{0}
-\setcounter{table}{0}
-
-\subsection*{Fox--dog encounters through the ages}
-
-The quick red fox jumps over the lazy brown dog.
-The quick red fox has always jumped over the lazy brown dog.
-The quick red fox began jumping over the lazy brown dog in the 19th century and has never ceased from so jumping, as we shall see in figure~\ref{Fig:Jumps}.
-But there can be surprises (figure~\ref{Fig:JumpsOk}).
-
-If the order and location of figures is not otherwise clear, feel free to include explanatory dummy text like this:
-
-[Figure A1 goes here.]
-
-[Figure A2 goes here.]
-
-\subsection*{Further insights}
-
-Tables in the appendices can appear in the appendix text (see table~\ref{Table:Rivers} for an example), unlike appendix figure legends which should be grouped at the end of the document together with the other figure legends.
-
-\begin{table}[h]
-\caption{Various rivers, cities, and animals}
-\label{Table:Rivers}
-\centering
-\begin{tabular}{lll}\hline
-River        & City        & Animal            \\ \hline
-Chicago      & Chicago     & Raccoon           \\
-Des Plaines  & Joliet      & Coyote            \\
-Illinois     & Peoria      & Cardinal          \\
-Kankakee     & Bourbonnais & White-tailed deer \\
-Mississippi  & Galena      & Bald eagle        \\ \hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: See table~\ref{Table:Okapi} below for further table formatting hints.}
-\end{table}
-
-Lorem ipsum dolor sit amet, as we have seen in figures~\ref{Fig:Jumps} and \ref{Fig:JumpsOk}.
-
-\newpage{}
-
-\section*{Appendix B: Additional Methods}
-
-\subsection*{Measuring the height of fox jumps without a meterstick}
-
-Pellentesque ac nibh placerat, luctus lectus non, elementum mauris. 
-Morbi odio velit, eleifend ut hendrerit vitae, consequat sit amet 
-nulla. Pellentesque porttitor vitae nisl quis tempus. Pellentesque 
-habitant morbi tristique senectus et netus et malesuada fames ac 
-turpis egestas. Praesent ut nisi odio. Vivamus vel lorem gravida 
-odio molestie volutpat condimentum et arcu.
-
-\begin{equation}
-{ \frac{1}{N_k-1} \sum \limits_{t=1}^{N_k} (M_{tjk} - \bar{M}_{jk})^2}
-\end{equation}
-
-\subsection*{Quantifying the brownness of the dog}
-
-Pellentesque eu nulla odio (\citealt{Xiao2015,CookEtAl2015}).
-Nulla aliquam porta metus, quis malesuada orci faucibus quis.
-Suspendisse nunc magna, tristique sit amet sollicitudin nec, elementum et lacus.
-Sed vitae elementum mi.
-In hac habitasse platea dictumst.
-Etiam eu tortor elit.
-Sed ac tortor purus.
-Aliquam volutpat, odio sit amet posuere pretium, dolor ex interdum ante, sed luctus quam eros ac nulla.
-
-\begin{equation}
-{ (\sum \limits_{p=1}^P {n_{sp}})^{-1}\sum \limits_{p=1}^P {n_{sp}Q_{p}}}
-\end{equation}
-
-\newpage{}
-
 %%%%%%%%%%%%%%%%%%%%%
@@
 
-\section*{Tables}
-\renewcommand{\thetable}{\arabic{table}}
-\setcounter{table}{0}
+%\section*{Tables}
+%\renewcommand{\thetable}{\arabic{table}}
+%\setcounter{table}{0}
 
-\begin{table}[h]
-\caption{Table for \textit{Iteomyia} Selection Gradients}
-\label{Table:Gradients}
-\centering
-\begin{tabular}{lcc}
-                                                                                  \\ \hline
-                                  & \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
-$\beta_{Diam}$                    & 0.47 [0.36,0.59] & 0.29 [0.23,0.37] \\
-$\beta_{Clutch}$                  & 0.06 [-0.05,0.19] & -0.09 [-0.17,-0.02] \\
-$\beta_{Pref}$                    & -0.24 [-0.38,-0.11] & -0.15 [-0.24,-0.07] \\
-$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
-$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.05] & -0.06 [-0.16,0.03] \\
-$\gamma_{Pref,Pref}$              & 0.39 [0.04,0.74] & -0.07 [-0.25,0.11] \\
-$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.00] \\
-$\gamma_{Diam,Pref}$              & -0.08 [-0.18,0.01] & -0.05 [-0.11,0.01] \\
-$\gamma_{Clutch,Pref}$            & 0.04 [-0.05,0.13] & 0.02 [-0.03,0.08]            \\ \hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Table titles should be short.
+%\begin{table}[h]
+%\caption{Selection gradients acting on \textit{Iteomyia} in complex vs. simple food webs.}
+%\label{Table:ComplexSimple}
+%\centering
+%\begin{tabular}{lcc}
+%                                                                                  \\ \hline
+                                  %& \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
+%\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
+%$\beta_{Diam}^a$                    & 0.47 [0.36,0.59] & 0.29 [0.23,0.37] \\
+%$\beta_{Clutch}$                  & 0.06 [-0.05,0.19] & -0.09 [-0.17,-0.02] \\
+%$\beta_{Pref}$                    & -0.24 [-0.38,-0.11] & -0.15 [-0.24,-0.07] \\
+%$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
+%$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.05] & -0.06 [-0.16,0.03] \\
+%$\gamma_{Pref,Pref}$              & 0.39 [0.04,0.74] & -0.07 [-0.25,0.11] \\
+%$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.00] \\
+%$\gamma_{Diam,Pref}$              & -0.08 [-0.18,0.01] & -0.05 [-0.11,0.01] \\
+%$\gamma_{Clutch,Pref}$            & 0.04 [-0.05,0.13] & 0.02 [-0.03,0.08]            \\ \hline
+%\end{tabular}
+%\bigskip{}
+%\\
+%{\footnotesize Note: Values within brackets represent 95\% confidence intervals. $^a$ Adjusted for bias.}
+%\end{table}
+
+%\newpage{}
+
+%\begin{table}[h]
+%\caption{Selection gradients imposed by larval vs. egg parasitoids on \textit{Iteomyia}.}
+%\label{Table:LarvalEgg}
+%\centering
+%\begin{tabular}{lcc}
+%                                                                                  \\ \hline
+                                  %& \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
+%\textbf{Selection gradient}       & \textbf{Larval} & \textbf{Egg}            \\ \hline
+%$\beta_{Diam}^a$                    & 0.47 [0.36,0.59] & 0.29 [0.23,0.37] \\
+%$\beta_{Clutch}$                  & 0.06 [-0.05,0.19] & -0.09 [-0.17,-0.02] \\
+%$\beta_{Pref}$                    & -0.24 [-0.38,-0.11] & -0.15 [-0.24,-0.07] \\
+%$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
+%$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.05] & -0.06 [-0.16,0.03] \\
+%$\gamma_{Pref,Pref}$              & 0.39 [0.04,0.74] & -0.07 [-0.25,0.11] \\
+%$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.00] \\
+%$\gamma_{Diam,Pref}$              & -0.08 [-0.18,0.01] & -0.05 [-0.11,0.01] \\
+%$\gamma_{Clutch,Pref}$            & 0.04 [-0.05,0.13] & 0.02 [-0.03,0.08]            \\ \hline
+%\end{tabular}
+%\bigskip{}
+%\\
+%{\footnotesize Note: Values within brackets represent 95\% confidence intervals.
+Selection gradients and confidence intervals for egg parasitoids are equivalent to estimates for the simple food web.
+$^a$ Adjusted for bias.}
+%\end{table}
+
+%\newpage{}
+
+%\begin{table}[h]
+%\caption{Table for bias}
+%\label{Table:Bias}
+%\centering
+%\begin{tabular}{lc}
+%                                                                  \\ \hline
+%\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
+%Complex (All)                 &  [ - ] \\
+%Complex (Larval guild)        &  [ - ] \\
+%Simple (\textit{Platygaster}) &  [ - ]                  \\ \hline
+%\end{tabular}
+%\bigskip{}
+%\\
+%{\footnotesize Note: Table titles should be short.
 Further details should go in a `notes' area after the tabular environment, like this.
 $^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
-\end{table}
+%\end{table}
 
-\newpage{}
+%\newpage{}
 
-\begin{table}[h]
-\caption{Table for bias}
-\label{Table:Bias}
-\centering
-\begin{tabular}{lc}
+%\begin{table}[h]
+%\caption{Table for \textit{Platygaster} Selection Differentials}
+%\label{Table:PlatySelection}
+%\centering
+%\begin{tabular}{lc}
                                                                   \\ \hline
-\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
-Complex (All)                 &  [ - ] \\
-Complex (Larval guild)        &  [ - ] \\
-Simple (\textit{Platygaster}) &  [ - ]                  \\ \hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Table titles should be short.
+%\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
+%$s_{Diam}$                      & 0.06 [-0.14,0.27] \\
+%$s_{Clutch}$                    & 0.20 [-0.10,0.51] \\
+%$s_{Pref}$                      & 0.20 [0.07,0.33 \\ 
+%$s_{Diam,Diam}$                 & -0.11 \\
+%$s_{Clutch,Clutch}$             & -0.91 \\
+%$s_{Pref,Pref}$                 & -0.24                \\ \hline
+%\end{tabular}
+%\bigskip{}
+%\\
+%{\footnotesize Note: Table titles should be short.
 Further details should go in a `notes' area after the tabular environment, like this.
 $^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
-\end{table}
+%\end{table}
 
-\newpage{}
-
-\begin{table}[h]
-\caption{Table for \textit{Platygaster} Selection Differentials}
-\label{Table:PlatySelection}
-\centering
-\begin{tabular}{lc}
-                                                                  \\ \hline
-\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
-$s_{Diam}$                      & 0.06 [-0.14,0.27] \\
-$s_{Clutch}$                    & 0.20 [-0.10,0.51] \\
-$s_{Pref}$                      & 0.20 [0.07,0.33 \\ 
-$s_{Diam,Diam}$                 & -0.11 \\
-$s_{Clutch,Clutch}$             & -0.91 \\
-$s_{Pref,Pref}$                 & -0.24                \\ \hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Table titles should be short.
-Further details should go in a `notes' area after the tabular environment, like this.
-$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
-\end{table}
-
-\newpage{}
+%\newpage{}
 
@@
 \begin{figure}[h!]
+%\includegraphics{FIGURE}
+\caption{Selection gradients acting on \textit{Iteomyia} phenotypes.
+Points and lines correspond to estimated means and 95\% confidence intervals, respectively.
+Orange and blue colors correspond to estimated gradients in complex and simple food webs, respectively.
+Yellow colors correspond to selection gradients imposed by larval parasitoids.
+Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web).}
+\label{Fig:LABEL}
+\end{figure}
+
+\begin{figure}[h!]
 \includegraphics{Univariate-Fitness-Landscapes-1.png}
-\caption{Selection gradients acting on \texit{Iteomyia} traits in complex vs.
+\caption{Adaptive landscape of \textit{Iteomyia} phenotypes in complex vs.
 simple food webs.
@@
 Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
-Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples.}
+Transparent lines represent bootstrapped replicates to show the uncertainty in estimated gradients.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 bootstrapped samples.
+Note the mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape.}
 \label{Fig:FL_1D}
@@
 \includegraphics{Multivariate-Fitness-Landscapes-1.png}
-\caption{Fitness landscapes of gall traits in complex vs.
+\caption{Two dimensional view of adaptive landscapes in complex vs.
 simple food webs.
 Each panel corresponds to a different combination of traits: clutch size and chamber diameter (A); clutch size and female preference (B); female preference and chamber diameter (C).
-Note that traits for all plots range 1 SD below and above the mean (=0).}
+Note the mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape.}
 \label{Fig:FL_2D}
@@
 
-%%%%%%%%%%%%%%%%%%%%%
-% Videos
-%%%%%%%%%%%%%%%%%%%%%
-% If you have videos, journal style for them is similar to that for
-% figures. You'll want to include a still image (such as a JPEG)
-% to give your readers a preview of what the video looks like.
+%\subsection*{Online figure legends}
 
-%%%%% Include the text below if you have videos
+%\renewcommand{\thefigure}{A\arabic{figure}}
+%\setcounter{figure}{0}
 
-\renewcommand{\figurename}{Video} 
-\setcounter{figure}{0}
-% Thanks to Flo Debarre for the pro tip of putting
-% \renewcommand{\figurename}{Video} before the Video legend and
-% \renewcommand{\figurename}{Figure} after it!
+%\begin{figure}[h!]
+%\includegraphics{jumps20m}
+%\caption{\textit{A}, the quick red fox proceeding to jump 20~m straight into the air over not one, but several lazy dogs.
+\textit{B}, the quick red fox landing gracefully despite the skepticism of naysayers.}
+%\label{Fig:Jumps}
+%\end{figure}
 
-\begin{figure}[h!]
-%\includegraphics{VideoScreengrab.jpg}
-\caption{Video legends can follow the same principles as figure legends. Counters should be set and reset so that videos and figures are enumerated separately.}
-\label{VideoExample}
-\end{figure}
+%\begin{figure}[h!]
+%\includegraphics{jumps20m}
+%\caption{The quicker the red fox jumps, the likelier it is to land near an okapi. For further details, see \citet{LemKapEx07}.}
+%\label{Fig:JumpsOk}
+%\end{figure}
 
-\renewcommand{\figurename}{Figure}
-\setcounter{figure}{1}
-
-%%%%% Include the above if you have videos
-
-\begin{figure}[h!]
-%\includegraphics{elegance}
-\caption{In this way, figure legends can be listed at the end of the document, with references that work, even though the graphic itself should be included for final files after acceptance.
-Instead, upload the relevant figure files separately to Editorial Manager; Editorial Manager should insert them at the end of the PDF automatically.}
-\label{Fig:AnotherFigure}
-\end{figure}
-
-\subsection*{Online figure legends}
-
-\renewcommand{\thefigure}{A\arabic{figure}}
-\setcounter{figure}{0}
-
-\begin{figure}[h!]
-%\includegraphics{jumps20m}
-\caption{\textit{A}, the quick red fox proceeding to jump 20~m straight into the air over not one, but several lazy dogs.
-\textit{B}, the quick red fox landing gracefully despite the skepticism of naysayers.}
-\label{Fig:Jumps}
-\end{figure}
-
-\begin{figure}[h!]
-%\includegraphics{jumps20m}
-\caption{The quicker the red fox jumps, the likelier it is to land near an okapi. For further details, see \citet{LemKapEx07}.}
-\label{Fig:JumpsOk}
-\end{figure}
-
-\renewcommand{\thefigure}{B\arabic{figure}}
-\setcounter{figure}{0}
+%\renewcommand{\thefigure}{B\arabic{figure}}
+%\setcounter{figure}{0}
 

### 2018-10-17 analyses/reproduce_analyses.Rmd
created new figure with selection gradients and tidied up some code.

@@
 
+Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.high,2)`).
+
 ```{r Plot Model 3, echo=FALSE}
@@
 ```
+
+```{r Average larval survival, cache=TRUE}
+model_4_survival_ests <- update(model_4_adj, .~. -1)
+
+boot_model_4_survival_ests <- bootMer(model_4_survival_ests, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_model_4_survival_ests <- tidy(boot_model_4_survival_ests, conf.int=T)
+
+tidy_model_4_survival_ests
+```
+
+Mean larval survival in complex food web = `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$statistic),2)` [`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$conf.low),2)`,`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$conf.high),2)`].
+
+Mean larval survival in simple food web = `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$statistic),2)` [`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$conf.low),2)`, `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$conf.high),2)`].
 
@@
 
+## Figure for manuscript
+
+Only use selection gradients for larval parasitoids, use both complex and simple food webs, and only bias adjusted for chamber diameter.
+
+```{r Prep selection gradients figure, echo=FALSE}
+
+focus_gradients <- bind_rows(filter(bias.adj_selection_gradients, term_ord == "Diam" & adjusted == "Yes" | term_ord != "Diam"),
+                             filter(egg.larval_selection_gradients, `Food web` == "Larval" & term_ord %in% c("Clutch","Pref^2"))) %>%
+  mutate(Type = ifelse(grepl("\\^2", .$term_ord)==TRUE, "Quadratic", ifelse(grepl(":", .$term_ord)==TRUE, "Correlational", "Directional")))
+
+focus_gradients$Type_ord <- factor(focus_gradients$Type, 
+                                   levels=c("Directional","Quadratic","Correlational"),
+                                   ordered = TRUE)
+
+focus_gradients$axis_x_labels <- as.character(focus_gradients$term_ord)
+
+max_gradient <- max(focus_gradients$`97.5%`)
+min_gradient <- min(focus_gradients$`2.5%`)
+gradient_limits <- c(-0.3, 0.75)
+
+legend_labels <- c("Egg + Larval (Complex)","Larval parasitoids","Egg parasitoid (Simple)")
+
+directional <- filter(focus_gradients, Type=="Directional") %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
+  #coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  ylab("Selection Gradient") +
+  scale_fill_manual(values=cbPalette[c(6,4,5)], labels=legend_labels) +
+  scale_color_manual(values=cbPalette[c(6,4,5)], labels=legend_labels) +
+  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  scale_y_continuous(limits = gradient_limits) +
+  theme(legend.title.align = 0.5)
+
+quadratic <- filter(focus_gradients, Type=="Quadratic") %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
+  #coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  ylab("Selection Gradient") +
+  scale_fill_manual(values=cbPalette[c(6,4,5)]) +
+  scale_color_manual(values=cbPalette[c(6,4,5)]) +
+  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  scale_y_continuous(limits = gradient_limits)
+
+correlational <- filter(focus_gradients, Type=="Correlational") %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
+  #coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  ylab("Selection Gradient") +
+  scale_fill_manual(values=cbPalette[c(6,5)]) + # changed from 6,4,5 since larval parasitoids didn't differ for any correlational gradients
+  scale_color_manual(values=cbPalette[c(6,5)]) + # same as above
+  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  scale_y_continuous(limits = gradient_limits)
+```
+
+Standardized selection gradients estimate selection on a trait in terms of the effects on relative fitness in units of (phenotypic) standard deviations of the trait, allowing direct comparisons among traits, fitness components, and study systems (Kingsolver et al.
+2001, Am.
+Nat.).
+
+```{r Selection-Gradients, echo=FALSE, fig.cap="Selection gradients. Points and lines represents means and 95% confidence intervals (n=1,000 bootstrapped samples)."}
+
+# Get legend
+gradients_legend <- get_legend(directional)
+
+# Format plots
+gradients_plots <- plot_grid(
+  directional + theme(legend.position = "none", axis.title = element_blank()),
+  quadratic + theme(legend.position = "none", axis.title = element_blank()),
+  correlational + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+gradients_plots_legend <- ggdraw(gradients_plots) + draw_grob(gradients_legend, x = 0.6, y=-0.2) # x = 0.7, y=-0.2
+gradients_y_title <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+gradients_figure <- plot_grid(gradients_y_title, gradients_plots_legend, ncol=2, rel_widths = c(0.05,1))
+gradients_figure
+```
+
 ## Selection on the egg parasitoid *Platygaster*
@@
 
-```{r Observe P matrix}
+```{r Observe P matrix, include=FALSE}
 
@@
 
-```{r Evo dynamics derived from observed phenotypic variance-covariance, include=FALSE}
+```{r Evo dynamics derived from observed phenotypic variance-covariance, include=FALSE, eval=FALSE}
 
@@
 
-```{r altered parameters}
+```{r altered parameters, include=FALSE, eval=FALSE}
 complex_betas
@@
 
-```{r Evo-Sim-Hyp-G, echo=FALSE, fig.cap="Evolutionary simulation of a hypothetical G-matrix"}
+```{r Evo-Sim-Hyp-G, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="Evolutionary simulation of a hypothetical G-matrix"}
 
@@
 
-```{r Compare changes in hypothetical G-matric over time, echo=FALSE}
+```{r Compare changes in hypothetical G-matric over time, echo=FALSE, include=FALSE, eval=FALSE}
 last(complex_z_feasible$Time)/last(simple_z_feasible$Time)
@@
 
-```{r Generate random G matrices and simulate Evo Dynamics, include=FALSE}
+```{r Generate random G matrices and simulate Evo Dynamics, include=FALSE, eval=FALSE}
 
@@
 
-```{r Plot evo sims of many G-matrices, include=FALSE}
+```{r Plot evo sims of many G-matrices, include=FALSE, eval=FALSE}
 evosim.manyG_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
@@
 
-```{r Evo-Sim-Many-G, echo=FALSE, fig.cap="Evolutionary simulation of a range of G-matrices"}
+```{r Evo-Sim-Many-G, include=FALSE, eval=FALSE, fig.cap="Evolutionary simulation of a range of G-matrices"}
 # Get legend
@@
 Here we are going to see how fast it took for the *Iteomyia* to hit the edge of the adaptive landscape across many different G-matrices.
-```{r Rate of phenotypic evolution, include=FALSE}
+```{r Rate of phenotypic evolution, include=FALSE, eval=FALSE}
 evo_sim_duration <-combine_tidied_evo_sims %>%
@@
 
-```{r Intuition about evolvability, eval=FALSE}
+```{r Intuition about evolvability, include=FALSE, eval=FALSE}
 base_matrix <- matrix(c(1,0,0,
@@
 
-```{r Intuition about matrix multiplication, eval=FALSE}
+```{r Intuition about matrix multiplication, include=FALSE, eval=FALSE}
 
@@
 
-```{r Compare evolvabilities at end of simulation, echo=FALSE}
+```{r Compare evolvabilities at end of simulation, include=FALSE, eval=FALSE}
 

### 2018-10-17 manuscript/manuscript.tex
completed draft of results.

@@
 simple food web (3 of 3).
-For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
-In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
+For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}).
+In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}).
 The absence of selection on clutch size in the complex food web appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
-Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (fig.~\ref{Fig:LABEL}).
+Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (fig.~\ref{Fig:Gradients}).
 
@@
 For example, the magnitude of directional selection in complex vs.
-simple food webs was \textasciitilde 60\% higher for both chamber diameter and female preference (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
+simple food webs was \textasciitilde 60\% higher for both chamber diameter and female preference (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}).
 This result was not due to any difference in the relationship between larva survival and gall phenotype ($\textrm{Simple:coef}_{Diam}=0.02 \ [-0.56,0.60]$; $\textrm{Simple:coef}_{Pref}=-0.16 \ [-0.83,0.61]$), but was due to the fact that the average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs.
@@
 Unlike the slope, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$) is influenced by directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
-Our food-web treatment did not appear to alter correlational selection for any combination of traits and there was no strong evidence that any of these selection gradients differed from zero (fig.~\ref{Fig:LABEL}).
-Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (fig.~\ref{Fig:LABEL}).
+Our food-web treatment did not appear to alter correlational selection for any combination of traits and there was no strong evidence that any of these selection gradients differed from zero (fig.~\ref{Fig:Gradients}).
+Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (fig.~\ref{Fig:Gradients}).
 In contrast, our food-web treatment did alter quadratic selection acting on female preference.
-Specifically, we found evidence for disruptive selection in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
-Disruptive selection in the complex food web appeared to be due to the presence of larval parasitoids enhancing the relative fitness of larva occuring on either low or high density trees (fig.~\ref{Fig:LABEL}).
+Specifically, we found evidence for disruptive selection in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:Gradients}; fig.~\ref{Fig:FL_1D}).
+Disruptive selection in the complex food web appeared to be due to the presence of larval parasitoids enhancing the relative fitness of larva occuring on either low or high density trees (fig.~\ref{Fig:Gradients}).
 
@@
 \begin{figure}[h!]
-%\includegraphics{FIGURE}
+\includegraphics{Selection-Gradients-1.png}
 \caption{Selection gradients acting on \textit{Iteomyia} phenotypes.
@@
 Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web).}
-\label{Fig:LABEL}
+\label{Fig:Gradients}
 \end{figure}

### 2018-10-17 temporary_morgue/To_Do.Rmd
moved to morgue, keeping track of project on github now

@@
 
-## Updated
+## Top Priority
 
-> Population all tables with R-code to make output reproducible
+> Write, write, write!!!
 
-> Decide whether to include 3-way interaction and update models appropriately.
-Right now, I'm thinking I shouldn't, because it doesn't jive with estimating the gamma matrix and consequences for the curvature of the fitness landscape.
+## Lower Priority
 
-> Duplicate coefficient estimates for bootstrapped models.
+> if I want to include host plant effects, I need to exclude chamber diameter as a phenotype under selection by the plant.
+including it would further confound selection on Chamber diameter since none-none larva are found in smaller galls.
+
+> Filter to get G-matrices at the end of each simulation, then compare differences in how the selective environment alters the evolvability of those populations.
 
@@
 
-> Consider a different way to subset the data: convert all estimates of "surviving" ectoparasitism to gall survival, even though this may include estimates of platygaster parasitism.
-
-> Need a graph showing the conflicting selection pressure imposed on clutch size and oviposition preference in the complex food web.
-
-> Consider calculate difference between curvature matrix of complex and simple food webs to describe the change in curvature
-
-----
-
-> look for uncompressed version of "complex_simple_foodwebs.pdf" on Ruthie or my Macbook
-
-> Use standard regression model to determine significant differences in selection gradients.
-
-> Log-transform predictor variables in order to get a best approximation of the fitness landscape. I can use AIC to justify or reject this idea.
-
-> Add a 3-way trait interaction term to test for these higher-order effects.
-
-> Standardize trait values at the level of the whole data set.
-
-> Calculate selection differentials and estimate how much I may have overestimated the effects of selection on gall diameter.
-
-> Test for differences in trait values among treatments to dispell this idea as a factor driving differences in my selection gradients.
-
-> Change position of figure legend for univariate plots (try placing middle-top with 3 plots across.)
-
-> Get bootstrapped estimates of selection intensity and compare between treatments/
-
-> Fix axis labels on plots (change to mean fitness and trait values)
-
-> Fix size of axis text on plots.
-
 > Modify color of figures for illustration of simple and complex food webs and make uncompressed.
-
-> Conduct an analysis that looks at the selection gradients imposed by each guild of parasitoids and visualizes it.
-
-> Spend 10 min. trying to figure out how to double-space the manuscript.
-
-> Tidy repo
-
-> Draft Discussion
-
-> Calculate selection gradients acting on Platygaster. This will enable me to have a discussion about potential indirect evolutionary cascades occuring via changes in network complexity.

### 2018-10-23 analyses/reproduce_analyses.Rmd
analyses updates

@@
 
+```{r Bias in gradients on chamber diameter}
+fixef(biased.diam_model_4)["sc.Diam"]
+```
+
+```{r Variance explained in chamber diameter}
+chamber_diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), data=gall_selection.df)
+summary(chamber_diam)
+car::Anova(chamber_diam, test="F")
+
+# variance explained by gall ID
+0.5374/(0.5374+0.0956+0.1671+0.2031)
+```
+
+```{r Variance explained in other traits}
+clutch_size <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, Gall_Number, sc.log.Clutch))
+summary(clutch_size)
+car::Anova(clutch_size, test="F")
+
+female_pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, sc.log1p.Pref))
+summary(female_pref)
+car::Anova(female_pref, test="F")
+```
+
+```{r female pref plot, echo=F}
+visreg::visreg(female_pref, xvar="Foodweb")
+```
+
 ```{r Plot of bias adjusted Selection Gradients, echo=FALSE}
@@
 platy_Pref_levene <- leveneTest(sc.log1p.Pref ~ Foodweb, platy_selection_df)
+```
+
+```{r Levene tests}
+platy_Diam_levene
+platy_Clutch_levene
+platy_Pref_levene
 ```
@@
 To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
+-->
 
@@
 ```
+
+## Contributions of egg parasitoids to selection gradients
+
+To identify the mechanisms by which food-web treatment altered selection gradients, we refit our models so that the complex food-web treatment only contained cases of parasitisms from egg parasitoids.
+Therefore, these analyses identify the change in apparent selection imposed by the egg parasitoid (egg parasitoid from simple food web; egg parasitoid from complex food web).
+
+```{r Egg vs. egg Parasitoids Model, cache=TRUE}
+
+# excludes cases of egg-parasitism from Complex food web
+egg.vs.egg_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & ectos < 1) #%>% 
+ # mutate(Foodweb = ifelse(Foodweb == "Simple", "Egg", "egg"))
+
+egg.vs.egg_df$Foodweb <- relevel(factor(egg.vs.egg_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids
+
+egg.egg_model_1 <- update(model_1, data=egg.vs.egg_df)
+summary(egg.egg_model_1)
+```
+
+```{r egg vs egg ggplot explore}
+densities <- gall_selection.df %>%
+  distinct(Foodweb, Genotype, Plant_Position, sc.log1p.Pref, Density_per_100_shoots)
+
+survival <- gall_selection.df %>%
+  group_by(Foodweb, Plant_Position) %>%
+  summarise_at(vars(gall_survival, egg_parasitoid, ectos), funs(sum, n())) %>%
+  ungroup() %>%
+  mutate(ptoids_sum = egg_parasitoid_sum + ectos_sum)
+
+left_join(densities, survival) %>%
+  filter(Foodweb=="Complex") %>%
+  ggplot(., aes(x=sc.log1p.Pref, y=ectos_sum/ptoids_sum)) +
+  geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial")) #+
+  #scale_x_continuous(limits=c(-2,1.25))
+
+left_join(densities, survival) %>%
+  filter(Foodweb=="Complex") %>%
+  ggplot(., aes(x=sc.log1p.Pref, y=egg_parasitoid_sum/ptoids_sum)) +
+  geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial"))
+
+left_join(densities, survival) %>%
+  ggplot(., aes(x=sc.log1p.Pref, y=gall_survival_sum/gall_survival_n, color=Foodweb)) +
+  geom_point(aes(size=gall_survival_n), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial"))
+
+left_join(densities, survival) %>%
+  ggplot(., aes(x=sc.log1p.Pref, y=gall_survival_n, color=Foodweb)) +
+  geom_point(aes(size=gall_survival_n), shape=21) +
+  geom_smooth(method = "lm", formula = y ~ x, aes(weight=gall_survival_n))
+
+left_join(densities, survival) %>%
+  filter(Foodweb=="Complex") %>%
+  ggplot(., aes(x=sc.log1p.Pref)) +
+  #geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) + 
+  scale_x_continuous(limits=c(-1,1))
+
+left_join(densities, survival) %>%
+  filter(Foodweb=="Simple") %>%
+  ggplot(., aes(x=sc.log1p.Pref)) +
+  #geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +  # geom_smooth(method = "lm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green")
+  scale_x_continuous(limits=c(-1,1))
+
+# in the complex food web, there is a positive relationship between the number of gall samples and gall density (makes sense); there is the opposite pattern in the simple foodweb...
+density_n_lm <- lm(gall_survival_n ~ sc.log1p.Pref*Foodweb, left_join(densities, survival))
+visreg::visreg(density_n_lm, xvar="sc.log1p.Pref", by="Foodweb")
+summary(density_n_lm)
+wt_density_n_lm <- lm(gall_survival_n ~ sc.log1p.Pref*Foodweb, left_join(densities, survival), weights = gall_survival_n)
+visreg::visreg(wt_density_n_lm, xvar="sc.log1p.Pref", by="Foodweb")
+summary(wt_density_n_lm)
+
+# good thing is that I get the same qualitative answer with or without weighting
+test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(densities, survival), family="quasibinomial")
+visreg::visreg(test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+summary(test_glm)
+
+wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(densities, survival), family="quasibinomial", weights = gall_survival_n)
+visreg::visreg(wt_test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+summary(wt_test_glm)
+
+# now with just egg parasitoids
+egg.densities <- egg.vs.egg_df %>%
+  distinct(Foodweb, Plant_Position, sc.log1p.Pref)
+
+egg.survival <- egg.vs.egg_df %>%
+  group_by(Foodweb, Plant_Position) %>%
+  summarise_at(vars(gall_survival, egg_parasitoid, ectos), funs(sum, n())) %>%
+  ungroup() %>%
+  mutate(ptoids_sum = egg_parasitoid_sum + ectos_sum)
+
+egg.test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial")
+visreg::visreg(egg.test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+summary(egg.test_glm)
+
+egg.wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial", weights = gall_survival_n)
+visreg::visreg(egg.wt_test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+summary(egg.wt_test_glm)
+
+## now use raw densities
+sqrt.raw_complex <- left_join(densities, survival) %>%
+  filter(Foodweb=="Complex") %>%
+  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
+  ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
+  #geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
+  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
+      geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") 
+  #facet_wrap(~Genotype, ncol=2, nrow=4)
+
+sqrt.raw_simple <- left_join(densities, survival) %>%
+    filter(Foodweb=="Simple") %>%
+    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
+    ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
+    #geom_point(aes(size=ptoids_sum), shape=21) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+    scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") 
+   # facet_wrap(~Genotype, ncol=2, nrow=4)
+
+plot_grid(sqrt.raw_complex, sqrt.raw_simple, ncol=2)
+
+raw_complex <- left_join(densities, survival) %>%
+  filter(Foodweb=="Complex") %>%
+  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
+  ggplot(., aes(x=(Density_per_100_shoots))) +
+  #geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
+  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,100)) +
+      geom_vline(xintercept=mean((densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) + sd((densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) - sd((densities$Density_per_100_shoots)), linetype="dotted") 
+  #facet_wrap(~Genotype, ncol=2, nrow=4)
+
+  raw_simple <- left_join(densities, survival) %>%
+    filter(Foodweb=="Simple") %>%
+    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
+    ggplot(., aes(x=(Density_per_100_shoots))) +
+    #geom_point(aes(size=ptoids_sum), shape=21) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+    scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,100)) +
+    geom_vline(xintercept=mean((densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) + sd((densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) - sd((densities$Density_per_100_shoots)), linetype="dotted") 
+   # facet_wrap(~Genotype, ncol=2, nrow=4)
+
+plot_grid(raw_complex, raw_simple, ncol=2)
+
+log1p.raw_complex <- left_join(densities, survival) %>%
+  filter(Foodweb=="Complex") %>%
+  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
+  ggplot(., aes(x=log1p(Density_per_100_shoots))) +
+  #geom_point(aes(size=ptoids_sum), shape=21) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
+  scale_y_continuous(limits=c(0,1)) + #scale_x_continuous(limits=c(0,100)) +
+      geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) + sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) - sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") 
+  #facet_wrap(~Genotype, ncol=2, nrow=4)
+
+log1p.raw_simple <- left_join(densities, survival) %>%
+    filter(Foodweb=="Simple") %>%
+    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
+    ggplot(., aes(x=log1p(Density_per_100_shoots))) +
+    #geom_point(aes(size=ptoids_sum), shape=21) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
+    scale_y_continuous(limits=c(0,1)) +# scale_x_continuous(limits=c(0,100)) +
+    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) + sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) - sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") 
+   # facet_wrap(~Genotype, ncol=2, nrow=4)
+
+plot_grid(log1p.raw_complex, log1p.raw_simple, ncol=2)
+
+left_join(densities, survival) %>%
+  ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
+    #geom_point(aes(size=ptoids_sum), shape=21) +
+    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n, color=Foodweb), method.args = list(family="binomial")) +
+  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
+    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted")
+
+ggplot(densities, aes(x=Genotype, y=Density_per_100_shoots, fill=Foodweb)) + geom_boxplot()
+ggplot(densities, aes(x=Genotype, y=sc.log1p.Pref, fill=Foodweb)) + geom_boxplot()
+
+summary(lm(Density_per_100_shoots ~ Foodweb, filter(densities, Density_per_100_shoots>0)))
+summary(lm(sqrt(Density_per_100_shoots) ~ Foodweb, filter(densities, Density_per_100_shoots>0)))
+car::Anova(lmer(sqrt(Density_per_100_shoots) ~ Foodweb + (1|Genotype), filter(densities, Density_per_100_shoots>0)), test="F")
+summary(lm(sc.log1p.Pref ~ Foodweb, densities))
+
+with(densities, table(Foodweb, Density_per_100_shoots))
+
+ggplot(densities, aes(x=Density_per_100_shoots, fill=Foodweb)) + geom_density(alpha=0.5)
+ggplot(densities, aes(x=sqrt(Density_per_100_shoots), fill=Foodweb)) + geom_density(alpha=0.5)
+ggplot(densities, aes(x=sc.log1p.Pref, fill=Foodweb)) + geom_density(alpha=0.5)
+
+shapiro.test(densities$Density_per_100_shoots)
+shapiro.test(sqrt(densities$Density_per_100_shoots))
+shapiro.test(log1p(densities$Density_per_100_shoots))
+
+clutches <- gall_selection.df %>%
+  distinct(Foodweb, Genotype, Plant_Position, sc.log.Clutch, gall_individuals)
+shapiro.test((clutches$gall_individuals))
+shapiro.test(sqrt(clutches$gall_individuals))
+shapiro.test(log(clutches$gall_individuals))
+
+shapiro.test((gall_selection.df$Gall_Height_mm))
+shapiro.test(sqrt(gall_selection.df$Gall_Height_mm))
+shapiro.test(log(gall_selection.df$Gall_Height_mm))
+```
+
+```{r Egg vs. Egg Bootstrap Model 1, include=FALSE, cache=TRUE}
+egg.egg_boot_model_1 <- bootMer(egg.egg_model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+egg.egg_tidy_model_1 <- tidy(egg.egg_boot_model_1, conf.int=T) %>% 
+  # filter terms that only matter for this analysis
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
+                     "FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)",
+                     "FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.log1p.Pref","FoodwebComplex:sc.log.Clutch:sc.log1p.Pref"))
+```
+
+There is no strong evidence that egg parasitism differs for nonlinear terms between complex and simple food webs. Although close perhaps for sc.Diam.
+
+```{r Egg vs. Egg Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE}
+knitr::kable(egg.egg_tidy_model_1)
+
+egg.egg_plot_model_1 <- egg.egg_tidy_model_1 %>%
+  mutate(Food_web = ifelse(grepl("FoodwebComplex", .$term)==TRUE,"Complex","Simple")) %>%
+  filter(Food_web == "Complex")
+
+egg.egg_plot_model_1$term_plot <- factor(egg.egg_plot_model_1$term,
+                                levels=c("FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.log1p.Pref","FoodwebComplex:sc.log.Clutch:sc.log1p.Pref"),
+                                ordered=TRUE)
+
+egg.egg_plot_model_1 %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(egg.egg_plot_model_1$term_plot))) +
+  ylab("Coefficient (logit scale)")
+
+visreg::visreg(egg.egg_model_1, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
+```
+
+Now we assess their contribution to the effect of food-web treatment on the linear terms.
+
+```{r Fit Egg vs. egg Parasitoid Model 3, cache=TRUE}
+egg.egg_model_3 <- update(model_3, data=egg.vs.egg_df) 
+```
+
+```{r Bootstrap Egg vs. egg Parasitoid Model 4, cache=TRUE, include=FALSE}
+boot_egg.egg_model_3 <- bootMer(egg.egg_model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_egg.egg_model_3 <- tidy(boot_egg.egg_model_3, conf.int=T) 
+```
+
+Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
+```{r Plot Egg vs. egg Parasitoid Model 4, echo=FALSE}
+egg.egg_plot_model_3 <- tidy_egg.egg_model_3 %>%
+  mutate(Food_web = ifelse(grepl("FoodwebComplex:", .$term)==TRUE,"Complex","Simple")) %>%
+  filter(Food_web == "Complex")
+
+egg.egg_plot_model_3$term_plot <- factor(egg.egg_plot_model_3$term,
+                                levels=c("FoodwebComplex:sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebComplex:sc.log1p.Pref"),
+                                ordered=TRUE)
+
+egg.egg_plot_model_3 %>%
+  ggplot(., aes(x=term_plot)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(egg.egg_plot_model_3$term_plot))) +
+  ylab("Coefficient (logit scale)")
+```
+
+```{r Fit Egg vs. egg Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE}
+egg.egg_model_4_adj <- update(model_4_adj, data=egg.vs.egg_df)
+```
+
+This reduced model returns the same qualitative result as before.
+Specifically, that the linear effect of clutch size depends on food-web treatment.
+Note also that egg survival is significantly higher in the simple food web compared to the complex food web (dotted line).
+These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
+
+```{r Bootstrap Egg vs. egg Parasitoid adjuted Model 4, cache=TRUE, include=FALSE, eval=FALSE}
+boot_egg.egg_model_4_adj <- bootMer(egg.egg_model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+tidy_egg.egg_model_4_adj <- tidy(boot_egg.egg_model_4_adj, conf.int=T) 
+```
+
+Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
+```{r Plot Egg vs. egg Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE}
+tidy_egg.egg_model_4_adj$term_ord <- factor(tidy_egg.egg_model_4_adj$term, 
+                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
+                                ordered = TRUE)
+
+plot_egg.egg_model_4_adj <- tidy_egg.egg_model_4_adj %>%
+  filter(term != "(Intercept)") %>%
+  droplevels()
+
+plot_egg.egg_model_4_adj %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
+  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(plot_egg.egg_model_4_adj$term_ord))) +
+  ylab("Coefficient (logit scale)")
+```
+
+## CALCULATE SELECTION GRADIENTS FOR EGG VS. egg PARASITOIDS
+
+```{r Organize and Transform egg vs. egg parasitoid Coefficients, include=FALSE, eval=FALSE}
+tidy_egg.egg_coefs <- bind_rows(
+  select(tidy_egg.egg_model_2_adj, term, estimate, conf.low, conf.high), 
+  select(tidy_egg.egg_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
+  filter(term != "(Intercept)", term != "FoodwebLarval") # remove main effects
+
+# Tidy common coefficients
+tidy_egg.egg_common_coefs <- tidy_egg.egg_coefs %>%
+  filter(term!="FoodwebEgg:I(sc.log1p.Pref^2)", term!="Foodwebegg:I(sc.log1p.Pref^2)",
+         term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")
+
+# Tidy unique coefficients to each food-web
+egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:I(sc.log1p.Pref^2)")
+egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
+egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:I(sc.log1p.Pref^2)")
+egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
+
+egg_clutch <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:sc.log.Clutch")
+egg_clutch$term <- "sc.log.Clutch"
+egg_clutch <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:sc.log.Clutch")
+egg_clutch$term <- "sc.log.Clutch"
+```
+
+```{r Calculate Egg vs. egg parasitoid Selection Gradients, include=FALSE, eval=FALSE}
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
+egg_predict <- predict(egg.egg_model_2, newdata=filter(egg.vs.egg_df, Foodweb=="egg"), type="response")
+egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
+egg_mean_fitness <- mean(egg_predict)
+
+egg_predict <- predict(egg.egg_model_2, newdata=filter(egg.vs.egg_df, Foodweb=="Egg"), type="response")
+egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
+egg_mean_fitness <- mean(egg_predict)
+
+# Double-check that using a different model (e.g.
+egg.egg_model_4) doesn't influence estimes of mean "brackets" and mean fitness.
+Using "Complex" food-web treatment as an example, but it doesn't matter
+alt_egg.egg_predict <- predict(egg.egg_model_4, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
+alt_egg.larval_mean_brackets <- mean(alt_egg.larval_predict * (1 - alt_egg.larval_predict))
+alt_egg.larval_mean_fitness <- mean(alt_egg.larval_predict)
+test_egg.larval_mean_brackets <- larval_mean_brackets
+test_egg.larval_mean_fitness <- larval_mean_fitness
+test_egg.larval_mean_brackets - alt_egg.larval_mean_brackets # virtually the same
+test_egg.larval_mean_fitness - alt_egg.larval_mean_fitness # virtually the same
+
+tidy_egg_grads <- bind_rows(tidy_egg.larval_common_coefs, egg_quad_pref, egg_clutch) %>%
+  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
+2008)
+  transmute(term=term,
+            gradient = egg_mean_brackets * estimate / egg_mean_fitness * Multiplier,
+            `2.5%` = egg_mean_brackets * conf.low / egg_mean_fitness * Multiplier,
+            `97.5%` = egg_mean_brackets * conf.high / egg_mean_fitness * Multiplier)
+
+tidy_larval_grads <- bind_rows(tidy_egg.larval_common_coefs, larval_quad_pref, larval_clutch) %>%
+    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
+2008)
+  transmute(term=term,
+            gradient = larval_mean_brackets * estimate / larval_mean_fitness * Multiplier,
+            `2.5%` = larval_mean_brackets * conf.low / larval_mean_fitness * Multiplier,
+            `97.5%` = larval_mean_brackets * conf.high / larval_mean_fitness * Multiplier)
+
+egg.larval_selection_gradients <- bind_rows(
+  mutate(tidy_egg_grads, `Food web`="Egg"),
+  mutate(tidy_larval_grads, `Food web`="Larval")) #%>%
+  #mutate(Type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic", ifelse(grepl(":", .$term)==TRUE, "Correlational", "Directional")))
+```
+
+```{r Table of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE}
+egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
+                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
+                                   ordered = TRUE)
+
+egg.larval_selection_gradients_table <- egg.larval_selection_gradients %>%
+  transmute(Term=term_ord, Parasitoid=`Food web`, Gradient=round(gradient,2), `2.5%`=round(`2.5%`,2), `97.5%`=round(`97.5%`,2)) %>% 
+  arrange(Term)
+
+knitr::kable(egg.larval_selection_gradients_table, caption = "Table of Egg vs. Larval Parasitoid Selection Gradients")
+```
+
+```{r Plot of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE}
+egg.larval_selection_gradients %>%
+  ggplot(., aes(x=term_ord)) +
+  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
+  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
+  coord_flip() +
+  geom_hline(yintercept=0, linetype="dotted") +
+  scale_x_discrete(name="", limits = rev(levels(egg.larval_selection_gradients$term_ord))) +
+  ylab("Selection Gradient") +
+  scale_fill_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) +
+  scale_color_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) 
+```

### 2018-10-23 manuscript/manuscript.tex
manuscript updates

@@
 
-\subsection*{Quantifying the Fitness Landscape}
+ Inferring the adaptive landscape from individual selection surfaces assumes that trait distributions are multivariate normal (Lande and Arnold 1983).
+To approximate this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
+We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
 
-To characterize the shape of the fitness landscape in simple and complex food webs, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
-We used a binomial error distribution (logit link function) since larval survival (0 or 1) was our response variable and measure of fitness.
-We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
-Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
-setting them to zero) to estimate selection gradients.
-Also, the fitness landscape assumes that traits distributions are multivariate normal.
-To better meet this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
-We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
-We used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95\% confidence intervals (@Bolker2009).
-We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
-Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
-This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean trait values of the population (Arnold 2001, Morrissey 2009).
+Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits which would bias our measurements of selection.
+%In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
+Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
+To estimate this bias, we subset our data to only include galls where there was variation in larval survival within the same gall (i.e.
+1 > mean survival > 0).
+Using the statistical methods discussed in the next section, we calculated the "apparent" relationship between chamber diameter and larva survival ($\alpha_{\text{Diam}}$).
+We detected a positive bias ($\alpha_{\text{Diam}}$= 0.35), indicating that unadjusted analyses would overestimate the strength of selection on chamber diameter.
+To account for this bias, we substracted 0.35 from our estimate of $\alpha_{\text{Diam}}$ with the full dataset prior to calculating directional selection on chamber diameter.
+Note that this analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
+Our data supports this assumption, as we found that gall ID explains 54\% of the variance in chamber diameter.
 
-Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits.
-Any influence on trait expression would bias selection gradients acting on those traits.
-In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
-Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
-To estimate this bias, we subset our data to only include galls where there was variation in larval survival (1 > survival > 0) within the same gall.
-We then calculated "apparent" selection differentials for each gall by comparing the average chamber diameter of all larva (before "selection") to the average chamber diameter of surviving larva and analyzed separate one-sample t-tests for each food-web treatment.
-This analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
-In general, we found that our estimates of directional selection on chamber diameter were positively biased (Appendix).
-In other words, our analyses were overestimating the magnitude of selection acting on gall diameter.
-Therefore, we adjusted our estimates of directional selection on chamber diameter ($\beta_{diam}$) by subtracting the biased selection differentials.
-Note that selection gradients and selection differentials for chamber diameter were virtually the same (Appendix).
+\subsection*{Quantifying the Adaptive Landscape}
 
-\subsection*{Quantifying Selective Constraints}
+Our analyses consisted of three parts.
+First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and phenotypic traits ($z_i$) of individuals \textemdash in each food-web treatment.
+Second, we translated our approximation of the selection surface into the scale of relative fitness ($w$) in order to calculate selection gradients.
+Third, we used our estimates of selection gradients to characterize the slope and curvature of the population's adaptive landscape.
 
-The strength and pattern of selective constraints can be measured as the slope and curvature of the fitness landscape (Arnold 1992).
+\textbf{Selection surface}: Since larva survival was our measure of absolute fitness we used a GLMM that assumed a binomial error distribution (and logit-link function).
+To approximate the selection surface, we modelled larva survival as a function of food-web treatment as well as linear ($\alpha_{z_i}$), quadratic ($\alpha_{z_i:z_i}$), and linear interactions ($\alpha_{z_i:z_j}$) between each trait.
+Other approaches have been advocated for approximating the selection surface (Schluter 1988); however, our approach enables us to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational selection ($\gamma_{z_i,z_j}$) gradients, and thus is more appropriate for our approximating the adaptive landscape (cite Arnold).
+We also allowed these $\alpha$ coefficients to vary between food-web treatments.
+To account for the nonindependence of individual estimates of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larva survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
+Including these random effects helps alleviated biased estimates of selection due to environmental covariances between traits and fitness (Rausher 1992 Evolution).
+With our full statistical model, we used parametric bootstrapping (1,000 replicates) to test whether our food-web treatment altered each $\alpha$ coefficient.
+If the 95\% confidence interval of this food-web:$\alpha$ effect overlapped with zero, then we removed this statistical interaction and refit the model.
+Note that our final model of the selection surface still included estimates (and 95\% CI) of our food-web treatment and all possible $\alpha$ coefficients, even if they overlapped with zero, but only a subset of possible food-web:$\alpha$ coefficients.
+Note also that we estimated linear coefficients ($\alpha_{z_i}$) by excluding quadratic and linear interaction terms in the statistical model (Lande and Arnold 1983).
+%To test how food-web complexity shapes the adaptive landscape, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
+We used a binomial error distribution (with logit-link function) since larval survival (0 or 1) was our response variable and measure of fitness.
+We specified linear and quadratic terms for each gall trait ($z_i$) as well as linear interaction terms between each gall trait as fixed effects ($\alpha$) in the statistical models.
+These linear ($\alpha_{z_i}$), quadratic ($\alpha_{z_i,z_i}$), and linear interaction ($\alpha_{z_i,z_j}$) terms are key components of our estimates of directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational selection ($\gamma_{z_i,z_j}$), respectively.
+We also specified main effects for food-web treatment and statistical interactions between food-web treatment and each $\alpha$.
+We used parametric bootstrapping (1,000 replicates) to quantify the effect of each $\alpha$ on larva survival and whether this varied between food-web treatments ($food-web \times \alpha$).
+If we did not observed an effect of food-web treatment, we fit a reduced model that only include the unique $\alpha$ term.
+In other words, our statistical model of the adaptive landscape included all possible $\alpha$ terms, but not statistical interactions between food-web treatment and each $\alpha$ term.
 
-We can translate selection surfaces of individuals to the fitness landscape of a population
+\textbf{Selection gradients}: Since we were interested in characterizing the adaptive landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
+setting them to zero) when calculating selection gradients.
+We then used the method of Janzen and Stern (1998) to translate our estimates (and 95\% CI) of each $\alpha$ coefficient into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
 
-To characterize the net effects of food-web complexity on the slope and curvature of *Iteomyia*'s fitness landscape, we took advantage of existing theory that links selection surfaces of individuals to the fitness landscape of the population (Phillips & Arnold 1998, Arnold 2003).
-Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
+\textbf{Adaptive landscape}: We took advantage of existing theory that translates estimates of selection gradients to the population's adaptive landscape (Phillips and Arnold 1998, Arnold 2003).
+Specifically, the slope of the adaptive landscape corresponds to the column vector of directional selection gradients:
 
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
-whereas the curvature of the fitness landscape is a function of the directional, nonlinear, and correlational selection gradients: 
-$$\text{Curvature} = \gamma - \beta \beta^T$$
-where \gamma represents the matrix of nonlinear and correlational selection gradients:
-$$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
+$$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
+
+whereas the curvature ($C$) of the adaptive landscape is a matrix that is determined by directional, quadratic, and correlational selection gradients:
+
+$$\text{Curvature} = C = \gamma - \beta \beta^T$$
+
+where $\gamma$ represents the matrix of quadratic (diagonal) and correlational (off-diagonal) selection gradients:
+
+$$\gamma = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix}$$
 
 Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
-Assuming that there is additive genetic variance and covariance between these traits under selection, then the slope and curvature of the fitness landscape give insight to how the population's mean trait value will change in the next generation as well as how additive genetic variance and covariance changes within a generation.
+Assuming that there is additive genetic variance and covariance between these traits, then the slope and curvature of the adaptive landscape give insight to changes in the population's mean trait value between generations ($\Delta z = \text{G} \beta$) and G-matrix structure within a generation ($\Delta \text{G} = \text{G} (\gamma - \beta \beta^\text{T}) \text{G}$).
 
-While making quantitative predictions about trait evolution requires knowledge of the additive genetic variance and covariance of these traits, the slope and curvature of the fitness landscape still give qualitative insight to the evolutionary trajectory of a population.
+Although quantitative predictions about trait and G-matrix evolution require knowledge of a population's G-matrix, the adaptive landscape can still yield valuable qualitative insight.
+In particular, we can infer selective constraints acting on a population by inspecting the structure of the matrix describing the curvature of the adaptive landscape.
+For example, the sign of the values along the diagonal of the curvature matrix dictate whether selection will increase ($+$), decrease ($-$), or cause no change ($0$) in the additive genetic variance of a trait.
+Similarly, any nonzero covariance terms (off-diagonal) are indicative of trait integration.
+We propose that you can infer selective constraints acting on a population by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal of the matrix (trait integration).
 
-If we assume that there is additive genetic variance and covariance between these traits, then the matrix describing the curvature of the fitness landscape gives qualitative insight to the selective constraints acting on the population.
-For example, the diagonal of the curvature matrix dictates (qualitatively) whether the additive genetic variance in each trait will increase ($+$), decrease ($-$), or stay the same ($0$).
-Similarly, the off-diagonal of the curvature matrix dictates whether selection favors trait integration (positive covariance), a tradeoff (negative covariance), or no change in genetic covariance.
-In other words, we can get qualitative insight to how food-web complexity influences constraints on the fitness landscape by counting the number of negative sign values along the diagnoal (which imply a decrease in additive genetic variance) and the number of positive or negative signs along the off diagonal (which imply changes in additive genetic covariance that lead to either trait integration or tradeoffs).
-
-All analyses and visualizations were conducted in R (@R2018).
-
-I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
-
-If we only retain non-zero selection gradients, then we can
-
-Our two dimensional surfaces are likely representative given the fact that there is no strong evidence of correlational selection (Phillips and Arnold 1989, Evolution)
-
-The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes additive genetic (co)variances ($\Delta \text{G}$) within a generation.
+%The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes additive genetic (co)variances ($\Delta \text{G}$) within a generation.
 Specifically, the diagonals of the curvature matrix describe the effect of the adaptive landscape on additive genetic variance within a generation; therefore, any negative values along the diagonal are evidence of selective constraints.
@@
 
-\subsection*{Simulating Phenotypic Evolution}
+\subsection*{Measuring selection on Platygaster sp.}
 
-We used the method proposed by Hansen and Houle (2008) to characterize the evolvability of the G-matrices resulting from different adaptive landscapes.
-Their index of evolvability is theoretically linked to the theory underlying G matrices and adaptive landscapes, and describes the ability of a population to evolve in the direction of selection when stabilizing selection is absent.
+Our experimental manipulation of food-web complexity enables us to also measure selection on the egg parasitoid (\textit{Platygaster sp.}), albeit with a different approach.
+Specifically, we can compare the distribution of gall traits that the egg parasitoid is observed in simple vs.
+complex food webs.
+In essence, the gall phenotype becomes the extended phenotype of the egg parasitoid, since its attributes can influence the egg parasitoid's survival in the face of intraguild predation (larval parasitoid guild).
+This cross-sectional analysis allows us to estimate directional and quadratic selection differentials, but not selection gradients.
 
-% Hansen and Houle 2008
-%Alternatively, but not
-%inconsistently, evolvability can be viewed in a quantitative
-%genetics context as a short-term ability to respond to
-%directional selection (Houle, 1992), which depends on
-%standing additive genetic variation in the traits under
-%selection and on the autonomy of this genetic variation
-%from other traits under stabilizing selection (Hansen
-%et al., 2003a, b; Hansen, 2003; Hansen & Houle, 2004)
+To quantify directional selection differentials, we used separate linear mixed models with the standardized gall trait as the response variable, food-web treatment as the fixed effect, and the same suite of random effects as for our primary analyses of \textit{Iteomyia} survival (i.e.
+gall ID, nested within plant ID, nested within plant genotype).
+
+To quantify quadratic selection differentials, we can calculate the difference in variance between simple and complex food webs.
+We then used Levene's test for homogeneity of variance to determine the statistical significance of these quadratic selection differentials.
+Note that this result should be interpreted cautiously, since we cannot account for the nonindependence of gall phenotypes due to plant genotype, plant ID, or gall ID.
+
+All analyses and visualizations were conducted in R (@R2018).
+Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
+This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean trait values of the population (Arnold 2001).
+We also plot mean larva survival on a natural log scale to accurately reflect the shape of the adaptive landscape.
 
@@
 
+\subsection*{Selection on the extended phenotype of egg parasitoid}
+
+We did not observed any evidence of directional or quadratic selection on chamber diameter ($s_{Diam}=0.06 [-0.14,0.27]; s_{Diam:Diam}=-0.11, P=0.28$) or clutch size ($s_{Clutch}=0.21 [-0.10,0.51]; s_{Clutch:Clutch}=-0.24, P=0.17$) that the egg parasitoid was associated with.
+However, we did observed directional selection for egg parasitoids to attack larva on high density trees ($s_{Pref}=0.20 [-0.10,0.51]) and an associated decrease in phenotypic variance ($s_{Pref:Pref}=-0.91, P<0.001$).
+
 \section*{Discussion}
-
-Our key finding was that phenotypic evolution was less constrained for a species that was embedded within a complex food web compared to a simple one. These
 
@@
 the simple food web.
+
+% If selection was present, it was stronger in complex food webs
+% - Difficult to judge how real this is given that it was artificially enhanced due to our food-web treatment.
+% - Importance of analyzing components of relative fitness for understanding the mechanisms.
+
+%% 2) Fewer selective constraints in complex vs. simple food webs.
+
+% - Due to fewer traits under directional selection, as well as the presence of disruptive selection.
+% - With just 1 less trait under selection, it influenced half of the (co)variance effects on the curvature matrix. 
+% - This was a result of conflicting selection pressures in the complex food web.
+% - Survival higher at small clutch sizes with egg parasitoids -> I expect this is a density mediated process, where higher local densities of eggs and first-instar larva are easier to detect.
+% - Survival higher at large clutch sizes with larval parasitoids -> This could be because neighboring larva could provide a buffer against parasitoid attack, thus enhancing the probability of survival at the individual level.
+
+% - Also due to disruptive selection on female preference.
+% - Disruptive pattern appears to be driven by larval guild.
+This could be a result of them being poorer colonizers and thus reach a saturation effect at higher larval density.
+This would result in larva at especially high densities to gain a "relative" refuge.
+In contrast, the egg parasitoid may be an effective forager at the field densities we observed resulting in simply higher parasitism rates.
+This is consistent with the fact of egg parasitoids being more effective searchers.
+Appears to be some evidence for this from Amaresekare 2000, Ecology (exploitation-interference tradeoff rather than competition colonization).
+% - I think my data is indicative of a type III functional response.
+
+% - Traits vs. ecological variables...female preference and host density as an example.
 
@@
 %Path relative to the main .tex file 
-\graphicspath{ {../analyses/reproduce_analyses_files/figure-html/} }
+\graphicspath{ {../analyses/} }
 
 \begin{figure}[h!]
-\includegraphics{Selection-Gradients-1.png}
+\includegraphics[scale=0.5]{complex_simple_foodwebs.jpeg}
+\caption{Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, \emph{Iteomyia salicisverruca}.
+Black arrows denote the flow of energy in this network of trophic interactions.}
+\label{Fig:Concept}
+\end{figure}
+
+\begin{figure}[h!]
+\includegraphics{reproduce_analyses_files/figure-html/Selection-Gradients-1.png}
 \caption{Selection gradients acting on \textit{Iteomyia} phenotypes.
@@
 \begin{figure}[h!]
-\includegraphics{Univariate-Fitness-Landscapes-1.png}
+\includegraphics{reproduce_analyses_files/figure-html/Univariate-Fitness-Landscapes-1.png}
 \caption{Adaptive landscape of \textit{Iteomyia} phenotypes in complex vs.
@@
 \begin{figure}[h!]
-\includegraphics{Multivariate-Fitness-Landscapes-1.png}
+\includegraphics{reproduce_analyses_files/figure-html/Multivariate-Fitness-Landscapes-1.png}
 \caption{Two dimensional view of adaptive landscapes in complex vs.

### 2018-10-24 analyses/reproduce_analyses.Rmd
changed from log1p to sqrt transformation of female preference

@@
          sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
-         sc.log1p.Pref = as.numeric(scale(log1p(Density_per_100_shoots))))
+         sc.sqrt.Pref = as.numeric(scale(sqrt(Density_per_100_shoots))))
 
@@
 
-mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.log1p.Pref), multivariatePlot = "qq", univariatePlot = "histogram")
-
-# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.log1p.Pref), multivariatePlot = "qq")
+mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq", univariatePlot = "histogram")
+
+# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
 
@@
 model_1 <- glmer(
-  gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.log1p.Pref +
-    Foodweb:(sc.Diam + sc.log.Clutch + sc.log1p.Pref) +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2) +
-    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref +
-    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.log1p.Pref + sc.log.Clutch:sc.log1p.Pref) +
+  gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
     (1|Genotype/Plant_Position/Gall_Number),
@@
 We use parametric bootstrapping (n=`r n_boots_analysis`) to evaluate the statistical significance of the effect of food-web treatment on nonlinear terms (i.e.
-Foodweb:trait^2 or Foodweb:trait_1:trait_2).
+Foodweb:trait~i~^2^ or Foodweb:trait~i~:trait~j~).
 Food-web treatment does influence the quadratic effect of of female preference on larva survival.
@@
 
-tidy_model_1 <- tidy(boot_model_1, conf.int=T) %>% 
+tidy_model_1 <- tidy(model_1, conf.int=T) %>% #tidy(boot_model_1, conf.int=T) %>% 
   # filter terms that only matter for this analysis
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref")) 
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
+                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.sqrt.Pref^2)",
+                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.sqrt.Pref","FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref")) 
 ```
@@
 plot_model_1$term_plot <- factor(plot_model_1$term,
-                                levels=c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.log1p.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.log1p.Pref","FoodwebSimple:sc.log.Clutch:sc.log1p.Pref"),
+                                levels=c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.sqrt.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.sqrt.Pref","FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref"),
                                 ordered=TRUE)
@@
   geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
+  geom_point(aes(y=estimate), shape=21, size=3, fill="grey") + # y=statistic for bootstrap
   coord_flip() +
@@
 model_2 <- update(model_1, 
-                  .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2)
-                  -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.log1p.Pref -Foodweb:sc.log.Clutch:sc.log1p.Pref)
+                  .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.sqrt.Pref^2)
+                  -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.sqrt.Pref -Foodweb:sc.log.Clutch:sc.sqrt.Pref)
 ```
@@
 
-tidy_model_2 <- tidy(model_2, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebSimple:I(sc.log1p.Pref^2)")) 
+tidy_model_2 <- tidy(model_2, conf.int=T) %>% # tidy(boot_model_2, conf.int=T) %>% 
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
+                     "FoodwebSimple:I(sc.sqrt.Pref^2)")) 
 ```
@@
 tidy_model_2$term_plot <- factor(tidy_model_2$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                             ordered = TRUE)
@@
   geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) +
+  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) + # y=statistic
   coord_flip() +
@@
 
-Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.log1p.Pref^2)* indicates that food-web treatment alters quadractic selection on female preference; however, this coefficient is not useful for actually calculating the selection gradient.
+Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.sqrt.Pref^2)* indicates that food-web treatment alters quadractic selection on female preference; however, this coefficient is not useful for actually calculating the selection gradient.
 To do this, we refit a model so rather than estimating the change in slope (currently), it will actually estimate the slope.
 See [Schielzeth 2010](https://doi.org/10.1111/j.2041-210X.2010.00012.x) for a detailed explanation of this approach.
-```{r Adjust Model 2 for Slopes}
-model_2_adj <- update(model_2, .~. -I(sc.log1p.Pref^2))
-```
-
-```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE}
+```{r Adjust Model 2 for Slopes, eval=FALSE}
+model_2_adj <- update(model_2, .~. -I(sc.sqrt.Pref^2))
+```
+
+```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE, eval=FALSE}
 boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 tidy_model_2_adj <- tidy(model_2_adj, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"))
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebSimple:I(sc.sqrt.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"))
 ```
@@
 
-```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE}
+```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE, eval=FALSE}
 tidy_model_2_adj$term_plot <- factor(tidy_model_2_adj$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebSimple:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebSimple:I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                             ordered = TRUE)
@@
 model_3 <- update(model_2, 
-                  .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.log1p.Pref^2) -Foodweb:I(sc.log1p.Pref^2) 
-                  -sc.Diam:sc.log.Clutch -sc.Diam:sc.log1p.Pref -sc.log.Clutch:sc.log1p.Pref)
+                  .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.sqrt.Pref^2) #-Foodweb:I(sc.sqrt.Pref^2) 
+                  -sc.Diam:sc.log.Clutch -sc.Diam:sc.sqrt.Pref -sc.log.Clutch:sc.sqrt.Pref)
 ```
@@
 
-tidy_model_3 <- tidy(boot_model_3, conf.int=T) 
-```
-
-Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.log1p.Pref")$conf.high,2)`).
+tidy_model_3 <- tidy(model_3, conf.int=T) # boot_model_3
+```
+
+Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$conf.high,2)`).
 
@@
 plot_model_3$term_ord <- factor(plot_model_3$term, 
-                                levels=c("FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log1p.Pref"),
+                                levels=c("FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.sqrt.Pref"),
                                 ordered = TRUE)
@@
   geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
+  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
   coord_flip() +
@@
 ```{r Fit Model 4, cache=TRUE}
-model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.log1p.Pref)
+model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.sqrt.Pref)
 ```
@@
 
-tidy_model_4 <- tidy(boot_model_4, conf.int=T) 
+tidy_model_4 <- tidy(model_4, conf.int=T) # boot_model_4
 ```
@@
 tidy_model_4$term_plot <- factor(tidy_model_4$term, 
-                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
+                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
                                 ordered = TRUE)
@@
 
-tidy_model_4_adj <- tidy(boot_model_4_adj, conf.int=T) 
+tidy_model_4_adj <- tidy(model_4_adj, conf.int=T) # boot_model_4_adj
 ```
@@
 tidy_model_4_adj$term_plot <- factor(tidy_model_4_adj$term, 
-                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
+                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
                                 ordered = TRUE)
@@
 
-tidy_model_4_survival_ests <- tidy(boot_model_4_survival_ests, conf.int=T)
-
-tidy_model_4_survival_ests
+tidy_model_4_survival_ests <- tidy(model_4_survival_ests, conf.int=T) # boot_model_4_survival_ests
+
+round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$estimate),2) # statistic
+round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$estimate),2) # statistic
 ```
@@
 
-Basically, I need to just multiply all of the coefficients by the simple and complex fitness. Except, however, for I(sc.log1p.Pref) and sc.log.Clutch. Here, we need the different coefficients.
+Basically, I need to just multiply all of the coefficients by the simple and complex fitness. Except, however, for I(sc.sqrt.Pref) and sc.log.Clutch. Here, we need the different coefficients.
 
@@
 tidy_coefs <- bind_rows(
-  select(tidy_model_2_adj, term, estimate, conf.low, conf.high), 
-  select(tidy_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
+  select(tidy_model_2, term, estimate, conf.low, conf.high), # estimate=statistic; tidy_model_2_adj no longer needed, since quadratic and correlational selection didn't differ among treatments
+  select(tidy_model_4_adj, term, estimate, conf.low, conf.high)) %>% # estimate=statistic
   filter(term != "(Intercept)", term != "FoodwebSimple") # remove main effects
@@
 tidy_common_coefs <- tidy_coefs %>%
-  filter(term!="FoodwebComplex:I(sc.log1p.Pref^2)", term!="FoodwebSimple:I(sc.log1p.Pref^2)",
+  filter(#term!="FoodwebComplex:I(sc.sqrt.Pref^2)", term!="FoodwebSimple:I(sc.sqrt.Pref^2)",
          term!="FoodwebComplex:sc.log.Clutch",term!="FoodwebSimple:sc.log.Clutch")
@@
 # Tidy unique coefficients to each food-web
-complex_quad_pref <- filter(tidy_coefs, term %in% "FoodwebComplex:I(sc.log1p.Pref^2)")
-complex_quad_pref$term <- "I(sc.log1p.Pref^2)"
-simple_quad_pref <- filter(tidy_coefs, term %in% "FoodwebSimple:I(sc.log1p.Pref^2)")
-simple_quad_pref$term <- "I(sc.log1p.Pref^2)"
+#complex_quad_pref <- filter(tidy_coefs, term %in% "FoodwebComplex:I(sc.sqrt.Pref^2)")
+#complex_quad_pref$term <- "I(sc.sqrt.Pref^2)"
+#simple_quad_pref <- filter(tidy_coefs, term %in% "FoodwebSimple:I(sc.sqrt.Pref^2)")
+#simple_quad_pref$term <- "I(sc.sqrt.Pref^2)"
 
@@
 
-tidy_simple_grads <- bind_rows(tidy_common_coefs, simple_quad_pref, simple_clutch) %>%
+tidy_simple_grads <- bind_rows(tidy_common_coefs, simple_clutch) %>% # simple_quad_pref, 
   mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
@@
 
-tidy_complex_grads <- bind_rows(tidy_common_coefs, complex_quad_pref, complex_clutch) %>%
+tidy_complex_grads <- bind_rows(tidy_common_coefs, complex_clutch) %>% # complex_quad_pref, 
     mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
@@
 selection_gradients$term_ord <- factor(selection_gradients$term, 
-                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                                   levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                                    labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
@@
 
-tidy_egg.larval_model_2 <- tidy(egg.larval_model_2, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebLarval:I(sc.log1p.Pref^2)")) 
+tidy_egg.larval_model_2 <- tidy(egg.larval_model_2, conf.int=T) %>% # boot_egg.larval_model_2
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"))#,
+                     #"FoodwebLarval:I(sc.sqrt.Pref^2)")) 
 ```
@@
 tidy_egg.larval_model_2$term_plot <- factor(tidy_egg.larval_model_2$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                             ordered = TRUE)
@@
  To put all of the coefficients on the same scale, we refit it as we did in the food-web treatment
-```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE}
+```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE, eval=FALSE}
 egg.larval_model_2_adj <- update(model_2_adj, data=egg.vs.larval_df)
@@
 
-```{r Bootstrap Egg vs. Larval Parasitoid adjusted Model 2, cache=TRUE, include=FALSE}
+```{r Bootstrap Egg vs. Larval Parasitoid adjusted Model 2, cache=TRUE, include=FALSE, eval=FALSE}
 
@@
 tidy_egg.larval_model_2_adj <- tidy(egg.larval_model_2_adj, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref")) 
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.sqrt.Pref^2)","FoodwebLarval:I(sc.sqrt.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) 
 ```
@@
 
-```{r Plot effect of Egg vs. Larval Parasitoid adjusted Model 2, echo=FALSE}
+```{r Plot effect of Egg vs. Larval Parasitoid adjusted Model 2, echo=FALSE, eval=FALSE}
 tidy_egg.larval_model_2_adj$term_plot <- factor(tidy_egg.larval_model_2_adj$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.log1p.Pref^2)","FoodwebLarval:I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.sqrt.Pref^2)","FoodwebLarval:I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                             ordered = TRUE)
@@
 
-tidy_egg.larval_model_4 <- tidy(boot_egg.larval_model_4, conf.int=T) 
+tidy_egg.larval_model_4 <- tidy(egg.larval_model_4, conf.int=T) # boot_egg.larval_model_4
 ```
@@
 tidy_egg.larval_model_4$term_ord <- factor(tidy_egg.larval_model_4$term, 
-                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.log1p.Pref"),
+                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.sqrt.Pref"),
                                 ordered = TRUE)
@@
 
-tidy_egg.larval_model_4_adj <- tidy(boot_egg.larval_model_4_adj, conf.int=T) 
+tidy_egg.larval_model_4_adj <- tidy(egg.larval_model_4_adj, conf.int=T) # boot_egg.larval_model_4_adj
 ```
@@
 tidy_egg.larval_model_4_adj$term_ord <- factor(tidy_egg.larval_model_4_adj$term, 
-                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","FoodwebEgg:sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.log1p.Pref"),
+                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","FoodwebEgg:sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.sqrt.Pref"),
                                 ordered = TRUE)
@@
 tidy_egg.larval_coefs <- bind_rows(
-  select(tidy_egg.larval_model_2_adj, term, estimate, conf.low, conf.high), 
-  select(tidy_egg.larval_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
+  select(tidy_egg.larval_model_2, term, estimate, conf.low, conf.high),  # estimate=statistic; tidy_egg.larval_model_2_adj no longer needed because no nonlinear difference on preference.
+  select(tidy_egg.larval_model_4_adj, term, estimate, conf.low, conf.high)) %>% # estimate=statistic
   filter(term != "(Intercept)", term != "FoodwebLarval") # remove main effects
@@
 tidy_egg.larval_common_coefs <- tidy_egg.larval_coefs %>%
-  filter(term!="FoodwebEgg:I(sc.log1p.Pref^2)", term!="FoodwebLarval:I(sc.log1p.Pref^2)",
+  filter(#term!="FoodwebEgg:I(sc.sqrt.Pref^2)", term!="FoodwebLarval:I(sc.sqrt.Pref^2)",
          term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")
@@
 # Tidy unique coefficients to each food-web
-egg_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebEgg:I(sc.log1p.Pref^2)")
-egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
-larval_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebLarval:I(sc.log1p.Pref^2)")
-larval_quad_pref$term <- "I(sc.log1p.Pref^2)"
+#egg_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebEgg:I(sc.sqrt.Pref^2)")
+#egg_quad_pref$term <- "I(sc.sqrt.Pref^2)"
+#larval_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebLarval:I(sc.sqrt.Pref^2)")
+#larval_quad_pref$term <- "I(sc.sqrt.Pref^2)"
 
@@
 
-tidy_egg_grads <- bind_rows(tidy_egg.larval_common_coefs, egg_quad_pref, egg_clutch) %>%
+tidy_egg_grads <- bind_rows(tidy_egg.larval_common_coefs, egg_clutch) %>% # egg_quad_pref, 
   mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
@@
 
-tidy_larval_grads <- bind_rows(tidy_egg.larval_common_coefs, larval_quad_pref, larval_clutch) %>%
+tidy_larval_grads <- bind_rows(tidy_egg.larval_common_coefs, larval_clutch) %>% # larval_quad_pref, 
     mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
@@
 egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
-                                   levels=c("sc.Diam","sc.log.Clutch","sc.log1p.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref"),
+                                   levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
                                    labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
@@
 biased.diam_model_4 <- update(model_4, data=biased_df)
-summary(biased.diam_model_4) # looks like the bias in our sc.Diam coefficient is 0.35
+summary(biased.diam_model_4) # looks like the bias in our sc.Diam coefficient is 0.34
 
@@
 # convert to selection gradient
-bias.adj_sc.Diam_complex <- bias.adj_complex_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_complex_mean_fitness * 1 # 0.11
-bias.adj_sc.Diam_simple <- bias.adj_simple_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_simple_mean_fitness * 1 # 0.07
+bias.adj_sc.Diam_complex <- bias.adj_complex_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_complex_mean_fitness * 1 # 0.16
+bias.adj_sc.Diam_simple <- bias.adj_simple_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_simple_mean_fitness * 1 # 0.18
 
@@
 
-female_pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, sc.log1p.Pref))
+female_pref <- lmer(sc.sqrt.Pref ~ Foodweb + (1|Genotype), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, sc.sqrt.Pref))
 summary(female_pref)
@@
 focus_gradients <- bind_rows(filter(bias.adj_selection_gradients, term_ord == "Diam" & adjusted == "Yes" | term_ord != "Diam"),
-                             filter(egg.larval_selection_gradients, `Food web` == "Larval" & term_ord %in% c("Clutch","Pref^2"))) %>%
+                             filter(egg.larval_selection_gradients, `Food web` == "Larval" & term_ord %in% c("Clutch"))) %>%   # ,"Pref^2"
   mutate(Type = ifelse(grepl("\\^2", .$term_ord)==TRUE, "Quadratic", ifelse(grepl(":", .$term_ord)==TRUE, "Correlational", "Directional")))
@@
   ylab("Selection Gradient") +
-  scale_fill_manual(values=cbPalette[c(6,4,5)]) +
-  scale_color_manual(values=cbPalette[c(6,4,5)]) +
+  scale_fill_manual(values=cbPalette[c(6,5)]) + # c(6,4,5) no longer effect on preference
+  scale_color_manual(values=cbPalette[c(6,5)]) + # c(6,4,5) no longer effect on preference
   facet_wrap(~Type_ord, ncol=2, scales="free_x") +
@@
 
-platy_Pref <- lmer(sc.log1p.Pref ~ Foodweb + (1|Genotype), platy_selection_df)
+platy_Pref <- lmer(sc.sqrt.Pref ~ Foodweb + (1|Genotype), platy_selection_df)
 
@@
 platy_Clutch_levene <- leveneTest(sc.log.Clutch ~ Foodweb, platy_selection_df)
-platy_Pref_levene <- leveneTest(sc.log1p.Pref ~ Foodweb, platy_selection_df)
+platy_Pref_levene <- leveneTest(sc.sqrt.Pref ~ Foodweb, platy_selection_df)
 ```
@@
 ```
+```{r}
+car::Anova(platy_Diam, test="F")
+car::Anova(platy_Clutch, test="F")
+car::Anova(platy_Pref, test="F")
+```
 
@@
 
-```{r Calculate Selection Differentials for Platygaster, cache=TRUE, include=FALSE}
+```{r Calculate Selection Differentials for Platygaster, cache=TRUE, include=FALSE, eval=FALSE}
 
@@
   group_by(Foodweb) %>%
-  summarise_at(c("sc.Diam","sc.log.Clutch","sc.log1p.Pref"), var) %>%
+  summarise_at(c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), var) %>%
   gather(key = Term, value = Variance, -Foodweb) %>%
@@
 
-```{r Table of Platygaster selection differentials, echo=FALSE}
+```{r Table of Platygaster selection differentials, echo=FALSE, eval=FALSE}
 platy_selection_differentials <- bind_rows(platy_linear_selection, platy_quadratic_selection)
@@
 newdata_Diam <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = 0))
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
 
@@
   logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
   newdata = newdata_Diam,
@@
 newdata_Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0))
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
 
@@
   logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
   newdata = newdata_Clutch,
@@
 newdata_Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
   logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
   newdata = newdata_Pref,
@@
 newdata_Clutch.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
   logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
   newdata = newdata_Clutch.Pref,
@@
 newdata_Diam.Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.log1p.Pref=0))
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
 
@@
   logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
   newdata = newdata_Diam.Clutch,
@@
 newdata_Diam.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.log1p.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
   logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.log1p.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.log1p.Pref^2)",
+  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
   newdata = newdata_Diam.Pref,
@@
           #mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.Clutch, -sc.log1p.Pref) %>%
+  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
   gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
@@
           #mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.Diam, -sc.log1p.Pref) %>%
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
   gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
@@
   select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.log1p.Pref, -Foodweb) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log1p.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
-  ggplot(., aes(x=sc.Diam, y=sc.log1p.Pref)) +
+  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
   geom_raster(aes(fill=average)) +
@@
 AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
-  ggplot(., aes(x=sc.log1p.Pref, y=sc.log.Clutch)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
   geom_raster(aes(fill=average)) +
@@
 P_matrix["Clutch","Clutch"] <- var(gall_selection.df$sc.log.Clutch)
-P_matrix["Pref","Pref"] <- var(gall_selection.df$sc.log1p.Pref)
+P_matrix["Pref","Pref"] <- var(gall_selection.df$sc.sqrt.Pref)
 
@@
 
-P_matrix["Diam","Pref"] <- with(gall_selection.df, cov(sc.Diam, sc.log1p.Pref))
+P_matrix["Diam","Pref"] <- with(gall_selection.df, cov(sc.Diam, sc.sqrt.Pref))
 P_matrix["Pref","Diam"] <- P_matrix["Diam","Pref"]
 
-P_matrix["Clutch","Pref"] <- with(gall_selection.df, cov(sc.log.Clutch, sc.log1p.Pref))
+P_matrix["Clutch","Pref"] <- with(gall_selection.df, cov(sc.log.Clutch, sc.sqrt.Pref))
 P_matrix["Pref","Clutch"] <- P_matrix["Clutch","Pref"]
@@
 densities <- gall_selection.df %>%
-  distinct(Foodweb, Genotype, Plant_Position, sc.log1p.Pref, Density_per_100_shoots)
+  distinct(Foodweb, Genotype, Plant_Position, sc.sqrt.Pref, Density_per_100_shoots)
 
@@
   filter(Foodweb=="Complex") %>%
-  ggplot(., aes(x=sc.log1p.Pref, y=ectos_sum/ptoids_sum)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=ectos_sum/ptoids_sum)) +
   geom_point(aes(size=ptoids_sum), shape=21) +
@@
   filter(Foodweb=="Complex") %>%
-  ggplot(., aes(x=sc.log1p.Pref, y=egg_parasitoid_sum/ptoids_sum)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=egg_parasitoid_sum/ptoids_sum)) +
   geom_point(aes(size=ptoids_sum), shape=21) +
@@
 left_join(densities, survival) %>%
-  ggplot(., aes(x=sc.log1p.Pref, y=gall_survival_sum/gall_survival_n, color=Foodweb)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=gall_survival_sum/gall_survival_n, color=Foodweb)) +
   geom_point(aes(size=gall_survival_n), shape=21) +
@@
 left_join(densities, survival) %>%
-  ggplot(., aes(x=sc.log1p.Pref, y=gall_survival_n, color=Foodweb)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=gall_survival_n, color=Foodweb)) +
   geom_point(aes(size=gall_survival_n), shape=21) +
@@
   filter(Foodweb=="Complex") %>%
-  ggplot(., aes(x=sc.log1p.Pref)) +
+  ggplot(., aes(x=sc.sqrt.Pref)) +
   #geom_point(aes(size=ptoids_sum), shape=21) +
@@
   filter(Foodweb=="Simple") %>%
-  ggplot(., aes(x=sc.log1p.Pref)) +
+  ggplot(., aes(x=sc.sqrt.Pref)) +
   #geom_point(aes(size=ptoids_sum), shape=21) +
@@
 # in the complex food web, there is a positive relationship between the number of gall samples and gall density (makes sense); there is the opposite pattern in the simple foodweb...
-density_n_lm <- lm(gall_survival_n ~ sc.log1p.Pref*Foodweb, left_join(densities, survival))
-visreg::visreg(density_n_lm, xvar="sc.log1p.Pref", by="Foodweb")
+density_n_lm <- lm(gall_survival_n ~ sc.sqrt.Pref*Foodweb, left_join(densities, survival))
+visreg::visreg(density_n_lm, xvar="sc.sqrt.Pref", by="Foodweb")
 summary(density_n_lm)
-wt_density_n_lm <- lm(gall_survival_n ~ sc.log1p.Pref*Foodweb, left_join(densities, survival), weights = gall_survival_n)
-visreg::visreg(wt_density_n_lm, xvar="sc.log1p.Pref", by="Foodweb")
+wt_density_n_lm <- lm(gall_survival_n ~ sc.sqrt.Pref*Foodweb, left_join(densities, survival), weights = gall_survival_n)
+visreg::visreg(wt_density_n_lm, xvar="sc.sqrt.Pref", by="Foodweb")
 summary(wt_density_n_lm)
@@
 # good thing is that I get the same qualitative answer with or without weighting
-test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(densities, survival), family="quasibinomial")
-visreg::visreg(test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(densities, survival), family="quasibinomial")
+visreg::visreg(test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
 summary(test_glm)
 
-wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(densities, survival), family="quasibinomial", weights = gall_survival_n)
-visreg::visreg(wt_test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(densities, survival), family="quasibinomial", weights = gall_survival_n)
+visreg::visreg(wt_test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
 summary(wt_test_glm)
@@
 egg.densities <- egg.vs.egg_df %>%
-  distinct(Foodweb, Plant_Position, sc.log1p.Pref)
+  distinct(Foodweb, Plant_Position, sc.sqrt.Pref)
 
@@
 
-egg.test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial")
-visreg::visreg(egg.test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+egg.test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial")
+visreg::visreg(egg.test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
 summary(egg.test_glm)
 
-egg.wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.log1p.Pref + I(sc.log1p.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial", weights = gall_survival_n)
-visreg::visreg(egg.wt_test_glm, xvar="sc.log1p.Pref", by="Foodweb", scale="response")
+egg.wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial", weights = gall_survival_n)
+visreg::visreg(egg.wt_test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
 summary(egg.wt_test_glm)
@@
 ggplot(densities, aes(x=Genotype, y=Density_per_100_shoots, fill=Foodweb)) + geom_boxplot()
-ggplot(densities, aes(x=Genotype, y=sc.log1p.Pref, fill=Foodweb)) + geom_boxplot()
+ggplot(densities, aes(x=Genotype, y=sc.sqrt.Pref, fill=Foodweb)) + geom_boxplot()
 
@@
 car::Anova(lmer(sqrt(Density_per_100_shoots) ~ Foodweb + (1|Genotype), filter(densities, Density_per_100_shoots>0)), test="F")
-summary(lm(sc.log1p.Pref ~ Foodweb, densities))
+summary(lm(sc.sqrt.Pref ~ Foodweb, densities))
 
@@
 ggplot(densities, aes(x=sqrt(Density_per_100_shoots), fill=Foodweb)) + geom_density(alpha=0.5)
-ggplot(densities, aes(x=sc.log1p.Pref, fill=Foodweb)) + geom_density(alpha=0.5)
+ggplot(densities, aes(x=sc.sqrt.Pref, fill=Foodweb)) + geom_density(alpha=0.5)
 
@@
   # filter terms that only matter for this analysis
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.log1p.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.log1p.Pref","sc.log.Clutch:sc.log1p.Pref",
-                     "FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)",
-                     "FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.log1p.Pref","FoodwebComplex:sc.log.Clutch:sc.log1p.Pref"))
+  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
+                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
+                     "FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)",
+                     "FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.sqrt.Pref","FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref"))
 ```
@@
 egg.egg_plot_model_1$term_plot <- factor(egg.egg_plot_model_1$term,
-                                levels=c("FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.log1p.Pref^2)","FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.log1p.Pref","FoodwebComplex:sc.log.Clutch:sc.log1p.Pref"),
+                                levels=c("FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.sqrt.Pref","FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref"),
                                 ordered=TRUE)
@@
 
-visreg::visreg(egg.egg_model_1, xvar="sc.log1p.Pref", by="Foodweb", scale = "response")
+visreg::visreg(egg.egg_model_1, xvar="sc.sqrt.Pref", by="Foodweb", scale = "response")
 ```
@@
 
-tidy_egg.egg_model_3 <- tidy(boot_egg.egg_model_3, conf.int=T) 
+tidy_egg.egg_model_3 <- tidy(egg.egg_model_3, conf.int=T) # boot_egg.egg_model_3
 ```
@@
 egg.egg_plot_model_3$term_plot <- factor(egg.egg_plot_model_3$term,
-                                levels=c("FoodwebComplex:sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebComplex:sc.log1p.Pref"),
+                                levels=c("FoodwebComplex:sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebComplex:sc.sqrt.Pref"),
                                 ordered=TRUE)
@@
   geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
+  geom_point(aes(y=estimate), shape=21, size=3, fill="grey") + # y=statistic
   coord_flip() +
@@
 tidy_egg.egg_model_4_adj$term_ord <- factor(tidy_egg.egg_model_4_adj$term, 
-                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.log1p.Pref"),
+                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
                                 ordered = TRUE)
@@
 tidy_egg.egg_common_coefs <- tidy_egg.egg_coefs %>%
-  filter(term!="FoodwebEgg:I(sc.log1p.Pref^2)", term!="Foodwebegg:I(sc.log1p.Pref^2)",
+  filter(term!="FoodwebEgg:I(sc.sqrt.Pref^2)", term!="Foodwebegg:I(sc.sqrt.Pref^2)",
          term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")
@@
 # Tidy unique coefficients to each food-web
-egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:I(sc.log1p.Pref^2)")
-egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
-egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:I(sc.log1p.Pref^2)")
-egg_quad_pref$term <- "I(sc.log1p.Pref^2)"
+egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:I(sc.sqrt.Pref^2)")
+egg_quad_pref$term <- "I(sc.sqrt.Pref^2)"
+egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:I(sc.sqrt.Pref^2)")
+egg_quad_pref$term <- "I(sc.sqrt.Pref^2)"
 

### 2018-10-29 analyses/reproduce_analyses.Rmd
incorporated new approach for calculating selection gradients.

@@
 
+## Get confidence intervals from bootstrapped samples
+conf.high <- function(x) quantile(x, probs = 0.975)
+conf.low <- function(x) quantile(x, probs = 0.025)
+
 ## Color palette
@@
 mvn_assumption$univariateNormality[1, ]
+```
+
+# Quantifying biased selection on chamber diameter
+
+We quantified biased selection on chamber diameter in the following way.
+First, we focus on multi-chambered galls where there is evidence of both survival and parasitism.
+The idea is that galls from the same clutch should be similar in size; therefore, any selection on diameter would be apparent.
+If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection differential to be the result of confounding factors.
+Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism.
+
+We calculated the bias in selection differential on chamber diameter by calculating the difference in mean chamber diameter before (i.e.
+all larva within the same gall) and after selection (only surviving larva).
+We then used a one-sample t-test to determine whether the selection differential was significantly different from zero.
+We conducted separate t-tests for each food-web treatment.
+
+We can then subtract this "biased selection differential" from the observed directional selection gradient on chamber diameter to adjust for the confounding effects of parasitism.
+
+We write the model in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larva survival.
+
+```{r Food-web model, cache=TRUE}
+foodweb_model <- glmer(
+  gall_survival ~ -1 + Foodweb + #sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    #I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
+    #sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df,
+  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+biased_foodweb_df <- gall_selection.df %>%
+  group_by(Foodweb, Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  ungroup()
+
+biased_foodweb_model <- glmer(gall_survival ~ -1 + Foodweb + Foodweb:sc.Diam + (1|Genotype/Plant_Position/Gall_Number),
+                              data = biased_foodweb_df,
+                              family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+```
+
+Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
+For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
+
+```{r Bootstrap food-web model, cache=TRUE, include=FALSE}
+boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Food-web alpha coefficients, include=FALSE}
+
+# Adjust coefficients with chamber diameter
+foodweb_adj_Diam <- as_tibble(boot_foodweb_model$t) %>%
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])#,
+         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_foodweb_model)["FoodwebComplex:I(sc.Diam^2)"],
+         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_foodweb_model)["FoodwebSimple:I(sc.Diam^2)"],
+         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
+         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
+         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
+         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+foodweb_alphas <- foodweb_adj_Diam %>%
+  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_foodweb_alphas <- foodweb_alphas %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
+                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+```
+
+```{r Plot food-web coefficients, echo=FALSE}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_foodweb_coefs <- c(min(filter(tidy_foodweb_alphas, type!="Diff")$conf.low), 
+                            max(filter(tidy_foodweb_alphas, type!="Diff")$conf.high))
+P_asterisk_foodweb_coefs <- 1.5
+P_size <- 8
+legend_foodweb_labels <- c("Complex","Simple")
+point.size <- 3
+
+# Plot mean fitness
+plot_foodweb_mean_fitness <- tidy_foodweb_alphas %>%
+  filter(type!="Diff", term=="(Intercept)") %>%
+  ggplot(., aes(x=type)) +
+  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
+  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Larva survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  xlab("Food web") +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)
+
+# Plot linear trait-fitness relationaships
+plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)
+
+# Plot quadratic trait-fitness relationships
+plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)
+
+# Plot correlational trait-fitness relationaships
+plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels)
+
+# Format plots for manuscript
+plot_foodweb_coefs <- plot_grid(
+  plot_foodweb_mean_fitness + theme(legend.position = "none"),
+  plot_foodweb_linear_coefs + theme(legend.position = "none"),
+  plot_foodweb_quadratic_coefs + theme(legend.position = "none"),
+  plot_foodweb_correlational_coefs + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "")
+
+figure_foodweb_coefs <- plot_foodweb_coefs 
+figure_foodweb_coefs
+```
+
+```{r Food-web selection gradients, include=FALSE}
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
+foodweb_complex_predict <- predict(foodweb_model, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
+foodweb_complex_mean_brackets <- mean(foodweb_complex_predict * (1 - foodweb_complex_predict))
+foodweb_complex_mean_fitness <- mean(foodweb_complex_predict)
+
+foodweb_simple_predict <- predict(foodweb_model, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
+foodweb_simple_mean_brackets <- mean(foodweb_simple_predict * (1 - foodweb_simple_predict))
+foodweb_simple_mean_fitness <- mean(foodweb_simple_predict)
+
+foodweb_complex_gradient <- function(x) foodweb_complex_mean_brackets * x / foodweb_complex_mean_fitness
+foodweb_simple_gradient <- function(x) foodweb_simple_mean_brackets * x / foodweb_simple_mean_fitness
+
+foodweb_complex_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebComplex:")) %>%
+  transmute_all(funs(foodweb_complex_gradient))
+
+foodweb_simple_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebSimple:")) %>%
+  transmute_all(funs(foodweb_simple_gradient))
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_foodweb_grads <- foodweb_grads %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+```{r Plot food-web gradients, echo=FALSE}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_foodweb_grads <- c(min(filter(tidy_foodweb_grads, type!="Diff")$conf.low), 
+                            max(filter(tidy_foodweb_grads, type!="Diff")$conf.high))
+P_asterisk_foodweb_grads <- 0.5
+P_size <- 8
+legend_foodweb_labels <- c("Complex","Simple")
+legend_foodweb_title <- "Food web"
+point.size <- 3
+
+# Plot directional selection gradients
+plot_foodweb_directional_grads <- tidy_foodweb_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels, name=legend_foodweb_title) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels, name=legend_foodweb_title)
+
+# Plot quadratic selection gradients
+plot_foodweb_quadratic_grads <- tidy_foodweb_grads %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels, name=legend_foodweb_title) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels, name=legend_foodweb_title)
+
+# Plot correlational selection gradients
+plot_foodweb_correlational_grads <- tidy_foodweb_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels, name=legend_foodweb_title) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_labels, name=legend_foodweb_title)
+
+# Get legend
+legend_foodweb_grads <- get_legend(plot_foodweb_directional_grads)
+
+# Format plots for manuscript
+plot_foodweb_grads <- plot_grid(
+  plot_foodweb_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_foodweb_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_foodweb_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+plot_legend_foodweb_grads <- ggdraw(plot_foodweb_grads) + draw_grob(legend_foodweb_grads, x = 0.7, y=-0.2)
+y_title_foodweb_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+figure_foodweb_grads <- plot_grid(y_title_foodweb_grads, plot_legend_foodweb_grads, ncol=2, rel_widths = c(0.05,1)) 
+figure_foodweb_grads
+```
+
+```{r Egg vs. larval ptoid model, cache=TRUE}
+# excludes cases of egg-parasitism from Complex food web
+egglarval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1)
+
+egglarval_model <- update(foodweb_model, data=egglarval_df)
+
+biased_egglarval_df <- egglarval_df %>%
+  group_by(Foodweb, Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  ungroup()
+
+biased_egglarval_model <- update(biased_foodweb_model, data=biased_egglarval_df)
+```
+
+Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
+For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
+
+```{r Bootstrap egg vs. larval ptoid model, cache=TRUE, include=FALSE}
+boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Egg vs. larval ptoid alpha coefficients, include=FALSE}
+
+# Adjust coefficients with chamber diameter
+egglarval_adj_Diam <- as_tibble(boot_egglarval_model$t) %>%
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])#,
+         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_egglarval_model)["FoodwebComplex:I(sc.Diam^2)"],
+         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_egglarval_model)["FoodwebSimple:I(sc.Diam^2)"],
+         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
+         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
+         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
+         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+egglarval_alphas <- egglarval_adj_Diam %>%
+  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_egglarval_alphas <- egglarval_alphas %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
+                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+```
+
+```{r Plot egglarval coefficients, echo=FALSE}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_egglarval_coefs <- c(min(filter(tidy_egglarval_alphas, type!="Diff")$conf.low), 
+                            max(filter(tidy_egglarval_alphas, type!="Diff")$conf.high))
+P_asterisk_egglarval_coefs <- 1.3
+P_size <- 8
+legend_egglarval_labels <- c("Larval","Egg")
+point.size <- 3
+
+# Plot mean fitness
+plot_egglarval_mean_fitness <- tidy_egglarval_alphas %>%
+  filter(type!="Diff", term=="(Intercept)") %>%
+  ggplot(., aes(x=type)) +
+  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
+  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Larva survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_x_discrete(name="Parasitoid", breaks=c("Complex","Simple"), labels=c("Larval","Egg")) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels)
+
+# Plot linear trait-fitness relationaships
+plot_egglarval_linear_coefs <- tidy_egglarval_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_egglarval_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels)
+
+# Plot quadratic trait-fitness relationships
+plot_egglarval_quadratic_coefs <- tidy_egglarval_alphas %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_egglarval_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels)
+
+# Plot correlational trait-fitness relationaships
+plot_egglarval_correlational_coefs <- tidy_egglarval_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_egglarval_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels)
+
+# Format plots for manuscript
+plot_egglarval_coefs <- plot_grid(
+  plot_egglarval_mean_fitness + theme(legend.position = "none"),
+  plot_egglarval_linear_coefs + theme(legend.position = "none"),
+  plot_egglarval_quadratic_coefs + theme(legend.position = "none"),
+  plot_egglarval_correlational_coefs + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "")
+
+figure_egglarval_coefs <- plot_egglarval_coefs 
+figure_egglarval_coefs
+```
+
+```{r Egg vs. larval ptoid selection gradients, include=FALSE}
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
+egglarval_complex_predict <- predict(egglarval_model, newdata=filter(egglarval_df, Foodweb=="Complex"), type="response")
+egglarval_complex_mean_brackets <- mean(egglarval_complex_predict * (1 - egglarval_complex_predict))
+egglarval_complex_mean_fitness <- mean(egglarval_complex_predict)
+
+egglarval_simple_predict <- predict(egglarval_model, newdata=filter(egglarval_df, Foodweb=="Simple"), type="response")
+egglarval_simple_mean_brackets <- mean(egglarval_simple_predict * (1 - egglarval_simple_predict))
+egglarval_simple_mean_fitness <- mean(egglarval_simple_predict)
+
+egglarval_complex_gradient <- function(x) egglarval_complex_mean_brackets * x / egglarval_complex_mean_fitness
+egglarval_simple_gradient <- function(x) egglarval_simple_mean_brackets * x / egglarval_simple_mean_fitness
+
+egglarval_complex_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebComplex:")) %>%
+  transmute_all(funs(egglarval_complex_gradient))
+
+egglarval_simple_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebSimple:")) %>%
+  transmute_all(funs(egglarval_simple_gradient))
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+egglarval_grads <- bind_cols(egglarval_complex_raw_gradients, egglarval_simple_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_egglarval_grads <- egglarval_grads %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+```{r Plot egg vs. larval ptoid gradients, echo=FALSE}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_egglarval_grads <- c(min(filter(tidy_egglarval_grads, type!="Diff")$conf.low), 
+                            max(filter(tidy_egglarval_grads, type!="Diff")$conf.high))
+P_asterisk_egglarval_grads <- 0.25
+P_size <- 8
+legend_egglarval_labels <- c("Larval","Egg")
+legend_egglarval_title <- "Parasitoid"
+point.size <- 3
+
+# Plot directional selection gradients
+plot_egglarval_directional_grads <- tidy_egglarval_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_egglarval_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels, name=legend_egglarval_title) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels, name=legend_egglarval_title)
+
+# Plot quadratic selection gradients
+plot_egglarval_quadratic_grads <- tidy_egglarval_grads %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_egglarval_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels, name=legend_egglarval_title) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels, name=legend_egglarval_title)
+
+# Plot correlational selection gradients
+plot_egglarval_correlational_grads <- tidy_egglarval_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_egglarval_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels, name=legend_egglarval_title) +
+  scale_color_manual(values=cbPalette[c(4,5)], labels=legend_egglarval_labels, name=legend_egglarval_title)
+
+# Get legend
+legend_egglarval_grads <- get_legend(plot_egglarval_directional_grads)
+
+# Format plots for manuscript
+plot_egglarval_grads <- plot_grid(
+  plot_egglarval_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_egglarval_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_egglarval_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+plot_legend_egglarval_grads <- ggdraw(plot_egglarval_grads) + draw_grob(legend_egglarval_grads, x = 0.7, y=-0.2)
+y_title_egglarval_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+figure_egglarval_grads <- plot_grid(y_title_egglarval_grads, plot_legend_egglarval_grads, ncol=2, rel_widths = c(0.05,1)) 
+figure_egglarval_grads
+```
+
+```{r Egg vs. egg ptoid model, cache=TRUE}
+# excludes cases of larval-parasitism from Complex food web
+#eggegg_df <- #filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & ectos < 1) %>%
+  #mutate(gall_survival = ifelse(gall_survival==1,0,1)) # attempt to look at survival of egg parasitoid
+
+# convert "gall_survival" to egg parasitoid survival. Note that both Iteomyia pupa and larva parasitoids result in 0.
+eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg_parasitoid==1,1,0))
+
+eggegg_model <- update(foodweb_model, data=eggegg_df)
+
+biased_eggegg_df <- eggegg_df %>%
+  group_by(Foodweb, Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  ungroup()
+
+biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
+```
+
+Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
+For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
+
+```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
+boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Egg vs. egg ptoid alpha coefficients, include=FALSE}
+
+# Adjust coefficients with chamber diameter
+eggegg_adj_Diam <- as_tibble(boot_eggegg_model$t) %>%
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])#,
+         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_eggegg_model)["FoodwebComplex:I(sc.Diam^2)"],
+         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_eggegg_model)["FoodwebSimple:I(sc.Diam^2)"],
+         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
+         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
+         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
+         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+eggegg_alphas <- eggegg_adj_Diam %>%
+  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_eggegg_alphas <- eggegg_alphas %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
+                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+```
+
+```{r Plot egg vs. egg ptoid coefficients, echo=FALSE}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_eggegg_coefs <- c(min(filter(tidy_eggegg_alphas, type!="Diff")$conf.low), 
+                            max(filter(tidy_eggegg_alphas, type!="Diff")$conf.high))
+P_asterisk_eggegg_coefs <- 1.7
+P_size <- 8
+legend_eggegg_labels <- c("Complex","Simple")
+point.size <- 3
+
+# Plot mean fitness
+plot_eggegg_mean_fitness <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term=="(Intercept)") %>%
+  ggplot(., aes(x=type)) +
+  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
+  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Probability of observing egg parasitoid", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_x_discrete(name="") +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Plot linear trait-fitness relationaships
+plot_eggegg_linear_coefs <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Plot quadratic trait-fitness relationships
+plot_eggegg_quadratic_coefs <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Plot correlational trait-fitness relationaships
+plot_eggegg_correlational_coefs <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Format plots for manuscript
+plot_eggegg_coefs <- plot_grid(
+  plot_eggegg_mean_fitness + theme(legend.position = "none"),
+  plot_eggegg_linear_coefs + theme(legend.position = "none"),
+  plot_eggegg_quadratic_coefs + theme(legend.position = "none"),
+  plot_eggegg_correlational_coefs + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "")
+
+figure_eggegg_coefs <- plot_eggegg_coefs 
+figure_eggegg_coefs
+```
+
+```{r Egg vs. egg ptoid selection gradients, include=FALSE}
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
+eggegg_complex_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Complex"), type="response")
+eggegg_complex_mean_brackets <- mean(eggegg_complex_predict * (1 - eggegg_complex_predict))
+eggegg_complex_mean_fitness <- mean(eggegg_complex_predict)
+
+eggegg_simple_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Simple"), type="response")
+eggegg_simple_mean_brackets <- mean(eggegg_simple_predict * (1 - eggegg_simple_predict))
+eggegg_simple_mean_fitness <- mean(eggegg_simple_predict)
+
+eggegg_complex_gradient <- function(x) eggegg_complex_mean_brackets * x / eggegg_complex_mean_fitness
+eggegg_simple_gradient <- function(x) eggegg_simple_mean_brackets * x / eggegg_simple_mean_fitness
+
+eggegg_complex_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebComplex:")) %>%
+  transmute_all(funs(eggegg_complex_gradient))
+
+eggegg_simple_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebSimple:")) %>%
+  transmute_all(funs(eggegg_simple_gradient))
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+eggegg_grads <- bind_cols(eggegg_complex_raw_gradients, eggegg_simple_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_eggegg_grads <- eggegg_grads %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+```{r Plot egg vs. egg ptoid gradients, echo=FALSE}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_eggegg_grads <- c(min(filter(tidy_eggegg_grads, type!="Diff")$conf.low), 
+                            max(filter(tidy_eggegg_grads, type!="Diff")$conf.high))
+P_asterisk_eggegg_grads <- 0.45
+P_size <- 8
+legend_eggegg_labels <- c("Complex","Simple")
+legend_eggegg_title <- "Food web"
+point.size <- 3
+
+# Plot directional selection gradients
+plot_eggegg_directional_grads <- tidy_eggegg_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
+
+# Plot quadratic selection gradients
+plot_eggegg_quadratic_grads <- tidy_eggegg_grads %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
+
+# Plot correlational selection gradients
+plot_eggegg_correlational_grads <- tidy_eggegg_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
+
+# Get legend
+legend_eggegg_grads <- get_legend(plot_eggegg_directional_grads)
+
+# Format plots for manuscript
+plot_eggegg_grads <- plot_grid(
+  plot_eggegg_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_eggegg_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_eggegg_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+plot_legend_eggegg_grads <- ggdraw(plot_eggegg_grads) + draw_grob(legend_eggegg_grads, x = 0.7, y=-0.2)
+y_title_eggegg_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+figure_eggegg_grads <- plot_grid(y_title_eggegg_grads, plot_legend_eggegg_grads, ncol=2, rel_widths = c(0.05,1)) 
+figure_eggegg_grads
+```
+
+To determine whether I should adjust any coefficients associated with chamber diameter, e.g.
+quadratic and correlation terms, I conducted a quick simulation.
+In the simulation, I assumed that if the larva survive, then the chamber diameter was the corrent one.
+However, if the larva did not survive, its size could be due to both its size and parasitism.
+I assumed a constant value of parasitism effect on gall size.
+```{r simulate bias in chamber diameter}
+n <- 10000
+diam <- rnorm(n, mean=0, sd=1) # simulate 1,000 chamber diameters from a normal distribution with mean=0 and sd=1
+pref <- rnorm(n, mean=0, sd=1)               # simulate 1,000 female preferences from a normal distribution with mean=0 and sd=1
+bias.adj <- 0.34                  # this value corresponds to actual estimates from my bias analyses.
+mean_survival <- 0.5              # approximate survival across food-web treatments
+logit_survival <- mean_survival + 1.5*diam + 0.1*diam*diam -0.2*pref + 0*pref*pref -0.2*diam*pref # using coefficients that closely match empirical estimates
+link_survival <- exp(logit_survival)/(1 + exp(logit_survival))
+survival <- (runif(n) < link_survival)
+
+sim_df <- data.frame(survival=survival, diam=diam, pref=pref) %>%
+  mutate(diam_adj = ifelse(survival==FALSE, diam + bias.adj, diam)) # adjust bias only if larva did not survive
+
+## Fit non-adjusted model
+nonadj_model <- glm(survival ~ diam + I(diam^2) + pref + I(pref^2) + diam*pref, data=sim_df, family=binomial) 
+summary(nonadj_model)
+
+adj_model <- glm(survival ~ diam_adj  + I(diam_adj^2) + pref + I(pref^2) + diam_adj*pref, data=sim_df, family=binomial) 
+summary(adj_model)
+
+## Interesting, it seems that my simulation design affects the intercept term; however, its clear that my biological hypothesis for how chamber diameter is influenced by parasitism (simply decreasing size of non-surviving larva), would not affect the quadratic or nonlinear terms.
+data.frame(terms = names(coef(nonadj_model)), nonadj_coefs = coef(nonadj_model), adj_coefs = coef(adj_model)) %>%
+  mutate(diff_coefs = nonadj_coefs - adj_coefs)
 ```

### 2018-11-13 analyses/ECD_Supp_Mat.Rmd
commit updated changes to analyses that calculate bootstrapped differences from zero and between treatments

---
title: "Predicting the effects of character displacement on food-web dynamics"
author: "Matt Barbour"
output:
  pdf_document:
    df_print: paged
    fig_caption: true
    citation_package: natbib
    includes:  
      in_header: preamble-latex.tex
bibliography: references_ECD_supp_mat.bib
fontsize: 12pt
---

Keywords: competition; eco-evolutionary dynamics; ecological speciation; three-spine stickleback; zooplankton

## Abstract

<!-- Ecological character displacement is a key driver of diversification and adaptive radiation; however, there has been little work examining the consequences of character displacement on the dynamics of ecological communities. Given the growing recognition for the role of evolution in structuring ecological communities, understanding how major evolutionary processes impact ecological dynamics is increasingly important. Here, we build a mathematical model to predict how exploitative competition between two consumers for two resources affects the evolution of consumer attack rates, and, in turn, consumer-resource population dynamics. Our model suggested that increasing ecological character displacement decreases the equilibrium density of resources, and with sufficient divergence, results in more oscillatory (destabilizing) consumer-resource dynamics. These results suggest that ecological character displacement can eventually have a negative feedback on food-web persistence in the absence of other processes. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE)

## Load required libraries
library(deSolve) # numerical integration library
library(rootSolve) # for runsteady integration function
library(pse) # for latin hypercube
library(plyr) # for ldply
library(dplyr) # for manipulating data
library(tidyr) # for tidying data
library(cowplot) # for better base, ggplot graphics

## color palette
cbPalette <- c("#D55E00", "#0072B2", "#009E73")
```

```{r Simulations, include=FALSE, messages=TRUE, cache=TRUE}

#### GET REQUIRED FUNCTIONS ####

source('identify_steady_state.R')
source('eco_evo_sim_function.R')
source('Consumer_Resource_Functions.R')
source('CR_dynamics.R')

#### GENERAL PARAMETERS AND STATE VARIABLES ####

## Intrinsic growth rates
r <- 1
r1 <- r 
r2 <- r

## Carrying capacity
K <- 4
K1 <- K
K2 <- K

## Conversion efficiency
e <- 0.8
e11 <- e 
e12 <- e 
e21 <- e 
e22 <- e

## Mortality rate
m <- 1
m1 <- m
m2 <- m

## General, non-evolving parameter set for 2C,2R model
general_parameters <- data.frame(r1 = r1, r2 = r2, K1 = K1, K2 = K2, e11 = e11, e12 = e12, e21 = e21, e22 = e22, m1 = m1, m2 = m2)

## Attack rate
A <- 2
aii <- A*0.6

## Habitat preference (for LawlorSmith and McCann models)
w <- 0.6
wii <- w
wij <- (1 - w)

## Handling time (only for McCann model)
h <- 0.4
h11 <- h
h12 <- h
h21 <- h
h22 <- h

## State variables
R <- 2
R1 <- R
R2 <- R
C <- 1
C1 <- C
C2 <- C

states_2C_2R <- data.frame(R1 = R1, R2 = R2, C1 = C1, C2 = C2)
states_1C_2R <- data.frame(R1 = R1, R2 = R2, C1 = C1)

## Trade-offs. Borrowed from Sargent and Otto, 2006 Am Nat
a12_tradeoff <- expression(A*(1-(a11m/A)^n)^(1/n)) 
a21_tradeoff <- expression(A*(1-(a22m/A)^n)^(1/n))

n_concaveDN <- 1.15
n_linear <- 1
n_concaveUP <- 0.85

concaveDN_df <- data.frame(n = n_concaveDN, aii = seq(0,A,0.01)) %>% mutate(aij = A*(1-(aii/A)^n_concaveDN)^(1/n_concaveDN))
linear_df <- data.frame(n = n_linear, aii = seq(0,A,0.01)) %>% mutate(aij = A*(1-(aii/A)^n_linear)^(1/n_linear))
concaveUP_df <- data.frame(n = n_concaveUP, aii = seq(0,A,0.01)) %>% mutate(aij = A*(1-(aii/A)^n_concaveUP)^(1/n_concaveUP))

bind_rows(concaveDN_df, linear_df, concaveUP_df) %>%
  ggplot(., aes(x=aii, y=aij, color = factor(n))) + geom_line() + ggtitle("Attack rate trade-offs")

bind_rows(concaveDN_df, linear_df, concaveUP_df) %>%
  ggplot(., aes(x=aii/(aii+aij), y=aii+aij, color = factor(n))) + geom_line() + ggtitle("Relationship between specialization and total attack rate")

######################################### MACARTHUR MODEL #######################################################

## Mutant growth rates
mC1_MacArthur <- expression(e11*a11m*R1 + e12*a12m*R2 - m1)
mC2_MacArthur <- expression(e21*a21m*R1 + e22*a22m*R2 - m2)

#### PARAMETERS ####

## Linear
params_2C_2R_MacArthur_linear <- data.frame(general_parameters,
                                            a11 = aii, 
                                            a12 = eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_linear)),                     
                                            a21 = eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_linear)), 
                                            a22 = aii)                      
params_1C_2R_MacArthur_linear <- params_2C_2R_MacArthur_linear[c("r1","r2","K1","K2","e11","e12","a11","a12","m1")]

## concaveDN
params_2C_2R_MacArthur_concaveDN <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_concaveDN["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveDN))
params_2C_2R_MacArthur_concaveDN["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveDN))
params_1C_2R_MacArthur_concaveDN <- params_2C_2R_MacArthur_concaveDN[c("r1","r2","K1","K2","e11","e12","a11","a12","m1")]

## concaveUP
params_2C_2R_MacArthur_concaveUP <- params_2C_2R_MacArthur_linear
params_2C_2R_MacArthur_concaveUP["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveUP))
params_2C_2R_MacArthur_concaveUP["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveUP))
params_1C_2R_MacArthur_concaveUP <- params_2C_2R_MacArthur_concaveUP[c("r1","r2","K1","K2","e11","e12","a11","a12","m1")]

#### SIMULATIONS ####

## Linear
sim_2C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_linear, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_MacArthur_linear <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_linear, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
sim_2C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveDN, 
                                init_states = states_2C_2R, 
                                eco_CR_model = MacArthur_2C_2R, 
                                AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                species_traits = c(1,2), 
                                eco_param_names = c("a11","a22"), 
                                eco_tradeoff_names = c("a12","a21"),  
                                evo_param_names = c("a11m","a22m"),  
                                evo_tradeoff_names = c("a12m","a21m"), 
                                tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
sim_1C_2R_MacArthur_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveDN, 
                                init_states = states_1C_2R, 
                                eco_CR_model = MacArthur_1C_2R, 
                                AD_CR_models = c(mC1_MacArthur),
                                species_traits = c(1), 
                                eco_param_names = c("a11"), 
                                eco_tradeoff_names = c("a12"),  
                                evo_param_names = c("a11m"),  
                                evo_tradeoff_names = c("a12m"), 
                                tradeoff_functions = c(a12_tradeoff),
                                extra_tradeoff_params = c(A=A, n=n_concaveDN))
## concaveUP
sim_2C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_MacArthur_concaveUP, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = MacArthur_2C_2R, 
                                       AD_CR_models = c(mC1_MacArthur, mC2_MacArthur),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_MacArthur_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_MacArthur_concaveUP, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = MacArthur_1C_2R, 
                                       AD_CR_models = c(mC1_MacArthur),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveUP))

######################################### LAWLOR SMITH COARSE-GRAIN MODEL #######################################################

## Mutant growth rates
mC1_LawlorSmith <- expression(e11*w11*a11m*R1 + e12*w12*a12m*R2 - m1)
mC2_LawlorSmith <- expression(e21*w21*a21m*R1 + e22*w22*a22m*R2 - m2)

#### PARAMETERS ####

## Linear
params_2C_2R_LawlorSmith_linear <- data.frame(general_parameters,
                                              a11 = aii,
                                              a12 = eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_linear)), 
                                              a21 = eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_linear)), 
                                              a22 = aii,
                                              w11 = wii, 
                                              w12 = wij, 
                                              w21 = wij,
                                              w22 = wii)
params_1C_2R_LawlorSmith_linear <- params_2C_2R_LawlorSmith_linear[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22")]

## concaveDN
params_2C_2R_LawlorSmith_concaveDN <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_concaveDN["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveDN))
params_2C_2R_LawlorSmith_concaveDN["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveDN))
params_1C_2R_LawlorSmith_concaveDN <- params_2C_2R_LawlorSmith_concaveDN[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22")]

## concaveUP
params_2C_2R_LawlorSmith_concaveUP <- params_2C_2R_LawlorSmith_linear
params_2C_2R_LawlorSmith_concaveUP["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveUP))
params_2C_2R_LawlorSmith_concaveUP["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveUP))
params_1C_2R_LawlorSmith_concaveUP <- params_2C_2R_LawlorSmith_concaveUP[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22")]

#### SIMULATIONS ####

## Linear
sim_2C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_linear, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_LawlorSmith_linear <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_linear, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
# max mut iter reach!
sim_2C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_2C_2R, 
                                       eco_CR_model = LawlorSmith_2C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                       species_traits = c(1,2), 
                                       eco_param_names = c("a11","a22"), 
                                       eco_tradeoff_names = c("a12","a21"),  
                                       evo_param_names = c("a11m","a22m"),  
                                       evo_tradeoff_names = c("a12m","a21m"), 
                                       tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
# note that although the max mutation iterations are reached, the evolving parameters appear to oscillate near high values, i.e. they are effectively at an ESS
plot(sim_2C_2R_LawlorSmith_concaveDN[,c("a11","a22")]) 
plot(sim_2C_2R_LawlorSmith_concaveDN[,c("a11","a22")], xlim=c(1.85,1.95))

sim_1C_2R_LawlorSmith_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveDN, 
                                       init_states = states_1C_2R, 
                                       eco_CR_model = LawlorSmith_1C_2R, 
                                       AD_CR_models = c(mC1_LawlorSmith),
                                       species_traits = c(1), 
                                       eco_param_names = c("a11"), 
                                       eco_tradeoff_names = c("a12"),  
                                       evo_param_names = c("a11m"),  
                                       evo_tradeoff_names = c("a12m"), 
                                       tradeoff_functions = c(a12_tradeoff),
                                       extra_tradeoff_params = c(A=A, n=n_concaveDN))
## concaveUP
sim_2C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_2C_2R, 
                                        eco_CR_model = LawlorSmith_2C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith, mC2_LawlorSmith),
                                        species_traits = c(1,2), 
                                        eco_param_names = c("a11","a22"), 
                                        eco_tradeoff_names = c("a12","a21"),  
                                        evo_param_names = c("a11m","a22m"),  
                                        evo_tradeoff_names = c("a12m","a21m"), 
                                        tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_LawlorSmith_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_LawlorSmith_concaveUP, 
                                        init_states = states_1C_2R, 
                                        eco_CR_model = LawlorSmith_1C_2R, 
                                        AD_CR_models = c(mC1_LawlorSmith),
                                        species_traits = c(1), 
                                        eco_param_names = c("a11"), 
                                        eco_tradeoff_names = c("a12"),  
                                        evo_param_names = c("a11m"),  
                                        evo_tradeoff_names = c("a12m"), 
                                        tradeoff_functions = c(a12_tradeoff),
                                        extra_tradeoff_params = c(A=A, n=n_concaveUP))

######################################### MCCANN MODEL #######################################################

## Mutant growth rates
mC1_McCann <- expression(e11*(((w11 * R1)/(w11 * R1 + w12 * R2)) * a11m * R1)/(1 + ((w11 * R1)/(w11 * R1 + w12 * R2)) * a11m * h11 * R1 + ((w12 * R2)/(w11 * R1 + w12 * R2)) * a12m * h12 * R2) + e12*(((w12 * R2)/(w11 * R1 + w12 * R2)) * a12m * R2)/(1 + ((w11 * R1)/(w11 * R1 + w12 * R2)) * a11m * h11 * R1 + ((w12 * R2)/(w11 * R1 + w12 * R2)) * a12m * h12 * R2) - m1)
mC2_McCann <- expression(e21*(((w21 * R1)/(w21 * R1 + w22 * R2)) * a21m * R1)/(1 + ((w21 * R1)/(w21 * R1 + w22 * R2)) * a21m * h21 * R1 + ((w22 * R2)/(w21 * R1 + w22 * R2)) * a22m * h22 * R2) + e22*(((w22 * R2)/(w21 * R1 + w22 * R2)) * a22m * R2)/(1 + ((w21 * R1)/(w21 * R1 + w22 * R2)) * a21m * h21 * R1 + ((w22 * R2)/(w21 * R1 + w22 * R2)) * a22m * h22 * R2) - m2)

#### PARAMETERS ####

## Linear
params_2C_2R_McCann_linear <- data.frame(general_parameters,
                                         a11 = aii,
                                         a12 = eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_linear)), 
                                         a21 = eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_linear)), 
                                         a22 = aii,
                                         w11 = wii, 
                                         w12 = wij, 
                                         w21 = wij,
                                         w22 = wii,
                                         h11 = h11,
                                         h12 = h12,
                                         h21 = h21,
                                         h22 = h22)

params_1C_2R_McCann_linear <- params_2C_2R_McCann_linear[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22","h11","h12","h21","h22")]

## concaveDN
params_2C_2R_McCann_concaveDN <- params_2C_2R_McCann_linear
params_2C_2R_McCann_concaveDN["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveDN))
params_2C_2R_McCann_concaveDN["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveDN))
params_1C_2R_McCann_concaveDN <- params_2C_2R_McCann_concaveDN[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22","h11","h12","h21","h22")]

## concaveUP
params_2C_2R_McCann_concaveUP <- params_2C_2R_McCann_linear
params_2C_2R_McCann_concaveUP["a12"] <- eval(a12_tradeoff, data.frame(A=A, a11m=aii, n=n_concaveUP))
params_2C_2R_McCann_concaveUP["a21"] <- eval(a21_tradeoff, data.frame(A=A, a22m=aii, n=n_concaveUP))
params_1C_2R_McCann_concaveUP <- params_2C_2R_McCann_concaveUP[c("r1","r2","K1","K2","e11","e12","a11","a12","m1","w11","w12","w21","w22","h11","h12","h21","h22")]

#### SIMULATIONS ####

## Linear
sim_2C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_2C_2R_McCann_linear, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))
sim_1C_2R_McCann_linear <- eco_evo_CR(init_parameters = params_1C_2R_McCann_linear, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_linear))

## concaveDN
# max mut iter
sim_2C_2R_McCann_concaveDN <- eco_evo_CR(init_parameters = params_2C_2R_McCann_concaveDN, 
                                         init_states = states_2C_2R, 
                                         eco_CR_model = McCann_2C_2R, 
                                         AD_CR_models = c(mC1_McCann, mC2_McCann),
                                         species_traits = c(1,2), 
                                         eco_param_names = c("a11","a22"), 
                                         eco_tradeoff_names = c("a12","a21"),  
                                         evo_param_names = c("a11m","a22m"),  
                                         evo_tradeoff_names = c("a12m","a21m"), 
                                         tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_concaveDN))
# note that although the max mutation iterations are reached, the evolving parameters appear to oscillate near high values. i.e. they are effectively at an ESS
plot(sim_2C_2R_McCann_concaveDN[,c("a11","a22")]) 
plot(sim_2C_2R_McCann_concaveDN[,c("a11","a22")], xlim=c(1.85,1.95))

sim_1C_2R_McCann_concaveDN <- eco_evo_CR(init_parameters = params_1C_2R_McCann_concaveDN, 
                                         init_states = states_1C_2R, 
                                         eco_CR_model = McCann_1C_2R, 
                                         AD_CR_models = c(mC1_McCann),
                                         species_traits = c(1), 
                                         eco_param_names = c("a11"), 
                                         eco_tradeoff_names = c("a12"),  
                                         evo_param_names = c("a11m"),  
                                         evo_tradeoff_names = c("a12m"), 
                                         tradeoff_functions = c(a12_tradeoff),
                                         extra_tradeoff_params = c(A=A, n=n_concaveDN))
## concaveUP
sim_2C_2R_McCann_concaveUP <- eco_evo_CR(init_parameters = params_2C_2R_McCann_concaveUP, 
                                          init_states = states_2C_2R, 
                                          eco_CR_model = McCann_2C_2R, 
                                          AD_CR_models = c(mC1_McCann, mC2_McCann),
                                          species_traits = c(1,2), 
                                          eco_param_names = c("a11","a22"), 
                                          eco_tradeoff_names = c("a12","a21"),  
                                          evo_param_names = c("a11m","a22m"),  
                                          evo_tradeoff_names = c("a12m","a21m"), 
                                          tradeoff_functions = c(a12_tradeoff, a21_tradeoff),
                                          extra_tradeoff_params = c(A=A, n=n_concaveUP))
sim_1C_2R_McCann_concaveUP <- eco_evo_CR(init_parameters = params_1C_2R_McCann_concaveUP, 
                                          init_states = states_1C_2R, 
                                          eco_CR_model = McCann_1C_2R, 
                                          AD_CR_models = c(mC1_McCann),
                                          species_traits = c(1), 
                                          eco_param_names = c("a11"), 
                                          eco_tradeoff_names = c("a12"),  
                                          evo_param_names = c("a11m"),  
                                          evo_tradeoff_names = c("a12m"), 
                                          tradeoff_functions = c(a12_tradeoff),
                                          extra_tradeoff_params = c(A=A, n=n_concaveUP))
```

```{r Organize_Simulation_Data, include=FALSE, cache=TRUE}

## Gather data. Note different formula for effective attack rate of consumer 1 "a_eff_C1". This accounts for the differences between fine- and coarse-grained environments
sim_data <- bind_rows(
  mutate(sim_2C_2R_MacArthur_linear, Model = "MacArthur", n = n_linear, Competitor = "Yes", a_eff_C1 = a11+a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_MacArthur_linear, Model = "MacArthur", n = n_linear, Competitor = "No", a_eff_C1 = a11+a12, Ctot = C1),
  mutate(sim_2C_2R_MacArthur_concaveDN, Model = "MacArthur", n = n_concaveDN, Competitor = "Yes", a_eff_C1 = a11+a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_MacArthur_concaveDN, Model = "MacArthur", n = n_concaveDN, Competitor = "No", a_eff_C1 = a11+a12, Ctot = C1),
  mutate(sim_2C_2R_MacArthur_concaveUP, Model = "MacArthur", n = n_concaveUP, Competitor = "Yes", a_eff_C1 = a11+a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_MacArthur_concaveUP, Model = "MacArthur", n = n_concaveUP, Competitor = "No", a_eff_C1 = a11+a12, Ctot = C1),
  mutate(sim_2C_2R_LawlorSmith_linear, Model = "LawlorSmith", n = n_linear, Competitor = "Yes", a_eff_C1 = w11*a11+w12*a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_LawlorSmith_linear, Model = "LawlorSmith", n = n_linear, Competitor = "No", a_eff_C1 = w11*a11+w12*a12, Ctot = C1),
  mutate(sim_2C_2R_LawlorSmith_concaveDN, Model = "LawlorSmith", n = n_concaveDN, Competitor = "Yes", a_eff_C1 = w11*a11+w12*a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_LawlorSmith_concaveDN, Model = "LawlorSmith", n = n_concaveDN, Competitor = "No", a_eff_C1 = w11*a11+w12*a12, Ctot = C1),
  mutate(sim_2C_2R_LawlorSmith_concaveUP, Model = "LawlorSmith", n = n_concaveUP, Competitor = "Yes", a_eff_C1 = w11*a11+w12*a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_LawlorSmith_concaveUP, Model = "LawlorSmith", n = n_concaveUP, Competitor = "No", a_eff_C1 = w11*a11+w12*a12, Ctot = C1),
  mutate(sim_2C_2R_McCann_linear, Model = "McCann", n = n_linear, Competitor = "Yes", a_eff_C1 = w11*a11+w12*a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_McCann_linear, Model = "McCann", n = n_linear, Competitor = "No", a_eff_C1 = w11*a11+w12*a12, Ctot = C1),
  mutate(sim_2C_2R_McCann_concaveDN, Model = "McCann", n = n_concaveDN, Competitor = "Yes", a_eff_C1 = w11*a11+w12*a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_McCann_concaveDN, Model = "McCann", n = n_concaveDN, Competitor = "No", a_eff_C1 = w11*a11+w12*a12, Ctot = C1),
  mutate(sim_2C_2R_McCann_concaveUP, Model = "McCann", n = n_concaveUP, Competitor = "Yes", a_eff_C1 = w11*a11+w12*a12, Ctot = C1+C2), 
  mutate(sim_1C_2R_McCann_concaveUP, Model = "McCann", n = n_concaveUP, Competitor = "No", a_eff_C1 = w11*a11+w12*a12, Ctot = C1))

#### PREDICTING EFFECTS OF CHARACTER DISPLACEMENT ON C-R DYNAMICS ####

tradeoff_df <- bind_rows(mutate(concaveDN_df, n = n_concaveDN), 
                         mutate(linear_df, n = n_linear), 
                         mutate(concaveUP_df, n = n_concaveUP)) %>%
  data.frame(., general_parameters) %>%
  mutate(a11 = aii, a12 = aij, a21 = aij, a22 = aii,
         w11 = wii, w12 = wij, w21 = wij, w22 = wii)

## MacArthur
MacArthur_displacements <- bind_rows(
  mutate(sim_2C_2R_MacArthur_linear, Model = "MacArthur", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_linear)), ], 
  mutate(sim_1C_2R_MacArthur_linear, Model = "MacArthur", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_linear)), ],
  mutate(sim_2C_2R_MacArthur_concaveDN, Model = "MacArthur", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_concaveDN)), ], 
  mutate(sim_1C_2R_MacArthur_concaveDN, Model = "MacArthur", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_concaveDN)), ],
  mutate(sim_2C_2R_MacArthur_concaveUP, Model = "MacArthur", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_MacArthur_concaveUP)), ], 
  mutate(sim_1C_2R_MacArthur_concaveUP, Model = "MacArthur", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_MacArthur_concaveUP)), ]) 
MacArthur_displacements$Time <- rep(c("Begin","End"),6)

MacArthur_2C_2R_tradeoff_dynamics <- CR_dynamics(init_parameters = select(tradeoff_df, r1:a22), init_states = states_2C_2R, eco_CR_model = MacArthur_2C_2R)
MacArthur_1C_2R_tradeoff_dynamics <- CR_dynamics(init_parameters = select(tradeoff_df, r1:a12), init_states = states_1C_2R, eco_CR_model = MacArthur_1C_2R)

## Lawlor Smith
LawlorSmith_displacements <- bind_rows(
  mutate(sim_2C_2R_LawlorSmith_linear, Model = "LawlorSmith", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_LawlorSmith_linear)), ], 
  mutate(sim_1C_2R_LawlorSmith_linear, Model = "LawlorSmith", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_LawlorSmith_linear)), ],
  mutate(sim_2C_2R_LawlorSmith_concaveDN, Model = "LawlorSmith", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_LawlorSmith_concaveDN)), ], 
  mutate(sim_1C_2R_LawlorSmith_concaveDN, Model = "LawlorSmith", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_LawlorSmith_concaveDN)), ],
  mutate(sim_2C_2R_LawlorSmith_concaveUP, Model = "LawlorSmith", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_LawlorSmith_concaveUP)), ], 
  mutate(sim_1C_2R_LawlorSmith_concaveUP, Model = "LawlorSmith", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_LawlorSmith_concaveUP)), ]) 
LawlorSmith_displacements$Time <- rep(c("Begin","End"),6)

LawlorSmith_2C_2R_tradeoff_dynamics <- CR_dynamics(init_parameters = select(tradeoff_df, r1:w22), init_states = states_2C_2R, eco_CR_model = LawlorSmith_2C_2R)
LawlorSmith_1C_2R_tradeoff_dynamics <- CR_dynamics(init_parameters = select(tradeoff_df, r1:a12, w11, w12), init_states = states_1C_2R, eco_CR_model = LawlorSmith_1C_2R)

## McCann
McCann_displacements <- bind_rows(
  mutate(sim_2C_2R_McCann_linear, Model = "McCann", n = n_linear, Competitor = "Yes")[c(1,nrow(sim_2C_2R_McCann_linear)), ], 
  mutate(sim_1C_2R_McCann_linear, Model = "McCann", n = n_linear, Competitor = "No")[c(1,nrow(sim_1C_2R_McCann_linear)), ],
  mutate(sim_2C_2R_McCann_concaveDN, Model = "McCann", n = n_concaveDN, Competitor = "Yes")[c(1,nrow(sim_2C_2R_McCann_concaveDN)), ], 
  mutate(sim_1C_2R_McCann_concaveDN, Model = "McCann", n = n_concaveDN, Competitor = "No")[c(1,nrow(sim_1C_2R_McCann_concaveDN)), ],
  mutate(sim_2C_2R_McCann_concaveUP, Model = "McCann", n = n_concaveUP, Competitor = "Yes")[c(1,nrow(sim_2C_2R_McCann_concaveUP)), ], 
  mutate(sim_1C_2R_McCann_concaveUP, Model = "McCann", n = n_concaveUP, Competitor = "No")[c(1,nrow(sim_1C_2R_McCann_concaveUP)), ]) 
McCann_displacements$Time <- rep(c("Begin","End"),6)

McCann_2C_2R_tradeoff_dynamics <- CR_dynamics(init_parameters = select(tradeoff_df, r1:w22), init_states = states_2C_2R, eco_CR_model = McCann_2C_2R)
McCann_1C_2R_tradeoff_dynamics <- CR_dynamics(init_parameters = select(tradeoff_df, r1:a12, w11, w12), init_states = states_1C_2R, eco_CR_model = McCann_1C_2R)

```

## Motivation

<!-- ECD as an important eco-evolutionary feedback -->

Ecological character displacement is thought to be a key evolutionary process in the diversification of species and consequently the generation of biodiversity (Schluter 2000; Pfennig and Pfennig 2010; Stuart and Losos 2013). Ecological character displacement describes the “process of phenotypic evolution in a species generated or maintained by [exploitative] resource competition with one or more coexisting species” (Schluter 2000). Over the past 40 years, a large body of theoretical (e.g. Lawlor and Smith 1976; Abrams 1986; Doebeli 1996; Taper and Case 1985) and empirical (reviewed in: Schluter 2000; Dayan and Simberloff 2005; Stuart and Losos 2013) work has been generated to understand the scenarios under which exploitative competition for resources leads to the divergence of consumer foraging traits. The general result emerging from these studies is that, if resources are nutritionally substitutable and there is no other strong source of density dependence acting on consumers (Abrams 1986; OTHER ABRAMS PAPER), then resource competition drives the divergence of consumer foraging traits (Lawlor and Smith 1976; Taper and Case 1985).

Another key insight emerging from past work is that character displacement is not simply driven by ecological differences, but also drives further ecological differentiation (cite?). This insight emerged from theoretical work that explicitly accounted for resource dynamics when modeling character displacement. If, for example, resources are treated as constants, the optimal strategy for each consumer species is unaffected by the presence or absence of a competitor.

This is because character divergence reduces interspecific competition relative to intraspecific competition, facilitating consumer coexistence.

In other words, ecological character displacement is the result of an eco-evolutionary feedback between consumers.

<!-- ECD on consumer coexistence -->

The consequence of this eco-evolutionary feedback for consumers has been well characterized

<!-- ECD effect on consumer-resource interactions -->

Yet, although resources mediate this eco-evolutionary feedback between consumers, the consequences of character displacement on consumer-resource interactions and food-web dynamics has received, surprisingly, little attention.

<!-- Ecological character displacement is not simply driven by ecological differences but also drives further ecological differentiation. In other words, ecological character displacement embodies an eco-evolutionary feedback between consumers. Character divergence in foraging traits also has ecological consequences, in that it promotes stable coexistence between competing consumers.

Yet, although the process of ecological character displacement is driven by consumers competing for shared resources (i.e. exploitative competition), the consequences of character displacement on consumer-resource interactions and food-web dynamics has received, suprisingly, little attention. -->

<!-- the interplay between competition and trait change, and hence is strongly dependent on resource availability, little of the work to date has explicitly considered how character displacement impacts other species within the community. Similarly, research on food-web dynamics has largely ignored the potential role of evolution in altering interactions and stability (Fussmann et al. 2007). Given the emerging evidence that evolutionary processes can drive ecological dynamics (Hairston et al. 2005, Post et al. 2008, Harmon et al. 2009, Schoener 2011, Rudman et al. 2015), understanding the ecological consequences of character displacement is an important step in investigating how evolutionary processes affect food-web dynamics. -->

<!-- Ecological character displacement has typically been considered to be a stabilizing factor in communities (Lawlor and Smith 1976). This is because divergence in foraging traits is thought to reduce the strength of interspecific competition between consumers. Reducing the strength of interspecific competition relative to intraspecific competition is a stabilizing force in consumer-resource systems. Consumer specialization on distinct resources suggests that there are niche differences between consumers. Mathematically, this is also often assumed to be the case, because using techniques such as evolutionary invasion analysis describe the ability for a consumer with a mutant allele to increase in abundance when rare, a demographic signature of niche differentiation. Therefore, if both consumers are able to invade when rare, then this suggests that they can coexist. On the other hand, relatively specialized consumers have also been shown to be a strongly stabilizing force in food webs (McCann et al. 2005). This is because these more specialized consumers may generate asynchrony in the dynamics of patchily distributed resources. This asynchrony in resources then permits consumers to move to habitat patches with higher resource densities after they have depleted the resources in a different patch. If, for example, the consumers were not specialized, then the resources would exhibit the same dynamics, so when the resources at low densities, consumers would be unable to switch to alternative resources, which would cause the consumer populations to crash, and oscillate more with their resources (McCann et al. 2005). Consequently, whether ecological character displacement will tend to stabilize (via asynchronous resource dynamics) or destabilize (via increased interaction strength) food webs is unclear.

On the other hand, ecological character displacement often results in the evolution of characters that enhance a consumer’s ability to capture resources, which tends to destabilize consumer-resource interactions (Murdoch et al. 2003; McCann 2011). This occurs because increases in a consumer’s attack rate results in the resource being suppressed well below its carrying capacity, which if sufficient enough, can generate oscillations, and hence less stable, consumer-resource dynamics (Rosenzweig 1971; Murdoch et al. 2003). Experimental decreases in interaction strength between consumers and resources has been shown to promote coexistence between consumers and resources (Luckinbill 1973). Moreover, there is broad support that specialized consumers, since they are tightly coupled to their resources, tend to exhibit consumer-resource cycles, whereas this is not the case for generalists (Murdoch et al. 2002). Therefore, although evolutionary responses to exploitative competition may reduce the strength of interactions between consumers, they ultimately increase the strength of interactions with their resources which can destabilize the direct consumer-resource interaction (rather than the indirect consumer-consumer interaction). While prior models of character displacement have included more realistic functional responses and spatial relationships between consumers and resources, they have focused more on whether these factors alter patterns of character displacement rather than the effects of character displacement on the stability of the ecological community. As a consequence, it is currently unclear whether ecological character displacement has a net stabilizing or destabilizing effect on ecological communities.

Here, we address this knowledge gap by building a mathematical model to examine how ecological character displacement affects consumer-resource dynamics. We then compared the predictions from our model to field data from one of the most well-studied examples of ecological character displacement in a natural system, threespine stickleback in lakes of southern British Columbia. We specifically sought to address two questions: (1) How does exploitative competition between two consumers for two resources affect the evolution of consumer attack rates? (2) How does the evolution of consumer attack rates affect community stability? -->

## Model of resource competition

To examine how ecological character displacement affects consumer-resource interactions and food-web dynamics, I analyzed a continuous-time model of two consumers ($C_1,C_2$) competing for two shared resources ($R_1,R_2$):

$$\frac{dR_1}{dt}=r_1K_1(1-\frac{R_1}{K_1})-F_{11}(R_1)C_1-F_{21}(R_1)C_2$$
$$\frac{dR_2}{dt}=r_2K_2(1-\frac{R_2}{K_2})-F_{12}(R_2)C_1-F_{22}(R_2)C_2$$
$$\frac{dC_1}{dt}=e_{11}F_{11}(R_1)C_1+e_{12}F_{12}(R_2)C_1-m_1C_1$$
$$\frac{dC_2}{dt}=e_{21}F_{21}(R_1)C_2+e_{22}F_{22}(R_2)C_2-m_2C_2$$

where $r_i$ represents the intrinsic growth rate of resource $i$, $K_i$ represents the carrying capacity of resource $i$, $e_{ji}$ represents the conversion efficiency of resource $i$ into consumer $j$, and $m_j$ represents the mortality rate of consumer $j$. $F_{ji}(R_i)$ represents consumer $j$'s feeding rate (i.e. functional response) on resource $i$. This model is a useful characterization of a scenario where consumers compete for two distinct resources (e.g. zooplankton and benthic invertebrates) rather than if resources are better characterized by a continuous trait distribution (e.g. seed size, see @Taper1985 for an example). In the scenario where consumer feeding rates increase linearly with resource density, such that $F_{ji}(R_i)=a_{ji}R_i$ where $a_{ji}$ is the attack rate of consumer $j$ on resource $i$, then this model becomes MacArthur's model of resource competition (@MacArthur1972). The evolution of consumer attack rates in this model (and several extensions) have been analyzed in detail (@Lawlor1976; @Abrams1986). The general result of these analyses is that divergent character displacement in attack rates is an inevitable outcome of resource competition. <!-- In other words, the presence of a competitor causes consumers to evolve more specialized attack rates ($\frac{a_{ii}}{a_{ii}+a_{ij}}$) compared to when no competitor is present. -->

Here, I examine the effects of this inevitable divergence in attack rates on food-web dynamics. In particular, I examine how divergence in attack rates affect resource densities as well as the local stability of both resources and consumers. I do this by (i) deriving analytical expressions for the relationship between attack rates and food-web dynamics in different foraging scenarios and (ii) simulating the effects of competition on the eco-evolutionary dynamics of consumers and resources. For these simulations, I used an Adaptive Dynamics approach. At each evolutionary time step, I created a mutant consumer by randomly choosing a consumer and modifying its attack rate on one resource by either subtracting or adding a small constant <!-- (0.001 in the following simulations) -->with equal probability. The mutant's attack rate on the other resource was determined by the shape of the tradeoff (details below). Assuming this mutant consumer is rare, I then determined whether the mutant had higher relative fitness than the resident consumer, and thus could invade and replace the resident consumer. If the mutant was able to invade, I updated the attack rate of the resident consumer to the mutant attack rate and allowed consumer and resource dynamics to reach a steady state. I then repeated the simulation up to 10,000 times, which was sufficient for consumers to either reach an evolutionary stable strategy (ESS, @Smith1973) or an evolutionary limit (e.g. $\frac{a_{ii}}{a_{ii}+a_{ij}}$ is constrained to a maximum of 1 and minimum of 0). I show that the consequences of character displacement on food-web dynamics are not intuitive and depend critically on the foraging scenario and tradeoff in consumer attack rates.

## Effect of character displacement on resource densities

I start by examing the effects of character displacement on the density of resources at equilibrium, which will also set the stage for a later analysis of food-web stability. In particular, I examine two different foraging scenarios: one where consumers forage for both resources simultaneously (e.g. @MacArthur1972) and one where they cannot because resources occur in distinct habitats (e.g. @Lawlor1976; @McCann2005). I say consumers have undergone divergent character displacement if there evolved attack rates are more specialized, defined as $|\frac{a_{ii}}{a_{ii}+a_{ij}}-0.5|$, when evolving with a competing consumer.

### Consumers forage for both resources simultaneously

An inherent assumption in MacArthur's model of resource competition is that consumers can forage for both resources simultaneously. In essence, this implies that both resources occur within the same habitat. To gain analytical insight to this scenario, I assume that resources are equivalent ($r=r_1=r_2$ and $K=K_1=K_2$) as well as consumers ($e=e_{11}=e_{12}=e_{21}=e_{22}$; $m=m_1=m_2$), except that consumer attack rates are mirror images of each other ($a_{ii}=a_{11}=a_{22}$; $a_{ij}=a_{12}=a_{21}$). While this scenario is arguably simplistic, it isolates the effect of character displacement rather than any dependence on inherent differences in consumers or resources. I show that when both consumers and resources are present that the density of resources at equilibrium are equivalent ($R=R_1=R_2$) and are determined by the following equation (*Mathematica* file with derivation available upon request):

$$\hat{R}=\frac{1}{a_{ii}+a_{ij}}\cdot\frac{m}{e}$$
Note that a key determinant of resource density is the consumer's total attack rate, $a_{ii}+a_{ij}$. Since the total attack rate is in the denominator, this implies that resource densities will decrease if evolution favors an increase in total attack rate. I assume that consumers are not 'Darwinian demons' (@Law1979) and thus the evolution of their attack rates are subject to certain constraints. I modelled these constraints such that $\big(a_{ii}/{A}\big)^n+\big(a_{ij}/{A}\big)^n=1$, where $A$ is the total investment in attack rates and $n$ describes the shape of the tradeoff (@Sargent2006). This function has the useful property that it differentiates between cases where intermediate combinations of $a_{ii}$ and $a_{ij}$ are higher, on average, than the extremes (when $n>1$, green line in Fig. \ref{fig:Tradeoff}) or, conversely, where the two extremes are higher, on average, than intermediate investments (when $n<1$, orange line Fig. \ref{fig:Tradeoff}). When $n=1$, the tradeoff function is linear, and all combinations of $a_{ii}$ and $a_{ij}$ have the same total attack rate (blue line in Fig. \ref{fig:Tradeoff}).

```{r Tradeoff, echo=FALSE, fig.cap="\\label{fig:Tradeoff}Tradeoff forms for consumer attack rates."}
tradeoff_plot <- bind_rows(concaveDN_df, linear_df, concaveUP_df) %>%
  ggplot(., aes(x=aii, y=aij, color = factor(n))) + 
  geom_line() + 
  xlab(expression(a[ii])) +
  ylab(expression(a[ij])) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)

tradeoff_plot
```

Previous work has shown that consumers undergo divergent character displacement regardless of the shape of the tradeoff (@Lawlor1976; @Abrams1986). Interestingly, I find that the shape of the tradeoff qualitatively affects the relationship between character displacement and resource density (Fig. \ref{fig:MacArthur_Resources}). For example, if consumer's are constrained by a linear tradeoff (blue lines), then there is no net change in total attack rate (Fig. \ref{fig:MacArthur_Resources}A) and character displacement has no effect on resource densities (Fig. \ref{fig:MacArthur_Resources}B). If the tradeoff is concave down (green lines), then resource abundances can actually increase under character displacement (Fig. \ref{fig:MacArthur_Resources}B). This is because the total attack rate of consumers is maximized at intermediate values ($a_{ii}=a_{ij}$) and decreases as consumers diverge (Fig. \ref{fig:MacArthur_Resources}A). Note that detecting this effect in nature would likely be difficult, since a concave-down tradeoff results in relatively small displacement relative to other tradeoff shapes (@Lawlor1976; green points in Fig. \ref{fig:MacArthur_Resources}A,B). When the tradeoff is concave up (orange lines), character displacement suppresses resource densities due to the increase in total attack rates (Fig. \ref{fig:MacArthur_Resources}A,B). Although the equation I derived for resource density was for the scenario where both consumers and both resources are present, it predicts well the density of resources when a single consumer reaches its ESS (triangles on respective colored lines in Fig. \ref{fig:MacArthur_Resources}B). This is because a single consumer evolves to be a generalist that has equal attack rates on each resource (triangles at 0.5 along x-axis in Fig. \ref{fig:MacArthur_Resources}A), resulting in equivalent resource densities.

```{r MacArthur_Resources, echo=FALSE, fig.cap="\\label{fig:MacArthur_Resources}Effect of character displacement on total attack rates (A) and resource densities (B) when consumers can forage for both resources simultaneously."}
Mac_attack <- ggplot(tradeoff_df, aes(x=aii/(aii+aij), y=aii+aij, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=a11+a12, fill=factor(n), shape=Competitor), size=5, color="black") + #, show.legend=FALSE) +
  #geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=a11+a12, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(a[ii]+a[ij])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Mac_resources <- cbind.data.frame(tradeoff_df, MacArthur_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=R1+R2, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=5, color="black") + #, show.legend=FALSE) +
  #geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(R[i]+R[j])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Mac_plots <- plot_grid(Mac_attack + theme(legend.position = "none"), Mac_resources, 
                       ncol=2, labels = "AUTO", rel_widths = c(0.65,1))
Mac_plots
```

### Consumers *cannot* forage for resources simultaneously

Most models of character displacement have assumed a scenario where consumers can forage for both resources simultaneously (e.g. @Taper1985; @Abrams1986). This assumption may be valid for some foraging scenarios (e.g. Darwin's finches foraging for seeds); however, in many situations consumers forage for resources that occur in different habitats, and thus cannot forage for both simultaneosly. The only character displacement model that I am aware of that modeled resources in different habitats was one examined by @Lawlor1976. This model takes the same form as the previous model, except now the consumer's feeding rate takes the form:

$$F_{ji}(R_i)=w_{ji}a_{ji}R_i$$

where $w_{ji}$ represents the proportion of time consumer $j$ spends foraging in a habitat where only resource $j$ is found (i.e. habitat preference). Note that since $w_{ji}$ is a proportion that $w_{jj}=1-w_{ji}$. As with attack rates, I assume that consumer habitat preferences are mirror images of each other ($w=w_{11}=w_{22}$).

@Lawlor1976 found that consumers still underwent divergent character displacement regardless of whether consumers could or could not forage for resources simultaneously. I find that the foraging scenario qualitatively affects the relationship between character displacement and resource densities. To demonstrate this, note that again resource densities are equivalent at equilibrium ($R=R_1=R_2$ when both consumers and resources present), but are now determined by the following equation (*Mathematica* file with derivation available upon request):

$$\hat{R}=\frac{1}{wa_{ii}+(1-w)a_{ij}}\cdot\frac{m}{e}$$

This equation implies that if consumers evolve to become specialists on resources that occur in their preferred habitat (e.g. $w>0.5$ and $a_{ii}>a_{ij}$), then character displacement will always increase the effective attack rate of consumers ($wa_{ii}+(1-w)a_{ij}$), regardless of the tradeoff (Fig. \ref{fig:LS_Resources}A). Thus, character displacement always results in resource suppression if consumers are competing for resources that occur in different habitats (Fig. \ref{fig:LS_Resources}B). Note that the shape of the tradeoff can modify the effect of character displacement. This is not so much due to the tradeoff affecting the magnitude of displacement (it does, but the effect is minor), but because the form of the tradeoff affects resource abundances when a single consumer has reached its ESS (triangles in Fig. \ref{fig:LS_Resources}B). In contrast, resource densities reach a similar value when consumers evolve in the presence of a competitor (circles in Fig. \ref{fig:LS_Resources}B), because character displacement tends to reach a constraint of complete specialization.

These results do lead to an interesting prediction that could be tested either experimentally or with field data. If consumers are competing for resources that occur in different habitats, then greater character displacement corresponds to a greater decrease in resource densities (line trajectories in Fig. \ref{fig:LS_Resources}B). This prediction likely only applies to comparisons within species where there is likely little difference in the shape of the tradeoff among populations.

It is worth noting that in this foraging scenario, resource densities are consistently higher at the single consumer ESS compared to the predictions I derived for when both consumers are present (deviation of triangles from respective colored lines in Fig. \ref{fig:LS_Resources}B). This is likely because consumers actually evolve to be slightly specialized on the resources that occur in their non-preferred habitat (deviation of triangles from 0.5 along x-axis in Fig. \ref{fig:LS_Resources}B). <!-- I will revisit this subtle point when I examine the effects of character displacement on food-web stability. -->

```{r LS_Resources, echo=FALSE, fig.cap="\\label{fig:LS_Resources}Effect of character displacement on effective attack rates (A) and resource densities (B) when consumers cannot forage for resources simultaneously."}
LS_attack <- ggplot(tradeoff_df, aes(x=aii/(aii+aij), y=wii*aii+wij*aij, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(LawlorSmith_displacements, Time=="End"), aes(x = a11/(a11+a12), y=w11*a11+w12*a12, fill=factor(n), shape=Competitor), size=5, color="black") + #, show.legend=FALSE) +
  #geom_point(data = filter(LawlorSmith_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=w11*a11+w12*a12, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(w*a[ii]+(1-w)*a[ij])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

LS_resources <- cbind.data.frame(tradeoff_df, LawlorSmith_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=R1+R2, color=factor(n))) + 
  geom_line() +
  geom_point(data = filter(LawlorSmith_displacements, Time=="End"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=5, color="black") + #, show.legend=FALSE) +
  #geom_point(data = filter(LawlorSmith_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(R[i]+R[j])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21)) +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

LS_plots <- plot_grid(LS_attack + theme(legend.position = "none"), LS_resources, 
                      ncol=2, labels = "AUTO", rel_widths = c(0.65,1))
LS_plots
```

The effect of the foraging scenario on the relationship between character displacement and resource densities appears to be quite general. For example, even if I consider a more realistic consumer functional response (derived by @McCann2005):

$$F_{ii}(R_i,R_j)=\frac{a_{ii}W_{ii}R_i}{1+a_{ii}hW_{ii}R_i+a_{ij}hW_{ij}R_j}$$

where consumer feeding rates on resource $i$ are influenced by both resource densities; saturate as resource densities increase (due to handling time $h$); and consumer habitat preferences are modified by relative resource densities, such that:

$$W_{ii}=\frac{wR_i}{wR_i+(1-w)R_j}$$

I still observe the same qualitative relationship between character displacement and resource suppression (Fig. \ref{fig:McCann_Resources} in Appendix). This is because resource competition always leads to character divergence and equilibrium resource densities are governed by similar dynamics  (*Mathematica* file with derivations available upon request):

$$\hat{R}=\frac{1}{wa_{ii}+(1-w)a_{ij}}\cdot\frac{m}{e-hm}$$

<!-- This more realistic consumer functional response does actually make an interesting evolutionary prediction that differs from the scenario where consumer feeding rate scales linearly with resource density. Specifically, a consumer's ESS in the absence of competition will remain slightly more specialized on the resources that occur in their preferred habitats. This is in contrast to the prediction when feeding rates scale linearly with resource density, where consumers evolve to be slightly more specialized on resources occurring in their non-preferred habitats. An important caveat for these predictions is that my model does not allow habitat preferences to evolve, which would likely alter these predictions. -->

## Effect of character displacement on food-web stability

Of the prior models of character displacement, only @Lawlor1976 examine the effect of character displacement on the ecological stability of the system. They conducted a detailed theoretical analysis of three different metrics of stability: (i) stable coexistence of consumers, defined as the mutual invasibility of each consumer; (ii) global stability of consumers, defined as the continued coexistence of both consumers when resource dynamics are perturbed; and (iii) local stability, defined as the rate at which the four-species food web returned to equilibrium after a small perturbation to species abundances. Note that the first two metrics correspond to the stable coexistence of consumers, while the third metric measures the stability of the entire food web. @Lawlor1976 found that character displacement enhanced the stable coexistence of consumers, yet had a small negative effect on the local stability of the food web.

@Lawlor1976's work gave fundamental insight to the effect of character displacement on ecological stability; however, none of their stability analyses compared food webs with and without a competing consumer. Such comparisons are necessary for inferring the effects of ecological character displacement, a point that has been made clear in the criteria to demonstrate character displacement (@Schluter2000; @Schluter1992). In fact, the first two metrics of stability can only be assessed when both consumers are present because it examines the effect of divergence on coexistence, which requires both consumers to be present. In contrast, local stability can be compared in food webs with and without a competing consumer, and thus provides a useful benchmark for examining the effects of character displacement on food-web stability.

Below, I plot the results from the same simulations I did previously except now local stability ($-1\times\operatorname{Re}(\lambda_{max})$) is on the y-axis (Fig. \ref{fig:Stability}). In general, I find that resource supression goes hand-in-hand with local stability, a tendency that has been noted by others (@Murdoch2003; @McCann2011). Whenever character displacement results in resource suppression, I observe a decrease in local stability (Fig. \ref{fig:Stability}). This is not simply a consequence of having an additional consumer in the system, but emerges from the eco-evolutionary feedback between character displacement and resource suppression (compare initial (small points) with evolved strategies (large points), Fig. \ref{fig:Stability}). Note that I reach the same fundamental conclusions when I incorporated a more realistic functional response for the consumers (Fig. \ref{fig:Stability_McCann} in Appendix).

```{r Stability, echo=FALSE, fig.cap="\\label{fig:Stability}Effect of character displacement on local stability when consumers can (A) and cannot (B) forage for both resources simultaneously. Small and large points correspond to initial and evolved strategies, respectively."}
Stability_Mac <- cbind.data.frame(tradeoff_df, MacArthur_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=-1*max.Re.eigen, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(MacArthur_displacements, Time=="End"), aes(x = a11/(a11+a12), y=-1*max.Re.eigen, fill=factor(n), shape=Competitor), size=5, color="black", show.legend=FALSE) +
  geom_point(data = filter(MacArthur_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=-1*max.Re.eigen, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  ylab(expression(-1%*%"Re"(lambda[max]))) +
  scale_shape_manual(values=c(24,21))  +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Stability_LS <- cbind.data.frame(tradeoff_df, LawlorSmith_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=-1*max.Re.eigen, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(LawlorSmith_displacements, Time=="End"), aes(x = a11/(a11+a12), y=-1*max.Re.eigen, fill=factor(n), shape=Competitor), size=5, color="black", show.legend=FALSE) +
  geom_point(data = filter(LawlorSmith_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=-1*max.Re.eigen, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  ylab(expression(-1%*%"Re"(lambda[max]))) +
  scale_shape_manual(values=c(24,21))  +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Stability_plots <- plot_grid(Stability_Mac + theme(legend.position = "none"), Stability_LS + theme( axis.title.y = element_blank()),
                             ncol = 2, labels = "AUTO", rel_widths = c(0.75,1))
Stability_plots
```

I conducted the previous simulations on a scenario where the food web remains locally stable ($\operatorname{Re}(\lambda_{max})<0$). Is it possible that character displacement would ever result in a locally unstable food web? To gain analytical insight to this question, I examined the conditions governing the local stability of the four-species food web when consumers exhibit a more realistic functional response (@McCann2005). I show that the four-species food web will transition from having a locally stable equilibrium to a limit cycle under the following conditions (*Mathematica* file with derivation available upon request):

$$wa_{ii}+(1-w)a_{ij} > \frac{e+hm}{hK(e-hm)}$$

Previously, I showed that character displacement always increases the effective attack rate of consumers ($wa_{ii}+(1-w)a_{ij}$), regardless of the the shape of the tradeoff (Fig. \ref{fig:LS_Resources}A). Thus, character displacement is capable of pushing food webs to a point where they are locally unstable.

## Predictions for threespine stickleback

The scenario where the relationship between character displacement and resource suppression is the strongest is when the tradeoff in attack rates is concave-up and consumers are competing for resources that occur in different habitats (orange points in Fig. \ref{fig:LS_Resources}B and Fig. \ref{fig:McCann_Resources}B). Prior work in threespine stickleback suggests that the evolution of stickleback attack rates are constrained by a concave-up tradeoff (@Schluter1993; @Arnegard2014) and that stickleback ecotypes are competing for resources that occur in different habitats (benthic vs. limnetic, @Schluter1992). Thus, I predict that ecological character displacement in sticklebacks would suppress resource densities and decrease local stability.

While measuring resource densities is relatively straightforward, measuring stability is notoriously difficult. One of the more easy to acquire empirical metrics of stability is the coefficient of variation ($CV=\frac{\sigma}{\mu}$) as this only requires measurements of resource (or consumer) densities over time. Interestingly, there is a close correspondence between the coefficient of variation and the local stability of a food web (@Gellner2016). <!-- This close correspondence emerges from the fact that stochastic perturbations in resource (or consumer) densities will determine the variability in abundances. And since food webs are constantly buffeted by stochastic processes in the real world, I expect that my predictions using local stability would correspond to the $CV$ of resources (or consumers). -->Thus, I predict that character displacement in threespine stickleback will increase the $CV$ of resource (or consumer) densities.

Consumer and resource densities in these dynamical models can be interpreted from either a population or biomass perspective (@Yodzis1992; @Murdoch2003; @McCann2011). For the stickleback system, you have data on seasonal dynamics of resources in terms of both abundances and biomass. Within a season, I do not expect stickleback abundances to be coupled to the abundances of zooplankton and benthic invertebrates, given that stickleback reproduce annually whereas zooplankton and benthic invertebrates can reproduce many times within a season. Instead, I expect that stickleback biomass will be coupled to the biomass of zooplankton and benthic invertebrates within a season. This is because there will be lots of young stickleback at the beginning of the season, and they will eat a lot of resources and grow in size as the season progresses. If this is true, I also expect to see the largest negative effect of stickleback on resource densities late in the season.

### Other relevant points

Although I used an Adaptive Dynamics approach here, I expect that these theoretical predictions would apply to models that assumed a different genetic architecture of attack rates (e.g. quantitative genetics). I expect this because, time and time again, models that explicitly include resource dynamics inevitably show that resource competition results in divergent character displacement, regardless of the genetic architecture of traits (see synthesis by @Taper1985). Finally, my conclusions only apply to biological resources that are nutritionally substitutable. It would be interesting to extend these current analyses to non-substitutable resources where convergent character displacement is expected (@Abrams1987; @Fox2008).

## Acknowledgement

The content of this paper was greatly enhanced by numerous conversations with Seth Rudman. Sally Otto provided much help in early analyses of the mathematical model and I would not have been able to take the theory as far as I did without her guidance and her pushing me.

## Appendix: More realistic functional response

```{r McCann_Resources, echo=FALSE, fig.cap="\\label{fig:McCann_Resources}Effect of character displacement on total attack rates (A) and resource densities (B) when consumers exhibit a more realistic functional response."}
McCann_attack <- ggplot(tradeoff_df, aes(x=aii/(aii+aij), y=wii*aii+wij*aij, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(McCann_displacements, Time=="End"), aes(x = a11/(a11+a12), y=w11*a11+w12*a12, fill=factor(n), shape=Competitor), size=5, color="black") + #, show.legend=FALSE) +
  #geom_point(data = filter(McCann_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=w11*a11+w12*a12, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(w*a[ii]+(1-w)*a[ij])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21))  +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

McCann_resources <- cbind.data.frame(tradeoff_df, McCann_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=R1+R2, color = factor(n))) + 
  geom_line() +
  geom_point(data = filter(McCann_displacements, Time=="End"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=5, color="black") + #, show.legend=FALSE) +
  #geom_point(data = filter(McCann_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=R1+R2, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  ylab(expression(R[i]+R[j])) +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  scale_shape_manual(values=c(24,21))  +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

McCann_plots <- plot_grid(McCann_attack + theme(legend.position = "none"), McCann_resources, 
                          ncol=2, labels = "AUTO", rel_widths = c(0.65,1))
McCann_plots
```

```{r Stability_McCann, echo=FALSE, fig.cap="\\label{fig:Stability_McCann}Effect of character displacement on local stability when consumers exhibit a more realistic functional response."}
Stability_McCann <- cbind.data.frame(tradeoff_df, McCann_2C_2R_tradeoff_dynamics) %>%
  ggplot(., aes(x=aii/(aii+aij), y=-1*max.Re.eigen, color=factor(n))) + 
  geom_line() +
  geom_point(data = filter(McCann_displacements, Time=="End"), aes(x = a11/(a11+a12), y=-1*max.Re.eigen, fill=factor(n), shape=Competitor), size=5, color="black", show.legend = FALSE) +
  geom_point(data = filter(McCann_displacements, Time=="Begin"), aes(x = a11/(a11+a12), y=-1*max.Re.eigen, fill=factor(n), shape=Competitor), size=1.5, color="black") +
  xlab(expression(frac(a[ii],a[ii]+a[ij]))) +
  ylab(expression(-1%*%"Re"(lambda[max]))) +
  scale_shape_manual(values=c(24,21))  +
  scale_color_manual(name="Tradeoff (n)", values=cbPalette)  +
  scale_fill_manual(name="Tradeoff (n)", values=cbPalette) +
  guides(fill = guide_legend(override.aes=list(shape=21)))

Stability_McCann
```

### 2018-11-13 analyses/reproduce_analyses.Rmd
commit updated changes to analyses that calculate bootstrapped differences from zero and between treatments

@@
 ---
-title: "Reproducing Analyses for Phenotypic evolution is less constrained in complex
-  food webs"
+title: "Supplementary Material"
 author: "Matthew A. Barbour"
@@
     highlight: github
+#output:
+#  pdf_document:
+#    df_print: paged
+#    fig_caption: true
+#    citation_package: natbib
+#    includes:  
+#      in_header: preamble-latex.tex
+#bibliography: references_ECD_supp_mat.bib
+fontsize: 12pt
 ---
@@
 
-We used graphical checks to evaluate whether our transformations of traits resulted in a multivariate normal distribution.
-As you can see from the multivariate qq-plot, it seems reasonable that our data approximates a multivariate normal distribution.
-Of course, statistical tests suggest otherwise.
-But as an example of how silly these tests can be, look at the distribution of gall diameter.
-It is the closest ecological variable I've ever seen that is normally distributed, yet a Shapiro-Wilks test says otherwise.
-
-```{r MVN Assumption, echo=FALSE}
-
-mvn_assumption <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq", univariatePlot = "histogram")
-
-# mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
-
-mvn_assumption$univariateNormality[1, ]
-```
-
-# Quantifying biased selection on chamber diameter
-
-We quantified biased selection on chamber diameter in the following way.
+We used graphical checks to evaluate whether our transformations of trait values resulted in a multivariate normal distribution.
+Figure S\ref{fig:Univariate_histograms} shows that our transformations resulted in approximately normal distributions for each phenotypic trait.
+Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line (fig.
+S\ref{fig:Multivariate_QQ}), suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.
+
+```{r Univariate_histograms, echo=FALSE, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
+mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
+```
+
+```{r Multivariate_QQ, echo=FALSE, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
+mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
+```
+
+# Effect of food-web treatment on trait-fitness relationships and selection gradients
+
+We write the model in a way the independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival.
+
+```{r Food-web model, cache=TRUE}
+foodweb_model <- glmer(
+  gall_survival ~ 
+    -1 + Foodweb + 
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
+    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df,
+  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+```
+
+Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
+For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
+
+```{r Bootstrap food-web model, cache=TRUE, include=FALSE}
+boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Linear food-web model, cache=TRUE}
+linear_foodweb_model <- glmer(
+  gall_survival ~ 
+    -1 + Foodweb + 
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df,
+  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+visreg::visreg(linear_foodweb_model, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
+```
+
+```{r Bootstrap linear food-web model, cache=TRUE, include=FALSE}
+boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+To estimate biased selection on chamber diameter, we subset our data to only include multi-chambered galls where there was variability in larval survival.
+We then fit a reduced model to estimate the bias in the logistic regression coefficient of chamber diameter in each food web.
+
+<!-- We quantified biased selection on chamber diameter in the following way.
 First, we focus on multi-chambered galls where there is evidence of both survival and parasitism.
@@
 Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism.
-
-We calculated the bias in selection differential on chamber diameter by calculating the difference in mean chamber diameter before (i.e.
-all larva within the same gall) and after selection (only surviving larva).
-We then used a one-sample t-test to determine whether the selection differential was significantly different from zero.
-We conducted separate t-tests for each food-web treatment.
-
-We can then subtract this "biased selection differential" from the observed directional selection gradient on chamber diameter to adjust for the confounding effects of parasitism.
-
-We write the model in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larva survival.
-
-```{r Food-web model, cache=TRUE}
-foodweb_model <- glmer(
-  gall_survival ~ -1 + Foodweb + #sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    #I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
-    #sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
+-->
+
+```{r Bias in food-web model, cache=TRUE}
 biased_foodweb_df <- gall_selection.df %>%
@@
 
-biased_foodweb_model <- glmer(gall_survival ~ -1 + Foodweb + Foodweb:sc.Diam + (1|Genotype/Plant_Position/Gall_Number),
+# using linear model, but I'm only interested in the chamber diameter coefficient
+biased_foodweb_model <- glmer(
+  gall_survival ~ -1 + Foodweb + 
+    Foodweb:sc.Diam + 
+    (1|Genotype/Plant_Position/Gall_Number),
   data = biased_foodweb_df,
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-```
-
-Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
-For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
-
-```{r Bootstrap food-web model, cache=TRUE, include=FALSE}
-boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+
+biased_foodweb_confint <- tidy(biased_foodweb_model, conf.int=TRUE) %>% filter(group=="fixed")
+
+knitr::kable(biased_foodweb_confint)
 ```
@@
 ```{r Food-web alpha coefficients, include=FALSE}
+foodweb_bind <- bind_cols(
+  as_tibble(boot_linear_foodweb_model$t),
+  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
 
 # Adjust coefficients with chamber diameter
-foodweb_adj_Diam <- as_tibble(boot_foodweb_model$t) %>%
+foodweb_adj_Diam <- foodweb_bind %>%
   mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])#,
-         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_foodweb_model)["FoodwebComplex:I(sc.Diam^2)"],
-         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_foodweb_model)["FoodwebSimple:I(sc.Diam^2)"],
-         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
-         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
-         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
-         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])
 
@@
 foodweb_alphas <- foodweb_adj_Diam %>%
-  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
+  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
   mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
@@
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+
+knitr::kable(tidy_foodweb_alphas)
 ```
@@
   ggplot(., aes(x=type)) +
-  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
-  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
   geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Larva survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
   xlab("Food web") +
@@
          conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+
+knitr::kable(tidy_foodweb_grads)
 ```
@@
 
+# Partitioning the contribution of egg and larval parasitoids to selection gradients
+
+Our simple food-web treatment allows us to estimate the unique contribution of egg parasitoids to selection on *Iteomyia* traits.
+To estimate the unique contribution of larval parasitoids, we subset our data so that our complex food-web treatment only contained attack by larval parasitoids (and gall survival).
+We then fit the same models as previously, including one to estimate bias.
+
 ```{r Egg vs. larval ptoid model, cache=TRUE}
@@
 
-Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
-For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
-
 ```{r Bootstrap egg vs. larval ptoid model, cache=TRUE, include=FALSE}
@@
 
+```{r Linear egg vs. larval ptoid model, cache=TRUE}
+linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
+```
+
+```{r Bootstrap linear egg vs. larval model, cache=TRUE, include=FALSE}
+boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
 ```{r Egg vs. larval ptoid alpha coefficients, include=FALSE}
+egglarval_bind <- bind_cols(
+  as_tibble(boot_linear_egglarval_model$t),
+  select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
 
@@
   mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])#,
-         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_egglarval_model)["FoodwebComplex:I(sc.Diam^2)"],
-         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_egglarval_model)["FoodwebSimple:I(sc.Diam^2)"],
-         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
-         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
-         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
-         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])
 
@@
 egglarval_alphas <- egglarval_adj_Diam %>%
-  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
+  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
   mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
@@
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+
+knitr::kable(tidy_egglarval_alphas)
 ```
@@
   ggplot(., aes(x=type)) +
-  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
-  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
   geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Larva survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
   scale_x_discrete(name="Parasitoid", breaks=c("Complex","Simple"), labels=c("Larval","Egg")) +
@@
          conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+
+knitr::kable(tidy_egglarval_grads)
 ```
@@
 
+# Reproduce Figure 2 of main manuscript
+
+We combine our estimates of selection gradients for each food-web treatment as well as the contribution of larval parasitoids to selection in the complex food web.
+
+```{r Figure-Selection-Gradients, echo=FALSE, fig.cap="**Selection gradients**.
+Estimates of standardized selection gradients in complex (orange) and simple (blue) food webs.
+The contribution of larval parasitoids (yellow) was estimated with a subset of the complex food-web data that only contained attacks from larval parasitoids (and gall survival).
+Points and lines correspond to estimates of the mean and 95% confidence intervals, respectively.
+Overlapping confidence intervals with zero (dotted line) indicate no strong evidence of selection."}
+tidy_foodwebegglarval_grads <- bind_rows(
+  tidy_foodweb_grads, mutate(filter(tidy_egglarval_grads, type=="Complex"), type="Larval")
+)
+tidy_foodwebegglarval_grads$type <- factor(tidy_foodwebegglarval_grads$type, levels=c("Complex","Simple","Larval","Diff"))
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_foodwebegglarval_grads <- c(min(filter(tidy_foodwebegglarval_grads, type!="Diff")$conf.low), 
+                            max(filter(tidy_foodwebegglarval_grads, type!="Diff")$conf.high))
+P_asterisk_foodwebegglarval_grads <- 0.25
+P_size <- 8
+legend_foodwebegglarval_labels <- c("Egg + Larval (Complex)","Egg (Simple)","Larval")
+legend_foodwebegglarval_title <- "Parasitoids"
+point.size <- 3
+
+# Plot directional selection gradients
+plot_foodwebegglarval_directional_grads <- tidy_foodwebegglarval_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+ # geom_text(data=filter(tidy_foodwebegglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+#            aes(y=P_asterisk_foodwebegglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodwebegglarval_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title)
+
+# Plot quadratic selection gradients
+plot_foodwebegglarval_quadratic_grads <- tidy_foodwebegglarval_grads %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+ # geom_text(data=filter(tidy_foodwebegglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+#            aes(y=P_asterisk_foodwebegglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodwebegglarval_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title)
+
+# Plot correlational selection gradients
+plot_foodwebegglarval_correlational_grads <- tidy_foodwebegglarval_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+ # geom_text(data=filter(tidy_foodwebegglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+#            aes(y=P_asterisk_foodwebegglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodwebegglarval_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title)
+
+# Get legend
+#legend_foodwebegglarval_grads <- get_legend(plot_foodwebegglarval_directional_grads)
+
+# Format plots for manuscript
+#plot_foodwebegglarval_grads <- plot_grid(
+#  plot_foodwebegglarval_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+#  plot_foodwebegglarval_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+#  plot_foodwebegglarval_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+#  nrow=2, align="hv", labels = "")
+#plot_legend_foodwebegglarval_grads <- ggdraw(plot_foodwebegglarval_grads) + draw_grob(legend_foodwebegglarval_grads, x = 0.7, y=-0.2)
+#y_title_foodwebegglarval_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+#figure_foodwebegglarval_grads <- plot_grid(y_title_foodwebegglarval_grads, plot_legend_foodwebegglarval_grads, ncol=2, rel_widths = c(0.05,1)) 
+#figure_foodwebegglarval_grads
+
+# Alt format
+legend_foodwebegglarval_grads <- get_legend(plot_foodwebegglarval_directional_grads + theme(legend.title.align = 0.5))
+
+plot_foodwebegglarval_grads <- plot_grid(
+  NULL, 
+  plot_foodwebegglarval_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_foodwebegglarval_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_foodwebegglarval_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+plot_legend_foodwebegglarval_grads <- ggdraw(plot_foodwebegglarval_grads) + draw_grob(legend_foodwebegglarval_grads, x = 0.1, y=0.25)
+y_title_foodwebegglarval_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+figure_foodwebegglarval_grads <- plot_grid(y_title_foodwebegglarval_grads, plot_legend_foodwebegglarval_grads, ncol=2, rel_widths = c(0.05,1)) 
+figure_foodwebegglarval_grads
+```
+
+# Partitioning the components of selection gradients
+
+Selection gradients are influenced by both trait-fitness relationships and population mean fitness. Here, we partition selection gradients into these underlying components.
+
+```{r Plot foodwebegglarval coefficients, echo=FALSE, fig.cap="**Partitioning Selection Gradients.**"}
+tidy_foodwebegglarval_alphas <- bind_rows(
+  tidy_foodweb_alphas, mutate(filter(tidy_egglarval_alphas, type=="Complex"), type="Larval")
+)
+tidy_foodwebegglarval_alphas$type <- factor(tidy_foodwebegglarval_alphas$type, levels=c("Complex","Simple","Larval","Diff"))
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_foodwebegglarval_coefs <- c(min(filter(tidy_foodwebegglarval_alphas, type!="Diff")$conf.low), 
+                            max(filter(tidy_foodwebegglarval_alphas, type!="Diff")$conf.high))
+P_asterisk_foodwebegglarval_coefs <- 1.3
+P_size <- 8
+legend_foodwebegglarval_labels <- c("Larval","Egg")
+point.size <- 3
+
+# Plot mean fitness
+plot_foodwebegglarval_mean_fitness <- tidy_foodwebegglarval_alphas %>%
+  filter(type!="Diff", term=="(Intercept)") %>%
+  ggplot(., aes(x=type)) +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+ # geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_x_discrete(name="Parasitoids", breaks=c("Complex","Simple","Larval"), labels=c("Egg + Larval","Egg","Larval")) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
+
+# Plot linear trait-fitness relationaships
+plot_foodwebegglarval_linear_coefs <- tidy_foodwebegglarval_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  #geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
+
+# Plot quadratic trait-fitness relationships
+plot_foodwebegglarval_quadratic_coefs <- tidy_foodwebegglarval_alphas %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  #geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
+
+# Plot correlational trait-fitness relationaships
+plot_foodwebegglarval_correlational_coefs <- tidy_foodwebegglarval_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+ # geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
+  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
+
+# Format plots for manuscript
+plot_foodwebegglarval_coefs <- plot_grid(
+  plot_foodwebegglarval_mean_fitness + theme(legend.position = "none"),
+  plot_foodwebegglarval_linear_coefs + theme(legend.position = "none"),
+  plot_foodwebegglarval_quadratic_coefs + theme(legend.position = "none"),
+  plot_foodwebegglarval_correlational_coefs + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "")
+
+figure_foodwebegglarval_coefs <- plot_foodwebegglarval_coefs 
+figure_foodwebegglarval_coefs
+```
+
+# Estimating selection on the egg parasitoid *Platygaster*
+
 ```{r Egg vs. egg ptoid model, cache=TRUE}
@@
 
-# convert "gall_survival" to egg parasitoid survival. Note that both Iteomyia pupa and larva parasitoids result in 0.
+# convert "gall_survival" to egg parasitoid survival.
+Note that both Iteomyia pupa and larva parasitoids result in 0.
+We do not change the name of the response variable to make clear that we are using the same statistical models as for Iteomyia.
 eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg_parasitoid==1,1,0))
@@
 
-Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
-For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
-
 ```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
@@
 
+```{r Linear egg vs. egg ptoid model, cache=TRUE}
+linear_eggegg_model <- update(linear_foodweb_model, data=eggegg_df)
+```
+
+```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
+boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
 ```{r Egg vs. egg ptoid alpha coefficients, include=FALSE}
+eggegg_bind <- bind_cols(
+  as_tibble(boot_linear_eggegg_model$t),
+  select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
 
@@
   mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])#,
-         #`FoodwebComplex:I(sc.Diam^2)` = `FoodwebComplex:I(sc.Diam^2)` - fixef(biased_eggegg_model)["FoodwebComplex:I(sc.Diam^2)"],
-         #`FoodwebSimple:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - fixef(biased_eggegg_model)["FoodwebSimple:I(sc.Diam^2)"],
-         #`FoodwebComplex:sc.Diam:sc.log.Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam:sc.log.Clutch"],
-         #`FoodwebSimple:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam:sc.log.Clutch"],
-         #`FoodwebComplex:sc.Diam:sc.sqrt.Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam:sc.sqrt.Pref"],
-         #`FoodwebSimple:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam:sc.sqrt.Pref"])
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])
 
@@
 eggegg_alphas <- eggegg_adj_Diam %>%
-  rename(`FoodwebSimple:(Intercept)`=FoodwebSimple, `FoodwebComplex:(Intercept)`=FoodwebComplex) %>%
+  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
   mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
@@
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+
+knitr::kable(tidy_eggegg_alphas)
 ```
@@
   ggplot(., aes(x=type)) +
-  geom_linerange(aes(ymax=inverse_logit(conf.high), ymin=inverse_logit(conf.low), color=type), position=dodge_width) +
-  geom_point(aes(y=inverse_logit(mean), fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
   geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
@@
          conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+
+knitr::kable(tidy_eggegg_grads)
 ```
@@
 
-To determine whether I should adjust any coefficients associated with chamber diameter, e.g.
+```{r simulate bias in chamber diameter, include=FALSE, eval=FALSE}
+
+# To determine whether I should adjust any coefficients associated with chamber diameter, e.g.
 quadratic and correlation terms, I conducted a quick simulation.
@@
 I assumed a constant value of parasitism effect on gall size.
-```{r simulate bias in chamber diameter}
+
 n <- 10000
 diam <- rnorm(n, mean=0, sd=1) # simulate 1,000 chamber diameters from a normal distribution with mean=0 and sd=1
-pref <- rnorm(n, mean=0, sd=1)               # simulate 1,000 female preferences from a normal distribution with mean=0 and sd=1
+pref <- rnorm(n, mean=0, sd=1)               # simulate 1,000 Oviposition preferences from a normal distribution with mean=0 and sd=1
 bias.adj <- 0.34                  # this value corresponds to actual estimates from my bias analyses.
@@
 
+# Reproduce Figure 4 - Univariate adaptive landscape
+
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE}
+newdata_Diam <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
+
+RF_Diam <- bootstrap_fitness(
+  logistic_model = foodweb_model, 
+  newdata = newdata_Diam,
+  bootstraps=n_boots_plots)
+
+egglarval_RF_Diam <- bootstrap_fitness(
+  logistic_model = egglarval_model,
+  newdata = newdata_Diam,
+  bootstraps=n_boots_plots)
+```
+
+```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE}
+newdata_Clutch <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
+
+RF_Clutch <- bootstrap_fitness(
+  logistic_model = foodweb_model,
+  newdata = newdata_Clutch,
+  bootstraps=n_boots_plots)
+
+egglarval_RF_Clutch <- bootstrap_fitness(
+  logistic_model = egglarval_model,
+  newdata = newdata_Clutch,
+  bootstraps=n_boots_plots)
+```
+
+```{r Get Oviposition preference Fitness Landscape, cache=TRUE, include=FALSE}
+
+newdata_Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+
+RF_Pref <- bootstrap_fitness(
+  logistic_model = foodweb_model, 
+  newdata = newdata_Pref,
+  bootstraps=n_boots_plots)
+
+egglarval_RF_Pref <- bootstrap_fitness(
+  logistic_model = egglarval_model, 
+  newdata = newdata_Pref,
+  bootstraps=n_boots_plots)
+
+eggegg_RF_Pref <- bootstrap_fitness(
+  logistic_model = eggegg_model, 
+  newdata = newdata_Pref,
+  bootstraps=n_boots_plots)
+
+linear_eggegg_RF_Pref <- bootstrap_fitness(
+  logistic_model = linear_eggegg_model, 
+  newdata = newdata_Pref,
+  bootstraps=n_boots_plots) 
+```
+
+```{r Plot Univariate Landscapes, include=FALSE}
+uni_breaks <- c(0.1,0.5,1.0)
+
+# Gall size 
+AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
+  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
+  coord_cartesian(ylim=c(0.07,1))
+
+# Oviposition preference
+AF_uni_Pref <- RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Oviposition preference (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+
+AF_uni_egglarval_Pref <- egglarval_RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Oviposition preference (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+
+# Clutch size -- food web
+AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% 
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = treatment_colors, name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+
+# Clutch size -- egg vs. larval ptoids
+AF_uni_egglarval_Clutch <- egglarval_RF_Clutch$absolute_fitness %>% 
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = factor(ifelse(Foodweb=="Complex","Larval","Simple"), levels=c("Simple","Larval"))) %>%
+  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = cbPalette[c(5,4)], name = "Food web") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))
+
+plot_foodweb_Clutch_df <- RF_Clutch$absolute_fitness %>% 
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"), facet="a")
+
+plot_egglarval_Clutch_df <- egglarval_RF_Clutch$absolute_fitness %>% 
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+  filter(ID_group=="average") %>%
+  bind_rows(., filter(plot_foodweb_Clutch_df, ID_group=="average", Foodweb=="Complex")) %>%
+  mutate(facet = "b")
+
+legend_only <- bind_rows(plot_foodweb_Clutch_df, plot_egglarval_Clutch_df) %>%
+  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)  ","Egg (Simple)  ","Larval"))) %>%
+  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1))+
+  facet_wrap(~facet) +
+  theme(strip.background=element_blank(), strip.text = element_blank()) +
+  guides(color=guide_legend(title.position="top"))
+
+## Female pref
+plot_foodweb_Pref_df <- RF_Pref$absolute_fitness %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"), facet="a")
+
+plot_egglarval_Pref_df <- egglarval_RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+  filter(ID_group=="average")  %>%
+  bind_rows(., filter(plot_foodweb_Pref_df, ID_group=="average", Foodweb=="Complex")) %>%
+  mutate(facet = "b")
+
+pref_legend_only <- bind_rows(plot_foodweb_Pref_df, plot_egglarval_Pref_df) %>%
+  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Oviposition preference (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1)) +
+  theme(legend.title.align = 0.5) +
+  facet_wrap(~facet) +
+  theme(strip.background=element_blank(), strip.text = element_blank())
+
+# Chamber diameter
+plot_foodweb_Diam_df <- RF_Diam$absolute_fitness %>% 
+  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"), facet="a")
+
+plot_egglarval_Diam_df <- egglarval_RF_Diam$absolute_fitness %>% 
+  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+  filter(ID_group=="average") %>%
+  bind_rows(., filter(plot_foodweb_Diam_df, ID_group=="average", Foodweb=="Complex")) %>%
+  mutate(facet = "b")
+
+Diam_legend_only <- bind_rows(plot_foodweb_Diam_df, plot_egglarval_Diam_df) %>%
+  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Mean larval survival") +
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
+  coord_cartesian(ylim=c(0.07,1)) +
+  theme(legend.title.align = 0.5) +
+  facet_wrap(~facet) +
+  theme(strip.background=element_blank(), strip.text = element_blank())
+```
+
+```{r Univariate-Fitness-Landscapes, echo=FALSE, eval=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and Oviposition preference (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
+Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples.", eval=FALSE}
+
+# Get legend
+AF_uni_legend <- get_legend(legend_only + theme(legend.title.align = 0.5)) #get_legend(AF_uni_Diam)
+
+# Make plots
+AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none", 
+                                              axis.text.x = element_text(size=10),
+                                              axis.title.x = element_text(size=11)), 
+                       AF_uni_Pref + theme(legend.position = "none", 
+                                           axis.title.y = element_blank(),
+                                           axis.text.x = element_text(size=10),
+                                           axis.title.x = element_text(size=11)),
+                      AF_uni_Clutch + theme(legend.position = "none",
+                                             axis.title.y = element_blank(), 
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                     legend_only + theme(legend.position = "none",                          
+                                             axis.title.y = element_blank(), 
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                       labels = "AUTO", ncol = 2, align='hv')
+
+AF_gradients <- plot_grid(AF_uni_legend, AF_uni_plots, nrow = 2, rel_heights = c(0.2,0.8)) 
+AF_gradients
+```
+
+```{r Figure-Univariate-Landscapes, echo=FALSE}
+# Get legend
+AF_uni_legend <- get_legend(legend_only + theme(legend.position="top", legend.title.align = 0.5) + guides(color=guide_legend(title.position="top")))
+
+# Make plots
+AF_uni_plots <- plot_grid(NULL,
+                          Diam_legend_only + theme(legend.position = "none",                         
+                                             axis.title.y = element_blank(),
+                                             axis.text.x = element_blank()),
+                     pref_legend_only + theme(legend.position = "none",                          
+                                             axis.title.y = element_blank(),
+                                             axis.text.x = element_blank()) + xlab("Preference (SDs)"),
+                     legend_only + theme(legend.position = "none",                         
+                                             axis.title.y = element_blank()),
+                       labels = c("","A", "B", "C"), hjust=0.06, vjust=0.1, 
+                     ncol = 1, nrow=4, align='hv', rel_heights = c(0.5,1,1,1))
+
+AF_uni_legend_plots <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x=0.15,y=0.4)
+y_title_AF_uni_plots <- ggdraw() + draw_label("Mean larval survival", angle = 90, size=16)
+
+AF_gradients <- plot_grid(y_title_AF_uni_plots, AF_uni_legend_plots, ncol=2, rel_widths = c(0.1,1))
+AF_gradients
+save_plot(filename = "UV_landscapes.pdf", plot = AF_gradients, base_height = 9, base_width = 7)
+```
+
+```{r Alt Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE}
+# Get legend
+AF_uni_legend <- get_legend(legend_only + theme(legend.title.align = 0.5))
+
+# Make plots
+AF_uni_plots <- plot_grid(NULL,
+                          Diam_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                                             axis.title.y = element_blank()), 
+                                             #axis.text.y = element_blank(),
+                                             #axis.text.x = element_text(size=10),
+                                             #axis.title.x = element_text(size=11)),
+                     pref_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                                             axis.title.y = element_blank()), 
+                                             #axis.text.y = element_blank(),
+                                             #axis.text.x = element_text(size=10),
+                                             #axis.title.x = element_text(size=11)),
+                     legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                                             axis.title.y = element_blank()), 
+                                             #axis.text.y = element_blank(),
+                                             #axis.text.x = element_text(size=10),
+                                             #axis.title.x = element_text(size=11)),
+                     #  labels = "AUTO", 
+                     ncol = 2, align='hv')
+
+AF_uni_legend_plots <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x=0.1, y=0.25) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
+y_title_AF_uni_plots <- ggdraw() + draw_label("Mean larval survival", angle = 90)
+AF_gradients <- plot_grid(y_title_AF_uni_plots, AF_uni_legend_plots, ncol=2, rel_widths = c(0.05,1))
+AF_gradients
+#AF_gradients <- plot_grid(AF_uni_legend, AF_uni_plots,  nrow = 2, rel_heights = c(0.1,1)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
+#AF_gradients
+
+```
+
+```{r Egg-Parasitoid-Selection, echo=F}
+eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  spread(Foodweb, absolute_fitness) %>%
+  mutate(fitness_difference = Complex-Simple)
+
+eggptoid_selection_plot <- eggptoid_plot_df %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
+  geom_line(color=cbPalette[5]) +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall midge preference (SDs)") + 
+  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  geom_hline(yintercept=0, linetype="dotted")
+
+eggptoid_selection_plot
+save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 6)
+```
+
+```{r Egg-Parasitoid-Selection-linear, echo=F}
+linear_eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  spread(Foodweb, absolute_fitness) %>%
+  #filter(ID_group=="average") %>%
+  mutate(fitness_difference = Complex-Simple)
+
+linear_eggptoid_selection_plot <- eggptoid_plot_df %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
+  geom_line(color=cbPalette[5]) +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall midge preference (SDs)") + 
+  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  geom_hline(yintercept=0, linetype="dotted") #+
+
+linear_eggptoid_selection_plot
+save_plot(filename = "linear_selection_on_Platygaster.pdf", plot = linear_eggptoid_selection_plot, base_height = 6)
+```
+
+```{r Plot Univariate RF Landscapes, include=FALSE}
+
+RF_plot_foodweb_Clutch_df <- RF_Clutch$absolute_fitness %>% 
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  filter(ID_group == "average") %>%
+  group_by(Foodweb) %>%
+  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness)) %>%
+  ungroup()
+
+RF_plot_egglarval_Clutch_df <- egglarval_RF_Clutch$absolute_fitness %>% 
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+  filter(Foodweb=="Larval", ID_group=="average") %>%
+  group_by(Foodweb) %>%
+  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+  ungroup()
+
+RF_legend_only <- bind_rows(RF_plot_foodweb_Clutch_df, RF_plot_egglarval_Clutch_df) %>%
+  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+  filter(ID_group=="average") %>%
+  ggplot(., aes(x=sc.log.Clutch, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Clutch size (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  coord_cartesian(ylim=c(0.2,2)) +
+  geom_hline(yintercept=1, linetype="dotted")
+
+## Female pref
+
+RF_plot_foodweb_Pref_df <- RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  filter(ID_group == "average") %>%
+  group_by(Foodweb) %>%
+  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+  ungroup()
+
+RF_plot_egglarval_Pref_df <- egglarval_RF_Pref$absolute_fitness %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+  filter(Foodweb=="Larval", ID_group=="average") %>%
+  group_by(Foodweb) %>%
+  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+  ungroup()
+
+RF_pref_legend_only <- bind_rows(RF_plot_foodweb_Pref_df, RF_plot_egglarval_Pref_df) %>%
+  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+  filter(ID_group=="average") %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Oviposition preference (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  coord_cartesian(ylim=c(0.2,2)) +
+  theme(legend.title.align = 0.5) +
+  geom_hline(yintercept=1, linetype="dotted")
+
+# Chamber diameter
+RF_plot_foodweb_Diam_df <- RF_Diam$absolute_fitness %>% 
+  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  filter(ID_group == "average") %>%
+  group_by(Foodweb) %>%
+  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+  ungroup()
+
+RF_plot_egglarval_Diam_df <- egglarval_RF_Diam$absolute_fitness %>% 
+  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+  filter(Foodweb=="Larval", ID_group=="average") %>%
+  group_by(Foodweb) %>%
+  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+  ungroup()
+
+RF_Diam_legend_only <- bind_rows(RF_plot_foodweb_Diam_df, RF_plot_egglarval_Diam_df) %>%
+  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+  filter(ID_group=="average") %>%
+  ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  geom_line() +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Relative fitness") +
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + # "Food web"
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  coord_cartesian(ylim=c(0.2,2)) +
+  theme(legend.title.align = 0.5) +
+  geom_hline(yintercept=1, linetype="dotted")
+
+# Get legend
+RF_uni_legend <- get_legend(RF_legend_only) #  + theme(legend.position = "top")
+
+# Make plots
+RF_uni_plots <- plot_grid(RF_Diam_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                                             #axis.title.y = element_blank(), 
+                                             #axis.text.y = element_blank(),
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                     RF_pref_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                                             axis.title.y = element_blank(), 
+                                             #axis.text.y = element_blank(),
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                     RF_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                                             axis.title.y = element_blank(), 
+                                             #axis.text.y = element_blank(),
+                                             axis.text.x = element_text(size=10),
+                                             axis.title.x = element_text(size=11)),
+                     #  labels = "AUTO", 
+                     ncol = 3, align='hv')
+
+RF_gradients <- plot_grid(RF_uni_plots, RF_uni_legend, ncol = 2, rel_widths = c(0.8,0.2)) 
+RF_gradients
+```
+
+# Multivariate fitness landscapes
+
+```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE, include=FALSE}
+
+newdata_Clutch.Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+
+RF_Clutch.Pref <- bootstrap_fitness(
+  logistic_model = foodweb_model, 
+  newdata = newdata_Clutch.Pref,
+  bootstraps=NULL)
+
+```
+
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam.Clutch <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
+
+RF_Diam.Clutch <- bootstrap_fitness(
+  logistic_model = foodweb_model, 
+  newdata = newdata_Diam.Clutch,
+  bootstraps=NULL)
+
+```
+
+```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE, include=FALSE}
+
+newdata_Diam.Pref <- bind_rows(
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+
+RF_Diam.Pref <- bootstrap_fitness(
+  logistic_model = foodweb_model, 
+  newdata = newdata_Diam.Pref,
+  bootstraps=NULL)
+
+```
+
+```{r Get plots of multivariate adaptive landscape, include=FALSE}
+
+# Plot helpers
+AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+my_breaks <- c(0.2,0.4,0.6,0.8)
+
+# Size x Clutch
+AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
+  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
+  geom_raster(aes(fill=average)) +
+  facet_wrap(~Foodweb) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
+
+# Size x Preference
+AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
+  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
+  geom_raster(aes(fill=average)) +
+  facet_wrap(~Foodweb) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Oviposition preference (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
+
+# Clutch x Preference
+AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
+  geom_raster(aes(fill=average)) +
+  facet_wrap(~Foodweb) +
+  xlab("Oviposition preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))
+
+```
+
+Reproduce Figure 5 in main manuscript.
+
+```{r Figure-Multivariate-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and Oviposition preference (B); Oviposition preference and gall diameter (C).
+Note that traits for all plots range 1 SD below and above the mean (=0)."}
+
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_Diam.Pref + theme(legend.text = element_text(size=10)))
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_Diam.Clutch + theme(legend.position = "none", 
+                              axis.title.x = element_blank(),
+                             axis.text.x = element_blank()),
+  AF_plot_Clutch.Pref + theme(legend.position = "none", 
+                              axis.title.y = element_blank(),
+                              axis.text.y = element_blank()) + xlab("Preference (SDs)"), 
+  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)"), 
+  nrow=2, align="hv", labels = "AUTO")
+
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+save_plot(filename = "MV_landscapes.pdf", plot = AF_landscape_2d, base_width=8, base_height = 6)
+```
+
+<!--
 # Effect of Food-Web Treatment on Larval Survival
@@
 
-```{r Model 1, cache=TRUE}
+```{r Model 1, cache=TRUE, eval=FALSE, include=FALSE}
 model_1 <- glmer(
@@
 Foodweb:trait~i~^2^ or Foodweb:trait~i~:trait~j~).
-Food-web treatment does influence the quadratic effect of of female preference on larva survival.
+Food-web treatment does influence the quadratic effect of of Oviposition preference on larval survival.
 None of the other terms statistically differ from zero.
 
-```{r Bootstrap Model 1, cache=TRUE, include=FALSE}
+```{r Bootstrap Model 1, cache=TRUE, include=FALSE, eval=FALSE}
 boot_model_1 <- bootMer(model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE}
+```{r Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE, eval=FALSE, include=FALSE}
 plot_model_1 <- tidy_model_1 %>%
@@
 
-```{r Model 2, cache=TRUE}
+```{r Model 2, cache=TRUE, eval=FALSE, include=FALSE}
 
@@
 
-```{r Bootstrap Model 2, cache=TRUE, include=FALSE}
+```{r Bootstrap Model 2, cache=TRUE, include=FALSE, eval=FALSE, include=FALSE}
 
@@
 
-```{r Plot Nonlinear Terms, echo=FALSE}
+```{r Plot Nonlinear Terms, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_model_2$term_plot <- factor(tidy_model_2$term,
@@
 
-Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.sqrt.Pref^2)* indicates that food-web treatment alters quadractic selection on female preference; however, this coefficient is not useful for actually calculating the selection gradient.
+Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.sqrt.Pref^2)* indicates that food-web treatment alters quadractic selection on Oviposition preference; however, this coefficient is not useful for actually calculating the selection gradient.
 To do this, we refit a model so rather than estimating the change in slope (currently), it will actually estimate the slope.
 See [Schielzeth 2010](https://doi.org/10.1111/j.2041-210X.2010.00012.x) for a detailed explanation of this approach.
-```{r Adjust Model 2 for Slopes, eval=FALSE}
+```{r Adjust Model 2 for Slopes, eval=FALSE, include=FALSE}
 model_2_adj <- update(model_2, .~. -I(sc.sqrt.Pref^2))
@@
 
-```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE, eval=FALSE}
+```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE, eval=FALSE, include=FALSE}
 boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE, eval=FALSE}
+```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_model_2_adj$term_plot <- factor(tidy_model_2_adj$term,
@@
 
-```{r Fit Model 3, cache=TRUE}
+```{r Fit Model 3, cache=TRUE, eval=FALSE, include=FALSE}
 model_3 <- update(model_2, 
@@
 
-We then use parametric bootstrapping to test whether food-web treatment alters the linear relationship between each trait and larva survival.
-
-```{r Bootstrap Model 3, cache=TRUE, include=FALSE}
+We then use parametric bootstrapping to test whether food-web treatment alters the linear relationship between each trait and larval survival.
+
+```{r Bootstrap Model 3, cache=TRUE, include=FALSE, eval=FALSE}
 boot_model_3 <- bootMer(model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-Note that there was no effect of food-web structure on on chamber diameter (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.Diam")$conf.high,2)`) or female preference (coef=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$statistic,2)`, 95%CI=`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$conf.low,2)`,`r round(filter(tidy_model_3, term=="FoodwebSimple:sc.sqrt.Pref")$conf.high,2)`).
-
-```{r Plot Model 3, echo=FALSE}
+```{r Plot Model 3, echo=FALSE, eval=FALSE, include=FALSE}
 plot_model_3 <- tidy_model_3 %>%
@@
 
-There is clear evidence that food-web treatment alters the linear effect of clutch size on larva survival, but it has no effect on chamber diameter or female preference.
+There is clear evidence that food-web treatment alters the linear effect of clutch size on larval survival, but it has no effect on chamber diameter or Oviposition preference.
 Therefore, we fit a reduced model that removes these non-significant effects:
 
-```{r Fit Model 4, cache=TRUE}
+```{r Fit Model 4, cache=TRUE, eval=FALSE, include=FALSE}
 model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.sqrt.Pref)
@@
 
-```{r Bootstrap Model 4, cache=TRUE, include=FALSE}
+```{r Bootstrap Model 4, cache=TRUE, include=FALSE, eval=FALSE, include=FALSE}
 boot_model_4 <- bootMer(model_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Plot Model 4, echo=FALSE}
+```{r Plot Model 4, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_model_4$term_plot <- factor(tidy_model_4$term, 
@@
 As we did with model 2, we refit the model by removing the slope term so that we can fit different slopes for each interaction term. 
-```{r Fit Model 4 adjusted for estimating clutch slopes, cache=TRUE}
+```{r Fit Model 4 adjusted for estimating clutch slopes, cache=TRUE, eval=FALSE, include=FALSE}
 model_4_adj <- update(model_4, .~. -sc.log.Clutch)
@@
 
-```{r Bootstrap adjusted model 4, cache=TRUE, include=FALSE}
+```{r Bootstrap adjusted model 4, cache=TRUE, include=FALSE, eval=FALSE}
 boot_model_4_adj <- bootMer(model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Plot adjusted model 4, echo=FALSE}
+```{r Plot adjusted model 4, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_model_4_adj$term_plot <- factor(tidy_model_4_adj$term, 
@@
 
-```{r Average larval survival, cache=TRUE}
+```{r Average larval survival, cache=TRUE, eval=FALSE, include=FALSE}
 model_4_survival_ests <- update(model_4_adj, .~. -1)
@@
 ```
-
-Mean larval survival in complex food web = `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$statistic),2)` [`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$conf.low),2)`,`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$conf.high),2)`].
-
-Mean larval survival in simple food web = `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$statistic),2)` [`r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$conf.low),2)`, `r round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$conf.high),2)`].
 
@@
 We then divided this value by the mean absolute fitness ($\bar W$) so our results are in terms of relative fitness ($w$).
-Note that we doubled all quadratic selection gradients ($\gamma_{z_i,z_i}) to put them on the same scale as the directional and correlational selection gradients (detailed explanation in [Stinchcombe et al.
+Note that we doubled all quadratic selection gradients ($\gamma_{z_i,z_i}$) to put them on the same scale as the directional and correlational selection gradients (detailed explanation in [Stinchcombe et al.
 2008](https://doi.org/10.1111/j.1558-5646.2008.00449.x)).
 
-```{r Organize and Transform Coefficients, include=FALSE}
+```{r Organize and Transform Coefficients, include=FALSE, eval=FALSE}
 tidy_coefs <- bind_rows(
@@
 
-```{r Calculate Selection Gradients, include=FALSE}
+```{r Calculate Selection Gradients, include=FALSE, eval=FALSE}
 
@@
 
-```{r Table of Selection Gradients, echo=FALSE}
+```{r Table of Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 selection_gradients$term_ord <- factor(selection_gradients$term, 
@@
 
-```{r Plot of Selection Gradients, echo=FALSE}
+```{r Plot of Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 selection_gradients %>%
@@
 
-## Contributions of larval parasitoids to selection gradients
+Contributions of larval parasitoids to selection gradients
 
@@
 
-```{r Egg vs. Larval Parasitoids Model, cache=TRUE}
+```{r Egg vs. Larval Parasitoids Model, cache=TRUE, eval=FALSE, include=FALSE}
 
@@
 
-```{r Bootstrap Egg vs. Larval Parasitoid Model 2, cache=TRUE, include=FALSE}
+```{r Bootstrap Egg vs. Larval Parasitoid Model 2, cache=TRUE, include=FALSE, eval=FALSE}
 
@@
 
-```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE}
+```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_egg.larval_model_2$term_plot <- factor(tidy_egg.larval_model_2$term,
@@
  To put all of the coefficients on the same scale, we refit it as we did in the food-web treatment
-```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE, eval=FALSE}
+```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE, eval=FALSE, include=FALSE}
 egg.larval_model_2_adj <- update(model_2_adj, data=egg.vs.larval_df)
@@
 
-```{r Plot effect of Egg vs. Larval Parasitoid adjusted Model 2, echo=FALSE, eval=FALSE}
+```{r Plot effect of Egg vs. Larval Parasitoid adjusted Model 2, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_egg.larval_model_2_adj$term_plot <- factor(tidy_egg.larval_model_2_adj$term,
@@
 
-```{r Fit Egg vs. Larval Parasitoid Model 4, cache=TRUE}
+```{r Fit Egg vs. Larval Parasitoid Model 4, cache=TRUE, eval=FALSE, include=FALSE}
 egg.larval_model_4 <- update(model_4, data=egg.vs.larval_df)
@@
 
-```{r Bootstrap Egg vs. Larval Parasitoid Model 4, cache=TRUE, include=FALSE}
+```{r Bootstrap Egg vs. Larval Parasitoid Model 4, cache=TRUE, include=FALSE, eval=FALSE}
 boot_egg.larval_model_4 <- bootMer(egg.larval_model_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. Larval Parasitoid Model 4, echo=FALSE}
+```{r Plot Egg vs. Larval Parasitoid Model 4, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_egg.larval_model_4$term_ord <- factor(tidy_egg.larval_model_4$term, 
@@
 
-```{r Fit Egg vs. Larval Parasitoid adjusted Model 4, cache=TRUE}
+```{r Fit Egg vs. Larval Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE, include=FALSE}
 egg.larval_model_4_adj <- update(model_4_adj, data=egg.vs.larval_df)
@@
 
-```{r Bootstrap Egg vs. Larval Parasitoid adjuted Model 4, cache=TRUE, include=FALSE}
+```{r Bootstrap Egg vs. Larval Parasitoid adjuted Model 4, cache=TRUE, include=FALSE, eval=FALSE}
 boot_egg.larval_model_4_adj <- bootMer(egg.larval_model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. Larval Parasitoid adjusted Model 4, echo=FALSE}
+```{r Plot Egg vs. Larval Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_egg.larval_model_4_adj$term_ord <- factor(tidy_egg.larval_model_4_adj$term, 
@@
 
-## CALCULATE SELECTION GRADIENTS FOR EGG VS. LARVAL PARASITOIDS
-
-```{r Organize and Transform egg vs. larval parasitoid Coefficients, include=FALSE}
+# CALCULATE SELECTION GRADIENTS FOR EGG VS. LARVAL PARASITOIDS
+
+```{r Organize and Transform egg vs. larval parasitoid Coefficients, include=FALSE, eval=FALSE}
 tidy_egg.larval_coefs <- bind_rows(
@@
 
-```{r Calculate Egg vs. larval parasitoid Selection Gradients, include=FALSE}
+```{r Calculate Egg vs. larval parasitoid Selection Gradients, include=FALSE, eval=FALSE}
 
@@
 
-```{r Table of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE}
+```{r Table of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
@@
 
-```{r Plot of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE}
+```{r Plot of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 egg.larval_selection_gradients %>%
@@
 
-```{r New approach for biased selection, include=FALSE}
+```{r New approach for biased selection, include=FALSE, eval=FALSE}
 biased_df <- gall_selection.df %>%
@@
 
-```{r Redo selection gradients, include=FALSE}
+```{r Redo selection gradients, include=FALSE, eval=FALSE}
 bias.adj_selection_gradients <- mutate(selection_gradients, adjusted = "No") %>%
@@
 
-```{r Bias in gradients on chamber diameter}
+```{r Bias in gradients on chamber diameter, eval=FALSE, include=FALSE}
 fixef(biased.diam_model_4)["sc.Diam"]
@@
 
-```{r Variance explained in chamber diameter}
+```{r Variance explained in chamber diameter, eval=FALSE, include=FALSE}
 chamber_diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), data=gall_selection.df)
@@
 
-```{r Variance explained in other traits}
+```{r Variance explained in other traits, eval=FALSE, include=FALSE}
 clutch_size <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, Gall_Number, sc.log.Clutch))
@@
 
-```{r female pref plot, echo=F}
+```{r female pref plot, echo=F, eval=FALSE, include=FALSE}
 visreg::visreg(female_pref, xvar="Foodweb")
@@
 
-```{r Plot of bias adjusted Selection Gradients, echo=FALSE}
+```{r Plot of bias adjusted Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 bias.adj_selection_gradients %>%
@@
 
-```{r Prep selection gradients figure, echo=FALSE}
+```{r Prep selection gradients figure, echo=FALSE, eval=FALSE, include=FALSE}
 
@@
 
-```{r Selection-Gradients, echo=FALSE, fig.cap="Selection gradients. Points and lines represents means and 95% confidence intervals (n=1,000 bootstrapped samples)."}
+```{r Selection-Gradients, echo=FALSE, fig.cap="Selection gradients. Points and lines represents means and 95% confidence intervals (n=1,000 bootstrapped samples).", eval=FALSE, include=FALSE}
 
@@
 
-We found no evidence of directional or quadratic selection on either chamber diameter or clutch size; however, we observed positive directional selection on *Iteomyia* female preference as well stabilizing selection on preference.
+We found no evidence of directional or quadratic selection on either chamber diameter or clutch size; however, we observed positive directional selection on *Iteomyia* Oviposition preference as well stabilizing selection on preference.
 
@@
 For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
-```{r Selection on Platygaster Traits, cache=TRUE}
+```{r Selection on Platygaster Traits, cache=TRUE, eval=FALSE, include=FALSE}
 
@@
 
-```{r Levene tests}
+```{r Levene tests, eval=FALSE, include=FALSE}
 platy_Diam_levene
@@
 ```
-```{r}
-car::Anova(platy_Diam, test="F")
-car::Anova(platy_Clutch, test="F")
-car::Anova(platy_Pref, test="F")
-```
-
-```{r Plot models of Platygaster selection differentials, echo=FALSE}
+
+```{r Plot models of Platygaster selection differentials, echo=FALSE, eval=FALSE, include=FALSE}
 visreg_platy_Diam <- visreg(platy_Diam, xvar="Foodweb", gg=TRUE) + ylab("Chamber diameter (SD)") + xlab("")
 visreg_platy_Clutch <- visreg(platy_Clutch, xvar="Foodweb", gg=TRUE) + ylab("Clutch size (SD)") + xlab("")
-visreg_platy_Pref <- visreg(platy_Pref, xvar="Foodweb", gg=TRUE) + ylab("Female preference (SD)") + xlab("")
+visreg_platy_Pref <- visreg(platy_Pref, xvar="Foodweb", gg=TRUE) + ylab("Oviposition preference (SD)") + xlab("")
 
@@
 
-```{r Table of Platygaster selection differentials, echo=FALSE, eval=FALSE}
+```{r Table of Platygaster selection differentials, echo=FALSE, eval=FALSE, include=FALSE}
 platy_selection_differentials <- bind_rows(platy_linear_selection, platy_quadratic_selection)
@@
 knitr::kable(platy_selection_differentials, caption="Table of selection differentials acting on the egg parasitoid Platygaster")
-```
-
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE}
-
-newdata_Diam <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
-
-RF_Diam <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
-  newdata = newdata_Diam,
-  bootstraps=n_boots_plots)
-
-# Control ----
-#RF_control_gall_size <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = seq(-1,1,length.out=1000), 
-#     sc.log.clutch_size = 0,
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-
-# Treatment ----
-#RF_treatment_gall_size <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = seq(-1,1,length.out=1000),
-#     sc.log.clutch_size = 0,
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-```
-
-```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE}
-newdata_Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
-
-RF_Clutch <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
-  newdata = newdata_Clutch,
-  bootstraps=n_boots_plots)
-
-# Control ----
-#RF_control_clutch_size <- bootstrap_fitness(
-#  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000),
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-
-# Treatment ----
-#RF_treatment_clutch_size <- bootstrap_fitness(
-#  logistic_model = model_2, #quad_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000),
-#     sc.log1p.female_preference = 0),
-#  bootstraps=n_boots_plots)
-```
-
-```{r Get Female Preference Fitness Landscape, cache=TRUE, include=FALSE}
-
-newdata_Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
-
-RF_Pref <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
-  newdata = newdata_Pref,
-  bootstraps=n_boots_plots)
-
-# Control ----
-#RF_control_female_preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = 0, 
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=n_boots_plots)
-
-# Treatment ----
-#RF_treatment_female_preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #quad_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2)",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = 0,
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=n_boots_plots)
-
-```
-
-```{r Get Clutch Size x Female Preference Landscape, cache=TRUE, include=FALSE}
-
-newdata_Clutch.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
-
-RF_Clutch.Pref <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
-  newdata = newdata_Clutch.Pref,
-  bootstraps=NULL)
-
-# Control ----
-#RF_control_clutch.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000), 
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=NULL)
-
-# Treatment ----
-#RF_treatment_clutch.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-#  newdata = expand.grid(
-#     sc.gall_size = 0,
-#     sc.log.clutch_size = seq(-1,1,length.out=1000),
-#     sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-#  bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, include=FALSE}
-
-newdata_Diam.Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
-
-RF_Diam.Clutch <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
-  newdata = newdata_Diam.Clutch,
-  bootstraps=NULL)
-
-# Control ----
-#RF_control_size.x.clutch <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
- # newdata = expand.grid(
-  #   sc.gall_size = seq(-1,1,length.out=1000),
-   #  sc.log.clutch_size = seq(-1,1,length.out=1000), 
-    # sc.log1p.female_preference = 0), 
-  #bootstraps=NULL)
-
-# Treatment ----
-#RF_treatment_size.x.clutch <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
- # newdata = expand.grid(
-  #   sc.gall_size = seq(-1,1,length.out=1000),
-   #  sc.log.clutch_size = seq(-1,1,length.out=1000),
-    # sc.log1p.female_preference = 0), 
-  #bootstraps=NULL)
-```
-
-```{r Get Gall Diameter x Female Preference Landscape, cache=TRUE, include=FALSE}
-
-newdata_Diam.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
-
-RF_Diam.Pref <- bootstrap_fitness(
-  logistic_model = model_2, #quad_control, 
-  #fixed_effects = "~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)",
-  newdata = newdata_Diam.Pref,
-  bootstraps=NULL)
-
-# Control ----
-#RF_control_size.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_control, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
-#  newdata = expand.grid(
- #    sc.gall_size = seq(-1,1,length.out=1000),
-  #   sc.log.clutch_size = 0, 
-   #  sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  ##bootstraps=NULL)
-
-# Treatment ----
-#RF_treatment_size.x.preference <- bootstrap_fitness(
-#  logistic_model = focus_nonlinear_foodweb_glmer, #corr_treatment, 
-  #fixed_effects = "~ sc.gall_size + sc.log.clutch_size + sc.log1p.female_preference + I(sc.gall_size^2) + I(sc.log.clutch_size^2) + I(sc.log1p.female_preference^2) + sc.gall_size:sc.log.clutch_size + sc.gall_size:sc.log1p.female_preference + sc.log.clutch_size:sc.log1p.female_preference",
- # newdata = expand.grid(
-  #   sc.gall_size = seq(-1,1,length.out=1000),
-   #  sc.log.clutch_size = 0,
-    # sc.log1p.female_preference = seq(-1,1,length.out=1000)), 
-  #bootstraps=NULL)
-```
-
-```{r Fitness Landscape Plot Helpers, include=FALSE}
-
-## Scale relative fitness across plots ----
-
-# 1D
-#RF_gradient_range <- bind_rows(RF_treatment_gall_size$relative_fitness, RF_control_gall_size$relative_fitness,
-#          RF_treatment_clutch_size$relative_fitness, RF_control_clutch_size$relative_fitness,
-#          RF_treatment_female_preference$relative_fitness, RF_control_female_preference$relative_fitness) %>%
-#  select(-sc.log.clutch_size, -sc.log1p.female_preference) %>%
-#  gather(ID, relative_fitness, -sc.gall_size) %>%
-#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-#  summarise(min = min(relative_fitness), max = max(relative_fitness))
-#RF_gradient_scale <- c(0,0.5,1,1.5,2) #,2.5) # adjusted based on range
-
-# 2D
-#RF_range <- bind_rows(RF_treatment_clutch.x.preference$relative_fitness, RF_control_clutch.x.preference$relative_fitness,
-#          RF_treatment_size.x.clutch$relative_fitness, RF_control_size.x.clutch$relative_fitness,
-#          RF_treatment_size.x.preference$relative_fitness, RF_control_size.x.preference$relative_fitness) %>%
-#  summarise(min = min(average), max = max(average))
-
-## Scale absolute fitness across plots ----
-
-# 1D
-AF_gradient_scale <- c(0,0.25,0.5,0.75,1) # adjusted based on range
-
-# 2D
-AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
-  summarise(min = min(average), max = max(average))
-```
-
-```{r Plot Univariate Landscapes, include=FALSE}
-uni_breaks <- c(0.1,0.5,1.0)
-
-# Gall size 
-AF_uni_Diam <- RF_Diam$absolute_fitness %>% #bind_rows(mutate(RF_treatment_gall_size$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_gall_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Chamber diameter (SDs)") +
-  ylab("Mean larva survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
-  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
-#AF_uni_size
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Clutch size
-AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% #bind_rows(mutate(RF_treatment_clutch_size$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_clutch_size$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Mean larva survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-
-# Female preference
-AF_uni_Pref <- RF_Pref$absolute_fitness %>% #bind_rows(mutate(RF_treatment_female_preference$absolute_fitness, Food_Web = "Simple"), 
-          #mutate(RF_control_female_preference$absolute_fitness, Food_Web = "Complex")) %>%
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Female preference (SDs)") +
-  ylab("Mean larva survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.05,1)) # c(0.07,1)
-  #scale_y_continuous(breaks = AF_gradient_scale, limits = c(min(AF_gradient_scale), max(AF_gradient_scale)), trans = "log")
-```
-
-```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and female preference (C).
-Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
-Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
-
-# Get legend
-AF_uni_legend <- get_legend(AF_uni_Diam)
-
-# Make plots
-AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none", 
-                                              axis.text.x = element_text(size=10),
-                                              axis.title.x = element_text(size=11)), 
-                       AF_uni_Clutch + theme(legend.position = "none",
-                                             axis.title.y = element_blank(), 
-                                             #axis.text.y = element_blank(),
-                                             axis.text.x = element_text(size=10),
-                                             axis.title.x = element_text(size=11)),
-                       AF_uni_Pref + theme(legend.position = "none", 
-                                           axis.title.y = element_blank(), 
-                                           #axis.text.y = element_blank(), 
-                                           axis.text.x = element_text(size=10),
-                                           axis.title.x = element_text(size=11)),
-                       labels = "AUTO", ncol = 3, align='hv')
-
-AF_gradients <- plot_grid(AF_uni_plots, AF_uni_legend, ncol = 2, rel_widths = c(1,0.2)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
-AF_gradients
-#AF_uni_plots
-# save_plot("FL_1D.pdf", AF_uni_plots, base_height = 6.5, base_width = 8)
-#save_plot("../figures/fitness_landscapes_1D.png", AF_gradients)#, base_height=6, base_width = 8)
-```
-
-```{r Plot Multivariate Fitness Landscape, include=FALSE}
-
-my_breaks <- c(0.2,0.4,0.6,0.8)
-
-# Size x Clutch
-AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
-  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
-  geom_raster(aes(fill=average)) +
-  facet_wrap(~Foodweb) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
-
-# Size x Preference
-AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
-  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
-  geom_raster(aes(fill=average)) +
-  facet_wrap(~Foodweb) +
-  xlab("Chamber diameter (SDs)") +
-  ylab("Female preference (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
-
-# Clutch x Preference
-AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
-  geom_raster(aes(fill=average)) +
-  facet_wrap(~Foodweb) +
-  xlab("Female preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larva\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) 
-```
-
-```{r Multivariate-Fitness-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and female preference (B); female preference and gall diameter (C).
-Note that traits for all plots range 1 SD below and above the mean (=0)."}
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_Diam.Pref)
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_Diam.Clutch + theme(legend.position = "none", 
-                              axis.title.y = element_text(size=11),
-                              axis.title.x = element_blank(),
-                              axis.text = element_text(size=10)),
-  AF_plot_Clutch.Pref + theme(legend.position = "none", 
-                              axis.title.y = element_blank(), 
-                              axis.text = element_text(size=10), 
-                              axis.title.x = element_text(size=11)),
-  AF_plot_Diam.Pref + theme(legend.position = "none", 
-                            axis.text = element_text(size=10),
-                            axis.title = element_text(size=11)), 
-  nrow=2, align="hv", labels = "AUTO")
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-#save_plot("AF_landscapes_2d.png", AF_landscape_2d, base_height=6, base_width = 8)
-#save_plot("../figures/fitness_landscapes_2D.png", AF_landscape_2d)#, base_height=6, base_width = 8)
 ```
@@
 For my data, since there is no correlational selection, it doesn't matter if there is genetic covariance between the traits, as this will not effect the change in genetic covariances within a generation (because there is no selection).
-Also, the G_matrix does not qualitatively alter the conclusions that there will be a decrease in additive genetic variance in gall diameter due to the strong directional selection; however, there will be an increase in the additive genetic variance in female preference.
+Also, the G_matrix does not qualitatively alter the conclusions that there will be a decrease in additive genetic variance in gall diameter due to the strong directional selection; however, there will be an increase in the additive genetic variance in Oviposition preference.
 Since this is an experiment, we can assume that the G-matrix is the same between treatments
@@
 
-Create a simple rule. If the confidence interval of the selection gradient overlaps zero, then I set it to zero. Otherwise, I set it to our best estimate of the gradient
+Create a simple rule. If the confidence interval of the selection gradient overlaps zero, then I set it to zero. Otherwise, I set it to our best estimate of the gradient-->
 
@@
 ## Create beta-matrix for complex food-web treatment
-complex_betas_df <- bias.adj_selection_gradients %>%
-  filter(`Food web`=="Complex", term_ord %in% c("Pref","Clutch") | term_ord == "Diam" & adjusted=="Yes") %>% 
-  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
-rownames(complex_betas_df) <- complex_betas_df$term_ord
+complex_betas_df <- tidy_foodweb_grads %>%
+  filter(type=="Complex", gradient_type=="Directional") %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+complex_betas_df$term <- factor(complex_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
+rownames(complex_betas_df) <- complex_betas_df$term
 
@@
 ## Create gamma-matrix for complex food-web treatment
-complex_gammas_df <- bias.adj_selection_gradients %>%
-  filter(`Food web`=="Complex", term_ord %in% c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref")) %>% 
-  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
-rownames(complex_gammas_df) <- complex_gammas_df$term_ord
+complex_gammas_df <- tidy_foodweb_grads %>%
+  filter(type=="Complex", gradient_type %in% c("Quadratic","Correlational")) %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+complex_gammas_df$term <- factor(complex_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+rownames(complex_gammas_df) <- complex_gammas_df$term
 
@@
 ## Create matrix of Betas in simple food-web treatment
-simple_betas_df <- bias.adj_selection_gradients %>%
-  filter(`Food web`=="Simple", term_ord %in% c("Pref","Clutch") | term_ord == "Diam" & adjusted=="Yes") %>% 
-  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
-rownames(simple_betas_df) <- simple_betas_df$term_ord
+simple_betas_df <- tidy_foodweb_grads %>%
+  filter(type=="Simple", gradient_type=="Directional") %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+simple_betas_df$term <- factor(simple_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
+rownames(simple_betas_df) <- simple_betas_df$term
 
@@
 ## Create gamma-matrix for simple food-web treatment
-simple_gammas_df <- bias.adj_selection_gradients %>%
-  filter(`Food web`=="Simple", term_ord %in% c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref")) %>% 
-  select(term_ord, gradient, low=`2.5%`, high=`97.5%`) %>% data.frame()
-rownames(simple_gammas_df) <- simple_gammas_df$term_ord
+simple_gammas_df <- tidy_foodweb_grads %>%
+  filter(type=="Simple", gradient_type %in% c("Quadratic","Correlational")) %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+simple_gammas_df$term <- factor(simple_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+rownames(simple_gammas_df) <- simple_gammas_df$term
 
@@
 ```
-
+<!--
 ## Slope of adaptive landscape
@@
 
-$$\text{Slope}_{complex} = \begin{pmatrix} `r complex_betas["Diam", ]` \\ `r complex_betas["Clutch", ]` \\ `r complex_betas["Pref", ]` \end{pmatrix}$$
-$$\text{Slope}_{simple} =  \begin{pmatrix} `r simple_betas["Diam", ]` \\ `r simple_betas["Clutch", ]` \\ `r simple_betas["Pref", ]` \end{pmatrix}$$
+$$\text{Slope}_{complex} = \begin{pmatrix} `r #complex_betas["Diam", ]` \\ `r #complex_betas["Clutch", ]` \\ `r #complex_betas["Pref", ]` \end{pmatrix}$$
+$$\text{Slope}_{simple} =  \begin{pmatrix} `r #simple_betas["Diam", ]` \\ `r #simple_betas["Clutch", ]` \\ `r #simple_betas["Pref", ]` \end{pmatrix}$$
 
@@
 $$\gamma = \begin{pmatrix} \gamma_{diam} & \gamma_{diam,clutch} & \gamma_{diam,pref} \\ \gamma_{clutch,diam} & \gamma_{clutch} & \gamma_{clutch,pref} \\ \gamma_{pref,diam} & \gamma_{pref,clutch} &\gamma_{pref} \end{pmatrix}$$
-$$\gamma_{complex} = \begin{pmatrix} `r complex_gammas["Diam","Diam"]` & `r complex_gammas["Diam","Clutch"]` & `r complex_gammas["Diam","Pref"]` \\  `r complex_gammas["Clutch","Diam"]` & `r complex_gammas["Clutch","Clutch"]` & `r complex_gammas["Clutch","Pref"]` \\  `r complex_gammas["Pref","Diam"]` & `r complex_gammas["Pref","Clutch"]` & `r complex_gammas["Pref","Pref"]` \end{pmatrix}$$
-$$\gamma_{simple} = \begin{pmatrix} `r simple_gammas["Diam","Diam"]` & `r simple_gammas["Diam","Clutch"]` & `r simple_gammas["Diam","Pref"]` \\  `r simple_gammas["Clutch","Diam"]` & `r simple_gammas["Clutch","Clutch"]` & `r simple_gammas["Clutch","Pref"]` \\  `r simple_gammas["Pref","Diam"]` & `r simple_gammas["Pref","Clutch"]` & `r simple_gammas["Pref","Pref"]` \end{pmatrix}$$
-
-$$\text{Curvature}_{complex} = \begin{pmatrix} `r complex_curvature["Diam","Diam"]` & `r complex_curvature["Diam","Clutch"]` & `r complex_curvature["Diam","Pref"]` \\  `r complex_curvature["Clutch","Diam"]` & `r complex_curvature["Clutch","Clutch"]` & `r complex_curvature["Clutch","Pref"]` \\  `r complex_curvature["Pref","Diam"]` & `r complex_curvature["Pref","Clutch"]` & `r complex_curvature["Pref","Pref"]` \end{pmatrix}$$
-
-$$\text{Curvature}_{simple} = \begin{pmatrix} `r simple_curvature["Diam","Diam"]` & `r simple_curvature["Diam","Clutch"]` & `r simple_curvature["Diam","Pref"]` \\  `r simple_curvature["Clutch","Diam"]` & `r simple_curvature["Clutch","Clutch"]` & `r simple_curvature["Clutch","Pref"]` \\  `r simple_curvature["Pref","Diam"]` & `r simple_curvature["Pref","Clutch"]` & `r simple_curvature["Pref","Pref"]` \end{pmatrix}$$
+$$\gamma_{complex} = \begin{pmatrix} `r #complex_gammas["Diam","Diam"]` & `r #complex_gammas["Diam","Clutch"]` & `r #complex_gammas["Diam","Pref"]` \\  `r #complex_gammas["Clutch","Diam"]` & `r #complex_gammas["Clutch","Clutch"]` & `r #complex_gammas["Clutch","Pref"]` \\  `r #complex_gammas["Pref","Diam"]` & `r #complex_gammas["Pref","Clutch"]` & `r #complex_gammas["Pref","Pref"]` \end{pmatrix}$$
+$$\gamma_{simple} = \begin{pmatrix} `r #simple_gammas["Diam","Diam"]` & `r #simple_gammas["Diam","Clutch"]` & `r #simple_gammas["Diam","Pref"]` \\  `r #simple_gammas["Clutch","Diam"]` & `r #simple_gammas["Clutch","Clutch"]` & `r #simple_gammas["Clutch","Pref"]` \\  `r #simple_gammas["Pref","Diam"]` & `r #simple_gammas["Pref","Clutch"]` & `r #simple_gammas["Pref","Pref"]` \end{pmatrix}$$
+
+$$\text{Curvature}_{complex} = \begin{pmatrix} `r #complex_curvature["Diam","Diam"]` & `r #complex_curvature["Diam","Clutch"]` & `r #complex_curvature["Diam","Pref"]` \\  `r #complex_curvature["Clutch","Diam"]` & `r #complex_curvature["Clutch","Clutch"]` & `r #complex_curvature["Clutch","Pref"]` \\  `r #complex_curvature["Pref","Diam"]` & `r #complex_curvature["Pref","Clutch"]` & `r #complex_curvature["Pref","Pref"]` \end{pmatrix}$$
+
+$$\text{Curvature}_{simple} = \begin{pmatrix} `r #simple_curvature["Diam","Diam"]` & `r #simple_curvature["Diam","Clutch"]` & `r #simple_curvature["Diam","Pref"]` \\  `r #simple_curvature["Clutch","Diam"]` & `r #simple_curvature["Clutch","Clutch"]` & `r #simple_curvature["Clutch","Pref"]` \\  `r #simple_curvature["Pref","Diam"]` & `r #simple_curvature["Pref","Clutch"]` & `r #simple_curvature["Pref","Pref"]` \end{pmatrix}$$
 
@@
 
-```{r Observe P matrix, include=FALSE}
+```{r Observe P matrix, include=FALSE, eval=FALSE}
 
@@
 
-$$\text{P} = \begin{pmatrix} `r round(P_matrix["Diam","Diam"],2)` & `r round(P_matrix["Diam","Clutch"],2)` & `r round(P_matrix["Diam","Pref"],2)` \\  `r round(P_matrix["Clutch","Diam"],2)` & `r round(P_matrix["Clutch","Clutch"],2)` & `r round(P_matrix["Clutch","Pref"],2)` \\  `r round(P_matrix["Pref","Diam"],2)` & `r round(P_matrix["Pref","Clutch"],2)` & `r round(P_matrix["Pref","Pref"],2)` \end{pmatrix}$$
+$$\text{P} = \begin{pmatrix} `r #round(P_matrix["Diam","Diam"],2)` & `r #round(P_matrix["Diam","Clutch"],2)` & `r #round(P_matrix["Diam","Pref"],2)` \\  `r #round(P_matrix["Clutch","Diam"],2)` & `r #round(P_matrix["Clutch","Clutch"],2)` & `r #round(P_matrix["Clutch","Pref"],2)` \\  `r #round(P_matrix["Pref","Diam"],2)` & `r #round(P_matrix["Pref","Clutch"],2)` & `r #round(P_matrix["Pref","Pref"],2)` \end{pmatrix}$$
 Note that the variance of each phenotypic trait is standardized to 1.
-If we assume that each phenotypic trait has a narrow-sense heritability ($h^2$) of `r heritability`, then the additive genetic variance of each trait is equal to its narrow-sense heritability.
+If we assume that each phenotypic trait has a narrow-sense heritability ($h^2$) of `r #heritability`, then the additive genetic variance of each trait is equal to its narrow-sense heritability.
 The resulting G-matrix is:
 
-$$\text{G} = \begin{pmatrix} `r round(G_matrix["Diam","Diam"],2)` & `r round(G_matrix["Diam","Clutch"],2)` & `r round(G_matrix["Diam","Pref"],2)` \\  `r round(G_matrix["Clutch","Diam"],2)` & `r round(G_matrix["Clutch","Clutch"],2)` & `r round(G_matrix["Clutch","Pref"],2)` \\  `r round(G_matrix["Pref","Diam"],2)` & `r round(G_matrix["Pref","Clutch"],2)` & `r round(G_matrix["Pref","Pref"],2)` \end{pmatrix}$$
-```{r Change in G-matrices, include=FALSE}
+$$\text{G} = \begin{pmatrix} `r #round(G_matrix["Diam","Diam"],2)` & `r #round(G_matrix["Diam","Clutch"],2)` & `r #round(G_matrix["Diam","Pref"],2)` \\  `r #round(G_matrix["Clutch","Diam"],2)` & `r #round(G_matrix["Clutch","Clutch"],2)` & `r #round(G_matrix["Clutch","Pref"],2)` \\  `r #round(G_matrix["Pref","Diam"],2)` & `r #round(G_matrix["Pref","Clutch"],2)` & `r #round(G_matrix["Pref","Pref"],2)` \end{pmatrix}$$
+```{r Change in G-matrices, include=FALSE, eval=FALSE}
 complex_G_matrix <- G_matrix + G_matrix %*% complex_curvature %*% G_matrix
@@
 
-$$\text{G}_{complex} = \begin{pmatrix} `r round(complex_G_matrix["Diam","Diam"],3)` & `r round(complex_G_matrix["Diam","Clutch"],3)` & `r round(complex_G_matrix["Diam","Pref"],3)` \\  `r round(complex_G_matrix["Clutch","Diam"],3)` & `r round(complex_G_matrix["Clutch","Clutch"],3)` & `r round(complex_G_matrix["Clutch","Pref"],3)` \\  `r round(complex_G_matrix["Pref","Diam"],3)` & `r round(complex_G_matrix["Pref","Clutch"],3)` & `r round(complex_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
+$$\text{G}_{complex} = \begin{pmatrix} `r #round(complex_G_matrix["Diam","Diam"],3)` & `r #round(complex_G_matrix["Diam","Clutch"],3)` & `r #round(complex_G_matrix["Diam","Pref"],3)` \\  `r #round(complex_G_matrix["Clutch","Diam"],3)` & `r #round(complex_G_matrix["Clutch","Clutch"],3)` & `r #round(complex_G_matrix["Clutch","Pref"],3)` \\  `r #round(complex_G_matrix["Pref","Diam"],3)` & `r #round(complex_G_matrix["Pref","Clutch"],3)` & `r #round(complex_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
 
@@
 
-$$\text{G}_{simple} = \begin{pmatrix} `r round(simple_G_matrix["Diam","Diam"],3)` & `r round(simple_G_matrix["Diam","Clutch"],3)` & `r round(simple_G_matrix["Diam","Pref"],3)` \\  `r round(simple_G_matrix["Clutch","Diam"],3)` & `r round(simple_G_matrix["Clutch","Clutch"],3)` & `r round(simple_G_matrix["Clutch","Pref"],3)` \\  `r round(simple_G_matrix["Pref","Diam"],3)` & `r round(simple_G_matrix["Pref","Clutch"],3)` & `r round(simple_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
+$$\text{G}_{simple} = \begin{pmatrix} `r #round(simple_G_matrix["Diam","Diam"],3)` & `r #round(simple_G_matrix["Diam","Clutch"],3)` & `r #round(simple_G_matrix["Diam","Pref"],3)` \\  `r #round(simple_G_matrix["Clutch","Diam"],3)` & `r #round(simple_G_matrix["Clutch","Clutch"],3)` & `r #round(simple_G_matrix["Clutch","Pref"],3)` \\  `r #round(simple_G_matrix["Pref","Diam"],3)` & `r #round(simple_G_matrix["Pref","Clutch"],3)` & `r #round(simple_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
 
@@
 
-<!--$$logit(E(W))=\mu+\beta_{diameter}+\beta_{clutch}+\beta_{preference}+$$
-$$logit(E(W))=\mu+treatment+s(diam):treat+s(clutch)+s(pref)+diam:cluch+diam:pref+clutch:pref+(1|Genotype/Plant/Gall)$$-->
-
-<!-- We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
-Larva survival (0 or 1) was our response variable and measure of fitness. 
-<!-- Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients. -->
-<!-- We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
+$$logit(E(W))=\mu+\beta_{diameter}+\beta_{clutch}+\beta_{preference}+$$
+$$logit(E(W))=\mu+treatment+s(diam):treat+s(clutch)+s(pref)+diam:cluch+diam:pref+clutch:pref+(1|Genotype/Plant/Gall)$$
+
+We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
+larval survival (0 or 1) was our response variable and measure of fitness.
+
+Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients.
+
+We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
 This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. 
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
--->
+To account for the correlated structure of clutch size (gall level) and Oviposition preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
 
@@
 
-In simple food webs, both clutch size and female preference experience directional selection, with smaller clutch sizes ($\beta_{clutch}=$
+In simple food webs, both clutch size and Oviposition preference experience directional selection, with smaller clutch sizes ($\beta_{clutch}=$
 `r paste0(filter(summary_beta_treatment, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Clutch size")$upper_97.5,"]")`
 and weaker preferences ($\beta_{pref}=$
-`r paste0(filter(summary_beta_treatment, Phenotype=="Female preference")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Female preference")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Female preference")$upper_97.5,"]")`
+`r paste0(filter(summary_beta_treatment, Phenotype=="Oviposition preference")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Oviposition preference")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Oviposition preference")$upper_97.5,"]")`
 ) resulting in higher larval survival (blue lines in Fig. \ref{fig:Univariate_Landscapes}B,C).
@@
 `r paste0(filter(summary_beta_control, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_control, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Clutch size")$upper_97.5,"]")`
-) or female preference ($\beta_{pref}=$
-`r paste0(filter(summary_beta_control, Phenotype=="Female preference")$Estimate," [",filter(summary_beta_control, Phenotype=="Female preference")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Female preference")$upper_97.5,"]")`
+) or Oviposition preference ($\beta_{pref}=$
+`r paste0(filter(summary_beta_control, Phenotype=="Oviposition preference")$Estimate," [",filter(summary_beta_control, Phenotype=="Oviposition preference")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Oviposition preference")$upper_97.5,"]")`
 ) in complex food webs (orange lines in Fig.
 \ref{fig:Univariate_Landscapes}B,C).
-The absence of selection on clutch size and female preference was likely a result of conflicting selection pressures imposed by each guild of parasitoids due to their different functional relationships with gall traits.
+The absence of selection on clutch size and Oviposition preference was likely a result of conflicting selection pressures imposed by each guild of parasitoids due to their different functional relationships with gall traits.
 Together, these different patterns of selection resulted in an ideal combination of traits having higher fitness in the simple food web (large diameter, smaller clutches, weaker preference), whereas there was a larger combination of trait values that had equal fitness in the complex food web (Fig.
@@
 
--->
 ```
@@
 
-```{r Egg vs. egg Parasitoids Model, cache=TRUE}
+```{r Egg vs. egg Parasitoids Model, cache=TRUE, eval=FALSE, include=FALSE}
 
@@
 
-```{r egg vs egg ggplot explore}
+```{r egg vs egg ggplot explore, eval=FALSE, include=FALSE}
 densities <- gall_selection.df %>%
@@
 
-```{r Egg vs. Egg Bootstrap Model 1, include=FALSE, cache=TRUE}
+```{r Egg vs. Egg Bootstrap Model 1, include=FALSE, cache=TRUE, eval=FALSE}
 egg.egg_boot_model_1 <- bootMer(egg.egg_model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Egg vs. Egg Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE}
+```{r Egg vs. Egg Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE, eval=FALSE, include=FALSE}
 knitr::kable(egg.egg_tidy_model_1)
@@
 
-```{r Fit Egg vs. egg Parasitoid Model 3, cache=TRUE}
+```{r Fit Egg vs. egg Parasitoid Model 3, cache=TRUE, eval=FALSE, include=FALSE}
 egg.egg_model_3 <- update(model_3, data=egg.vs.egg_df) 
@@
 
-```{r Bootstrap Egg vs. egg Parasitoid Model 4, cache=TRUE, include=FALSE}
+```{r Bootstrap Egg vs. egg Parasitoid Model 4, cache=TRUE, include=FALSE, eval=FALSE}
 boot_egg.egg_model_3 <- bootMer(egg.egg_model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. egg Parasitoid Model 4, echo=FALSE}
+```{r Plot Egg vs. egg Parasitoid Model 4, echo=FALSE, eval=FALSE, include=FALSE}
 egg.egg_plot_model_3 <- tidy_egg.egg_model_3 %>%
@@
 
-```{r Fit Egg vs. egg Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE}
+```{r Fit Egg vs. egg Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE, include=FALSE}
 egg.egg_model_4_adj <- update(model_4_adj, data=egg.vs.egg_df)
@@
 Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. egg Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE}
+```{r Plot Egg vs. egg Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE, include=FALSE}
 tidy_egg.egg_model_4_adj$term_ord <- factor(tidy_egg.egg_model_4_adj$term, 
@@
 
-```{r Table of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE}
+```{r Table of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
@@
 
-```{r Plot of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE}
+```{r Plot of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
 egg.larval_selection_gradients %>%
@@
 ```
+-->

### 2018-11-13 manuscript.Rmd
commit updated changes to analyses that calculate bootstrapped differences from zero and between treatments

@@
 ---
-title: "Food-web complexity flattens the fitness landscape of an insect herbivore"
-author: "Matthew A. Barbour"
-date: "6/4/2018"
+title: Food-web complexity simplifies the adaptive landscape of an insect herbivore
+#  | Phenotypic evolution is less constrained in complex food webs
+#  | Phenotypic evolution is more constrained in simple food webs
+#  | Food-web simplification constrains phenotypic evolution
+#  | Food-web complexity smooths the adaptive landscape of an insect herbivore
+author: 
+- Matthew A. Barbour$^{1,2,\ast}$
+- Christopher J. Greyson-Gaito$^{1,3}$ 
+- Arezoo Sootodeh$^{3}$ 
+- Brendan Locke$^{4}$ 
+- Jordi Bascompte$^{2}$
+# potentially use for 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348 for cross-format compatibility, with | to create new sections.
+#date: | 
+#    | 1. Affiliation
 output:
   pdf_document:
-    template: AmNat_MS_template.tex
+    toc: false
+    number_sections: false
+    df_print: paged
+    fig_caption: true
+    #citation_package: natbib
+    template: Rmd_AmNat_MS_template.tex
+    includes:  
+      in_header: Am-Nat-preamble-latex.tex
+      #after_body: test_2.tex
+bibliography: references.bib
+biblio-style: amnat.bst
+fontsize: 11pt
+fontfamily: mathpazo
+documentclass: article
+linkcolor: black
+urlcolor: black
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup ms, include=FALSE}
+## Rerun supp mat ----
+knitr::knit("analyses/reproduce_analyses.Rmd")
+
+## Get sample size info
+no_larvae <- dim(distinct(gall_selection.df, Gall_Number, Gall_ID))[1]
+no_galls <- dim(distinct(gall_selection.df, Gall_Number))[1]
+no_plants <- dim(distinct(gall_selection.df, Plant_Position))[1]
+no_genotypes <- dim(distinct(gall_selection.df, Genotype))[1]
 ```
 
-## R Markdown
+<!-- Begin title page formatting -->
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+\noindent 1. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada;
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+\noindent 2. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;
 
-```{r cars}
-summary(cars)
+\noindent 3. University of Guelph, Department of Integrative Biology, Guelph, ON N1G 2W1, Canada;
+
+\noindent 4. Humboldt State University, Department of Biological Sciences, Arcata, CA 95521, USA.
+
+$^\ast$ Corresponding author; e-mail: matthew.barbour@ieu.uzh.ch
+
+\bigskip
+
+*Manuscript elements*: Figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
+
+\bigskip
+
+*Keywords*: fitness landscape, host-parasitoid, natural selection, G-matrix, community context, ecological networks.
+
+\bigskip
+
+*Manuscript type*: Article. <!-- Or e-article, note, e-note, natural history miscellany, e-natural history miscellany, comment, reply, invited symposium, or countdown to 150.-->
+
+\bigskip
+
+\footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize
+
+<!-- End title page formatting -->
+
+\linenumbers{}
+\modulolinenumbers[3]
+
+\newpage
+
+# Abstract
+
+Adaptive landscapes describe the selective constraints acting on phenotypic evolution, but often treat the community context of evolving populations as a ``black box''.
+In contrast, ecological networks provide an explicit representation of the community context, yet often ignore the role of natural selection.
+Global change is simplifying the structure of ecological networks; however, we are currently in a poor position to predict how these simplified communities will affect the evolutionary potential of populations.
+Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
+We conducted a field experiment that manipulated the diversity of insect parasitoids (food-web complexity) that were able to impose selection on an insect herbivore.
+We then measured herbivore survival as a function of three key phenotypic traits.
+We found that fewer traits were under selection in complex vs.
+simple food webs.
+This occurred because different parasitoid species impose different selection pressures, minimizing relative fitness differences among phenotypes in complex food webs.
+Our results suggest that phenotypic evolution becomes more constrained in simplified food webs.
+This indicates that the simplification of ecological communities may constrain the adaptive potential of populations to future environmental change.
+
+\newpage
+
+# Introduction
+
+The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes, to phenotypes, to species [@Wright1931; @Simpson1944; @Arnold2001].
+More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory].
+Ecological interactions often play a key role in shaping adaptive landscapes, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.<!--, often play a key role in shaping the adaptive landscape and phenotypic evolution in multiple traits [; ;].
+For example, competition for shared prey in threespine stickleback has driven their adaptive divergence into ecotypes with specialized body and gill morphologies [@Schluter2000, other papers].
+Similarly, the elongated, red corollas of many flowering species have evolved in response to the efficient pollination of hummingbirds [cite].--> Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we also know that most species interact with multiple species in a community context [@Darwin1859].
+Understanding how the adaptive landscape is shaped by community context represents a major frontier for evolutionary ecologists [@McPeek2017; @terHorst2018].
+Resolution on this front is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].
+
+Ecological networks, such as a food web describing who eats whom, provide an explicit representation of the community context.
+These networks describe the interdependency of populations within an ecological community, providing an effective framework for predicting how the strength and organization of ecological interactions (network structure) affect population and community dynamics [@Bascompte2014; @McCann2012].
+Nevertheless, these networks often lack quantitative information on how ecological interactions influence selection on phenotypic traits.
+Thus, it remains unclear how network structure shapes adaptive landscapes of interacting populations.
+This represents a major barrier in our current ability to predict how changes in community context will affect phenotypic evolution.
+
+Here, we integrate ecological networks and adaptive landscapes to understand how community context constrains evolutionary change [@Arnold1992].
+Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape.
+For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
+Evolutionary trajectories become more constrained with an increase in the number of traits under selection, as this diminishes the number of optimal solutions [@Arnold2003].
+The curvature of the adaptive landscape can also constrain evolution through its indirect effect on genetic constraints [@Arnold1992; @Hansen2008].
+Genetic constraints are largely governed by a population's **G**-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
+In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].
+Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].
+If we want to predict how community context constrains evolutionary change, we must understand how ecological networks shape the adaptive landscape.
+
+To examine the effect of network structure on adaptive landscapes, we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
+\ref{fig:Conceptual}).
+The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006].
+These galls protect larva from attack by generalist predators (e.g.
+ants, spiders), but they suffer high mortaltiy from egg and larval parasitoids [@Barbour2016].
+We manipulated food-web complexity by either excluding the guild of larval parasitoids (simple food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (complex food web; fig.
+\ref{fig:Conceptual}).
+Food-web complexity may influence the adaptive landscape in a number of ways.
+For example, if each parasitoid imposes directional selection on a different trait, then more complex food webs may constrain evolution by increasing the number of traits under selection.
+Alternatively, if parasitoids impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
+To examine these different possibilities (among others), we applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
+Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, may constrain the evolution of interacting populations.
+
+<!--
+Here, we integrate ecological networks and the adaptive landscape to understand how changes in network structure affect the dynamics of natural selection.
+In particular, we are interested in how network structure constrains or enables phenotypic evolution [@Arnold1992].
+We can gain insight to the selective constraints imposed by network structure by examining its effect on the slope and curvature of the adaptive landscape.
+To illustrate this, let us examine the adaptive landscape of two hypothetical traits, $z_i$ and $z_j$.
+The slope of the adaptive landscape is described by a column vector of directional selection gradients acting on these traits (cite):
+
+$$\text{Slope} = \beta = \begin{pmatrix} \beta_{z_i} \\ \beta_{z_j} \end{pmatrix} $$
+
+If each phenotypic trait experiences directional selection ($\beta_{z_i},\beta_{z_j}\neq0$), then this implies that there is an optimal phenotype (adaptive peak) and thus strong constraints on the trajectory of evolution.
+In contrast, if selection is absent on a trait (say $\beta_{z_i}=0$), then there may be multiple peaks (a line across all possible $z_i$ in this example) where fitness is equivalent and thus weaker selective constraints [@Arnold1992].
+The curvature of the adaptive landscape may also constrain phenotypic evolution through its indirect effect on genetic constraints [@Arnold1992].
+Genetic constraints on phenotypic evolution are largely governed by a population's **G**-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
+For our hypothetical example, the **G**-matrix takes the form:
+
+$$\text{G} = \begin{pmatrix} V_{z_i:z_i} & \\ V_{z_i:z_j} & V_{z_j:z_j} \end{pmatrix} $$
+
+where $V_{z_i:z_i}$ is the additive genetic variance in $z_i$ and $V_{z_i:z_j}$ is the additive genetic covariance between $z_i$ and $z_j$.
+Changes in the **G**-matrix within a generation are governed by the following equation [cite]:
+
+$$\Delta \text{G}=\text{G}(\gamma-\beta \beta^{\text{T}})\text{G}$$
+where $\gamma$ corresponds to the matrix of quadratic ($\gamma_{z_i:z_i}$) and correlational ($\gamma_{z_i:z_j}$) selection gradients.
+The terms in parentheses in the above equation describe the curvature (C) of the adaptive landscape, or the effects of nonlinear selection.
+To make explicit how landscape curvature affects the **G**-matrix, we rewrite the curvature matrix as:
+
+$$\text{C}= \begin{pmatrix} \gamma_{z_i:z_i} & \\ \gamma_{z_i:z_j} & \gamma_{z_j:z_j} \end{pmatrix} - \begin{pmatrix} \beta_{z_i}\beta_{z_i} & \\ \beta_{z_i}\beta_{z_j} & \beta_{z_j}\beta_{z_j} \end{pmatrix} $$
+$$\text{C} = \begin{pmatrix} C_{z_i:z_i} & \\ C_{z_i:z_j} & C_{z_j:z_j} \end{pmatrix}$$
+The diagonal terms of this curvature matrix describe how selection changes the additive genetic variance of traits ($V_{z_i:z_i}$).
+If selection acts to decrease the additive genetic variance, which is common when there is no disruptive selection ($\gamma_{z_i:z_i}>0$), then this will constrain the trait's evolutionary response to future selection [@Hansen2008].
+The off-diagonal terms of the curvature matrix are also important as they describe the change in additive genetic covariances between traits.
+Nonzero values along the off-diagonal indicate that selection favors trait integration, which may result in stronger genetic constraints [@Hansen2008].
+
+To examine how network structure shapes the adaptive landscape, we conducted a field experiment that manipulated the complexity of a food web associated with an abundant leaf-galling midge (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
+\ref{fig:Conceptual}).
+The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006].
+These galls protect larva from attack by generalist predators (e.g.
+ants, spiders), but they suffer a high degree of mortaltiy from four parasitoid wasps.
+To manipulate food-web complexity, we experimentally excluded the diversity of parasitoids that were able to impose selection on gall midge larvae (fig.
+\ref{fig:Conceptual}).
+
+Food-web complexity may shape the adaptive landscape, and thus selective constraints, in a number of ways.
+For example, if each consumer imposes directional selection on a different trait, then more complex food webs may increase the number of traits under selection, thereby increasing selective constraints.
+Alternatively, if consumers impose selection on different values of a trait, then their selective effects may cancel each other in more complex food webs, which would alleviate selective constraints.
+Food-web complexity may also indirectly affect genetic constraints.
+For example, if each consumer imposes selection on a different rare phenotype (i.e.
+each end of a trait distribution), then there would be stabilizing selection for an optimal phenotype, which would increase genetic constraints.
+Alternatively, if consumers are adapted to attacking the population's mean phenotype, then the relative fitness of rarer phenotypes would increase (disruptive selection), which would decrease genetic constraints.
+To tease apart these diverse possibilities, we applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
+Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, shape the adaptive landscape of interconnected populations.
+-->
+
+<!-- Old last paragraph
+Here, we integrate ecological networks and the adaptive landscape to understand how changes in network structure affect the dynamics of natural selection.
+We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant leaf-galling midge (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
+\ref{fig:Conceptual}).
+The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006].
+Since these galls provide protection from generalist predators (e.g.
+ants, spiders), our experiment provides an effective manipulation of the diversity of trophic interactions, or food-web complexity, that this insect herbivore experiences.
+We then applied modern statistical methods to test how food-web complexity shapes the slope and curvature of the herbivore's adaptive landscape.
+Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, shape the adaptive landscape of interconnected populations.
+-->
+
+<!-- Useful paragraph explaining the effect of increased mortality on strength of selection
+Also, unless consumers are equivalent, then we may generally expect lower average survival in complex food webs, which would increase the strength of selection.
+The logic behind this is made clear if we rewrite the selection gradient, which is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$ [@Hunter2018].
+This alternative expression makes clear that lower survival, and thus mean fitness, increases the strength of selection.
+Note that if consumers are equivalent in their selective effects (i.e.
+functionally redundant), then we would not expect any effect of food-web complexity on the adaptive landscape.
+-->
+
+# Methods
+
+## Study Site
+
+We conducted our study within a four-year old common garden experiment of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40 40'53"N, 124 12'4"W) near Loleta, California, USA.
+This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
+Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
+Willows at our study site begin flowering in February and reach their peak growth in early August.
+During this study, willows had reached 5 - 9m in height.
+Further details on the genotyping and planting of the common garden are available in @Barbour2015.
+
+## Manipulating Food-web Complexity
+
+We setup our food-web manipulation across 128 plants soon after galls began developing on willows in early June of 2013.
+These 128 plants came from eight different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
+For the complex food-web treatment (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
+Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
+For the simple food-web treatment, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
+This treatment did not exclude the egg parasitoid *Platygaster* sp., which attacks prior to gall initiation [larva initiate gall development in Cecidomyiid midges: @Gagne1989].
+In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature.
+We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
+Since we were interested in selection imposed by parasitoids, we excluded unknown sources of mortality.<!--restricted our data to larvae that either survived to pupation or were parasitized by an egg or larval parasitoid.--> For the food-web treatment that excluded larval parasitoids (simple food web), we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
+This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
+Our final dataset contains survival estimates for `r no_larvae` larvae from `r no_galls` galls and `r no_plants` plants.
+
+## Measuring Phenotypic Traits
+
+We collected data on three different traits that we expected to influence larval survival based on our previous work [@Barbour2016] and others work with gall midges [@Weis1983; @Heath2018].
+First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
+Our previous work has shown that larger galls are associated with higher survival [@Barbour2016].
+Second, we measured clutch size by counting the number of chambers in each gall [@Weis1983; @Heath2018].
+All larvae collected from the same multi-chambered gall were scored with the same clutch size.
+Third, we measured oviposition (egg laying) preference as the density of larvae observed on a plant in an independent survey.
+We did this randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
+We then converted these counts to a measure of larval density per 100 shoots by counting the number of shoots on the last branch we sampled.
+All larvae collected from the same plant were scored with the same oviposition preference.
+Measuring larval densities on plants in the field is a common method for measuring oviposition preference [@Gripenberg2010]; however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference [@Singer1986].
+Fortunately, a couple of features of our study system suggest that larval densities may be a good proxy for oviposition preference.
+For example, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
+Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
+
+## Quantifying the Adaptive Landscape
+
+Our analyses consisted of three parts.
+First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and phenotypic traits ($z_i$) of individuals \textemdash in each food-web treatment.
+Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate selection gradients.
+Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape.
+Note that inferring adaptive landscapes from selection surfaces assumes that trait distributions are multivariate normal [@Lande1983].
+To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
+We then scaled all phenotypic traits (mean=0 and SD=1) in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
+
+**Selection surface**: Since larval survival was our measure of absolute fitness, we used a GLMM that assumed a binomial error distribution (and logit-link function).
+To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_{z_i}$), quadratic ($\alpha_{z_i:z_i}$), and linear interactions ($\alpha_{z_i:z_j}$) between each trait.
+We also allowed these trait-fitness relationships ($\alpha$) to vary between food-web treatments.
+Note that to obtain valid estimates of linear trait-fitness relationships, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
+Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the adaptive landscape [@Arnold2003].
+To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall ID nested within plant ID nested within genotype ID as random effects.
+Although statistical models with random effects are not common in analyses of natural selection, we think this is a mistake since modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
+Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e.
+setting them to zero) when calculating trait-fitness relationships.
+We then used parametric bootstrapping (1,000 replicates) to estimate the effect of food-web treatment on larval survival as well as trait-fitness relationships in each food-web treatment.
+To determine whether trait-fitness relationships differed between food-web treatments, we calculated the difference in bootstrapped replicates between treatments.
+
+**Selection gradients**: We used the method of @Janzen1998 to translate trait-fitness relationships ($\alpha$) into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i:z_i}$), and correlational ($\gamma_{z_i:z_j}$) selection gradients.
+Briefly, this method calculates the average gradient of selection surfaces by multiplying the average of $W(z)[1-W(z)]$ by each regression coefficient (e.g.
+$\alpha_{z_i}$, $\alpha_{z_i:z_i}$, or $\alpha_{z_i:z_j}$).
+We then divided this average gradient by mean fitness ($\bar W$) to put it on the scale of relative fitness, and thus interpretable as a selection gradient.
+We estimated selection gradients separately for each food-web treatment.
+Note that we doubled all quadratic terms prior to calculating selection gradients to put them on the same scale as estimates of directional and correlational selection [@Stinchcombe2008].
+
+**Adaptive landscape**: We took advantage of existing theory that translates estimates of selection gradients to the adaptive landscape [@Phillips1989; @Arnold2003].
+The shape of the adaptive landscape can be described by both its slope and curvature, each of which describe different aspects of constraints on phenotypic evolution.
+Specifically, the slope corresponds to the column vector of directional selection gradients, which in our study corresponds to:
+
+<!-- need to make beta a bold symbol, may need to add a package -->
+
+$$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
+This slope describes the selective constraints acting on the trajectory of phenotypic evolution, which is governed by the 'Lande equation', $\Delta \bar z=\text{G}\beta$ [@Lande1979].
+Quantitative predictions of evolutionary trajectories requires knowledge of a population's **G**-matrix; however, we can gain qualitative insight to evolutionary constraints by counting the number of phenotypic traits under directional selection [selective constraints, @Arnold1992].
+
+The curvature (**C**) of the adaptive landscape is a matrix that is determined by directional, quadratic, and correlational selection gradients, such that \boldmath$\text{C}=\gamma - \beta \beta^\text{T}$, or more explicitly:
+
+$$\textbf{C} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
+$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
+
+Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
+This curvature matrix describes the indirect effects of selection on genetic constraints within a generation ($\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}$).
+For example, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (less trait independence).
+Therefore, we can infer the indirect effects of selection on genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
+
+## Adjusting for biased measurements of selection
+
+Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits which could bias measurements of selection.
+In our system, it was plausible that parasitoids may influence chamber diameter by altering larval feeding behavior or killing larvae before they complete their development.
+To estimate this potential bias, we subset our data to only include galls where there was variation in larval survival within the same gall (i.e.
+1 > mean survival > 0).
+If we assume that larvae within each gall should have similar chamber diameters because they come from the same clutch and experience the same local environment (an assumption our data supports: gall ID explains 54% of the variance in chamber diameter), then the relationship between chamber diameter and larval survival in this data subset represents the effect of parasitism on trait expression (i.e.
+bias).
+We used a GLMM with the same structure as described above except that we only modelled a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
+We detected a positive bias in both food-web treatments (complex $\alpha_{\text{Diam}}$=
+`r round(fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],2)` 
+[`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.low,2)`,
+`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.high,2)`]; simple $\alpha_{\text{Diam}}$=
+`r round(fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"],2)` 
+[`r round(filter(biased_foodweb_confint, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,
+`r round(filter(biased_foodweb_confint, term=="FoodwebSimple:sc.Diam")$conf.high,2)`]), indicating that unadjusted relationships would overestimate the strength of selection on chamber diameter.
+To account for this bias, we substracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's trait-fitness relationship and directional selection gradient.
+
+## Measuring selection on the extended phenotype of egg parasitoids
+
+Once parasitized, the gall phenotype becomes the extended phenotype of the egg parasitoid.
+This extended phenotype may influence the egg parasitoid's survival in the face of larval parasitoids, and thus experiences selection.
+Our food-web manipulation allows us to measure selection imposed by larval parasitoids on the extended phenotype of egg parasitoids.
+Using the same models as described above, we substituted egg parasitism as our response variable to quantify trait-fitness relationships and selection gradients acting on the egg parasitoid.
+Note that we cannot test the effect of food-web complexity on the egg parasitoid's adaptive landscape ---we can only estimate the selection imposed by larval parasitoids.
+This comparison is still useful though in determining the extent to which the community context may have indirect evolutionary effects by altering selection on multiple interacting populations.
+
+All analyses and visualizations were conducted in R [@R2018].
+Unless otherwise noted, we report mean estimates of trait-fitness relationships and selection gradients with 95% confidence intervals in brackets.
+Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
+This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [@Arnold2001].
+We also plot mean larval survival on a natural log scale to accurately reflect the shape of the adaptive landscape [@Arnold2003].
+
+# Results
+
+## Food-web complexity reduces selective constraints
+
+\indent We found that fewer gall midge traits experienced directional selection in the complex (1 of 3) vs.
+simple food web (3 of 3)(table \ref{Table:Gradients}).
+For example, we observed directional selection for smaller clutch sizes in the simple food web, but there was no evidence of selection acting on this trait in the complex food web (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}C).
+This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids (fig.
+\ref{fig:UV_Landscape}C).
+Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`]).
+In the simple food web, we also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}B); however, there was less clear evidence for this relationship in complex food webs (table \ref{Table:Gradients}).
+This was likely a result of the weaker and nonlinear relationship between oviposition preference and fitness consequences imposed by larval parasitoids ($\beta_{\text{Pref}}$=
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`]; $\gamma_{\text{Pref:Pref}}$=
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
+Food-web complexity did not alter the strong directional selection for larger chamber diameters (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}).
+
+## Food-web complexity reduces genetic constraints
+
+\indent The curvature of the adaptive landscape indirectly affects genetic constraints and is influenced by directional, quadratic, and correlational selection gradients.
+Our food-web treatment did not alter correlational selection for any combination of traits (table \ref{Table:Gradients}).
+Similarly, our food-web treatment did not influence quadratic selection on either chamber diameter or clutch size (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}A,C).
+In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
+The negative relationship between oviposition preference and larval survival dampened at high densities in complex, but not simple food webs (fig.
+\ref{fig:UV_Landscape}).
+This dampened relationship was partly due to differences in selection imposed by larval parasitoids (contrast $\gamma_{\text{Pref:Pref}}$=
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
+
+To estimate the net effect of food-web complexity on the curvature ($C$) of the adaptive landscape, we only retained nonzero selection gradients (i.e.
+95\% CI did not overlap zero) prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
+We found that the curvatures of the adaptive landscape exhibited the following structures:
+
+$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
+`r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(complex_curvature["Clutch","Diam"],2)` & `r round(complex_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
+`r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(simple_curvature["Clutch","Diam"],2)` & `r round(simple_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+The structure of these matrices indicate that there are more selective constraints imposed on the gall midge in the simple (6 of 6) vs.
+complex (1 of 6) food web.
+Simple food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the complex food web.
+For genetic covariances, the simple food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
+\ref{fig:MV_Landscape}).
+In contrast, there was no strong evidence of trait integration in the complex food web (fig.
+\ref{fig:MV_Landscape}).
+
+## Selection on the extended phenotype of egg parasitoids
+
+Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\gamma_{\text{Pref:Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
+This indicates that larval parasitoids impose nonlinear selection on this extended phenotype of the egg parasitoid (fig.
+\ref{fig:EggPtoid_Selection}).
+Larval parasitoids also dampened the linear relationship between probability of observing egg parasitoids and gall midge preference (contrast $\alpha_{\text{Pref}}$=
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
+), but this did not translate into an effect on directional selection 
+(contrast $\beta_{\text{Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]).
+This was likely because there was a tendency (albeit not statistically signficant) for a higher probability of egg-parasitoid survival in the simple vs.
+complex food webs
+(contrast=`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$mean,2)` [
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
+Larval parasitoids did not alter directional, quadratic, or correlational selection on any other extended phenotypes of egg parasitoids (see Supplementary Material).
+
+<!--
+## Slope of the adaptive landscape
+
+\indent We found that food-web complexity altered the slope of the adaptive landscape ($\beta$) in two key ways.
+First, there were fewer traits under directional selection in the complex (2 of 3) vs.
+simple food webs (3 of 3)(table \ref{Table:Gradients}).
+For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}).
+In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}).
+This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids (fig.
+\ref{fig:UV_Landscape}).
+Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`]).
+
+The second key effect of food-web complexity was to increase the strength of selection acting on chamber diameter. Directional selection on chamber diameter was 
+`r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean * 100),0)`% higher in complex vs.
+simple food webs (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}).
+This result was not due to any difference in the relationship between larval survival and chamber diameter (table \ref{Table:Coefs}), but was due to the fact that the average probability of larval survival decreased from
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean,2)` in the simple food web to
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean,2)` in the more complex one (contrast=
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean,2)*-1` 
+[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)*-1`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)*-1`]).
+Note that although the selection gradient is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, it can be rewritten as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$.
+This alternative expression makes clear that lower survival, and thus mean fitness, will always increase the strength of selection.
+-->
+<!-- survival result written in terms of percent decrease `r #round(((filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean - filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean) / filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean * 100),0)*-1 # multiply by -1 to match written description`% lower in complex vs.
+simple food webs -->
+<!--
+## Curvature of the adaptive landscape
+
+Unlike the slope, the curvature of the adaptive landscape is influenced by directional, quadratic, and correlational selection gradients.
+Our food-web treatment did not alter correlational selection for any combination of traits, although there was evidence that correlational selection on chamber diameter and oviposition preference differed from zero in the complex food web (table \ref{Table:Gradients}; fig.
+\ref{fig:MV_Landscape}).
+Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}).
+In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
+Specifically, the negative relationship between oviposition preference and larval survival dampened at high densities in complex, but not simple food webs (fig.
+\ref{fig:UV_Landscape}).
+This dampened relationship was partly due to differences in selection imposed by larval parasitoids (contrast $\gamma_{\text{Pref:Pref}}$=
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
+
+To estimate the net effect of food-web complexity on the curvature ($C$) of the adaptive landscape, we only retained nonzero selection gradients (i.e.
+95\% CI did not overlap zero) before subtracting the matrix of directional selection gradients ($\beta \beta^\text{T}$) from the matrix of quadratic and correlational selection gradients ($\gamma$).
+We found that the curvatures of the adaptive landscape exhibited the following structures:
+
+$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
+`r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(complex_curvature["Clutch","Diam"],2)` & `r round(complex_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
+`r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(simple_curvature["Clutch","Diam"],2)` & `r round(simple_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+The structure of these matrices indicate that there are more selective constraints imposed on the gall midge in the simple (6 of 6) vs.
+complex (2 of 6) food web.
+Simple food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the complex food web.
+For genetic covariances, the simple food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
+\ref{fig:MV_Landscape}).
+In contrast, the complex food web only constrained genetic covariance by favoring integration between chamber diameter and oviposition preference (fig.
+\ref{fig:MV_Landscape}).
+
+## Indirect selection acting on egg parasitoids
+
+Larval parasitoids altered nonlinear selection acting on the egg parasitoid's extended phenotype of midge preference (contrast $\gamma_{\text{Pref:Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
+This nonlinear selection was a result of a reduced probability of observing egg parasitoids at high midge densities in complex food webs (fig.
+\ref{fig:EggPtoid_Selection}).
+Larval parasitoids also dampened the linear relationship between egg parasitoids and the extended phenotype of midge preference (contrast $\alpha_{\text{Pref}}$=
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
+), but this did not translate into an effect on directional selection 
+(contrast $\beta_{\text{Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]).
+This was likely because there was a tendency (albeit not statistically signficant) for a higher probability of egg-parasitoid survival in the simple vs.
+complex food webs
+(contrast=`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$mean,2)` [
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
+Larval parasitoids did not alter directional, quadratic, or correlational selection on any other extended phenotypes (see Supplementary Material).
+-->
+
+# Discussion
+
+\begin{enumerate}
+
+ \item Summary of key results
+    \begin{enumerate}
+    \item Gall midges experience fewer selective and genetic constraints in complex food webs.
+    \end{enumerate}
+
+ \item Natural history and comparison to other studies of natural selection in galling insects.
+    \begin{enumerate}
+    \item \textbf{Important Studies for Comparison}: @Abrahamson1997; @Weis1983; @Heath2018; Start, Weis, and Gilbert In Press Am.
+Nat; @Start2016; @Start2018urbanization; Peter Price's work; Timothy Craig's work; Cheryl Briggs work.
+    \item \textbf{Topics to discuss}: Persistent pattern in selection for larger galls; Contrasting effects of egg and larval parasitoids on clutch size; Nonlinear selection at high gall densities is likely reflective of the poorer searching ability of larval vs.
+egg parasitoids (and thus it saturates more quickly).
+    \end{enumerate}
+
+ \item Selective constraints:
+    \begin{enumerate}
+    \item \textbf{Key Result}: Fewer traits under directional selection in complex (1 of 3) vs.
+simple (3 of 3) food webs.
+Need to be wary of interpreting no selection on oviposition preference in complex food webs though.
+Even if there is selection on oviposition preference, this does not change our qualitative result.
+    \item \textbf{Implications}: The trajectory of phenotypic evolution is less constrained in complex vs.
+simple food webs.
+In other words, there are more potential adaptive peaks in complex food webs.
+    \end{enumerate}
+
+ \item Indirect effects of selection on genetic constraints: 
+    \begin{enumerate}
+    \item \textbf{Key Result}: Fewer traits experience a decrease in additive genetic variance and fewer trait combinations experience selection for trait integration. 
+    \item \textbf{Implications}: The structure of the G-matrix is under less influence of selection in complex vs.
+simple food webs.
+Thus the trajectory of phenotypic evolution may be dictated more by genetic rather than selective constraints.
+This is in line with empirical evidence (from complex natural systems) that evolution tends to proceed along genetic lines of least resistance [@Schluter1996].
+    \end{enumerate}
+
+ \item Indirect evolutionary effects:
+    \begin{enumerate}
+    \item \textbf{Key Result}: Evidence of nonlinear selection on the extended phenotype of egg parasitoids.
+    \item \textbf{Implications}: Hints at a dynamic adaptive landscape in complex food webs.
+    \end{enumerate}
+
+ \item Caveats: 
+    \begin{enumerate} 
+    \item \textbf{Key Caveat}: Experimental artifact of lower larval survival in complex food-web treatment.
+    \item \textbf{Implications}: Artificially increased the magnitude of selection in complex food webs.
+Note however, that this does not qualitatively change any of our results.
+In fact, we are actually underestimating the constraints imposed by our simple food-web treatment.
+This is because the egg parasitoids would be released from their intraguild predator, and thus could increase in abundance over future generations and impose stronger selection on gall midges.
+    \end{enumerate}
+
+\item Conclusions
+
+\end{enumerate}
+
+# Acknowledgements
+
+# References
+
+<div id="refs"></div> <!-- this code inserts references wherever you want rather than at the end of the document -->
+
+\newpage
+
+# Tables
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\hline
+$\beta_{\text{Diam}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\beta_{\text{Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+
+$\beta_{\text{Pref}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\newpage
+
+\begin{table}[h]
+\caption{Relationship between absolute fitness (larval survival) and phenotypic traits of gall midges in complex vs. simple food webs.}
+\label{Table:Coefs}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Coefficient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\hline
+$\alpha_{\text{Diam}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\alpha_{\text{Clutch}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+
+$\alpha_{\text{Pref}}$ &
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\alpha_{\text{Diam,Diam}}$ &
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\alpha_{\text{Clutch,Clutch}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\alpha_{\text{Pref,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\
+
+$\alpha_{\text{Diam,Clutch}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\alpha_{\text{Diam,Pref}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\alpha_{\text{Clutch,Pref}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\alpha_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\newpage
+
+# Figure Legends
+
+**Figure \ref{fig:Conceptual}**: Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
+In the complex food-web treatment (A), we allowed the full suite of egg (blue rectangle) and larval (yellow rectangle) parasitoids to impose selection.
+In the simple food-web treatment (B), we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+Black arrows denote the flow of energy in this network of trophic interactions.
+Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
+(Family: Pteromalidae); *Tetrastichus* sp.
+(Family: Eulophidae); and *Torymus* sp.
+(Family: Torymidae).
+
+**Figure \ref{fig:UV_Landscape}**: Adaptive landscape of gall midge phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
+Solid lines represent selection experienced in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
+Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape.
+
+**Figure \ref{fig:MV_Landscape}**: Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
+Selection favors trait integration for each combination of traits in simple food webs, whereas there is no strong evidence for trait integration in complex food webs.
+Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape.
+
+**Figure \ref{fig:EggPtoid_Selection}**: Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
+The solid line represents the average difference in the probability of observing the egg parasitoid in complex vs.
+simple food webs as a function of gall midge oviposition preference.
+Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on the extended phenotype of egg parasitoids.
+
+```{r Conceptual, echo=FALSE, fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
+In the complex food-web treatment (A), we allowed the full suite of egg (blue rectangle) and larval (yellow rectangle) parasitoids to impose selection.
+In the simple food-web treatment (B), we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+Black arrows denote the flow of energy in this network of trophic interactions.
+Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
+(Family: Pteromalidae); *Tetrastichus* sp.
+(Family: Eulophidae); and *Torymus* sp.
+(Family: Torymidae)."}
+knitr::include_graphics("analyses/complex_simple_foodwebs.jpeg")
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r UV_Landscape, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}"}
+knitr::include_graphics("analyses/UV_landscapes.pdf")
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r MV_Landscape, echo=FALSE, fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
+Selection favors trait integration for each combination of traits in simple food webs, whereas there is no strong evidence for trait integration in complex food webs.
+Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape."}
+knitr::include_graphics("analyses/MV_landscapes.pdf")
+```
+
+```{r EggPtoid_Selection, echo=FALSE, fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
+The solid line represents the average difference in the probability of observing the egg parasitoid in complex vs.
+simple food webs as a function of gall midge oviposition preference.
+Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on the extended phenotype of egg parasitoids."}
+knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
+```

### 2018-11-13 test.Rmd
commit updated changes to analyses that calculate bootstrapped differences from zero and between treatments

--- 2018-06-07 manuscript.Rmd
@@
 ---
-title: "Food-web complexity flattens the fitness landscape of an insect herbivore"
+title: "test"
 author: "Matthew A. Barbour"
-date: "6/4/2018"
+date: "11/9/2018"
 output:
+  html_document:
+    keep_md: true
   pdf_document:
-    template: AmNat_MS_template.tex
+    toc: false
+    number_sections: false
+    df_print: paged
+    fig_caption: true
+    #citation_package: natbib
+    template: Rmd_AmNat_MS_template.tex
+    keep_tex: true
+    includes:  
+      in_header: Am-Nat-preamble-latex.tex
 ---
 
-```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+```{r setup tables and figures, include=FALSE}
+## Rerun supp mat ----
+knitr::knit("analyses/reproduce_analyses.Rmd")
 ```
 
-## R Markdown
+\newpage
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
+\begin{table}[h]
+\caption{Standardized selection gradients acting on \textit{Iteomyia} in complex vs. simple food webs.}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\hline
+$\beta_{\text{Diam}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
 
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
+$\beta_{\text{Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
 
-```{r cars}
-summary(cars)
+$\beta_{\text{Pref}}$ &
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\begin{table}[h]
+\caption{Relationship between absolute fitness (larva survival) and phenotypic traits of \textit{Iteomyia} in complex vs. simple food webs.}
+\label{Table:Coefs}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Coefficient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\hline
+$\alpha_{\text{Diam}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\alpha_{\text{Clutch}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+
+$\alpha_{\text{Pref}}$ &
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\alpha_{\text{Diam,Diam}}$ &
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\alpha_{\text{Clutch,Clutch}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\alpha_{\text{Pref,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\alpha_{\text{Diam,Clutch}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\alpha_{\text{Diam,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\alpha_{\text{Clutch,Pref}}$ & 
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. $\alpha_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\newpage
+
+\section*{Figure legends}
+
+<!-- Figures -->
+
+```{r Conceptual, echo=FALSE, fig.cap="\\label{fig:Conceptual}Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
+Black arrows denote the flow of energy in this network of trophic interactions."}
+#knitr::include_graphics("analyses/complex_simple_foodwebs.jpeg")
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r Gradients, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Gradients}Selection gradients acting on *Iteomyia* phenotypes.
+Points and lines correspond to estimated means and 95% confidence intervals, respectively.
+Orange and blue colors correspond to estimated gradients in complex and simple food webs, respectively.
+Yellow colors correspond to selection gradients imposed by larval parasitoids.
+Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web)."}
+knitr::include_graphics("analyses/reproduce_analyses_files/figure-html/Figure-Selection-Gradients-1.png")
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r UV_Landscape, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of \\textit{Iteomyia} phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); female preference (B); and clutch size (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates to show the uncertainty in estimated gradients.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 bootstrapped samples.
+Note the mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape."}
+knitr::include_graphics("analyses/UV_landscapes.pdf")
+```
+
+```{r MV_Landscape, echo=FALSE, fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and chamber diameter (A); clutch size and female preference (B); female preference and chamber diameter (C).
+Note that mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape."}
+knitr::include_graphics("analyses/MV_landscapes.pdf")
+```
+
+```{r EggPtoid_Selection, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:EggPtoid_Selection}."}
+knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
+```

### 2018-11-13 test_2.Rmd
commit updated changes to analyses that calculate bootstrapped differences from zero and between treatments

--- 2018-06-07 manuscript.Rmd
@@
 ---
-title: "Food-web complexity flattens the fitness landscape of an insect herbivore"
+title: "test 2"
 author: "Matthew A. Barbour"
-date: "6/4/2018"
+date: "11/9/2018"
 output:   
-  pdf_document:
-    template: AmNat_MS_template.tex
+  html_document:
+    keep_md: true
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+#rmarkdown::pandoc_convert("test_2.md", to = "latex", output = "test_2.tex")
 ```
 
-## R Markdown
+<!-- Figures -->
 
-This is an R Markdown document. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.
-
-When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.
-You can embed an R code chunk like this:
-
-```{r cars}
-summary(cars)
+```{r Conceptual, echo=FALSE, fig.cap="\\label{fig:Conceptual}Illustrations of complex (A) and simple (B) food webs associated with the insect herbivore, *Iteomyia salicisverruca*.
+Black arrows denote the flow of energy in this network of trophic interactions."}
+knitr::include_graphics("analyses/complex_simple_foodwebs.jpeg")
 ```
 
-## Including Plots
-
-You can also embed plots, for example:
-
-```{r pressure, echo=FALSE}
-plot(pressure)
+```{r Gradients, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:Gradients}Selection gradients acting on *Iteomyia* phenotypes.
+Points and lines correspond to estimated means and 95% confidence intervals, respectively.
+Orange and blue colors correspond to estimated gradients in complex and simple food webs, respectively.
+Yellow colors correspond to selection gradients imposed by larval parasitoids.
+Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web)."}
+knitr::include_graphics("analyses/reproduce_analyses_files/figure-html/Figure-Selection-Gradients-1.png")
 ```
 
-Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
+```{r EggPtoid_Selection, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:EggPtoid_Selection}."}
+knitr::include_graphics("manuscript_files/figure-latex/EggPtoid_Selection-1.pdf") #eggptoid_selection #knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
+```
+
+```{r UV_Landscape, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of \\textit{Iteomyia} phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); female preference (B); and clutch size (C).
+Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates to show the uncertainty in estimated gradients.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 bootstrapped samples.
+Note the mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape."}
+knitr::include_graphics("analyses/UV_landscapes.pdf")
+```
+
+```{r MV_Landscape, eval=FALSE, echo=FALSE, fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and chamber diameter (A); clutch size and female preference (B); female preference and chamber diameter (C).
+Note that mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape."}
+knitr::include_graphics("analyses/MV_landscapes.pdf")
+```

### 2018-11-22 analyses/reproduce_analyses.Rmd
updates through sending first draft to Jordi

@@
   mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
+  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
   mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
@@
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
-
+```
+
+```{r Table of food web coefficients, echo=F}
 knitr::kable(tidy_foodweb_alphas)
@@
          conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
-
+```
+
+```{r Table of food web selection gradients, echo=F}
 knitr::kable(tidy_foodweb_grads)
@@
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
-
+```
+
+```{r Tabel of egg vs. larval coefficients, echo=FALSE}
 knitr::kable(tidy_egglarval_alphas)
@@
          conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
-
+```
+
+```{r Egg vs. larval selection gradients, echo=F}
 knitr::kable(tidy_egglarval_grads)
@@
 biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
+
+visreg::visreg(eggegg_model, xvar="sc.sqrt.Pref", by="sc.Diam", scale="response", cond = list(Foodweb="Simple"))
+visreg::visreg(eggegg_model, xvar="sc.sqrt.Pref", by="sc.Diam", scale="response", cond = list(Foodweb="Complex"))
+visreg::visreg(eggegg_model, xvar="sc.Diam", by="sc.sqrt.Pref", scale="response", cond = list(Foodweb="Simple"))
+visreg::visreg(eggegg_model, xvar="sc.Diam", by="sc.sqrt.Pref", scale="response", cond = list(Foodweb="Complex"))
 ```
@@
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
-
+```
+
+```{r Egg vs. egg ptoid coefficients, echo=F}
 knitr::kable(tidy_eggegg_alphas)
@@
          conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
-
+```
+
+```{r Table of egg vs. egg ptoid gradients, echo=F}
 knitr::kable(tidy_eggegg_grads)
@@
 ```{r Egg-Parasitoid-Selection-linear, echo=F}
-linear_eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
+linear_eggptoid_plot_df <- linear_eggegg_RF_Pref$absolute_fitness %>% 
   select(-sc.Diam, -sc.log.Clutch) %>%
@@
 
-linear_eggptoid_selection_plot <- eggptoid_plot_df %>%
+linear_eggptoid_selection_plot <- linear_eggptoid_plot_df %>%
   ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +

### 2018-11-22 manuscript.Rmd
updates through sending first draft to Jordi

@@
 ---
-title: Food-web complexity simplifies the adaptive landscape of an insect herbivore
+title: Phenotypic evolution is more constrained in simple food webs
+#  | Food-web complexity simplifies the adaptive landscape of an insect herbivore
 #  | Phenotypic evolution is less constrained in complex food webs
-#  | Phenotypic evolution is more constrained in simple food webs
+#  | 
 #  | Food-web simplification constrains phenotypic evolution
@@
   pdf_document:
+    keep_tex: true
     toc: false
@@
       in_header: Am-Nat-preamble-latex.tex
-      #after_body: test_2.tex
 bibliography: references.bib
@@
 ## Rerun supp mat ----
-knitr::knit("analyses/reproduce_analyses.Rmd")
+knitr::knit("analyses/reproduce_analyses.Rmd") # try changing to knitr::render() and see if it'll also produce the .html document.
 
@@
 We then measured herbivore survival as a function of three key phenotypic traits.
-We found that fewer traits were under selection in complex vs.
-simple food webs.
-This occurred because different parasitoid species impose different selection pressures, minimizing relative fitness differences among phenotypes in complex food webs.
+We found that more traits were under selection in simple vs.
+complex food webs.
+The adaptive landscape was more neutral in complex food webs because different parasitoid species impose different selection pressures, minimizing relative fitness differences among phenotypes.
 Our results suggest that phenotypic evolution becomes more constrained in simplified food webs.
@@
 
-\indent We found that fewer gall midge traits experienced directional selection in the complex (1 of 3) vs.
-simple food web (3 of 3)(table \ref{Table:Gradients}).
+\indent We found that more gall midge traits experienced directional selection in the simple (3 of 3) vs.
+complex food webs (1 of 3)(table \ref{Table:Gradients}).
 For example, we observed directional selection for smaller clutch sizes in the simple food web, but there was no evidence of selection acting on this trait in the complex food web (table \ref{Table:Gradients}; fig.
@@
 In the simple food web, we also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, there was less clear evidence for this relationship in complex food webs (table \ref{Table:Gradients}).
-This was likely a result of the weaker and nonlinear relationship between oviposition preference and fitness consequences imposed by larval parasitoids ($\beta_{\text{Pref}}$=
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`]; $\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
-Food-web complexity did not alter the strong directional selection for larger chamber diameters (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}B); however, this relationship was weaker in complex food webs (table \ref{Table:Gradients}).
+This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on the extended phenotype of egg parasitoids section), and thus a less than additive effect on gall midges.
+Chamber diameter experienced positive directional selection in both food-web treatments, but selection was `r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}).
+This was not due to any difference between egg and larval parasitoids (fig.
+\ref{fig:UV_Landscape}), but was due to the lower average survival in complex food webs (contrast `r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean*-1, 2)`
+[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low*-1, 2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high*-1, 2)`]).
 
@@
 \ref{fig:UV_Landscape}).
-This dampened relationship was partly due to differences in selection imposed by larval parasitoids (contrast $\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
+This dampened relationship was partly due to a trend for nonlinear selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
 
@@
 
-Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\gamma_{\text{Pref:Pref}}$=
+Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\alpha_{\text{Pref}}$=
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
+).
+Specifically, larval parasitoids decreased the probability of observing egg parasitoids at high gall midge densities (fig.
+\ref{fig:EggPtoid_Selection}).
+Note however that this trait-fitness relationship did not translate into a significant difference in selection (contrast $\beta_{\text{Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
+). This was likely because there was a tendency (albeit not statistically signficant) for a lower probability of egg-parasitoid survival in complex vs. simple food webs 
+(contrast=`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$mean,2)` [
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]), which masks this trait-fitness relationship.
+We also observed two other interesting trends, although neither significantly differed between treatments.
+Specifically, there was a tendency for the impact of larval parasitoids to increase nonlinearly at higher gall midge densities (fig.
+\ref{fig:EggPtoid_Selection}; complex $\alpha_{\text{Pref:Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]; but contrast $\alpha_{\text{Pref:Pref}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
+There was also a tendency for egg parasitoids to obtain a refuge in large gall chambers at high gall midge densities (complex $\alpha_{\text{Pref:Diam}}$=
+`r round(filter(tidy_eggegg_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]; but contrast $\alpha_{\text{Pref:Diam}}$=
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` 
+[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]).
+
+<!--
+(contrast $\gamma_{\text{Pref:Pref}}$=
 `r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
@@
 \ref{fig:EggPtoid_Selection}).
-Larval parasitoids also dampened the linear relationship between probability of observing egg parasitoids and gall midge preference (contrast $\alpha_{\text{Pref}}$=
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
-), but this did not translate into an effect on directional selection 
+Larval parasitoids also dampened the linear relationship between probability of observing egg parasitoids and gall midge preference , but this did not translate into an effect on directional selection
 (contrast $\beta_{\text{Pref}}$=
@@
 Larval parasitoids did not alter directional, quadratic, or correlational selection on any other extended phenotypes of egg parasitoids (see Supplementary Material).
+-->
 
@@
     \begin{enumerate}
-    \item Gall midges experience fewer selective and genetic constraints in complex food webs.
+    \item Gall midges experience more selective and constraints in simple food webs.
     \end{enumerate}
@@
     \begin{enumerate}
-    \item \textbf{Key Result}: Fewer traits under directional selection in complex (1 of 3) vs.
-simple (3 of 3) food webs.
+    \item \textbf{Key Result}: More traits under directional selection in simple (3 of 3) vs.
+complex (1 of 3) food webs.
 Need to be wary of interpreting no selection on oviposition preference in complex food webs though.
@@
     \begin{enumerate}
-    \item \textbf{Key Result}: Fewer traits experience a decrease in additive genetic variance and fewer trait combinations experience selection for trait integration. 
+    \item \textbf{Key Result}: More traits experience a decrease in additive genetic variance and more trait combinations experience selection for trait integration in simple food webs. 
     \item \textbf{Implications}: The structure of the G-matrix is under less influence of selection in complex vs.
@@
     \begin{enumerate}
-    \item \textbf{Key Result}: Evidence of nonlinear selection on the extended phenotype of egg parasitoids.
-    \item \textbf{Implications}: Hints at a dynamic adaptive landscape in complex food webs.
+    \item \textbf{Key Result}: Evidence of selection on the extended phenotype of egg parasitoids.
+    \item \textbf{Implications}: Hints at a dynamic adaptive landscape and potential indirect evolutionary effects in complex food webs.
     \end{enumerate}
@@
 For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on the extended phenotype of egg parasitoids.
+The decrease in the probability of observing egg parasitoids at high gall-midge densities indicates the increasing impact of larval parasitoids.
 

### 2018-11-22 manuscript_complexity_selection.tex
updates through sending first draft to Jordi

\documentclass[11pt,]{article}
\usepackage{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Matthew A. Barbour\^{}\{1,2,\textbackslash{}ast\}; Christopher J. Greyson-Gaito\^{}\{1,3\}; Arezoo Sootodeh\^{}\{3\}; Brendan Locke\^{}\{4\}; Jordi Bascompte\^{}\{2\}},
            pdftitle={Phenotypic evolution is more constrained in simple food webs},
            colorlinks=true,
            citecolor=blue,
            urlcolor=black,
            linkcolor=black,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

%%% Use protect on footnotes to avoid problems with footnotes in titles
\let\rmarkdownfootnote\footnote%
\def\footnote{\protect\rmarkdownfootnote}

  \title{Phenotypic evolution is more constrained in simple food webs}
    \author{Matthew A. Barbour\(^{1,2,\ast}\) \\ Christopher J. Greyson-Gaito\(^{1,3}\) \\ Arezoo Sootodeh\(^{3}\) \\ Brendan Locke\(^{4}\) \\ Jordi Bascompte\(^{2}\)}
    \date{}

%%% From AmNat_MS_template.tex
%\documentclass[11pt]{article}
%\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
\usepackage{fullpage}
%\usepackage[authoryear,sectionbib,sort]{natbib}
\linespread{1.7}
%\usepackage[utf8]{inputenc}
\usepackage{lineno}

%%%%%%% Sections not currently working properly
%\usepackage{titlesec}
%\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
%\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
%\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
%\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}

%%% My added packages
%\usepackage{amsmath} % for matrices
%\usepackage{graphicx} % for organizing figures
%\usepackage{lmodern} % for tilde
%\usepackage[T1]{fontenc} % for tilde

%%%%%%%%% Previous - likely useful though
%\usepackage{setspace}\doublespacing
%\usepackage{float}
%\let\origfigure\figure
%\let\endorigfigure\endfigure
%\renewenvironment{figure}[1][2] {
%    \expandafter\origfigure\expandafter[H]
%} {
%    \endorigfigure
%}

\begin{document}

\maketitle

\noindent 1. University of British Columbia, Department of Zoology,
Vancouver, BC V6T 1Z4, Canada;

\noindent 2. University of Zurich, Department of Evolutionary Biology
and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich,
Switzerland;

\noindent 3. University of Guelph, Department of Integrative Biology,
Guelph, ON N1G 2W1, Canada;

\noindent 4. Humboldt State University, Department of Biological
Sciences, Arcata, CA 95521, USA.

\(^\ast\) Corresponding author; e-mail:
\href{mailto:matthew.barbour@ieu.uzh.ch}{\nolinkurl{matthew.barbour@ieu.uzh.ch}}

\bigskip

\emph{Manuscript elements}: Figure 1, figure 2, figure 3, figure 4. All
figures should be printed in color.

\bigskip

\emph{Keywords}: fitness landscape, host-parasitoid, natural selection,
G-matrix, community context, ecological networks.

\bigskip

\emph{Manuscript type}: Article.

\bigskip

\footnotesize Prepared using an \emph{Am. Nat.} inspired \LaTeX{}
template for Rmarkdown. \normalsize

\linenumbers{} \modulolinenumbers[3]

\newpage

\section{Abstract}\label{abstract}

Adaptive landscapes describe the selective constraints acting on
phenotypic evolution, but often treat the community context of evolving
populations as a ``black box''. In contrast, ecological networks provide
an explicit representation of the community context, yet often ignore
the role of natural selection. Global change is simplifying the
structure of ecological networks; however, we are currently in a poor
position to predict how these simplified communities will affect the
evolutionary potential of populations. Here, we integrate ecological
networks and adaptive landscapes to examine how changes in food-web
complexity shape evolutionary constraints. We conducted a field
experiment that manipulated the diversity of insect parasitoids
(food-web complexity) that were able to impose selection on an insect
herbivore. We then measured herbivore survival as a function of three
key phenotypic traits. We found that more traits were under selection in
simple vs.~complex food webs. The adaptive landscape was more neutral in
complex food webs because different parasitoid species impose different
selection pressures, minimizing relative fitness differences among
phenotypes. Our results suggest that phenotypic evolution becomes more
constrained in simplified food webs. This indicates that the
simplification of ecological communities may constrain the adaptive
potential of populations to future environmental change.

\newpage

\section{Introduction}\label{introduction}

The adaptive landscape provides a powerful framework for understanding
how natural selection has shaped the evolution of biodiversity ---from
genes, to phenotypes, to species (Wright 1931; Simpson 1944; Arnold,
Pfrender, and Jones 2001). More than a metaphor, the adaptive landscape
links quantitative genetic and phenotypic variation to evolution by
natural selection (Lande 1979; Stevan J. Arnold and Wade 1984a; Stevan
J. Arnold and Wade 1984b). Ecological interactions often play a key role
in shaping adaptive landscapes, as evidenced by the role of antagonistic
(Schluter 2000; Abrams 2000) and mutualistic (Bronstein, Alarcón, and
Geber 2006) interactions in driving evolutionary change. Although there
is clear evidence that pairwise interactions can shape the adaptive
landscape, we also know that most species interact with multiple species
in a community context (Darwin 1859). Understanding how the adaptive
landscape is shaped by community context represents a major frontier for
evolutionary ecologists (McPeek 2017; terHorst et al. 2018). Resolution
on this front is urgently needed though, given the rapid impacts of
climate change on ecological communities (Scheffers et al. 2016).

Ecological networks, such as a food web describing who eats whom,
provide an explicit representation of the community context. These
networks describe the interdependency of populations within an
ecological community, providing an effective framework for predicting
how the strength and organization of ecological interactions (network
structure) affect population and community dynamics (Bascompte and
Jordano 2014; McCann 2012). Nevertheless, these networks often lack
quantitative information on how ecological interactions influence
selection on phenotypic traits. Thus, it remains unclear how network
structure shapes adaptive landscapes of interacting populations. This
represents a major barrier in our current ability to predict how changes
in community context will affect phenotypic evolution.

Here, we integrate ecological networks and adaptive landscapes to
understand how community context constrains evolutionary change (Arnold
1992). Different aspects of evolutionary constraints can be inferred by
quantifying the slope and curvature of the adaptive landscape. For
example, the slope is determined by directional selection gradients
acting on each phenotypic trait and influences the trajectory of
evolutionary change (Lande 1979; Arnold 1992). Evolutionary trajectories
become more constrained with an increase in the number of traits under
selection, as this diminishes the number of optimal solutions (Arnold
2003). The curvature of the adaptive landscape can also constrain
evolution through its indirect effect on genetic constraints (Arnold
1992; Hansen and Houle 2008). Genetic constraints are largely governed
by a population's \textbf{G}-matrix ---the additive genetic variances
and covariances between traits (Hansen and Houle 2008). In general,
genetic constraints will increase with the number of traits under
directional or stabilizing selection, as this will decrease the additive
genetic variance in those traits (Hansen and Houle 2008). Genetic
constraints may also increase with the number of trait combinations
under correlational selection, as this type of selection decreases the
evolutionary independence of traits (Hansen and Houle 2008). If we want
to predict how community context constrains evolutionary change, we must
understand how ecological networks shape the adaptive landscape.

To examine the effect of network structure on adaptive landscapes, we
conducted a field experiment that manipulated the complexity of trophic
interactions (hereafter food-web complexity) associated with an abundant
insect herbivore (\emph{Iteomyia salicisverruca}; Family
Cecidomyiidae)(fig. \ref{fig:Conceptual}). The larvae of this herbivore
induce tooth-shaped galls when they feed on the developing leaves of
willow trees (\emph{Salix} sp., Russo 2006). These galls protect larva
from attack by generalist predators (e.g.~ants, spiders), but they
suffer high mortaltiy from egg and larval parasitoids (Barbour et al.
2016). We manipulated food-web complexity by either excluding the guild
of larval parasitoids (simple food web) or allowing both egg and larval
parasitoids to impose selection on gall midge traits (complex food web;
fig. \ref{fig:Conceptual}). Food-web complexity may influence the
adaptive landscape in a number of ways. For example, if each parasitoid
imposes directional selection on a different trait, then more complex
food webs may constrain evolution by increasing the number of traits
under selection. Alternatively, if parasitoids impose selection on
different values of a trait, then their selective effects would cancel
each other out in more complex food webs. To examine these different
possibilities (among others), we applied modern statistical methods to
quantify the effect of food-web complexity on the slope and curvature of
the gall midge's adaptive landscape. Taken together, our study gives
insight to how local extinctions, and concomitant decreases in food-web
complexity, may constrain the evolution of interacting populations.

\section{Methods}\label{methods}

\subsection{Study Site}\label{study-site}

We conducted our study within a four-year old common garden experiment
of coastal willow (\emph{Salix hookeriana}) located at Humboldt Bay
National Wildlife Refuge (HBNWR) (40 40'53``N, 124 12'4''W) near Loleta,
California, USA. This common garden consists of 26 different willow
genotypes that were collected from a single population of willows
growing around Humboldt Bay. Stem cuttings of each genotype (25
replicates per genotypes) were planted in a completely randomized design
in two hectares of a former cattle pasture at HBNWR. Willows at our
study site begin flowering in February and reach their peak growth in
early August. During this study, willows had reached 5 - 9m in height.
Further details on the genotyping and planting of the common garden are
available in Barbour et al. (2015).

\subsection{Manipulating Food-web
Complexity}\label{manipulating-food-web-complexity}

We setup our food-web manipulation across 128 plants soon after galls
began developing on willows in early June of 2013. These 128 plants came
from eight different plant genotypes that spanned the range of trait
variation observed in this willow population (Barbour et al. 2015). For
the complex food-web treatment (eight replicates per genotype), we used
flagging tape to mark 14 galled leaves per plant (\textasciitilde{}30
larvae), allowing the full suite of egg and larval parasitoids to impose
selection. Marking galls with flagging tape ensured that we compared
control and treatment galls with similar phenology when we collected
galls later in the season. For the simple food-web treatment, we
enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant
Prairie, WI, USA) to exclude three parasitoid species that attack during
larval development. This treatment did not exclude the egg parasitoid
\emph{Platygaster} sp., which attacks prior to gall initiation (larva
initiate gall development in Cecidomyiid midges: Gagné 1989). In late
August, we collected marked and bagged galls from each plant, placed
them into 30 mL vials and kept them in the lab for 4 months at room
temperature. We then opened galls under a dissecting scope and
determined whether larvae survived to pupation (our measure of fitness)
or were parasitized. Since we were interested in selection imposed by
parasitoids, we excluded unknown sources of mortality. For the food-web
treatment that excluded larval parasitoids (simple food web), we further
restricted our data by removing any incidental instances of parasitism
by a larval parasitoid. This represented less than 3\% of the
observations in this food-web treatment and allowed us to focus our
inferences of selection on those imposed by the egg parasitoid. Our
final dataset contains survival estimates for 1285 larvae from 613 galls
and 111 plants.

\subsection{Measuring Phenotypic
Traits}\label{measuring-phenotypic-traits}

We collected data on three different traits that we expected to
influence larval survival based on our previous work (Barbour et al.
2016) and others work with gall midges (Weis, Price, and Lynch 1983;
Heath, Abbot, and Stireman 2018). First, we measured gall diameter as
the size of each gall chamber to the nearest 0.01 mm at its maximum
diameter (perpendicular to the direction of plant tissue growth). Our
previous work has shown that larger galls are associated with higher
survival (Barbour et al. 2016). Second, we measured clutch size by
counting the number of chambers in each gall (Weis, Price, and Lynch
1983; Heath, Abbot, and Stireman 2018). All larvae collected from the
same multi-chambered gall were scored with the same clutch size. Third,
we measured oviposition (egg laying) preference as the density of larvae
observed on a plant in an independent survey. We did this randomly
sampling five branches per tree and counting the number of individual
gall chambers (number of larvae). We then converted these counts to a
measure of larval density per 100 shoots by counting the number of
shoots on the last branch we sampled. All larvae collected from the same
plant were scored with the same oviposition preference. Measuring larval
densities on plants in the field is a common method for measuring
oviposition preference (Gripenberg et al. 2010); however, caution must
be taken in inferring `preference' as larval densities can be influenced
by processes other than preference (Singer 1986). Fortunately, a couple
of features of our study system suggest that larval densities may be a
good proxy for oviposition preference. For example, since our data comes
from a randomized placement of plant genotypes in a common garden, there
is no consistent bias in which plant genotypes females are exposed to
while searching for oviposition sites. Also, egg predation is a minor
source of mortality for galling insects in general (Hawkins, Cornell,
and Hochberg 1997); therefore, we do not expect any prior egg predation
to bias our estimates of observed larval densities.

\subsection{Quantifying the Adaptive
Landscape}\label{quantifying-the-adaptive-landscape}

Our analyses consisted of three parts. First, we used generalized linear
mixed models (GLMM) to quantify selection surfaces \textemdash linear
and nonlinear relationships between absolute fitness (\(W\)) and
phenotypic traits (\(z_i\)) of individuals \textemdash in each food-web
treatment. Second, we translated selection surfaces into the scale of
relative fitness (\(w\)) in order to calculate selection gradients.
Third, we used our estimates of selection gradients to characterize the
slope and curvature of the adaptive landscape. Note that inferring
adaptive landscapes from selection surfaces assumes that trait
distributions are multivariate normal (Lande and Arnold 1983). To
approximate this assumption, we log-transformed clutch size and
square-root transformed oviposition preference. We then scaled all
phenotypic traits (mean=0 and SD=1) in order to calculate standardized
selection gradients that were comparable across traits and with other
studies of natural selection.

\textbf{Selection surface}: Since larval survival was our measure of
absolute fitness, we used a GLMM that assumed a binomial error
distribution (and logit-link function). To approximate the selection
surface, we modelled larval survival as a function of food-web treatment
as well as linear (\(\alpha_{z_i}\)), quadratic (\(\alpha_{z_i:z_i}\)),
and linear interactions (\(\alpha_{z_i:z_j}\)) between each trait. We
also allowed these trait-fitness relationships (\(\alpha\)) to vary
between food-web treatments. Note that to obtain valid estimates of
linear trait-fitness relationships, we removed nonlinear terms prior to
estimating linear relationships (Lande and Arnold 1983). Other
approaches have been advocated for approximating selection surfaces
(Schluter 1988); however, our approach enables us to calculate selection
gradients, and thus is more appropriate for approximating the adaptive
landscape (Arnold 2003). To account for the nonindependence of clutch
size (measured at gall level) and oviposition preference (measured at
plant level) as well as any independent effects of willow genotype on
larval survival, we modelled gall ID nested within plant ID nested
within genotype ID as random effects. Although statistical models with
random effects are not common in analyses of natural selection, we think
this is a mistake since modelling random effects can mitigate biased
estimates of selection due to environmental covariances between traits
and fitness (Rausher 1992). Since our end goal was to characterize the
relationship between mean trait values and mean fitness (adaptive
landscape), we assumed the mean value of our random effects
(i.e.~setting them to zero) when calculating trait-fitness
relationships. We then used parametric bootstrapping (1,000 replicates)
to estimate the effect of food-web treatment on larval survival as well
as trait-fitness relationships in each food-web treatment. To determine
whether trait-fitness relationships differed between food-web
treatments, we calculated the difference in bootstrapped replicates
between treatments.

\textbf{Selection gradients}: We used the method of Janzen and Stern
(1998) to translate trait-fitness relationships (\(\alpha\)) into the
scale of relative fitness in order to calculate directional
(\(\beta_{z_i}\)), quadratic (\(\gamma_{z_i:z_i}\)), and correlational
(\(\gamma_{z_i:z_j}\)) selection gradients. Briefly, this method
calculates the average gradient of selection surfaces by multiplying the
average of \(W(z)[1-W(z)]\) by each regression coefficient (e.g.
\(\alpha_{z_i}\), \(\alpha_{z_i:z_i}\), or \(\alpha_{z_i:z_j}\)). We
then divided this average gradient by mean fitness (\(\bar W\)) to put
it on the scale of relative fitness, and thus interpretable as a
selection gradient. We estimated selection gradients separately for each
food-web treatment. Note that we doubled all quadratic terms prior to
calculating selection gradients to put them on the same scale as
estimates of directional and correlational selection (Stinchcombe et al.
2008).

\textbf{Adaptive landscape}: We took advantage of existing theory that
translates estimates of selection gradients to the adaptive landscape
(Phillips and Arnold 1989; Arnold 2003). The shape of the adaptive
landscape can be described by both its slope and curvature, each of
which describe different aspects of constraints on phenotypic evolution.
Specifically, the slope corresponds to the column vector of directional
selection gradients, which in our study corresponds to:

\[\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} \]
This slope describes the selective constraints acting on the trajectory
of phenotypic evolution, which is governed by the `Lande equation',
\(\Delta \bar z=\text{G}\beta\) (Lande 1979). Quantitative predictions
of evolutionary trajectories requires knowledge of a population's
\textbf{G}-matrix; however, we can gain qualitative insight to
evolutionary constraints by counting the number of phenotypic traits
under directional selection (selective constraints, Arnold 1992).

The curvature (\textbf{C}) of the adaptive landscape is a matrix that is
determined by directional, quadratic, and correlational selection
gradients, such that
\boldmath\(\text{C}=\gamma - \beta \beta^\text{T}\), or more explicitly:

\[\textbf{C} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}\]
\[\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}\]

Note that we ommitted the upper triangle of each matrix for clarity
since it is simply the reflection of the lower triangle. This curvature
matrix describes the indirect effects of selection on genetic
constraints within a generation
(\(\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}\)).
For example, the sign of diagonal terms of the curvature matrix dictate
whether selection will increase (+), decrease (-), or cause no change
(0) in the additive genetic variance of a trait. Similarly, any nonzero
covariance terms (off-diagonal) are indicative of selection for trait
integration (less trait independence). Therefore, we can infer the
indirect effects of selection on genetic constraints by counting the
number of negative signs along the diagonal (decrease in additive
genetic variance) and the number of nonzero terms along the off-diagonal
(trait integration) of the curvature matrix.

\subsection{Adjusting for biased measurements of
selection}\label{adjusting-for-biased-measurements-of-selection}

Rather than imposing selection, parasitoids may themselves influence the
expression of herbivore traits which could bias measurements of
selection. In our system, it was plausible that parasitoids may
influence chamber diameter by altering larval feeding behavior or
killing larvae before they complete their development. To estimate this
potential bias, we subset our data to only include galls where there was
variation in larval survival within the same gall (i.e.~1 \textgreater{}
mean survival \textgreater{} 0). If we assume that larvae within each
gall should have similar chamber diameters because they come from the
same clutch and experience the same local environment (an assumption our
data supports: gall ID explains 54\% of the variance in chamber
diameter), then the relationship between chamber diameter and larval
survival in this data subset represents the effect of parasitism on
trait expression (i.e.~bias). We used a GLMM with the same structure as
described above except that we only modelled a linear relationship
between chamber diameter and larval survival (\(\alpha_{\text{Diam}}\)).
We detected a positive bias in both food-web treatments (complex
\(\alpha_{\text{Diam}}\)= 0.36 {[}0.05, 0.67{]}; simple
\(\alpha_{\text{Diam}}\)= 0.42 {[}0.01, 0.82{]}), indicating that
unadjusted relationships would overestimate the strength of selection on
chamber diameter. To account for this bias, we substracted our mean
estimates of bias from our estimates with the full dataset prior to
calculating chamber diameter's trait-fitness relationship and
directional selection gradient.

\subsection{Measuring selection on the extended phenotype of egg
parasitoids}\label{measuring-selection-on-the-extended-phenotype-of-egg-parasitoids}

Once parasitized, the gall phenotype becomes the extended phenotype of
the egg parasitoid. This extended phenotype may influence the egg
parasitoid's survival in the face of larval parasitoids, and thus
experiences selection. Our food-web manipulation allows us to measure
selection imposed by larval parasitoids on the extended phenotype of egg
parasitoids. Using the same models as described above, we substituted
egg parasitism as our response variable to quantify trait-fitness
relationships and selection gradients acting on the egg parasitoid. Note
that we cannot test the effect of food-web complexity on the egg
parasitoid's adaptive landscape ---we can only estimate the selection
imposed by larval parasitoids. This comparison is still useful though in
determining the extent to which the community context may have indirect
evolutionary effects by altering selection on multiple interacting
populations.

All analyses and visualizations were conducted in R (R Core Team 2018).
Unless otherwise noted, we report mean estimates of trait-fitness
relationships and selection gradients with 95\% confidence intervals in
brackets. Note that for visualizing the adaptive landscape we restrict
trait axes to \(\pm 1\) SD of the mean trait value. This emphasizes the
fact that we can only reliably estimate the shape of the adaptive
landscape near the mean phenotype of the population (Arnold, Pfrender,
and Jones 2001). We also plot mean larval survival on a natural log
scale to accurately reflect the shape of the adaptive landscape (Arnold
2003).

\section{Results}\label{results}

\subsection{Food-web complexity reduces selective
constraints}\label{food-web-complexity-reduces-selective-constraints}

\indent We found that more gall midge traits experienced directional
selection in the simple (3 of 3) vs.~complex food webs (1 of 3)(table
\ref{Table:Gradients}). For example, we observed directional selection
for smaller clutch sizes in the simple food web, but there was no
evidence of selection acting on this trait in the complex food web
(table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This
absence of selection appeared to be a result of conflicting selection
pressures imposed by each guild of parasitoids (fig.
\ref{fig:UV_Landscape}C). Specifically, when we subset our data to focus
on differences between parasitoid guilds, we found that larval
parasitoids actually impose directional selection for larger clutch
sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.03, 0.23{]}). In the simple
food web, we also observed clear evidence of directional selection for
midges to avoid ovipositing on plants with high densities of
conspecifics (table \ref{Table:Gradients}; fig.
\ref{fig:UV_Landscape}B); however, this relationship was weaker in
complex food webs (table \ref{Table:Gradients}). This was likely a
result of larval parasitoids imposing greater mortality on egg
parasitoids at high gall midge densities (see Selection on the extended
phenotype of egg parasitoids section), and thus a less than additive
effect on gall midges. Chamber diameter experienced positive directional
selection in both food-web treatments, but selection was 65\% higher in
complex food webs (table \ref{Table:Gradients}; fig.
\ref{fig:UV_Landscape}). This was not due to any difference between egg
and larval parasitoids (fig. \ref{fig:UV_Landscape}), but was due to the
lower average survival in complex food webs (contrast -0.26 {[}-0.12,
-0.42{]}).

\subsection{Food-web complexity reduces genetic
constraints}\label{food-web-complexity-reduces-genetic-constraints}

\indent The curvature of the adaptive landscape indirectly affects
genetic constraints and is influenced by directional, quadratic, and
correlational selection gradients. Our food-web treatment did not alter
correlational selection for any combination of traits (table
\ref{Table:Gradients}). Similarly, our food-web treatment did not
influence quadratic selection on either chamber diameter or clutch size
(table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}A,C). In
contrast, our food-web treatment did alter quadratic selection acting on
oviposition preference (table \ref{Table:Gradients}). The negative
relationship between oviposition preference and larval survival dampened
at high densities in complex, but not simple food webs (fig.
\ref{fig:UV_Landscape}). This dampened relationship was partly due to a
trend for nonlinear selection imposed by larval parasitoids
(\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.01, 0.42{]}), but was also
magnified by the lower average survival in complex food webs.

To estimate the net effect of food-web complexity on the curvature
(\(C\)) of the adaptive landscape, we only retained nonzero selection
gradients (i.e.~95\% CI did not overlap zero) prior to calculating the
curvature (\(\gamma - \beta \beta^\text{T}\)) in each food-web
treatment. We found that the curvatures of the adaptive landscape
exhibited the following structures:

\[\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}\]

\[\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
-0.12 &  &  \\  
0 & 0 &  \\  
0 & 0 & 0.33 \end{pmatrix}\]

\[\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
-0.04 &  &  \\  
0.02 & -0.01 &  \\  
0.03 & -0.01 & -0.03 \end{pmatrix}\]

The structure of these matrices indicate that there are more selective
constraints imposed on the gall midge in the simple (6 of 6) vs.~complex
(1 of 6) food web. Simple food webs acted to decrease genetic variance
for all three phenotypic traits (negative diagonal terms), whereas only
one trait (chamber diameter) experienced a decrease in additive genetic
variance in the complex food web. For genetic covariances, the simple
food web favored integration among all three phenotypic traits (nonzero
off-diagonal terms), and thus constraints along all three axes of
covariance (fig. \ref{fig:MV_Landscape}). In contrast, there was no
strong evidence of trait integration in the complex food web (fig.
\ref{fig:MV_Landscape}).

\subsection{Selection on the extended phenotype of egg
parasitoids}\label{selection-on-the-extended-phenotype-of-egg-parasitoids}

Gall midge preference influenced the probability of observing egg
parasitoids in complex vs.~simple food webs (contrast
\(\alpha_{\text{Pref}}\)= 1 {[}0.03, 2.22{]} ). Specifically, larval
parasitoids decreased the probability of observing egg parasitoids at
high gall midge densities (fig. \ref{fig:EggPtoid_Selection}). Note
however that this trait-fitness relationship did not translate into a
significant difference in selection (contrast \(\beta_{\text{Pref}}\)=
0.24 {[}-0.09, 0.62{]} ). This was likely because there was a tendency
(albeit not statistically signficant) for a lower probability of
egg-parasitoid survival in complex vs.~simple food webs (contrast=0.1
{[} -0.08, 0.31{]}), which masks this trait-fitness relationship. We
also observed two other interesting trends, although neither
significantly differed between treatments. Specifically, there was a
tendency for the impact of larval parasitoids to increase nonlinearly at
higher gall midge densities (fig. \ref{fig:EggPtoid_Selection}; complex
\(\alpha_{\text{Pref:Pref}}\)= -0.49 {[}-1.08, -0.1{]}; but contrast
\(\alpha_{\text{Pref:Pref}}\)= 0.46 {[}-0.03, 1.1{]}). There was also a
tendency for egg parasitoids to obtain a refuge in large gall chambers
at high gall midge densities (complex \(\alpha_{\text{Pref:Diam}}\)=
0.25 {[}0.02, 0.5{]}; but contrast \(\alpha_{\text{Pref:Diam}}\)= -0.25
{[}-0.57, 0.04{]}).

\section{Discussion}\label{discussion}

\begin{enumerate}

 \item Summary of key results
    \begin{enumerate}
    \item Gall midges experience more selective and constraints in simple food webs.
    \end{enumerate}

 \item Natural history and comparison to other studies of natural selection in galling insects.
    \begin{enumerate}
    \item \textbf{Important Studies for Comparison}: @Abrahamson1997; @Weis1983; @Heath2018; Start, Weis, and Gilbert In Press Am. Nat; @Start2016; @Start2018urbanization; Peter Price's work; Timothy Craig's work; Cheryl Briggs work.
    \item \textbf{Topics to discuss}: Persistent pattern in selection for larger galls; Contrasting effects of egg and larval parasitoids on clutch size; Nonlinear selection at high gall densities is likely reflective of the poorer searching ability of larval vs. egg parasitoids (and thus it saturates more quickly).  
    \end{enumerate}

 \item Selective constraints:
    \begin{enumerate}
    \item \textbf{Key Result}: More traits under directional selection in simple (3 of 3) vs. complex (1 of 3) food webs. Need to be wary of interpreting no selection on oviposition preference in complex food webs though. Even if there is selection on oviposition preference, this does not change our qualitative result.
    \item \textbf{Implications}: The trajectory of phenotypic evolution is less constrained in complex vs. simple food webs. In other words, there are more potential adaptive peaks in complex food webs. 
    \end{enumerate}

 \item Indirect effects of selection on genetic constraints: 
    \begin{enumerate}
    \item \textbf{Key Result}: More traits experience a decrease in additive genetic variance and more trait combinations experience selection for trait integration in simple food webs. 
    \item \textbf{Implications}: The structure of the G-matrix is under less influence of selection in complex vs. simple food webs. Thus the trajectory of phenotypic evolution may be dictated more by genetic rather than selective constraints. This is in line with empirical evidence (from complex natural systems) that evolution tends to proceed along genetic lines of least resistance [@Schluter1996].
    \end{enumerate}

 \item Indirect evolutionary effects:
    \begin{enumerate}
    \item \textbf{Key Result}: Evidence of selection on the extended phenotype of egg parasitoids.
    \item \textbf{Implications}: Hints at a dynamic adaptive landscape and potential indirect evolutionary effects in complex food webs.
    \end{enumerate}

 \item Caveats: 
    \begin{enumerate} 
    \item \textbf{Key Caveat}: Experimental artifact of lower larval survival in complex food-web treatment.
    \item \textbf{Implications}: Artificially increased the magnitude of selection in complex food webs. Note however, that this does not qualitatively change any of our results. In fact, we are actually underestimating the constraints imposed by our simple food-web treatment. This is because the egg parasitoids would be released from their intraguild predator, and thus could increase in abundance over future generations and impose stronger selection on gall midges. 
    \end{enumerate}

\item Conclusions

\end{enumerate}

\section{Acknowledgements}\label{acknowledgements}

\section{References}\label{references}

\hypertarget{refs}{}
\hypertarget{ref-Abrams2000}{}
Abrams, Peter A. 2000. ``The Evolution of Predator-Prey Interactions:
Theory and Evidence.'' \emph{Annual Review of Ecology and Systematics}
31 (1): 79--105.
doi:\href{https://doi.org/10.1146/annurev.ecolsys.31.1.79}{10.1146/annurev.ecolsys.31.1.79}.

\hypertarget{ref-Arnold1992}{}
Arnold, Stevan J. 1992. ``Constraints on Phenotypic Evolution.''
\emph{The American Naturalist} 140. University of Chicago Press:
S85--S107.

\hypertarget{ref-Arnold2003}{}
Arnold, Stevan J. 2003. ``Performance Surfaces and Adaptive
Landscapes1.'' \emph{Integrative and Comparative Biology} 43 (3):
367--75.
doi:\href{https://doi.org/10.1093/icb/43.3.367}{10.1093/icb/43.3.367}.

\hypertarget{ref-Arnold1984applications}{}
Arnold, Stevan J., and Michael J. Wade. 1984a. ``On the Measurement of
Natural and Sexual Selection: Applications.'' \emph{Evolution} 38 (4):
720--34. \url{http://www.jstor.org/stable/2408384}.

\hypertarget{ref-Arnold1984theory}{}
---------. 1984b. ``On the Measurement of Natural and Sexual Selection:
Theory.'' \emph{Evolution} 38 (4): 709--19.
\url{http://www.jstor.org/stable/2408383}.

\hypertarget{ref-Arnold2001}{}
Arnold, Stevan J., Michael E. Pfrender, and Adam G. Jones. 2001. ``The
Adaptive Landscape as a Conceptual Bridge Between Micro- and
Macroevolution.'' \emph{Genetica} 112 (1): 9--32.
doi:\href{https://doi.org/10.1023/A:1013373907708}{10.1023/A:1013373907708}.

\hypertarget{ref-Barbour2016}{}
Barbour, Matthew A., Miguel A. Fortuna, Jordi Bascompte, Joshua R.
Nicholson, Riitta Julkunen-Tiitto, Erik S. Jules, and Gregory M.
Crutsinger. 2016. ``Genetic Specificity of a Plantinsect Food Web:
Implications for Linking Genetic Variation to Network Complexity.''
\emph{Proceedings of the National Academy of Sciences} 113 (8). National
Academy of Sciences: 2128--33.
doi:\href{https://doi.org/10.1073/pnas.1513633113}{10.1073/pnas.1513633113}.

\hypertarget{ref-Barbour2015}{}
Barbour, Matthew A., Mariano A. Rodriguez-Cabal, Elizabeth T. Wu, Riitta
Julkunen-Tiitto, Carol E. Ritland, Allyson E. Miscampbell, Erik S.
Jules, and Gregory M. Crutsinger. 2015. ``Multiple Plant Traits Shape
the Genetic Basis of Herbivore Community Assembly.'' \emph{Functional
Ecology} 29 (8): 995--1006.
doi:\href{https://doi.org/10.1111/1365-2435.12409}{10.1111/1365-2435.12409}.

\hypertarget{ref-Bascompte2014}{}
Bascompte, Jordi, and Pedri Jordano. 2014. \emph{Mutualistic Networks}.
Princeton University Press.
\url{http://www.jstor.org/stable/j.ctt5hhnpq}.

\hypertarget{ref-Bronstein2006}{}
Bronstein, Judith L., Ruben Alarcón, and Monica Geber. 2006. ``The
Evolution of Plant--insect Mutualisms.'' \emph{New Phytologist} 172 (3):
412--28.
doi:\href{https://doi.org/10.1111/j.1469-8137.2006.01864.x}{10.1111/j.1469-8137.2006.01864.x}.

\hypertarget{ref-Darwin1859}{}
Darwin, Charles. 1859. \emph{On the Origin of Species by Means of
Natural Selection}. London: Murray.

\hypertarget{ref-Gagne1989}{}
Gagné, R J. 1989. ``The Plant-Feeding Gall Midges of North America.''
agris.fao.org.

\hypertarget{ref-Gripenberg2010}{}
Gripenberg, Sofia, Peter J. Mayhew, Mark Parnell, and Tomas Roslin.
2010. ``A Meta-Analysis of Preference--performance Relationships in
Phytophagous Insects.'' \emph{Ecology Letters} 13 (3): 383--93.
doi:\href{https://doi.org/10.1111/j.1461-0248.2009.01433.x}{10.1111/j.1461-0248.2009.01433.x}.

\hypertarget{ref-Hansen2008}{}
Hansen, T F, and D Houle. 2008. ``Measuring and Comparing Evolvability
and Constraint in Multivariate Characters.'' \emph{J. Evol. Biol.} 21
(5): 1201--19.

\hypertarget{ref-Hawkins1997}{}
Hawkins, Bradford A., Howard V. Cornell, and Michael E. Hochberg. 1997.
``Predators, Parasitoids, and Pathogens as Mortality Agents in
Phytophagous Insect Populations.'' \emph{Ecology} 78 (7): 2145--52.
doi:\href{https://doi.org/10.1890/0012-9658(1997)078\%5B2145:PPAPAM\%5D2.0.CO;2}{10.1890/0012-9658(1997)078{[}2145:PPAPAM{]}2.0.CO;2}.

\hypertarget{ref-Heath2018}{}
Heath, Jeremy J., Patrick Abbot, and John O. Stireman. 2018. ``Adaptive
Divergence in a Defense Symbiosis Driven from the Top down.'' \emph{The
American Naturalist} 192 (1): E21--E36.
doi:\href{https://doi.org/10.1086/697446}{10.1086/697446}.

\hypertarget{ref-Janzen1998}{}
Janzen, Fredric J., and Hal S. Stern. 1998. ``Logistic Regression for
Empirical Studies of Multivariate Selection.'' \emph{Evolution} 52 (6):
1564--71.
doi:\href{https://doi.org/10.1111/j.1558-5646.1998.tb02237.x}{10.1111/j.1558-5646.1998.tb02237.x}.

\hypertarget{ref-Lande1979}{}
Lande, Russell. 1979. ``Quantitative Genetic Analysis of Multivariate
Evolution, Applied to Brain:body Size Allometry.'' \emph{Evolution} 33
(1Part2): 402--16.
doi:\href{https://doi.org/10.1111/j.1558-5646.1979.tb04694.x}{10.1111/j.1558-5646.1979.tb04694.x}.

\hypertarget{ref-Lande1983}{}
Lande, Russell, and Stevan J. Arnold. 1983. ``The Measurement of
Selection on Correlated Characters.'' \emph{Evolution} 37 (6): 1210--26.
\url{http://www.jstor.org/stable/2408842}.

\hypertarget{ref-McCann2012}{}
McCann, Kevin S. 2012. \emph{Food Webs}. Princeton University Press.
\url{http://www.jstor.org/stable/j.ctt7rr0s}.

\hypertarget{ref-McPeek2017}{}
McPeek, Mark A. 2017. \emph{Evolutionary Community Ecology}. Princeton
University Press. \url{http://www.jstor.org/stable/j.ctt1p0vjqn}.

\hypertarget{ref-Phillips1989}{}
Phillips, Patrick C., and Stevan J. Arnold. 1989. ``Visualizing
Multivariate Selection.'' \emph{Evolution} 43 (6): 1209--22.
doi:\href{https://doi.org/10.1111/j.1558-5646.1989.tb02569.x}{10.1111/j.1558-5646.1989.tb02569.x}.

\hypertarget{ref-R2018}{}
R Core Team. 2018. \emph{R: A Language and Environment for Statistical
Computing}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\hypertarget{ref-Rausher1992}{}
Rausher, Mark D. 1992. ``THE Measurement of Selection on Quantitative
Traits: BIASES Due to Environmental Covariances Between Traits and
Fitness.'' \emph{Evolution} 46 (3): 616--26.
doi:\href{https://doi.org/10.1111/j.1558-5646.1992.tb02070.x}{10.1111/j.1558-5646.1992.tb02070.x}.

\hypertarget{ref-Russo2006}{}
Russo, Ron. 2006. \emph{Field Guide to Plant Galls of California and
Other Western States}. 1st ed. University of California Press.
\url{http://www.jstor.org/stable/10.1525/j.ctt1pnc33}.

\hypertarget{ref-Scheffers2016}{}
Scheffers, Brett R., Luc De Meester, Tom C. L. Bridge, Ary A. Hoffmann,
John M. Pandolfi, Richard T. Corlett, Stuart H. M. Butchart, et al.
2016. ``The Broad Footprint of Climate Change from Genes to Biomes to
People.'' \emph{Science} 354 (6313). American Association for the
Advancement of Science.
doi:\href{https://doi.org/10.1126/science.aaf7671}{10.1126/science.aaf7671}.

\hypertarget{ref-Schluter1988}{}
Schluter, Dolph. 1988. ``ESTIMATING the Form of Natural Selection on a
Quantitative Trait.'' \emph{Evolution} 42 (5): 849--61.
doi:\href{https://doi.org/10.1111/j.1558-5646.1988.tb02507.x}{10.1111/j.1558-5646.1988.tb02507.x}.

\hypertarget{ref-Schluter2000}{}
---------. 2000. ``Ecological Character Displacement in Adaptive
Radiation.'' \emph{The American Naturalist} 156 (S4): S4--S16.
\url{http://www.jstor.org/stable/10.1086/303412}.

\hypertarget{ref-Simpson1944}{}
Simpson, George Gaylord. 1944. \emph{Tempo and Mode in Evolution}.
Columbia University Press.

\hypertarget{ref-Singer1986}{}
Singer, Michael C. 1986. ``The Definition and Measurement of Oviposition
Preference in Plant-Feeding Insects.'' In \emph{Insect-Plant
Interactions}, edited by James R. Miller and Thomas A. Miller, 65--94.
New York, NY: Springer New York.
doi:\href{https://doi.org/10.1007/978-1-4612-4910-8_3}{10.1007/978-1-4612-4910-8\_3}.

\hypertarget{ref-Stinchcombe2008}{}
Stinchcombe, John R, Aneil F Agrawal, Paul A Hohenlohe, Stevan J Arnold,
and Mark W Blows. 2008. ``Estimating Nonlinear Selection Gradients Using
Quadratic Regression Coefficients: Double or Nothing?'' \emph{Evolution}
62 (9): 2435--40.

\hypertarget{ref-terHorst2018}{}
terHorst, Casey P, Peter C Zee, Katy D Heath, Thomas E Miller, Abigail I
Pastore, Swati Patel, Sebastian J Schreiber, Michael J Wade, and Matthew
R Walsh. 2018. ``Evolution in a Community Context: Trait Responses to
Multiple Species Interactions*.'' \emph{Am. Nat.}, January. University
of Chicago PressChicago, IL.

\hypertarget{ref-Weis1983}{}
Weis, Arthur E., Peter W. Price, and Michael Lynch. 1983. ``Selective
Pressures on Clutch Size in the Gall Maker Asteromyia Carbonifera.''
\emph{Ecology} 64 (4): 688--95.
\url{http://www.jstor.org/stable/1937190}.

\hypertarget{ref-Wright1931}{}
Wright, Sewall. 1931. ``EVOLUTION in Mendelian Populations.''
\emph{Genetics} 16 (2). Genetics: 97--159.
\url{http://www.genetics.org/content/16/2/97}.

\newpage

\section{Tables}\label{tables}

\begin{table}[h]
\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
\label{Table:Gradients}
\centering
\begin{tabular}{lccc}
\\ 
\hline
\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
\hline
$\beta_{\text{Diam}}$ & 
\textbf{
0.34 [
0.22,
0.47] }& 
\textbf{
0.21 [
0.13,
0.3] }&

-0.13 [
-0.26,
0.01] \\

$\beta_{\text{Clutch}}$ & 
0.06 [
-0.04,
0.17] & 
\textbf{
-0.09 [
-0.18,
-0.02] }& 
\textbf{
-0.15 [
-0.29,
-0.02] }\\

$\beta_{\text{Pref}}$ &
-0.12 [
-0.29,
0.05] & 
\textbf{
-0.16 [
-0.25,
-0.07] }&

-0.04 [
-0.22,
0.14] \\

$\gamma_{\text{Diam,Diam}}$ &
0.14 [
-0.06,
0.32] &

0.1 [
-0.03,
0.25] &

-0.04 [
-0.27,
0.2] \\

$\gamma_{\text{Clutch,Clutch}}$ & 
-0.05 [
-0.25,
0.16] &

-0.12 [
-0.27,
0.03] &

-0.06 [
-0.33,
0.19] \\

$\gamma_{\text{Pref,Pref}}$ & 
\textbf{
0.33 [
0.06,
0.64] }&

0.01 [
-0.14,
0.17] & 
\textbf{
-0.32 [
-0.66,
0] }\\

$\gamma_{\text{Diam,Clutch}}$ & 
-0.05 [
-0.17,
0.08] &

-0.07 [
-0.15,
0.02] &

-0.02 [
-0.16,
0.13] \\

$\gamma_{\text{Diam,Pref}}$ & 
-0.13 [
-0.28,
0] &

-0.02 [
-0.09,
0.06] &

0.12 [
-0.05,
0.29] \\

$\gamma_{\text{Clutch,Pref}}$ & 
0.03 [
-0.11,
0.18] &

0 [
-0.07,
0.07] &

-0.03 [
-0.19,
0.12] \\ 
\hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
\end{table}

\newpage

\begin{table}[h]
\caption{Relationship between absolute fitness (larval survival) and phenotypic traits of gall midges in complex vs. simple food webs.}
\label{Table:Coefs}
\centering
\begin{tabular}{lccc}
\\ 
\hline
\textbf{Coefficient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
\hline
$\alpha_{\text{Diam}}$ & 
\textbf{
1.14 [
0.73,
1.57] }& 
\textbf{
1.1 [
0.68,
1.58] }&

-0.04 [
-0.57,
0.51] \\

$\alpha_{\text{Clutch}}$ & 
0.21 [
-0.13,
0.57] & 
\textbf{
-0.47 [
-0.94,
-0.09] }& 
\textbf{
-0.68 [
-1.27,
-0.13] }\\

$\alpha_{\text{Pref}}$ &
-0.41 [
-0.97,
0.15] & 
\textbf{
-0.84 [
-1.35,
-0.36] }&

-0.43 [
-1.16,
0.25] \\

$\alpha_{\text{Diam,Diam}}$ &
0.23 [
-0.1,
0.54] &

0.27 [
-0.07,
0.65] &

0.04 [
-0.43,
0.52] \\

$\alpha_{\text{Clutch,Clutch}}$ & 
-0.09 [
-0.42,
0.26] &

-0.31 [
-0.71,
0.08] &

-0.22 [
-0.77,
0.31] \\

$\alpha_{\text{Pref,Pref}}$ & 
\textbf{
0.56 [
0.1,
1.07] }&

0.03 [
-0.38,
0.46] &

-0.52 [
-1.18,
0.09] \\

$\alpha_{\text{Diam,Clutch}}$ & 
-0.16 [
-0.57,
0.25] &

-0.35 [
-0.78,
0.08] &

-0.19 [
-0.78,
0.44] \\

$\alpha_{\text{Diam,Pref}}$ & 
-0.44 [
-0.95,
0.01] &

-0.09 [
-0.5,
0.3] &

0.36 [
-0.27,
0.97] \\

$\alpha_{\text{Clutch,Pref}}$ & 
0.1 [
-0.37,
0.59] &

0 [
-0.37,
0.38] &

-0.1 [
-0.69,
0.49] \\ 
\hline
\end{tabular}
\bigskip{}
\\
{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\alpha_{\text{Diam}}$ has been adjusted for bias.}
\end{table}

\newpage

\section{Figure Legends}\label{figure-legends}

\textbf{Figure \ref{fig:Conceptual}}: Experimental manipulation of
food-web complexity associated with a leaf-galling midge (\emph{Iteomyia
salicisverruca}) feeding on the willow \emph{Salix hookeriana}. In the
complex food-web treatment (A), we allowed the full suite of egg (blue
rectangle) and larval (yellow rectangle) parasitoids to impose
selection. In the simple food-web treatment (B), we used mesh bags to
exclude the guild of larval parasitoids, only allowing the egg
parasitoid (\emph{Platygaster} sp.) to impose selection. Black arrows
denote the flow of energy in this network of trophic interactions.
Larval parasitoids include the following species (from left to right):
\emph{Mesopolobus} sp. (Family: Pteromalidae); \emph{Tetrastichus} sp.
(Family: Eulophidae); and \emph{Torymus} sp. (Family: Torymidae).

\textbf{Figure \ref{fig:UV_Landscape}}: Adaptive landscape of gall midge
phenotypes in complex vs.~simple food webs. Each panel corresponds to a
different phenotypic trait: chamber diameter (A); oviposition preference
(B); and clutch size (C). Solid lines represent selection experienced in
complex (orange) and simple (blue) food webs. Transparent lines
represent bootstrapped replicates to show the uncertainty in selection.
For clarity, we only display 100 bootstraps even though inferences are
based on 1,000 replicates. Solid yellow lines represent selection
imposed by larval parasitoids in the complex food web. Note that mean
larval survival is plotted on a natural log scale to accurately reflect
the adaptive landscape.

\textbf{Figure \ref{fig:MV_Landscape}}: Two dimensional view of adaptive
landscapes of gall midge phenotypes in complex vs.~simple food webs.
Each panel corresponds to a different combination of phenotypic traits:
clutch size and chamber diameter (A); clutch size and oviposition
preference (B); oviposition preference and chamber diameter (C).
Selection favors trait integration for each combination of traits in
simple food webs, whereas there is no strong evidence for trait
integration in complex food webs. Note that mean larval survival is
plotted on a natural log scale to accurately reflect the adaptive
landscape.

\textbf{Figure \ref{fig:EggPtoid_Selection}}: Selection imposed by
larval parasitoids on the extended phenotype of egg parasitoids
(\emph{Platygaster} sp.). The solid line represents the average
difference in the probability of observing the egg parasitoid in complex
vs.~simple food webs as a function of gall midge oviposition preference.
Transparent lines represent bootstrapped replicates to show the
uncertainty in selection. For clarity, we only display 100 bootstraps
even though inferences are based on 1,000 replicates. The decrease in
the probability of observing egg parasitoids at high gall-midge
densities indicates the increasing impact of larval parasitoids.

\begin{figure}
\centering
\includegraphics{analyses/complex_simple_foodwebs.jpeg}
\caption{\label{fig:Conceptual}Experimental manipulation of food-web
complexity associated with a leaf-galling midge (\emph{Iteomyia
salicisverruca}) feeding on the willow \emph{Salix hookeriana}. In the
complex food-web treatment (A), we allowed the full suite of egg (blue
rectangle) and larval (yellow rectangle) parasitoids to impose
selection. In the simple food-web treatment (B), we used mesh bags to
exclude the guild of larval parasitoids, only allowing the egg
parasitoid (\emph{Platygaster} sp.) to impose selection. Black arrows
denote the flow of energy in this network of trophic interactions.
Larval parasitoids include the following species (from left to right):
\emph{Mesopolobus} sp. (Family: Pteromalidae); \emph{Tetrastichus} sp.
(Family: Eulophidae); and \emph{Torymus} sp. (Family: Torymidae).}
\end{figure}

\begin{figure}
\centering
\includegraphics{analyses/UV_landscapes.pdf}
\caption{\label{fig:UV_Landscape}}
\end{figure}

\begin{figure}
\centering
\includegraphics{analyses/MV_landscapes.pdf}
\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
landscapes of gall midge phenotypes in complex vs.~simple food webs.
Each panel corresponds to a different combination of phenotypic traits:
clutch size and chamber diameter (A); clutch size and oviposition
preference (B); oviposition preference and chamber diameter (C).
Selection favors trait integration for each combination of traits in
simple food webs, whereas there is no strong evidence for trait
integration in complex food webs. Note that mean larval survival is
plotted on a natural log scale to accurately reflect the adaptive
landscape.}
\end{figure}

\begin{figure}
\centering
\includegraphics{analyses/selection_on_Platygaster.pdf}
\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
parasitoids on the extended phenotype of egg parasitoids
(\emph{Platygaster} sp.). The solid line represents the average
difference in the probability of observing the egg parasitoid in complex
vs.~simple food webs as a function of gall midge oviposition preference.
Transparent lines represent bootstrapped replicates to show the
uncertainty in selection. For clarity, we only display 100 bootstraps
even though inferences are based on 1,000 replicates. The decrease in
the probability of observing egg parasitoids at high gall-midge
densities indicate that larval parasitoids impose nonlinear selection on
the extended phenotype of egg parasitoids.}
\end{figure}

\end{document}

### 2018-11-22 manuscript.Rmd
change title

@@
 ---
-title: Phenotypic evolution is more constrained in simple food webs
+title: Phenotypic evolution is more constrained in simpler food webs
 #  | Food-web complexity simplifies the adaptive landscape of an insect herbivore

### 2018-11-22 manuscript.Rmd
incorporate Jordi's feedback into Abstract

@@
 
-Adaptive landscapes describe the selective constraints acting on phenotypic evolution, but often treat the community context of evolving populations as a ``black box''.
-In contrast, ecological networks provide an explicit representation of the community context, yet often ignore the role of natural selection.
-Global change is simplifying the structure of ecological networks; however, we are currently in a poor position to predict how these simplified communities will affect the evolutionary potential of populations.
-Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
+Global change is simplifying the structure of ecological networks; however, we are currently in a poor position to predict how these simplified communities will affect the evolutionary potential of remaining populations.
+Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treat the community context of evolving populations as a ``black box''.
+<!--In contrast, ecological networks provide an explicit representation of the community context, yet often ignore the role of natural selection.-->Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
 We conducted a field experiment that manipulated the diversity of insect parasitoids (food-web complexity) that were able to impose selection on an insect herbivore.
 We then measured herbivore survival as a function of three key phenotypic traits.
-We found that more traits were under selection in simple vs.
-complex food webs.
+We found that more traits were under selection in simpler vs.
+more complex food webs.
 The adaptive landscape was more neutral in complex food webs because different parasitoid species impose different selection pressures, minimizing relative fitness differences among phenotypes.
 Our results suggest that phenotypic evolution becomes more constrained in simplified food webs.
-This indicates that the simplification of ecological communities may constrain the adaptive potential of populations to future environmental change.
+This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
 

### 2018-11-22 manuscript.Rmd
incorporated Jordi's comments on Intro.

@@
 
-The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes, to phenotypes, to species [@Wright1931; @Simpson1944; @Arnold2001].
+The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
 More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory].
@@
 For example, competition for shared prey in threespine stickleback has driven their adaptive divergence into ecotypes with specialized body and gill morphologies [@Schluter2000, other papers].
-Similarly, the elongated, red corollas of many flowering species have evolved in response to the efficient pollination of hummingbirds [cite].--> Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we also know that most species interact with multiple species in a community context [@Darwin1859].
-Understanding how the adaptive landscape is shaped by community context represents a major frontier for evolutionary ecologists [@McPeek2017; @terHorst2018].
-Resolution on this front is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].
+Similarly, the elongated, red corollas of many flowering species have evolved in response to the efficient pollination of hummingbirds [cite].--> Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we do not know how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018].
+Resolution on how the community context shapes phenotypic evolution is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].
 
-Ecological networks, such as a food web describing who eats whom, provide an explicit representation of the community context.
-These networks describe the interdependency of populations within an ecological community, providing an effective framework for predicting how the strength and organization of ecological interactions (network structure) affect population and community dynamics [@Bascompte2014; @McCann2012].
+Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012].<!--These networks describe the interdependency of populations within an ecological community, providing an effective framework for predicting how the strength and organization of ecological interactions (network structure) affect population and community dynamics [@Bascompte2014; @McCann2012].
 Nevertheless, these networks often lack quantitative information on how ecological interactions influence selection on phenotypic traits.
 Thus, it remains unclear how network structure shapes adaptive landscapes of interacting populations.
-This represents a major barrier in our current ability to predict how changes in community context will affect phenotypic evolution.
-
-Here, we integrate ecological networks and adaptive landscapes to understand how community context constrains evolutionary change [@Arnold1992].
+This represents a major barrier in our current ability to predict how changes in community context will affect phenotypic evolution.--> Here, we integrate ecological networks and adaptive landscapes to understand how community context constrains evolutionary change [@Arnold1992].
 Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape.
@@
 
-To examine the effect of network structure on adaptive landscapes, we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
+Global change is simplifying the structure of ecological communities, which may influence evolutionary constraints in a number of ways.
+For example, in a multitrophic community or food web, if different consumers impose directional selection on different traits of a shared resource, then more complex food webs may constrain evolution by increasing the number of traits under selection.
+Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
+To examine these different possibilities (among others), <!--To examine the effect of network structure on adaptive landscapes, -->we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
 \ref{fig:Conceptual}).
@@
 \ref{fig:Conceptual}).
-Food-web complexity may influence the adaptive landscape in a number of ways.
+<!--Food-web complexity may influence the adaptive landscape in a number of ways.
 For example, if each parasitoid imposes directional selection on a different trait, then more complex food webs may constrain evolution by increasing the number of traits under selection.
 Alternatively, if parasitoids impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
-To examine these different possibilities (among others), we applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
+To examine these different possibilities (among others), -->We then applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
 Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, may constrain the evolution of interacting populations.

### 2018-11-22 manuscript.Rmd
incorporated Jordi's comments on Results.

@@
 To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall ID nested within plant ID nested within genotype ID as random effects.
-Although statistical models with random effects are not common in analyses of natural selection, we think this is a mistake since modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
-Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e.
-setting them to zero) when calculating trait-fitness relationships.
+Although statistical models with random effects are not common in analyses of natural selection, we think that modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
+Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e., setting them to zero) when calculating trait-fitness relationships.
 We then used parametric bootstrapping (1,000 replicates) to estimate the effect of food-web treatment on larval survival as well as trait-fitness relationships in each food-web treatment.
@@
 
-**Adaptive landscape**: We took advantage of existing theory that translates estimates of selection gradients to the adaptive landscape [@Phillips1989; @Arnold2003].
+**Evolutionary constraints**: We quantified the effects of food-web complexity on evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
+<!--Adaptive landscape**: We took advantage of existing theory that translates estimates of selection gradients to the adaptive landscape [@Phillips1989; @Arnold2003].
 The shape of the adaptive landscape can be described by both its slope and curvature, each of which describe different aspects of constraints on phenotypic evolution.
-Specifically, the slope corresponds to the column vector of directional selection gradients, which in our study corresponds to:
+Specifically, -->The number of selective constraints is determined by the slope of the adaptive landscape<!-- corresponds to the column vector of directional selection gradients-->, which in our study corresponds to:
 
@@
 $$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-This slope describes the selective constraints acting on the trajectory of phenotypic evolution, which is governed by the 'Lande equation', $\Delta \bar z=\text{G}\beta$ [@Lande1979].
-Quantitative predictions of evolutionary trajectories requires knowledge of a population's **G**-matrix; however, we can gain qualitative insight to evolutionary constraints by counting the number of phenotypic traits under directional selection [selective constraints, @Arnold1992].
+<!--This slope describes the selective constraints acting on the trajectory of phenotypic evolution, which is governed by the 'Lande equation', $\Delta \bar z=\text{G}\beta$ [@Lande1979].
+Quantitative predictions of evolutionary trajectories require knowledge of a population's **G**-matrix; however, We quantified the degree to which phenotypic evolution was constrained by selection <!--can gain qualitative insight to evolutionary constraints by counting the number of phenotypic traits under directional selection [selective constraints, @Arnold1992].-->
+By comparing the number of traits that determine the slope (i.e., nonzero directional selection gradients) in simpler vs.
+more complex food webs, we can infer the effect of food-web complexity on selective constraints.
 
-The curvature (**C**) of the adaptive landscape is a matrix that is determined by directional, quadratic, and correlational selection gradients, such that \boldmath$\text{C}=\gamma - \beta \beta^\text{T}$, or more explicitly:
+The indirect effects of selection on genetic constraints is governed by the curvature of the adaptive landscape, which in our study corresponds to:
+<!--The curvature (**C**) of the adaptive landscape is a matrix that is determined by directional, quadratic, and correlational selection gradients, such that \boldmath$\text{C}=\gamma - \beta \beta^\text{T}$, or more explicitly:-->
 
@@
 Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
-This curvature matrix describes the indirect effects of selection on genetic constraints within a generation ($\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}$).
-For example, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
-Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (less trait independence).
+<!--This curvature matrix describes the indirect effects of selection on genetic constraints within a generation ($\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}$).
+For example, -->The sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
 Therefore, we can infer the indirect effects of selection on genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
@@
 
-Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits which could bias measurements of selection.
+Rather than imposing selection, parasitoids may influence the expression of herbivore traits which could bias measurements of selection.
 In our system, it was plausible that parasitoids may influence chamber diameter by altering larval feeding behavior or killing larvae before they complete their development.
@@
 
-The structure of these matrices indicate that there are more selective constraints imposed on the gall midge in the simple (6 of 6) vs.
-complex (1 of 6) food web.
-Simple food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the complex food web.
-For genetic covariances, the simple food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
+Remember that we can infer the indirect effects of selection on genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
+The structure of these matrices indicates that there are more selective constraints imposed on the gall midge in the simpler (6 of 6) vs.
+more complex (1 of 6) food web.
+Simpler food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the more complex food web.
+For genetic covariances, the simpler food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
 \ref{fig:MV_Landscape}).
-In contrast, there was no strong evidence of trait integration in the complex food web (fig.
+In contrast, there was no strong evidence of trait integration in the more complex food web (fig.
 \ref{fig:MV_Landscape}).
@@
 ```
+
+# Appendix

### 2018-11-22 manuscript.Rmd
update figure legends based on Jordi's comments.

@@
 Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
-Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
 
@@
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Selection favors trait integration for each combination of traits in simple food webs, whereas there is no strong evidence for trait integration in complex food webs.
-Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape.
+Note the flat landscape in mean larval survival for clutch size and oviposition preference in more complex food webs, whereas all three traits shape the adaptive landscape in simpler food webs.
+This indicates that selection favors trait integration for each combination of traits in simpler food webs, whereas there is no strong evidence for trait integration in more complex food webs.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
 

### 2018-11-23 analyses/reproduce_analyses.Rmd
updated figures and created a very rough draft o the entire discussion.

@@
 
-```{r Univariate-Fitness-Landscapes, echo=FALSE, eval=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
+```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
 simple food webs.
@@
 Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
-Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples.", eval=FALSE}
+Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
 
 # Get legend
-AF_uni_legend <- get_legend(legend_only + theme(legend.title.align = 0.5)) #get_legend(AF_uni_Diam)
+AF_uni_legend <- get_legend(AF_uni_Diam + theme(legend.title.align = 0.5)) #get_legend(AF_uni_Diam)
 
 # Make plots
-AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none", 
-                                              axis.text.x = element_text(size=10),
-                                              axis.title.x = element_text(size=11)), 
+AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none"), 
+                                           #   axis.text.x = element_text(size=10),
+                                          #    axis.title.x = element_text(size=11)), 
                        AF_uni_Pref + theme(legend.position = "none", 
-                                           axis.title.y = element_blank(),
-                                           axis.text.x = element_text(size=10),
-                                           axis.title.x = element_text(size=11)),
+                                           axis.title.y = element_blank()) + xlab("Preference (SDs)"),
+                                           #axis.text.x = element_text(size=10),
+                                           #axis.title.x = element_text(size=11)),
                       AF_uni_Clutch + theme(legend.position = "none",
-                                             axis.title.y = element_blank(), 
-                                             axis.text.x = element_text(size=10),
-                                             axis.title.x = element_text(size=11)),
-                     legend_only + theme(legend.position = "none",                          
-                                             axis.title.y = element_blank(), 
-                                             axis.text.x = element_text(size=10),
-                                             axis.title.x = element_text(size=11)),
-                       labels = "AUTO", ncol = 2, align='hv')
-
-AF_gradients <- plot_grid(AF_uni_legend, AF_uni_plots, nrow = 2, rel_heights = c(0.2,0.8)) 
+                                             axis.title.y = element_blank()), 
+                                            # axis.text.x = element_text(size=10),
+                                            # axis.title.x = element_text(size=11)),
+                    # legend_only + theme(legend.position = "none",                          
+                    #                         axis.title.y = element_blank(), 
+                    #                         axis.text.x = element_text(size=10),
+                    #                         axis.title.x = element_text(size=11)),
+                       labels = "AUTO", nrow = 1, align='hv')
+
+AF_gradients <- plot_grid(AF_uni_plots, AF_uni_legend, ncol = 2, rel_widths = c(0.8,0.2)) 
 AF_gradients
-```
-
-```{r Figure-Univariate-Landscapes, echo=FALSE}
+save_plot(filename = "UV_landscapes.pdf", plot = AF_gradients, base_height = 5, base_width = 8.5)
+```
+
+```{r Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE}
 # Get legend
@@
   scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))#,
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
+  theme(strip.background = element_blank(),
+        strip.text.x=element_text(margin=margin(b=4)))
 
@@
   scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max))
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
+  theme(strip.background = element_blank(),
+        strip.text.x=element_text(margin=margin(b=4)))
 

### 2018-11-23 manuscript.Rmd
updated figures and created a very rough draft o the entire discussion.

@@
     fig_caption: true
-    #citation_package: natbib
+    citation_package: natbib
     template: Rmd_AmNat_MS_template.tex
@@
       in_header: Am-Nat-preamble-latex.tex
-bibliography: references.bib
-biblio-style: amnat.bst
+bibliography: references
+#references.bib
+#csl: the-american-naturalist.csl
+biblio-style: amnat
+#amnat.bst
 fontsize: 11pt
@@
 All larvae collected from the same multi-chambered gall were scored with the same clutch size.
-Third, we measured oviposition (egg laying) preference as the density of larvae observed on a plant in an independent survey.
+Third, we measured oviposition preference as the density of larvae observed on a plant in an independent survey.
 We did this randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
@@
 For example, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
+Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of oSimilar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982]Similar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982]bserved larval densities.
 
@@
 Unless otherwise noted, we report mean estimates of trait-fitness relationships and selection gradients with 95% confidence intervals in brackets.
-Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
+Note that for visualizing the adaptive landscape weSimilar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982] restrict trait axes to $\pm 1$ SD of the mean trait value.
 This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [@Arnold2001].
@@
 
-\begin{enumerate}
-
- \item Summary of key results
-    \begin{enumerate}
-    \item Gall midges experience more selective and constraints in simple food webs.
-    \end{enumerate}
-
- \item Natural history and comparison to other studies of natural selection in galling insects.
-    \begin{enumerate}
-    \item \textbf{Important Studies for Comparison}: @Abrahamson1997; @Weis1983; @Heath2018; Start, Weis, and Gilbert In Press Am.
+<!--
+Summary of key results
+
+Gall midges experience more selective and constraints in simple food webs.
+-->
+
+<!-- 
+Natural history and comparison to other studies of natural selection in galling insects.
+
+Important Studies for Comparison: @Abrahamson1997; @Weis1983; @Heath2018; Start, Weis, and Gilbert In Press Am.
 Nat; @Start2016; @Start2018urbanization; Peter Price's work; Timothy Craig's work; Cheryl Briggs work.
-    \item \textbf{Topics to discuss}: Persistent pattern in selection for larger galls; Contrasting effects of egg and larval parasitoids on clutch size; Nonlinear selection at high gall densities is likely reflective of the poorer searching ability of larval vs.
+
+Topics to discuss: Persistent pattern in selection for larger galls; Contrasting effects of egg and larval parasitoids on clutch size; Nonlinear selection at high gall densities is likely reflective of the poorer searching ability of larval vs.
 egg parasitoids (and thus it saturates more quickly).
-    \end{enumerate}
-
- \item Selective constraints:
-    \begin{enumerate}
-    \item \textbf{Key Result}: More traits under directional selection in simple (3 of 3) vs.
+-->
+Our finding that phenotypic evolution was more constrained in simpler food webs corresponds to the natural history of this system.
+This particular gall-parasitoid community has only been studied one other time [@Barbour2016].
+But a persistent pattern seen in others work is that parasitoids generally impose selection for larger galls [@Abrahamson1997; @Heath2018; @Start2016; @Start2018urbanization].
+In many cases, there may be functional or development constraints acting on gall size that constrains phenotypic evolution.
+It is curious though that we still observed directional selection for larger chamber diameters in the simpler food web.
+This is because egg parasitoids attack before the gall is formed.
+Thus, the apparent selection on chamber diameter is likely due to selection with a correlated trait (e.g.
+ability to encapsulate endoparasitoid eggs).
+In terms of clutch size, we likely observe conflicting selection pressures for the following reason.
+First, egg parasitoids reduce the probability of larval survival in higher clutch sizes, because they cue in more to the local density when foraging.
+Indeed oviposition itself can induce plant volatiles that influence egg parasitoid foraging behavior [reviewed in @Hilker2006].
+In contrast, clutch sizes can increase the probability of larval survival in the face of larval parasitoids by creating more of a refuge from parasitoids that have to oviposit through the gall tissue.
+Similar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982].
+Alternatively, in another gall midge, the same reduction in percent parasitism has been shown [@Weis1983].
+This previous work did not explore a relationship with the egg parasitoid Platygaster because it was too low in abundance, which is in contrast to our community where this species is the dominant parasitoid.
+Counterintuitively, this may not be due to a greater refuge, but simple a result of the parasitoids using a fixed-time strategy to search for hosts.
+Thus, parasitoids actually have a lower success attacking small galls, but a good chance of attacking one host in large galls and then just moving on to the next.
+In regard to oviposition preference, our results correspond to biological differences between egg and larval parasitoids.
+For example, egg parasitoids, such as Platygaster are known to be efficient foragers, whereas larval parasitoids are less efficient.
+This may create a pattern where larval parasitoid attack saturates more quickly at high host densities, as we observed here.
+The fact that Platygaster attack rates increased with host density suggest that host densities were relatively low, so we actually may be in the lower part of a type 3 functional response.
+
+A key question is whether our results would have changed if we had instead manipulated it so that only one of the larval parasitoid species could attack vs.
+the full complement.
+Based on the above biology, we may have expected two things.
+One we would may have seen no selection on oviposition preference in both food webs, since the larval parasitoid tends to have a nonlinear response that actually may enhance genetic variation in oviposition preference.
+However, we still would have seen selection reduced selection for clutch size, which would free this trait and covarying traits from selective constraints.
+Also, if we had just included one of the larval parasitoids, which were at lower densities, then the selection gradients would have been weaker simply due to the enhanced survival of gall midge larva.
+This highlights the importance of studies that manipulate community context in not only looking at the effects on the trait-fitness relationships, but also the effects on average survival.
+This is especially true in experimental contexts, such as ours, where density of consumers were artificially low, and thus we are only observing a transient dynamic in the strength of selection.
+
+<!--
+Selective constraints:
+
+Key Result: More traits under directional selection in simple (3 of 3) vs.
 complex (1 of 3) food webs.
@@
 Even if there is selection on oviposition preference, this does not change our qualitative result.
-    \item \textbf{Implications}: The trajectory of phenotypic evolution is less constrained in complex vs.
-simple food webs.
-In other words, there are more potential adaptive peaks in complex food webs.
-    \end{enumerate}
-
- \item Indirect effects of selection on genetic constraints: 
-    \begin{enumerate}
-    \item \textbf{Key Result}: More traits experience a decrease in additive genetic variance and more trait combinations experience selection for trait integration in simple food webs. 
-    \item \textbf{Implications}: The structure of the G-matrix is under less influence of selection in complex vs.
+
+Implications: The trajectory of phenotypic evolution is less constrained in complex vs. simple food webs. In other words, there are more potential adaptive peaks in complex food webs. 
+-->
+
+The fact that more traits contributed to the slope of the adaptive landscape (number of traits under directional selection) in the simple food web suggests that the trajectory of evolution is more constrained.
+For the phenotypic traits we examine, it also implies that there is an optimal combination of phenotypes that maximizes larval survival (i.e.
+large chamber diameter, small clutch sizes, and avoid conspecifics) in simpler food webs.
+In contrast, there are no selective constrains on the evolution of clutch size and oviposition preference in the more complex food web.
+This suggests that there are multiple adaptive peaks, or in this case, a flat adaptive landscape across these phenotypic traits, such that there are no consequences to move across the adaptive landscape in these directions.
+Interestingly, this also implies that as selective constraints weaken in more complex food webs, then the trajectory of evolution becomes more influenced by genetic constraints, or the population's G-matrix.
+This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the populations additive genetic variance and covariances between traits (G-matrix).
+As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
+Interestingly, this corresponds to data on trait evolution in complex natural systems.
+Specifically, @Schluter1996 suggested that evolution often follows 'genetic lines of least resistance'.
+This data came from data on natural populations of threespine sticklebacks, three species of songbirds, and *Peromyscus* mice.
+This also implies that simplification of ecological communities may actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.
+This insight also helps resolve the balance between neutral and adaptationist views of phenotypic evolution.
+In fact, the ability for neutral evolutionary theories to give insight to evolution may be due to the net neutral selection pressures in complex natural systems.
+However, this highlights that we will need further integration of these perspectives in the context of global change and concomittant changes in the selective environment.
+
+Moreover, current theoretical models of evolution in a community context often focus on the evolution of a single trait.
+Our results highlight though, that in the context of global change, we may begin to experience selection changing to cause change in multiple traits that influence fitness.
+
+<!--    
+Indirect effects of selection on genetic constraints:
+
+Key Result: More traits experience a decrease in additive genetic variance and more trait combinations experience selection for trait integration in simple food webs.
+
+Implications: The structure of the G-matrix is under less influence of selection in complex vs.
 simple food webs.
@@
 This is in line with empirical evidence (from complex natural systems) that evolution tends to proceed along genetic lines of least resistance [@Schluter1996].
-    \end{enumerate}
-
- \item Indirect evolutionary effects:
-    \begin{enumerate}
-    \item \textbf{Key Result}: Evidence of selection on the extended phenotype of egg parasitoids.
-    \item \textbf{Implications}: Hints at a dynamic adaptive landscape and potential indirect evolutionary effects in complex food webs.
-    \end{enumerate}
-
- \item Caveats: 
-    \begin{enumerate} 
-    \item \textbf{Key Caveat}: Experimental artifact of lower larval survival in complex food-web treatment.
-    \item \textbf{Implications}: Artificially increased the magnitude of selection in complex food webs.
+-->
+
+In addition, we also found that the indirect effects of selection on genetic constraints were fewer in complex vs.
+simpler food webs.
+Key components that contribute to the evolvability of populations are determined by the additive genetic variance in traits as well as patterns of additive genetic covariance (i.e.
+G-matrix structure).
+Specifically, weak covariances allow trait evolution to be independent, which gives more autonomy in trait evolutionary responses to changing environments.
+Similar, decreases in genetic variance contstrain potential for the trait itself to evolve.
+Together, this suggest the simpler food webs can actually act to decrease the evolutionary potential of populations by indirectly selecting for decrases in genetic variance in multiple traits and favoring trait integration [@Hansen2008].
+At present, these indirect effects of selection imposed by the community context are often ignored in theoretical models, often assuming genetic variance is unchanging parameter in models.
+Our empirical results highlight the need to explore the evolutionary consequences of how not only the direct (current focus), but indirect effects of community context on phenotypic evolution.
+
+<!--
+Indirect evolutionary effects:
+
+Key Result: Evidence of selection on the extended phenotype of egg parasitoids.
+
+Implications: Hints at a dynamic adaptive landscape and potential indirect evolutionary effects in complex food webs.
+-->
+
+Right now, most studies treat the selection gradients imposed by the adaptive landscape as static [but see @McPeek2017].
+Our results suggest though that we also observe indirect evolutionary effects (cite Start, Weis, and Gilbert's new Am Nat paper).
+This suggests the adaptive landscape itself may be a more dynamic entity in more complex food webs.
+Where these dynamics end up cancelling each other out in their net selective effects over time, or allow phenotypic evolution to change direction is currently unclear, and we need more empirical work on this front.
+
+<!-- Community context in altering adaptation to environmental change
+
+Relevant review paragraph from @Osmond2017PredatorsHelpPrey about studies incorporating gradual, directional environmental change but also species interactions.
+
+There is a small but growing number of theoretical studies on adaptation to gradual, directional environmental change that incorporate interactions between species (de Mazancourt et al.
+2008; Johansson 2008; Jones 2008; Norberg et al.
+2012; Mellard et al.
+2015).
+Only two of these studies assessed predator-prey interactions.
+Jones (2008) used simulations to study, among other things, a predator-prey system where the predator trait evolves to match the prey trait and the prey trait evolves both to match the changing environmental optimum and escape the predator.
+His main finding was that predation can sometimes increase the persistence time of the prey, presumably when the predator removes prey that are maladapted to the abiotic environment.
+Mellard et al.
+(2015) studied an explicit resource-plant-herbivore trophic chain using a primarily numerical approach to ask how the addition of an herbivore affects plant persistence in a warming environment.
+They analytically clarified the conditions required for the predator to hasten prey evolution but found in simulations that, regardless of the effect on evolutionary rates, herbivory almost never aided plant persistence.
+In addition, Northfield and Ives (2013), who did not explicitly model a gradually changing environment, analytically demonstrated that conflicting interactions, such as predation, tended to dampen the direct effect of small environmental changes on the equilibrium densities of interacting species, potentially facilitating persistence.
+In their model, coevolution facilitates persistence through negative feedback loops.
+For example, as the predator nears extinction, the prey invests less in defense, making it easier for the predator to consume prey and rebound in abundance.
+Thus, up to this point, while it is clear that predators can theoretically help prey adapt in changing environments, the effect of predators on prey persistence remains unresolved.
+
+-->
+
+The role of community context and diversity in shaping communities has been explored theoretically in terms of competitive communities [@De_Mazancourt2008; @Johansson2008].
+Other work has also highlighted the role of competition in shaping evolutionary rescue [@Osmond2013].
+Other studies have also explored the role of predators in helping prey adaptive to environmental change [@Osmond2017PredatorsHelpPrey].
+This work has suggested that biodiversity may constrain phenotypic evolution, because more species occupy different niches, presenting the "movement" of species across the adaptive landscape into different ecological niches.
+This may be true for competitive communities, but in multitrophic communities our empirical results suggest the opposite.
+Still, in natural communities we are likely to see multiple interaction types that shape the survival of species.
+The role of different interaction types in shaping evolution in a community context remains both a theoretical and empirical frontier.
+
+<!--
+Caveats:
+
+Key Caveat: Experimental artifact of lower larval survival in complex food-web treatment.
+
+Implications: Artificially increased the magnitude of selection in complex food webs.
 Note however, that this does not qualitatively change any of our results.
@@
 This is because the egg parasitoids would be released from their intraguild predator, and thus could increase in abundance over future generations and impose stronger selection on gall midges.
-    \end{enumerate}
-
-\item Conclusions
-
-\end{enumerate}
+-->
+
+One of the things that our study did was artificially reduce the mortality induced by parasitoids, in general, in the simpler food web.
+Importantly though, this would actually make it more difficult to observed selection due to the fact that reductions in mean fitness, all else equal, intensify the strength of selection [@Hunter2018].
+Indeed, we are likely underestimating the constraints imposed by simpler food web, because over time, egg parasitoid abundances would increase, thus increasing selective constraints.
+
+## Conclusions
+
+Our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, increases evolutionary constraints.
+This occurs because selection imposed by simpler food webs constrains optimal evolutionary trajectories and the ability for populations to reach those adaptive peaks (e.g.
+via genetic constraints).
+This implies has unexplored, but an insidious effect of local extinctions.
+Not only may it compromise community robustness and resilience to future change, but it may also cause this at the population level.
+We are in urgent need of future empirical and theoretical work that understands these rippling effects on the robustness of populations and communities to environmental change.
 
@@
 Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.<!-- Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
+-->Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
 
@@
 
-```{r UV_Landscape, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}"}
+```{r UV_Landscape, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
+Solid lines represent selection experienced in complex (orange) and simple (blue) food webs.
+Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
 knitr::include_graphics("analyses/UV_landscapes.pdf")

### 2018-11-23 manuscript.tex
updated figures and created a very rough draft o the entire discussion.

--- 2018-11-22 manuscript_complexity_selection.tex
@@
 }{}
+\usepackage{natbib}
+\bibliographystyle{amnat}
 \usepackage{graphicx}
@@
             pdfauthor={Matthew A. Barbour\^{}\{1,2,\textbackslash{}ast\}; Christopher J. Greyson-Gaito\^{}\{1,3\}; Arezoo Sootodeh\^{}\{3\}; Brendan Locke\^{}\{4\}; Jordi Bascompte\^{}\{2\}},
-            pdftitle={Phenotypic evolution is more constrained in simple food webs},
+            pdftitle={Phenotypic evolution is more constrained in simpler food webs},
             colorlinks=true,
@@
 
-  \title{Phenotypic evolution is more constrained in simple food webs}
+  \title{Phenotypic evolution is more constrained in simpler food webs}
     \author{Matthew A. Barbour\(^{1,2,\ast}\) \\ Christopher J. Greyson-Gaito\(^{1,3}\) \\ Arezoo Sootodeh\(^{3}\) \\ Brendan Locke\(^{4}\) \\ Jordi Bascompte\(^{2}\)}
@@
 
-Adaptive landscapes describe the selective constraints acting on
-phenotypic evolution, but often treat the community context of evolving
-populations as a ``black box''. In contrast, ecological networks provide
-an explicit representation of the community context, yet often ignore
-the role of natural selection. Global change is simplifying the
-structure of ecological networks; however, we are currently in a poor
-position to predict how these simplified communities will affect the
-evolutionary potential of populations. Here, we integrate ecological
-networks and adaptive landscapes to examine how changes in food-web
-complexity shape evolutionary constraints. We conducted a field
-experiment that manipulated the diversity of insect parasitoids
-(food-web complexity) that were able to impose selection on an insect
-herbivore. We then measured herbivore survival as a function of three
-key phenotypic traits. We found that more traits were under selection in
-simple vs.~complex food webs. The adaptive landscape was more neutral in
+Global change is simplifying the structure of ecological networks;
+however, we are currently in a poor position to predict how these
+simplified communities will affect the evolutionary potential of
+remaining populations. Theory on adaptive landscapes provides a
+framework for predicting how selection constrains phenotypic evolution,
+but often treat the community context of evolving populations as a
+``black box''. Here, we integrate ecological networks and adaptive
+landscapes to examine how changes in food-web complexity shape
+evolutionary constraints. We conducted a field experiment that
+manipulated the diversity of insect parasitoids (food-web complexity)
+that were able to impose selection on an insect herbivore. We then
+measured herbivore survival as a function of three key phenotypic
+traits. We found that more traits were under selection in simpler
+vs.~more complex food webs. The adaptive landscape was more neutral in
 complex food webs because different parasitoid species impose different
@@
 simplification of ecological communities may constrain the adaptive
-potential of populations to future environmental change.
+potential of remaining populations to future environmental change.
 
@@
 how natural selection has shaped the evolution of biodiversity ---from
-genes, to phenotypes, to species (Wright 1931; Simpson 1944; Arnold,
-Pfrender, and Jones 2001). More than a metaphor, the adaptive landscape
-links quantitative genetic and phenotypic variation to evolution by
-natural selection (Lande 1979; Stevan J. Arnold and Wade 1984a; Stevan
-J. Arnold and Wade 1984b). Ecological interactions often play a key role
-in shaping adaptive landscapes, as evidenced by the role of antagonistic
-(Schluter 2000; Abrams 2000) and mutualistic (Bronstein, Alarcón, and
-Geber 2006) interactions in driving evolutionary change. Although there
-is clear evidence that pairwise interactions can shape the adaptive
-landscape, we also know that most species interact with multiple species
-in a community context (Darwin 1859). Understanding how the adaptive
-landscape is shaped by community context represents a major frontier for
-evolutionary ecologists (McPeek 2017; terHorst et al. 2018). Resolution
-on this front is urgently needed though, given the rapid impacts of
-climate change on ecological communities (Scheffers et al. 2016).
-
-Ecological networks, such as a food web describing who eats whom,
-provide an explicit representation of the community context. These
-networks describe the interdependency of populations within an
-ecological community, providing an effective framework for predicting
-how the strength and organization of ecological interactions (network
-structure) affect population and community dynamics (Bascompte and
-Jordano 2014; McCann 2012). Nevertheless, these networks often lack
-quantitative information on how ecological interactions influence
-selection on phenotypic traits. Thus, it remains unclear how network
-structure shapes adaptive landscapes of interacting populations. This
-represents a major barrier in our current ability to predict how changes
-in community context will affect phenotypic evolution.
-
-Here, we integrate ecological networks and adaptive landscapes to
-understand how community context constrains evolutionary change (Arnold
-1992). Different aspects of evolutionary constraints can be inferred by
-quantifying the slope and curvature of the adaptive landscape. For
-example, the slope is determined by directional selection gradients
-acting on each phenotypic trait and influences the trajectory of
-evolutionary change (Lande 1979; Arnold 1992). Evolutionary trajectories
-become more constrained with an increase in the number of traits under
-selection, as this diminishes the number of optimal solutions (Arnold
-2003). The curvature of the adaptive landscape can also constrain
-evolution through its indirect effect on genetic constraints (Arnold
-1992; Hansen and Houle 2008). Genetic constraints are largely governed
+genes to phenotypes to species
+\citep{Wright1931, Simpson1944, Arnold2001}. More than a metaphor, the
+adaptive landscape links quantitative genetic and phenotypic variation
+to evolution by natural selection
+\citep{Lande1979, Arnold1984applications, Arnold1984theory}. Ecological
+interactions often play a key role in shaping adaptive landscapes, as
+evidenced by the role of antagonistic \citep{Schluter2000, Abrams2000}
+and mutualistic \citep{Bronstein2006} interactions in driving
+evolutionary change. Although there is clear evidence that pairwise
+interactions can shape the adaptive landscape, we do not know how the
+adaptive landscape is shaped by the community context
+\citep{McPeek2017, terHorst2018}. Resolution on how the community
+context shapes phenotypic evolution is urgently needed though, given the
+rapid impacts of climate change on ecological communities
+\citep{Scheffers2016}.
+
+Ecological networks, such as food webs describing who-eats-whom in
+ecological communities, provide an explicit representation of the
+community context \citep{Bascompte2014, McCann2012}. Here, we integrate
+ecological networks and adaptive landscapes to understand how community
+context constrains evolutionary change \citep{Arnold1992}. Different
+aspects of evolutionary constraints can be inferred by quantifying the
+slope and curvature of the adaptive landscape. For example, the slope is
+determined by directional selection gradients acting on each phenotypic
+trait and influences the trajectory of evolutionary change
+\citep{Lande1979, Arnold1992}. Evolutionary trajectories become more
+constrained with an increase in the number of traits under selection, as
+this diminishes the number of optimal solutions \citep{Arnold2003}. The
+curvature of the adaptive landscape can also constrain evolution through
+its indirect effect on genetic constraints
+\citep{Arnold1992, Hansen2008}. Genetic constraints are largely governed
 by a population's \textbf{G}-matrix ---the additive genetic variances
-and covariances between traits (Hansen and Houle 2008). In general,
-genetic constraints will increase with the number of traits under
-directional or stabilizing selection, as this will decrease the additive
-genetic variance in those traits (Hansen and Houle 2008). Genetic
-constraints may also increase with the number of trait combinations
-under correlational selection, as this type of selection decreases the
-evolutionary independence of traits (Hansen and Houle 2008). If we want
-to predict how community context constrains evolutionary change, we must
-understand how ecological networks shape the adaptive landscape.
-
-To examine the effect of network structure on adaptive landscapes, we
-conducted a field experiment that manipulated the complexity of trophic
-interactions (hereafter food-web complexity) associated with an abundant
-insect herbivore (\emph{Iteomyia salicisverruca}; Family
-Cecidomyiidae)(fig. \ref{fig:Conceptual}). The larvae of this herbivore
-induce tooth-shaped galls when they feed on the developing leaves of
-willow trees (\emph{Salix} sp., Russo 2006). These galls protect larva
-from attack by generalist predators (e.g.~ants, spiders), but they
-suffer high mortaltiy from egg and larval parasitoids (Barbour et al.
-2016). We manipulated food-web complexity by either excluding the guild
-of larval parasitoids (simple food web) or allowing both egg and larval
+and covariances between traits \citep{Hansen2008}. In general, genetic
+constraints will increase with the number of traits under directional or
+stabilizing selection, as this will decrease the additive genetic
+variance in those traits \citep{Hansen2008}. Genetic constraints may
+also increase with the number of trait combinations under correlational
+selection, as this type of selection decreases the evolutionary
+independence of traits \citep{Hansen2008}. If we want to predict how
+community context constrains evolutionary change, we must understand how
+ecological networks shape the adaptive landscape.
+
+Global change is simplifying the structure of ecological communities,
+which may influence evolutionary constraints in a number of ways. For
+example, in a multitrophic community or food web, if different consumers
+impose directional selection on different traits of a shared resource,
+then more complex food webs may constrain evolution by increasing the
+number of traits under selection. Alternatively, if consumers impose
+selection on different values of a trait, then their selective effects
+would cancel each other out in more complex food webs. To examine these
+different possibilities (among others), we conducted a field experiment
+that manipulated the complexity of trophic interactions (hereafter
+food-web complexity) associated with an abundant insect herbivore
+(\emph{Iteomyia salicisverruca}; Family Cecidomyiidae)(fig.
+\ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped
+galls when they feed on the developing leaves of willow trees
+\citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect larva from
+attack by generalist predators (e.g.~ants, spiders), but they suffer
+high mortaltiy from egg and larval parasitoids \citep{Barbour2016}. We
+manipulated food-web complexity by either excluding the guild of larval
+parasitoids (simple food web) or allowing both egg and larval
 parasitoids to impose selection on gall midge traits (complex food web;
-fig. \ref{fig:Conceptual}). Food-web complexity may influence the
-adaptive landscape in a number of ways. For example, if each parasitoid
-imposes directional selection on a different trait, then more complex
-food webs may constrain evolution by increasing the number of traits
-under selection. Alternatively, if parasitoids impose selection on
-different values of a trait, then their selective effects would cancel
-each other out in more complex food webs. To examine these different
-possibilities (among others), we applied modern statistical methods to
-quantify the effect of food-web complexity on the slope and curvature of
-the gall midge's adaptive landscape. Taken together, our study gives
+fig. \ref{fig:Conceptual}). We then applied modern statistical methods
+to quantify the effect of food-web complexity on the slope and curvature
+of the gall midge's adaptive landscape. Taken together, our study gives
 insight to how local extinctions, and concomitant decreases in food-web
@@
 Further details on the genotyping and planting of the common garden are
-available in Barbour et al. (2015).
+available in \citet{Barbour2015}.
 
@@
 from eight different plant genotypes that spanned the range of trait
-variation observed in this willow population (Barbour et al. 2015). For
+variation observed in this willow population \citep{Barbour2015}. For
 the complex food-web treatment (eight replicates per genotype), we used
@@
 larval development. This treatment did not exclude the egg parasitoid
-\emph{Platygaster} sp., which attacks prior to gall initiation (larva
-initiate gall development in Cecidomyiid midges: Gagné 1989). In late
-August, we collected marked and bagged galls from each plant, placed
-them into 30 mL vials and kept them in the lab for 4 months at room
-temperature. We then opened galls under a dissecting scope and
-determined whether larvae survived to pupation (our measure of fitness)
-or were parasitized. Since we were interested in selection imposed by
-parasitoids, we excluded unknown sources of mortality. For the food-web
-treatment that excluded larval parasitoids (simple food web), we further
-restricted our data by removing any incidental instances of parasitism
-by a larval parasitoid. This represented less than 3\% of the
-observations in this food-web treatment and allowed us to focus our
-inferences of selection on those imposed by the egg parasitoid. Our
-final dataset contains survival estimates for 1285 larvae from 613 galls
-and 111 plants.
+\emph{Platygaster} sp., which attacks prior to gall initiation
+\citep[larva initiate gall development in Cecidomyiid
+midges:][]{Gagne1989}. In late August, we collected marked and bagged
+galls from each plant, placed them into 30 mL vials and kept them in the
+lab for 4 months at room temperature. We then opened galls under a
+dissecting scope and determined whether larvae survived to pupation (our
+measure of fitness) or were parasitized. Since we were interested in
+selection imposed by parasitoids, we excluded unknown sources of
+mortality. For the food-web treatment that excluded larval parasitoids
+(simple food web), we further restricted our data by removing any
+incidental instances of parasitism by a larval parasitoid. This
+represented less than 3\% of the observations in this food-web treatment
+and allowed us to focus our inferences of selection on those imposed by
+the egg parasitoid. Our final dataset contains survival estimates for
+1285 larvae from 613 galls and 111 plants.
 
@@
 We collected data on three different traits that we expected to
-influence larval survival based on our previous work (Barbour et al.
-2016) and others work with gall midges (Weis, Price, and Lynch 1983;
-Heath, Abbot, and Stireman 2018). First, we measured gall diameter as
-the size of each gall chamber to the nearest 0.01 mm at its maximum
-diameter (perpendicular to the direction of plant tissue growth). Our
-previous work has shown that larger galls are associated with higher
-survival (Barbour et al. 2016). Second, we measured clutch size by
-counting the number of chambers in each gall (Weis, Price, and Lynch
-1983; Heath, Abbot, and Stireman 2018). All larvae collected from the
-same multi-chambered gall were scored with the same clutch size. Third,
-we measured oviposition (egg laying) preference as the density of larvae
-observed on a plant in an independent survey. We did this randomly
-sampling five branches per tree and counting the number of individual
-gall chambers (number of larvae). We then converted these counts to a
-measure of larval density per 100 shoots by counting the number of
-shoots on the last branch we sampled. All larvae collected from the same
-plant were scored with the same oviposition preference. Measuring larval
-densities on plants in the field is a common method for measuring
-oviposition preference (Gripenberg et al. 2010); however, caution must
-be taken in inferring `preference' as larval densities can be influenced
-by processes other than preference (Singer 1986). Fortunately, a couple
-of features of our study system suggest that larval densities may be a
-good proxy for oviposition preference. For example, since our data comes
-from a randomized placement of plant genotypes in a common garden, there
-is no consistent bias in which plant genotypes females are exposed to
-while searching for oviposition sites. Also, egg predation is a minor
-source of mortality for galling insects in general (Hawkins, Cornell,
-and Hochberg 1997); therefore, we do not expect any prior egg predation
-to bias our estimates of observed larval densities.
+influence larval survival based on our previous work \citep{Barbour2016}
+and others work with gall midges \citep{Weis1983, Heath2018}. First, we
+measured gall diameter as the size of each gall chamber to the nearest
+0.01 mm at its maximum diameter (perpendicular to the direction of plant
+tissue growth). Our previous work has shown that larger galls are
+associated with higher survival \citep{Barbour2016}. Second, we measured
+clutch size by counting the number of chambers in each gall
+\citep{Weis1983, Heath2018}. All larvae collected from the same
+multi-chambered gall were scored with the same clutch size. Third, we
+measured oviposition preference as the density of larvae observed on a
+plant in an independent survey. We did this randomly sampling five
+branches per tree and counting the number of individual gall chambers
+(number of larvae). We then converted these counts to a measure of
+larval density per 100 shoots by counting the number of shoots on the
+last branch we sampled. All larvae collected from the same plant were
+scored with the same oviposition preference. Measuring larval densities
+on plants in the field is a common method for measuring oviposition
+preference \citep{Gripenberg2010}; however, caution must be taken in
+inferring `preference' as larval densities can be influenced by
+processes other than preference \citep{Singer1986}. Fortunately, a
+couple of features of our study system suggest that larval densities may
+be a good proxy for oviposition preference. For example, since our data
+comes from a randomized placement of plant genotypes in a common garden,
+there is no consistent bias in which plant genotypes females are exposed
+to while searching for oviposition sites. Also, egg predation is a minor
+source of mortality for galling insects in general \citep{Hawkins1997};
+therefore, we do not expect any prior egg predation to bias our
+estimates of observed larval densities.
 
@@
 adaptive landscapes from selection surfaces assumes that trait
-distributions are multivariate normal (Lande and Arnold 1983). To
-approximate this assumption, we log-transformed clutch size and
-square-root transformed oviposition preference. We then scaled all
-phenotypic traits (mean=0 and SD=1) in order to calculate standardized
-selection gradients that were comparable across traits and with other
-studies of natural selection.
+distributions are multivariate normal \citep{Lande1983}. To approximate
+this assumption, we log-transformed clutch size and square-root
+transformed oviposition preference. We then scaled all phenotypic traits
+(mean=0 and SD=1) in order to calculate standardized selection gradients
+that were comparable across traits and with other studies of natural
+selection.
 
@@
 linear trait-fitness relationships, we removed nonlinear terms prior to
-estimating linear relationships (Lande and Arnold 1983). Other
-approaches have been advocated for approximating selection surfaces
-(Schluter 1988); however, our approach enables us to calculate selection
-gradients, and thus is more appropriate for approximating the adaptive
-landscape (Arnold 2003). To account for the nonindependence of clutch
-size (measured at gall level) and oviposition preference (measured at
-plant level) as well as any independent effects of willow genotype on
-larval survival, we modelled gall ID nested within plant ID nested
-within genotype ID as random effects. Although statistical models with
-random effects are not common in analyses of natural selection, we think
-this is a mistake since modelling random effects can mitigate biased
-estimates of selection due to environmental covariances between traits
-and fitness (Rausher 1992). Since our end goal was to characterize the
-relationship between mean trait values and mean fitness (adaptive
-landscape), we assumed the mean value of our random effects
-(i.e.~setting them to zero) when calculating trait-fitness
+estimating linear relationships \citep{Lande1983}. Other approaches have
+been advocated for approximating selection surfaces
+\citep{Schluter1988}; however, our approach enables us to calculate
+selection gradients, and thus is more appropriate for approximating the
+adaptive landscape \citep{Arnold2003}. To account for the
+nonindependence of clutch size (measured at gall level) and oviposition
+preference (measured at plant level) as well as any independent effects
+of willow genotype on larval survival, we modelled gall ID nested within
+plant ID nested within genotype ID as random effects. Although
+statistical models with random effects are not common in analyses of
+natural selection, we think that modelling random effects can mitigate
+biased estimates of selection due to environmental covariances between
+traits and fitness \citep{Rausher1992}. Since our end goal was to
+characterize the relationship between mean trait values and mean fitness
+(adaptive landscape), we assumed the mean value of our random effects
+(i.e., setting them to zero) when calculating trait-fitness
 relationships. We then used parametric bootstrapping (1,000 replicates)
@@
 
-\textbf{Selection gradients}: We used the method of Janzen and Stern
-(1998) to translate trait-fitness relationships (\(\alpha\)) into the
-scale of relative fitness in order to calculate directional
-(\(\beta_{z_i}\)), quadratic (\(\gamma_{z_i:z_i}\)), and correlational
+\textbf{Selection gradients}: We used the method of \citet{Janzen1998}
+to translate trait-fitness relationships (\(\alpha\)) into the scale of
+relative fitness in order to calculate directional (\(\beta_{z_i}\)),
+quadratic (\(\gamma_{z_i:z_i}\)), and correlational
 (\(\gamma_{z_i:z_j}\)) selection gradients. Briefly, this method
@@
 calculating selection gradients to put them on the same scale as
-estimates of directional and correlational selection (Stinchcombe et al.
-2008).
-
-\textbf{Adaptive landscape}: We took advantage of existing theory that
-translates estimates of selection gradients to the adaptive landscape
-(Phillips and Arnold 1989; Arnold 2003). The shape of the adaptive
-landscape can be described by both its slope and curvature, each of
-which describe different aspects of constraints on phenotypic evolution.
-Specifically, the slope corresponds to the column vector of directional
-selection gradients, which in our study corresponds to:
+estimates of directional and correlational selection
+\citep{Stinchcombe2008}.
+
+\textbf{Evolutionary constraints}: We quantified the effects of food-web
+complexity on evolutionary constraints by inspecting the slope and
+curvature of the adaptive landscape. The number of selective constraints
+is determined by the slope of the adaptive landscape, which in our study
+corresponds to:
 
 \[\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} \]
-This slope describes the selective constraints acting on the trajectory
-of phenotypic evolution, which is governed by the `Lande equation',
-\(\Delta \bar z=\text{G}\beta\) (Lande 1979). Quantitative predictions
-of evolutionary trajectories requires knowledge of a population's
-\textbf{G}-matrix; however, we can gain qualitative insight to
-evolutionary constraints by counting the number of phenotypic traits
-under directional selection (selective constraints, Arnold 1992).
-
-The curvature (\textbf{C}) of the adaptive landscape is a matrix that is
-determined by directional, quadratic, and correlational selection
-gradients, such that
-\boldmath\(\text{C}=\gamma - \beta \beta^\text{T}\), or more explicitly:
+By comparing the number of traits that determine the slope (i.e.,
+nonzero directional selection gradients) in simpler vs.~more complex
+food webs, we can infer the effect of food-web complexity on selective
+constraints.
+
+The indirect effects of selection on genetic constraints is governed by
+the curvature of the adaptive landscape, which in our study corresponds
+to:
 
@@
 Note that we ommitted the upper triangle of each matrix for clarity
-since it is simply the reflection of the lower triangle. This curvature
-matrix describes the indirect effects of selection on genetic
-constraints within a generation
-(\(\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}\)).
-For example, the sign of diagonal terms of the curvature matrix dictate
-whether selection will increase (+), decrease (-), or cause no change
-(0) in the additive genetic variance of a trait. Similarly, any nonzero
-covariance terms (off-diagonal) are indicative of selection for trait
-integration (less trait independence). Therefore, we can infer the
-indirect effects of selection on genetic constraints by counting the
-number of negative signs along the diagonal (decrease in additive
-genetic variance) and the number of nonzero terms along the off-diagonal
-(trait integration) of the curvature matrix.
+since it is simply the reflection of the lower triangle. The sign of
+diagonal terms of the curvature matrix dictate whether selection will
+increase (+), decrease (-), or cause no change (0) in the additive
+genetic variance of a trait. Similarly, any nonzero covariance terms
+(off-diagonal) are indicative of selection for trait integration (i.e.,
+less independence). Therefore, we can infer the indirect effects of
+selection on genetic constraints by counting the number of negative
+signs along the diagonal (decrease in additive genetic variance) and the
+number of nonzero terms along the off-diagonal (trait integration) of
+the curvature matrix.
 
@@
 
-Rather than imposing selection, parasitoids may themselves influence the
-expression of herbivore traits which could bias measurements of
-selection. In our system, it was plausible that parasitoids may
-influence chamber diameter by altering larval feeding behavior or
-killing larvae before they complete their development. To estimate this
-potential bias, we subset our data to only include galls where there was
-variation in larval survival within the same gall (i.e.~1 \textgreater{}
-mean survival \textgreater{} 0). If we assume that larvae within each
-gall should have similar chamber diameters because they come from the
-same clutch and experience the same local environment (an assumption our
-data supports: gall ID explains 54\% of the variance in chamber
-diameter), then the relationship between chamber diameter and larval
-survival in this data subset represents the effect of parasitism on
-trait expression (i.e.~bias). We used a GLMM with the same structure as
-described above except that we only modelled a linear relationship
-between chamber diameter and larval survival (\(\alpha_{\text{Diam}}\)).
-We detected a positive bias in both food-web treatments (complex
+Rather than imposing selection, parasitoids may influence the expression
+of herbivore traits which could bias measurements of selection. In our
+system, it was plausible that parasitoids may influence chamber diameter
+by altering larval feeding behavior or killing larvae before they
+complete their development. To estimate this potential bias, we subset
+our data to only include galls where there was variation in larval
+survival within the same gall (i.e.~1 \textgreater{} mean survival
+\textgreater{} 0). If we assume that larvae within each gall should have
+similar chamber diameters because they come from the same clutch and
+experience the same local environment (an assumption our data supports:
+gall ID explains 54\% of the variance in chamber diameter), then the
+relationship between chamber diameter and larval survival in this data
+subset represents the effect of parasitism on trait expression
+(i.e.~bias). We used a GLMM with the same structure as described above
+except that we only modelled a linear relationship between chamber
+diameter and larval survival (\(\alpha_{\text{Diam}}\)). We detected a
+positive bias in both food-web treatments (complex
 \(\alpha_{\text{Diam}}\)= 0.36 {[}0.05, 0.67{]}; simple
@@
 
-All analyses and visualizations were conducted in R (R Core Team 2018).
+All analyses and visualizations were conducted in R \citep{R2018}.
 Unless otherwise noted, we report mean estimates of trait-fitness
@@
 fact that we can only reliably estimate the shape of the adaptive
-landscape near the mean phenotype of the population (Arnold, Pfrender,
-and Jones 2001). We also plot mean larval survival on a natural log
-scale to accurately reflect the shape of the adaptive landscape (Arnold
-2003).
+landscape near the mean phenotype of the population \citep{Arnold2001}.
+We also plot mean larval survival on a natural log scale to accurately
+reflect the shape of the adaptive landscape \citep{Arnold2003}.
 
@@
 
-The structure of these matrices indicate that there are more selective
-constraints imposed on the gall midge in the simple (6 of 6) vs.~complex
-(1 of 6) food web. Simple food webs acted to decrease genetic variance
-for all three phenotypic traits (negative diagonal terms), whereas only
-one trait (chamber diameter) experienced a decrease in additive genetic
-variance in the complex food web. For genetic covariances, the simple
-food web favored integration among all three phenotypic traits (nonzero
-off-diagonal terms), and thus constraints along all three axes of
-covariance (fig. \ref{fig:MV_Landscape}). In contrast, there was no
-strong evidence of trait integration in the complex food web (fig.
-\ref{fig:MV_Landscape}).
+Remember that we can infer the indirect effects of selection on genetic
+constraints by counting the number of negative signs along the diagonal
+(decrease in additive genetic variance) and the number of nonzero terms
+along the off-diagonal (trait integration) of the curvature matrix. The
+structure of these matrices indicates that there are more selective
+constraints imposed on the gall midge in the simpler (6 of 6) vs.~more
+complex (1 of 6) food web. Simpler food webs acted to decrease genetic
+variance for all three phenotypic traits (negative diagonal terms),
+whereas only one trait (chamber diameter) experienced a decrease in
+additive genetic variance in the more complex food web. For genetic
+covariances, the simpler food web favored integration among all three
+phenotypic traits (nonzero off-diagonal terms), and thus constraints
+along all three axes of covariance (fig. \ref{fig:MV_Landscape}). In
+contrast, there was no strong evidence of trait integration in the more
+complex food web (fig. \ref{fig:MV_Landscape}).
 
@@
 \hypertarget{refs}{}
-\hypertarget{ref-Abrams2000}{}
-Abrams, Peter A. 2000. ``The Evolution of Predator-Prey Interactions:
-Theory and Evidence.'' \emph{Annual Review of Ecology and Systematics}
-31 (1): 79--105.
-doi:\href{https://doi.org/10.1146/annurev.ecolsys.31.1.79}{10.1146/annurev.ecolsys.31.1.79}.
-
-\hypertarget{ref-Arnold1992}{}
-Arnold, Stevan J. 1992. ``Constraints on Phenotypic Evolution.''
-\emph{The American Naturalist} 140. University of Chicago Press:
-S85--S107.
-
-\hypertarget{ref-Arnold2003}{}
-Arnold, Stevan J. 2003. ``Performance Surfaces and Adaptive
-Landscapes1.'' \emph{Integrative and Comparative Biology} 43 (3):
-367--75.
-doi:\href{https://doi.org/10.1093/icb/43.3.367}{10.1093/icb/43.3.367}.
-
-\hypertarget{ref-Arnold1984applications}{}
-Arnold, Stevan J., and Michael J. Wade. 1984a. ``On the Measurement of
-Natural and Sexual Selection: Applications.'' \emph{Evolution} 38 (4):
-720--34. \url{http://www.jstor.org/stable/2408384}.
-
-\hypertarget{ref-Arnold1984theory}{}
----------. 1984b. ``On the Measurement of Natural and Sexual Selection:
-Theory.'' \emph{Evolution} 38 (4): 709--19.
-\url{http://www.jstor.org/stable/2408383}.
-
-\hypertarget{ref-Arnold2001}{}
-Arnold, Stevan J., Michael E. Pfrender, and Adam G. Jones. 2001. ``The
-Adaptive Landscape as a Conceptual Bridge Between Micro- and
-Macroevolution.'' \emph{Genetica} 112 (1): 9--32.
-doi:\href{https://doi.org/10.1023/A:1013373907708}{10.1023/A:1013373907708}.
-
-\hypertarget{ref-Barbour2016}{}
-Barbour, Matthew A., Miguel A. Fortuna, Jordi Bascompte, Joshua R.
-Nicholson, Riitta Julkunen-Tiitto, Erik S. Jules, and Gregory M.
-Crutsinger. 2016. ``Genetic Specificity of a Plantinsect Food Web:
-Implications for Linking Genetic Variation to Network Complexity.''
-\emph{Proceedings of the National Academy of Sciences} 113 (8). National
-Academy of Sciences: 2128--33.
-doi:\href{https://doi.org/10.1073/pnas.1513633113}{10.1073/pnas.1513633113}.
-
-\hypertarget{ref-Barbour2015}{}
-Barbour, Matthew A., Mariano A. Rodriguez-Cabal, Elizabeth T. Wu, Riitta
-Julkunen-Tiitto, Carol E. Ritland, Allyson E. Miscampbell, Erik S.
-Jules, and Gregory M. Crutsinger. 2015. ``Multiple Plant Traits Shape
-the Genetic Basis of Herbivore Community Assembly.'' \emph{Functional
-Ecology} 29 (8): 995--1006.
-doi:\href{https://doi.org/10.1111/1365-2435.12409}{10.1111/1365-2435.12409}.
-
-\hypertarget{ref-Bascompte2014}{}
-Bascompte, Jordi, and Pedri Jordano. 2014. \emph{Mutualistic Networks}.
-Princeton University Press.
-\url{http://www.jstor.org/stable/j.ctt5hhnpq}.
-
-\hypertarget{ref-Bronstein2006}{}
-Bronstein, Judith L., Ruben Alarcón, and Monica Geber. 2006. ``The
-Evolution of Plant--insect Mutualisms.'' \emph{New Phytologist} 172 (3):
-412--28.
-doi:\href{https://doi.org/10.1111/j.1469-8137.2006.01864.x}{10.1111/j.1469-8137.2006.01864.x}.
-
-\hypertarget{ref-Darwin1859}{}
-Darwin, Charles. 1859. \emph{On the Origin of Species by Means of
-Natural Selection}. London: Murray.
-
-\hypertarget{ref-Gagne1989}{}
-Gagné, R J. 1989. ``The Plant-Feeding Gall Midges of North America.''
-agris.fao.org.
-
-\hypertarget{ref-Gripenberg2010}{}
-Gripenberg, Sofia, Peter J. Mayhew, Mark Parnell, and Tomas Roslin.
-2010. ``A Meta-Analysis of Preference--performance Relationships in
-Phytophagous Insects.'' \emph{Ecology Letters} 13 (3): 383--93.
-doi:\href{https://doi.org/10.1111/j.1461-0248.2009.01433.x}{10.1111/j.1461-0248.2009.01433.x}.
-
-\hypertarget{ref-Hansen2008}{}
-Hansen, T F, and D Houle. 2008. ``Measuring and Comparing Evolvability
-and Constraint in Multivariate Characters.'' \emph{J. Evol. Biol.} 21
-(5): 1201--19.
-
-\hypertarget{ref-Hawkins1997}{}
-Hawkins, Bradford A., Howard V. Cornell, and Michael E. Hochberg. 1997.
-``Predators, Parasitoids, and Pathogens as Mortality Agents in
-Phytophagous Insect Populations.'' \emph{Ecology} 78 (7): 2145--52.
-doi:\href{https://doi.org/10.1890/0012-9658(1997)078\%5B2145:PPAPAM\%5D2.0.CO;2}{10.1890/0012-9658(1997)078{[}2145:PPAPAM{]}2.0.CO;2}.
-
-\hypertarget{ref-Heath2018}{}
-Heath, Jeremy J., Patrick Abbot, and John O. Stireman. 2018. ``Adaptive
-Divergence in a Defense Symbiosis Driven from the Top down.'' \emph{The
-American Naturalist} 192 (1): E21--E36.
-doi:\href{https://doi.org/10.1086/697446}{10.1086/697446}.
-
-\hypertarget{ref-Janzen1998}{}
-Janzen, Fredric J., and Hal S. Stern. 1998. ``Logistic Regression for
-Empirical Studies of Multivariate Selection.'' \emph{Evolution} 52 (6):
-1564--71.
-doi:\href{https://doi.org/10.1111/j.1558-5646.1998.tb02237.x}{10.1111/j.1558-5646.1998.tb02237.x}.
-
-\hypertarget{ref-Lande1979}{}
-Lande, Russell. 1979. ``Quantitative Genetic Analysis of Multivariate
-Evolution, Applied to Brain:body Size Allometry.'' \emph{Evolution} 33
-(1Part2): 402--16.
-doi:\href{https://doi.org/10.1111/j.1558-5646.1979.tb04694.x}{10.1111/j.1558-5646.1979.tb04694.x}.
-
-\hypertarget{ref-Lande1983}{}
-Lande, Russell, and Stevan J. Arnold. 1983. ``The Measurement of
-Selection on Correlated Characters.'' \emph{Evolution} 37 (6): 1210--26.
-\url{http://www.jstor.org/stable/2408842}.
-
-\hypertarget{ref-McCann2012}{}
-McCann, Kevin S. 2012. \emph{Food Webs}. Princeton University Press.
-\url{http://www.jstor.org/stable/j.ctt7rr0s}.
-
-\hypertarget{ref-McPeek2017}{}
-McPeek, Mark A. 2017. \emph{Evolutionary Community Ecology}. Princeton
-University Press. \url{http://www.jstor.org/stable/j.ctt1p0vjqn}.
-
-\hypertarget{ref-Phillips1989}{}
-Phillips, Patrick C., and Stevan J. Arnold. 1989. ``Visualizing
-Multivariate Selection.'' \emph{Evolution} 43 (6): 1209--22.
-doi:\href{https://doi.org/10.1111/j.1558-5646.1989.tb02569.x}{10.1111/j.1558-5646.1989.tb02569.x}.
-
-\hypertarget{ref-R2018}{}
-R Core Team. 2018. \emph{R: A Language and Environment for Statistical
-Computing}. Vienna, Austria: R Foundation for Statistical Computing.
-\url{https://www.R-project.org/}.
-
-\hypertarget{ref-Rausher1992}{}
-Rausher, Mark D. 1992. ``THE Measurement of Selection on Quantitative
-Traits: BIASES Due to Environmental Covariances Between Traits and
-Fitness.'' \emph{Evolution} 46 (3): 616--26.
-doi:\href{https://doi.org/10.1111/j.1558-5646.1992.tb02070.x}{10.1111/j.1558-5646.1992.tb02070.x}.
-
-\hypertarget{ref-Russo2006}{}
-Russo, Ron. 2006. \emph{Field Guide to Plant Galls of California and
-Other Western States}. 1st ed. University of California Press.
-\url{http://www.jstor.org/stable/10.1525/j.ctt1pnc33}.
-
-\hypertarget{ref-Scheffers2016}{}
-Scheffers, Brett R., Luc De Meester, Tom C. L. Bridge, Ary A. Hoffmann,
-John M. Pandolfi, Richard T. Corlett, Stuart H. M. Butchart, et al.
-2016. ``The Broad Footprint of Climate Change from Genes to Biomes to
-People.'' \emph{Science} 354 (6313). American Association for the
-Advancement of Science.
-doi:\href{https://doi.org/10.1126/science.aaf7671}{10.1126/science.aaf7671}.
-
-\hypertarget{ref-Schluter1988}{}
-Schluter, Dolph. 1988. ``ESTIMATING the Form of Natural Selection on a
-Quantitative Trait.'' \emph{Evolution} 42 (5): 849--61.
-doi:\href{https://doi.org/10.1111/j.1558-5646.1988.tb02507.x}{10.1111/j.1558-5646.1988.tb02507.x}.
-
-\hypertarget{ref-Schluter2000}{}
----------. 2000. ``Ecological Character Displacement in Adaptive
-Radiation.'' \emph{The American Naturalist} 156 (S4): S4--S16.
-\url{http://www.jstor.org/stable/10.1086/303412}.
-
-\hypertarget{ref-Simpson1944}{}
-Simpson, George Gaylord. 1944. \emph{Tempo and Mode in Evolution}.
-Columbia University Press.
-
-\hypertarget{ref-Singer1986}{}
-Singer, Michael C. 1986. ``The Definition and Measurement of Oviposition
-Preference in Plant-Feeding Insects.'' In \emph{Insect-Plant
-Interactions}, edited by James R. Miller and Thomas A. Miller, 65--94.
-New York, NY: Springer New York.
-doi:\href{https://doi.org/10.1007/978-1-4612-4910-8_3}{10.1007/978-1-4612-4910-8\_3}.
-
-\hypertarget{ref-Stinchcombe2008}{}
-Stinchcombe, John R, Aneil F Agrawal, Paul A Hohenlohe, Stevan J Arnold,
-and Mark W Blows. 2008. ``Estimating Nonlinear Selection Gradients Using
-Quadratic Regression Coefficients: Double or Nothing?'' \emph{Evolution}
-62 (9): 2435--40.
-
-\hypertarget{ref-terHorst2018}{}
-terHorst, Casey P, Peter C Zee, Katy D Heath, Thomas E Miller, Abigail I
-Pastore, Swati Patel, Sebastian J Schreiber, Michael J Wade, and Matthew
-R Walsh. 2018. ``Evolution in a Community Context: Trait Responses to
-Multiple Species Interactions*.'' \emph{Am. Nat.}, January. University
-of Chicago PressChicago, IL.
-
-\hypertarget{ref-Weis1983}{}
-Weis, Arthur E., Peter W. Price, and Michael Lynch. 1983. ``Selective
-Pressures on Clutch Size in the Gall Maker Asteromyia Carbonifera.''
-\emph{Ecology} 64 (4): 688--95.
-\url{http://www.jstor.org/stable/1937190}.
-
-\hypertarget{ref-Wright1931}{}
-Wright, Sewall. 1931. ``EVOLUTION in Mendelian Populations.''
-\emph{Genetics} 16 (2). Genetics: 97--159.
-\url{http://www.genetics.org/content/16/2/97}.
 
@@
 For clarity, we only display 100 bootstraps even though inferences are
-based on 1,000 replicates. Solid yellow lines represent selection
-imposed by larval parasitoids in the complex food web. Note that mean
-larval survival is plotted on a natural log scale to accurately reflect
-the adaptive landscape.
+based on 1,000 replicates.Note that mean larval survival is plotted on a
+natural log scale to reflect the mathematical defintion of the adaptive
+landscape.
 
@@
 clutch size and chamber diameter (A); clutch size and oviposition
-preference (B); oviposition preference and chamber diameter (C).
-Selection favors trait integration for each combination of traits in
-simple food webs, whereas there is no strong evidence for trait
-integration in complex food webs. Note that mean larval survival is
-plotted on a natural log scale to accurately reflect the adaptive
-landscape.
+preference (B); oviposition preference and chamber diameter (C). Note
+the flat landscape in mean larval survival for clutch size and
+oviposition preference in more complex food webs, whereas all three
+traits shape the adaptive landscape in simpler food webs. This indicates
+that selection favors trait integration for each combination of traits
+in simpler food webs, whereas there is no strong evidence for trait
+integration in more complex food webs. Note that mean larval survival is
+plotted on a natural log scale to reflect the mathematical defintion of
+the adaptive landscape.
 
@@
 \includegraphics{analyses/UV_landscapes.pdf}
-\caption{\label{fig:UV_Landscape}}
+\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
+phenotypes in complex vs.~simple food webs. Each panel corresponds to a
+different phenotypic trait: chamber diameter (A); oviposition preference
+(B); and clutch size (C). Solid lines represent selection experienced in
+complex (orange) and simple (blue) food webs. Transparent lines
+represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are
+based on 1,000 replicates. Note that mean larval survival is plotted on
+a natural log scale to reflect the mathematical defintion of the
+adaptive landscape.}
 \end{figure}
@@
 
+\renewcommand\refname{Appendix}
+\bibliography{references}
+
 \end{document}

### 2019-01-09 analyses/reproduce_analyses.Rmd
update fig. 3 with arrows and contours

@@
 
+# Arrow data
+gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
+                                    sc.Diam = c(0,0), 
+                                    sc.log.Clutch = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
+
+gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
+                                    sc.sqrt.Pref = c(0,0), 
+                                    sc.log.Clutch = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
+
+gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
+                                    sc.Diam = c(0,0), 
+                                    sc.sqrt.Pref = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))
+
+# Set contour breaks
+breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
+
 # Format plots
@@
                               axis.title.x = element_blank(),
-                             axis.text.x = element_blank()),
+                             axis.text.x = element_blank()) +
+    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
+    geom_segment(data = gradients_Diam.Clutch, 
+                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
+                 arrow = arrow(length = unit(0.03, "npc"))),
   AF_plot_Clutch.Pref + theme(legend.position = "none", 
                               axis.title.y = element_blank(),
-                              axis.text.y = element_blank()) + xlab("Preference (SDs)"), 
-  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)"), 
+                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
+    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
+    geom_segment(data = gradients_Clutch.Pref, 
+                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
+                 arrow = arrow(length = unit(0.03, "npc"))), 
+  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
+    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
+    geom_segment(data = gradients_Diam.Pref, 
+                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
+                 arrow = arrow(length = unit(0.03, "npc"))), 
   nrow=2, align="hv", labels = "AUTO")

### 2019-01-09 manuscript.Rmd
update fig. 3 with arrows and contours

@@
 
-\noindent 1. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada;
+\noindent 1. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada; <!-- consider removing -->
 
@@
 
-*Keywords*: fitness landscape, host-parasitoid, natural selection, G-matrix, community context, ecological networks.
+*Keywords*: fitness landscape, host-parasitoid, natural selection, G-matrix, community context, ecological networks, evolutionary ecology, eco-evolutionary dynamics.
 
@@
 
+> "What escapes the eye, however, is a much more insidious kind of extinction: the extinction of ecological interactions." @Janzen1974
+
 # Introduction
@@
 For example, competition for shared prey in threespine stickleback has driven their adaptive divergence into ecotypes with specialized body and gill morphologies [@Schluter2000, other papers].
-Similarly, the elongated, red corollas of many flowering species have evolved in response to the efficient pollination of hummingbirds [cite].--> Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we do not know how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018].
+Similarly, the elongated, red corollas of many flowering species have evolved in response to the efficient pollination of hummingbirds [cite].--> Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we do not know how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018]<!--SOFTEN THIS STATEMENT-->.
 Resolution on how the community context shapes phenotypic evolution is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].
 
-Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012].<!--These networks describe the interdependency of populations within an ecological community, providing an effective framework for predicting how the strength and organization of ecological interactions (network structure) affect population and community dynamics [@Bascompte2014; @McCann2012].
+Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012]<!--SENTENCE SEEMS MISPLACED-->.
+<!--These networks describe the interdependency of populations within an ecological community, providing an effective framework for predicting how the strength and organization of ecological interactions (network structure) affect population and community dynamics [@Bascompte2014; @McCann2012].
 Nevertheless, these networks often lack quantitative information on how ecological interactions influence selection on phenotypic traits.
@@
 If we want to predict how community context constrains evolutionary change, we must understand how ecological networks shape the adaptive landscape.
+<!-- need to cite more than just Hansen and Houle 2008 here -->
 
@@
 These galls protect larva from attack by generalist predators (e.g.
-ants, spiders), but they suffer high mortaltiy from egg and larval parasitoids [@Barbour2016].
+ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016].
 We manipulated food-web complexity by either excluding the guild of larval parasitoids (simple food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (complex food web; fig.
@@
 Third, we measured oviposition preference as the density of larvae observed on a plant in an independent survey.
-We did this randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
+We did this by randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
 We then converted these counts to a measure of larval density per 100 shoots by counting the number of shoots on the last branch we sampled.
@@
 For example, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of oSimilar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982]Similar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982]bserved larval densities.
+Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
 
@@
 
-The indirect effects of selection on genetic constraints is governed by the curvature of the adaptive landscape, which in our study corresponds to:
+The indirect effects of selection on genetic constraints is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 <!--The curvature (**C**) of the adaptive landscape is a matrix that is determined by directional, quadratic, and correlational selection gradients, such that \boldmath$\text{C}=\gamma - \beta \beta^\text{T}$, or more explicitly:-->
@@
 Unless otherwise noted, we report mean estimates of trait-fitness relationships and selection gradients with 95% confidence intervals in brackets.
-Note that for visualizing the adaptive landscape weSimilar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982] restrict trait axes to $\pm 1$ SD of the mean trait value.
+Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
 This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [@Arnold2001].
-We also plot mean larval survival on a natural log scale to accurately reflect the shape of the adaptive landscape [@Arnold2003].
+We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
 
@@
 
-## Food-web complexity reduces selective constraints
+<!-- TRIPLE CHECK ALL RESULT OUTPUTS AND WRITTEN INTERPRETATIONS -->
+
+## Simpler food webs increase selective constraints
 
 \indent We found that more gall midge traits experienced directional selection in the simple (3 of 3) vs.
-complex food webs (1 of 3)(table \ref{Table:Gradients}).
+complex food-web treatment (1 of 3)(table \ref{Table:Gradients}).
 For example, we observed directional selection for smaller clutch sizes in the simple food web, but there was no evidence of selection acting on this trait in the complex food web (table \ref{Table:Gradients}; fig.
@@
 This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids (fig.
-\ref{fig:UV_Landscape}C).
+\ref{fig:UV_Landscape}).
 Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
@@
 
-## Food-web complexity reduces genetic constraints
+## Simpler food webs increase genetic constraints
 
@@
 The negative relationship between oviposition preference and larval survival dampened at high densities in complex, but not simple food webs (fig.
-\ref{fig:UV_Landscape}).
+\ref{fig:UV_Landscape}B).
 This dampened relationship was partly due to a trend for nonlinear selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
@@
 ## Selection on the extended phenotype of egg parasitoids
+
+<!-- CONSIDER AVOIDING EXTENDED PHENOTYPE AND FOCUS ON INDIRECT EFFECTS OR INDIRECT SELECTION -->
 
@@
 
+<!--Summary-->
+Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs.
+More traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting that the trajectory of phenotypic evolution is more constrained.
+Similarly, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
+We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs.
+Taken together, our study provides experimental evidence from the field that the simplification of ecological communities may constrain the adaptive potential of remaining populations.
+
+<!--Selective constraints-->
+All three phenotypic traits we examined experienced directional selection in the simpler food web, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
+large chamber diameter, small clutch size, and avoidance of conspecifics).
+In contrast, we did not observe selective constraints on clutch size and oviposition preference in the more complex food web.
+This suggests that there are many optimal phenotypes (adaptive peaks), or in this case, a flat adaptive landscape where there are no fitness consequences for phenotypic change in these traits.
+This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by genetic constraints.
+This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
+As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
+Interestingly, this corresponds to @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
+@Schluter1996 found support for this hypothesis from data on natural populations of several vertebrate species, including threespine sticklebacks, a few species of songbirds, and mice from the genus *Peromyscus*.
+All of these species occupy intermediate trophic levels and are likely embedded in complex food webs, which is consistent with our suggestion that genetic constraints may have a stronger influence in more complex food webs.
+
+<!--Indirect effects of selective constraints-->
+We also found evidence for more genetic constraints in simpler food webs due to indirect effects of selection on the population's G-matrix.
+The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
+When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
+Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
+Together, this suggests that simpler food webs may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
+Current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the community context [@McPeek2017; @Guimaraes2017].
+Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that are shaped by the community context.
+
+<!-- Generality of results -->
+The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
+In the simplest case, when consumers do not differ from each other, then we do not expect changes in food-web complexity to modify selective constraints.
+Also, many consumers may be at too low of abundances to impose selection on their resources.
+Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
+When consumers are abundant though, the effect of food-web complexity will depend on whether different species impose conflicting selection pressures or select for distinct traits.
+For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997; @Start2016].
+Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.
+On the other hand, different consumers may impose selection on different traits, favoring trait integration and increasing genetic constraints.
+Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
+We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.
+
+<!--Indirect evolutionary effects-->
+Our results suggest that the simplification of ecological communities may not only directly affect connected species, but also result in indirect evolutionary effects.
+In our study, this indirect effect arises from egg parasitoids being released from intraguild predation in simpler food webs.
+This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
+A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018]<!--; Start et al.
+in press-->.
+If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the simplification of food webs will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
+
+<!-- Community context shaping adaptation to environmental change --> 
+There are a growing number of theoretical studies on adaptation to directional environmental change that incorporate species interactions [e.g.
+@deMazancourt2008; @Johansson2008; @Norberg2012; @Osmond2017PredatorsHelpPrey].
+This work has given insight to the mechanisms by which pairwise interactions modify the adaptive potential of species.
+Our study hints at a novel mechanism, whereby food-web complexity flattens the adaptive landscape, thus facilitating future adaptation by allowing genetic and phenotypic variation to persist.
+This mechanism only emerges once we move beyond pairwise interactions to consider selection on multiple traits in a community context.
+However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
+This negative effect of species diversity on adaptation occurs because there is a greater chance that the optimal phenotype is already occupied by a competitor in a more diverse community.
+More work is needed to examine how the distribution of different interaction types affects adaptation to environmental change in species-rich communities.
+
+<!-- Conclusions -->
+Our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, increase evolutionary constraints.
+This hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
+Our work also highlights some key challenges for predicting phenotypic evolution in the face of global change.
+First, the simplification of ecological communities may actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.
+Second, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait, yet our results highlight that the number of traits under selection may change with the community context.
+Importantly, while the net effects of selection in complex communities may be dampened, we still found that different species/guilds imposed different selection pressures.
+Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the community context.
+We expect that a continued integration of adaptive landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
+
 <!--
@@
 -->
-
+<!--More phenotypic traits experienced directional selection in the simple food-web treatment, suggesting that the trajectory of phenotypic evolution is more constrained.-->
+
+<!--, because the egg parasitoids that attack larva on high density trees have a higher chance of surviving.-->
+
+<!--In the context of global change, our results imply that the simplification of ecological communities may actually reduce the predictability of phenotypic evolution of remaining populations.
+This is because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.-->
+
+<!-- what should the focus be? 
+Conceptually, I don't think it'll be that interesting to try and review past studies.
+
+I think it would be more interesting to discuss the implications of our results and there generality. In other words, under what conditions do we expect them to hold. When will they break down?
+
+Highlight that we could gain more predictive power from theoretical models that also examine how selection modifies selection pressures of consumers.
+i.e.
+we need models of ecological character displacement that go beyoned pairwise interactions.
+In some communities, intraguild predation will be common so we also need models that examine how the community context shapes the evolution of trophic levels and the resulting feedbacks on associated communities (cite JP's Frontiers in Ecology and Evolution MS).
+
+Such indirect effects may be quite common when moving from complex to simple communities, and highlights the fact that species evolve in a community context.<!-- and the release of selection pressures may have rippling effects.-->  <!--If indirect evolutionary effects are common [@Walsh2013], then predicting the evolutionary trajectories of remaining populations after local extinctions will not only require knowledge of these indirect effects, but also require knowledge on the order of local extinctions.
+
+It is well known that increases in consumer diversity can driver character divergence in foraging traits due to ecological character displacment [@Schluter2000].
+In this case, we would expect the local extinction of a consumer to
+- Ecology example: selection on gall size in Eurosta
+- Evolution example: ecological character displacement tends to drive divergence.
+-->
+
+<!--
+Detailed case studies of natural selection on a single trait in a community context highlight the potential generality of our results.
+For example, galls induced by the fly *Eurosta solidaginis* experience directional selection for larger sizes by parasitoids (as we observed in our study), but selection for smaller sizes by birds [@Weis1985; @Abrahamson1997; @Start2016].
+Therefore, the dynamics of natural selection on gall size depend on the relative abundance of these consumers.
+A recent study in this system demonstrated that the loss of birds across a gradient of urbanization caused a shift from neutral to directional selection on gall size [@Start2018].
+This observational study supports our experimental demonstration that the loss of consumer diversity increases selective constraints.
+
+In a different system, the direction of selection on swimming speed in *Enallagama* damselflies depends on whether they occur in fish or fishless lakes [@McPeek1996; @McPeek1997].
+Lakes with fish select for damselflies , whereas dragonflies become the top predator in fishless lakes and select for adaptations to increase swimming speed.
+
+fish and dragonflies impose opposite directional selection on swimming speed in *Enallagma* damselflies . This has resulted in
+
+Lakes with fish likely have a much more diverse community of damselfly predators (multiple fish species and some smaller dragonfly species),
+
+Our study focused on an experimental manipulation of a focused community of consumers, leaving an open question to how our results generalize to more diverse consumer communities.
+
+-->
+<!--
+The generality of our results depends on the extent to which different consumer species are functionally different and their relative abundance.
+In the simplest case, when consumers do not differ from each other (i.e.
+neutral communities), then we do not expect changes in food-web complexity to modify selective constraints.
+Also, many consumer species may be at too low of abundances --><!--This may be the case with many consumers in diverse communities, where their abundances are simply not high enough --><!-- to impose selection on the mean trait values of resource populations.
+Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
+For abundant species though, the effect of food-web complexity depends on whether different species impose selection on different trait values vs.
+distinct traits.
+
+Current theory on character displacement suggests that consumers will usually diverge in foraging traits when foraging on a biological resource.
+On one end, theory should be extended beyond two consumers to examine trait dynamics in more diverse consumer communities.
+On the other hand, we also need to examine selection in the resources themselves.
+-->
+<!--
+Actually, different predator species impose selection on different axes of trait variation. 
+For example, habitat shifts into lakes where dragonflies are the top predator (instead of fish) promote adaptations for increased swimming speed in multiple lineages of *Enallagma* damselflies [@McPeek1996].
+Phenotypic selection study with damselflies [@McPeek1997].
+Biochemical evolution study with damselflies [@McPeek1999], still related to swimming speed.
+In McPeek's study though, there aren't dragonflies in lakes with fish?
+
+Lakes with fish are the ancestral state, and they move to fishless lakes.
+Although the fishless lakes may have simpler communities, we see a clear effect of the dominance hierarchy which highlights the importance of abundance.
+In this case, we have a strong intraguild predator that reduces the density of intraguild prey (dragonfly larvae), thus reducing their selection pressures.
+This indicates that its' not simply the presence/absence of different predators, but the evenness of these selection pressures.
+-->
+<!--
+Maybe they break down with plant-herbivore interactions? Or maybe these provide a useful example for thinking about when they'll break down or for highlighting indirect effects on genetic constraints?
+
+We suggest that being able to predict how changes in community context shape evolutionary constraints requires a deep understanding of the ecological and evolutionary feedbacks that shape trait variation and community structure.
+
+Here, we focus on how changes in food-web complexity affects evolutionary constraints on a single resource population. However, predicting h
+
+Predicting how evolution occurs in a community context thus requires an explicit examination of the eco-evolutionary feedbacks that propogate through the networks.
+The textbook example of such a feedback in structuring communities is ecological character displacement, "the process of phenotypic evolution in a species generated or maintained by resource competition with one or more coexisting species" [@Schluter2000].
+In scenarios, that promote character divergence in consumers, we would expect those consumers to impose selection on different axes of trait variation (although typically, a resource spectrum is used), resulting in more neutral selection on traits compared to a community with only one consumer.
+The character displacement framework would provide a useful starting point for theoretical studies that explore feedbacks between evolutiona and ecology in a community context [@McPeek2017].
+Importantly though, our results suggest that it would be useful in exploring multiple traits.
+In other words, we need to be able to predict not just how diversity itself affects phenotypic evolution of resources, but also of consumers.
+The body of research on character displacement provides a useful starting point, as there have been extensive examinations of how community context shapes phenotypic evolution of competing consumers [Abrams work, Taper and Case's work].
+Still, much of this work has focused on pairwise competitive interactions, with little exploration of the direct and indirect effects that may occurs in competitive communities [@Levine2017].
+-->
+<!--
+rather than how the complexity of interactions itself shapes the adaptive landscape, although a careful review of these studies can give valuable insights.
+For example, we found that fewer traits were under selection in complex vs.
+simple communities.
+In cases whether natural enemies impose selection on different axes of trait variation, we would expect complex communities to neutralize selective pressures.
+Recent work of pollinator communities [@Sahli2011; @terHorst2015; @Schiestl2018] has similarly shown a tendency for more traits to experience directional selection in simpler vs.
+more complex pollinator communities.
+
+@Stinchcombe2001 found that there was selection for increased deer resistance only in the presence of insects rather than their absence.
+
+For example, @Juenger1998 found that flies and caterpillars imposed the strongest reduction in plant fitness in isolation, but these effects were minimized when they were together, highlight a nonadditive interactions that result in neutral selection on flower time when both were present (unclipped treatment)
+
+However, @Lankau2007 only observed selection on chemical concentration of *Brassica* when both herbivores were present, but only when there was a heterospecif neighbor.
+In contrast, in the presence of conspecifics, then aphids and mollusks imposed contrasting selection pressures, resulting in no net selection.
+These different responses appear to be due to differences in diet breadth of mollusks and aphids.
+
+Schiestel et al.
+Evolution 2018: In the generalized treatment, only 1 axis of trait variation had a nonzero selection gradient.
+In the bumblebee only, there were 2-5 trait axes (depending whether you count marginal significance), in the hoverfly, there was only 1 trait axis.
+Interestingly, pollinator network complexity appears to dampen the selection gradients imposed by the most efficient pollinator (bumblebee), so I would say the interpretation is consistent.
+Here there appear to be some non-additive selection pressures at play.
+[greenhouse study with experimental manipulation of community]
+
+in terHorst 2010 Am.
+Nat, they also observed that increasing complexity often cancelled out the selection pressures shown by each species in isolation (e.g.
+cell area and population growth, or cell speed), although here, there appears to be non-additive selection pressures at play.
+Indeed, the indirect effects often result in little net evolution of multiple traits in multispecies populations that experienced both direct and indirect effects.
+(so it is tough to say for my experiment what might happen if we remove the parasitoids altogether...)[lab study with protist microcosms]
+
+Walsh's Rivulus work (Walsh and Reznick, 2008 and 2010) as well as Start's work is more of an indirect effect due to a specific selection pressure (predator then resources, and for Start's a herbivore competitor).[start was a field experiment, Walsh's work took advantage of evolved pops in different contexts, also manipulated food availability to tease apart direct vs.
+indirect eco-evo effects].
+
+There is also a study by Lau 2012 in Oecologia, but it's hard to follow.
+[field study with experimental manipulation of community].
+Actually, the reanalysis by terHorst et al.
+2015 suggests that selection for resistance follows the observed pattern (dampened selection in more complex community).
+
+Again for Sahli and Conner (2011 in Evolution), in the presence of all three pollinators, we lacked selection on Exsertion and Dimorphism. This evidence is quite compelling and interesting...
+
+Studies like Wise and Rausher show wide spread evidence for diffuse coevolution, but not through community members altering selection pressures, but via genetic covariances in resistance to herbivore species.
+They argue that diffuse interactions had an overwhelmingly constraining rather than facilitat effect, which may well be the case with a lot of covariances.
+[fiel study, no experimental manipulation of community]
+
+Lankau and Strauss 2007: (community complexity drives patterns of natural selection on a chemical defense of brassica nigra).
+
+Mauricio and Rausher 1997 Evolution did a field study where they sprayed the field and looked at selection.
+Interestingly, they only observed stabilizing selection (i.e.
+indirect genetic constraints) on glucosinolate concentration in the simply food web, but in general the selection pressures were quite similar...somthing funky with their analyses?
+Perhaps though this is again the argument of measuring selection in a "disturbed" community...
+-->
+
+<!--How does my study improve or differ from these? Perhaps the focus on 
 <!-- 
@@
 -->
+
+<!--
 Our finding that phenotypic evolution was more constrained in simpler food webs corresponds to the natural history of this system.
+Simpler food webs selected for gall midges with smaller clutch sizes and ovipositing on trees with low densities of conspecifics, which was likely due to the increased apparency of large clutches and trees with high densities to egg parasitoids searching for hosts.
+This is because herbivore oviposition can induce plant volatiles that attract egg parasitoids [reviewed in @Hilker2006], and the concentration of these volatiles may increase with the number of eggs that herbivores oviposit.
+In contrast, clutch size and oviposition preference did not experience directional selection in more complex food webs, which appeared to be a result of conflicting selection pressures.
+The absence of selection on clutch size
+
+Interestingly, we still observed selection for larger chamber diameters in the simple food web despite the fact that egg parasitoids attack before the gall is formed.
+This suggests that selection imposed by egg parasitoids on chamber diameter is likely due to selection with a correlated trait (e.g.
+ability to encapsulate parasitoid eggs).
+
 This particular gall-parasitoid community has only been studied one other time [@Barbour2016].
@@
 
-The fact that more traits contributed to the slope of the adaptive landscape (number of traits under directional selection) in the simple food web suggests that the trajectory of evolution is more constrained.
-For the phenotypic traits we examine, it also implies that there is an optimal combination of phenotypes that maximizes larval survival (i.e.
-large chamber diameter, small clutch sizes, and avoid conspecifics) in simpler food webs.
-In contrast, there are no selective constrains on the evolution of clutch size and oviposition preference in the more complex food web.
-This suggests that there are multiple adaptive peaks, or in this case, a flat adaptive landscape across these phenotypic traits, such that there are no consequences to move across the adaptive landscape in these directions.
-Interestingly, this also implies that as selective constraints weaken in more complex food webs, then the trajectory of evolution becomes more influenced by genetic constraints, or the population's G-matrix.
-This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the populations additive genetic variance and covariances between traits (G-matrix).
-As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
-Interestingly, this corresponds to data on trait evolution in complex natural systems.
-Specifically, @Schluter1996 suggested that evolution often follows 'genetic lines of least resistance'.
-This data came from data on natural populations of threespine sticklebacks, three species of songbirds, and *Peromyscus* mice.
-This also implies that simplification of ecological communities may actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.
-This insight also helps resolve the balance between neutral and adaptationist views of phenotypic evolution.
+ <!-- This insight also helps resolve the balance between neutral and adaptationist views of phenotypic evolution.
 In fact, the ability for neutral evolutionary theories to give insight to evolution may be due to the net neutral selection pressures in complex natural systems.
-However, this highlights that we will need further integration of these perspectives in the context of global change and concomittant changes in the selective environment.
-
-Moreover, current theoretical models of evolution in a community context often focus on the evolution of a single trait.
-Our results highlight though, that in the context of global change, we may begin to experience selection changing to cause change in multiple traits that influence fitness.
+However, this highlights that we will need further integration of these perspectives in the context of global change and concomittant changes in the selective environment.-->
 
@@
 
-In addition, we also found that the indirect effects of selection on genetic constraints were fewer in complex vs.
-simpler food webs.
-Key components that contribute to the evolvability of populations are determined by the additive genetic variance in traits as well as patterns of additive genetic covariance (i.e.
-G-matrix structure).
-Specifically, weak covariances allow trait evolution to be independent, which gives more autonomy in trait evolutionary responses to changing environments.
-Similar, decreases in genetic variance contstrain potential for the trait itself to evolve.
-Together, this suggest the simpler food webs can actually act to decrease the evolutionary potential of populations by indirectly selecting for decrases in genetic variance in multiple traits and favoring trait integration [@Hansen2008].
-At present, these indirect effects of selection imposed by the community context are often ignored in theoretical models, often assuming genetic variance is unchanging parameter in models.
-Our empirical results highlight the need to explore the evolutionary consequences of how not only the direct (current focus), but indirect effects of community context on phenotypic evolution.
-
 <!--
@@
 
+<!--response to local extinctions will
+
+Thus, our results hint that indirect evolutionary effects may be common, but latent, in complex communities, and thus local extinctions may trigger their apparent effects.
+
+Understanding these hidden selection pressures in complex communities is important; however, for predicting trajectories of evolutionary change, as they trajectory of evolution will depend on the order of local extinctions or changes in species abundances [Start et al.
+in press].
+-->
+
+<!--
 Right now, most studies treat the selection gradients imposed by the adaptive landscape as static [but see @McPeek2017].
@@
 Where these dynamics end up cancelling each other out in their net selective effects over time, or allow phenotypic evolution to change direction is currently unclear, and we need more empirical work on this front.
+-->
 
@@
 -->
-
+<!--
 The role of community context and diversity in shaping communities has been explored theoretically in terms of competitive communities [@De_Mazancourt2008; @Johansson2008].
@@
 Other studies have also explored the role of predators in helping prey adaptive to environmental change [@Osmond2017PredatorsHelpPrey].
-This work has suggested that biodiversity may constrain phenotypic evolution, because more species occupy different niches, presenting the "movement" of species across the adaptive landscape into different ecological niches.
+This work has suggested that biodiversity may constrain phenotypic evolution, because more species occupy different niches, preventing the "movement" of species across the adaptive landscape into different ecological niches.
 This may be true for competitive communities, but in multitrophic communities our empirical results suggest the opposite.
@@
 The role of different interaction types in shaping evolution in a community context remains both a theoretical and empirical frontier.
+-->
 
@@
 -->
-
+<!--
 One of the things that our study did was artificially reduce the mortality induced by parasitoids, in general, in the simpler food web.
@@
 
-## Conclusions
-
-Our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, increases evolutionary constraints.
-This occurs because selection imposed by simpler food webs constrains optimal evolutionary trajectories and the ability for populations to reach those adaptive peaks (e.g.
-via genetic constraints).
-This implies has unexplored, but an insidious effect of local extinctions.
-Not only may it compromise community robustness and resilience to future change, but it may also cause this at the population level.
-We are in urgent need of future empirical and theoretical work that understands these rippling effects on the robustness of populations and communities to environmental change.
+<!-- Review past experimental studies of complexity -->
+<!--There are a growing number of experimental studies examining how the community context shapes the adaptive landscape [@Stinchcombe2001; @Juenger1998; @Lankau2007; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018].
+This body of work focused on testing the extent to which selection imposed by different species is additive or non-additive in a community context [@terHorst2015], a critical step for accurately predicting changes in the trajectory of phenotypic evolution.
+<!--Put another way, this work gives insight to the direct and indirect effects of selection pressures in a community context.
+--><!--In contrast, we test how the community context shapes the range of possible evolutionary trajectories (i.e.
+constraints).
+We can re-examine the results of this prior work though to see the generality of our results.
+For example, recent greenhouse experiments with plant-pollinator interactions have shown a tendency for more traits to experience directional selection in simpler vs.
+more diverse pollinator communities [@Sahli2011; @terHorst2015; @Schiestl2018].
+Similarly, @Juenger1998 found that two insect herbviores <!--flies and caterpillars --><!--imposed the strongest reduction in plant fitness in isolation, but these effects were minimized when they were together <!--, highlight a nonadditive interactions that --><!--resulting in neutral selection on flowering time when both were present<!--(unclipped treatment)-->
+
+<!--Our results also suggest an insidious effect of local extinctions.
+Not only may it compromise community robustness and resilience to future change [@McCann2011], but it may also cause this at the population level.
+We are in urgent need of future empirical and theoretical work that understands these rippling effects on the robustness of populations and communities to environmental change.-->
 
@@
 
+We thank the staff of Humboldt Bay National Wildlife Refuge (U.S.
+Fish and Wildlife Service) for facilitating experimental logistics.
+For assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
+For funding support, we thank the University of British Columbia (James Robert Thompson Fellowship and Four-Year Fellowship to M.A.
+Barbour), NSERC (Discovery grant to Greg Crutsinger), and the Swiss National Science Foundation (grant 31003A_160671 to J.
+Bascompte).
+
 # References
 
+<!-- NEED TO PROPERLY FORMAT -->
+
 <div id="refs"></div> <!-- this code inserts references wherever you want rather than at the end of the document -->
@@
 # Tables
+
+<!-- CONSIDER ITALICIZING RELATIONSHIPS WHERE 90% CI DOES NOT OVERLAP ZERO -->
 
@@
 
+<!--TABLE NOT REFERENCED IN RESULTS-->
+
 \begin{table}[h]
@@
 \newpage 
-
+<!--
 # Figure Legends
@@
 Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.<!-- Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
--->Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
 
@@
 The decrease in the probability of observing egg parasitoids at high gall-midge densities indicates the increasing impact of larval parasitoids.
+-->
 
 ```{r Conceptual, echo=FALSE, fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
-In the complex food-web treatment (A), we allowed the full suite of egg (blue rectangle) and larval (yellow rectangle) parasitoids to impose selection.
-In the simple food-web treatment (B), we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
 Black arrows denote the flow of energy in this network of trophic interactions.
+In the complex food-web treatment, we allowed the full suite of egg and larval parasitoids to impose selection.
+In the simple food-web treatment, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
 Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
@@
 (Family: Torymidae)."}
-knitr::include_graphics("analyses/complex_simple_foodwebs.jpeg")
+knitr::include_graphics("analyses/complex_simple_foodwebs_v2.jpeg")
 ```
@@
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Selection favors trait integration for each combination of traits in simple food webs, whereas there is no strong evidence for trait integration in complex food webs.
-Note that mean larval survival is plotted on a natural log scale to accurately reflect the adaptive landscape."}
+Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype (i.e., all traits = 0) in each food-web treatment.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the simple vs.
+complex food-web treatment.
+This indicates that trait integration (covariance) is more strongly favored in simpler vs.
+more complex food webs.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
 knitr::include_graphics("analyses/MV_landscapes.pdf")
@@
 ```
-
-# Appendix

### 2019-01-09 manuscript.tex
update fig. 3 with arrows and contours

@@
 \emph{Keywords}: fitness landscape, host-parasitoid, natural selection,
-G-matrix, community context, ecological networks.
+G-matrix, community context, ecological networks, evolutionary ecology,
+eco-evolutionary dynamics.
 
@@
 \newpage
+
+\begin{quote}
+``What escapes the eye, however, is a much more insidious kind of
+extinction: the extinction of ecological interactions.''
+\citet{Janzen1974}
+\end{quote}
 
@@
 attack by generalist predators (e.g.~ants, spiders), but they suffer
-high mortaltiy from egg and larval parasitoids \citep{Barbour2016}. We
+high mortality from egg and larval parasitoids \citep{Barbour2016}. We
 manipulated food-web complexity by either excluding the guild of larval
@@
 measured oviposition preference as the density of larvae observed on a
-plant in an independent survey. We did this randomly sampling five
+plant in an independent survey. We did this by randomly sampling five
 branches per tree and counting the number of individual gall chambers
@@
 The indirect effects of selection on genetic constraints is governed by
-the curvature of the adaptive landscape, which in our study corresponds
-to:
+the curvature of the adaptive landscape
+(\(\text{C}=\gamma - \beta \beta^\text{T}\)), which in our study
+corresponds to:
 
@@
 We also plot mean larval survival on a natural log scale to accurately
-reflect the shape of the adaptive landscape \citep{Arnold2003}.
+reflect the mathematical definition of the adaptive landscape
+\citep{Arnold2003}.
 
@@
 
-\subsection{Food-web complexity reduces selective
-constraints}\label{food-web-complexity-reduces-selective-constraints}
+\subsection{Simpler food webs increase selective
+constraints}\label{simpler-food-webs-increase-selective-constraints}
 
 \indent We found that more gall midge traits experienced directional
-selection in the simple (3 of 3) vs.~complex food webs (1 of 3)(table
-\ref{Table:Gradients}). For example, we observed directional selection
-for smaller clutch sizes in the simple food web, but there was no
-evidence of selection acting on this trait in the complex food web
+selection in the simple (3 of 3) vs.~complex food-web treatment (1 of
+3)(table \ref{Table:Gradients}). For example, we observed directional
+selection for smaller clutch sizes in the simple food web, but there was
+no evidence of selection acting on this trait in the complex food web
 (table \ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This
@@
 pressures imposed by each guild of parasitoids (fig.
-\ref{fig:UV_Landscape}C). Specifically, when we subset our data to focus
+\ref{fig:UV_Landscape}). Specifically, when we subset our data to focus
 on differences between parasitoid guilds, we found that larval
@@
 
-\subsection{Food-web complexity reduces genetic
-constraints}\label{food-web-complexity-reduces-genetic-constraints}
+\subsection{Simpler food webs increase genetic
+constraints}\label{simpler-food-webs-increase-genetic-constraints}
 
@@
 at high densities in complex, but not simple food webs (fig.
-\ref{fig:UV_Landscape}). This dampened relationship was partly due to a
+\ref{fig:UV_Landscape}B). This dampened relationship was partly due to a
 trend for nonlinear selection imposed by larval parasitoids
@@
 
-\begin{enumerate}
-
- \item Summary of key results
-    \begin{enumerate}
-    \item Gall midges experience more selective and constraints in simple food webs.
-    \end{enumerate}
-
- \item Natural history and comparison to other studies of natural selection in galling insects.
-    \begin{enumerate}
-    \item \textbf{Important Studies for Comparison}: @Abrahamson1997; @Weis1983; @Heath2018; Start, Weis, and Gilbert In Press Am.
-Nat; @Start2016; @Start2018urbanization; Peter Price's work; Timothy Craig's work; Cheryl Briggs work.
-    \item \textbf{Topics to discuss}: Persistent pattern in selection for larger galls; Contrasting effects of egg and larval parasitoids on clutch size; Nonlinear selection at high gall densities is likely reflective of the poorer searching ability of larval vs.
-egg parasitoids (and thus it saturates more quickly).
-    \end{enumerate}
-
- \item Selective constraints:
-    \begin{enumerate}
-    \item \textbf{Key Result}: More traits under directional selection in simple (3 of 3) vs.
-complex (1 of 3) food webs.
-Need to be wary of interpreting no selection on oviposition preference in complex food webs though.
-Even if there is selection on oviposition preference, this does not change our qualitative result.
-    \item \textbf{Implications}: The trajectory of phenotypic evolution is less constrained in complex vs.
-simple food webs.
-In other words, there are more potential adaptive peaks in complex food webs.
-    \end{enumerate}
-
- \item Indirect effects of selection on genetic constraints: 
-    \begin{enumerate}
-    \item \textbf{Key Result}: More traits experience a decrease in additive genetic variance and more trait combinations experience selection for trait integration in simple food webs. 
-    \item \textbf{Implications}: The structure of the G-matrix is under less influence of selection in complex vs.
-simple food webs.
-Thus the trajectory of phenotypic evolution may be dictated more by genetic rather than selective constraints.
-This is in line with empirical evidence (from complex natural systems) that evolution tends to proceed along genetic lines of least resistance [@Schluter1996].
-    \end{enumerate}
-
- \item Indirect evolutionary effects:
-    \begin{enumerate}
-    \item \textbf{Key Result}: Evidence of selection on the extended phenotype of egg parasitoids.
-    \item \textbf{Implications}: Hints at a dynamic adaptive landscape and potential indirect evolutionary effects in complex food webs.
-    \end{enumerate}
-
- \item Caveats: 
-    \begin{enumerate} 
-    \item \textbf{Key Caveat}: Experimental artifact of lower larval survival in complex food-web treatment.
-    \item \textbf{Implications}: Artificially increased the magnitude of selection in complex food webs.
-Note however, that this does not qualitatively change any of our results.
-In fact, we are actually underestimating the constraints imposed by our simple food-web treatment.
-This is because the egg parasitoids would be released from their intraguild predator, and thus could increase in abundance over future generations and impose stronger selection on gall midges.
-    \end{enumerate}
-
-\item Conclusions
-
-\end{enumerate}
+Our key finding was that phenotypic evolution in gall midges was more
+constrained in simpler food webs. More traits contributed to the slope
+of the adaptive landscape in the simpler food web, suggesting that the
+trajectory of phenotypic evolution is more constrained. Similarly, the
+simple food-web treatment indirectly increased the number of genetic
+constraints, which could act to constrain the gall midge's adaptive
+potential in the face of novel selection pressures. We also found
+evidence of indirect selection pressures in more complex food webs,
+suggesting that the adaptive landscape may be more dynamic in complex
+food webs. Taken together, our study provides experimental evidence from
+the field that the simplification of ecological communities may
+constrain the adaptive potential of remaining populations.
+
+All three phenotypic traits we examined experienced directional
+selection in the simpler food web, indicating that there is an optimal
+phenotype that maximizes larval survival (i.e.~large chamber diameter,
+small clutch size, and avoidance of conspecifics). In contrast, we did
+not observe selective constraints on clutch size and oviposition
+preference in the more complex food web. This suggests that there are
+many optimal phenotypes (adaptive peaks), or in this case, a flat
+adaptive landscape where there are no fitness consequences for
+phenotypic change in these traits. This also implies that as selective
+constraints dampen in more complex food webs, then the trajectory of
+evolution becomes more determined by genetic constraints. This is made
+clear if we inspect the `Lande equation', \(\Delta z = \text{G} \beta\),
+where G corresponds to the population's G-matrix. As the components of
+\(\beta\) go to zero, then \(\Delta z\) is more influenced by the
+G-matrix. Interestingly, this corresponds to \citet{Schluter1996}`s
+hypothesis that phenotypic evolution often follows 'genetic lines of
+least resistance'. \citet{Schluter1996} found support for this
+hypothesis from data on natural populations of several vertebrate
+species, including threespine sticklebacks, a few species of songbirds,
+and mice from the genus \emph{Peromyscus}. All of these species occupy
+intermediate trophic levels and are likely embedded in complex food
+webs, which is consistent with our suggestion that genetic constraints
+may have a stronger influence in more complex food webs.
+
+We also found evidence for more genetic constraints in simpler food webs
+due to indirect effects of selection on the population's G-matrix. The
+ability of a population to adapt to novel selection pressures
+(evolvability) is largely governed by the structure of its G-matrix
+\citep{Hansen2008}. When selection favors genetic covariance between
+traits (positive or negative), this results in less autonomy of
+evolutionary responses to changing environments. Similarly, decreases in
+genetic variance constrain potential for the trait itself to evolve.
+Together, this suggests that simpler food webs may decrease the
+evolutionary potential of populations by indirectly selecting for
+decreases in genetic variance in multiple traits and favoring trait
+integration. Current theory often assumes genetic variances and
+covariances remain constant over time rather than dynamically changing
+with the community context \citep{McPeek2017, Guimaraes2017}. Our
+empirical results highlight the need to explore the evolutionary
+consequences of not only direct effects of selection, but indirect
+effects on genetic constraints that are shaped by the community context.
+
+The generality of our results likely depends on the relative abundance
+and functional differences between consumers in a community. In the
+simplest case, when consumers do not differ from each other, then we do
+not expect changes in food-web complexity to modify selective
+constraints. Also, many consumers may be at too low of abundances to
+impose selection on their resources. Rank abundance curves
+\citep{Preston1948} and the disproportionate number of weak interactions
+in diverse communities \citep{Paine1992} support this notion. When
+consumers are abundant though, the effect of food-web complexity will
+depend on whether different species impose conflicting selection
+pressures or select for distinct traits. For example, parisitoids and
+birds impose conflicting selection pressures on the size of galls
+induced by the fly \emph{Eurosta solidaginis}
+\citep{Weis1985, Abrahamson1997, Start2016}. Recent studies in this
+system have shown that decreases in the relative abundance of birds, due
+to either small patch sizes \citep{Start2016} or proximity to urban
+areas \citep{Start2018} causes a shift from neutral to directional
+selection on gall size. On the other hand, different consumers may
+impose selection on different traits, favoring trait integration and
+increasing genetic constraints. Examples of this include strong genetic
+covariances in plant resistance to different insect herbivores
+\citep{Maddox1990, Wise2007, Wise2013}, although there are also examples
+where these covariances are weak \citep{Roche1997, Barbour2015}, or vary
+from year-to-year \citep{Johnson2007}. We suggest that gaining
+predictive insight to the effects of food-web disassembly requires an
+understanding of the mechanisms governing the assembly of trophic
+interactions.
+
+Our results suggest that the simplification of ecological communities
+may not only directly affect connected species, but also result in
+indirect evolutionary effects. In our study, this indirect effect arises
+from egg parasitoids being released from intraguild predation in simpler
+food webs. This release occurs more on trees with high larval densities,
+which could intensify selection on gall midge oviposition preference. A
+growing number of experiments over the past two decades have
+demonstrated the presence and potential importance of indirect
+evolutionary effects that emerge in a community context
+\citep{Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018}.
+If indirect evolutionary effects are common \citep{Walsh2013}, then
+predicting evolutionary trajectories resulting from the simplification
+of food webs will require evolutionary studies to explicitly account for
+the ecological networks that species are embedded in.
+
+There are a growing number of theoretical studies on adaptation to
+directional environmental change that incorporate species interactions
+\citep[e.g.][]{deMazancourt2008, Johansson2008, Norberg2012, Osmond2017PredatorsHelpPrey}.
+This work has given insight to the mechanisms by which pairwise
+interactions modify the adaptive potential of species. Our study hints
+at a novel mechanism, whereby food-web complexity flattens the adaptive
+landscape, thus facilitating future adaptation by allowing genetic and
+phenotypic variation to persist. This mechanism only emerges once we
+move beyond pairwise interactions to consider selection on multiple
+traits in a community context. However, a study on competition has
+highlighted that we may expect the opposite effect of species diversity
+in competitive communities \citep{deMazancourt2008}. This negative
+effect of species diversity on adaptation occurs because there is a
+greater chance that the optimal phenotype is already occupied by a
+competitor in a more diverse community. More work is needed to examine
+how the distribution of different interaction types affects adaptation
+to environmental change in species-rich communities.
+
+Our study gives insight to how local extinctions, and concomitant
+decreases in food-web complexity, increase evolutionary constraints.
+This hints at a potential insidious effect of local extinctions that
+compromises the robustness of remaining populations to future
+environmental change. Our work also highlights some key challenges for
+predicting phenotypic evolution in the face of global change. First, the
+simplification of ecological communities may actually reduce the
+predictability of phenotypic evolution, because knowledge is required of
+both selective and genetic constraints, rather than potentially just
+genetic constraints in more complex systems. Second, many theoretical
+models of eco-evolutionary dynamics focus on phenotypic change in a
+single trait, yet our results highlight that the number of traits under
+selection may change with the community context. Importantly, while the
+net effects of selection in complex communities may be dampened, we
+still found that different species/guilds imposed different selection
+pressures. Knowing these hidden selection pressures is critical for
+prediction, because the trajectory of evolution will depend on the
+nature of change in the community context. We expect that a continued
+integration of adaptive landscapes and ecological networks will enhance
+our ability to predict the evolutionary consequences of changes in
+ecological communities.
 
 \section{Acknowledgements}\label{acknowledgements}
+
+We thank the staff of Humboldt Bay National Wildlife Refuge (U.S. Fish
+and Wildlife Service) for facilitating experimental logistics. For
+assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
+For funding support, we thank the University of British Columbia (James
+Robert Thompson Fellowship and Four-Year Fellowship to M.A.~Barbour),
+NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
+Science Foundation (grant 31003A\_160671 to J. Bascompte).
 
@@
 
-\section{Figure Legends}\label{figure-legends}
-
-\textbf{Figure \ref{fig:Conceptual}}: Experimental manipulation of
-food-web complexity associated with a leaf-galling midge (\emph{Iteomyia
-salicisverruca}) feeding on the willow \emph{Salix hookeriana}. In the
-complex food-web treatment (A), we allowed the full suite of egg (blue
-rectangle) and larval (yellow rectangle) parasitoids to impose
-selection. In the simple food-web treatment (B), we used mesh bags to
-exclude the guild of larval parasitoids, only allowing the egg
-parasitoid (\emph{Platygaster} sp.) to impose selection. Black arrows
-denote the flow of energy in this network of trophic interactions.
-Larval parasitoids include the following species (from left to right):
-\emph{Mesopolobus} sp. (Family: Pteromalidae); \emph{Tetrastichus} sp.
-(Family: Eulophidae); and \emph{Torymus} sp. (Family: Torymidae).
-
-\textbf{Figure \ref{fig:UV_Landscape}}: Adaptive landscape of gall midge
-phenotypes in complex vs.~simple food webs. Each panel corresponds to a
-different phenotypic trait: chamber diameter (A); oviposition preference
-(B); and clutch size (C). Solid lines represent selection experienced in
-complex (orange) and simple (blue) food webs. Transparent lines
-represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are
-based on 1,000 replicates.Note that mean larval survival is plotted on a
-natural log scale to reflect the mathematical defintion of the adaptive
-landscape.
-
-\textbf{Figure \ref{fig:MV_Landscape}}: Two dimensional view of adaptive
-landscapes of gall midge phenotypes in complex vs.~simple food webs.
-Each panel corresponds to a different combination of phenotypic traits:
-clutch size and chamber diameter (A); clutch size and oviposition
-preference (B); oviposition preference and chamber diameter (C). Note
-the flat landscape in mean larval survival for clutch size and
-oviposition preference in more complex food webs, whereas all three
-traits shape the adaptive landscape in simpler food webs. This indicates
-that selection favors trait integration for each combination of traits
-in simpler food webs, whereas there is no strong evidence for trait
-integration in more complex food webs. Note that mean larval survival is
-plotted on a natural log scale to reflect the mathematical defintion of
-the adaptive landscape.
-
-\textbf{Figure \ref{fig:EggPtoid_Selection}}: Selection imposed by
-larval parasitoids on the extended phenotype of egg parasitoids
-(\emph{Platygaster} sp.). The solid line represents the average
-difference in the probability of observing the egg parasitoid in complex
-vs.~simple food webs as a function of gall midge oviposition preference.
-Transparent lines represent bootstrapped replicates to show the
-uncertainty in selection. For clarity, we only display 100 bootstraps
-even though inferences are based on 1,000 replicates. The decrease in
-the probability of observing egg parasitoids at high gall-midge
-densities indicates the increasing impact of larval parasitoids.
-
 \begin{figure}
 \centering
-\includegraphics{analyses/complex_simple_foodwebs.jpeg}
+\includegraphics{analyses/complex_simple_foodwebs_v2.jpeg}
 \caption{\label{fig:Conceptual}Experimental manipulation of food-web
 complexity associated with a leaf-galling midge (\emph{Iteomyia
-salicisverruca}) feeding on the willow \emph{Salix hookeriana}. In the
-complex food-web treatment (A), we allowed the full suite of egg (blue
-rectangle) and larval (yellow rectangle) parasitoids to impose
-selection. In the simple food-web treatment (B), we used mesh bags to
-exclude the guild of larval parasitoids, only allowing the egg
-parasitoid (\emph{Platygaster} sp.) to impose selection. Black arrows
-denote the flow of energy in this network of trophic interactions.
-Larval parasitoids include the following species (from left to right):
-\emph{Mesopolobus} sp. (Family: Pteromalidae); \emph{Tetrastichus} sp.
-(Family: Eulophidae); and \emph{Torymus} sp. (Family: Torymidae).}
+salicisverruca}) feeding on the willow \emph{Salix hookeriana}. Black
+arrows denote the flow of energy in this network of trophic
+interactions. In the complex food-web treatment, we allowed the full
+suite of egg and larval parasitoids to impose selection. In the simple
+food-web treatment, we used mesh bags to exclude the guild of larval
+parasitoids, only allowing the egg parasitoid (\emph{Platygaster} sp.)
+to impose selection. Larval parasitoids include the following species
+(from left to right): \emph{Mesopolobus} sp. (Family: Pteromalidae);
+\emph{Tetrastichus} sp. (Family: Eulophidae); and \emph{Torymus} sp.
+(Family: Torymidae).}
 \end{figure}
@@
 clutch size and chamber diameter (A); clutch size and oviposition
-preference (B); oviposition preference and chamber diameter (C).
-Selection favors trait integration for each combination of traits in
-simple food webs, whereas there is no strong evidence for trait
-integration in complex food webs. Note that mean larval survival is
-plotted on a natural log scale to accurately reflect the adaptive
-landscape.}
+preference (B); oviposition preference and chamber diameter (C). Arrows
+represent mean estimates of directional selection gradients, while
+contours represent predicted larval survival of the mean phenotype
+(i.e., all traits = 0) in each food-web treatment. Notice that arrows
+point more toward a corner of the adaptive landscape for each
+combination of traits in the simple vs.~complex food-web treatment. This
+indicates that trait integration (covariance) is more strongly favored
+in simpler vs.~more complex food webs. Note that mean larval survival is
+plotted on a natural log scale to reflect the mathematical definition of
+the adaptive landscape.}
 \end{figure}
@@
 
-\renewcommand\refname{Appendix}
 \bibliography{references}

### 2019-01-09 manuscript.Rmd
incorporate minor editing suggestions from Jordi.

@@
 Global change is simplifying the structure of ecological networks; however, we are currently in a poor position to predict how these simplified communities will affect the evolutionary potential of remaining populations.
-Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treat the community context of evolving populations as a ``black box''.
+Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the community context of evolving populations as a ``black box''.
 <!--In contrast, ecological networks provide an explicit representation of the community context, yet often ignore the role of natural selection.-->Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
@@
 Thus, it remains unclear how network structure shapes adaptive landscapes of interacting populations.
-This represents a major barrier in our current ability to predict how changes in community context will affect phenotypic evolution.--> Here, we integrate ecological networks and adaptive landscapes to understand how community context constrains evolutionary change [@Arnold1992].
+This represents a major barrier in our current ability to predict how changes in community context will affect phenotypic evolution.--> Here, we integrate ecological networks and adaptive landscapes to understand how the community context constrains evolutionary change [@Arnold1992].
 Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape.
@@
 Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].
-If we want to predict how community context constrains evolutionary change, we must understand how ecological networks shape the adaptive landscape.
+If we want to predict how the community context constrains evolutionary change, we must understand how ecological networks shape the adaptive landscape.
 <!-- need to cite more than just Hansen and Houle 2008 here -->
@@
 Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
-To examine these different possibilities (among others), <!--To examine the effect of network structure on adaptive landscapes, -->we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
+To examine these different possibilities, <!--To examine the effect of network structure on adaptive landscapes, -->we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
 \ref{fig:Conceptual}).
@@
 <!--This curvature matrix describes the indirect effects of selection on genetic constraints within a generation ($\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}$).
-For example, -->The sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+For example, -->The sign of diagonal terms of the curvature matrix dictates whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
 Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
@@
 As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
-Interestingly, this corresponds to @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
+Interestingly, this aligns with @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
 @Schluter1996 found support for this hypothesis from data on natural populations of several vertebrate species, including threespine sticklebacks, a few species of songbirds, and mice from the genus *Peromyscus*.
@@
 <!-- Community context shaping adaptation to environmental change --> 
-There are a growing number of theoretical studies on adaptation to directional environmental change that incorporate species interactions [e.g.
+There is a growing number of theoretical studies on adaptation to directional environmental change that incorporate species interactions [e.g.
 @deMazancourt2008; @Johansson2008; @Norberg2012; @Osmond2017PredatorsHelpPrey].

### 2019-01-09 manuscript.Rmd
edit beginning of discussion to make clear that simpler food webs constrained phenotypic evolution at two levels (trajectory of change and genetic potential).

@@
 <!--Summary-->
-Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs.
+<!-- Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs.
 More traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting that the trajectory of phenotypic evolution is more constrained.
-Similarly, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
+-->
+We found that simpler food webs constrained phenotypic evolution in gall midges in two key ways.
+First, more traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting greater constraints on the trajectory of phenotypic evolution.
+Second, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
 We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs.

### 2019-01-09 analyses/reproduce_analyses.Rmd
add seed to bootstrap to ensure reproducibility

@@
   if(is.null(bootstraps) == FALSE){
+    set.seed(34) # make sure results are reproducible
     get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)

### 2019-01-09 manuscript.Rmd
change citation color to black

@@
 urlcolor: black
+citecolor: black
 ---

### 2019-01-10 manuscript.Rmd
figures and tables currently at end of text. Moving them to be in-line.

@@
 
-# References
-
-<!-- NEED TO PROPERLY FORMAT -->
-
-<div id="refs"></div> <!-- this code inserts references wherever you want rather than at the end of the document -->
+<!-- <div id="references"></div> this code inserts references wherever you want rather than at the end of the document -->
 
@@
 -->
+# Figures
 
@@
 
+\newpage
+
 ```{r UV_Landscape, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in complex vs.
@@
 Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Solid lines represent selection experienced in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
+Bold lines represent selection experienced in complex (orange) and simple (blue) food webs.
+Thin lines represent bootstrapped replicates to show the uncertainty in selection.
 For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
@@
 ```
+
+\newpage
 
@@
 
+\newpage
+
 ```{r EggPtoid_Selection, echo=FALSE, fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
-The solid line represents the average difference in the probability of observing the egg parasitoid in complex vs.
+The bold line represents the average difference in the probability of observing the egg parasitoid in complex vs.
 simple food webs as a function of gall midge oviposition preference.
-Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
+Thin lines represent bootstrapped replicates to show the uncertainty in selection.
 For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
@@
 ```
+
+\newpage

### 2019-01-10 manuscript.Rmd
removed Table 2 and embedded figures in main text.

@@
 
+```{r Conceptual, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
+Black arrows denote the flow of energy in this network of trophic interactions.
+In the complex food-web treatment, we allowed the full suite of egg and larval parasitoids to impose selection.
+In the simple food-web treatment, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
+(Family: Pteromalidae); *Tetrastichus* sp.
+(Family: Eulophidae); and *Torymus* sp.
+(Family: Torymidae)."}
+knitr::include_graphics("analyses/complex_simple_foodwebs_v2.jpeg")
+```
+
 <!--
@@
 
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\hline
+$\beta_{\text{Diam}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\beta_{\text{Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+
+$\beta_{\text{Pref}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref,Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
+Bold lines represent selection experienced in complex (orange) and simple (blue) food webs.
+Thin lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
+knitr::include_graphics("analyses/UV_landscapes.pdf")
+```
+
 ## Simpler food webs increase genetic constraints
@@
 \ref{fig:MV_Landscape}).
+
+```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
+Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype (i.e., all traits = 0) in each food-web treatment.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the simple vs.
+complex food-web treatment.
+This indicates that trait integration (covariance) is more strongly favored in simpler vs.
+more complex food webs.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
+knitr::include_graphics("analyses/MV_landscapes.pdf")
+```
 
@@
 
+```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
+The bold line represents the average difference in the probability of observing the egg parasitoid in complex vs.
+simple food webs as a function of gall midge oviposition preference.
+Thin lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on the extended phenotype of egg parasitoids."}
+knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
+```
+
 <!--
@@
 
-\newpage
-
-# Tables
-
 <!-- CONSIDER ITALICIZING RELATIONSHIPS WHERE 90% CI DOES NOT OVERLAP ZERO -->
 
-\begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
-\label{Table:Gradients}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
-\hline
-$\beta_{\text{Diam}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
-
-$\beta_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
-
-$\beta_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam,Diam}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch,Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Pref,Pref}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
-
-$\gamma_{\text{Diam,Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam,Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch,Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-\newpage
-
-<!--TABLE NOT REFERENCED IN RESULTS-->
+<!--TABLE NOT REFERENCED IN RESULTS
 
@@
 -->
-# Figures
-
-```{r Conceptual, echo=FALSE, fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
-Black arrows denote the flow of energy in this network of trophic interactions.
-In the complex food-web treatment, we allowed the full suite of egg and larval parasitoids to impose selection.
-In the simple food-web treatment, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
-Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
-(Family: Pteromalidae); *Tetrastichus* sp.
-(Family: Eulophidae); and *Torymus* sp.
-(Family: Torymidae)."}
-knitr::include_graphics("analyses/complex_simple_foodwebs_v2.jpeg")
-```
-
-\newpage
-
-```{r UV_Landscape, echo=FALSE, fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in complex vs.
-simple food webs.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in complex (orange) and simple (blue) food webs.
-Thin lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
-knitr::include_graphics("analyses/UV_landscapes.pdf")
-```
-
-\newpage
-
-```{r MV_Landscape, echo=FALSE, fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype (i.e., all traits = 0) in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the simple vs.
-complex food-web treatment.
-This indicates that trait integration (covariance) is more strongly favored in simpler vs.
-more complex food webs.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
-knitr::include_graphics("analyses/MV_landscapes.pdf")
-```
-
-\newpage
-
-```{r EggPtoid_Selection, echo=FALSE, fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid in complex vs.
-simple food webs as a function of gall midge oviposition preference.
-Thin lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on the extended phenotype of egg parasitoids."}
-knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
-```
-
-\newpage

### 2019-01-10 analyses/reproduce_analyses.Rmd
reduced fig and font size for Platygaster selection (Fig. 4)

@@
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  geom_hline(yintercept=0, linetype="dotted")
+  geom_hline(yintercept=0, linetype="dotted") +
+  theme_cowplot(font_size = 12)
 
 eggptoid_selection_plot
-save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 6)
+save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6
 ```
@@
 
+# Set contour breaks
+breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
+names(breaks) <- c("Complex","Simple")
+
 # Size x Clutch
 AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>% 
+  filter(Foodweb == "Complex") %>%
   ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
   geom_raster(aes(fill=average)) +
+  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
   facet_wrap(~Foodweb) +
@@
 AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
+  filter(Foodweb == "Complex") %>%
   ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
   geom_raster(aes(fill=average)) +
+  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
+  facet_wrap(~Foodweb) +
+  xlab("Chamber diameter (SDs)") +
+  ylab("Oviposition preference (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
+  theme(strip.background = element_blank(),
+        strip.text.x=element_text(margin=margin(b=4)))
+
+# Clutch x Preference
+AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
+  filter(Foodweb == "Complex") %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
+  geom_raster(aes(fill=average)) +
+  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
+  facet_wrap(~Foodweb) +
+  xlab("Oviposition preference (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
+  theme(strip.background = element_blank(),
+        strip.text.x=element_text(margin=margin(b=4)))
+
+```
+
+Reproduce Figure 5 in main manuscript.
+
+```{r Figure-Multivariate-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
+simple food webs.
+Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and Oviposition preference (B); Oviposition preference and gall diameter (C).
+Note that traits for all plots range 1 SD below and above the mean (=0)."}
+
+# Get legend
+AF_landscape_legend <- get_legend(AF_plot_Diam.Pref + theme(legend.text = element_text(size=10)))
+
+# Arrow data
+gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
+                                    sc.Diam = c(0,0), 
+                                    sc.log.Clutch = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
+
+gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
+                                    sc.sqrt.Pref = c(0,0), 
+                                    sc.log.Clutch = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
+
+gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
+                                    sc.Diam = c(0,0), 
+                                    sc.sqrt.Pref = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))
+
+# Format plots
+AF_landscape_plots <- plot_grid(
+  AF_plot_Diam.Clutch + theme(legend.position = "none", 
+                              axis.title.x = element_blank(),
+                             axis.text.x = element_blank()) +
+    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
+    geom_segment(data = gradients_Diam.Clutch, 
+                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
+                 arrow = arrow(length = unit(0.03, "npc"))),
+  AF_plot_Clutch.Pref + theme(legend.position = "none", 
+                              axis.title.y = element_blank(),
+                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
+    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
+    geom_segment(data = gradients_Clutch.Pref, 
+                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
+                 arrow = arrow(length = unit(0.03, "npc"))), 
+  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
+    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
+    geom_segment(data = gradients_Diam.Pref, 
+                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
+                 arrow = arrow(length = unit(0.03, "npc"))), 
+  nrow=2, align="hv", labels = "AUTO")
+
+AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
+AF_landscape_2d
+save_plot(filename = "MV_landscapes.pdf", plot = AF_landscape_2d, base_width=8, base_height = 6)
+```
+
+```{r }
+# Plot helpers
+AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
+  summarise(min = min(average), max = max(average))
+
+my_breaks <- c(0.2,0.4,0.6,0.8)
+
+# Set contour breaks
+breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
+names(breaks) <- c("Complex","Simple")
+
+# Size x Clutch
+AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
+  filter(Foodweb == "Complex") %>%
+  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
+  geom_raster(aes(fill=average)) +
+  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
+  facet_wrap(~Foodweb) +
+  xlab("Gall diameter (SDs)") +
+  ylab("Clutch size (SDs)") +
+  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
+  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
+  theme(strip.background = element_blank(),
+        strip.text.x=element_text(margin=margin(b=4)))
+
+# Size x Preference
+AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
+  #filter(Foodweb == "Complex") %>%
+  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
+  geom_raster(aes(fill=average)) +
+  #stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
+  #geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
+  #stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
   facet_wrap(~Foodweb) +
@@
 
-Reproduce Figure 5 in main manuscript.
-
-```{r Figure-Multivariate-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
+Remove 2nd contour line
+
+```{r Figure-Multivariate-Landscapes-2, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
 simple food webs.
@@
 
-# Set contour breaks
-breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
-
 # Format plots
@@
                              axis.text.x = element_blank()) +
-    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
+   # stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
     geom_segment(data = gradients_Diam.Clutch, 
@@
   AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
-    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
+    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
     geom_segment(data = gradients_Diam.Pref, 
@@
 AF_landscape_2d
-save_plot(filename = "MV_landscapes.pdf", plot = AF_landscape_2d, base_width=8, base_height = 6)
+save_plot(filename = "MV_landscapes_2.pdf", plot = AF_landscape_2d, base_width=8, base_height = 6)
 ```

### 2019-01-10 analyses/reproduce_analyses.Rmd
moved old evolution simulations on the adaptive landscape to a separate .Rmd file

@@
 ---
-title: "Supplementary Material"
+title: "Reproduce Analyses Reported in "Phenotypic evolution is more constrained in simpler food webs""
 author: "Matthew A. Barbour"
 date: "`r Sys.Date()`"
-output:
-  prettydoc::html_pretty:
-    theme: architect
-    highlight: github
-#output:
-#  pdf_document:
-#    df_print: paged
-#    fig_caption: true
-#    citation_package: natbib
-#    includes:  
-#      in_header: preamble-latex.tex
-#bibliography: references_ECD_supp_mat.bib
+output: github_document
+# Trying github_document for easy viewing on github
+#  prettydoc::html_pretty:
+#    theme: architect
+#    highlight: github
 fontsize: 12pt
@@
 ## Load required libraries ----
-library(evolqg) # need to load before dplyr
+#library(evolqg) # need to load before dplyr
 library(car)        # for homogeneity of variance test
@@
 library(latex2exp)  # using Latex notation for axes labels
-library(kableExtra)
+#library(kableExtra)
 library(stringr)
@@
 
-Reproduce Figure 5 in main manuscript.
+Reproduce Figure 3 in main manuscript.
 
@@
 
-```{r }
-# Plot helpers
-AF_range <- bind_rows(RF_Clutch.Pref$absolute_fitness, RF_Diam.Clutch$absolute_fitness, RF_Diam.Pref$absolute_fitness) %>%
-  summarise(min = min(average), max = max(average))
-
-my_breaks <- c(0.2,0.4,0.6,0.8)
-
-# Set contour breaks
-breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
-names(breaks) <- c("Complex","Simple")
-
-# Size x Clutch
-AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
-  filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
-  geom_raster(aes(fill=average)) +
-  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb) +
-  xlab("Gall diameter (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
-  theme(strip.background = element_blank(),
-        strip.text.x=element_text(margin=margin(b=4)))
-
-# Size x Preference
-AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
-  #filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
-  geom_raster(aes(fill=average)) +
-  #stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
-  #geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
-  #stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb) +
-  xlab("Chamber diameter (SDs)") +
-  ylab("Oviposition preference (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
-  theme(strip.background = element_blank(),
-        strip.text.x=element_text(margin=margin(b=4)))
-
-# Clutch x Preference
-AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
-  geom_raster(aes(fill=average)) +
-  facet_wrap(~Foodweb) +
-  xlab("Oviposition preference (SDs)") +
-  ylab("Clutch size (SDs)") +
-  scale_x_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_continuous(labels = c(-1,-0.5,0,0.5,1)) +
-  scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
-  theme(strip.background = element_blank(),
-        strip.text.x=element_text(margin=margin(b=4)))
-
-```
-
-Remove 2nd contour line
-
-```{r Figure-Multivariate-Landscapes-2, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and Oviposition preference (B); Oviposition preference and gall diameter (C).
-Note that traits for all plots range 1 SD below and above the mean (=0)."}
-
-# Get legend
-AF_landscape_legend <- get_legend(AF_plot_Diam.Pref + theme(legend.text = element_text(size=10)))
-
-# Arrow data
-gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.Diam = c(0,0), 
-                                    sc.log.Clutch = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
-
-gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.sqrt.Pref = c(0,0), 
-                                    sc.log.Clutch = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
-
-gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.Diam = c(0,0), 
-                                    sc.sqrt.Pref = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))
-
-# Format plots
-AF_landscape_plots <- plot_grid(
-  AF_plot_Diam.Clutch + theme(legend.position = "none", 
-                              axis.title.x = element_blank(),
-                             axis.text.x = element_blank()) +
-   # stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
-    geom_segment(data = gradients_Diam.Clutch, 
-                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
-                 arrow = arrow(length = unit(0.03, "npc"))),
-  AF_plot_Clutch.Pref + theme(legend.position = "none", 
-                              axis.title.y = element_blank(),
-                              axis.text.y = element_blank()) + xlab("Preference (SDs)") +
-    stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
-    geom_segment(data = gradients_Clutch.Pref, 
-                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
-                 arrow = arrow(length = unit(0.03, "npc"))), 
-  AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
-    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
-    geom_segment(data = gradients_Diam.Pref, 
-                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
-                 arrow = arrow(length = unit(0.03, "npc"))), 
-  nrow=2, align="hv", labels = "AUTO")
-
-AF_landscape_2d <- ggdraw(AF_landscape_plots) + draw_grob(AF_landscape_legend, x = 0.7, y=-0.2)
-AF_landscape_2d
-save_plot(filename = "MV_landscapes_2.pdf", plot = AF_landscape_2d, base_width=8, base_height = 6)
-```
-
-<!--
-# Effect of Food-Web Treatment on Larval Survival
-
-First we fit the full generalized linear mixed model to our data.
-This will enable us to evaluate whether there is any evidence that food-web treatment alters nonlinear selection on gall phenotypic variation.
-Note that we are not interested in directional selection yet, because we need to remove the nonlinear terms to evaluate its effects ([Lande and Arnold 1983](https://doi.org/10.1111/j.1558-5646.1983.tb00236.x)).
-
-```{r Model 1, cache=TRUE, eval=FALSE, include=FALSE}
-model_1 <- glmer(
-  gall_survival ~ Foodweb + sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-```
-
-We use parametric bootstrapping (n=`r n_boots_analysis`) to evaluate the statistical significance of the effect of food-web treatment on nonlinear terms (i.e.
-Foodweb:trait~i~^2^ or Foodweb:trait~i~:trait~j~).
-Food-web treatment does influence the quadratic effect of of Oviposition preference on larval survival.
-None of the other terms statistically differ from zero.
-
-```{r Bootstrap Model 1, cache=TRUE, include=FALSE, eval=FALSE}
-boot_model_1 <- bootMer(model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_1 <- tidy(model_1, conf.int=T) %>% #tidy(boot_model_1, conf.int=T) %>% 
-  # filter terms that only matter for this analysis
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
-                     "FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.sqrt.Pref^2)",
-                     "FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.sqrt.Pref","FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref")) 
-```
-
-```{r Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE, eval=FALSE, include=FALSE}
-plot_model_1 <- tidy_model_1 %>%
-  mutate(Food_web = ifelse(grepl("FoodwebSimple", .$term)==TRUE,"Simple","Complex")) %>%
-  filter(Food_web == "Simple")
-
-plot_model_1$term_plot <- factor(plot_model_1$term,
-                                levels=c("FoodwebSimple:I(sc.Diam^2)","FoodwebSimple:I(sc.log.Clutch^2)","FoodwebSimple:I(sc.sqrt.Pref^2)","FoodwebSimple:sc.Diam:sc.log.Clutch","FoodwebSimple:sc.Diam:sc.sqrt.Pref","FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref"),
-                                ordered=TRUE)
-
-plot_model_1 %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), shape=21, size=3, fill="grey") + # y=statistic for bootstrap
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(plot_model_1$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-Therefore, we are going to drop them from the model.
-Note that we are still fitting the full curvature of the fitness landscape, but that we aren't allowing some aspects of it to vary between food-web treatments (since there was no evidence for it)
-
-```{r Model 2, cache=TRUE, eval=FALSE, include=FALSE}
-
-# Remove non-signficiant effect of food-web treatment on quadratic and trait_i:trait_j interactions
-
-model_2 <- update(model_1, 
-                  .~. -Foodweb:I(sc.Diam^2) -Foodweb:I(sc.log.Clutch^2) -Foodweb:I(sc.sqrt.Pref^2)
-                  -Foodweb:sc.Diam:sc.log.Clutch -Foodweb:sc.Diam:sc.sqrt.Pref -Foodweb:sc.log.Clutch:sc.sqrt.Pref)
-```
-
-```{r Bootstrap Model 2, cache=TRUE, include=FALSE, eval=FALSE, include=FALSE}
-
-boot_model_2 <- bootMer(model_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_2 <- tidy(model_2, conf.int=T) %>% # tidy(boot_model_2, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
-                     "FoodwebSimple:I(sc.sqrt.Pref^2)")) 
-```
-
-This represents our nonlinear regression coefficients.
-
-```{r Plot Nonlinear Terms, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_model_2$term_plot <- factor(tidy_model_2$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                            ordered = TRUE)
-
-tidy_model_2 %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(tidy_model_2$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-Note that the non-overlapping 95% CI for *FoodwebSimple:I(sc.sqrt.Pref^2)* indicates that food-web treatment alters quadractic selection on Oviposition preference; however, this coefficient is not useful for actually calculating the selection gradient.
-To do this, we refit a model so rather than estimating the change in slope (currently), it will actually estimate the slope.
-See [Schielzeth 2010](https://doi.org/10.1111/j.2041-210X.2010.00012.x) for a detailed explanation of this approach.
-```{r Adjust Model 2 for Slopes, eval=FALSE, include=FALSE}
-model_2_adj <- update(model_2, .~. -I(sc.sqrt.Pref^2))
-```
-
-```{r Boot Adjusted Model 2 for accurate slope estimates, cache=TRUE, eval=FALSE, include=FALSE}
-boot_model_2_adj <- bootMer(model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_2_adj <- tidy(model_2_adj, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebSimple:I(sc.sqrt.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"))
-```
-
-Importantly we see now that although quadratic selection varies between treatments, it is not different from zero in the simple food web.
-
-```{r Plot Nonlinear Terms on appropriate scale, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_model_2_adj$term_plot <- factor(tidy_model_2_adj$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebSimple:I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                            ordered = TRUE)
-
-tidy_model_2_adj %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), fill="grey", shape=21, size=3) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(tidy_model_2_adj$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-Now we fit a reduced model to assess the effects of whether food-web treatments alters components of directional selection
-
-```{r Fit Model 3, cache=TRUE, eval=FALSE, include=FALSE}
-model_3 <- update(model_2, 
-                  .~. -I(sc.Diam^2) -I(sc.log.Clutch^2) -I(sc.sqrt.Pref^2) #-Foodweb:I(sc.sqrt.Pref^2) 
-                  -sc.Diam:sc.log.Clutch -sc.Diam:sc.sqrt.Pref -sc.log.Clutch:sc.sqrt.Pref)
-```
-
-We then use parametric bootstrapping to test whether food-web treatment alters the linear relationship between each trait and larval survival.
-
-```{r Bootstrap Model 3, cache=TRUE, include=FALSE, eval=FALSE}
-boot_model_3 <- bootMer(model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_3 <- tidy(model_3, conf.int=T) # boot_model_3
-```
-
-```{r Plot Model 3, echo=FALSE, eval=FALSE, include=FALSE}
-plot_model_3 <- tidy_model_3 %>%
-  mutate(Food_web = ifelse(grepl("FoodwebSimple:", .$term)==TRUE,"Simple","Complex")) %>%
-  filter(Food_web == "Simple")
-
-plot_model_3$term_ord <- factor(plot_model_3$term, 
-                                levels=c("FoodwebSimple:sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.sqrt.Pref"),
-                                ordered = TRUE)
-plot_model_3 %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(limits=rev(levels(plot_model_3$term_ord))) +
-  ylab("Coefficient (logit scale)")
-```
-
-There is clear evidence that food-web treatment alters the linear effect of clutch size on larval survival, but it has no effect on chamber diameter or Oviposition preference.
-Therefore, we fit a reduced model that removes these non-significant effects:
-
-```{r Fit Model 4, cache=TRUE, eval=FALSE, include=FALSE}
-model_4 <- update(model_3, .~. -Foodweb:sc.Diam -Foodweb:sc.sqrt.Pref)
-```
-
-This reduced model returns the same qualitative result as before.
-Specifically, that the linear effect of clutch size depends on food-web treatment.
-Note also that larval survival is significantly higher in the simple food web compared to the complex food web (dotted line).
-These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
-
-```{r Bootstrap Model 4, cache=TRUE, include=FALSE, eval=FALSE, include=FALSE}
-boot_model_4 <- bootMer(model_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_4 <- tidy(model_4, conf.int=T) # boot_model_4
-```
-
-```{r Plot Model 4, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_model_4$term_plot <- factor(tidy_model_4$term, 
-                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
-                                ordered = TRUE)
-
-plot_model_4 <- tidy_model_4 %>%
-  filter(term != "(Intercept)") %>%
-  droplevels()
-
-plot_model_4 %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(plot_model_4$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-As we did with model 2, we refit the model by removing the slope term so that we can fit different slopes for each interaction term. 
-```{r Fit Model 4 adjusted for estimating clutch slopes, cache=TRUE, eval=FALSE, include=FALSE}
-model_4_adj <- update(model_4, .~. -sc.log.Clutch)
-```
-
-```{r Bootstrap adjusted model 4, cache=TRUE, include=FALSE, eval=FALSE}
-boot_model_4_adj <- bootMer(model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_4_adj <- tidy(model_4_adj, conf.int=T) # boot_model_4_adj
-```
-
-```{r Plot adjusted model 4, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_model_4_adj$term_plot <- factor(tidy_model_4_adj$term, 
-                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
-                                ordered = TRUE)
-
-plot_model_4_adj <- tidy_model_4_adj %>%
-  filter(term != "(Intercept)") %>%
-  droplevels()
-
-plot_model_4_adj %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(plot_model_4_adj$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-```{r Average larval survival, cache=TRUE, eval=FALSE, include=FALSE}
-model_4_survival_ests <- update(model_4_adj, .~. -1)
-
-boot_model_4_survival_ests <- bootMer(model_4_survival_ests, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_model_4_survival_ests <- tidy(model_4_survival_ests, conf.int=T) # boot_model_4_survival_ests
-
-round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebComplex")$estimate),2) # statistic
-round(inverse_logit(filter(tidy_model_4_survival_ests, term=="FoodwebSimple")$estimate),2) # statistic
-```
-
-So, for plotting the results, we are going to use the focused nonlinear model.
-This provides the best representation of the fitness landscape (although we can't use it to assess to quantify the effects of directional selection.
-
-Note that while there is no evidence to let the slopes vary among treatments, there is a clear effect of food web treatment on fitness.
-This could influence estimates of selection by magnifying them in the complex vs.
-simple food web.
-
-So to calculate the selection gradients, we used Janzen and Stern's method to transform the regression coefficients.
-
-Basically, I need to just multiply all of the coefficients by the simple and complex fitness. Except, however, for I(sc.sqrt.Pref) and sc.log.Clutch. Here, we need the different coefficients.
-
-# Selection Gradients
-
-We used the method of [Janzen and Stern (1998)](https://doi.org/10.1111/j.1558-5646.1998.tb02237.x) to calculate selection gradients.
-Specifically, we first multiply each regression coefficient (and confidence interval) by the average of $W(z)[1-W(z)]$, where $W(z)$ corresponds to the predicted absolute fitness of an individual (in this case 1 if the larva survived, 0 if not) given its multivariate phenotype ($z$).
-We then divided this value by the mean absolute fitness ($\bar W$) so our results are in terms of relative fitness ($w$).
-Note that we doubled all quadratic selection gradients ($\gamma_{z_i,z_i}$) to put them on the same scale as the directional and correlational selection gradients (detailed explanation in [Stinchcombe et al.
-2008](https://doi.org/10.1111/j.1558-5646.2008.00449.x)).
-
-```{r Organize and Transform Coefficients, include=FALSE, eval=FALSE}
-tidy_coefs <- bind_rows(
-  select(tidy_model_2, term, estimate, conf.low, conf.high), # estimate=statistic; tidy_model_2_adj no longer needed, since quadratic and correlational selection didn't differ among treatments
-  select(tidy_model_4_adj, term, estimate, conf.low, conf.high)) %>% # estimate=statistic
-  filter(term != "(Intercept)", term != "FoodwebSimple") # remove main effects
-
-# Tidy common coefficients
-tidy_common_coefs <- tidy_coefs %>%
-  filter(#term!="FoodwebComplex:I(sc.sqrt.Pref^2)", term!="FoodwebSimple:I(sc.sqrt.Pref^2)",
-         term!="FoodwebComplex:sc.log.Clutch",term!="FoodwebSimple:sc.log.Clutch")
-
-# Tidy unique coefficients to each food-web
-#complex_quad_pref <- filter(tidy_coefs, term %in% "FoodwebComplex:I(sc.sqrt.Pref^2)")
-#complex_quad_pref$term <- "I(sc.sqrt.Pref^2)"
-#simple_quad_pref <- filter(tidy_coefs, term %in% "FoodwebSimple:I(sc.sqrt.Pref^2)")
-#simple_quad_pref$term <- "I(sc.sqrt.Pref^2)"
-
-complex_clutch <- filter(tidy_coefs, term %in% "FoodwebComplex:sc.log.Clutch")
-complex_clutch$term <- "sc.log.Clutch"
-simple_clutch <- filter(tidy_coefs, term %in% "FoodwebSimple:sc.log.Clutch")
-simple_clutch$term <- "sc.log.Clutch"
-```
-
-```{r Calculate Selection Gradients, include=FALSE, eval=FALSE}
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-complex_predict <- predict(model_2, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-complex_mean_brackets <- mean(complex_predict * (1 - complex_predict))
-complex_mean_fitness <- mean(complex_predict)
-
-simple_predict <- predict(model_2, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-simple_mean_brackets <- mean(simple_predict * (1 - simple_predict))
-simple_mean_fitness <- mean(simple_predict)
-
-# Double-check that using a different model (e.g.
-model_4) doesn't influence estimes of mean "brackets" and mean fitness.
-Below, I test this using the "Complex" food-web treatment as an example, but it doesn't matter
-alt_predict <- predict(model_4, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-alt_mean_brackets <- mean(alt_predict * (1 - alt_predict))
-alt_mean_fitness <- mean(alt_predict)
-test_mean_brackets <- complex_mean_brackets
-test_mean_fitness <- complex_mean_fitness
-test_mean_brackets - alt_mean_brackets # virtually the same
-test_mean_fitness - alt_mean_fitness # virtually the same
-
-tidy_simple_grads <- bind_rows(tidy_common_coefs, simple_clutch) %>% # simple_quad_pref, 
-  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
-2008)
-  transmute(term=term,
-            gradient = simple_mean_brackets * estimate / simple_mean_fitness * Multiplier,
-            `2.5%` = simple_mean_brackets * conf.low / simple_mean_fitness * Multiplier,
-            `97.5%` = simple_mean_brackets * conf.high / simple_mean_fitness * Multiplier)
-
-tidy_complex_grads <- bind_rows(tidy_common_coefs, complex_clutch) %>% # complex_quad_pref, 
-    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
-2008)
-  transmute(term=term,
-            gradient = complex_mean_brackets * estimate / complex_mean_fitness * Multiplier,
-            `2.5%` = complex_mean_brackets * conf.low / complex_mean_fitness * Multiplier,
-            `97.5%` = complex_mean_brackets * conf.high / complex_mean_fitness * Multiplier)
-
-selection_gradients <- bind_rows(
-  mutate(tidy_simple_grads, `Food web`="Simple"),
-  mutate(tidy_complex_grads, `Food web`="Complex")) #%>%
-  #mutate(Type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic", ifelse(grepl(":", .$term)==TRUE, "Correlational", "Directional")))
-```
-
-```{r Table of Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-selection_gradients$term_ord <- factor(selection_gradients$term, 
-                                   levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
-                                   ordered = TRUE)
-
-selection_gradients_table <- selection_gradients %>%
-  transmute(Term=term_ord, `Food web`, Gradient=round(gradient,2), `2.5%`=round(`2.5%`,2), `97.5%`=round(`97.5%`,2)) %>% 
-  arrange(Term)
-
-knitr::kable(selection_gradients_table, caption = "Table of Selection Gradients")
-```
-
-```{r Plot of Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-selection_gradients %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(selection_gradients$term_ord))) +
-  ylab("Selection Gradient") +
-  scale_fill_manual(values=treatment_colors) +
-  scale_color_manual(values=treatment_colors)
-```
-
-Contributions of larval parasitoids to selection gradients
-
-To identify the mechanisms by which food-web treatment altered selection gradients, we refit our models so that the complex food-web treatment only contained cases of parasitisms from larval parasitoids.
-Therefore, these analyses identify the unique contribution of each parasitoid guild to the selection gradients (egg parasitoid from simple food web; larval parasitoid from complex food web).
-Note that cases of larval parasitism may have been initially parasitized by an egg parasitoid.
-
-We restrict our model analyses to those where we observed different effects of food-web treatment on larval survival from the prior analyses (i.e. model 2 and model 4).
-
-```{r Egg vs. Larval Parasitoids Model, cache=TRUE, eval=FALSE, include=FALSE}
-
-# excludes cases of egg-parasitism from Complex food web
-egg.vs.larval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1) %>% 
-  mutate(Foodweb = ifelse(Foodweb == "Simple", "Egg", "Larval"))
-
-egg.larval_model_2 <- update(model_2, data=egg.vs.larval_df)
-```
-
-```{r Bootstrap Egg vs. Larval Parasitoid Model 2, cache=TRUE, include=FALSE, eval=FALSE}
-
-boot_egg.larval_model_2 <- bootMer(egg.larval_model_2, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_egg.larval_model_2 <- tidy(egg.larval_model_2, conf.int=T) %>% # boot_egg.larval_model_2
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"))#,
-                     #"FoodwebLarval:I(sc.sqrt.Pref^2)")) 
-```
-
-This represents our nonlinear regression coefficients.
-
-```{r Plot effect of Egg vs. Larval Parasitoid Model 2, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_egg.larval_model_2$term_plot <- factor(tidy_egg.larval_model_2$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                            ordered = TRUE)
-
-tidy_egg.larval_model_2 %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-   geom_point(aes(y=estimate), size=3, shape=21, fill="grey") +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(tidy_egg.larval_model_2$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
- To put all of the coefficients on the same scale, we refit it as we did in the food-web treatment
-```{r Egg vs. Larval Parasitoids adjusted model 2, cache=TRUE, eval=FALSE, include=FALSE}
-egg.larval_model_2_adj <- update(model_2_adj, data=egg.vs.larval_df)
-```
-
-```{r Bootstrap Egg vs. Larval Parasitoid adjusted Model 2, cache=TRUE, include=FALSE, eval=FALSE}
-
-boot_egg.larval_model_2_adj <- bootMer(egg.larval_model_2_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_egg.larval_model_2_adj <- tidy(egg.larval_model_2_adj, conf.int=T) %>% 
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.sqrt.Pref^2)","FoodwebLarval:I(sc.sqrt.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) 
-```
-
-This represents our nonlinear regression coefficients.
-
-```{r Plot effect of Egg vs. Larval Parasitoid adjusted Model 2, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_egg.larval_model_2_adj$term_plot <- factor(tidy_egg.larval_model_2_adj$term,
-                            levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","FoodwebEgg:I(sc.sqrt.Pref^2)","FoodwebLarval:I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                            ordered = TRUE)
-
-tidy_egg.larval_model_2_adj %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-   geom_point(aes(y=estimate), size=3, shape=21, fill="grey") +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(tidy_egg.larval_model_2_adj$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-Now we assess their contribution to the effect of food-web treatment on the linear terms.
-
-```{r Fit Egg vs. Larval Parasitoid Model 4, cache=TRUE, eval=FALSE, include=FALSE}
-egg.larval_model_4 <- update(model_4, data=egg.vs.larval_df)
-```
-
-This reduced model returns the same qualitative result as before.
-Specifically, that the linear effect of clutch size depends on food-web treatment.
-Note also that larval survival is significantly higher in the simple food web compared to the complex food web (dotted line).
-These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
-
-```{r Bootstrap Egg vs. Larval Parasitoid Model 4, cache=TRUE, include=FALSE, eval=FALSE}
-boot_egg.larval_model_4 <- bootMer(egg.larval_model_4, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_egg.larval_model_4 <- tidy(egg.larval_model_4, conf.int=T) # boot_egg.larval_model_4
-```
-
-Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. Larval Parasitoid Model 4, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_egg.larval_model_4$term_ord <- factor(tidy_egg.larval_model_4$term, 
-                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.sqrt.Pref"),
-                                ordered = TRUE)
-
-plot_egg.larval_model_4 <- tidy_egg.larval_model_4 %>%
-  filter(term != "(Intercept)") %>%
-  droplevels()
-
-plot_egg.larval_model_4 %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(plot_egg.larval_model_4$term_ord))) +
-  ylab("Coefficient (logit scale)")
-```
-
-```{r Fit Egg vs. Larval Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE, include=FALSE}
-egg.larval_model_4_adj <- update(model_4_adj, data=egg.vs.larval_df)
-```
-
-This reduced model returns the same qualitative result as before.
-Specifically, that the linear effect of clutch size depends on food-web treatment.
-Note also that larval survival is significantly higher in the simple food web compared to the complex food web (dotted line).
-These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
-
-```{r Bootstrap Egg vs. Larval Parasitoid adjuted Model 4, cache=TRUE, include=FALSE, eval=FALSE}
-boot_egg.larval_model_4_adj <- bootMer(egg.larval_model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_egg.larval_model_4_adj <- tidy(egg.larval_model_4_adj, conf.int=T) # boot_egg.larval_model_4_adj
-```
-
-Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. Larval Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_egg.larval_model_4_adj$term_ord <- factor(tidy_egg.larval_model_4_adj$term, 
-                                levels = c("(Intercept)","FoodwebLarval","sc.Diam","FoodwebEgg:sc.log.Clutch","FoodwebLarval:sc.log.Clutch","sc.sqrt.Pref"),
-                                ordered = TRUE)
-
-plot_egg.larval_model_4_adj <- tidy_egg.larval_model_4_adj %>%
-  filter(term != "(Intercept)") %>%
-  droplevels()
-
-plot_egg.larval_model_4_adj %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), size=3, shape=21, fill="grey") + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(plot_egg.larval_model_4_adj$term_ord))) +
-  ylab("Coefficient (logit scale)")
-```
-
-# CALCULATE SELECTION GRADIENTS FOR EGG VS. LARVAL PARASITOIDS
-
-```{r Organize and Transform egg vs. larval parasitoid Coefficients, include=FALSE, eval=FALSE}
-tidy_egg.larval_coefs <- bind_rows(
-  select(tidy_egg.larval_model_2, term, estimate, conf.low, conf.high),  # estimate=statistic; tidy_egg.larval_model_2_adj no longer needed because no nonlinear difference on preference.
-  select(tidy_egg.larval_model_4_adj, term, estimate, conf.low, conf.high)) %>% # estimate=statistic
-  filter(term != "(Intercept)", term != "FoodwebLarval") # remove main effects
-
-# Tidy common coefficients
-tidy_egg.larval_common_coefs <- tidy_egg.larval_coefs %>%
-  filter(#term!="FoodwebEgg:I(sc.sqrt.Pref^2)", term!="FoodwebLarval:I(sc.sqrt.Pref^2)",
-         term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")
-
-# Tidy unique coefficients to each food-web
-#egg_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebEgg:I(sc.sqrt.Pref^2)")
-#egg_quad_pref$term <- "I(sc.sqrt.Pref^2)"
-#larval_quad_pref <- filter(tidy_egg.larval_coefs, term %in% "FoodwebLarval:I(sc.sqrt.Pref^2)")
-#larval_quad_pref$term <- "I(sc.sqrt.Pref^2)"
-
-egg_clutch <- filter(tidy_egg.larval_coefs, term %in% "FoodwebEgg:sc.log.Clutch")
-egg_clutch$term <- "sc.log.Clutch"
-larval_clutch <- filter(tidy_egg.larval_coefs, term %in% "FoodwebLarval:sc.log.Clutch")
-larval_clutch$term <- "sc.log.Clutch"
-```
-
-```{r Calculate Egg vs. larval parasitoid Selection Gradients, include=FALSE, eval=FALSE}
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-larval_predict <- predict(egg.larval_model_2, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
-larval_mean_brackets <- mean(larval_predict * (1 - larval_predict))
-larval_mean_fitness <- mean(larval_predict)
-
-egg_predict <- predict(egg.larval_model_2, newdata=filter(egg.vs.larval_df, Foodweb=="Egg"), type="response")
-egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
-egg_mean_fitness <- mean(egg_predict)
-
-# Double-check that using a different model (e.g.
-egg.larval_model_4) doesn't influence estimes of mean "brackets" and mean fitness.
-Using "Complex" food-web treatment as an example, but it doesn't matter
-alt_egg.larval_predict <- predict(egg.larval_model_4, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
-alt_egg.larval_mean_brackets <- mean(alt_egg.larval_predict * (1 - alt_egg.larval_predict))
-alt_egg.larval_mean_fitness <- mean(alt_egg.larval_predict)
-test_egg.larval_mean_brackets <- larval_mean_brackets
-test_egg.larval_mean_fitness <- larval_mean_fitness
-test_egg.larval_mean_brackets - alt_egg.larval_mean_brackets # virtually the same
-test_egg.larval_mean_fitness - alt_egg.larval_mean_fitness # virtually the same
-
-tidy_egg_grads <- bind_rows(tidy_egg.larval_common_coefs, egg_clutch) %>% # egg_quad_pref, 
-  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
-2008)
-  transmute(term=term,
-            gradient = egg_mean_brackets * estimate / egg_mean_fitness * Multiplier,
-            `2.5%` = egg_mean_brackets * conf.low / egg_mean_fitness * Multiplier,
-            `97.5%` = egg_mean_brackets * conf.high / egg_mean_fitness * Multiplier)
-
-tidy_larval_grads <- bind_rows(tidy_egg.larval_common_coefs, larval_clutch) %>% # larval_quad_pref, 
-    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
-2008)
-  transmute(term=term,
-            gradient = larval_mean_brackets * estimate / larval_mean_fitness * Multiplier,
-            `2.5%` = larval_mean_brackets * conf.low / larval_mean_fitness * Multiplier,
-            `97.5%` = larval_mean_brackets * conf.high / larval_mean_fitness * Multiplier)
-
-egg.larval_selection_gradients <- bind_rows(
-  mutate(tidy_egg_grads, `Food web`="Egg"),
-  mutate(tidy_larval_grads, `Food web`="Larval")) #%>%
-  #mutate(Type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic", ifelse(grepl(":", .$term)==TRUE, "Correlational", "Directional")))
-```
-
-```{r Table of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
-                                   levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
-                                   ordered = TRUE)
-
-egg.larval_selection_gradients_table <- egg.larval_selection_gradients %>%
-  transmute(Term=term_ord, Parasitoid=`Food web`, Gradient=round(gradient,2), `2.5%`=round(`2.5%`,2), `97.5%`=round(`97.5%`,2)) %>% 
-  arrange(Term)
-
-knitr::kable(egg.larval_selection_gradients_table, caption = "Table of Egg vs. Larval Parasitoid Selection Gradients")
-```
-
-```{r Plot of Egg vs. Larval Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-egg.larval_selection_gradients %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(egg.larval_selection_gradients$term_ord))) +
-  ylab("Selection Gradient") +
-  scale_fill_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) +
-  scale_color_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) 
-```
-
-# Quantifying biased selection on chamber diameter
-
-We quantified biased selection on chamber diameter in the following way.
-First, we focus on multi-chambered galls where there is evidence of both survival and parasitism.
-The idea is that galls from the same clutch should be similar in size; therefore, any selection on diameter would be apparent.
-If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection differential to be the result of confounding factors.
-Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism.
-
-We calculated the bias in selection differential on chamber diameter by calculating the difference in mean chamber diameter before (i.e.
-all larva within the same gall) and after selection (only surviving larva).
-We then used a one-sample t-test to determine whether the selection differential was significantly different from zero.
-We conducted separate t-tests for each food-web treatment.
-
-We can then subtract this "biased selection differential" from the observed directional selection gradient on chamber diameter to adjust for the confounding effects of parasitism.
-
-```{r New approach for biased selection, include=FALSE, eval=FALSE}
-biased_df <- gall_selection.df %>%
-  group_by(Foodweb, Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1)
-
-summary(update(model_1, data=biased_df)) # no clear effects here...
-summary(update(model_2, data=biased_df)) # seeing the bias here, but its still not what we actually assess the differences on
-summary(update(model_3, data=biased_df)) # we're going to focus on diameter since that's our focus now. It doesn't appear that the slope differes between food-web treatments
-biased.diam_model_4 <- update(model_4, data=biased_df)
-summary(biased.diam_model_4) # looks like the bias in our sc.Diam coefficient is 0.34
-
-bias.adj_complex_predict <- predict(biased.diam_model_4, newdata=filter(biased_df, Foodweb=="Complex"), type="response")
-bias.adj_complex_mean_brackets <- mean(bias.adj_complex_predict * (1 - bias.adj_complex_predict))
-bias.adj_complex_mean_fitness <- mean(bias.adj_complex_predict)
-
-bias.adj_simple_predict <- predict(biased.diam_model_4, newdata=filter(biased_df, Foodweb=="Simple"), type="response")
-bias.adj_simple_mean_brackets <- mean(bias.adj_simple_predict * (1 - bias.adj_simple_predict))
-bias.adj_simple_mean_fitness <- mean(bias.adj_simple_predict)
-
-# convert to selection gradient
-bias.adj_sc.Diam_complex <- bias.adj_complex_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_complex_mean_fitness * 1 # 0.16
-bias.adj_sc.Diam_simple <- bias.adj_simple_mean_brackets * fixef(biased.diam_model_4)["sc.Diam"] / bias.adj_simple_mean_fitness * 1 # 0.18
-
-# This analysis suggests that there is a little bias, but not too much. 
-```
-
-```{r Redo selection gradients, include=FALSE, eval=FALSE}
-bias.adj_selection_gradients <- mutate(selection_gradients, adjusted = "No") %>%
-  # add bias adjusted directional selection gradient for Diameter in complex food-web
-  add_row(term="sc.Diam", 
-          gradient = complex_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$estimate - fixef(biased.diam_model_4)["sc.Diam"]) / complex_mean_fitness, 
-          `2.5%` = complex_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.low - fixef(biased.diam_model_4)["sc.Diam"]) / complex_mean_fitness, 
-          `97.5%` = complex_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.high - fixef(biased.diam_model_4)["sc.Diam"]) / complex_mean_fitness, 
-          `Food web` = "Complex", 
-          term_ord = "Diam", 
-          adjusted="Yes") %>%
-  # add bias adjusted directional selection gradient for Diameter in simple food-web
-  add_row(term="sc.Diam", 
-          gradient = simple_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$estimate - fixef(biased.diam_model_4)["sc.Diam"]) / simple_mean_fitness, 
-          `2.5%` = simple_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.low - fixef(biased.diam_model_4)["sc.Diam"]) / simple_mean_fitness, 
-          `97.5%` = simple_mean_brackets * (filter(tidy_common_coefs, term=="sc.Diam")$conf.high - fixef(biased.diam_model_4)["sc.Diam"]) / simple_mean_fitness, 
-          `Food web` = "Simple", 
-          term_ord = "Diam", 
-          adjusted="Yes")
-```
-
-```{r Bias in gradients on chamber diameter, eval=FALSE, include=FALSE}
-fixef(biased.diam_model_4)["sc.Diam"]
-```
-
-```{r Variance explained in chamber diameter, eval=FALSE, include=FALSE}
-chamber_diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), data=gall_selection.df)
-summary(chamber_diam)
-car::Anova(chamber_diam, test="F")
-
-# variance explained by gall ID
-0.5374/(0.5374+0.0956+0.1671+0.2031)
-```
-
-```{r Variance explained in other traits, eval=FALSE, include=FALSE}
-clutch_size <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, Gall_Number, sc.log.Clutch))
-summary(clutch_size)
-car::Anova(clutch_size, test="F")
-
-female_pref <- lmer(sc.sqrt.Pref ~ Foodweb + (1|Genotype), data=distinct(gall_selection.df, Foodweb, Genotype, Plant_Position, sc.sqrt.Pref))
-summary(female_pref)
-car::Anova(female_pref, test="F")
-```
-
-```{r female pref plot, echo=F, eval=FALSE, include=FALSE}
-visreg::visreg(female_pref, xvar="Foodweb")
-```
-
-```{r Plot of bias adjusted Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-bias.adj_selection_gradients %>%
-  ggplot(., aes(x=term_ord, shape=adjusted)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=1)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=1)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(bias.adj_selection_gradients$term_ord))) +
-  ylab("Selection Gradient") +
-  scale_fill_manual(values=treatment_colors) +
-  scale_color_manual(values=treatment_colors) +
-  scale_shape_manual(name="Bias\nadjusted", values=c(21,23))
-```
-
-## Figure for manuscript
-
-Only use selection gradients for larval parasitoids, use both complex and simple food webs, and only bias adjusted for chamber diameter.
-
-```{r Prep selection gradients figure, echo=FALSE, eval=FALSE, include=FALSE}
-
-focus_gradients <- bind_rows(filter(bias.adj_selection_gradients, term_ord == "Diam" & adjusted == "Yes" | term_ord != "Diam"),
-                             filter(egg.larval_selection_gradients, `Food web` == "Larval" & term_ord %in% c("Clutch"))) %>%   # ,"Pref^2"
-  mutate(Type = ifelse(grepl("\\^2", .$term_ord)==TRUE, "Quadratic", ifelse(grepl(":", .$term_ord)==TRUE, "Correlational", "Directional")))
-
-focus_gradients$Type_ord <- factor(focus_gradients$Type, 
-                                   levels=c("Directional","Quadratic","Correlational"),
-                                   ordered = TRUE)
-
-focus_gradients$axis_x_labels <- as.character(focus_gradients$term_ord)
-
-max_gradient <- max(focus_gradients$`97.5%`)
-min_gradient <- min(focus_gradients$`2.5%`)
-gradient_limits <- c(-0.3, 0.75)
-
-legend_labels <- c("Egg + Larval (Complex)","Larval parasitoids","Egg parasitoid (Simple)")
-
-directional <- filter(focus_gradients, Type=="Directional") %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
-  #coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  ylab("Selection Gradient") +
-  scale_fill_manual(values=cbPalette[c(6,4,5)], labels=legend_labels) +
-  scale_color_manual(values=cbPalette[c(6,4,5)], labels=legend_labels) +
-  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
-  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
-  scale_y_continuous(limits = gradient_limits) +
-  theme(legend.title.align = 0.5)
-
-quadratic <- filter(focus_gradients, Type=="Quadratic") %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
-  #coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  ylab("Selection Gradient") +
-  scale_fill_manual(values=cbPalette[c(6,5)]) + # c(6,4,5) no longer effect on preference
-  scale_color_manual(values=cbPalette[c(6,5)]) + # c(6,4,5) no longer effect on preference
-  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
-  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
-  scale_y_continuous(limits = gradient_limits)
-
-correlational <- filter(focus_gradients, Type=="Correlational") %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.5)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", size=3, position=position_dodge(width=0.5), shape=21) +
-  #coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  ylab("Selection Gradient") +
-  scale_fill_manual(values=cbPalette[c(6,5)]) + # changed from 6,4,5 since larval parasitoids didn't differ for any correlational gradients
-  scale_color_manual(values=cbPalette[c(6,5)]) + # same as above
-  facet_wrap(~Type_ord, ncol=2, scales="free_x") +
-  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
-  scale_y_continuous(limits = gradient_limits)
-```
-
-Standardized selection gradients estimate selection on a trait in terms of the effects on relative fitness in units of (phenotypic) standard deviations of the trait, allowing direct comparisons among traits, fitness components, and study systems (Kingsolver et al.
-2001, Am.
-Nat.).
-
-```{r Selection-Gradients, echo=FALSE, fig.cap="Selection gradients. Points and lines represents means and 95% confidence intervals (n=1,000 bootstrapped samples).", eval=FALSE, include=FALSE}
-
-# Get legend
-gradients_legend <- get_legend(directional)
-
-# Format plots
-gradients_plots <- plot_grid(
-  directional + theme(legend.position = "none", axis.title = element_blank()),
-  quadratic + theme(legend.position = "none", axis.title = element_blank()),
-  correlational + theme(legend.position = "none", axis.title = element_blank()), 
-  nrow=2, align="hv", labels = "")
-gradients_plots_legend <- ggdraw(gradients_plots) + draw_grob(gradients_legend, x = 0.6, y=-0.2) # x = 0.7, y=-0.2
-gradients_y_title <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
-
-gradients_figure <- plot_grid(gradients_y_title, gradients_plots_legend, ncol=2, rel_widths = c(0.05,1))
-gradients_figure
-```
-
-## Selection on the egg parasitoid *Platygaster*
-
-We cannot calculate selection on the egg parasitoids *Platygaster* with the same method as we did for the herbivore *Iteomyia*.
-This is because the unique biology of host-parasitoid interactions enables us to determine whether the host (herbivore) has survived or not.
-With the egg parasitoid, we only have a record of the gall it was found in.
-But, we can take advantage of our treatment which excludes the guild of larval parasitoids.
-Specifically, we can compare the mean gall phenotype that egg parasitoids are reared from in the absence of larval parasitoids ("before" selection) to the mean gall phenotype in the presence of larval parasitoids ("after" selection).
-Therefore, we can use this cross-sectional data to quantify directional and quadratic selection differentials acting on the gall phenotypes.
-In essence, the gall phenotype becomes the extended phenotype of the egg parasitoid, since its attributes can influence the egg parasitoid's survival to its intraguild predator (larval parasitoid).
-
-To quantify the selection differential acting on the egg parasitoid, we used separate linear mixed models with the gall phenotype as the response variable, food-web treatment as the fixed effect, and then the same suite of random effects as for our primary analyses of *Iteomyia* survival (i.e.
-gall ID, nested within plant ID, nested within plant genotype).
-
-We found no evidence of directional or quadratic selection on either chamber diameter or clutch size; however, we observed positive directional selection on *Iteomyia* Oviposition preference as well stabilizing selection on preference.
-
-Appears to be selection for Platygaster to attack larva at high densities in more complex food webs (and a decrease in the variance).
-This may be a result of the poorer searching ability of parasitoids at very high gall densities, potentially due to saturation.
-This suggests that the fitness landscape may be dynamic because these selective effects (assuming there is heritable variation in the egg parasitoid) will change the following year.
-This could be an important discussion point to take into account for future work.
-This is different from simply altering the strength of selection, which will occur as species move along the fitness landscape, but this result suggests that the nature of the fitness landscape may actually be changing.
-For example, larval parasitoids could be driving selection on Platygaster to be very efficient at foraging, which will dampen once this pressure is removed, and then could also dampen the selection acting on the galling herbivore.
-```{r Selection on Platygaster Traits, cache=TRUE, eval=FALSE, include=FALSE}
-
-## Subset the data to analyse change in gall phenotypes associated with Platygaster
-platy_selection_df <- gall_selection.df %>%
-  filter(egg_parasitoid > 0) 
-platy_selection_df$Foodweb <- relevel(factor(platy_selection_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids
-
-## Linear mixed models of linear selection differentials (change in mean phenotype)
-platy_Diam <- lmer(sc.Diam ~ Foodweb + (1|Genotype/Plant_Position/Gall_Number), platy_selection_df)
-
-platy_Clutch <- lmer(sc.log.Clutch ~ Foodweb + (1|Genotype/Plant_Position), platy_selection_df)
-
-platy_Pref <- lmer(sc.sqrt.Pref ~ Foodweb + (1|Genotype), platy_selection_df)
-
-## Levene's test for quadratic selection differentials (change in phenotypic variance)
-# Note that this result should be interepreted cautiously since we cannot account for non-independence due to plant genotype, plant ID, or gall ID
-platy_Diam_levene <- leveneTest(sc.Diam ~ Foodweb, platy_selection_df)
-platy_Clutch_levene <- leveneTest(sc.log.Clutch ~ Foodweb, platy_selection_df)
-platy_Pref_levene <- leveneTest(sc.sqrt.Pref ~ Foodweb, platy_selection_df)
-```
-
-```{r Levene tests, eval=FALSE, include=FALSE}
-platy_Diam_levene
-platy_Clutch_levene
-platy_Pref_levene
-```
-
-```{r Plot models of Platygaster selection differentials, echo=FALSE, eval=FALSE, include=FALSE}
-visreg_platy_Diam <- visreg(platy_Diam, xvar="Foodweb", gg=TRUE) + ylab("Chamber diameter (SD)") + xlab("")
-visreg_platy_Clutch <- visreg(platy_Clutch, xvar="Foodweb", gg=TRUE) + ylab("Clutch size (SD)") + xlab("")
-visreg_platy_Pref <- visreg(platy_Pref, xvar="Foodweb", gg=TRUE) + ylab("Oviposition preference (SD)") + xlab("")
-
-plot_grid(visreg_platy_Diam, visreg_platy_Clutch, visreg_platy_Pref, align="hv", ncol=3)
-```
-
-```{r Calculate Selection Differentials for Platygaster, cache=TRUE, include=FALSE, eval=FALSE}
-
-## Calculation linear selection differentials
-boot_platy_Diam <- bootMer(platy_Diam, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-tidy_platy_Diam <- tidy(boot_platy_Diam, conf.int=T) %>% filter(term=="FoodwebComplex") %>% mutate(term="Diam")
-
-boot_platy_Clutch <- bootMer(platy_Clutch, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-tidy_platy_Clutch <- tidy(boot_platy_Clutch, conf.int=T) %>% filter(term=="FoodwebComplex") %>% mutate(term="Clutch")
-
-boot_platy_Pref <- bootMer(platy_Pref, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-tidy_platy_Pref <- tidy(boot_platy_Pref, conf.int=T) %>% filter(term=="FoodwebComplex") %>% mutate(term="Pref")
-
-platy_linear_selection <- bind_rows(tidy_platy_Diam, tidy_platy_Clutch, tidy_platy_Pref) %>% select(Term=term, Estimate=statistic, `2.5%`=conf.low, `97.5%`=conf.high)
-platy_linear_selection$Significance <- c("NS","NS","P < 0.05")
-
-## Calculate quadratic selection differentials
-# statistical significance is based on Levene's test of homogeneity of variances
-platy_quadratic_selection <- platy_selection_df %>%
-  group_by(Foodweb) %>%
-  summarise_at(c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), var) %>%
-  gather(key = Term, value = Variance, -Foodweb) %>%
-  spread(Foodweb, Variance) %>%
-  mutate(Estimate = Complex - Simple) %>%
-  select(Term, Estimate)
-platy_quadratic_selection$Term <- c("Diam^2","Pref^2","Clutch^2")
-platy_quadratic_selection$Significance <- c("NS","P < 0.05","NS")
-```
-
-```{r Table of Platygaster selection differentials, echo=FALSE, eval=FALSE, include=FALSE}
-platy_selection_differentials <- bind_rows(platy_linear_selection, platy_quadratic_selection)
-
-knitr::kable(platy_selection_differentials, caption="Table of selection differentials acting on the egg parasitoid Platygaster")
-```
-
-Note that equation 3 in Phillips and Arnold 1998 is good justification for why quadratic selection cofficients should be multiplied by two (but not correlational ones?)
-
-The G-matrix is essentially a scalar.
-For my data, since there is no correlational selection, it doesn't matter if there is genetic covariance between the traits, as this will not effect the change in genetic covariances within a generation (because there is no selection).
-Also, the G_matrix does not qualitatively alter the conclusions that there will be a decrease in additive genetic variance in gall diameter due to the strong directional selection; however, there will be an increase in the additive genetic variance in Oviposition preference.
-Since this is an experiment, we can assume that the G-matrix is the same between treatments
-
-Remember that the diagonals refer to additive genetic CO-variances.
-Thus, positive or negative values for delta_G give insight to whether selection will act to integrate traits (positive covariance) or create trade-offs (negative covariance).
-
-Assuming that there is positive additive genetic variance and co-variance in these traits (i.e.
-all values of G-matrix are positive), then the curvature of the fitness landscape can give insight to qualitative changes in the G matrix.
-This is because the G-matrix acts as a scalar of changes in the fitness landscape.
-
-Create a simple rule. If the confidence interval of the selection gradient overlaps zero, then I set it to zero. Otherwise, I set it to our best estimate of the gradient-->
-
 ```{r Slope and Curvature of the Adaptive Landscape, include=FALSE}
@@
 ```
-<!--
-## Slope of adaptive landscape
-
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix}$$
-
-$$\text{Slope}_{complex} = \begin{pmatrix} `r #complex_betas["Diam", ]` \\ `r #complex_betas["Clutch", ]` \\ `r #complex_betas["Pref", ]` \end{pmatrix}$$
-$$\text{Slope}_{simple} =  \begin{pmatrix} `r #simple_betas["Diam", ]` \\ `r #simple_betas["Clutch", ]` \\ `r #simple_betas["Pref", ]` \end{pmatrix}$$
-
-## Curvature of adaptive landscape
-
-$$\text{Curvature} = \gamma - \beta \beta^\text{T}$$
-
-$$\gamma = \begin{pmatrix} \gamma_{diam} & \gamma_{diam,clutch} & \gamma_{diam,pref} \\ \gamma_{clutch,diam} & \gamma_{clutch} & \gamma_{clutch,pref} \\ \gamma_{pref,diam} & \gamma_{pref,clutch} &\gamma_{pref} \end{pmatrix}$$
-$$\gamma_{complex} = \begin{pmatrix} `r #complex_gammas["Diam","Diam"]` & `r #complex_gammas["Diam","Clutch"]` & `r #complex_gammas["Diam","Pref"]` \\  `r #complex_gammas["Clutch","Diam"]` & `r #complex_gammas["Clutch","Clutch"]` & `r #complex_gammas["Clutch","Pref"]` \\  `r #complex_gammas["Pref","Diam"]` & `r #complex_gammas["Pref","Clutch"]` & `r #complex_gammas["Pref","Pref"]` \end{pmatrix}$$
-$$\gamma_{simple} = \begin{pmatrix} `r #simple_gammas["Diam","Diam"]` & `r #simple_gammas["Diam","Clutch"]` & `r #simple_gammas["Diam","Pref"]` \\  `r #simple_gammas["Clutch","Diam"]` & `r #simple_gammas["Clutch","Clutch"]` & `r #simple_gammas["Clutch","Pref"]` \\  `r #simple_gammas["Pref","Diam"]` & `r #simple_gammas["Pref","Clutch"]` & `r #simple_gammas["Pref","Pref"]` \end{pmatrix}$$
-
-$$\text{Curvature}_{complex} = \begin{pmatrix} `r #complex_curvature["Diam","Diam"]` & `r #complex_curvature["Diam","Clutch"]` & `r #complex_curvature["Diam","Pref"]` \\  `r #complex_curvature["Clutch","Diam"]` & `r #complex_curvature["Clutch","Clutch"]` & `r #complex_curvature["Clutch","Pref"]` \\  `r #complex_curvature["Pref","Diam"]` & `r #complex_curvature["Pref","Clutch"]` & `r #complex_curvature["Pref","Pref"]` \end{pmatrix}$$
-
-$$\text{Curvature}_{simple} = \begin{pmatrix} `r #simple_curvature["Diam","Diam"]` & `r #simple_curvature["Diam","Clutch"]` & `r #simple_curvature["Diam","Pref"]` \\  `r #simple_curvature["Clutch","Diam"]` & `r #simple_curvature["Clutch","Clutch"]` & `r #simple_curvature["Clutch","Pref"]` \\  `r #simple_curvature["Pref","Diam"]` & `r #simple_curvature["Pref","Clutch"]` & `r #simple_curvature["Pref","Pref"]` \end{pmatrix}$$
-
-## Observed phenotypic variance-covariance matrix
-
-```{r Observe P matrix, include=FALSE, eval=FALSE}
-
-## setup P-matrix
-P_matrix <- matrix(1, nrow=3, ncol=3, dimnames = list(c("Diam","Clutch","Pref"),c("Diam","Clutch","Pref")))
-
-## confirm that variance of phenotypic traits = 1
-P_matrix["Diam","Diam"] <- var(gall_selection.df$sc.Diam)
-P_matrix["Clutch","Clutch"] <- var(gall_selection.df$sc.log.Clutch)
-P_matrix["Pref","Pref"] <- var(gall_selection.df$sc.sqrt.Pref)
-
-## calculate covariance between phenotypic traits
-P_matrix["Diam","Clutch"] <- with(gall_selection.df, cov(sc.Diam, sc.log.Clutch))
-P_matrix["Clutch","Diam"] <- P_matrix["Diam","Clutch"]
-
-P_matrix["Diam","Pref"] <- with(gall_selection.df, cov(sc.Diam, sc.sqrt.Pref))
-P_matrix["Pref","Diam"] <- P_matrix["Diam","Pref"]
-
-P_matrix["Clutch","Pref"] <- with(gall_selection.df, cov(sc.log.Clutch, sc.sqrt.Pref))
-P_matrix["Pref","Clutch"] <- P_matrix["Clutch","Pref"]
-
-heritability <- 0.3 # since all traits are scaled to SD (and variance)=1, then a narrow-sense heritability of 0.3 (which is reasonable) corresponds to an additive genetic variance of 0.3 (Vg = h2 * Vp)
-
-G_matrix <- P_matrix * heritability
-```
-
-$$\text{P} = \begin{pmatrix} `r #round(P_matrix["Diam","Diam"],2)` & `r #round(P_matrix["Diam","Clutch"],2)` & `r #round(P_matrix["Diam","Pref"],2)` \\  `r #round(P_matrix["Clutch","Diam"],2)` & `r #round(P_matrix["Clutch","Clutch"],2)` & `r #round(P_matrix["Clutch","Pref"],2)` \\  `r #round(P_matrix["Pref","Diam"],2)` & `r #round(P_matrix["Pref","Clutch"],2)` & `r #round(P_matrix["Pref","Pref"],2)` \end{pmatrix}$$
-Note that the variance of each phenotypic trait is standardized to 1.
-If we assume that each phenotypic trait has a narrow-sense heritability ($h^2$) of `r #heritability`, then the additive genetic variance of each trait is equal to its narrow-sense heritability.
-The resulting G-matrix is:
-
-$$\text{G} = \begin{pmatrix} `r #round(G_matrix["Diam","Diam"],2)` & `r #round(G_matrix["Diam","Clutch"],2)` & `r #round(G_matrix["Diam","Pref"],2)` \\  `r #round(G_matrix["Clutch","Diam"],2)` & `r #round(G_matrix["Clutch","Clutch"],2)` & `r #round(G_matrix["Clutch","Pref"],2)` \\  `r #round(G_matrix["Pref","Diam"],2)` & `r #round(G_matrix["Pref","Clutch"],2)` & `r #round(G_matrix["Pref","Pref"],2)` \end{pmatrix}$$
-```{r Change in G-matrices, include=FALSE, eval=FALSE}
-complex_G_matrix <- G_matrix + G_matrix %*% complex_curvature %*% G_matrix
-simple_G_matrix <- G_matrix + G_matrix %*% simple_curvature %*% G_matrix
-```
-
-# Change in complex G-matrix
-
-$$\text{G}_{complex} = \begin{pmatrix} `r #round(complex_G_matrix["Diam","Diam"],3)` & `r #round(complex_G_matrix["Diam","Clutch"],3)` & `r #round(complex_G_matrix["Diam","Pref"],3)` \\  `r #round(complex_G_matrix["Clutch","Diam"],3)` & `r #round(complex_G_matrix["Clutch","Clutch"],3)` & `r #round(complex_G_matrix["Clutch","Pref"],3)` \\  `r #round(complex_G_matrix["Pref","Diam"],3)` & `r #round(complex_G_matrix["Pref","Clutch"],3)` & `r #round(complex_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
-
-# Change in simple G-matrix
-
-$$\text{G}_{simple} = \begin{pmatrix} `r #round(simple_G_matrix["Diam","Diam"],3)` & `r #round(simple_G_matrix["Diam","Clutch"],3)` & `r #round(simple_G_matrix["Diam","Pref"],3)` \\  `r #round(simple_G_matrix["Clutch","Diam"],3)` & `r #round(simple_G_matrix["Clutch","Clutch"],3)` & `r #round(simple_G_matrix["Clutch","Pref"],3)` \\  `r #round(simple_G_matrix["Pref","Diam"],3)` & `r #round(simple_G_matrix["Pref","Clutch"],3)` & `r #round(simple_G_matrix["Pref","Pref"],3)` \end{pmatrix}$$
-
-```{r Evo dynamics derived from observed phenotypic variance-covariance, include=FALSE, eval=FALSE}
-
-# initial trait values
-z_initial <- matrix(0, nrow=3, ncol=1, dimnames = list(c("Diam","Clutch","Pref")))
-
-# checks to see whether disruptive selection on preference is driving the relationship
-alt_complex_gammas <- complex_gammas
-alt_complex_gammas["Pref","Pref"] <- 0
-
-# basically, controls for differences in mean fitness
-alt_simple_betas <- complex_betas 
-alt_simple_betas["Clutch", ] <- simple_betas["Clutch", ] * simple_mean_fitness / complex_mean_fitness # best estimate on complex mean fitness scale, need to confirm...
-
-# simulate evolutionary dynamics
-complex_evo_dynamics <- evolutionary_dynamics(betas = complex_betas, 
-                                              gammas = complex_gammas, 
-                                              G_0 = G_matrix,
-                                              z_0 = z_initial,
-                                              t = n_evo_sims)
-
-simple_evo_dynamics <- evolutionary_dynamics(betas = simple_betas, 
-                                             gammas = simple_gammas, 
-                                             G_0 = G_matrix,
-                                             z_0 = z_initial,
-                                             t = n_evo_sims)
-
-## Tidy simulations
-complex_z_feasible <- mutate(tidy_evo_sims(complex_evo_dynamics), Foodweb="Complex")
-
-simple_z_feasible <- mutate(tidy_evo_sims(simple_evo_dynamics), Foodweb="Simple")
-```
-
-```{r altered parameters, include=FALSE, eval=FALSE}
-complex_betas
-```
-
-## Walk across the adaptive landscape
-
-```{r Evo-Sim-Hyp-G, include=FALSE, eval=FALSE, echo=FALSE, fig.cap="Evolutionary simulation of a hypothetical G-matrix"}
-
-# Make plots
-evosim_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
-  geom_line(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Clutch)) +
-  geom_point(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Clutch))
-
-evosim_AF_plot_Clutch.Pref <- AF_plot_Clutch.Pref +
-  geom_line(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Pref, y=Clutch)) +
-  geom_point(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Pref, y=Clutch))
-
-evosim_AF_plot_Diam.Pref <-  AF_plot_Diam.Pref +
-  geom_line(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Pref)) +
-  geom_point(data=bind_rows(complex_z_feasible, simple_z_feasible), aes(x=Diam, y=Pref))
-
-# Get legend
-evosim_AF_landscape_legend <- get_legend(evosim_AF_plot_Diam.Pref)
-
-# Format plots
-evosim_AF_landscape_plots <- plot_grid(
-  evosim_AF_plot_Diam.Clutch + theme(legend.position = "none", 
-                              axis.title.y = element_text(size=11),
-                              axis.title.x = element_blank(),
-                              axis.text = element_text(size=10)),
- evosim_AF_plot_Clutch.Pref + theme(legend.position = "none", 
-                              axis.title.y = element_blank(), 
-                              axis.text = element_text(size=10), 
-                              axis.title.x = element_text(size=11)),
-  evosim_AF_plot_Diam.Pref + theme(legend.position = "none", 
-                            axis.text = element_text(size=10),
-                            axis.title = element_text(size=11)), 
-  nrow=2, align="hv", labels = "AUTO")
-evosim_AF_landscape_2d <- ggdraw(evosim_AF_landscape_plots) + draw_grob(evosim_AF_landscape_legend, x = 0.7, y=-0.2)
-evosim_AF_landscape_2d
-```
-
-## Compare evolvabilities of hypothetical G-matrix over time
-
-Since my covariance is standardized, it should be okay to calculate the mean squared correlation as an overall measure of trait integration.
-
-```{r Compare changes in hypothetical G-matric over time, echo=FALSE, include=FALSE, eval=FALSE}
-last(complex_z_feasible$Time)/last(simple_z_feasible$Time)
-
-complex_evolvability <- c()
-complex_conditional.evolvability <- c()
-complex_constraints <- c()
-complex_autonomy <- c()
-complex_MeanSquaredCorrelation <- c()
-for(i in 1:last(complex_z_feasible$Time)){
-  complex_evolvability[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["evolvability"] 
-  complex_conditional.evolvability[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["conditional.evolvability"]
-  complex_constraints[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["constraints"]
-  complex_autonomy[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["autonomy"]
-  complex_MeanSquaredCorrelation[i] <- MeanMatrixStatistics(complex_evo_dynamics$G[[i]])["MeanSquaredCorrelation"]
-}
-
-simple_evolvability <- c()
-simple_conditional.evolvability <- c()
-simple_constraints <- c()
-simple_autonomy <- c()
-simple_MeanSquaredCorrelation <- c()
-for(i in 1:last(simple_z_feasible$Time)){
-  simple_evolvability[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["evolvability"] 
-  simple_conditional.evolvability[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["conditional.evolvability"]
-  simple_constraints[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["constraints"] 
-  simple_autonomy[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["autonomy"]
-  simple_MeanSquaredCorrelation[i] <- MeanMatrixStatistics(simple_evo_dynamics$G[[i]])["MeanSquaredCorrelation"]
-}
-
-gather_G_matrix_data <- bind_rows(
-  data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", 
-             evolvability=complex_evolvability,
-             conditional.evolvability=complex_conditional.evolvability,
-             constraints=complex_constraints,
-             autonomy=complex_autonomy,
-             MeanSquaredCorrelation=complex_MeanSquaredCorrelation),
-  data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple",
-             evolvability=simple_evolvability,
-             conditional.evolvability=simple_conditional.evolvability,
-             constraints=simple_constraints,
-             autonomy=simple_autonomy,
-             MeanSquaredCorrelation=simple_MeanSquaredCorrelation)) %>%
-  gather(key=G_metric, value=value, -Time, -Foodweb)
-
-gather_G_matrix_data %>%
-  ggplot(., aes(x=Time, y=value, color=Foodweb)) +
-  geom_point() +
-  geom_line() +
-  scale_color_manual(values=treatment_colors) +
-  facet_wrap(~G_metric, ncol=2, scales = "free_y")
-
-#bind_rows(data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", conditional.evolvability=complex_conditional.evolvability),
-#          data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple", conditional.evolvability=simple_conditional.evolvability)) %>%
-#  ggplot(., aes(x=Time, y=conditional.evolvability, color=Foodweb)) +
-#  geom_point() +
-#  geom_line() +
-#  scale_color_manual(values=treatment_colors)
-
-#bind_rows(data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", constraints=complex_constraints),
-#          data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple", constraints=simple_constraints)) %>%
-#  ggplot(., aes(x=Time, y=constraints, color=Foodweb)) +
-#  geom_point() +
-#  geom_line() +
-#  scale_color_manual(values=treatment_colors)
-
-#bind_rows(data.frame(Time=1:last(complex_z_feasible$Time), Foodweb="Complex", autonomy=complex_autonomy),
-#          data.frame(Time=1:last(simple_z_feasible$Time), Foodweb="Simple", autonomy=simple_autonomy)) %>%
-#  ggplot(., aes(x=Time, y=autonomy, color=Foodweb)) +
-#  geom_point() +
-#  geom_line() +
-#  scale_color_manual(values=treatment_colors)
-```
-
-## More walks across the adaptive landscape
-
-```{r Generate random G matrices and simulate Evo Dynamics, include=FALSE, eval=FALSE}
-
-## Define the maximum additive genetic variance
-max_add_G <- 0.5
-
-## Number of G-matrix simulations
-n_G_sims <- 200 # 1000
-
-## Simulate G-matrices
-
-## ALTERNATIVE APPROACH: RandomMatrix(num.traits=3, num.matrices = 1, min.var=0, max.var=0.5)
-
-# additive genetic variance is sampled from a random uniform distribution and varies between 0 and max_add_G
-# additive genetic covariances can be positive or negative with a maximum absolute value determined by the product of additive genetic variances.
-sim_G <- list()
-for(i in 1:n_G_sims){
-  sim_G[[i]] <- diag(x = runif(n=3, min = 0, max = max_add_G), nrow = 3)
-  sim_G[[i]][1,2] <- runif(n=1, min=-(sim_G[[i]][1,1]*sim_G[[i]][2,2]), max=(sim_G[[i]][1,1]*sim_G[[i]][2,2]))
-  sim_G[[i]][2,1] <- sim_G[[i]][1,2]
-  sim_G[[i]][1,3] <- runif(n=1, min=-(sim_G[[i]][1,1]*sim_G[[i]][3,3]), max=(sim_G[[i]][1,1]*sim_G[[i]][3,3]))
-  sim_G[[i]][3,1] <- sim_G[[i]][1,3]
-  sim_G[[i]][2,3] <- runif(n=1, min=-(sim_G[[i]][2,2]*sim_G[[i]][3,3]), max=(sim_G[[i]][2,2]*sim_G[[i]][3,3]))
-  sim_G[[i]][3,2] <- sim_G[[i]][2,3]
-}
-
-## Simulations for complex food-web treatment
-complex_evo_sims <- lapply(X = sim_G, FUN = function(x) evolutionary_dynamics(betas = complex_betas, # test_betas, #
-                                                                              gammas = complex_gammas, # test_gammas, #
-                                                                              G_0 = x, z_0 = z_initial, t = n_evo_sims))
-
-tidy_complex_sims <- lapply(X = complex_evo_sims, FUN = tidy_evo_sims)
-
-tidier_complex_sims <- list()
-for(i in 1:length(tidy_complex_sims)){
-  tidier_complex_sims[[i]] <- mutate(tidy_complex_sims[[i]], simulation = i, Foodweb="Complex")
-}
-
-tidiest_complex_sims <- bind_rows(tidier_complex_sims)
-
-## Simulations for simple food-web treatment
-simple_evo_sims <- lapply(X = sim_G, FUN = function(x) evolutionary_dynamics(betas = simple_betas, # simple_betas
-                                                                             gammas = simple_gammas, # test_gammas, #
-                                                                             G_0 = x, z_0 = z_initial, t = n_evo_sims))
-
-tidy_simple_sims <- lapply(X = simple_evo_sims, FUN = tidy_evo_sims)
-
-tidier_simple_sims <- list()
-for(i in 1:length(tidy_simple_sims)){
-  tidier_simple_sims[[i]] <- mutate(tidy_simple_sims[[i]], simulation = i, Foodweb="Simple")
-}
-
-tidiest_simple_sims <- bind_rows(tidier_simple_sims)
-
-## Combine evolutionary simulations for plotting
-combine_tidied_evo_sims <- bind_rows(tidiest_complex_sims, tidiest_simple_sims)
-
-sims_to_subsample <- sample(unique(combine_tidied_evo_sims$simulation), 100)
-
-sub_tidied_evo_sims <- combine_tidied_evo_sims %>% filter(simulation %in% sims_to_subsample) # subsample 100 for plotting
-```
-
-```{r Plot evo sims of many G-matrices, include=FALSE, eval=FALSE}
-evosim.manyG_AF_plot_Diam.Clutch <- AF_plot_Diam.Clutch +
-  geom_line(data=sub_tidied_evo_sims, aes(x=Diam, y=Clutch, group=simulation), alpha=0.1)
-
-evosim.manyG_AF_plot_Clutch.Pref <- AF_plot_Clutch.Pref +
-  geom_line(data=sub_tidied_evo_sims, aes(x=Pref, y=Clutch, group=simulation), alpha=0.1)
-
-evosim.manyG_AF_plot_Diam.Pref <-  AF_plot_Diam.Pref +
-  geom_line(data=sub_tidied_evo_sims, aes(x=Diam, y=Pref, group=simulation), alpha=0.1)
-```
-
-```{r Evo-Sim-Many-G, include=FALSE, eval=FALSE, fig.cap="Evolutionary simulation of a range of G-matrices"}
-# Get legend
-evosim.manyG_AF_landscape_legend <- get_legend(evosim.manyG_AF_plot_Diam.Pref)
-
-# Format plots
-evosim.manyG_AF_landscape_plots <- plot_grid(
-  evosim.manyG_AF_plot_Diam.Clutch + theme(legend.position = "none", 
-                              axis.title.y = element_text(size=11),
-                              axis.title.x = element_blank(),
-                              axis.text = element_text(size=10)),
- evosim.manyG_AF_plot_Clutch.Pref + theme(legend.position = "none", 
-                              axis.title.y = element_blank(), 
-                              axis.text = element_text(size=10), 
-                              axis.title.x = element_text(size=11)),
-  evosim.manyG_AF_plot_Diam.Pref + theme(legend.position = "none", 
-                            axis.text = element_text(size=10),
-                            axis.title = element_text(size=11)), 
-  nrow=2, align="hv", labels = "AUTO")
-evosim.manyG_AF_landscape_2d <- ggdraw(evosim.manyG_AF_landscape_plots) + draw_grob(evosim.manyG_AF_landscape_legend, x = 0.7, y=-0.2)
-evosim.manyG_AF_landscape_2d
-```
-
-## Multivariate trait differences
-
-```{r Multivariate trait differences, include=FALSE, eval=FALSE}
-library(vegan)
-
-multivariate_trait_evolution <- combine_tidied_evo_sims %>%
-  group_by(simulation, Foodweb) %>%
-  summarise_at(vars(Diam, Clutch, Pref), funs(last)) %>%
-  ungroup()
-
-multivariate_trait_evolution %>%
-  group_by(Foodweb) %>%
-  summarise_at(vars(Diam, Clutch, Pref), funs(mean, sd))
-
-multivariate_trait_distance <- vegdist(x = select(multivariate_trait_evolution, Diam, Clutch, Pref), method = "euclidean")
-# multivariate_traits <- adonis(multivariate_trait_distance ~ Foodweb, data = multivariate_trait_evolution)
-
-trait_disper <- betadisper(d = multivariate_trait_distance, group = multivariate_trait_evolution$Foodweb)
-anova(trait_disper)
-plot(trait_disper)
-boxplot(trait_disper)
-```
-
-## How does the adaptive landscape influence the rate of evolution?
-
-Here we are going to see how fast it took for the *Iteomyia* to hit the edge of the adaptive landscape across many different G-matrices.
-```{r Rate of phenotypic evolution, include=FALSE, eval=FALSE}
-evo_sim_duration <-combine_tidied_evo_sims %>%
-  group_by(simulation, Foodweb) %>%
-  summarise_at(vars(Time), funs(last))
-
-which(evo_sim_duration$Time == n_evo_sims) # note that a boundary was hit on the adaptive landscape for all simulations prior to the simulation duration
-
-evo_sim_duration %>%
-  ggplot(., aes(x=Foodweb, y=Time, group=simulation)) +
-  geom_point() + 
-  geom_line() +
-  scale_y_log10() +
-  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
-
-# only 10 times out of 500 simulations where it took longer to hit the boundary in the complex food web (so in general, its faster)
-spread(evo_sim_duration, Foodweb, Time) %>%
-  filter(Complex > Simple)
-
-wide_evo_sim_duration <- spread(evo_sim_duration, Foodweb, Time) %>%
-  mutate(Diff = Simple - Complex, Diff.Percent = Diff/Complex, Diff.Fold = Simple/Complex)
-
-round(mean(wide_evo_sim_duration$Diff.Fold),1)
-```
-
-In general, *Iteomyia* hit the edge of the adaptive landscape faster in the complex vs. simple food web.
-
-```{r Intuition about evolvability, include=FALSE, eval=FALSE}
-base_matrix <- matrix(c(1,0,0,
-                        0,1,0,
-                        0,0,1), nrow=3, ncol=3)
-base_G <- 0.5
-
-G_1 <- base_G*base_matrix
-MeanMatrixStatistics(G_1)
-G_2 <- G_1
-G_2[2,1] <- -G_1[1,1]*G_1[2,2]
-G_2[1,2] <- G_2[2,1]
-MeanMatrixStatistics(G_2)
-G_3 <- G_2
-G_3[3,1] <- -G_2[1,1]*G_2[3,3]
-G_3[1,3] <- G_3[3,1]
-MeanMatrixStatistics(G_3)
-G_4 <- G_3
-G_4[3,2] <- -G_3[2,2]*G_3[3,3]
-G_4[2,3] <- G_4[3,2]
-MeanMatrixStatistics(G_4)
-
-G_5 <- base_G*base_matrix
-MeanMatrixStatistics(G_5)
-G_6 <- G_5
-G_6[2,1] <- G_5[1,1]*G_5[2,2]
-G_6[1,2] <- G_6[2,1]
-MeanMatrixStatistics(G_6)
-G_7 <- G_6
-G_7[3,1] <- G_6[1,1]*G_6[3,3]
-G_7[1,3] <- G_7[3,1]
-MeanMatrixStatistics(G_7)
-G_8 <- G_7
-G_8[3,2] <- G_7[2,2]*G_7[3,3]
-G_8[2,3] <- G_8[3,2]
-MeanMatrixStatistics(G_8)
-
-bind_rows(MeanMatrixStatistics(G_1), MeanMatrixStatistics(G_2), MeanMatrixStatistics(G_3), #MeanMatrixStatistics(G_4),
-          MeanMatrixStatistics(G_5), MeanMatrixStatistics(G_6), MeanMatrixStatistics(G_7), MeanMatrixStatistics(G_8)) %>%
-  mutate(G_name = c(1:3,5:8), base_G = base_G) %>%
-  select(G_name, evolvability, conditional.evolvability, autonomy, constraints)
-```
-
-```{r Intuition about matrix multiplication, include=FALSE, eval=FALSE}
-
-beta <- matrix(c(0.2,0,0.1), nrow = 3)
-- (beta %*% t(beta)) # decrease in genetic covariance between traits 1 and 3
-
-beta2 <- matrix(c(0.2,0,-0.1), nrow = 3)
-- (beta2 %*% t(beta2)) # increase in genetic covariance between traits 1 and 3
-
-cov.test <- matrix(1, nrow = 3, ncol=3)*0.5
-cov.test[2,1] <- cov.test[1,1]*cov.test[2,2]
-cov.test[1,2] <- cov.test[2,1]
-cov.test[3,1] <- cov.test[1,1]*cov.test[3,3]
-cov.test[1,3] <- cov.test[3,1]
-cov.test[2,3] <- cov.test[3,3]*cov.test[2,2]
-cov.test[3,2] <- cov.test[2,3]
-
-sim_data <- MASS::mvrnorm(n=10, mu=rep(0,3), Sigma=cov.test)
-plot(sim_data[,1] ~ sim_data[,2])
-```
-
-```{r Compare evolvabilities at end of simulation, include=FALSE, eval=FALSE}
-
-complex_G_end <- list()
-simple_G_end <- list()
-for(i in 1:n_evo_sims){ #n_evo_sims
-
-  complex_time_end <- filter(evo_sim_duration, Foodweb=="Complex", simulation == i)$Time
-  simple_time_end <- filter(evo_sim_duration, Foodweb=="Simple", simulation == i)$Time
-
-  if(isSymmetric(complex_evo_sims[[i]]$G[[complex_time_end]])==TRUE){
-    complex_G_end[[i]] <- data.frame(t(MeanMatrixStatistics(complex_evo_sims[[i]]$G[[complex_time_end]]))) %>% select(evolvability, conditional.evolvability, autonomy, constraints, MeanSquaredCorrelation)
-  } else {complex_G_end[[i]] <- data.frame(evolvability=NA, conditional.evolvability=NA, autonomy=NA, constraints=NA, MeanSquaredCorrelation=NA)}
-
-  if(isSymmetric(simple_evo_sims[[i]]$G[[simple_time_end]])==TRUE){
-    simple_G_end[[i]] <- data.frame(t(MeanMatrixStatistics(simple_evo_sims[[i]]$G[[simple_time_end]]))) %>% select(evolvability, conditional.evolvability, autonomy, constraints, MeanSquaredCorrelation)
-  } else {simple_G_end[[i]] <- data.frame(evolvability=NA, conditional.evolvability=NA, autonomy=NA, constraints=NA, MeanSquaredCorrelation=NA)}
-}
-
-tidy_G_matrix_stats <- bind_rows(
-  mutate(bind_rows(complex_G_end), sim = 1:n_evo_sims, Foodweb="Complex"),
-  mutate(bind_rows(simple_G_end), sim = 1:n_evo_sims, Foodweb="Simple")) %>%
-  gather(key=G_metric, value=value, -sim, -Foodweb)
-
-tidy_G_matrix_stats %>%
-  ggplot(., aes(x=Foodweb, y=value, group=sim)) +
-  geom_point() + 
-  geom_line() +
-  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb)) +
-  facet_wrap(~G_metric, ncol=2, scales="free_y")
-
-#tidy_G_matrix_stats %>%
-#  ggplot(., aes(x=Foodweb, y=evolvability, group=sim)) +
-#  geom_point() + 
-#  geom_line() +
-#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
-
-#tidy_G_matrix_stats %>%
-#  ggplot(., aes(x=Foodweb, y=conditional.evolvability, group=sim)) +
-#  geom_point() + 
-#  geom_line() +
-#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
-
-#tidy_G_matrix_stats %>%
-#  ggplot(., aes(x=Foodweb, y=autonomy, group=sim)) +
-#  geom_point() + 
-#  geom_line() +
-#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
-
-#tidy_G_matrix_stats %>%
-#  ggplot(., aes(x=Foodweb, y=constraints, group=sim)) +
-#  geom_point() + 
-#  geom_line() +
-#  stat_summary(fun.y = "mean", color="red", geom="point", size=5, mapping=aes(group=Foodweb))
-
-#evolvability_stats <- tidy_G_matrix_stats %>%
-#  select(sim, Foodweb, evolvability) %>%
-#  spread(Foodweb, evolvability) %>%
-#  mutate(Diff.mag = Complex/Simple)
-
-#mean(evolvability_stats$Diff.mag, na.rm=T) # Resulting G-matrix is 2x more evolvable in complex vs. simple food web.
-```
-
-```{r Mortality, include=FALSE, eval=FALSE}
-# 8-10% mortality induced by intraguild predators
-mean(control_df$platy)
-mean(treatment_df$platy)
-mean(eggptoid_control_df$platy)
-
-# Gall mortality to Platy
-1 - mean(treatment_df$pupa)
-
-# Gall mortality to Ectos
-
-# Platy mortality to intraguild predation
-mean(treatment_df$platy) - mean(control_df$platy)
-
-mean(control_df$ectos)
-mean(treatment_df$ectos)
-mean(ectoptoid_control_df$ectos)
-
-mean(control_df$pupa)
-mean(treatment_df$pupa)
-mean(eggptoid_control_df$pupa)
-mean(ectoptoid_control_df$pupa)
-```
-
-$$logit(E(W))=\mu+\beta_{diameter}+\beta_{clutch}+\beta_{preference}+$$
-$$logit(E(W))=\mu+treatment+s(diam):treat+s(clutch)+s(pref)+diam:cluch+diam:pref+clutch:pref+(1|Genotype/Plant/Gall)$$
-
-We used generalized linear mixed models (GLMMs, @Bolker2009) to test the effects of food-web complexity on the shape of the fitness landscape. 
-larval survival (0 or 1) was our response variable and measure of fitness.
-
-Need to clean up the language part of this section without it being too complicated and confusing. I should also include tests of non-linear selection gradients.
-
-We specified our food-web treatment, each gall trait, two-way interactions between gall traits, as well interactions between gall trait and food-web treatment, as fixed effects to fully explore the effects of food-web complexity on the fitness landscape.
-This analysis implicitly assumes that selection is linear, which we felt was a necessary trade-off for exploring the shape of the fitness landscape. 
-To account for the correlated structure of clutch size (gall level) and Oviposition preference (plant level) as well as any other independent effects of willow genotype on parasitism rates, we specified gall ID nested within plant ID nested within plant genotype as random intercepts in our statistical models.
-
-```{r OLD TEXT, include=FALSE, eval=FALSE}
-$\chi^2_{`r foodweb_test$[2,"Chi.Df"]`}=`r foodweb_test$[2,"statistic"]`, P=`r foodweb_test$[2,"p.value"]`$).
-
-Two key patterns emerged from our analyses. First, fewer phenotypic traits were under selection in the complex vs. simple food web. 
-In both complex and simple food webs, gall diameter was under strong directional selection, with larger galls resulting in higher larval survival (complex $\beta_{diam}=$`r paste0(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_control, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Gall diameter")$upper_97.5,"]")`; simple $\beta_{diam}=$ `r paste0(filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Gall diameter")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Gall diameter")$upper_97.5,"]")`)(Fig.
-\ref{fig:Univariate_Landscapes}A).
-
-In the complex food web, we found that there was no selection acting on clutch size
-
-In simple food webs, both clutch size and Oviposition preference experience directional selection, with smaller clutch sizes ($\beta_{clutch}=$
-`r paste0(filter(summary_beta_treatment, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Clutch size")$upper_97.5,"]")`
-and weaker preferences ($\beta_{pref}=$
-`r paste0(filter(summary_beta_treatment, Phenotype=="Oviposition preference")$Estimate," [",filter(summary_beta_treatment, Phenotype=="Oviposition preference")$lower_2.5,",",filter(summary_beta_treatment, Phenotype=="Oviposition preference")$upper_97.5,"]")`
-) resulting in higher larval survival (blue lines in Fig. \ref{fig:Univariate_Landscapes}B,C).
-In contrast, there was no evidence of selection on clutch size ($\beta_{clutch}=$
-`r paste0(filter(summary_beta_control, Phenotype=="Clutch size")$Estimate," [",filter(summary_beta_control, Phenotype=="Clutch size")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Clutch size")$upper_97.5,"]")`
-) or Oviposition preference ($\beta_{pref}=$
-`r paste0(filter(summary_beta_control, Phenotype=="Oviposition preference")$Estimate," [",filter(summary_beta_control, Phenotype=="Oviposition preference")$lower_2.5,",",filter(summary_beta_control, Phenotype=="Oviposition preference")$upper_97.5,"]")`
-) in complex food webs (orange lines in Fig.
-\ref{fig:Univariate_Landscapes}B,C).
-The absence of selection on clutch size and Oviposition preference was likely a result of conflicting selection pressures imposed by each guild of parasitoids due to their different functional relationships with gall traits.
-Together, these different patterns of selection resulted in an ideal combination of traits having higher fitness in the simple food web (large diameter, smaller clutches, weaker preference), whereas there was a larger combination of trait values that had equal fitness in the complex food web (Fig.
-\ref{fig:Multivariate_Landscapes}).
-We did not find any strong evidence for nonlinear or correlational selection gradients acting on gall traits in either food-web treatment.
-The second major pattern was that the overall intensity of selection was stronger in the complex vs.
-simple food web.
-This result appeared to be driven by selection on gall diameter in the complex food web, which was more than
-`r round(filter(summary_beta_control, Phenotype=="Gall diameter")$Estimate/filter(summary_beta_treatment, Phenotype=="Gall diameter")$Estimate,1)`
-$\times$ larger than any other selection gradient in our analyses.
-
-```
-
-## Contributions of egg parasitoids to selection gradients
-
-To identify the mechanisms by which food-web treatment altered selection gradients, we refit our models so that the complex food-web treatment only contained cases of parasitisms from egg parasitoids.
-Therefore, these analyses identify the change in apparent selection imposed by the egg parasitoid (egg parasitoid from simple food web; egg parasitoid from complex food web).
-
-```{r Egg vs. egg Parasitoids Model, cache=TRUE, eval=FALSE, include=FALSE}
-
-# excludes cases of egg-parasitism from Complex food web
-egg.vs.egg_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & ectos < 1) #%>% 
- # mutate(Foodweb = ifelse(Foodweb == "Simple", "Egg", "egg"))
-
-egg.vs.egg_df$Foodweb <- relevel(factor(egg.vs.egg_df$Foodweb), ref = "Simple") # this represents the baseline or absence of selection by larval parasitoids
-
-egg.egg_model_1 <- update(model_1, data=egg.vs.egg_df)
-summary(egg.egg_model_1)
-```
-
-```{r egg vs egg ggplot explore, eval=FALSE, include=FALSE}
-densities <- gall_selection.df %>%
-  distinct(Foodweb, Genotype, Plant_Position, sc.sqrt.Pref, Density_per_100_shoots)
-
-survival <- gall_selection.df %>%
-  group_by(Foodweb, Plant_Position) %>%
-  summarise_at(vars(gall_survival, egg_parasitoid, ectos), funs(sum, n())) %>%
-  ungroup() %>%
-  mutate(ptoids_sum = egg_parasitoid_sum + ectos_sum)
-
-left_join(densities, survival) %>%
-  filter(Foodweb=="Complex") %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=ectos_sum/ptoids_sum)) +
-  geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial")) #+
-  #scale_x_continuous(limits=c(-2,1.25))
-
-left_join(densities, survival) %>%
-  filter(Foodweb=="Complex") %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=egg_parasitoid_sum/ptoids_sum)) +
-  geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial"))
-
-left_join(densities, survival) %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=gall_survival_sum/gall_survival_n, color=Foodweb)) +
-  geom_point(aes(size=gall_survival_n), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), method.args = list(family="binomial"))
-
-left_join(densities, survival) %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=gall_survival_n, color=Foodweb)) +
-  geom_point(aes(size=gall_survival_n), shape=21) +
-  geom_smooth(method = "lm", formula = y ~ x, aes(weight=gall_survival_n))
-
-left_join(densities, survival) %>%
-  filter(Foodweb=="Complex") %>%
-  ggplot(., aes(x=sc.sqrt.Pref)) +
-  #geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) + 
-  scale_x_continuous(limits=c(-1,1))
-
-left_join(densities, survival) %>%
-  filter(Foodweb=="Simple") %>%
-  ggplot(., aes(x=sc.sqrt.Pref)) +
-  #geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +  # geom_smooth(method = "lm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green")
-  scale_x_continuous(limits=c(-1,1))
-
-# in the complex food web, there is a positive relationship between the number of gall samples and gall density (makes sense); there is the opposite pattern in the simple foodweb...
-density_n_lm <- lm(gall_survival_n ~ sc.sqrt.Pref*Foodweb, left_join(densities, survival))
-visreg::visreg(density_n_lm, xvar="sc.sqrt.Pref", by="Foodweb")
-summary(density_n_lm)
-wt_density_n_lm <- lm(gall_survival_n ~ sc.sqrt.Pref*Foodweb, left_join(densities, survival), weights = gall_survival_n)
-visreg::visreg(wt_density_n_lm, xvar="sc.sqrt.Pref", by="Foodweb")
-summary(wt_density_n_lm)
-
-# good thing is that I get the same qualitative answer with or without weighting
-test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(densities, survival), family="quasibinomial")
-visreg::visreg(test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
-summary(test_glm)
-
-wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(densities, survival), family="quasibinomial", weights = gall_survival_n)
-visreg::visreg(wt_test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
-summary(wt_test_glm)
-
-# now with just egg parasitoids
-egg.densities <- egg.vs.egg_df %>%
-  distinct(Foodweb, Plant_Position, sc.sqrt.Pref)
-
-egg.survival <- egg.vs.egg_df %>%
-  group_by(Foodweb, Plant_Position) %>%
-  summarise_at(vars(gall_survival, egg_parasitoid, ectos), funs(sum, n())) %>%
-  ungroup() %>%
-  mutate(ptoids_sum = egg_parasitoid_sum + ectos_sum)
-
-egg.test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial")
-visreg::visreg(egg.test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
-summary(egg.test_glm)
-
-egg.wt_test_glm <- glm(gall_survival_sum/gall_survival_n ~ Foodweb*(sc.sqrt.Pref + I(sc.sqrt.Pref^2)), left_join(egg.densities, egg.survival), family="quasibinomial", weights = gall_survival_n)
-visreg::visreg(egg.wt_test_glm, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
-summary(egg.wt_test_glm)
-
-## now use raw densities
-sqrt.raw_complex <- left_join(densities, survival) %>%
-  filter(Foodweb=="Complex") %>%
-  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
-  ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
-  #geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
-  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
-      geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") 
-  #facet_wrap(~Genotype, ncol=2, nrow=4)
-
-sqrt.raw_simple <- left_join(densities, survival) %>%
-    filter(Foodweb=="Simple") %>%
-    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
-    ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
-    #geom_point(aes(size=ptoids_sum), shape=21) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-    scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") 
-   # facet_wrap(~Genotype, ncol=2, nrow=4)
-
-plot_grid(sqrt.raw_complex, sqrt.raw_simple, ncol=2)
-
-raw_complex <- left_join(densities, survival) %>%
-  filter(Foodweb=="Complex") %>%
-  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
-  ggplot(., aes(x=(Density_per_100_shoots))) +
-  #geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
-  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,100)) +
-      geom_vline(xintercept=mean((densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) + sd((densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) - sd((densities$Density_per_100_shoots)), linetype="dotted") 
-  #facet_wrap(~Genotype, ncol=2, nrow=4)
-
-  raw_simple <- left_join(densities, survival) %>%
-    filter(Foodweb=="Simple") %>%
-    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
-    ggplot(., aes(x=(Density_per_100_shoots))) +
-    #geom_point(aes(size=ptoids_sum), shape=21) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-    scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,100)) +
-    geom_vline(xintercept=mean((densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) + sd((densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean((densities$Density_per_100_shoots)) - sd((densities$Density_per_100_shoots)), linetype="dotted") 
-   # facet_wrap(~Genotype, ncol=2, nrow=4)
-
-plot_grid(raw_complex, raw_simple, ncol=2)
-
-log1p.raw_complex <- left_join(densities, survival) %>%
-  filter(Foodweb=="Complex") %>%
-  #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
-  ggplot(., aes(x=log1p(Density_per_100_shoots))) +
-  #geom_point(aes(size=ptoids_sum), shape=21) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-  geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=ectos_sum/gall_survival_n), color="green", method.args = list(family="binomial")) +
-  scale_y_continuous(limits=c(0,1)) + #scale_x_continuous(limits=c(0,100)) +
-      geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) + sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) - sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") 
-  #facet_wrap(~Genotype, ncol=2, nrow=4)
-
-log1p.raw_simple <- left_join(densities, survival) %>%
-    filter(Foodweb=="Simple") %>%
-    #filter(Density_per_100_shoots>0 & sqrt(Density_per_100_shoots)<9.5) %>%
-    ggplot(., aes(x=log1p(Density_per_100_shoots))) +
-    #geom_point(aes(size=ptoids_sum), shape=21) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n), color="red", method.args = list(family="binomial")) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=egg_parasitoid_sum/gall_survival_n), color="black", method.args = list(family="binomial")) +
-    scale_y_continuous(limits=c(0,1)) +# scale_x_continuous(limits=c(0,100)) +
-    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) + sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean(log1p(densities$Density_per_100_shoots)) - sd(log1p(densities$Density_per_100_shoots)), linetype="dotted") 
-   # facet_wrap(~Genotype, ncol=2, nrow=4)
-
-plot_grid(log1p.raw_complex, log1p.raw_simple, ncol=2)
-
-left_join(densities, survival) %>%
-  ggplot(., aes(x=sqrt(Density_per_100_shoots))) +
-    #geom_point(aes(size=ptoids_sum), shape=21) +
-    geom_smooth(method = "glm", formula = y ~ x + I(x^2), aes(weight=gall_survival_n, y=gall_survival_sum/gall_survival_n, color=Foodweb), method.args = list(family="binomial")) +
-  scale_y_continuous(limits=c(0,1)) + scale_x_continuous(limits=c(0,10)) +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots))) +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) + sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted") +
-    geom_vline(xintercept=mean(sqrt(densities$Density_per_100_shoots)) - sd(sqrt(densities$Density_per_100_shoots)), linetype="dotted")
-
-ggplot(densities, aes(x=Genotype, y=Density_per_100_shoots, fill=Foodweb)) + geom_boxplot()
-ggplot(densities, aes(x=Genotype, y=sc.sqrt.Pref, fill=Foodweb)) + geom_boxplot()
-
-summary(lm(Density_per_100_shoots ~ Foodweb, filter(densities, Density_per_100_shoots>0)))
-summary(lm(sqrt(Density_per_100_shoots) ~ Foodweb, filter(densities, Density_per_100_shoots>0)))
-car::Anova(lmer(sqrt(Density_per_100_shoots) ~ Foodweb + (1|Genotype), filter(densities, Density_per_100_shoots>0)), test="F")
-summary(lm(sc.sqrt.Pref ~ Foodweb, densities))
-
-with(densities, table(Foodweb, Density_per_100_shoots))
-
-ggplot(densities, aes(x=Density_per_100_shoots, fill=Foodweb)) + geom_density(alpha=0.5)
-ggplot(densities, aes(x=sqrt(Density_per_100_shoots), fill=Foodweb)) + geom_density(alpha=0.5)
-ggplot(densities, aes(x=sc.sqrt.Pref, fill=Foodweb)) + geom_density(alpha=0.5)
-
-shapiro.test(densities$Density_per_100_shoots)
-shapiro.test(sqrt(densities$Density_per_100_shoots))
-shapiro.test(log1p(densities$Density_per_100_shoots))
-
-clutches <- gall_selection.df %>%
-  distinct(Foodweb, Genotype, Plant_Position, sc.log.Clutch, gall_individuals)
-shapiro.test((clutches$gall_individuals))
-shapiro.test(sqrt(clutches$gall_individuals))
-shapiro.test(log(clutches$gall_individuals))
-
-shapiro.test((gall_selection.df$Gall_Height_mm))
-shapiro.test(sqrt(gall_selection.df$Gall_Height_mm))
-shapiro.test(log(gall_selection.df$Gall_Height_mm))
-```
-
-```{r Egg vs. Egg Bootstrap Model 1, include=FALSE, cache=TRUE, eval=FALSE}
-egg.egg_boot_model_1 <- bootMer(egg.egg_model_1, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-egg.egg_tidy_model_1 <- tidy(egg.egg_boot_model_1, conf.int=T) %>% 
-  # filter terms that only matter for this analysis
-  filter(term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
-                     "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref",
-                     "FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)",
-                     "FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.sqrt.Pref","FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref"))
-```
-
-There is no strong evidence that egg parasitism differs for nonlinear terms between complex and simple food webs. Although close perhaps for sc.Diam.
-
-```{r Egg vs. Egg Plot Effect of Food-web on Nonlinear Terms in Model 1, echo=FALSE, eval=FALSE, include=FALSE}
-knitr::kable(egg.egg_tidy_model_1)
-
-egg.egg_plot_model_1 <- egg.egg_tidy_model_1 %>%
-  mutate(Food_web = ifelse(grepl("FoodwebComplex", .$term)==TRUE,"Complex","Simple")) %>%
-  filter(Food_web == "Complex")
-
-egg.egg_plot_model_1$term_plot <- factor(egg.egg_plot_model_1$term,
-                                levels=c("FoodwebComplex:I(sc.Diam^2)","FoodwebComplex:I(sc.log.Clutch^2)","FoodwebComplex:I(sc.sqrt.Pref^2)","FoodwebComplex:sc.Diam:sc.log.Clutch","FoodwebComplex:sc.Diam:sc.sqrt.Pref","FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref"),
-                                ordered=TRUE)
-
-egg.egg_plot_model_1 %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=statistic), shape=21, size=3, fill="grey") +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(egg.egg_plot_model_1$term_plot))) +
-  ylab("Coefficient (logit scale)")
-
-visreg::visreg(egg.egg_model_1, xvar="sc.sqrt.Pref", by="Foodweb", scale = "response")
-```
-
-Now we assess their contribution to the effect of food-web treatment on the linear terms.
-
-```{r Fit Egg vs. egg Parasitoid Model 3, cache=TRUE, eval=FALSE, include=FALSE}
-egg.egg_model_3 <- update(model_3, data=egg.vs.egg_df) 
-```
-
-```{r Bootstrap Egg vs. egg Parasitoid Model 4, cache=TRUE, include=FALSE, eval=FALSE}
-boot_egg.egg_model_3 <- bootMer(egg.egg_model_3, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_egg.egg_model_3 <- tidy(egg.egg_model_3, conf.int=T) # boot_egg.egg_model_3
-```
-
-Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. egg Parasitoid Model 4, echo=FALSE, eval=FALSE, include=FALSE}
-egg.egg_plot_model_3 <- tidy_egg.egg_model_3 %>%
-  mutate(Food_web = ifelse(grepl("FoodwebComplex:", .$term)==TRUE,"Complex","Simple")) %>%
-  filter(Food_web == "Complex")
-
-egg.egg_plot_model_3$term_plot <- factor(egg.egg_plot_model_3$term,
-                                levels=c("FoodwebComplex:sc.Diam","FoodwebComplex:sc.log.Clutch","FoodwebComplex:sc.sqrt.Pref"),
-                                ordered=TRUE)
-
-egg.egg_plot_model_3 %>%
-  ggplot(., aes(x=term_plot)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=estimate), shape=21, size=3, fill="grey") + # y=statistic
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(egg.egg_plot_model_3$term_plot))) +
-  ylab("Coefficient (logit scale)")
-```
-
-```{r Fit Egg vs. egg Parasitoid adjusted Model 4, cache=TRUE, eval=FALSE, include=FALSE}
-egg.egg_model_4_adj <- update(model_4_adj, data=egg.vs.egg_df)
-```
-
-This reduced model returns the same qualitative result as before.
-Specifically, that the linear effect of clutch size depends on food-web treatment.
-Note also that egg survival is significantly higher in the simple food web compared to the complex food web (dotted line).
-These are the regression coefficients we will use when calculating directional selection gradients ($\beta$).
-
-```{r Bootstrap Egg vs. egg Parasitoid adjuted Model 4, cache=TRUE, include=FALSE, eval=FALSE}
-boot_egg.egg_model_4_adj <- bootMer(egg.egg_model_4_adj, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-
-tidy_egg.egg_model_4_adj <- tidy(boot_egg.egg_model_4_adj, conf.int=T) 
-```
-
-Here, we observe clear evidence of conflicting selection pressures on clutch size. This results in net zero selection gradient acting on clutch size in the complex food web.
-```{r Plot Egg vs. egg Parasitoid adjusted Model 4, echo=FALSE, eval=FALSE, include=FALSE}
-tidy_egg.egg_model_4_adj$term_ord <- factor(tidy_egg.egg_model_4_adj$term, 
-                                levels = c("(Intercept)","FoodwebSimple","sc.Diam","FoodwebSimple:sc.log.Clutch","FoodwebSimple:sc.log.Clutch","sc.sqrt.Pref"),
-                                ordered = TRUE)
-
-plot_egg.egg_model_4_adj <- tidy_egg.egg_model_4_adj %>%
-  filter(term != "(Intercept)") %>%
-  droplevels()
-
-plot_egg.egg_model_4_adj %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=conf.low, ymax=conf.high)) +
-  geom_point(aes(y=statistic), size=3, shape=21, fill="grey") +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(plot_egg.egg_model_4_adj$term_ord))) +
-  ylab("Coefficient (logit scale)")
-```
-
-## CALCULATE SELECTION GRADIENTS FOR EGG VS. egg PARASITOIDS
-
-```{r Organize and Transform egg vs. egg parasitoid Coefficients, include=FALSE, eval=FALSE}
-tidy_egg.egg_coefs <- bind_rows(
-  select(tidy_egg.egg_model_2_adj, term, estimate, conf.low, conf.high), 
-  select(tidy_egg.egg_model_4_adj, term, estimate=statistic, conf.low, conf.high)) %>%
-  filter(term != "(Intercept)", term != "FoodwebLarval") # remove main effects
-
-# Tidy common coefficients
-tidy_egg.egg_common_coefs <- tidy_egg.egg_coefs %>%
-  filter(term!="FoodwebEgg:I(sc.sqrt.Pref^2)", term!="Foodwebegg:I(sc.sqrt.Pref^2)",
-         term!="FoodwebEgg:sc.log.Clutch",term!="FoodwebLarval:sc.log.Clutch")
-
-# Tidy unique coefficients to each food-web
-egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:I(sc.sqrt.Pref^2)")
-egg_quad_pref$term <- "I(sc.sqrt.Pref^2)"
-egg_quad_pref <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:I(sc.sqrt.Pref^2)")
-egg_quad_pref$term <- "I(sc.sqrt.Pref^2)"
-
-egg_clutch <- filter(tidy_egg.egg_coefs, term %in% "FoodwebEgg:sc.log.Clutch")
-egg_clutch$term <- "sc.log.Clutch"
-egg_clutch <- filter(tidy_egg.egg_coefs, term %in% "FoodwebLarval:sc.log.Clutch")
-egg_clutch$term <- "sc.log.Clutch"
-```
-
-```{r Calculate Egg vs. egg parasitoid Selection Gradients, include=FALSE, eval=FALSE}
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-egg_predict <- predict(egg.egg_model_2, newdata=filter(egg.vs.egg_df, Foodweb=="egg"), type="response")
-egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
-egg_mean_fitness <- mean(egg_predict)
-
-egg_predict <- predict(egg.egg_model_2, newdata=filter(egg.vs.egg_df, Foodweb=="Egg"), type="response")
-egg_mean_brackets <- mean(egg_predict * (1 - egg_predict))
-egg_mean_fitness <- mean(egg_predict)
-
-# Double-check that using a different model (e.g.
-egg.egg_model_4) doesn't influence estimes of mean "brackets" and mean fitness.
-Using "Complex" food-web treatment as an example, but it doesn't matter
-alt_egg.egg_predict <- predict(egg.egg_model_4, newdata=filter(egg.vs.larval_df, Foodweb=="Larval"), type="response")
-alt_egg.larval_mean_brackets <- mean(alt_egg.larval_predict * (1 - alt_egg.larval_predict))
-alt_egg.larval_mean_fitness <- mean(alt_egg.larval_predict)
-test_egg.larval_mean_brackets <- larval_mean_brackets
-test_egg.larval_mean_fitness <- larval_mean_fitness
-test_egg.larval_mean_brackets - alt_egg.larval_mean_brackets # virtually the same
-test_egg.larval_mean_fitness - alt_egg.larval_mean_fitness # virtually the same
-
-tidy_egg_grads <- bind_rows(tidy_egg.larval_common_coefs, egg_quad_pref, egg_clutch) %>%
-  mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
-2008)
-  transmute(term=term,
-            gradient = egg_mean_brackets * estimate / egg_mean_fitness * Multiplier,
-            `2.5%` = egg_mean_brackets * conf.low / egg_mean_fitness * Multiplier,
-            `97.5%` = egg_mean_brackets * conf.high / egg_mean_fitness * Multiplier)
-
-tidy_larval_grads <- bind_rows(tidy_egg.larval_common_coefs, larval_quad_pref, larval_clutch) %>%
-    mutate(Multiplier = ifelse(grepl("\\^2", .$term)==TRUE, 2, 1)) %>% # double all quadratic gradients so they are on the same scale as other directional and correlational selection gradients (detailed explanation in Stinchcombe et al.
-2008)
-  transmute(term=term,
-            gradient = larval_mean_brackets * estimate / larval_mean_fitness * Multiplier,
-            `2.5%` = larval_mean_brackets * conf.low / larval_mean_fitness * Multiplier,
-            `97.5%` = larval_mean_brackets * conf.high / larval_mean_fitness * Multiplier)
-
-egg.larval_selection_gradients <- bind_rows(
-  mutate(tidy_egg_grads, `Food web`="Egg"),
-  mutate(tidy_larval_grads, `Food web`="Larval")) #%>%
-  #mutate(Type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic", ifelse(grepl(":", .$term)==TRUE, "Correlational", "Directional")))
-```
-
-```{r Table of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-egg.larval_selection_gradients$term_ord <- factor(egg.larval_selection_gradients$term, 
-                                   levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref","I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
-                                   labels=c("Diam","Clutch","Pref","Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"),
-                                   ordered = TRUE)
-
-egg.larval_selection_gradients_table <- egg.larval_selection_gradients %>%
-  transmute(Term=term_ord, Parasitoid=`Food web`, Gradient=round(gradient,2), `2.5%`=round(`2.5%`,2), `97.5%`=round(`97.5%`,2)) %>% 
-  arrange(Term)
-
-knitr::kable(egg.larval_selection_gradients_table, caption = "Table of Egg vs. Larval Parasitoid Selection Gradients")
-```
-
-```{r Plot of Egg vs. Egg Parasitoid Selection Gradients, echo=FALSE, eval=FALSE, include=FALSE}
-egg.larval_selection_gradients %>%
-  ggplot(., aes(x=term_ord)) +
-  geom_linerange(aes(ymin=`2.5%`, ymax=`97.5%`, color=`Food web`), position=position_dodge(width=0.3)) +
-  geom_point(aes(y=gradient, fill=`Food web`), color="black", shape=21, size=3, position=position_dodge(width=0.3)) +
-  coord_flip() +
-  geom_hline(yintercept=0, linetype="dotted") +
-  scale_x_discrete(name="", limits = rev(levels(egg.larval_selection_gradients$term_ord))) +
-  ylab("Selection Gradient") +
-  scale_fill_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) +
-  scale_color_manual(name="Parasitoid", values=treatment_colors[c(2,1)]) 
-```
--->

### 2019-01-11 analyses/reproduce_analyses.Rmd
testing as github_document

@@
 ---
-title: "Reproduce Analyses Reported in "Phenotypic evolution is more constrained in simpler food webs""
+title: "Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*"
 author: "Matthew A. Barbour"
@@
          egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
+         # transform and scale traits to approximate multivariate normal assumption
          sc.Diam = as.numeric(scale(Gall_Height_mm)), 
@@
 ## Bootstrap fitness estimates
-bootstrap_fitness <- function(logistic_model, #fixed_effects, 
-                              newdata, bootstraps, intervals=c(0.025,0.975)){
-  #model_matrix <- model.matrix(formula(fixed_effects), newdata)
+bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){
 
   # Absolute fitness
-  get_absolute_fitness <- function(.) predict(., newdata=newdata, type="response", re.form=~0) #inverse_logit(model_matrix %*% fixef(.))
+  get_absolute_fitness <- function(.) predict(., newdata=newdata, type="response", re.form=~0)
 
@@
   if(is.null(bootstraps) == FALSE){
+    set.seed(34) # make sure results are reproducible
     get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
@@
 
-## Predicting evolutionary dynamics 
-evolutionary_dynamics <- function (betas,    # one-column matrix of directional selection gradients
-                                   gammas,   # matrix of nonlinear selection gradients
-                                   G_0,      # initial G-matrix
-                                   z_0,      # one-column matrix of initial trait values
-                                   t) {       # evolutionary time steps 
-    # Equation 2 from Phillips and Arnold 1989, Evolution
-    G <- rep(list(G_0), t) 
-    for (i in 1:t) G[[i + 1]] <- {
-      G[[i]] + G[[i]] %*% (gammas - betas %*% t(betas)) %*% G[[i]] # may need to add mutation/recombination matrix (see Phillips and Arnold 1989)
-    }
-
-    # Equation 1 from Phillips and Arnold 1989, Evolution
-    z <- rep(list(z_0), t) 
-    for (i in 1:t) z[[i + 1]] <- {
-        z[[i]] + G[[i]] %*% betas
-    }
-    return(list(z=z,G=G))
-}
-
-## Number of evolutionary time steps for simulation
-n_evo_sims <- 200 # 1000
-
-## Tidy up evolutionary simulations
-tidy_evo_sims <- function(evo_sims) {
-  tidy_sim <- data.frame(matrix(unlist(evo_sims$z), ncol=3, byrow=T)) %>% 
-    transmute(Time=1:length(evo_sims$z), Diam=round(X1,2), Clutch=round(X2,2), Pref=round(X3,2)) %>%
-    filter(Diam < 1, Diam > -1, Clutch < 1, Clutch > -1, Pref < 1, Pref > -1)
-
-  return(tidy_sim)
-}
-
 ## Get confidence intervals from bootstrapped samples
@@
 
-## Color palette
+## Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
 
@@
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-
-visreg::visreg(linear_foodweb_model, xvar="sc.sqrt.Pref", by="Foodweb", scale="response")
 ```
@@
 We then fit a reduced model to estimate the bias in the logistic regression coefficient of chamber diameter in each food web.
-
-<!-- We quantified biased selection on chamber diameter in the following way.
-First, we focus on multi-chambered galls where there is evidence of both survival and parasitism.
-The idea is that galls from the same clutch should be similar in size; therefore, any selection on diameter would be apparent.
-If we assume that this is all due to the effect of parasitism on larval development, truncating gall diameter, then we can consider this new selection differential to be the result of confounding factors.
-Note that this method likely overestimates the confounding effect of parasitism, since we are assuming that any heterogeneity in chamber diameter (for this subset) is due to parasitism.
--->
 
@@
 
-# Reproduce Figure 2 of main manuscript
-
 We combine our estimates of selection gradients for each food-web treatment as well as the contribution of larval parasitoids to selection in the complex food web.
@@
 
-# Get legend
-#legend_foodwebegglarval_grads <- get_legend(plot_foodwebegglarval_directional_grads)
-
-# Format plots for manuscript
-#plot_foodwebegglarval_grads <- plot_grid(
-#  plot_foodwebegglarval_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
-#  plot_foodwebegglarval_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
-#  plot_foodwebegglarval_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
-#  nrow=2, align="hv", labels = "")
-#plot_legend_foodwebegglarval_grads <- ggdraw(plot_foodwebegglarval_grads) + draw_grob(legend_foodwebegglarval_grads, x = 0.7, y=-0.2)
-#y_title_foodwebegglarval_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
-
-#figure_foodwebegglarval_grads <- plot_grid(y_title_foodwebegglarval_grads, plot_legend_foodwebegglarval_grads, ncol=2, rel_widths = c(0.05,1)) 
-#figure_foodwebegglarval_grads
-
 # Alt format
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
- # geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  #geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  #geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
- # geom_text(data=filter(tidy_foodwebegglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-  #          aes(y=P_asterisk_foodwebegglarval_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
@@
 ```{r Egg vs. egg ptoid model, cache=TRUE}
-# excludes cases of larval-parasitism from Complex food web
-#eggegg_df <- #filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & ectos < 1) %>%
-  #mutate(gall_survival = ifelse(gall_survival==1,0,1)) # attempt to look at survival of egg parasitoid
 
@@
 biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
-
-visreg::visreg(eggegg_model, xvar="sc.sqrt.Pref", by="sc.Diam", scale="response", cond = list(Foodweb="Simple"))
-visreg::visreg(eggegg_model, xvar="sc.sqrt.Pref", by="sc.Diam", scale="response", cond = list(Foodweb="Complex"))
-visreg::visreg(eggegg_model, xvar="sc.Diam", by="sc.sqrt.Pref", scale="response", cond = list(Foodweb="Simple"))
-visreg::visreg(eggegg_model, xvar="sc.Diam", by="sc.sqrt.Pref", scale="response", cond = list(Foodweb="Complex"))
 ```
@@
 quadratic and correlation terms, I conducted a quick simulation.
-In the simulation, I assumed that if the larva survive, then the chamber diameter was the corrent one.
+In the simulation, I assumed that if the larva survive, then the chamber diameter was the correct one.
 However, if the larva did not survive, its size could be due to both its size and parasitism.
@@
 AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none"), 
-                                           #   axis.text.x = element_text(size=10),
-                                          #    axis.title.x = element_text(size=11)), 
                        AF_uni_Pref + theme(legend.position = "none", 
                                            axis.title.y = element_blank()) + xlab("Preference (SDs)"),
-                                           #axis.text.x = element_text(size=10),
-                                           #axis.title.x = element_text(size=11)),
                       AF_uni_Clutch + theme(legend.position = "none",
                                              axis.title.y = element_blank()), 
-                                            # axis.text.x = element_text(size=10),
-                                            # axis.title.x = element_text(size=11)),
-                    # legend_only + theme(legend.position = "none",                          
-                    #                         axis.title.y = element_blank(), 
-                    #                         axis.text.x = element_text(size=10),
-                    #                         axis.title.x = element_text(size=11)),
                        labels = "AUTO", nrow = 1, align='hv')
@@
 eggptoid_selection_plot
-save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6
+save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
 ```
@@
   spread(Foodweb, absolute_fitness) %>%
-  #filter(ID_group=="average") %>%
   mutate(fitness_difference = Complex-Simple)
@@
   ylab("Relative fitness") +
-  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + # "Food web"
+  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
@@
 # Get legend
-RF_uni_legend <- get_legend(RF_legend_only) #  + theme(legend.position = "top")
+RF_uni_legend <- get_legend(RF_legend_only)
 
 # Make plots
-RF_uni_plots <- plot_grid(RF_Diam_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
-                                             #axis.title.y = element_blank(), 
-                                             #axis.text.y = element_blank(),
+RF_uni_plots <- plot_grid(RF_Diam_legend_only + theme(legend.position = "none", 
                                              axis.text.x = element_text(size=10),
                                              axis.title.x = element_text(size=11)),
-                     RF_pref_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                     RF_pref_legend_only + theme(legend.position = "none",                          
                                              axis.title.y = element_blank(), 
-                                             #axis.text.y = element_blank(),
                                              axis.text.x = element_text(size=10),
                                              axis.title.x = element_text(size=11)),
-                     RF_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
+                     RF_legend_only + theme(legend.position = "none",                          
                                              axis.title.y = element_blank(), 
-                                             #axis.text.y = element_blank(),
                                              axis.text.x = element_text(size=10),
                                              axis.title.x = element_text(size=11)),
-                     #  labels = "AUTO", 
                      ncol = 3, align='hv')
@@
                              axis.text.x = element_blank()) +
-    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") + # mean(RF_Diam.Pref$absolute_fitness$average)
     geom_segment(data = gradients_Diam.Clutch, 
@@
                               axis.text.y = element_blank()) + xlab("Preference (SDs)") +
-    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
     geom_segment(data = gradients_Clutch.Pref, 
@@
   AF_plot_Diam.Pref + theme(legend.position = "none") + ylab("Preference (SDs)") +
-    #stat_contour(aes(z = average), breaks = breaks, linetype = "dotted", color = "black") +
     geom_segment(data = gradients_Diam.Pref, 

### 2019-01-11 manuscript.tex

@@
             colorlinks=true,
-            citecolor=blue,
+            citecolor=black,
             urlcolor=black,
@@
 %\usepackage{setspace}\doublespacing
-%\usepackage{float}
-%\let\origfigure\figure
-%\let\endorigfigure\endfigure
-%\renewenvironment{figure}[1][2] {
-%    \expandafter\origfigure\expandafter[H]
-%} {
-%    \endorigfigure
-%}
+\usepackage{float}
+\let\origfigure\figure
+\let\endorigfigure\endfigure
+\renewenvironment{figure}[1][2] {
+    \expandafter\origfigure\expandafter[H]
+} {
+    \endorigfigure
+}
 
@@
 framework for predicting how selection constrains phenotypic evolution,
-but often treat the community context of evolving populations as a
+but often treats the community context of evolving populations as a
 ``black box''. Here, we integrate ecological networks and adaptive
@@
 community context \citep{Bascompte2014, McCann2012}. Here, we integrate
-ecological networks and adaptive landscapes to understand how community
-context constrains evolutionary change \citep{Arnold1992}. Different
-aspects of evolutionary constraints can be inferred by quantifying the
-slope and curvature of the adaptive landscape. For example, the slope is
-determined by directional selection gradients acting on each phenotypic
-trait and influences the trajectory of evolutionary change
-\citep{Lande1979, Arnold1992}. Evolutionary trajectories become more
-constrained with an increase in the number of traits under selection, as
-this diminishes the number of optimal solutions \citep{Arnold2003}. The
-curvature of the adaptive landscape can also constrain evolution through
-its indirect effect on genetic constraints
-\citep{Arnold1992, Hansen2008}. Genetic constraints are largely governed
-by a population's \textbf{G}-matrix ---the additive genetic variances
-and covariances between traits \citep{Hansen2008}. In general, genetic
-constraints will increase with the number of traits under directional or
-stabilizing selection, as this will decrease the additive genetic
-variance in those traits \citep{Hansen2008}. Genetic constraints may
-also increase with the number of trait combinations under correlational
-selection, as this type of selection decreases the evolutionary
-independence of traits \citep{Hansen2008}. If we want to predict how
-community context constrains evolutionary change, we must understand how
-ecological networks shape the adaptive landscape.
+ecological networks and adaptive landscapes to understand how the
+community context constrains evolutionary change \citep{Arnold1992}.
+Different aspects of evolutionary constraints can be inferred by
+quantifying the slope and curvature of the adaptive landscape. For
+example, the slope is determined by directional selection gradients
+acting on each phenotypic trait and influences the trajectory of
+evolutionary change \citep{Lande1979, Arnold1992}. Evolutionary
+trajectories become more constrained with an increase in the number of
+traits under selection, as this diminishes the number of optimal
+solutions \citep{Arnold2003}. The curvature of the adaptive landscape
+can also constrain evolution through its indirect effect on genetic
+constraints \citep{Arnold1992, Hansen2008}. Genetic constraints are
+largely governed by a population's \textbf{G}-matrix ---the additive
+genetic variances and covariances between traits \citep{Hansen2008}. In
+general, genetic constraints will increase with the number of traits
+under directional or stabilizing selection, as this will decrease the
+additive genetic variance in those traits \citep{Hansen2008}. Genetic
+constraints may also increase with the number of trait combinations
+under correlational selection, as this type of selection decreases the
+evolutionary independence of traits \citep{Hansen2008}. If we want to
+predict how the community context constrains evolutionary change, we
+must understand how ecological networks shape the adaptive landscape.
 
@@
 would cancel each other out in more complex food webs. To examine these
-different possibilities (among others), we conducted a field experiment
-that manipulated the complexity of trophic interactions (hereafter
-food-web complexity) associated with an abundant insect herbivore
-(\emph{Iteomyia salicisverruca}; Family Cecidomyiidae)(fig.
-\ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped
-galls when they feed on the developing leaves of willow trees
-\citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect larva from
-attack by generalist predators (e.g.~ants, spiders), but they suffer
-high mortality from egg and larval parasitoids \citep{Barbour2016}. We
-manipulated food-web complexity by either excluding the guild of larval
-parasitoids (simple food web) or allowing both egg and larval
-parasitoids to impose selection on gall midge traits (complex food web;
-fig. \ref{fig:Conceptual}). We then applied modern statistical methods
-to quantify the effect of food-web complexity on the slope and curvature
-of the gall midge's adaptive landscape. Taken together, our study gives
+different possibilities, we conducted a field experiment that
+manipulated the complexity of trophic interactions (hereafter food-web
+complexity) associated with an abundant insect herbivore (\emph{Iteomyia
+salicisverruca}, Family Cecidomyiidae; fig. \ref{fig:Conceptual}). The
+larvae of this herbivore induce tooth-shaped galls when they feed on the
+developing leaves of willow trees \citep[\emph{Salix}
+sp.,][]{Russo2006}. These galls protect larva from attack by generalist
+predators (e.g.~ants, spiders), but they suffer high mortality from egg
+and larval parasitoids \citep{Barbour2016}. We manipulated food-web
+complexity by either excluding the guild of larval parasitoids (simple
+food web) or allowing both egg and larval parasitoids to impose
+selection on gall midge traits (complex food web; fig.
+\ref{fig:Conceptual}). We then applied modern statistical methods to
+quantify the effect of food-web complexity on the slope and curvature of
+the gall midge's adaptive landscape. Taken together, our study gives
 insight to how local extinctions, and concomitant decreases in food-web
 complexity, may constrain the evolution of interacting populations.
+
+\begin{figure}
+\centering
+\includegraphics{analyses/complex_simple_foodwebs_v2.jpeg}
+\caption{\label{fig:Conceptual}Experimental manipulation of food-web
+complexity associated with a leaf-galling midge (\emph{Iteomyia
+salicisverruca}) feeding on the willow \emph{Salix hookeriana}. Black
+arrows denote the flow of energy in this network of trophic
+interactions. In the complex food-web treatment, we allowed the full
+suite of egg and larval parasitoids to impose selection. In the simple
+food-web treatment, we used mesh bags to exclude the guild of larval
+parasitoids, only allowing the egg parasitoid (\emph{Platygaster} sp.)
+to impose selection. Larval parasitoids include the following species
+(from left to right): \emph{Mesopolobus} sp. (Family: Pteromalidae);
+\emph{Tetrastichus} sp. (Family: Eulophidae); and \emph{Torymus} sp.
+(Family: Torymidae).}
+\end{figure}
 
@@
 since it is simply the reflection of the lower triangle. The sign of
-diagonal terms of the curvature matrix dictate whether selection will
+diagonal terms of the curvature matrix dictates whether selection will
 increase (+), decrease (-), or cause no change (0) in the additive
@@
 
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\hline
+$\beta_{\text{Diam}}$ & 
+\textbf{
+0.34 [
+0.22,
+0.47] }& 
+\textbf{
+0.21 [
+0.13,
+0.3] }&
+
+-0.13 [
+-0.26,
+0.01] \\
+
+$\beta_{\text{Clutch}}$ & 
+0.06 [
+-0.04,
+0.17] & 
+\textbf{
+-0.09 [
+-0.18,
+-0.02] }& 
+\textbf{
+-0.15 [
+-0.29,
+-0.02] }\\
+
+$\beta_{\text{Pref}}$ &
+-0.12 [
+-0.29,
+0.05] & 
+\textbf{
+-0.16 [
+-0.25,
+-0.07] }&
+
+-0.04 [
+-0.22,
+0.14] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+0.14 [
+-0.06,
+0.32] &
+
+0.1 [
+-0.03,
+0.25] &
+
+-0.04 [
+-0.27,
+0.2] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ & 
+-0.05 [
+-0.25,
+0.16] &
+
+-0.12 [
+-0.27,
+0.03] &
+
+-0.06 [
+-0.33,
+0.19] \\
+
+$\gamma_{\text{Pref,Pref}}$ & 
+\textbf{
+0.33 [
+0.06,
+0.64] }&
+
+0.01 [
+-0.14,
+0.17] & 
+\textbf{
+-0.32 [
+-0.66,
+0] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ & 
+-0.05 [
+-0.17,
+0.08] &
+
+-0.07 [
+-0.15,
+0.02] &
+
+-0.02 [
+-0.16,
+0.13] \\
+
+$\gamma_{\text{Diam,Pref}}$ & 
+-0.13 [
+-0.28,
+0] &
+
+-0.02 [
+-0.09,
+0.06] &
+
+0.12 [
+-0.05,
+0.29] \\
+
+$\gamma_{\text{Clutch,Pref}}$ & 
+0.03 [
+-0.11,
+0.18] &
+
+0 [
+-0.07,
+0.07] &
+
+-0.03 [
+-0.19,
+0.12] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{analyses/UV_landscapes.pdf}
+\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
+phenotypes in complex vs.~simple food webs. Each panel corresponds to a
+different phenotypic trait: chamber diameter (A); oviposition preference
+(B); and clutch size (C). Bold lines represent selection experienced in
+complex (orange) and simple (blue) food webs. Thin lines represent
+bootstrapped replicates to show the uncertainty in selection. For
+clarity, we only display 100 bootstraps even though inferences are based
+on 1,000 replicates. Note that mean larval survival is plotted on a
+natural log scale to reflect the mathematical defintion of the adaptive
+landscape.}
+\end{figure}
+
 \subsection{Simpler food webs increase genetic
@@
 complex food web (fig. \ref{fig:MV_Landscape}).
+
+\begin{figure}
+\centering
+\includegraphics{analyses/MV_landscapes.pdf}
+\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
+landscapes of gall midge phenotypes in complex vs.~simple food webs.
+Each panel corresponds to a different combination of phenotypic traits:
+clutch size and chamber diameter (A); clutch size and oviposition
+preference (B); oviposition preference and chamber diameter (C). Arrows
+represent mean estimates of directional selection gradients, while
+contours represent predicted larval survival of the mean phenotype
+(i.e., all traits = 0) in each food-web treatment. Notice that arrows
+point more toward a corner of the adaptive landscape for each
+combination of traits in the simple vs.~complex food-web treatment. This
+indicates that trait integration (covariance) is more strongly favored
+in simpler vs.~more complex food webs. Note that mean larval survival is
+plotted on a natural log scale to reflect the mathematical definition of
+the adaptive landscape.}
+\end{figure}
 
@@
 
+\begin{figure}
+\centering
+\includegraphics{analyses/selection_on_Platygaster.pdf}
+\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
+parasitoids on the extended phenotype of egg parasitoids
+(\emph{Platygaster} sp.). The bold line represents the average
+difference in the probability of observing the egg parasitoid in complex
+vs.~simple food webs as a function of gall midge oviposition preference.
+Thin lines represent bootstrapped replicates to show the uncertainty in
+selection. For clarity, we only display 100 bootstraps even though
+inferences are based on 1,000 replicates. The decrease in the
+probability of observing egg parasitoids at high gall-midge densities
+indicate that larval parasitoids impose nonlinear selection on the
+extended phenotype of egg parasitoids.}
+\end{figure}
+
 \section{Discussion}\label{discussion}
 
-Our key finding was that phenotypic evolution in gall midges was more
-constrained in simpler food webs. More traits contributed to the slope
-of the adaptive landscape in the simpler food web, suggesting that the
-trajectory of phenotypic evolution is more constrained. Similarly, the
+We found that simpler food webs constrained phenotypic evolution in gall
+midges in two key ways. First, more traits contributed to the slope of
+the adaptive landscape in the simpler food web, suggesting greater
+constraints on the trajectory of phenotypic evolution. Second, the
 simple food-web treatment indirectly increased the number of genetic
@@
 \(\beta\) go to zero, then \(\Delta z\) is more influenced by the
-G-matrix. Interestingly, this corresponds to \citet{Schluter1996}`s
+G-matrix. Interestingly, this aligns with \citet{Schluter1996}`s
 hypothesis that phenotypic evolution often follows 'genetic lines of
@@
 
-There are a growing number of theoretical studies on adaptation to
+There is a growing number of theoretical studies on adaptation to
 directional environmental change that incorporate species interactions
@@
 
-\section{References}\label{references}
-
-\hypertarget{refs}{}
-
 \newpage
@@
 \section{Tables}\label{tables}
-
-\begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
-\label{Table:Gradients}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
-\hline
-$\beta_{\text{Diam}}$ & 
-\textbf{
-0.34 [
-0.22,
-0.47] }& 
-\textbf{
-0.21 [
-0.13,
-0.3] }&
-
--0.13 [
--0.26,
-0.01] \\
-
-$\beta_{\text{Clutch}}$ & 
-0.06 [
--0.04,
-0.17] & 
-\textbf{
--0.09 [
--0.18,
--0.02] }& 
-\textbf{
--0.15 [
--0.29,
--0.02] }\\
-
-$\beta_{\text{Pref}}$ &
--0.12 [
--0.29,
-0.05] & 
-\textbf{
--0.16 [
--0.25,
--0.07] }&
-
--0.04 [
--0.22,
-0.14] \\
-
-$\gamma_{\text{Diam,Diam}}$ &
-0.14 [
--0.06,
-0.32] &
-
-0.1 [
--0.03,
-0.25] &
-
--0.04 [
--0.27,
-0.2] \\
-
-$\gamma_{\text{Clutch,Clutch}}$ & 
--0.05 [
--0.25,
-0.16] &
-
--0.12 [
--0.27,
-0.03] &
-
--0.06 [
--0.33,
-0.19] \\
-
-$\gamma_{\text{Pref,Pref}}$ & 
-\textbf{
-0.33 [
-0.06,
-0.64] }&
-
-0.01 [
--0.14,
-0.17] & 
-\textbf{
--0.32 [
--0.66,
-0] }\\
-
-$\gamma_{\text{Diam,Clutch}}$ & 
--0.05 [
--0.17,
-0.08] &
-
--0.07 [
--0.15,
-0.02] &
-
--0.02 [
--0.16,
-0.13] \\
-
-$\gamma_{\text{Diam,Pref}}$ & 
--0.13 [
--0.28,
-0] &
-
--0.02 [
--0.09,
-0.06] &
-
-0.12 [
--0.05,
-0.29] \\
-
-$\gamma_{\text{Clutch,Pref}}$ & 
-0.03 [
--0.11,
-0.18] &
-
-0 [
--0.07,
-0.07] &
-
--0.03 [
--0.19,
-0.12] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
 
@@
 
-\begin{figure}
-\centering
-\includegraphics{analyses/complex_simple_foodwebs_v2.jpeg}
-\caption{\label{fig:Conceptual}Experimental manipulation of food-web
-complexity associated with a leaf-galling midge (\emph{Iteomyia
-salicisverruca}) feeding on the willow \emph{Salix hookeriana}. Black
-arrows denote the flow of energy in this network of trophic
-interactions. In the complex food-web treatment, we allowed the full
-suite of egg and larval parasitoids to impose selection. In the simple
-food-web treatment, we used mesh bags to exclude the guild of larval
-parasitoids, only allowing the egg parasitoid (\emph{Platygaster} sp.)
-to impose selection. Larval parasitoids include the following species
-(from left to right): \emph{Mesopolobus} sp. (Family: Pteromalidae);
-\emph{Tetrastichus} sp. (Family: Eulophidae); and \emph{Torymus} sp.
-(Family: Torymidae).}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{analyses/UV_landscapes.pdf}
-\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
-phenotypes in complex vs.~simple food webs. Each panel corresponds to a
-different phenotypic trait: chamber diameter (A); oviposition preference
-(B); and clutch size (C). Solid lines represent selection experienced in
-complex (orange) and simple (blue) food webs. Transparent lines
-represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are
-based on 1,000 replicates. Note that mean larval survival is plotted on
-a natural log scale to reflect the mathematical defintion of the
-adaptive landscape.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{analyses/MV_landscapes.pdf}
-\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
-landscapes of gall midge phenotypes in complex vs.~simple food webs.
-Each panel corresponds to a different combination of phenotypic traits:
-clutch size and chamber diameter (A); clutch size and oviposition
-preference (B); oviposition preference and chamber diameter (C). Arrows
-represent mean estimates of directional selection gradients, while
-contours represent predicted larval survival of the mean phenotype
-(i.e., all traits = 0) in each food-web treatment. Notice that arrows
-point more toward a corner of the adaptive landscape for each
-combination of traits in the simple vs.~complex food-web treatment. This
-indicates that trait integration (covariance) is more strongly favored
-in simpler vs.~more complex food webs. Note that mean larval survival is
-plotted on a natural log scale to reflect the mathematical definition of
-the adaptive landscape.}
-\end{figure}
-
-\begin{figure}
-\centering
-\includegraphics{analyses/selection_on_Platygaster.pdf}
-\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
-parasitoids on the extended phenotype of egg parasitoids
-(\emph{Platygaster} sp.). The solid line represents the average
-difference in the probability of observing the egg parasitoid in complex
-vs.~simple food webs as a function of gall midge oviposition preference.
-Transparent lines represent bootstrapped replicates to show the
-uncertainty in selection. For clarity, we only display 100 bootstraps
-even though inferences are based on 1,000 replicates. The decrease in
-the probability of observing egg parasitoids at high gall-midge
-densities indicate that larval parasitoids impose nonlinear selection on
-the extended phenotype of egg parasitoids.}
-\end{figure}
-
 \bibliography{references}

### 2019-01-11 manuscript.Rmd
remove alternative titles

@@
 title: Phenotypic evolution is more constrained in simpler food webs
-#  | Food-web complexity simplifies the adaptive landscape of an insect herbivore
-#  | Phenotypic evolution is less constrained in complex food webs
-#  | 
-#  | Food-web simplification constrains phenotypic evolution
-#  | Food-web complexity smooths the adaptive landscape of an insect herbivore
 author: 
@@
 - Jordi Bascompte$^{2}$
-# potentially use for 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348 for cross-format compatibility, with | to create new sections.
+# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
 #date: | 

### 2019-01-11 manuscript.Rmd
tidy YAML header.

@@
 bibliography: references
-#references.bib
-#csl: the-american-naturalist.csl
 biblio-style: amnat
-#amnat.bst
 fontsize: 11pt

### 2019-01-11 manuscript.Rmd
adjust affiliation order and manuscript elements.

@@
 - Christopher J. Greyson-Gaito$^{1,3}$ 
-- Arezoo Sootodeh$^{3}$ 
+- Arezoo Sootodeh$^{2}$ 
 - Brendan Locke$^{4}$ 
-- Jordi Bascompte$^{2}$
+- Jordi Bascompte$^{1}$
 # for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
@@
 
-\noindent 1. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada; <!-- consider removing -->
-
-\noindent 2. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;
+\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;
+
+\noindent 2. University of British Columbia, Department of Zoology, Vancouver, BC V6T 1Z4, Canada;
 
@@
 
-*Manuscript elements*: Figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
+*Manuscript elements*: Table 1, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
 

### 2019-01-11 manuscript.Rmd
paired down number of keywords
adj affiliation for Chris and add dynamic word count of MS

@@
 - Matthew A. Barbour$^{1,2,\ast}$
-- Christopher J. Greyson-Gaito$^{1,3}$ 
+- Christopher J. Greyson-Gaito$^{2,3}$ 
 - Arezoo Sootodeh$^{2}$ 
@@
 
-*Keywords*: fitness landscape, host-parasitoid, natural selection, G-matrix, community context, ecological networks, evolutionary ecology, eco-evolutionary dynamics.
+*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid.
+
+\bigskip
+
+*Number of words*: `r wordcountaddin::word_count("manuscript.Rmd")`
 

### 2019-01-11 manuscript.Rmd
comment out identifying info in author affiliations and acknowledgements.

@@
 
-\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;
+<!-- Remove author info for double-blind peer review
+\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, 8057 Zurich, Switzerland;
 
@@
 \bigskip
+-->
 
@@
 
+<!-- Remove for double-blind peer review process
 # Acknowledgements
@@
 Bascompte).
+-->
 

### 2019-01-11 manuscript.Rmd
remove old figure legends section

@@
 \end{table}
-
-\newpage 
-<!--
-# Figure Legends
-
-**Figure \ref{fig:Conceptual}**: Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
-In the complex food-web treatment (A), we allowed the full suite of egg (blue rectangle) and larval (yellow rectangle) parasitoids to impose selection.
-In the simple food-web treatment (B), we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
-Black arrows denote the flow of energy in this network of trophic interactions.
-Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
-(Family: Pteromalidae); *Tetrastichus* sp.
-(Family: Eulophidae); and *Torymus* sp.
-(Family: Torymidae).
-
-**Figure \ref{fig:UV_Landscape}**: Adaptive landscape of gall midge phenotypes in complex vs.
-simple food webs.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Solid lines represent selection experienced in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Solid yellow lines represent selection imposed by larval parasitoids in the complex food web.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
-
-**Figure \ref{fig:MV_Landscape}**: Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Note the flat landscape in mean larval survival for clutch size and oviposition preference in more complex food webs, whereas all three traits shape the adaptive landscape in simpler food webs.
-This indicates that selection favors trait integration for each combination of traits in simpler food webs, whereas there is no strong evidence for trait integration in more complex food webs.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape.
-
-**Figure \ref{fig:EggPtoid_Selection}**: Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
-The solid line represents the average difference in the probability of observing the egg parasitoid in complex vs.
-simple food webs as a function of gall midge oviposition preference.
-Transparent lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-The decrease in the probability of observing egg parasitoids at high gall-midge densities indicates the increasing impact of larval parasitoids.
--->

### 2019-01-11 manuscript.Rmd
remove old attempt to place references before figs and tables
remove old drafts of text from discussion

@@
 
-<!--
-Summary of key results
-
-Gall midges experience more selective and constraints in simple food webs.
--->
-<!--More phenotypic traits experienced directional selection in the simple food-web treatment, suggesting that the trajectory of phenotypic evolution is more constrained.-->
-
-<!--, because the egg parasitoids that attack larva on high density trees have a higher chance of surviving.-->
-
-<!--In the context of global change, our results imply that the simplification of ecological communities may actually reduce the predictability of phenotypic evolution of remaining populations.
-This is because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.-->
-
-<!-- what should the focus be? 
-Conceptually, I don't think it'll be that interesting to try and review past studies.
-
-I think it would be more interesting to discuss the implications of our results and there generality. In other words, under what conditions do we expect them to hold. When will they break down?
-
-Highlight that we could gain more predictive power from theoretical models that also examine how selection modifies selection pressures of consumers.
-i.e.
-we need models of ecological character displacement that go beyoned pairwise interactions.
-In some communities, intraguild predation will be common so we also need models that examine how the community context shapes the evolution of trophic levels and the resulting feedbacks on associated communities (cite JP's Frontiers in Ecology and Evolution MS).
-
-Such indirect effects may be quite common when moving from complex to simple communities, and highlights the fact that species evolve in a community context.<!-- and the release of selection pressures may have rippling effects.-->  <!--If indirect evolutionary effects are common [@Walsh2013], then predicting the evolutionary trajectories of remaining populations after local extinctions will not only require knowledge of these indirect effects, but also require knowledge on the order of local extinctions.
-
-It is well known that increases in consumer diversity can driver character divergence in foraging traits due to ecological character displacment [@Schluter2000].
-In this case, we would expect the local extinction of a consumer to
-- Ecology example: selection on gall size in Eurosta
-- Evolution example: ecological character displacement tends to drive divergence.
--->
-
-<!--
-Detailed case studies of natural selection on a single trait in a community context highlight the potential generality of our results.
-For example, galls induced by the fly *Eurosta solidaginis* experience directional selection for larger sizes by parasitoids (as we observed in our study), but selection for smaller sizes by birds [@Weis1985; @Abrahamson1997; @Start2016].
-Therefore, the dynamics of natural selection on gall size depend on the relative abundance of these consumers.
-A recent study in this system demonstrated that the loss of birds across a gradient of urbanization caused a shift from neutral to directional selection on gall size [@Start2018].
-This observational study supports our experimental demonstration that the loss of consumer diversity increases selective constraints.
-
-In a different system, the direction of selection on swimming speed in *Enallagama* damselflies depends on whether they occur in fish or fishless lakes [@McPeek1996; @McPeek1997].
-Lakes with fish select for damselflies , whereas dragonflies become the top predator in fishless lakes and select for adaptations to increase swimming speed.
-
-fish and dragonflies impose opposite directional selection on swimming speed in *Enallagma* damselflies . This has resulted in
-
-Lakes with fish likely have a much more diverse community of damselfly predators (multiple fish species and some smaller dragonfly species),
-
-Our study focused on an experimental manipulation of a focused community of consumers, leaving an open question to how our results generalize to more diverse consumer communities.
-
--->
-<!--
-The generality of our results depends on the extent to which different consumer species are functionally different and their relative abundance.
-In the simplest case, when consumers do not differ from each other (i.e.
-neutral communities), then we do not expect changes in food-web complexity to modify selective constraints.
-Also, many consumer species may be at too low of abundances --><!--This may be the case with many consumers in diverse communities, where their abundances are simply not high enough --><!-- to impose selection on the mean trait values of resource populations.
-Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
-For abundant species though, the effect of food-web complexity depends on whether different species impose selection on different trait values vs.
-distinct traits.
-
-Current theory on character displacement suggests that consumers will usually diverge in foraging traits when foraging on a biological resource.
-On one end, theory should be extended beyond two consumers to examine trait dynamics in more diverse consumer communities.
-On the other hand, we also need to examine selection in the resources themselves.
--->
-<!--
-Actually, different predator species impose selection on different axes of trait variation. 
-For example, habitat shifts into lakes where dragonflies are the top predator (instead of fish) promote adaptations for increased swimming speed in multiple lineages of *Enallagma* damselflies [@McPeek1996].
-Phenotypic selection study with damselflies [@McPeek1997].
-Biochemical evolution study with damselflies [@McPeek1999], still related to swimming speed.
-In McPeek's study though, there aren't dragonflies in lakes with fish?
-
-Lakes with fish are the ancestral state, and they move to fishless lakes.
-Although the fishless lakes may have simpler communities, we see a clear effect of the dominance hierarchy which highlights the importance of abundance.
-In this case, we have a strong intraguild predator that reduces the density of intraguild prey (dragonfly larvae), thus reducing their selection pressures.
-This indicates that its' not simply the presence/absence of different predators, but the evenness of these selection pressures.
--->
-<!--
-Maybe they break down with plant-herbivore interactions? Or maybe these provide a useful example for thinking about when they'll break down or for highlighting indirect effects on genetic constraints?
-
-We suggest that being able to predict how changes in community context shape evolutionary constraints requires a deep understanding of the ecological and evolutionary feedbacks that shape trait variation and community structure.
-
-Here, we focus on how changes in food-web complexity affects evolutionary constraints on a single resource population. However, predicting h
-
-Predicting how evolution occurs in a community context thus requires an explicit examination of the eco-evolutionary feedbacks that propogate through the networks.
-The textbook example of such a feedback in structuring communities is ecological character displacement, "the process of phenotypic evolution in a species generated or maintained by resource competition with one or more coexisting species" [@Schluter2000].
-In scenarios, that promote character divergence in consumers, we would expect those consumers to impose selection on different axes of trait variation (although typically, a resource spectrum is used), resulting in more neutral selection on traits compared to a community with only one consumer.
-The character displacement framework would provide a useful starting point for theoretical studies that explore feedbacks between evolutiona and ecology in a community context [@McPeek2017].
-Importantly though, our results suggest that it would be useful in exploring multiple traits.
-In other words, we need to be able to predict not just how diversity itself affects phenotypic evolution of resources, but also of consumers.
-The body of research on character displacement provides a useful starting point, as there have been extensive examinations of how community context shapes phenotypic evolution of competing consumers [Abrams work, Taper and Case's work].
-Still, much of this work has focused on pairwise competitive interactions, with little exploration of the direct and indirect effects that may occurs in competitive communities [@Levine2017].
--->
-<!--
-rather than how the complexity of interactions itself shapes the adaptive landscape, although a careful review of these studies can give valuable insights.
-For example, we found that fewer traits were under selection in complex vs.
-simple communities.
-In cases whether natural enemies impose selection on different axes of trait variation, we would expect complex communities to neutralize selective pressures.
-Recent work of pollinator communities [@Sahli2011; @terHorst2015; @Schiestl2018] has similarly shown a tendency for more traits to experience directional selection in simpler vs.
-more complex pollinator communities.
-
-@Stinchcombe2001 found that there was selection for increased deer resistance only in the presence of insects rather than their absence.
-
-For example, @Juenger1998 found that flies and caterpillars imposed the strongest reduction in plant fitness in isolation, but these effects were minimized when they were together, highlight a nonadditive interactions that result in neutral selection on flower time when both were present (unclipped treatment)
-
-However, @Lankau2007 only observed selection on chemical concentration of *Brassica* when both herbivores were present, but only when there was a heterospecif neighbor.
-In contrast, in the presence of conspecifics, then aphids and mollusks imposed contrasting selection pressures, resulting in no net selection.
-These different responses appear to be due to differences in diet breadth of mollusks and aphids.
-
-Schiestel et al.
-Evolution 2018: In the generalized treatment, only 1 axis of trait variation had a nonzero selection gradient.
-In the bumblebee only, there were 2-5 trait axes (depending whether you count marginal significance), in the hoverfly, there was only 1 trait axis.
-Interestingly, pollinator network complexity appears to dampen the selection gradients imposed by the most efficient pollinator (bumblebee), so I would say the interpretation is consistent.
-Here there appear to be some non-additive selection pressures at play.
-[greenhouse study with experimental manipulation of community]
-
-in terHorst 2010 Am.
-Nat, they also observed that increasing complexity often cancelled out the selection pressures shown by each species in isolation (e.g.
-cell area and population growth, or cell speed), although here, there appears to be non-additive selection pressures at play.
-Indeed, the indirect effects often result in little net evolution of multiple traits in multispecies populations that experienced both direct and indirect effects.
-(so it is tough to say for my experiment what might happen if we remove the parasitoids altogether...)[lab study with protist microcosms]
-
-Walsh's Rivulus work (Walsh and Reznick, 2008 and 2010) as well as Start's work is more of an indirect effect due to a specific selection pressure (predator then resources, and for Start's a herbivore competitor).[start was a field experiment, Walsh's work took advantage of evolved pops in different contexts, also manipulated food availability to tease apart direct vs.
-indirect eco-evo effects].
-
-There is also a study by Lau 2012 in Oecologia, but it's hard to follow.
-[field study with experimental manipulation of community].
-Actually, the reanalysis by terHorst et al.
-2015 suggests that selection for resistance follows the observed pattern (dampened selection in more complex community).
-
-Again for Sahli and Conner (2011 in Evolution), in the presence of all three pollinators, we lacked selection on Exsertion and Dimorphism. This evidence is quite compelling and interesting...
-
-Studies like Wise and Rausher show wide spread evidence for diffuse coevolution, but not through community members altering selection pressures, but via genetic covariances in resistance to herbivore species.
-They argue that diffuse interactions had an overwhelmingly constraining rather than facilitat effect, which may well be the case with a lot of covariances.
-[fiel study, no experimental manipulation of community]
-
-Lankau and Strauss 2007: (community complexity drives patterns of natural selection on a chemical defense of brassica nigra).
-
-Mauricio and Rausher 1997 Evolution did a field study where they sprayed the field and looked at selection.
-Interestingly, they only observed stabilizing selection (i.e.
-indirect genetic constraints) on glucosinolate concentration in the simply food web, but in general the selection pressures were quite similar...somthing funky with their analyses?
-Perhaps though this is again the argument of measuring selection in a "disturbed" community...
--->
-
-<!--How does my study improve or differ from these? Perhaps the focus on 
-<!-- 
-Natural history and comparison to other studies of natural selection in galling insects.
-
-Important Studies for Comparison: @Abrahamson1997; @Weis1983; @Heath2018; Start, Weis, and Gilbert In Press Am.
-Nat; @Start2016; @Start2018urbanization; Peter Price's work; Timothy Craig's work; Cheryl Briggs work.
-
-Topics to discuss: Persistent pattern in selection for larger galls; Contrasting effects of egg and larval parasitoids on clutch size; Nonlinear selection at high gall densities is likely reflective of the poorer searching ability of larval vs.
-egg parasitoids (and thus it saturates more quickly).
--->
-
-<!--
-Our finding that phenotypic evolution was more constrained in simpler food webs corresponds to the natural history of this system.
-Simpler food webs selected for gall midges with smaller clutch sizes and ovipositing on trees with low densities of conspecifics, which was likely due to the increased apparency of large clutches and trees with high densities to egg parasitoids searching for hosts.
-This is because herbivore oviposition can induce plant volatiles that attract egg parasitoids [reviewed in @Hilker2006], and the concentration of these volatiles may increase with the number of eggs that herbivores oviposit.
-In contrast, clutch size and oviposition preference did not experience directional selection in more complex food webs, which appeared to be a result of conflicting selection pressures.
-The absence of selection on clutch size
-
-Interestingly, we still observed selection for larger chamber diameters in the simple food web despite the fact that egg parasitoids attack before the gall is formed.
-This suggests that selection imposed by egg parasitoids on chamber diameter is likely due to selection with a correlated trait (e.g.
-ability to encapsulate parasitoid eggs).
-
-This particular gall-parasitoid community has only been studied one other time [@Barbour2016].
-But a persistent pattern seen in others work is that parasitoids generally impose selection for larger galls [@Abrahamson1997; @Heath2018; @Start2016; @Start2018urbanization].
-In many cases, there may be functional or development constraints acting on gall size that constrains phenotypic evolution.
-It is curious though that we still observed directional selection for larger chamber diameters in the simpler food web.
-This is because egg parasitoids attack before the gall is formed.
-Thus, the apparent selection on chamber diameter is likely due to selection with a correlated trait (e.g.
-ability to encapsulate endoparasitoid eggs).
-In terms of clutch size, we likely observe conflicting selection pressures for the following reason.
-First, egg parasitoids reduce the probability of larval survival in higher clutch sizes, because they cue in more to the local density when foraging.
-Indeed oviposition itself can induce plant volatiles that influence egg parasitoid foraging behavior [reviewed in @Hilker2006].
-In contrast, clutch sizes can increase the probability of larval survival in the face of larval parasitoids by creating more of a refuge from parasitoids that have to oviposit through the gall tissue.
-Similar patterns in larval parasitoids has been observed for other a related gall midge species [@Weis1982].
-Alternatively, in another gall midge, the same reduction in percent parasitism has been shown [@Weis1983].
-This previous work did not explore a relationship with the egg parasitoid Platygaster because it was too low in abundance, which is in contrast to our community where this species is the dominant parasitoid.
-Counterintuitively, this may not be due to a greater refuge, but simple a result of the parasitoids using a fixed-time strategy to search for hosts.
-Thus, parasitoids actually have a lower success attacking small galls, but a good chance of attacking one host in large galls and then just moving on to the next.
-In regard to oviposition preference, our results correspond to biological differences between egg and larval parasitoids.
-For example, egg parasitoids, such as Platygaster are known to be efficient foragers, whereas larval parasitoids are less efficient.
-This may create a pattern where larval parasitoid attack saturates more quickly at high host densities, as we observed here.
-The fact that Platygaster attack rates increased with host density suggest that host densities were relatively low, so we actually may be in the lower part of a type 3 functional response.
-
-A key question is whether our results would have changed if we had instead manipulated it so that only one of the larval parasitoid species could attack vs.
-the full complement.
-Based on the above biology, we may have expected two things.
-One we would may have seen no selection on oviposition preference in both food webs, since the larval parasitoid tends to have a nonlinear response that actually may enhance genetic variation in oviposition preference.
-However, we still would have seen selection reduced selection for clutch size, which would free this trait and covarying traits from selective constraints.
-Also, if we had just included one of the larval parasitoids, which were at lower densities, then the selection gradients would have been weaker simply due to the enhanced survival of gall midge larva.
-This highlights the importance of studies that manipulate community context in not only looking at the effects on the trait-fitness relationships, but also the effects on average survival.
-This is especially true in experimental contexts, such as ours, where density of consumers were artificially low, and thus we are only observing a transient dynamic in the strength of selection.
-
-<!--
-Selective constraints:
-
-Key Result: More traits under directional selection in simple (3 of 3) vs.
-complex (1 of 3) food webs.
-Need to be wary of interpreting no selection on oviposition preference in complex food webs though.
-Even if there is selection on oviposition preference, this does not change our qualitative result.
-
-Implications: The trajectory of phenotypic evolution is less constrained in complex vs. simple food webs. In other words, there are more potential adaptive peaks in complex food webs. 
--->
-
- <!-- This insight also helps resolve the balance between neutral and adaptationist views of phenotypic evolution.
-In fact, the ability for neutral evolutionary theories to give insight to evolution may be due to the net neutral selection pressures in complex natural systems.
-However, this highlights that we will need further integration of these perspectives in the context of global change and concomittant changes in the selective environment.-->
-
-<!--    
-Indirect effects of selection on genetic constraints:
-
-Key Result: More traits experience a decrease in additive genetic variance and more trait combinations experience selection for trait integration in simple food webs.
-
-Implications: The structure of the G-matrix is under less influence of selection in complex vs.
-simple food webs.
-Thus the trajectory of phenotypic evolution may be dictated more by genetic rather than selective constraints.
-This is in line with empirical evidence (from complex natural systems) that evolution tends to proceed along genetic lines of least resistance [@Schluter1996].
--->
-
-<!--
-Indirect evolutionary effects:
-
-Key Result: Evidence of selection on the extended phenotype of egg parasitoids.
-
-Implications: Hints at a dynamic adaptive landscape and potential indirect evolutionary effects in complex food webs.
--->
-
-<!--response to local extinctions will
-
-Thus, our results hint that indirect evolutionary effects may be common, but latent, in complex communities, and thus local extinctions may trigger their apparent effects.
-
-Understanding these hidden selection pressures in complex communities is important; however, for predicting trajectories of evolutionary change, as they trajectory of evolution will depend on the order of local extinctions or changes in species abundances [Start et al.
-in press].
--->
-
-<!--
-Right now, most studies treat the selection gradients imposed by the adaptive landscape as static [but see @McPeek2017].
-Our results suggest though that we also observe indirect evolutionary effects (cite Start, Weis, and Gilbert's new Am Nat paper).
-This suggests the adaptive landscape itself may be a more dynamic entity in more complex food webs.
-Where these dynamics end up cancelling each other out in their net selective effects over time, or allow phenotypic evolution to change direction is currently unclear, and we need more empirical work on this front.
--->
-
-<!-- Community context in altering adaptation to environmental change
-
-Relevant review paragraph from @Osmond2017PredatorsHelpPrey about studies incorporating gradual, directional environmental change but also species interactions.
-
-There is a small but growing number of theoretical studies on adaptation to gradual, directional environmental change that incorporate interactions between species (de Mazancourt et al.
-2008; Johansson 2008; Jones 2008; Norberg et al.
-2012; Mellard et al.
-2015).
-Only two of these studies assessed predator-prey interactions.
-Jones (2008) used simulations to study, among other things, a predator-prey system where the predator trait evolves to match the prey trait and the prey trait evolves both to match the changing environmental optimum and escape the predator.
-His main finding was that predation can sometimes increase the persistence time of the prey, presumably when the predator removes prey that are maladapted to the abiotic environment.
-Mellard et al.
-(2015) studied an explicit resource-plant-herbivore trophic chain using a primarily numerical approach to ask how the addition of an herbivore affects plant persistence in a warming environment.
-They analytically clarified the conditions required for the predator to hasten prey evolution but found in simulations that, regardless of the effect on evolutionary rates, herbivory almost never aided plant persistence.
-In addition, Northfield and Ives (2013), who did not explicitly model a gradually changing environment, analytically demonstrated that conflicting interactions, such as predation, tended to dampen the direct effect of small environmental changes on the equilibrium densities of interacting species, potentially facilitating persistence.
-In their model, coevolution facilitates persistence through negative feedback loops.
-For example, as the predator nears extinction, the prey invests less in defense, making it easier for the predator to consume prey and rebound in abundance.
-Thus, up to this point, while it is clear that predators can theoretically help prey adapt in changing environments, the effect of predators on prey persistence remains unresolved.
-
--->
-<!--
-The role of community context and diversity in shaping communities has been explored theoretically in terms of competitive communities [@De_Mazancourt2008; @Johansson2008].
-Other work has also highlighted the role of competition in shaping evolutionary rescue [@Osmond2013].
-Other studies have also explored the role of predators in helping prey adaptive to environmental change [@Osmond2017PredatorsHelpPrey].
-This work has suggested that biodiversity may constrain phenotypic evolution, because more species occupy different niches, preventing the "movement" of species across the adaptive landscape into different ecological niches.
-This may be true for competitive communities, but in multitrophic communities our empirical results suggest the opposite.
-Still, in natural communities we are likely to see multiple interaction types that shape the survival of species.
-The role of different interaction types in shaping evolution in a community context remains both a theoretical and empirical frontier.
--->
-
-<!--
-Caveats:
-
-Key Caveat: Experimental artifact of lower larval survival in complex food-web treatment.
-
-Implications: Artificially increased the magnitude of selection in complex food webs.
-Note however, that this does not qualitatively change any of our results.
-In fact, we are actually underestimating the constraints imposed by our simple food-web treatment.
-This is because the egg parasitoids would be released from their intraguild predator, and thus could increase in abundance over future generations and impose stronger selection on gall midges.
--->
-<!--
-One of the things that our study did was artificially reduce the mortality induced by parasitoids, in general, in the simpler food web.
-Importantly though, this would actually make it more difficult to observed selection due to the fact that reductions in mean fitness, all else equal, intensify the strength of selection [@Hunter2018].
-Indeed, we are likely underestimating the constraints imposed by simpler food web, because over time, egg parasitoid abundances would increase, thus increasing selective constraints.
-
-<!-- Review past experimental studies of complexity -->
-<!--There are a growing number of experimental studies examining how the community context shapes the adaptive landscape [@Stinchcombe2001; @Juenger1998; @Lankau2007; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018].
-This body of work focused on testing the extent to which selection imposed by different species is additive or non-additive in a community context [@terHorst2015], a critical step for accurately predicting changes in the trajectory of phenotypic evolution.
-<!--Put another way, this work gives insight to the direct and indirect effects of selection pressures in a community context.
---><!--In contrast, we test how the community context shapes the range of possible evolutionary trajectories (i.e.
-constraints).
-We can re-examine the results of this prior work though to see the generality of our results.
-For example, recent greenhouse experiments with plant-pollinator interactions have shown a tendency for more traits to experience directional selection in simpler vs.
-more diverse pollinator communities [@Sahli2011; @terHorst2015; @Schiestl2018].
-Similarly, @Juenger1998 found that two insect herbviores <!--flies and caterpillars --><!--imposed the strongest reduction in plant fitness in isolation, but these effects were minimized when they were together <!--, highlight a nonadditive interactions that --><!--resulting in neutral selection on flowering time when both were present<!--(unclipped treatment)-->
-
-<!--Our results also suggest an insidious effect of local extinctions.
-Not only may it compromise community robustness and resilience to future change [@McCann2011], but it may also cause this at the population level.
-We are in urgent need of future empirical and theoretical work that understands these rippling effects on the robustness of populations and communities to environmental change.-->
-
 <!-- Remove for double-blind peer review process
@@
 -->
-
-<!-- <div id="references"></div> this code inserts references wherever you want rather than at the end of the document -->
-
-<!-- CONSIDER ITALICIZING RELATIONSHIPS WHERE 90% CI DOES NOT OVERLAP ZERO -->
 

### 2019-01-11 manuscript.Rmd
added Start, Weis, and Gilbert In Press and removed old beginning to intro.

@@
 <!--Summary-->
-<!-- Our key finding was that phenotypic evolution in gall midges was more constrained in simpler food webs.
-More traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting that the trajectory of phenotypic evolution is more constrained.
--->
 We found that simpler food webs constrained phenotypic evolution in gall midges in two key ways.
@@
 This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
-A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018]<!--; Start et al.
-in press-->.
+A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @StartInPress].
 If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the simplification of food webs will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.

### 2019-01-11 manuscript.Rmd
remove old draft of text from results

@@
 
-<!-- TRIPLE CHECK ALL RESULT OUTPUTS AND WRITTEN INTERPRETATIONS -->
-
 ## Simpler food webs increase selective constraints
@@
 
-<!-- CONSIDER AVOIDING EXTENDED PHENOTYPE AND FOCUS ON INDIRECT EFFECTS OR INDIRECT SELECTION -->
-
 Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\alpha_{\text{Pref}}$=
@@
 ```
-
-<!--
-(contrast $\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
-This indicates that larval parasitoids impose nonlinear selection on this extended phenotype of the egg parasitoid (fig.
-\ref{fig:EggPtoid_Selection}).
-Larval parasitoids also dampened the linear relationship between probability of observing egg parasitoids and gall midge preference , but this did not translate into an effect on directional selection
-(contrast $\beta_{\text{Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]).
-This was likely because there was a tendency (albeit not statistically signficant) for a higher probability of egg-parasitoid survival in the simple vs.
-complex food webs
-(contrast=`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$mean,2)` [
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
-Larval parasitoids did not alter directional, quadratic, or correlational selection on any other extended phenotypes of egg parasitoids (see Supplementary Material).
--->
-
-<!--
-## Slope of the adaptive landscape
-
-\indent We found that food-web complexity altered the slope of the adaptive landscape ($\beta$) in two key ways.
-First, there were fewer traits under directional selection in the complex (2 of 3) vs.
-simple food webs (3 of 3)(table \ref{Table:Gradients}).
-For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}).
-In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}).
-This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids (fig.
-\ref{fig:UV_Landscape}).
-Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`]).
-
-The second key effect of food-web complexity was to increase the strength of selection acting on chamber diameter. Directional selection on chamber diameter was 
-`r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean * 100),0)`% higher in complex vs.
-simple food webs (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}).
-This result was not due to any difference in the relationship between larval survival and chamber diameter (table \ref{Table:Coefs}), but was due to the fact that the average probability of larval survival decreased from
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean,2)` in the simple food web to
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean,2)` in the more complex one (contrast=
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean,2)*-1` 
-[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)*-1`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)*-1`]).
-Note that although the selection gradient is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, it can be rewritten as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$.
-This alternative expression makes clear that lower survival, and thus mean fitness, will always increase the strength of selection.
--->
-<!-- survival result written in terms of percent decrease `r #round(((filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean - filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean) / filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean * 100),0)*-1 # multiply by -1 to match written description`% lower in complex vs.
-simple food webs -->
-<!--
-## Curvature of the adaptive landscape
-
-Unlike the slope, the curvature of the adaptive landscape is influenced by directional, quadratic, and correlational selection gradients.
-Our food-web treatment did not alter correlational selection for any combination of traits, although there was evidence that correlational selection on chamber diameter and oviposition preference differed from zero in the complex food web (table \ref{Table:Gradients}; fig.
-\ref{fig:MV_Landscape}).
-Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}).
-In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
-Specifically, the negative relationship between oviposition preference and larval survival dampened at high densities in complex, but not simple food webs (fig.
-\ref{fig:UV_Landscape}).
-This dampened relationship was partly due to differences in selection imposed by larval parasitoids (contrast $\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
-
-To estimate the net effect of food-web complexity on the curvature ($C$) of the adaptive landscape, we only retained nonzero selection gradients (i.e.
-95\% CI did not overlap zero) before subtracting the matrix of directional selection gradients ($\beta \beta^\text{T}$) from the matrix of quadratic and correlational selection gradients ($\gamma$).
-We found that the curvatures of the adaptive landscape exhibited the following structures:
-
-$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
-
-$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
-`r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(complex_curvature["Clutch","Diam"],2)` & `r round(complex_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
-`r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(simple_curvature["Clutch","Diam"],2)` & `r round(simple_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-The structure of these matrices indicate that there are more selective constraints imposed on the gall midge in the simple (6 of 6) vs.
-complex (2 of 6) food web.
-Simple food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the complex food web.
-For genetic covariances, the simple food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
-\ref{fig:MV_Landscape}).
-In contrast, the complex food web only constrained genetic covariance by favoring integration between chamber diameter and oviposition preference (fig.
-\ref{fig:MV_Landscape}).
-
-## Indirect selection acting on egg parasitoids
-
-Larval parasitoids altered nonlinear selection acting on the egg parasitoid's extended phenotype of midge preference (contrast $\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
-This nonlinear selection was a result of a reduced probability of observing egg parasitoids at high midge densities in complex food webs (fig.
-\ref{fig:EggPtoid_Selection}).
-Larval parasitoids also dampened the linear relationship between egg parasitoids and the extended phenotype of midge preference (contrast $\alpha_{\text{Pref}}$=
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
-), but this did not translate into an effect on directional selection 
-(contrast $\beta_{\text{Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]).
-This was likely because there was a tendency (albeit not statistically signficant) for a higher probability of egg-parasitoid survival in the simple vs.
-complex food webs
-(contrast=`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$mean,2)` [
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
-Larval parasitoids did not alter directional, quadratic, or correlational selection on any other extended phenotypes (see Supplementary Material).
--->
 

### 2019-01-11 manuscript.Rmd
remove old draft of text from Methods

@@
 We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by parasitoids, we excluded unknown sources of mortality.<!--restricted our data to larvae that either survived to pupation or were parasitized by an egg or larval parasitoid.--> For the food-web treatment that excluded larval parasitoids (simple food web), we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
+Since we were interested in selection imposed by parasitoids, we excluded unknown sources of mortality.
+For the food-web treatment that excluded larval parasitoids (simple food web), we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
 This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
@@
 **Evolutionary constraints**: We quantified the effects of food-web complexity on evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
-<!--Adaptive landscape**: We took advantage of existing theory that translates estimates of selection gradients to the adaptive landscape [@Phillips1989; @Arnold2003].
-The shape of the adaptive landscape can be described by both its slope and curvature, each of which describe different aspects of constraints on phenotypic evolution.
-Specifically, -->The number of selective constraints is determined by the slope of the adaptive landscape<!-- corresponds to the column vector of directional selection gradients-->, which in our study corresponds to:
-
-<!-- need to make beta a bold symbol, may need to add a package -->
+The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
 
 $$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-<!--This slope describes the selective constraints acting on the trajectory of phenotypic evolution, which is governed by the 'Lande equation', $\Delta \bar z=\text{G}\beta$ [@Lande1979].
-Quantitative predictions of evolutionary trajectories require knowledge of a population's **G**-matrix; however, We quantified the degree to which phenotypic evolution was constrained by selection <!--can gain qualitative insight to evolutionary constraints by counting the number of phenotypic traits under directional selection [selective constraints, @Arnold1992].-->
 By comparing the number of traits that determine the slope (i.e., nonzero directional selection gradients) in simpler vs.
@@
 The indirect effects of selection on genetic constraints is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
-<!--The curvature (**C**) of the adaptive landscape is a matrix that is determined by directional, quadratic, and correlational selection gradients, such that \boldmath$\text{C}=\gamma - \beta \beta^\text{T}$, or more explicitly:-->
 
@@
 Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
-<!--This curvature matrix describes the indirect effects of selection on genetic constraints within a generation ($\Delta \text{G}=\text{G}(\gamma -\beta \beta^{\text{T}})\text{G}$).
-For example, -->The sign of diagonal terms of the curvature matrix dictates whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+The sign of diagonal terms of the curvature matrix dictates whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
 Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).

### 2019-01-11 manuscript.Rmd
remove old draft of text from Abstract and Intro

@@
 Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the community context of evolving populations as a ``black box''.
-<!--In contrast, ecological networks provide an explicit representation of the community context, yet often ignore the role of natural selection.-->Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
+Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
 We conducted a field experiment that manipulated the diversity of insect parasitoids (food-web complexity) that were able to impose selection on an insect herbivore.
@@
 More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory].
-Ecological interactions often play a key role in shaping adaptive landscapes, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.<!--, often play a key role in shaping the adaptive landscape and phenotypic evolution in multiple traits [; ;].
-For example, competition for shared prey in threespine stickleback has driven their adaptive divergence into ecotypes with specialized body and gill morphologies [@Schluter2000, other papers].
-Similarly, the elongated, red corollas of many flowering species have evolved in response to the efficient pollination of hummingbirds [cite].--> Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we do not know how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018]<!--SOFTEN THIS STATEMENT-->.
+Ecological interactions often play a key role in shaping adaptive landscapes, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.
+Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we do not know how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018]<!--SOFTEN THIS STATEMENT-->.
 Resolution on how the community context shapes phenotypic evolution is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].
 
-Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012]<!--SENTENCE SEEMS MISPLACED-->.
-<!--These networks describe the interdependency of populations within an ecological community, providing an effective framework for predicting how the strength and organization of ecological interactions (network structure) affect population and community dynamics [@Bascompte2014; @McCann2012].
-Nevertheless, these networks often lack quantitative information on how ecological interactions influence selection on phenotypic traits.
-Thus, it remains unclear how network structure shapes adaptive landscapes of interacting populations.
-This represents a major barrier in our current ability to predict how changes in community context will affect phenotypic evolution.--> Here, we integrate ecological networks and adaptive landscapes to understand how the community context constrains evolutionary change [@Arnold1992].
+Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012].
+Here, we integrate ecological networks and adaptive landscapes to understand how the community context constrains evolutionary change [@Arnold1992].
 Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape.
@@
 If we want to predict how the community context constrains evolutionary change, we must understand how ecological networks shape the adaptive landscape.
-<!-- need to cite more than just Hansen and Houle 2008 here -->
 
@@
 Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
-To examine these different possibilities, <!--To examine the effect of network structure on adaptive landscapes, -->we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
+To examine these different possibilities, we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
 \ref{fig:Conceptual}).
@@
 \ref{fig:Conceptual}).
-<!--Food-web complexity may influence the adaptive landscape in a number of ways.
-For example, if each parasitoid imposes directional selection on a different trait, then more complex food webs may constrain evolution by increasing the number of traits under selection.
-Alternatively, if parasitoids impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
-To examine these different possibilities (among others), -->We then applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
+We then applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
 Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, may constrain the evolution of interacting populations.
@@
 ```
-
-<!--
-Here, we integrate ecological networks and the adaptive landscape to understand how changes in network structure affect the dynamics of natural selection.
-In particular, we are interested in how network structure constrains or enables phenotypic evolution [@Arnold1992].
-We can gain insight to the selective constraints imposed by network structure by examining its effect on the slope and curvature of the adaptive landscape.
-To illustrate this, let us examine the adaptive landscape of two hypothetical traits, $z_i$ and $z_j$.
-The slope of the adaptive landscape is described by a column vector of directional selection gradients acting on these traits (cite):
-
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{z_i} \\ \beta_{z_j} \end{pmatrix} $$
-
-If each phenotypic trait experiences directional selection ($\beta_{z_i},\beta_{z_j}\neq0$), then this implies that there is an optimal phenotype (adaptive peak) and thus strong constraints on the trajectory of evolution.
-In contrast, if selection is absent on a trait (say $\beta_{z_i}=0$), then there may be multiple peaks (a line across all possible $z_i$ in this example) where fitness is equivalent and thus weaker selective constraints [@Arnold1992].
-The curvature of the adaptive landscape may also constrain phenotypic evolution through its indirect effect on genetic constraints [@Arnold1992].
-Genetic constraints on phenotypic evolution are largely governed by a population's **G**-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
-For our hypothetical example, the **G**-matrix takes the form:
-
-$$\text{G} = \begin{pmatrix} V_{z_i:z_i} & \\ V_{z_i:z_j} & V_{z_j:z_j} \end{pmatrix} $$
-
-where $V_{z_i:z_i}$ is the additive genetic variance in $z_i$ and $V_{z_i:z_j}$ is the additive genetic covariance between $z_i$ and $z_j$.
-Changes in the **G**-matrix within a generation are governed by the following equation [cite]:
-
-$$\Delta \text{G}=\text{G}(\gamma-\beta \beta^{\text{T}})\text{G}$$
-where $\gamma$ corresponds to the matrix of quadratic ($\gamma_{z_i:z_i}$) and correlational ($\gamma_{z_i:z_j}$) selection gradients.
-The terms in parentheses in the above equation describe the curvature (C) of the adaptive landscape, or the effects of nonlinear selection.
-To make explicit how landscape curvature affects the **G**-matrix, we rewrite the curvature matrix as:
-
-$$\text{C}= \begin{pmatrix} \gamma_{z_i:z_i} & \\ \gamma_{z_i:z_j} & \gamma_{z_j:z_j} \end{pmatrix} - \begin{pmatrix} \beta_{z_i}\beta_{z_i} & \\ \beta_{z_i}\beta_{z_j} & \beta_{z_j}\beta_{z_j} \end{pmatrix} $$
-$$\text{C} = \begin{pmatrix} C_{z_i:z_i} & \\ C_{z_i:z_j} & C_{z_j:z_j} \end{pmatrix}$$
-The diagonal terms of this curvature matrix describe how selection changes the additive genetic variance of traits ($V_{z_i:z_i}$).
-If selection acts to decrease the additive genetic variance, which is common when there is no disruptive selection ($\gamma_{z_i:z_i}>0$), then this will constrain the trait's evolutionary response to future selection [@Hansen2008].
-The off-diagonal terms of the curvature matrix are also important as they describe the change in additive genetic covariances between traits.
-Nonzero values along the off-diagonal indicate that selection favors trait integration, which may result in stronger genetic constraints [@Hansen2008].
-
-To examine how network structure shapes the adaptive landscape, we conducted a field experiment that manipulated the complexity of a food web associated with an abundant leaf-galling midge (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
-\ref{fig:Conceptual}).
-The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006].
-These galls protect larva from attack by generalist predators (e.g.
-ants, spiders), but they suffer a high degree of mortaltiy from four parasitoid wasps.
-To manipulate food-web complexity, we experimentally excluded the diversity of parasitoids that were able to impose selection on gall midge larvae (fig.
-\ref{fig:Conceptual}).
-
-Food-web complexity may shape the adaptive landscape, and thus selective constraints, in a number of ways.
-For example, if each consumer imposes directional selection on a different trait, then more complex food webs may increase the number of traits under selection, thereby increasing selective constraints.
-Alternatively, if consumers impose selection on different values of a trait, then their selective effects may cancel each other in more complex food webs, which would alleviate selective constraints.
-Food-web complexity may also indirectly affect genetic constraints.
-For example, if each consumer imposes selection on a different rare phenotype (i.e.
-each end of a trait distribution), then there would be stabilizing selection for an optimal phenotype, which would increase genetic constraints.
-Alternatively, if consumers are adapted to attacking the population's mean phenotype, then the relative fitness of rarer phenotypes would increase (disruptive selection), which would decrease genetic constraints.
-To tease apart these diverse possibilities, we applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
-Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, shape the adaptive landscape of interconnected populations.
--->
-
-<!-- Old last paragraph
-Here, we integrate ecological networks and the adaptive landscape to understand how changes in network structure affect the dynamics of natural selection.
-We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant leaf-galling midge (*Iteomyia salicisverruca*; Family Cecidomyiidae)(fig.
-\ref{fig:Conceptual}).
-The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006].
-Since these galls provide protection from generalist predators (e.g.
-ants, spiders), our experiment provides an effective manipulation of the diversity of trophic interactions, or food-web complexity, that this insect herbivore experiences.
-We then applied modern statistical methods to test how food-web complexity shapes the slope and curvature of the herbivore's adaptive landscape.
-Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, shape the adaptive landscape of interconnected populations.
--->
-
-<!-- Useful paragraph explaining the effect of increased mortality on strength of selection
-Also, unless consumers are equivalent, then we may generally expect lower average survival in complex food webs, which would increase the strength of selection.
-The logic behind this is made clear if we rewrite the selection gradient, which is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$ [@Hunter2018].
-This alternative expression makes clear that lower survival, and thus mean fitness, increases the strength of selection.
-Note that if consumers are equivalent in their selective effects (i.e.
-functionally redundant), then we would not expect any effect of food-web complexity on the adaptive landscape.
--->
 

### 2019-01-11 manuscript.Rmd
soften intro statement from saying "we do not know" to "we still have a poor understanding" in regard to the adaptive landscape and community context.

@@
 Ecological interactions often play a key role in shaping adaptive landscapes, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.
-Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we do not know how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018]<!--SOFTEN THIS STATEMENT-->.
+Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018].
 Resolution on how the community context shapes phenotypic evolution is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].

### 2019-01-11 manuscript.Rmd
remove old note about knitr::render()
finalized MS formatting

@@
 ---
-title: Phenotypic evolution is more constrained in simpler food webs
-author: 
-- Matthew A. Barbour$^{1,2,\ast}$
-- Christopher J. Greyson-Gaito$^{2,3}$ 
-- Arezoo Sootodeh$^{2}$ 
-- Brendan Locke$^{4}$ 
-- Jordi Bascompte$^{1}$
+# Decided to manually format the title page because I had greater control. Note that you should use put this info in the YAML header for compatability across document formats (e.g. html)
+#title: Phenotypic evolution is more constrained in simpler food webs
+#author: 
+#- Matthew A. Barbour$^{1,2,\ast}$ 
+#- Christopher J. Greyson-Gaito$^{2,3}$ 
+#- Arezoo Sootodeh$^{2}$ 
+#- Brendan Locke$^{4}$ 
+#- Jordi Bascompte$^{1}$ 
 # for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
@@
 ```{r setup ms, include=FALSE}
-## Rerun supp mat ----
-knitr::knit("analyses/reproduce_analyses.Rmd") # try changing to knitr::render() and see if it'll also produce the .html document.
+## Reproduce analyses ----
+knitr::knit("analyses/reproduce_analyses.Rmd")
 
@@
 
-<!-- Remove author info for double-blind peer review
-\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, 8057 Zurich, Switzerland;
+\vspace*{0.1cm} 
+\begin{center} \LARGE Phenotypic evolution is more constrained in simpler food webs \end{center}
+
+<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission -->
+\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
+
+\noindent 1. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Zurich, 8057 ZH, Switzerland;
 
@@
 \bigskip
--->
 
-*Manuscript elements*: Table 1, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
+*Manuscript elements*: table 1, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
 
@@
 
-<!--TABLE NOT REFERENCED IN RESULTS
+<!-- TABLE NOT REFERENCED IN RESULTS
 
@@
 \end{table}
+-->

### 2019-01-11 manuscript.Rmd
turns out my custom template is not needed, only the in_header document. This is because I manually specified the title page. If I wanted it produced in a similar format within YAML, I could keep my template.

@@
     citation_package: natbib
-    template: Rmd_AmNat_MS_template.tex
+    #template: Rmd_AmNat_MS_template.tex
     includes:  
@@
 
+\bigskip
+
 <!-- Remove author info for double-blind peer review; Keep for bioRxiv submission -->
 \begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
+
+\bigskip
 

### 2019-01-14 analyses/reproduce_analyses.Rmd
adding explanations for each code chunk and general tidying.

@@
 output: github_document
-# Trying github_document for easy viewing on github
-#  prettydoc::html_pretty:
-#    theme: architect
-#    highlight: github
 fontsize: 12pt
@@
 ## Load required libraries ----
-#library(evolqg) # need to load before dplyr
 library(car)        # for homogeneity of variance test
@@
 library(latex2exp)  # using Latex notation for axes labels
-#library(kableExtra)
 library(stringr)
@@
 
-We write the model in a way the independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival.
+We write the model in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival.
+The resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
+For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
 
@@
 
-Note that the resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
-For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
-
-```{r Bootstrap food-web model, cache=TRUE, include=FALSE}
+We used parametric bootstrapping to calculate 95% confidence intervals of trait-fitness relationships.
+
+```{r Bootstrap food-web model, cache=TRUE}
 boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
 ```
+
+In order to reliably quantify linear trait-fitness relationships, we remove all higher-order terms from the model [Stinchcombe et al.
+2008](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x).
 
@@
 
-```{r Bootstrap linear food-web model, cache=TRUE, include=FALSE}
+And refit using parametric bootstrapping.
+
+```{r Bootstrap linear food-web model, cache=TRUE}
 boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-To estimate biased selection on chamber diameter, we subset our data to only include multi-chambered galls where there was variability in larval survival.
+Chamber diameter, but not the other phenotypes, could be influenced by parasitism itself rather than being under natural selection.
+To estimate this potential bias, we subset our data to only include multi-chambered galls where there was variability in larval survival.
 We then fit a reduced model to estimate the bias in the logistic regression coefficient of chamber diameter in each food web.
@@
 ```{r Bias in food-web model, cache=TRUE}
+
+# Subset data
 biased_foodweb_df <- gall_selection.df %>%
@@
 
-# using linear model, but I'm only interested in the chamber diameter coefficient
+# Fit linear model with only chamber diameter 
 biased_foodweb_model <- glmer(
@@
 
+# Accuracy of confidence intervals is not a priority here, so we just use the asymptotic estimates rather than parametric bootstrapping.
 biased_foodweb_confint <- tidy(biased_foodweb_model, conf.int=TRUE) %>% filter(group=="fixed")
 
+# Print table
 knitr::kable(biased_foodweb_confint)
@@
 
-```{r Food-web alpha coefficients, include=FALSE}
+We gather regression coefficients from the full and reduced model to display trait-fitness relationships.
+For chamber diameter, we subtracted the coefficient due to bias to better approximate the trait-fitness relationship.
+We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).
+The code for tidying this data is not displayed, but is available in the 'reproduce_analyses.Rmd'.
+
+```{r Food-web alpha coefficients}
 foodweb_bind <- bind_cols(
@@
 
-```{r Table of food web coefficients, echo=F}
+Table of trait-fitness relationships:
+
+```{r Table of food web coefficients}
 knitr::kable(tidy_foodweb_alphas)
@@
 
-```{r Plot food-web coefficients, echo=FALSE}
+Plot these trait-fitness relationships:
+
+```{r Plot food-web coefficients}
 
@@
 
-```{r Food-web selection gradients, include=FALSE}
+Using the methods proposed by [Janzen and Stern, 1998](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we estimated selection gradients from our trait-fitness relationships.
+
+```{r Food-web selection gradients}
 
@@
 
+Table of selection gradients.
+
 ```{r Table of food web selection gradients, echo=F}
@@
 
-```{r Plot food-web gradients, echo=FALSE}
+Plot of selection gradients.
+
+```{r Plot food-web gradients}
 
@@
 
+# fit model with same structure as foodweb_model
 egglarval_model <- update(foodweb_model, data=egglarval_df)
 
+# subset data to estimate bias
 biased_egglarval_df <- egglarval_df %>%
@@
 
+# fit model with same structure as biased_foodweb_model
 biased_egglarval_model <- update(biased_foodweb_model, data=biased_egglarval_df)
@@
 
-```{r Bootstrap egg vs. larval ptoid model, cache=TRUE, include=FALSE}
+Parametric bootstrapping to estimate confidence intervals
+
+```{r Bootstrap egg vs. larval ptoid model, cache=TRUE}
 boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
 ```
+
+Fit a reduced model to reliably estimate linear trait-fitness relationships.
 
@@
 
-```{r Bootstrap linear egg vs. larval model, cache=TRUE, include=FALSE}
+Parametric bootstrapping to estimate confidence intervals.
+
+```{r Bootstrap linear egg vs. larval model, cache=TRUE}
 boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
@@
 
-```{r Egg vs. larval ptoid alpha coefficients, include=FALSE}
+Tidy trait-fitness relationships for egg and larval parasitoids from above models.
+
+```{r Egg vs. larval ptoid alpha coefficients}
 egglarval_bind <- bind_cols(
@@
 
-```{r Tabel of egg vs. larval coefficients, echo=FALSE}
+Table of trait-fitness relationships for egg and larval parasitoids.
+
+```{r Tabel of egg vs. larval coefficients}
 knitr::kable(tidy_egglarval_alphas)
@@
 
-```{r Plot egglarval coefficients, echo=FALSE}
+Plot of trait-fitness relationships for egg and larval parasitoids.
+
+```{r Plot egglarval coefficients}
 
@@
 
-```{r Egg vs. larval ptoid selection gradients, include=FALSE}
+Calculate selection gradients from trait-fitness relationships.
+
+```{r Egg vs. larval ptoid selection gradients}
 
@@
 
+Table of selection gradients imposed by egg and larval parasitoids.
+
 ```{r Egg vs. larval selection gradients, echo=F}
@@
 ```
+
+Plot of selection gradients imposed by egg and larval parasitoids.
 
@@
 Points and lines correspond to estimates of the mean and 95% confidence intervals, respectively.
-Overlapping confidence intervals with zero (dotted line) indicate no strong evidence of selection."}
+Overlapping confidence intervals with zero (dotted line) indicate no strong evidence of selection.", include=FALSE}
 tidy_foodwebegglarval_grads <- bind_rows(
@@
 
-```{r Plot foodwebegglarval coefficients, echo=FALSE, fig.cap="**Partitioning Selection Gradients.**"}
+```{r Plot foodwebegglarval coefficients, echo=FALSE, fig.cap="**Partitioning Selection Gradients.**", include=FALSE}
 tidy_foodwebegglarval_alphas <- bind_rows(
@@
 
-# Reproduce Figure 4 - Univariate adaptive landscape
-
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, include=FALSE}
+# Reproduce Figure 2 in main text of manuscript.
+
+Use the fitted model to generate predicted estimates of mean fitness for changes in the mean trait value of a population.
+I restrict these predictions to +/- 1 SD because we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [Arnold et al., 2001](https://link.springer.com/article/10.1023/A:1013373907708).
+Other trait values are held constant at the mean phenotype (i.e.
+trait = 0).
+
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE}
 newdata_Diam <- bind_rows(
@@
 
-```{r Get Clutch Size Fitness Landscape, cache=TRUE, include=FALSE}
+```{r Get Clutch Size Fitness Landscape, cache=TRUE}
 newdata_Clutch <- bind_rows(
@@
 
-```{r Get Oviposition preference Fitness Landscape, cache=TRUE, include=FALSE}
+```{r Get Oviposition preference Fitness Landscape, cache=TRUE}
 
@@
 
-```{r Plot Univariate Landscapes, include=FALSE}
+Create plots for each panel of Figure 2 in main text.
+
+```{r Plot Univariate Landscapes}
 uni_breaks <- c(0.1,0.5,1.0)
@@
 
+Fit plots together to reproduce Figure 2.
+
 ```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
@@
 # Get legend
-AF_uni_legend <- get_legend(AF_uni_Diam + theme(legend.title.align = 0.5)) #get_legend(AF_uni_Diam)
+AF_uni_legend <- get_legend(AF_uni_Diam + theme(legend.title.align = 0.5))
 
@@
 
-```{r Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE}
+```{r Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE, include=F}
 # Get legend
@@
 
-```{r Alt Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE}
+```{r Alt Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE, include=F}
 # Get legend
@@
 
-```{r Egg-Parasitoid-Selection-linear, echo=F}
+```{r Egg-Parasitoid-Selection-linear, echo=F, eval=F, include=F}
 linear_eggptoid_plot_df <- linear_eggegg_RF_Pref$absolute_fitness %>% 
@@
 
-# Multivariate fitness landscapes
-
-```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE, include=FALSE}
+# Reproduce Figure 3 presented in main text.
+
+Use the fitted model to generate predicted estimates of mean fitness for different phenotypic combinations.
+I restrict these predictions to +/- 1 SD because we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [Arnold et al., 2001](https://link.springer.com/article/10.1023/A:1013373907708).
+
+```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE}
 
@@
 
-```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, include=FALSE}
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE}
 
@@
 
-```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE, include=FALSE}
+```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE}
 
@@
 
-```{r Get plots of multivariate adaptive landscape, include=FALSE}
+Create plots for each panel.
+
+```{r Get plots of multivariate adaptive landscape}
 
@@
 
-Reproduce Figure 3 in main manuscript.
-
-```{r Figure-Multivariate-Landscapes, echo=FALSE, fig.cap="Fitness landscapes of gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of traits: clutch size and gall diameter (A); clutch size and Oviposition preference (B); Oviposition preference and gall diameter (C).
-Note that traits for all plots range 1 SD below and above the mean (=0)."}
+Fit plots together to reproduce Figure 3.
+
+```{r Figure-Multivariate-Landscapes}
 
@@
 
-```{r Slope and Curvature of the Adaptive Landscape, include=FALSE}
+# Calculating Slope and Curvature of the Adaptive Landscape
+
+Below is the code I used to get estimates for the slope and curvature of the adaptive landscape in each food-web treatment.
+If 95% confidence intervals of selection gradients overlap zero, then they are set to zero; otherwise, I retain the mean estimate.
+
+```{r Slope and Curvature of the Adaptive Landscape}
 
@@
 ```
+
+I use these estimates to populate the curvature matrices presented in the **Results** of the main text. I reproduce these estimates here for clarity:
+
+$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
+`r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(complex_curvature["Clutch","Diam"],2)` & `r round(complex_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
+`r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(simple_curvature["Clutch","Diam"],2)` & `r round(simple_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$

### 2019-01-14 analyses/reproduce_analyses.Rmd
remove simulation to confirm that only linear coefficients associated with chamber diameter need to be adjusted (not quadratic and correlational terms).

@@
 figure_eggegg_grads
-```
-
-```{r simulate bias in chamber diameter, include=FALSE, eval=FALSE}
-
-# To determine whether I should adjust any coefficients associated with chamber diameter, e.g.
-quadratic and correlation terms, I conducted a quick simulation.
-In the simulation, I assumed that if the larva survive, then the chamber diameter was the correct one.
-However, if the larva did not survive, its size could be due to both its size and parasitism.
-I assumed a constant value of parasitism effect on gall size.
-
-n <- 10000
-diam <- rnorm(n, mean=0, sd=1) # simulate 1,000 chamber diameters from a normal distribution with mean=0 and sd=1
-pref <- rnorm(n, mean=0, sd=1)               # simulate 1,000 Oviposition preferences from a normal distribution with mean=0 and sd=1
-bias.adj <- 0.34                  # this value corresponds to actual estimates from my bias analyses.
-mean_survival <- 0.5              # approximate survival across food-web treatments
-logit_survival <- mean_survival + 1.5*diam + 0.1*diam*diam -0.2*pref + 0*pref*pref -0.2*diam*pref # using coefficients that closely match empirical estimates
-link_survival <- exp(logit_survival)/(1 + exp(logit_survival))
-survival <- (runif(n) < link_survival)
-
-sim_df <- data.frame(survival=survival, diam=diam, pref=pref) %>%
-  mutate(diam_adj = ifelse(survival==FALSE, diam + bias.adj, diam)) # adjust bias only if larva did not survive
-
-## Fit non-adjusted model
-nonadj_model <- glm(survival ~ diam + I(diam^2) + pref + I(pref^2) + diam*pref, data=sim_df, family=binomial) 
-summary(nonadj_model)
-
-adj_model <- glm(survival ~ diam_adj  + I(diam_adj^2) + pref + I(pref^2) + diam_adj*pref, data=sim_df, family=binomial) 
-summary(adj_model)
-
-## Interesting, it seems that my simulation design affects the intercept term; however, its clear that my biological hypothesis for how chamber diameter is influenced by parasitism (simply decreasing size of non-surviving larva), would not affect the quadratic or nonlinear terms.
-data.frame(terms = names(coef(nonadj_model)), nonadj_coefs = coef(nonadj_model), adj_coefs = coef(adj_model)) %>%
-  mutate(diff_coefs = nonadj_coefs - adj_coefs)
 ```

### 2019-01-14 analyses/reproduce_analyses.Rmd
remove plot of linear selection on extended phenotype of egg parasitoid.

@@
 
-```{r Egg-Parasitoid-Selection-linear, echo=F, eval=F, include=F}
-linear_eggptoid_plot_df <- linear_eggegg_RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  spread(Foodweb, absolute_fitness) %>%
-  mutate(fitness_difference = Complex-Simple)
-
-linear_eggptoid_selection_plot <- linear_eggptoid_plot_df %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
-  geom_line(color=cbPalette[5]) +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall midge preference (SDs)") + 
-  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  geom_hline(yintercept=0, linetype="dotted") #+
-
-linear_eggptoid_selection_plot
-save_plot(filename = "linear_selection_on_Platygaster.pdf", plot = linear_eggptoid_selection_plot, base_height = 6)
-```
-
 ```{r Plot Univariate RF Landscapes, include=FALSE}

### 2019-01-14 analyses/reproduce_analyses.Rmd
moved reproduction of Fig. 4 to end of file.

@@
 
-```{r Egg-Parasitoid-Selection, echo=F}
-eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  spread(Foodweb, absolute_fitness) %>%
-  mutate(fitness_difference = Complex-Simple)
-
-eggptoid_selection_plot <- eggptoid_plot_df %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
-  geom_line(color=cbPalette[5]) +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Gall midge preference (SDs)") + 
-  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  theme_cowplot(font_size = 12)
-
-eggptoid_selection_plot
-save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
-```
-
 ```{r Plot Univariate RF Landscapes, include=FALSE}
@@
 `r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+# Reproduce Figure 4 in main text
+
+```{r Egg-Parasitoid-Selection}
+eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  spread(Foodweb, absolute_fitness) %>%
+  mutate(fitness_difference = Complex-Simple)
+
+eggptoid_selection_plot <- eggptoid_plot_df %>%
+  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
+  geom_line(color=cbPalette[5]) +
+  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
+  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
+  xlab("Gall midge preference (SDs)") + 
+  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
+  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  theme_cowplot(font_size = 12)
+
+eggptoid_selection_plot
+save_plot(filename = "selection_on_Platygaster.pdf", plot = eggptoid_selection_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
+```

### 2019-01-14 analyses/reproduce_analyses.Rmd
Display relative fitness plot of univariate adaptive landscape. This isn't in the main text of the manuscript, but its still a useful visualization.
Remove prior versions of univariate landscapes that tried to also include selection due to larval parasitoids.

@@
 
-```{r Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE, include=F}
-# Get legend
-AF_uni_legend <- get_legend(legend_only + theme(legend.position="top", legend.title.align = 0.5) + guides(color=guide_legend(title.position="top")))
-
-# Make plots
-AF_uni_plots <- plot_grid(NULL,
-                          Diam_legend_only + theme(legend.position = "none",                         
-                                             axis.title.y = element_blank(),
-                                             axis.text.x = element_blank()),
-                     pref_legend_only + theme(legend.position = "none",                          
-                                             axis.title.y = element_blank(),
-                                             axis.text.x = element_blank()) + xlab("Preference (SDs)"),
-                     legend_only + theme(legend.position = "none",                         
-                                             axis.title.y = element_blank()),
-                       labels = c("","A", "B", "C"), hjust=0.06, vjust=0.1, 
-                     ncol = 1, nrow=4, align='hv', rel_heights = c(0.5,1,1,1))
-
-AF_uni_legend_plots <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x=0.15,y=0.4)
-y_title_AF_uni_plots <- ggdraw() + draw_label("Mean larval survival", angle = 90, size=16)
-
-AF_gradients <- plot_grid(y_title_AF_uni_plots, AF_uni_legend_plots, ncol=2, rel_widths = c(0.1,1))
-AF_gradients
-save_plot(filename = "UV_landscapes.pdf", plot = AF_gradients, base_height = 9, base_width = 7)
-```
-
-```{r Alt Figure-Univariate-Landscapes, echo=FALSE, eval=FALSE, include=F}
-# Get legend
-AF_uni_legend <- get_legend(legend_only + theme(legend.title.align = 0.5))
-
-# Make plots
-AF_uni_plots <- plot_grid(NULL,
-                          Diam_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
-                                             axis.title.y = element_blank()), 
-                                             #axis.text.y = element_blank(),
-                                             #axis.text.x = element_text(size=10),
-                                             #axis.title.x = element_text(size=11)),
-                     pref_legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
-                                             axis.title.y = element_blank()), 
-                                             #axis.text.y = element_blank(),
-                                             #axis.text.x = element_text(size=10),
-                                             #axis.title.x = element_text(size=11)),
-                     legend_only + theme(legend.position = "none",                          # AF_uni_egglarval_Clutch
-                                             axis.title.y = element_blank()), 
-                                             #axis.text.y = element_blank(),
-                                             #axis.text.x = element_text(size=10),
-                                             #axis.title.x = element_text(size=11)),
-                     #  labels = "AUTO", 
-                     ncol = 2, align='hv')
-
-AF_uni_legend_plots <- ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x=0.1, y=0.25) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
-y_title_AF_uni_plots <- ggdraw() + draw_label("Mean larval survival", angle = 90)
-AF_gradients <- plot_grid(y_title_AF_uni_plots, AF_uni_legend_plots, ncol=2, rel_widths = c(0.05,1))
-AF_gradients
-#AF_gradients <- plot_grid(AF_uni_legend, AF_uni_plots,  nrow = 2, rel_heights = c(0.1,1)) #ggdraw(AF_uni_plots) + draw_grob(AF_uni_legend, x = 0.7, y=-0.2) # draw_grob(AF_uni_legend, x = 0.8, y=0)
-#AF_gradients
-
-```
-
-```{r Plot Univariate RF Landscapes, include=FALSE}
+# Replot univariate adaptive landscapes in terms of relative fitness
+
+```{r Plot Univariate RF Landscapes}
 

### 2019-01-14 analyses/reproduce_analyses.Rmd
remove old code the created the different panels for landscapes of foodweb, then egg vs. larval parasitoids.

@@
 
-AF_uni_egglarval_Pref <- egglarval_RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Oviposition preference (SDs)") +
-  ylab("Mean larval survival") +
-  scale_color_manual(values = treatment_colors, name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-
-# Clutch size -- food web
+# Clutch size 
 AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% 
@@
   coord_cartesian(ylim=c(0.07,1))
-
-# Clutch size -- egg vs. larval ptoids
-AF_uni_egglarval_Clutch <- egglarval_RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = factor(ifelse(Foodweb=="Complex","Larval","Simple"), levels=c("Simple","Larval"))) %>%
-  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Mean larval survival") +
-  scale_color_manual(values = cbPalette[c(5,4)], name = "Food web") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
-
-plot_foodweb_Clutch_df <- RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate"), facet="a")
-
-plot_egglarval_Clutch_df <- egglarval_RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-  filter(ID_group=="average") %>%
-  bind_rows(., filter(plot_foodweb_Clutch_df, ID_group=="average", Foodweb=="Complex")) %>%
-  mutate(facet = "b")
-
-legend_only <- bind_rows(plot_foodweb_Clutch_df, plot_egglarval_Clutch_df) %>%
-  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)  ","Egg (Simple)  ","Larval"))) %>%
-  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Clutch size (SDs)") +
-  ylab("Mean larval survival") +
-  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") +
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))+
-  facet_wrap(~facet) +
-  theme(strip.background=element_blank(), strip.text = element_blank()) +
-  guides(color=guide_legend(title.position="top"))
-
-## Female pref
-plot_foodweb_Pref_df <- RF_Pref$absolute_fitness %>%
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate"), facet="a")
-
-plot_egglarval_Pref_df <- egglarval_RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-  filter(ID_group=="average")  %>%
-  bind_rows(., filter(plot_foodweb_Pref_df, ID_group=="average", Foodweb=="Complex")) %>%
-  mutate(facet = "b")
-
-pref_legend_only <- bind_rows(plot_foodweb_Pref_df, plot_egglarval_Pref_df) %>%
-  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Oviposition preference (SDs)") +
-  ylab("Mean larval survival") +
-  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1)) +
-  theme(legend.title.align = 0.5) +
-  facet_wrap(~facet) +
-  theme(strip.background=element_blank(), strip.text = element_blank())
-
-# Chamber diameter
-plot_foodweb_Diam_df <- RF_Diam$absolute_fitness %>% 
-  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate"), facet="a")
-
-plot_egglarval_Diam_df <- egglarval_RF_Diam$absolute_fitness %>% 
-  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-  filter(ID_group=="average") %>%
-  bind_rows(., filter(plot_foodweb_Diam_df, ID_group=="average", Foodweb=="Complex")) %>%
-  mutate(facet = "b")
-
-Diam_legend_only <- bind_rows(plot_foodweb_Diam_df, plot_egglarval_Diam_df) %>%
-  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
-  geom_line() +
-  scale_alpha_manual(values=c(1,0.2), guide=FALSE) +
-  scale_size_manual(values=c(1.5,0.25), guide=FALSE) +
-  xlab("Chamber diameter (SDs)") +
-  ylab("Mean larval survival") +
-  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
-  scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
-  scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1)) +
-  theme(legend.title.align = 0.5) +
-  facet_wrap(~facet) +
-  theme(strip.background=element_blank(), strip.text = element_blank())
 ```

### 2019-01-14 analyses/reproduce_analyses.Rmd
remove bootstrap calls for old figures of univariate landscapes.

@@
 
-egglarval_RF_Diam <- bootstrap_fitness(
-  logistic_model = egglarval_model,
-  newdata = newdata_Diam,
-  bootstraps=n_boots_plots)
 ```
@@
 
-egglarval_RF_Clutch <- bootstrap_fitness(
-  logistic_model = egglarval_model,
-  newdata = newdata_Clutch,
-  bootstraps=n_boots_plots)
 ```
@@
 
-egglarval_RF_Pref <- bootstrap_fitness(
-  logistic_model = egglarval_model, 
-  newdata = newdata_Pref,
-  bootstraps=n_boots_plots)
-
+# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
 eggegg_RF_Pref <- bootstrap_fitness(
   logistic_model = eggegg_model, 
-  newdata = newdata_Pref,
-  bootstraps=n_boots_plots)
-
-linear_eggegg_RF_Pref <- bootstrap_fitness(
-  logistic_model = linear_eggegg_model, 
   newdata = newdata_Pref,

### 2019-01-14 analyses/reproduce_analyses.Rmd
move all code relating to selection on extended phenotype of egg parasitoid to the end of the manuscript.
remove echo=F calls so all underlying code is displayed.

@@
 
-```{r Univariate_histograms, echo=FALSE, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
+```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
 mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
@@
 
-```{r Multivariate_QQ, echo=FALSE, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
+```{r Multivariate_QQ, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
 mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
@@
 
-```{r Table of food web selection gradients, echo=F}
+```{r Table of food web selection gradients}
 knitr::kable(tidy_foodweb_grads)
@@
 
-```{r Egg vs. larval selection gradients, echo=F}
+```{r Egg vs. larval selection gradients}
 knitr::kable(tidy_egglarval_grads)
@@
 
-```{r Plot egg vs. larval ptoid gradients, echo=FALSE}
+```{r Plot egg vs. larval ptoid gradients}
 
@@
 
-```{r Figure-Selection-Gradients, echo=FALSE, fig.cap="**Selection gradients**.
+```{r Figure-Selection-Gradients, fig.cap="**Selection gradients**.
 Estimates of standardized selection gradients in complex (orange) and simple (blue) food webs.
@@
 
-```{r Plot foodwebegglarval coefficients, echo=FALSE, fig.cap="**Partitioning Selection Gradients.**", include=FALSE}
+```{r Plot foodwebegglarval coefficients, fig.cap="**Partitioning Selection Gradients.**", include=FALSE}
 tidy_foodwebegglarval_alphas <- bind_rows(
@@
 figure_foodwebegglarval_coefs
-```
-
-# Estimating selection on the egg parasitoid *Platygaster*
-
-```{r Egg vs. egg ptoid model, cache=TRUE}
-
-# convert "gall_survival" to egg parasitoid survival.
-Note that both Iteomyia pupa and larva parasitoids result in 0.
-We do not change the name of the response variable to make clear that we are using the same statistical models as for Iteomyia.
-eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg_parasitoid==1,1,0))
-
-eggegg_model <- update(foodweb_model, data=eggegg_df)
-
-biased_eggegg_df <- eggegg_df %>%
-  group_by(Foodweb, Gall_Number) %>%
-  mutate(mean_survival = mean(gall_survival)) %>%
-  filter(mean_survival > 0, mean_survival < 1) %>%
-  ungroup()
-
-biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
-```
-
-```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
-boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-```
-
-```{r Linear egg vs. egg ptoid model, cache=TRUE}
-linear_eggegg_model <- update(linear_foodweb_model, data=eggegg_df)
-```
-
-```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
-boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
-```
-
-```{r Egg vs. egg ptoid alpha coefficients, include=FALSE}
-eggegg_bind <- bind_cols(
-  as_tibble(boot_linear_eggegg_model$t),
-  select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
-)
-
-# Adjust coefficients with chamber diameter
-eggegg_adj_Diam <- as_tibble(boot_eggegg_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])
-
-# Calculate differences between food-web treatments, then estimate means and confidence intervals
-eggegg_alphas <- eggegg_adj_Diam %>%
-  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
-  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
-  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
-         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
-  summarise_all(funs(mean, conf.high, conf.low))
-
-# Tidy up estimates
-tidy_eggegg_alphas <- eggegg_alphas %>%
-  t() %>%
-  as.data.frame() %>%
-  transmute(rows = rownames(.), value=V1) %>%
-  separate(col = rows, into = c("term","estimate"), sep="_") %>%
-  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
-  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
-  separate(col = type, into = c("extra","type"), sep = 7) %>%
-  select(type, term, estimate, value) %>%
-  spread(estimate, value) %>%
-  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
-         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
-                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
-                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
-```
-
-```{r Egg vs. egg ptoid coefficients, echo=F}
-knitr::kable(tidy_eggegg_alphas)
-```
-
-```{r Plot egg vs. egg ptoid coefficients, echo=FALSE}
-
-# Plot helpers
-dodge_width <- position_dodge(width=0.5)
-y_limits_eggegg_coefs <- c(min(filter(tidy_eggegg_alphas, type!="Diff")$conf.low), 
-                            max(filter(tidy_eggegg_alphas, type!="Diff")$conf.high))
-P_asterisk_eggegg_coefs <- 1.7
-P_size <- 8
-legend_eggegg_labels <- c("Complex","Simple")
-point.size <- 3
-
-# Plot mean fitness
-plot_eggegg_mean_fitness <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term=="(Intercept)") %>%
-  ggplot(., aes(x=type)) +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Probability of observing egg parasitoid", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
-  scale_x_discrete(name="") +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
-
-# Plot linear trait-fitness relationaships
-plot_eggegg_linear_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
-  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
-
-# Plot quadratic trait-fitness relationships
-plot_eggegg_quadratic_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
-  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
-
-# Plot correlational trait-fitness relationaships
-plot_eggegg_correlational_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
-  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
-
-# Format plots for manuscript
-plot_eggegg_coefs <- plot_grid(
-  plot_eggegg_mean_fitness + theme(legend.position = "none"),
-  plot_eggegg_linear_coefs + theme(legend.position = "none"),
-  plot_eggegg_quadratic_coefs + theme(legend.position = "none"),
-  plot_eggegg_correlational_coefs + theme(legend.position = "none"), 
-  nrow=2, align="hv", labels = "")
-
-figure_eggegg_coefs <- plot_eggegg_coefs 
-figure_eggegg_coefs
-```
-
-```{r Egg vs. egg ptoid selection gradients, include=FALSE}
-
-# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-eggegg_complex_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Complex"), type="response")
-eggegg_complex_mean_brackets <- mean(eggegg_complex_predict * (1 - eggegg_complex_predict))
-eggegg_complex_mean_fitness <- mean(eggegg_complex_predict)
-
-eggegg_simple_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Simple"), type="response")
-eggegg_simple_mean_brackets <- mean(eggegg_simple_predict * (1 - eggegg_simple_predict))
-eggegg_simple_mean_fitness <- mean(eggegg_simple_predict)
-
-eggegg_complex_gradient <- function(x) eggegg_complex_mean_brackets * x / eggegg_complex_mean_fitness
-eggegg_simple_gradient <- function(x) eggegg_simple_mean_brackets * x / eggegg_simple_mean_fitness
-
-eggegg_complex_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebComplex:")) %>%
-  transmute_all(funs(eggegg_complex_gradient))
-
-eggegg_simple_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebSimple:")) %>%
-  transmute_all(funs(eggegg_simple_gradient))
-
-# Calculate differences between food-web treatments, then estimate means and confidence intervals
-eggegg_grads <- bind_cols(eggegg_complex_raw_gradients, eggegg_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
-  summarise_all(funs(mean, conf.high, conf.low))
-
-# Tidy up estimates
-tidy_eggegg_grads <- eggegg_grads %>%
-  t() %>%
-  as.data.frame() %>%
-  transmute(rows = rownames(.), value=V1) %>%
-  separate(col = rows, into = c("term","estimate"), sep="_") %>%
-  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
-  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
-  separate(col = type, into = c("extra","type"), sep = 7) %>%
-  select(type, term, estimate, value) %>%
-  spread(estimate, value) %>%
-  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
-         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
-                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
-         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
-         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
-         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
-```
-
-```{r Table of egg vs. egg ptoid gradients, echo=F}
-knitr::kable(tidy_eggegg_grads)
-```
-
-```{r Plot egg vs. egg ptoid gradients, echo=FALSE}
-
-# Plot helpers
-dodge_width <- position_dodge(width=0.5)
-y_limits_eggegg_grads <- c(min(filter(tidy_eggegg_grads, type!="Diff")$conf.low), 
-                            max(filter(tidy_eggegg_grads, type!="Diff")$conf.high))
-P_asterisk_eggegg_grads <- 0.45
-P_size <- 8
-legend_eggegg_labels <- c("Complex","Simple")
-legend_eggegg_title <- "Food web"
-point.size <- 3
-
-# Plot directional selection gradients
-plot_eggegg_directional_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
-  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
-  facet_wrap(~gradient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
-
-# Plot quadratic selection gradients
-plot_eggegg_quadratic_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
-  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
-  facet_wrap(~gradient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
-
-# Plot correlational selection gradients
-plot_eggegg_correlational_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
-  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
-  facet_wrap(~gradient_type) +
-  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
-  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
-
-# Get legend
-legend_eggegg_grads <- get_legend(plot_eggegg_directional_grads)
-
-# Format plots for manuscript
-plot_eggegg_grads <- plot_grid(
-  plot_eggegg_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
-  plot_eggegg_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
-  plot_eggegg_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
-  nrow=2, align="hv", labels = "")
-plot_legend_eggegg_grads <- ggdraw(plot_eggegg_grads) + draw_grob(legend_eggegg_grads, x = 0.7, y=-0.2)
-y_title_eggegg_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
-
-figure_eggegg_grads <- plot_grid(y_title_eggegg_grads, plot_legend_eggegg_grads, ncol=2, rel_widths = c(0.05,1)) 
-figure_eggegg_grads
 ```
@@
 
-```{r Univariate-Fitness-Landscapes, echo=FALSE, fig.cap="Selection gradients acting on gall traits in complex vs.
+```{r Univariate-Fitness-Landscapes, fig.cap="Selection gradients acting on gall traits in complex vs.
 simple food webs.
@@
 
+# Estimating selection on the egg parasitoid *Platygaster*
+
+```{r Egg vs. egg ptoid model, cache=TRUE}
+
+# convert "gall_survival" to egg parasitoid survival.
+Note that both Iteomyia pupa and larva parasitoids result in 0.
+We do not change the name of the response variable to make clear that we are using the same statistical models as for Iteomyia.
+eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg_parasitoid==1,1,0))
+
+eggegg_model <- update(foodweb_model, data=eggegg_df)
+
+biased_eggegg_df <- eggegg_df %>%
+  group_by(Foodweb, Gall_Number) %>%
+  mutate(mean_survival = mean(gall_survival)) %>%
+  filter(mean_survival > 0, mean_survival < 1) %>%
+  ungroup()
+
+biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
+```
+
+```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
+boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Linear egg vs. egg ptoid model, cache=TRUE}
+linear_eggegg_model <- update(linear_foodweb_model, data=eggegg_df)
+```
+
+```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
+boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+```
+
+```{r Egg vs. egg ptoid alpha coefficients, include=FALSE}
+eggegg_bind <- bind_cols(
+  as_tibble(boot_linear_eggegg_model$t),
+  select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
+
+# Adjust coefficients with chamber diameter
+eggegg_adj_Diam <- as_tibble(boot_eggegg_model$t) %>%
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+eggegg_alphas <- eggegg_adj_Diam %>%
+  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
+  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_eggegg_alphas <- eggegg_alphas %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
+                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                          ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
+```
+
+```{r Egg vs. egg ptoid coefficients}
+knitr::kable(tidy_eggegg_alphas)
+```
+
+```{r Plot egg vs. egg ptoid coefficients}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_eggegg_coefs <- c(min(filter(tidy_eggegg_alphas, type!="Diff")$conf.low), 
+                            max(filter(tidy_eggegg_alphas, type!="Diff")$conf.high))
+P_asterisk_eggegg_coefs <- 1.7
+P_size <- 8
+legend_eggegg_labels <- c("Complex","Simple")
+point.size <- 3
+
+# Plot mean fitness
+plot_eggegg_mean_fitness <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term=="(Intercept)") %>%
+  ggplot(., aes(x=type)) +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Probability of observing egg parasitoid", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_x_discrete(name="") +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Plot linear trait-fitness relationaships
+plot_eggegg_linear_coefs <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Plot quadratic trait-fitness relationships
+plot_eggegg_quadratic_coefs <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Plot correlational trait-fitness relationaships
+plot_eggegg_correlational_coefs <- tidy_eggegg_alphas %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
+  facet_wrap(~coefficient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels)
+
+# Format plots for manuscript
+plot_eggegg_coefs <- plot_grid(
+  plot_eggegg_mean_fitness + theme(legend.position = "none"),
+  plot_eggegg_linear_coefs + theme(legend.position = "none"),
+  plot_eggegg_quadratic_coefs + theme(legend.position = "none"),
+  plot_eggegg_correlational_coefs + theme(legend.position = "none"), 
+  nrow=2, align="hv", labels = "")
+
+figure_eggegg_coefs <- plot_eggegg_coefs 
+figure_eggegg_coefs
+```
+
+```{r Egg vs. egg ptoid selection gradients, include=FALSE}
+
+# Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
+eggegg_complex_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Complex"), type="response")
+eggegg_complex_mean_brackets <- mean(eggegg_complex_predict * (1 - eggegg_complex_predict))
+eggegg_complex_mean_fitness <- mean(eggegg_complex_predict)
+
+eggegg_simple_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Simple"), type="response")
+eggegg_simple_mean_brackets <- mean(eggegg_simple_predict * (1 - eggegg_simple_predict))
+eggegg_simple_mean_fitness <- mean(eggegg_simple_predict)
+
+eggegg_complex_gradient <- function(x) eggegg_complex_mean_brackets * x / eggegg_complex_mean_fitness
+eggegg_simple_gradient <- function(x) eggegg_simple_mean_brackets * x / eggegg_simple_mean_fitness
+
+eggegg_complex_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebComplex:")) %>%
+  transmute_all(funs(eggegg_complex_gradient))
+
+eggegg_simple_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebSimple:")) %>%
+  transmute_all(funs(eggegg_simple_gradient))
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+eggegg_grads <- bind_cols(eggegg_complex_raw_gradients, eggegg_simple_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_eggegg_grads <- eggegg_grads %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+```{r Table of egg vs. egg ptoid gradients}
+knitr::kable(tidy_eggegg_grads)
+```
+
+```{r Plot egg vs. egg ptoid gradients}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_eggegg_grads <- c(min(filter(tidy_eggegg_grads, type!="Diff")$conf.low), 
+                            max(filter(tidy_eggegg_grads, type!="Diff")$conf.high))
+P_asterisk_eggegg_grads <- 0.45
+P_size <- 8
+legend_eggegg_labels <- c("Complex","Simple")
+legend_eggegg_title <- "Food web"
+point.size <- 3
+
+# Plot directional selection gradients
+plot_eggegg_directional_grads <- tidy_eggegg_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
+
+# Plot quadratic selection gradients
+plot_eggegg_quadratic_grads <- tidy_eggegg_grads %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
+
+# Plot correlational selection gradients
+plot_eggegg_correlational_grads <- tidy_eggegg_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title) +
+  scale_color_manual(values=cbPalette[c(2,5)], labels=legend_eggegg_labels, name=legend_eggegg_title)
+
+# Get legend
+legend_eggegg_grads <- get_legend(plot_eggegg_directional_grads)
+
+# Format plots for manuscript
+plot_eggegg_grads <- plot_grid(
+  plot_eggegg_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_eggegg_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_eggegg_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+plot_legend_eggegg_grads <- ggdraw(plot_eggegg_grads) + draw_grob(legend_eggegg_grads, x = 0.7, y=-0.2)
+y_title_eggegg_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+figure_eggegg_grads <- plot_grid(y_title_eggegg_grads, plot_legend_eggegg_grads, ncol=2, rel_widths = c(0.05,1)) 
+figure_eggegg_grads
+```
+
 # Reproduce Figure 4 in main text

### 2019-01-14 analyses/reproduce_analyses.Rmd
specify seed=34 within bootMer function throughout code.

@@
   if(is.null(bootstraps) == FALSE){
-    set.seed(34) # make sure results are reproducible
-    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+    get_bootstraps_absolute_fitness <-bootMer(logistic_model, FUN = get_absolute_fitness, nsim=bootstraps, parallel="multicore", ncpus=32, seed=34)
 
@@
   if(is.null(bootstraps) == FALSE){
-    set.seed(34) # make sure results are reproducible
-    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32)
+
+    get_bootstraps_relative_fitness <-bootMer(logistic_model, FUN = get_relative_fitness, nsim=bootstraps, parallel="multicore", ncpus=32, seed=34)
 
@@
 ```{r Bootstrap food-web model, cache=TRUE}
-boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
@@
 ```{r Bootstrap linear food-web model, cache=TRUE}
-boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
@@
 ```{r Bootstrap egg vs. larval ptoid model, cache=TRUE}
-boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
@@
 ```{r Bootstrap linear egg vs. larval model, cache=TRUE}
-boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
@@
 ```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
-boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
@@
 ```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
-boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32)
+boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```

### 2019-01-14 analyses/reproduce_analyses.Rmd
clarify role of bootstrap_fitness function as a plotting tool. I used bootMer for model inferences. Note that bootstrap_fitness is based on bootMer, but I only used 100 reps for visualization.

@@
 
-## Bootstrap fitness estimates
+## Get data for plotting bootstrapped estimates in Figures 2, 3, and 4 of main text
 bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){

### 2019-01-14 analyses/reproduce_analyses.Rmd
move eggegg_RF_Pref to come after the eggegg_model

@@
   logistic_model = foodweb_model, 
-  newdata = newdata_Pref,
-  bootstraps=n_boots_plots)
-
-# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
-eggegg_RF_Pref <- bootstrap_fitness(
-  logistic_model = eggegg_model, 
   newdata = newdata_Pref,
@@
 ```{r Egg-Parasitoid-Selection}
+# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
+eggegg_RF_Pref <- bootstrap_fitness(
+  logistic_model = eggegg_model, 
+  newdata = newdata_Pref,
+  bootstraps=n_boots_plots)
+
 eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 

### 2019-01-15 manuscript.Rmd
incorporated Chris' comments

@@
 ## Reproduce analyses ----
-knitr::knit("analyses/reproduce_analyses.Rmd")
+rmarkdown::render("analyses/reproduce_analyses.Rmd")
 
@@
 
-We collected data on three different traits that we expected to influence larval survival based on our previous work [@Barbour2016] and others work with gall midges [@Weis1983; @Heath2018].
+We collected data on three different traits that we expected to influence larval survival based on our previous work [@Barbour2016] and other work with gall midges [@Weis1983; @Heath2018].
 First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
@@
 bias).
-We used a GLMM with the same structure as described above except that we only modelled a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
+We used a GLMM with the same structure as described above except that we modelled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
 We detected a positive bias in both food-web treatments (complex $\alpha_{\text{Diam}}$=
@@
 The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
-In the simplest case, when consumers do not differ from each other, then we do not expect changes in food-web complexity to modify selective constraints.
+For example, if consumers do not differ from each other, then we do not expect changes in food-web complexity to modify selective constraints.
 Also, many consumers may be at too low of abundances to impose selection on their resources.
@@
 Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
-We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.
+We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.
+<!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
 

### 2019-01-15 analyses/reproduce_analyses.Rmd
minor edits to identify problems with knitting.

@@
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  filter(ID_group == "average") %>%
+  #filter(ID_group == "average") %>%
   group_by(Foodweb) %>%
@@
 
-RF_plot_egglarval_Clutch_df <- egglarval_RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-  filter(Foodweb=="Larval", ID_group=="average") %>%
-  group_by(Foodweb) %>%
-  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
-  ungroup()
-
-RF_legend_only <- bind_rows(RF_plot_foodweb_Clutch_df, RF_plot_egglarval_Clutch_df) %>%
-  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-  filter(ID_group=="average") %>%
+#RF_plot_egglarval_Clutch_df <- egglarval_RF_Clutch$absolute_fitness %>% 
+#  select(-sc.Diam, -sc.sqrt.Pref) %>%
+#  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+#  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+#  filter(Foodweb=="Larval", ID_group=="average") %>%
+#  group_by(Foodweb) %>%
+#  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+#  ungroup()
+
+RF_uni_Clutch <- RF_plot_foodweb_Clutch_df %>%
+#  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+#  filter(ID_group=="average") %>%
   ggplot(., aes(x=sc.log.Clutch, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
   ylab("Relative fitness") +
-  scale_color_manual(values = cbPalette[c(6,5,4)], name = "Parasitoids") + 
+  scale_color_manual(values = cbPalette[c(6,5)], name = "Food web") + 
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +
@@
 
-RF_plot_egglarval_Pref_df <- egglarval_RF_Pref$absolute_fitness %>%
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-  filter(Foodweb=="Larval", ID_group=="average") %>%
-  group_by(Foodweb) %>%
-  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
-  ungroup()
-
-RF_pref_legend_only <- bind_rows(RF_plot_foodweb_Pref_df, RF_plot_egglarval_Pref_df) %>%
-  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-  filter(ID_group=="average") %>%
+#RF_plot_egglarval_Pref_df <- egglarval_RF_Pref$absolute_fitness %>%
+#  select(-sc.Diam, -sc.log.Clutch) %>%
+#  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+#  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+#  filter(Foodweb=="Larval", ID_group=="average") %>%
+#  group_by(Foodweb) %>%
+#  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+#  ungroup()
+
+RF_uni_Pref <- RF_plot_foodweb_Pref_df %>%
+#  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+#  filter(ID_group=="average") %>%
   ggplot(., aes(x=sc.sqrt.Pref, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
-RF_plot_egglarval_Diam_df <- egglarval_RF_Diam$absolute_fitness %>% 
-  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-  filter(Foodweb=="Larval", ID_group=="average") %>%
-  group_by(Foodweb) %>%
-  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
-  ungroup()
-
-RF_Diam_legend_only <- bind_rows(RF_plot_foodweb_Diam_df, RF_plot_egglarval_Diam_df) %>%
-  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-  filter(ID_group=="average") %>%
+#RF_plot_egglarval_Diam_df <- egglarval_RF_Diam$absolute_fitness %>% 
+#  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
+#  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+#  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
+#  filter(Foodweb=="Larval", ID_group=="average") %>%
+#  group_by(Foodweb) %>%
+#  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
+#  ungroup()
+
+RF_uni_Diam <- RF_plot_foodweb_Diam_df %>%
+#  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
+#  filter(ID_group=="average") %>%
   ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 # Get legend
-RF_uni_legend <- get_legend(RF_legend_only)
+RF_uni_legend <- get_legend(RF_uni_Diam)
 
 # Make plots
-RF_uni_plots <- plot_grid(RF_Diam_legend_only + theme(legend.position = "none", 
+RF_uni_plots <- plot_grid(RF_uni_Diam + theme(legend.position = "none", 
                                              axis.text.x = element_text(size=10),
                                              axis.title.x = element_text(size=11)),
-                     RF_pref_legend_only + theme(legend.position = "none",                          
+                     RF_uni_Pref + theme(legend.position = "none",                          
                                              axis.title.y = element_blank(), 
@@
                                              axis.title.x = element_text(size=11)),
-                     RF_legend_only + theme(legend.position = "none",                          
+                     RF_uni_Clutch + theme(legend.position = "none",                          
                                              axis.title.y = element_blank(), 

### 2019-01-16 finalize_manuscript_dataset.Rmd
wrote script to finalize dataset for manuscript.

---
title: "Finalize dataset for *Phenotypic evolution is more constrained in simpler food webs*"
author: "Matthew A. Barbour"
date: "1/15/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)  # for managing data
```

Focus cleaned dataset on galls marked for the experiment (phenology == "early") and that were collected while they were still on the tree (rather than bags that fell to the ground). Subsetting galls that remained on trees removes potential bias between treatments, because we were not able to recover galls that had fallen from the tree in the Control treatment (they only had flagging tape placed nearby rather than being enclosed within a bag).

```{r Filter dataset}
gall_selection.df <- read_csv("data/raw_data_management/gall_selection_data.csv") %>%
  filter(phenology == "early", Location == "tree") %>%
  select(Treatment = Treatment.focus, 
         # unique identifying information at the plant- and gall-level
         Genotype, # plant genotype ID
         Plant_Position, # unique plant ID (also corresponds to position within the common garden experiment)
         Gall_Number, # unique multi-chambered gall ID
         Gall_Letter, # unique chamber ID within gall number
         # rename traits and add measurement units to variable
         chamber.diameter_mm = Gall_Height_mm, # chamber-level
         oviposition.preference_individuals.per.100.shoots = Density_per_100_shoots, # plant-level
         clutch.size_individuals = gall_individuals, # gall-level
         pupa, # successful pupation of larval Iteomyia salicisverruca
         egg.ptoid = platy, # reared egg parasitoid, Platygaster sp. from gall chamber
         larval.ptoid = ectos, # reared larval parasitoid (most of which were ectoparasitoids) from gall chamber
         early.larval.death = none.none) # early larval death = no larva or exit hole associated with gall chamber

write_csv(gall_selection.df, "data/gall_selection_manuscript_dataset.csv")
```

### 2019-01-16 analyses/reproduce_analyses.Rmd
many minor formatting edits to make it easier to understand the code and results.

@@
 date: "`r Sys.Date()`"
-output: github_document
-fontsize: 12pt
+output:  
+  prettydoc::html_pretty:
+    theme: architect
+    highlight: github
+fontsize: 11pt
 ---
 
-```{r setup, include=FALSE}
-
-## Load required libraries ----
+```{r setup}
+knitr::opts_chunk$set(messages=FALSE, warning=FALSE, error=FALSE)
+
+# Load required libraries ----
 library(car)        # for homogeneity of variance test
@@
 library(broom)      # for tidying multiple linear models
-library(visreg)     # for quick visualizations of model effects
+#library(visreg)     # for quick visualizations of model effects
 library(viridis)    # for color palette
 library(lme4)       # for generalized linear mixed models
-library(piecewiseSEM) # for calculating model R-square
+#library(piecewiseSEM) # for calculating model R-square
 library(latex2exp)  # using Latex notation for axes labels
@@
 
-## Load and manage data ----
-
-gall_selection.df <- read_csv("../data/gall_selection_data.csv") %>%
+# Load and manage data ----
+
+gall_selection.df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
   # convert appropriate variables to characters instead of integers
@@
   # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  filter(Treatment.focus == "Ectoparasitoid exclusion" & ectos < 1 | Treatment.focus == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
-  mutate(Foodweb = ifelse(Treatment.focus=="Control","Complex","Simple"),
+  filter(#phenology == "early", Location == "tree",
+         egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"),
          gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
+         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber.
+I set these to 1 to permit an analysis with a binomial model.
          # transform and scale traits to approximate multivariate normal assumption
-         sc.Diam = as.numeric(scale(Gall_Height_mm)), 
-         sc.log.Clutch = as.numeric(scale(log(gall_individuals))), 
-         sc.sqrt.Pref = as.numeric(scale(sqrt(Density_per_100_shoots))))
-
-## Custom functions to avoid repetitive code ----
-
-## Transform logit to probability
+         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
+         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
+         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))
+
+# Custom functions to avoid repetitive code ----
+
+# Transform logit to probability
 inverse_logit <- function(x) exp(x)/(1+exp(x))
 
-## Get data for plotting bootstrapped estimates in Figures 2, 3, and 4 of main text
+# Get data for plotting bootstrapped estimates in Figures 2, 3, and 4 of main text
 bootstrap_fitness <- function(logistic_model, newdata, bootstraps, intervals=c(0.025,0.975)){
@@
 
-## Number of bootstrap replicates
-n_boots_analysis <- 1000
-n_boots_plots <- 100
-
-## Get confidence intervals from bootstrapped samples
+# Number of bootstrap replicates
+n_boots_analysis <- 100
+n_boots_plots <- 10
+
+# Get confidence intervals from bootstrapped samples
 conf.high <- function(x) quantile(x, probs = 0.975)
@@
 
-## Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/
-
-# order -> orange, light blue, green, yellow, dark blue, red, pink
+# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; order -> orange, light blue, green, yellow, dark blue, red, pink
 cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
-complex_color <- cbPalette[6] # 1
-simple_color <- cbPalette[5] # 2
+complex_color <- cbPalette[6] 
+simple_color <- cbPalette[5] 
 treatment_colors <- c(complex_color, simple_color)
@@
 
-# Evaluating assumption of multivariate normality
+\
+
+## Evaluating assumption of multivariate normality
 
 We used graphical checks to evaluate whether our transformations of trait values resulted in a multivariate normal distribution.
-Figure S\ref{fig:Univariate_histograms} shows that our transformations resulted in approximately normal distributions for each phenotypic trait.
-Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line (fig.
-S\ref{fig:Multivariate_QQ}), suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.
+The histograms below show that our transformations resulted in approximately normal distributions for each phenotypic trait.
+Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line, suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.
 
@@
 
-```{r Multivariate_QQ, fig.cap="\\label{fig:Multivariate_QQ}Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
+```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
 mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
@@
 
-# Effect of food-web treatment on trait-fitness relationships and selection gradients
+## Gall trait-fitness relationships: effect of food-web treatment
 
@@
 biased_foodweb_confint <- tidy(biased_foodweb_model, conf.int=TRUE) %>% filter(group=="fixed")
-
+```
+
+```{r biased foodweb table, echo=FALSE}
 # Print table
-knitr::kable(biased_foodweb_confint)
+biased_foodweb_confint %>%
+  select(term, estimate, conf.low, conf.high) %>%
+  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
+  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
 ```
@@
 We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).
-The code for tidying this data is not displayed, but is available in the 'reproduce_analyses.Rmd'.
 
@@
 ```
-
-Table of trait-fitness relationships:
-
-```{r Table of food web coefficients}
-knitr::kable(tidy_foodweb_alphas)
-```
-
-Plot these trait-fitness relationships:
-
-```{r Plot food-web coefficients}
+\
+
+```{r Table of food web coefficients, echo=FALSE}
+tidy_foodweb_alphas %>%
+  filter(type != "Diff") %>%
+  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+ knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
+```
+
+\
+
+```{r Table of differences in food web coefficients, echo=FALSE}
+tidy_foodweb_alphas %>%
+  filter(type == "Diff") %>%
+  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+ knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
+```
+
+\
+
+The table is good for details, but it is easier to see the results as a figure.
+
+```{r Plot food-web coefficients, fig.cap="Plot of mean fitness differences between treatments and trait-fitness relationships.
+Asterisks denote significant differences (*P* < 0.05) between treatments."}
 
@@
   geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
   xlab("Food web") +
@@
 ```
+
+\
+
+## Gall trait selection gradients
 
@@
 
-Table of selection gradients.
-
-```{r Table of food web selection gradients}
-knitr::kable(tidy_foodweb_grads)
-```
-
-Plot of selection gradients.
-
-```{r Plot food-web gradients}
+\
+
+Reproduce numbers reported in **Table 1** of the manuscript.
+
+```{r Table of food web selection gradients, echo=FALSE}
+tidy_foodweb_grads %>%
+  filter(type != "Diff") %>%
+  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
+```
+
+\
+
+```{r Table of differences in selection gradients between food-web treatments, echo=FALSE}
+tidy_foodweb_grads %>%
+  filter(type == "Diff") %>%
+  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
+```
+
+\
+
+Now visualize the table output as a figure.
+
+```{r Plot food-web gradients, fig.cap="Plot of selection gradients in each food-web treatment. Asterisks denote significant differences (*P* < 0.05) between food-web treatments."}
 
@@
 
-# Partitioning the contribution of egg and larval parasitoids to selection gradients
+\
+
+## Gall trait-fitness relationships: contribution of egg and larval parasitoids
 
@@
 # excludes cases of egg-parasitism from Complex food web
-egglarval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & platy < 1)
+egglarval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & egg.ptoid < 1)
 
@@
 
-Parametric bootstrapping to estimate confidence intervals
+Parametric bootstrapping to estimate confidence intervals.
 
@@
 
-Table of trait-fitness relationships for egg and larval parasitoids.
-
-```{r Tabel of egg vs. larval coefficients}
-knitr::kable(tidy_egglarval_alphas)
-```
-
-Plot of trait-fitness relationships for egg and larval parasitoids.
-
-```{r Plot egglarval coefficients}
+\
+
+```{r Table of egg vs. larval coefficients, echo=FALSE}
+tidy_egglarval_alphas %>%
+  filter(type != "Diff") %>%
+  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of gall trait-fitness relationships imposed by egg and larval parasitoids.
+Note that type = Simple = Egg parasitoid and Complex = Larval parasitoid.")
+```
+
+```{r Table of differences in egg vs. larval coefficients, echo=FALSE}
+tidy_egglarval_alphas %>%
+  filter(type == "Diff") %>%
+  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of differences in gall trait-fitness relationships between egg and larval parasitoids.")
+```
+
+See the table results in figure form.
+
+```{r Plot egglarval coefficients, fig.cap="Trait-fitness relationships for egg and larval parasitoids. Asterisks denote significant differences (*P* < 0.05) between parasitoid guilds."}
 
@@
   geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
   scale_x_discrete(name="Parasitoid", breaks=c("Complex","Simple"), labels=c("Larval","Egg")) +
@@
 
-Calculate selection gradients from trait-fitness relationships.
+## Selection gradients acting on gall traits due to egg and larval parasitoids
 
@@
 
-Table of selection gradients imposed by egg and larval parasitoids.
-
-```{r Egg vs. larval selection gradients}
-knitr::kable(tidy_egglarval_grads)
-```
-
-Plot of selection gradients imposed by egg and larval parasitoids.
-
-```{r Plot egg vs. larval ptoid gradients}
+\
+
+```{r Egg vs. larval selection gradients, echo=FALSE}
+tidy_egglarval_grads %>%
+  filter(type != "Diff") %>%
+  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of selection gradients imposed by egg and larval parasitoids.")
+```
+
+\
+
+```{r Table of differences in selection gradients between egg and larval parasitoids, echo=FALSE}
+tidy_egglarval_grads %>%
+  filter(type == "Diff") %>%
+  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in selection gradients imposed by egg and larval parasitoids.")
+```
+
+\
+
+See table results in figure form.
+
+```{r Plot egg vs. larval ptoid gradients, fig.cap="Selection gradients imposed by egg and larval parasitoids. Asterisks denote significant differences (*P* < 0.05) between parasitoid guilds."}
 
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  scale_y_continuous(name="larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
   scale_x_discrete(name="Parasitoids", breaks=c("Complex","Simple","Larval"), labels=c("Egg + Larval","Egg","Larval")) +
@@
 
-# Reproduce Figure 2 in main text of manuscript.
+\
+
+## Reproduce Figure 2 in manuscript.
 
@@
 
-```{r Univariate-Fitness-Landscapes, fig.cap="Selection gradients acting on gall traits in complex vs.
-simple food webs.
-Each panel corresponds to a different gall trait: gall diameter (A); clutch size (B); and Oviposition preference (C).
-Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates (n=100) to show the uncertainty in estimated gradients.
-Note that only 100 bootstraps are displayed here, but that inferences are based on 1,000 bootstrapped samples."}
+```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs."}
 
@@
 
-# Replot univariate adaptive landscapes in terms of relative fitness
-
-```{r Plot Univariate RF Landscapes}
+\
+
+## Replot adaptive landscapes of gall traits in terms of relative fitness
+
+```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness."}
 
@@
 
-## Female pref
+# Female pref
 
@@
 
-# Reproduce Figure 3 presented in main text.
+## Reproduce Figure 3 in manuscript
 
@@
 
-```{r Figure-Multivariate-Landscapes}
+```{r Figure-Multivariate-Landscapes, fig.cap="Multivariate adaptive landscapes of gall phenotypes in complex and simple food webs.
+Dotted lines denote fitness for the mean phenotype.
+Arrows represent the vector of directional selection gradients acting on each phenotype."}
 
@@
 
-# Calculating Slope and Curvature of the Adaptive Landscape
+## Slope and curvature of the adaptive landscape of gall traits
 
@@
 
-## Create beta-matrix for complex food-web treatment
+# Create beta-matrix for complex food-web treatment
 complex_betas_df <- tidy_foodweb_grads %>%
@@
 
-## Create gamma-matrix for complex food-web treatment
+# Create gamma-matrix for complex food-web treatment
 complex_gammas_df <- tidy_foodweb_grads %>%
@@
 
-## Create matrix of Betas in simple food-web treatment
+# Create matrix of Betas in simple food-web treatment
 simple_betas_df <- tidy_foodweb_grads %>%
@@
 
-## Create gamma-matrix for simple food-web treatment
+# Create gamma-matrix for simple food-web treatment
 simple_gammas_df <- tidy_foodweb_grads %>%
@@
 
-## Calculate Curvature of the Fitness landscape
+# Calculate Curvature of the Fitness landscape
 complex_curvature <- complex_gammas - complex_betas %*% t(complex_betas)
@@
 
-# Estimating selection on the egg parasitoid *Platygaster*
+\
+
+## Trait-fitness relationships of the extended phenotype of the egg parasitoid *Platygaster* sp.
 
@@
 We do not change the name of the response variable to make clear that we are using the same statistical models as for Iteomyia.
-eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg_parasitoid==1,1,0))
-
+eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg.ptoid==1,1,0))
+
+# fit trait-fitness relationship using the same model structure
 eggegg_model <- update(foodweb_model, data=eggegg_df)
 
+# subset data for quantifying biased selection on chamber diameter
 biased_eggegg_df <- eggegg_df %>%
@@
 
+# quantify bias
 biased_eggegg_model <- update(biased_foodweb_model, data=biased_eggegg_df)
 ```
+
+Use parametric bootstrapping to calculating 95% confidence intervals of trait-fitness relationships.
 
@@
 
+Remove all higher-order terms to quantify linear trait-fitness relationships.
+
 ```{r Linear egg vs. egg ptoid model, cache=TRUE}
@@
 
-```{r Bootstrap linear egg vs. egg model, cache=TRUE, include=FALSE}
+And refit using parametric bootstrapping.
+
+```{r Bootstrap linear egg vs. egg model, cache=TRUE}
 boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 
-```{r Egg vs. egg ptoid alpha coefficients, include=FALSE}
+Gather regression coefficients to display trait-fitness relationships.
+
+```{r Egg vs. egg ptoid alpha coefficients}
 eggegg_bind <- bind_cols(
@@
 
-```{r Egg vs. egg ptoid coefficients}
-knitr::kable(tidy_eggegg_alphas)
-```
-
-```{r Plot egg vs. egg ptoid coefficients}
+\
+
+```{r Egg ptoid coefficients in each food-web treatment, echo=FALSE}
+tidy_eggegg_alphas %>%
+  filter(type != "Diff") %>%
+  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of trait-fitness relationships of extended phenotype of egg parasitoids in complex and simple food webs.")
+```
+
+\
+
+```{r Table of differences in egg parasitoid coefficients between food-web treatments, echo=FALSE}
+tidy_eggegg_alphas %>%
+  filter(type == "Diff") %>%
+  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in trait-fitness relationships of egg parasitoids between food-web treatment.")
+```
+
+\
+
+Visualize tables in figure form.
+
+```{r Plot egg vs.
+egg ptoid coefficients, fig.cap="Trait-fitness relationships of egg parasitoid's extended phenotype in complex and simple food webs.
+Asterisks denote significant differences (*P* < 0.05) between food-web treatments."}
 
@@
 
-```{r Egg vs. egg ptoid selection gradients, include=FALSE}
+\
+
+## Selection gradients acting on extended phenotype of the egg parasitoid
+
+```{r Egg vs. egg ptoid selection gradients}
 
@@
 
-```{r Table of egg vs. egg ptoid gradients}
-knitr::kable(tidy_eggegg_grads)
-```
-
-```{r Plot egg vs. egg ptoid gradients}
+\
+
+```{r Egg vs. ptoid selection gradients, echo=FALSE}
+tidy_eggegg_grads %>%
+  filter(type != "Diff") %>%
+  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of selection gradients acting on extended phenotype of egg parasitoids in complex and simple food webs.")
+```
+
+\
+
+```{r Table of differences in selection gradients acting on egg parasitoids between food-web treatment, echo=FALSE}
+tidy_eggegg_grads %>%
+  filter(type == "Diff") %>%
+  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in selection gradients acting on egg parasitoids between food-web treatment.")
+```
+
+\
+
+Now let's see the table results as a figure.
+
+```{r Plot egg vs.
+egg ptoid gradients, fig.cap="Selection gradients acting on egg parasitoid's extended phenotype in complex and simple food webs.
+Asterisks denote significant differences (*P* < 0.05) between food-web treatments."}
 
@@
 
-# Reproduce Figure 4 in main text
-
-```{r Egg-Parasitoid-Selection}
+## Reproduce Figure 4 in main text
+
+```{r Egg-Parasitoid-Selection, include=FALSE, eval=FALSE}
 # this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.

### 2019-01-16 analyses/reproduce_analyses.Rmd
remove old code that combined the results from each food-web treatment and egg vs. larval parasitoids into a figure of selection gradients and trait fitness relationships.

@@
 figure_egglarval_grads
-```
-
-We combine our estimates of selection gradients for each food-web treatment as well as the contribution of larval parasitoids to selection in the complex food web.
-
-```{r Figure-Selection-Gradients, fig.cap="**Selection gradients**.
-Estimates of standardized selection gradients in complex (orange) and simple (blue) food webs.
-The contribution of larval parasitoids (yellow) was estimated with a subset of the complex food-web data that only contained attacks from larval parasitoids (and gall survival).
-Points and lines correspond to estimates of the mean and 95% confidence intervals, respectively.
-Overlapping confidence intervals with zero (dotted line) indicate no strong evidence of selection.", include=FALSE}
-tidy_foodwebegglarval_grads <- bind_rows(
-  tidy_foodweb_grads, mutate(filter(tidy_egglarval_grads, type=="Complex"), type="Larval")
-)
-tidy_foodwebegglarval_grads$type <- factor(tidy_foodwebegglarval_grads$type, levels=c("Complex","Simple","Larval","Diff"))
-
-# Plot helpers
-dodge_width <- position_dodge(width=0.5)
-y_limits_foodwebegglarval_grads <- c(min(filter(tidy_foodwebegglarval_grads, type!="Diff")$conf.low), 
-                            max(filter(tidy_foodwebegglarval_grads, type!="Diff")$conf.high))
-P_asterisk_foodwebegglarval_grads <- 0.25
-P_size <- 8
-legend_foodwebegglarval_labels <- c("Egg + Larval (Complex)","Egg (Simple)","Larval")
-legend_foodwebegglarval_title <- "Parasitoids"
-point.size <- 3
-
-# Plot directional selection gradients
-plot_foodwebegglarval_directional_grads <- tidy_foodwebegglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
- # geom_text(data=filter(tidy_foodwebegglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-#            aes(y=P_asterisk_foodwebegglarval_grads, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Gradient", limits=y_limits_foodwebegglarval_grads) +
-  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
-  facet_wrap(~gradient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title)
-
-# Plot quadratic selection gradients
-plot_foodwebegglarval_quadratic_grads <- tidy_foodwebegglarval_grads %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
- # geom_text(data=filter(tidy_foodwebegglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-#            aes(y=P_asterisk_foodwebegglarval_grads, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Gradient", limits=y_limits_foodwebegglarval_grads) +
-  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
-  facet_wrap(~gradient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title)
-
-# Plot correlational selection gradients
-plot_foodwebegglarval_correlational_grads <- tidy_foodwebegglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
- # geom_text(data=filter(tidy_foodwebegglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-#            aes(y=P_asterisk_foodwebegglarval_grads, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Gradient", limits=y_limits_foodwebegglarval_grads) +
-  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
-  facet_wrap(~gradient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels, name=legend_foodwebegglarval_title)
-
-# Alt format
-legend_foodwebegglarval_grads <- get_legend(plot_foodwebegglarval_directional_grads + theme(legend.title.align = 0.5))
-
-plot_foodwebegglarval_grads <- plot_grid(
-  NULL, 
-  plot_foodwebegglarval_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
-  plot_foodwebegglarval_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
-  plot_foodwebegglarval_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
-  nrow=2, align="hv", labels = "")
-plot_legend_foodwebegglarval_grads <- ggdraw(plot_foodwebegglarval_grads) + draw_grob(legend_foodwebegglarval_grads, x = 0.1, y=0.25)
-y_title_foodwebegglarval_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
-
-figure_foodwebegglarval_grads <- plot_grid(y_title_foodwebegglarval_grads, plot_legend_foodwebegglarval_grads, ncol=2, rel_widths = c(0.05,1)) 
-figure_foodwebegglarval_grads
-```
-
-# Partitioning the components of selection gradients
-
-Selection gradients are influenced by both trait-fitness relationships and population mean fitness. Here, we partition selection gradients into these underlying components.
-
-```{r Plot foodwebegglarval coefficients, fig.cap="**Partitioning Selection Gradients.**", include=FALSE}
-tidy_foodwebegglarval_alphas <- bind_rows(
-  tidy_foodweb_alphas, mutate(filter(tidy_egglarval_alphas, type=="Complex"), type="Larval")
-)
-tidy_foodwebegglarval_alphas$type <- factor(tidy_foodwebegglarval_alphas$type, levels=c("Complex","Simple","Larval","Diff"))
-
-# Plot helpers
-dodge_width <- position_dodge(width=0.5)
-y_limits_foodwebegglarval_coefs <- c(min(filter(tidy_foodwebegglarval_alphas, type!="Diff")$conf.low), 
-                            max(filter(tidy_foodwebegglarval_alphas, type!="Diff")$conf.high))
-P_asterisk_foodwebegglarval_coefs <- 1.3
-P_size <- 8
-legend_foodwebegglarval_labels <- c("Larval","Egg")
-point.size <- 3
-
-# Plot mean fitness
-plot_foodwebegglarval_mean_fitness <- tidy_foodwebegglarval_alphas %>%
-  filter(type!="Diff", term=="(Intercept)") %>%
-  ggplot(., aes(x=type)) +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
-  scale_x_discrete(name="Parasitoids", breaks=c("Complex","Simple","Larval"), labels=c("Egg + Larval","Egg","Larval")) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
-
-# Plot linear trait-fitness relationaships
-plot_foodwebegglarval_linear_coefs <- tidy_foodwebegglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
-  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
-
-# Plot quadratic trait-fitness relationships
-plot_foodwebegglarval_quadratic_coefs <- tidy_foodwebegglarval_alphas %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
-  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
-
-# Plot correlational trait-fitness relationaships
-plot_foodwebegglarval_correlational_coefs <- tidy_foodwebegglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
-  ggplot(., aes(x=term, color=type)) +
-  geom_hline(yintercept=0, linetype="dotted") +
-  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
-  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  scale_y_continuous(name="Coefficient", limits=y_limits_foodwebegglarval_coefs) +
-  scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
-  facet_wrap(~coefficient_type) +
-  scale_fill_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels) +
-  scale_color_manual(values=cbPalette[c(6,5,4)], labels=legend_foodwebegglarval_labels)
-
-# Format plots for manuscript
-plot_foodwebegglarval_coefs <- plot_grid(
-  plot_foodwebegglarval_mean_fitness + theme(legend.position = "none"),
-  plot_foodwebegglarval_linear_coefs + theme(legend.position = "none"),
-  plot_foodwebegglarval_quadratic_coefs + theme(legend.position = "none"),
-  plot_foodwebegglarval_correlational_coefs + theme(legend.position = "none"), 
-  nrow=2, align="hv", labels = "")
-
-figure_foodwebegglarval_coefs <- plot_foodwebegglarval_coefs 
-figure_foodwebegglarval_coefs
 ```

### 2019-01-16 analyses/reproduce_analyses.Rmd
many minor edits to improve document aesthetics

@@
 
+## Setup
+
+Suppress messages, warnings, and errors for document aesthetics.
+
 ```{r setup}
-knitr::opts_chunk$set(messages=FALSE, warning=FALSE, error=FALSE)
-
-# Load required libraries ----
+knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE)
+```
+
+Read in data, packages, and required functions.
+
+```{r read data and functions, results='hide'}
+# Load required libraries
 library(car)        # for homogeneity of variance test
@@
 library(broom)      # for tidying multiple linear models
-#library(visreg)     # for quick visualizations of model effects
 library(viridis)    # for color palette
 library(lme4)       # for generalized linear mixed models
-#library(piecewiseSEM) # for calculating model R-square
 library(latex2exp)  # using Latex notation for axes labels
@@
 
-# Load and manage data ----
+# Load and manage data
 
@@
   # subset data for analysis
-  filter(#phenology == "early", Location == "tree",
-         egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
+  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% # eliminate unknown sources of mortality
   filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
@@
 
-# Custom functions to avoid repetitive code ----
+# Custom functions and parameters to avoid repetitive code
 
@@
 n_boots_analysis <- 100
-n_boots_plots <- 10
+n_boots_plots <- 100
 
@@
 ```
+
+\
 
@@
   filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
+  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
   knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
 ```
+
+\
 
@@
 ```
+
 \
@@
 
+\
+
 ```{r Table of differences in egg vs. larval coefficients, echo=FALSE}
@@
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-  #filter(ID_group == "average") %>%
   group_by(Foodweb) %>%
@@
 
-#RF_plot_egglarval_Clutch_df <- egglarval_RF_Clutch$absolute_fitness %>% 
-#  select(-sc.Diam, -sc.sqrt.Pref) %>%
-#  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-#  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-#  filter(Foodweb=="Larval", ID_group=="average") %>%
-#  group_by(Foodweb) %>%
-#  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
-#  ungroup()
-
 RF_uni_Clutch <- RF_plot_foodweb_Clutch_df %>%
-#  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-#  filter(ID_group=="average") %>%
   ggplot(., aes(x=sc.log.Clutch, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
-# Female pref
+# Oviposition preference
 
@@
 
-#RF_plot_egglarval_Pref_df <- egglarval_RF_Pref$absolute_fitness %>%
-#  select(-sc.Diam, -sc.log.Clutch) %>%
-#  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-#  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-#  filter(Foodweb=="Larval", ID_group=="average") %>%
-#  group_by(Foodweb) %>%
-#  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
-#  ungroup()
-
 RF_uni_Pref <- RF_plot_foodweb_Pref_df %>%
-#  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-#  filter(ID_group=="average") %>%
   ggplot(., aes(x=sc.sqrt.Pref, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
-#RF_plot_egglarval_Diam_df <- egglarval_RF_Diam$absolute_fitness %>% 
-#  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
-#  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-#  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
-#  mutate(Foodweb = ifelse(Foodweb=="Complex","Larval","Simple")) %>%
-#  filter(Foodweb=="Larval", ID_group=="average") %>%
-#  group_by(Foodweb) %>%
-#  mutate(relative_fitness = absolute_fitness/mean(absolute_fitness))%>%
-#  ungroup()
-
 RF_uni_Diam <- RF_plot_foodweb_Diam_df %>%
-#  mutate(Foodweb=factor(Foodweb, levels=c("Complex","Simple","Larval"), labels=c("Egg + Larval (Complex)","Egg (Simple)","Larval"))) %>%
-#  filter(ID_group=="average") %>%
   ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
+\
+
 ## Slope and curvature of the adaptive landscape of gall traits
@@
 
+\
+
 ## Reproduce Figure 4 in main text

### 2019-01-16 analyses/reproduce_analyses.Rmd
I'm now happy with the aesthetics of the reproducible analyses.

@@
 
-Read in data, packages, and required functions.
-
-```{r read data and functions, results='hide'}
-# Load required libraries
+Load required libraries.
+
+```{r required libraries, results='hide'}
 library(car)        # for homogeneity of variance test
@@
 library(MVN)        # assessing multivariate normality assumption
-
-# Load and manage data
-
-gall_selection.df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
-  # convert appropriate variables to characters instead of integers
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-
-  # subset data for analysis
-  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% # eliminate unknown sources of mortality
-  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
-  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"),
-         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber.
-I set these to 1 to permit an analysis with a binomial model.
-         # transform and scale traits to approximate multivariate normal assumption
-         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
-         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
-         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))
-
-# Custom functions and parameters to avoid repetitive code
-
+```
+
+Write custom functions to avoid repetitive code.
+
+```{r custom functions}
 # Transform logit to probability
 inverse_logit <- function(x) exp(x)/(1+exp(x))
+
+# Get confidence intervals from bootstrapped samples
+conf.high <- function(x) quantile(x, probs = 0.975)
+conf.low <- function(x) quantile(x, probs = 0.025)
 
@@
 }
-
+```
+
+Set parameters for analyses and plots.
+
+```{r set parameters}
 # Number of bootstrap replicates
@@
 
-# Get confidence intervals from bootstrapped samples
-conf.high <- function(x) quantile(x, probs = 0.975)
-conf.low <- function(x) quantile(x, probs = 0.025)
-
-# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; order -> orange, light blue, green, yellow, dark blue, red, pink
+# Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
+# order: orange, light blue, green, yellow, dark blue, red, pink
 cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
@@
 treatment_colors <- c(complex_color, simple_color)
+```
+
+Read and tidy data for analyses.
+
+```{r read and tidy data}
+
+gall_selection.df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
+  # convert appropriate variables to characters instead of integers
+  mutate(Plant_Position = as.character(Plant_Position),
+         Gall_Number = as.character(Gall_Number)) %>%
+  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
+
+  # eliminate unknown sources of mortality
+  filter(egg.ptoid > 0 | larval.ptoid > 0 | pupa > 0) %>% 
+  # excluding any larva that were parasitized by an ectoparasitoid in the exclusion experiment.
+  filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% 
+  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"), # rename Treatment to match presentation in manuscript
+         gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
+         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber.
+I set these to 1 to permit an analysis with a binomial model.
+
+         # transform and scale traits to approximate multivariate normal assumption
+         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
+         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
+         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))
 
@@
 
-```{r Egg-Parasitoid-Selection, include=FALSE, eval=FALSE}
+```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids"}
 # this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.

### 2019-01-17 manuscript.tex
updated MS prior to sending to Chris, Brendan and Arezoo. I don't like the fact that manuscript creates a cache of figures that aren't in the manuscript, but are in the reproduce_analyses cache too. Need to fix this.
rerun reproducible analyses for manuscript

@@
 \documentclass[11pt,]{article}
-\usepackage{mathpazo}
+\usepackage[]{mathpazo}
 \usepackage{amssymb,amsmath}
@@
     \usepackage{mathspec}
-    \usepackage{xltxtra,xunicode}
   \else
@@
   \fi
-  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
-  \newcommand{\euro}{€}
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
 \fi
@@
 }{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\hypersetup{unicode=true,
+            colorlinks=true,
+            linkcolor=black,
+            citecolor=black,
+            urlcolor=black,
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
 \usepackage{natbib}
 \bibliographystyle{amnat}
-\usepackage{graphicx}
+\usepackage{graphicx,grffile}
 \makeatletter
@@
 \setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
-\ifxetex
-  \usepackage[setpagesize=false, % page size defined by xetex
-              unicode=false, % unicode breaks when used with xetex
-              xetex]{hyperref}
-\else
-  \usepackage[unicode=true]{hyperref}
-\fi
-\hypersetup{breaklinks=true,
-            bookmarks=true,
-            pdfauthor={Matthew A. Barbour\^{}\{1,2,\textbackslash{}ast\}; Christopher J. Greyson-Gaito\^{}\{1,3\}; Arezoo Sootodeh\^{}\{3\}; Brendan Locke\^{}\{4\}; Jordi Bascompte\^{}\{2\}},
-            pdftitle={Phenotypic evolution is more constrained in simpler food webs},
-            colorlinks=true,
-            citecolor=black,
-            urlcolor=black,
-            linkcolor=black,
-            pdfborder={0 0 0}}
-\urlstyle{same}  % don't use monospace font for urls
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
 \setlength{\parindent}{0pt}
 \setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
 \setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
 \setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
 
@@
 
-  \title{Phenotypic evolution is more constrained in simpler food webs}
-    \author{Matthew A. Barbour\(^{1,2,\ast}\) \\ Christopher J. Greyson-Gaito\(^{1,3}\) \\ Arezoo Sootodeh\(^{3}\) \\ Brendan Locke\(^{4}\) \\ Jordi Bascompte\(^{2}\)}
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\newcommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+
+  \title{}
+    \pretitle{\vspace{\droptitle}}
+  \posttitle{}
+    \author{}
+    \preauthor{}\postauthor{}
     \date{}
-
-%%% From AmNat_MS_template.tex
-%\documentclass[11pt]{article}
-%\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
+    \predate{}\postdate{}
+
+%%% Modified from Latex Template for Am. Nat., many other details aren't necessary because they are specified in YAML header of Rmarkdown document.
 \usepackage{fullpage}
-%\usepackage[authoryear,sectionbib,sort]{natbib}
 \linespread{1.7}
-%\usepackage[utf8]{inputenc}
 \usepackage{lineno}
 
-%%%%%%% Sections not currently working properly
-%\usepackage{titlesec}
-%\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
-%\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
-%\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
-%\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
-
-%%% My added packages
-%\usepackage{amsmath} % for matrices
-%\usepackage{graphicx} % for organizing figures
-%\usepackage{lmodern} % for tilde
-%\usepackage[T1]{fontenc} % for tilde
-
-%%%%%%%%% Previous - likely useful though
-%\usepackage{setspace}\doublespacing
+% code below is important for holding figure positions in main text. Make sure to set fig.pos="H" in code chunk for figure.
 \usepackage{float}
@@
 }
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage[table]{xcolor}
+\usepackage{wrapfig}
+\usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
 
@@
 
-\maketitle
-
-\noindent 1. University of British Columbia, Department of Zoology,
+\vspace*{0.1cm}
+
+\begin{center} \LARGE Phenotypic evolution is more constrained in simpler food webs \end{center}
+
+\bigskip
+
+\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
+
+\bigskip
+
+\noindent 1. University of Zurich, Department of Evolutionary Biology
+and Environmental Studies, Zurich, 8057 ZH, Switzerland;
+
+\noindent 2. University of British Columbia, Department of Zoology,
 Vancouver, BC V6T 1Z4, Canada;
-
-\noindent 2. University of Zurich, Department of Evolutionary Biology
-and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich,
-Switzerland;
 
@@
 
-\emph{Manuscript elements}: Figure 1, figure 2, figure 3, figure 4. All
-figures should be printed in color.
+\emph{Manuscript elements}: table 1, figure 1, figure 2, figure 3,
+figure 4. All figures should be printed in color.
 
@@
 
-\emph{Keywords}: fitness landscape, host-parasitoid, natural selection,
-G-matrix, community context, ecological networks, evolutionary ecology,
-eco-evolutionary dynamics.
+\emph{Keywords}: adaptive landscape, ecological networks,
+eco-evolutionary dynamics, natural selection, host-parasitoid.
+
+\bigskip
+
+\emph{Number of words}: 5075
 
@@
 evolutionary change. Although there is clear evidence that pairwise
-interactions can shape the adaptive landscape, we do not know how the
-adaptive landscape is shaped by the community context
-\citep{McPeek2017, terHorst2018}. Resolution on how the community
-context shapes phenotypic evolution is urgently needed though, given the
-rapid impacts of climate change on ecological communities
+interactions can shape the adaptive landscape, we still have a poor
+understanding of how the adaptive landscape is shaped by the community
+context \citep{McPeek2017, terHorst2018}. Resolution on how the
+community context shapes phenotypic evolution is urgently needed though,
+given the rapid impacts of climate change on ecological communities
 \citep{Scheffers2016}.
@@
 influence larval survival based on our previous work \citep{Barbour2016}
-and others work with gall midges \citep{Weis1983, Heath2018}. First, we
+and other work with gall midges \citep{Weis1983, Heath2018}. First, we
 measured gall diameter as the size of each gall chamber to the nearest
@@
 (i.e.~bias). We used a GLMM with the same structure as described above
-except that we only modelled a linear relationship between chamber
+except that we modelled only a linear relationship between chamber
 diameter and larval survival (\(\alpha_{\text{Diam}}\)). We detected a
@@
 parasitoids actually impose directional selection for larger clutch
-sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.03, 0.23{]}). In the simple
+sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}). In the simple
 food web, we also observed clear evidence of directional selection for
@@
 effect on gall midges. Chamber diameter experienced positive directional
-selection in both food-web treatments, but selection was 65\% higher in
+selection in both food-web treatments, but selection was 66\% higher in
 complex food webs (table \ref{Table:Gradients}; fig.
@@
 and larval parasitoids (fig. \ref{fig:UV_Landscape}), but was due to the
-lower average survival in complex food webs (contrast -0.26 {[}-0.12,
+lower average survival in complex food webs (contrast -0.27 {[}-0.11,
 -0.42{]}).
@@
 0.22,
-0.47] }& 
+0.48] }& 
 \textbf{
 0.21 [
-0.13,
-0.3] }&
-
--0.13 [
--0.26,
-0.01] \\
+0.12,
+0.31] }&
+
+-0.14 [
+-0.27,
+0] \\
 
@@
 0.06 [
--0.04,
+-0.05,
 0.17] & 
@@
 -0.09 [
--0.18,
--0.02] }& 
+-0.17,
+-0.01] }& 
 \textbf{
@@
 -0.29,
--0.02] }\\
+-0.03] }\\
 
 $\beta_{\text{Pref}}$ &
--0.12 [
+-0.13 [
 -0.29,
@@
 -0.16 [
--0.25,
--0.07] }&
-
--0.04 [
--0.22,
-0.14] \\
+-0.26,
+-0.06] }&
+
+-0.03 [
+-0.21,
+0.15] \\
 
 $\gamma_{\text{Diam,Diam}}$ &
-0.14 [
+0.13 [
 -0.06,
-0.32] &
+0.33] &
 
 0.1 [
--0.03,
-0.25] &
-
--0.04 [
+-0.02,
+0.23] &
+
+-0.03 [
 -0.27,
@@
 -0.05 [
--0.25,
-0.16] &
-
--0.12 [
 -0.27,
+0.18] &
+
+-0.11 [
+-0.28,
 0.03] &
@@
 -0.06 [
--0.33,
-0.19] \\
+-0.32,
+0.2] \\
 
@@
 \textbf{
-0.33 [
-0.06,
-0.64] }&
-
-0.01 [
+0.34 [
+0.07,
+0.63] }&
+
+0.02 [
 -0.14,
-0.17] & 
+0.18] & 
 \textbf{
 -0.32 [
--0.66,
-0] }\\
+-0.64,
+-0.01] }\\
 
 $\gamma_{\text{Diam,Clutch}}$ & 
--0.05 [
--0.17,
+-0.04 [
+-0.16,
 0.08] &
@@
 -0.02 [
--0.16,
-0.13] \\
+-0.17,
+0.12] \\
 
@@
 -0.13 [
--0.28,
-0] &
+-0.29,
+0.02] &
 
 -0.02 [
--0.09,
-0.06] &
+-0.1,
+0.07] &
 
@@
 -0.05,
-0.29] \\
+0.3] \\
 
@@
 0.03 [
--0.11,
+-0.1,
 0.18] &
@@
 -0.03 [
--0.19,
+-0.18,
 0.12] \\ 
@@
 trend for nonlinear selection imposed by larval parasitoids
-(\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.01, 0.42{]}), but was also
+(\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02, 0.42{]}), but was also
 magnified by the lower average survival in complex food webs.
@@
 0 & 0 &  \\  
-0 & 0 & 0.33 \end{pmatrix}\]
+0 & 0 & 0.34 \end{pmatrix}\]
 
@@
 parasitoids in complex vs.~simple food webs (contrast
-\(\alpha_{\text{Pref}}\)= 1 {[}0.03, 2.22{]} ). Specifically, larval
+\(\alpha_{\text{Pref}}\)= 1.03 {[}0.04, 2.31{]} ). Specifically, larval
 parasitoids decreased the probability of observing egg parasitoids at
@@
 significant difference in selection (contrast \(\beta_{\text{Pref}}\)=
-0.24 {[}-0.09, 0.62{]} ). This was likely because there was a tendency
+0.25 {[}-0.09, 0.64{]} ). This was likely because there was a tendency
 (albeit not statistically signficant) for a lower probability of
 egg-parasitoid survival in complex vs.~simple food webs (contrast=0.1
-{[} -0.08, 0.31{]}), which masks this trait-fitness relationship. We
+{[} -0.09, 0.32{]}), which masks this trait-fitness relationship. We
 also observed two other interesting trends, although neither
@@
 higher gall midge densities (fig. \ref{fig:EggPtoid_Selection}; complex
-\(\alpha_{\text{Pref:Pref}}\)= -0.49 {[}-1.08, -0.1{]}; but contrast
-\(\alpha_{\text{Pref:Pref}}\)= 0.46 {[}-0.03, 1.1{]}). There was also a
+\(\alpha_{\text{Pref:Pref}}\)= -0.49 {[}-1.04, -0.13{]}; but contrast
+\(\alpha_{\text{Pref:Pref}}\)= 0.46 {[}0.02, 1.07{]}). There was also a
 tendency for egg parasitoids to obtain a refuge in large gall chambers
 at high gall midge densities (complex \(\alpha_{\text{Pref:Diam}}\)=
-0.25 {[}0.02, 0.5{]}; but contrast \(\alpha_{\text{Pref:Diam}}\)= -0.25
-{[}-0.57, 0.04{]}).
+0.25 {[}0.01, 0.54{]}; but contrast \(\alpha_{\text{Pref:Diam}}\)= -0.25
+{[}-0.6, 0.05{]}).
 
@@
 The generality of our results likely depends on the relative abundance
-and functional differences between consumers in a community. In the
-simplest case, when consumers do not differ from each other, then we do
-not expect changes in food-web complexity to modify selective
-constraints. Also, many consumers may be at too low of abundances to
-impose selection on their resources. Rank abundance curves
-\citep{Preston1948} and the disproportionate number of weak interactions
-in diverse communities \citep{Paine1992} support this notion. When
-consumers are abundant though, the effect of food-web complexity will
-depend on whether different species impose conflicting selection
-pressures or select for distinct traits. For example, parisitoids and
-birds impose conflicting selection pressures on the size of galls
-induced by the fly \emph{Eurosta solidaginis}
-\citep{Weis1985, Abrahamson1997, Start2016}. Recent studies in this
-system have shown that decreases in the relative abundance of birds, due
-to either small patch sizes \citep{Start2016} or proximity to urban
-areas \citep{Start2018} causes a shift from neutral to directional
-selection on gall size. On the other hand, different consumers may
-impose selection on different traits, favoring trait integration and
-increasing genetic constraints. Examples of this include strong genetic
-covariances in plant resistance to different insect herbivores
-\citep{Maddox1990, Wise2007, Wise2013}, although there are also examples
-where these covariances are weak \citep{Roche1997, Barbour2015}, or vary
-from year-to-year \citep{Johnson2007}. We suggest that gaining
-predictive insight to the effects of food-web disassembly requires an
+and functional differences between consumers in a community. For
+example, if consumers do not differ from each other, then we do not
+expect changes in food-web complexity to modify selective constraints.
+Also, many consumers may be at too low of abundances to impose selection
+on their resources. Rank abundance curves \citep{Preston1948} and the
+disproportionate number of weak interactions in diverse communities
+\citep{Paine1992} support this notion. When consumers are abundant
+though, the effect of food-web complexity will depend on whether
+different species impose conflicting selection pressures or select for
+distinct traits. For example, parisitoids and birds impose conflicting
+selection pressures on the size of galls induced by the fly
+\emph{Eurosta solidaginis} \citep{Weis1985, Abrahamson1997, Start2016}.
+Recent studies in this system have shown that decreases in the relative
+abundance of birds, due to either small patch sizes \citep{Start2016} or
+proximity to urban areas \citep{Start2018} causes a shift from neutral
+to directional selection on gall size. On the other hand, different
+consumers may impose selection on different traits, favoring trait
+integration and increasing genetic constraints. Examples of this include
+strong genetic covariances in plant resistance to different insect
+herbivores \citep{Maddox1990, Wise2007, Wise2013}, although there are
+also examples where these covariances are weak
+\citep{Roche1997, Barbour2015}, or vary from year-to-year
+\citep{Johnson2007}. We suggest that gaining predictive insight to the
+evolutionary consequences of food-web disassembly requires an
 understanding of the mechanisms governing the assembly of trophic
@@
 evolutionary effects that emerge in a community context
-\citep{Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018}.
+\citep{Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, StartInPress}.
 If indirect evolutionary effects are common \citep{Walsh2013}, then
@@
 
-\section{Acknowledgements}\label{acknowledgements}
-
-We thank the staff of Humboldt Bay National Wildlife Refuge (U.S. Fish
-and Wildlife Service) for facilitating experimental logistics. For
-assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
-For funding support, we thank the University of British Columbia (James
-Robert Thompson Fellowship and Four-Year Fellowship to M.A.~Barbour),
-NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
-Science Foundation (grant 31003A\_160671 to J. Bascompte).
-
-\newpage
-
-\section{Tables}\label{tables}
-
-\newpage
-
-\begin{table}[h]
-\caption{Relationship between absolute fitness (larval survival) and phenotypic traits of gall midges in complex vs. simple food webs.}
-\label{Table:Coefs}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Coefficient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
-\hline
-$\alpha_{\text{Diam}}$ & 
-\textbf{
-1.14 [
-0.73,
-1.57] }& 
-\textbf{
-1.1 [
-0.68,
-1.58] }&
-
--0.04 [
--0.57,
-0.51] \\
-
-$\alpha_{\text{Clutch}}$ & 
-0.21 [
--0.13,
-0.57] & 
-\textbf{
--0.47 [
--0.94,
--0.09] }& 
-\textbf{
--0.68 [
--1.27,
--0.13] }\\
-
-$\alpha_{\text{Pref}}$ &
--0.41 [
--0.97,
-0.15] & 
-\textbf{
--0.84 [
--1.35,
--0.36] }&
-
--0.43 [
--1.16,
-0.25] \\
-
-$\alpha_{\text{Diam,Diam}}$ &
-0.23 [
--0.1,
-0.54] &
-
-0.27 [
--0.07,
-0.65] &
-
-0.04 [
--0.43,
-0.52] \\
-
-$\alpha_{\text{Clutch,Clutch}}$ & 
--0.09 [
--0.42,
-0.26] &
-
--0.31 [
--0.71,
-0.08] &
-
--0.22 [
--0.77,
-0.31] \\
-
-$\alpha_{\text{Pref,Pref}}$ & 
-\textbf{
-0.56 [
-0.1,
-1.07] }&
-
-0.03 [
--0.38,
-0.46] &
-
--0.52 [
--1.18,
-0.09] \\
-
-$\alpha_{\text{Diam,Clutch}}$ & 
--0.16 [
--0.57,
-0.25] &
-
--0.35 [
--0.78,
-0.08] &
-
--0.19 [
--0.78,
-0.44] \\
-
-$\alpha_{\text{Diam,Pref}}$ & 
--0.44 [
--0.95,
-0.01] &
-
--0.09 [
--0.5,
-0.3] &
-
-0.36 [
--0.27,
-0.97] \\
-
-$\alpha_{\text{Clutch,Pref}}$ & 
-0.1 [
--0.37,
-0.59] &
-
-0 [
--0.37,
-0.38] &
-
--0.1 [
--0.69,
-0.49] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\alpha_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-\newpage
-
 \bibliography{references}

### 2019-01-17 temporary_morgue/Fontant_TED_index.R
moved all leftover files to original Genotype_Ptoid_Phenology_Experiment folder on my computer. Most of this is junk, temporary, mistakes, and duplicated info. I'm only retaining essential components of manuscript and study in this repository.

@@ -1,173 +1,0 @@
-######################################################################################
-# Function to compute trait evenness index TED (Fontana et al. 2015)                 
-#                                                                                     
-# It requires R libraries 'geozoo', 'flexmix' and 'geometry'                                                              #                                                
-# input:                                                                             
-# - data frame 'traits': every row represents an individual, every column a trait    
-# - NA are not allowed                                                                         
-# - ADVICE: it is generally meaningful to standardise trait values (mean=0 and sd=1)
-######################################################################################
-
-
-
-#####################
-##    TED index    ##
-#####################
-# comparison between sample and an assemblage of equidistant points (with the same number of individuals)
-
-library(geozoo)
-library(flexmix)
-library(geometry)
-
-
-#############################
-# List of possible REFERENCES
-#############################
-
-# Open biggest sample
-# Change filename to name of file with maximum points
-control.survivors <- filter(gall_selection.df, Treatment.focus=="Control", gall_survival==1) %>% 
-  select(Plant_Position, sc.Gall_Height_mm, sc.gall_individuals, sc.Density_per_100_shoots)
-nrow(control.survivors)
-
-treatment.survivors <- filter(gall_selection.df, Treatment.focus=="Ectoparasitoid exclusion", gall_survival==1) %>% 
-  select(Plant_Position, sc.Gall_Height_mm, sc.gall_individuals, sc.Density_per_100_shoots)
-nrow(treatment.survivors)
-
-traits.max <- treatment.survivors[,-1] #read.csv("File_with_maximum_points.csv",sep=",",header=T)
-
-# Define maximum number of points (max1) and number of traits under consideration (dim1)
-# Alternatively, it is possible to manually define max1 and dim1!!
-max1 <- nrow(traits.max)
-dim1 <- ncol(traits.max)
-
-ref.matrix<-matrix(ncol=2,nrow=max1)
-if (dim1 == 1) {
-  i=0.9 } else { i=1.9 }
-n <- 0
-rows1<-0
[…]

### 2019-01-17 temporary_morgue/McPeek_perspective.R

@@ -1,628 +1,0 @@
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-library(tidyverse)
-library(cowplot) # pretty default ggplots
-#library(broom) # for tidying multiple linear models
-#library(mgcv) # generalized additive models
-#library(gsg) # calculating selection gradients
-library(visreg)
-library(viridis)
-
-mean_log <- function(x) mean(log(x))
-var_log <- function(x) var(log(x))
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  # convert appropriate variables to characters instead of integers
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) 
-
-## CREATE SEPARATE DATASETS FOR SELECTION ANALYSES ----
-control_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Control")
-
-treatment_df <- gall_selection.df %>%
-  filter(Treatment.focus == "Ectoparasitoid exclusion") 
-
-# summarize each data set at tree-level
-all_tree <- gall_selection.df %>%
-  # summarise first at gall level
-  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean)) %>%
-  
-  # then summarise at the plant level
-  group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise_at(vars(Density_per_100_shoots, Gall_Height_mm, gall_individuals, gall_survival), funs(mean, var, mean_log, var_log, n())) %>%
-  ungroup() %>%
-  select(-Density_per_100_shoots_n, -Gall_Height_mm_n) %>%
-  mutate(c.Gall_Height_mm_mean = Gall_Height_mm_mean - mean(Gall_Height_mm_mean),
[…]

### 2019-01-17 temporary_morgue/brms_gradients.R

@@ -1,50 +1,0 @@
-
-predict(control.major.brm, summary = T)[ ,"Estimate"]
-control.major.gam$gam$model
-
-## TEST FUNCTION FOR CALCULATING GRADIENTS WITH BRMS
-
-Wbar <- function(x, mod, phenotype,covariates) {
-  new.d <- as.data.frame(mod$data[,c(phenotype,covariates)])
-  names(new.d)<-c(phenotype,covariates)
-  new.d2<-new.d
-  for (i in 1:length(x)) {
-    new.d[,as.character(phenotype[i])] <-
-      new.d[,as.character(phenotype[i])]+x[i]
-  }
-  
-  p <- predict(
-    object=mod,
-    newdata=new.d,
-    #newdata.guaranteed=TRUE,
-    type="response"
-  )[ ,"Estimate"]
-  return(mean(p))
-}
-
-gradients <- function(m, phenotype, covariates) {
-  nTraits = length(phenotype)
-  first.derivatives <- grad(func=Wbar, x=rep(0, nTraits), 
-                            mod=m, phenotype=phenotype, covariates=covariates)
-  second.derivatives <- hessian(func=Wbar, x=rep(0, nTraits), 
-                                mod=m, phenotype=phenotype, covariates=covariates)
-  denom <- Wbar(x=rep(0,nTraits), mod=m, phenotype=phenotype,
-                covariates=covariates)
-  
-  beta <- first.derivatives  / denom
-  gamma <- second.derivatives / denom
-  
-  #if(standardized){
-  #  sds<-apply(as.matrix(mod$model[,phenotype]),2,sd)
-  #  beta<-beta*sds
-  #  gamma<-gamma*outer(sds,sds)
-  #}
-  return( list(
-    beta  = beta,
-    gamma = gamma
-  ))
-}
-library(numDeriv)
-gradients(m = control.major.brm, phenotype = "term1", covariates = NULL)
-
-# well the first round didn't work...

### 2019-01-17 temporary_morgue/final_analysis.R

@@ -1,274 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-library(tidyverse)
-library(cowplot) # pretty default ggplots
-#library(broom) # for tidying multiple linear models
-#library(mgcv) # generalized additive models
-#library(gsg) # calculating selection gradients
-library(lme4)
-library(visreg)
-library(viridis)
-
-overdisp_fun <- function(model) {
-  ## number of variance parameters in 
-  ##   an n-by-n variance-covariance matrix
-  vpars <- function(m) {
-    nrow(m)*(nrow(m)+1)/2
-  }
-  model.df <- sum(sapply(VarCorr(model),vpars))+length(fixef(model))
-  rdf <- nrow(model.frame(model))-model.df
-  rp <- residuals(model,type="pearson")
-  Pearson.chisq <- sum(rp^2)
-  prat <- Pearson.chisq/rdf
-  pval <- pchisq(Pearson.chisq, df=rdf, lower.tail=FALSE)
-  c(chisq=Pearson.chisq,ratio=prat,rdf=rdf,p=pval)
-}
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  # convert appropriate variables to characters instead of integers
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0))) 
-
-# summarize at gall-level for gall individuals
-all_gall <- gall_selection.df %>%
-  group_by(Genotype, Treatment.focus, Plant_Position, Gall_Number) %>%
-  summarise(gall_individuals = mean(gall_individuals)) %>%
-  group_by(Genotype, Treatment.focus, Plant_Position) %>%
-  summarise(gall_sample_size = n(),
-            gall_survival_mean.gall.level = mean(gall_survival), 
-            gall_individuals_mean = mean(gall_individuals),
[…]

### 2019-01-17 temporary_morgue/gsg_models.R

@@ -1,1140 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-library(raster)
-library(tidyverse)
-library(FD)
-library(mgcv)
-library(gamm4) # for generalized additive mixed models #
-library(gsg)
-#library(lme4)
-library(cowplot) # pretty default ggplots
-#library(visreg) # quick visualizations of model outputs
-#library(brms)
-library(belg) # calculating configurational entropy of a 2D landscape
-
-#################   BE CAREFUL IN HOW DATA IS SUBSETTED !!! ###################
-
-## LOAD & MANAGE DATASET ----
-
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.character(Plant_Position),
-         Gall_Number = as.character(Gall_Number),
-         Treatment.focus = as.character(Treatment.focus),
-         Treatment = as.character(Treatment),
-         Genotype = as.character(Genotype),
-         Gall_Letter = as.character(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%                  # eliminate unknown sources of mortality
-  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
-         egg_parasitoid = as.numeric(ifelse(platy > 0, 1, 0)),
-         sc.Gall_Height_mm = as.numeric(scale(Gall_Height_mm)), # sqrt()
-         sc.gall_individuals = as.numeric(scale(gall_individuals)), # log()
-         sc.Density_per_100_shoots = as.numeric(scale(Density_per_100_shoots))) # sqrt()
-
-## GENERALIZED ADDITIVE MIXED MODELS + GENERALIZED PROJECTION PURSUIT REGRESSION ----
-
-gamm.model <- function(formula, data) {
-  gamm4(formula, data, 
-        random = ~(1|Genotype/Plant_Position/Gall_Number),
-        family = binomial(link = logit))
-}
-
-gamm.plot <- function(gamm.model, ...) {
-  plot(gamm.model$gam, seWithMean = T, shift = mean(predict(gamm.model$gam)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
-}
-
[…]

### 2019-01-17 temporary_morgue/hierarchical_explore.R

@@ -1,279 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES ----
-library(tidyverse)
-library(brms)
-library(cowplot)
-
-## LOAD DATASET ----
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.factor(Plant_Position),
-         Gall_Number = as.factor(Gall_Number),
-         Treatment.focus = as.factor(Treatment.focus),
-         Treatment = as.factor(Treatment),
-         Location = as.factor(Location),
-         phenology = as.factor(phenology),
-         Genotype = as.factor(Genotype),
-         Gall_Letter = as.factor(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis and make useful transformations
-  filter(phenology == "early", Location == "tree") %>%
-  mutate(gall_survival = ifelse(pupa > 0, 1, 0),
-         
-         # playing around with effectiveness of transformations in fitting complex models.
-         Gall_Height_mm = sqrt(Gall_Height_mm),
-         gall_individuals = log(gall_individuals),
-         Density_per_100_shoots = sqrt(Density_per_100_shoots)) # interesting that there are occassions with more than one individual within a gall chamber
-
-# get info at different hierarchical levels
-mean.NA.rm <- function(x) mean(x, na.rm = TRUE)
-
-size.gall_number <- gall_selection.df %>%
-  group_by(Genotype, Plant_Position, Gall_Number) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), mean.NA.rm) %>%
-  ungroup()
-
-size.number_plant <- size.gall_number %>%
-  group_by(Genotype, Plant_Position) %>%
-  summarise_at(vars(Gall_Height_mm, gall_individuals, Density_per_100_shoots), mean.NA.rm) %>%
-  ungroup()
-
-survival_plant <- gall_selection.df %>%
-  group_by(Treatment.focus, Genotype, Plant_Position) %>%
-  summarise_at(vars(pupa, total), sum) %>%
-  ungroup()
-
-survival_gall <- gall_selection.df %>%
-  group_by(Treatment.focus, Genotype, Plant_Position, Gall_Number) %>%
-  summarise_at(vars(pupa, total), sum) %>%
-  ungroup()
-
[…]

### 2019-01-17 temporary_morgue/hierarchical_models.R

@@ -1,93 +1,0 @@
-
-## LOAD REQUIRED LIBRARIES & SET OPTIONS ----
-library(tidyverse)
-library(brms)
-library(cowplot)
-library(bayesplot)
-
-options(mc.cores = parallel::detectCores()) # use all available cores
-
-## LOAD DATASET ----
-gall_selection.df <- read_csv("gall_selection_data.csv") %>%
-  mutate(Plant_Position = as.factor(Plant_Position),
-            Gall_Number = as.factor(Gall_Number),
-            Treatment.focus = as.factor(Treatment.focus),
-            Treatment = as.factor(Treatment),
-            Genotype = as.factor(Genotype),
-            Gall_Letter = as.factor(Gall_Letter)) %>%
-  unite(Gall_ID, Gall_Number, Gall_Letter, remove = FALSE) %>%
-  
-  # subset data for analysis
-  filter(phenology == "early", Location == "tree",
-         platy > 0 | ectos > 0 | pupa > 0) %>%     # eliminate unknown sources of mortality
-  mutate(gall_survival = ifelse(pupa > 0, 1, 0))
-
-## EXPLORE DISTRIBUTIONS OF PHENOTYPIC TRAITS.
-# important implications for selection gradient analysis
-
-trans.ind <- log(gall_selection.df$gall_individuals) # closes transformation to normality
-hist(trans.ind)
-qqnorm(trans.ind)
-qqline(trans.ind, col = "red")
-shapiro.test(trans.ind)
-
-trans.size <- gall_selection.df$Gall_Height_mm # no transformation needed
-hist(trans.size)
-qqnorm(trans.size)
-qqline(trans.size, col = "red") 
-shapiro.test(trans.size) # doesn't pass the test though
-
-trans.density <- sqrt(gall_selection.df$Density_per_100_shoots) # sqrt is the closest
-hist(trans.density)
-qqnorm(trans.density)
-qqline(trans.density, col = "red") 
-shapiro.test(trans.density)
-
-gall_selection.df <- mutate(gall_selection.df,
-                            sc.size = scale(Gall_Height_mm),
-                            sc.log.ind = scale(log(gall_individuals)),
-                            sc.sqrt.density = scale(sqrt(Density_per_100_shoots)))
-
-## SPECIFYING PRIORS ----
-
-uninf_priors <- c(set_prior("normal(0,1)", class = "b"), set_prior("normal(0,2)", class = "sd")) # generic, weakly informative priors
-
-## BAYESIAN MODEL ---- 
-
[…]

### 2019-01-17 temporary_morgue/morgue.R

@@ -1,753 +1,0 @@
-
-
-## EXPLORE DISTRIBUTIONS ----
-ggplot(gall_selection.df, aes(x = Gall_Height_mm)) + geom_histogram() + scale_x_sqrt()
-summary(gall_selection.df$Gall_Height_mm)
-summary(sqrt(gall_selection.df$Gall_Height_mm)) # most symmetric distribution around median and mean.
-summary(log(gall_selection.df$Gall_Height_mm))
-
-gall_selection.df %>%
-  distinct(Genotype, Plant_Position, Gall_Number, gall_individuals) %>% # avoids pseudo replication
-  ggplot(., aes(x = gall_individuals)) + geom_histogram() + scale_x_log10()
-summary(gall_selection.df$gall_individuals)
-summary(sqrt(gall_selection.df$gall_individuals))
-summary(log(gall_selection.df$gall_individuals)) # most symmetric distribution around median and mean.
-
-gall_selection.df %>%
-  distinct(Genotype, Plant_Position, Density_per_100_shoots) %>% # avoids pseudo replication
-  ggplot(., aes(x = sqrt(Density_per_100_shoots))) + geom_histogram() # more normal, except for low values
-summary(gall_selection.df$Density_per_100_shoots)
-summary(sqrt(gall_selection.df$Density_per_100_shoots)) # most symmetric distribution around median and mean
-summary(log(gall_selection.df$Density_per_100_shoots+1))
-
-gall_selection.df <- mutate(gall_selection.df,
-                            sc.sqrt.size = scale(sqrt(Gall_Height_mm)),
-                            sc.log.indiv = scale(log(gall_individuals)),
-                            sc.sqrt.density = scale(sqrt(Density_per_100_shoots)))
-
-# correlations among predictors are virtually absent, except for between gall size and gall density
-car::scatterplotMatrix(select(gall_selection.df, sc.sqrt.size, sc.log.indiv, sc.sqrt.density)) # closer correspondence between loess and linear fits
[…]

### 2019-01-17 temporary_morgue/raster_entropy.R

@@ -1,24 +1,0 @@
-library(raster)
-
-# Example Data
-set.seed(1)
-r <- raster(matrix(sample(1:10, 100, replace=T), 10, 10))
-
-# Calculate a weights matrix, and reset elements to 0s and 1s 
-# rather than true weights
-fw <- focalWeight(r, 0.2, 'circle')
-fw <- ifelse(fw == 0, NA, 1)
-
-# Neighbourhood richness
-richness <- function(x, ...) {
-  length(unique(na.omit(x)))
-}
-richOut <- focal(r, fw, fun=richness, pad=T)
-
-# Neighbourhood Shannon Diversity Index
-shannon <- function(x, ...) {
-  cnts <- table(x)
-  cnts <- cnts / sum(cnts)
-  -sum(cnts * log(cnts))
-}
-shanOut <- focal(r, fw, fun=shannon, pad=T)

### 2019-01-17 temporary_morgue/specifying_priors.R

@@ -1,143 +1,0 @@
-
-library(RCurl)
-library(tidyverse)
-
-gall_network_2012 <-read.csv(text=getURL("https://raw.githubusercontent.com/mabarbour/Genotype_Networks/master/raw_data_management/data/gall_network_data.csv"), header = T)
-
-vLG_network <- gall_network_2012 %>%
-  filter(gall.sp == "vLG") %>%
-  distinct(Genotype, plant.position, gall.id.nest, g.height, shootEst.all, shootEst.no18, gall_contents, value) %>%
-  spread(gall_contents, value, fill = 0)
-
-vLG_network$total <- rowSums(select(vLG_network, Eulo.fem:vLG.pupa))
-vLG_network$ectos <- rowSums(select(vLG_network, Eulo.fem, Eulo.mal, Mesopol, Ptero.2, Tory.fem, Tory.mal))
-
-vLG_counts <- vLG_network %>%
-  group_by(Genotype, plant.position) %>%
-  summarise_at(vars(total), sum) %>%
-  rename(vLG_count = total)
-
-vLG_network <- left_join(vLG_network, vLG_counts) %>%
-  mutate(Density_per_100_shoots = vLG_count/shootEst.all*100)
-
-## EXPLORATORY PLOTS ----
-density.cut.2012 <- quantile(vLG_network$Density_per_100_shoots, probs = c(0,0.33,0.66,1), include.lowest = TRUE)
-vLG_network %>%
-  mutate(density.cut = cut(Density_per_100_shoots, density.cut.2012)) %>%
-  ggplot(., aes(x = g.height, y = vLG.pupa/total, weight = total)) +
-  geom_point(alpha = 0.5, aes(size = total)) +
-  binomial_smooth(formula = y ~ x) + facet_wrap(~density.cut)
-  
-
-## CONTINUED ----
-
-hist(vLG_network$g.height)
-hist(sqrt(vLG_network$g.height))
-
-hist(vLG_network$Density_per_100_shoots)
-hist(sqrt(vLG_network$Density_per_100_shoots))
-
-vLG_network <- mutate(vLG_network,
-                      sc.sqrt.size = (sqrt(g.height) - mean(sqrt(g.height), na.rm = T))/sd(sqrt(g.height), na.rm = T),
-                      sc.size = (g.height - mean(g.height, na.rm = T))/sd(g.height, na.rm = T),
[…]

### 2019-01-17 data/raw_data_management/finalize_manuscript_dataset.Rmd
moved to a new folder and changed file path

--- 2019-01-16 finalize_manuscript_dataset.Rmd
@@
 ```{r Filter dataset}
-gall_selection.df <- read_csv("data/raw_data_management/gall_selection_data.csv") %>%
+gall_selection.df <- read_csv("gall_selection_data.csv") %>%
   filter(phenology == "early", Location == "tree") %>%

### 2019-01-22 manuscript.Rmd
rerun reproducible analyses for manuscript
minor edits to manuscript.

@@
 ## Reproduce analyses ----
-rmarkdown::render("analyses/reproduce_analyses.Rmd")
+knitr::knit("analyses/reproduce_analyses.Rmd")
 
@@
 This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
+Stem cuttings of each genotype (25 replicates per genotype) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
 Willows at our study site begin flowering in February and reach their peak growth in early August.
@@
 Measuring larval densities on plants in the field is a common method for measuring oviposition preference [@Gripenberg2010]; however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference [@Singer1986].
-Fortunately, a couple of features of our study system suggest that larval densities may be a good proxy for oviposition preference.
+Fortunately, a couple features of our study system suggest that larval densities may be a good proxy for oviposition preference.
 For example, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
@@
 
-Our analyses consisted of three parts.
+Our analysis consisted of three parts.
 First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and phenotypic traits ($z_i$) of individuals \textemdash in each food-web treatment.
@@
 We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
+Data and code to reproduce these analyses is publically available at the GitHub repository: https://github.com/mabarbour/complexity_selection.
 
@@
 \ref{fig:UV_Landscape}C).
-This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids (fig.
-\ref{fig:UV_Landscape}).
+This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
 Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
@@
 \ref{fig:UV_Landscape}).
-This was not due to any difference between egg and larval parasitoids (fig.
-\ref{fig:UV_Landscape}), but was due to the lower average survival in complex food webs (contrast `r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean*-1, 2)`
+This was not due to any difference between egg and larval parasitoids (\alpha_{Diam} contrast =
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was due to the lower average survival in complex food webs (contrast `r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean*-1, 2)`
 [`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low*-1, 2)`,
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }& 
-
+\textbf{
 `r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
 `r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
 
@@
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype (i.e., all traits = 0) in each food-web treatment.
+Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
 Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the simple vs.
@@
 When consumers are abundant though, the effect of food-web complexity will depend on whether different species impose conflicting selection pressures or select for distinct traits.
-For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997; @Start2016].
+For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
 Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.

### 2019-01-22 manuscript.Rmd
added new table and made extended phenotype paragraph much simpler.

@@
 
-*Manuscript elements*: table 1, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
+*Manuscript elements*: table 1, table 2, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
 
@@
 \ref{fig:UV_Landscape}).
-This was not due to any difference between egg and larval parasitoids (\alpha_{Diam} contrast =
+This was not due to any difference between egg and larval parasitoids ($\beta_{Diam}$ contrast =
 `r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
@@
 
+Only gall midge preference influenced the probability of observing egg parasitoids in complex vs.
+simple food webs (table \ref{Table:ExtendedGradients}).
+Specifically, the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
+\ref{fig:EggPtoid_Selection}).
+
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on the extended phenotype of the egg parasitoid \textit{Platygaster} sp.}
+\label{Table:ExtendedGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Contrast}  \\ 
+\hline
+$\beta_{\text{Diam}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\beta_{\text{Clutch}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
+
+$\beta_{\text{Pref}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref,Pref}}$ &
+
+\textbf{
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Pref}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Pref}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+<!--
 Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\alpha_{\text{Pref}}$=
@@
 `r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]).
+-->
 

### 2019-01-22 manuscript.Rmd
multiplied "Diff" gradients by -1 so Contrast = Complex - Simple

--- 2019-01-22 manuscript.Rmd
@@
 \ref{fig:UV_Landscape}).
-This was not due to any difference between egg and larval parasitoids (\alpha_{Diam} contrast =
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was due to the lower average survival in complex food webs (contrast `r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean*-1, 2)`
-[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low*-1, 2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high*-1, 2)`]).
+This was not due to any difference between egg and larval parasitoids ($\beta_{\text{Diam}}$ contrast =
+`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was due to the lower average survival in complex food webs ($\bar W$ contrast `r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean, 2)`
+[`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low, 2)`,
+`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high, 2)`]).
 
@@
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
 
@@
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
 
@@
 
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
 
@@
 
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
 
@@
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
 
@@
 
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
 
@@
 
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
 \hline
@@
 
+Only gall midge preference influenced the probability of observing egg parasitoids in complex vs.
+simple food webs (table \ref{Table:ExtendedGradients}).
+Specifically, the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
+\ref{fig:EggPtoid_Selection}).
+
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on the extended phenotype of the egg parasitoid \textit{Platygaster} sp.}
+\label{Table:ExtendedGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Contrast = Complex - Simple}  \\ 
+\hline
+$\beta_{\text{Diam}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\beta_{\text{Clutch}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
+
+$\beta_{\text{Pref}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref,Pref}}$ &
+
+\textbf{
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam,Pref}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch,Pref}}$ &
+
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+<!--
 Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\alpha_{\text{Pref}}$=

### 2019-01-22 manuscript.Rmd
tidy edit to Table 2 name
added Zenodo DOI

@@
 We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
-Data and code to reproduce these analyses is publically available at the GitHub repository: https://github.com/mabarbour/complexity_selection.
+All data and code to reproduce the reported results are publically available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
 
@@
 \begin{table}[h]
-\caption{Standardized selection gradients acting on the extended phenotype of the egg parasitoid \textit{Platygaster} sp.}
+\caption{Standardized selection gradients acting on the extended phenotype of egg parasitoids (\textit{Platygaster} sp.)}
 \label{Table:ExtendedGradients}

### 2019-01-22 manuscript.tex
finalize manuscript for bioRxiv

@@
 
-\emph{Manuscript elements}: table 1, figure 1, figure 2, figure 3,
-figure 4. All figures should be printed in color.
+\emph{Manuscript elements}: table 1, table 2, figure 1, figure 2, figure
+3, figure 4. All figures should be printed in color.
 
@@
 
-\emph{Number of words}: 5075
+\emph{Number of words}: 5069
 
@@
 growing around Humboldt Bay. Stem cuttings of each genotype (25
-replicates per genotypes) were planted in a completely randomized design
+replicates per genotype) were planted in a completely randomized design
 in two hectares of a former cattle pasture at HBNWR. Willows at our
@@
 processes other than preference \citep{Singer1986}. Fortunately, a
-couple of features of our study system suggest that larval densities may
-be a good proxy for oviposition preference. For example, since our data
+couple features of our study system suggest that larval densities may be
+a good proxy for oviposition preference. For example, since our data
 comes from a randomized placement of plant genotypes in a common garden,
@@
 
-Our analyses consisted of three parts. First, we used generalized linear
+Our analysis consisted of three parts. First, we used generalized linear
 mixed models (GLMM) to quantify selection surfaces \textemdash linear
@@
 reflect the mathematical definition of the adaptive landscape
-\citep{Arnold2003}.
+\citep{Arnold2003}. All data and code to reproduce the reported results
+are publically available on GitHub
+(\url{https://github.com/mabarbour/complexity_selection}) and have been
+archived on Zenodo (\url{https://zenodo.org/badge/latestdoi/108833263}).
 
@@
 absence of selection appeared to be a result of conflicting selection
-pressures imposed by each guild of parasitoids (fig.
-\ref{fig:UV_Landscape}). Specifically, when we subset our data to focus
-on differences between parasitoid guilds, we found that larval
-parasitoids actually impose directional selection for larger clutch
-sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}). In the simple
-food web, we also observed clear evidence of directional selection for
-midges to avoid ovipositing on plants with high densities of
-conspecifics (table \ref{Table:Gradients}; fig.
+pressures imposed by each guild of parasitoids. Specifically, when we
+subset our data to focus on differences between parasitoid guilds, we
+found that larval parasitoids actually impose directional selection for
+larger clutch sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}).
+In the simple food web, we also observed clear evidence of directional
+selection for midges to avoid ovipositing on plants with high densities
+of conspecifics (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}B); however, this relationship was weaker in
@@
 \ref{fig:UV_Landscape}). This was not due to any difference between egg
-and larval parasitoids (fig. \ref{fig:UV_Landscape}), but was due to the
-lower average survival in complex food webs (contrast -0.27 {[}-0.11,
--0.42{]}).
+and larval parasitoids (\(\beta_{\text{Diam}}\) contrast = 0.01 {[}
+0.15, -0.11{]}), but was due to the lower average survival in complex
+food webs (\(\bar W\) contrast -0.27 {[}-0.11, -0.42{]}).
 
@@
 0.31] }& 
-
--0.14 [
--0.27,
-0] \\
+\textbf{
+0.14 [
+0.27,
+0] }\\
 
@@
 \textbf{
--0.15 [
--0.29,
--0.03] }\\
+0.15 [
+0.29,
+0.03] }\\
 
@@
 
--0.03 [
--0.21,
-0.15] \\
+0.03 [
+0.21,
+-0.15] \\
 
@@
 
--0.03 [
--0.27,
-0.2] \\
+0.03 [
+0.27,
+-0.2] \\
 
@@
 
--0.06 [
--0.32,
-0.2] \\
+0.06 [
+0.32,
+-0.2] \\
 
@@
 \textbf{
--0.32 [
--0.64,
--0.01] }\\
+0.32 [
+0.64,
+0.01] }\\
 
@@
 
--0.02 [
--0.17,
-0.12] \\
+0.02 [
+0.17,
+-0.12] \\
 
@@
 
-0.12 [
--0.05,
-0.3] \\
+-0.12 [
+0.05,
+-0.3] \\
 
@@
 
--0.03 [
--0.18,
-0.12] \\ 
+0.03 [
+0.18,
+-0.12] \\ 
 \hline
@@
 represent mean estimates of directional selection gradients, while
-contours represent predicted larval survival of the mean phenotype
-(i.e., all traits = 0) in each food-web treatment. Notice that arrows
-point more toward a corner of the adaptive landscape for each
-combination of traits in the simple vs.~complex food-web treatment. This
-indicates that trait integration (covariance) is more strongly favored
-in simpler vs.~more complex food webs. Note that mean larval survival is
-plotted on a natural log scale to reflect the mathematical definition of
-the adaptive landscape.}
+contours represent predicted larval survival of the mean phenotype in
+each food-web treatment. Notice that arrows point more toward a corner
+of the adaptive landscape for each combination of traits in the simple
+vs.~complex food-web treatment. This indicates that trait integration
+(covariance) is more strongly favored in simpler vs.~more complex food
+webs. Note that mean larval survival is plotted on a natural log scale
+to reflect the mathematical definition of the adaptive landscape.}
 \end{figure}
@@
 
-Gall midge preference influenced the probability of observing egg
-parasitoids in complex vs.~simple food webs (contrast
-\(\alpha_{\text{Pref}}\)= 1.03 {[}0.04, 2.31{]} ). Specifically, larval
-parasitoids decreased the probability of observing egg parasitoids at
-high gall midge densities (fig. \ref{fig:EggPtoid_Selection}). Note
-however that this trait-fitness relationship did not translate into a
-significant difference in selection (contrast \(\beta_{\text{Pref}}\)=
-0.25 {[}-0.09, 0.64{]} ). This was likely because there was a tendency
-(albeit not statistically signficant) for a lower probability of
-egg-parasitoid survival in complex vs.~simple food webs (contrast=0.1
-{[} -0.09, 0.32{]}), which masks this trait-fitness relationship. We
-also observed two other interesting trends, although neither
-significantly differed between treatments. Specifically, there was a
-tendency for the impact of larval parasitoids to increase nonlinearly at
-higher gall midge densities (fig. \ref{fig:EggPtoid_Selection}; complex
-\(\alpha_{\text{Pref:Pref}}\)= -0.49 {[}-1.04, -0.13{]}; but contrast
-\(\alpha_{\text{Pref:Pref}}\)= 0.46 {[}0.02, 1.07{]}). There was also a
-tendency for egg parasitoids to obtain a refuge in large gall chambers
-at high gall midge densities (complex \(\alpha_{\text{Pref:Diam}}\)=
-0.25 {[}0.01, 0.54{]}; but contrast \(\alpha_{\text{Pref:Diam}}\)= -0.25
-{[}-0.6, 0.05{]}).
+Only gall midge preference influenced the probability of observing egg
+parasitoids in complex vs.~simple food webs (table
+\ref{Table:ExtendedGradients}). Specifically, the impact of larval
+parasitoids increased nonlinearly with higher gall midge densities (fig.
+\ref{fig:EggPtoid_Selection}).
+
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on the extended phenotype of egg parasitoids (\textit{Platygaster} sp.)}
+\label{Table:ExtendedGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Contrast = Complex - Simple}  \\ 
+\hline
+$\beta_{\text{Diam}}$ &
+
+-0.03 [
+0.25,
+-0.3] \\
+
+$\beta_{\text{Clutch}}$ &
+
+0.07 [
+0.38,
+-0.26] \\
+
+$\beta_{\text{Pref}}$ &
+
+-0.25 [
+0.09,
+-0.64] \\
+
+$\gamma_{\text{Diam,Diam}}$ &
+
+-0.05 [
+0.33,
+-0.43] \\
+
+$\gamma_{\text{Clutch,Clutch}}$ &
+
+-0.21 [
+0.26,
+-0.68] \\
+
+$\gamma_{\text{Pref,Pref}}$ &
+
+\textbf{
+-0.46 [
+-0.02,
+-1.07] }\\
+
+$\gamma_{\text{Diam,Clutch}}$ &
+
+0 [
+0.27,
+-0.29] \\
+
+$\gamma_{\text{Diam,Pref}}$ &
+
+0.25 [
+0.6,
+-0.05] \\
+
+$\gamma_{\text{Clutch,Pref}}$ &
+
+-0.18 [
+0.12,
+-0.52] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
 
@@
 selection pressures on the size of galls induced by the fly
-\emph{Eurosta solidaginis} \citep{Weis1985, Abrahamson1997, Start2016}.
-Recent studies in this system have shown that decreases in the relative
+\emph{Eurosta solidaginis} \citep{Weis1985, Abrahamson1997}. Recent
+studies in this system have shown that decreases in the relative
 abundance of birds, due to either small patch sizes \citep{Start2016} or

### 2019-01-22 manuscript.Rmd
deleted old commented out text from selection on extended phenotype paragraph.

@@
 
-<!--
-Gall midge preference influenced the probability of observing egg parasitoids in complex vs. simple food webs (contrast $\alpha_{\text{Pref}}$=
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
-).
-Specifically, larval parasitoids decreased the probability of observing egg parasitoids at high gall midge densities (fig.
-\ref{fig:EggPtoid_Selection}).
-Note however that this trait-fitness relationship did not translate into a significant difference in selection (contrast $\beta_{\text{Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`]
-). This was likely because there was a tendency (albeit not statistically signficant) for a lower probability of egg-parasitoid survival in complex vs. simple food webs 
-(contrast=`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$mean,2)` [
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]), which masks this trait-fitness relationship.
-We also observed two other interesting trends, although neither significantly differed between treatments.
-Specifically, there was a tendency for the impact of larval parasitoids to increase nonlinearly at higher gall midge densities (fig.
-\ref{fig:EggPtoid_Selection}; complex $\alpha_{\text{Pref:Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]; but contrast $\alpha_{\text{Pref:Pref}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]).
-There was also a tendency for egg parasitoids to obtain a refuge in large gall chambers at high gall midge densities (complex $\alpha_{\text{Pref:Diam}}$=
-`r round(filter(tidy_eggegg_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]; but contrast $\alpha_{\text{Pref:Diam}}$=
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` 
-[`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]).
--->
-
 ```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).

### 2019-01-22 manuscript.tex
add Acknowledgements back to manuscript for bioRxiv submission.

@@
 
-\emph{Number of words}: 5069
+\emph{Number of words}: 5138
 
@@
 
+\section{Acknowledgements}\label{acknowledgements}
+
+We thank the staff of Humboldt Bay National Wildlife Refuge (U.S. Fish
+and Wildlife Service) for facilitating experimental logistics. For
+assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
+For funding support, we thank the University of British Columbia (James
+Robert Thompson Fellowship and Four-Year Fellowship to M.A.~Barbour),
+NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
+Science Foundation (grant 31003A\_160671 to J. Bascompte).
+
 \bibliography{references}

### 2019-01-22 manuscript.Rmd
add Acknowledgements to bioRxiv submission.
prepped for Am Nat double-blind peer review: removed author identification info, links to repositories, and changed references to prior work to third person.

@@
 
-<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission -->
+<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission 
 \begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
@@
 \bigskip
-
+-->
 *Manuscript elements*: table 1, table 2, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
@@
 
-We collected data on three different traits that we expected to influence larval survival based on our previous work [@Barbour2016] and other work with gall midges [@Weis1983; @Heath2018].
+We collected data on three different traits that we expected to influence larval survival based on previous work in this system [@Barbour2016] and other work with gall midges [@Weis1983; @Heath2018].
 First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
-Our previous work has shown that larger galls are associated with higher survival [@Barbour2016].
+Previous work in this system has shown that larger galls are associated with higher survival [@Barbour2016].
 Second, we measured clutch size by counting the number of chambers in each gall [@Weis1983; @Heath2018].
@@
 We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
-All data and code to reproduce the reported results are publically available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
+All data and code to reproduce the reported results are publically available on GitHub <!--(https://github.com/mabarbour/complexity_selection)-->and have been archived on Zenodo (links are available from the journal office)<!--(https://zenodo.org/badge/latestdoi/108833263)-->.
 
@@
 -->
-
 <!-- TABLE NOT REFERENCED IN RESULTS

### 2019-01-22 manuscript.tex
update pdf without author identifying info

--- 2019-01-22 manuscript.tex
@@
 
-\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
-
-\bigskip
-
-\noindent 1. University of Zurich, Department of Evolutionary Biology
-and Environmental Studies, Zurich, 8057 ZH, Switzerland;
-
-\noindent 2. University of British Columbia, Department of Zoology,
-Vancouver, BC V6T 1Z4, Canada;
-
-\noindent 3. University of Guelph, Department of Integrative Biology,
-Guelph, ON N1G 2W1, Canada;
-
-\noindent 4. Humboldt State University, Department of Biological
-Sciences, Arcata, CA 95521, USA.
-
-\(^\ast\) Corresponding author; e-mail:
-\href{mailto:matthew.barbour@ieu.uzh.ch}{\nolinkurl{matthew.barbour@ieu.uzh.ch}}
-
-\bigskip
-
 \emph{Manuscript elements}: table 1, table 2, figure 1, figure 2, figure
@@
 
-\emph{Number of words}: 5069
+\emph{Number of words}: 5080
 
@@
 We collected data on three different traits that we expected to
-influence larval survival based on our previous work \citep{Barbour2016}
-and other work with gall midges \citep{Weis1983, Heath2018}. First, we
-measured gall diameter as the size of each gall chamber to the nearest
-0.01 mm at its maximum diameter (perpendicular to the direction of plant
-tissue growth). Our previous work has shown that larger galls are
-associated with higher survival \citep{Barbour2016}. Second, we measured
-clutch size by counting the number of chambers in each gall
+influence larval survival based on previous work in this system
+\citep{Barbour2016} and other work with gall midges
+\citep{Weis1983, Heath2018}. First, we measured gall diameter as the
+size of each gall chamber to the nearest 0.01 mm at its maximum diameter
+(perpendicular to the direction of plant tissue growth). Previous work
+in this system has shown that larger galls are associated with higher
+survival \citep{Barbour2016}. Second, we measured clutch size by
+counting the number of chambers in each gall
 \citep{Weis1983, Heath2018}. All larvae collected from the same
@@
 \citep{Arnold2003}. All data and code to reproduce the reported results
-are publically available on GitHub
-(\url{https://github.com/mabarbour/complexity_selection}) and have been
-archived on Zenodo (\url{https://zenodo.org/badge/latestdoi/108833263}).
+are publically available on GitHub and have been archived on Zenodo
+(links are available from the journal office).
 

### 2019-01-22 manuscript.Rmd
edit misspelling

@@
 We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
-All data and code to reproduce the reported results are publically available on GitHub <!--(https://github.com/mabarbour/complexity_selection)-->and have been archived on Zenodo (links are available from the journal office)<!--(https://zenodo.org/badge/latestdoi/108833263)-->.
+All data and code to reproduce the reported results are publicly available on GitHub <!--(https://github.com/mabarbour/complexity_selection)-->and have been archived on Zenodo (links are available from the journal office)<!--(https://zenodo.org/badge/latestdoi/108833263)-->.
 

### 2019-03-29 manuscript.Rmd
edited intro to remove focus on community complexity.

@@
 Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the community context of evolving populations as a ``black box''.
-Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web complexity shape evolutionary constraints.
-We conducted a field experiment that manipulated the diversity of insect parasitoids (food-web complexity) that were able to impose selection on an insect herbivore.
+Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web structure shape evolutionary constraints.
+We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an insect herbivore.
 We then measured herbivore survival as a function of three key phenotypic traits.
@@
 The adaptive landscape was more neutral in complex food webs because different parasitoid species impose different selection pressures, minimizing relative fitness differences among phenotypes.
-Our results suggest that phenotypic evolution becomes more constrained in simplified food webs.
+Our results suggest that the loss of species interactions can impose greater constraints on phenotypic evolution.
 This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
@@
 
-Global change is simplifying the structure of ecological communities, which may influence evolutionary constraints in a number of ways.
-For example, in a multitrophic community or food web, if different consumers impose directional selection on different traits of a shared resource, then more complex food webs may constrain evolution by increasing the number of traits under selection.
-Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more complex food webs.
-To examine these different possibilities, we conducted a field experiment that manipulated the complexity of trophic interactions (hereafter food-web complexity) associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
+Global change is altering the structure of ecological communities, which may influence evolutionary constraints in a number of ways.
+For example, in a multitrophic community or food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection.
+Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities.
+To examine these different possibilities, we conducted a field experiment that simulated the extinction of a consumer guild associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
 \ref{fig:Conceptual}).
@@
 ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016].
-We manipulated food-web complexity by either excluding the guild of larval parasitoids (simple food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (complex food web; fig.
+We manipulated food-web structure by either excluding or allowing the guild of larval parasitoids to impose selection on gall midge and egg parasitoid traits (fig.
 \ref{fig:Conceptual}).
-We then applied modern statistical methods to quantify the effect of food-web complexity on the slope and curvature of the gall midge's adaptive landscape.
-Taken together, our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, may constrain the evolution of interacting populations.
+We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the adaptive landscape of the gall midge and egg parasitoid.
+Taken together, our study gives insight to how local extinctions may constrain the evolution of interacting populations.
 

### 2019-03-29 manuscript.Rmd
edited discussion to reduce emphasis on food-web complexity.

@@
 <!--Summary-->
-We found that simpler food webs constrained phenotypic evolution in gall midges in two key ways.
-First, more traits contributed to the slope of the adaptive landscape in the simpler food web, suggesting greater constraints on the trajectory of phenotypic evolution.
-Second, the simple food-web treatment indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
-We also found evidence of indirect selection pressures in more complex food webs, suggesting that the adaptive landscape may be more dynamic in complex food webs.
-Taken together, our study provides experimental evidence from the field that the simplification of ecological communities may constrain the adaptive potential of remaining populations.
+We found that the extinction of larval parasitoids constrained phenotypic evolution in gall midges in two key ways.
+First, more traits contributed to the slope of the adaptive landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
+Second, excluding larval parasitoids indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
+Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of species interactions may have complex effects on the trajectories of phenotypic evolution.
+Taken together, our study provides experimental evidence from the field that the loss of species interactions may constrain the adaptive potential of remaining populations.
 
 <!--Selective constraints-->
-All three phenotypic traits we examined experienced directional selection in the simpler food web, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
+All three phenotypic traits we examined experienced directional selection in the absence of larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
 large chamber diameter, small clutch size, and avoidance of conspecifics).
-In contrast, we did not observe selective constraints on clutch size and oviposition preference in the more complex food web.
+In contrast, we did not observe selective constraints on clutch size and oviposition preference in the presence of larval parasitoids.
 This suggests that there are many optimal phenotypes (adaptive peaks), or in this case, a flat adaptive landscape where there are no fitness consequences for phenotypic change in these traits.
+<!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
 This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by genetic constraints.
@@
 <!--Indirect effects of selective constraints-->
-We also found evidence for more genetic constraints in simpler food webs due to indirect effects of selection on the population's G-matrix.
+We also found evidence for more genetic constraints when we excluded larval parasitoids due to indirect effects of selection on the population's G-matrix.
 The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
@@
 Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
-Together, this suggests that simpler food webs may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
+Together, this suggests that the loss of species interactions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
 Current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the community context [@McPeek2017; @Guimaraes2017].
@@
 The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
-For example, if consumers do not differ from each other, then we do not expect changes in food-web complexity to modify selective constraints.
+For example, if consumers do not differ from each other, then we do not expect changes in food-web structure to modify selective constraints.
 Also, many consumers may be at too low of abundances to impose selection on their resources.
 Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
-When consumers are abundant though, the effect of food-web complexity will depend on whether different species impose conflicting selection pressures or select for distinct traits.
+When consumers are abundant though, the effect of food-web structure will depend on whether different species impose conflicting selection pressures or select for distinct traits.
 For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
@@
 <!--Indirect evolutionary effects-->
-Our results suggest that the simplification of ecological communities may not only directly affect connected species, but also result in indirect evolutionary effects.
-In our study, this indirect effect arises from egg parasitoids being released from intraguild predation in simpler food webs.
+Our results suggest that the loss of species interactions may not only directly affect connected species, but also result in indirect evolutionary effects.
+In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we exlcuded larval parasitoids.
 This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
 A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @StartInPress].
-If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the simplification of food webs will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
+If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the loss of species interactions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 
@@
 This work has given insight to the mechanisms by which pairwise interactions modify the adaptive potential of species.
-Our study hints at a novel mechanism, whereby food-web complexity flattens the adaptive landscape, thus facilitating future adaptation by allowing genetic and phenotypic variation to persist.
+Our study hints at a novel mechanism, whereby more complex food webs flatten the adaptive landscape, thus facilitating future adaptation by allowing genetic and phenotypic variation to persist.
 This mechanism only emerges once we move beyond pairwise interactions to consider selection on multiple traits in a community context.
@@
 <!-- Conclusions -->
-Our study gives insight to how local extinctions, and concomitant decreases in food-web complexity, increase evolutionary constraints.
-This hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
+Our study gives insight to how local extinctions alter evolutionary constraints on remaining populations.
+In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
 Our work also highlights some key challenges for predicting phenotypic evolution in the face of global change.
@@
 Second, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait, yet our results highlight that the number of traits under selection may change with the community context.
-Importantly, while the net effects of selection in complex communities may be dampened, we still found that different species/guilds imposed different selection pressures.
+Importantly, we found that different species/guilds imposed different selection pressures.
 Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the community context.

### 2019-03-29 manuscript.Rmd
edit methods and a bit of results to reduce emphasis on food-web complexity. Also altered wording to make clear that I standardized traits for all treatments.

@@
 
-```{r Conceptual, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web complexity associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
+```{r Conceptual, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
 Black arrows denote the flow of energy in this network of trophic interactions.
@@
 
-## Manipulating Food-web Complexity
+## Manipulating Food-web Structure
 
@@
 These 128 plants came from eight different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
-For the complex food-web treatment (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
+As a control (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
-For the simple food-web treatment, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
+To exclude the guild of larval parasitoids, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
 This treatment did not exclude the egg parasitoid *Platygaster* sp., which attacks prior to gall initiation [larva initiate gall development in Cecidomyiid midges: @Gagne1989].
@@
 Since we were interested in selection imposed by parasitoids, we excluded unknown sources of mortality.
-For the food-web treatment that excluded larval parasitoids (simple food web), we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
+For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
 This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
@@
 
+Inferring adaptive landscapes assumes that trait distributions are multivariate normal [@Lande1983]. 
+To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
+To ensure that our estimates of selection were comparable across traits and with other studies, we scaled all phenotypic traits (mean=0 and SD=1) prior to our analyses (detailed below).
+
 Our analysis consisted of three parts.
-First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and phenotypic traits ($z_i$) of individuals \textemdash in each food-web treatment.
-Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate selection gradients.
+First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($z_i$) of individuals \textemdash in each food-web treatment.
+Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients.
 Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape.
-Note that inferring adaptive landscapes from selection surfaces assumes that trait distributions are multivariate normal [@Lande1983].
-To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
-We then scaled all phenotypic traits (mean=0 and SD=1) in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
 
@@
 
-**Evolutionary constraints**: We quantified the effects of food-web complexity on evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
+**Evolutionary constraints**: We quantified the effects of food-web structure on evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
 The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
@@
 $$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-By comparing the number of traits that determine the slope (i.e., nonzero directional selection gradients) in simpler vs.
-more complex food webs, we can infer the effect of food-web complexity on selective constraints.
+By comparing the number of traits that determine the slope (i.e., nonzero directional selection gradients) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
 
@@
 bias).
-We used a GLMM with the same structure as described above except that we modelled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
+We used a GLMM with the same structure as described above except that we modeled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
 We detected a positive bias in both food-web treatments (complex $\alpha_{\text{Diam}}$=
@@
 Using the same models as described above, we substituted egg parasitism as our response variable to quantify trait-fitness relationships and selection gradients acting on the egg parasitoid.
-Note that we cannot test the effect of food-web complexity on the egg parasitoid's adaptive landscape ---we can only estimate the selection imposed by larval parasitoids.
+Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate the selection imposed by larval parasitoids.
 This comparison is still useful though in determining the extent to which the community context may have indirect evolutionary effects by altering selection on multiple interacting populations.
@@
 
-## Simpler food webs increase selective constraints
+## Loss of species interactions increase selective constraints
 
@@
 
-## Simpler food webs increase genetic constraints
+## Loss of species interactions increase genetic constraints
 
@@
 
-To estimate the net effect of food-web complexity on the curvature ($C$) of the adaptive landscape, we only retained nonzero selection gradients (i.e.
+To estimate the net effect of food-web structure on the curvature ($C$) of the adaptive landscape, we only retained nonzero selection gradients (i.e.
 95\% CI did not overlap zero) prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
@@
 
-Only gall midge preference influenced the probability of observing egg parasitoids in complex vs.
-simple food webs (table \ref{Table:ExtendedGradients}).
+The exctinction of larval parasitoids only altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}).
 Specifically, the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.

### 2019-03-29 analyses/reproduce_analyses.Rmd
reset bootstraps to 1000 for statistical inferences.
added code to calculate curvature. the problem is that bootstrapped gammas and betas are estimated from different models, so bootstrap i for the gammas doesn't correspond to bootstrap i for the betas. I'm going to start a branch that alters upstream code to implement poly(x,2) so I can estimate linear (betas) and nonlinear terms (gammas) within the same model.

@@
 # Number of bootstrap replicates
-n_boots_analysis <- 100
+n_boots_analysis <- 1000
 n_boots_plots <- 100
@@
 \
+
+```{r Curvature, echo=FALSE}
+# Calculate curvatures for complex food web
+foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
+  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
+         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
+         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
+         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)
+
+# Calculate curvatures for simple food web
+foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
+  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.Diam`,
+         `FoodwebSimple:C.Clutch` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.log.Clutch`,
+         `FoodwebSimple:C.Pref` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebSimple:sc.sqrt.Pref`*`FoodwebSimple:sc.sqrt.Pref`,
+         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.log.Clutch`,
+         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.sqrt.Pref`,
+         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.sqrt.Pref`)
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+foodweb_curvs <- bind_cols(foodweb_complex_raw_curvs, foodweb_simple_raw_curvs) %>%
+  mutate(`FoodwebDiff:C.Diam` = `FoodwebSimple:C.Diam` - `FoodwebComplex:C.Diam`,
+         `FoodwebDiff:C.Clutch` = `FoodwebSimple:C.Clutch` - `FoodwebComplex:C.Clutch`,
+         `FoodwebDiff:C.Pref` = `FoodwebSimple:C.Pref` - `FoodwebComplex:C.Pref`,
+         `FoodwebDiff:C.Diam:Clutch` = `FoodwebSimple:C.Diam:Clutch` - `FoodwebComplex:C.Diam:Clutch`,
+         `FoodwebDiff:C.Diam:Pref` = `FoodwebSimple:C.Diam:Pref` - `FoodwebComplex:C.Diam:Pref`,
+         `FoodwebDiff:C.Clutch:Pref` = `FoodwebSimple:C.Clutch:Pref` - `FoodwebComplex:C.Clutch:Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_foodweb_curvs <- foodweb_curvs %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"))#,
+         #gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+         #                       ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         #mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         #conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         #conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+\
+
+```{r Table of food web curvatures, echo=FALSE}
+tidy_foodweb_curvs %>%
+  filter(type != "Diff") %>%
+  select(term, type, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
+```
+
+\
+
+```{r Table of differences in curvatures between food-web treatments, echo=FALSE}
+tidy_foodweb_curvs %>%
+  filter(type == "Diff") %>%
+  select(term, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
+```
 

### 2019-03-29 analyses/reproduce_analyses.Rmd
created orthogonal polynomials and adjusted downstream code to match names appropriately. let's see if it works.

@@
          sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
-         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))
-
+         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))),
+         # create orthogonal polynomial terms
+         sc.Diam.1 = poly(sc.Diam, 2)[ ,1],
+         sc.Diam.2 = poly(sc.Diam, 2)[ ,2],
+         sc.log.Clutch.1 = poly(sc.log.Clutch, 2)[ ,1],
+         sc.log.Clutch.2 = poly(sc.log.Clutch, 2)[ ,1],
+         sc.sqrt.Pref.1 = poly(sc.sqrt.Pref, 2)[ ,1],
+         sc.sqrt.Pref.2 = poly(sc.sqrt.Pref, 2)[ ,2]) 
 ```
@@
 ```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
-mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
+mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), univariatePlot = "histogram")
 ```
@@
 ```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
-mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
+mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), multivariatePlot = "qq")
 ```
@@
     -1 + Foodweb + 
-    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
-    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
+    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
+    Foodweb:(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
+    Foodweb:(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
     (1|Genotype/Plant_Position/Gall_Number),
@@
 
-```{r Linear food-web model, cache=TRUE}
+```{r Linear food-web model, cache=TRUE, eval=FALSE}
 linear_foodweb_model <- glmer(
@@
     -1 + Foodweb + 
-    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
     (1|Genotype/Plant_Position/Gall_Number),
@@
 
-```{r Bootstrap linear food-web model, cache=TRUE}
+```{r Bootstrap linear food-web model, cache=TRUE, eval=FALSE}
 boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
   gall_survival ~ -1 + Foodweb + 
-    Foodweb:sc.Diam + 
+    Foodweb:sc.Diam.1 + 
     (1|Genotype/Plant_Position/Gall_Number),
@@
   select(term, estimate, conf.low, conf.high) %>%
-  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
+  filter(term %in% c("FoodwebComplex:sc.Diam.1","FoodwebSimple:sc.Diam.1")) %>%
   mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 ```{r Food-web alpha coefficients}
-foodweb_bind <- bind_cols(
-  as_tibble(boot_linear_foodweb_model$t),
-  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
-)
+foodweb_bind <- as_tibble(boot_foodweb_model$t) #bind_cols(
+  #as_tibble(boot_linear_foodweb_model$t),
+  #select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
+#)
 
@@
 foodweb_adj_Diam <- foodweb_bind %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])
+  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"],
+         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"])
 
@@
   mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
-         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+         `FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
+         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
+         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
+         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
+         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
          coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
-                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                   ifelse(grepl("\\.2", .$term)==TRUE, "Quadratic",
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
@@
 plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
             aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
+         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
+         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
+         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
+         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
   mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
-         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+         gradient_type = ifelse(grepl("\\.2", .$term)==TRUE, "Quadratic",
                                 ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
@@
 foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
-  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
-         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
-         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
-         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)
+  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:sc.Diam.2` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.Diam.1`,
+         `FoodwebComplex:C.Clutch` = `FoodwebComplex:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.1`*`FoodwebComplex:sc.log.Clutch.1`,
+         `FoodwebComplex:C.Pref` = `FoodwebComplex:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.1`*`FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.log.Clutch.1`,
+         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1`*`FoodwebComplex:sc.sqrt.Pref.1`)
 
@@
 foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
-  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.Diam`,
-         `FoodwebSimple:C.Clutch` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.log.Clutch`,
-         `FoodwebSimple:C.Pref` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebSimple:sc.sqrt.Pref`*`FoodwebSimple:sc.sqrt.Pref`,
-         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.log.Clutch`,
-         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.sqrt.Pref`,
-         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.sqrt.Pref`)
+  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:sc.Diam.2` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.Diam.1`,
+         `FoodwebSimple:C.Clutch` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebSimple:sc.log.Clutch.1`*`FoodwebSimple:sc.log.Clutch.1`,
+         `FoodwebSimple:C.Pref` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebSimple:sc.sqrt.Pref.1`*`FoodwebSimple:sc.sqrt.Pref.1`,
+         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.log.Clutch.1`,
+         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.sqrt.Pref.1`,
+         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebSimple:sc.log.Clutch.1`*`FoodwebSimple:sc.sqrt.Pref.1`)
 
@@
 plot_foodweb_directional_grads <- tidy_foodweb_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_quadratic_grads <- tidy_foodweb_grads %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
             aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_correlational_grads <- tidy_foodweb_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
@@
 
-```{r Linear egg vs. larval ptoid model, cache=TRUE}
+```{r Linear egg vs. larval ptoid model, cache=TRUE, eval=FALSE}
 linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
@@
 
-```{r Bootstrap linear egg vs. larval model, cache=TRUE}
+```{r Bootstrap linear egg vs. larval model, cache=TRUE, eval=FALSE}
 boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 ```{r Egg vs. larval ptoid alpha coefficients}
-egglarval_bind <- bind_cols(
-  as_tibble(boot_linear_egglarval_model$t),
-  select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
-)
+egglarval_bind <- as_tibble(boot_egglarval_model$t) #bind_cols(
+  #as_tibble(boot_linear_egglarval_model$t),
+  #select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
+#)
 
@@
 egglarval_adj_Diam <- as_tibble(boot_egglarval_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])
+  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam.1"],
+         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam.1"])
 
@@
 plot_egglarval_linear_coefs <- tidy_egglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_quadratic_coefs <- tidy_egglarval_alphas %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
             aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_correlational_coefs <- tidy_egglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 egglarval_grads <- bind_cols(egglarval_complex_raw_gradients, egglarval_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
+         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
+         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
+         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
+         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 plot_egglarval_directional_grads <- tidy_egglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_quadratic_grads <- tidy_egglarval_grads %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
             aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_correlational_grads <- tidy_egglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
@@
 newdata_Diam <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
+  expand.grid(Foodweb = "Complex", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = 0))
 
@@
 newdata_Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
+  expand.grid(Foodweb = "Complex", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = 0))
 
@@
 newdata_Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam.1 = 0, sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam.1 = 0, sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)))
 
@@
 AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
-  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  select(-sc.log.Clutch.1, -sc.sqrt.Pref.1) %>%
+  gather(ID, absolute_fitness, -sc.Diam.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.Diam.1, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 AF_uni_Pref <- RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  select(-sc.Diam.1, -sc.log.Clutch.1) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref.1, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  select(-sc.Diam.1, -sc.sqrt.Pref.1) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.log.Clutch.1, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 RF_plot_foodweb_Clutch_df <- RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam, -sc.sqrt.Pref) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
+  select(-sc.Diam.1, -sc.sqrt.Pref.1) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 RF_uni_Clutch <- RF_plot_foodweb_Clutch_df %>%
-  ggplot(., aes(x=sc.log.Clutch, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.log.Clutch.1, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 RF_plot_foodweb_Pref_df <- RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  select(-sc.Diam.1, -sc.log.Clutch.1) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 RF_uni_Pref <- RF_plot_foodweb_Pref_df %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref.1, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 RF_plot_foodweb_Diam_df <- RF_Diam$absolute_fitness %>% 
-  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
+  select(-sc.sqrt.Pref.1, -sc.log.Clutch.1) %>%
+  gather(ID, absolute_fitness, -sc.Diam.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 RF_uni_Diam <- RF_plot_foodweb_Diam_df %>%
-  ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.Diam.1, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 newdata_Clutch.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)))
 
@@
 newdata_Diam.Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
+  expand.grid(Foodweb = "Complex", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1=0))
 
@@
 newdata_Diam.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)))
 
@@
 # Set contour breaks
-breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
+breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam.1 = c(0,0), sc.log.Clutch.1 = c(0,0), sc.sqrt.Pref.1 = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
 names(breaks) <- c("Complex","Simple")
@@
   filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
+  ggplot(., aes(x=sc.Diam.1, y=sc.log.Clutch.1)) +
   geom_raster(aes(fill=average)) +
@@
   filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
+  ggplot(., aes(x=sc.Diam.1, y=sc.sqrt.Pref.1)) +
   geom_raster(aes(fill=average)) +
@@
   filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
+  ggplot(., aes(x=sc.sqrt.Pref.1, y=sc.log.Clutch.1)) +
   geom_raster(aes(fill=average)) +
@@
 gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.Diam = c(0,0), 
-                                    sc.log.Clutch = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
+                                    sc.Diam.1 = c(0,0), 
+                                    sc.log.Clutch.1 = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam.1")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam.1")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch.1")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch.1")$mean))
 
 gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.sqrt.Pref = c(0,0), 
-                                    sc.log.Clutch = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
+                                    sc.sqrt.Pref.1 = c(0,0), 
+                                    sc.log.Clutch.1 = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref.1")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref.1")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch.1")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch.1")$mean))
 
 gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.Diam = c(0,0), 
-                                    sc.sqrt.Pref = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))
+                                    sc.Diam.1 = c(0,0), 
+                                    sc.sqrt.Pref.1 = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam.1")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam.1")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref.1")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref.1")$mean))
 
@@
     geom_segment(data = gradients_Diam.Clutch, 
-                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
+                 aes(x = sc.Diam.1, y = sc.log.Clutch.1, xend = xend, yend = yend), 
                  arrow = arrow(length = unit(0.03, "npc"))),
@@
     geom_segment(data = gradients_Clutch.Pref, 
-                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
+                 aes(x = sc.sqrt.Pref.1, y = sc.log.Clutch.1, xend = xend, yend = yend), 
                  arrow = arrow(length = unit(0.03, "npc"))), 
@@
     geom_segment(data = gradients_Diam.Pref, 
-                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
+                 aes(x = sc.Diam.1, y = sc.sqrt.Pref.1, xend = xend, yend = yend), 
                  arrow = arrow(length = unit(0.03, "npc"))), 
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-complex_betas_df$term <- factor(complex_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
+complex_betas_df$term <- factor(complex_betas_df$term, levels=c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1"), labels=c("Diam","Clutch","Pref"), order=TRUE)
 rownames(complex_betas_df) <- complex_betas_df$term
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-complex_gammas_df$term <- factor(complex_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+complex_gammas_df$term <- factor(complex_gammas_df$term, levels=c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2","sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
 rownames(complex_gammas_df) <- complex_gammas_df$term
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-simple_betas_df$term <- factor(simple_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
+simple_betas_df$term <- factor(simple_betas_df$term, levels=c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1"), labels=c("Diam","Clutch","Pref"), order=TRUE)
 rownames(simple_betas_df) <- simple_betas_df$term
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-simple_gammas_df$term <- factor(simple_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+simple_gammas_df$term <- factor(simple_gammas_df$term, levels=c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2","sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
 rownames(simple_gammas_df) <- simple_gammas_df$term
@@
 
-```{r Linear egg vs. egg ptoid model, cache=TRUE}
+```{r Linear egg vs. egg ptoid model, cache=TRUE, eval=FALSE}
 linear_eggegg_model <- update(linear_foodweb_model, data=eggegg_df)
@@
 
-```{r Bootstrap linear egg vs. egg model, cache=TRUE}
+```{r Bootstrap linear egg vs. egg model, cache=TRUE, eval=FALSE}
 boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 ```{r Egg vs. egg ptoid alpha coefficients}
-eggegg_bind <- bind_cols(
-  as_tibble(boot_linear_eggegg_model$t),
-  select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
-)
+eggegg_bind <- as_tibble(boot_eggegg_model$t)#bind_cols(
+ # as_tibble(boot_linear_eggegg_model$t),
+ # select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
+#)
 
@@
 eggegg_adj_Diam <- as_tibble(boot_eggegg_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])
+  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam.1"],
+         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam.1"])
 
@@
 plot_eggegg_linear_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_quadratic_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
             aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_correlational_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 eggegg_grads <- bind_cols(eggegg_complex_raw_gradients, eggegg_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
+         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
+         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
+         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
+         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
+         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
+         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 plot_eggegg_directional_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_quadratic_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
             aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_correlational_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
             aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
@@
 eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam, -sc.log.Clutch) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
+  select(-sc.Diam.1, -sc.log.Clutch.1) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref.1, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 eggptoid_selection_plot <- eggptoid_plot_df %>%
-  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref.1, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
   geom_line(color=cbPalette[5]) +

### 2019-04-05 analyses/reproduce_analyses.Rmd
add all commits to polynomial_model. I'm concerned that there is too much variance when including all terms in the same model, even after centering and scaling. I'm going to explore ways to reduce model complexity.

@@
 ```{r required libraries, results='hide'}
+library(MuMIn)      # for standardizing regression coefficients
 library(car)        # for homogeneity of variance test
@@
          # transform and scale traits to approximate multivariate normal assumption
-         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
-         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
-         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))),
+         Diam = chamber.diameter_mm, 
+         log.Clutch = log(clutch.size_individuals), 
+         sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots),
          # create orthogonal polynomial terms
-         sc.Diam.1 = poly(sc.Diam, 2)[ ,1],
-         sc.Diam.2 = poly(sc.Diam, 2)[ ,2],
-         sc.log.Clutch.1 = poly(sc.log.Clutch, 2)[ ,1],
-         sc.log.Clutch.2 = poly(sc.log.Clutch, 2)[ ,1],
-         sc.sqrt.Pref.1 = poly(sc.sqrt.Pref, 2)[ ,1],
-         sc.sqrt.Pref.2 = poly(sc.sqrt.Pref, 2)[ ,2]) 
+         sc.Diam.1 = as.numeric(scale(Diam)), #poly(Diam, 2)[ ,1],
+         sc.Diam.2 = sc.Diam.1^2, #poly(Diam, 2)[ ,2],
+         sc.log.Clutch.1 = as.numeric(scale(log.Clutch)),#poly(log.Clutch, 2)[ ,1],
+         sc.log.Clutch.2 = sc.log.Clutch.1^2, #poly(log.Clutch, 2)[ ,2],
+         sc.sqrt.Pref.1 = as.numeric(scale(sqrt.Pref)),#poly(sqrt.Pref, 2)[ ,1],
+         sc.sqrt.Pref.2 = sc.sqrt.Pref.1^2)#poly(sqrt.Pref, 2)[ ,2])
+
+# scaling before including the model inflates the variance above 1, when everything should be on the same scale
+with(gall_selection.df, sd(scale(sc.Diam.1)*scale(sc.log.Clutch.1)))
+with(gall_selection.df, sd(scale(sc.Diam.1*sc.log.Clutch.1)))
+with(gall_selection.df, sd(scale(sc.Diam.1)*scale(sc.sqrt.Pref.1)))
+with(gall_selection.df, sd(scale(sc.Diam.1*sc.sqrt.Pref.1)))
+with(gall_selection.df, sd(scale(sc.log.Clutch.1)*scale(sc.sqrt.Pref.1)))
+with(gall_selection.df, sd(scale(sc.log.Clutch.1*sc.sqrt.Pref.1)))
+
+# scaling before including the model also can cause deviations from 0, when everything should be zero
+with(gall_selection.df, mean(scale(sc.Diam.1)*scale(sc.log.Clutch.1)))
+with(gall_selection.df, mean(scale(sc.Diam.1*sc.log.Clutch.1)))
+with(gall_selection.df, mean(scale(sc.Diam.1)*scale(sc.sqrt.Pref.1)))
+with(gall_selection.df, mean(scale(sc.Diam.1*sc.sqrt.Pref.1)))
+with(gall_selection.df, mean(scale(sc.log.Clutch.1)*scale(sc.sqrt.Pref.1)))
+with(gall_selection.df, mean(scale(sc.log.Clutch.1*sc.sqrt.Pref.1)))
+
+with(gall_selection.df, cor(sc.sqrt.Pref.1, sc.sqrt.Pref.2))
 ```
@@
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+
+### THIS APPROACH IS WRONG, IT ALSO STANDARDIZES FITNESS, WHICH IS NOT THE GOAL.
+### ONLY THE TRAIT SHOULD BE STANDARDIZED...
+### EASIEST WAY TO DO THIS IS TO SCALE BEFORE PUTTING INTO THE MODEL...
+
+# I don't need partial.sd = TRUE, I should actually have it be false...this will be more consistent with the interterpration of intensity of selection.
+I don't know exactly how the partial changes things...it also may only be relevant when I examine different combinations of predictions through a model selection procedure.
+std.coefs <- function(model, partial.sd = FALSE){
+  treatments <- fixef(model)[c("FoodwebComplex","FoodwebSimple")]
+  temp <- std.coef(model, partial.sd = partial.sd)
+  std.coefs <- setNames(c(t(temp[ ,1])), nm = rownames(temp))
+  std.coefs[c("FoodwebComplex","FoodwebSimple")] <- treatments # only standardizing trait-fitness relationships, and not main effects of treatment.
+It doesn't make sense to standardize it as it will alter estimates of mean fitness, which are critical for calculating selection gradients.
+  return(std.coefs)
+}
+
+std.coef(foodweb_model, partial.sd = FALSE)
+cbind(fixef(foodweb_model), std.coefs(foodweb_model))
+
+fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]
+std.coefs(foodweb_model)["FoodwebComplex:sc.Diam.1"]
+fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]*sd(gall_selection.df$sc.Diam.1)
+fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]*sd(filter(gall_selection.df, Foodweb=="Complex")$sc.Diam.1)
+```
+
+```{r glmmLasso, eval=FALSE}
+library(glmmLasso)
+gall_selection.df_test <- gall_selection.df %>%
+  mutate(f.Foodweb = factor(Foodweb),
+         f.Genotype = factor(Genotype),
+         f.Plant_Position = factor(Plant_Position),
+         f.Gall_Number = factor(Gall_Number),
+         sc.Diam = as.numeric(scale(Diam)),
+         sc.log.Clutch = as.numeric(scale(log.Clutch)),
+         sc.sqrt.Pref = as.numeric(scale(sqrt.Pref)))
+
+lambda <- seq(500, 0, by=-5)
+BIC_vec <- rep(Inf,length(lambda))
+AIC_vec <- rep(Inf,length(lambda))
+
+## specify starting values
+Delta.start<-as.matrix(t(rep(0, 20+8+111))) # 8+111+613 set intercept, all 19 coefficients, and random effects to starting values of zero
+Q.start <- 0.1 #$list(0.1) # diag(c(0.1) using default values from glmmLassoControl
+
+for(i in 1:length(lambda)){
+  print(paste("Iteration ", i, sep = ""))
+
+  lasso <- glmmLasso(gall_survival ~ f.Foodweb + 
+                       sc.Diam + sc.log.Clutch + sc.sqrt.Pref + 
+                       f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
+                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+                       f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
+                       sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+                       f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref,
+                     rnd = list(f.Genotype=~1, f.Plant_Position=~1), # , f.Gall_Number=~1
+                     family = binomial(link=logit),
+                     data = gall_selection.df_test,
+                     lambda = lambda[i],
+                     switch.NR = F,
+                     final.re = TRUE,
+                     control = list(start = Delta.start[i, ])) # difficulty providing starting values for random effects, it was easier to use the default.
+
+  print(colnames(lasso$Deltamatrix)[2:20][lasso$Deltamatrix[lasso$conv.step,2:20]!=0])
+
+  BIC_vec[i]<-lasso$bic
+  AIC_vec[i]<-lasso$aic
+
+  Delta.start <- rbind(Delta.start, lasso$Deltamatrix[lasso$conv.step, ])
+
+}
+
+plot(AIC_vec ~ lambda)
+plot(BIC_vec ~ lambda)
+
+optLassoAIC <- which.min(AIC_vec) # choose whether to optimize with AIC or BIC
+optLassoBIC <- which.min(BIC_vec)
+
+# with the full random effect structure, the optimal lambda = 0...
+lambda[optLassoAIC]
+lambda[optLassoBIC]
+
+# after removing Gall_Number, there is minimal shrinkage for AIC, but substantial shrinkage for BIC
+# but how do I decide which method is "best"
+lasso_final <- glmmLasso(gall_survival ~ f.Foodweb + 
+                       sc.Diam + sc.log.Clutch + sc.sqrt.Pref + 
+                       f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
+                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+                       f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
+                       sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+                       f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref,
+                     rnd = list(f.Genotype=~1, f.Plant_Position=~1), # , f.Gall_Number=~1
+                     family = binomial(link=logit),
+                     data = gall_selection.df_test,
+                     lambda = lambda[optLassoBIC], # lambda = 43 now, instead of 27...
+                     switch.NR = F,
+                     final.re = TRUE,
+                     control = list(start = Delta.start[optLassoBIC, ]))
+
+summary(lasso_final)
+
+## plot coefficient paths
+plot(lambda, Delta.start[2:(length(lambda)+1),2], type="l", lty=1, ylim=c(-0.5,0.5), ylab=expression(hat(beta[i])))
+abline(v = lambda[optLasso])
+lines(lambda, Delta.start[2:(length(lambda)+1),3], lty=2)
+lines(lambda, Delta.start[2:(length(lambda)+1),4], lty=3)
+lines(lambda, Delta.start[2:(length(lambda)+1),5], lty=4)
+lines(lambda, Delta.start[2:(length(lambda)+1),6], lty=5)
+lines(lambda, Delta.start[2:(length(lambda)+1),7], lty=6)
+lines(lambda, Delta.start[2:(length(lambda)+1),8], lty=7)
+lines(lambda, Delta.start[2:(length(lambda)+1),9], lty=8)
+```
+
+```{r test, eval=FALSE}
+full_glmer <- glmer(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    f.Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
+    f.Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"))
+summary(full_glmer)
+drop1(full_glmer, test="Chisq") # no clear evidence of food-web structure altering correlation or quadratic gradients
+
+lin_glmer <- glmer(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"))
+summary(lin_glmer)
+drop1(lin_glmer, test="Chisq") # only clear evidence of food-web structure altering selection on clutch size
+
+red_glmer <- glmer(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    f.Foodweb:sc.log.Clutch +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"))
+summary(red_glmer)
+
+gall_selection.df_test <- gall_selection.df_test %>%
+  mutate(c.Diam = Diam - mean(Diam),
+         c.log.Clutch = log.Clutch - mean(log.Clutch),
+         c.sqrt.Pref = sqrt.Pref - mean(sqrt.Pref))
+library(MASS)
+red_glmer2 <- glmer(
+  gall_survival ~ 
+    Foodweb + 
+    c.Diam + c.log.Clutch + c.sqrt.Pref +
+    I(c.Diam^2) + I(c.log.Clutch^2) + I(c.sqrt.Pref^2) +
+    c.Diam:c.log.Clutch + c.Diam:c.sqrt.Pref + c.log.Clutch:c.sqrt.Pref +
+    Foodweb:c.log.Clutch +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"),
+  contrast = list(Foodweb="contr.Sum"))
+summary(red_glmer2)
+
+red_glmer3 <- glmer(
+  gall_survival ~ 
+    Foodweb*(scale(poly(Diam, 2)) + scale(poly(log.Clutch, 2)) + scale(poly(sqrt.Pref, 2))) +
+    Foodweb*(scale(poly(Diam, 2)[ ,1]):scale(poly(log.Clutch, 2)[ ,1]) + scale(poly(Diam, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1]) + scale(poly(log.Clutch, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1])) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"))
+summary(red_glmer3)
+
+gall_selection.df_test <- gall_selection.df_test %>% mutate(poly.log.Clutch = poly(log.Clutch, 2))
+
+red_glmer4 <- glmer(
+  gall_survival ~ 
+    Foodweb + (scale(poly(Diam, 2)) + scale(poly(log.Clutch, 2)) + scale(poly(sqrt.Pref, 2))) +
+    Foodweb:scale(poly(log.Clutch, 2)[ ,1]) +
+    Foodweb + (scale(poly(Diam, 2)[ ,1]):scale(poly(log.Clutch, 2)[ ,1]) + scale(poly(Diam, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1]) + scale(poly(log.Clutch, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1])) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"))
+summary(red_glmer4)
+
+fixef(red_glmer4)
+MuMIn::std.coef(red_glmer4, partial.sd = T)
+MuMIn::stdizeFit(red_glmer2, data=gall_selection.df_test, scale=T)
+fixef(red_glmer2)
+
+# so, with this interpretation, having a significant effect of clutch size will constrain both the slope and curvature of the adaptive landscape more.
+
+# I think I need to rely more on interpreting differences between food-web treatments, rather than getting separate estimates for each food-web treatment, which will have weaker signals.
+Plus, this will enable me to fill in the covariance matrix...the issue now is, how does the mortality propogate through to affect the selection gradients?
+# the unfortunate thing, is that this may require me to code things a bit differently from the beginning...
+
+test_foodweb_correl <- update(full_glmer, .~. -f.Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref))
+summary(test_foodweb_correl)
+anova(full_glmer, test_foodweb_correl, test="LR") # no diff, indicates there is no clear effect of food-web on correlational gradients
+
+test_foodweb_quad <- update(full_glmer, .~. -f.Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)))
+anova(full_glmer, test_foodweb_quad, test="LR") # no sig. diff, indicates there is no clear effect of food-web on quadratic gradients
+
+test_correl <- update(test_foodweb_correl, .~. -(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref))
+anova(test_foodweb_correl, test_correl, test="LR") # sig. diff, argues to keep correlational gradients
+
+test_quad <- update(test_foodweb_quad, .~. -(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)))
+anova(test_foodweb_quad, test_quad, test="LR") # sig. diff, argues to keep quadratic gradients
+
+test_foodweb_lin <- glmer(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    (1|Genotype) + (1|Plant_Position),
+  data = gall_selection.df_test,
+  family=binomial(link=logit))
+
+test_lin <- update(test_foodweb_lin, .~. -f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref))
+anova(test_foodweb_lin, test_lin, test="LR") # indicates that food-web alters linear selection gradients
+
+test_model <- glmer(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    (1|Genotype) + (1|Plant_Position),
+  data = gall_selection.df_test,
+  family=binomial(link=logit))
+summary(test_model)
+
+library(polywog)
+test_polywog <- polywog(gall_survival ~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref, 
+                        degree = 2,
+                        #boot = 100,
+                        family="binomial", data=filter(gall_selection.df_test, f.Foodweb=="Complex"))
+summary(test_polywog)
+
+library(parcor)
+
+full_glm <- glm(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  na.action = "na.fail") 
+```
+
+```{r test model selection, eval=FALSE}
+library(MuMIn)
+
+full_glmer <- glmer(
+  gall_survival ~ 
+    f.Foodweb + 
+    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
+    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
+    f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
+    f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
+    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df_test,
+  family=binomial(link=logit),
+  control=glmerControl(optimizer="bobyqa"),
+  na.action = "na.fail")
+summary(full_glmer)
+drop1(full_glmer, test="Chisq") # marginal quadratic effect of Pref. no clear effect of food-web on correlational or quadratic gradients.
+drop1(update(full_glmer, .~. -(f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
+    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq") # marginal effects of quadratic Diam and Pref and Diam:Clutch
+drop1(update(full_glmer, .~. -(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref + f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
+    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq") # clear effect of food web on clutch
+drop1(update(full_glmer, .~. -(f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
+    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref + f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
+    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq")
+
+# Set up the cluster
+clusterType <- if(length(find.package("snow", quiet = TRUE))) "SOCK" else "PSOCK"
+clust <- try(parallel::makeCluster(getOption("cl.cores", 32), type = clusterType))
+
+clusterExport(clust, "gall_selection.df_test")
+clusterEvalQ(clust, library(lme4))
+
+# BIC model is VERY restrictive: only foodweb, diam, and pref left everything else exluded in model with lowest BIC
+test_dredge <- MuMIn::pdredge(full_glmer, 
+                              #fixed = c("f.Foodweb", "sc.Diam", "sc.log.Clutch", "sc.sqrt.Pref", "f.Foodweb:sc.Diam", "f.Foodweb:sc.log.Clutch", "f.Foodweb:sc.sqrt.Pref"), 
+                              trace = 2, 
+                              rank = "BIC", # AICc # using BIC removes all higher order terms...
+                              cluster = clust)
+
+summary(get.models(test_dredge, 1)[[1]])
+
+subset(test_dredge, delta < 10)
+
+test_sub <- MuMIn::model.avg(test_dredge, subset = delta < 10)
+test_sub
+coefTable(test_sub)
+#coefTable(test_dredge)
 ```
@@
 ```{r Bootstrap food-web model, cache=TRUE}
-boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
+boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, #std.coefs, # 
+                              nsim=n_boots_analysis, 
+                              parallel="multicore", ncpus=32, seed=34)
 ```
@@
   filter(term %in% c("FoodwebComplex:sc.Diam.1","FoodwebSimple:sc.Diam.1")) %>%
-  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
+  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
+  #knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
 ```
@@
 foodweb_adj_Diam <- foodweb_bind %>%
-  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"],
-         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"])
+  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` -fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"], # std.coefs(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"], #
+         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"]) #std.coefs(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"]) #
 
@@
   select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
- knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3))# %>%
+# knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
 ```
@@
   select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
- knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3))# %>%
+# knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
 ```
@@
   select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
+#knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
 ```
@@
   select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-  knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
+ # knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
 ```
@@
   select(term, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
+#knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
 ```
@@
   select(term, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
+  #knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
 ```
@@
 
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE}
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, eval=FALSE}
 newdata_Diam <- bind_rows(
@@
 
-```{r Get Clutch Size Fitness Landscape, cache=TRUE}
+```{r Get Clutch Size Fitness Landscape, cache=TRUE, eval=FALSE}
 newdata_Clutch <- bind_rows(
@@
 
-```{r Get Oviposition preference Fitness Landscape, cache=TRUE}
+```{r Get Oviposition preference Fitness Landscape, cache=TRUE, eval=FALSE}
 
@@
 
-```{r Plot Univariate Landscapes}
+```{r Plot Univariate Landscapes, eval=FALSE}
 uni_breaks <- c(0.1,0.5,1.0)
@@
 
-```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs."}
+```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs.", eval=FALSE}
 
@@
 
-```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness."}
+```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness.", eval=FALSE}
 
@@
 
-```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE}
+```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE, eval=FALSE}
 
@@
 
-```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE}
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, eval=FALSE}
 
@@
 
-```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE}
+```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE, eval=FALSE}
 
@@
 
-```{r Get plots of multivariate adaptive landscape}
+```{r Get plots of multivariate adaptive landscape, eval=FALSE}
 
@@
 Dotted lines denote fitness for the mean phenotype.
-Arrows represent the vector of directional selection gradients acting on each phenotype."}
+Arrows represent the vector of directional selection gradients acting on each phenotype.", eval=FALSE}
 
@@
 
-```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids"}
+```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids", eval=FALSE}
 # this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.

### 2019-04-05 analyses/reproduce_analyses.Rmd
added treatment effects. Results are counterintuitive though. I see no clear evidence of clutch size on selection gradients, even though it clearly differs between treatments in the trait-fitness relationships.

@@
 
-```{r Food-web model, cache=TRUE}
+```{r Food-web contrast model, cache=TRUE}
+foodweb_contrast_model <- glmer(
+  gall_survival ~ 
+    Foodweb*(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
+    Foodweb*(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
+    Foodweb*(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df,
+  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+summary(foodweb_contrast_model) # Chi-square tests below correspond to Wald z-tests in summary
+
+drop1(foodweb_contrast_model, test="Chisq") # marginal effect of sqrt.Pref^2
+
+# manually testing lower order terms as I've already scaled them to make them mostly orthrogonal
+anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.Diam.1), test="Chisq")
+anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.log.Clutch.1), test="Chisq") # clear effect
+anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.sqrt.Pref.1), test="Chisq")
+anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb), test="Chisq") # clear effect
+
+# Revised food-web model after removing non-significant terms
+foodweb_model <- glmer(
+  gall_survival ~ 
+    Foodweb + 
+    (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
+    Foodweb:sc.log.Clutch.1 +
+    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
+    Foodweb:sc.sqrt.Pref.2 +
+    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df,
+  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+summary(foodweb_model)
+```
+
+```{r Food-web model, cache=TRUE, eval=FALSE}
 foodweb_model <- glmer(
@@
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
+```
+
+```{r Food-web model old, eval=FALSE}
+
+car::vif(foodweb_model) # GVIF vary between 1.4 and 4, which I don't like
+
+# we get a clear reduction in VIF when we specify a simpler model.
+foodweb_contrast_model <- glmer(
+  gall_survival ~ 
+    Foodweb + (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
+    Foodweb:sc.log.Clutch.1 +
+    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
+    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
+    (1|Genotype/Plant_Position/Gall_Number),
+  data = gall_selection.df,
+  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))#,
+  #contrast = list(Foodweb = "contr.sum"))
+summary(foodweb_contrast_model)
+car::vif(foodweb_contrast_model) # after specifying contr.sum, most values are less than 2 (max 2.5)
 
@@
 ```{r Food-web alpha coefficients}
-foodweb_bind <- as_tibble(boot_foodweb_model$t) #bind_cols(
+foodweb_bind <- as_tibble(boot_foodweb_model$t) %>%
+  rename(FoodwebComplex = `(Intercept)`,
+         `FoodwebComplex:sc.Diam.1` = sc.Diam.1,
+         `FoodwebComplex:sc.log.Clutch.1` = sc.log.Clutch.1,
+         `FoodwebComplex:sc.sqrt.Pref.1` = sc.sqrt.Pref.1,
+         `FoodwebComplex:sc.Diam.2` = sc.Diam.2,
+         `FoodwebComplex:sc.log.Clutch.2` = sc.log.Clutch.2,
+         `FoodwebComplex:sc.sqrt.Pref.2` = sc.sqrt.Pref.2,
+         `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1` = `sc.Diam.1:sc.log.Clutch.1`,
+         `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1` = `sc.Diam.1:sc.sqrt.Pref.1`,
+         `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1` = `sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
+  # set trait-fitness relationships equal for appropriate terms
+  mutate(`FoodwebSimple:sc.Diam.1` = `FoodwebComplex:sc.Diam.1`,
+         #`FoodwebSimple:sc.log.Clutch.1` # we estimate food-web effects for this term
+         `FoodwebSimple:sc.sqrt.Pref.1` = `FoodwebComplex:sc.sqrt.Pref.1`,
+         `FoodwebSimple:sc.Diam.2` = `FoodwebComplex:sc.Diam.2`,
+         `FoodwebSimple:sc.log.Clutch.2` = `FoodwebComplex:sc.log.Clutch.2`,
+         #`FoodwebSimple:sc.sqrt.Pref.2` # we estimate food-web effects for this term
+         `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` = `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
+         `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
+         `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`)
+  #bind_cols(
   #as_tibble(boot_linear_foodweb_model$t),

### 2019-04-05 analyses/reproduce_analyses.Rmd
added treatment effects. Results are counterintuitive though. I see no clear evidence of clutch size on selection gradients, even though it clearly differs between treatments in the trait-fitness relationships.

@@
 summary(foodweb_model)
+car::vif(foodweb_model) # higher VIF than I anticipated
 ```

### 2019-04-05 analyses/reproduce_analyses.Rmd

--- 2019-04-05 analyses/reproduce_analyses.Rmd
@@
 summary(foodweb_model)
+car::vif(foodweb_model) # higher VIF than I anticipated
+car::vif(foodweb_model) 
 ```

### 2019-05-02 manuscript.Rmd
add manuscript changes on polynomial_model branch to master

@@
 \vspace*{0.1cm} 
-\begin{center} \LARGE Phenotypic evolution is more constrained in simpler food webs \end{center}
+\begin{center} \LARGE Extinction of a consumer guild constrains phenotypic evolution in an insect herbivore \end{center}
 
@@
 
-Global change is simplifying the structure of ecological networks; however, we are currently in a poor position to predict how these simplified communities will affect the evolutionary potential of remaining populations.
+Global change is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
 Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the community context of evolving populations as a ``black box''.
 Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web structure shape evolutionary constraints.
-We conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an insect herbivore.
+We conducted a field experiment that manipulated whether a guild of larval parasitoids were able to impose selection on an insect herbivore.
 We then measured herbivore survival as a function of three key phenotypic traits.
-We found that more traits were under selection in simpler vs.
-more complex food webs.
-The adaptive landscape was more neutral in complex food webs because different parasitoid species impose different selection pressures, minimizing relative fitness differences among phenotypes.
-Our results suggest that the loss of species interactions can impose greater constraints on phenotypic evolution.
+We found that more traits were under selection when we excluded interactions with larval parasitoids.
+The adaptive landscape was more neutral in the intact food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
+Our results suggest that the loss of trophic interactions can impose greater constraints on phenotypic evolution.
 This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
@@
 We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by parasitoids, we excluded unknown sources of mortality.
+Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`%).
+
 For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
@@
 
-**Selection gradients**: We used the method of @Janzen1998 to translate trait-fitness relationships ($\alpha$) into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i:z_i}$), and correlational ($\gamma_{z_i:z_j}$) selection gradients.
+**Selection gradients**: Selection gradients cannot be estimated directly from generalized linear (mixed) models, because the coefficients are on a nonlinear scale.
+For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e., $\text{ln}\{W(z)[1-W(z)]\}$) associated with a unit change in a trait with all other traits held fixed.
+Therefore, we used the method developed by @Janzen1998 to translate trait-fitness relationships from the above model into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i:z_i}$), and correlational ($\gamma_{z_i:z_j}$) selection gradients.
 Briefly, this method calculates the average gradient of selection surfaces by multiplying the average of $W(z)[1-W(z)]$ by each regression coefficient (e.g.
@@
 
-## Measuring selection on the extended phenotype of egg parasitoids
+## Measuring selection on egg parasitoids
 
-Once parasitized, the gall phenotype becomes the extended phenotype of the egg parasitoid.
-This extended phenotype may influence the egg parasitoid's survival in the face of larval parasitoids, and thus experiences selection.
-Our food-web manipulation allows us to measure selection imposed by larval parasitoids on the extended phenotype of egg parasitoids.
+Once parasitized, the gall phenotype becomes the phenotype of the egg parasitoid.
+This phenotype may influence the egg parasitoid's survival in the face of larval parasitoids, and thus experiences selection.
+Our food-web manipulation allows us to measure selection imposed by larval parasitoids on the phenotype of egg parasitoids.
 Using the same models as described above, we substituted egg parasitism as our response variable to quantify trait-fitness relationships and selection gradients acting on the egg parasitoid.
@@
 
-## Loss of species interactions increase selective constraints
+## Loss of trophic interactions increase selective constraints
 
@@
 
-## Loss of species interactions increase genetic constraints
+## Loss of trophic interactions increase genetic constraints
 
@@
 
-## Selection on the extended phenotype of egg parasitoids
+## Selection on egg parasitoids
 
@@
 Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of species interactions may have complex effects on the trajectories of phenotypic evolution.
-Taken together, our study provides experimental evidence from the field that the loss of species interactions may constrain the adaptive potential of remaining populations.
+Taken together, our study provides experimental evidence from the field that the loss of trophic interactions may constrain the adaptive potential of remaining populations.
 
@@
 <!--Indirect evolutionary effects-->
-Our results suggest that the loss of species interactions may not only directly affect connected species, but also result in indirect evolutionary effects.
+Our results suggest that the loss of trophic interactions may not only directly affect connected species, but also result in indirect evolutionary effects.
 In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we exlcuded larval parasitoids.

### 2019-05-02 analyses/reproduce_analyses.Rmd
add full data so I could calculate other sources of larval mortality.

--- 2019-04-05 analyses/reproduce_analyses.Rmd
@@
 ```{r required libraries, results='hide'}
-library(MuMIn)      # for standardizing regression coefficients
 library(car)        # for homogeneity of variance test
@@
 
-gall_selection.df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
+full_df <- read_csv("../data/gall_selection_manuscript_dataset.csv") %>%
+  mutate(gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)), # there were a couple of times where two pupa were found in a single chamber. I set these to 1 to permit an analysis with a binomial model
+         egg.ptoid = as.numeric(ifelse(egg.ptoid > 0, 1, 0)), # there were a couple occassions where two egg parasitoids were found in a single chamber.
+I set these to 1 to permit an analysis with a binomial model.
+         unknown_mortality = ifelse(rowSums(select(., pupa:early.larval.death)) < 1, 1, 0))
+
+# all sources of mortality
+mean(full_df$gall_survival) + mean(full_df$egg.ptoid) + mean(full_df$larval.ptoid) + mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)
+
+mean(full_df$gall_survival) # 40% survival
+mean(full_df$egg.ptoid) # 26% egg parasitism
+mean(full_df$larval.ptoid) # 11% larval parasitism
+mean(full_df$early.larval.death) # 17% early larval death
+mean(full_df$unknown_mortality) # 7% unknown
+
+gall_selection.df <- full_df %>%
   # convert appropriate variables to characters instead of integers
@@
          # transform and scale traits to approximate multivariate normal assumption
-         Diam = chamber.diameter_mm, 
-         log.Clutch = log(clutch.size_individuals), 
-         sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots),
-         # create orthogonal polynomial terms
-         sc.Diam.1 = as.numeric(scale(Diam)), #poly(Diam, 2)[ ,1],
-         sc.Diam.2 = sc.Diam.1^2, #poly(Diam, 2)[ ,2],
-         sc.log.Clutch.1 = as.numeric(scale(log.Clutch)),#poly(log.Clutch, 2)[ ,1],
-         sc.log.Clutch.2 = sc.log.Clutch.1^2, #poly(log.Clutch, 2)[ ,2],
-         sc.sqrt.Pref.1 = as.numeric(scale(sqrt.Pref)),#poly(sqrt.Pref, 2)[ ,1],
-         sc.sqrt.Pref.2 = sc.sqrt.Pref.1^2)#poly(sqrt.Pref, 2)[ ,2])
-
-# scaling before including the model inflates the variance above 1, when everything should be on the same scale
-with(gall_selection.df, sd(scale(sc.Diam.1)*scale(sc.log.Clutch.1)))
-with(gall_selection.df, sd(scale(sc.Diam.1*sc.log.Clutch.1)))
-with(gall_selection.df, sd(scale(sc.Diam.1)*scale(sc.sqrt.Pref.1)))
-with(gall_selection.df, sd(scale(sc.Diam.1*sc.sqrt.Pref.1)))
-with(gall_selection.df, sd(scale(sc.log.Clutch.1)*scale(sc.sqrt.Pref.1)))
-with(gall_selection.df, sd(scale(sc.log.Clutch.1*sc.sqrt.Pref.1)))
-
-# scaling before including the model also can cause deviations from 0, when everything should be zero
-with(gall_selection.df, mean(scale(sc.Diam.1)*scale(sc.log.Clutch.1)))
-with(gall_selection.df, mean(scale(sc.Diam.1*sc.log.Clutch.1)))
-with(gall_selection.df, mean(scale(sc.Diam.1)*scale(sc.sqrt.Pref.1)))
-with(gall_selection.df, mean(scale(sc.Diam.1*sc.sqrt.Pref.1)))
-with(gall_selection.df, mean(scale(sc.log.Clutch.1)*scale(sc.sqrt.Pref.1)))
-with(gall_selection.df, mean(scale(sc.log.Clutch.1*sc.sqrt.Pref.1)))
-
-with(gall_selection.df, cor(sc.sqrt.Pref.1, sc.sqrt.Pref.2))
+         sc.Diam = as.numeric(scale(chamber.diameter_mm)), 
+         sc.log.Clutch = as.numeric(scale(log(clutch.size_individuals))), 
+         sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots))))
+
 ```
@@
 ```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
-mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), univariatePlot = "histogram")
+mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
 ```
@@
 ```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
-mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam.1, sc.log.Clutch.1, sc.sqrt.Pref.1), multivariatePlot = "qq")
+mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")
 ```
@@
 
-```{r Food-web contrast model, cache=TRUE}
-foodweb_contrast_model <- glmer(
+```{r Food-web model, cache=TRUE}
+foodweb_model <- glmer(
   gall_survival ~ 
-    Foodweb*(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
-    Foodweb*(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
-    Foodweb*(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
+    -1 + Foodweb + 
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
+    Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
+    Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
     (1|Genotype/Plant_Position/Gall_Number),
@@
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-summary(foodweb_contrast_model) # Chi-square tests below correspond to Wald z-tests in summary
-
-drop1(foodweb_contrast_model, test="Chisq") # marginal effect of sqrt.Pref^2
-
-# manually testing lower order terms as I've already scaled them to make them mostly orthrogonal
-anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.Diam.1), test="Chisq")
-anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.log.Clutch.1), test="Chisq") # clear effect
-anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb:sc.sqrt.Pref.1), test="Chisq")
-anova(foodweb_contrast_model, update(foodweb_contrast_model, .~. -Foodweb), test="Chisq") # clear effect
-
-# Revised food-web model after removing non-significant terms
-foodweb_model <- glmer(
+```
+
+We used parametric bootstrapping to calculate 95% confidence intervals of trait-fitness relationships.
+
+```{r Bootstrap food-web model, cache=TRUE}
+boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
+```
+
+In order to reliably quantify linear trait-fitness relationships, we remove all higher-order terms from the model [Stinchcombe et al.
+2008](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x).
+
+```{r Linear food-web model, cache=TRUE}
+linear_foodweb_model <- glmer(
   gall_survival ~ 
-    Foodweb + 
-    (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
-    Foodweb:sc.log.Clutch.1 +
-    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
-    Foodweb:sc.sqrt.Pref.2 +
-    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
+    -1 + Foodweb + 
+    Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
     (1|Genotype/Plant_Position/Gall_Number),
@@
   family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-summary(foodweb_model)
-```
-
-```{r Food-web model, cache=TRUE, eval=FALSE}
-foodweb_model <- glmer(
-  gall_survival ~ 
-    -1 + Foodweb + 
-    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
-    Foodweb:(sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
-    Foodweb:(sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-```
-
-```{r Food-web model old, eval=FALSE}
-
-car::vif(foodweb_model) # GVIF vary between 1.4 and 4, which I don't like
-
-# we get a clear reduction in VIF when we specify a simpler model.
-foodweb_contrast_model <- glmer(
-  gall_survival ~ 
-    Foodweb + (sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
-    Foodweb:sc.log.Clutch.1 +
-    (sc.Diam.2 + sc.log.Clutch.2 + sc.sqrt.Pref.2) +
-    (sc.Diam.1:sc.log.Clutch.1 + sc.Diam.1:sc.sqrt.Pref.1 + sc.log.Clutch.1:sc.sqrt.Pref.1) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))#,
-  #contrast = list(Foodweb = "contr.sum"))
-summary(foodweb_contrast_model)
-car::vif(foodweb_contrast_model) # after specifying contr.sum, most values are less than 2 (max 2.5)
-
-### THIS APPROACH IS WRONG, IT ALSO STANDARDIZES FITNESS, WHICH IS NOT THE GOAL.
-### ONLY THE TRAIT SHOULD BE STANDARDIZED...
-### EASIEST WAY TO DO THIS IS TO SCALE BEFORE PUTTING INTO THE MODEL...
-
-# I don't need partial.sd = TRUE, I should actually have it be false...this will be more consistent with the interterpration of intensity of selection.
-I don't know exactly how the partial changes things...it also may only be relevant when I examine different combinations of predictions through a model selection procedure.
-std.coefs <- function(model, partial.sd = FALSE){
-  treatments <- fixef(model)[c("FoodwebComplex","FoodwebSimple")]
-  temp <- std.coef(model, partial.sd = partial.sd)
-  std.coefs <- setNames(c(t(temp[ ,1])), nm = rownames(temp))
-  std.coefs[c("FoodwebComplex","FoodwebSimple")] <- treatments # only standardizing trait-fitness relationships, and not main effects of treatment.
-It doesn't make sense to standardize it as it will alter estimates of mean fitness, which are critical for calculating selection gradients.
-  return(std.coefs)
-}
-
-std.coef(foodweb_model, partial.sd = FALSE)
-cbind(fixef(foodweb_model), std.coefs(foodweb_model))
-
-fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]
-std.coefs(foodweb_model)["FoodwebComplex:sc.Diam.1"]
-fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]*sd(gall_selection.df$sc.Diam.1)
-fixef(foodweb_model)["FoodwebComplex:sc.Diam.1"]*sd(filter(gall_selection.df, Foodweb=="Complex")$sc.Diam.1)
-```
-
-```{r glmmLasso, eval=FALSE}
-library(glmmLasso)
-gall_selection.df_test <- gall_selection.df %>%
-  mutate(f.Foodweb = factor(Foodweb),
-         f.Genotype = factor(Genotype),
-         f.Plant_Position = factor(Plant_Position),
-         f.Gall_Number = factor(Gall_Number),
-         sc.Diam = as.numeric(scale(Diam)),
-         sc.log.Clutch = as.numeric(scale(log.Clutch)),
-         sc.sqrt.Pref = as.numeric(scale(sqrt.Pref)))
-
-lambda <- seq(500, 0, by=-5)
-BIC_vec <- rep(Inf,length(lambda))
-AIC_vec <- rep(Inf,length(lambda))
-
-## specify starting values
-Delta.start<-as.matrix(t(rep(0, 20+8+111))) # 8+111+613 set intercept, all 19 coefficients, and random effects to starting values of zero
-Q.start <- 0.1 #$list(0.1) # diag(c(0.1) using default values from glmmLassoControl
-
-for(i in 1:length(lambda)){
-  print(paste("Iteration ", i, sep = ""))
-
-  lasso <- glmmLasso(gall_survival ~ f.Foodweb + 
-                       sc.Diam + sc.log.Clutch + sc.sqrt.Pref + 
-                       f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
-                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-                       f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
-                       sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-                       f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref,
-                     rnd = list(f.Genotype=~1, f.Plant_Position=~1), # , f.Gall_Number=~1
-                     family = binomial(link=logit),
-                     data = gall_selection.df_test,
-                     lambda = lambda[i],
-                     switch.NR = F,
-                     final.re = TRUE,
-                     control = list(start = Delta.start[i, ])) # difficulty providing starting values for random effects, it was easier to use the default.
-
-  print(colnames(lasso$Deltamatrix)[2:20][lasso$Deltamatrix[lasso$conv.step,2:20]!=0])
-
-  BIC_vec[i]<-lasso$bic
-  AIC_vec[i]<-lasso$aic
-
-  Delta.start <- rbind(Delta.start, lasso$Deltamatrix[lasso$conv.step, ])
-
-}
-
-plot(AIC_vec ~ lambda)
-plot(BIC_vec ~ lambda)
-
-optLassoAIC <- which.min(AIC_vec) # choose whether to optimize with AIC or BIC
-optLassoBIC <- which.min(BIC_vec)
-
-# with the full random effect structure, the optimal lambda = 0...
-lambda[optLassoAIC]
-lambda[optLassoBIC]
-
-# after removing Gall_Number, there is minimal shrinkage for AIC, but substantial shrinkage for BIC
-# but how do I decide which method is "best"
-lasso_final <- glmmLasso(gall_survival ~ f.Foodweb + 
-                       sc.Diam + sc.log.Clutch + sc.sqrt.Pref + 
-                       f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
-                       I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-                       f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
-                       sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-                       f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref,
-                     rnd = list(f.Genotype=~1, f.Plant_Position=~1), # , f.Gall_Number=~1
-                     family = binomial(link=logit),
-                     data = gall_selection.df_test,
-                     lambda = lambda[optLassoBIC], # lambda = 43 now, instead of 27...
-                     switch.NR = F,
-                     final.re = TRUE,
-                     control = list(start = Delta.start[optLassoBIC, ]))
-
-summary(lasso_final)
-
-## plot coefficient paths
-plot(lambda, Delta.start[2:(length(lambda)+1),2], type="l", lty=1, ylim=c(-0.5,0.5), ylab=expression(hat(beta[i])))
-abline(v = lambda[optLasso])
-lines(lambda, Delta.start[2:(length(lambda)+1),3], lty=2)
-lines(lambda, Delta.start[2:(length(lambda)+1),4], lty=3)
-lines(lambda, Delta.start[2:(length(lambda)+1),5], lty=4)
-lines(lambda, Delta.start[2:(length(lambda)+1),6], lty=5)
-lines(lambda, Delta.start[2:(length(lambda)+1),7], lty=6)
-lines(lambda, Delta.start[2:(length(lambda)+1),8], lty=7)
-lines(lambda, Delta.start[2:(length(lambda)+1),9], lty=8)
-```
-
-```{r test, eval=FALSE}
-full_glmer <- glmer(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    f.Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)) +
-    f.Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"))
-summary(full_glmer)
-drop1(full_glmer, test="Chisq") # no clear evidence of food-web structure altering correlation or quadratic gradients
-
-lin_glmer <- glmer(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"))
-summary(lin_glmer)
-drop1(lin_glmer, test="Chisq") # only clear evidence of food-web structure altering selection on clutch size
-
-red_glmer <- glmer(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    f.Foodweb:sc.log.Clutch +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"))
-summary(red_glmer)
-
-gall_selection.df_test <- gall_selection.df_test %>%
-  mutate(c.Diam = Diam - mean(Diam),
-         c.log.Clutch = log.Clutch - mean(log.Clutch),
-         c.sqrt.Pref = sqrt.Pref - mean(sqrt.Pref))
-library(MASS)
-red_glmer2 <- glmer(
-  gall_survival ~ 
-    Foodweb + 
-    c.Diam + c.log.Clutch + c.sqrt.Pref +
-    I(c.Diam^2) + I(c.log.Clutch^2) + I(c.sqrt.Pref^2) +
-    c.Diam:c.log.Clutch + c.Diam:c.sqrt.Pref + c.log.Clutch:c.sqrt.Pref +
-    Foodweb:c.log.Clutch +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"),
-  contrast = list(Foodweb="contr.Sum"))
-summary(red_glmer2)
-
-red_glmer3 <- glmer(
-  gall_survival ~ 
-    Foodweb*(scale(poly(Diam, 2)) + scale(poly(log.Clutch, 2)) + scale(poly(sqrt.Pref, 2))) +
-    Foodweb*(scale(poly(Diam, 2)[ ,1]):scale(poly(log.Clutch, 2)[ ,1]) + scale(poly(Diam, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1]) + scale(poly(log.Clutch, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1])) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"))
-summary(red_glmer3)
-
-gall_selection.df_test <- gall_selection.df_test %>% mutate(poly.log.Clutch = poly(log.Clutch, 2))
-
-red_glmer4 <- glmer(
-  gall_survival ~ 
-    Foodweb + (scale(poly(Diam, 2)) + scale(poly(log.Clutch, 2)) + scale(poly(sqrt.Pref, 2))) +
-    Foodweb:scale(poly(log.Clutch, 2)[ ,1]) +
-    Foodweb + (scale(poly(Diam, 2)[ ,1]):scale(poly(log.Clutch, 2)[ ,1]) + scale(poly(Diam, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1]) + scale(poly(log.Clutch, 2)[ ,1]):scale(poly(sqrt.Pref, 2)[, 1])) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"))
-summary(red_glmer4)
-
-fixef(red_glmer4)
-MuMIn::std.coef(red_glmer4, partial.sd = T)
-MuMIn::stdizeFit(red_glmer2, data=gall_selection.df_test, scale=T)
-fixef(red_glmer2)
-
-# so, with this interpretation, having a significant effect of clutch size will constrain both the slope and curvature of the adaptive landscape more.
-
-# I think I need to rely more on interpreting differences between food-web treatments, rather than getting separate estimates for each food-web treatment, which will have weaker signals.
-Plus, this will enable me to fill in the covariance matrix...the issue now is, how does the mortality propogate through to affect the selection gradients?
-# the unfortunate thing, is that this may require me to code things a bit differently from the beginning...
-
-test_foodweb_correl <- update(full_glmer, .~. -f.Foodweb:(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref))
-summary(test_foodweb_correl)
-anova(full_glmer, test_foodweb_correl, test="LR") # no diff, indicates there is no clear effect of food-web on correlational gradients
-
-test_foodweb_quad <- update(full_glmer, .~. -f.Foodweb:(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)))
-anova(full_glmer, test_foodweb_quad, test="LR") # no sig. diff, indicates there is no clear effect of food-web on quadratic gradients
-
-test_correl <- update(test_foodweb_correl, .~. -(sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref))
-anova(test_foodweb_correl, test_correl, test="LR") # sig. diff, argues to keep correlational gradients
-
-test_quad <- update(test_foodweb_quad, .~. -(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2)))
-anova(test_foodweb_quad, test_quad, test="LR") # sig. diff, argues to keep quadratic gradients
-
-test_foodweb_lin <- glmer(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    (1|Genotype) + (1|Plant_Position),
-  data = gall_selection.df_test,
-  family=binomial(link=logit))
-
-test_lin <- update(test_foodweb_lin, .~. -f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref))
-anova(test_foodweb_lin, test_lin, test="LR") # indicates that food-web alters linear selection gradients
-
-test_model <- glmer(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref) +
-    (1|Genotype) + (1|Plant_Position),
-  data = gall_selection.df_test,
-  family=binomial(link=logit))
-summary(test_model)
-
-library(polywog)
-test_polywog <- polywog(gall_survival ~ sc.Diam + sc.log.Clutch + sc.sqrt.Pref, 
-                        degree = 2,
-                        #boot = 100,
-                        family="binomial", data=filter(gall_selection.df_test, f.Foodweb=="Complex"))
-summary(test_polywog)
-
-library(parcor)
-
-full_glm <- glm(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    f.Foodweb:(sc.Diam + sc.log.Clutch + sc.sqrt.Pref),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  na.action = "na.fail") 
-```
-
-```{r test model selection, eval=FALSE}
-library(MuMIn)
-
-full_glmer <- glmer(
-  gall_survival ~ 
-    f.Foodweb + 
-    sc.Diam + sc.log.Clutch + sc.sqrt.Pref +
-    I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref +
-    f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref +
-    f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
-    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df_test,
-  family=binomial(link=logit),
-  control=glmerControl(optimizer="bobyqa"),
-  na.action = "na.fail")
-summary(full_glmer)
-drop1(full_glmer, test="Chisq") # marginal quadratic effect of Pref. no clear effect of food-web on correlational or quadratic gradients.
-drop1(update(full_glmer, .~. -(f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
-    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq") # marginal effects of quadratic Diam and Pref and Diam:Clutch
-drop1(update(full_glmer, .~. -(I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref + f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
-    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq") # clear effect of food web on clutch
-drop1(update(full_glmer, .~. -(f.Foodweb:sc.Diam + f.Foodweb:sc.log.Clutch + f.Foodweb:sc.sqrt.Pref + I(sc.Diam^2) + I(sc.log.Clutch^2) + I(sc.sqrt.Pref^2) +
-    sc.Diam:sc.log.Clutch + sc.Diam:sc.sqrt.Pref + sc.log.Clutch:sc.sqrt.Pref + f.Foodweb:I(sc.Diam^2) + f.Foodweb:I(sc.log.Clutch^2) + f.Foodweb:I(sc.sqrt.Pref^2) +
-    f.Foodweb:sc.Diam:sc.log.Clutch + f.Foodweb:sc.Diam:sc.sqrt.Pref + f.Foodweb:sc.log.Clutch:sc.sqrt.Pref)), test="Chisq")
-
-# Set up the cluster
-clusterType <- if(length(find.package("snow", quiet = TRUE))) "SOCK" else "PSOCK"
-clust <- try(parallel::makeCluster(getOption("cl.cores", 32), type = clusterType))
-
-clusterExport(clust, "gall_selection.df_test")
-clusterEvalQ(clust, library(lme4))
-
-# BIC model is VERY restrictive: only foodweb, diam, and pref left everything else exluded in model with lowest BIC
-test_dredge <- MuMIn::pdredge(full_glmer, 
-                              #fixed = c("f.Foodweb", "sc.Diam", "sc.log.Clutch", "sc.sqrt.Pref", "f.Foodweb:sc.Diam", "f.Foodweb:sc.log.Clutch", "f.Foodweb:sc.sqrt.Pref"), 
-                              trace = 2, 
-                              rank = "BIC", # AICc # using BIC removes all higher order terms...
-                              cluster = clust)
-
-summary(get.models(test_dredge, 1)[[1]])
-
-subset(test_dredge, delta < 10)
-
-test_sub <- MuMIn::model.avg(test_dredge, subset = delta < 10)
-test_sub
-coefTable(test_sub)
-#coefTable(test_dredge)
-```
-
-We used parametric bootstrapping to calculate 95% confidence intervals of trait-fitness relationships.
-
-```{r Bootstrap food-web model, cache=TRUE}
-boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, #std.coefs, # 
-                              nsim=n_boots_analysis, 
-                              parallel="multicore", ncpus=32, seed=34)
-```
-
-In order to reliably quantify linear trait-fitness relationships, we remove all higher-order terms from the model [Stinchcombe et al.
-2008](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x).
-
-```{r Linear food-web model, cache=TRUE, eval=FALSE}
-linear_foodweb_model <- glmer(
-  gall_survival ~ 
-    -1 + Foodweb + 
-    Foodweb:(sc.Diam.1 + sc.log.Clutch.1 + sc.sqrt.Pref.1) +
-    (1|Genotype/Plant_Position/Gall_Number),
-  data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
 ```
@@
 
-```{r Bootstrap linear food-web model, cache=TRUE, eval=FALSE}
+```{r Bootstrap linear food-web model, cache=TRUE}
 boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
   gall_survival ~ -1 + Foodweb + 
-    Foodweb:sc.Diam.1 + 
+    Foodweb:sc.Diam + 
     (1|Genotype/Plant_Position/Gall_Number),
@@
   select(term, estimate, conf.low, conf.high) %>%
-  filter(term %in% c("FoodwebComplex:sc.Diam.1","FoodwebSimple:sc.Diam.1")) %>%
-  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
-  #knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
+  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
+  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
 ```
@@
 ```{r Food-web alpha coefficients}
-foodweb_bind <- as_tibble(boot_foodweb_model$t) %>%
-  rename(FoodwebComplex = `(Intercept)`,
-         `FoodwebComplex:sc.Diam.1` = sc.Diam.1,
-         `FoodwebComplex:sc.log.Clutch.1` = sc.log.Clutch.1,
-         `FoodwebComplex:sc.sqrt.Pref.1` = sc.sqrt.Pref.1,
-         `FoodwebComplex:sc.Diam.2` = sc.Diam.2,
-         `FoodwebComplex:sc.log.Clutch.2` = sc.log.Clutch.2,
-         `FoodwebComplex:sc.sqrt.Pref.2` = sc.sqrt.Pref.2,
-         `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1` = `sc.Diam.1:sc.log.Clutch.1`,
-         `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1` = `sc.Diam.1:sc.sqrt.Pref.1`,
-         `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1` = `sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
-  # set trait-fitness relationships equal for appropriate terms
-  mutate(`FoodwebSimple:sc.Diam.1` = `FoodwebComplex:sc.Diam.1`,
-         #`FoodwebSimple:sc.log.Clutch.1` # we estimate food-web effects for this term
-         `FoodwebSimple:sc.sqrt.Pref.1` = `FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebSimple:sc.Diam.2` = `FoodwebComplex:sc.Diam.2`,
-         `FoodwebSimple:sc.log.Clutch.2` = `FoodwebComplex:sc.log.Clutch.2`,
-         #`FoodwebSimple:sc.sqrt.Pref.2` # we estimate food-web effects for this term
-         `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` = `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
-         `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
-         `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`)
-  #bind_cols(
-  #as_tibble(boot_linear_foodweb_model$t),
-  #select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
-#)
+foodweb_bind <- bind_cols(
+  as_tibble(boot_linear_foodweb_model$t),
+  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
 
@@
 foodweb_adj_Diam <- foodweb_bind %>%
-  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` -fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"], # std.coefs(biased_foodweb_model)["FoodwebComplex:sc.Diam.1"], #
-         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"]) #std.coefs(biased_foodweb_model)["FoodwebSimple:sc.Diam.1"]) #
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])
 
@@
   mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
-         `FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
-         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
-         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
-         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
-         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
+         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
          coefficient_type = ifelse(term=="(Intercept)","Mean fitness",
-                                   ifelse(grepl("\\.2", .$term)==TRUE, "Quadratic",
+                                   ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                           ifelse(grepl(":", .$term)==TRUE, "Correlational","Linear"))))
@@
   select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3))# %>%
-# knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+ knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
 ```
@@
   select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3))# %>%
-# knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+ knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
 ```
@@
 plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
             aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
             aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_correlational_coefs <- tidy_foodweb_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
             aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
-         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
-         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
-         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
-         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
   mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
-         gradient_type = ifelse(grepl("\\.2", .$term)==TRUE, "Quadratic",
+         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
                                 ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
@@
   select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
-#knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
 ```
@@
   select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
- # knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
 ```
@@
 foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
-  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:sc.Diam.2` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.Diam.1`,
-         `FoodwebComplex:C.Clutch` = `FoodwebComplex:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.1`*`FoodwebComplex:sc.log.Clutch.1`,
-         `FoodwebComplex:C.Pref` = `FoodwebComplex:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.1`*`FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.log.Clutch.1`,
-         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1`*`FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1`*`FoodwebComplex:sc.sqrt.Pref.1`)
+  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
+         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
+         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
+         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)
 
@@
 foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
-  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:sc.Diam.2` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.Diam.1`,
-         `FoodwebSimple:C.Clutch` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebSimple:sc.log.Clutch.1`*`FoodwebSimple:sc.log.Clutch.1`,
-         `FoodwebSimple:C.Pref` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebSimple:sc.sqrt.Pref.1`*`FoodwebSimple:sc.sqrt.Pref.1`,
-         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.log.Clutch.1`,
-         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebSimple:sc.Diam.1`*`FoodwebSimple:sc.sqrt.Pref.1`,
-         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebSimple:sc.log.Clutch.1`*`FoodwebSimple:sc.sqrt.Pref.1`)
+  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.Diam`,
+         `FoodwebSimple:C.Clutch` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.log.Clutch`,
+         `FoodwebSimple:C.Pref` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebSimple:sc.sqrt.Pref`*`FoodwebSimple:sc.sqrt.Pref`,
+         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.log.Clutch`,
+         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.sqrt.Pref`,
+         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.sqrt.Pref`)
 
@@
   select(term, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
-#knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
 ```
@@
   select(term, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) #%>%
-  #knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
 ```
@@
 plot_foodweb_directional_grads <- tidy_foodweb_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
             aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_quadratic_grads <- tidy_foodweb_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
             aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_foodweb_correlational_grads <- tidy_foodweb_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
             aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
@@
 
-```{r Linear egg vs. larval ptoid model, cache=TRUE, eval=FALSE}
+```{r Linear egg vs. larval ptoid model, cache=TRUE}
 linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
@@
 
-```{r Bootstrap linear egg vs. larval model, cache=TRUE, eval=FALSE}
+```{r Bootstrap linear egg vs. larval model, cache=TRUE}
 boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 ```{r Egg vs. larval ptoid alpha coefficients}
-egglarval_bind <- as_tibble(boot_egglarval_model$t) #bind_cols(
-  #as_tibble(boot_linear_egglarval_model$t),
-  #select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
-#)
+egglarval_bind <- bind_cols(
+  as_tibble(boot_linear_egglarval_model$t),
+  select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
 
@@
 egglarval_adj_Diam <- as_tibble(boot_egglarval_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam.1"],
-         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam.1"])
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])
 
@@
 plot_egglarval_linear_coefs <- tidy_egglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
             aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_quadratic_coefs <- tidy_egglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
             aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_correlational_coefs <- tidy_egglarval_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
             aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 egglarval_grads <- bind_cols(egglarval_complex_raw_gradients, egglarval_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
-         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
-         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
-         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
-         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 plot_egglarval_directional_grads <- tidy_egglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
             aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_quadratic_grads <- tidy_egglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
             aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_egglarval_correlational_grads <- tidy_egglarval_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
             aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
@@
 
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE, eval=FALSE}
+```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE}
 newdata_Diam <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = 0))
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
 
@@
 
-```{r Get Clutch Size Fitness Landscape, cache=TRUE, eval=FALSE}
+```{r Get Clutch Size Fitness Landscape, cache=TRUE}
 newdata_Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = 0))
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
 
@@
 
-```{r Get Oviposition preference Fitness Landscape, cache=TRUE, eval=FALSE}
+```{r Get Oviposition preference Fitness Landscape, cache=TRUE}
 
 newdata_Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam.1 = 0, sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam.1 = 0, sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
 
-```{r Plot Univariate Landscapes, eval=FALSE}
+```{r Plot Univariate Landscapes}
 uni_breaks <- c(0.1,0.5,1.0)
@@
 AF_uni_Diam <- RF_Diam$absolute_fitness %>% 
-  select(-sc.log.Clutch.1, -sc.sqrt.Pref.1) %>%
-  gather(ID, absolute_fitness, -sc.Diam.1, -Foodweb) %>%
+  select(-sc.log.Clutch, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.Diam.1, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 AF_uni_Pref <- RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam.1, -sc.log.Clutch.1) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref.1, -Foodweb) %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.sqrt.Pref.1, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 AF_uni_Clutch <- RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam.1, -sc.sqrt.Pref.1) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch.1, -Foodweb) %>%
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
-  ggplot(., aes(x=sc.log.Clutch.1, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 
-```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs.", eval=FALSE}
+```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs."}
 
@@
 
-```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness.", eval=FALSE}
+```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness."}
 
 RF_plot_foodweb_Clutch_df <- RF_Clutch$absolute_fitness %>% 
-  select(-sc.Diam.1, -sc.sqrt.Pref.1) %>%
-  gather(ID, absolute_fitness, -sc.log.Clutch.1, -Foodweb) %>%
+  select(-sc.Diam, -sc.sqrt.Pref) %>%
+  gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 RF_uni_Clutch <- RF_plot_foodweb_Clutch_df %>%
-  ggplot(., aes(x=sc.log.Clutch.1, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.log.Clutch, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 RF_plot_foodweb_Pref_df <- RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam.1, -sc.log.Clutch.1) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref.1, -Foodweb) %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 RF_uni_Pref <- RF_plot_foodweb_Pref_df %>%
-  ggplot(., aes(x=sc.sqrt.Pref.1, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 RF_plot_foodweb_Diam_df <- RF_Diam$absolute_fitness %>% 
-  select(-sc.sqrt.Pref.1, -sc.log.Clutch.1) %>%
-  gather(ID, absolute_fitness, -sc.Diam.1, -Foodweb) %>%
+  select(-sc.sqrt.Pref, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 RF_uni_Diam <- RF_plot_foodweb_Diam_df %>%
-  ggplot(., aes(x=sc.Diam.1, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.Diam, y=relative_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
   geom_line() +
@@
 
-```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE, eval=FALSE}
+```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE}
 
 newdata_Clutch.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam.1 = 0, sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
 
-```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, eval=FALSE}
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE}
 
 newdata_Diam.Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1 = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = seq(-1,1,length.out=1000), sc.sqrt.Pref.1=0))
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
 
@@
 
-```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE, eval=FALSE}
+```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE}
 
 newdata_Diam.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam.1 = seq(-1,1,length.out=1000), sc.log.Clutch.1 = 0, sc.sqrt.Pref.1 = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
 
-```{r Get plots of multivariate adaptive landscape, eval=FALSE}
+```{r Get plots of multivariate adaptive landscape}
 
@@
 # Set contour breaks
-breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam.1 = c(0,0), sc.log.Clutch.1 = c(0,0), sc.sqrt.Pref.1 = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
+breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
 names(breaks) <- c("Complex","Simple")
@@
   filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.Diam.1, y=sc.log.Clutch.1)) +
+  ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
   geom_raster(aes(fill=average)) +
@@
   filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.Diam.1, y=sc.sqrt.Pref.1)) +
+  ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
   geom_raster(aes(fill=average)) +
@@
   filter(Foodweb == "Complex") %>%
-  ggplot(., aes(x=sc.sqrt.Pref.1, y=sc.log.Clutch.1)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
   geom_raster(aes(fill=average)) +
@@
 Dotted lines denote fitness for the mean phenotype.
-Arrows represent the vector of directional selection gradients acting on each phenotype.", eval=FALSE}
+Arrows represent the vector of directional selection gradients acting on each phenotype."}
 
@@
 gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.Diam.1 = c(0,0), 
-                                    sc.log.Clutch.1 = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam.1")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam.1")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch.1")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch.1")$mean))
+                                    sc.Diam = c(0,0), 
+                                    sc.log.Clutch = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
 
 gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.sqrt.Pref.1 = c(0,0), 
-                                    sc.log.Clutch.1 = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref.1")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref.1")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch.1")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch.1")$mean))
+                                    sc.sqrt.Pref = c(0,0), 
+                                    sc.log.Clutch = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
 
 gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
-                                    sc.Diam.1 = c(0,0), 
-                                    sc.sqrt.Pref.1 = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam.1")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam.1")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref.1")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref.1")$mean))
+                                    sc.Diam = c(0,0), 
+                                    sc.sqrt.Pref = c(0,0), 
+                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))
 
@@
     geom_segment(data = gradients_Diam.Clutch, 
-                 aes(x = sc.Diam.1, y = sc.log.Clutch.1, xend = xend, yend = yend), 
+                 aes(x = sc.Diam, y = sc.log.Clutch, xend = xend, yend = yend), 
                  arrow = arrow(length = unit(0.03, "npc"))),
@@
     geom_segment(data = gradients_Clutch.Pref, 
-                 aes(x = sc.sqrt.Pref.1, y = sc.log.Clutch.1, xend = xend, yend = yend), 
+                 aes(x = sc.sqrt.Pref, y = sc.log.Clutch, xend = xend, yend = yend), 
                  arrow = arrow(length = unit(0.03, "npc"))), 
@@
     geom_segment(data = gradients_Diam.Pref, 
-                 aes(x = sc.Diam.1, y = sc.sqrt.Pref.1, xend = xend, yend = yend), 
+                 aes(x = sc.Diam, y = sc.sqrt.Pref, xend = xend, yend = yend), 
                  arrow = arrow(length = unit(0.03, "npc"))), 
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-complex_betas_df$term <- factor(complex_betas_df$term, levels=c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1"), labels=c("Diam","Clutch","Pref"), order=TRUE)
+complex_betas_df$term <- factor(complex_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
 rownames(complex_betas_df) <- complex_betas_df$term
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-complex_gammas_df$term <- factor(complex_gammas_df$term, levels=c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2","sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+complex_gammas_df$term <- factor(complex_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
 rownames(complex_gammas_df) <- complex_gammas_df$term
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-simple_betas_df$term <- factor(simple_betas_df$term, levels=c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1"), labels=c("Diam","Clutch","Pref"), order=TRUE)
+simple_betas_df$term <- factor(simple_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
 rownames(simple_betas_df) <- simple_betas_df$term
@@
   select(term, gradient=mean, low=conf.low, high=conf.high)
-simple_gammas_df$term <- factor(simple_gammas_df$term, levels=c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2","sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+simple_gammas_df$term <- factor(simple_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
 rownames(simple_gammas_df) <- simple_gammas_df$term
@@
 
-```{r Linear egg vs. egg ptoid model, cache=TRUE, eval=FALSE}
+```{r Linear egg vs. egg ptoid model, cache=TRUE}
 linear_eggegg_model <- update(linear_foodweb_model, data=eggegg_df)
@@
 
-```{r Bootstrap linear egg vs. egg model, cache=TRUE, eval=FALSE}
+```{r Bootstrap linear egg vs. egg model, cache=TRUE}
 boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 ```{r Egg vs. egg ptoid alpha coefficients}
-eggegg_bind <- as_tibble(boot_eggegg_model$t)#bind_cols(
- # as_tibble(boot_linear_eggegg_model$t),
- # select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:sc.Diam.2`:`FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1`) # only retain nonlinear coefficients from full model
-#)
+eggegg_bind <- bind_cols(
+  as_tibble(boot_linear_eggegg_model$t),
+  select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+)
 
@@
 eggegg_adj_Diam <- as_tibble(boot_eggegg_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam.1` = `FoodwebComplex:sc.Diam.1` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam.1"],
-         `FoodwebSimple:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam.1"])
+  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
+         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])
 
@@
 plot_eggegg_linear_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
             aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_quadratic_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
             aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_correlational_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
             aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
@@
 eggegg_grads <- bind_cols(eggegg_complex_raw_gradients, eggegg_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam.1` = `FoodwebSimple:sc.Diam.1` - `FoodwebComplex:sc.Diam.1`,
-         `FoodwebDiff:sc.log.Clutch.1` = `FoodwebSimple:sc.log.Clutch.1` - `FoodwebComplex:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.sqrt.Pref.1` = `FoodwebSimple:sc.sqrt.Pref.1` - `FoodwebComplex:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.Diam.2` = `FoodwebSimple:sc.Diam.2` - `FoodwebComplex:sc.Diam.2`,
-         `FoodwebDiff:sc.log.Clutch.2` = `FoodwebSimple:sc.log.Clutch.2` - `FoodwebComplex:sc.log.Clutch.2`,
-         `FoodwebDiff:sc.sqrt.Pref.2` = `FoodwebSimple:sc.sqrt.Pref.2` - `FoodwebComplex:sc.sqrt.Pref.2`,
-         `FoodwebDiff:sc.Diam.1:sc.log.Clutch.1` = `FoodwebSimple:sc.Diam.1:sc.log.Clutch.1` - `FoodwebComplex:sc.Diam.1:sc.log.Clutch.1`,
-         `FoodwebDiff:sc.Diam.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.Diam.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.Diam.1:sc.sqrt.Pref.1`,
-         `FoodwebDiff:sc.log.Clutch.1:sc.sqrt.Pref.1` = `FoodwebSimple:sc.log.Clutch.1:sc.sqrt.Pref.1` - `FoodwebComplex:sc.log.Clutch.1:sc.sqrt.Pref.1`) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 plot_eggegg_directional_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam.1","sc.log.Clutch.1","sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
             aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_quadratic_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")) %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam.2","sc.log.Clutch.2","sc.sqrt.Pref.2")), 
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
             aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
@@
 plot_eggegg_correlational_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")) %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam.1:sc.log.Clutch.1","sc.Diam.1:sc.sqrt.Pref.1","sc.log.Clutch.1:sc.sqrt.Pref.1")), 
+  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
             aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
@@
 
-```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids", eval=FALSE}
+```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids"}
 # this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
@@
 eggptoid_plot_df <- eggegg_RF_Pref$absolute_fitness %>% 
-  select(-sc.Diam.1, -sc.log.Clutch.1) %>%
-  gather(ID, absolute_fitness, -sc.sqrt.Pref.1, -Foodweb) %>%
+  select(-sc.Diam, -sc.log.Clutch) %>%
+  gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
   mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
@@
 eggptoid_selection_plot <- eggptoid_plot_df %>%
-  ggplot(., aes(x=sc.sqrt.Pref.1, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
+  ggplot(., aes(x=sc.sqrt.Pref, y=fitness_difference, group=ID, alpha=ID_group, size=ID_group)) +
   geom_line(color=cbPalette[5]) +

### 2019-05-03 manuscript.Rmd
many minor edits to address response letter.

@@
 Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web structure shape evolutionary constraints.
-We conducted a field experiment that manipulated whether a guild of larval parasitoids were able to impose selection on an insect herbivore.
+We conducted a field experiment that simulated the extinction of a guild of larval parasitoids that were able to impose selection on an insect herbivore.
 We then measured herbivore survival as a function of three key phenotypic traits.
-We found that more traits were under selection when we excluded interactions with larval parasitoids.
-The adaptive landscape was more neutral in the intact food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
+We found that the number of traits under selection increased with the extinction of larval parasitoids.
+In contrast, the adaptive landscape was more neutral in the intact food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
 Our results suggest that the loss of trophic interactions can impose greater constraints on phenotypic evolution.
@@
 For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
-Evolutionary trajectories become more constrained with an increase in the number of traits under selection, as this diminishes the number of optimal solutions [@Arnold2003].
+Selective constraints on evolution increase with the number of traits under directional selection, as this diminishes the number of optimal solutions [@Arnold2003].
 The curvature of the adaptive landscape can also constrain evolution through its indirect effect on genetic constraints [@Arnold1992; @Hansen2008].
@@
 Black arrows denote the flow of energy in this network of trophic interactions.
-In the complex food-web treatment, we allowed the full suite of egg and larval parasitoids to impose selection.
-In the simple food-web treatment, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+In the intact food web, we allowed the full suite of egg and larval parasitoids to impose selection.
+To simulate consumer extinction, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
 Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
@@
 We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`%).
-
+Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
+Another reason why we excluded other sources of mortality, such as early larval death, is that they can influence the expression of the gall phenotype and confound estimates of selection.
 For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
@@
 
-**Selection gradients**: Selection gradients cannot be estimated directly from generalized linear (mixed) models, because the coefficients are on a nonlinear scale.
+**Selection gradients**: Selection gradients cannot be estimated directly from GLMMs on selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
 For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e., $\text{ln}\{W(z)[1-W(z)]\}$) associated with a unit change in a trait with all other traits held fixed.
-Therefore, we used the method developed by @Janzen1998 to translate trait-fitness relationships from the above model into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i:z_i}$), and correlational ($\gamma_{z_i:z_j}$) selection gradients.
+Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i:z_i}$), and correlational ($\gamma_{z_i:z_j}$) selection gradients.
 Briefly, this method calculates the average gradient of selection surfaces by multiplying the average of $W(z)[1-W(z)]$ by each regression coefficient (e.g.
@@
 $$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-By comparing the number of traits that determine the slope (i.e., nonzero directional selection gradients) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
+By comparing the number of traits that show clear evidence of contributing to the slope (i.e., directional selection gradients where the 95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
 
-The indirect effects of selection on genetic constraints is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
+The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 
@@
 Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
-Therefore, we can infer the indirect effects of selection on genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
+Therefore, we can infer the number of genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
+For these analyses, we only retained selection gradients that showed clear evidence of being different from zero (i.e.
+95% CI did not overlap zero) prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
+This provided us with a conservative estimate of the factors contributing to the curvature of the adaptive landscape and guarding against any false positive (i.e.
+Type I error).
+
+Note that we do not put much stock in differences in the magnitude of selection between food-web treatments, but instead are concerned primarily with whether these gradients are clearly nonzero.
+This is because their is a high likelihood that we are underestimating the magnitude of each selection gradient in our treatment that excludes larval parasitoids.
+This occurs because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (X% mortality).
+Therefore, our short-term removal of larval parasitoids has not allowed for a numerical response in egg parasitoids.
+An increase in the abundance of egg parasitoids would surely increase the magnitude of selection estimates in the extinction treatment due to the increased mortality of gall midges, which would increase variance in relative fitness.
+A recent paper by @Hunter2008 highlight this pervasive effect of survival on the magnitude of selection estimates.
+Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.
+This is why we put more stock in our qualitative estimates of selection (i.e.
+selective constraints = number of traits under directional selection; genetic constraints = number of negative variances + nonzero covariances).
 
@@
 `r round(filter(biased_foodweb_confint, term=="FoodwebSimple:sc.Diam")$conf.high,2)`]), indicating that unadjusted relationships would overestimate the strength of selection on chamber diameter.
-To account for this bias, we substracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's trait-fitness relationship and directional selection gradient.
+To account for this bias, we substracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's selection surface and directional selection gradient.
 
@@
 Our food-web manipulation allows us to measure selection imposed by larval parasitoids on the phenotype of egg parasitoids.
-Using the same models as described above, we substituted egg parasitism as our response variable to quantify trait-fitness relationships and selection gradients acting on the egg parasitoid.
+Using the same models as described above, we substituted egg parasitism as our response variable to quantify selection surfaces and selection gradients acting on the egg parasitoid.
 Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate the selection imposed by larval parasitoids.
@@
 All analyses and visualizations were conducted in R [@R2018].
-Unless otherwise noted, we report mean estimates of trait-fitness relationships and selection gradients with 95% confidence intervals in brackets.
+Unless otherwise noted, we report mean estimates of selection surfaces and selection gradients with 95% confidence intervals in brackets.
 Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
@@
 In the simple food web, we also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, this relationship was weaker in complex food webs (table \ref{Table:Gradients}).
-This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on the extended phenotype of egg parasitoids section), and thus a less than additive effect on gall midges.
+\ref{fig:UV_Landscape}B); however, there was no clear relationship in complex food webs (table \ref{Table:Gradients}).
+This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on egg parasitoids section), and thus a less than additive effect on gall midges.
 Chamber diameter experienced positive directional selection in both food-web treatments, but selection was `r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
@@
 \begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in complex vs. simple food webs.}
+\caption{Standardized selection gradients acting on gall midges in intact food webs vs. under consumer extinction.}
 \label{Table:Gradients}
 \centering
-\begin{tabular}{lccc}
+\begin{tabular}{lcc} %c
 \\ 
 \hline
-\textbf{Selection gradient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\textbf{Selection gradient} & \textbf{Intact} & \textbf{Extinction}   \\ %& \textbf{Contrast}
 \hline
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }& 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }\\%& 
+%\textbf{
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }\\%& 
+%\textbf{
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }\\%&
 
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] \\%&
 
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\%&
 
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\%& 
+%\textbf{
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\%&
 
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\%&
 
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\%&
 
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
 \hline
@@
 
-```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in complex vs.
-simple food webs.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in complex (orange) and simple (blue) food webs.
-Thin lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
-knitr::include_graphics("analyses/UV_landscapes.pdf")
-```
-
 ## Loss of trophic interactions increase genetic constraints
@@
 \indent The curvature of the adaptive landscape indirectly affects genetic constraints and is influenced by directional, quadratic, and correlational selection gradients.
-Our food-web treatment did not alter correlational selection for any combination of traits (table \ref{Table:Gradients}).
-Similarly, our food-web treatment did not influence quadratic selection on either chamber diameter or clutch size (table \ref{Table:Gradients}; fig.
+There was no clear evidence of correlational selection for any combination of traits in either food-web treatment (table \ref{Table:Gradients}).
+Similarly, there was no clear evidence of quadratic selection on chamber diameter or clutch size in either food-web treatment (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}A,C).
@@
 
-To estimate the net effect of food-web structure on the curvature ($C$) of the adaptive landscape, we only retained nonzero selection gradients (i.e.
-95\% CI did not overlap zero) prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
+```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in intact food webs vs.
+consumer extinction.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
+Bold lines represent selection experienced in intact food webs (orange) and with consumer extinction (blue).
+Thin lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
+knitr::include_graphics("analyses/UV_landscapes.pdf")
+```
+
+Using our estimates of directional, quadratic, and correlation selection, we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
+In order to be conservative in the factors contributing to curvature, we only used those estimates that clearly differed from zero (i.e.
+95% CI did not overlap zero), otherwise we set the component gradients to zero.
 We found that the curvatures of the adaptive landscape exhibited the following structures:
 
-$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
+$$\textbf{C} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
+
+$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
+`r round(complex_gammas["Diam","Diam"],2)` &  &  \\  
+`r round(complex_gammas["Clutch","Diam"],2)` & `r round(complex_gammas["Clutch","Clutch"],2)` &  \\  
+`r round(complex_gammas["Pref","Diam"],2)` & `r round(complex_gammas["Pref","Clutch"],2)` & `r round(complex_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
+`r round(complex_betas["Diam",],2)`\cdot`r round(complex_betas["Diam",],2)` &  &  \\  
+`r round(complex_betas["Clutch",],2)`\cdot`r round(complex_betas["Diam",],2)` & `r round(complex_betas["Clutch",],2)`\cdot`r round(complex_betas["Clutch",],2)` &  \\  
+`r round(complex_betas["Pref",],2)`\cdot`r round(complex_betas["Diam",],2)` & `r round(complex_betas["Pref",],2)`\cdot`r round(complex_betas["Clutch",],2)` & `r round(complex_betas["Pref",],2)`\cdot`r round(complex_betas["Pref",],2)` \end{pmatrix}$$
 
@@
 `r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
+`r round(simple_gammas["Diam","Diam"],2)` &  &  \\  
+`r round(simple_gammas["Clutch","Diam"],2)` & `r round(simple_gammas["Clutch","Clutch"],2)` &  \\  
+`r round(simple_gammas["Pref","Diam"],2)` & `r round(simple_gammas["Pref","Clutch"],2)` & `r round(simple_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
+`r round(simple_betas["Diam",],2)`\cdot`r round(simple_betas["Diam",],2)` &  &  \\  
+`r round(simple_betas["Clutch",],2)`\cdot`r round(simple_betas["Diam",],2)` & `r round(simple_betas["Clutch",],2)`\cdot`r round(simple_betas["Clutch",],2)` &  \\  
+`r round(simple_betas["Pref",],2)`\cdot`r round(simple_betas["Diam",],2)` & `r round(simple_betas["Pref",],2)`\cdot`r round(simple_betas["Clutch",],2)` & `r round(simple_betas["Pref",],2)`\cdot`r round(simple_betas["Pref",],2)` \end{pmatrix}$$
 
@@
 more complex (1 of 6) food web.
-Simpler food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the more complex food web.
-For genetic covariances, the simpler food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
+Simpler food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms) due to directional selection, whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the more complex food web.
+For genetic covariances, directional selection in the simpler food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
 \ref{fig:MV_Landscape}).
-In contrast, there was no strong evidence of trait integration in the more complex food web (fig.
+In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the more complex food web (fig.
 \ref{fig:MV_Landscape}).
 
-```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in complex vs.
-simple food webs.
+```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in intact food webs vs.
+consumer extinction.
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
 Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the simple vs.
-complex food-web treatment.
-This indicates that trait integration (covariance) is more strongly favored in simpler vs.
-more complex food webs.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the extinction vs.
+intact food-web treatment.
+This indicates that trait integration (covariance) is more strongly favored with consumer extinction vs.
+intact food webs.
 Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
@@
 \begin{table}[h]
-\caption{Standardized selection gradients acting on the extended phenotype of egg parasitoids (\textit{Platygaster} sp.)}
+\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
 \label{Table:ExtendedGradients}
@@
 \hline
-\textbf{Selection gradient} & \textbf{Contrast = Complex - Simple}  \\ 
+\textbf{Selection gradient} & \textbf{Contrast = Intact - Extinction}  \\ 
 \hline
@@
 ```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid in complex vs.
-simple food webs as a function of gall midge oviposition preference.
+The bold line represents the average difference in the probability of observing the egg parasitoid in intact food webs vs.
+consumer extinction as a function of gall midge oviposition preference.
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
 For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on the extended phenotype of egg parasitoids."}
+The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on egg parasitoids."}
 knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
@@
 <!--Selective constraints-->
-All three phenotypic traits we examined experienced directional selection in the absence of larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
+All three phenotypic traits we examined experienced directional selection with the extinction of larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
 large chamber diameter, small clutch size, and avoidance of conspecifics).
@@
 <!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
-This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by genetic constraints.
-This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
+This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by how genetic constraints interact with other evolutionary processes (e.g.
+genetic drift, gene flow, and mutation).<!-- This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
 As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
+[Removing because this statement is simply not true]-->
 Interestingly, this aligns with @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
@@
 Our results suggest that the loss of trophic interactions may not only directly affect connected species, but also result in indirect evolutionary effects.
-In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we exlcuded larval parasitoids.
+In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we excluded larval parasitoids.
 This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
@@
 <!-- Conclusions -->
-Our study gives insight to how local extinctions alter evolutionary constraints on remaining populations.
+Our study gives insight to how consumer extinctions alter evolutionary constraints on remaining populations.
 In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.

### 2019-05-07 analyses/reproduce_analyses.Rmd
finished draft of revision and sent to Jordi for comments

@@
   gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
+         Foodweb = factor(ifelse(Foodweb == "Complex", "Intact", "Extinction"), levels = c("Intact", "Extinction"))) %>% 
   ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
+labels_2D <- list("Complex"="Intact", "Simple"="Extinction")
+labeller_2D <- function(variable, value) {
+  return(labels_2D[value])
+}
+
 # Size x Clutch
@@
   stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb) +
+  facet_wrap(~Foodweb, labeller = labeller_2D) +
   xlab("Gall diameter (SDs)") +
@@
   stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb) +
+  facet_wrap(~Foodweb, labeller = labeller_2D) +
   xlab("Chamber diameter (SDs)") +
@@
   stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb) +
+  facet_wrap(~Foodweb, labeller = labeller_2D) +
   xlab("Oviposition preference (SDs)") +
@@
   xlab("Gall midge preference (SDs)") + 
-  ylab(expression(paste(Delta," egg parasitoid survival (complex - simple)"))) +
+  ylab(expression(paste(Delta," egg parasitoid survival (intact - extinction)"))) +
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +

### 2019-05-07 manuscript.Rmd
finished draft of revision and sent to Jordi for comments

@@
 \vspace*{0.1cm} 
-\begin{center} \LARGE Extinction of a consumer guild constrains phenotypic evolution in an insect herbivore \end{center}
+\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in an insect herbivore \end{center}
 
@@
 In contrast, the adaptive landscape was more neutral in the intact food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
-Our results suggest that the loss of trophic interactions can impose greater constraints on phenotypic evolution.
+Our results suggest that the loss of trophic interactions due to consumer extinctions can impose greater constraints on phenotypic evolution.
 This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
@@
 These 128 plants came from eight different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
-As a control (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
+For intact food webs (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
-To exclude the guild of larval parasitoids, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
+To simulate consumer extinctions, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
 This treatment did not exclude the egg parasitoid *Platygaster* sp., which attacks prior to gall initiation [larva initiate gall development in Cecidomyiid midges: @Gagne1989].
@@
 We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
-Another reason why we excluded other sources of mortality, such as early larval death, is that they can influence the expression of the gall phenotype and confound estimates of selection.
-For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
+We removed other sources of mortality, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
+<!--Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
+Another reason why we excluded other sources of mortality, such as early larval death, is that they can influence the expression of the gall phenotype and confound estimates of selection.--> For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
 This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
@@
 
-**Selection surface**: Since larval survival was our measure of absolute fitness, we used a GLMM that assumed a binomial error distribution (and logit-link function).
+**Selection surfaces**: Since larval survival was our measure of absolute fitness, we used a GLMM that assumed a binomial error distribution (and logit-link function).
 To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_{z_i}$), quadratic ($\alpha_{z_i:z_i}$), and linear interactions ($\alpha_{z_i:z_j}$) between each trait.
-We also allowed these trait-fitness relationships ($\alpha$) to vary between food-web treatments.
-Note that to obtain valid estimates of linear trait-fitness relationships, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
+We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.
+Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
 Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the adaptive landscape [@Arnold2003].
@@
 Although statistical models with random effects are not common in analyses of natural selection, we think that modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
-Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e., setting them to zero) when calculating trait-fitness relationships.
-We then used parametric bootstrapping (1,000 replicates) to estimate the effect of food-web treatment on larval survival as well as trait-fitness relationships in each food-web treatment.
-To determine whether trait-fitness relationships differed between food-web treatments, we calculated the difference in bootstrapped replicates between treatments.
+Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e., setting them to zero) when calculating selection surfaces.
+We then used parametric bootstrapping (1,000 replicates) to estimate the effect of food-web treatment on larval survival as well as selection surfaces in each food-web treatment.
+<!--To determine whether trait-fitness relationships differed between food-web treatments, we calculated the difference in bootstrapped replicates between treatments.-->
 
@@
 $$\textbf{C} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
-$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
+$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
 
@@
 Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
-Therefore, we can infer the number of genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-For these analyses, we only retained selection gradients that showed clear evidence of being different from zero (i.e.
-95% CI did not overlap zero) prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
-This provided us with a conservative estimate of the factors contributing to the curvature of the adaptive landscape and guarding against any false positive (i.e.
-Type I error).
+Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
+For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
+This provides a conservative estimate of the factors contributing to the curvature of the adaptive landscape.
 
-Note that we do not put much stock in differences in the magnitude of selection between food-web treatments, but instead are concerned primarily with whether these gradients are clearly nonzero.
-This is because their is a high likelihood that we are underestimating the magnitude of each selection gradient in our treatment that excludes larval parasitoids.
-This occurs because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (X% mortality).
-Therefore, our short-term removal of larval parasitoids has not allowed for a numerical response in egg parasitoids.
-An increase in the abundance of egg parasitoids would surely increase the magnitude of selection estimates in the extinction treatment due to the increased mortality of gall midges, which would increase variance in relative fitness.
-A recent paper by @Hunter2008 highlight this pervasive effect of survival on the magnitude of selection estimates.
-Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.
-This is why we put more stock in our qualitative estimates of selection (i.e.
-selective constraints = number of traits under directional selection; genetic constraints = number of negative variances + nonzero covariances).
+Note that our metrics of selective and genetic constraints do not put much stock in differences in the magnitude of selection between food-web treatments.
+This is because there is a high likelihood that we are underestimating the magnitude of selection in our treatment that excludes larval parasitoids.
+We expect this because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (fig.
+\ref{fig:Conceptual}).
+Therefore, our short-term removal of larval parasitoids has not allowed for an increase in egg parasitoid abundance after being released from intraguild predation.
+An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates.
+A recent paper by @Hunter2008 highlight this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--> This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).
 
@@
 We used a GLMM with the same structure as described above except that we modeled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
-We detected a positive bias in both food-web treatments (complex $\alpha_{\text{Diam}}$=
+We detected a positive bias in both food-web treatments (intact $\alpha_{\text{Diam}}$=
 `r round(fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],2)` 
 [`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.low,2)`,
-`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.high,2)`]; simple $\alpha_{\text{Diam}}$=
+`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
 `r round(fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"],2)` 
@@
 Using the same models as described above, we substituted egg parasitism as our response variable to quantify selection surfaces and selection gradients acting on the egg parasitoid.
-Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate the selection imposed by larval parasitoids.
+Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate selection imposed by larval parasitoids.
 This comparison is still useful though in determining the extent to which the community context may have indirect evolutionary effects by altering selection on multiple interacting populations.
@@
 
-## Loss of trophic interactions increase selective constraints
+## Consumer extinctions increase selective constraints
 
-\indent We found that more gall midge traits experienced directional selection in the simple (3 of 3) vs.
-complex food-web treatment (1 of 3)(table \ref{Table:Gradients}).
-For example, we observed directional selection for smaller clutch sizes in the simple food web, but there was no evidence of selection acting on this trait in the complex food web (table \ref{Table:Gradients}; fig.
+\indent We found that the extinction of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the intact food web (1 of 3)(table \ref{Table:Gradients}).
+For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the intact food web (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}C).
@@
 `r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`]).
-In the simple food web, we also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, there was no clear relationship in complex food webs (table \ref{Table:Gradients}).
+We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}B); however, there was no clear relationship in the intact food web (table \ref{Table:Gradients}).
 This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on egg parasitoids section), and thus a less than additive effect on gall midges.
-Chamber diameter experienced positive directional selection in both food-web treatments, but selection was `r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
+Chamber diameter experienced positive directional selection in both food-web treatments (fig.
+\ref{fig:UV_Landscape}A).
+Although the magnitude of selection on chamber diameter was relatively higher in the intact food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival (selection surfaces: intact $\alpha_{\text{Diam}}$=
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in intact food webs (intact $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$conf.high,2)`]; extinction $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$conf.high,2)`]).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}).
@@
 [`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low, 2)`,
-`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high, 2)`]).
+`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high, 2)`]).-->
 
@@
 \begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in intact food webs vs. under consumer extinction.}
+\caption{Standardized selection gradients acting on gall midges in the intact food web and with the extinction of larval parasitoids.}
 \label{Table:Gradients}
@@
 
-## Loss of trophic interactions increase genetic constraints
+## Consumer extinctions increase genetic constraints
 
@@
 In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
-The negative relationship between oviposition preference and larval survival dampened at high densities in complex, but not simple food webs (fig.
+The negative relationship between oviposition preference and larval survival dampened at high densities in intact food webs, but not with the exclusion of larval parasitoids (fig.
 \ref{fig:UV_Landscape}B).
@@
 
-```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in intact food webs vs.
-consumer extinction.
+```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the intact food web and with the extinction of larval parasitoids.
 Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in intact food webs (orange) and with consumer extinction (blue).
+Bold lines represent selection experienced in intact food webs (orange) and with consumer extinctions (blue).
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 Using our estimates of directional, quadratic, and correlation selection, we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
-In order to be conservative in the factors contributing to curvature, we only used those estimates that clearly differed from zero (i.e.
-95% CI did not overlap zero), otherwise we set the component gradients to zero.
-We found that the curvatures of the adaptive landscape exhibited the following structures:
+In our study, this corresponds to:
 
@@
 $$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+\bigskip
+
+In order to obtain a conservative estimate of the factors contributing to the curvature, we only used estimates of selection that clearly differed from zero (bold values in table \ref{Table:Gradients}), otherwise we set estimates of selection to zero (non-bold values in table \ref{Table:Gradients}) prior to our calculation.
+We found that the curvatures of the adaptive landscape exhibited the following structures:
 
@@
 
-Remember that we can infer the indirect effects of selection on genetic constraints by counting the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-The structure of these matrices indicates that there are more selective constraints imposed on the gall midge in the simpler (6 of 6) vs.
-more complex (1 of 6) food web.
-Simpler food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms) due to directional selection, whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the more complex food web.
-For genetic covariances, directional selection in the simpler food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
+Remember that we can infer the indirect effects of selection on genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
+The structure of these matrices indicates that the extinction of larval parasitoids increased the number of genetic constraints on gall midges (6 of 6) relative to the intact food web (1 of 6).
+For example, directional selection resulting from the exclusion of larval parasitoids acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the intact food web.
+For genetic covariances, the combined effects of directional selection resulting from consumer extinctions favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
 \ref{fig:MV_Landscape}).
-In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the more complex food web (fig.
+In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the intact food web (fig.
 \ref{fig:MV_Landscape}).
 
-```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in intact food webs vs.
-consumer extinction.
+```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the intact food web and with the extinction of larval parasitoids.
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
 Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits in the extinction vs.
-intact food-web treatment.
-This indicates that trait integration (covariance) is more strongly favored with consumer extinction vs.
-intact food webs.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the intact food web.
+This indicates that consumer extinctions more strongly favored trait integration (covariance).
 Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
@@
 
-```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on the extended phenotype of egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid in intact food webs vs.
-consumer extinction as a function of gall midge oviposition preference.
+```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.).
+The bold line represents the average difference in the probability of observing the egg parasitoid (intact - extinction of larval parastioids) as a function of gall midge oviposition preference.
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 Second, excluding larval parasitoids indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
-Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of species interactions may have complex effects on the trajectories of phenotypic evolution.
-Taken together, our study provides experimental evidence from the field that the loss of trophic interactions may constrain the adaptive potential of remaining populations.
+Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
+Taken together, our study provides experimental evidence from the field that consumer extinctions may constrain the adaptive potential of remaining populations.
 
 <!--Selective constraints-->
-All three phenotypic traits we examined experienced directional selection with the extinction of larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
+All three phenotypic traits we examined experienced directional selection when we excluded larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
 large chamber diameter, small clutch size, and avoidance of conspecifics).
-In contrast, we did not observe selective constraints on clutch size and oviposition preference in the presence of larval parasitoids.
+In contrast, we did not observe clear evidence of selective constraints on clutch size and oviposition preference in the intact food web.
 This suggests that there are many optimal phenotypes (adaptive peaks), or in this case, a flat adaptive landscape where there are no fitness consequences for phenotypic change in these traits.
@@
 Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
-Together, this suggests that the loss of species interactions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
+Together, this suggests that consumer extinctions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
 Current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the community context [@McPeek2017; @Guimaraes2017].
@@
 The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
-For example, if consumers do not differ from each other, then we do not expect changes in food-web structure to modify selective constraints.
+For example, if consumers do not differ from each other, then we do not expect changes in food-web structure to modify evolutionary constraints.
 Also, many consumers may be at too low of abundances to impose selection on their resources.
@@
 <!--Indirect evolutionary effects-->
-Our results suggest that the loss of trophic interactions may not only directly affect connected species, but also result in indirect evolutionary effects.
+Our results suggest that the loss of consumers may not only directly affect connected species, but also result in indirect evolutionary effects.
 In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we excluded larval parasitoids.
@@
 A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @StartInPress].
-If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from the loss of species interactions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
+If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from consumer extinctions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 

### 2019-05-13 manuscript.Rmd
added caveats paragraph in Discussion.

@@
 
+<!-- Caveats -->
+Our study has some limitations to consider when relating our findings to the effects of consumer extinctions on evolutionary constraints more generally.
+First, we removed other sources of mortality prior to our analyses.
+While this was necessary to avoid confounding estimates of selection with effects on phenotypic expression, we may be overestimating the effects of selection due to parasitoids.
+Second, our metrics of evolutionary constraints do not account for variation in the magnitude of selection pressures.
+While quantitative metrics are possible and more ideal [@Hansen2008], we felt they were not appropriate to apply here as our experimental removal of larval parasitoids results in a transient dynamic in the strength (but not direction) of selection.
+Such transient dynamics may be common in short-term experimental studies of natural selection, but they can be detected by using natural history information and dissecting the sources of selection (e.g.
+quantifying selection surfaces and treatment effects on mean fitness) as we did here.
+
 <!-- Conclusions -->

### 2019-05-14 manuscript.Rmd
incorporated Jordi's suggested edits

@@
 \vspace*{0.1cm} 
-\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in an insect herbivore \end{center}
+\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in the resulting food web \end{center}
 
@@
 We found that the number of traits under selection increased with the extinction of larval parasitoids.
-In contrast, the adaptive landscape was more neutral in the intact food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
+In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
 Our results suggest that the loss of trophic interactions due to consumer extinctions can impose greater constraints on phenotypic evolution.
@@
 
-> "What escapes the eye, however, is a much more insidious kind of extinction: the extinction of ecological interactions." @Janzen1974
+<!-- > "What escapes the eye, however, is a much more insidious kind of extinction: the extinction of ecological interactions." @Janzen1974 -->
 
@@
 Black arrows denote the flow of energy in this network of trophic interactions.
-In the intact food web, we allowed the full suite of egg and larval parasitoids to impose selection.
+In the original food web, we allowed the full suite of egg and larval parasitoids to impose selection.
 To simulate consumer extinction, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
@@
 These 128 plants came from eight different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
-For intact food webs (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
+For the original food web (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
 Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
@@
 Our analysis consisted of three parts.
-First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($z_i$) of individuals \textemdash in each food-web treatment.
+First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment.
 Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients.
-Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape.
+Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we use to quantify evolutionary constraints.
 
 **Selection surfaces**: Since larval survival was our measure of absolute fitness, we used a GLMM that assumed a binomial error distribution (and logit-link function).
-To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_{z_i}$), quadratic ($\alpha_{z_i:z_i}$), and linear interactions ($\alpha_{z_i:z_j}$) between each trait.
+To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_i$), quadratic ($\alpha_{ii}$), and linear interactions ($\alpha_{ij}$) between each trait.
 We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.
@@
 For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e., $\text{ln}\{W(z)[1-W(z)]\}$) associated with a unit change in a trait with all other traits held fixed.
-Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i:z_i}$), and correlational ($\gamma_{z_i:z_j}$) selection gradients.
+Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlational ($\gamma_{ij}$) selection gradients.
 Briefly, this method calculates the average gradient of selection surfaces by multiplying the average of $W(z)[1-W(z)]$ by each regression coefficient (e.g.
-$\alpha_{z_i}$, $\alpha_{z_i:z_i}$, or $\alpha_{z_i:z_j}$).
-We then divided this average gradient by mean fitness ($\bar W$) to put it on the scale of relative fitness, and thus interpretable as a selection gradient.
+$\alpha_i$, $\alpha_{ii}$, or $\alpha_{ij}$).
+We then divided this average gradient by the mean fitness ($\bar W$) to put it on the scale of relative fitness, and thus interpretable as a selection gradient.
 We estimated selection gradients separately for each food-web treatment.
@@
 
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-By comparing the number of traits that show clear evidence of contributing to the slope (i.e., directional selection gradients where the 95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
+$$\text{Slope} = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
+where each $\beta$ corresponds to the directional selection gradient acting on each trait.
+By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e., 95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
 
@@
 
-$$\textbf{C} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
-$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+$$\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
 
+where each $\gamma$ along the diagonal corresponds to the quadratic selection gradient acting on a trait, each $\gamma$ along the off-diagonal corresponds to the correlational selection gradient acting on a particular trait combination.
 Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
-The sign of diagonal terms of the curvature matrix dictates whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+Subtracting these two matrices results in the curvature matrix of the adaptive landscape:
+
+$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+where each $\text{C}$ along the diagonal represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}$ along the off-diagonal represents the effect of selection on the additive genetic covariance between a particular trait combination.
+Therefore, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
 Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
@@
 An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates.
-A recent paper by @Hunter2008 highlight this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--> This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).
+A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--> This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).
 
@@
 We used a GLMM with the same structure as described above except that we modeled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
-We detected a positive bias in both food-web treatments (intact $\alpha_{\text{Diam}}$=
+We detected a positive bias in both food-web treatments (original $\alpha_{\text{Diam}}$=
 `r round(fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],2)` 
@@
 
-\indent We found that the extinction of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the intact food web (1 of 3)(table \ref{Table:Gradients}).
-For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the intact food web (table \ref{Table:Gradients}; fig.
+\indent We found that the extinction of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
+For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}C).
@@
 We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, there was no clear relationship in the intact food web (table \ref{Table:Gradients}).
+\ref{fig:UV_Landscape}B); however, there was no clear relationship in the original food web (table \ref{Table:Gradients}).
 This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on egg parasitoids section), and thus a less than additive effect on gall midges.
@@
 \ref{fig:UV_Landscape}A).
-Although the magnitude of selection on chamber diameter was relatively higher in the intact food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival (selection surfaces: intact $\alpha_{\text{Diam}}$=
+Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival (selection surfaces: original $\alpha_{\text{Diam}}$=
 `r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$mean,2)` 
@@
 [`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in intact food webs (intact $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web (original $\bar W$=
 `r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean,2)` 
@@
 \begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in the intact food web and with the extinction of larval parasitoids.}
+\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
 \label{Table:Gradients}
@@
 \hline
-\textbf{Selection gradient} & \textbf{Intact} & \textbf{Extinction}   \\ %& \textbf{Contrast}
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction}   \\ %& \textbf{Contrast}
 \hline
@@
 
-$\gamma_{\text{Diam,Diam}}$ &
+$\gamma_{\text{Diam:Diam}}$ &
 `r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
@@
 
-$\gamma_{\text{Clutch,Clutch}}$ & 
+$\gamma_{\text{Clutch:Clutch}}$ & 
 `r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
@@
 
-$\gamma_{\text{Pref,Pref}}$ & 
+$\gamma_{\text{Pref:Pref}}$ & 
 \textbf{
@@
 
-$\gamma_{\text{Diam,Clutch}}$ & 
+$\gamma_{\text{Diam:Clutch}}$ & 
 `r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
@@
 
-$\gamma_{\text{Diam,Pref}}$ & 
+$\gamma_{\text{Diam:Pref}}$ & 
 `r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
@@
 
-$\gamma_{\text{Clutch,Pref}}$ & 
+$\gamma_{\text{Clutch:Pref}}$ & 
 `r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
@@
 In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
-The negative relationship between oviposition preference and larval survival dampened at high densities in intact food webs, but not with the exclusion of larval parasitoids (fig.
+The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the exclusion of larval parasitoids (fig.
 \ref{fig:UV_Landscape}B).
@@
 
-```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the intact food web and with the extinction of larval parasitoids.
+```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
 Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in intact food webs (orange) and with consumer extinctions (blue).
+Bold lines represent selection experienced in the original food web (orange) and with consumer extinctions (blue).
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 
-Using our estimates of directional, quadratic, and correlation selection, we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
+Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
 In our study, this corresponds to:
 
-$$\textbf{C} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
+$$\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
 
-$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
 \bigskip
 
+where each $\text{C}$ along the diagonal represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}$ along the off-diagonal represents the effect of selection on the additive genetic covariance between a particular trait combination.
 In order to obtain a conservative estimate of the factors contributing to the curvature, we only used estimates of selection that clearly differed from zero (bold values in table \ref{Table:Gradients}), otherwise we set estimates of selection to zero (non-bold values in table \ref{Table:Gradients}) prior to our calculation.
@@
 
-$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
 `r round(complex_gammas["Diam","Diam"],2)` &  &  \\  
@@
 
-$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
 `r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
@@
 
-$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
 `r round(simple_gammas["Diam","Diam"],2)` &  &  \\  
@@
 
-$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
 `r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
@@
 Remember that we can infer the indirect effects of selection on genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-The structure of these matrices indicates that the extinction of larval parasitoids increased the number of genetic constraints on gall midges (6 of 6) relative to the intact food web (1 of 6).
-For example, directional selection resulting from the exclusion of larval parasitoids acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the intact food web.
+The structure of these matrices indicates that the extinction of larval parasitoids increased the number of genetic constraints on gall midges (6 of 6) relative to the original food web (1 of 6).
+For example, directional selection resulting from the exclusion of larval parasitoids acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the original food web.
 For genetic covariances, the combined effects of directional selection resulting from consumer extinctions favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
 \ref{fig:MV_Landscape}).
-In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the intact food web (fig.
+In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the original food web (fig.
 \ref{fig:MV_Landscape}).
 
-```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the intact food web and with the extinction of larval parasitoids.
+```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
 Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the intact food web.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the original food web.
 This indicates that consumer extinctions more strongly favored trait integration (covariance).
@@
 \hline
-\textbf{Selection gradient} & \textbf{Contrast = Intact - Extinction}  \\ 
+\textbf{Selection gradient} & \textbf{Contrast = Original - Extinction}  \\ 
 \hline
@@
 
-$\gamma_{\text{Diam,Diam}}$ &
+$\gamma_{\text{Diam:Diam}}$ &
 
@@
 
-$\gamma_{\text{Clutch,Clutch}}$ &
+$\gamma_{\text{Clutch:Clutch}}$ &
 
@@
 
-$\gamma_{\text{Pref,Pref}}$ &
+$\gamma_{\text{Pref:Pref}}$ &
 
@@
 
-$\gamma_{\text{Diam,Clutch}}$ &
+$\gamma_{\text{Diam:Clutch}}$ &
 
@@
 
-$\gamma_{\text{Diam,Pref}}$ &
+$\gamma_{\text{Diam:Pref}}$ &
 
@@
 
-$\gamma_{\text{Clutch,Pref}}$ &
+$\gamma_{\text{Clutch:Pref}}$ &
 
@@
 ```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid (intact - extinction of larval parastioids) as a function of gall midge oviposition preference.
+The bold line represents the average difference in the probability of observing the egg parasitoid (original - extinction of larval parastioids) as a function of gall midge oviposition preference.
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 large chamber diameter, small clutch size, and avoidance of conspecifics).
-In contrast, we did not observe clear evidence of selective constraints on clutch size and oviposition preference in the intact food web.
+In contrast, we did not observe clear evidence of selective constraints on clutch size and oviposition preference in the original food web.
 This suggests that there are many optimal phenotypes (adaptive peaks), or in this case, a flat adaptive landscape where there are no fitness consequences for phenotypic change in these traits.

### 2019-05-19 analyses/reproduce_analyses.Rmd
aesthetic changes. transitioning this into a document where the .html serves as supplementary material.

@@
 ---
-title: "Reproduce analyses reported in: *Phenotypic evolution is more constrained in simpler food webs*"
-author: "Matthew A. Barbour"
+title: "Consumer extinctions constrain phenotypic evolution in the resulting food web"
+subtitle: "Supplementary information"
+author: "Code author: Matthew A. Barbour"
 date: "`r Sys.Date()`"
 output: 
-  prettydoc::html_pretty:
-    theme: architect
-    highlight: github
-fontsize: 11pt
+  tufte::tufte_html:
+    toc: true
+#fontsize: 11pt
 ---
 
-## Setup
-
-Suppress messages, warnings, and errors for document aesthetics.
-
-```{r setup}
-knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE)
-```
-
-Load required libraries.
+This document presents a hybrid summary of the code used to reproduce these analyses.
+It is intended to give the reader a higher-level picture of the analyses, but does not display more minor code related to aesthetics.
+The underlying code for this document is provided in *reproduce_analyses.Rmd* and is available at https://github.com/mabarbour/complexity_selection.
+
+```{r setup, include=FALSE}
+# Suppress messages, warnings, and errors for document aesthetics.
+knitr::opts_chunk$set(message=FALSE, warning=FALSE, error=FALSE, echo=FALSE, dev="png")
+```
 
 ```{r required libraries, results='hide'}
+# Load required libraries.
 library(car)        # for homogeneity of variance test
@@
 
-Write custom functions to avoid repetitive code.
-
 ```{r custom functions}
+## Write custom functions to avoid repetitive code.
+
 # Transform logit to probability
@@
 
-Set parameters for analyses and plots.
-
-```{r set parameters}
-# Number of bootstrap replicates
+Set number of bootstrap replicates for analyses and plots.
+
+```{r set parameters, echo=TRUE}
 n_boots_analysis <- 1000
 n_boots_plots <- 100
-
+```
+
+```{r color palette}
 # Color-blind friendly palette: http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/; 
@@
 
-Read and tidy data for analyses.
-
 ```{r read and tidy data}
+## Read and tidy data for analyses.
 
@@
          unknown_mortality = ifelse(rowSums(select(., pupa:early.larval.death)) < 1, 1, 0))
-
-# all sources of mortality
-mean(full_df$gall_survival) + mean(full_df$egg.ptoid) + mean(full_df$larval.ptoid) + mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)
-
-mean(full_df$gall_survival) # 40% survival
-mean(full_df$egg.ptoid) # 26% egg parasitism
-mean(full_df$larval.ptoid) # 11% larval parasitism
-mean(full_df$early.larval.death) # 17% early larval death
-mean(full_df$unknown_mortality) # 7% unknown
 
@@
 
-## Evaluating assumption of multivariate normality
+## Multivariate normality of phenotypic traits
 
@@
 
-```{r Univariate_histograms, fig.cap="\\label{fig:Univariate_histograms}Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
+\
+
+```{r Univariate_histograms,  fig.cap="Histograms of each phenotypic trait after transformation. The red line illustrates a normal distribution."}
 mvn_univariate_hist <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), univariatePlot = "histogram")
@@
 
-```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
+\
+
+```{r Multivariate_QQ, fig.show = 'asis', fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
 mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")  
@@
 
-## Gall trait-fitness relationships: effect of food-web treatment
+## Selection surfaces on gall midges: food-web treatments
 
@@
 
-```{r Food-web model, cache=TRUE}
+```{r Food-web model, cache=TRUE, echo=TRUE}
 foodweb_model <- glmer(
@@
 
+\
+
 We used parametric bootstrapping to calculate 95% confidence intervals of trait-fitness relationships.
 
-```{r Bootstrap food-web model, cache=TRUE}
+```{r Bootstrap food-web model, cache=TRUE, echo=TRUE}
 boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
+
+\
 
@@
 
-```{r Linear food-web model, cache=TRUE}
+```{r Linear food-web model, cache=TRUE, echo=TRUE}
 linear_foodweb_model <- glmer(
@@
 
+\
+
 And refit using parametric bootstrapping.
 
-```{r Bootstrap linear food-web model, cache=TRUE}
+```{r Bootstrap linear food-web model, cache=TRUE, echo=TRUE}
 boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
 ```
+
+\
 
@@
 
-```{r Bias in food-web model, cache=TRUE}
+```{r Bias in food-web model, cache=TRUE, echo=TRUE}
 
@@
 
+\
+
 ```{r biased foodweb table, echo=FALSE}
@@
   mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-  knitr::kable(., caption = "Estimates of bias in trait-fitness relationship of chamber diameter in each food-web treatment.")
+  knitr::kable(., caption = "Estimates of bias in selection surface of chamber diameter in each food-web treatment.")
 ```
@@
 For chamber diameter, we subtracted the coefficient due to bias to better approximate the trait-fitness relationship.
-We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).
+<!--We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).-->
 
@@
 
-```{r Table of food web coefficients, echo=FALSE}
+```{r Table of food web coefficients}
 tidy_foodweb_alphas %>%
   filter(type != "Diff") %>%
-  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  select(Term = term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  mutate(Term = term, Treatment = type, Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
  knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
@@
 
-```{r Table of differences in food web coefficients, echo=FALSE}
+```{r Table of differences in food web coefficients, include=FALSE}
 tidy_foodweb_alphas %>%
   filter(type == "Diff") %>%
-  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
- knitr::kable(., caption = "Table of differences in mean fitness and trait-fitness relationships between food-web treatments.")
+  select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  mutate(Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
+ knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces between food-web treatments.")
 ```
@@
 
-## Gall trait selection gradients
-
-Using the methods proposed by [Janzen and Stern, 1998](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we estimated selection gradients from our trait-fitness relationships.
-
-```{r Food-web selection gradients}
+## Selection gradients on gall midges: food-web treatments
+
+Using the methods proposed by [Janzen and Stern, 1998](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we estimated selection gradients from our selection surfaces.
+
+```{r Food-web selection gradients, echo=TRUE}
 
@@
   transmute_all(funs(foodweb_simple_gradient))
-
+```
+
+```{r Tidy up selection gradients}
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
@@
 
-```{r Table of food web selection gradients, echo=FALSE}
+```{r Table of food web selection gradients}
 tidy_foodweb_grads %>%
   filter(type != "Diff") %>%
-  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 
-```{r Table of differences in selection gradients between food-web treatments, echo=FALSE}
+```{r Table of differences in selection gradients between food-web treatments, include=FALSE}
 tidy_foodweb_grads %>%
   filter(type == "Diff") %>%
-  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 
-```{r Curvature, echo=FALSE}
+```{r Curvature, include=FALSE}
 # Calculate curvatures for complex food web
@@
 
-```{r Table of food web curvatures, echo=FALSE}
+```{r Table of food web curvatures, include=FALSE}
 tidy_foodweb_curvs %>%
@@
 
-```{r Table of differences in curvatures between food-web treatments, echo=FALSE}
+```{r Table of differences in curvatures between food-web treatments, include=FALSE}
 tidy_foodweb_curvs %>%
@@
 
+plot_grid(y_title_foodweb_grads, plot_legend_foodweb_grads, ncol=2, rel_widths = c(0.05,1))
+
 figure_foodweb_grads <- plot_grid(y_title_foodweb_grads, plot_legend_foodweb_grads, ncol=2, rel_widths = c(0.05,1)) 
@@
 
-## Gall trait-fitness relationships: contribution of egg and larval parasitoids
+## Selection surfaces on gall midges: egg vs. larval parasitoids
 
@@
 
-```{r Egg vs. larval ptoid model, cache=TRUE}
+```{r Egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
 # excludes cases of egg-parasitism from Complex food web
@@
 
+\
+
 Parametric bootstrapping to estimate confidence intervals.
 
-```{r Bootstrap egg vs. larval ptoid model, cache=TRUE}
+```{r Bootstrap egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
 boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 
+\
+
 Fit a reduced model to reliably estimate linear trait-fitness relationships.
 
-```{r Linear egg vs. larval ptoid model, cache=TRUE}
+```{r Linear egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
 linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
@@
 
+\
+
 Parametric bootstrapping to estimate confidence intervals.
 
-```{r Bootstrap linear egg vs. larval model, cache=TRUE}
+```{r Bootstrap linear egg vs. larval model, cache=TRUE, echo=TRUE}
 boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
@@
 
-Tidy trait-fitness relationships for egg and larval parasitoids from above models.
+\
+
+Tidy selection surfaces imposed by egg and larval parasitoids from above models.
 
@@
 
-```{r Table of egg vs. larval coefficients, echo=FALSE}
+```{r Table of egg vs. larval coefficients}
 tidy_egglarval_alphas %>%
   filter(type != "Diff") %>%
-  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of gall trait-fitness relationships imposed by egg and larval parasitoids.
+  select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of gall selection surfaces imposed by egg and larval parasitoids.
 Note that type = Simple = Egg parasitoid and Complex = Larval parasitoid.")
@@
 
-```{r Table of differences in egg vs. larval coefficients, echo=FALSE}
+```{r Table of differences in egg vs. larval coefficients, include=FALSE}
 tidy_egglarval_alphas %>%
   filter(type == "Diff") %>%
-  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of differences in gall trait-fitness relationships between egg and larval parasitoids.")
@@
 
-## Selection gradients acting on gall traits due to egg and larval parasitoids
-
-```{r Egg vs. larval ptoid selection gradients}
+## Selection gradients on gall midges: egg vs. larval parasitoids
+
+```{r Egg vs. larval ptoid selection gradients, echo=TRUE}
 
@@
   transmute_all(funs(egglarval_simple_gradient))
-
+```
+
+```{r Tidy egg vs. larval ptoid selection gradients}
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
@@
 
-```{r Egg vs. larval selection gradients, echo=FALSE}
+```{r Egg vs. larval selection gradients}
 tidy_egglarval_grads %>%
   filter(type != "Diff") %>%
-  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 
-```{r Table of differences in selection gradients between egg and larval parasitoids, echo=FALSE}
+```{r Table of differences in selection gradients between egg and larval parasitoids, include=FALSE}
 tidy_egglarval_grads %>%
   filter(type == "Diff") %>%
-  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, gradient_type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 
-Create plots for each panel of Figure 2 in main text.
-
 ```{r Plot Univariate Landscapes}
+## Create plots for each panel of Figure 2 in main text.
+
 uni_breaks <- c(0.1,0.5,1.0)
@@
   mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
-         Foodweb = factor(ifelse(Foodweb == "Complex", "Intact", "Extinction"), levels = c("Intact", "Extinction"))) %>% 
+         Foodweb = factor(ifelse(Foodweb == "Complex", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
   ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
-Fit plots together to reproduce Figure 2.
-
 ```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs."}
+## Fit plots together to reproduce Figure 2.
 
@@
 
-## Replot adaptive landscapes of gall traits in terms of relative fitness
+## Replot gall midge adaptive landscapes in terms of relative fitness
 
@@
 
-Create plots for each panel.
-
 ```{r Get plots of multivariate adaptive landscape}
+## Create plots for each panel.
 
@@
 
-labels_2D <- list("Complex"="Intact", "Simple"="Extinction")
+labels_2D <- list("Complex"="Original", "Simple"="Extinction")
 labeller_2D <- function(variable, value) {
@@
 
-Fit plots together to reproduce Figure 3.
-
 ```{r Figure-Multivariate-Landscapes, fig.cap="Multivariate adaptive landscapes of gall phenotypes in complex and simple food webs.
@@
 Arrows represent the vector of directional selection gradients acting on each phenotype."}
+
+## Fit plots together to reproduce Figure 3.
 
@@
 
-## Trait-fitness relationships of the extended phenotype of the egg parasitoid *Platygaster* sp.
-
-```{r Egg vs. egg ptoid model, cache=TRUE}
+## Selection surfaces of the egg parasitoid *Platygaster* sp.
+
+```{r Egg vs. egg ptoid model, cache=TRUE, echo=TRUE}
 
@@
 
-Use parametric bootstrapping to calculating 95% confidence intervals of trait-fitness relationships.
+\
+
+Use parametric bootstrapping to calculating 95% confidence intervals of selection surfaces.
 
@@
 
-Remove all higher-order terms to quantify linear trait-fitness relationships.
+\
+
+Remove all higher-order terms to quantify linear selection surfaces.
 
@@
 
+\
+
 And refit using parametric bootstrapping.
@@
 
-Gather regression coefficients to display trait-fitness relationships.
+\
+
+Gather regression coefficients to display selection surfaces.
 
@@
 
-```{r Egg ptoid coefficients in each food-web treatment, echo=FALSE}
+```{r Egg ptoid coefficients in each food-web treatment}
 tidy_eggegg_alphas %>%
   filter(type != "Diff") %>%
-  select(term, coefficient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 
-```{r Table of differences in egg parasitoid coefficients between food-web treatments, echo=FALSE}
+```{r Table of differences in egg parasitoid coefficients between food-web treatments, include=FALSE}
 tidy_eggegg_alphas %>%
   filter(type == "Diff") %>%
-  select(term, coefficient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
 
-## Selection gradients acting on extended phenotype of the egg parasitoid
-
-```{r Egg vs. egg ptoid selection gradients}
+## Selection gradients acting on the egg parasitoid
+
+```{r Egg vs. egg ptoid selection gradients, echo=TRUE}
 
@@
   transmute_all(funs(eggegg_simple_gradient))
-
+```
+
+```{r Tidy egg vs. egg ptoid selection gradients}
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
@@
 
-```{r Egg vs. ptoid selection gradients, echo=FALSE}
+```{r Egg vs. ptoid selection gradients}
 tidy_eggegg_grads %>%
   filter(type != "Diff") %>%
-  select(term, gradient_type, type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of selection gradients acting on extended phenotype of egg parasitoids in complex and simple food webs.")
-```
-
-\
-
-```{r Table of differences in selection gradients acting on egg parasitoids between food-web treatment, echo=FALSE}
+knitr::kable(., caption = "Table of selection gradients acting on egg parasitoids in complex and simple food webs.")
+```
+
+\
+
+```{r Table of differences in selection gradients acting on egg parasitoids between food-web treatment, include=FALSE}
 tidy_eggegg_grads %>%
   filter(type == "Diff") %>%
-  select(term, gradient_type, mean, conf.low, conf.high, P_cutoff) %>%
+  select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
   mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
@@
   xlab("Gall midge preference (SDs)") + 
-  ylab(expression(paste(Delta," egg parasitoid survival (intact - extinction)"))) +
+  ylab(expression(paste(Delta," egg parasitoid survival (original - extinction)"))) +
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +

### 2019-05-19 manuscript.Rmd
replaced Complex and Simple with Original and Extinction in Fig. 1

@@
 ## Reproduce analyses ----
-knitr::knit("analyses/reproduce_analyses.Rmd")
+#knitr::knit("analyses/reproduce_analyses.Rmd") 
+rmarkdown::render("analyses/reproduce_analyses.Rmd", clean = FALSE)
 
@@
 
-<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission 
+<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission --> 
 \begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
@@
 \bigskip
--->
+<!---->
 *Manuscript elements*: table 1, table 2, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
@@
 
-*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid.
+*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid; complexity.
 
@@
 
-Global change is altering the structure of ecological communities, which may influence evolutionary constraints in a number of ways.
-For example, in a multitrophic community or food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection.
+Global change is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways.
+For example, in a <!--multitrophic community or -->food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection.
 Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities.
@@
 (Family: Torymidae)."}
-knitr::include_graphics("analyses/complex_simple_foodwebs_v2.jpeg")
+knitr::include_graphics("analyses/complex_simple_foodwebs_v3.jpeg")
 ```
@@
 For the original food web (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
-Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season.
+Marking galls with flagging tape ensured that all galls had similar phenology when we collected galls later in the season.
 To simulate consumer extinctions, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
@@
 We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-We removed other sources of mortality, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
+We did not include other sources of mortality, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
 <!--Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
@@
 To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
-To ensure that our estimates of selection were comparable across traits and with other studies, we scaled all phenotypic traits (mean=0 and SD=1) prior to our analyses (detailed below).
+We then scaled all phenotypic traits (mean=0 and SD=1) prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
 
@@
 Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients.
-Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we use to quantify evolutionary constraints.
+Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we used to measure evolutionary constraints.
 
@@
 
-**Selection gradients**: Selection gradients cannot be estimated directly from GLMMs on selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e., $\text{ln}\{W(z)[1-W(z)]\}$) associated with a unit change in a trait with all other traits held fixed.
+**Selection gradients**: Selection gradients cannot be estimated directly from GLMMs of selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
+For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e., $\text{ln}\{W(z)/[1-W(z)]\}$) associated with 1 SD change in a trait with all other traits held fixed at their mean.
 Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlational ($\gamma_{ij}$) selection gradients.
@@
 
-**Evolutionary constraints**: We quantified the effects of food-web structure on evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
+**Evolutionary constraints**: We measured evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
 The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
 
-$$\text{Slope} = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-where each $\beta$ corresponds to the directional selection gradient acting on each trait.
+$$\textbf{Slope} = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
+where each $\beta_i$ corresponds to the directional selection gradient acting on each trait.
 By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e., 95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
@@
 
-where each $\gamma$ along the diagonal corresponds to the quadratic selection gradient acting on a trait, each $\gamma$ along the off-diagonal corresponds to the correlational selection gradient acting on a particular trait combination.
+where each $\gamma_{ii}$ (diagonal) corresponds to the quadratic selection gradient acting on a trait, and each $\gamma_{ij}$ (off-diagonal) corresponds to the correlational selection gradient acting on a particular trait combination.
 Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
@@
 $$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
-where each $\text{C}$ along the diagonal represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}$ along the off-diagonal represents the effect of selection on the additive genetic covariance between a particular trait combination.
-Therefore, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
+In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
 Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
 Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature ($\gamma - \beta \beta^\text{T}$) in each food-web treatment.
+For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature matrix in each food-web treatment.
 This provides a conservative estimate of the factors contributing to the curvature of the adaptive landscape.
@@
 
-where each $\text{C}$ along the diagonal represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}$ along the off-diagonal represents the effect of selection on the additive genetic covariance between a particular trait combination.
+where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
 In order to obtain a conservative estimate of the factors contributing to the curvature, we only used estimates of selection that clearly differed from zero (bold values in table \ref{Table:Gradients}), otherwise we set estimates of selection to zero (non-bold values in table \ref{Table:Gradients}) prior to our calculation.
@@
 This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
-A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @StartInPress].
+A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
 If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from consumer extinctions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
@@
 Second, our metrics of evolutionary constraints do not account for variation in the magnitude of selection pressures.
-While quantitative metrics are possible and more ideal [@Hansen2008], we felt they were not appropriate to apply here as our experimental removal of larval parasitoids results in a transient dynamic in the strength (but not direction) of selection.
+While quantitative metrics are possible [@Hansen2008], we felt they were not appropriate to apply here as our experimental removal of larval parasitoids results in a transient dynamic in the strength (but not direction) of selection.
 Such transient dynamics may be common in short-term experimental studies of natural selection, but they can be detected by using natural history information and dissecting the sources of selection (e.g.

### 2019-05-19 manuscript/manuscript.Rmd
organized into the folder 'manuscript'

--- 2019-05-19 manuscript.Rmd
@@
 ## Reproduce analyses ----
-#knitr::knit("analyses/reproduce_analyses.Rmd") 
-rmarkdown::render("analyses/reproduce_analyses.Rmd", clean = FALSE)
+#knitr::knit("../analysesreproduce_analyses.Rmd") 
+rmarkdown::render("../analyses/reproduce_analyses.Rmd", clean = FALSE)
 
@@
 (Family: Torymidae)."}
-knitr::include_graphics("analyses/complex_simple_foodwebs_v3.jpeg")
+knitr::include_graphics("../analyses/complex_simple_foodwebs_v3.jpeg")
 ```
@@
 We detected a positive bias in both food-web treatments (original $\alpha_{\text{Diam}}$=
-`r round(fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],2)` 
-[`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.low,2)`,
-`r round(filter(biased_foodweb_confint, term=="FoodwebComplex:sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
-`r round(fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"],2)` 
-[`r round(filter(biased_foodweb_confint, term=="FoodwebSimple:sc.Diam")$conf.low,2)`,
-`r round(filter(biased_foodweb_confint, term=="FoodwebSimple:sc.Diam")$conf.high,2)`]), indicating that unadjusted relationships would overestimate the strength of selection on chamber diameter.
+`r round(fixef(biased_foodweb_model)["FoodwebOriginal:sc.Diam"],2)` 
+[`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.low,2)`,
+`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
+`r round(fixef(biased_foodweb_model)["FoodwebExtinction:sc.Diam"],2)` 
+[`r round(filter(biased_foodweb_confint, term=="FoodwebExtinction:sc.Diam")$conf.low,2)`,
+`r round(filter(biased_foodweb_confint, term=="FoodwebExtinction:sc.Diam")$conf.high,2)`]), indicating that unadjusted relationships would overestimate the strength of selection on chamber diameter.
 To account for this bias, we substracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's selection surface and directional selection gradient.
@@
 Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`]).
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`]).
 We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig.
@@
 Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival (selection surfaces: original $\alpha_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web (original $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="(Intercept)")$conf.high,2)`]; extinction $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="(Intercept)")$conf.high,2)`]).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web (original $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$conf.high,2)`]; extinction $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`]).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}).
@@
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] }& 
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$conf.high,2)`] }\\%& 
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] }\\%& 
 %\textbf{
@@
 $\beta_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }\\%& 
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] }\\%& 
 %\textbf{
@@
 $\beta_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }\\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] }\\%&
 
@@
 $\gamma_{\text{Diam:Diam}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] \\%&
 
@@
 $\gamma_{\text{Clutch:Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\%&
 
@@
 \textbf{
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
 
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\%& 
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\%& 
 %\textbf{
@@
 $\gamma_{\text{Diam:Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\%&
 
@@
 $\gamma_{\text{Diam:Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\%&
 
@@
 $\gamma_{\text{Clutch:Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\%&
 
@@
 This dampened relationship was partly due to a trend for nonlinear selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
+[`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
 
@@
 Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
-knitr::include_graphics("analyses/UV_landscapes.pdf")
+knitr::include_graphics("../analyses/UV_landscapes.pdf")
 ```
@@
 $$\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
-`r round(complex_gammas["Diam","Diam"],2)` &  &  \\  
-`r round(complex_gammas["Clutch","Diam"],2)` & `r round(complex_gammas["Clutch","Clutch"],2)` &  \\  
-`r round(complex_gammas["Pref","Diam"],2)` & `r round(complex_gammas["Pref","Clutch"],2)` & `r round(complex_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
-`r round(complex_betas["Diam",],2)`\cdot`r round(complex_betas["Diam",],2)` &  &  \\  
-`r round(complex_betas["Clutch",],2)`\cdot`r round(complex_betas["Diam",],2)` & `r round(complex_betas["Clutch",],2)`\cdot`r round(complex_betas["Clutch",],2)` &  \\  
-`r round(complex_betas["Pref",],2)`\cdot`r round(complex_betas["Diam",],2)` & `r round(complex_betas["Pref",],2)`\cdot`r round(complex_betas["Clutch",],2)` & `r round(complex_betas["Pref",],2)`\cdot`r round(complex_betas["Pref",],2)` \end{pmatrix}$$
+`r round(original_gammas["Diam","Diam"],2)` &  &  \\  
+`r round(original_gammas["Clutch","Diam"],2)` & `r round(original_gammas["Clutch","Clutch"],2)` &  \\  
+`r round(original_gammas["Pref","Diam"],2)` & `r round(original_gammas["Pref","Clutch"],2)` & `r round(original_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
+`r round(original_betas["Diam",],2)`\cdot`r round(original_betas["Diam",],2)` &  &  \\  
+`r round(original_betas["Clutch",],2)`\cdot`r round(original_betas["Diam",],2)` & `r round(original_betas["Clutch",],2)`\cdot`r round(original_betas["Clutch",],2)` &  \\  
+`r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Diam",],2)` & `r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Clutch",],2)` & `r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Pref",],2)` \end{pmatrix}$$
 
 $$\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
-`r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(complex_curvature["Clutch","Diam"],2)` & `r round(complex_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+`r round(original_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(original_curvature["Clutch","Diam"],2)` & `r round(original_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(original_curvature["Pref","Diam"],2)` & `r round(original_curvature["Pref","Clutch"],2)` & `r round(original_curvature["Pref","Pref"],2)` \end{pmatrix}$$
 
 $$\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
-`r round(simple_gammas["Diam","Diam"],2)` &  &  \\  
-`r round(simple_gammas["Clutch","Diam"],2)` & `r round(simple_gammas["Clutch","Clutch"],2)` &  \\  
-`r round(simple_gammas["Pref","Diam"],2)` & `r round(simple_gammas["Pref","Clutch"],2)` & `r round(simple_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
-`r round(simple_betas["Diam",],2)`\cdot`r round(simple_betas["Diam",],2)` &  &  \\  
-`r round(simple_betas["Clutch",],2)`\cdot`r round(simple_betas["Diam",],2)` & `r round(simple_betas["Clutch",],2)`\cdot`r round(simple_betas["Clutch",],2)` &  \\  
-`r round(simple_betas["Pref",],2)`\cdot`r round(simple_betas["Diam",],2)` & `r round(simple_betas["Pref",],2)`\cdot`r round(simple_betas["Clutch",],2)` & `r round(simple_betas["Pref",],2)`\cdot`r round(simple_betas["Pref",],2)` \end{pmatrix}$$
+`r round(extinction_gammas["Diam","Diam"],2)` &  &  \\  
+`r round(extinction_gammas["Clutch","Diam"],2)` & `r round(extinction_gammas["Clutch","Clutch"],2)` &  \\  
+`r round(extinction_gammas["Pref","Diam"],2)` & `r round(extinction_gammas["Pref","Clutch"],2)` & `r round(extinction_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
+`r round(extinction_betas["Diam",],2)`\cdot`r round(extinction_betas["Diam",],2)` &  &  \\  
+`r round(extinction_betas["Clutch",],2)`\cdot`r round(extinction_betas["Diam",],2)` & `r round(extinction_betas["Clutch",],2)`\cdot`r round(extinction_betas["Clutch",],2)` &  \\  
+`r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Diam",],2)` & `r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Clutch",],2)` & `r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Pref",],2)` \end{pmatrix}$$
 
 $$\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
-`r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(simple_curvature["Clutch","Diam"],2)` & `r round(simple_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+`r round(extinction_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(extinction_curvature["Clutch","Diam"],2)` & `r round(extinction_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(extinction_curvature["Pref","Diam"],2)` & `r round(extinction_curvature["Pref","Clutch"],2)` & `r round(extinction_curvature["Pref","Pref"],2)` \end{pmatrix}$$
 
@@
 Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
-knitr::include_graphics("analyses/MV_landscapes.pdf")
+knitr::include_graphics("../analyses/MV_landscapes.pdf")
 ```
@@
 The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on egg parasitoids."}
-knitr::include_graphics("analyses/selection_on_Platygaster.pdf")
+knitr::include_graphics("../analyses/selection_on_Platygaster.pdf")
 ```
@@
 \hline
-\textbf{Coefficient} & \textbf{Complex} & \textbf{Simple} & \textbf{Contrast}  \\ 
+\textbf{Coefficient} & \textbf{Original} & \textbf{Extinction} & \textbf{Contrast}  \\ 
 \hline
@@
 \textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam")$conf.high,2)`] }& 
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.high,2)`] }& 
 \textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam")$conf.high,2)`] }&
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`] }&
 
@@
 $\alpha_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch")$conf.high,2)`] & 
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
 \textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch")$conf.high,2)`] }& 
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] }& 
 \textbf{
@@
 $\alpha_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
 \textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.sqrt.Pref")$conf.high,2)`] }&
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] }&
 
@@
 $\alpha_{\text{Diam,Diam}}$ &
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.Diam^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.Diam^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
 
@@
 $\alpha_{\text{Clutch,Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
 
@@
 \textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
 
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] &
 
@@
 $\alpha_{\text{Diam,Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
 
@@
 $\alpha_{\text{Diam,Pref}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
 
@@
 $\alpha_{\text{Clutch,Pref}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Complex", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
 
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Simple", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
 

### 2019-05-19 manuscript/manuscript.tex
changed from log1p to sqrt transformation of female preference
organized into the folder 'manuscript'

--- 2018-10-15 manuscript/manuscript.tex
@@
-\documentclass[11pt]{article}
-\usepackage[sc]{mathpazo} %Like Palatino with extensive math support
+\documentclass[11pt,]{article}
+\usepackage[]{mathpazo}
+\usepackage{amssymb,amsmath}
+\usepackage{ifxetex,ifluatex}
+\usepackage{fixltx2e} % provides \textsubscript
+\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+  \usepackage[T1]{fontenc}
+  \usepackage[utf8]{inputenc}
+\else % if luatex or xelatex
+  \ifxetex
+    \usepackage{mathspec}
+  \else
+    \usepackage{fontspec}
+  \fi
+  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
+\fi
+% use upquote if available, for straight quotes in verbatim environments
+\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
+% use microtype if available
+\IfFileExists{microtype.sty}{%
+\usepackage{microtype}
+\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
+}{}
+\usepackage[margin=1in]{geometry}
+\usepackage{hyperref}
+\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
+\hypersetup{unicode=true,
+            colorlinks=true,
+            linkcolor=black,
+            citecolor=black,
+            urlcolor=black,
+            breaklinks=true}
+\urlstyle{same}  % don't use monospace font for urls
+\usepackage{natbib}
+\bibliographystyle{amnat}
+\usepackage{graphicx,grffile}
+\makeatletter
+\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
+\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
+\makeatother
+% Scale images if necessary, so that they will not overflow the page
+% margins by default, and it is still possible to overwrite the defaults
+% using explicit options in \includegraphics[width, height, ...]{}
+\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
+\IfFileExists{parskip.sty}{%
+\usepackage{parskip}
+}{% else
+\setlength{\parindent}{0pt}
+\setlength{\parskip}{6pt plus 2pt minus 1pt}
+}
+\setlength{\emergencystretch}{3em}  % prevent overfull lines
+\providecommand{\tightlist}{%
+  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
+\setcounter{secnumdepth}{0}
+% Redefines (sub)paragraphs to behave more like sections
+\ifx\paragraph\undefined\else
+\let\oldparagraph\paragraph
+\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
+\fi
+\ifx\subparagraph\undefined\else
+\let\oldsubparagraph\subparagraph
+\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
+\fi
+
+%%% Use protect on footnotes to avoid problems with footnotes in titles
+\let\rmarkdownfootnote\footnote%
+\def\footnote{\protect\rmarkdownfootnote}
+
+%%% Change title format to be more compact
+\usepackage{titling}
+
+% Create subtitle command for use in maketitle
+\providecommand{\subtitle}[1]{
+  \posttitle{
+    \begin{center}\large#1\end{center}
+    }
+}
+
+\setlength{\droptitle}{-2em}
+
+  \title{}
+    \pretitle{\vspace{\droptitle}}
+  \posttitle{}
+    \author{}
+    \preauthor{}\postauthor{}
+    \date{}
+    \predate{}\postdate{}
+
+%%% Modified from Latex Template for Am. Nat., many other details aren't necessary because they are specified in YAML header of Rmarkdown document.
 \usepackage{fullpage}
-\usepackage[authoryear,sectionbib,sort]{natbib}
 \linespread{1.7}
-\usepackage[utf8]{inputenc}
 \usepackage{lineno}
-\usepackage{titlesec}
-\titleformat{\section}[block]{\Large\bfseries\filcenter}{\thesection}{1em}{}
-\titleformat{\subsection}[block]{\Large\itshape\filcenter}{\thesubsection}{1em}{}
-\titleformat{\subsubsection}[block]{\large\itshape}{\thesubsubsection}{1em}{}
-\titleformat{\paragraph}[runin]{\itshape}{\theparagraph}{1em}{}[. ]\renewcommand{\refname}{Literature Cited}
 
-% Added packages
-\usepackage{amsmath} % for matrices
-\usepackage{graphicx} % for organizing figures
-\usepackage{lmodern} % for tilde
-\usepackage[T1]{fontenc} % for tilde
-
-%%%%%%%%%%%%%%%%%%%%%
-% Line numbering
-%%%%%%%%%%%%%%%%%%%%%
-%\usepackage{lineno}
-% Please use line numbering with your initial submission and
-% subsequent revisions. After acceptance, please turn line numbering
-% off by adding percent signs to the lines %\usepackage{lineno} and
-% to %\linenumbers{} and %\modulolinenumbers[3] below.
-
-\title{TBD}
-% 1. Populations experience fewer selective constraints in complex food webs
-% 2. Complex food webs impose fewer selective constraints on linked populations
-% 3. Food-web complexity reduces selective constraints on an insect herbivore
-% 4. Phenotypic evolution is less constrained in complex food webs
-
-% This version of the LaTeX template was last updated on
-% January 11, 2018.
-
-%%%%%%%%%%%%%%%%%%%%%
-% Authorship
-%%%%%%%%%%%%%%%%%%%%%
-% Please remove authorship information while your paper is under review,
-% unless you wish to waive your anonymity under double-blind review. You
-% will need to add this information back in to your final files after
-% acceptance.
-
-\author{Matthew A. Barbour$^{1,2,\ast}$ \\ 
-Christopher J. Greyson-Gaito$^{1,3}$ \\ 
-Arezoo Sootodeh$^{3}$ \\
-Brendan Locke$^{4} \\
-Jordi Bascompte$^{2}}
-
-\date{}
+% code below is important for holding figure positions in main text. Make sure to set fig.pos="H" in code chunk for figure.
+\usepackage{float}
+\let\origfigure\figure
+\let\endorigfigure\endfigure
+\renewenvironment{figure}[1][2] {
+    \expandafter\origfigure\expandafter[H]
+} {
+    \endorigfigure
+}
 
@@
 
-\maketitle
+\vspace*{0.1cm}
 
-\noindent{} 1. University of British Columbia, Department of Zoology, Vancouver, British Columbia V6T 1Z4, Canada;
-
-\noindent{} 2. University of Zurich, Department of Evolutionary Biology and Environmental Studies, Winterthurerstrasse 190, 8057 Zurich, Switzerland;
-
-\noindent{} 3. University of Guelph, Department of Integrative Biology, Guelph, Ontario N1G 2W1, Canada;
-
-\noindent{} 3. Humboldt State University, Department of Biological Sciences, Arcata, California 95521, USA.
-
-\noindent{} $\ast$ Corresponding author; e-mail: matthew.barbour@ieu.uzh.ch.
+\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in the resulting food web \end{center}
 
@@
 
-\textit{Manuscript elements}: Figure~1, figure~2, figure~3. All figures should be printed in color.
+\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
 
@@
 
-\textit{Keywords}: Adaptive landscape, host-parasitoid, natural selection, G-matrix.
+\noindent 1. University of Zurich, Department of Evolutionary Biology
+and Environmental Studies, Zurich, 8057 ZH, Switzerland;
+
+\noindent 2. University of British Columbia, Department of Zoology,
+Vancouver, BC V6T 1Z4, Canada;
+
+\noindent 3. University of Guelph, Department of Integrative Biology,
+Guelph, ON N1G 2W1, Canada;
+
+\noindent 4. Humboldt State University, Department of Biological
+Sciences, Arcata, CA 95521, USA.
+
+\(^\ast\) Corresponding author; e-mail:
+\href{mailto:matthew.barbour@ieu.uzh.ch}{\nolinkurl{matthew.barbour@ieu.uzh.ch}}
+
+\bigskip
+<!----> \emph{Manuscript elements}: table 1, table 2, figure 1, figure
+2, figure 3, figure 4. All figures should be printed in color.
 
@@
 
-\textit{Manuscript type}: Article. %Or e-article, note, e-note, natural history miscellany, e-natural history miscellany, comment, reply, invited symposium, or countdown to 150.
+\emph{Keywords}: adaptive landscape, ecological networks,
+eco-evolutionary dynamics, natural selection, host-parasitoid;
+complexity.
 
@@
 
-\noindent{\footnotesize Prepared using the suggested \LaTeX{} template for \textit{Am.\ Nat.}}
+\emph{Number of words}: 3109
 
-%\linenumbers{}
-%\modulolinenumbers[3]
+\bigskip
 
-\newpage{}
+\emph{Manuscript type}: Article.
 
-\section*{Abstract}
+\bigskip
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Sed non risus. Suspendisse lectus tortor, dignissim sit amet, adipiscing nec, ultricies sed, dolor. Cras elementum ultrices diam.
+\footnotesize Prepared using an \emph{Am. Nat.} inspired \LaTeX{}
+template for Rmarkdown. \normalsize
 
-\newpage{}
+\linenumbers{} \modulolinenumbers[3]
 
-\section*{Introduction}
+\newpage
 
-% The journal does not have numbered sections in the main portion of
-% articles. Please refrain from using section references (à la
-% section~\ref{section:CountingOwlEggs}), and refer to sections by name
-% (e.g. section ``Counting Owl Eggs'').
+\section{Abstract}\label{abstract}
 
-% I. Adaptive landscape is a powerful framework for understanding the evolution of biological diversity (or phenotypic evolution).
+Global change is altering the structure of ecological networks; however,
+we are currently in a poor position to predict how these altered
+communities will affect the evolutionary potential of remaining
+populations. Theory on adaptive landscapes provides a framework for
+predicting how selection constrains phenotypic evolution, but often
+treats the community context of evolving populations as a ``black box''.
+Here, we integrate ecological networks and adaptive landscapes to
+examine how changes in food-web structure shape evolutionary
+constraints. We conducted a field experiment that simulated the
+extinction of a guild of larval parasitoids that were able to impose
+selection on an insect herbivore. We then measured herbivore survival as
+a function of three key phenotypic traits. We found that the number of
+traits under selection increased with the extinction of larval
+parasitoids. In contrast, the adaptive landscape was more neutral in the
+original food web because different parasitoid guilds impose different
+selection pressures, minimizing relative fitness differences among
+phenotypes. Our results suggest that the loss of trophic interactions
+due to consumer extinctions can impose greater constraints on phenotypic
+evolution. This indicates that the simplification of ecological
+communities may constrain the adaptive potential of remaining
+populations to future environmental change.
 
-The adaptive landscape provides a powerful framework for understanding and predicting the evolution of biological diversity \textemdash from genes, to phenotypes, to species (Wright and Simpson).
-More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection (Lande 1979, Arnold papers).
-In particular, the shape of the adaptive landscape represents the presence and strength of different selection pressures imposed by the environment (Arnold's work).
-Species interactions often play a key role in defining the selective environment, as evidenced by the influence of resource competition (Schluter 2000), mutualisms (Jordano 1987), and predation (Abrams 2000) on the evolution of biological diversity.
-Although there is clear evidence that pairwise interactions shape the adaptive landscape, we also know that most species interact with multiple species in an ecological community.
-Understanding how the adaptive landscape is shaped by community context represents a major challenge for both empiricists and theoreticians given the diversity of selection pressures that a population is likely to experience in a natural ecological community.
+\newpage
 
-% II. Species-interaction networks provide an explicit representation of the community context that populations are embedded within.
+\section{Introduction}\label{introduction}
 
-Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the community context.
-These networks describe the interdependency of species within an ecological community, providing an effective framework for predicting how changes in the density of directly and indirectly connected species will impact other species, and in turn, community dynamics.
-Despite the importance of species-interaction networks for predicting ecological dynamics, these networks often lack quantitative information on how species interactions influence natural selection.
-Consequently, it is unclear how species-interaction networks shape the adaptive landscape, creating a major hurdle in our current ability to predict how changes in community context will affect phenotypic evolution.
+The adaptive landscape provides a powerful framework for understanding
+how natural selection has shaped the evolution of biodiversity ---from
+genes to phenotypes to species
+\citep{Wright1931, Simpson1944, Arnold2001}. More than a metaphor, the
+adaptive landscape links quantitative genetic and phenotypic variation
+to evolution by natural selection
+\citep{Lande1979, Arnold1984applications, Arnold1984theory}. Ecological
+interactions often play a key role in shaping adaptive landscapes, as
+evidenced by the role of antagonistic \citep{Schluter2000, Abrams2000}
+and mutualistic \citep{Bronstein2006} interactions in driving
+evolutionary change. Although there is clear evidence that pairwise
+interactions can shape the adaptive landscape, we still have a poor
+understanding of how the adaptive landscape is shaped by the community
+context \citep{McPeek2017, terHorst2018}. Resolution on how the
+community context shapes phenotypic evolution is urgently needed though,
+given the rapid impacts of climate change on ecological communities
+\citep{Scheffers2016}.
 
-% III. Here we combine these frameworks to predict how changes in community context will affect phenotypic evolution. (empirically?)
+Ecological networks, such as food webs describing who-eats-whom in
+ecological communities, provide an explicit representation of the
+community context \citep{Bascompte2014, McCann2012}. Here, we integrate
+ecological networks and adaptive landscapes to understand how the
+community context constrains evolutionary change \citep{Arnold1992}.
+Different aspects of evolutionary constraints can be inferred by
+quantifying the slope and curvature of the adaptive landscape. For
+example, the slope is determined by directional selection gradients
+acting on each phenotypic trait and influences the trajectory of
+evolutionary change \citep{Lande1979, Arnold1992}. Selective constraints
+on evolution increase with the number of traits under directional
+selection, as this diminishes the number of optimal solutions
+\citep{Arnold2003}. The curvature of the adaptive landscape can also
+constrain evolution through its indirect effect on genetic constraints
+\citep{Arnold1992, Hansen2008}. Genetic constraints are largely governed
+by a population's \textbf{G}-matrix ---the additive genetic variances
+and covariances between traits \citep{Hansen2008}. In general, genetic
+constraints will increase with the number of traits under directional or
+stabilizing selection, as this will decrease the additive genetic
+variance in those traits \citep{Hansen2008}. Genetic constraints may
+also increase with the number of trait combinations under correlational
+selection, as this type of selection decreases the evolutionary
+independence of traits \citep{Hansen2008}. If we want to predict how the
+community context constrains evolutionary change, we must understand how
+ecological networks shape the adaptive landscape.
 
-Here, we integrate species-interaction networks and the adaptive landscape to predict how changes in network structure will affect phenotypic evolution.
-We did this by conducting a field experiment to characterize the effect of network structure on the adaptive landscape of a constituent species.
-Specifically, we conducted a field experiment that manipulated the diversity of insect parasitoids that were able to impose selection on an abundant insect herbivore (\textit{Iteomyia salicisverruca})(Fig.
-1).
-The larva of this herbivore species induce tooth-shaped galls when they feed on the developing leaves of willow trees (\textit{Salix} sp., @Russo2006).
-These galls provide protection from generalist predators (e.g.
-ants, spiders), thus the network of interacting parasitoids provides a realistic representation of the biotic environment this insect herbivore is experiencing.
-Therefore, our manipulation of parasitoid diversity alters the diversity of interactions, or food-web complexity, that this insect herbivore experiences.
+Global change is altering the structure of ecological networks, which
+may influence evolutionary constraints in a number of ways. For example,
+in a food web, if different consumers impose directional selection on
+different traits of a shared resource, then a more diverse consumer
+community may constrain evolution by increasing the number of traits
+under selection. Alternatively, if consumers impose selection on
+different values of a trait, then their selective effects would cancel
+each other out in more diverse communities. To examine these different
+possibilities, we conducted a field experiment that simulated the
+extinction of a consumer guild associated with an abundant insect
+herbivore (\emph{Iteomyia salicisverruca}, Family Cecidomyiidae; fig.
+\ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped
+galls when they feed on the developing leaves of willow trees
+\citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect larva from
+attack by generalist predators (e.g.~ants, spiders), but they suffer
+high mortality from egg and larval parasitoids \citep{Barbour2016}. We
+manipulated food-web structure by either excluding or allowing the guild
+of larval parasitoids to impose selection on gall midge and egg
+parasitoid traits (fig. \ref{fig:Conceptual}). We then applied modern
+statistical methods to quantify how changes in food-web structure
+altered the slope and curvature of the adaptive landscape of the gall
+midge and egg parasitoid. Taken together, our study gives insight to how
+local extinctions may constrain the evolution of interacting
+populations.
 
-% IV. Lay out predictions for how changes in network structure influence the adaptive landscape.
-
-Changes in food-web complexity could influence a resource population's adaptive landscape in at least two ways.
-First, if a more diverse community of consumers is more effective at suppressing resource densities (@Ives2005), then this will result in lower mean fitness of the resource population.
-A reduction in mean fitness, all else equal, will intensify natural selection (@Hunter2018).
-On the other hand, if consumers impose different selection pressures on resource traits, then more diverse communities could dampen the strength of selection acting on a given trait.
-This is because a greater diversity in selection pressures is equivalent to greater uncertainty in the selective environment.
-Thus, a more diverse consumer community may relax the net selection pressures acting on resource traits.
-Here, we evaluate these hypothesized relationships through an experimental test of how changes in food-web complexity alters the adaptive landscape of a resource population.
-
-% Confronting this challenge is important now more than ever before, given the rapid changes we are witnessing in the diversity and composition of local communities (cite global change papers).
-
-% Natural selection is inherently an ecological process, describing how the environment changes phenotypic distributions of a population due to differences in fitness. %within a generation
-
-%At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
-However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
-Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
-Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
-
-% For example, the Lande equation ($\delta z=G\beta$) predicts the evolutionary trajectory of phenotypes ($\delta z$) as a function of directional selection gradients ($\beta$) and the additive genetic variance and covariance between these phenotypes (G-matrix, $G$).
-Similarly, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$).
-also shapes the G-matrix, which ultimately determines the ...
-.
-Importantly, the components of this theoretical framework can be est quantities that predict evolutionary change can all be estimated empirically
-
-% People have often studied pairwise species interactions.
-There is also tantalizing evidence that community context can alter natural selection on phenotypic distributions, but predicting these changes remains difficult.
-This is because work hasn't explicitly embodied the environment (which a network can).
-
-% Key part here is environment, which a food web or species-interaction network can provide an explicit representation of (i.e. community context).
-
-% Biological diversity \textemdash from genes, to phenotypes, to species \textemdash has and continues to be shaped by the interplay between ecological and evolutionary processes.
-Much of this biological diversity has been molded by natural selection arising from species interactions, such as resource competition (Schluter 2000), mutualisms (Jordano 1987), and predation (Abrams 2000).
-While there is clear evidence that pairwise interactions can drive evolution, we also know that most species interact with multiple species in an ecological community.
-Understanding and predicting how evolutionary dynamics unfold in a community context represents a major challenge both empirically and theoretically, given the diversity of selection pressures that a population is likely to experience in an ecological community.
-Answering this question also has important applications, especially given the rapid changes we are witnessing in the diversity and composition of local communities (cite global change papers).
-
-% is a key challenge and predicting how changes in ecological communities is challenging and eminently theoretical (@McPeek2017, @De_Mazancourt2008, @Guimaraes2017, @Nuismer2013).
-
-%<!-- Do I need to give more credit here to work by @TerHorst2018 and others?).
-I think it would be useful to show that there is some field and lab experiments demonstrating that community context can alter evolutionary trajectories -->
-%<!-- Given the rapid loss of species diversity we are experiencing throughout the world (cite), we are in urgent need of work that makes and tests predictions for how the loss of species will affect the evolutionary process in natural communities.
-
-%<!-- Theoretical models have begun to examine how the network structure of species interactions drives evolutionary change (Nuismer paper; Guimeras paper; Ecology Letters paper from a spanish guy...; @McPeek2017); however, we are currently lacking experimental tests of how changes in network structure will alter the dynamics of natural selection in the field.
--->
-
-% The fitness landscape provides a unifying framework for linking the ecology and evolution of populations (Lande 2007; McPeek 2017).
-The average fitness of a population is a common currency in ecology and evolution, but usually goes by different names in each field.
-Ecologists refer to it as per-capita population growth rate ($dN/Ndt$), whereas evolutionary biologists call it the natural log of population mean fitness ($ln(\bar W_N)$).
-In addition to having different names, ecologists and evolutionary biologists have typically focused on different processes that shape the fitness landscape.
-For example, population ecologists have long studied the effect of a population's density on its per-capita growth rate (i.e.
-density-dependence, CITE Foundational and current work).
-In contrast, evolutionary biologists have focused on how the mean trait value of a population influences its average fitness, as this describes the direction and magnitude of natural selection (CITE foundational and current work).
-Therefore, the fitness landscape describes the joint ecological and evolutionary dynamics of a population in a given environment.
-
-% Community ecologists have extended the ecological side of the fitness landscape by incorporating network theory.
-Species-interaction networks, such as a food web describing who eats whom, provide an explicit representation of the biotic environment as they describe the interdependency of populations within an ecological community.
-This has provided an effective framework for predicting how changes in the biotic environment (e.g.
-density of directly and indirectly connected species) will impact population dynamics within species-rich communities.
-At the same time, evolutionary biologists have long recognized that changes in the biotic environment can alter the dynamics of natural selection.
-However, the biotic environment in which populations are evolving often remains a bit of a "black box" that's labelled by a general ecological process such as competition, predation, or mutualism.
-Because of this, it remains difficult to predict how changes in the biotic environment will affect the direction and magnitude of natural selection.
-Such predictions are urgently needed given the rapid changes in the biotic environment that most populations are currently experiencing throughout the world.
-
-\section*{Methods}
-
-\subsection*{Study Site}
-
-We conducted our study within a four-year old common garden of coastal willow (\textit{Salix hookeriana}) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40\textdegree 40'53"N, 124\textdegree 12'4"W) near Loleta, California, USA.
-This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-Stem cuttings of each genotype (25 replicates per genotypes) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows in our garden begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 5 - 9m in height.
-Further details on the genotyping and planting of the common garden are available in @Barbour2015.
-
-\subsection*{Food-web Manipulation}
-
-We setup our food-web manipulation across 128 plants soon after galls began developing on *S. hookeriana* in early June of 2013. 
-These 128 plants came from eight different plant genotypes, spanning the range of trait variation observed in this willow population (@Barbour2015). 
-On treatment plants (8 replicates per genotype), we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larva development (hereafter larval parasitoids).
-This treatment did not exclude the egg parasitoid *Platygaster* sp. which attacks prior to gall initiation (note that in Cecidomyiid midges, larva initiate gall development CITE). 
-On control plants (8 replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larva), allowing the full suite of parasitoids to attack \textit{Iteomyia}. 
-Marking galls with flagging tape ensured that we compared control and treatment galls with similar phenology when we collected galls later in the season. 
-Our food-web manipulation altered the average number of trophic interactions that \textit{Iteomyia} was exposed to from BLANK on control plants to BLANK on treatment plants. 
-Thus, we refer to galls on control plants as being exposed to a 'complex' food web, whereas galls on treatment plants were exposed to a 'simple' food web.
-In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature. 
-We then opened galls under a dissecting scope and determined whether larva survived to pupation (our measure of fitness) or were parasitized.
-Since we were interested in selection imposed by interactions with parasitoids, we restricted our data to larva that either survived to pupation, was parasitized by an egg parasitoid (\textit{Platygaster} sp.), or was parasitized by a larval parasitoid.
-For the food-web treatment that excluded parasitoids, we further restricted our data by removing any instances of parasitism by a larval parasitoid.
-This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
-Together, we had survival estimates for 1,306 larva from 607 galls, 111 plants, and 8 plant genotypes.
-
-\subsection*{Measuring Gall Traits}
-
-We collected data on three different traits that we anticipated would experience selection based on our previous work (@Barbour2016) and others work with Cecidomyiid midges (@Weis1983, @Heath2018) (\citealt{Heath2018}).
-First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth). 
-Our previous work has shown that a larger gall diameter provides a refuge for larva from parasitoid attack (@Barbour2016).
-<!-- Consider whether it is important to make the distinction that diameter was measured at the multi-chambered gall level in previous work -->
-Second, we measured the clutch size of adult female midges by counting the number of chambers in each gall (@Weis1983). 
-All larva collected from the same multi-chambered gall were scored with the same clutch size. 
-Third, we measured female preference for oviposition (egg-laying) sites as the density of larva observed on a plant in an independent survey.
-Specifically, we randomly sampled five branches per tree and summed the number of individual gall chambers observed.
-We then converted these counts to a measure of gall density per 100 shoots by counting the number of shoots on the last branch we sampled.
-All larva collected from the same plant were scored with the same female preference.
-The measurement of larval densities on plants in the field is a commonly used index for measuring oviposition preference (@Gripenberg2010); however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference (@Singer1986).
-Fortunately, a couple of features of our study system suggest that larval density on a plant may be a good proxy for female preference.
-For example, since our data comes from a randomized placement of willow genotypes in a common garden, there is no consistent bias in which willow genotypes that females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general (@Hawkins1997), thus we do not expect any prior egg predation to bias our estimates of observed larval densities.
-
-\subsection*{Quantifying the Fitness Landscape}
-
-To characterize the shape of the fitness landscape in simple and complex food webs, we first used a generalized linear mixed model to quantify selection surfaces on individual traits.
-We used a binomial error distribution (logit link function) since larval survival (0 or 1) was our response variable and measure of fitness.
-We specified linear and quadratic terms for each gall trait as well as linear interaction terms between each gall trait as fixed effects in the statistical models.
-To account for the correlated structure of clutch size (gall level) and female preference (plant level) as well as any independent effects of willow genotype on larval survival, we specified gall ID nested within plant ID nested within plant genotype as random effects.
-Since we were interested in characterizing the fitness landscape -- the relationship between mean trait values and population mean fitness -- we assumed the mean value of our random effects (i.e.
-setting them to zero) to estimate selection gradients.
-Also, the fitness landscape assumes that traits distributions are multivariate normal.
-To better meet this assumption, we log-transformed clutch size and added a small constant (1) to female preference before log transforming, since our surveys occassionaly estimated zero larval densities.
-We then scaled all phenotypic traits to mean=0 and SD=1 in order to calculate standardized selection gradients that were comparable across traits and with other studies of natural selection.
-We used the method of @Janzen1998 to calculate directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients and used parametric bootstrapping (1000 replicates) to calculate their 95\% confidence intervals (@Bolker2009).
-We estimated directional selection gradients by excluding quadratic terms and statistical interactions in the model.
-Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
-This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean trait values of the population (Arnold 2001, Morrissey 2009).
-
-Rather than imposing selection, parasitoids may themselves influence the expression of herbivore traits.
-Any influence on trait expression would bias selection gradients acting on those traits.
-In our system, it was plausible that parasitoids may influence chamber growth by promoting larval feeding (cite), speeding up larva development (cite), or killing larva before they complete their development (cite).
-Therefore, our estimates of selection on chamber diameter may be positively or negatively biased.
-To estimate this bias, we subset our data to only include galls where there was variation in larval survival (1 > survival > 0) within the same gall.
-We then calculated "apparent" selection differentials for each gall by comparing the average chamber diameter of all larva (before "selection") to the average chamber diameter of surviving larva and analyzed separate one-sample t-tests for each food-web treatment.
-This analysis is based on the assumption that larva within each gall come from the same clutch and therefore should have similar chamber diameters regardless of whether they are parasitized.
-In general, we found that our estimates of directional selection on chamber diameter were positively biased (Appendix).
-In other words, our analyses were overestimating the magnitude of selection acting on gall diameter.
-Therefore, we adjusted our estimates of directional selection on chamber diameter ($\beta_{diam}$) by subtracting the biased selection differentials.
-Note that selection gradients and selection differentials for chamber diameter were virtually the same (Appendix).
-
-\subsection*{Quantifying Selective Constraints}
-
-The strength and pattern of selective constraints can be measured as the slope and curvature of the fitness landscape (Arnold 1992).
-
-We can translate selection surfaces of individuals to the fitness landscape of a population
-
-To characterize the net effects of food-web complexity on the slope and curvature of *Iteomyia*'s fitness landscape, we took advantage of existing theory that links selection surfaces of individuals to the fitness landscape of the population (Phillips & Arnold 1998, Arnold 2003).
-Specifically, the slope of the fitness landscape corresponds to the column vector of directional selection gradients:
-
-$$\text{Slope} = \beta = \begin{pmatrix} \beta_{diam} \\ \beta_{clutch} \\ \beta_{pref} \end{pmatrix} $$
-whereas the curvature of the fitness landscape is a function of the directional, nonlinear, and correlational selection gradients: 
-$$\text{Curvature} = \gamma - \beta \beta^T$$
-where \gamma represents the matrix of nonlinear and correlational selection gradients:
-$$\gamma = \begin{pmatrix} \gamma_{diam,diam}&& \\ \gamma_{diam,clutch}&\gamma_{clutch,clutch}& \\ \gamma_{diam,pref} & \gamma_{clutch,pref} &\gamma_{pref,pref} \end{pmatrix}$$
-
-Note that we ommitted the upper triangle of the matrix for clarity since it is simply the reflection of the lower triangle.
-Assuming that there is additive genetic variance and covariance between these traits under selection, then the slope and curvature of the fitness landscape give insight to how the population's mean trait value will change in the next generation as well as how additive genetic variance and covariance changes within a generation.
-
-While making quantitative predictions about trait evolution requires knowledge of the additive genetic variance and covariance of these traits, the slope and curvature of the fitness landscape still give qualitative insight to the evolutionary trajectory of a population.
-
-If we assume that there is additive genetic variance and covariance between these traits, then the matrix describing the curvature of the fitness landscape gives qualitative insight to the selective constraints acting on the population.
-For example, the diagonal of the curvature matrix dictates (qualitatively) whether the additive genetic variance in each trait will increase ($+$), decrease ($-$), or stay the same ($0$).
-Similarly, the off-diagonal of the curvature matrix dictates whether selection favors trait integration (positive covariance), a tradeoff (negative covariance), or no change in genetic covariance.
-In other words, we can get qualitative insight to how food-web complexity influences constraints on the fitness landscape by counting the number of negative sign values along the diagnoal (which imply a decrease in additive genetic variance) and the number of positive or negative signs along the off diagonal (which imply changes in additive genetic covariance that lead to either trait integration or tradeoffs).
-
-All analyses and visualizations were conducted in R (@R2018).
-
-I need to go back to estimate a common alpha coefficient if the treatments do not differ from each other.
-
-If we only retain non-zero selection gradients, then we can
-
-Our two dimensional surfaces are likely representative given the fact that there is no strong evidence of correlational selection (Phillips and Arnold 1989, Evolution)
-
-The curvature ($\gamma - \beta \beta^\text{T}$) of the adaptive landscape describes how natural selection changes additive genetic (co)variances ($\Delta \text{G}$) within a generation.
-Specifically, the diagonals of the curvature matrix describe the effect of the adaptive landscape on additive genetic variance within a generation; therefore, any negative values along the diagonal are evidence of selective constraints.
-The off-diagonals of the curvature matrix describe the effect of the adaptive landscape on additive genetic covariances within a generation; therefore, any non-zero values are evidence of selective constraints as they favor trait integration.
-
-\subsection*{Simulating Phenotypic Evolution}
-
-We used the method proposed by Hansen and Houle (2008) to characterize the evolvability of the G-matrices resulting from different adaptive landscapes.
-Their index of evolvability is theoretically linked to the theory underlying G matrices and adaptive landscapes, and describes the ability of a population to evolve in the direction of selection when stabilizing selection is absent.
-
-% Hansen and Houle 2008
-%Alternatively, but not
-%inconsistently, evolvability can be viewed in a quantitative
-%genetics context as a short-term ability to respond to
-%directional selection (Houle, 1992), which depends on
-%standing additive genetic variation in the traits under
-%selection and on the autonomy of this genetic variation
-%from other traits under stabilizing selection (Hansen
-%et al., 2003a, b; Hansen, 2003; Hansen & Houle, 2004)
-
-\section*{Results}
-
-\subsection*{Slope of the adaptive landscape}
-
-We found that food-web complexity altered the slope of the adaptive landscape ($\beta$) in two key ways.
-First, there were fewer traits under directional selection in the complex (2 of 3) vs.
-simple food web (3 of 3).
-For example, in both simple and complex food webs there was directional selection for larger chamber diameters and for adult females to avoid ovipositing on trees with high densities of conspecifics (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
-In the simple food web, we also observed directional selection for smaller clutch sizes, but there was no evidence of selection acting on this trait in the complex food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
-The absence of selection on clutch size in the complex food web appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
-Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (fig.~\ref{Fig:LABEL}).
-
-The second key effect of food-web complexity was to steepen the slope of the adaptive landscape (i.e.
-increase strength of selection).
-For example, the magnitude of directional selection in complex vs.
-simple food webs was \textasciitilde 60\% higher for both chamber diameter and female preference (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
-This result was not due to any difference in the relationship between larva survival and gall phenotype ($\textrm{Simple:coef}_{Diam}=0.02 \ [-0.56,0.60]$; $\textrm{Simple:coef}_{Pref}=-0.16 \ [-0.83,0.61]$), but was due to the fact that the average probability of larval survival was lower in complex (0.44 [0.30,0.58]) vs.
-simple food webs (0.69 [0.54,0.80]).
-%Note that although the selection gradient is typically expressed as the covariance between relative fitness ($w$) and phenotype ($z_i$), $\beta_{z_i}=\textrm{cov}(w,z_i)$, it can be rewritten as a function of both absolute fitness ($W$) and mean fitness ($\bar W$), $\beta_{z_i}=\textrm{cov}(W,z_i)/ \bar W$.
-This alternative expression makes clear that lower survival, and thus mean fitness, will always increase the strength of selection.
-
-\subsection*{Curvature of the adaptive landscape}
-
-Unlike the slope, the curvature of the adaptive landscape ($\gamma - \beta \beta^\text{T}$) is influenced by directional ($\beta_{z_i}$), quadratic ($\gamma_{z_i,z_i}$), and correlational ($\gamma_{z_i,z_j}$) selection gradients.
-Our food-web treatment did not appear to alter correlational selection for any combination of traits and there was no strong evidence that any of these selection gradients differed from zero (fig.~\ref{Fig:LABEL}).
-Similarly, our food-web treatment did not influence quadratic selection on chamber diameter or clutch size and there was no strong evidence that these selection gradients differed from zero (fig.~\ref{Fig:LABEL}).
-In contrast, our food-web treatment did alter quadratic selection acting on female preference.
-Specifically, we found evidence for disruptive selection in the complex food web, but no evidence of disruptive or stabilizing selection in the simple food web (fig.~\ref{Fig:LABEL}; fig.~\ref{Fig:FL_1D}).
-Disruptive selection in the complex food web appeared to be due to the presence of larval parasitoids enhancing the relative fitness of larva occuring on either low or high density trees (fig.~\ref{Fig:LABEL}).
-
-We can quantify the curvature ($C$) of the adaptive landscape by subtracting the matrix of directional selection gradients ($\beta \beta^\text{T}$) from the matrix of quadratic and correlational selection gradients ($\gamma$):
-
-$$C = \begin{pmatrix} C_{Diam,Diam} &  &  \\  C_{Clutch,Diam} & C_{Clutch,Clutch} &  \\  C_{Pref,Diam} & C_{Pref,Clutch} & C_{Pref,Pref} \end{pmatrix}$$
-
-We omit the upper triangle of the matrix for clarity, because it is a mirror image of the lower triangle.
-Each component of this matrix describes how the adaptive landscape changes additive genetic (co)variances in phenotypic traits within a generation.
-To empirically estimate the curvature, we only retained nonzero selection gradients (i.e.
-95\% CI does not overlap with zero).
-We found that the curvature of the adaptive landscape in the complex and simple food web exhibited the following structures:
-
-$$C_{Complex} = \begin{pmatrix} -0.13 &  &  \\ 0 & 0 &  \\ 0.09 & 0 & 0.33 \end{pmatrix}$$
-
-$$C_{Simple} = \begin{pmatrix} -0.05 &  &  \\  0.02 & -0.01 &  \\  0.03 & -0.01 & -0.02 \end{pmatrix}$$
-
-Comparing these matrices, we find evidence of selective constraints acting on 2 of 6 trait (co)variances in the complex food web, whereas 6 of 6 trait (co)variances experience selective constraints in the simple food web.
-Specifically, we found that simple food webs acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the complex food web.
-For genetic covariances, we found that the simple food web favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.~\ref{Fig:FL_2D}).
-In contrast, the complex food web only constrained genetic covariance by favoring integration between chamber diameter and female preference (fig.~\ref{Fig:FL_2D}).
-
-\section*{Discussion}
-
-Our key finding was that phenotypic evolution was less constrained for a species that was embedded within a complex food web compared to a simple one. These
-
-Two key patterns emerged from our study.
-First, selection was stronger and thus the potential speed of evolution in complex compared to simple food webs.
-Second, the adaptive landscape was less constrained in the complex vs.
-the simple food web.
-
-\section*{Conclusion}
-
-%%%%%%%%%%%%%%%%%%%%%
-% Acknowledgments
-%%%%%%%%%%%%%%%%%%%%%
-% You may wish to remove the Acknowledgments section while your paper 
-% is under review (unless you wish to waive your anonymity under
-% double-blind review) if the Acknowledgments reveal your identity.
-% If you remove this section, you will need to add it back in to your
-% final files after acceptance.
-
-\section*{Acknowledgments}
-
-\newpage{}
-
-%%%%%%%%%%%%%%%%%%%%%
-% Bibliography
-%%%%%%%%%%%%%%%%%%%%%
-% You can either type your references following the examples below, or
-% compile your BiBTeX database and paste the contents of your .bbl file
-% here. The amnatnat.bst style file should work for this---but please
-% let us know if you run into any hitches with it!
-% The list below includes sample journal articles, book chapters, and
-% Dryad references.
-
-\bibliographystyle{amnat}
-\bibliography{bibliography}
-
-\newpage{}
-
-%\section*{Tables}
-%\renewcommand{\thetable}{\arabic{table}}
-%\setcounter{table}{0}
-
-%\begin{table}[h]
-%\caption{Selection gradients acting on \textit{Iteomyia} in complex vs. simple food webs.}
-%\label{Table:ComplexSimple}
-%\centering
-%\begin{tabular}{lcc}
-%                                                                                  \\ \hline
-                                  %& \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-%\textbf{Selection gradient}       & \textbf{Complex} & \textbf{Simple}            \\ \hline
-%$\beta_{Diam}^a$                    & 0.47 [0.36,0.59] & 0.29 [0.23,0.37] \\
-%$\beta_{Clutch}$                  & 0.06 [-0.05,0.19] & -0.09 [-0.17,-0.02] \\
-%$\beta_{Pref}$                    & -0.24 [-0.38,-0.11] & -0.15 [-0.24,-0.07] \\
-%$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
-%$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.05] & -0.06 [-0.16,0.03] \\
-%$\gamma_{Pref,Pref}$              & 0.39 [0.04,0.74] & -0.07 [-0.25,0.11] \\
-%$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.00] \\
-%$\gamma_{Diam,Pref}$              & -0.08 [-0.18,0.01] & -0.05 [-0.11,0.01] \\
-%$\gamma_{Clutch,Pref}$            & 0.04 [-0.05,0.13] & 0.02 [-0.03,0.08]            \\ \hline
-%\end{tabular}
-%\bigskip{}
-%\\
-%{\footnotesize Note: Values within brackets represent 95\% confidence intervals. $^a$ Adjusted for bias.}
-%\end{table}
-
-%\newpage{}
-
-%\begin{table}[h]
-%\caption{Selection gradients imposed by larval vs. egg parasitoids on \textit{Iteomyia}.}
-%\label{Table:LarvalEgg}
-%\centering
-%\begin{tabular}{lcc}
-%                                                                                  \\ \hline
-                                  %& \multicolumn{2}{c}{Food web (Estimate [95\% CI])} \\
-%\textbf{Selection gradient}       & \textbf{Larval} & \textbf{Egg}            \\ \hline
-%$\beta_{Diam}^a$                    & 0.47 [0.36,0.59] & 0.29 [0.23,0.37] \\
-%$\beta_{Clutch}$                  & 0.06 [-0.05,0.19] & -0.09 [-0.17,-0.02] \\
-%$\beta_{Pref}$                    & -0.24 [-0.38,-0.11] & -0.15 [-0.24,-0.07] \\
-%$\gamma_{Diam,Diam}$              & 0.13 [0.00,0.26] & 0.08 [0.00,0.16] \\
-%$\gamma_{Clutch,Clutch}$          & -0.10 [-0.25,0.05] & -0.06 [-0.16,0.03] \\
-%$\gamma_{Pref,Pref}$              & 0.39 [0.04,0.74] & -0.07 [-0.25,0.11] \\
-%$\gamma_{Diam,Clutch}$            & -0.08 [-0.16,0.01] & -0.05 [-0.10,0.00] \\
-%$\gamma_{Diam,Pref}$              & -0.08 [-0.18,0.01] & -0.05 [-0.11,0.01] \\
-%$\gamma_{Clutch,Pref}$            & 0.04 [-0.05,0.13] & 0.02 [-0.03,0.08]            \\ \hline
-%\end{tabular}
-%\bigskip{}
-%\\
-%{\footnotesize Note: Values within brackets represent 95\% confidence intervals.
-Selection gradients and confidence intervals for egg parasitoids are equivalent to estimates for the simple food web.
-$^a$ Adjusted for bias.}
-%\end{table}
-
-%\newpage{}
-
-%\begin{table}[h]
-%\caption{Table for bias}
-%\label{Table:Bias}
-%\centering
-%\begin{tabular}{lc}
-%                                                                  \\ \hline
-%\textbf{Type}                 & \textbf{Bias} \boldmath$s_{Diam}$ \\ \hline
-%Complex (All)                 &  [ - ] \\
-%Complex (Larval guild)        &  [ - ] \\
-%Simple (\textit{Platygaster}) &  [ - ]                  \\ \hline
-%\end{tabular}
-%\bigskip{}
-%\\
-%{\footnotesize Note: Table titles should be short.
-Further details should go in a `notes' area after the tabular environment, like this.
-$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
-%\end{table}
-
-%\newpage{}
-
-%\begin{table}[h]
-%\caption{Table for \textit{Platygaster} Selection Differentials}
-%\label{Table:PlatySelection}
-%\centering
-%\begin{tabular}{lc}
-                                                                  \\ \hline
-%\textbf{Selection differential} & \textbf{Estimate [95\% CI]}     \\ \hline
-%$s_{Diam}$                      & 0.06 [-0.14,0.27] \\
-%$s_{Clutch}$                    & 0.20 [-0.10,0.51] \\
-%$s_{Pref}$                      & 0.20 [0.07,0.33 \\ 
-%$s_{Diam,Diam}$                 & -0.11 \\
-%$s_{Clutch,Clutch}$             & -0.91 \\
-%$s_{Pref,Pref}$                 & -0.24                \\ \hline
-%\end{tabular}
-%\bigskip{}
-%\\
-%{\footnotesize Note: Table titles should be short.
-Further details should go in a `notes' area after the tabular environment, like this.
-$^a$ Okapis are not native to Chicago, but they are to be met with in both of the major Chicagoland zoos.}
-%\end{table}
-
-%\newpage{}
-
-\section*{Figure legends}
-
-%Path relative to the main .tex file 
-\graphicspath{ {../analyses/reproduce_analyses_files/figure-html/} }
-
-\begin{figure}[h!]
-%\includegraphics{FIGURE}
-\caption{Selection gradients acting on \textit{Iteomyia} phenotypes.
-Points and lines correspond to estimated means and 95\% confidence intervals, respectively.
-Orange and blue colors correspond to estimated gradients in complex and simple food webs, respectively.
-Yellow colors correspond to selection gradients imposed by larval parasitoids.
-Note that we only plot selection gradients for larval parasitoids when they differed from egg parasitoids (simple food web).}
-\label{Fig:LABEL}
+\begin{figure}
+\centering
+\includegraphics{analyses/complex_simple_foodwebs_v2.jpeg}
+\caption{\label{fig:Conceptual}Experimental manipulation of food-web
+structure associated with a leaf-galling midge (\emph{Iteomyia
+salicisverruca}) feeding on the willow \emph{Salix hookeriana}. Black
+arrows denote the flow of energy in this network of trophic
+interactions. In the original food web, we allowed the full suite of egg
+and larval parasitoids to impose selection. To simulate consumer
+extinction, we used mesh bags to exclude the guild of larval
+parasitoids, only allowing the egg parasitoid (\emph{Platygaster} sp.)
+to impose selection. Larval parasitoids include the following species
+(from left to right): \emph{Mesopolobus} sp. (Family: Pteromalidae);
+\emph{Tetrastichus} sp. (Family: Eulophidae); and \emph{Torymus} sp.
+(Family: Torymidae).}
 \end{figure}
 
-\begin{figure}[h!]
-\includegraphics{Univariate-Fitness-Landscapes-1.png}
-\caption{Adaptive landscape of \textit{Iteomyia} phenotypes in complex vs.
-simple food webs.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); clutch size (B); and female preference (C).
-Solid lines represent the estimated gradients in complex (orange) and simple (blue) food webs.
-Transparent lines represent bootstrapped replicates to show the uncertainty in estimated gradients.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 bootstrapped samples.
-Note the mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape.}
-\label{Fig:FL_1D}
+\section{Methods}\label{methods}
+
+\subsection{Study Site}\label{study-site}
+
+We conducted our study within a four-year old common garden experiment
+of coastal willow (\emph{Salix hookeriana}) located at Humboldt Bay
+National Wildlife Refuge (HBNWR) (40 40'53``N, 124 12'4''W) near Loleta,
+California, USA. This common garden consists of 26 different willow
+genotypes that were collected from a single population of willows
+growing around Humboldt Bay. Stem cuttings of each genotype (25
+replicates per genotype) were planted in a completely randomized design
+in two hectares of a former cattle pasture at HBNWR. Willows at our
+study site begin flowering in February and reach their peak growth in
+early August. During this study, willows had reached 5 - 9m in height.
+Further details on the genotyping and planting of the common garden are
+available in \citet{Barbour2015}.
+
+\subsection{Manipulating Food-web
+Structure}\label{manipulating-food-web-structure}
+
+We setup our food-web manipulation across 128 plants soon after galls
+began developing on willows in early June of 2013. These 128 plants came
+from eight different plant genotypes that spanned the range of trait
+variation observed in this willow population \citep{Barbour2015}. For
+the original food web (eight replicates per genotype), we used flagging
+tape to mark 14 galled leaves per plant (\textasciitilde{}30 larvae),
+allowing the full suite of egg and larval parasitoids to impose
+selection. Marking galls with flagging tape ensured that all galls had
+similar phenology when we collected galls later in the season. To
+simulate consumer extinctions, we enclosed 14 galled leaves with 10x15cm
+organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three
+parasitoid species that attack during larval development. This treatment
+did not exclude the egg parasitoid \emph{Platygaster} sp., which attacks
+prior to gall initiation \citep[larva initiate gall development in
+Cecidomyiid midges:][]{Gagne1989}. In late August, we collected marked
+and bagged galls from each plant, placed them into 30 mL vials and kept
+them in the lab for 4 months at room temperature. We then opened galls
+under a dissecting scope and determined whether larvae survived to
+pupation (our measure of fitness) or were parasitized. We did not
+include other sources of mortality, such as early larval death, as they
+could influence the expression of the gall phenotype and confound
+estimates of selection. For the food-web treatment that excluded larval
+parasitoids, we further restricted our data by removing any incidental
+instances of parasitism by a larval parasitoid. This represented less
+than 3\% of the observations in this food-web treatment and allowed us
+to focus our inferences of selection on those imposed by the egg
+parasitoid. Our final dataset contains survival estimates for 1285
+larvae from 613 galls and 111 plants.
+
+\subsection{Measuring Phenotypic
+Traits}\label{measuring-phenotypic-traits}
+
+We collected data on three different traits that we expected to
+influence larval survival based on previous work in this system
+\citep{Barbour2016} and other work with gall midges
+\citep{Weis1983, Heath2018}. First, we measured gall diameter as the
+size of each gall chamber to the nearest 0.01 mm at its maximum diameter
+(perpendicular to the direction of plant tissue growth). Previous work
+in this system has shown that larger galls are associated with higher
+survival \citep{Barbour2016}. Second, we measured clutch size by
+counting the number of chambers in each gall
+\citep{Weis1983, Heath2018}. All larvae collected from the same
+multi-chambered gall were scored with the same clutch size. Third, we
+measured oviposition preference as the density of larvae observed on a
+plant in an independent survey. We did this by randomly sampling five
+branches per tree and counting the number of individual gall chambers
+(number of larvae). We then converted these counts to a measure of
+larval density per 100 shoots by counting the number of shoots on the
+last branch we sampled. All larvae collected from the same plant were
+scored with the same oviposition preference. Measuring larval densities
+on plants in the field is a common method for measuring oviposition
+preference \citep{Gripenberg2010}; however, caution must be taken in
+inferring `preference' as larval densities can be influenced by
+processes other than preference \citep{Singer1986}. Fortunately, a
+couple features of our study system suggest that larval densities may be
+a good proxy for oviposition preference. For example, since our data
+comes from a randomized placement of plant genotypes in a common garden,
+there is no consistent bias in which plant genotypes females are exposed
+to while searching for oviposition sites. Also, egg predation is a minor
+source of mortality for galling insects in general \citep{Hawkins1997};
+therefore, we do not expect any prior egg predation to bias our
+estimates of observed larval densities.
+
+\subsection{Quantifying the Adaptive
+Landscape}\label{quantifying-the-adaptive-landscape}
+
+Inferring adaptive landscapes assumes that trait distributions are
+multivariate normal \citep{Lande1983}. To approximate this assumption,
+we log-transformed clutch size and square-root transformed oviposition
+preference. We then scaled all phenotypic traits (mean=0 and SD=1) prior
+to our analyses (detailed below) to ensure that our estimates of
+selection were comparable across traits and with other studies.
+
+Our analysis consisted of three parts. First, we used generalized linear
+mixed models (GLMM) to quantify selection surfaces \textemdash linear
+and nonlinear relationships between absolute fitness (\(W\)) and
+standardized phenotypic traits (\(i\)) of individuals \textemdash in
+each food-web treatment. Second, we translated selection surfaces into
+the scale of relative fitness (\(w\)) in order to calculate standardized
+selection gradients. Third, we used our estimates of selection gradients
+to characterize the slope and curvature of the adaptive landscape, which
+we used to measure evolutionary constraints.
+
+\textbf{Selection surfaces}: Since larval survival was our measure of
+absolute fitness, we used a GLMM that assumed a binomial error
+distribution (and logit-link function). To approximate the selection
+surface, we modelled larval survival as a function of food-web treatment
+as well as linear (\(\alpha_i\)), quadratic (\(\alpha_{ii}\)), and
+linear interactions (\(\alpha_{ij}\)) between each trait. We also
+allowed these selection surfaces (\(\alpha\)) to vary between food-web
+treatments. Note that to obtain valid estimates of linear selection
+surfaces, we removed nonlinear terms prior to estimating linear
+relationships \citep{Lande1983}. Other approaches have been advocated
+for approximating selection surfaces \citep{Schluter1988}; however, our
+approach enables us to calculate selection gradients, and thus is more
+appropriate for approximating the adaptive landscape \citep{Arnold2003}.
+To account for the nonindependence of clutch size (measured at gall
+level) and oviposition preference (measured at plant level) as well as
+any independent effects of willow genotype on larval survival, we
+modelled gall ID nested within plant ID nested within genotype ID as
+random effects. Although statistical models with random effects are not
+common in analyses of natural selection, we think that modelling random
+effects can mitigate biased estimates of selection due to environmental
+covariances between traits and fitness \citep{Rausher1992}. Since our
+end goal was to characterize the relationship between mean trait values
+and mean fitness (adaptive landscape), we assumed the mean value of our
+random effects (i.e., setting them to zero) when calculating selection
+surfaces. We then used parametric bootstrapping (1,000 replicates) to
+estimate the effect of food-web treatment on larval survival as well as
+selection surfaces in each food-web treatment.
+
+\textbf{Selection gradients}: Selection gradients cannot be estimated
+directly from GLMMs of selection surfaces because the response is in
+terms of absolute fitness and the coefficients are on a nonlinear scale.
+For example, the coefficients in the above model measure the change in
+the logarithm of the odds of surviving (i.e.,
+\(\text{ln}\{W(z)/[1-W(z)]\}\)) associated with 1 SD change in a trait
+with all other traits held fixed at their mean. Therefore, we used the
+method developed by \citet{Janzen1998} to translate selection surfaces
+from the above model into the scale of relative fitness in order to
+calculate directional (\(\beta_i\)), quadratic (\(\gamma_{ii}\)), and
+correlational (\(\gamma_{ij}\)) selection gradients. Briefly, this
+method calculates the average gradient of selection surfaces by
+multiplying the average of \(W(z)[1-W(z)]\) by each regression
+coefficient (e.g. \(\alpha_i\), \(\alpha_{ii}\), or \(\alpha_{ij}\)). We
+then divided this average gradient by the mean fitness (\(\bar W\)) to
+put it on the scale of relative fitness, and thus interpretable as a
+selection gradient. We estimated selection gradients separately for each
+food-web treatment. Note that we doubled all quadratic terms prior to
+calculating selection gradients to put them on the same scale as
+estimates of directional and correlational selection
+\citep{Stinchcombe2008}.
+
+\textbf{Evolutionary constraints}: We measured evolutionary constraints
+by inspecting the slope and curvature of the adaptive landscape. The
+number of selective constraints is determined by the slope of the
+adaptive landscape, which in our study corresponds to:
+
+\[\textbf{Slope} = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} \]
+where each \(\beta_i\) corresponds to the directional selection gradient
+acting on each trait. By comparing the number of directional selection
+gradients that show clear evidence of contributing to the slope (i.e.,
+95\% CI does not overlap zero) in our food-web treatments, we can infer
+the effect of food-web structure on selective constraints.
+
+The indirect effects of selection on the G-matrix
+(\(\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}\)) is
+governed by the curvature of the adaptive landscape
+(\(\text{C}=\gamma - \beta \beta^\text{T}\)), which in our study
+corresponds to:
+
+\[\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}\]
+
+where each \(\gamma_{ii}\) (diagonal) corresponds to the quadratic
+selection gradient acting on a trait, and each \(\gamma_{ij}\)
+(off-diagonal) corresponds to the correlational selection gradient
+acting on a particular trait combination. Note that we ommitted the
+upper triangle of each matrix for clarity since it is simply the
+reflection of the lower triangle. Subtracting these two matrices results
+in the curvature matrix of the adaptive landscape:
+
+\[\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}\]
+where each \(\text{C}_{ii}\) (diagonal) represents the effect of
+selection on the additive genetic variance in a trait, and each
+\(\text{C}_{ij}\) (off-diagonal) represents the effect of selection on
+the additive genetic covariance between a particular trait combination.
+In other words, the sign of diagonal terms of the curvature matrix
+dictate whether selection will increase (+), decrease (-), or cause no
+change (0) in the additive genetic variance of a trait. Similarly, any
+nonzero covariance terms (off-diagonal) are indicative of selection for
+trait integration (i.e., less independence). Therefore, we can infer the
+number of genetic constraints by summing the number of negative signs
+along the diagonal (decrease in additive genetic variance) and the
+number of nonzero terms along the off-diagonal (trait integration) of
+the curvature matrix. For these analyses, we retained estimates for
+selection gradients that showed clear evidence of being different from
+zero (i.e., 95\% CI did not overlap zero) and set other gradients to
+zero, prior to calculating the curvature matrix in each food-web
+treatment. This provides a conservative estimate of the factors
+contributing to the curvature of the adaptive landscape.
+
+Note that our metrics of selective and genetic constraints do not put
+much stock in differences in the magnitude of selection between food-web
+treatments. This is because there is a high likelihood that we are
+underestimating the magnitude of selection in our treatment that
+excludes larval parasitoids. We expect this because larval parasitoids
+not only impose mortality on gall midges, but egg parasitoids as well
+(fig. \ref{fig:Conceptual}). Therefore, our short-term removal of larval
+parasitoids has not allowed for an increase in egg parasitoid abundance
+after being released from intraguild predation. An increase in the
+abundance of egg parasitoids would decrease mean survival of gall
+midges, thus increasing the variance in relative fitness of midges, and
+consequently the magnitude of selection estimates. A recent paper by
+\citet{Hunter2018} highlights this pervasive effect of survival on the
+magnitude of selection estimates. This is why we use more qualitative
+metrics of evolutionary constraints (i.e., selective constraints =
+number of traits under directional selection; genetic constraints =
+number of decreasing variances + nonzero covariances).
+
+\subsection{Adjusting for biased measurements of
+selection}\label{adjusting-for-biased-measurements-of-selection}
+
+Rather than imposing selection, parasitoids may influence the expression
+of herbivore traits which could bias measurements of selection. In our
+system, it was plausible that parasitoids may influence chamber diameter
+by altering larval feeding behavior or killing larvae before they
+complete their development. To estimate this potential bias, we subset
+our data to only include galls where there was variation in larval
+survival within the same gall (i.e.~1 \textgreater{} mean survival
+\textgreater{} 0). If we assume that larvae within each gall should have
+similar chamber diameters because they come from the same clutch and
+experience the same local environment (an assumption our data supports:
+gall ID explains 54\% of the variance in chamber diameter), then the
+relationship between chamber diameter and larval survival in this data
+subset represents the effect of parasitism on trait expression
+(i.e.~bias). We used a GLMM with the same structure as described above
+except that we modeled only a linear relationship between chamber
+diameter and larval survival (\(\alpha_{\text{Diam}}\)). We detected a
+positive bias in both food-web treatments (original
+\(\alpha_{\text{Diam}}\)= 0.36 {[}0.05, 0.67{]}; extinction
+\(\alpha_{\text{Diam}}\)= 0.42 {[}0.01, 0.82{]}), indicating that
+unadjusted relationships would overestimate the strength of selection on
+chamber diameter. To account for this bias, we substracted our mean
+estimates of bias from our estimates with the full dataset prior to
+calculating chamber diameter's selection surface and directional
+selection gradient.
+
+\subsection{Measuring selection on egg
+parasitoids}\label{measuring-selection-on-egg-parasitoids}
+
+Once parasitized, the gall phenotype becomes the phenotype of the egg
+parasitoid. This phenotype may influence the egg parasitoid's survival
+in the face of larval parasitoids, and thus experiences selection. Our
+food-web manipulation allows us to measure selection imposed by larval
+parasitoids on the phenotype of egg parasitoids. Using the same models
+as described above, we substituted egg parasitism as our response
+variable to quantify selection surfaces and selection gradients acting
+on the egg parasitoid. Note that we cannot test the effect of food-web
+structure on the egg parasitoid's adaptive landscape ---we can only
+estimate selection imposed by larval parasitoids. This comparison is
+still useful though in determining the extent to which the community
+context may have indirect evolutionary effects by altering selection on
+multiple interacting populations.
+
+All analyses and visualizations were conducted in R \citep{R2018}.
+Unless otherwise noted, we report mean estimates of selection surfaces
+and selection gradients with 95\% confidence intervals in brackets. Note
+that for visualizing the adaptive landscape we restrict trait axes to
+\(\pm 1\) SD of the mean trait value. This emphasizes the fact that we
+can only reliably estimate the shape of the adaptive landscape near the
+mean phenotype of the population \citep{Arnold2001}. We also plot mean
+larval survival on a natural log scale to accurately reflect the
+mathematical definition of the adaptive landscape \citep{Arnold2003}.
+All data and code to reproduce the reported results are publicly
+available on GitHub and have been archived on Zenodo (links are
+available from the journal office).
+
+\section{Results}\label{results}
+
+\subsection{Consumer extinctions increase selective
+constraints}\label{consumer-extinctions-increase-selective-constraints}
+
+\indent We found that the extinction of larval parasitoids increased the
+number of gall midge traits under directional selection (3 of 3)
+relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
+For example, we observed directional selection for smaller clutch sizes
+when we excluded larval parasitoids, but there was no evidence of
+selection acting on this trait in the original food web (table
+\ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This absence of
+selection appeared to be a result of conflicting selection pressures
+imposed by each guild of parasitoids. Specifically, when we subset our
+data to focus on differences between parasitoid guilds, we found that
+larval parasitoids actually impose directional selection for larger
+clutch sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}). We also
+observed clear evidence of directional selection for midges to avoid
+ovipositing on plants with high densities of conspecifics when we
+excluded larval parasitoids (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}B); however, there was no clear relationship in
+the original food web (table \ref{Table:Gradients}). This was likely a
+result of larval parasitoids imposing greater mortality on egg
+parasitoids at high gall midge densities (see Selection on egg
+parasitoids section), and thus a less than additive effect on gall
+midges. Chamber diameter experienced positive directional selection in
+both food-web treatments (fig. \ref{fig:UV_Landscape}A). Although the
+magnitude of selection on chamber diameter was relatively higher in the
+original food web (table \ref{Table:Gradients}), this was not due to any
+difference in the relationship between chamber diameter and survival
+(selection surfaces: original \(\alpha_{\text{Diam}}\)= 1.15 {[}0.75,
+1.61{]}; extinction \(\alpha_{\text{Diam}}\)= 1.1 {[}0.64, 1.65{]}), but
+was simply a consequence of the (expected) lower survival in the
+original food web (original \(\bar W\)= 0.42 {[}0.28, 0.56{]};
+extinction \(\bar W\)= 0.68 {[}0.54, 0.81{]}).
+
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lcc} %c
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction}   \\ %& \textbf{Contrast}
+\hline
+$\beta_{\text{Diam}}$ & 
+\textbf{
+0.34 [
+0.22,
+0.48] }& 
+\textbf{
+0.21 [
+0.12,
+0.31] }\\%& 
+%\textbf{
+%0.14 [
+%0.27,
+%0] }\\
+
+$\beta_{\text{Clutch}}$ & 
+0.06 [
+-0.05,
+0.17] & 
+\textbf{
+-0.09 [
+-0.17,
+-0.01] }\\%& 
+%\textbf{
+%0.15 [
+%0.29,
+%0.03] }\\
+
+$\beta_{\text{Pref}}$ &
+-0.13 [
+-0.29,
+0.05] & 
+\textbf{
+-0.16 [
+-0.26,
+-0.06] }\\%&
+
+%0.03 [
+%0.21,
+%-0.15] \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+0.13 [
+-0.06,
+0.33] &
+
+0.1 [
+-0.02,
+0.23] \\%&
+
+%0.03 [
+%0.27,
+%-0.2] \\
+
+$\gamma_{\text{Clutch:Clutch}}$ & 
+-0.05 [
+-0.27,
+0.18] &
+
+-0.11 [
+-0.28,
+0.03] \\%&
+
+%0.06 [
+%0.32,
+%-0.2] \\
+
+$\gamma_{\text{Pref:Pref}}$ & 
+\textbf{
+0.34 [
+0.07,
+0.63] }&
+
+0.02 [
+-0.14,
+0.18] \\%& 
+%\textbf{
+%0.32 [
+%0.64,
+%0.01] }\\
+
+$\gamma_{\text{Diam:Clutch}}$ & 
+-0.04 [
+-0.16,
+0.08] &
+
+-0.07 [
+-0.15,
+0.02] \\%&
+
+%0.02 [
+%0.17,
+%-0.12] \\
+
+$\gamma_{\text{Diam:Pref}}$ & 
+-0.13 [
+-0.29,
+0.02] &
+
+-0.02 [
+-0.1,
+0.07] \\%&
+
+%-0.12 [
+%0.05,
+%-0.3] \\
+
+$\gamma_{\text{Clutch:Pref}}$ & 
+0.03 [
+-0.1,
+0.18] &
+
+0 [
+-0.07,
+0.07] \\%&
+
+%0.03 [
+%0.18,
+%-0.12] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\subsection{Consumer extinctions increase genetic
+constraints}\label{consumer-extinctions-increase-genetic-constraints}
+
+\indent The curvature of the adaptive landscape indirectly affects
+genetic constraints and is influenced by directional, quadratic, and
+correlational selection gradients. There was no clear evidence of
+correlational selection for any combination of traits in either food-web
+treatment (table \ref{Table:Gradients}). Similarly, there was no clear
+evidence of quadratic selection on chamber diameter or clutch size in
+either food-web treatment (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}A,C). In contrast, our food-web treatment did
+alter quadratic selection acting on oviposition preference (table
+\ref{Table:Gradients}). The negative relationship between oviposition
+preference and larval survival dampened at high densities in the
+original food web, but not with the exclusion of larval parasitoids
+(fig. \ref{fig:UV_Landscape}B). This dampened relationship was partly
+due to a trend for nonlinear selection imposed by larval parasitoids
+(\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02, 0.42{]}), but was also
+magnified by the lower average survival in complex food webs.
+
+\begin{figure}
+\centering
+\includegraphics{analyses/UV_landscapes.pdf}
+\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
+phenotypes in the original food web and with the extinction of larval
+parasitoids. Each panel corresponds to a different phenotypic trait:
+chamber diameter (A); oviposition preference (B); and clutch size (C).
+Bold lines represent selection experienced in the original food web
+(orange) and with consumer extinctions (blue). Thin lines represent
+bootstrapped replicates to show the uncertainty in selection. For
+clarity, we only display 100 bootstraps even though inferences are based
+on 1,000 replicates. Note that mean larval survival is plotted on a
+natural log scale to reflect the mathematical defintion of the adaptive
+landscape.}
 \end{figure}
 
-\begin{figure}[h!]
-\includegraphics{Multivariate-Fitness-Landscapes-1.png}
-\caption{Two dimensional view of adaptive landscapes in complex vs.
-simple food webs.
-Each panel corresponds to a different combination of traits: clutch size and chamber diameter (A); clutch size and female preference (B); female preference and chamber diameter (C).
-Note the mean larva survival is plotted on a natural log scale to accurately reflect the shape of the adaptive landscape.}
-\label{Fig:FL_2D}
+Using our estimates of directional (\(\beta_i\)), quadratic
+(\(\gamma_{ii}\)), and correlation selection (\(\gamma_{ij}\)), we
+calculated the curvature (\(\text{C}=\gamma - \beta \beta^\text{T}\)) of
+the adaptive landscape in each food-web treatment. In our study, this
+corresponds to:
+
+\[\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}\]
+
+\[\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}\]
+\bigskip
+
+where each \(\text{C}_{ii}\) (diagonal) represents the effect of
+selection on the additive genetic variance in a trait, and each
+\(\text{C}_{ij}\) (off-diagonal) represents the effect of selection on
+the additive genetic covariance between a particular trait combination.
+In order to obtain a conservative estimate of the factors contributing
+to the curvature, we only used estimates of selection that clearly
+differed from zero (bold values in table \ref{Table:Gradients}),
+otherwise we set estimates of selection to zero (non-bold values in
+table \ref{Table:Gradients}) prior to our calculation. We found that the
+curvatures of the adaptive landscape exhibited the following structures:
+
+\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
+0 &  &  \\  
+0 & 0 &  \\  
+0 & 0 & 0.34 \end{pmatrix} - \begin{pmatrix} 
+0.34\cdot0.34 &  &  \\  
+0\cdot0.34 & 0\cdot0 &  \\  
+0\cdot0.34 & 0\cdot0 & 0\cdot0 \end{pmatrix}\]
+
+\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
+-0.12 &  &  \\  
+0 & 0 &  \\  
+0 & 0 & 0.34 \end{pmatrix}\]
+
+\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
+0 &  &  \\  
+0 & 0 &  \\  
+0 & 0 & 0 \end{pmatrix} - \begin{pmatrix} 
+0.21\cdot0.21 &  &  \\  
+-0.09\cdot0.21 & -0.09\cdot-0.09 &  \\  
+-0.16\cdot0.21 & -0.16\cdot-0.09 & -0.16\cdot-0.16 \end{pmatrix}\]
+
+\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
+-0.04 &  &  \\  
+0.02 & -0.01 &  \\  
+0.03 & -0.01 & -0.03 \end{pmatrix}\]
+
+Remember that we can infer the indirect effects of selection on genetic
+constraints by summing the number of negative signs along the diagonal
+(decrease in additive genetic variance) and the number of nonzero terms
+along the off-diagonal (trait integration) of the curvature matrix. The
+structure of these matrices indicates that the extinction of larval
+parasitoids increased the number of genetic constraints on gall midges
+(6 of 6) relative to the original food web (1 of 6). For example,
+directional selection resulting from the exclusion of larval parasitoids
+acted to decrease genetic variance for all three phenotypic traits
+(negative diagonal terms), whereas only one trait (chamber diameter)
+experienced a decrease in additive genetic variance in the original food
+web. For genetic covariances, the combined effects of directional
+selection resulting from consumer extinctions favored integration among
+all three phenotypic traits (nonzero off-diagonal terms), and thus
+constraints along all three axes of covariance (fig.
+\ref{fig:MV_Landscape}). In contrast, the absence of directional
+selection in clutch size and oviposition preference did not promote
+trait integration along any axis in the original food web (fig.
+\ref{fig:MV_Landscape}).
+
+\begin{figure}
+\centering
+\includegraphics{analyses/MV_landscapes.pdf}
+\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
+landscapes of gall midge phenotypes in the original food web and with
+the extinction of larval parasitoids. Each panel corresponds to a
+different combination of phenotypic traits: clutch size and chamber
+diameter (A); clutch size and oviposition preference (B); oviposition
+preference and chamber diameter (C). Arrows represent mean estimates of
+directional selection gradients, while contours represent predicted
+larval survival of the mean phenotype in each food-web treatment. Notice
+that arrows point more toward a corner of the adaptive landscape for
+each combination of traits with the extinction of larval parasitoids
+compared to the original food web. This indicates that consumer
+extinctions more strongly favored trait integration (covariance). Note
+that mean larval survival is plotted on a natural log scale to reflect
+the mathematical definition of the adaptive landscape.}
 \end{figure}
 
-%\subsection*{Online figure legends}
+\subsection{Selection on egg
+parasitoids}\label{selection-on-egg-parasitoids}
 
-%\renewcommand{\thefigure}{A\arabic{figure}}
-%\setcounter{figure}{0}
+The exctinction of larval parasitoids only altered the relationship
+between gall midge preference and the probability of observing egg
+parasitoids (table \ref{Table:ExtendedGradients}). Specifically, the
+impact of larval parasitoids increased nonlinearly with higher gall
+midge densities (fig. \ref{fig:EggPtoid_Selection}).
 
-%\begin{figure}[h!]
-%\includegraphics{jumps20m}
-%\caption{\textit{A}, the quick red fox proceeding to jump 20~m straight into the air over not one, but several lazy dogs.
-\textit{B}, the quick red fox landing gracefully despite the skepticism of naysayers.}
-%\label{Fig:Jumps}
-%\end{figure}
+\bigskip
 
-%\begin{figure}[h!]
-%\includegraphics{jumps20m}
-%\caption{The quicker the red fox jumps, the likelier it is to land near an okapi. For further details, see \citet{LemKapEx07}.}
-%\label{Fig:JumpsOk}
-%\end{figure}
+\begin{table}[h]
+\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
+\label{Table:ExtendedGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Contrast = Original - Extinction}  \\ 
+\hline
+$\beta_{\text{Diam}}$ &
 
-%\renewcommand{\thefigure}{B\arabic{figure}}
-%\setcounter{figure}{0}
+-0.03 [
+0.25,
+-0.3] \\
+
+$\beta_{\text{Clutch}}$ &
+
+0.07 [
+0.38,
+-0.26] \\
+
+$\beta_{\text{Pref}}$ &
+
+-0.25 [
+0.09,
+-0.64] \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+
+-0.05 [
+0.33,
+-0.43] \\
+
+$\gamma_{\text{Clutch:Clutch}}$ &
+
+-0.21 [
+0.26,
+-0.68] \\
+
+$\gamma_{\text{Pref:Pref}}$ &
+
+\textbf{
+-0.46 [
+-0.02,
+-1.07] }\\
+
+$\gamma_{\text{Diam:Clutch}}$ &
+
+0 [
+0.27,
+-0.29] \\
+
+$\gamma_{\text{Diam:Pref}}$ &
+
+0.25 [
+0.6,
+-0.05] \\
+
+$\gamma_{\text{Clutch:Pref}}$ &
+
+-0.18 [
+0.12,
+-0.52] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\begin{figure}
+\centering
+\includegraphics{analyses/selection_on_Platygaster.pdf}
+\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
+parasitoids on egg parasitoids (\emph{Platygaster} sp.). The bold line
+represents the average difference in the probability of observing the
+egg parasitoid (original - extinction of larval parastioids) as a
+function of gall midge oviposition preference. Thin lines represent
+bootstrapped replicates to show the uncertainty in selection. For
+clarity, we only display 100 bootstraps even though inferences are based
+on 1,000 replicates. The decrease in the probability of observing egg
+parasitoids at high gall-midge densities indicate that larval
+parasitoids impose nonlinear selection on egg parasitoids.}
+\end{figure}
+
+\section{Discussion}\label{discussion}
+
+We found that the extinction of larval parasitoids constrained
+phenotypic evolution in gall midges in two key ways. First, more traits
+contributed to the slope of the adaptive landscape in the absence of
+larval parasitoids, suggesting greater constraints on the trajectory of
+phenotypic evolution. Second, excluding larval parasitoids indirectly
+increased the number of genetic constraints, which could act to
+constrain the gall midge's adaptive potential in the face of novel
+selection pressures. Our experiment also revealed evidence of indirect
+selection pressures, suggesting that the loss of consumers may have
+complex effects on the trajectories of phenotypic evolution. Taken
+together, our study provides experimental evidence from the field that
+consumer extinctions may constrain the adaptive potential of remaining
+populations.
+
+All three phenotypic traits we examined experienced directional
+selection when we excluded larval parasitoids, indicating that there is
+an optimal phenotype that maximizes larval survival (i.e.~large chamber
+diameter, small clutch size, and avoidance of conspecifics). In
+contrast, we did not observe clear evidence of selective constraints on
+clutch size and oviposition preference in the original food web. This
+suggests that there are many optimal phenotypes (adaptive peaks), or in
+this case, a flat adaptive landscape where there are no fitness
+consequences for phenotypic change in these traits. This also implies
+that as selective constraints dampen in more complex food webs, then the
+trajectory of evolution becomes more determined by how genetic
+constraints interact with other evolutionary processes (e.g.~genetic
+drift, gene flow, and mutation). Interestingly, this aligns with
+\citet{Schluter1996}`s hypothesis that phenotypic evolution often
+follows 'genetic lines of least resistance'. \citet{Schluter1996} found
+support for this hypothesis from data on natural populations of several
+vertebrate species, including threespine sticklebacks, a few species of
+songbirds, and mice from the genus \emph{Peromyscus}. All of these
+species occupy intermediate trophic levels and are likely embedded in
+complex food webs, which is consistent with our suggestion that genetic
+constraints may have a stronger influence in more complex food webs.
+
+We also found evidence for more genetic constraints when we excluded
+larval parasitoids due to indirect effects of selection on the
+population's G-matrix. The ability of a population to adapt to novel
+selection pressures (evolvability) is largely governed by the structure
+of its G-matrix \citep{Hansen2008}. When selection favors genetic
+covariance between traits (positive or negative), this results in less
+autonomy of evolutionary responses to changing environments. Similarly,
+decreases in genetic variance constrain potential for the trait itself
+to evolve. Together, this suggests that consumer extinctions may
+decrease the evolutionary potential of populations by indirectly
+selecting for decreases in genetic variance in multiple traits and
+favoring trait integration. Current theory often assumes genetic
+variances and covariances remain constant over time rather than
+dynamically changing with the community context
+\citep{McPeek2017, Guimaraes2017}. Our empirical results highlight the
+need to explore the evolutionary consequences of not only direct effects
+of selection, but indirect effects on genetic constraints that are
+shaped by the community context.
+
+The generality of our results likely depends on the relative abundance
+and functional differences between consumers in a community. For
+example, if consumers do not differ from each other, then we do not
+expect changes in food-web structure to modify evolutionary constraints.
+Also, many consumers may be at too low of abundances to impose selection
+on their resources. Rank abundance curves \citep{Preston1948} and the
+disproportionate number of weak interactions in diverse communities
+\citep{Paine1992} support this notion. When consumers are abundant
+though, the effect of food-web structure will depend on whether
+different species impose conflicting selection pressures or select for
+distinct traits. For example, parisitoids and birds impose conflicting
+selection pressures on the size of galls induced by the fly
+\emph{Eurosta solidaginis} \citep{Weis1985, Abrahamson1997}. Recent
+studies in this system have shown that decreases in the relative
+abundance of birds, due to either small patch sizes \citep{Start2016} or
+proximity to urban areas \citep{Start2018} causes a shift from neutral
+to directional selection on gall size. On the other hand, different
+consumers may impose selection on different traits, favoring trait
+integration and increasing genetic constraints. Examples of this include
+strong genetic covariances in plant resistance to different insect
+herbivores \citep{Maddox1990, Wise2007, Wise2013}, although there are
+also examples where these covariances are weak
+\citep{Roche1997, Barbour2015}, or vary from year-to-year
+\citep{Johnson2007}. We suggest that gaining predictive insight to the
+evolutionary consequences of food-web disassembly requires an
+understanding of the mechanisms governing the assembly of trophic
+interactions.
+
+Our results suggest that the loss of consumers may not only directly
+affect connected species, but also result in indirect evolutionary
+effects. In our study, this indirect effect arises from egg parasitoids
+being released from intraguild predation when we excluded larval
+parasitoids. This release occurs more on trees with high larval
+densities, which could intensify selection on gall midge oviposition
+preference. A growing number of experiments over the past two decades
+have demonstrated the presence and potential importance of indirect
+evolutionary effects that emerge in a community context
+\citep{Pilson1996, Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, Start2019}.
+If indirect evolutionary effects are common \citep{Walsh2013}, then
+predicting evolutionary trajectories resulting from consumer extinctions
+will require evolutionary studies to explicitly account for the
+ecological networks that species are embedded in.
+
+There is a growing number of theoretical studies on adaptation to
+directional environmental change that incorporate species interactions
+\citep[e.g.][]{deMazancourt2008, Johansson2008, Norberg2012, Osmond2017PredatorsHelpPrey}.
+This work has given insight to the mechanisms by which pairwise
+interactions modify the adaptive potential of species. Our study hints
+at a novel mechanism, whereby more complex food webs flatten the
+adaptive landscape, thus facilitating future adaptation by allowing
+genetic and phenotypic variation to persist. This mechanism only emerges
+once we move beyond pairwise interactions to consider selection on
+multiple traits in a community context. However, a study on competition
+has highlighted that we may expect the opposite effect of species
+diversity in competitive communities \citep{deMazancourt2008}. This
+negative effect of species diversity on adaptation occurs because there
+is a greater chance that the optimal phenotype is already occupied by a
+competitor in a more diverse community. More work is needed to examine
+how the distribution of different interaction types affects adaptation
+to environmental change in species-rich communities.
+
+Our study has some limitations to consider when relating our findings to
+the effects of consumer extinctions on evolutionary constraints more
+generally. First, we removed other sources of mortality prior to our
+analyses. While this was necessary to avoid confounding estimates of
+selection with effects on phenotypic expression, we may be
+overestimating the effects of selection due to parasitoids. Second, our
+metrics of evolutionary constraints do not account for variation in the
+magnitude of selection pressures. While quantitative metrics are
+possible \citep{Hansen2008}, we felt they were not appropriate to apply
+here as our experimental removal of larval parasitoids results in a
+transient dynamic in the strength (but not direction) of selection. Such
+transient dynamics may be common in short-term experimental studies of
+natural selection, but they can be detected by using natural history
+information and dissecting the sources of selection (e.g.~quantifying
+selection surfaces and treatment effects on mean fitness) as we did
+here.
+
+Our study gives insight to how consumer extinctions alter evolutionary
+constraints on remaining populations. In particular, it hints at a
+potential insidious effect of local extinctions that compromises the
+robustness of remaining populations to future environmental change. Our
+work also highlights some key challenges for predicting phenotypic
+evolution in the face of global change. First, the simplification of
+ecological communities may actually reduce the predictability of
+phenotypic evolution, because knowledge is required of both selective
+and genetic constraints, rather than potentially just genetic
+constraints in more complex systems. Second, many theoretical models of
+eco-evolutionary dynamics focus on phenotypic change in a single trait,
+yet our results highlight that the number of traits under selection may
+change with the community context. Importantly, we found that different
+species/guilds imposed different selection pressures. Knowing these
+hidden selection pressures is critical for prediction, because the
+trajectory of evolution will depend on the nature of change in the
+community context. We expect that a continued integration of adaptive
+landscapes and ecological networks will enhance our ability to predict
+the evolutionary consequences of changes in ecological communities.
+
+\bibliography{references}
 

### 2019-05-21 analyses/reproduce_analyses.Rmd
update analyses folder.

@@
     toc: true
-#fontsize: 11pt
 ---
 
-This document presents a hybrid summary of the code used to reproduce these analyses.
-It is intended to give the reader a higher-level picture of the analyses, but does not display more minor code related to aesthetics.
-The underlying code for this document is provided in *reproduce_analyses.Rmd* and is available at https://github.com/mabarbour/complexity_selection.
+\
+
+This document presents a detailed overview of the analyses presented in the main text.
+It highlights the essential R code used to conduct these analyses, but does not display code related to table and plot aesthetics.
+The underlying code for this document is provided in **reproduce_analyses.Rmd** and is available at https://github.com/mabarbour/complexity_selection.
+
+\
 
@@
 
-Set number of bootstrap replicates for analyses and plots.
-
-```{r set parameters, echo=TRUE}
-n_boots_analysis <- 1000
-n_boots_plots <- 100
-```
-
 ```{r color palette}
@@
 cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7", "#000000", "#999999")
-complex_color <- cbPalette[6] 
-simple_color <- cbPalette[5] 
-treatment_colors <- c(complex_color, simple_color)
-```
+original_color <- cbPalette[6] 
+extinction_color <- cbPalette[5] 
+treatment_colors <- c(original_color, extinction_color)
+```
+
+## Summary of dataset
 
@@
   filter(Treatment == "Ectoparasitoid exclusion" & larval.ptoid < 1 | Treatment == "Control") %>% 
-  mutate(Foodweb = ifelse(Treatment=="Control","Complex","Simple"), # rename Treatment to match presentation in manuscript
+  mutate(Foodweb = ifelse(Treatment=="Control", "Original", "Extinction"), # rename Treatment to match presentation in manuscript
          gall_survival = as.numeric(ifelse(pupa > 0, 1, 0)),
@@
          sc.sqrt.Pref = as.numeric(scale(sqrt(oviposition.preference_individuals.per.100.shoots)))) 
-
-```
+```
+
+Below is a summary of the raw trait data for the gall midge, *Iteomyia salicisverruca*.
+Gall chamber diameter (**Diam**) is measured in mm, clutch size (**Clutch**) is measured as the number of chambers per gall, and oviposition preference (**Pref**) is measured as the number of chambers per 100 shoots on the plant.
+Note that each chamber contains one individual larva.
+
+```{r raw trait summary}
+raw_means <- gall_selection.df %>%
+  transmute(Diam = chamber.diameter_mm, 
+            Clutch = clutch.size_individuals, 
+            Pref = oviposition.preference_individuals.per.100.shoots) %>%
+  summarise_all(funs(mean))
+
+raw_SDs <- gall_selection.df %>%
+  transmute(Diam = chamber.diameter_mm, 
+            Clutch = clutch.size_individuals, 
+            Pref = oviposition.preference_individuals.per.100.shoots) %>%
+  summarise_all(funs(sd))
+
+data.frame(Trait = c("Diam", "Clutch", "Pref"),
+           Mean = round(c(raw_means$Diam, raw_means$Clutch, raw_means$Pref), 1),
+           SD = round(c(raw_SDs$Diam, raw_SDs$Clutch, raw_SDs$Pref), 1)) %>%
+  knitr::kable(., caption = "Mean and SD of phenotypic traits.")
+```
+
+Clutch size and oviposition preference were not normally distributed, so we log and square-root transformed these traits, respectively.
+
+```{r transformed trait summary}
+trans_means <- gall_selection.df %>%
+  transmute(log.Clutch = log(clutch.size_individuals), 
+            sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots)) %>%
+  summarise_all(funs(mean))
+
+trans_SDs <- gall_selection.df %>%
+  transmute(log.Clutch = log(clutch.size_individuals), 
+            sqrt.Pref = sqrt(oviposition.preference_individuals.per.100.shoots)) %>%
+  summarise_all(funs(sd))
+
+data.frame(Trait = c("log.Clutch", "sqrt.Pref"),
+           Mean = round(c(trans_means$log.Clutch, trans_means$sqrt.Pref), 1),
+           SD = round(c(trans_SDs$log.Clutch, trans_SDs$sqrt.Pref), 1)) %>%
+  knitr::kable(., caption = "Mean and SD of transformed phenotypic traits.")
+```
+
+For our subsequent analyses, we scaled each phenotypic trait (mean = 0, SD = 1) so that estimates of selection surfaces and gradients were comparable between traits and with traits in other studies.
+Below, we show a random subset of the data used in our subsequent analyses.
+
+```{r illustrate data used in analyses}
+set.seed(34)
+sample_n(gall_selection.df, size = 10) %>%
+  select(Foodweb, Genotype, Plant_Position, Gall_Number, Gall_ID, gall_survival, sc.Diam, sc.log.Clutch, sc.sqrt.Pref) %>%
+  mutate(sc.Diam = round(sc.Diam, 2), sc.log.Clutch = round(sc.log.Clutch, 2), sc.sqrt.Pref = round(sc.sqrt.Pref, 2)) %>%
+  knitr::kable(., caption = "Random sample of 10 data points used for our analyses.")
+```
+
+- **Foodweb** = food-web treatment (Original or Extinction)
+- **Genotype** = plant genotype ID (n = `r length(unique(gall_selection.df$Genotype))`)
+- **Plant_Position** = plant ID (n = `r length(unique(gall_selection.df$Plant_Position))`)
+- **Gall_Number** = multi-chambered gall ID (n = `r length(unique(gall_selection.df$Gall_Number))`)
+- **Gall_ID** = individual chamber ID (n = `r length(unique(gall_selection.df$Gall_ID))`)
+- **gall_survival** = measure of larval fitness (0 = dead; 1 = survived to pupation)
+- **sc.Diam** = scaled chamber diameter
+- **sc.log.Clutch** = scaled logarithm of clutch size
+- **sc.sqrt.Pref** = scaled square-root of oviposition preference
 
@@
 
-We used graphical checks to evaluate whether our transformations of trait values resulted in a multivariate normal distribution.
+We used graphical checks to evaluate whether our transformations resulted in traits with a multivariate normal distribution.
 The histograms below show that our transformations resulted in approximately normal distributions for each phenotypic trait.
-Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line, suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.
-
-\
 
@@
 
+Note also that in the multivariate quantile-quantile (Q-Q) plot, most points fall along the expected line, suggesting that our transformations provide a reasonable approximation of a multivariate normal distribution.
+
+```{r Multivariate_QQ, fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
+mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")  
+```
+
 \
 
-```{r Multivariate_QQ, fig.show = 'asis', fig.cap="Multivariate quantile-quantile (Q-Q) plot to assess deviations from multivariate normality (black line)."}
-mvn_multivariate_qq <- mvn(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref), multivariatePlot = "qq")  
-```
-
-\
-
-## Selection surfaces on gall midges: food-web treatments
-
-We write the model in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival.
-The resulting estimates and confidence intervals are useful for determining whether trait-fitness relationships differ from zero, but not whether they differ between food-web treatments.
-For the later, we calculate the differences between each food-web treatment from the bootstrapped samples.
+## Selection surfaces for the gall midge: food-web treatments
+
+We wrote the generalized linear mixed-effects model (GLMM) in a way that independently estimates the effect of food-web treatment, each trait, and all two-way and three-way statistical interactions, on larval survival.
+The resulting estimates and confidence intervals are useful for determining whether selection surfaces differ from zero, but not whether they differ between food-web treatments.
+In the main text, we discuss why we do not put much stock in differences in the magnitude of selection between food-web treatments (last paragraph of **Quantifying the Adaptive Landscape**), and therefore do not present these calculations.
 
@@
   data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-```
-
-\
-
-We used parametric bootstrapping to calculate 95% confidence intervals of trait-fitness relationships.
+  family = binomial(link = logit), 
+  control=glmerControl(optimizer = "bobyqa"))
+```
+
+We then used parametric bootstrapping (n = 1000) to calculate 95% confidence intervals of selection surfaces.
 
 ```{r Bootstrap food-web model, cache=TRUE, echo=TRUE}
-boot_foodweb_model <- bootMer(foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
-```
-
-\
-
-In order to reliably quantify linear trait-fitness relationships, we remove all higher-order terms from the model [Stinchcombe et al.
-2008](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x).
+n_boots_analysis <- 1000
+
+boot_foodweb_model <- bootMer(
+  x = foodweb_model, 
+  FUN = fixef, 
+  nsim = n_boots_analysis, 
+  parallel="multicore", ncpus=32, seed=34)
+```
+
+In order to reliably estimate linear relationships, we removed all higher-order terms from the model [(Stinchcombe et al.
+2008)](https://onlinelibrary.wiley.com/doi/full/10.1111/j.1558-5646.2008.00449.x),
 
@@
   data = gall_selection.df,
-  family = binomial(link = logit), control=glmerControl(optimizer = "bobyqa"))
-```
-
-\
-
-And refit using parametric bootstrapping.
+  family = binomial(link = logit), 
+  control=glmerControl(optimizer = "bobyqa"))
+```
+
+and refit using parametric bootstrapping.
 
 ```{r Bootstrap linear food-web model, cache=TRUE, echo=TRUE}
-boot_linear_foodweb_model <- bootMer(linear_foodweb_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
-```
-
-\
+boot_linear_foodweb_model <- bootMer(
+  x = linear_foodweb_model, 
+  FUN = fixef, 
+  nsim = n_boots_analysis, 
+  parallel="multicore", ncpus=32, seed=34)
+```
 
@@
 To estimate this potential bias, we subset our data to only include multi-chambered galls where there was variability in larval survival.
-We then fit a reduced model to estimate the bias in the logistic regression coefficient of chamber diameter in each food web.
+We then fit a reduced model to estimate the bias in selection surfaces of chamber diameter in each food-web treatment.
 
@@
 
-\
-
-```{r biased foodweb table, echo=FALSE}
+```{r biased foodweb table}
 # Print table
 biased_foodweb_confint %>%
-  select(term, estimate, conf.low, conf.high) %>%
-  filter(term %in% c("FoodwebComplex:sc.Diam","FoodwebSimple:sc.Diam")) %>%
-  mutate(estimate = round(estimate, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  #select(term, estimate, conf.low, conf.high) %>%
+  filter(term %in% c("FoodwebOriginal:sc.Diam","FoodwebExtinction:sc.Diam")) %>%
+  transmute(Term = term, Estimate = round(estimate, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
   knitr::kable(., caption = "Estimates of bias in selection surface of chamber diameter in each food-web treatment.")
@@
 
-\
-
-We gather regression coefficients from the full and reduced model to display trait-fitness relationships.
-For chamber diameter, we subtracted the coefficient due to bias to better approximate the trait-fitness relationship.
-<!--We also used the bootstrapped samples to calculate the differences in estimates between treatments (labelled **Diff**).-->
-
-```{r Food-web alpha coefficients}
+We then gathered bootstrapped estimates from both models, only retaining nonlinear terms from the full model,
+
+```{r Gather food-web alphas, echo=TRUE}
 foodweb_bind <- bind_cols(
   as_tibble(boot_linear_foodweb_model$t),
-  select(as_tibble(boot_foodweb_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+  # only retain nonlinear coefficients from full model
+  select(as_tibble(boot_foodweb_model$t), `FoodwebExtinction:I(sc.Diam^2)`:`FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) 
 )
-
-# Adjust coefficients with chamber diameter
+```
+
+and subtracted the bias in chamber diameter to better approximate its selection surface.
+
+```{r Adjust food-web alphas for chamber diameter, echo=TRUE}
 foodweb_adj_Diam <- foodweb_bind %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_foodweb_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_foodweb_model)["FoodwebSimple:sc.Diam"])
+  mutate(`FoodwebOriginal:sc.Diam` = `FoodwebOriginal:sc.Diam` - fixef(biased_foodweb_model)["FoodwebOriginal:sc.Diam"],
+         `FoodwebExtinction:sc.Diam` = `FoodwebExtinction:sc.Diam` - fixef(biased_foodweb_model)["FoodwebExtinction:sc.Diam"])
+```
+
+We then summarize these bootstrapped estimates and 95% confidence intervals as a table.
+
+```{r Tidy food-web alphas}
 
@@
 foodweb_alphas <- foodweb_adj_Diam %>%
-  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
-  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
-  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
-         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  mutate(`FoodwebExtinction:(Intercept)`=inverse_logit(FoodwebExtinction), `FoodwebOriginal:(Intercept)`=inverse_logit(FoodwebOriginal)) %>% # logit transform to make intercept interpretable as a probability
+  select(-FoodwebExtinction, -FoodwebOriginal) %>% # translated into (Intercept) terms
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebExtinction:(Intercept)` - `FoodwebOriginal:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
   select(type, term, estimate, value) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
   spread(estimate, value) %>%
@@
 
-\
-
 ```{r Table of food web coefficients}
@@
   filter(type != "Diff") %>%
-  select(Term = term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
-  mutate(Term = term, Treatment = type, Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
- knitr::kable(., caption = "Table of mean fitness and trait-fitness relationships in each food-web treatment.")
-```
-
-\
+  #select(Term = term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+  arrange(desc(Term)) %>%
+ knitr::kable(., caption = "Table of estimates for larval survival and selection surfaces in each food-web treatment.")
+```
 
@@
   filter(type == "Diff") %>%
-  select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
-  mutate(Estimate = round(mean, 3), `2.5%` = round(conf.low, 3), `97.5%` = round(conf.high, 3)) %>%
- knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces between food-web treatments.")
-```
-
-\
+  #select(Term = term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+ knitr::kable(., caption = "Table of differences in mean fitness and selection surfaces for gall midges between food-web treatments.")
+```
 
@@
 
-```{r Plot food-web coefficients, fig.cap="Plot of mean fitness differences between treatments and trait-fitness relationships.
-Asterisks denote significant differences (*P* < 0.05) between treatments."}
+```{r Plot food-web coefficients, fig.cap="Plot of larval survival and selection surfaces in each food-web treatment."}
+## Note that we do not focus on differences between treatments.
 
@@
 P_size <- 8
-legend_foodweb_labels <- c("Complex","Simple")
+legend_foodweb_labels <- c("Original","Extinction")
 point.size <- 3
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.8, x=1.5, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
@@
 
-# Plot linear trait-fitness relationaships
+# Plot linear trait-fitness relationships
 plot_foodweb_linear_coefs <- tidy_foodweb_alphas %>%
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
@@
 
-# Plot quadratic trait-fitness relationships
+# Plot quadratic selection surfaces
 plot_foodweb_quadratic_coefs <- tidy_foodweb_alphas %>%
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_foodweb_coefs) +
@@
 
-## Selection gradients on gall midges: food-web treatments
-
-Using the methods proposed by [Janzen and Stern, 1998](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we estimated selection gradients from our selection surfaces.
+## Selection gradients for the gall midge: food-web treatments
+
+Using the methods proposed by [Janzen and Stern (1998)](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x), we used our estimates of mean fitness and selection surfaces to calculate selection gradients.
 
@@
 # Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-foodweb_complex_predict <- predict(foodweb_model, newdata=filter(gall_selection.df, Foodweb=="Complex"), type="response")
-foodweb_complex_mean_brackets <- mean(foodweb_complex_predict * (1 - foodweb_complex_predict))
-foodweb_complex_mean_fitness <- mean(foodweb_complex_predict)
-
-foodweb_simple_predict <- predict(foodweb_model, newdata=filter(gall_selection.df, Foodweb=="Simple"), type="response")
-foodweb_simple_mean_brackets <- mean(foodweb_simple_predict * (1 - foodweb_simple_predict))
-foodweb_simple_mean_fitness <- mean(foodweb_simple_predict)
-
-foodweb_complex_gradient <- function(x) foodweb_complex_mean_brackets * x / foodweb_complex_mean_fitness
-foodweb_simple_gradient <- function(x) foodweb_simple_mean_brackets * x / foodweb_simple_mean_fitness
-
-foodweb_complex_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebComplex:")) %>%
-  transmute_all(funs(foodweb_complex_gradient))
-
-foodweb_simple_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebSimple:")) %>%
-  transmute_all(funs(foodweb_simple_gradient))
+foodweb_original_predict <- predict(foodweb_model, newdata=filter(gall_selection.df, Foodweb=="Original"), type="response")
+foodweb_original_mean_brackets <- mean(foodweb_original_predict * (1 - foodweb_original_predict))
+foodweb_original_mean_fitness <- mean(foodweb_original_predict)
+
+foodweb_extinction_predict <- predict(foodweb_model, newdata=filter(gall_selection.df, Foodweb=="Extinction"), type="response")
+foodweb_extinction_mean_brackets <- mean(foodweb_extinction_predict * (1 - foodweb_extinction_predict))
+foodweb_extinction_mean_fitness <- mean(foodweb_extinction_predict)
+
+foodweb_original_gradient <- function(x) foodweb_original_mean_brackets * x / foodweb_original_mean_fitness
+foodweb_extinction_gradient <- function(x) foodweb_extinction_mean_brackets * x / foodweb_extinction_mean_fitness
+
+foodweb_original_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebOriginal:")) %>%
+  transmute_all(funs(foodweb_original_gradient))
+
+foodweb_extinction_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebExtinction:")) %>%
+  transmute_all(funs(foodweb_extinction_gradient))
 ```
@@
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
-foodweb_grads <- bind_cols(foodweb_complex_raw_gradients, foodweb_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+foodweb_grads <- bind_cols(foodweb_original_raw_gradients, foodweb_extinction_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 
-\
-
-Reproduce numbers reported in **Table 1** of the manuscript.
+We then reproduce the estimates of selection gradients and 95% confidence intervals reported in **Table 1** of the main text.
 
@@
   filter(type != "Diff") %>%
-  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of selection gradients acting on gall traits in each food-web treatment.")
-```
-
-\
+  #select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+  arrange(desc(Term)) %>%
+knitr::kable(., caption = "Table of standardized selection gradients acting on gall midges in each food-web treatment.")
+```
 
@@
   filter(type == "Diff") %>%
-  select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  #select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
   knitr::kable(., caption = "Table of differences in selection gradients acting on gall traits between food-web treatment.")
@@
 
-\
-
 ```{r Curvature, include=FALSE}
-# Calculate curvatures for complex food web
-foodweb_complex_raw_curvs <- foodweb_complex_raw_gradients %>%
-  transmute(`FoodwebComplex:C.Diam` = `FoodwebComplex:I(sc.Diam^2)` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.Diam`,
-         `FoodwebComplex:C.Clutch` = `FoodwebComplex:I(sc.log.Clutch^2)` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.log.Clutch`,
-         `FoodwebComplex:C.Pref` = `FoodwebComplex:I(sc.sqrt.Pref^2)` - `FoodwebComplex:sc.sqrt.Pref`*`FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebComplex:C.Diam:Clutch` = `FoodwebComplex:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.log.Clutch`,
-         `FoodwebComplex:C.Diam:Pref` = `FoodwebComplex:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam`*`FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebComplex:C.Clutch:Pref` = `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch`*`FoodwebComplex:sc.sqrt.Pref`)
-
-# Calculate curvatures for simple food web
-foodweb_simple_raw_curvs <- foodweb_simple_raw_gradients %>%
-  transmute(`FoodwebSimple:C.Diam` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.Diam`,
-         `FoodwebSimple:C.Clutch` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.log.Clutch`,
-         `FoodwebSimple:C.Pref` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebSimple:sc.sqrt.Pref`*`FoodwebSimple:sc.sqrt.Pref`,
-         `FoodwebSimple:C.Diam:Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.log.Clutch`,
-         `FoodwebSimple:C.Diam:Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebSimple:sc.Diam`*`FoodwebSimple:sc.sqrt.Pref`,
-         `FoodwebSimple:C.Clutch:Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebSimple:sc.log.Clutch`*`FoodwebSimple:sc.sqrt.Pref`)
+# Calculate curvatures for original food web
+foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
+  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
+         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
+
+# Calculate curvatures for extinction food web
+foodweb_extinction_raw_curvs <- foodweb_extinction_raw_gradients %>%
+  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
+         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
 
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
-foodweb_curvs <- bind_cols(foodweb_complex_raw_curvs, foodweb_simple_raw_curvs) %>%
-  mutate(`FoodwebDiff:C.Diam` = `FoodwebSimple:C.Diam` - `FoodwebComplex:C.Diam`,
-         `FoodwebDiff:C.Clutch` = `FoodwebSimple:C.Clutch` - `FoodwebComplex:C.Clutch`,
-         `FoodwebDiff:C.Pref` = `FoodwebSimple:C.Pref` - `FoodwebComplex:C.Pref`,
-         `FoodwebDiff:C.Diam:Clutch` = `FoodwebSimple:C.Diam:Clutch` - `FoodwebComplex:C.Diam:Clutch`,
-         `FoodwebDiff:C.Diam:Pref` = `FoodwebSimple:C.Diam:Pref` - `FoodwebComplex:C.Diam:Pref`,
-         `FoodwebDiff:C.Clutch:Pref` = `FoodwebSimple:C.Clutch:Pref` - `FoodwebComplex:C.Clutch:Pref`) %>%
+foodweb_curvs <- bind_cols(foodweb_original_raw_curvs, foodweb_extinction_raw_curvs) %>%
+  mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
+         `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
+         `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
+         `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
+         `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
+         `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 
-\
-
 ```{r Table of food web curvatures, include=FALSE}
@@
   select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
 knitr::kable(., caption = "Table of curvatures on gall traits in each food-web treatment.")
 ```
-
-\
 
@@
   select(term, mean, conf.low, conf.high, P_cutoff) %>%
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
   knitr::kable(., caption = "Table of differences in curvatures on gall traits between food-web treatment.")
@@
 
-Now visualize the table output as a figure.
-
-```{r Plot food-web gradients, fig.cap="Plot of selection gradients in each food-web treatment. Asterisks denote significant differences (*P* < 0.05) between food-web treatments."}
+As before, we can visualize the table output as a figure.
+
+```{r Plot food-web gradients, fig.cap="Plot of standardized selection gradients acting on gall midges in each food-web treatment."}
 
@@
 P_size <- 8
-legend_foodweb_labels <- c("Complex","Simple")
+legend_foodweb_labels <- c("Original","Extinction")
 legend_foodweb_title <- "Food web"
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_foodweb_grads) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_foodweb_grads) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_foodweb_grads) +
@@
 
-plot_grid(y_title_foodweb_grads, plot_legend_foodweb_grads, ncol=2, rel_widths = c(0.05,1))
-
 figure_foodweb_grads <- plot_grid(y_title_foodweb_grads, plot_legend_foodweb_grads, ncol=2, rel_widths = c(0.05,1)) 
@@
 
-## Selection surfaces on gall midges: egg vs. larval parasitoids
-
-Our simple food-web treatment allows us to estimate the unique contribution of egg parasitoids to selection on *Iteomyia* traits.
-To estimate the unique contribution of larval parasitoids, we subset our data so that our complex food-web treatment only contained attack by larval parasitoids (and gall survival).
+## Selection surface for the gall midge: egg vs. larval parasitoids
+
+Our extinction food-web treatment allows us to estimate the unique contribution of egg parasitoids to selection on gall midge traits.
+To estimate the unique contribution of larval parasitoids, we subset our data so that our original food-web treatment only contained attack by larval parasitoids (and gall survival).
 We then fit the same models as previously, including one to estimate bias.
@@
 ```{r Egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
-# excludes cases of egg-parasitism from Complex food web
-egglarval_df <- filter(gall_selection.df, Foodweb == "Simple" | Foodweb == "Complex" & egg.ptoid < 1)
+# excludes cases of egg-parasitism from Original food web
+egglarval_df <- gall_selection.df %>%
+  filter(Foodweb == "Extinction" | Foodweb == "Original" & egg.ptoid < 1)
 
@@
 
-\
-
-Parametric bootstrapping to estimate confidence intervals.
+We then used parametric bootstrapping to estimate confidence intervals from the full model.
 
 ```{r Bootstrap egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
-boot_egglarval_model <- bootMer(egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
-```
-
-\
-
-Fit a reduced model to reliably estimate linear trait-fitness relationships.
+boot_egglarval_model <- bootMer(
+  x = egglarval_model, 
+  FUN = fixef, 
+  nsim = n_boots_analysis, 
+  parallel="multicore", ncpus=32, seed=34)
+```
+
+We also fit a reduced model to reliably estimate linear selection surfaces,
 
 ```{r Linear egg vs. larval ptoid model, cache=TRUE, echo=TRUE}
-linear_egglarval_model <- update(linear_foodweb_model, data=egglarval_df)
-```
-
-\
-
-Parametric bootstrapping to estimate confidence intervals.
+linear_egglarval_model <- update(linear_foodweb_model, data = egglarval_df)
+```
+
+and used parametric bootstrapping to estimate those confidence intervals.
 
 ```{r Bootstrap linear egg vs. larval model, cache=TRUE, echo=TRUE}
-boot_linear_egglarval_model <- bootMer(linear_egglarval_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
-```
-
-\
-
-Tidy selection surfaces imposed by egg and larval parasitoids from above models.
-
-```{r Egg vs. larval ptoid alpha coefficients}
+boot_linear_egglarval_model <- bootMer(
+  x = linear_egglarval_model, 
+  FUN = fixef, 
+  nsim = n_boots_analysis, 
+  parallel="multicore", ncpus=32, seed=34)
+```
+
+We then combined estimates from the linear model with those nonlinear terms from the full model,
+
+```{r Egg vs. larval ptoid alpha coefficients, echo=TRUE}
 egglarval_bind <- bind_cols(
   as_tibble(boot_linear_egglarval_model$t),
-  select(as_tibble(boot_egglarval_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+  # only retain nonlinear coefficients from full model
+  select(as_tibble(boot_egglarval_model$t), `FoodwebExtinction:I(sc.Diam^2)`:`FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) 
 )
 
-# Adjust coefficients with chamber diameter
+```
+
+and adjusted chamber diameter coefficients to reduce bias.
+
+```{r Adjust egg vs. larval alphas for chamber diameter, echo=TRUE}
 egglarval_adj_Diam <- as_tibble(boot_egglarval_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_egglarval_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_egglarval_model)["FoodwebSimple:sc.Diam"])
+  mutate(`FoodwebOriginal:sc.Diam` = `FoodwebOriginal:sc.Diam` - fixef(biased_egglarval_model)["FoodwebOriginal:sc.Diam"],
+         `FoodwebExtinction:sc.Diam` = `FoodwebExtinction:sc.Diam` - fixef(biased_egglarval_model)["FoodwebExtinction:sc.Diam"])
+```
+
+Below, we display the estimates and 95% confidence intervals of selection surfaces imposed by egg and larval parasitoids on gall midges as a table,
+
+```{r Egg vs. larval ptoid alphas for table}
 
@@
 egglarval_alphas <- egglarval_adj_Diam %>%
-  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
-  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
-  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
-         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  mutate(`FoodwebExtinction:(Intercept)`=inverse_logit(FoodwebExtinction), `FoodwebOriginal:(Intercept)`=inverse_logit(FoodwebOriginal)) %>% # logit transform to make intercept interpretable as a probability
+  select(-FoodwebExtinction, -FoodwebOriginal) %>% # translated into (Intercept) terms
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebExtinction:(Intercept)` - `FoodwebOriginal:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 
-\
-
 ```{r Table of egg vs. larval coefficients}
@@
   filter(type != "Diff") %>%
-  select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of gall selection surfaces imposed by egg and larval parasitoids.
-Note that type = Simple = Egg parasitoid and Complex = Larval parasitoid.")
-```
-
-\
+  #select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  transmute(Term = term, 
+            Type = ifelse(type == "Original", "Larval ptoid", "Egg ptoid"),
+            Estimate = round(mean, 2), 
+            `2.5%` = round(conf.low, 2), 
+            `97.5%` = round(conf.high, 2)) %>% 
+  arrange(desc(Term)) %>%
+  knitr::kable(., caption = "Table of gall survival and standardized selection surfaces imposed by egg and larval parasitoids.")
+```
 
@@
   filter(type == "Diff") %>%
-  select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%   knitr::kable(., caption = "Table of differences in gall trait-fitness relationships between egg and larval parasitoids.")
-```
-
-\
-
-See the table results in figure form.
-
-```{r Plot egglarval coefficients, fig.cap="Trait-fitness relationships for egg and larval parasitoids. Asterisks denote significant differences (*P* < 0.05) between parasitoid guilds."}
+  #select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  transmute(Term = term, 
+            Type = ifelse(type == "Original", "Larval ptoid", "Egg ptoid"),
+            Estimate = round(mean, 2), 
+            `2.5%` = round(conf.low, 2), 
+            `97.5%` = round(conf.high, 2)) %>%   knitr::kable(., caption = "Table of differences in gall selection surfaces between egg and larval parasitoids.")
+```
+
+and in figure form.
+
+```{r Plot egglarval coefficients, fig.cap="Plot of gall survival and standardized selection surfaces imposed by egg and larval parasitoids."}
 
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Larval survival", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
-  scale_x_discrete(name="Parasitoid", breaks=c("Complex","Simple"), labels=c("Larval","Egg")) +
+  scale_x_discrete(name="Parasitoid", breaks=c("Original","Extinction"), labels=c("Larval","Egg")) +
   facet_wrap(~coefficient_type) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_egglarval_coefs) +
@@
 
-# Plot quadratic trait-fitness relationships
+# Plot quadratic selection surfaces
 plot_egglarval_quadratic_coefs <- tidy_egglarval_alphas %>%
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_egglarval_coefs) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_egglarval_coefs, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Coefficient", limits=y_limits_egglarval_coefs) +
@@
 
-## Selection gradients on gall midges: egg vs. larval parasitoids
+## Selection gradients for the gall midge: egg vs. larval parasitoids
+
+We again use the method of [Janzen and Stern (1998)](https://onlinelibrary.wiley.com/doi/10.1111/j.1558-5646.1998.tb02237.x) to calculate selection gradients from our estimates of larval survival and selection surfaces,
 
@@
 # Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-egglarval_complex_predict <- predict(egglarval_model, newdata=filter(egglarval_df, Foodweb=="Complex"), type="response")
-egglarval_complex_mean_brackets <- mean(egglarval_complex_predict * (1 - egglarval_complex_predict))
-egglarval_complex_mean_fitness <- mean(egglarval_complex_predict)
-
-egglarval_simple_predict <- predict(egglarval_model, newdata=filter(egglarval_df, Foodweb=="Simple"), type="response")
-egglarval_simple_mean_brackets <- mean(egglarval_simple_predict * (1 - egglarval_simple_predict))
-egglarval_simple_mean_fitness <- mean(egglarval_simple_predict)
-
-egglarval_complex_gradient <- function(x) egglarval_complex_mean_brackets * x / egglarval_complex_mean_fitness
-egglarval_simple_gradient <- function(x) egglarval_simple_mean_brackets * x / egglarval_simple_mean_fitness
-
-egglarval_complex_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebComplex:")) %>%
-  transmute_all(funs(egglarval_complex_gradient))
-
-egglarval_simple_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebSimple:")) %>%
-  transmute_all(funs(egglarval_simple_gradient))
-```
+egglarval_original_predict <- predict(egglarval_model, newdata=filter(egglarval_df, Foodweb=="Original"), type="response")
+egglarval_original_mean_brackets <- mean(egglarval_original_predict * (1 - egglarval_original_predict))
+egglarval_original_mean_fitness <- mean(egglarval_original_predict)
+
+egglarval_extinction_predict <- predict(egglarval_model, newdata=filter(egglarval_df, Foodweb=="Extinction"), type="response")
+egglarval_extinction_mean_brackets <- mean(egglarval_extinction_predict * (1 - egglarval_extinction_predict))
+egglarval_extinction_mean_fitness <- mean(egglarval_extinction_predict)
+
+egglarval_original_gradient <- function(x) egglarval_original_mean_brackets * x / egglarval_original_mean_fitness
+egglarval_extinction_gradient <- function(x) egglarval_extinction_mean_brackets * x / egglarval_extinction_mean_fitness
+
+egglarval_original_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebOriginal:")) %>%
+  transmute_all(funs(egglarval_original_gradient))
+
+egglarval_extinction_raw_gradients <- select(egglarval_adj_Diam, starts_with("FoodwebExtinction:")) %>%
+  transmute_all(funs(egglarval_extinction_gradient))
+```
+
+and summarize our estimates and 95% confidence intervals as a table,
 
 ```{r Tidy egg vs. larval ptoid selection gradients}
+
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
-egglarval_grads <- bind_cols(egglarval_complex_raw_gradients, egglarval_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+egglarval_grads <- bind_cols(egglarval_original_raw_gradients, egglarval_extinction_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
@@
 
-\
-
 ```{r Egg vs. larval selection gradients}
@@
   filter(type != "Diff") %>%
-  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of selection gradients imposed by egg and larval parasitoids.")
-```
-
-\
+  #select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, 
+            Parasitoid = ifelse(type == "Original", "Larval ptoid", "Egg ptoid"), 
+            Estimate = round(mean, 2), 
+            `2.5%` = round(conf.low, 2), 
+            `97.5%` = round(conf.high, 2)) %>%
+  arrange(desc(Term)) %>%
+knitr::kable(., caption = "Table of selection gradients imposed by egg and larval parasitoids on gall midges.")
+```
 
@@
   filter(type == "Diff") %>%
-  select(term, gradient_type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
+  #select(term, gradient_type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, 
+            Parasitoid = ifelse(type == "Original", "Larval ptoid", "Egg ptoid"), 
+            Estimate = round(mean, 2), 
+            `2.5%` = round(conf.low, 2), 
+            `97.5%` = round(conf.high, 2)) %>%
   knitr::kable(., caption = "Table of differences in selection gradients imposed by egg and larval parasitoids.")
@@
 
-\
-
-See table results in figure form.
-
-```{r Plot egg vs. larval ptoid gradients, fig.cap="Selection gradients imposed by egg and larval parasitoids. Asterisks denote significant differences (*P* < 0.05) between parasitoid guilds."}
+and as a figure.
+
+```{r Plot egg vs. larval ptoid gradients, fig.cap="Plot of selection gradients imposed by egg and larval parasitoids on gall midges."}
+
+## Note: I'm not plotting asterisks that denote significant differences (*P* < 0.05) between parasitoid guilds.
 
@@
   filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction"))) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_egglarval_grads) +
@@
   filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction"))) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_egglarval_grads) +
@@
   filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction"))) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_egglarval_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_egglarval_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_egglarval_grads) +
@@
 
-\
-
-## Reproduce Figure 2 in manuscript.
-
-Use the fitted model to generate predicted estimates of mean fitness for changes in the mean trait value of a population.
-I restrict these predictions to +/- 1 SD because we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [Arnold et al., 2001](https://link.springer.com/article/10.1023/A:1013373907708).
+## Reproduce Figure 2 in main text
+
+We used the full model to generate predicted estimates of mean larval survival for changes in the mean trait value of the population.
+I restrict these predictions to +/- 1 SD because we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [(Arnold et al., 2001)](https://link.springer.com/article/10.1023/A:1013373907708).
 Other trait values are held constant at the mean phenotype (i.e.
 trait = 0).
-
-```{r Get Gall Diameter Relative Fitness Landscape, cache=TRUE}
+We then performed 100 bootstraps to illustrate the uncertainty in our estimates.
+
+```{r Get Gall Diameter Fitness Landscape, cache=TRUE, echo=TRUE}
+n_boots_plots <- 100
+
+## Gall diameter
 newdata_Diam <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
+  expand.grid(Foodweb = "Original", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Extinction", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = 0))
 
@@
   bootstraps=n_boots_plots)
-
-```
-
-```{r Get Clutch Size Fitness Landscape, cache=TRUE}
+```
+
+```{r Get Clutch Size Fitness Landscape, cache=TRUE, echo=TRUE}
+## Clutch size
 newdata_Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
+  expand.grid(Foodweb = "Original", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Extinction", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0))
 
@@
   bootstraps=n_boots_plots)
-
-```
-
-```{r Get Oviposition preference Fitness Landscape, cache=TRUE}
-
+```
+
+```{r Get Oviposition preference Fitness Landscape, cache=TRUE, echo=TRUE}
+## Oviposition preference
 newdata_Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Original", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Extinction", sc.Diam = 0, sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
 
+We then gathered these predictions to plot the adaptive landscape of gall midge traits in each food-web treatment.
+Note that we plot mean larval survival on a log-scale to reflect the mathematical definition of the adaptive landscape.
+
 ```{r Plot Univariate Landscapes}
+
 ## Create plots for each panel of Figure 2 in main text.
@@
   mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
-         Foodweb = factor(ifelse(Foodweb == "Complex", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
   ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
   gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
   ggplot(., aes(x=sc.sqrt.Pref, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
   gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>% 
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
   ggplot(., aes(x=sc.log.Clutch, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 
-```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in complex and simple food webs."}
+```{r Univariate-Fitness-Landscapes, fig.cap="Adaptive landscapes of gall midge phenotypes in the original food web and with the extinction of larval parasitoids."}
+
 ## Fit plots together to reproduce Figure 2.
@@
 AF_gradients
+
 save_plot(filename = "UV_landscapes.pdf", plot = AF_gradients, base_height = 5, base_width = 8.5)
@@
 
-\
+```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness.", include=FALSE}
 
 ## Replot gall midge adaptive landscapes in terms of relative fitness
-
-```{r Plot Univariate RF Landscapes, fig.cap="Adaptive landscapes of gall phenotypes in terms of relative fitness."}
 
@@
   gather(ID, absolute_fitness, -sc.log.Clutch, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>%
   group_by(Foodweb) %>%
@@
   gather(ID, absolute_fitness, -sc.sqrt.Pref, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>%
   group_by(Foodweb) %>%
@@
   gather(ID, absolute_fitness, -sc.Diam, -Foodweb) %>%
-  mutate(ID_group = ifelse(ID == "average", "average", "replicate")) %>%
+  mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>%
   group_by(Foodweb) %>%
@@
 
-\
-
-## Reproduce Figure 3 in manuscript
-
-Use the fitted model to generate predicted estimates of mean fitness for different phenotypic combinations.
-I restrict these predictions to +/- 1 SD because we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [Arnold et al., 2001](https://link.springer.com/article/10.1023/A:1013373907708).
-
-```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE}
-
+## Reproduce Figure 3 in main text
+
+As before, we use the full model to generate predicted estimates of mean larval survival, but do so now for different phenotypic combinations.
+
+```{r Get Clutch Size x Oviposition preference Landscape, cache=TRUE, echo=TRUE}
+## Clutch size x Oviposition preference
 newdata_Clutch.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Original", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Extinction", sc.Diam = 0, sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
   bootstraps=NULL)
-
-```
-
-```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE}
-
+```
+
+```{r Get Gall Diameter x Clutch Size Landscape, cache=TRUE, echo=TRUE}
+## Gall diameter x Clutch size
 newdata_Diam.Clutch <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
+  expand.grid(Foodweb = "Original", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref = 0),
+  expand.grid(Foodweb = "Extinction", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = seq(-1,1,length.out=1000), sc.sqrt.Pref=0))
 
@@
   bootstraps=NULL)
-
-```
-
-```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE}
-
+```
+
+```{r Get Gall Diameter x Oviposition preference Landscape, cache=TRUE, echo=TRUE}
+## Gall diameter by oviposition preference
 newdata_Diam.Pref <- bind_rows(
-  expand.grid(Foodweb = "Complex", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
-  expand.grid(Foodweb = "Simple", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
+  expand.grid(Foodweb = "Original", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)),
+  expand.grid(Foodweb = "Extinction", sc.Diam = seq(-1,1,length.out=1000), sc.log.Clutch = 0, sc.sqrt.Pref = seq(-1,1,length.out=1000)))
 
@@
   bootstraps=NULL)
-
-```
+```
+
+And gather these predictions to plot two-dimensional views of the adaptive landscape for each combination of phenotypic traits in each food-web treatment.
 
 ```{r Get plots of multivariate adaptive landscape}
+
 ## Create plots for each panel.
@@
 # Set contour breaks
-breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Complex","Simple")), type="response", re.form=~0)
-names(breaks) <- c("Complex","Simple")
-
-labels_2D <- list("Complex"="Original", "Simple"="Extinction")
+breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Original","Extinction")), type="response", re.form=~0)
+names(breaks) <- c("Original","Extinction")
+
+labels_2D <- list("Original"="Original", "Extinction"="Extinction")
 labeller_2D <- function(variable, value) {
@@
 # Size x Clutch
+RF_Diam.Clutch$absolute_fitness <- RF_Diam.Clutch$absolute_fitness %>%
+  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))
+
 AF_plot_Diam.Clutch <- RF_Diam.Clutch$absolute_fitness %>%
-  filter(Foodweb == "Complex") %>%
+  filter(Foodweb == "Original") %>%
   ggplot(., aes(x=sc.Diam, y=sc.log.Clutch)) +
   geom_raster(aes(fill=average)) +
-  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb, labeller = labeller_2D) +
+  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
+  facet_wrap(~Foodweb) + # , labeller = labeller_2D
   xlab("Gall diameter (SDs)") +
@@
 # Size x Preference
+RF_Diam.Pref$absolute_fitness <- RF_Diam.Pref$absolute_fitness %>% 
+  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))
+
 AF_plot_Diam.Pref <- RF_Diam.Pref$absolute_fitness %>% 
-  filter(Foodweb == "Complex") %>%
+  filter(Foodweb == "Original") %>%
   ggplot(., aes(x=sc.Diam, y=sc.sqrt.Pref)) +
   geom_raster(aes(fill=average)) +
-  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb, labeller = labeller_2D) +
+  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
+  facet_wrap(~Foodweb) + # , labeller = labeller_2D
   xlab("Chamber diameter (SDs)") +
@@
 # Clutch x Preference
+RF_Clutch.Pref$absolute_fitness <- RF_Clutch.Pref$absolute_fitness %>%
+  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))
+
 AF_plot_Clutch.Pref <- RF_Clutch.Pref$absolute_fitness %>%
-  filter(Foodweb == "Complex") %>%
+  filter(Foodweb == "Original") %>%
   ggplot(., aes(x=sc.sqrt.Pref, y=sc.log.Clutch)) +
   geom_raster(aes(fill=average)) +
-  stat_contour(aes(z = average), breaks = breaks["Complex"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Simple"), aes(z = average), breaks = breaks["Simple"], linetype = "dotted", color = "black") +
-  facet_wrap(~Foodweb, labeller = labeller_2D) +
+  stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
+  facet_wrap(~Foodweb) + # , labeller = labeller_2D
   xlab("Oviposition preference (SDs)") +
@@
 
-```{r Figure-Multivariate-Landscapes, fig.cap="Multivariate adaptive landscapes of gall phenotypes in complex and simple food webs.
+```{r Figure-Multivariate-Landscapes, fig.cap="Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
 Dotted lines denote fitness for the mean phenotype.
@@
 # Arrow data
-gradients_Diam.Clutch <- data.frame(Foodweb = c("Complex","Simple"),
+gradients_Diam.Clutch <- data.frame(Foodweb = c("Original","Extinction"),
                                     sc.Diam = c(0,0), 
                                     sc.log.Clutch = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
-
-gradients_Clutch.Pref <- data.frame(Foodweb = c("Complex","Simple"),
+                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean))
+
+gradients_Clutch.Pref <- data.frame(Foodweb = c("Original","Extinction"),
                                     sc.sqrt.Pref = c(0,0), 
                                     sc.log.Clutch = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.log.Clutch")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.log.Clutch")$mean))
-
-gradients_Diam.Pref <- data.frame(Foodweb = c("Complex","Simple"),
+                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean))
+
+gradients_Diam.Pref <- data.frame(Foodweb = c("Original","Extinction"),
                                     sc.Diam = c(0,0), 
                                     sc.sqrt.Pref = c(0,0), 
-                                    xend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.Diam")$mean,
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.Diam")$mean), 
-                                    yend = c(filter(tidy_foodweb_grads, type=="Complex", term=="sc.sqrt.Pref")$mean, 
-                                             filter(tidy_foodweb_grads, type=="Simple", term=="sc.sqrt.Pref")$mean))
+                                    xend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,
+                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean), 
+                                    yend = c(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean, 
+                                             filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean))
 
@@
 
+## Slope and curvature of the adaptive landscape of gall traits
+
+Below is the code used to get estimates for the slope ($\beta$) and curvature ($\gamma-\beta\beta^\text{T}$) of the adaptive landscape in each food-web treatment.
+If 95% confidence intervals of selection gradients overlap zero, then they were set to zero; otherwise, we retain the estimate.
+
+For the original food web, we create the matrix of $\beta$s,
+
+```{r Betas for original food web, echo=TRUE}
+# Get direction selection gradients from original food web
+original_betas_df <- tidy_foodweb_grads %>%
+  filter(type=="Original", gradient_type=="Directional") %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+
+# Relabel each term 
+original_betas_df$term <- factor(
+  original_betas_df$term, 
+  levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), 
+  labels=c("Diam","Clutch","Pref"), order=TRUE)
+
+rownames(original_betas_df) <- original_betas_df$term
+
+# Create empty matrix
+original_betas <- matrix(nrow = 3, 
+                         ncol = 1, 
+                         dimnames = list(c("Diam","Clutch","Pref"), c("")))
+
+# Populate the empty matrix with ifelse() statements
+# If the 95% CI does not overlap zero, 
+# then the "low" multiplied by the "high" interval is always greater than zero.
+# If that's true, then I retain the estimate.
+# If it's false, then I set the estimate to zero.
+original_betas["Diam",] <- ifelse(
+  original_betas_df["Diam","low"]*original_betas_df["Diam","high"] > 0, 
+  original_betas_df["Diam","gradient"], 0)
+
+original_betas["Clutch",] <- ifelse(
+  original_betas_df["Clutch","low"]*original_betas_df["Clutch","high"] > 0, 
+  original_betas_df["Clutch","gradient"], 0)
+
+original_betas["Pref",] <- ifelse(
+  original_betas_df["Pref","low"]*original_betas_df["Pref","high"] > 0,
+  original_betas_df["Pref","gradient"], 0)
+
+original_betas <- round(original_betas, 2)
+```
+
+and the matrix of $\gamma$s.
+
+```{r Gammas for original food web, echo=TRUE}
+# Get nonlinear selection gradients from original food web
+original_gammas_df <- tidy_foodweb_grads %>%
+  filter(type=="Original", gradient_type %in% c("Quadratic","Correlational")) %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+
+# Relabel each term
+original_gammas_df$term <- factor(
+  original_gammas_df$term, 
+  levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
+           "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), 
+  labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+
+rownames(original_gammas_df) <- original_gammas_df$term
+
+# Create empty matrix  
+original_gammas <- matrix(nrow = 3, 
+                          ncol = 3, 
+                          dimnames = list(c("Diam","Clutch","Pref"), c("Diam","Clutch","Pref")))
+
+# Populate the empty matrix with ifelse() statements 
+# to determine if 95% CI overlaps with zero or not (see previous logic)
+original_gammas["Diam","Diam"] <- ifelse(
+  original_gammas_df["Diam^2","low"]*original_gammas_df["Diam^2","high"] > 0,
+  original_gammas_df["Diam^2","gradient"], 0)
+
+original_gammas["Clutch","Clutch"] <- ifelse(
+  original_gammas_df["Clutch^2","low"]*original_gammas_df["Clutch^2","high"] > 0, 
+  original_gammas_df["Clutch^2","gradient"], 0)
+
+original_gammas["Pref","Pref"] <- ifelse(
+  original_gammas_df["Pref^2","low"]*original_gammas_df["Pref^2","high"] > 0, 
+  original_gammas_df["Pref^2","gradient"], 0)
+
+original_gammas["Diam","Clutch"] <- ifelse(
+  original_gammas_df["Diam:Clutch","low"]*original_gammas_df["Diam:Clutch","high"] > 0,
+  original_gammas_df["Diam:Clutch","gradient"], 0)
+
+original_gammas["Clutch","Diam"] <- original_gammas["Diam","Clutch"]
+
+original_gammas["Diam","Pref"] <- ifelse(
+  original_gammas_df["Diam:Pref","low"]*original_gammas_df["Diam:Pref","high"] > 0,
+  original_gammas_df["Diam:Pref","gradient"], 0)
+
+original_gammas["Pref","Diam"] <- original_gammas["Diam","Pref"]
+
+original_gammas["Clutch","Pref"] <- ifelse(
+  original_gammas_df["Clutch:Pref","low"]*original_gammas_df["Clutch:Pref","high"] > 0,
+  original_gammas_df["Clutch:Pref","gradient"], 0)
+
+original_gammas["Pref","Clutch"] <- original_gammas["Clutch","Pref"]
+
+original_gammas <- round(original_gammas, 2)
+```
+
+Likewise for the extinction web, we create the matrix of $\beta$s,
+
+```{r Betas for extinction food web, echo=TRUE}
+# Get direction selection gradients from extinction food web
+extinction_betas_df <- tidy_foodweb_grads %>%
+  filter(type=="Extinction", gradient_type=="Directional") %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+
+# Relabel each term 
+extinction_betas_df$term <- factor(
+  extinction_betas_df$term, 
+  levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), 
+  labels=c("Diam","Clutch","Pref"), order=TRUE)
+
+rownames(extinction_betas_df) <- extinction_betas_df$term
+
+# Create empty matrix
+extinction_betas <- matrix(nrow = 3, 
+                           ncol = 1, 
+                           dimnames = list(c("Diam","Clutch","Pref"), c("")))
+
+# Populate the empty matrix with ifelse() statements 
+# to determine if 95% CI overlaps with zero or not (see previous logic)
+extinction_betas["Diam",] <- ifelse(
+  extinction_betas_df["Diam","low"]*extinction_betas_df["Diam","high"] > 0,
+  extinction_betas_df["Diam","gradient"], 0)
+
+extinction_betas["Clutch",] <- ifelse(
+  extinction_betas_df["Clutch","low"]*extinction_betas_df["Clutch","high"] > 0,
+  extinction_betas_df["Clutch","gradient"], 0)
+
+extinction_betas["Pref",] <- ifelse(
+  extinction_betas_df["Pref","low"]*extinction_betas_df["Pref","high"] > 0,
+  extinction_betas_df["Pref","gradient"], 0)
+
+extinction_betas <- round(extinction_betas, 2)
+```
+
+and $\gamma$s.
+
+```{r Gammas for extinction food web, echo=TRUE}
+# Get nonlinear selection gradients from extinction food web
+extinction_gammas_df <- tidy_foodweb_grads %>%
+  filter(type=="Extinction", gradient_type %in% c("Quadratic","Correlational")) %>%
+  select(term, gradient=mean, low=conf.low, high=conf.high)
+
+# Relabel each term
+extinction_gammas_df$term <- factor(
+  extinction_gammas_df$term, 
+  levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)",
+           "sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"),
+  labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
+
+rownames(extinction_gammas_df) <- extinction_gammas_df$term
+
+# Create empty matrix
+extinction_gammas <- matrix(nrow = 3, 
+                            ncol = 3, 
+                            dimnames = list(c("Diam","Clutch","Pref"), c("Diam","Clutch","Pref")))
+
+# Populate the empty matrix with ifelse() statements 
+# to determine if 95% CI overlaps with zero or not (see previous logic)
+extinction_gammas["Diam","Diam"] <- ifelse(
+  extinction_gammas_df["Diam^2","low"]*extinction_gammas_df["Diam^2","high"] > 0,
+  extinction_gammas_df["Diam^2","gradient"], 0)
+
+extinction_gammas["Clutch","Clutch"] <- ifelse(
+  extinction_gammas_df["Clutch^2","low"]*extinction_gammas_df["Clutch^2","high"] > 0,
+  extinction_gammas_df["Clutch^2","gradient"], 0)
+
+extinction_gammas["Pref","Pref"] <- ifelse(
+  extinction_gammas_df["Pref^2","low"]*extinction_gammas_df["Pref^2","high"] > 0,
+  extinction_gammas_df["Pref^2","gradient"], 0)
+
+extinction_gammas["Diam","Clutch"] <- ifelse(
+  extinction_gammas_df["Diam:Clutch","low"]*extinction_gammas_df["Diam:Clutch","high"] > 0,
+  extinction_gammas_df["Diam:Clutch","gradient"], 0)
+
+extinction_gammas["Clutch","Diam"] <- extinction_gammas["Diam","Clutch"]
+
+extinction_gammas["Diam","Pref"] <- ifelse(
+  extinction_gammas_df["Diam:Pref","low"]*extinction_gammas_df["Diam:Pref","high"] > 0,
+  extinction_gammas_df["Diam:Pref","gradient"], 0)
+
+extinction_gammas["Pref","Diam"] <- extinction_gammas["Diam","Pref"]
+
+extinction_gammas["Clutch","Pref"] <- ifelse(
+  extinction_gammas_df["Clutch:Pref","low"]*extinction_gammas_df["Clutch:Pref","high"] > 0,
+  extinction_gammas_df["Clutch:Pref","gradient"], 0)
+
+extinction_gammas["Pref","Clutch"] <- extinction_gammas["Clutch","Pref"]
+
+extinction_gammas <- round(extinction_gammas, 2)
+```
+
+After all of this, we can easily calculate the curvature matrix ($\gamma-\beta\beta^\text{T}$) in each food-web treatment.
+
+```{r Calculate curvature in each food-web treatment, echo=TRUE}
+original_curvature <- original_gammas - original_betas %*% t(original_betas)
+
+extinction_curvature <- extinction_gammas - extinction_betas %*% t(extinction_betas)
+```
+
+I then used these estimates to populate the curvature matrices presented in the **Results** of the main text, but also reproduce them here:
+
+$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Original}} = \begin{pmatrix} 
+`r round(original_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(original_curvature["Clutch","Diam"],2)` & `r round(original_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(original_curvature["Pref","Diam"],2)` & `r round(original_curvature["Pref","Clutch"],2)` & `r round(original_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Extinction}} = \begin{pmatrix} 
+`r round(extinction_curvature["Diam","Diam"],2)` &  &  \\  
+`r round(extinction_curvature["Clutch","Diam"],2)` & `r round(extinction_curvature["Clutch","Clutch"],2)` &  \\  
+`r round(extinction_curvature["Pref","Diam"],2)` & `r round(extinction_curvature["Pref","Clutch"],2)` & `r round(extinction_curvature["Pref","Pref"],2)` \end{pmatrix}$$
+
 \
 
-## Slope and curvature of the adaptive landscape of gall traits
-
-Below is the code I used to get estimates for the slope and curvature of the adaptive landscape in each food-web treatment.
-If 95% confidence intervals of selection gradients overlap zero, then they are set to zero; otherwise, I retain the mean estimate.
-
-```{r Slope and Curvature of the Adaptive Landscape}
-
-# Create beta-matrix for complex food-web treatment
-complex_betas_df <- tidy_foodweb_grads %>%
-  filter(type=="Complex", gradient_type=="Directional") %>%
-  select(term, gradient=mean, low=conf.low, high=conf.high)
-complex_betas_df$term <- factor(complex_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
-rownames(complex_betas_df) <- complex_betas_df$term
-
-complex_betas <- matrix(nrow = 3, ncol = 1, dimnames = list(c("Diam","Clutch","Pref"), c("")))
-complex_betas["Diam",] <- ifelse(complex_betas_df["Diam","low"]*complex_betas_df["Diam","high"] > 0, 
-                                        complex_betas_df["Diam","gradient"], 0)
-complex_betas["Clutch",] <- ifelse(complex_betas_df["Clutch","low"]*complex_betas_df["Clutch","high"] > 0,
-                                            complex_betas_df["Clutch","gradient"], 0)
-complex_betas["Pref",] <- ifelse(complex_betas_df["Pref","low"]*complex_betas_df["Pref","high"] > 0,
-                                        complex_betas_df["Pref","gradient"], 0)
-complex_betas <- round(complex_betas, 2)
-
-# Create gamma-matrix for complex food-web treatment
-complex_gammas_df <- tidy_foodweb_grads %>%
-  filter(type=="Complex", gradient_type %in% c("Quadratic","Correlational")) %>%
-  select(term, gradient=mean, low=conf.low, high=conf.high)
-complex_gammas_df$term <- factor(complex_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
-rownames(complex_gammas_df) <- complex_gammas_df$term
-
-complex_gammas <- matrix(nrow = 3, ncol = 3, dimnames = list(c("Diam","Clutch","Pref"), c("Diam","Clutch","Pref")))
-complex_gammas["Diam","Diam"] <- ifelse(complex_gammas_df["Diam^2","low"]*complex_gammas_df["Diam^2","high"] > 0, 
-                                        complex_gammas_df["Diam^2","gradient"], 0)
-complex_gammas["Clutch","Clutch"] <- ifelse(complex_gammas_df["Clutch^2","low"]*complex_gammas_df["Clutch^2","high"] > 0,
-                                            complex_gammas_df["Clutch^2","gradient"], 0)
-complex_gammas["Pref","Pref"] <- ifelse(complex_gammas_df["Pref^2","low"]*complex_gammas_df["Pref^2","high"] > 0,
-                                        complex_gammas_df["Pref^2","gradient"], 0)
-complex_gammas["Diam","Clutch"] <- ifelse(complex_gammas_df["Diam:Clutch","low"]*complex_gammas_df["Diam:Clutch","high"] > 0,
-                                          complex_gammas_df["Diam:Clutch","gradient"], 0)
-complex_gammas["Clutch","Diam"] <- complex_gammas["Diam","Clutch"]
-complex_gammas["Diam","Pref"] <- ifelse(complex_gammas_df["Diam:Pref","low"]*complex_gammas_df["Diam:Pref","high"] > 0,
-                                            complex_gammas_df["Diam:Pref","gradient"], 0)
-complex_gammas["Pref","Diam"] <- complex_gammas["Diam","Pref"]
-complex_gammas["Clutch","Pref"] <- ifelse(complex_gammas_df["Clutch:Pref","low"]*complex_gammas_df["Clutch:Pref","high"] > 0, 
-                                        complex_gammas_df["Clutch:Pref","gradient"], 0)
-complex_gammas["Pref","Clutch"] <- complex_gammas["Clutch","Pref"]
-complex_gammas <- round(complex_gammas, 2)
-
-# Create matrix of Betas in simple food-web treatment
-simple_betas_df <- tidy_foodweb_grads %>%
-  filter(type=="Simple", gradient_type=="Directional") %>%
-  select(term, gradient=mean, low=conf.low, high=conf.high)
-simple_betas_df$term <- factor(simple_betas_df$term, levels=c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref"), labels=c("Diam","Clutch","Pref"), order=TRUE)
-rownames(simple_betas_df) <- simple_betas_df$term
-
-simple_betas <- matrix(nrow = 3, ncol = 1, dimnames = list(c("Diam","Clutch","Pref"), c("")))
-simple_betas["Diam",] <- ifelse(simple_betas_df["Diam","low"]*simple_betas_df["Diam","high"] > 0, 
-                                        simple_betas_df["Diam","gradient"], 0)
-simple_betas["Clutch",] <- ifelse(simple_betas_df["Clutch","low"]*simple_betas_df["Clutch","high"] > 0,
-                                            simple_betas_df["Clutch","gradient"], 0)
-simple_betas["Pref",] <- ifelse(simple_betas_df["Pref","low"]*simple_betas_df["Pref","high"] > 0,
-                                        simple_betas_df["Pref","gradient"], 0)
-simple_betas <- round(simple_betas, 2)
-
-# Create gamma-matrix for simple food-web treatment
-simple_gammas_df <- tidy_foodweb_grads %>%
-  filter(type=="Simple", gradient_type %in% c("Quadratic","Correlational")) %>%
-  select(term, gradient=mean, low=conf.low, high=conf.high)
-simple_gammas_df$term <- factor(simple_gammas_df$term, levels=c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)","sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref"), labels=c("Diam^2","Clutch^2","Pref^2","Diam:Clutch","Diam:Pref","Clutch:Pref"), order=TRUE)
-rownames(simple_gammas_df) <- simple_gammas_df$term
-
-simple_gammas <- matrix(nrow = 3, ncol = 3, dimnames = list(c("Diam","Clutch","Pref"), c("Diam","Clutch","Pref")))
-simple_gammas["Diam","Diam"] <- ifelse(simple_gammas_df["Diam^2","low"]*simple_gammas_df["Diam^2","high"] > 0, 
-                                        simple_gammas_df["Diam^2","gradient"], 0)
-simple_gammas["Clutch","Clutch"] <- ifelse(simple_gammas_df["Clutch^2","low"]*simple_gammas_df["Clutch^2","high"] > 0,
-                                            simple_gammas_df["Clutch^2","gradient"], 0)
-simple_gammas["Pref","Pref"] <- ifelse(simple_gammas_df["Pref^2","low"]*simple_gammas_df["Pref^2","high"] > 0,
-                                        simple_gammas_df["Pref^2","gradient"], 0)
-simple_gammas["Diam","Clutch"] <- ifelse(simple_gammas_df["Diam:Clutch","low"]*simple_gammas_df["Diam:Clutch","high"] > 0,
-                                          simple_gammas_df["Diam:Clutch","gradient"], 0)
-simple_gammas["Clutch","Diam"] <- simple_gammas["Diam","Clutch"]
-simple_gammas["Diam","Pref"] <- ifelse(simple_gammas_df["Diam:Pref","low"]*simple_gammas_df["Diam:Pref","high"] > 0,
-                                            simple_gammas_df["Diam:Pref","gradient"], 0)
-simple_gammas["Pref","Diam"] <- simple_gammas["Diam","Pref"]
-simple_gammas["Clutch","Pref"] <- ifelse(simple_gammas_df["Clutch:Pref","low"]*simple_gammas_df["Clutch:Pref","high"] > 0, 
-                                        simple_gammas_df["Clutch:Pref","gradient"], 0)
-simple_gammas["Pref","Clutch"] <- simple_gammas["Clutch","Pref"]
-simple_gammas <- round(simple_gammas, 2)
-
-# Calculate Curvature of the Fitness landscape
-complex_curvature <- complex_gammas - complex_betas %*% t(complex_betas)
-simple_curvature <- simple_gammas - simple_betas %*% t(simple_betas)
-```
-
-I use these estimates to populate the curvature matrices presented in the **Results** of the main text. I reproduce these estimates here for clarity:
-
-$$\textbf{C} = \begin{pmatrix} C_{\text{Diam:Diam}}&& \\ C_{\text{Clutch:Diam}} & C_{\text{Clutch:Clutch}} & \\ C_{\text{Pref:Diam}} & C_{\text{Pref:Clutch}} & C_{\text{Pref:Pref}} \end{pmatrix}$$
-
-$$\textbf{C}_{\text{Complex}} = \begin{pmatrix} 
-`r round(complex_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(complex_curvature["Clutch","Diam"],2)` & `r round(complex_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(complex_curvature["Pref","Diam"],2)` & `r round(complex_curvature["Pref","Clutch"],2)` & `r round(complex_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-$$\textbf{C}_{\text{Simple}} = \begin{pmatrix} 
-`r round(simple_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(simple_curvature["Clutch","Diam"],2)` & `r round(simple_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(simple_curvature["Pref","Diam"],2)` & `r round(simple_curvature["Pref","Clutch"],2)` & `r round(simple_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-\
-
-## Selection surfaces of the egg parasitoid *Platygaster* sp.
+## Selection surfaces for the egg parasitoid
+
+We fit the same models as before, except presence/absence of an egg parasitoid is the response variable.
+Importantly, we can only estimate selection by calculating the difference in probability of observing egg parasitoids between food-web treatments.
+We do this by calculating the difference in bootstrapped estimates between treatments after fitting our models.
 
@@
 We do not change the name of the response variable to make clear that we are using the same statistical models as for Iteomyia.
-eggegg_df <- mutate(gall_selection.df, gall_survival = ifelse(egg.ptoid==1,1,0))
+eggegg_df <- gall_selection.df %>%
+  mutate(gall_survival = ifelse(egg.ptoid == 1, 1, 0))
 
@@
 
-\
-
-Use parametric bootstrapping to calculating 95% confidence intervals of selection surfaces.
-
-```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, include=FALSE}
-boot_eggegg_model <- bootMer(eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
-```
-
-\
-
-Remove all higher-order terms to quantify linear selection surfaces.
-
-```{r Linear egg vs. egg ptoid model, cache=TRUE}
+We used parametric bootstrapping to calculate 95% confidence intervals of selection surfaces.
+
+```{r Bootstrap egg vs. egg ptoid model, cache=TRUE, echo=TRUE}
+boot_eggegg_model <- bootMer(
+  x = eggegg_model, 
+  FUN = fixef, 
+  nsim = n_boots_analysis, 
+  parallel="multicore", ncpus=32, seed=34)
+```
+
+As before, we removed all higher-order terms to estimate linear relationships,
+
+```{r Linear egg vs. egg ptoid model, cache=TRUE, echo=TRUE}
 linear_eggegg_model <- update(linear_foodweb_model, data=eggegg_df)
@@
 
-\
-
-And refit using parametric bootstrapping.
-
-```{r Bootstrap linear egg vs. egg model, cache=TRUE}
-boot_linear_eggegg_model <- bootMer(linear_eggegg_model, FUN = fixef, nsim=n_boots_analysis, parallel="multicore", ncpus=32, seed=34)
-```
-
-\
-
-Gather regression coefficients to display selection surfaces.
-
-```{r Egg vs. egg ptoid alpha coefficients}
+and refit using parametric bootstrapping.
+
+```{r Bootstrap linear egg vs. egg model, cache=TRUE, echo=TRUE}
+boot_linear_eggegg_model <- bootMer(
+  x = linear_eggegg_model, 
+  FUN = fixef, 
+  nsim = n_boots_analysis, 
+  parallel="multicore", ncpus=32, seed=34)
+```
+
+We then gather bootstrapped estimates from the full (nonlinear terms only) and reduced models,
+
+```{r gather egg vs. egg ptoid alphas, echo=TRUE}
 eggegg_bind <- bind_cols(
   as_tibble(boot_linear_eggegg_model$t),
-  select(as_tibble(boot_eggegg_model$t), `FoodwebComplex:I(sc.Diam^2)`:`FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref`) # only retain nonlinear coefficients from full model
+  # only retain nonlinear coefficients from full model
+  select(as_tibble(boot_eggegg_model$t), `FoodwebExtinction:I(sc.Diam^2)`:`FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) 
 )
-
-# Adjust coefficients with chamber diameter
+```
+
+and adjusted for biased coefficients in chamber diameter.
+
+```{r Adjust egg vs. egg ptoid alphas for chamber diameter, echo=TRUE}
 eggegg_adj_Diam <- as_tibble(boot_eggegg_model$t) %>%
-  mutate(`FoodwebComplex:sc.Diam` = `FoodwebComplex:sc.Diam` - fixef(biased_eggegg_model)["FoodwebComplex:sc.Diam"],
-         `FoodwebSimple:sc.Diam` = `FoodwebSimple:sc.Diam` - fixef(biased_eggegg_model)["FoodwebSimple:sc.Diam"])
-
-# Calculate differences between food-web treatments, then estimate means and confidence intervals
+  mutate(`FoodwebOriginal:sc.Diam` = `FoodwebOriginal:sc.Diam` - fixef(biased_eggegg_model)["FoodwebOriginal:sc.Diam"],
+         `FoodwebExtinction:sc.Diam` = `FoodwebExtinction:sc.Diam` - fixef(biased_eggegg_model)["FoodwebExtinction:sc.Diam"])
+```
+
+Finally, we calculate the differences between food-web treatments in order to estimate selection imposed by larval parasitoids.
+
+```{r Egg vs. egg ptoid alpha differences, echo=TRUE}
 eggegg_alphas <- eggegg_adj_Diam %>%
-  mutate(`FoodwebSimple:(Intercept)`=inverse_logit(FoodwebSimple), `FoodwebComplex:(Intercept)`=inverse_logit(FoodwebComplex)) %>% # logit transform to make intercept interpretable as a probability
-  select(-FoodwebSimple, -FoodwebComplex) %>% # translated into (Intercept) terms
-  mutate(`FoodwebDiff:(Intercept)` = `FoodwebSimple:(Intercept)` - `FoodwebComplex:(Intercept)`,
-         `FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  # logit transform to make intercept interpretable as a probability of survival
+  mutate(`FoodwebExtinction:(Intercept)` = inverse_logit(FoodwebExtinction),
+         `FoodwebOriginal:(Intercept)` = inverse_logit(FoodwebOriginal)) %>% 
+  select(-FoodwebExtinction, -FoodwebOriginal) %>% # translated into (Intercept) terms
+  # calculate differences
+  mutate(`FoodwebDiff:(Intercept)` = `FoodwebOriginal:(Intercept)` - `FoodwebExtinction:(Intercept)`,
+         `FoodwebDiff:sc.Diam` = `FoodwebOriginal:sc.Diam` - `FoodwebExtinction:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebOriginal:sc.log.Clutch` - `FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebOriginal:sc.sqrt.Pref` - `FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebOriginal:I(sc.Diam^2)` - `FoodwebExtinction:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebOriginal:I(sc.log.Clutch^2)` - `FoodwebExtinction:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - `FoodwebExtinction:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - `FoodwebExtinction:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - `FoodwebExtinction:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref`) %>%
   summarise_all(funs(mean, conf.high, conf.low))
+```
+
+Below, we display the estimates and 95% confidence intervals in selection surfaces for egg parasitoids as a table,
+
+```{r Tidy egg vs. egg ptoid alpha coefficients}
 
@@
 
-\
-
-```{r Egg ptoid coefficients in each food-web treatment}
+```{r Egg ptoid coefficients in each food-web treatment, include=FALSE}
 tidy_eggegg_alphas %>%
   filter(type != "Diff") %>%
-  select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of trait-fitness relationships of extended phenotype of egg parasitoids in complex and simple food webs.")
-```
-
-\
-
-```{r Table of differences in egg parasitoid coefficients between food-web treatments, include=FALSE}
+  #select(term, type, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+knitr::kable(., caption = "Table of selection surfaces for egg parasitoids in original and extinction food webs.")
+```
+
+```{r Table of differences in egg parasitoid coefficients between food-web treatments}
 tidy_eggegg_alphas %>%
   filter(type == "Diff") %>%
-  select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-  knitr::kable(., caption = "Table of differences in trait-fitness relationships of egg parasitoids between food-web treatment.")
-```
-
-\
-
-Visualize tables in figure form.
-
-```{r Plot egg vs.
-egg ptoid coefficients, fig.cap="Trait-fitness relationships of egg parasitoid's extended phenotype in complex and simple food webs.
-Asterisks denote significant differences (*P* < 0.05) between food-web treatments."}
+  #select(term, mean, conf.low, conf.high) %>% # coefficient_type, P_cutoff
+  transmute(Term = term, `Original - Extinction` = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of standardized selection surfaces acting on egg parasitoids (*Platygaster* sp.).")
+```
+
+and in figure form.
+
+```{r Plot egg vs. egg ptoid coefficients, fig.cap="Plot of selection surfaces acting on egg parasitoids."}
 
@@
 dodge_width <- position_dodge(width=0.5)
-y_limits_eggegg_coefs <- c(min(filter(tidy_eggegg_alphas, type!="Diff")$conf.low), 
-                            max(filter(tidy_eggegg_alphas, type!="Diff")$conf.high))
+y_limits_eggegg_coefs <- c(min(filter(tidy_eggegg_alphas, type=="Diff")$conf.low), 
+                            max(filter(tidy_eggegg_alphas, type=="Diff")$conf.high))
 P_asterisk_eggegg_coefs <- 1.7
 P_size <- 8
-legend_eggegg_labels <- c("Complex","Simple")
+legend_eggegg_labels <- c("Original","Extinction")
 point.size <- 3
@@
 plot_eggegg_mean_fitness <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term=="(Intercept)") %>%
+  filter(type=="Diff", term=="(Intercept)") %>%
   ggplot(., aes(x=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Probability of observing egg parasitoid", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
+  #geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term=="(Intercept)"), aes(y=0.9, x=1.5, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Probability of observing\negg parasitoid", limits=c(0,1), breaks=c(0,0.2,0.4,0.6,0.8,1)) +
   scale_x_discrete(name="") +
@@
 plot_eggegg_linear_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  #geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Original - Extinction", limits=y_limits_eggegg_coefs) +
   scale_x_discrete(name="", labels=parse(text=c("alpha[Diam]","alpha[Clutch]","alpha[Pref]"))) +
@@
 
-# Plot quadratic trait-fitness relationships
+# Plot quadratic selection surfaces
 plot_eggegg_quadratic_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  #geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Original - Extinction", limits=y_limits_eggegg_coefs) +
   scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Diam]","alpha[Clutch:Clutch]","alpha[Pref:Pref]"))) +
@@
 plot_eggegg_correlational_coefs <- tidy_eggegg_alphas %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
-  scale_y_continuous(name="Coefficient", limits=y_limits_eggegg_coefs) +
+  #geom_text(data=filter(tidy_eggegg_alphas, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_eggegg_coefs, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Original - Extinction", limits=y_limits_eggegg_coefs) +
   scale_x_discrete(name="", labels=parse(text=c("alpha[Diam:Clutch]","alpha[Diam:Pref]","alpha[Clutch:Pref]"))) +
@@
 plot_eggegg_coefs <- plot_grid(
-  plot_eggegg_mean_fitness + theme(legend.position = "none"),
+  #plot_eggegg_mean_fitness + theme(legend.position = "none"),
   plot_eggegg_linear_coefs + theme(legend.position = "none"),
@@
 
-## Selection gradients acting on the egg parasitoid
+## Selection gradients for the egg parasitoid
 
@@
 # Estimate mean fitness and mean "brackets" for each food-web treatment (see Janzen and Stern 1998 equation 4 for details about "brackets")
-eggegg_complex_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Complex"), type="response")
-eggegg_complex_mean_brackets <- mean(eggegg_complex_predict * (1 - eggegg_complex_predict))
-eggegg_complex_mean_fitness <- mean(eggegg_complex_predict)
-
-eggegg_simple_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Simple"), type="response")
-eggegg_simple_mean_brackets <- mean(eggegg_simple_predict * (1 - eggegg_simple_predict))
-eggegg_simple_mean_fitness <- mean(eggegg_simple_predict)
-
-eggegg_complex_gradient <- function(x) eggegg_complex_mean_brackets * x / eggegg_complex_mean_fitness
-eggegg_simple_gradient <- function(x) eggegg_simple_mean_brackets * x / eggegg_simple_mean_fitness
-
-eggegg_complex_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebComplex:")) %>%
-  transmute_all(funs(eggegg_complex_gradient))
-
-eggegg_simple_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebSimple:")) %>%
-  transmute_all(funs(eggegg_simple_gradient))
-```
+eggegg_original_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Original"), type="response")
+eggegg_original_mean_brackets <- mean(eggegg_original_predict * (1 - eggegg_original_predict))
+eggegg_original_mean_fitness <- mean(eggegg_original_predict)
+
+eggegg_extinction_predict <- predict(eggegg_model, newdata=filter(eggegg_df, Foodweb=="Extinction"), type="response")
+eggegg_extinction_mean_brackets <- mean(eggegg_extinction_predict * (1 - eggegg_extinction_predict))
+eggegg_extinction_mean_fitness <- mean(eggegg_extinction_predict)
+
+eggegg_original_gradient <- function(x) eggegg_original_mean_brackets * x / eggegg_original_mean_fitness
+eggegg_extinction_gradient <- function(x) eggegg_extinction_mean_brackets * x / eggegg_extinction_mean_fitness
+
+eggegg_original_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebOriginal:")) %>%
+  transmute_all(funs(eggegg_original_gradient))
+
+eggegg_extinction_raw_gradients <- select(eggegg_adj_Diam, starts_with("FoodwebExtinction:")) %>%
+  transmute_all(funs(eggegg_extinction_gradient))
+```
+
+Calculate differences between food-web treatments, then estimate means and confidence intervals
+
+```{r Calculate diffs in egg vs. egg ptoid gradients, echo=TRUE}
+eggegg_grads <- bind_cols(eggegg_original_raw_gradients, eggegg_extinction_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebOriginal:sc.Diam` - `FoodwebExtinction:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebOriginal:sc.log.Clutch` - `FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebOriginal:sc.sqrt.Pref` - `FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebOriginal:I(sc.Diam^2)` - `FoodwebExtinction:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebOriginal:I(sc.log.Clutch^2)` - `FoodwebExtinction:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - `FoodwebExtinction:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - `FoodwebExtinction:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - `FoodwebExtinction:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+```
+
+Below, we display estimates of standardized selection gradients (and 95% confidence intervals) imposed by larval parasitoids on egg parasitoids as a table,
 
 ```{r Tidy egg vs. egg ptoid selection gradients}
-# Calculate differences between food-web treatments, then estimate means and confidence intervals
-eggegg_grads <- bind_cols(eggegg_complex_raw_gradients, eggegg_simple_raw_gradients) %>%
-  mutate(`FoodwebDiff:sc.Diam` = `FoodwebSimple:sc.Diam` - `FoodwebComplex:sc.Diam`,
-         `FoodwebDiff:sc.log.Clutch` = `FoodwebSimple:sc.log.Clutch` - `FoodwebComplex:sc.log.Clutch`,
-         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebSimple:sc.sqrt.Pref` - `FoodwebComplex:sc.sqrt.Pref`,
-         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebSimple:I(sc.Diam^2)` - `FoodwebComplex:I(sc.Diam^2)`,
-         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebSimple:I(sc.log.Clutch^2)` - `FoodwebComplex:I(sc.log.Clutch^2)`,
-         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebSimple:I(sc.sqrt.Pref^2)` - `FoodwebComplex:I(sc.sqrt.Pref^2)`,
-         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebSimple:sc.Diam:sc.log.Clutch` - `FoodwebComplex:sc.Diam:sc.log.Clutch`,
-         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebSimple:sc.Diam:sc.sqrt.Pref` - `FoodwebComplex:sc.Diam:sc.sqrt.Pref`,
-         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebSimple:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebComplex:sc.log.Clutch:sc.sqrt.Pref`) %>%
-  summarise_all(funs(mean, conf.high, conf.low))
 
@@
 
-\
-
-```{r Egg vs. ptoid selection gradients}
+```{r Egg vs. ptoid selection gradients, include=FALSE}
 tidy_eggegg_grads %>%
   filter(type != "Diff") %>%
-  select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-knitr::kable(., caption = "Table of selection gradients acting on egg parasitoids in complex and simple food webs.")
-```
-
-\
-
-```{r Table of differences in selection gradients acting on egg parasitoids between food-web treatment, include=FALSE}
+  #select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+knitr::kable(., caption = "Table of standardized selection gradients acting on egg parasitoids in original and extinction food webs.")
+```
+
+```{r Table of differences in selection gradients acting on egg parasitoids between food-web treatment}
 tidy_eggegg_grads %>%
   filter(type == "Diff") %>%
-  select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
-  mutate(mean = round(mean, 3), conf.low = round(conf.low, 3), conf.high = round(conf.high, 3)) %>%
-  knitr::kable(., caption = "Table of differences in selection gradients acting on egg parasitoids between food-web treatment.")
-```
-
-\
-
-Now let's see the table results as a figure.
-
-```{r Plot egg vs.
-egg ptoid gradients, fig.cap="Selection gradients acting on egg parasitoid's extended phenotype in complex and simple food webs.
-Asterisks denote significant differences (*P* < 0.05) between food-web treatments."}
+  #select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, `Original - Extinction` = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of standardized selection gradients acting on egg parasitoids (*Platygaster* sp.).")
+```
+
+and in figure form.
+
+```{r Plot egg vs. egg ptoid gradients, fig.cap="Plot of standardized selection gradients acting on egg parasitoids."}
 
@@
 dodge_width <- position_dodge(width=0.5)
-y_limits_eggegg_grads <- c(min(filter(tidy_eggegg_grads, type!="Diff")$conf.low), 
-                            max(filter(tidy_eggegg_grads, type!="Diff")$conf.high))
+y_limits_eggegg_grads <- c(min(filter(tidy_eggegg_grads, type=="Diff")$conf.low), 
+                            max(filter(tidy_eggegg_grads, type=="Diff")$conf.high))
 P_asterisk_eggegg_grads <- 0.45
 P_size <- 8
-legend_eggegg_labels <- c("Complex","Simple")
+legend_eggegg_labels <- c("Original","Extinction")
 legend_eggegg_title <- "Food web"
@@
 plot_eggegg_directional_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  filter(type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
@@
 plot_eggegg_quadratic_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  filter(type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), 
-            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
@@
 plot_eggegg_correlational_grads <- tidy_eggegg_grads %>%
-  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  filter(type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
   ggplot(., aes(x=term, color=type)) +
@@
   geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
-  geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), 
-            aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
+  #geom_text(data=filter(tidy_eggegg_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_eggegg_grads, label=P_cutoff), size=P_size, color="black") +
   scale_y_continuous(name="Gradient", limits=y_limits_eggegg_grads) +
@@
   nrow=2, align="hv", labels = "")
-plot_legend_eggegg_grads <- ggdraw(plot_eggegg_grads) + draw_grob(legend_eggegg_grads, x = 0.7, y=-0.2)
-y_title_eggegg_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
-
-figure_eggegg_grads <- plot_grid(y_title_eggegg_grads, plot_legend_eggegg_grads, ncol=2, rel_widths = c(0.05,1)) 
+#plot_legend_eggegg_grads <- ggdraw(plot_eggegg_grads) + draw_grob(legend_eggegg_grads, x = 0.7, y=-0.2)
+y_title_eggegg_grads <- ggdraw() + draw_label("Original - Extinction", angle = 90)
+
+figure_eggegg_grads <- plot_grid(y_title_eggegg_grads, plot_eggegg_grads, ncol=2, rel_widths = c(0.05,1)) 
 figure_eggegg_grads
@@
 
-\
-
 ## Reproduce Figure 4 in main text
 
-```{r Egg-Parasitoid-Selection, fig.cap="Selection on extended phenotype (oviposition preference) of egg parasitoids"}
-# this is used for plotting selection on egg parasitoids extended phenotype. We only did this for preference since this was the only trait under selection.
+Using a similar approach as for gall midge traits, we plot the difference in the probability of observing egg parasitoids (original - extinction) as a function of gall midge (now egg parasitoid) traits.
+Gall midge preference was the only phenotype of egg parasitoids that appeared to be under selection, so we only calculate this relationship,
+
+```{r Egg parasitoid bootstraps, cache=TRUE, echo=TRUE}
+## Oviposition preference
 eggegg_RF_Pref <- bootstrap_fitness(
@@
   bootstraps=n_boots_plots) 
+```
+
+and plot it.
+
+```{r Egg-Parasitoid-Selection, fig.cap="Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.)."}
 
@@
   spread(Foodweb, absolute_fitness) %>%
-  mutate(fitness_difference = Complex-Simple)
+  mutate(fitness_difference = Original-Extinction)
 

### 2019-05-21 manuscript/manuscript.Rmd
finalized version for resubmission to Am Nat

@@
 
-<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission --> 
+<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission 
 \begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
@@
 \bigskip
-<!---->
+-->
 *Manuscript elements*: table 1, table 2, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
@@
 Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012].
-Here, we integrate ecological networks and adaptive landscapes to understand how the community context constrains evolutionary change [@Arnold1992].
-Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape.
+Here, we integrate ecological networks and adaptive landscapes to understand how the community context constrains evolutionary change.
+Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
 For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
@@
 Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].
-If we want to predict how the community context constrains evolutionary change, we must understand how ecological networks shape the adaptive landscape.
+If we want to predict how the community context constrains phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
 
@@
 ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016].
-We manipulated food-web structure by either excluding or allowing the guild of larval parasitoids to impose selection on gall midge and egg parasitoid traits (fig.
+We manipulated food-web structure by either excluding the guild of larval parasitoids (extinction food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (original food web, fig.
 \ref{fig:Conceptual}).
-We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the adaptive landscape of the gall midge and egg parasitoid.
+We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
 Taken together, our study gives insight to how local extinctions may constrain the evolution of interacting populations.
@@
 
-$$\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
 `r round(original_gammas["Diam","Diam"],2)` &  &  \\  
@@
 
-$$\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
 `r round(original_curvature["Diam","Diam"],2)` &  &  \\  
@@
 
-$$\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
 `r round(extinction_gammas["Diam","Diam"],2)` &  &  \\  
@@
 
-$$\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
+$$\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
 `r round(extinction_curvature["Diam","Diam"],2)` &  &  \\  
@@
 
-The exctinction of larval parasitoids only altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}).
+The extinction of larval parasitoids only altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}).
 Specifically, the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
@@
 A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
-If indirect evolutionary effects are common [@Walsh2013], then predicting evolutionary trajectories resulting from consumer extinctions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
+If indirect evolutionary effects are common [@Miller1996; @Walsh2013], then predicting evolutionary trajectories resulting from consumer extinctions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 
@@
 <!-- Caveats -->
-Our study has some limitations to consider when relating our findings to the effects of consumer extinctions on evolutionary constraints more generally.
+Our study has some limitations to consider when relating our findings to the effect of consumer extinctions on evolutionary constraints more generally.
 First, we removed other sources of mortality prior to our analyses.
-While this was necessary to avoid confounding estimates of selection with effects on phenotypic expression, we may be overestimating the effects of selection due to parasitoids.
+While this was necessary to avoid confounding estimates of selection with effects on phenotypic expression, we may be overestimating the effects of selection due to consumers.
 Second, our metrics of evolutionary constraints do not account for variation in the magnitude of selection pressures.
-While quantitative metrics are possible [@Hansen2008], we felt they were not appropriate to apply here as our experimental removal of larval parasitoids results in a transient dynamic in the strength (but not direction) of selection.
+While metrics that incorporate the magnitude of selection are possible [@Hansen2008], they were not appropriate for our study as our experimental removal of larval parasitoids artificially increased the mean fitness of gall midges (in the short term), which dampens the magnitude of selection gradients in this treatment [@Hunter2018].
+This is why we used more qualitative metrics of evolutionary constraints, which are robust to this artificial effect and simply require sufficient sample sizes to detect evidence of selection.
+<!--Note though that this should have made it more difficult to detect selection in this treatment, yet it was this extinction treatment that increased the number of traits under selection.
+<!--results in a transient dynamic in the strength (but not direction) of selection.
 Such transient dynamics may be common in short-term experimental studies of natural selection, but they can be detected by using natural history information and dissecting the sources of selection (e.g.
 quantifying selection surfaces and treatment effects on mean fitness) as we did here.
+-->
 

### 2019-05-21 manuscript/manuscript.tex
finalized version for resubmission to Am Nat

@@
 
-\begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
-
-\bigskip
-
-\noindent 1. University of Zurich, Department of Evolutionary Biology
-and Environmental Studies, Zurich, 8057 ZH, Switzerland;
-
-\noindent 2. University of British Columbia, Department of Zoology,
-Vancouver, BC V6T 1Z4, Canada;
-
-\noindent 3. University of Guelph, Department of Integrative Biology,
-Guelph, ON N1G 2W1, Canada;
-
-\noindent 4. Humboldt State University, Department of Biological
-Sciences, Arcata, CA 95521, USA.
-
-\(^\ast\) Corresponding author; e-mail:
-\href{mailto:matthew.barbour@ieu.uzh.ch}{\nolinkurl{matthew.barbour@ieu.uzh.ch}}
-
-\bigskip
-<!----> \emph{Manuscript elements}: table 1, table 2, figure 1, figure
-2, figure 3, figure 4. All figures should be printed in color.
+\emph{Manuscript elements}: table 1, table 2, figure 1, figure 2, figure
+3, figure 4. All figures should be printed in color.
 
@@
 
-\emph{Number of words}: 3109
+\emph{Number of words}: 3108
 
@@
 ecological networks and adaptive landscapes to understand how the
-community context constrains evolutionary change \citep{Arnold1992}.
-Different aspects of evolutionary constraints can be inferred by
-quantifying the slope and curvature of the adaptive landscape. For
-example, the slope is determined by directional selection gradients
-acting on each phenotypic trait and influences the trajectory of
-evolutionary change \citep{Lande1979, Arnold1992}. Selective constraints
-on evolution increase with the number of traits under directional
-selection, as this diminishes the number of optimal solutions
-\citep{Arnold2003}. The curvature of the adaptive landscape can also
-constrain evolution through its indirect effect on genetic constraints
+community context constrains evolutionary change. Different aspects of
+evolutionary constraints can be inferred by quantifying the slope and
+curvature of the adaptive landscape \citep{Arnold1992}. For example, the
+slope is determined by directional selection gradients acting on each
+phenotypic trait and influences the trajectory of evolutionary change
+\citep{Lande1979, Arnold1992}. Selective constraints on evolution
+increase with the number of traits under directional selection, as this
+diminishes the number of optimal solutions \citep{Arnold2003}. The
+curvature of the adaptive landscape can also constrain evolution through
+its indirect effect on genetic constraints
 \citep{Arnold1992, Hansen2008}. Genetic constraints are largely governed
@@
 independence of traits \citep{Hansen2008}. If we want to predict how the
-community context constrains evolutionary change, we must understand how
-ecological networks shape the adaptive landscape.
+community context constrains phenotypic evolution, we must understand
+how ecological networks shape the adaptive landscape.
 
@@
 high mortality from egg and larval parasitoids \citep{Barbour2016}. We
-manipulated food-web structure by either excluding or allowing the guild
-of larval parasitoids to impose selection on gall midge and egg
-parasitoid traits (fig. \ref{fig:Conceptual}). We then applied modern
-statistical methods to quantify how changes in food-web structure
-altered the slope and curvature of the adaptive landscape of the gall
-midge and egg parasitoid. Taken together, our study gives insight to how
-local extinctions may constrain the evolution of interacting
-populations.
+manipulated food-web structure by either excluding the guild of larval
+parasitoids (extinction food web) or allowing both egg and larval
+parasitoids to impose selection on gall midge traits (original food web,
+fig. \ref{fig:Conceptual}). We then applied modern statistical methods
+to quantify how changes in food-web structure altered the slope and
+curvature of the gall midge's adaptive landscape. Taken together, our
+study gives insight to how local extinctions may constrain the evolution
+of interacting populations.
 
@@
 \centering
-\includegraphics{analyses/complex_simple_foodwebs_v2.jpeg}
+\includegraphics{../analyses/complex_simple_foodwebs_v3.jpeg}
 \caption{\label{fig:Conceptual}Experimental manipulation of food-web
@@
 0.02 [
--0.14,
+-0.15,
 0.18] \\%& 
@@
 \centering
-\includegraphics{analyses/UV_landscapes.pdf}
+\includegraphics{../analyses/UV_landscapes.pdf}
 \caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
@@
 
-\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
+\[\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
 0 &  &  \\  
@@
 
-\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
+\[\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
 -0.12 &  &  \\  
@@
 
-\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
+\[\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
 0 &  &  \\  
@@
 
-\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
+\[\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
 -0.04 &  &  \\  
@@
 \centering
-\includegraphics{analyses/MV_landscapes.pdf}
+\includegraphics{../analyses/MV_landscapes.pdf}
 \caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
@@
 
-The exctinction of larval parasitoids only altered the relationship
+The extinction of larval parasitoids only altered the relationship
 between gall midge preference and the probability of observing egg
@@
 
--0.03 [
-0.25,
--0.3] \\
+0.03 [
+0.3,
+-0.25] \\
 
@@
 
-0.07 [
-0.38,
+-0.07 [
+0.26,
+-0.39] \\
+
+$\beta_{\text{Pref}}$ &
+
+0.25 [
+0.64,
+-0.09] \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+
+0.05 [
+0.43,
+-0.33] \\
+
+$\gamma_{\text{Clutch:Clutch}}$ &
+
+0.21 [
+0.68,
 -0.26] \\
 
-$\beta_{\text{Pref}}$ &
+$\gamma_{\text{Pref:Pref}}$ &
+
+\textbf{
+0.46 [
+1.07,
+0.02] }\\
+
+$\gamma_{\text{Diam:Clutch}}$ &
+
+0 [
+0.29,
+-0.27] \\
+
+$\gamma_{\text{Diam:Pref}}$ &
 
 -0.25 [
-0.09,
--0.64] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-
--0.05 [
-0.33,
--0.43] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ &
-
--0.21 [
-0.26,
--0.68] \\
-
-$\gamma_{\text{Pref:Pref}}$ &
-
-\textbf{
--0.46 [
--0.02,
--1.07] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ &
-
-0 [
-0.27,
--0.29] \\
-
-$\gamma_{\text{Diam:Pref}}$ &
-
-0.25 [
-0.6,
--0.05] \\
+0.04,
+-0.6] \\
 
@@
 
--0.18 [
-0.12,
--0.52] \\ 
+0.18 [
+0.52,
+-0.12] \\ 
 \hline
@@
 \centering
-\includegraphics{analyses/selection_on_Platygaster.pdf}
+\includegraphics{../analyses/selection_on_Platygaster.pdf}
 \caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
@@
 \citep{Pilson1996, Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, Start2019}.
-If indirect evolutionary effects are common \citep{Walsh2013}, then
-predicting evolutionary trajectories resulting from consumer extinctions
-will require evolutionary studies to explicitly account for the
-ecological networks that species are embedded in.
+If indirect evolutionary effects are common
+\citep{Miller1996, Walsh2013}, then predicting evolutionary trajectories
+resulting from consumer extinctions will require evolutionary studies to
+explicitly account for the ecological networks that species are embedded
+in.
 
@@
 Our study has some limitations to consider when relating our findings to
-the effects of consumer extinctions on evolutionary constraints more
+the effect of consumer extinctions on evolutionary constraints more
 generally. First, we removed other sources of mortality prior to our
@@
 selection with effects on phenotypic expression, we may be
-overestimating the effects of selection due to parasitoids. Second, our
+overestimating the effects of selection due to consumers. Second, our
 metrics of evolutionary constraints do not account for variation in the
-magnitude of selection pressures. While quantitative metrics are
-possible \citep{Hansen2008}, we felt they were not appropriate to apply
-here as our experimental removal of larval parasitoids results in a
-transient dynamic in the strength (but not direction) of selection. Such
-transient dynamics may be common in short-term experimental studies of
-natural selection, but they can be detected by using natural history
-information and dissecting the sources of selection (e.g.~quantifying
-selection surfaces and treatment effects on mean fitness) as we did
-here.
+magnitude of selection pressures. While metrics that incorporate the
+magnitude of selection are possible \citep{Hansen2008}, they were not
+appropriate for our study as our experimental removal of larval
+parasitoids artificially increased the mean fitness of gall midges (in
+the short term), which dampens the magnitude of selection gradients in
+this treatment \citep{Hunter2018}. This is why we used more qualitative
+metrics of evolutionary constraints, which are robust to this artificial
+effect and simply require sufficient sample sizes to detect evidence of
+selection.
 

### 2019-05-22 manuscript/manuscript.Rmd
removed sign flip for parasitoid selection table, because I already corrected it in reproduce_analyses.Rmd

@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
 
@@
 \textbf{
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
 \hline

### 2019-08-30 analyses/reproduce_analyses.Rmd
add calculations of curvature differences between treatments as well as effects on evolvability.

@@
 # Load required libraries.
+library(evolqg)     # calculate evolvability
 library(car)        # for homogeneity of variance test
@@
 ```{r Curvature, include=FALSE}
+# Get mean estimates for directional selection gradients
+foodweb_original_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Original", term == "sc.Diam")$mean
+foodweb_original_mean_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Original", term == "sc.log.Clutch")$mean
+foodweb_original_mean_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Original", term == "sc.sqrt.Pref")$mean
+
+foodweb_extinction_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.Diam")$mean
+foodweb_extinction_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.log.Clutch")$mean
+foodweb_extinction_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean
+
 # Calculate curvatures for original food web
 foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
-  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
-         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
-         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
-         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
-         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
-         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
+  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.Diam, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
+         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - foodweb_original_mean_sc.sqrt.Pref*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
 
@@
 foodweb_extinction_raw_curvs <- foodweb_extinction_raw_gradients %>%
-  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
-         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
-         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
-         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
-         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
-         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
+  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
+         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - foodweb_extinction_sc.log.Clutch*foodweb_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - foodweb_extinction_sc.sqrt.Pref*foodweb_extinction_sc.sqrt.Pref,# `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_sc.sqrt.Pref,# `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - foodweb_extinction_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref)# `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
 
@@
 figure_foodweb_grads
+```
+
+\
+
+## Long-term selection gradients for the gall midge: food-web treatments
+
+```{r Long-term food-web selection gradients, echo=TRUE}
+
+# Nothing changes for the original food web
+
+# use mean fitness from original food-web treatment to approximate long-term fitness of Extinction food web
+# once egg parasitoids increase in abundance after being released from intraguild predation
+foodweb_long_extinction_gradient <- function(x) foodweb_extinction_mean_brackets * x / foodweb_original_mean_fitness
+
+foodweb_long_extinction_raw_gradients <- select(foodweb_adj_Diam, starts_with("FoodwebExtinction:")) %>%
+  transmute_all(funs(foodweb_long_extinction_gradient))
+```
+
+```{r Tidy up long-term selection gradients}
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+foodweb_long_grads <- bind_cols(foodweb_original_raw_gradients, foodweb_long_extinction_raw_gradients) %>%
+  mutate(`FoodwebDiff:sc.Diam` = `FoodwebExtinction:sc.Diam` - `FoodwebOriginal:sc.Diam`,
+         `FoodwebDiff:sc.log.Clutch` = `FoodwebExtinction:sc.log.Clutch` - `FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebDiff:sc.sqrt.Pref` = `FoodwebExtinction:sc.sqrt.Pref` - `FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebDiff:I(sc.Diam^2)` = `FoodwebExtinction:I(sc.Diam^2)` - `FoodwebOriginal:I(sc.Diam^2)`,
+         `FoodwebDiff:I(sc.log.Clutch^2)` = `FoodwebExtinction:I(sc.log.Clutch^2)` - `FoodwebOriginal:I(sc.log.Clutch^2)`,
+         `FoodwebDiff:I(sc.sqrt.Pref^2)` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - `FoodwebOriginal:I(sc.sqrt.Pref^2)`,
+         `FoodwebDiff:sc.Diam:sc.log.Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - `FoodwebOriginal:sc.Diam:sc.log.Clutch`,
+         `FoodwebDiff:sc.Diam:sc.sqrt.Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - `FoodwebOriginal:sc.Diam:sc.sqrt.Pref`,
+         `FoodwebDiff:sc.log.Clutch:sc.sqrt.Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_foodweb_long_grads <- foodweb_long_grads %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"),
+         gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+                                ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+We then calculate selection gradients and 95% confidence intervals.
+
+```{r Table of long-term food web selection gradients}
+tidy_foodweb_long_grads %>%
+  filter(type != "Diff") %>%
+  #select(term, type, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+  arrange(desc(Term)) %>%
+  knitr::kable(., caption = "Table of long-term standardized selection gradients acting on gall midges in each food-web treatment.")
+```
+
+```{r Table of differences in long-term selection gradients between food-web treatments}
+tidy_foodweb_long_grads %>%
+  filter(type == "Diff") %>%
+  #select(term, mean, conf.low, conf.high) %>% # gradient_type, P_cutoff
+  transmute(Term = term, Treatment = type, Estimate = round(mean, 2), `2.5%` = round(conf.low, 2), `97.5%` = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of differences in long-term selection gradients acting on gall traits between food-web treatment.")
+```
+
+```{r Curvature long-term, include=FALSE}
+# Get mean estimates for directional selection gradients
+# Note we already have the mean estimates for the original food web
+
+foodweb_long_extinction_mean_sc.Diam <- filter(tidy_foodweb_long_grads, type == "Extinction", term == "sc.Diam")$mean
+foodweb_long_extinction_sc.log.Clutch <- filter(tidy_foodweb_long_grads, type == "Extinction", term == "sc.log.Clutch")$mean
+foodweb_long_extinction_sc.sqrt.Pref <- filter(tidy_foodweb_long_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean
+
+# Calculate curvatures for original food web
+foodweb_original_raw_curvs <- foodweb_original_raw_gradients %>%
+  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.Diam, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
+         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.log.Clutch, #`FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - foodweb_original_mean_sc.sqrt.Pref*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.log.Clutch, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.sqrt.Pref)# `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
+
+# Calculate long-term curvatures for extinction food web
+foodweb_long_extinction_raw_curvs <- foodweb_long_extinction_raw_gradients %>%
+  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - foodweb_long_extinction_mean_sc.Diam*foodweb_long_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
+         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - foodweb_long_extinction_sc.log.Clutch*foodweb_long_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - foodweb_long_extinction_sc.sqrt.Pref*foodweb_long_extinction_sc.sqrt.Pref, # `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - foodweb_long_extinction_mean_sc.Diam*foodweb_long_extinction_sc.log.Clutch, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - foodweb_long_extinction_mean_sc.Diam*foodweb_long_extinction_sc.sqrt.Pref, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - foodweb_long_extinction_sc.log.Clutch*foodweb_long_extinction_sc.sqrt.Pref) # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+foodweb_long_curvs <- bind_cols(foodweb_original_raw_curvs, foodweb_long_extinction_raw_curvs) %>%
+  mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
+         `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
+         `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
+         `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
+         `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
+         `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_foodweb_long_curvs <- foodweb_long_curvs %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"))#,
+         #gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+         #                       ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         #mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         #conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         #conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+```{r Table of long-term food web curvatures}
+tidy_foodweb_long_curvs %>%
+  filter(type != "Diff") %>%
+  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
+  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of long-term curvatures on gall traits in each food-web treatment.")
+```
+
+```{r Table of differences in long-term curvatures between food-web treatments, include=FALSE}
+tidy_foodweb_long_curvs %>%
+  filter(type == "Diff") %>%
+  select(term, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of differences in long-term curvatures on gall traits between food-web treatment.")
+```
+
+As before, we can visualize the table output as a figure.
+
+```{r Plot long-term food-web gradients, fig.cap="Plot of long-term standardized selection gradients acting on gall midges in each food-web treatment."}
+
+# Plot helpers
+dodge_width <- position_dodge(width=0.5)
+y_limits_foodweb_long_grads <- c(min(filter(tidy_foodweb_long_grads, type!="Diff")$conf.low), 
+                            max(filter(tidy_foodweb_long_grads, type!="Diff")$conf.high))
+P_asterisk_foodweb_grads <- 0.5
+P_size <- 8
+legend_foodweb_long_labels <- c("Original","Extinction-Long")
+legend_foodweb_title <- "Food web"
+point.size <- 3
+
+# Plot directional selection gradients
+plot_foodweb_long_directional_grads <- tidy_foodweb_long_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam","sc.log.Clutch","sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_long_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("beta[Diam]","beta[Clutch]","beta[Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title)
+
+# Plot quadratic selection gradients
+plot_foodweb_long_quadratic_grads <- tidy_foodweb_long_grads %>%
+  filter(type!="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("I(sc.Diam^2)","I(sc.log.Clutch^2)","I(sc.sqrt.Pref^2)")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_long_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Diam]","gamma[Clutch:Clutch]","gamma[Pref:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title)
+
+# Plot correlational selection gradients
+plot_foodweb_long_correlational_grads <- tidy_foodweb_long_grads %>%
+  filter(type!="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")) %>%
+  ggplot(., aes(x=term, color=type)) +
+  geom_hline(yintercept=0, linetype="dotted") +
+  geom_linerange(aes(ymax=conf.high, ymin=conf.low, color=type), position=dodge_width) +
+  geom_point(aes(y=mean, fill=type), position=dodge_width, shape=21, color="black", size=point.size) +
+  #geom_text(data=filter(tidy_foodweb_grads, type=="Diff", term %in% c("sc.Diam:sc.log.Clutch","sc.Diam:sc.sqrt.Pref","sc.log.Clutch:sc.sqrt.Pref")), aes(y=P_asterisk_foodweb_grads, label=P_cutoff), size=P_size, color="black") +
+  scale_y_continuous(name="Gradient", limits=y_limits_foodweb_long_grads) +
+  scale_x_discrete(name="", labels=parse(text=c("gamma[Diam:Clutch]","gamma[Diam:Pref]","gamma[Clutch:Pref]"))) +
+  facet_wrap(~gradient_type) +
+  scale_fill_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title) +
+  scale_color_manual(values=cbPalette[c(6,5)], labels=legend_foodweb_long_labels, name=legend_foodweb_title)
+
+# Get legend
+legend_foodweb_long_grads <- get_legend(plot_foodweb_long_directional_grads)
+
+# Format plots for manuscript
+plot_foodweb_long_grads <- plot_grid(
+  plot_foodweb_long_directional_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_foodweb_long_quadratic_grads + theme(legend.position = "none", axis.title = element_blank()),
+  plot_foodweb_long_correlational_grads + theme(legend.position = "none", axis.title = element_blank()), 
+  nrow=2, align="hv", labels = "")
+plot_legend_foodweb_long_grads <- ggdraw(plot_foodweb_long_grads) + draw_grob(legend_foodweb_long_grads, x = 0.7, y=-0.2)
+y_title_foodweb_long_grads <- ggdraw() + draw_label("Selection gradient (SDs)", angle = 90)
+
+figure_foodweb_long_grads <- plot_grid(y_title_foodweb_long_grads, plot_legend_foodweb_long_grads, ncol=2, rel_widths = c(0.05,1)) 
+figure_foodweb_long_grads
 ```
@@
 
+```{r Genetic constraints, include=F, eval=F}
+bootstrapped_foodweb_curvs <- bind_cols(foodweb_original_raw_curvs, foodweb_extinction_raw_curvs) #%>%
+  #mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
+  #       `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
+  #       `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
+  #       `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
+  #       `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
+  #       `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`)
+#bootstrapped_foodweb_curvs
+
+Pmat <- matrix(diag(c(1,1,1)), byrow = T, ncol = 3)#cov(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref))
+Gmat <- 0.3*Pmat # assuming heritability of 0.3
+
+registerDoParallel(cores = 32)
+foodweb_original_genetic_constraints <- c()
+foodweb_extinction_genetic_constraints <- c()
+for(i in 1:dim(bootstrapped_foodweb_curvs)[1]){ #
+
+  # original
+  original_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],
+                    bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],
+                    bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Pref`[i]),
+                  byrow = T, ncol = 3)
+  original_new_G <- Gmat + Gmat %*% original_C %*% Gmat
+  original_new_G2 <- original_new_G + original_new_G %*% original_C %*% original_new_G
+  original_new_G3 <- original_new_G2 + original_new_G2 %*% original_C %*% original_new_G2
+  original_new_G4 <- original_new_G3 + original_new_G3 %*% original_C %*% original_new_G3
+  original_new_G5 <- original_new_G4 + original_new_G4 %*% original_C %*% original_new_G4
+  original_new_G6 <- original_new_G5 + original_new_G5 %*% original_C %*% original_new_G5
+  original_new_G7 <- original_new_G6 + original_new_G6 %*% original_C %*% original_new_G6
+  original_new_G8 <- original_new_G7 + original_new_G7 %*% original_C %*% original_new_G7
+
+  foodweb_original_genetic_constraints[i] <- try(MeanMatrixStatistics(original_new_G, iterations = 1000, parallel = TRUE))["evolvability"]
+
+  # extinction
+  extinction_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Pref`[i],
+                    bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],
+                    bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Pref`[i]),
+                  byrow = T, ncol = 3)
+  extinction_new_G <- Gmat + Gmat %*% extinction_C %*% Gmat
+  extinction_new_G2 <- extinction_new_G + extinction_new_G %*% extinction_C %*% extinction_new_G
+  extinction_new_G3 <- extinction_new_G2 + extinction_new_G2 %*% extinction_C %*% extinction_new_G2
+  extinction_new_G4 <- extinction_new_G3 + extinction_new_G3 %*% extinction_C %*% extinction_new_G3
+  extinction_new_G5 <- extinction_new_G4 + extinction_new_G4 %*% extinction_C %*% extinction_new_G4
+  extinction_new_G6 <- extinction_new_G5 + extinction_new_G5 %*% extinction_C %*% extinction_new_G5
+  extinction_new_G7 <- extinction_new_G6 + extinction_new_G6 %*% extinction_C %*% extinction_new_G6
+  extinction_new_G8 <- extinction_new_G7 + extinction_new_G7 %*% extinction_C %*% extinction_new_G7
+
+  foodweb_extinction_genetic_constraints[i] <- try(MeanMatrixStatistics(extinction_new_G, iterations = 1000, parallel = TRUE))["evolvability"]
+
+  # progress
+  print(paste(i/dim(bootstrapped_foodweb_curvs)[1]*100, "% done!"))
+}
+
+## Note that higher values of conditional evolvability indicate less genetic constraints
+
+# heritability does affect constraints
+
+bootstrapped_genetic_constraints <- data.frame(Original = as.numeric(foodweb_original_genetic_constraints), Extinction = as.numeric(foodweb_extinction_genetic_constraints)) %>%
+  mutate(Diff = Original - Extinction)
+
+bootstrapped_summary_constraints <- bootstrapped_genetic_constraints %>%
+summarise_all(list(~mean(., na.rm = T), ~quantile(., probs=0.975, na.rm = T), ~quantile(., probs=0.025, na.rm = T))) %>%
+  gather(key = type, value = Estimate) %>%
+  separate(col = type, into = c("Foodweb", "Type")) %>%
+  arrange(Foodweb)
+
+sum(bootstrapped_genetic_constraints$Diff > 0) / length(bootstrapped_genetic_constraints$Diff)
+
+bootstrapped_summary_constraints
+
+bootstrapped_genetic_constraints %>%
+  ggplot(., aes(x = Diff)) +
+  geom_histogram() +
+  geom_vline(xintercept = 0, linetype = "dotted")
+```
+
+```{r mean curvature effects on random G-matrices}
+# Generate random G-matrices
+random_Gmats <- RandomMatrix(num.traits = 3, num.matrices = 10000, min.var = 0, max.var = 0.5)
+
+## Get mean estimates for curvature matrix
+
+# Original
+foodweb_original_mean_C.Diam <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Diam")$mean
+foodweb_original_mean_C.Clutch <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Clutch")$mean
+foodweb_original_mean_C.Pref <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Pref")$mean
+foodweb_original_mean_C.Diam.Clutch <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Diam:Clutch")$mean
+foodweb_original_mean_C.Diam.Pref <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Diam:Pref")$mean
+foodweb_original_mean_C.Clutch.Pref <- filter(tidy_foodweb_curvs, type == "Original", term == "C.Clutch:Pref")$mean
+
+mean_curv_original <- matrix(c(foodweb_original_mean_C.Diam, foodweb_original_mean_C.Diam.Clutch, foodweb_original_mean_C.Diam.Pref,
+                               foodweb_original_mean_C.Diam.Clutch, foodweb_original_mean_C.Clutch, foodweb_original_mean_C.Clutch.Pref,
+                               foodweb_original_mean_C.Diam.Pref, foodweb_original_mean_C.Clutch.Pref, foodweb_original_mean_C.Pref),
+                             byrow = T, ncol = 3)
+
+# Extinction
+foodweb_extinction_mean_C.Diam <- filter(tidy_foodweb_curvs, type == "Extinction", term == "C.Diam")$mean
+foodweb_extinction_mean_C.Clutch <- filter(tidy_foodweb_curvs, type == "Extinction", term == "C.Clutch")$mean
+foodweb_extinction_mean_C.Pref <- filter(tidy_foodweb_curvs, type == "Extinction", term == "C.Pref")$mean
+foodweb_extinction_mean_C.Diam.Clutch <- filter(tidy_foodweb_curvs, type == "Extinction", term == "C.Diam:Clutch")$mean
+foodweb_extinction_mean_C.Diam.Pref <- filter(tidy_foodweb_curvs, type == "Extinction", term == "C.Diam:Pref")$mean
+foodweb_extinction_mean_C.Clutch.Pref <- filter(tidy_foodweb_curvs, type == "Extinction", term == "C.Clutch:Pref")$mean
+
+mean_curv_extinction <- matrix(c(foodweb_extinction_mean_C.Diam, foodweb_extinction_mean_C.Diam.Clutch, foodweb_extinction_mean_C.Diam.Pref,
+                               foodweb_extinction_mean_C.Diam.Clutch, foodweb_extinction_mean_C.Clutch, foodweb_extinction_mean_C.Clutch.Pref,
+                               foodweb_extinction_mean_C.Diam.Pref, foodweb_extinction_mean_C.Clutch.Pref, foodweb_extinction_mean_C.Pref),
+                             byrow = T, ncol = 3)
+
+## Functions to calculate effect of mean curvature on random G-matrices
+curv_original_random_matrices_evolvabilities <- function(x){
+  new_Gmat <- x + x %*% mean_curv_original %*% x
+  MeanMatrixStatistics(new_Gmat, iterations = 1000, parallel = TRUE)["evolvability"]
+}
+
+curv_extinction_random_matrices_evolvabilities <- function(x){
+  new_Gmat <- x + x %*% mean_curv_extinction %*% x
+  MeanMatrixStatistics(new_Gmat, iterations = 1000, parallel = TRUE)["evolvability"]
+}
+
+original_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_original_random_matrices_evolvabilities)) %>%
+  select(Original = evolvability)
+
+extinction_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_extinction_random_matrices_evolvabilities)) %>% 
+  select(Extinction = evolvability)
+
+random_evolvabilities <- bind_cols(original_evolvability_list, extinction_evolvability_list) %>%
+  mutate(Diff = Extinction - Original)
+```
+
+We see that for our best estimates of the curvature matrix, that the extinction food web tends to decrease evolvability (`r sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff)`) of the gall midge population.
+
+```{r Delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices"}
+delta_evolvability_plot <- ggplot(random_evolvabilities, aes(x = Diff)) +
+  geom_histogram() +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  xlab(expression(paste(Delta," evolvability (extinction - original)"))) +
+  ylab("Count")
+
+delta_evolvability_plot
+save_plot(filename = "delta_evolvability.pdf", plot = delta_evolvability_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
+```
+
+```{r full sim random G and bootstrapped curvs, include=F, eval=F}
+bootstrapped_foodweb_curvs <- bind_cols(foodweb_original_raw_curvs, foodweb_extinction_raw_curvs)
+
+# Generate random G-matrices
+set.seed(34)
+random_Gmats <- RandomMatrix(num.traits = 3, num.matrices = 100, min.var = 0, max.var = 0.5)
+
+registerDoParallel(cores = 32)
+
+bootstrap_curvs_random_Gmats <- function(x){
+
+  foodweb_original_genetic_constraints <- c()
+  foodweb_extinction_genetic_constraints <- c()
+  for(i in 1:dim(bootstrapped_foodweb_curvs)[1]){ #
+
+    # original
+    original_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],
+                      bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],
+                      bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Pref`[i]),
+                    byrow = T, ncol = 3)
+    original_new_G <- x + x %*% original_C %*% x
+
+    foodweb_original_genetic_constraints[i] <- try(MeanMatrixStatistics(original_new_G, iterations = 1000, parallel = TRUE))["evolvability"]
+
+    # extinction
+    extinction_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Pref`[i],
+                      bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],
+                      bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebExtinction:C.Pref`[i]),
+                    byrow = T, ncol = 3)
+    extinction_new_G <- x + x %*% extinction_C %*% x
+
+    foodweb_extinction_genetic_constraints[i] <- try(MeanMatrixStatistics(extinction_new_G, iterations = 1000, parallel = TRUE))["evolvability"]
+  }
+  bootstrapped_genetic_constraints <- data.frame(Original = as.numeric(foodweb_original_genetic_constraints), 
+                                                 Extinction = as.numeric(foodweb_extinction_genetic_constraints)) %>%
+    mutate(Diff = Original - Extinction)
+
+  mean_diff <- mean(bootstrapped_genetic_constraints$Diff, na.rm = T)
+  prop_positive_diff <- sum(bootstrapped_genetic_constraints$Diff > 0, na.rm = T) / length(bootstrapped_genetic_constraints$Diff[!is.na(bootstrapped_genetic_constraints$Diff)])
+
+  return(data.frame(mean_diff = mean_diff, prop_positive_diff = prop_positive_diff))
+}
+
+# this takes ~1.5 days to run just 100 random Gmats...
+diffs.df <- lapply(X = random_Gmats, FUN = bootstrap_curvs_random_Gmats)
+```
+
+```{r include=F, eval=F}
+# of the 100, none were significant...
+plyr::ldply(diffs.df) %>%
+  mutate(Sig = ifelse(prop_positive_diff > 0.975 | prop_positive_diff < 0.025, 1, 0)) %>%
+  ggplot(., aes(x = mean_diff, fill = factor(Sig))) +
+  geom_histogram() +
+  geom_vline(xintercept = 0, linetype = "dotted")
+
+write_csv(plyr::ldply(diffs.df), "bootstrap_random_Gmat_evolvabilities.csv")
+```
+
+```{r long-term genetic constraints, include=F, eval=F}
+bootstrapped_foodweb_long_curvs <- foodweb_long_extinction_raw_curvs #bind_cols(foodweb_original_raw_curvs, foodweb_long_extinction_raw_curvs) #%>%
+  #mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
+  #       `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
+  #       `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
+  #       `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
+  #       `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
+  #       `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`)
+#bootstrapped_foodweb_curvs
+
+Pmat <- cov(select(gall_selection.df, sc.Diam, sc.log.Clutch, sc.sqrt.Pref))
+Gmat <- 0.3*Pmat # assuming heritability of 0.3
+
+#registerDoParallel(cores = 32)
+#foodweb_original_genetic_constraints <- c()
+foodweb_long_extinction_genetic_constraints <- c()
+for(i in 1:dim(bootstrapped_foodweb_long_curvs)[1]){ #
+
+  # original
+  #original_C <- matrix(c(bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],
+  #                  bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],
+  #                  bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Diam:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Clutch:Pref`[i],bootstrapped_foodweb_curvs$`FoodwebOriginal:C.Pref`[i]),
+  #                byrow = T, ncol = 3)
+  #original_new_G <- Gmat + Gmat %*% original_C %*% Gmat
+  #foodweb_original_genetic_constraints[i] <- try(MeanMatrixStatistics(original_new_G, iterations = 10000, parallel = TRUE))["conditional.evolvability"]
+
+  # extinction
+  long_extinction_C <- matrix(c(bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Diam`[i],bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Diam:Pref`[i],
+                    bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Diam:Clutch`[i],bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Clutch`[i],bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],
+                    bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Diam:Pref`[i],bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Clutch:Pref`[i],bootstrapped_foodweb_long_curvs$`FoodwebExtinction:C.Pref`[i]),
+                  byrow = T, ncol = 3)
+  long_extinction_new_G <- Gmat + Gmat %*% long_extinction_C %*% Gmat
+  foodweb_long_extinction_genetic_constraints[i] <- try(MeanMatrixStatistics(long_extinction_new_G, iterations = 10000, parallel = TRUE))["conditional.evolvability"]
+
+  # progress
+  print(paste(i/dim(bootstrapped_foodweb_long_curvs)[1]*100, "% done!"))
+}
+
+## Note that higher values of conditional evolvability indicate less genetic constraints
+
+bootstrapped_long_genetic_constraints <- data.frame(Original = as.numeric(foodweb_original_genetic_constraints), Extinction = as.numeric(foodweb_long_extinction_genetic_constraints)) %>%
+  mutate(Diff = Original - Extinction)
+
+bootstrapped_long_summary_constraints <- bootstrapped_long_genetic_constraints %>%
+summarise_all(list(~mean(., na.rm = T), ~quantile(., probs=0.975, na.rm = T), ~quantile(., probs=0.025, na.rm = T))) %>%
+  gather(key = type, value = Estimate) %>%
+  separate(col = type, into = c("Foodweb", "Type")) %>%
+  arrange(Foodweb)
+
+bootstrapped_long_summary_constraints
+
+hist(bootstrapped_long_genetic_constraints$Diff)
+```
+
+\
+
 ## Selection surfaces for the egg parasitoid

### 2019-08-30 analyses/reproduce_analyses.Rmd
tighten up curvature calculations and estimate long-term effects on evolvability

@@
 
-```{r Curvature, include=FALSE}
+```{r Curvature}
 # Get mean estimates for directional selection gradients
@@
 foodweb_extinction_mean_sc.Diam <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.Diam")$mean
-foodweb_extinction_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.log.Clutch")$mean
-foodweb_extinction_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean
+foodweb_extinction_mean_sc.log.Clutch <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.log.Clutch")$mean
+foodweb_extinction_mean_sc.sqrt.Pref <- filter(tidy_foodweb_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean
 
@@
   transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
-         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - foodweb_extinction_sc.log.Clutch*foodweb_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
-         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - foodweb_extinction_sc.sqrt.Pref*foodweb_extinction_sc.sqrt.Pref,# `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
-         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_sc.log.Clutch, # `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
-         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_sc.sqrt.Pref,# `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
-         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - foodweb_extinction_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref)# `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
+         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - foodweb_extinction_mean_sc.log.Clutch*foodweb_extinction_mean_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - foodweb_extinction_mean_sc.sqrt.Pref*foodweb_extinction_mean_sc.sqrt.Pref,# `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_mean_sc.log.Clutch, # `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - foodweb_extinction_mean_sc.Diam*foodweb_extinction_mean_sc.sqrt.Pref,# `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - foodweb_extinction_mean_sc.log.Clutch*foodweb_extinction_mean_sc.sqrt.Pref)# `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
 
@@
 
-```{r mean curvature effects on random G-matrices}
-# Generate random G-matrices
+```{r Mean curvature effects on random G-matrices, echo=TRUE}
+## Generate random G-matrices
 random_Gmats <- RandomMatrix(num.traits = 3, num.matrices = 10000, min.var = 0, max.var = 0.5)
@@
 
-```{r Delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices"}
+```{r Delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices using our best (mean) estimates of the curvature matrix."}
 delta_evolvability_plot <- ggplot(random_evolvabilities, aes(x = Diff)) +
@@
 save_plot(filename = "delta_evolvability.pdf", plot = delta_evolvability_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
+```
+
+```{r Long-term mean curvature effects on random G-matrices, echo=TRUE}
+## Use same random G-matrices as above
+
+## Get mean estimates for curvature matrix
+
+# Note that original food web is same as before
+
+# Long-term extinction
+foodweb_long_extinction_mean_C.Diam <- filter(tidy_foodweb_long_curvs, type == "Extinction", term == "C.Diam")$mean
+foodweb_long_extinction_mean_C.Clutch <- filter(tidy_foodweb_long_curvs, type == "Extinction", term == "C.Clutch")$mean
+foodweb_long_extinction_mean_C.Pref <- filter(tidy_foodweb_long_curvs, type == "Extinction", term == "C.Pref")$mean
+foodweb_long_extinction_mean_C.Diam.Clutch <- filter(tidy_foodweb_long_curvs, type == "Extinction", term == "C.Diam:Clutch")$mean
+foodweb_long_extinction_mean_C.Diam.Pref <- filter(tidy_foodweb_long_curvs, type == "Extinction", term == "C.Diam:Pref")$mean
+foodweb_long_extinction_mean_C.Clutch.Pref <- filter(tidy_foodweb_long_curvs, type == "Extinction", term == "C.Clutch:Pref")$mean
+
+long_mean_curv_extinction <- matrix(c(foodweb_long_extinction_mean_C.Diam, foodweb_long_extinction_mean_C.Diam.Clutch, foodweb_long_extinction_mean_C.Diam.Pref,
+                               foodweb_long_extinction_mean_C.Diam.Clutch, foodweb_long_extinction_mean_C.Clutch, foodweb_long_extinction_mean_C.Clutch.Pref,
+                               foodweb_long_extinction_mean_C.Diam.Pref, foodweb_long_extinction_mean_C.Clutch.Pref, foodweb_long_extinction_mean_C.Pref),
+                             byrow = T, ncol = 3)
+
+## Functions to calculate effect of mean curvature on random G-matrices
+curv_long_extinction_random_matrices_evolvabilities <- function(x){
+  new_Gmat <- x + x %*% long_mean_curv_extinction %*% x
+  MeanMatrixStatistics(new_Gmat, iterations = 1000, parallel = TRUE)["evolvability"]
+}
+
+long_extinction_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_long_extinction_random_matrices_evolvabilities)) %>% 
+  select(Extinction = evolvability)
+
+long_random_evolvabilities <- bind_cols(original_evolvability_list, long_extinction_evolvability_list) %>%
+  mutate(Diff = Extinction - Original)
+```
+
+Over the long-term (after egg parasitoids recover and impose similar fitness impact), we see that for our best estimates of the curvature matrix, that the extinction food web tends to decrease evolvability (`r sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff)`) of the gall midge population.
+
+```{r Long-term delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices using our best (mean) estimates of the curvature matrix over the long term."}
+long_delta_evolvability_plot <- ggplot(long_random_evolvabilities, aes(x = Diff)) +
+  geom_histogram() +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  xlab(expression(paste(Delta," evolvability (extinction - original)"))) +
+  ylab("Count")
+
+long_delta_evolvability_plot
 ```

### 2019-09-02 manuscript/manuscript.Rmd
minor edits to MS and changed style file.

@@
     citation_package: natbib
-    #template: Rmd_AmNat_MS_template.tex
     includes:  
@@
 bibliography: references
-biblio-style: amnat
+biblio-style: eco_let
 fontsize: 11pt
@@
 
-<!-- Remove author info for double-blind peer review; Keep for bioRxiv submission 
 \begin{center} \large Matthew A. Barbour$^{1,2,\ast}$, Christopher J. Greyson-Gaito$^{2,3}$, Arezoo Sootodeh$^{2}$, Brendan Locke$^{4}$, Jordi Bascompte$^{1}$ \normalsize \end{center}
@@
 \bigskip
--->
+
 *Manuscript elements*: table 1, table 2, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
@@
 
-Global change is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
+The loss of biodiversity<!--Global change--> is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
 Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the community context of evolving populations as a ``black box''.
@@
 The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
-More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory].
-Ecological interactions often play a key role in shaping adaptive landscapes, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.
-Although there is clear evidence that pairwise interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by the community context [@McPeek2017; @terHorst2018].
-Resolution on how the community context shapes phenotypic evolution is urgently needed though, given the rapid impacts of climate change on ecological communities [@Scheffers2016].
+More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], and gives insight to the direct and indirect effects of selective constraints [@Arnold1992].
+Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.
+Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018].
+Resolution on how ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].
 
-Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of the community context [@Bascompte2014; @McCann2012].
-Here, we integrate ecological networks and adaptive landscapes to understand how the community context constrains evolutionary change.
-Different aspects of evolutionary constraints can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
+Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of species interactions in an ecological community [@Bascompte2014; @McCann2012].
+Here, we integrate ecological networks and adaptive landscapes to understand how ecological communities constrain evolutionary change.
+The direct and indirect effects of selective constraints can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
 For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
 Selective constraints on evolution increase with the number of traits under directional selection, as this diminishes the number of optimal solutions [@Arnold2003].
-The curvature of the adaptive landscape can also constrain evolution through its indirect effect on genetic constraints [@Arnold1992; @Hansen2008].
+The curvature of the adaptive landscape is governed by nonlinear selection gradients and acts to indirectly constrain evolution through its effect on genetic constraints [@Arnold1992; @Hansen2008].
 Genetic constraints are largely governed by a population's **G**-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
-In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].
-Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].
-If we want to predict how the community context constrains phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
+Stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection may alter the genetic covariance between traits, which may facilitate or hinder future adaptation depending on pattern of selection on those traits [@Hansen2008].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
 
-Global change is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways.
+The loss of biodiversity is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways.
 For example, in a <!--multitrophic community or -->food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection.
@@
 \ref{fig:Conceptual}).
+The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
+While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
+Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
 We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
-Taken together, our study gives insight to how local extinctions may constrain the evolution of interacting populations.
+Taken together, our study gives insight to how the loss of biodiversity may constrain the evolution of interacting populations.
 
@@
 To simulate consumer extinction, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
 Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
@@
 This treatment did not exclude the egg parasitoid *Platygaster* sp., which attacks prior to gall initiation [larva initiate gall development in Cecidomyiid midges: @Gagne1989].
+It was not possible to reciprocally manipulate parasitoid attack (i.e.
+exclude egg parasitoid, but allow larval parasitoids), because it was not possible to identify midge oviposition sites prior to gall formation.
 In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature.
@@
 We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
-All data and code to reproduce the reported results are publicly available on GitHub <!--(https://github.com/mabarbour/complexity_selection)-->and have been archived on Zenodo (links are available from the journal office)<!--(https://zenodo.org/badge/latestdoi/108833263)-->.
+All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
 
@@
 For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical defintion of the adaptive landscape."}
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
 knitr::include_graphics("../analyses/UV_landscapes.pdf")
@@
 @deMazancourt2008; @Johansson2008; @Norberg2012; @Osmond2017PredatorsHelpPrey].
-This work has given insight to the mechanisms by which pairwise interactions modify the adaptive potential of species.
+This work has given insight to the mechanisms by which interactions between species can modify their adaptive potential<!--pairwise interactions modify the adaptive potential of species-->.
 Our study hints at a novel mechanism, whereby more complex food webs flatten the adaptive landscape, thus facilitating future adaptation by allowing genetic and phenotypic variation to persist.
-This mechanism only emerges once we move beyond pairwise interactions to consider selection on multiple traits in a community context.
-However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
+This mechanism only emerges once we consider selection imposed by multiple species on multiple traits.
+<!--move beyond pairwise interactions to consider selection on multiple traits in a community context.-->However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
 This negative effect of species diversity on adaptation occurs because there is a greater chance that the optimal phenotype is already occupied by a competitor in a more diverse community.

### 2019-09-05 manuscript/manuscript.Rmd
added in evolvability results and adjusted methods. also tried to include some more biological reasoning for the patterns of selection.

@@
 bibliography: references
-biblio-style: eco_let
+biblio-style: amnat
 fontsize: 11pt
@@
 
-*Manuscript type*: Article. <!-- Or e-article, note, e-note, natural history miscellany, e-natural history miscellany, comment, reply, invited symposium, or countdown to 150.-->
+*Manuscript type*: Letter.
 
@@
 
-\footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize
+<!-- \footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize -->
 
@@
 The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
-While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
-Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
+<!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
+-->Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
 We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
@@
 
-Our analysis consisted of three parts.
+Our analysis consisted of four parts.
 First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment.
@@
 Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we used to measure evolutionary constraints.
+Finally, we used a simulation to examine how the curvature of the adaptive landscape could alter the evolvability of populations in the next generation.
 
@@
 In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
-Similarly, any nonzero covariance terms (off-diagonal) are indicative of selection for trait integration (i.e., less independence).
+Similarly, any nonzero covariance terms (off-diagonal) indicate the effects of selection on additive genetic covariance between two traits.
+We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI.
+We also used this information to determine whether the curvature of each component differed between our food-web treatments.
+
+Knowledge of the curvature matrix alone gives an incomplete picture of its indirect effect on genetic constraints.
+This is because genetic constraints are ultimately determined by the structure of the G-matrix, and thus may depend on its structure before selection.
+Although we do not know the underlying G-matrix for the traits we measured in this experiment, we can still gain insight to how our food-web treatment would alter genetic constraints.
+Specifically, we first calculated how our best estimate of the curvature matrix (mean values) in each treatment changed the structure of `r n_Gmats` random G-matrices.
+If we assume that recombination/mutation would have the same effect on gall midge populations in the original and extinction food webs, then we can estimate how the curvature matrix in the previous generation alters the G-matrix for the next generation.
+
+The G-matrix itself is a complex structure, but recent theory has shown how its structure affects the evolvability of a population [@Hansen2008].
+<!--We used evolvability as our measure of genetic constraint, as it has a solid foundation in theory of quantitative genetics and adaptive landscapes [@Hansen2008].
+-->Evolvability measures the ability for a trait to evolve toward a given direction of selection, ignoring responses in every other direction [@Hansen2008].
+In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can assess its evolutionary potential by computing its average evolvability over random selection gradients (here, we used `r n_random_gradients`).
+By computing the average evolvability for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of a population.
+We report the distribution of these effect sizes, rather than conduct a statistical test, because the number of replicates in a simulation can be arbitrarily high, thus making any effect size statistically significant [@White2014].
+
+<!--
 Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
@@
 An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates.
-A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--> This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).
+A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--><!-- This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).-->
 
@@
 This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
-Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes ($\beta_{\text{Clutch}}$=
+Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (larval parasitoids $\beta_{\text{Clutch}}$=
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` 
@@
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`]).
+This conflicting selection is likely due to trait differences between guilds, as larger clutches may be easier targets for egg parasitoids to find, but also create a more complex gall structure that is more difficult for larval parasitoids to oviposit through.
+
 We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, there was no clear relationship in the original food web (table \ref{Table:Gradients}).
-This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see Selection on egg parasitoids section), and thus a less than additive effect on gall midges.
+\ref{fig:UV_Landscape}B); however, the overall magnitude of selection did not differ between treatments (table \ref{Table:Gradients}).
+Still, there was no clear evidence of selection on oviposition in the original food web (table \ref{Table:Gradients}).
+This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.
 Chamber diameter experienced positive directional selection in both food-web treatments (fig.
 \ref{fig:UV_Landscape}A).
-Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival (selection surfaces: original $\alpha_{\text{Diam}}$=
+Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival <!--(selection surfaces: original $\alpha_{\text{Diam}}$=
 `r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` 
@@
 [`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web (original $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`])-->
+(selection surfaces: contrast $\alpha_{\text{Diam}}$=
+`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` 
+[`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web <!--(original $\bar W$=
 `r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$mean,2)` 
@@
 [`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`]).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
+`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`])-->
+(contrast $\bar W$=
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean,2)` 
+[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
+We expect this difference to be transient though, since egg parasitoids would increase in abundance once they are released from intraguild predation, which would make the strength of selection on gall diameter comparable to the original food web (if extinction $\bar W$=original $\bar W$, then contrast $\beta_{\text{Diam}}$=
+`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$mean,2)` 
+[`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]).
+It is worth noting that this pattern of selection is unexpected.
+For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is strongly correlated with another unmeasured trait that is under selection (e.g.
+immune response).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
 \ref{fig:UV_Landscape}).
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
@@
 \centering
-\begin{tabular}{lcc} %c
+\begin{tabular}{lccc}
 \\ 
 \hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction}   \\ %& \textbf{Contrast}
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction} & \textbf{Contrast} \\
 \hline
@@
 `r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] }& 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
 \textbf{
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] }\\%& 
-%\textbf{
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
+\textbf{
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] }\\%& 
-%\textbf{
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] } & 
+\textbf{
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] }\\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] } &
 
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
 
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
 
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\%& 
-%\textbf{
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
+\textbf{
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
 
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
 
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
 
@@
 `r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\%&
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
 
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-%`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
 \hline
@@
 
-## Consumer extinctions increase genetic constraints
+```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
+Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
+Bold lines represent selection experienced in the original food web (orange) and with consumer extinctions (blue).
+Thin lines represent bootstrapped replicates to show the uncertainty in selection.
+For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
+knitr::include_graphics("../analyses/UV_landscapes.pdf")
+```
+
+To visualize the multivariate effects of these selective constraints, we plotted the adaptive landscape for each trait combination (fig.
+\ref{fig:MV_Landscape}).
+The arrows in fig.
+\ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while contours represent predicted survival of the mean phenotype in each food-web treatment.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the original food web.
+This is indicative of the increase in selective constraints resulting from consumer extinctions.
+
+```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
+Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
+Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the original food web.
+This indicates that consumer extinctions more strongly favored trait integration (covariance).
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
+knitr::include_graphics("../analyses/MV_landscapes.pdf")
+```
+
+## Consumer extinctions tend to increase genetic constraints
 
@@
 
-```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in the original food web (orange) and with consumer extinctions (blue).
-Thin lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
-knitr::include_graphics("../analyses/UV_landscapes.pdf")
-```
+Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
 
-Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
-In our study, this corresponds to:
+$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
+
+Of the different components of the curvature matrix, we found that only the curvature of oviposition preference differed between food-web treatments.
+Specifically, selection in the extinction food web acted to decrease the genetic variation in preference relative to the original food web.
+
+$$\textbf{C}_{\text{Original}} = \begin{pmatrix} 
+`r round(original_curvs_df["C.Diam","mean"],2)`\: [`r round(original_curvs_df["C.Diam","low"],2)`,`r round(original_curvs_df["C.Diam","high"],2)`] &  &  \\  
+`r round(original_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(original_curvs_df["C.Diam:Clutch","low"],2)`,`r round(original_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(original_curvs_df["C.Clutch","mean"],2)`\: [`r round(original_curvs_df["C.Clutch","low"],2)`,`r round(original_curvs_df["C.Clutch","high"],2)`] &  \\
+`r round(original_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(original_curvs_df["C.Diam:Pref","low"],2)`,`r round(original_curvs_df["C.Diam:Pref","high"],2)`] & `r round(original_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(original_curvs_df["C.Clutch:Pref","low"],2)`,`r round(original_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(original_curvs_df["C.Pref","mean"],2)`\: [`r round(original_curvs_df["C.Pref","low"],2)`,`r round(original_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Extinction}} = \begin{pmatrix} 
+`r round(extinction_curvs_df["C.Diam","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam","low"],2)`,`r round(extinction_curvs_df["C.Diam","high"],2)`] &  &  \\  
+`r round(extinction_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Clutch","low"],2)`,`r round(extinction_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(extinction_curvs_df["C.Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch","low"],2)`,`r round(extinction_curvs_df["C.Clutch","high"],2)`] &  \\
+`r round(extinction_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Pref","low"],2)`,`r round(extinction_curvs_df["C.Diam:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch:Pref","low"],2)`,`r round(extinction_curvs_df["C.Clutch:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Pref","low"],2)`,`r round(extinction_curvs_df["C.Pref","high"],2)`] \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Extinction-Original}} = \begin{pmatrix} 
+`r round(difference_curvs_df["C.Diam","mean"],2)`\: [`r round(difference_curvs_df["C.Diam","low"],2)`,`r round(difference_curvs_df["C.Diam","high"],2)`] &  &  \\  
+`r round(difference_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Clutch","low"],2)`,`r round(difference_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(difference_curvs_df["C.Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch","low"],2)`,`r round(difference_curvs_df["C.Clutch","high"],2)`] &  \\
+`r round(difference_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Pref","low"],2)`,`r round(difference_curvs_df["C.Diam:Pref","high"],2)`] & `r round(difference_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch:Pref","low"],2)`,`r round(difference_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(difference_curvs_df["C.Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Pref","low"],2)`,`r round(difference_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$
+
+Interestingly, when we translate the effect of the curvature matrix onto the G-matrix and evolvability of the next generation, we see that the extinction food web had a general tendency to decrease evolvability (fig.
+\ref{fig:Evolvability}).
+Specifically, the extinction food web decreased the average evolvability of `r round(sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff) * 100,0)`% of the random G-matrices in our simulation.
+If anything, we expect that this underestimates the true effect of our extinction treatment.
+For example, if we assume egg parasitoids would eventually impose similar impact on mean fitness once they are released from intraguild predation (i.e.
+extinction $\bar W$=original $\bar W$), then the extinction food web decreases the average evolvability in `r round(sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff) * 100,0)`% of the G-matrix scenarios.
+
+<!--In our study, this corresponds to:
 
@@
 \ref{fig:MV_Landscape}).
+-->
 
-```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
-Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the original food web.
-This indicates that consumer extinctions more strongly favored trait integration (covariance).
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
-knitr::include_graphics("../analyses/MV_landscapes.pdf")
+```{r Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment.
+We found that the curvature of the extinction food web decreased evolvability in 71% of the G-matrices, suggesting that consumer extinctions tended to decrease evolutionary potential in our study."}
+knitr::include_graphics("../analyses/delta_evolvability.pdf")
 ```
@@
 
-\begin{table}[h]
+\begin{table}[H]
 \caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
@@
 First, more traits contributed to the slope of the adaptive landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
-Second, excluding larval parasitoids indirectly increased the number of genetic constraints, which could act to constrain the gall midge's adaptive potential in the face of novel selection pressures.
+Second, excluding larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of the traits we measured.
+Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's adaptive potential in the face of novel selection pressures.
 Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
@@
 <!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
-This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by how genetic constraints interact with other evolutionary processes (e.g.
+This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
 genetic drift, gene flow, and mutation).<!-- This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
@@
 The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
-When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
+<!--When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
 Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
 Together, this suggests that consumer extinctions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
-Current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the community context [@McPeek2017; @Guimaraes2017].
+-->Current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the community context [@McPeek2017; @Guimaraes2017].
 Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that are shaped by the community context.
@@
 
-<!-- Caveats -->
+<!-- Caveats 
 Our study has some limitations to consider when relating our findings to the effect of consumer extinctions on evolutionary constraints more generally.
@@
 This is why we used more qualitative metrics of evolutionary constraints, which are robust to this artificial effect and simply require sufficient sample sizes to detect evidence of selection.
+-->
 <!--Note though that this should have made it more difficult to detect selection in this treatment, yet it was this extinction treatment that increased the number of traits under selection.
@@
 Importantly, we found that different species/guilds imposed different selection pressures.
-Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the community context.
+Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the ecological community.
 We expect that a continued integration of adaptive landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
 
-<!-- Remove for double-blind peer review process
 # Acknowledgements
@@
 Bascompte).
--->
+
 <!-- TABLE NOT REFERENCED IN RESULTS

### 2019-09-13 manuscript/manuscript.Rmd
edits before sending to Jordi; also incorporated Jordi's edits into Impact Summary.

@@
 \vspace*{0.1cm} 
-\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in the resulting food web \end{center}
+\begin{center} \LARGE Loss of consumers constrains phenotypic evolution in the resulting food web \end{center}
 
@@
 
-*Manuscript elements*: table 1, table 2, figure 1, figure 2, figure 3, figure 4. All figures should be printed in color.
+*Short Running Title*: Consumer loss constrains phenotypic evolution
 
@@
 
-*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid; complexity.
+*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid; complexity; biodiversity.
 
@@
 
-*Number of words*: `r wordcountaddin::word_count("manuscript.Rmd")`
+*Abstract Word Count*: 251
+
+\bigskip
+
+*Total Word Count*: `r wordcountaddin::word_count("manuscript.Rmd") - 587` <!-- subtract estimate of Abstract, Impact, Acknowledgements, Author Contributions, and Data Accessibility -->
 
@@
 The loss of biodiversity<!--Global change--> is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
-Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the community context of evolving populations as a ``black box''.
+Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the network context of evolving populations as a ``black box''.
 Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web structure shape evolutionary constraints.
-We conducted a field experiment that simulated the extinction of a guild of larval parasitoids that were able to impose selection on an insect herbivore.
-We then measured herbivore survival as a function of three key phenotypic traits.
-We found that the number of traits under selection increased with the extinction of larval parasitoids.
-In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.
-Our results suggest that the loss of trophic interactions due to consumer extinctions can impose greater constraints on phenotypic evolution.
+We conducted a field experiment that removed<!--simulated the extinction of--> a guild of larval parasitoids that imposed direct and indirect selection pressures on an insect herbivore.
+We then measured herbivore survival as a function of three key phenotypic traits to estimate directional, quadratic, and correlational selection gradients in each treatment.
+We used these selection gradients to characterize the slope and curvature of the adaptive landscape to understand the direct and indirect effects of consumer loss on evolutionary constraints.
+We found that the number of traits under directional selection increased with the removal of larval parasitoids, indicating greater selective constraints on the trajectory of evolutionary change.
+Similarly, we found that the removal of larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of the traits we measured in the next generation.<!--In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.--> Our results suggest that the loss of trophic interactions <!--due to consumer extinctions -->can impose greater constraints on phenotypic evolution.
 This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
@@
 
+# Impact Summary
+
+<!-- Authors should provide an approximately 300 word summary, explaining why the article makes an important contribution to Evolutionary Biology.
+It should be accessible to a wide audience, e.g.
+journalists, non-expert public interested in evolution, school science teachers.
+-->
+
+The loss of biodiversity is rewiring the web of life; however, we are currently in a poor position to predict how this will affect the ability of populations to evolve and adapt to future environments.
+To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or only allowed one of the predators to impose selection on a common prey.
+We found that the loss of predators increased the number of prey traits under selection.
+This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits.
+Moreover, we found that that the loss of predators could make it more difficult for prey to adapt to future environments.
+Taken together, our results suggest that the loss of biodiversity may rewire interactions in such a way that constrains the adaptive potential of remaining populations.
+
+\newpage
+
 <!-- > "What escapes the eye, however, is a much more insidious kind of extinction: the extinction of ecological interactions." @Janzen1974 -->
@@
 The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
-More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], and gives insight to the direct and indirect effects of selective constraints [@Arnold1992].
+More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], giving insight to the direct and indirect effects of selective constraints [@Arnold1992].
 Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.
 Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018].
-Resolution on how ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].
-
-Ecological networks, such as food webs describing who-eats-whom in ecological communities, provide an explicit representation of species interactions in an ecological community [@Bascompte2014; @McCann2012].
+Resolution on how change in ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].
+
+Ecological networks, such as food webs describing who-eats-whom, provide an explicit representation of the direct and indirect effects that emerge in a community of interacting species [@Bascompte2014; @McCann2012].
 Here, we integrate ecological networks and adaptive landscapes to understand how ecological communities constrain evolutionary change.
-The direct and indirect effects of selective constraints can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
+The direct and indirect effects of natural selection can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
 For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
@@
 Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities.
-To examine these different possibilities, we conducted a field experiment that simulated the extinction of a consumer guild associated with an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
+To examine these different possibilities, we conducted a field experiment that removed a consumer guild that directly and indirectly impacts fitness of an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
 \ref{fig:Conceptual}).
@@
 ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016].
-We manipulated food-web structure by either excluding the guild of larval parasitoids (extinction food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (original food web, fig.
+We manipulated food-web structure by either removing larval parasitoids (removal food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (original food web, fig.
 \ref{fig:Conceptual}).
@@
 <!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
--->Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
-We then applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
+-->Larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid (fig.
+\ref{fig:Conceptual}).
+We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
 Taken together, our study gives insight to how the loss of biodiversity may constrain the evolution of interacting populations.
@@
 In the original food web, we allowed the full suite of egg and larval parasitoids to impose selection.
-To simulate consumer extinction, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+In the removal food web, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
 Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
@@
 Marking galls with flagging tape ensured that all galls had similar phenology when we collected galls later in the season.
-To simulate consumer extinctions, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
+For the removal food web, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
 This treatment did not exclude the egg parasitoid *Platygaster* sp., which attacks prior to gall initiation [larva initiate gall development in Cecidomyiid midges: @Gagne1989].
@@
 To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
-We then scaled all phenotypic traits (mean=0 and SD=1) prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
+We then scaled all phenotypic traits (mean=0 and SD=1) across treatments prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
 
@@
 Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients.
-Third, we used our estimates of selection gradients to characterize the slope and curvature of the adaptive landscape, which we used to measure evolutionary constraints.
-Finally, we used a simulation to examine how the curvature of the adaptive landscape could alter the evolvability of populations in the next generation.
+Third, we used our estimates of directional selection gradients to characterize the slope of the adaptive landscape, which we used to measure selective constraints.
+Finally, we estimated the curvature of the adaptive landscape and used a simulation to explore its effects on the adaptive potential of the gall midge population in the next generation.
 
@@
 Although statistical models with random effects are not common in analyses of natural selection, we think that modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
-Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e., setting them to zero) when calculating selection surfaces.
+Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e.
+setting them to zero) when calculating selection surfaces.
 We then used parametric bootstrapping (1,000 replicates) to estimate the effect of food-web treatment on larval survival as well as selection surfaces in each food-web treatment.
-<!--To determine whether trait-fitness relationships differed between food-web treatments, we calculated the difference in bootstrapped replicates between treatments.-->
+To determine whether trait-fitness relationships differed between food-web treatments, we calculated the difference in bootstrapped replicates between treatments.
 
 **Selection gradients**: Selection gradients cannot be estimated directly from GLMMs of selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e., $\text{ln}\{W(z)/[1-W(z)]\}$) associated with 1 SD change in a trait with all other traits held fixed at their mean.
+For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e.
+$\text{ln}\{W(z)/[1-W(z)]\}$) associated with 1 SD change in a trait with all other traits held fixed at their mean.
 Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlational ($\gamma_{ij}$) selection gradients.
@@
 We estimated selection gradients separately for each food-web treatment.
+We also determined whether selection gradients differed between food-web treatments by calculating the difference in bootstrapped replicates between treatments.
 Note that we doubled all quadratic terms prior to calculating selection gradients to put them on the same scale as estimates of directional and correlational selection [@Stinchcombe2008].
 
-**Evolutionary constraints**: We measured evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
-The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
+**Selective constraints**: <!--We measured evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
+-->The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
 
@@
 where each $\beta_i$ corresponds to the directional selection gradient acting on each trait.
-By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e., 95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
-
-The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
+By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e.
+95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
+This gives insight as to whether there is a specific combination of phenotypes favored by natural selection (i.e.
+more traits under directional selection), or whether multiple trait combinations have comparable fitness (i.e.
+less traits under directional selection).
+
+**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 
@@
 where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
-In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
+<!--In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
 Similarly, any nonzero covariance terms (off-diagonal) indicate the effects of selection on additive genetic covariance between two traits.
-We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI.
+-->We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI.
 We also used this information to determine whether the curvature of each component differed between our food-web treatments.
@@
 Knowledge of the curvature matrix alone gives an incomplete picture of its indirect effect on genetic constraints.
-This is because genetic constraints are ultimately determined by the structure of the G-matrix, and thus may depend on its structure before selection.
-Although we do not know the underlying G-matrix for the traits we measured in this experiment, we can still gain insight to how our food-web treatment would alter genetic constraints.
-Specifically, we first calculated how our best estimate of the curvature matrix (mean values) in each treatment changed the structure of `r n_Gmats` random G-matrices.
-If we assume that recombination/mutation would have the same effect on gall midge populations in the original and extinction food webs, then we can estimate how the curvature matrix in the previous generation alters the G-matrix for the next generation.
-
-The G-matrix itself is a complex structure, but recent theory has shown how its structure affects the evolvability of a population [@Hansen2008].
+This is because genetic constraints are ultimately determined by the structure of the G-matrix, and therefore also depend on its structure before selection.
+Although we do not know the underlying G-matrix for the traits we measured in this experiment, we can still gain insight to how our food-web treatment would alter genetic constraints more generally.
+Specifically, we calculated how our best estimate of the curvature matrix (mean values) in each treatment changed the structure of `r n_Gmats` random G-matrices for the next generation.
+We restricted the range of additive genetic variance (*V~G~*) in these G-matrices to between 0 and 0.5 to reflect typical ranges in narrow-sense heritability values (*h*^2^; note that *h*^2^ = *V~G~* when the phenotypic variance is scaled to 1).
+Note that this analysis assumes that the effects of recombination and mutation on the G-matrix are much smaller than the effects of selection, which appears to be a reasonable assumption over short time scales [@Arnold2008].
+
+The G-matrix itself is a complex structure, but has a clear theoretical link to the evolvability of phenotypic traits [@Hansen2008].
 <!--We used evolvability as our measure of genetic constraint, as it has a solid foundation in theory of quantitative genetics and adaptive landscapes [@Hansen2008].
--->Evolvability measures the ability for a trait to evolve toward a given direction of selection, ignoring responses in every other direction [@Hansen2008].
-In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can assess its evolutionary potential by computing its average evolvability over random selection gradients (here, we used `r n_random_gradients`).
-By computing the average evolvability for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of a population.
+-->Evolvability measures the ability for a trait to evolve toward a given direction of selection [@Hansen2008].
+In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can compute its average evolvability over random selection gradients [@Hansen2008; @Melo2015].
+By computing the average evolvability (here, we used `r n_random_gradients` random $\beta$s) for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of the associated traits.
 We report the distribution of these effect sizes, rather than conduct a statistical test, because the number of replicates in a simulation can be arbitrarily high, thus making any effect size statistically significant [@White2014].
@@
 bias).
-We used a GLMM with the same structure as described above except that we modeled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
+We used a GLMM with the same structure as described previously except that we modeled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
 We detected a positive bias in both food-web treatments (original $\alpha_{\text{Diam}}$=
@@
 [`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.low,2)`,
-`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
+`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.high,2)`]; removal $\alpha_{\text{Diam}}$=
 `r round(fixef(biased_foodweb_model)["FoodwebExtinction:sc.Diam"],2)` 
@@
 Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate selection imposed by larval parasitoids.
-This comparison is still useful though in determining the extent to which the community context may have indirect evolutionary effects by altering selection on multiple interacting populations.
+This comparison is still useful though in determining the extent to which the loss of consumers may have indirect evolutionary effects by altering selection on multiple interacting populations.
 
@@
 
-## Consumer extinctions increase selective constraints
-
-\indent We found that the extinction of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
+## Consumer loss increases selective constraints
+
+\indent We found that the removal of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
 For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (table \ref{Table:Gradients}; fig.
@@
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`]).
-This conflicting selection is likely due to trait differences between guilds, as larger clutches may be easier targets for egg parasitoids to find, but also create a more complex gall structure that is more difficult for larval parasitoids to oviposit through.
+This conflicting selection is likely due to trait differences between guilds, as larger clutches may be easier targets for egg parasitoids to find, but the more complex gall structure may be more difficult for larval parasitoids to oviposit through.
 
@@
 \ref{fig:UV_Landscape}B); however, the overall magnitude of selection did not differ between treatments (table \ref{Table:Gradients}).
-Still, there was no clear evidence of selection on oviposition in the original food web (table \ref{Table:Gradients}).
-This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.
-Chamber diameter experienced positive directional selection in both food-web treatments (fig.
+Still, there was no clear evidence of directional selection on oviposition in the original food web (table \ref{Table:Gradients}).
+<!--This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.-->Chamber diameter experienced positive directional selection in both food-web treatments (fig.
 \ref{fig:UV_Landscape}A).
@@
 [`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival in the original food web <!--(original $\bar W$=
+`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival of gall midges in the original food web <!--(original $\bar W$=
 `r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$mean,2)` 
@@
 `r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
-We expect this difference to be transient though, since egg parasitoids would increase in abundance once they are released from intraguild predation, which would make the strength of selection on gall diameter comparable to the original food web (if extinction $\bar W$=original $\bar W$, then contrast $\beta_{\text{Diam}}$=
+We expect this difference to be transient though, since egg parasitoids would increase in abundance once they are released from intraguild predation, which would make the strength of selection on gall diameter comparable to the original food web (if removal $\bar W$=original $\bar W$, then contrast $\beta_{\text{Diam}}$=
 `r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$mean,2)` 
@@
 `r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]).
-It is worth noting that this pattern of selection is unexpected.
-For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is strongly correlated with another unmeasured trait that is under selection (e.g.
+It is worth noting that positive selection on chamber diameter in both treatments was unexpected.
+For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is strongly correlated with an unmeasured trait that is under selection (e.g.
 immune response).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
@@
 \begin{table}[H]
-\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
+\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
 \label{Table:Gradients}
@@
 \hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction} & \textbf{Contrast} \\
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
 \hline
@@
 
-```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
+```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
 Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in the original food web (orange) and with consumer extinctions (blue).
+Bold lines represent selection experienced in the original (orange) and removal (blue) food webs (orange).
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 
-To visualize the multivariate effects of these selective constraints, we plotted the adaptive landscape for each trait combination (fig.
+To visualize the multivariate effects of these selective constraints, we plotted the adaptive landscape for each trait combination in each treatment (fig.
 \ref{fig:MV_Landscape}).
@@
 \ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while contours represent predicted survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the original food web.
-This is indicative of the increase in selective constraints resulting from consumer extinctions.
-
-```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the extinction of larval parasitoids.
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
+This indicates that the loss of consumers more strongly favored a specific combination of traits, rather than allowing for multiple trait combinations to have comparable fitness.
+
+```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
 Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the extinction of larval parasitoids compared to the original food web.
-This indicates that consumer extinctions more strongly favored trait integration (covariance).
+Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
+This indicates that the loss of consumers more strongly favored a specific combination of traits.
 Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
@@
 
-## Consumer extinctions tend to increase genetic constraints
+## Consumer loss indirectly increases genetic constraints
 
@@
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
+This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.
 
@@
 Of the different components of the curvature matrix, we found that only the curvature of oviposition preference differed between food-web treatments.
-Specifically, selection in the extinction food web acted to decrease the genetic variation in preference relative to the original food web.
+Specifically, selection in the removal food web acted to decrease the additive genetic variance in preference relative to the original food web.
 
@@
 
-Interestingly, when we translate the effect of the curvature matrix onto the G-matrix and evolvability of the next generation, we see that the extinction food web had a general tendency to decrease evolvability (fig.
+Interestingly, when we translate the effect of the curvature matrix onto genetic constraints in the next generation, we see that the loss of consumers had a general tendency to decrease evolvability (fig.
 \ref{fig:Evolvability}).
-Specifically, the extinction food web decreased the average evolvability of `r round(sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff) * 100,0)`% of the random G-matrices in our simulation.
-If anything, we expect that this underestimates the true effect of our extinction treatment.
+Specifically, the removal food web decreased the average evolvability of `r round(sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff) * 100,0)`% of the random G-matrices in our simulation.
+If anything, we expect that this underestimates the true effect of our removal treatment.
 For example, if we assume egg parasitoids would eventually impose similar impact on mean fitness once they are released from intraguild predation (i.e.
-extinction $\bar W$=original $\bar W$), then the extinction food web decreases the average evolvability in `r round(sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff) * 100,0)`% of the G-matrix scenarios.
+removal $\bar W$=original $\bar W$), then the removal food web decreases the average evolvability in `r round(sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff) * 100,0)`% of the G-matrix scenarios.
 
@@
 ```{r Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment.
-We found that the curvature of the extinction food web decreased evolvability in 71% of the G-matrices, suggesting that consumer extinctions tended to decrease evolutionary potential in our study."}
+We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices, suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
 knitr::include_graphics("../analyses/delta_evolvability.pdf")
@@
 
-The extinction of larval parasitoids only altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}).
-Specifically, the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
+The removal of larval parasitoids not only had direct effects on gall midge fitness, but also imposed indirect effects that would be felt in the next generation.
+For example, the removal of larval parasitoids altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}), such that the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
 \ref{fig:EggPtoid_Selection}).
@@
 ```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid (original - extinction of larval parastioids) as a function of gall midge oviposition preference.
+The bold line represents the average difference in the probability of observing the egg parasitoid (original - removal of larval parastioids) as a function of gall midge oviposition preference.
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 <!--Summary-->
-We found that the extinction of larval parasitoids constrained phenotypic evolution in gall midges in two key ways.
+We found that the removal of larval parasitoids constrained phenotypic evolution in gall midges in two key ways.
 First, more traits contributed to the slope of the adaptive landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
-Second, excluding larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of the traits we measured.
+Second, excluding larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of associated traits.
 Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's adaptive potential in the face of novel selection pressures.
 Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
-Taken together, our study provides experimental evidence from the field that consumer extinctions may constrain the adaptive potential of remaining populations.
+Taken together, our study provides experimental evidence from the field that the loss of consumers may constrain the adaptive potential of remaining populations.
 
@@
 <!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
-This also implies that as selective constraints dampen in more complex food webs, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
+This also implies that as selective constraints dampen in food webs with more consumers, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
 genetic drift, gene flow, and mutation).<!-- This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
@@
 @Schluter1996 found support for this hypothesis from data on natural populations of several vertebrate species, including threespine sticklebacks, a few species of songbirds, and mice from the genus *Peromyscus*.
-All of these species occupy intermediate trophic levels and are likely embedded in complex food webs, which is consistent with our suggestion that genetic constraints may have a stronger influence in more complex food webs.
+All of these species occupy intermediate trophic levels and are likely embedded in complex food webs, which is consistent with our suggestion that genetic constraints may have a stronger influence in food webs with more consumers.
 
 <!--Indirect effects of selective constraints-->
-We also found evidence for more genetic constraints when we excluded larval parasitoids due to indirect effects of selection on the population's G-matrix.
-The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
-<!--When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
+We also found evidence for a general decrease in trait evolvability when we excluded larval parasitoids due to changes in the curvature of the adaptive landscape<!--indirect effects of selection on the population's G-matrix-->.
+This result was driven by nonlinear selection on gall midge oviposition preference in the original food web, which was due to both increases in intraguild predation and the lower mean survival of gall midges.
+While these results are intriguing, they still indicate that the indirect effects of selection are contingent on the structure of a population's G-matrix (i.e.
+consumer removals *increased* evolvability in 29% of the scenarios).
+This highlights the importance of future studies to characterize the G-matrix in order to accurately predict how changes in network context will alter the evolutionary potential of remaining populations.
+<!--The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
+When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
 Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
 Together, this suggests that consumer extinctions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
--->Current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the community context [@McPeek2017; @Guimaraes2017].
-Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that are shaped by the community context.
+-->Indeed, current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017].
+Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that emerge in a network of interacting species.
 
@@
 The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
-For example, if consumers do not differ from each other, then we do not expect changes in food-web structure to modify evolutionary constraints.
+For example, if consumers do not differ from each other, then we do not expect the loss of consumers to modify evolutionary constraints.
 Also, many consumers may be at too low of abundances to impose selection on their resources.
 Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
-When consumers are abundant though, the effect of food-web structure will depend on whether different species impose conflicting selection pressures or select for distinct traits.
+This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles.
+When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits.
 For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
 Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.
-On the other hand, different consumers may impose selection on different traits, favoring trait integration and increasing genetic constraints.
+On the other hand, different consumers may impose selection on different traits, favoring a particular combination of traits and thus greater selective constraints.
 Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
@@
 <!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
+
+<!-- Caveats -->
+An important caveat of our study is that we did not due a factorial manipulation of both parasitoid guilds, making it difficult to conclude whether our results would change if we manipulated the presence/absence of the dominant egg parasitoid.
+If we assume that higher-order interactions [@Levine2017] are weak between parasitoid guilds, then we can gain insight to how the loss of the egg parasitoid would alter selection by isolating the contribution of larval parasitoids to selection in our original food-web treatment.
+When we do this, we see the same qualitative effects as we do when we removed larval parasitoids.
+For example, we see clear evidence of all three traits being under directional selection (i.e.
+greater selective constraints, Appendix A) as well as a decrease, albeit smaller, in trait evolvability under different G-matrix scenarios (`r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`%, Appendix A).
+This suggests that our results could be robust to this caveat, which was simply not possible to manipulate given the biology of our system (see *Manipulating Food-web Structure* section for explanation).
 
@@
 A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
-If indirect evolutionary effects are common [@Miller1996; @Walsh2013], then predicting evolutionary trajectories resulting from consumer extinctions will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
+If indirect evolutionary effects are common [@Miller1996; @Walsh2013], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 
@@
 This work has given insight to the mechanisms by which interactions between species can modify their adaptive potential<!--pairwise interactions modify the adaptive potential of species-->.
-Our study hints at a novel mechanism, whereby more complex food webs flatten the adaptive landscape, thus facilitating future adaptation by allowing genetic and phenotypic variation to persist.
+Our study hints at a novel mechanism, whereby a more diverse consumer community alters the adaptive landscape in such a way that facilitates future adaptation by allowing genetic and phenotypic variation to persist.
 This mechanism only emerges once we consider selection imposed by multiple species on multiple traits.
@@
 <!-- Conclusions -->
-Our study gives insight to how consumer extinctions alter evolutionary constraints on remaining populations.
+Our study gives insight to how the loss of consumers alters evolutionary constraints on remaining populations.
 In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
-Our work also highlights some key challenges for predicting phenotypic evolution in the face of global change.
+Our work also highlights some key challenges for predicting phenotypic evolution in rapidly changing communities.
 First, the simplification of ecological communities may actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.
@@
 Bascompte).
+
+# Author Contributions
+
+M.A.B.
+conceived the idea behind the study and designed the field experiment.
+M.A.B.
+and B.L.
+setup and conducted the experiment.
+M.A.B., A.S., and C.J.G.
+collected the data.
+M.A.B.
+analyzed the data.
+M.A.B.
+wrote the manuscript with primary input from J.B.
+and additional feedback from C.J.G.
+
+# Data Accessibility
+
+All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
 
@@
 -->
+
+# Appendix A
+
+\bigskip
+
+\begin{table}[H]
+\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web.
+This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
+\label{Table:LarvalGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
+\hline
+$\beta_{\text{Diam}}$ & 
+%\textbf{
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
+\textbf{
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } \\
+
+$\beta_{\text{Clutch}}$ & 
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] }\\
+
+$\beta_{\text{Pref}}$ &
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] } \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`]  \\
+
+$\gamma_{\text{Clutch:Clutch}}$ & 
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref:Pref}}$ & 
+%\textbf{
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam:Clutch}}$ & 
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`]  \\
+
+$\gamma_{\text{Diam:Pref}}$ & 
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]  \\
+
+$\gamma_{\text{Clutch:Pref}}$ & 
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`]  \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+<!-- Add the XX% change in evolvability -->
+
+```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs.
+the original food web.
+We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices, which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
+knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")
+```

### 2019-09-13 manuscript/manuscript.Rmd
incorporated minor edits from Jordi

@@
 More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], giving insight to the direct and indirect effects of selective constraints [@Arnold1992].
-Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic [@Schluter2000; @Abrams2000] and mutualistic [@Bronstein2006] interactions in driving evolutionary change.
+Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006].
 Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018].
@@
 
-```{r Conceptual, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
+```{r Conceptual, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
 Black arrows denote the flow of energy in this network of trophic interactions.
@@
 
-**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) is governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
+**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) are governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
@@
 
-```{r UV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
+```{r UV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
 Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
@@
 
-```{r MV_Landscape, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
+```{r MV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
@@
 
-$$\textbf{C}_{\text{Extinction}} = \begin{pmatrix} 
+$$\textbf{C}_{\text{Removal}} = \begin{pmatrix} 
 `r round(extinction_curvs_df["C.Diam","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam","low"],2)`,`r round(extinction_curvs_df["C.Diam","high"],2)`] &  &  \\  
@@
 
-$$\textbf{C}_{\text{Extinction-Original}} = \begin{pmatrix} 
+$$\textbf{C}_{\text{Removal-Original}} = \begin{pmatrix} 
 `r round(difference_curvs_df["C.Diam","mean"],2)`\: [`r round(difference_curvs_df["C.Diam","low"],2)`,`r round(difference_curvs_df["C.Diam","high"],2)`] &  &  \\  
@@
 
-```{r Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment.
-We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices, suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
+```{r Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment.
+We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices (i.e.
+the change in evolvability was negative for 71% of the simulations), suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
 knitr::include_graphics("../analyses/delta_evolvability.pdf")
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
@@
 \hline
-\textbf{Selection gradient} & \textbf{Contrast = Original - Extinction}  \\ 
+\textbf{Selection gradient} & \textbf{Contrast = Original - Removal}  \\ 
 \hline
@@
 
-```{r EggPtoid_Selection, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid (original - removal of larval parastioids) as a function of gall midge oviposition preference.
+```{r EggPtoid_Selection, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.).
+The bold line represents the average difference in the probability of observing the egg parasitoid (original minus removal of larval parastioids) as a function of gall midge oviposition preference.
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
-We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.
+We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions [@Bascompte2009].
 <!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
@@
 A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
-If indirect evolutionary effects are common [@Miller1996; @Walsh2013], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
+If indirect evolutionary effects are common [@Miller1996; @Walsh2013; @Guimaraes2017], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 
@@
 
-\begin{table}[H]
+\begin{table}[h]
 \caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web.
@@
 
-```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="H", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs.
+```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs.
 the original food web.
-We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices, which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
+We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e.
+the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
 knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")

### 2019-09-13 analyses/reproduce_analyses.Rmd
updated file and changed figures labels in main text to "removal" instead of "extinction".

@@
 
-```{r Table of differences in food web coefficients, include=FALSE}
+```{r Table of differences in food web coefficients}
 tidy_foodweb_alphas %>%
@@
 
-```{r Curvature}
+```{r Curvature, echo=TRUE}
 # Get mean estimates for directional selection gradients
@@
          `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - foodweb_original_mean_sc.Diam*foodweb_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
-         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_extinction_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
+         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - foodweb_original_mean_sc.log.Clutch*foodweb_original_mean_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
 
@@
 
-```{r Table of food web curvatures, include=FALSE}
+```{r Table of food web curvatures}
 tidy_foodweb_curvs %>%
@@
 
-```{r Table of differences in curvatures between food-web treatments, include=FALSE}
+```{r Table of differences in curvatures between food-web treatments}
 tidy_foodweb_curvs %>%
@@
 
-```{r Tidy up long-term selection gradients}
+```{r Tidy up long-term selection gradients, echo=TRUE}
 # Calculate differences between food-web treatments, then estimate means and confidence intervals
@@
 
-```{r Curvature long-term, include=FALSE}
+```{r Curvature long-term, echo=TRUE}
 # Get mean estimates for directional selection gradients
@@
 
-```{r Table of differences in long-term curvatures between food-web treatments, include=FALSE}
+```{r Table of differences in long-term curvatures between food-web treatments}
 tidy_foodweb_long_curvs %>%
@@
 
+```{r Curvature egg vs. larval, echo=TRUE}
+# Get mean estimates for directional selection gradients
+egglarval_original_mean_sc.Diam <- filter(tidy_egglarval_grads, type == "Original", term == "sc.Diam")$mean
+egglarval_original_mean_sc.log.Clutch <- filter(tidy_egglarval_grads, type == "Original", term == "sc.log.Clutch")$mean
+egglarval_original_mean_sc.sqrt.Pref <- filter(tidy_egglarval_grads, type == "Original", term == "sc.sqrt.Pref")$mean
+
+egglarval_extinction_mean_sc.Diam <- filter(tidy_egglarval_grads, type == "Extinction", term == "sc.Diam")$mean
+egglarval_extinction_mean_sc.log.Clutch <- filter(tidy_egglarval_grads, type == "Extinction", term == "sc.log.Clutch")$mean
+egglarval_extinction_mean_sc.sqrt.Pref <- filter(tidy_egglarval_grads, type == "Extinction", term == "sc.sqrt.Pref")$mean
+
+# Calculate curvatures for original food web
+egglarval_original_raw_curvs <- egglarval_original_raw_gradients %>%
+  transmute(`FoodwebOriginal:C.Diam` = `FoodwebOriginal:I(sc.Diam^2)` - egglarval_original_mean_sc.Diam*egglarval_original_mean_sc.Diam, #`FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.Diam`,
+         `FoodwebOriginal:C.Clutch` = `FoodwebOriginal:I(sc.log.Clutch^2)` - egglarval_original_mean_sc.log.Clutch*egglarval_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Pref` = `FoodwebOriginal:I(sc.sqrt.Pref^2)` - egglarval_original_mean_sc.sqrt.Pref*egglarval_original_mean_sc.sqrt.Pref, #`FoodwebOriginal:sc.sqrt.Pref`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Diam:Clutch` = `FoodwebOriginal:sc.Diam:sc.log.Clutch` - egglarval_original_mean_sc.Diam*egglarval_original_mean_sc.log.Clutch, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.log.Clutch`,
+         `FoodwebOriginal:C.Diam:Pref` = `FoodwebOriginal:sc.Diam:sc.sqrt.Pref` - egglarval_original_mean_sc.Diam*egglarval_original_mean_sc.sqrt.Pref, # `FoodwebOriginal:sc.Diam`*`FoodwebOriginal:sc.sqrt.Pref`,
+         `FoodwebOriginal:C.Clutch:Pref` = `FoodwebOriginal:sc.log.Clutch:sc.sqrt.Pref` - egglarval_original_mean_sc.log.Clutch*egglarval_original_mean_sc.sqrt.Pref) # `FoodwebOriginal:sc.log.Clutch`*`FoodwebOriginal:sc.sqrt.Pref`)
+
+# Calculate curvatures for extinction food web
+egglarval_extinction_raw_curvs <- egglarval_extinction_raw_gradients %>%
+  transmute(`FoodwebExtinction:C.Diam` = `FoodwebExtinction:I(sc.Diam^2)` - egglarval_extinction_mean_sc.Diam*egglarval_extinction_mean_sc.Diam, #`FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.Diam`,
+         `FoodwebExtinction:C.Clutch` = `FoodwebExtinction:I(sc.log.Clutch^2)` - egglarval_extinction_mean_sc.log.Clutch*egglarval_extinction_mean_sc.log.Clutch, # `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Pref` = `FoodwebExtinction:I(sc.sqrt.Pref^2)` - egglarval_extinction_mean_sc.sqrt.Pref*egglarval_extinction_mean_sc.sqrt.Pref,# `FoodwebExtinction:sc.sqrt.Pref`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Diam:Clutch` = `FoodwebExtinction:sc.Diam:sc.log.Clutch` - egglarval_extinction_mean_sc.Diam*egglarval_extinction_mean_sc.log.Clutch, # `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.log.Clutch`,
+         `FoodwebExtinction:C.Diam:Pref` = `FoodwebExtinction:sc.Diam:sc.sqrt.Pref` - egglarval_extinction_mean_sc.Diam*egglarval_extinction_mean_sc.sqrt.Pref,# `FoodwebExtinction:sc.Diam`*`FoodwebExtinction:sc.sqrt.Pref`,
+         `FoodwebExtinction:C.Clutch:Pref` = `FoodwebExtinction:sc.log.Clutch:sc.sqrt.Pref` - egglarval_extinction_mean_sc.log.Clutch*egglarval_extinction_mean_sc.sqrt.Pref)# `FoodwebExtinction:sc.log.Clutch`*`FoodwebExtinction:sc.sqrt.Pref`)
+
+# Calculate differences between food-web treatments, then estimate means and confidence intervals
+egglarval_curvs <- bind_cols(egglarval_original_raw_curvs, egglarval_extinction_raw_curvs) %>%
+  mutate(`FoodwebDiff:C.Diam` = `FoodwebExtinction:C.Diam` - `FoodwebOriginal:C.Diam`,
+         `FoodwebDiff:C.Clutch` = `FoodwebExtinction:C.Clutch` - `FoodwebOriginal:C.Clutch`,
+         `FoodwebDiff:C.Pref` = `FoodwebExtinction:C.Pref` - `FoodwebOriginal:C.Pref`,
+         `FoodwebDiff:C.Diam:Clutch` = `FoodwebExtinction:C.Diam:Clutch` - `FoodwebOriginal:C.Diam:Clutch`,
+         `FoodwebDiff:C.Diam:Pref` = `FoodwebExtinction:C.Diam:Pref` - `FoodwebOriginal:C.Diam:Pref`,
+         `FoodwebDiff:C.Clutch:Pref` = `FoodwebExtinction:C.Clutch:Pref` - `FoodwebOriginal:C.Clutch:Pref`) %>%
+  summarise_all(funs(mean, conf.high, conf.low))
+
+# Tidy up estimates
+tidy_egglarval_curvs <- egglarval_curvs %>%
+  t() %>%
+  as.data.frame() %>%
+  transmute(rows = rownames(.), value=V1) %>%
+  separate(col = rows, into = c("term","estimate"), sep="_") %>%
+  separate(col = term, into = c("type","term_1","term_2"), sep=":", extra="drop") %>%
+  mutate(term = ifelse(is.na(term_2), term_1, paste(term_1,term_2,sep=":"))) %>%
+  separate(col = type, into = c("extra","type"), sep = 7) %>%
+  select(type, term, estimate, value) %>%
+  mutate(type = factor(type, levels = c("Original", "Extinction", "Diff"))) %>%
+  spread(estimate, value) %>%
+  mutate(P_cutoff = ifelse(conf.high*conf.low < 0, "","*"))#,
+         #gradient_type = ifelse(grepl("\\^2", .$term)==TRUE, "Quadratic",
+         #                       ifelse(grepl(":", .$term)==TRUE, "Correlational","Directional")),
+         #mean = ifelse(gradient_type=="Quadratic", 2*mean, mean),
+         #conf.low = ifelse(gradient_type=="Quadratic", 2*conf.low, conf.low),
+         #conf.high = ifelse(gradient_type=="Quadratic", 2*conf.high, conf.high))
+```
+
+```{r Table of curvatures for egg and larval parasitoids}
+tidy_egglarval_curvs %>%
+  filter(type != "Diff") %>%
+  select(term, type, mean, conf.low, conf.high, P_cutoff) %>% 
+  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of curvatures on gall traits due to egg and larval parasitoids.")
+```
+
+```{r Table of differences in curvatures between egg and larval parasitoids}
+tidy_egglarval_curvs %>%
+  filter(type == "Diff") %>%
+  select(term, mean, conf.low, conf.high, P_cutoff) %>%
+  mutate(mean = round(mean, 2), conf.low = round(conf.low, 2), conf.high = round(conf.high, 2)) %>%
+  knitr::kable(., caption = "Table of differences in curvatures on gall traits between egg and larval parasitoids.")
+```
+
 ## Reproduce Figure 2 in main text
@@
   mutate(ID_group = ifelse(ID == "average", "average", "replicate"),
-         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction"))) %>% 
+         Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal"))) %>% 
   ggplot(., aes(x=sc.Diam, y=absolute_fitness, group=interaction(ID,Foodweb), color=Foodweb, alpha=ID_group, size=ID_group)) +
@@
 # Make plots
-AF_uni_plots <- plot_grid(AF_uni_Diam + theme(legend.position = "none"), 
+AF_uni_plots <- plot_grid(AF_uni_Clutch + theme(legend.position = "none"),
                           AF_uni_Pref + theme(legend.position = "none", 
                                            axis.title.y = element_blank()) + xlab("Preference (SDs)"),
-                      AF_uni_Clutch + theme(legend.position = "none",
+                          AF_uni_Diam + theme(legend.position = "none",
                                              axis.title.y = element_blank()), 
@@
 breaks <- predict(foodweb_model, newdata=data.frame(sc.Diam = c(0,0), sc.log.Clutch = c(0,0), sc.sqrt.Pref = c(0,0), Foodweb = c("Original","Extinction")), type="response", re.form=~0)
-names(breaks) <- c("Original","Extinction")
+names(breaks) <- c("Original","Removal")
 
@@
 RF_Diam.Clutch$absolute_fitness <- RF_Diam.Clutch$absolute_fitness %>%
-  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))
+  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal")))
 
@@
   stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Removal"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Clutch$absolute_fitness, Foodweb == "Removal"), aes(z = average), breaks = breaks["Removal"], linetype = "dotted", color = "black") +
   facet_wrap(~Foodweb) + # , labeller = labeller_2D
@@
 RF_Diam.Pref$absolute_fitness <- RF_Diam.Pref$absolute_fitness %>% 
-  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))
+  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal")))
 
@@
   stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Removal"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Diam.Pref$absolute_fitness, Foodweb == "Removal"), aes(z = average), breaks = breaks["Removal"], linetype = "dotted", color = "black") +
   facet_wrap(~Foodweb) + # , labeller = labeller_2D
@@
 RF_Clutch.Pref$absolute_fitness <- RF_Clutch.Pref$absolute_fitness %>%
-  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Extinction"), levels = c("Original", "Extinction")))
+  mutate(Foodweb = factor(ifelse(Foodweb == "Original", "Original", "Removal"), levels = c("Original", "Removal")))
 
@@
   stat_contour(aes(z = average), breaks = breaks["Original"], linetype = "dotted", color = "black") +
-  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Extinction"), aes(fill=average)) +
-  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Extinction"), aes(z = average), breaks = breaks["Extinction"], linetype = "dotted", color = "black") +
+  geom_raster(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Removal"), aes(fill=average)) +
+  stat_contour(data = filter(RF_Clutch.Pref$absolute_fitness, Foodweb == "Removal"), aes(z = average), breaks = breaks["Removal"], linetype = "dotted", color = "black") +
   facet_wrap(~Foodweb) + # , labeller = labeller_2D
@@
 
+```{r Curvatures in matrix form, echo=TRUE}
+## Original
+
+# Get curvatures from original food web
+original_curvs_df <- tidy_foodweb_curvs %>%
+  filter(type=="Original") %>%
+  select(term, mean, low=conf.low, high=conf.high)
+
+rownames(original_curvs_df) <- original_curvs_df$term
+
+## Extinction
+
+# Get curvatures from extinction food web
+extinction_curvs_df <- tidy_foodweb_curvs %>%
+  filter(type=="Extinction") %>%
+  select(term, mean, low=conf.low, high=conf.high)
+
+rownames(extinction_curvs_df) <- extinction_curvs_df$term
+
+## Difference
+difference_curvs_df <- tidy_foodweb_curvs %>%
+  filter(type=="Diff") %>%
+  select(term, mean, low=conf.low, high=conf.high)
+
+rownames(difference_curvs_df) <- difference_curvs_df$term
+```
+
+$$\textbf{C}_{\text{Original}} = \begin{pmatrix} 
+`r round(original_curvs_df["C.Diam","mean"],2)`\: [`r round(original_curvs_df["C.Diam","low"],2)`,`r round(original_curvs_df["C.Diam","high"],2)`] &  &  \\  
+`r round(original_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(original_curvs_df["C.Diam:Clutch","low"],2)`,`r round(original_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(original_curvs_df["C.Clutch","mean"],2)`\: [`r round(original_curvs_df["C.Clutch","low"],2)`,`r round(original_curvs_df["C.Clutch","high"],2)`] &  \\
+`r round(original_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(original_curvs_df["C.Diam:Pref","low"],2)`,`r round(original_curvs_df["C.Diam:Pref","high"],2)`] & `r round(original_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(original_curvs_df["C.Clutch:Pref","low"],2)`,`r round(original_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(original_curvs_df["C.Pref","mean"],2)`\: [`r round(original_curvs_df["C.Pref","low"],2)`,`r round(original_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Extinction}} = \begin{pmatrix} 
+`r round(extinction_curvs_df["C.Diam","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam","low"],2)`,`r round(extinction_curvs_df["C.Diam","high"],2)`] &  &  \\  
+`r round(extinction_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Clutch","low"],2)`,`r round(extinction_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(extinction_curvs_df["C.Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch","low"],2)`,`r round(extinction_curvs_df["C.Clutch","high"],2)`] &  \\
+`r round(extinction_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Pref","low"],2)`,`r round(extinction_curvs_df["C.Diam:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch:Pref","low"],2)`,`r round(extinction_curvs_df["C.Clutch:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Pref","low"],2)`,`r round(extinction_curvs_df["C.Pref","high"],2)`] \end{pmatrix}$$
+
+$$\textbf{C}_{\text{Extinction-Original}} = \begin{pmatrix} 
+`r round(difference_curvs_df["C.Diam","mean"],2)`\: [`r round(difference_curvs_df["C.Diam","low"],2)`,`r round(difference_curvs_df["C.Diam","high"],2)`] &  &  \\  
+`r round(difference_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Clutch","low"],2)`,`r round(difference_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(difference_curvs_df["C.Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch","low"],2)`,`r round(difference_curvs_df["C.Clutch","high"],2)`] &  \\
+`r round(difference_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Pref","low"],2)`,`r round(difference_curvs_df["C.Diam:Pref","high"],2)`] & `r round(difference_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch:Pref","low"],2)`,`r round(difference_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(difference_curvs_df["C.Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Pref","low"],2)`,`r round(difference_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$
+
 Below is the code used to get estimates for the slope ($\beta$) and curvature ($\gamma-\beta\beta^\text{T}$) of the adaptive landscape in each food-web treatment.
@@
 
-```{r Mean curvature effects on random G-matrices, echo=TRUE}
+```{r Mean curvature effects on random G-matrices, echo=TRUE, cache=TRUE}
 ## Generate random G-matrices
-random_Gmats <- RandomMatrix(num.traits = 3, num.matrices = 10000, min.var = 0, max.var = 0.5)
+n_Gmats <- 10000
+min_variance <- 0
+max_variance <- 0.5
+set.seed(34)
+random_Gmats <- RandomMatrix(num.traits = 3, num.matrices = n_Gmats, min.var = min_variance, max.var = max_variance)
 
@@
 
+n_random_gradients <- 1000
+
 ## Functions to calculate effect of mean curvature on random G-matrices
@@
   new_Gmat <- x + x %*% mean_curv_original %*% x
-  MeanMatrixStatistics(new_Gmat, iterations = 1000, parallel = TRUE)["evolvability"]
+  try(MeanMatrixStatistics(new_Gmat, iterations = n_random_gradients, parallel = TRUE))["evolvability"]
 }
@@
   new_Gmat <- x + x %*% mean_curv_extinction %*% x
-  MeanMatrixStatistics(new_Gmat, iterations = 1000, parallel = TRUE)["evolvability"]
+  try(MeanMatrixStatistics(new_Gmat, iterations = n_random_gradients, parallel = TRUE))["evolvability"]
 }
@@
 original_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_original_random_matrices_evolvabilities)) %>%
-  select(Original = evolvability)
+  mutate(Original = as.numeric(evolvability))
 
 extinction_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_extinction_random_matrices_evolvabilities)) %>% 
-  select(Extinction = evolvability)
+  mutate(Extinction = as.numeric(evolvability))
 
 random_evolvabilities <- bind_cols(original_evolvability_list, extinction_evolvability_list) %>%
+  drop_na() %>%
   mutate(Diff = Extinction - Original)
@@
 
-We see that for our best estimates of the curvature matrix, that the extinction food web tends to decrease evolvability (`r sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff)`) of the gall midge population.
-
-```{r Delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices using our best (mean) estimates of the curvature matrix."}
+We see that for our best estimates of the curvature matrix, that the extinction food web tends to decrease evolvability (`r round(sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff) * 100,0)`%) of the gall midge population.
+
+```{r Delta evolvability, fig.cap = "Change in evolvability for `r n_Gmats` random G-matrices using our best (mean) estimates of the curvature matrix."}
 delta_evolvability_plot <- ggplot(random_evolvabilities, aes(x = Diff)) +
-  geom_histogram() +
+  geom_histogram(alpha = 0.5, binwidth = 0.001) +
   geom_vline(xintercept = 0, linetype = "dotted") +
-  xlab(expression(paste(Delta," evolvability (extinction - original)"))) +
+  xlab(expression(paste(Delta," evolvability (removal - original)"))) +
   ylab("Count")
@@
 
-```{r Long-term mean curvature effects on random G-matrices, echo=TRUE}
+```{r Long-term mean curvature effects on random G-matrices, echo=TRUE, cache=TRUE}
 ## Use same random G-matrices as above
@@
   new_Gmat <- x + x %*% long_mean_curv_extinction %*% x
-  MeanMatrixStatistics(new_Gmat, iterations = 1000, parallel = TRUE)["evolvability"]
+  try(MeanMatrixStatistics(new_Gmat, iterations = n_random_gradients, parallel = TRUE))["evolvability"]
 }
@@
 long_extinction_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_long_extinction_random_matrices_evolvabilities)) %>% 
-  select(Extinction = evolvability)
+  mutate(Extinction = as.numeric(evolvability))
 
 long_random_evolvabilities <- bind_cols(original_evolvability_list, long_extinction_evolvability_list) %>%
+  drop_na() %>%
   mutate(Diff = Extinction - Original)
@@
 
-Over the long-term (after egg parasitoids recover and impose similar fitness impact), we see that for our best estimates of the curvature matrix, that the extinction food web tends to decrease evolvability (`r sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff)`) of the gall midge population.
-
-```{r Long-term delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices using our best (mean) estimates of the curvature matrix over the long term."}
+Over the long-term (after egg parasitoids recover and impose similar fitness impact), we see that for our best estimates of the curvature matrix, that the extinction food web tends to decrease evolvability (`r round(sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff) * 100,0)`%) of the gall midge population.
+
+```{r Long-term delta evolvability, fig.cap = "Change in evolvability for 1,000 random G-matrices using our best (mean) estimates of the curvature matrix over the long term."}
 long_delta_evolvability_plot <- ggplot(long_random_evolvabilities, aes(x = Diff)) +
-  geom_histogram() +
+  geom_histogram(alpha = 0.5) +
   geom_vline(xintercept = 0, linetype = "dotted") +
-  xlab(expression(paste(Delta," evolvability (extinction - original)"))) +
+  xlab(expression(paste(Delta," evolvability (removal - original)"))) +
   ylab("Count")
@@
 long_delta_evolvability_plot
+```
+
+Now we look at the curvature effects of larval parasitoids compared to the original food web.
+
+```{r Mean curvature effects of larval parasitoids on random G-matrices, echo=TRUE, cache=TRUE}
+
+# Extinction
+larvalptoid_mean_C.Diam <- filter(tidy_egglarval_curvs, type == "Original", term == "C.Diam")$mean
+larvalptoid_mean_C.Clutch <- filter(tidy_egglarval_curvs, type == "Original", term == "C.Clutch")$mean
+larvalptoid_mean_C.Pref <- filter(tidy_egglarval_curvs, type == "Original", term == "C.Pref")$mean
+larvalptoid_mean_C.Diam.Clutch <- filter(tidy_egglarval_curvs, type == "Original", term == "C.Diam:Clutch")$mean
+larvalptoid_mean_C.Diam.Pref <- filter(tidy_egglarval_curvs, type == "Original", term == "C.Diam:Pref")$mean
+larvalptoid_mean_C.Clutch.Pref <- filter(tidy_egglarval_curvs, type == "Original", term == "C.Clutch:Pref")$mean
+
+mean_curv_larvalptoid <- matrix(c(larvalptoid_mean_C.Diam, larvalptoid_mean_C.Diam.Clutch, larvalptoid_mean_C.Diam.Pref,
+                               larvalptoid_mean_C.Diam.Clutch, larvalptoid_mean_C.Clutch, larvalptoid_mean_C.Clutch.Pref,
+                               larvalptoid_mean_C.Diam.Pref, larvalptoid_mean_C.Clutch.Pref, larvalptoid_mean_C.Pref),
+                             byrow = T, ncol = 3)
+
+## Functions to calculate effect of mean curvature on random G-matrices
+
+curv_larvalptoid_random_matrices_evolvabilities <- function(x){
+  new_Gmat <- x + x %*% mean_curv_larvalptoid %*% x
+  try(MeanMatrixStatistics(new_Gmat, iterations = n_random_gradients, parallel = TRUE))["evolvability"]
+}
+
+larvalptoid_evolvability_list <- plyr::ldply(lapply(X = random_Gmats, FUN = curv_larvalptoid_random_matrices_evolvabilities)) %>% 
+  mutate(LarvalPtoid = as.numeric(evolvability))
+
+larvalptoid_random_evolvabilities <- bind_cols(original_evolvability_list, larvalptoid_evolvability_list) %>%
+  drop_na() %>%
+  mutate(Diff = LarvalPtoid - Original)
+```
+
+We see that for our best estimates of the curvature matrix, that the larval parasitoids tend decrease evolvability in `r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`% of the G-matrix scenarios relative to the original food web..
+
+```{r Larval vs Original delta evolvability, fig.cap = "Change in evolvability for 10,000 random G-matrices using our best (mean) estimates of the curvature matrix for larval parasitoids vs original food web."}
+larvalptoid_delta_evolvability_plot <- ggplot(larvalptoid_random_evolvabilities, aes(x = Diff)) +
+  geom_histogram(alpha = 0.5, binwidth = 0.001) +
+  geom_vline(xintercept = 0, linetype = "dotted") +
+  xlab(expression(paste(Delta," evolvability (larval parasitoids - original)"))) +
+  ylab("Count")
+
+larvalptoid_delta_evolvability_plot
+save_plot(filename = "larvalptoid_delta_evolvability.pdf", plot = larvalptoid_delta_evolvability_plot, base_height = 4) # base_height = 6 is to large for PDF of manuscript
 ```
@@
   #original_new_G <- Gmat + Gmat %*% original_C %*% Gmat
-  #foodweb_original_genetic_constraints[i] <- try(MeanMatrixStatistics(original_new_G, iterations = 10000, parallel = TRUE))["conditional.evolvability"]
+  #foodweb_original_genetic_constraints[i] <- try(MeanMatrixStatistics(original_new_G, iterations = 10000, parallel = TRUE))["evolvability"]
 
@@
   long_extinction_new_G <- Gmat + Gmat %*% long_extinction_C %*% Gmat
-  foodweb_long_extinction_genetic_constraints[i] <- try(MeanMatrixStatistics(long_extinction_new_G, iterations = 10000, parallel = TRUE))["conditional.evolvability"]
+  foodweb_long_extinction_genetic_constraints[i] <- try(MeanMatrixStatistics(long_extinction_new_G, iterations = 10000, parallel = TRUE))["evolvability"]
 

### 2019-09-13 manuscript/manuscript.Rmd
minor edits to impact summary.

@@
 
-The loss of biodiversity is rewiring the web of life; however, we are currently in a poor position to predict how this will affect the ability of populations to evolve and adapt to future environments.
-To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or only allowed one of the predators to impose selection on a common prey.
-We found that the loss of predators increased the number of prey traits under selection.
-This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits.
+The loss of biodiversity is rewiring the web of life; however, it is uncertain <!--we are currently in a poor position to predict-->how this will affect the ability of remaining populations to evolve and adapt to future environments.
+To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or removed all but one of the predators that was able to impose selection on a common prey.
+We found that the loss of predators increased the number of prey traits under selection, indicating that the trajectory of evolution was more constrained to a specific combination of traits<!--.
+This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits-->.
 Moreover, we found that that the loss of predators could make it more difficult for prey to adapt to future environments.

### 2019-09-18 analyses/reproduce_analyses.Rmd
update analyses with evolvability

@@
 # Arrow data
-gradients_Diam.Clutch <- data.frame(Foodweb = c("Original","Extinction"),
+gradients_Diam.Clutch <- data.frame(Foodweb = c("Original","Removal"),
                                     sc.Diam = c(0,0), 
@@
 
-gradients_Clutch.Pref <- data.frame(Foodweb = c("Original","Extinction"),
+gradients_Clutch.Pref <- data.frame(Foodweb = c("Original","Removal"),
                                     sc.sqrt.Pref = c(0,0), 
@@
 
-gradients_Diam.Pref <- data.frame(Foodweb = c("Original","Extinction"),
+gradients_Diam.Pref <- data.frame(Foodweb = c("Original","Removal"),
                                     sc.Diam = c(0,0), 
@@
   xlab("Gall midge preference (SDs)") + 
-  ylab(expression(paste(Delta," egg parasitoid survival (original - extinction)"))) +
+  ylab(expression(paste(Delta," egg parasitoid survival (original - removal)"))) +
   scale_x_continuous(breaks=c(-1,-0.5,0,0.5,1), labels = c(-1,-0.5,0,0.5,1)) +

### 2019-09-18 manuscript/manuscript.Rmd
update manuscript with Chris' suggestions and attempt moving figures to fit nicely.

@@
 
-*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid; complexity; biodiversity.
+*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, complexity, biodiversity, community context.
 
@@
 
-The loss of biodiversity is rewiring the web of life; however, it is uncertain <!--we are currently in a poor position to predict-->how this will affect the ability of remaining populations to evolve and adapt to future environments.
+The loss of biodiversity is rewiring the web of life; however, it is uncertain how this will affect the ability of remaining populations to evolve and adapt to future environments.
 To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or removed all but one of the predators that was able to impose selection on a common prey.
+We found that the loss of predators acted to constrain prey evolution toward a particular combination of traits.
+Moreover, we found that the loss of predators could make it more difficult for prey to adapt to uncertain future environments.
+Taken together, our results suggest that the simplification of the web of life may constrain the adaptive potential of remaining populations.
+
+<!--
 We found that the loss of predators increased the number of prey traits under selection, indicating that the trajectory of evolution was more constrained to a specific combination of traits<!--.
-This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits-->.
-Moreover, we found that that the loss of predators could make it more difficult for prey to adapt to future environments.
+This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits--><!--.
+In addition, we found that that the loss of predators could make it more difficult for prey to adapt to future environments.
 Taken together, our results suggest that the loss of biodiversity may rewire interactions in such a way that constrains the adaptive potential of remaining populations.
+-->
 
@@
 \ref{fig:Conceptual}).
-The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
+<!--The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
 <!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
@@
 We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-We did not include other sources of mortality, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
+We did not include other sources of mortality in our analyses, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
 <!--Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
@@
 `r round(filter(biased_foodweb_confint, term=="FoodwebExtinction:sc.Diam")$conf.high,2)`]), indicating that unadjusted relationships would overestimate the strength of selection on chamber diameter.
-To account for this bias, we substracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's selection surface and directional selection gradient.
+To account for this bias, we subtracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's selection surface and directional selection gradient.
 
@@
 This conflicting selection is likely due to trait differences between guilds, as larger clutches may be easier targets for egg parasitoids to find, but the more complex gall structure may be more difficult for larval parasitoids to oviposit through.
+
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
+\label{Table:Gradients}
+\centering
+\begin{tabular}{lccc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
+\hline
+$\beta_{\text{Diam}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
+\textbf{
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
+
+$\beta_{\text{Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] } & 
+\textbf{
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+
+$\beta_{\text{Pref}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] } &
+
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
+
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch:Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
+
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref:Pref}}$ & 
+\textbf{
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
+
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
+\textbf{
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam:Clutch}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
+
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam:Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch:Pref}}$ & 
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
+
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
 
@@
 
-\begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
-\label{Table:Gradients}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
-\hline
-$\beta_{\text{Diam}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
-
-$\beta_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] } & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
-
-$\beta_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] } &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Pref:Pref}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
 ```{r UV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
@@
 The removal of larval parasitoids not only had direct effects on gall midge fitness, but also imposed indirect effects that would be felt in the next generation.
-For example, the removal of larval parasitoids altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}), such that the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
+For example, the removal of larval parasitoids altered the relationship between gall midge preference and the probability of observing egg parasitoids (`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }, Appendix A), such that the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
 \ref{fig:EggPtoid_Selection}).
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
-\label{Table:ExtendedGradients}
-\centering
-\begin{tabular}{lc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Contrast = Original - Removal}  \\ 
-\hline
-$\beta_{\text{Diam}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
-
-$\beta_{\text{Clutch}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
-
-$\beta_{\text{Pref}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Pref:Pref}}$ &
-
-\textbf{
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Pref}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Pref}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
 
@@
 
-<!--Selective constraints-->
+<!--Selective constraints
 All three phenotypic traits we examined experienced directional selection when we excluded larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
@@
 <!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
-This also implies that as selective constraints dampen in food webs with more consumers, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
+<!--This also implies that as selective constraints dampen in food webs with more consumers, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
 genetic drift, gene flow, and mutation).<!-- This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
@@
 [Removing because this statement is simply not true]-->
-Interestingly, this aligns with @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
+<!--Interestingly, this aligns with @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
 @Schluter1996 found support for this hypothesis from data on natural populations of several vertebrate species, including threespine sticklebacks, a few species of songbirds, and mice from the genus *Peromyscus*.
 All of these species occupy intermediate trophic levels and are likely embedded in complex food webs, which is consistent with our suggestion that genetic constraints may have a stronger influence in food webs with more consumers.
+-->
+<!-- Generality of results -->
+The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
+For example, if consumers do not differ from each other, then we do not expect the loss of consumers to modify selective constraints.
+Also, many consumers may be at too low of abundances to impose selection on their resources.
+Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
+This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles.
+When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits.
+When consumers impose conflicting selection on traits, as in our study and others [@Weis1985; @Abrahamson1997; @Start2016; @Start2018], then consumer diversity acts to neutralize selection and relax selective constraints.<!-- For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
+Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.--> On the other hand, different consumers may impose selection on different traits; therefore, a more diverse consumer community may favor a particular combination of traits and increase selective constraints.
+Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
+We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions [@Bascompte2009].
+<!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
 
@@
 This result was driven by nonlinear selection on gall midge oviposition preference in the original food web, which was due to both increases in intraguild predation and the lower mean survival of gall midges.
-While these results are intriguing, they still indicate that the indirect effects of selection are contingent on the structure of a population's G-matrix (i.e.
+While these results are intriguing, they still indicate that the indirect effects of selection are contingent on the structure of a population's G-matrix (e.g.
 consumer removals *increased* evolvability in 29% of the scenarios).
@@
 
-<!-- Generality of results -->
-The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
-For example, if consumers do not differ from each other, then we do not expect the loss of consumers to modify evolutionary constraints.
-Also, many consumers may be at too low of abundances to impose selection on their resources.
-Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
-This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles.
-When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits.
-For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
-Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.
-On the other hand, different consumers may impose selection on different traits, favoring a particular combination of traits and thus greater selective constraints.
-Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
-We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions [@Bascompte2009].
-<!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
-
 <!-- Caveats -->
-An important caveat of our study is that we did not due a factorial manipulation of both parasitoid guilds, making it difficult to conclude whether our results would change if we manipulated the presence/absence of the dominant egg parasitoid.
+An important caveat of our study is that we did not do a factorial manipulation of both parasitoid guilds, making it difficult to conclude whether our results would change if we manipulated the presence/absence of the dominant egg parasitoid.
 If we assume that higher-order interactions [@Levine2017] are weak between parasitoid guilds, then we can gain insight to how the loss of the egg parasitoid would alter selection by isolating the contribution of larval parasitoids to selection in our original food-web treatment.
@@
 In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we excluded larval parasitoids.
-This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
-A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
+This release occurs more on trees with high larval densities, which could intensify future selection on gall midge oviposition preference.
+A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in ecological communities [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
 If indirect evolutionary effects are common [@Miller1996; @Walsh2013; @Guimaraes2017], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 
-<!-- Community context shaping adaptation to environmental change --> 
+<!-- Community context shaping adaptation to environmental change
 There is a growing number of theoretical studies on adaptation to directional environmental change that incorporate species interactions [e.g.
 @deMazancourt2008; @Johansson2008; @Norberg2012; @Osmond2017PredatorsHelpPrey].
-This work has given insight to the mechanisms by which interactions between species can modify their adaptive potential<!--pairwise interactions modify the adaptive potential of species-->.
+This work has given insight to the mechanisms by which interactions between species can modify their adaptive potential<!--pairwise interactions modify the adaptive potential of species--><!--.
 Our study hints at a novel mechanism, whereby a more diverse consumer community alters the adaptive landscape in such a way that facilitates future adaptation by allowing genetic and phenotypic variation to persist.
 This mechanism only emerges once we consider selection imposed by multiple species on multiple traits.
-<!--move beyond pairwise interactions to consider selection on multiple traits in a community context.-->However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
+<!--move beyond pairwise interactions to consider selection on multiple traits in a community context.--><!--However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
 This negative effect of species diversity on adaptation occurs because there is a greater chance that the optimal phenotype is already occupied by a competitor in a more diverse community.
 More work is needed to examine how the distribution of different interaction types affects adaptation to environmental change in species-rich communities.
-
+--> 
 <!-- Caveats 
@@
 Our work also highlights some key challenges for predicting phenotypic evolution in rapidly changing communities.
-First, the simplification of ecological communities may actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.
-Second, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait, yet our results highlight that the number of traits under selection may change with the community context.
+<!--First, the simplification of ecological communities may increase selective constraints, requiring knowledge of genetic variances and covariances of multiple traits to accurately predict evolutionary change.--><!--actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.-->For example, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait, yet our results highlight that the number of traits under selection may change with the network context.
 Importantly, we found that different species/guilds imposed different selection pressures.
@@
 # Appendix A
+
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
+\label{Table:ExtendedGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Contrast = Original - Removal}  \\ 
+\hline
+$\beta_{\text{Diam}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
+
+$\beta_{\text{Clutch}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
+
+$\beta_{\text{Pref}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch:Clutch}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+
+$\gamma_{\text{Pref:Pref}}$ &
+
+\textbf{
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+
+$\gamma_{\text{Diam:Clutch}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+
+$\gamma_{\text{Diam:Pref}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+
+$\gamma_{\text{Clutch:Pref}}$ &
+
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
 

### 2019-09-18 manuscript/manuscript.tex
updated signs of selection gradients in Table 2
update manuscript with Chris' suggestions and attempt moving figures to fit nicely.

--- 2019-05-19 manuscript/manuscript.tex
@@
 }{}
-\usepackage[margin=1in]{geometry}
 \usepackage{hyperref}
@@
 
-\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in the resulting food web \end{center}
+\begin{center} \LARGE Loss of consumers constrains phenotypic evolution in the resulting food web \end{center}
 
@@
 \bigskip
-<!----> \emph{Manuscript elements}: table 1, table 2, figure 1, figure
-2, figure 3, figure 4. All figures should be printed in color.
+
+\emph{Short Running Title}: Consumer loss constrains phenotypic
+evolution
 
@@
 \emph{Keywords}: adaptive landscape, ecological networks,
-eco-evolutionary dynamics, natural selection, host-parasitoid;
-complexity.
+eco-evolutionary dynamics, natural selection, host-parasitoid,
+complexity, biodiversity, community context.
 
@@
 
-\emph{Number of words}: 3109
+\emph{Abstract Word Count}: 251
 
@@
 
-\emph{Manuscript type}: Article.
+\emph{Total Word Count}: 5769
 
@@
 
-\footnotesize Prepared using an \emph{Am. Nat.} inspired \LaTeX{}
-template for Rmarkdown. \normalsize
+\emph{Manuscript type}: Letter.
+
+\bigskip
 
@@
 
-Global change is altering the structure of ecological networks; however,
-we are currently in a poor position to predict how these altered
-communities will affect the evolutionary potential of remaining
-populations. Theory on adaptive landscapes provides a framework for
-predicting how selection constrains phenotypic evolution, but often
-treats the community context of evolving populations as a ``black box''.
-Here, we integrate ecological networks and adaptive landscapes to
-examine how changes in food-web structure shape evolutionary
-constraints. We conducted a field experiment that simulated the
-extinction of a guild of larval parasitoids that were able to impose
-selection on an insect herbivore. We then measured herbivore survival as
-a function of three key phenotypic traits. We found that the number of
-traits under selection increased with the extinction of larval
-parasitoids. In contrast, the adaptive landscape was more neutral in the
-original food web because different parasitoid guilds impose different
-selection pressures, minimizing relative fitness differences among
-phenotypes. Our results suggest that the loss of trophic interactions
-due to consumer extinctions can impose greater constraints on phenotypic
+The loss of biodiversity is altering the structure of ecological
+networks; however, we are currently in a poor position to predict how
+these altered communities will affect the evolutionary potential of
+remaining populations. Theory on adaptive landscapes provides a
+framework for predicting how selection constrains phenotypic evolution,
+but often treats the network context of evolving populations as a
+``black box''. Here, we integrate ecological networks and adaptive
+landscapes to examine how changes in food-web structure shape
+evolutionary constraints. We conducted a field experiment that removed a
+guild of larval parasitoids that imposed direct and indirect selection
+pressures on an insect herbivore. We then measured herbivore survival as
+a function of three key phenotypic traits to estimate directional,
+quadratic, and correlational selection gradients in each treatment. We
+used these selection gradients to characterize the slope and curvature
+of the adaptive landscape to understand the direct and indirect effects
+of consumer loss on evolutionary constraints. We found that the number
+of traits under directional selection increased with the removal of
+larval parasitoids, indicating greater selective constraints on the
+trajectory of evolutionary change. Similarly, we found that the removal
+of larval parasitoids altered the curvature of the adaptive landscape in
+such a way that tended to decrease the evolvability of the traits we
+measured in the next generation. Our results suggest that the loss of
+trophic interactions can impose greater constraints on phenotypic
 evolution. This indicates that the simplification of ecological
@@
 populations to future environmental change.
+
+\newpage
+
+\section{Impact Summary}\label{impact-summary}
+
+The loss of biodiversity is rewiring the web of life; however, it is
+uncertain how this will affect the ability of remaining populations to
+evolve and adapt to future environments. To gain insight to these
+effects, we conducted a field experiment that either maintained a
+natural community of predators or removed all but one of the predators
+that was able to impose selection on a common prey. We found that the
+loss of predators acted to constrain prey evolution toward a particular
+combination of traits. Moreover, we found that the loss of predators
+could make it more difficult for prey to adapt to uncertain future
+environments. Taken together, our results suggest that the
+simplification of the web of life may constrain the adaptive potential
+of remaining populations.
 
@@
 to evolution by natural selection
-\citep{Lande1979, Arnold1984applications, Arnold1984theory}. Ecological
-interactions often play a key role in shaping adaptive landscapes, as
-evidenced by the role of antagonistic \citep{Schluter2000, Abrams2000}
-and mutualistic \citep{Bronstein2006} interactions in driving
-evolutionary change. Although there is clear evidence that pairwise
-interactions can shape the adaptive landscape, we still have a poor
-understanding of how the adaptive landscape is shaped by the community
-context \citep{McPeek2017, terHorst2018}. Resolution on how the
-community context shapes phenotypic evolution is urgently needed though,
-given the rapid impacts of climate change on ecological communities
-\citep{Scheffers2016}.
-
-Ecological networks, such as food webs describing who-eats-whom in
-ecological communities, provide an explicit representation of the
-community context \citep{Bascompte2014, McCann2012}. Here, we integrate
-ecological networks and adaptive landscapes to understand how the
-community context constrains evolutionary change \citep{Arnold1992}.
-Different aspects of evolutionary constraints can be inferred by
-quantifying the slope and curvature of the adaptive landscape. For
-example, the slope is determined by directional selection gradients
-acting on each phenotypic trait and influences the trajectory of
-evolutionary change \citep{Lande1979, Arnold1992}. Selective constraints
-on evolution increase with the number of traits under directional
-selection, as this diminishes the number of optimal solutions
-\citep{Arnold2003}. The curvature of the adaptive landscape can also
-constrain evolution through its indirect effect on genetic constraints
-\citep{Arnold1992, Hansen2008}. Genetic constraints are largely governed
-by a population's \textbf{G}-matrix ---the additive genetic variances
-and covariances between traits \citep{Hansen2008}. In general, genetic
-constraints will increase with the number of traits under directional or
-stabilizing selection, as this will decrease the additive genetic
-variance in those traits \citep{Hansen2008}. Genetic constraints may
-also increase with the number of trait combinations under correlational
-selection, as this type of selection decreases the evolutionary
-independence of traits \citep{Hansen2008}. If we want to predict how the
-community context constrains evolutionary change, we must understand how
+\citep{Lande1979, Arnold1984applications, Arnold1984theory}, giving
+insight to the direct and indirect effects of selective constraints
+\citep{Arnold1992}. Ecological interactions often play a key role in
+shaping selective constraints, as evidenced by the role of antagonistic
+and mutualistic interactions in driving evolutionary change
+\citep{Schluter2000, Abrams2000, Bronstein2006}. Although there is clear
+evidence that species interactions can shape the adaptive landscape, we
+still have a poor understanding of how the adaptive landscape is shaped
+by a community of interacting species \citep{McPeek2017, terHorst2018}.
+Resolution on how change in ecological communities shape phenotypic
+evolution is urgently needed though, given the rapid losses of
+biodiversity we are observing in the Anthropocene \citep{Scheffers2016}.
+
+Ecological networks, such as food webs describing who-eats-whom, provide
+an explicit representation of the direct and indirect effects that
+emerge in a community of interacting species
+\citep{Bascompte2014, McCann2012}. Here, we integrate ecological
+networks and adaptive landscapes to understand how ecological
+communities constrain evolutionary change. The direct and indirect
+effects of natural selection can be inferred by quantifying the slope
+and curvature of the adaptive landscape \citep{Arnold1992}. For example,
+the slope is determined by directional selection gradients acting on
+each phenotypic trait and influences the trajectory of evolutionary
+change \citep{Lande1979, Arnold1992}. Selective constraints on evolution
+increase with the number of traits under directional selection, as this
+diminishes the number of optimal solutions \citep{Arnold2003}. The
+curvature of the adaptive landscape is governed by nonlinear selection
+gradients and acts to indirectly constrain evolution through its effect
+on genetic constraints \citep{Arnold1992, Hansen2008}. Genetic
+constraints are largely governed by a population's \textbf{G}-matrix
+---the additive genetic variances and covariances between traits
+\citep{Hansen2008}. Stabilizing selection acts to erode genetic variance
+in traits, which can impose a constraint on the ability of those traits
+to respond to future selection \citep{Hansen2008}. Correlational
+selection may alter the genetic covariance between traits, which may
+facilitate or hinder future adaptation depending on pattern of selection
+on those traits \citep{Hansen2008}. If we want to predict how ecological
+communities shape phenotypic evolution, we must understand how
 ecological networks shape the adaptive landscape.
 
-Global change is altering the structure of ecological networks, which
-may influence evolutionary constraints in a number of ways. For example,
-in a food web, if different consumers impose directional selection on
-different traits of a shared resource, then a more diverse consumer
-community may constrain evolution by increasing the number of traits
-under selection. Alternatively, if consumers impose selection on
-different values of a trait, then their selective effects would cancel
-each other out in more diverse communities. To examine these different
-possibilities, we conducted a field experiment that simulated the
-extinction of a consumer guild associated with an abundant insect
-herbivore (\emph{Iteomyia salicisverruca}, Family Cecidomyiidae; fig.
-\ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped
-galls when they feed on the developing leaves of willow trees
-\citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect larva from
-attack by generalist predators (e.g.~ants, spiders), but they suffer
-high mortality from egg and larval parasitoids \citep{Barbour2016}. We
-manipulated food-web structure by either excluding or allowing the guild
-of larval parasitoids to impose selection on gall midge and egg
-parasitoid traits (fig. \ref{fig:Conceptual}). We then applied modern
-statistical methods to quantify how changes in food-web structure
-altered the slope and curvature of the adaptive landscape of the gall
-midge and egg parasitoid. Taken together, our study gives insight to how
-local extinctions may constrain the evolution of interacting
-populations.
+The loss of biodiversity is altering the structure of ecological
+networks, which may influence evolutionary constraints in a number of
+ways. For example, in a food web, if different consumers impose
+directional selection on different traits of a shared resource, then a
+more diverse consumer community may constrain evolution by increasing
+the number of traits under selection. Alternatively, if consumers impose
+selection on different values of a trait, then their selective effects
+would cancel each other out in more diverse communities. To examine
+these different possibilities, we conducted a field experiment that
+removed a consumer guild that directly and indirectly impacts fitness of
+an abundant insect herbivore (\emph{Iteomyia salicisverruca}, Family
+Cecidomyiidae; fig. \ref{fig:Conceptual}). The larvae of this herbivore
+induce tooth-shaped galls when they feed on the developing leaves of
+willow trees \citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect
+larva from attack by generalist predators (e.g.~ants, spiders), but they
+suffer high mortality from egg and larval parasitoids
+\citep{Barbour2016}. We manipulated food-web structure by either
+removing larval parasitoids (removal food web) or allowing both egg and
+larval parasitoids to impose selection on gall midge traits (original
+food web, fig. \ref{fig:Conceptual}). The relative abundance of these
+larval parasitoids is much lower than the egg parasitoid
+\citep{Barbour2016}, and thus represents a plausible extinction scenario
+for this system. Larval parasitoids also impose indirect effects on gall
+midge fitness through intraguild predation on the egg parasitoid (fig.
+\ref{fig:Conceptual}). We applied modern statistical methods to quantify
+how changes in food-web structure altered the slope and curvature of the
+gall midge's adaptive landscape. Taken together, our study gives insight
+to how the loss of biodiversity may constrain the evolution of
+interacting populations.
 
@@
 interactions. In the original food web, we allowed the full suite of egg
-and larval parasitoids to impose selection. To simulate consumer
-extinction, we used mesh bags to exclude the guild of larval
-parasitoids, only allowing the egg parasitoid (\emph{Platygaster} sp.)
-to impose selection. Larval parasitoids include the following species
-(from left to right): \emph{Mesopolobus} sp. (Family: Pteromalidae);
-\emph{Tetrastichus} sp. (Family: Eulophidae); and \emph{Torymus} sp.
-(Family: Torymidae).}
+and larval parasitoids to impose selection. In the removal food web, we
+used mesh bags to exclude the guild of larval parasitoids, only allowing
+the egg parasitoid (\emph{Platygaster} sp.) to impose selection. Note
+that larval parasitoids also impose indirect effects on gall midge
+fitness through intraguild predation on the egg parasitoid. Larval
+parasitoids include the following species (from left to right):
+\emph{Mesopolobus} sp. (Family: Pteromalidae); \emph{Tetrastichus} sp.
+(Family: Eulophidae); and \emph{Torymus} sp. (Family: Torymidae).}
 \end{figure}
@@
 selection. Marking galls with flagging tape ensured that all galls had
-similar phenology when we collected galls later in the season. To
-simulate consumer extinctions, we enclosed 14 galled leaves with 10x15cm
-organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three
-parasitoid species that attack during larval development. This treatment
-did not exclude the egg parasitoid \emph{Platygaster} sp., which attacks
-prior to gall initiation \citep[larva initiate gall development in
-Cecidomyiid midges:][]{Gagne1989}. In late August, we collected marked
-and bagged galls from each plant, placed them into 30 mL vials and kept
-them in the lab for 4 months at room temperature. We then opened galls
-under a dissecting scope and determined whether larvae survived to
-pupation (our measure of fitness) or were parasitized. We did not
-include other sources of mortality, such as early larval death, as they
-could influence the expression of the gall phenotype and confound
-estimates of selection. For the food-web treatment that excluded larval
-parasitoids, we further restricted our data by removing any incidental
-instances of parasitism by a larval parasitoid. This represented less
-than 3\% of the observations in this food-web treatment and allowed us
-to focus our inferences of selection on those imposed by the egg
-parasitoid. Our final dataset contains survival estimates for 1285
-larvae from 613 galls and 111 plants.
+similar phenology when we collected galls later in the season. For the
+removal food web, we enclosed 14 galled leaves with 10x15cm organza bags
+(ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species
+that attack during larval development. This treatment did not exclude
+the egg parasitoid \emph{Platygaster} sp., which attacks prior to gall
+initiation \citep[larva initiate gall development in Cecidomyiid
+midges:][]{Gagne1989}. It was not possible to reciprocally manipulate
+parasitoid attack (i.e.~exclude egg parasitoid, but allow larval
+parasitoids), because it was not possible to identify midge oviposition
+sites prior to gall formation. In late August, we collected marked and
+bagged galls from each plant, placed them into 30 mL vials and kept them
+in the lab for 4 months at room temperature. We then opened galls under
+a dissecting scope and determined whether larvae survived to pupation
+(our measure of fitness) or were parasitized. We did not include other
+sources of mortality, such as early larval death, as they could
+influence the expression of the gall phenotype and confound estimates of
+selection. For the food-web treatment that excluded larval parasitoids,
+we further restricted our data by removing any incidental instances of
+parasitism by a larval parasitoid. This represented less than 3\% of the
+observations in this food-web treatment and allowed us to focus our
+inferences of selection on those imposed by the egg parasitoid. Our
+final dataset contains survival estimates for 1285 larvae from 613 galls
+and 111 plants.
 
@@
 we log-transformed clutch size and square-root transformed oviposition
-preference. We then scaled all phenotypic traits (mean=0 and SD=1) prior
-to our analyses (detailed below) to ensure that our estimates of
-selection were comparable across traits and with other studies.
-
-Our analysis consisted of three parts. First, we used generalized linear
+preference. We then scaled all phenotypic traits (mean=0 and SD=1)
+across treatments prior to our analyses (detailed below) to ensure that
+our estimates of selection were comparable across traits and with other
+studies.
+
+Our analysis consisted of four parts. First, we used generalized linear
 mixed models (GLMM) to quantify selection surfaces \textemdash linear
@@
 the scale of relative fitness (\(w\)) in order to calculate standardized
-selection gradients. Third, we used our estimates of selection gradients
-to characterize the slope and curvature of the adaptive landscape, which
-we used to measure evolutionary constraints.
+selection gradients. Third, we used our estimates of directional
+selection gradients to characterize the slope of the adaptive landscape,
+which we used to measure selective constraints. Finally, we estimated
+the curvature of the adaptive landscape and used a simulation to explore
+its effects on the adaptive potential of the gall midge population in
+the next generation.
 
@@
 and mean fitness (adaptive landscape), we assumed the mean value of our
-random effects (i.e., setting them to zero) when calculating selection
+random effects (i.e.~setting them to zero) when calculating selection
 surfaces. We then used parametric bootstrapping (1,000 replicates) to
 estimate the effect of food-web treatment on larval survival as well as
-selection surfaces in each food-web treatment.
+selection surfaces in each food-web treatment. To determine whether
+trait-fitness relationships differed between food-web treatments, we
+calculated the difference in bootstrapped replicates between treatments.
 
@@
 For example, the coefficients in the above model measure the change in
-the logarithm of the odds of surviving (i.e.,
+the logarithm of the odds of surviving (i.e.
 \(\text{ln}\{W(z)/[1-W(z)]\}\)) associated with 1 SD change in a trait
@@
 selection gradient. We estimated selection gradients separately for each
-food-web treatment. Note that we doubled all quadratic terms prior to
-calculating selection gradients to put them on the same scale as
-estimates of directional and correlational selection
+food-web treatment. We also determined whether selection gradients
+differed between food-web treatments by calculating the difference in
+bootstrapped replicates between treatments. Note that we doubled all
+quadratic terms prior to calculating selection gradients to put them on
+the same scale as estimates of directional and correlational selection
 \citep{Stinchcombe2008}.
 
-\textbf{Evolutionary constraints}: We measured evolutionary constraints
-by inspecting the slope and curvature of the adaptive landscape. The
-number of selective constraints is determined by the slope of the
-adaptive landscape, which in our study corresponds to:
+\textbf{Selective constraints}: The number of selective constraints is
+determined by the slope of the adaptive landscape, which in our study
+corresponds to:
 
@@
 acting on each trait. By comparing the number of directional selection
-gradients that show clear evidence of contributing to the slope (i.e.,
-95\% CI does not overlap zero) in our food-web treatments, we can infer
-the effect of food-web structure on selective constraints.
-
-The indirect effects of selection on the G-matrix
-(\(\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}\)) is
+gradients that show clear evidence of contributing to the slope
+(i.e.~95\% CI does not overlap zero) in our food-web treatments, we can
+infer the effect of food-web structure on selective constraints. This
+gives insight as to whether there is a specific combination of
+phenotypes favored by natural selection (i.e.~more traits under
+directional selection), or whether multiple trait combinations have
+comparable fitness (i.e.~less traits under directional selection).
+
+\textbf{Genetic constraints}: The indirect effects of selection on the
+G-matrix
+(\(\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}\)) are
 governed by the curvature of the adaptive landscape
@@
 the additive genetic covariance between a particular trait combination.
-In other words, the sign of diagonal terms of the curvature matrix
-dictate whether selection will increase (+), decrease (-), or cause no
-change (0) in the additive genetic variance of a trait. Similarly, any
-nonzero covariance terms (off-diagonal) are indicative of selection for
-trait integration (i.e., less independence). Therefore, we can infer the
-number of genetic constraints by summing the number of negative signs
-along the diagonal (decrease in additive genetic variance) and the
-number of nonzero terms along the off-diagonal (trait integration) of
-the curvature matrix. For these analyses, we retained estimates for
-selection gradients that showed clear evidence of being different from
-zero (i.e., 95\% CI did not overlap zero) and set other gradients to
-zero, prior to calculating the curvature matrix in each food-web
-treatment. This provides a conservative estimate of the factors
-contributing to the curvature of the adaptive landscape.
-
-Note that our metrics of selective and genetic constraints do not put
-much stock in differences in the magnitude of selection between food-web
-treatments. This is because there is a high likelihood that we are
-underestimating the magnitude of selection in our treatment that
-excludes larval parasitoids. We expect this because larval parasitoids
-not only impose mortality on gall midges, but egg parasitoids as well
-(fig. \ref{fig:Conceptual}). Therefore, our short-term removal of larval
-parasitoids has not allowed for an increase in egg parasitoid abundance
-after being released from intraguild predation. An increase in the
-abundance of egg parasitoids would decrease mean survival of gall
-midges, thus increasing the variance in relative fitness of midges, and
-consequently the magnitude of selection estimates. A recent paper by
-\citet{Hunter2018} highlights this pervasive effect of survival on the
-magnitude of selection estimates. This is why we use more qualitative
-metrics of evolutionary constraints (i.e., selective constraints =
-number of traits under directional selection; genetic constraints =
-number of decreasing variances + nonzero covariances).
+We used bootstrapped values of each selection gradient to estimate the
+curvature of each component of the matrix and its associated 95\% CI. We
+also used this information to determine whether the curvature of each
+component differed between our food-web treatments.
+
+Knowledge of the curvature matrix alone gives an incomplete picture of
+its indirect effect on genetic constraints. This is because genetic
+constraints are ultimately determined by the structure of the G-matrix,
+and therefore also depend on its structure before selection. Although we
+do not know the underlying G-matrix for the traits we measured in this
+experiment, we can still gain insight to how our food-web treatment
+would alter genetic constraints more generally. Specifically, we
+calculated how our best estimate of the curvature matrix (mean values)
+in each treatment changed the structure of \ensuremath{10^{4}} random
+G-matrices for the next generation. We restricted the range of additive
+genetic variance (\emph{V\textsubscript{G}}) in these G-matrices to
+between 0 and 0.5 to reflect typical ranges in narrow-sense heritability
+values (\emph{h}\textsuperscript{2}; note that
+\emph{h}\textsuperscript{2} = \emph{V\textsubscript{G}} when the
+phenotypic variance is scaled to 1). Note that this analysis assumes
+that the effects of recombination and mutation on the G-matrix are much
+smaller than the effects of selection, which appears to be a reasonable
+assumption over short time scales \citep{Arnold2008}.
+
+The G-matrix itself is a complex structure, but has a clear theoretical
+link to the evolvability of phenotypic traits \citep{Hansen2008}.
+Evolvability measures the ability for a trait to evolve toward a given
+direction of selection \citep{Hansen2008}. In the absence of knowledge
+about the direction of selection that a population will actually
+experience in the next generation, we can compute its average
+evolvability over random selection gradients
+\citep{Hansen2008, Melo2015}. By computing the average evolvability
+(here, we used 1000 random \(\beta\)s) for each of \ensuremath{10^{4}}
+random G-matrices, we can then assess how changes in the curvature
+matrix alter the evolutionary potential of the associated traits. We
+report the distribution of these effect sizes, rather than conduct a
+statistical test, because the number of replicates in a simulation can
+be arbitrarily high, thus making any effect size statistically
+significant \citep{White2014}.
 
@@
 subset represents the effect of parasitism on trait expression
-(i.e.~bias). We used a GLMM with the same structure as described above
-except that we modeled only a linear relationship between chamber
-diameter and larval survival (\(\alpha_{\text{Diam}}\)). We detected a
-positive bias in both food-web treatments (original
-\(\alpha_{\text{Diam}}\)= 0.36 {[}0.05, 0.67{]}; extinction
+(i.e.~bias). We used a GLMM with the same structure as described
+previously except that we modeled only a linear relationship between
+chamber diameter and larval survival (\(\alpha_{\text{Diam}}\)). We
+detected a positive bias in both food-web treatments (original
+\(\alpha_{\text{Diam}}\)= 0.36 {[}0.05, 0.67{]}; removal
 \(\alpha_{\text{Diam}}\)= 0.42 {[}0.01, 0.82{]}), indicating that
@@
 estimate selection imposed by larval parasitoids. This comparison is
-still useful though in determining the extent to which the community
-context may have indirect evolutionary effects by altering selection on
-multiple interacting populations.
+still useful though in determining the extent to which the loss of
+consumers may have indirect evolutionary effects by altering selection
+on multiple interacting populations.
 
@@
 All data and code to reproduce the reported results are publicly
-available on GitHub and have been archived on Zenodo (links are
-available from the journal office).
+available on GitHub
+(\url{https://github.com/mabarbour/complexity_selection}) and have been
+archived on Zenodo (\url{https://zenodo.org/badge/latestdoi/108833263}).
 
@@
 
-\subsection{Consumer extinctions increase selective
-constraints}\label{consumer-extinctions-increase-selective-constraints}
-
-\indent We found that the extinction of larval parasitoids increased the
+\subsection{Consumer loss increases selective
+constraints}\label{consumer-loss-increases-selective-constraints}
+
+\indent We found that the removal of larval parasitoids increased the
 number of gall midge traits under directional selection (3 of 3)
@@
 larval parasitoids actually impose directional selection for larger
-clutch sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}). We also
-observed clear evidence of directional selection for midges to avoid
-ovipositing on plants with high densities of conspecifics when we
-excluded larval parasitoids (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, there was no clear relationship in
-the original food web (table \ref{Table:Gradients}). This was likely a
-result of larval parasitoids imposing greater mortality on egg
-parasitoids at high gall midge densities (see Selection on egg
-parasitoids section), and thus a less than additive effect on gall
-midges. Chamber diameter experienced positive directional selection in
-both food-web treatments (fig. \ref{fig:UV_Landscape}A). Although the
-magnitude of selection on chamber diameter was relatively higher in the
-original food web (table \ref{Table:Gradients}), this was not due to any
-difference in the relationship between chamber diameter and survival
-(selection surfaces: original \(\alpha_{\text{Diam}}\)= 1.15 {[}0.75,
-1.61{]}; extinction \(\alpha_{\text{Diam}}\)= 1.1 {[}0.64, 1.65{]}), but
-was simply a consequence of the (expected) lower survival in the
-original food web (original \(\bar W\)= 0.42 {[}0.28, 0.56{]};
-extinction \(\bar W\)= 0.68 {[}0.54, 0.81{]}).
+clutch sizes (larval parasitoids \(\beta_{\text{Clutch}}\)= 0.13
+{[}0.04, 0.24{]}). This conflicting selection is likely due to trait
+differences between guilds, as larger clutches may be easier targets for
+egg parasitoids to find, but the more complex gall structure may be more
+difficult for larval parasitoids to oviposit through.
 
@@
 \begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
+\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
 \label{Table:Gradients}
 \centering
-\begin{tabular}{lcc} %c
+\begin{tabular}{lccc}
 \\ 
 \hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction}   \\ %& \textbf{Contrast}
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
 \hline
@@
 0.22,
-0.48] }& 
+0.48] } & 
 \textbf{
@@
 0.12,
-0.31] }\\%& 
-%\textbf{
-%0.14 [
-%0.27,
-%0] }\\
+0.31] } & 
+\textbf{
+0.14 [
+0.27,
+0] }\\
 
@@
 -0.17,
--0.01] }\\%& 
-%\textbf{
-%0.15 [
-%0.29,
-%0.03] }\\
+-0.01] } & 
+\textbf{
+0.15 [
+0.29,
+0.03] }\\
 
@@
 -0.26,
--0.06] }\\%&
-
-%0.03 [
-%0.21,
-%-0.15] \\
+-0.06] } &
+
+0.03 [
+0.21,
+-0.15] \\
 
@@
 -0.02,
-0.23] \\%&
-
-%0.03 [
-%0.27,
-%-0.2] \\
+0.23] &
+
+0.03 [
+0.27,
+-0.2] \\
 
@@
 -0.28,
-0.03] \\%&
-
-%0.06 [
-%0.32,
-%-0.2] \\
+0.03] &
+
+0.06 [
+0.32,
+-0.2] \\
 
@@
 0.02 [
--0.14,
-0.18] \\%& 
-%\textbf{
-%0.32 [
-%0.64,
-%0.01] }\\
+-0.15,
+0.18] & 
+\textbf{
+0.32 [
+0.64,
+0.01] }\\
 
@@
 -0.15,
-0.02] \\%&
-
-%0.02 [
-%0.17,
-%-0.12] \\
+0.02] &
+
+0.02 [
+0.17,
+-0.12] \\
 
@@
 -0.1,
-0.07] \\%&
-
-%-0.12 [
-%0.05,
-%-0.3] \\
+0.07] &
+
+-0.12 [
+0.05,
+-0.3] \\
 
@@
 -0.07,
-0.07] \\%&
-
-%0.03 [
-%0.18,
-%-0.12] \\ 
+0.07] &
+
+0.03 [
+0.18,
+-0.12] \\ 
 \hline
@@
 
-\subsection{Consumer extinctions increase genetic
-constraints}\label{consumer-extinctions-increase-genetic-constraints}
+We also observed clear evidence of directional selection for midges to
+avoid ovipositing on plants with high densities of conspecifics when we
+excluded larval parasitoids (table \ref{Table:Gradients}; fig.
+\ref{fig:UV_Landscape}B); however, the overall magnitude of selection
+did not differ between treatments (table \ref{Table:Gradients}). Still,
+there was no clear evidence of directional selection on oviposition in
+the original food web (table \ref{Table:Gradients}). Chamber diameter
+experienced positive directional selection in both food-web treatments
+(fig. \ref{fig:UV_Landscape}A). Although the magnitude of selection on
+chamber diameter was relatively higher in the original food web (table
+\ref{Table:Gradients}), this was not due to any difference in the
+relationship between chamber diameter and survival (selection surfaces:
+contrast \(\alpha_{\text{Diam}}\)= 0.04 {[}0.55, -0.5{]}), but was
+simply a consequence of the (expected) lower survival of gall midges in
+the original food web (contrast \(\bar W\)= 0.27 {[}0.11, 0.42{]}). We
+expect this difference to be transient though, since egg parasitoids
+would increase in abundance once they are released from intraguild
+predation, which would make the strength of selection on gall diameter
+comparable to the original food web (if removal \(\bar W\)=original
+\(\bar W\), then contrast \(\beta_{\text{Diam}}\)= -0.06 {[}-0.2,
+0.1{]}). It is worth noting that positive selection on chamber diameter
+in both treatments was unexpected. For example, the fact that larger
+galls provide more of a refuge from larval parasitoids makes sense since
+they attack after the gall is formed; however, egg parasitoids attack
+prior to gall formation, which suggests that chamber diameter is
+strongly correlated with an unmeasured trait that is under selection
+(e.g.~immune response).
+
+\bigskip
+
+\begin{figure}
+\centering
+\includegraphics{../analyses/UV_landscapes.pdf}
+\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
+phenotypes in the original food web and with the removal of larval
+parasitoids. Each panel corresponds to a different phenotypic trait:
+chamber diameter (A); oviposition preference (B); and clutch size (C).
+Bold lines represent selection experienced in the original (orange) and
+removal (blue) food webs (orange). Thin lines represent bootstrapped
+replicates to show the uncertainty in selection. For clarity, we only
+display 100 bootstraps even though inferences are based on 1,000
+replicates. Note that mean larval survival is plotted on a natural log
+scale to reflect the mathematical definition of the adaptive landscape.}
+\end{figure}
+
+To visualize the multivariate effects of these selective constraints, we
+plotted the adaptive landscape for each trait combination in each
+treatment (fig. \ref{fig:MV_Landscape}). The arrows in fig.
+\ref{fig:MV_Landscape} represent mean estimates of directional selection
+gradients, while contours represent predicted survival of the mean
+phenotype in each food-web treatment. Notice that arrows point more
+toward a corner of the adaptive landscape for each combination of traits
+with the removal of larval parasitoids compared to the original food
+web. This indicates that the loss of consumers more strongly favored a
+specific combination of traits, rather than allowing for multiple trait
+combinations to have comparable fitness.
+
+\begin{figure}
+\centering
+\includegraphics{../analyses/MV_landscapes.pdf}
+\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
+landscapes of gall midge phenotypes in the original food web and with
+the removal of larval parasitoids. Each panel corresponds to a different
+combination of phenotypic traits: clutch size and chamber diameter (A);
+clutch size and oviposition preference (B); oviposition preference and
+chamber diameter (C). Arrows represent mean estimates of directional
+selection gradients, while contours represent predicted larval survival
+of the mean phenotype in each food-web treatment. Notice that arrows
+point more toward a corner of the adaptive landscape for each
+combination of traits with the removal of larval parasitoids compared to
+the original food web. This indicates that the loss of consumers more
+strongly favored a specific combination of traits. Note that mean larval
+survival is plotted on a natural log scale to reflect the mathematical
+definition of the adaptive landscape.}
+\end{figure}
+
+\subsection{Consumer loss indirectly increases genetic
+constraints}\label{consumer-loss-indirectly-increases-genetic-constraints}
 
@@
 (\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02, 0.42{]}), but was also
-magnified by the lower average survival in complex food webs.
-
-\begin{figure}
-\centering
-\includegraphics{analyses/UV_landscapes.pdf}
-\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
-phenotypes in the original food web and with the extinction of larval
-parasitoids. Each panel corresponds to a different phenotypic trait:
-chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in the original food web
-(orange) and with consumer extinctions (blue). Thin lines represent
-bootstrapped replicates to show the uncertainty in selection. For
-clarity, we only display 100 bootstraps even though inferences are based
-on 1,000 replicates. Note that mean larval survival is plotted on a
-natural log scale to reflect the mathematical defintion of the adaptive
-landscape.}
-\end{figure}
+magnified by the lower average survival in complex food webs. This was
+likely a result of larval parasitoids imposing greater mortality on egg
+parasitoids at high gall midge densities (see \textbf{Selection on egg
+parasitoids} section), and thus a less than additive effect on gall
+midges.
 
@@
 calculated the curvature (\(\text{C}=\gamma - \beta \beta^\text{T}\)) of
-the adaptive landscape in each food-web treatment. In our study, this
-corresponds to:
-
-\[\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}\]
-
-\[\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}\]
-\bigskip
-
-where each \(\text{C}_{ii}\) (diagonal) represents the effect of
-selection on the additive genetic variance in a trait, and each
-\(\text{C}_{ij}\) (off-diagonal) represents the effect of selection on
-the additive genetic covariance between a particular trait combination.
-In order to obtain a conservative estimate of the factors contributing
-to the curvature, we only used estimates of selection that clearly
-differed from zero (bold values in table \ref{Table:Gradients}),
-otherwise we set estimates of selection to zero (non-bold values in
-table \ref{Table:Gradients}) prior to our calculation. We found that the
-curvatures of the adaptive landscape exhibited the following structures:
-
-\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
-0 &  &  \\  
-0 & 0 &  \\  
-0 & 0 & 0.34 \end{pmatrix} - \begin{pmatrix} 
-0.34\cdot0.34 &  &  \\  
-0\cdot0.34 & 0\cdot0 &  \\  
-0\cdot0.34 & 0\cdot0 & 0\cdot0 \end{pmatrix}\]
-
-\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
--0.12 &  &  \\  
-0 & 0 &  \\  
-0 & 0 & 0.34 \end{pmatrix}\]
-
-\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
-0 &  &  \\  
-0 & 0 &  \\  
-0 & 0 & 0 \end{pmatrix} - \begin{pmatrix} 
-0.21\cdot0.21 &  &  \\  
--0.09\cdot0.21 & -0.09\cdot-0.09 &  \\  
--0.16\cdot0.21 & -0.16\cdot-0.09 & -0.16\cdot-0.16 \end{pmatrix}\]
-
-\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
--0.04 &  &  \\  
-0.02 & -0.01 &  \\  
-0.03 & -0.01 & -0.03 \end{pmatrix}\]
-
-Remember that we can infer the indirect effects of selection on genetic
-constraints by summing the number of negative signs along the diagonal
-(decrease in additive genetic variance) and the number of nonzero terms
-along the off-diagonal (trait integration) of the curvature matrix. The
-structure of these matrices indicates that the extinction of larval
-parasitoids increased the number of genetic constraints on gall midges
-(6 of 6) relative to the original food web (1 of 6). For example,
-directional selection resulting from the exclusion of larval parasitoids
-acted to decrease genetic variance for all three phenotypic traits
-(negative diagonal terms), whereas only one trait (chamber diameter)
-experienced a decrease in additive genetic variance in the original food
-web. For genetic covariances, the combined effects of directional
-selection resulting from consumer extinctions favored integration among
-all three phenotypic traits (nonzero off-diagonal terms), and thus
-constraints along all three axes of covariance (fig.
-\ref{fig:MV_Landscape}). In contrast, the absence of directional
-selection in clutch size and oviposition preference did not promote
-trait integration along any axis in the original food web (fig.
-\ref{fig:MV_Landscape}).
+the adaptive landscape in each food-web treatment.
+
+\[\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}\]
+
+Of the different components of the curvature matrix, we found that only
+the curvature of oviposition preference differed between food-web
+treatments. Specifically, selection in the removal food web acted to
+decrease the additive genetic variance in preference relative to the
+original food web.
+
+\[\textbf{C}_{\text{Original}} = \begin{pmatrix} 
+-0.05\: [-0.15,0.05] &  &  \\  
+-0.06\: [-0.18,0.06] & -0.03\: [-0.14,0.09] &  \\  
+-0.09\: [-0.25,0.06] & 0.04\: [-0.1,0.18] & \textbf{0.15\: [0.02,0.3]} \end{pmatrix}\]
+
+\[\textbf{C}_{\text{Removal}} = \begin{pmatrix} 
+0.01\: [-0.05,0.07] &  &  \\  
+-0.05\: [-0.13,0.03] & -0.06\: [-0.15,0.01] &  \\  
+0.02\: [-0.07,0.1] & -0.01\: [-0.09,0.06] & -0.02\: [-0.1,0.06] \end{pmatrix}\]
+
+\[\textbf{C}_{\text{Removal-Original}} = \begin{pmatrix} 
+0.06\: [-0.06,0.18] &  &  \\  
+0.02\: [-0.13,0.16] & -0.03\: [-0.16,0.1] &  \\  
+0.11\: [-0.06,0.29] & -0.05\: [-0.21,0.1] & \textbf{-0.17\: [-0.33,-0.01]} \end{pmatrix}\]
+
+Interestingly, when we translate the effect of the curvature matrix onto
+genetic constraints in the next generation, we see that the loss of
+consumers had a general tendency to decrease evolvability (fig.
+\ref{fig:Evolvability}). Specifically, the removal food web decreased
+the average evolvability of 71\% of the random G-matrices in our
+simulation. If anything, we expect that this underestimates the true
+effect of our removal treatment. For example, if we assume egg
+parasitoids would eventually impose similar impact on mean fitness once
+they are released from intraguild predation (i.e.~removal
+\(\bar W\)=original \(\bar W\)), then the removal food web decreases the
+average evolvability in 78\% of the G-matrix scenarios.
 
@@
 \centering
-\includegraphics{analyses/MV_landscapes.pdf}
-\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
-landscapes of gall midge phenotypes in the original food web and with
-the extinction of larval parasitoids. Each panel corresponds to a
-different combination of phenotypic traits: clutch size and chamber
-diameter (A); clutch size and oviposition preference (B); oviposition
-preference and chamber diameter (C). Arrows represent mean estimates of
-directional selection gradients, while contours represent predicted
-larval survival of the mean phenotype in each food-web treatment. Notice
-that arrows point more toward a corner of the adaptive landscape for
-each combination of traits with the extinction of larval parasitoids
-compared to the original food web. This indicates that consumer
-extinctions more strongly favored trait integration (covariance). Note
-that mean larval survival is plotted on a natural log scale to reflect
-the mathematical definition of the adaptive landscape.}
+\includegraphics{../analyses/delta_evolvability.pdf}
+\caption{\label{fig:Evolvability}Change in average evolvability for
+10,000 random G-matrices using our best (mean) estimate of the curvature
+matrix for each food-web treatment. We found that the curvature of the
+removal food web decreased evolvability in 71\% of the G-matrices
+(i.e.~the change in evolvability was negative for 71\% of the
+simulations), suggesting that the loss of consumers tended to decrease
+evolutionary potential of traits in our study.}
 \end{figure}
@@
 
-The exctinction of larval parasitoids only altered the relationship
-between gall midge preference and the probability of observing egg
-parasitoids (table \ref{Table:ExtendedGradients}). Specifically, the
-impact of larval parasitoids increased nonlinearly with higher gall
-midge densities (fig. \ref{fig:EggPtoid_Selection}).
+The removal of larval parasitoids not only had direct effects on gall
+midge fitness, but also imposed indirect effects that would be felt in
+the next generation. For example, the removal of larval parasitoids
+altered the relationship between gall midge preference and the
+probability of observing egg parasitoids (-0.46 {[} -1.07, -0.02{]} \},
+Appendix A), such that the impact of larval parasitoids increased
+nonlinearly with higher gall midge densities (fig.
+\ref{fig:EggPtoid_Selection}).
+
+\begin{figure}
+\centering
+\includegraphics{../analyses/selection_on_Platygaster.pdf}
+\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
+parasitoids on egg parasitoids (\emph{Platygaster} sp.). The bold line
+represents the average difference in the probability of observing the
+egg parasitoid (original minus removal of larval parastioids) as a
+function of gall midge oviposition preference. Thin lines represent
+bootstrapped replicates to show the uncertainty in selection. For
+clarity, we only display 100 bootstraps even though inferences are based
+on 1,000 replicates. The decrease in the probability of observing egg
+parasitoids at high gall-midge densities indicate that larval
+parasitoids impose nonlinear selection on egg parasitoids.}
+\end{figure}
+
+\section{Discussion}\label{discussion}
+
+We found that the removal of larval parasitoids constrained phenotypic
+evolution in gall midges in two key ways. First, more traits contributed
+to the slope of the adaptive landscape in the absence of larval
+parasitoids, suggesting greater constraints on the trajectory of
+phenotypic evolution. Second, excluding larval parasitoids altered the
+curvature of the adaptive landscape in such a way that tended to
+decrease the evolvability of associated traits. Assuming these traits
+have other ecological functions, then this decrease in evolvability
+could constrain the gall midge's adaptive potential in the face of novel
+selection pressures. Our experiment also revealed evidence of indirect
+selection pressures, suggesting that the loss of consumers may have
+complex effects on the trajectories of phenotypic evolution. Taken
+together, our study provides experimental evidence from the field that
+the loss of consumers may constrain the adaptive potential of remaining
+populations.
+
+The generality of our results likely depends on the relative abundance
+and functional differences between consumers in a community. For
+example, if consumers do not differ from each other, then we do not
+expect the loss of consumers to modify selective constraints. Also, many
+consumers may be at too low of abundances to impose selection on their
+resources. Rank abundance curves \citep{Preston1948} and the
+disproportionate number of weak interactions in diverse communities
+\citep{Paine1992} support this notion. This logic suggests that we may
+not have observed the effects we did if we had only removed one larval
+parasitoid, because each species had relatively low abundance
+\citep{Barbour2016} and they likely share similar ecological roles. When
+consumers are functionally different and abundant though, the effect of
+consumer loss will depend on whether different species impose
+conflicting selection pressures or select for distinct traits. When
+consumers impose conflicting selection on traits, as in our study and
+others \citep{Weis1985, Abrahamson1997, Start2016, Start2018}, then
+consumer diversity acts to neutralize selection and relax selective
+constraints. On the other hand, different consumers may impose selection
+on different traits; therefore, a more diverse consumer community may
+favor a particular combination of traits and increase selective
+constraints. Examples of this include strong genetic covariances in
+plant resistance to different insect herbivores
+\citep{Maddox1990, Wise2007, Wise2013}, although there are also examples
+where these covariances are weak \citep{Roche1997, Barbour2015}, or vary
+from year-to-year \citep{Johnson2007}. We suggest that gaining
+predictive insight to the evolutionary consequences of food-web
+disassembly requires an understanding of the mechanisms governing the
+assembly of trophic interactions \citep{Bascompte2009}.
+
+We also found evidence for a general decrease in trait evolvability when
+we excluded larval parasitoids due to changes in the curvature of the
+adaptive landscape. This result was driven by nonlinear selection on
+gall midge oviposition preference in the original food web, which was
+due to both increases in intraguild predation and the lower mean
+survival of gall midges. While these results are intriguing, they still
+indicate that the indirect effects of selection are contingent on the
+structure of a population's G-matrix (e.g.~consumer removals
+\emph{increased} evolvability in 29\% of the scenarios). This highlights
+the importance of future studies to characterize the G-matrix in order
+to accurately predict how changes in network context will alter the
+evolutionary potential of remaining populations. Indeed, current theory
+often assumes genetic variances and covariances remain constant over
+time rather than dynamically changing with the network context
+\citep{McPeek2017, Guimaraes2017}. Our empirical results highlight the
+need to explore the evolutionary consequences of not only direct effects
+of selection, but indirect effects on genetic constraints that emerge in
+a network of interacting species.
+
+An important caveat of our study is that we did not due a factorial
+manipulation of both parasitoid guilds, making it difficult to conclude
+whether our results would change if we manipulated the presence/absence
+of the dominant egg parasitoid. If we assume that higher-order
+interactions \citep{Levine2017} are weak between parasitoid guilds, then
+we can gain insight to how the loss of the egg parasitoid would alter
+selection by isolating the contribution of larval parasitoids to
+selection in our original food-web treatment. When we do this, we see
+the same qualitative effects as we do when we removed larval
+parasitoids. For example, we see clear evidence of all three traits
+being under directional selection (i.e.~greater selective constraints,
+Appendix A) as well as a decrease, albeit smaller, in trait evolvability
+under different G-matrix scenarios (57\%, Appendix A). This suggests
+that our results could be robust to this caveat, which was simply not
+possible to manipulate given the biology of our system (see
+\emph{Manipulating Food-web Structure} section for explanation).
+
+Our results suggest that the loss of consumers may not only directly
+affect connected species, but also result in indirect evolutionary
+effects. In our study, this indirect effect arises from egg parasitoids
+being released from intraguild predation when we excluded larval
+parasitoids. This release occurs more on trees with high larval
+densities, which could intensify future selection on gall midge
+oviposition preference. A growing number of experiments over the past
+two decades have demonstrated the presence and potential importance of
+indirect evolutionary effects that emerge in ecological communities
+\citep{Pilson1996, Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, Start2019}.
+If indirect evolutionary effects are common
+\citep{Miller1996, Walsh2013, Guimaraes2017}, then predicting
+evolutionary trajectories resulting from the loss of consumers will
+require evolutionary studies to explicitly account for the ecological
+networks that species are embedded in.
+
+Our study gives insight to how the loss of consumers alters evolutionary
+constraints on remaining populations. In particular, it hints at a
+potential insidious effect of local extinctions that compromises the
+robustness of remaining populations to future environmental change. Our
+work also highlights some key challenges for predicting phenotypic
+evolution in rapidly changing communities. For example, many theoretical
+models of eco-evolutionary dynamics focus on phenotypic change in a
+single trait, yet our results highlight that the number of traits under
+selection may change with the network context. Importantly, we found
+that different species/guilds imposed different selection pressures.
+Knowing these hidden selection pressures is critical for prediction,
+because the trajectory of evolution will depend on the nature of change
+in the ecological community. We expect that a continued integration of
+adaptive landscapes and ecological networks will enhance our ability to
+predict the evolutionary consequences of changes in ecological
+communities.
+
+\section{Acknowledgements}\label{acknowledgements}
+
+We thank the staff of Humboldt Bay National Wildlife Refuge (U.S. Fish
+and Wildlife Service) for facilitating experimental logistics. For
+assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
+For funding support, we thank the University of British Columbia (James
+Robert Thompson Fellowship and Four-Year Fellowship to M.A.~Barbour),
+NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
+Science Foundation (grant 31003A\_160671 to J. Bascompte).
+
+\section{Author Contributions}\label{author-contributions}
+
+M.A.B. conceived the idea behind the study and designed the field
+experiment. M.A.B. and B.L. setup and conducted the experiment. M.A.B.,
+A.S., and C.J.G. collected the data. M.A.B. analyzed the data. M.A.B.
+wrote the manuscript with primary input from J.B. and additional
+feedback from C.J.G.
+
+\section{Data Accessibility}\label{data-accessibility}
+
+All data and code to reproduce the reported results are publicly
+available on GitHub
+(\url{https://github.com/mabarbour/complexity_selection}) and have been
+archived on Zenodo (\url{https://zenodo.org/badge/latestdoi/108833263}).
+
+\section{Appendix A}\label{appendix-a}
 
@@
 -0.03 [
-0.25,
--0.3] \\
+-0.3,
+0.25] \\
 
@@
 0.07 [
-0.38,
--0.26] \\
+-0.26,
+0.39] \\
 
@@
 -0.25 [
-0.09,
--0.64] \\
+-0.64,
+0.09] \\
 
@@
 -0.05 [
-0.33,
--0.43] \\
+-0.43,
+0.33] \\
 
@@
 -0.21 [
-0.26,
--0.68] \\
+-0.68,
+0.26] \\
 
@@
 -0.46 [
--0.02,
--1.07] }\\
+-1.07,
+-0.02] }\\
 
@@
 0 [
-0.27,
--0.29] \\
+-0.29,
+0.27] \\
 
@@
 0.25 [
-0.6,
--0.05] \\
+-0.04,
+0.6] \\
 
@@
 -0.18 [
-0.12,
--0.52] \\ 
+-0.52,
+0.12] \\ 
 \hline
@@
 
+\bigskip
+
+\begin{table}[h]
+\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web.
+This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
+\label{Table:LarvalGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
+\hline
+$\beta_{\text{Diam}}$ & 
+%\textbf{
+%0.34 [
+%0.22,
+%0.48] } & 
+\textbf{
+0.23 [
+0.13,
+0.36] } \\
+
+$\beta_{\text{Clutch}}$ & 
+%0.06 [
+%-0.05,
+%0.17] & 
+\textbf{
+0.13 [
+0.04,
+0.24] }\\
+
+$\beta_{\text{Pref}}$ &
+%-0.13 [
+%-0.29,
+%0.05] & 
+\textbf{
+-0.17 [
+-0.34,
+-0.03] } \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+%0.13 [
+%-0.06,
+%0.33] &
+
+0.06 [
+-0.07,
+0.2]  \\
+
+$\gamma_{\text{Clutch:Clutch}}$ & 
+%-0.05 [
+%-0.27,
+%0.18] &
+
+0.01 [
+-0.14,
+0.15] \\
+
+$\gamma_{\text{Pref:Pref}}$ & 
+%\textbf{
+%0.34 [
+%0.07,
+%0.63] }&
+
+0.18 [
+-0.02,
+0.42] \\
+
+$\gamma_{\text{Diam:Clutch}}$ & 
+%-0.04 [
+%-0.16,
+%0.08] &
+
+0.02 [
+-0.07,
+0.11]  \\
+
+$\gamma_{\text{Diam:Pref}}$ & 
+%-0.13 [
+%-0.29,
+%0.02] &
+
+-0.05 [
+-0.18,
+0.06]  \\
+
+$\gamma_{\text{Clutch:Pref}}$ & 
+%0.03 [
+%-0.1,
+%0.18] &
+
+-0.04 [
+-0.14,
+0.06]  \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
 \begin{figure}
 \centering
-\includegraphics{analyses/selection_on_Platygaster.pdf}
-\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
-parasitoids on egg parasitoids (\emph{Platygaster} sp.). The bold line
-represents the average difference in the probability of observing the
-egg parasitoid (original - extinction of larval parastioids) as a
-function of gall midge oviposition preference. Thin lines represent
-bootstrapped replicates to show the uncertainty in selection. For
-clarity, we only display 100 bootstraps even though inferences are based
-on 1,000 replicates. The decrease in the probability of observing egg
-parasitoids at high gall-midge densities indicate that larval
-parasitoids impose nonlinear selection on egg parasitoids.}
+\includegraphics{../analyses/larvalptoid_delta_evolvability.pdf}
+\caption{\label{fig:LarvalPtoidEvolvability}Change in average
+evolvability for 10,000 random G-matrices using our best (mean) estimate
+of the curvature matrix for selection in the absence of egg parasitoids
+vs.~the original food web. We found that the curvature imposed by the
+loss of egg parasitoids decreased evolvability in 57\% of the G-matrices
+(i.e.~the change in evolvability was negative for 57\% of the
+simulations), which is smaller in magnitude, but in the same direction,
+as the effects of losing larval parasitoids.}
 \end{figure}
 
-\section{Discussion}\label{discussion}
-
-We found that the extinction of larval parasitoids constrained
-phenotypic evolution in gall midges in two key ways. First, more traits
-contributed to the slope of the adaptive landscape in the absence of
-larval parasitoids, suggesting greater constraints on the trajectory of
-phenotypic evolution. Second, excluding larval parasitoids indirectly
-increased the number of genetic constraints, which could act to
-constrain the gall midge's adaptive potential in the face of novel
-selection pressures. Our experiment also revealed evidence of indirect
-selection pressures, suggesting that the loss of consumers may have
-complex effects on the trajectories of phenotypic evolution. Taken
-together, our study provides experimental evidence from the field that
-consumer extinctions may constrain the adaptive potential of remaining
-populations.
-
-All three phenotypic traits we examined experienced directional
-selection when we excluded larval parasitoids, indicating that there is
-an optimal phenotype that maximizes larval survival (i.e.~large chamber
-diameter, small clutch size, and avoidance of conspecifics). In
-contrast, we did not observe clear evidence of selective constraints on
-clutch size and oviposition preference in the original food web. This
-suggests that there are many optimal phenotypes (adaptive peaks), or in
-this case, a flat adaptive landscape where there are no fitness
-consequences for phenotypic change in these traits. This also implies
-that as selective constraints dampen in more complex food webs, then the
-trajectory of evolution becomes more determined by how genetic
-constraints interact with other evolutionary processes (e.g.~genetic
-drift, gene flow, and mutation). Interestingly, this aligns with
-\citet{Schluter1996}`s hypothesis that phenotypic evolution often
-follows 'genetic lines of least resistance'. \citet{Schluter1996} found
-support for this hypothesis from data on natural populations of several
-vertebrate species, including threespine sticklebacks, a few species of
-songbirds, and mice from the genus \emph{Peromyscus}. All of these
-species occupy intermediate trophic levels and are likely embedded in
-complex food webs, which is consistent with our suggestion that genetic
-constraints may have a stronger influence in more complex food webs.
-
-We also found evidence for more genetic constraints when we excluded
-larval parasitoids due to indirect effects of selection on the
-population's G-matrix. The ability of a population to adapt to novel
-selection pressures (evolvability) is largely governed by the structure
-of its G-matrix \citep{Hansen2008}. When selection favors genetic
-covariance between traits (positive or negative), this results in less
-autonomy of evolutionary responses to changing environments. Similarly,
-decreases in genetic variance constrain potential for the trait itself
-to evolve. Together, this suggests that consumer extinctions may
-decrease the evolutionary potential of populations by indirectly
-selecting for decreases in genetic variance in multiple traits and
-favoring trait integration. Current theory often assumes genetic
-variances and covariances remain constant over time rather than
-dynamically changing with the community context
-\citep{McPeek2017, Guimaraes2017}. Our empirical results highlight the
-need to explore the evolutionary consequences of not only direct effects
-of selection, but indirect effects on genetic constraints that are
-shaped by the community context.
-
-The generality of our results likely depends on the relative abundance
-and functional differences between consumers in a community. For
-example, if consumers do not differ from each other, then we do not
-expect changes in food-web structure to modify evolutionary constraints.
-Also, many consumers may be at too low of abundances to impose selection
-on their resources. Rank abundance curves \citep{Preston1948} and the
-disproportionate number of weak interactions in diverse communities
-\citep{Paine1992} support this notion. When consumers are abundant
-though, the effect of food-web structure will depend on whether
-different species impose conflicting selection pressures or select for
-distinct traits. For example, parisitoids and birds impose conflicting
-selection pressures on the size of galls induced by the fly
-\emph{Eurosta solidaginis} \citep{Weis1985, Abrahamson1997}. Recent
-studies in this system have shown that decreases in the relative
-abundance of birds, due to either small patch sizes \citep{Start2016} or
-proximity to urban areas \citep{Start2018} causes a shift from neutral
-to directional selection on gall size. On the other hand, different
-consumers may impose selection on different traits, favoring trait
-integration and increasing genetic constraints. Examples of this include
-strong genetic covariances in plant resistance to different insect
-herbivores \citep{Maddox1990, Wise2007, Wise2013}, although there are
-also examples where these covariances are weak
-\citep{Roche1997, Barbour2015}, or vary from year-to-year
-\citep{Johnson2007}. We suggest that gaining predictive insight to the
-evolutionary consequences of food-web disassembly requires an
-understanding of the mechanisms governing the assembly of trophic
-interactions.
-
-Our results suggest that the loss of consumers may not only directly
-affect connected species, but also result in indirect evolutionary
-effects. In our study, this indirect effect arises from egg parasitoids
-being released from intraguild predation when we excluded larval
-parasitoids. This release occurs more on trees with high larval
-densities, which could intensify selection on gall midge oviposition
-preference. A growing number of experiments over the past two decades
-have demonstrated the presence and potential importance of indirect
-evolutionary effects that emerge in a community context
-\citep{Pilson1996, Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, Start2019}.
-If indirect evolutionary effects are common \citep{Walsh2013}, then
-predicting evolutionary trajectories resulting from consumer extinctions
-will require evolutionary studies to explicitly account for the
-ecological networks that species are embedded in.
-
-There is a growing number of theoretical studies on adaptation to
-directional environmental change that incorporate species interactions
-\citep[e.g.][]{deMazancourt2008, Johansson2008, Norberg2012, Osmond2017PredatorsHelpPrey}.
-This work has given insight to the mechanisms by which pairwise
-interactions modify the adaptive potential of species. Our study hints
-at a novel mechanism, whereby more complex food webs flatten the
-adaptive landscape, thus facilitating future adaptation by allowing
-genetic and phenotypic variation to persist. This mechanism only emerges
-once we move beyond pairwise interactions to consider selection on
-multiple traits in a community context. However, a study on competition
-has highlighted that we may expect the opposite effect of species
-diversity in competitive communities \citep{deMazancourt2008}. This
-negative effect of species diversity on adaptation occurs because there
-is a greater chance that the optimal phenotype is already occupied by a
-competitor in a more diverse community. More work is needed to examine
-how the distribution of different interaction types affects adaptation
-to environmental change in species-rich communities.
-
-Our study has some limitations to consider when relating our findings to
-the effects of consumer extinctions on evolutionary constraints more
-generally. First, we removed other sources of mortality prior to our
-analyses. While this was necessary to avoid confounding estimates of
-selection with effects on phenotypic expression, we may be
-overestimating the effects of selection due to parasitoids. Second, our
-metrics of evolutionary constraints do not account for variation in the
-magnitude of selection pressures. While quantitative metrics are
-possible \citep{Hansen2008}, we felt they were not appropriate to apply
-here as our experimental removal of larval parasitoids results in a
-transient dynamic in the strength (but not direction) of selection. Such
-transient dynamics may be common in short-term experimental studies of
-natural selection, but they can be detected by using natural history
-information and dissecting the sources of selection (e.g.~quantifying
-selection surfaces and treatment effects on mean fitness) as we did
-here.
-
-Our study gives insight to how consumer extinctions alter evolutionary
-constraints on remaining populations. In particular, it hints at a
-potential insidious effect of local extinctions that compromises the
-robustness of remaining populations to future environmental change. Our
-work also highlights some key challenges for predicting phenotypic
-evolution in the face of global change. First, the simplification of
-ecological communities may actually reduce the predictability of
-phenotypic evolution, because knowledge is required of both selective
-and genetic constraints, rather than potentially just genetic
-constraints in more complex systems. Second, many theoretical models of
-eco-evolutionary dynamics focus on phenotypic change in a single trait,
-yet our results highlight that the number of traits under selection may
-change with the community context. Importantly, we found that different
-species/guilds imposed different selection pressures. Knowing these
-hidden selection pressures is critical for prediction, because the
-trajectory of evolution will depend on the nature of change in the
-community context. We expect that a continued integration of adaptive
-landscapes and ecological networks will enhance our ability to predict
-the evolutionary consequences of changes in ecological communities.
-
 \bibliography{references}

### 2019-09-18 manuscript/supplementary_material.Rmd
generate supplementary material.

--- 2019-09-13 manuscript/manuscript.Rmd
@@
 \vspace*{0.1cm} 
-\begin{center} \LARGE Loss of consumers constrains phenotypic evolution in the resulting food web \end{center}
+\begin{center} \LARGE Supplementary Material: \\
+Loss of consumers constrains phenotypic evolution in the resulting food web \end{center}
 
@@
 
-\bigskip
-
-*Short Running Title*: Consumer loss constrains phenotypic evolution
-
-\bigskip
-
-*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid; complexity; biodiversity.
-
-\bigskip
-
-*Abstract Word Count*: 251
-
-\bigskip
-
-*Total Word Count*: `r wordcountaddin::word_count("manuscript.Rmd") - 587` <!-- subtract estimate of Abstract, Impact, Acknowledgements, Author Contributions, and Data Accessibility -->
-
-\bigskip
-
-*Manuscript type*: Letter.
-
-\bigskip
-
-<!-- \footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize -->
-
 <!-- End title page formatting -->
@@
 
-\newpage
+<!-- For Appendix figures and tables 
+http://bytesizebio.net/2013/03/11/adding-supplementary-tables-and-figures-in-latex/
+-->
 
-# Abstract
-
-The loss of biodiversity<!--Global change--> is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
-Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the network context of evolving populations as a ``black box''.
-Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web structure shape evolutionary constraints.
-We conducted a field experiment that removed<!--simulated the extinction of--> a guild of larval parasitoids that imposed direct and indirect selection pressures on an insect herbivore.
-We then measured herbivore survival as a function of three key phenotypic traits to estimate directional, quadratic, and correlational selection gradients in each treatment.
-We used these selection gradients to characterize the slope and curvature of the adaptive landscape to understand the direct and indirect effects of consumer loss on evolutionary constraints.
-We found that the number of traits under directional selection increased with the removal of larval parasitoids, indicating greater selective constraints on the trajectory of evolutionary change.
-Similarly, we found that the removal of larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of the traits we measured in the next generation.<!--In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.--> Our results suggest that the loss of trophic interactions <!--due to consumer extinctions -->can impose greater constraints on phenotypic evolution.
-This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
+\newcommand{\beginsupplement}{%
+        \setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+     }
 
@@
 
-# Impact Summary
-
-<!-- Authors should provide an approximately 300 word summary, explaining why the article makes an important contribution to Evolutionary Biology.
-It should be accessible to a wide audience, e.g.
-journalists, non-expert public interested in evolution, school science teachers.
--->
-
-The loss of biodiversity is rewiring the web of life; however, we are currently in a poor position to predict how this will affect the ability of populations to evolve and adapt to future environments.
-To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or only allowed one of the predators to impose selection on a common prey.
-We found that the loss of predators increased the number of prey traits under selection.
-This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits.
-Moreover, we found that that the loss of predators could make it more difficult for prey to adapt to future environments.
-Taken together, our results suggest that the loss of biodiversity may rewire interactions in such a way that constrains the adaptive potential of remaining populations.
-
-\newpage
-
-<!-- > "What escapes the eye, however, is a much more insidious kind of extinction: the extinction of ecological interactions." @Janzen1974 -->
-
-# Introduction
-
-The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
-More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], giving insight to the direct and indirect effects of selective constraints [@Arnold1992].
-Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006].
-Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018].
-Resolution on how change in ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].
-
-Ecological networks, such as food webs describing who-eats-whom, provide an explicit representation of the direct and indirect effects that emerge in a community of interacting species [@Bascompte2014; @McCann2012].
-Here, we integrate ecological networks and adaptive landscapes to understand how ecological communities constrain evolutionary change.
-The direct and indirect effects of natural selection can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
-For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
-Selective constraints on evolution increase with the number of traits under directional selection, as this diminishes the number of optimal solutions [@Arnold2003].
-The curvature of the adaptive landscape is governed by nonlinear selection gradients and acts to indirectly constrain evolution through its effect on genetic constraints [@Arnold1992; @Hansen2008].
-Genetic constraints are largely governed by a population's **G**-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
-Stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection may alter the genetic covariance between traits, which may facilitate or hinder future adaptation depending on pattern of selection on those traits [@Hansen2008].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
-
-The loss of biodiversity is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways.
-For example, in a <!--multitrophic community or -->food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection.
-Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities.
-To examine these different possibilities, we conducted a field experiment that removed a consumer guild that directly and indirectly impacts fitness of an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
-\ref{fig:Conceptual}).
-The larvae of this herbivore induce tooth-shaped galls when they feed on the developing leaves of willow trees [*Salix* sp., @Russo2006].
-These galls protect larva from attack by generalist predators (e.g.
-ants, spiders), but they suffer high mortality from egg and larval parasitoids [@Barbour2016].
-We manipulated food-web structure by either removing larval parasitoids (removal food web) or allowing both egg and larval parasitoids to impose selection on gall midge traits (original food web, fig.
-\ref{fig:Conceptual}).
-The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
-<!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
--->Larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid (fig.
-\ref{fig:Conceptual}).
-We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
-Taken together, our study gives insight to how the loss of biodiversity may constrain the evolution of interacting populations.
-
-```{r Conceptual, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
-Black arrows denote the flow of energy in this network of trophic interactions.
-In the original food web, we allowed the full suite of egg and larval parasitoids to impose selection.
-In the removal food web, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
-Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
-Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
-(Family: Pteromalidae); *Tetrastichus* sp.
-(Family: Eulophidae); and *Torymus* sp.
-(Family: Torymidae)."}
-knitr::include_graphics("../analyses/complex_simple_foodwebs_v3.jpeg")
-```
-
-# Methods
-
-## Study Site
-
-We conducted our study within a four-year old common garden experiment of coastal willow (*Salix hookeriana*) located at Humboldt Bay National Wildlife Refuge (HBNWR) (40 40'53"N, 124 12'4"W) near Loleta, California, USA.
-This common garden consists of 26 different willow genotypes that were collected from a single population of willows growing around Humboldt Bay.
-Stem cuttings of each genotype (25 replicates per genotype) were planted in a completely randomized design in two hectares of a former cattle pasture at HBNWR.
-Willows at our study site begin flowering in February and reach their peak growth in early August.
-During this study, willows had reached 5 - 9m in height.
-Further details on the genotyping and planting of the common garden are available in @Barbour2015.
-
-## Manipulating Food-web Structure
-
-We setup our food-web manipulation across 128 plants soon after galls began developing on willows in early June of 2013.
-These 128 plants came from eight different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
-For the original food web (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
-Marking galls with flagging tape ensured that all galls had similar phenology when we collected galls later in the season.
-For the removal food web, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
-This treatment did not exclude the egg parasitoid *Platygaster* sp., which attacks prior to gall initiation [larva initiate gall development in Cecidomyiid midges: @Gagne1989].
-It was not possible to reciprocally manipulate parasitoid attack (i.e.
-exclude egg parasitoid, but allow larval parasitoids), because it was not possible to identify midge oviposition sites prior to gall formation.
-In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature.
-We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-We did not include other sources of mortality, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
-<!--Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
-Another reason why we excluded other sources of mortality, such as early larval death, is that they can influence the expression of the gall phenotype and confound estimates of selection.--> For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
-This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
-Our final dataset contains survival estimates for `r no_larvae` larvae from `r no_galls` galls and `r no_plants` plants.
-
-## Measuring Phenotypic Traits
-
-We collected data on three different traits that we expected to influence larval survival based on previous work in this system [@Barbour2016] and other work with gall midges [@Weis1983; @Heath2018].
-First, we measured gall diameter as the size of each gall chamber to the nearest 0.01 mm at its maximum diameter (perpendicular to the direction of plant tissue growth).
-Previous work in this system has shown that larger galls are associated with higher survival [@Barbour2016].
-Second, we measured clutch size by counting the number of chambers in each gall [@Weis1983; @Heath2018].
-All larvae collected from the same multi-chambered gall were scored with the same clutch size.
-Third, we measured oviposition preference as the density of larvae observed on a plant in an independent survey.
-We did this by randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
-We then converted these counts to a measure of larval density per 100 shoots by counting the number of shoots on the last branch we sampled.
-All larvae collected from the same plant were scored with the same oviposition preference.
-Measuring larval densities on plants in the field is a common method for measuring oviposition preference [@Gripenberg2010]; however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference [@Singer1986].
-Fortunately, a couple features of our study system suggest that larval densities may be a good proxy for oviposition preference.
-For example, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
-
-## Quantifying the Adaptive Landscape
-
-Inferring adaptive landscapes assumes that trait distributions are multivariate normal [@Lande1983]. 
-To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
-We then scaled all phenotypic traits (mean=0 and SD=1) across treatments prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
-
-Our analysis consisted of four parts.
-First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment.
-Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients.
-Third, we used our estimates of directional selection gradients to characterize the slope of the adaptive landscape, which we used to measure selective constraints.
-Finally, we estimated the curvature of the adaptive landscape and used a simulation to explore its effects on the adaptive potential of the gall midge population in the next generation.
-
-**Selection surfaces**: Since larval survival was our measure of absolute fitness, we used a GLMM that assumed a binomial error distribution (and logit-link function).
-To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_i$), quadratic ($\alpha_{ii}$), and linear interactions ($\alpha_{ij}$) between each trait.
-We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.
-Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
-Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the adaptive landscape [@Arnold2003].
-To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall ID nested within plant ID nested within genotype ID as random effects.
-Although statistical models with random effects are not common in analyses of natural selection, we think that modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
-Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e.
-setting them to zero) when calculating selection surfaces.
-We then used parametric bootstrapping (1,000 replicates) to estimate the effect of food-web treatment on larval survival as well as selection surfaces in each food-web treatment.
-To determine whether trait-fitness relationships differed between food-web treatments, we calculated the difference in bootstrapped replicates between treatments.
-
-**Selection gradients**: Selection gradients cannot be estimated directly from GLMMs of selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e.
-$\text{ln}\{W(z)/[1-W(z)]\}$) associated with 1 SD change in a trait with all other traits held fixed at their mean.
-Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlational ($\gamma_{ij}$) selection gradients.
-Briefly, this method calculates the average gradient of selection surfaces by multiplying the average of $W(z)[1-W(z)]$ by each regression coefficient (e.g.
-$\alpha_i$, $\alpha_{ii}$, or $\alpha_{ij}$).
-We then divided this average gradient by the mean fitness ($\bar W$) to put it on the scale of relative fitness, and thus interpretable as a selection gradient.
-We estimated selection gradients separately for each food-web treatment.
-We also determined whether selection gradients differed between food-web treatments by calculating the difference in bootstrapped replicates between treatments.
-Note that we doubled all quadratic terms prior to calculating selection gradients to put them on the same scale as estimates of directional and correlational selection [@Stinchcombe2008].
-
-**Selective constraints**: <!--We measured evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
--->The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
-
-$$\textbf{Slope} = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} $$
-where each $\beta_i$ corresponds to the directional selection gradient acting on each trait.
-By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e.
-95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
-This gives insight as to whether there is a specific combination of phenotypes favored by natural selection (i.e.
-more traits under directional selection), or whether multiple trait combinations have comparable fitness (i.e.
-less traits under directional selection).
-
-**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) are governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
-
-$$\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
-
-where each $\gamma_{ii}$ (diagonal) corresponds to the quadratic selection gradient acting on a trait, and each $\gamma_{ij}$ (off-diagonal) corresponds to the correlational selection gradient acting on a particular trait combination.
-Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
-Subtracting these two matrices results in the curvature matrix of the adaptive landscape:
-
-$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
-where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
-<!--In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
-Similarly, any nonzero covariance terms (off-diagonal) indicate the effects of selection on additive genetic covariance between two traits.
--->We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI.
-We also used this information to determine whether the curvature of each component differed between our food-web treatments.
-
-Knowledge of the curvature matrix alone gives an incomplete picture of its indirect effect on genetic constraints.
-This is because genetic constraints are ultimately determined by the structure of the G-matrix, and therefore also depend on its structure before selection.
-Although we do not know the underlying G-matrix for the traits we measured in this experiment, we can still gain insight to how our food-web treatment would alter genetic constraints more generally.
-Specifically, we calculated how our best estimate of the curvature matrix (mean values) in each treatment changed the structure of `r n_Gmats` random G-matrices for the next generation.
-We restricted the range of additive genetic variance (*V~G~*) in these G-matrices to between 0 and 0.5 to reflect typical ranges in narrow-sense heritability values (*h*^2^; note that *h*^2^ = *V~G~* when the phenotypic variance is scaled to 1).
-Note that this analysis assumes that the effects of recombination and mutation on the G-matrix are much smaller than the effects of selection, which appears to be a reasonable assumption over short time scales [@Arnold2008].
-
-The G-matrix itself is a complex structure, but has a clear theoretical link to the evolvability of phenotypic traits [@Hansen2008].
-<!--We used evolvability as our measure of genetic constraint, as it has a solid foundation in theory of quantitative genetics and adaptive landscapes [@Hansen2008].
--->Evolvability measures the ability for a trait to evolve toward a given direction of selection [@Hansen2008].
-In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can compute its average evolvability over random selection gradients [@Hansen2008; @Melo2015].
-By computing the average evolvability (here, we used `r n_random_gradients` random $\beta$s) for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of the associated traits.
-We report the distribution of these effect sizes, rather than conduct a statistical test, because the number of replicates in a simulation can be arbitrarily high, thus making any effect size statistically significant [@White2014].
-
-<!--
-Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature matrix in each food-web treatment.
-This provides a conservative estimate of the factors contributing to the curvature of the adaptive landscape.
-
-Note that our metrics of selective and genetic constraints do not put much stock in differences in the magnitude of selection between food-web treatments.
-This is because there is a high likelihood that we are underestimating the magnitude of selection in our treatment that excludes larval parasitoids.
-We expect this because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (fig.
-\ref{fig:Conceptual}).
-Therefore, our short-term removal of larval parasitoids has not allowed for an increase in egg parasitoid abundance after being released from intraguild predation.
-An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates.
-A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--><!-- This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).-->
-
-## Adjusting for biased measurements of selection
-
-Rather than imposing selection, parasitoids may influence the expression of herbivore traits which could bias measurements of selection.
-In our system, it was plausible that parasitoids may influence chamber diameter by altering larval feeding behavior or killing larvae before they complete their development.
-To estimate this potential bias, we subset our data to only include galls where there was variation in larval survival within the same gall (i.e.
-1 > mean survival > 0).
-If we assume that larvae within each gall should have similar chamber diameters because they come from the same clutch and experience the same local environment (an assumption our data supports: gall ID explains 54% of the variance in chamber diameter), then the relationship between chamber diameter and larval survival in this data subset represents the effect of parasitism on trait expression (i.e.
-bias).
-We used a GLMM with the same structure as described previously except that we modeled only a linear relationship between chamber diameter and larval survival ($\alpha_{\text{Diam}}$).
-We detected a positive bias in both food-web treatments (original $\alpha_{\text{Diam}}$=
-`r round(fixef(biased_foodweb_model)["FoodwebOriginal:sc.Diam"],2)` 
-[`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.low,2)`,
-`r round(filter(biased_foodweb_confint, term=="FoodwebOriginal:sc.Diam")$conf.high,2)`]; removal $\alpha_{\text{Diam}}$=
-`r round(fixef(biased_foodweb_model)["FoodwebExtinction:sc.Diam"],2)` 
-[`r round(filter(biased_foodweb_confint, term=="FoodwebExtinction:sc.Diam")$conf.low,2)`,
-`r round(filter(biased_foodweb_confint, term=="FoodwebExtinction:sc.Diam")$conf.high,2)`]), indicating that unadjusted relationships would overestimate the strength of selection on chamber diameter.
-To account for this bias, we substracted our mean estimates of bias from our estimates with the full dataset prior to calculating chamber diameter's selection surface and directional selection gradient.
-
-## Measuring selection on egg parasitoids
-
-Once parasitized, the gall phenotype becomes the phenotype of the egg parasitoid.
-This phenotype may influence the egg parasitoid's survival in the face of larval parasitoids, and thus experiences selection.
-Our food-web manipulation allows us to measure selection imposed by larval parasitoids on the phenotype of egg parasitoids.
-Using the same models as described above, we substituted egg parasitism as our response variable to quantify selection surfaces and selection gradients acting on the egg parasitoid.
-Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate selection imposed by larval parasitoids.
-This comparison is still useful though in determining the extent to which the loss of consumers may have indirect evolutionary effects by altering selection on multiple interacting populations.
-
-All analyses and visualizations were conducted in R [@R2018].
-Unless otherwise noted, we report mean estimates of selection surfaces and selection gradients with 95% confidence intervals in brackets.
-Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
-This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [@Arnold2001].
-We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
-All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
-
-# Results
-
-## Consumer loss increases selective constraints
-
-\indent We found that the removal of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
-For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}C).
-This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
-Specifically, when we subset our data to focus on differences between parasitoid guilds, we found that larval parasitoids actually impose directional selection for larger clutch sizes (larval parasitoids $\beta_{\text{Clutch}}$=
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`]).
-This conflicting selection is likely due to trait differences between guilds, as larger clutches may be easier targets for egg parasitoids to find, but the more complex gall structure may be more difficult for larval parasitoids to oviposit through.
-
-We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, the overall magnitude of selection did not differ between treatments (table \ref{Table:Gradients}).
-Still, there was no clear evidence of directional selection on oviposition in the original food web (table \ref{Table:Gradients}).
-<!--This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.-->Chamber diameter experienced positive directional selection in both food-web treatments (fig.
-\ref{fig:UV_Landscape}A).
-Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival <!--(selection surfaces: original $\alpha_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`])-->
-(selection surfaces: contrast $\alpha_{\text{Diam}}$=
-`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` 
-[`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival of gall midges in the original food web <!--(original $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$conf.high,2)`]; extinction $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`])-->
-(contrast $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high,2)`]).
-We expect this difference to be transient though, since egg parasitoids would increase in abundance once they are released from intraguild predation, which would make the strength of selection on gall diameter comparable to the original food web (if removal $\bar W$=original $\bar W$, then contrast $\beta_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_long_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]).
-It is worth noting that positive selection on chamber diameter in both treatments was unexpected.
-For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is strongly correlated with an unmeasured trait that is under selection (e.g.
-immune response).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}).
-This was not due to any difference between egg and larval parasitoids ($\beta_{\text{Diam}}$ contrast =
-`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was due to the lower average survival in complex food webs ($\bar W$ contrast `r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean, 2)`
-[`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low, 2)`,
-`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high, 2)`]).-->
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in the original food web and with the removal of larval parasitoids.}
-\label{Table:Gradients}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
-\hline
-$\beta_{\text{Diam}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$conf.high,2)`] } & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
-
-$\beta_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] } & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
-
-$\beta_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] } &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Pref:Pref}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] & 
-\textbf{
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Pref}}$ & 
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_grads, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-```{r UV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in the original (orange) and removal (blue) food webs (orange).
-Thin lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
-knitr::include_graphics("../analyses/UV_landscapes.pdf")
-```
-
-To visualize the multivariate effects of these selective constraints, we plotted the adaptive landscape for each trait combination in each treatment (fig.
-\ref{fig:MV_Landscape}).
-The arrows in fig.
-\ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while contours represent predicted survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
-This indicates that the loss of consumers more strongly favored a specific combination of traits, rather than allowing for multiple trait combinations to have comparable fitness.
-
-```{r MV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
-Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
-This indicates that the loss of consumers more strongly favored a specific combination of traits.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
-knitr::include_graphics("../analyses/MV_landscapes.pdf")
-```
-
-## Consumer loss indirectly increases genetic constraints
-
-\indent The curvature of the adaptive landscape indirectly affects genetic constraints and is influenced by directional, quadratic, and correlational selection gradients.
-There was no clear evidence of correlational selection for any combination of traits in either food-web treatment (table \ref{Table:Gradients}).
-Similarly, there was no clear evidence of quadratic selection on chamber diameter or clutch size in either food-web treatment (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}A,C).
-In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
-The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the exclusion of larval parasitoids (fig.
-\ref{fig:UV_Landscape}B).
-This dampened relationship was partly due to a trend for nonlinear selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
-[`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
-This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.
-
-Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
-
-$$\textbf{C} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
-
-Of the different components of the curvature matrix, we found that only the curvature of oviposition preference differed between food-web treatments.
-Specifically, selection in the removal food web acted to decrease the additive genetic variance in preference relative to the original food web.
-
-$$\textbf{C}_{\text{Original}} = \begin{pmatrix} 
-`r round(original_curvs_df["C.Diam","mean"],2)`\: [`r round(original_curvs_df["C.Diam","low"],2)`,`r round(original_curvs_df["C.Diam","high"],2)`] &  &  \\  
-`r round(original_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(original_curvs_df["C.Diam:Clutch","low"],2)`,`r round(original_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(original_curvs_df["C.Clutch","mean"],2)`\: [`r round(original_curvs_df["C.Clutch","low"],2)`,`r round(original_curvs_df["C.Clutch","high"],2)`] &  \\
-`r round(original_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(original_curvs_df["C.Diam:Pref","low"],2)`,`r round(original_curvs_df["C.Diam:Pref","high"],2)`] & `r round(original_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(original_curvs_df["C.Clutch:Pref","low"],2)`,`r round(original_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(original_curvs_df["C.Pref","mean"],2)`\: [`r round(original_curvs_df["C.Pref","low"],2)`,`r round(original_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$
-
-$$\textbf{C}_{\text{Removal}} = \begin{pmatrix} 
-`r round(extinction_curvs_df["C.Diam","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam","low"],2)`,`r round(extinction_curvs_df["C.Diam","high"],2)`] &  &  \\  
-`r round(extinction_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Clutch","low"],2)`,`r round(extinction_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(extinction_curvs_df["C.Clutch","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch","low"],2)`,`r round(extinction_curvs_df["C.Clutch","high"],2)`] &  \\
-`r round(extinction_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Diam:Pref","low"],2)`,`r round(extinction_curvs_df["C.Diam:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Clutch:Pref","low"],2)`,`r round(extinction_curvs_df["C.Clutch:Pref","high"],2)`] & `r round(extinction_curvs_df["C.Pref","mean"],2)`\: [`r round(extinction_curvs_df["C.Pref","low"],2)`,`r round(extinction_curvs_df["C.Pref","high"],2)`] \end{pmatrix}$$
-
-$$\textbf{C}_{\text{Removal-Original}} = \begin{pmatrix} 
-`r round(difference_curvs_df["C.Diam","mean"],2)`\: [`r round(difference_curvs_df["C.Diam","low"],2)`,`r round(difference_curvs_df["C.Diam","high"],2)`] &  &  \\  
-`r round(difference_curvs_df["C.Diam:Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Clutch","low"],2)`,`r round(difference_curvs_df["C.Diam:Clutch","high"],2)`] & `r round(difference_curvs_df["C.Clutch","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch","low"],2)`,`r round(difference_curvs_df["C.Clutch","high"],2)`] &  \\
-`r round(difference_curvs_df["C.Diam:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Diam:Pref","low"],2)`,`r round(difference_curvs_df["C.Diam:Pref","high"],2)`] & `r round(difference_curvs_df["C.Clutch:Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Clutch:Pref","low"],2)`,`r round(difference_curvs_df["C.Clutch:Pref","high"],2)`] & \textbf{`r round(difference_curvs_df["C.Pref","mean"],2)`\: [`r round(difference_curvs_df["C.Pref","low"],2)`,`r round(difference_curvs_df["C.Pref","high"],2)`]} \end{pmatrix}$$
-
-Interestingly, when we translate the effect of the curvature matrix onto genetic constraints in the next generation, we see that the loss of consumers had a general tendency to decrease evolvability (fig.
-\ref{fig:Evolvability}).
-Specifically, the removal food web decreased the average evolvability of `r round(sum(random_evolvabilities$Diff < 0) / length(random_evolvabilities$Diff) * 100,0)`% of the random G-matrices in our simulation.
-If anything, we expect that this underestimates the true effect of our removal treatment.
-For example, if we assume egg parasitoids would eventually impose similar impact on mean fitness once they are released from intraguild predation (i.e.
-removal $\bar W$=original $\bar W$), then the removal food web decreases the average evolvability in `r round(sum(long_random_evolvabilities$Diff < 0) / length(long_random_evolvabilities$Diff) * 100,0)`% of the G-matrix scenarios.
-
-<!--In our study, this corresponds to:
-
-$$\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
-
-$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
-\bigskip
-
-where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
-In order to obtain a conservative estimate of the factors contributing to the curvature, we only used estimates of selection that clearly differed from zero (bold values in table \ref{Table:Gradients}), otherwise we set estimates of selection to zero (non-bold values in table \ref{Table:Gradients}) prior to our calculation.
-We found that the curvatures of the adaptive landscape exhibited the following structures:
-
-$$\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
-`r round(original_gammas["Diam","Diam"],2)` &  &  \\  
-`r round(original_gammas["Clutch","Diam"],2)` & `r round(original_gammas["Clutch","Clutch"],2)` &  \\  
-`r round(original_gammas["Pref","Diam"],2)` & `r round(original_gammas["Pref","Clutch"],2)` & `r round(original_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
-`r round(original_betas["Diam",],2)`\cdot`r round(original_betas["Diam",],2)` &  &  \\  
-`r round(original_betas["Clutch",],2)`\cdot`r round(original_betas["Diam",],2)` & `r round(original_betas["Clutch",],2)`\cdot`r round(original_betas["Clutch",],2)` &  \\  
-`r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Diam",],2)` & `r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Clutch",],2)` & `r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Pref",],2)` \end{pmatrix}$$
-
-$$\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
-`r round(original_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(original_curvature["Clutch","Diam"],2)` & `r round(original_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(original_curvature["Pref","Diam"],2)` & `r round(original_curvature["Pref","Clutch"],2)` & `r round(original_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-$$\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
-`r round(extinction_gammas["Diam","Diam"],2)` &  &  \\  
-`r round(extinction_gammas["Clutch","Diam"],2)` & `r round(extinction_gammas["Clutch","Clutch"],2)` &  \\  
-`r round(extinction_gammas["Pref","Diam"],2)` & `r round(extinction_gammas["Pref","Clutch"],2)` & `r round(extinction_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
-`r round(extinction_betas["Diam",],2)`\cdot`r round(extinction_betas["Diam",],2)` &  &  \\  
-`r round(extinction_betas["Clutch",],2)`\cdot`r round(extinction_betas["Diam",],2)` & `r round(extinction_betas["Clutch",],2)`\cdot`r round(extinction_betas["Clutch",],2)` &  \\  
-`r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Diam",],2)` & `r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Clutch",],2)` & `r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Pref",],2)` \end{pmatrix}$$
-
-$$\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
-`r round(extinction_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(extinction_curvature["Clutch","Diam"],2)` & `r round(extinction_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(extinction_curvature["Pref","Diam"],2)` & `r round(extinction_curvature["Pref","Clutch"],2)` & `r round(extinction_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-Remember that we can infer the indirect effects of selection on genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-The structure of these matrices indicates that the extinction of larval parasitoids increased the number of genetic constraints on gall midges (6 of 6) relative to the original food web (1 of 6).
-For example, directional selection resulting from the exclusion of larval parasitoids acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the original food web.
-For genetic covariances, the combined effects of directional selection resulting from consumer extinctions favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
-\ref{fig:MV_Landscape}).
-In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the original food web (fig.
-\ref{fig:MV_Landscape}).
--->
-
-```{r Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Evolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for each food-web treatment.
-We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices (i.e.
-the change in evolvability was negative for 71% of the simulations), suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
-knitr::include_graphics("../analyses/delta_evolvability.pdf")
-```
-
-## Selection on egg parasitoids
-
-The removal of larval parasitoids not only had direct effects on gall midge fitness, but also imposed indirect effects that would be felt in the next generation.
-For example, the removal of larval parasitoids altered the relationship between gall midge preference and the probability of observing egg parasitoids (table \ref{Table:ExtendedGradients}), such that the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
-\ref{fig:EggPtoid_Selection}).
-
-\bigskip
+\beginsupplement <!-- start numbering for supplementary material -->
 
@@
 
-```{r EggPtoid_Selection, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:EggPtoid_Selection}Selection imposed by larval parasitoids on egg parasitoids (*Platygaster* sp.).
-The bold line represents the average difference in the probability of observing the egg parasitoid (original minus removal of larval parastioids) as a function of gall midge oviposition preference.
-Thin lines represent bootstrapped replicates to show the uncertainty in selection.
-For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-The decrease in the probability of observing egg parasitoids at high gall-midge densities indicate that larval parasitoids impose nonlinear selection on egg parasitoids."}
-knitr::include_graphics("../analyses/selection_on_Platygaster.pdf")
-```
-
-# Discussion
-
-<!--Summary-->
-We found that the removal of larval parasitoids constrained phenotypic evolution in gall midges in two key ways.
-First, more traits contributed to the slope of the adaptive landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
-Second, excluding larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of associated traits.
-Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's adaptive potential in the face of novel selection pressures.
-Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
-Taken together, our study provides experimental evidence from the field that the loss of consumers may constrain the adaptive potential of remaining populations.
-
-<!--Selective constraints-->
-All three phenotypic traits we examined experienced directional selection when we excluded larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
-large chamber diameter, small clutch size, and avoidance of conspecifics).
-In contrast, we did not observe clear evidence of selective constraints on clutch size and oviposition preference in the original food web.
-This suggests that there are many optimal phenotypes (adaptive peaks), or in this case, a flat adaptive landscape where there are no fitness consequences for phenotypic change in these traits.
-<!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
-This also implies that as selective constraints dampen in food webs with more consumers, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
-genetic drift, gene flow, and mutation).<!-- This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
-As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
-[Removing because this statement is simply not true]-->
-Interestingly, this aligns with @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
-@Schluter1996 found support for this hypothesis from data on natural populations of several vertebrate species, including threespine sticklebacks, a few species of songbirds, and mice from the genus *Peromyscus*.
-All of these species occupy intermediate trophic levels and are likely embedded in complex food webs, which is consistent with our suggestion that genetic constraints may have a stronger influence in food webs with more consumers.
-
-<!--Indirect effects of selective constraints-->
-We also found evidence for a general decrease in trait evolvability when we excluded larval parasitoids due to changes in the curvature of the adaptive landscape<!--indirect effects of selection on the population's G-matrix-->.
-This result was driven by nonlinear selection on gall midge oviposition preference in the original food web, which was due to both increases in intraguild predation and the lower mean survival of gall midges.
-While these results are intriguing, they still indicate that the indirect effects of selection are contingent on the structure of a population's G-matrix (i.e.
-consumer removals *increased* evolvability in 29% of the scenarios).
-This highlights the importance of future studies to characterize the G-matrix in order to accurately predict how changes in network context will alter the evolutionary potential of remaining populations.
-<!--The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
-When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
-Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
-Together, this suggests that consumer extinctions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
--->Indeed, current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017].
-Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that emerge in a network of interacting species.
-
-<!-- Generality of results -->
-The generality of our results likely depends on the relative abundance and functional differences between consumers in a community.
-For example, if consumers do not differ from each other, then we do not expect the loss of consumers to modify evolutionary constraints.
-Also, many consumers may be at too low of abundances to impose selection on their resources.
-Rank abundance curves [@Preston1948] and the disproportionate number of weak interactions in diverse communities [@Paine1992] support this notion.
-This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles.
-When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits.
-For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
-Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.
-On the other hand, different consumers may impose selection on different traits, favoring a particular combination of traits and thus greater selective constraints.
-Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
-We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions [@Bascompte2009].
-<!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
-
-<!-- Caveats -->
-An important caveat of our study is that we did not due a factorial manipulation of both parasitoid guilds, making it difficult to conclude whether our results would change if we manipulated the presence/absence of the dominant egg parasitoid.
-If we assume that higher-order interactions [@Levine2017] are weak between parasitoid guilds, then we can gain insight to how the loss of the egg parasitoid would alter selection by isolating the contribution of larval parasitoids to selection in our original food-web treatment.
-When we do this, we see the same qualitative effects as we do when we removed larval parasitoids.
-For example, we see clear evidence of all three traits being under directional selection (i.e.
-greater selective constraints, Appendix A) as well as a decrease, albeit smaller, in trait evolvability under different G-matrix scenarios (`r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`%, Appendix A).
-This suggests that our results could be robust to this caveat, which was simply not possible to manipulate given the biology of our system (see *Manipulating Food-web Structure* section for explanation).
-
-<!--Indirect evolutionary effects-->
-Our results suggest that the loss of consumers may not only directly affect connected species, but also result in indirect evolutionary effects.
-In our study, this indirect effect arises from egg parasitoids being released from intraguild predation when we excluded larval parasitoids.
-This release occurs more on trees with high larval densities, which could intensify selection on gall midge oviposition preference.
-A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in a community context [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
-If indirect evolutionary effects are common [@Miller1996; @Walsh2013; @Guimaraes2017], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
-
-<!-- Community context shaping adaptation to environmental change --> 
-There is a growing number of theoretical studies on adaptation to directional environmental change that incorporate species interactions [e.g.
-@deMazancourt2008; @Johansson2008; @Norberg2012; @Osmond2017PredatorsHelpPrey].
-This work has given insight to the mechanisms by which interactions between species can modify their adaptive potential<!--pairwise interactions modify the adaptive potential of species-->.
-Our study hints at a novel mechanism, whereby a more diverse consumer community alters the adaptive landscape in such a way that facilitates future adaptation by allowing genetic and phenotypic variation to persist.
-This mechanism only emerges once we consider selection imposed by multiple species on multiple traits.
-<!--move beyond pairwise interactions to consider selection on multiple traits in a community context.-->However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
-This negative effect of species diversity on adaptation occurs because there is a greater chance that the optimal phenotype is already occupied by a competitor in a more diverse community.
-More work is needed to examine how the distribution of different interaction types affects adaptation to environmental change in species-rich communities.
-
-<!-- Caveats 
-Our study has some limitations to consider when relating our findings to the effect of consumer extinctions on evolutionary constraints more generally.
-First, we removed other sources of mortality prior to our analyses.
-While this was necessary to avoid confounding estimates of selection with effects on phenotypic expression, we may be overestimating the effects of selection due to consumers.
-Second, our metrics of evolutionary constraints do not account for variation in the magnitude of selection pressures.
-While metrics that incorporate the magnitude of selection are possible [@Hansen2008], they were not appropriate for our study as our experimental removal of larval parasitoids artificially increased the mean fitness of gall midges (in the short term), which dampens the magnitude of selection gradients in this treatment [@Hunter2018].
-This is why we used more qualitative metrics of evolutionary constraints, which are robust to this artificial effect and simply require sufficient sample sizes to detect evidence of selection.
--->
-<!--Note though that this should have made it more difficult to detect selection in this treatment, yet it was this extinction treatment that increased the number of traits under selection.
-<!--results in a transient dynamic in the strength (but not direction) of selection.
-Such transient dynamics may be common in short-term experimental studies of natural selection, but they can be detected by using natural history information and dissecting the sources of selection (e.g.
-quantifying selection surfaces and treatment effects on mean fitness) as we did here.
--->
-
-<!-- Conclusions -->
-Our study gives insight to how the loss of consumers alters evolutionary constraints on remaining populations.
-In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
-Our work also highlights some key challenges for predicting phenotypic evolution in rapidly changing communities.
-First, the simplification of ecological communities may actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.
-Second, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait, yet our results highlight that the number of traits under selection may change with the community context.
-Importantly, we found that different species/guilds imposed different selection pressures.
-Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the ecological community.
-We expect that a continued integration of adaptive landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
-
-# Acknowledgements
-
-We thank the staff of Humboldt Bay National Wildlife Refuge (U.S.
-Fish and Wildlife Service) for facilitating experimental logistics.
-For assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
-For funding support, we thank the University of British Columbia (James Robert Thompson Fellowship and Four-Year Fellowship to M.A.
-Barbour), NSERC (Discovery grant to Greg Crutsinger), and the Swiss National Science Foundation (grant 31003A_160671 to J.
-Bascompte).
-
-# Author Contributions
-
-M.A.B.
-conceived the idea behind the study and designed the field experiment.
-M.A.B.
-and B.L.
-setup and conducted the experiment.
-M.A.B., A.S., and C.J.G.
-collected the data.
-M.A.B.
-analyzed the data.
-M.A.B.
-wrote the manuscript with primary input from J.B.
-and additional feedback from C.J.G.
-
-# Data Accessibility
-
-All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
-
-<!-- TABLE NOT REFERENCED IN RESULTS
-
-\begin{table}[h]
-\caption{Relationship between absolute fitness (larval survival) and phenotypic traits of gall midges in complex vs. simple food webs.}
-\label{Table:Coefs}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Coefficient} & \textbf{Original} & \textbf{Extinction} & \textbf{Contrast}  \\ 
-\hline
-$\alpha_{\text{Diam}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.high,2)`] }& 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
-
-$\alpha_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] }& 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
-
-$\alpha_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\alpha_{\text{Diam,Diam}}$ &
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\alpha_{\text{Clutch,Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\alpha_{\text{Pref,Pref}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\
-
-$\alpha_{\text{Diam,Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\alpha_{\text{Diam,Pref}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\alpha_{\text{Clutch,Pref}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\alpha_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
--->
-
-# Appendix A
-
-\bigskip
+\newpage
 
@@
 
-<!-- Add the XX% change in evolvability -->
+\newpage
 

### 2019-09-18 manuscript/supplementary_material.tex
generate supplementary material.

--- 2019-05-19 manuscript/manuscript.tex
@@
 
-\begin{center} \LARGE Consumer extinctions constrain phenotypic evolution in the resulting food web \end{center}
+\begin{center} \LARGE Supplementary Material: \\
+Loss of consumers constrains phenotypic evolution in the resulting food web \end{center}
 
@@
 
-\bigskip
-<!----> \emph{Manuscript elements}: table 1, table 2, figure 1, figure
-2, figure 3, figure 4. All figures should be printed in color.
+\linenumbers{} \modulolinenumbers[3]
 
-\bigskip
-
-\emph{Keywords}: adaptive landscape, ecological networks,
-eco-evolutionary dynamics, natural selection, host-parasitoid;
-complexity.
-
-\bigskip
-
-\emph{Number of words}: 3109
-
-\bigskip
-
-\emph{Manuscript type}: Article.
-
-\bigskip
-
-\footnotesize Prepared using an \emph{Am. Nat.} inspired \LaTeX{}
-template for Rmarkdown. \normalsize
-
-\linenumbers{} \modulolinenumbers[3]
+\newcommand{\beginsupplement}{%
+        \setcounter{table}{0}
+        \renewcommand{\thetable}{S\arabic{table}}%
+        \setcounter{figure}{0}
+        \renewcommand{\thefigure}{S\arabic{figure}}%
+     }
 
@@
 
-\section{Abstract}\label{abstract}
-
-Global change is altering the structure of ecological networks; however,
-we are currently in a poor position to predict how these altered
-communities will affect the evolutionary potential of remaining
-populations. Theory on adaptive landscapes provides a framework for
-predicting how selection constrains phenotypic evolution, but often
-treats the community context of evolving populations as a ``black box''.
-Here, we integrate ecological networks and adaptive landscapes to
-examine how changes in food-web structure shape evolutionary
-constraints. We conducted a field experiment that simulated the
-extinction of a guild of larval parasitoids that were able to impose
-selection on an insect herbivore. We then measured herbivore survival as
-a function of three key phenotypic traits. We found that the number of
-traits under selection increased with the extinction of larval
-parasitoids. In contrast, the adaptive landscape was more neutral in the
-original food web because different parasitoid guilds impose different
-selection pressures, minimizing relative fitness differences among
-phenotypes. Our results suggest that the loss of trophic interactions
-due to consumer extinctions can impose greater constraints on phenotypic
-evolution. This indicates that the simplification of ecological
-communities may constrain the adaptive potential of remaining
-populations to future environmental change.
-
-\newpage
-
-\section{Introduction}\label{introduction}
-
-The adaptive landscape provides a powerful framework for understanding
-how natural selection has shaped the evolution of biodiversity ---from
-genes to phenotypes to species
-\citep{Wright1931, Simpson1944, Arnold2001}. More than a metaphor, the
-adaptive landscape links quantitative genetic and phenotypic variation
-to evolution by natural selection
-\citep{Lande1979, Arnold1984applications, Arnold1984theory}. Ecological
-interactions often play a key role in shaping adaptive landscapes, as
-evidenced by the role of antagonistic \citep{Schluter2000, Abrams2000}
-and mutualistic \citep{Bronstein2006} interactions in driving
-evolutionary change. Although there is clear evidence that pairwise
-interactions can shape the adaptive landscape, we still have a poor
-understanding of how the adaptive landscape is shaped by the community
-context \citep{McPeek2017, terHorst2018}. Resolution on how the
-community context shapes phenotypic evolution is urgently needed though,
-given the rapid impacts of climate change on ecological communities
-\citep{Scheffers2016}.
-
-Ecological networks, such as food webs describing who-eats-whom in
-ecological communities, provide an explicit representation of the
-community context \citep{Bascompte2014, McCann2012}. Here, we integrate
-ecological networks and adaptive landscapes to understand how the
-community context constrains evolutionary change \citep{Arnold1992}.
-Different aspects of evolutionary constraints can be inferred by
-quantifying the slope and curvature of the adaptive landscape. For
-example, the slope is determined by directional selection gradients
-acting on each phenotypic trait and influences the trajectory of
-evolutionary change \citep{Lande1979, Arnold1992}. Selective constraints
-on evolution increase with the number of traits under directional
-selection, as this diminishes the number of optimal solutions
-\citep{Arnold2003}. The curvature of the adaptive landscape can also
-constrain evolution through its indirect effect on genetic constraints
-\citep{Arnold1992, Hansen2008}. Genetic constraints are largely governed
-by a population's \textbf{G}-matrix ---the additive genetic variances
-and covariances between traits \citep{Hansen2008}. In general, genetic
-constraints will increase with the number of traits under directional or
-stabilizing selection, as this will decrease the additive genetic
-variance in those traits \citep{Hansen2008}. Genetic constraints may
-also increase with the number of trait combinations under correlational
-selection, as this type of selection decreases the evolutionary
-independence of traits \citep{Hansen2008}. If we want to predict how the
-community context constrains evolutionary change, we must understand how
-ecological networks shape the adaptive landscape.
-
-Global change is altering the structure of ecological networks, which
-may influence evolutionary constraints in a number of ways. For example,
-in a food web, if different consumers impose directional selection on
-different traits of a shared resource, then a more diverse consumer
-community may constrain evolution by increasing the number of traits
-under selection. Alternatively, if consumers impose selection on
-different values of a trait, then their selective effects would cancel
-each other out in more diverse communities. To examine these different
-possibilities, we conducted a field experiment that simulated the
-extinction of a consumer guild associated with an abundant insect
-herbivore (\emph{Iteomyia salicisverruca}, Family Cecidomyiidae; fig.
-\ref{fig:Conceptual}). The larvae of this herbivore induce tooth-shaped
-galls when they feed on the developing leaves of willow trees
-\citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect larva from
-attack by generalist predators (e.g.~ants, spiders), but they suffer
-high mortality from egg and larval parasitoids \citep{Barbour2016}. We
-manipulated food-web structure by either excluding or allowing the guild
-of larval parasitoids to impose selection on gall midge and egg
-parasitoid traits (fig. \ref{fig:Conceptual}). We then applied modern
-statistical methods to quantify how changes in food-web structure
-altered the slope and curvature of the adaptive landscape of the gall
-midge and egg parasitoid. Taken together, our study gives insight to how
-local extinctions may constrain the evolution of interacting
-populations.
-
-\begin{figure}
-\centering
-\includegraphics{analyses/complex_simple_foodwebs_v2.jpeg}
-\caption{\label{fig:Conceptual}Experimental manipulation of food-web
-structure associated with a leaf-galling midge (\emph{Iteomyia
-salicisverruca}) feeding on the willow \emph{Salix hookeriana}. Black
-arrows denote the flow of energy in this network of trophic
-interactions. In the original food web, we allowed the full suite of egg
-and larval parasitoids to impose selection. To simulate consumer
-extinction, we used mesh bags to exclude the guild of larval
-parasitoids, only allowing the egg parasitoid (\emph{Platygaster} sp.)
-to impose selection. Larval parasitoids include the following species
-(from left to right): \emph{Mesopolobus} sp. (Family: Pteromalidae);
-\emph{Tetrastichus} sp. (Family: Eulophidae); and \emph{Torymus} sp.
-(Family: Torymidae).}
-\end{figure}
-
-\section{Methods}\label{methods}
-
-\subsection{Study Site}\label{study-site}
-
-We conducted our study within a four-year old common garden experiment
-of coastal willow (\emph{Salix hookeriana}) located at Humboldt Bay
-National Wildlife Refuge (HBNWR) (40 40'53``N, 124 12'4''W) near Loleta,
-California, USA. This common garden consists of 26 different willow
-genotypes that were collected from a single population of willows
-growing around Humboldt Bay. Stem cuttings of each genotype (25
-replicates per genotype) were planted in a completely randomized design
-in two hectares of a former cattle pasture at HBNWR. Willows at our
-study site begin flowering in February and reach their peak growth in
-early August. During this study, willows had reached 5 - 9m in height.
-Further details on the genotyping and planting of the common garden are
-available in \citet{Barbour2015}.
-
-\subsection{Manipulating Food-web
-Structure}\label{manipulating-food-web-structure}
-
-We setup our food-web manipulation across 128 plants soon after galls
-began developing on willows in early June of 2013. These 128 plants came
-from eight different plant genotypes that spanned the range of trait
-variation observed in this willow population \citep{Barbour2015}. For
-the original food web (eight replicates per genotype), we used flagging
-tape to mark 14 galled leaves per plant (\textasciitilde{}30 larvae),
-allowing the full suite of egg and larval parasitoids to impose
-selection. Marking galls with flagging tape ensured that all galls had
-similar phenology when we collected galls later in the season. To
-simulate consumer extinctions, we enclosed 14 galled leaves with 10x15cm
-organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three
-parasitoid species that attack during larval development. This treatment
-did not exclude the egg parasitoid \emph{Platygaster} sp., which attacks
-prior to gall initiation \citep[larva initiate gall development in
-Cecidomyiid midges:][]{Gagne1989}. In late August, we collected marked
-and bagged galls from each plant, placed them into 30 mL vials and kept
-them in the lab for 4 months at room temperature. We then opened galls
-under a dissecting scope and determined whether larvae survived to
-pupation (our measure of fitness) or were parasitized. We did not
-include other sources of mortality, such as early larval death, as they
-could influence the expression of the gall phenotype and confound
-estimates of selection. For the food-web treatment that excluded larval
-parasitoids, we further restricted our data by removing any incidental
-instances of parasitism by a larval parasitoid. This represented less
-than 3\% of the observations in this food-web treatment and allowed us
-to focus our inferences of selection on those imposed by the egg
-parasitoid. Our final dataset contains survival estimates for 1285
-larvae from 613 galls and 111 plants.
-
-\subsection{Measuring Phenotypic
-Traits}\label{measuring-phenotypic-traits}
-
-We collected data on three different traits that we expected to
-influence larval survival based on previous work in this system
-\citep{Barbour2016} and other work with gall midges
-\citep{Weis1983, Heath2018}. First, we measured gall diameter as the
-size of each gall chamber to the nearest 0.01 mm at its maximum diameter
-(perpendicular to the direction of plant tissue growth). Previous work
-in this system has shown that larger galls are associated with higher
-survival \citep{Barbour2016}. Second, we measured clutch size by
-counting the number of chambers in each gall
-\citep{Weis1983, Heath2018}. All larvae collected from the same
-multi-chambered gall were scored with the same clutch size. Third, we
-measured oviposition preference as the density of larvae observed on a
-plant in an independent survey. We did this by randomly sampling five
-branches per tree and counting the number of individual gall chambers
-(number of larvae). We then converted these counts to a measure of
-larval density per 100 shoots by counting the number of shoots on the
-last branch we sampled. All larvae collected from the same plant were
-scored with the same oviposition preference. Measuring larval densities
-on plants in the field is a common method for measuring oviposition
-preference \citep{Gripenberg2010}; however, caution must be taken in
-inferring `preference' as larval densities can be influenced by
-processes other than preference \citep{Singer1986}. Fortunately, a
-couple features of our study system suggest that larval densities may be
-a good proxy for oviposition preference. For example, since our data
-comes from a randomized placement of plant genotypes in a common garden,
-there is no consistent bias in which plant genotypes females are exposed
-to while searching for oviposition sites. Also, egg predation is a minor
-source of mortality for galling insects in general \citep{Hawkins1997};
-therefore, we do not expect any prior egg predation to bias our
-estimates of observed larval densities.
-
-\subsection{Quantifying the Adaptive
-Landscape}\label{quantifying-the-adaptive-landscape}
-
-Inferring adaptive landscapes assumes that trait distributions are
-multivariate normal \citep{Lande1983}. To approximate this assumption,
-we log-transformed clutch size and square-root transformed oviposition
-preference. We then scaled all phenotypic traits (mean=0 and SD=1) prior
-to our analyses (detailed below) to ensure that our estimates of
-selection were comparable across traits and with other studies.
-
-Our analysis consisted of three parts. First, we used generalized linear
-mixed models (GLMM) to quantify selection surfaces \textemdash linear
-and nonlinear relationships between absolute fitness (\(W\)) and
-standardized phenotypic traits (\(i\)) of individuals \textemdash in
-each food-web treatment. Second, we translated selection surfaces into
-the scale of relative fitness (\(w\)) in order to calculate standardized
-selection gradients. Third, we used our estimates of selection gradients
-to characterize the slope and curvature of the adaptive landscape, which
-we used to measure evolutionary constraints.
-
-\textbf{Selection surfaces}: Since larval survival was our measure of
-absolute fitness, we used a GLMM that assumed a binomial error
-distribution (and logit-link function). To approximate the selection
-surface, we modelled larval survival as a function of food-web treatment
-as well as linear (\(\alpha_i\)), quadratic (\(\alpha_{ii}\)), and
-linear interactions (\(\alpha_{ij}\)) between each trait. We also
-allowed these selection surfaces (\(\alpha\)) to vary between food-web
-treatments. Note that to obtain valid estimates of linear selection
-surfaces, we removed nonlinear terms prior to estimating linear
-relationships \citep{Lande1983}. Other approaches have been advocated
-for approximating selection surfaces \citep{Schluter1988}; however, our
-approach enables us to calculate selection gradients, and thus is more
-appropriate for approximating the adaptive landscape \citep{Arnold2003}.
-To account for the nonindependence of clutch size (measured at gall
-level) and oviposition preference (measured at plant level) as well as
-any independent effects of willow genotype on larval survival, we
-modelled gall ID nested within plant ID nested within genotype ID as
-random effects. Although statistical models with random effects are not
-common in analyses of natural selection, we think that modelling random
-effects can mitigate biased estimates of selection due to environmental
-covariances between traits and fitness \citep{Rausher1992}. Since our
-end goal was to characterize the relationship between mean trait values
-and mean fitness (adaptive landscape), we assumed the mean value of our
-random effects (i.e., setting them to zero) when calculating selection
-surfaces. We then used parametric bootstrapping (1,000 replicates) to
-estimate the effect of food-web treatment on larval survival as well as
-selection surfaces in each food-web treatment.
-
-\textbf{Selection gradients}: Selection gradients cannot be estimated
-directly from GLMMs of selection surfaces because the response is in
-terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the above model measure the change in
-the logarithm of the odds of surviving (i.e.,
-\(\text{ln}\{W(z)/[1-W(z)]\}\)) associated with 1 SD change in a trait
-with all other traits held fixed at their mean. Therefore, we used the
-method developed by \citet{Janzen1998} to translate selection surfaces
-from the above model into the scale of relative fitness in order to
-calculate directional (\(\beta_i\)), quadratic (\(\gamma_{ii}\)), and
-correlational (\(\gamma_{ij}\)) selection gradients. Briefly, this
-method calculates the average gradient of selection surfaces by
-multiplying the average of \(W(z)[1-W(z)]\) by each regression
-coefficient (e.g. \(\alpha_i\), \(\alpha_{ii}\), or \(\alpha_{ij}\)). We
-then divided this average gradient by the mean fitness (\(\bar W\)) to
-put it on the scale of relative fitness, and thus interpretable as a
-selection gradient. We estimated selection gradients separately for each
-food-web treatment. Note that we doubled all quadratic terms prior to
-calculating selection gradients to put them on the same scale as
-estimates of directional and correlational selection
-\citep{Stinchcombe2008}.
-
-\textbf{Evolutionary constraints}: We measured evolutionary constraints
-by inspecting the slope and curvature of the adaptive landscape. The
-number of selective constraints is determined by the slope of the
-adaptive landscape, which in our study corresponds to:
-
-\[\textbf{Slope} = \begin{pmatrix} \beta_{\text{Diam}} \\ \beta_{\text{Clutch}} \\ \beta_{\text{Pref}} \end{pmatrix} \]
-where each \(\beta_i\) corresponds to the directional selection gradient
-acting on each trait. By comparing the number of directional selection
-gradients that show clear evidence of contributing to the slope (i.e.,
-95\% CI does not overlap zero) in our food-web treatments, we can infer
-the effect of food-web structure on selective constraints.
-
-The indirect effects of selection on the G-matrix
-(\(\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}\)) is
-governed by the curvature of the adaptive landscape
-(\(\text{C}=\gamma - \beta \beta^\text{T}\)), which in our study
-corresponds to:
-
-\[\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}\]
-
-where each \(\gamma_{ii}\) (diagonal) corresponds to the quadratic
-selection gradient acting on a trait, and each \(\gamma_{ij}\)
-(off-diagonal) corresponds to the correlational selection gradient
-acting on a particular trait combination. Note that we ommitted the
-upper triangle of each matrix for clarity since it is simply the
-reflection of the lower triangle. Subtracting these two matrices results
-in the curvature matrix of the adaptive landscape:
-
-\[\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}\]
-where each \(\text{C}_{ii}\) (diagonal) represents the effect of
-selection on the additive genetic variance in a trait, and each
-\(\text{C}_{ij}\) (off-diagonal) represents the effect of selection on
-the additive genetic covariance between a particular trait combination.
-In other words, the sign of diagonal terms of the curvature matrix
-dictate whether selection will increase (+), decrease (-), or cause no
-change (0) in the additive genetic variance of a trait. Similarly, any
-nonzero covariance terms (off-diagonal) are indicative of selection for
-trait integration (i.e., less independence). Therefore, we can infer the
-number of genetic constraints by summing the number of negative signs
-along the diagonal (decrease in additive genetic variance) and the
-number of nonzero terms along the off-diagonal (trait integration) of
-the curvature matrix. For these analyses, we retained estimates for
-selection gradients that showed clear evidence of being different from
-zero (i.e., 95\% CI did not overlap zero) and set other gradients to
-zero, prior to calculating the curvature matrix in each food-web
-treatment. This provides a conservative estimate of the factors
-contributing to the curvature of the adaptive landscape.
-
-Note that our metrics of selective and genetic constraints do not put
-much stock in differences in the magnitude of selection between food-web
-treatments. This is because there is a high likelihood that we are
-underestimating the magnitude of selection in our treatment that
-excludes larval parasitoids. We expect this because larval parasitoids
-not only impose mortality on gall midges, but egg parasitoids as well
-(fig. \ref{fig:Conceptual}). Therefore, our short-term removal of larval
-parasitoids has not allowed for an increase in egg parasitoid abundance
-after being released from intraguild predation. An increase in the
-abundance of egg parasitoids would decrease mean survival of gall
-midges, thus increasing the variance in relative fitness of midges, and
-consequently the magnitude of selection estimates. A recent paper by
-\citet{Hunter2018} highlights this pervasive effect of survival on the
-magnitude of selection estimates. This is why we use more qualitative
-metrics of evolutionary constraints (i.e., selective constraints =
-number of traits under directional selection; genetic constraints =
-number of decreasing variances + nonzero covariances).
-
-\subsection{Adjusting for biased measurements of
-selection}\label{adjusting-for-biased-measurements-of-selection}
-
-Rather than imposing selection, parasitoids may influence the expression
-of herbivore traits which could bias measurements of selection. In our
-system, it was plausible that parasitoids may influence chamber diameter
-by altering larval feeding behavior or killing larvae before they
-complete their development. To estimate this potential bias, we subset
-our data to only include galls where there was variation in larval
-survival within the same gall (i.e.~1 \textgreater{} mean survival
-\textgreater{} 0). If we assume that larvae within each gall should have
-similar chamber diameters because they come from the same clutch and
-experience the same local environment (an assumption our data supports:
-gall ID explains 54\% of the variance in chamber diameter), then the
-relationship between chamber diameter and larval survival in this data
-subset represents the effect of parasitism on trait expression
-(i.e.~bias). We used a GLMM with the same structure as described above
-except that we modeled only a linear relationship between chamber
-diameter and larval survival (\(\alpha_{\text{Diam}}\)). We detected a
-positive bias in both food-web treatments (original
-\(\alpha_{\text{Diam}}\)= 0.36 {[}0.05, 0.67{]}; extinction
-\(\alpha_{\text{Diam}}\)= 0.42 {[}0.01, 0.82{]}), indicating that
-unadjusted relationships would overestimate the strength of selection on
-chamber diameter. To account for this bias, we substracted our mean
-estimates of bias from our estimates with the full dataset prior to
-calculating chamber diameter's selection surface and directional
-selection gradient.
-
-\subsection{Measuring selection on egg
-parasitoids}\label{measuring-selection-on-egg-parasitoids}
-
-Once parasitized, the gall phenotype becomes the phenotype of the egg
-parasitoid. This phenotype may influence the egg parasitoid's survival
-in the face of larval parasitoids, and thus experiences selection. Our
-food-web manipulation allows us to measure selection imposed by larval
-parasitoids on the phenotype of egg parasitoids. Using the same models
-as described above, we substituted egg parasitism as our response
-variable to quantify selection surfaces and selection gradients acting
-on the egg parasitoid. Note that we cannot test the effect of food-web
-structure on the egg parasitoid's adaptive landscape ---we can only
-estimate selection imposed by larval parasitoids. This comparison is
-still useful though in determining the extent to which the community
-context may have indirect evolutionary effects by altering selection on
-multiple interacting populations.
-
-All analyses and visualizations were conducted in R \citep{R2018}.
-Unless otherwise noted, we report mean estimates of selection surfaces
-and selection gradients with 95\% confidence intervals in brackets. Note
-that for visualizing the adaptive landscape we restrict trait axes to
-\(\pm 1\) SD of the mean trait value. This emphasizes the fact that we
-can only reliably estimate the shape of the adaptive landscape near the
-mean phenotype of the population \citep{Arnold2001}. We also plot mean
-larval survival on a natural log scale to accurately reflect the
-mathematical definition of the adaptive landscape \citep{Arnold2003}.
-All data and code to reproduce the reported results are publicly
-available on GitHub and have been archived on Zenodo (links are
-available from the journal office).
-
-\section{Results}\label{results}
-
-\subsection{Consumer extinctions increase selective
-constraints}\label{consumer-extinctions-increase-selective-constraints}
-
-\indent We found that the extinction of larval parasitoids increased the
-number of gall midge traits under directional selection (3 of 3)
-relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
-For example, we observed directional selection for smaller clutch sizes
-when we excluded larval parasitoids, but there was no evidence of
-selection acting on this trait in the original food web (table
-\ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This absence of
-selection appeared to be a result of conflicting selection pressures
-imposed by each guild of parasitoids. Specifically, when we subset our
-data to focus on differences between parasitoid guilds, we found that
-larval parasitoids actually impose directional selection for larger
-clutch sizes (\(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}). We also
-observed clear evidence of directional selection for midges to avoid
-ovipositing on plants with high densities of conspecifics when we
-excluded larval parasitoids (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, there was no clear relationship in
-the original food web (table \ref{Table:Gradients}). This was likely a
-result of larval parasitoids imposing greater mortality on egg
-parasitoids at high gall midge densities (see Selection on egg
-parasitoids section), and thus a less than additive effect on gall
-midges. Chamber diameter experienced positive directional selection in
-both food-web treatments (fig. \ref{fig:UV_Landscape}A). Although the
-magnitude of selection on chamber diameter was relatively higher in the
-original food web (table \ref{Table:Gradients}), this was not due to any
-difference in the relationship between chamber diameter and survival
-(selection surfaces: original \(\alpha_{\text{Diam}}\)= 1.15 {[}0.75,
-1.61{]}; extinction \(\alpha_{\text{Diam}}\)= 1.1 {[}0.64, 1.65{]}), but
-was simply a consequence of the (expected) lower survival in the
-original food web (original \(\bar W\)= 0.42 {[}0.28, 0.56{]};
-extinction \(\bar W\)= 0.68 {[}0.54, 0.81{]}).
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients acting on gall midges in the original food web and with the extinction of larval parasitoids.}
-\label{Table:Gradients}
-\centering
-\begin{tabular}{lcc} %c
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Extinction}   \\ %& \textbf{Contrast}
-\hline
-$\beta_{\text{Diam}}$ & 
-\textbf{
-0.34 [
-0.22,
-0.48] }& 
-\textbf{
-0.21 [
-0.12,
-0.31] }\\%& 
-%\textbf{
-%0.14 [
-%0.27,
-%0] }\\
-
-$\beta_{\text{Clutch}}$ & 
-0.06 [
--0.05,
-0.17] & 
-\textbf{
--0.09 [
--0.17,
--0.01] }\\%& 
-%\textbf{
-%0.15 [
-%0.29,
-%0.03] }\\
-
-$\beta_{\text{Pref}}$ &
--0.13 [
--0.29,
-0.05] & 
-\textbf{
--0.16 [
--0.26,
--0.06] }\\%&
-
-%0.03 [
-%0.21,
-%-0.15] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-0.13 [
--0.06,
-0.33] &
-
-0.1 [
--0.02,
-0.23] \\%&
-
-%0.03 [
-%0.27,
-%-0.2] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ & 
--0.05 [
--0.27,
-0.18] &
-
--0.11 [
--0.28,
-0.03] \\%&
-
-%0.06 [
-%0.32,
-%-0.2] \\
-
-$\gamma_{\text{Pref:Pref}}$ & 
-\textbf{
-0.34 [
-0.07,
-0.63] }&
-
-0.02 [
--0.14,
-0.18] \\%& 
-%\textbf{
-%0.32 [
-%0.64,
-%0.01] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ & 
--0.04 [
--0.16,
-0.08] &
-
--0.07 [
--0.15,
-0.02] \\%&
-
-%0.02 [
-%0.17,
-%-0.12] \\
-
-$\gamma_{\text{Diam:Pref}}$ & 
--0.13 [
--0.29,
-0.02] &
-
--0.02 [
--0.1,
-0.07] \\%&
-
-%-0.12 [
-%0.05,
-%-0.3] \\
-
-$\gamma_{\text{Clutch:Pref}}$ & 
-0.03 [
--0.1,
-0.18] &
-
-0 [
--0.07,
-0.07] \\%&
-
-%0.03 [
-%0.18,
-%-0.12] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-\subsection{Consumer extinctions increase genetic
-constraints}\label{consumer-extinctions-increase-genetic-constraints}
-
-\indent The curvature of the adaptive landscape indirectly affects
-genetic constraints and is influenced by directional, quadratic, and
-correlational selection gradients. There was no clear evidence of
-correlational selection for any combination of traits in either food-web
-treatment (table \ref{Table:Gradients}). Similarly, there was no clear
-evidence of quadratic selection on chamber diameter or clutch size in
-either food-web treatment (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}A,C). In contrast, our food-web treatment did
-alter quadratic selection acting on oviposition preference (table
-\ref{Table:Gradients}). The negative relationship between oviposition
-preference and larval survival dampened at high densities in the
-original food web, but not with the exclusion of larval parasitoids
-(fig. \ref{fig:UV_Landscape}B). This dampened relationship was partly
-due to a trend for nonlinear selection imposed by larval parasitoids
-(\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02, 0.42{]}), but was also
-magnified by the lower average survival in complex food webs.
-
-\begin{figure}
-\centering
-\includegraphics{analyses/UV_landscapes.pdf}
-\caption{\label{fig:UV_Landscape}Adaptive landscape of gall midge
-phenotypes in the original food web and with the extinction of larval
-parasitoids. Each panel corresponds to a different phenotypic trait:
-chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in the original food web
-(orange) and with consumer extinctions (blue). Thin lines represent
-bootstrapped replicates to show the uncertainty in selection. For
-clarity, we only display 100 bootstraps even though inferences are based
-on 1,000 replicates. Note that mean larval survival is plotted on a
-natural log scale to reflect the mathematical defintion of the adaptive
-landscape.}
-\end{figure}
-
-Using our estimates of directional (\(\beta_i\)), quadratic
-(\(\gamma_{ii}\)), and correlation selection (\(\gamma_{ij}\)), we
-calculated the curvature (\(\text{C}=\gamma - \beta \beta^\text{T}\)) of
-the adaptive landscape in each food-web treatment. In our study, this
-corresponds to:
-
-\[\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}\]
-
-\[\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}\]
-\bigskip
-
-where each \(\text{C}_{ii}\) (diagonal) represents the effect of
-selection on the additive genetic variance in a trait, and each
-\(\text{C}_{ij}\) (off-diagonal) represents the effect of selection on
-the additive genetic covariance between a particular trait combination.
-In order to obtain a conservative estimate of the factors contributing
-to the curvature, we only used estimates of selection that clearly
-differed from zero (bold values in table \ref{Table:Gradients}),
-otherwise we set estimates of selection to zero (non-bold values in
-table \ref{Table:Gradients}) prior to our calculation. We found that the
-curvatures of the adaptive landscape exhibited the following structures:
-
-\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
-0 &  &  \\  
-0 & 0 &  \\  
-0 & 0 & 0.34 \end{pmatrix} - \begin{pmatrix} 
-0.34\cdot0.34 &  &  \\  
-0\cdot0.34 & 0\cdot0 &  \\  
-0\cdot0.34 & 0\cdot0 & 0\cdot0 \end{pmatrix}\]
-
-\[\textbf{Curvature}_{\text{Original}} = \begin{pmatrix} 
--0.12 &  &  \\  
-0 & 0 &  \\  
-0 & 0 & 0.34 \end{pmatrix}\]
-
-\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
-0 &  &  \\  
-0 & 0 &  \\  
-0 & 0 & 0 \end{pmatrix} - \begin{pmatrix} 
-0.21\cdot0.21 &  &  \\  
--0.09\cdot0.21 & -0.09\cdot-0.09 &  \\  
--0.16\cdot0.21 & -0.16\cdot-0.09 & -0.16\cdot-0.16 \end{pmatrix}\]
-
-\[\textbf{Curvature}_{\text{Extinction}} = \begin{pmatrix} 
--0.04 &  &  \\  
-0.02 & -0.01 &  \\  
-0.03 & -0.01 & -0.03 \end{pmatrix}\]
-
-Remember that we can infer the indirect effects of selection on genetic
-constraints by summing the number of negative signs along the diagonal
-(decrease in additive genetic variance) and the number of nonzero terms
-along the off-diagonal (trait integration) of the curvature matrix. The
-structure of these matrices indicates that the extinction of larval
-parasitoids increased the number of genetic constraints on gall midges
-(6 of 6) relative to the original food web (1 of 6). For example,
-directional selection resulting from the exclusion of larval parasitoids
-acted to decrease genetic variance for all three phenotypic traits
-(negative diagonal terms), whereas only one trait (chamber diameter)
-experienced a decrease in additive genetic variance in the original food
-web. For genetic covariances, the combined effects of directional
-selection resulting from consumer extinctions favored integration among
-all three phenotypic traits (nonzero off-diagonal terms), and thus
-constraints along all three axes of covariance (fig.
-\ref{fig:MV_Landscape}). In contrast, the absence of directional
-selection in clutch size and oviposition preference did not promote
-trait integration along any axis in the original food web (fig.
-\ref{fig:MV_Landscape}).
-
-\begin{figure}
-\centering
-\includegraphics{analyses/MV_landscapes.pdf}
-\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
-landscapes of gall midge phenotypes in the original food web and with
-the extinction of larval parasitoids. Each panel corresponds to a
-different combination of phenotypic traits: clutch size and chamber
-diameter (A); clutch size and oviposition preference (B); oviposition
-preference and chamber diameter (C). Arrows represent mean estimates of
-directional selection gradients, while contours represent predicted
-larval survival of the mean phenotype in each food-web treatment. Notice
-that arrows point more toward a corner of the adaptive landscape for
-each combination of traits with the extinction of larval parasitoids
-compared to the original food web. This indicates that consumer
-extinctions more strongly favored trait integration (covariance). Note
-that mean larval survival is plotted on a natural log scale to reflect
-the mathematical definition of the adaptive landscape.}
-\end{figure}
-
-\subsection{Selection on egg
-parasitoids}\label{selection-on-egg-parasitoids}
-
-The exctinction of larval parasitoids only altered the relationship
-between gall midge preference and the probability of observing egg
-parasitoids (table \ref{Table:ExtendedGradients}). Specifically, the
-impact of larval parasitoids increased nonlinearly with higher gall
-midge densities (fig. \ref{fig:EggPtoid_Selection}).
-
-\bigskip
+\beginsupplement
 
@@
 
+\newpage
+
+\begin{table}[h]
+\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web.
+This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
+\label{Table:LarvalGradients}
+\centering
+\begin{tabular}{lc}
+\\ 
+\hline
+\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
+\hline
+$\beta_{\text{Diam}}$ & 
+%\textbf{
+%0.34 [
+%0.22,
+%0.48] } & 
+\textbf{
+0.23 [
+0.13,
+0.36] } \\
+
+$\beta_{\text{Clutch}}$ & 
+%0.06 [
+%-0.05,
+%0.17] & 
+\textbf{
+0.13 [
+0.04,
+0.24] }\\
+
+$\beta_{\text{Pref}}$ &
+%-0.13 [
+%-0.29,
+%0.05] & 
+\textbf{
+-0.17 [
+-0.34,
+-0.03] } \\
+
+$\gamma_{\text{Diam:Diam}}$ &
+%0.13 [
+%-0.06,
+%0.33] &
+
+0.06 [
+-0.07,
+0.2]  \\
+
+$\gamma_{\text{Clutch:Clutch}}$ & 
+%-0.05 [
+%-0.27,
+%0.18] &
+
+0.01 [
+-0.14,
+0.15] \\
+
+$\gamma_{\text{Pref:Pref}}$ & 
+%\textbf{
+%0.34 [
+%0.07,
+%0.63] }&
+
+0.18 [
+-0.02,
+0.42] \\
+
+$\gamma_{\text{Diam:Clutch}}$ & 
+%-0.04 [
+%-0.16,
+%0.08] &
+
+0.02 [
+-0.07,
+0.11]  \\
+
+$\gamma_{\text{Diam:Pref}}$ & 
+%-0.13 [
+%-0.29,
+%0.02] &
+
+-0.05 [
+-0.18,
+0.06]  \\
+
+$\gamma_{\text{Clutch:Pref}}$ & 
+%0.03 [
+%-0.1,
+%0.18] &
+
+-0.04 [
+-0.14,
+0.06]  \\ 
+\hline
+\end{tabular}
+\bigskip{}
+\\
+{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
+\end{table}
+
+\newpage
+
 \begin{figure}
 \centering
-\includegraphics{analyses/selection_on_Platygaster.pdf}
-\caption{\label{fig:EggPtoid_Selection}Selection imposed by larval
-parasitoids on egg parasitoids (\emph{Platygaster} sp.). The bold line
-represents the average difference in the probability of observing the
-egg parasitoid (original - extinction of larval parastioids) as a
-function of gall midge oviposition preference. Thin lines represent
-bootstrapped replicates to show the uncertainty in selection. For
-clarity, we only display 100 bootstraps even though inferences are based
-on 1,000 replicates. The decrease in the probability of observing egg
-parasitoids at high gall-midge densities indicate that larval
-parasitoids impose nonlinear selection on egg parasitoids.}
+\includegraphics{../analyses/larvalptoid_delta_evolvability.pdf}
+\caption{\label{fig:LarvalPtoidEvolvability}Change in average
+evolvability for 10,000 random G-matrices using our best (mean) estimate
+of the curvature matrix for selection in the absence of egg parasitoids
+vs.~the original food web. We found that the curvature imposed by the
+loss of egg parasitoids decreased evolvability in 57\% of the G-matrices
+(i.e.~the change in evolvability was negative for 57\% of the
+simulations), which is smaller in magnitude, but in the same direction,
+as the effects of losing larval parasitoids.}
 \end{figure}
-
-\section{Discussion}\label{discussion}
-
-We found that the extinction of larval parasitoids constrained
-phenotypic evolution in gall midges in two key ways. First, more traits
-contributed to the slope of the adaptive landscape in the absence of
-larval parasitoids, suggesting greater constraints on the trajectory of
-phenotypic evolution. Second, excluding larval parasitoids indirectly
-increased the number of genetic constraints, which could act to
-constrain the gall midge's adaptive potential in the face of novel
-selection pressures. Our experiment also revealed evidence of indirect
-selection pressures, suggesting that the loss of consumers may have
-complex effects on the trajectories of phenotypic evolution. Taken
-together, our study provides experimental evidence from the field that
-consumer extinctions may constrain the adaptive potential of remaining
-populations.
-
-All three phenotypic traits we examined experienced directional
-selection when we excluded larval parasitoids, indicating that there is
-an optimal phenotype that maximizes larval survival (i.e.~large chamber
-diameter, small clutch size, and avoidance of conspecifics). In
-contrast, we did not observe clear evidence of selective constraints on
-clutch size and oviposition preference in the original food web. This
-suggests that there are many optimal phenotypes (adaptive peaks), or in
-this case, a flat adaptive landscape where there are no fitness
-consequences for phenotypic change in these traits. This also implies
-that as selective constraints dampen in more complex food webs, then the
-trajectory of evolution becomes more determined by how genetic
-constraints interact with other evolutionary processes (e.g.~genetic
-drift, gene flow, and mutation). Interestingly, this aligns with
-\citet{Schluter1996}`s hypothesis that phenotypic evolution often
-follows 'genetic lines of least resistance'. \citet{Schluter1996} found
-support for this hypothesis from data on natural populations of several
-vertebrate species, including threespine sticklebacks, a few species of
-songbirds, and mice from the genus \emph{Peromyscus}. All of these
-species occupy intermediate trophic levels and are likely embedded in
-complex food webs, which is consistent with our suggestion that genetic
-constraints may have a stronger influence in more complex food webs.
-
-We also found evidence for more genetic constraints when we excluded
-larval parasitoids due to indirect effects of selection on the
-population's G-matrix. The ability of a population to adapt to novel
-selection pressures (evolvability) is largely governed by the structure
-of its G-matrix \citep{Hansen2008}. When selection favors genetic
-covariance between traits (positive or negative), this results in less
-autonomy of evolutionary responses to changing environments. Similarly,
-decreases in genetic variance constrain potential for the trait itself
-to evolve. Together, this suggests that consumer extinctions may
-decrease the evolutionary potential of populations by indirectly
-selecting for decreases in genetic variance in multiple traits and
-favoring trait integration. Current theory often assumes genetic
-variances and covariances remain constant over time rather than
-dynamically changing with the community context
-\citep{McPeek2017, Guimaraes2017}. Our empirical results highlight the
-need to explore the evolutionary consequences of not only direct effects
-of selection, but indirect effects on genetic constraints that are
-shaped by the community context.
-
-The generality of our results likely depends on the relative abundance
-and functional differences between consumers in a community. For
-example, if consumers do not differ from each other, then we do not
-expect changes in food-web structure to modify evolutionary constraints.
-Also, many consumers may be at too low of abundances to impose selection
-on their resources. Rank abundance curves \citep{Preston1948} and the
-disproportionate number of weak interactions in diverse communities
-\citep{Paine1992} support this notion. When consumers are abundant
-though, the effect of food-web structure will depend on whether
-different species impose conflicting selection pressures or select for
-distinct traits. For example, parisitoids and birds impose conflicting
-selection pressures on the size of galls induced by the fly
-\emph{Eurosta solidaginis} \citep{Weis1985, Abrahamson1997}. Recent
-studies in this system have shown that decreases in the relative
-abundance of birds, due to either small patch sizes \citep{Start2016} or
-proximity to urban areas \citep{Start2018} causes a shift from neutral
-to directional selection on gall size. On the other hand, different
-consumers may impose selection on different traits, favoring trait
-integration and increasing genetic constraints. Examples of this include
-strong genetic covariances in plant resistance to different insect
-herbivores \citep{Maddox1990, Wise2007, Wise2013}, although there are
-also examples where these covariances are weak
-\citep{Roche1997, Barbour2015}, or vary from year-to-year
-\citep{Johnson2007}. We suggest that gaining predictive insight to the
-evolutionary consequences of food-web disassembly requires an
-understanding of the mechanisms governing the assembly of trophic
-interactions.
-
-Our results suggest that the loss of consumers may not only directly
-affect connected species, but also result in indirect evolutionary
-effects. In our study, this indirect effect arises from egg parasitoids
-being released from intraguild predation when we excluded larval
-parasitoids. This release occurs more on trees with high larval
-densities, which could intensify selection on gall midge oviposition
-preference. A growing number of experiments over the past two decades
-have demonstrated the presence and potential importance of indirect
-evolutionary effects that emerge in a community context
-\citep{Pilson1996, Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, Start2019}.
-If indirect evolutionary effects are common \citep{Walsh2013}, then
-predicting evolutionary trajectories resulting from consumer extinctions
-will require evolutionary studies to explicitly account for the
-ecological networks that species are embedded in.
-
-There is a growing number of theoretical studies on adaptation to
-directional environmental change that incorporate species interactions
-\citep[e.g.][]{deMazancourt2008, Johansson2008, Norberg2012, Osmond2017PredatorsHelpPrey}.
-This work has given insight to the mechanisms by which pairwise
-interactions modify the adaptive potential of species. Our study hints
-at a novel mechanism, whereby more complex food webs flatten the
-adaptive landscape, thus facilitating future adaptation by allowing
-genetic and phenotypic variation to persist. This mechanism only emerges
-once we move beyond pairwise interactions to consider selection on
-multiple traits in a community context. However, a study on competition
-has highlighted that we may expect the opposite effect of species
-diversity in competitive communities \citep{deMazancourt2008}. This
-negative effect of species diversity on adaptation occurs because there
-is a greater chance that the optimal phenotype is already occupied by a
-competitor in a more diverse community. More work is needed to examine
-how the distribution of different interaction types affects adaptation
-to environmental change in species-rich communities.
-
-Our study has some limitations to consider when relating our findings to
-the effects of consumer extinctions on evolutionary constraints more
-generally. First, we removed other sources of mortality prior to our
-analyses. While this was necessary to avoid confounding estimates of
-selection with effects on phenotypic expression, we may be
-overestimating the effects of selection due to parasitoids. Second, our
-metrics of evolutionary constraints do not account for variation in the
-magnitude of selection pressures. While quantitative metrics are
-possible \citep{Hansen2008}, we felt they were not appropriate to apply
-here as our experimental removal of larval parasitoids results in a
-transient dynamic in the strength (but not direction) of selection. Such
-transient dynamics may be common in short-term experimental studies of
-natural selection, but they can be detected by using natural history
-information and dissecting the sources of selection (e.g.~quantifying
-selection surfaces and treatment effects on mean fitness) as we did
-here.
-
-Our study gives insight to how consumer extinctions alter evolutionary
-constraints on remaining populations. In particular, it hints at a
-potential insidious effect of local extinctions that compromises the
-robustness of remaining populations to future environmental change. Our
-work also highlights some key challenges for predicting phenotypic
-evolution in the face of global change. First, the simplification of
-ecological communities may actually reduce the predictability of
-phenotypic evolution, because knowledge is required of both selective
-and genetic constraints, rather than potentially just genetic
-constraints in more complex systems. Second, many theoretical models of
-eco-evolutionary dynamics focus on phenotypic change in a single trait,
-yet our results highlight that the number of traits under selection may
-change with the community context. Importantly, we found that different
-species/guilds imposed different selection pressures. Knowing these
-hidden selection pressures is critical for prediction, because the
-trajectory of evolution will depend on the nature of change in the
-community context. We expect that a continued integration of adaptive
-landscapes and ecological networks will enhance our ability to predict
-the evolutionary consequences of changes in ecological communities.
 

### 2019-09-18 manuscript/manuscript.Rmd
update repo for Evolutionary Letters submission

@@
 
-*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, complexity, biodiversity, community context.
+*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, <!--complexity, biodiversity,-->community context, extinction.
 
@@
 
-*Total Word Count*: `r wordcountaddin::word_count("manuscript.Rmd") - 587` <!-- subtract estimate of Abstract, Impact, Acknowledgements, Author Contributions, and Data Accessibility -->
+*Total Word Count*: `r wordcountaddin::word_count("manuscript.Rmd") - 527` <!-- subtract estimate of Abstract, Impact, Acknowledgements, Author Contributions, Data Accessibility, and their associated headers -->
 
@@
 The curvature of the adaptive landscape is governed by nonlinear selection gradients and acts to indirectly constrain evolution through its effect on genetic constraints [@Arnold1992; @Hansen2008].
-Genetic constraints are largely governed by a population's **G**-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
-Stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection may alter the genetic covariance between traits, which may facilitate or hinder future adaptation depending on pattern of selection on those traits [@Hansen2008].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
+Genetic constraints are largely governed by a population's G-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
+Stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection may alter the genetic covariance between traits, which may facilitate or hinder future adaptation depending on the pattern of selection on those traits [@Hansen2008].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
 
@@
 \ref{fig:Conceptual}).
-<!--The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
+The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
 <!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
@@
 (Family: Torymidae)."}
-knitr::include_graphics("../analyses/complex_simple_foodwebs_v3.jpeg")
+knitr::include_graphics("../analyses/complex_simple_foodwebs_v4.jpeg")
 ```
@@
 
-## Consumer loss increases selective constraints
+## Consumer removal increases selective constraints
 
 \indent We found that the removal of larval parasitoids increased the number of gall midge traits under directional selection (3 of 3) relative to the original food web (1 of 3)(table \ref{Table:Gradients}).
-For example, we observed directional selection for smaller clutch sizes when we excluded larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}C).
+For example, we observed directional selection for smaller clutch sizes when we removed larval parasitoids, but there was no evidence of selection acting on this trait in the original food web (fig.
+\ref{fig:UV_Landscape}A).
 This absence of selection appeared to be a result of conflicting selection pressures imposed by each guild of parasitoids.
@@
 
-We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we excluded larval parasitoids (table \ref{Table:Gradients}; fig.
+We also observed clear evidence of directional selection for midges to avoid ovipositing on plants with high densities of conspecifics when we removed larval parasitoids (fig.
 \ref{fig:UV_Landscape}B); however, the overall magnitude of selection did not differ between treatments (table \ref{Table:Gradients}).
@@
 <!--This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.-->Chamber diameter experienced positive directional selection in both food-web treatments (fig.
-\ref{fig:UV_Landscape}A).
+\ref{fig:UV_Landscape}C).
 Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival <!--(selection surfaces: original $\alpha_{\text{Diam}}$=
@@
 ```{r UV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:UV_Landscape}Adaptive landscape of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
-Each panel corresponds to a different phenotypic trait: chamber diameter (A); oviposition preference (B); and clutch size (C).
-Bold lines represent selection experienced in the original (orange) and removal (blue) food webs (orange).
+Each panel corresponds to a different phenotypic trait: clutch size (A); oviposition preference (B); and chamber diameter (C).
+Bold lines represent selection experienced in the original (orange) and removal (blue) food webs.
 Thin lines represent bootstrapped replicates to show the uncertainty in selection.
@@
 
+\bigskip
+
 To visualize the multivariate effects of these selective constraints, we plotted the adaptive landscape for each trait combination in each treatment (fig.
@@
 Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
-This indicates that the loss of consumers more strongly favored a specific combination of traits, rather than allowing for multiple trait combinations to have comparable fitness.
+This indicates that the removal of consumers more strongly favored a specific combination of traits, rather than allowing for multiple trait combinations to have comparable fitness.
 
@@
 Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
-This indicates that the loss of consumers more strongly favored a specific combination of traits.
+This indicates that the removal of consumers more strongly favored a specific combination of traits.
 Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
@@
 
-## Consumer loss indirectly increases genetic constraints
+\bigskip
+
+## Consumer removal indirectly increases genetic constraints
 
@@
 There was no clear evidence of correlational selection for any combination of traits in either food-web treatment (table \ref{Table:Gradients}).
-Similarly, there was no clear evidence of quadratic selection on chamber diameter or clutch size in either food-web treatment (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}A,C).
+Similarly, there was no clear evidence of quadratic selection on chamber diameter or clutch size in either food-web treatment (table \ref{Table:Gradients}).
 In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
-The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the exclusion of larval parasitoids (fig.
+The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the removal of larval parasitoids (fig.
 \ref{fig:UV_Landscape}B).
@@
 [`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in complex food webs.
+`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in the original food web.
 This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.
@@
 
-Interestingly, when we translate the effect of the curvature matrix onto genetic constraints in the next generation, we see that the loss of consumers had a general tendency to decrease evolvability (fig.
+Interestingly, when we translate the effect of the curvature matrix onto genetic constraints in the next generation, we see that the removal of consumers had a general tendency to decrease evolvability (fig.
 \ref{fig:Evolvability}).
@@
 -->
+\bigskip
 
@@
 We found that the curvature of the removal food web decreased evolvability in 71% of the G-matrices (i.e.
-the change in evolvability was negative for 71% of the simulations), suggesting that the loss of consumers tended to decrease evolutionary potential of traits in our study."}
+the change in evolvability was negative for 71% of the simulations), suggesting that the removal of consumers tended to decrease evolutionary potential of traits in our study."}
 knitr::include_graphics("../analyses/delta_evolvability.pdf")
@@
 
+\bigskip
+
 ## Selection on egg parasitoids
@@
 The removal of larval parasitoids not only had direct effects on gall midge fitness, but also imposed indirect effects that would be felt in the next generation.
-For example, the removal of larval parasitoids altered the relationship between gall midge preference and the probability of observing egg parasitoids (`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
+For example, the removal of larval parasitoids altered the relationship between gall midge preference and the probability of observing egg parasitoids ($\gamma_{\text{Pref:Pref}}$=`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
 `r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }, Appendix A), such that the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
+`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`], table S1), such that the impact of larval parasitoids increased nonlinearly with higher gall midge densities (fig.
 \ref{fig:EggPtoid_Selection}).
+
+\bigskip
 
@@
 
+\bigskip
+
 # Discussion
@@
 First, more traits contributed to the slope of the adaptive landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
-Second, excluding larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of associated traits.
+Second, removing larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of associated traits.
 Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's adaptive potential in the face of novel selection pressures.
@@
 This logic suggests that we may not have observed the effects we did if we had only removed one larval parasitoid, because each species had relatively low abundance [@Barbour2016] and they likely share similar ecological roles.
-When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different species impose conflicting selection pressures or select for distinct traits.
+When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different consumers impose conflicting selection pressures or select for distinct traits.
 When consumers impose conflicting selection on traits, as in our study and others [@Weis1985; @Abrahamson1997; @Start2016; @Start2018], then consumer diversity acts to neutralize selection and relax selective constraints.<!-- For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
@@
 For example, we see clear evidence of all three traits being under directional selection (i.e.
-greater selective constraints, Appendix A) as well as a decrease, albeit smaller, in trait evolvability under different G-matrix scenarios (`r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`%, Appendix A).
-This suggests that our results could be robust to this caveat, which was simply not possible to manipulate given the biology of our system (see *Manipulating Food-web Structure* section for explanation).
+greater selective constraints, table S2) as well as a decrease, albeit smaller, in trait evolvability under different G-matrix scenarios (`r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`%, fig.
+S1).
+This suggests that our results could be robust to this caveat, which was simply not possible to manipulate given the biology of our system (see **Manipulating Food-web Structure** section for explanation).
 
@@
 Bascompte).
+The authors declare no conflict of interest.
 
@@
 \end{table}
--->
 
@@
 
-<!-- Add the XX% change in evolvability -->
-
 ```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs.

### 2019-09-18 manuscript/manuscript.tex
update repo for Evolutionary Letters submission

@@
 \emph{Keywords}: adaptive landscape, ecological networks,
-eco-evolutionary dynamics, natural selection, host-parasitoid,
-complexity, biodiversity, community context.
+eco-evolutionary dynamics, natural selection, host-parasitoid, community
+context, extinction.
 
@@
 
-\emph{Total Word Count}: 5769
+\emph{Total Word Count}: 5833
 
@@
 on genetic constraints \citep{Arnold1992, Hansen2008}. Genetic
-constraints are largely governed by a population's \textbf{G}-matrix
----the additive genetic variances and covariances between traits
+constraints are largely governed by a population's G-matrix ---the
+additive genetic variances and covariances between traits
 \citep{Hansen2008}. Stabilizing selection acts to erode genetic variance
@@
 selection may alter the genetic covariance between traits, which may
-facilitate or hinder future adaptation depending on pattern of selection
-on those traits \citep{Hansen2008}. If we want to predict how ecological
-communities shape phenotypic evolution, we must understand how
-ecological networks shape the adaptive landscape.
+facilitate or hinder future adaptation depending on the pattern of
+selection on those traits \citep{Hansen2008}. If we want to predict how
+ecological communities shape phenotypic evolution, we must understand
+how ecological networks shape the adaptive landscape.
 
@@
 \centering
-\includegraphics{../analyses/complex_simple_foodwebs_v3.jpeg}
+\includegraphics{../analyses/complex_simple_foodwebs_v4.jpeg}
 \caption{\label{fig:Conceptual}Experimental manipulation of food-web
@@
 (our measure of fitness) or were parasitized. We did not include other
-sources of mortality, such as early larval death, as they could
-influence the expression of the gall phenotype and confound estimates of
-selection. For the food-web treatment that excluded larval parasitoids,
-we further restricted our data by removing any incidental instances of
-parasitism by a larval parasitoid. This represented less than 3\% of the
-observations in this food-web treatment and allowed us to focus our
-inferences of selection on those imposed by the egg parasitoid. Our
-final dataset contains survival estimates for 1285 larvae from 613 galls
-and 111 plants.
+sources of mortality in our analyses, such as early larval death, as
+they could influence the expression of the gall phenotype and confound
+estimates of selection. For the food-web treatment that excluded larval
+parasitoids, we further restricted our data by removing any incidental
+instances of parasitism by a larval parasitoid. This represented less
+than 3\% of the observations in this food-web treatment and allowed us
+to focus our inferences of selection on those imposed by the egg
+parasitoid. Our final dataset contains survival estimates for 1285
+larvae from 613 galls and 111 plants.
 
@@
 unadjusted relationships would overestimate the strength of selection on
-chamber diameter. To account for this bias, we substracted our mean
+chamber diameter. To account for this bias, we subtracted our mean
 estimates of bias from our estimates with the full dataset prior to
@@
 
-\subsection{Consumer loss increases selective
-constraints}\label{consumer-loss-increases-selective-constraints}
+\subsection{Consumer removal increases selective
+constraints}\label{consumer-removal-increases-selective-constraints}
 
@@
 For example, we observed directional selection for smaller clutch sizes
-when we excluded larval parasitoids, but there was no evidence of
-selection acting on this trait in the original food web (table
-\ref{Table:Gradients}; fig. \ref{fig:UV_Landscape}C). This absence of
-selection appeared to be a result of conflicting selection pressures
-imposed by each guild of parasitoids. Specifically, when we subset our
-data to focus on differences between parasitoid guilds, we found that
-larval parasitoids actually impose directional selection for larger
-clutch sizes (larval parasitoids \(\beta_{\text{Clutch}}\)= 0.13
-{[}0.04, 0.24{]}). This conflicting selection is likely due to trait
-differences between guilds, as larger clutches may be easier targets for
-egg parasitoids to find, but the more complex gall structure may be more
-difficult for larval parasitoids to oviposit through.
+when we removed larval parasitoids, but there was no evidence of
+selection acting on this trait in the original food web (fig.
+\ref{fig:UV_Landscape}A). This absence of selection appeared to be a
+result of conflicting selection pressures imposed by each guild of
+parasitoids. Specifically, when we subset our data to focus on
+differences between parasitoid guilds, we found that larval parasitoids
+actually impose directional selection for larger clutch sizes (larval
+parasitoids \(\beta_{\text{Clutch}}\)= 0.13 {[}0.04, 0.24{]}). This
+conflicting selection is likely due to trait differences between guilds,
+as larger clutches may be easier targets for egg parasitoids to find,
+but the more complex gall structure may be more difficult for larval
+parasitoids to oviposit through.
 
@@
 avoid ovipositing on plants with high densities of conspecifics when we
-excluded larval parasitoids (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}B); however, the overall magnitude of selection
-did not differ between treatments (table \ref{Table:Gradients}). Still,
-there was no clear evidence of directional selection on oviposition in
-the original food web (table \ref{Table:Gradients}). Chamber diameter
-experienced positive directional selection in both food-web treatments
-(fig. \ref{fig:UV_Landscape}A). Although the magnitude of selection on
-chamber diameter was relatively higher in the original food web (table
+removed larval parasitoids (fig. \ref{fig:UV_Landscape}B); however, the
+overall magnitude of selection did not differ between treatments (table
+\ref{Table:Gradients}). Still, there was no clear evidence of
+directional selection on oviposition in the original food web (table
+\ref{Table:Gradients}). Chamber diameter experienced positive
+directional selection in both food-web treatments (fig.
+\ref{fig:UV_Landscape}C). Although the magnitude of selection on chamber
+diameter was relatively higher in the original food web (table
 \ref{Table:Gradients}), this was not due to any difference in the
@@
 parasitoids. Each panel corresponds to a different phenotypic trait:
-chamber diameter (A); oviposition preference (B); and clutch size (C).
+clutch size (A); oviposition preference (B); and chamber diameter (C).
 Bold lines represent selection experienced in the original (orange) and
-removal (blue) food webs (orange). Thin lines represent bootstrapped
-replicates to show the uncertainty in selection. For clarity, we only
-display 100 bootstraps even though inferences are based on 1,000
-replicates. Note that mean larval survival is plotted on a natural log
-scale to reflect the mathematical definition of the adaptive landscape.}
+removal (blue) food webs. Thin lines represent bootstrapped replicates
+to show the uncertainty in selection. For clarity, we only display 100
+bootstraps even though inferences are based on 1,000 replicates. Note
+that mean larval survival is plotted on a natural log scale to reflect
+the mathematical definition of the adaptive landscape.}
 \end{figure}
+
+\bigskip
 
@@
 with the removal of larval parasitoids compared to the original food
-web. This indicates that the loss of consumers more strongly favored a
-specific combination of traits, rather than allowing for multiple trait
-combinations to have comparable fitness.
+web. This indicates that the removal of consumers more strongly favored
+a specific combination of traits, rather than allowing for multiple
+trait combinations to have comparable fitness.
 
@@
 combination of traits with the removal of larval parasitoids compared to
-the original food web. This indicates that the loss of consumers more
+the original food web. This indicates that the removal of consumers more
 strongly favored a specific combination of traits. Note that mean larval
@@
 
-\subsection{Consumer loss indirectly increases genetic
-constraints}\label{consumer-loss-indirectly-increases-genetic-constraints}
+\bigskip
+
+\subsection{Consumer removal indirectly increases genetic
+constraints}\label{consumer-removal-indirectly-increases-genetic-constraints}
 
@@
 evidence of quadratic selection on chamber diameter or clutch size in
-either food-web treatment (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}A,C). In contrast, our food-web treatment did
-alter quadratic selection acting on oviposition preference (table
-\ref{Table:Gradients}). The negative relationship between oviposition
-preference and larval survival dampened at high densities in the
-original food web, but not with the exclusion of larval parasitoids
-(fig. \ref{fig:UV_Landscape}B). This dampened relationship was partly
-due to a trend for nonlinear selection imposed by larval parasitoids
-(\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02, 0.42{]}), but was also
-magnified by the lower average survival in complex food webs. This was
-likely a result of larval parasitoids imposing greater mortality on egg
-parasitoids at high gall midge densities (see \textbf{Selection on egg
-parasitoids} section), and thus a less than additive effect on gall
-midges.
+either food-web treatment (table \ref{Table:Gradients}). In contrast,
+our food-web treatment did alter quadratic selection acting on
+oviposition preference (table \ref{Table:Gradients}). The negative
+relationship between oviposition preference and larval survival dampened
+at high densities in the original food web, but not with the removal of
+larval parasitoids (fig. \ref{fig:UV_Landscape}B). This dampened
+relationship was partly due to a trend for nonlinear selection imposed
+by larval parasitoids (\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02,
+0.42{]}), but was also magnified by the lower average survival in the
+original food web. This was likely a result of larval parasitoids
+imposing greater mortality on egg parasitoids at high gall midge
+densities (see \textbf{Selection on egg parasitoids} section), and thus
+a less than additive effect on gall midges.
 
@@
 Interestingly, when we translate the effect of the curvature matrix onto
-genetic constraints in the next generation, we see that the loss of
+genetic constraints in the next generation, we see that the removal of
 consumers had a general tendency to decrease evolvability (fig.
@@
 
+\bigskip
+
 \begin{figure}
@@
 (i.e.~the change in evolvability was negative for 71\% of the
-simulations), suggesting that the loss of consumers tended to decrease
-evolutionary potential of traits in our study.}
+simulations), suggesting that the removal of consumers tended to
+decrease evolutionary potential of traits in our study.}
 \end{figure}
+
+\bigskip
 
@@
 altered the relationship between gall midge preference and the
-probability of observing egg parasitoids (-0.46 {[} -1.07, -0.02{]} \},
-Appendix A), such that the impact of larval parasitoids increased
-nonlinearly with higher gall midge densities (fig.
-\ref{fig:EggPtoid_Selection}).
+probability of observing egg parasitoids
+(\(\gamma_{\text{Pref:Pref}}\)=-0.46 {[} -1.07, -0.02{]}, table S1),
+such that the impact of larval parasitoids increased nonlinearly with
+higher gall midge densities (fig. \ref{fig:EggPtoid_Selection}).
+
+\bigskip
 
@@
 
+\bigskip
+
 \section{Discussion}\label{discussion}
@@
 parasitoids, suggesting greater constraints on the trajectory of
-phenotypic evolution. Second, excluding larval parasitoids altered the
+phenotypic evolution. Second, removing larval parasitoids altered the
 curvature of the adaptive landscape in such a way that tended to
@@
 consumers are functionally different and abundant though, the effect of
-consumer loss will depend on whether different species impose
+consumer loss will depend on whether different consumers impose
 conflicting selection pressures or select for distinct traits. When
@@
 
-An important caveat of our study is that we did not due a factorial
+An important caveat of our study is that we did not do a factorial
 manipulation of both parasitoid guilds, making it difficult to conclude
@@
 being under directional selection (i.e.~greater selective constraints,
-Appendix A) as well as a decrease, albeit smaller, in trait evolvability
-under different G-matrix scenarios (57\%, Appendix A). This suggests
-that our results could be robust to this caveat, which was simply not
+table S2) as well as a decrease, albeit smaller, in trait evolvability
+under different G-matrix scenarios (57\%, fig. S1). This suggests that
+our results could be robust to this caveat, which was simply not
 possible to manipulate given the biology of our system (see
-\emph{Manipulating Food-web Structure} section for explanation).
+\textbf{Manipulating Food-web Structure} section for explanation).
 
@@
 NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
-Science Foundation (grant 31003A\_160671 to J. Bascompte).
+Science Foundation (grant 31003A\_160671 to J. Bascompte). The authors
+declare no conflict of interest.
 
@@
 
-\section{Appendix A}\label{appendix-a}
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
-\label{Table:ExtendedGradients}
-\centering
-\begin{tabular}{lc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Contrast = Original - Removal}  \\ 
-\hline
-$\beta_{\text{Diam}}$ &
-
--0.03 [
--0.3,
-0.25] \\
-
-$\beta_{\text{Clutch}}$ &
-
-0.07 [
--0.26,
-0.39] \\
-
-$\beta_{\text{Pref}}$ &
-
--0.25 [
--0.64,
-0.09] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-
--0.05 [
--0.43,
-0.33] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ &
-
--0.21 [
--0.68,
-0.26] \\
-
-$\gamma_{\text{Pref:Pref}}$ &
-
-\textbf{
--0.46 [
--1.07,
--0.02] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ &
-
-0 [
--0.29,
-0.27] \\
-
-$\gamma_{\text{Diam:Pref}}$ &
-
-0.25 [
--0.04,
-0.6] \\
-
-$\gamma_{\text{Clutch:Pref}}$ &
-
--0.18 [
--0.52,
-0.12] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web.
-This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
-\label{Table:LarvalGradients}
-\centering
-\begin{tabular}{lc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
-\hline
-$\beta_{\text{Diam}}$ & 
-%\textbf{
-%0.34 [
-%0.22,
-%0.48] } & 
-\textbf{
-0.23 [
-0.13,
-0.36] } \\
-
-$\beta_{\text{Clutch}}$ & 
-%0.06 [
-%-0.05,
-%0.17] & 
-\textbf{
-0.13 [
-0.04,
-0.24] }\\
-
-$\beta_{\text{Pref}}$ &
-%-0.13 [
-%-0.29,
-%0.05] & 
-\textbf{
--0.17 [
--0.34,
--0.03] } \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-%0.13 [
-%-0.06,
-%0.33] &
-
-0.06 [
--0.07,
-0.2]  \\
-
-$\gamma_{\text{Clutch:Clutch}}$ & 
-%-0.05 [
-%-0.27,
-%0.18] &
-
-0.01 [
--0.14,
-0.15] \\
-
-$\gamma_{\text{Pref:Pref}}$ & 
-%\textbf{
-%0.34 [
-%0.07,
-%0.63] }&
-
-0.18 [
--0.02,
-0.42] \\
-
-$\gamma_{\text{Diam:Clutch}}$ & 
-%-0.04 [
-%-0.16,
-%0.08] &
-
-0.02 [
--0.07,
-0.11]  \\
-
-$\gamma_{\text{Diam:Pref}}$ & 
-%-0.13 [
-%-0.29,
-%0.02] &
-
--0.05 [
--0.18,
-0.06]  \\
-
-$\gamma_{\text{Clutch:Pref}}$ & 
-%0.03 [
-%-0.1,
-%0.18] &
-
--0.04 [
--0.14,
-0.06]  \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-\begin{figure}
-\centering
-\includegraphics{../analyses/larvalptoid_delta_evolvability.pdf}
-\caption{\label{fig:LarvalPtoidEvolvability}Change in average
-evolvability for 10,000 random G-matrices using our best (mean) estimate
-of the curvature matrix for selection in the absence of egg parasitoids
-vs.~the original food web. We found that the curvature imposed by the
-loss of egg parasitoids decreased evolvability in 57\% of the G-matrices
-(i.e.~the change in evolvability was negative for 57\% of the
-simulations), which is smaller in magnitude, but in the same direction,
-as the effects of losing larval parasitoids.}
-\end{figure}
-
 \bibliography{references}

### 2019-09-18 manuscript/supplementary_material.Rmd
update repo for Evolutionary Letters submission

@@
 
-\beginsupplement <!-- start numbering for supplementary material -->
+<!-- start numbering for supplementary material -->
+\beginsupplement
 
@@
 the original food web.
-We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e.
-the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
+We found that the curvature imposed by the simulated removal of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e.
+the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of removing larval parasitoids."}
 knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")

### 2019-09-18 manuscript/supplementary_material.tex
update repo for Evolutionary Letters submission

@@
 vs.~the original food web. We found that the curvature imposed by the
-loss of egg parasitoids decreased evolvability in 57\% of the G-matrices
-(i.e.~the change in evolvability was negative for 57\% of the
-simulations), which is smaller in magnitude, but in the same direction,
-as the effects of losing larval parasitoids.}
+simulated removal of egg parasitoids decreased evolvability in 57\% of
+the G-matrices (i.e.~the change in evolvability was negative for 57\% of
+the simulations), which is smaller in magnitude, but in the same
+direction, as the effects of removing larval parasitoids.}
 \end{figure}

### 2020-01-13 manuscript/manuscript.Rmd
first draft of incorporating reviewer comments

@@
 
-*Keywords*: adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, <!--complexity, biodiversity,-->community context, extinction.
+*Keywords*: **fitness landscape**, adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, <!--complexity, biodiversity,-->community context, extinction.
 
@@
 The loss of biodiversity<!--Global change--> is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
-Theory on adaptive landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the network context of evolving populations as a ``black box''.
-Here, we integrate ecological networks and adaptive landscapes to examine how changes in food-web structure shape evolutionary constraints.
+Theory on **fitness** landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the network context of evolving populations as a ``black box''.
+Here, we integrate ecological networks and **fitness** landscapes to examine how changes in food-web structure shape evolutionary constraints.
 We conducted a field experiment that removed<!--simulated the extinction of--> a guild of larval parasitoids that imposed direct and indirect selection pressures on an insect herbivore.
 We then measured herbivore survival as a function of three key phenotypic traits to estimate directional, quadratic, and correlational selection gradients in each treatment.
-We used these selection gradients to characterize the slope and curvature of the adaptive landscape to understand the direct and indirect effects of consumer loss on evolutionary constraints.
+We used these selection gradients to characterize the slope and curvature of the **fitness** landscape to understand the direct and indirect effects of consumer loss on evolutionary constraints.
 We found that the number of traits under directional selection increased with the removal of larval parasitoids, indicating greater selective constraints on the trajectory of evolutionary change.
-Similarly, we found that the removal of larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of the traits we measured in the next generation.<!--In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.--> Our results suggest that the loss of trophic interactions <!--due to consumer extinctions -->can impose greater constraints on phenotypic evolution.
+Similarly, we found that the removal of larval parasitoids altered the curvature of the **fitness** landscape in such a way that tended to decrease the evolvability of the traits we measured in the next generation.<!--In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.--> Our results suggest that the loss of trophic interactions <!--due to consumer extinctions -->can impose greater constraints on phenotypic evolution.
 This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
@@
 
-The adaptive landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
-More than a metaphor, the adaptive landscape links quantitative genetic and phenotypic variation to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory], giving insight to the direct and indirect effects of selective constraints [@Arnold1992].
-Ecological interactions often play a key role in shaping selective constraints, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006].
-Although there is clear evidence that species interactions can shape the adaptive landscape, we still have a poor understanding of how the adaptive landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018].
+The **fitness** landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
+More than a metaphor, the **fitness** landscape links quantitative genetic and phenotypic variation **in multiple traits** to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory]<!--, giving insight to the direct and indirect effects of selective constraints [@Arnold1992]-->.
+Ecological interactions often play a key role in shaping natural selection<!--selective constraints-->, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006].
+Although there is clear evidence that species interactions can shape the **fitness** landscape, we still have a poor understanding of how the **fitness** landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018; **@Hui2018**].
 Resolution on how change in ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].
@@
 Ecological networks, such as food webs describing who-eats-whom, provide an explicit representation of the direct and indirect effects that emerge in a community of interacting species [@Bascompte2014; @McCann2012].
-Here, we integrate ecological networks and adaptive landscapes to understand how ecological communities constrain evolutionary change.
-The direct and indirect effects of natural selection can be inferred by quantifying the slope and curvature of the adaptive landscape [@Arnold1992].
-For example, the slope is determined by directional selection gradients acting on each phenotypic trait and influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
-Selective constraints on evolution increase with the number of traits under directional selection, as this diminishes the number of optimal solutions [@Arnold2003].
-The curvature of the adaptive landscape is governed by nonlinear selection gradients and acts to indirectly constrain evolution through its effect on genetic constraints [@Arnold1992; @Hansen2008].
-Genetic constraints are largely governed by a population's G-matrix ---the additive genetic variances and covariances between traits [@Hansen2008].
-Stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection may alter the genetic covariance between traits, which may facilitate or hinder future adaptation depending on the pattern of selection on those traits [@Hansen2008].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the adaptive landscape.
-
-The loss of biodiversity is altering the structure of ecological networks<!--communities-->, which may influence evolutionary constraints in a number of ways.
-For example, in a <!--multitrophic community or -->food web, if different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community may constrain evolution by increasing the number of traits under selection.
-Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities.
-To examine these different possibilities, we conducted a field experiment that removed a consumer guild that directly and indirectly impacts fitness of an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
+Here, we integrate ecological networks and **fitness** landscapes to understand how ecological communities constrain evolutionary change **[@Hui2018]**.
+The <!--direct and indirect -->effects of natural selection can be inferred by quantifying the slope and curvature of the **fitness** landscape **for multiple phenotypic traits** [@Arnold1992].
+<!--For example, t-->The slope is determined by the **strength of** directional selection <!--gradients -->acting on each trait**,which** influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
+**This fact is made clear by the 'Lande equation', $\Delta \bar z = \beta\text{G}$, where $\Delta \bar z$ is a column vector of the average change in each trait between generations, $\beta$ is a column vector of directional selection gradients acting on each trait (i.e.
+slope), and $\text{G}$ is the additive genetic (co)variance matrix for these traits (i.e.
+G-matrix).
+@Grant1995 used their knowledge of the slope of the fitness landscape for multiple traits related to body and beak size in Darwin's finches <!--, in addition to the G-matrix of those traits, -->to accurately predict the trajectory of evolution in these traits in response to different episodes of selection imposed by drought.**
+<!--For example, a drought in 1976-1977 on Daphne Major in the Gal\'apagos imposed directional selection for large weight, wing length, and bill depth in medium ground finches, and this equation predicted well the evolutionary response in all three of these traits in the next generation (Grant and Grant 1995).
+This equation has been used to predict short-term evolutionary change in Darwin's finches (Grant and Grant 1995).-->
+<!--Selective constraints on evolution increase with the number of traits under directional selection, as this diminishes the number of optimal solutions [@Arnold2003].-->
+The curvature of the **fitness** landscape is governed by the **strength of stabilizing, disruptive, and correlational selection acting on each trait<!--directional, quadratic, and correlational <!--nonlinear selection gradients-->, which <!--and acts to to indirectly constrain evolution -->can alter the potential for evolutionary change through its effect on <!--genetic constraints [@Arnold1992; @Hansen2008].
+Genetic constraints are largely governed by--><!-- a population's -->the G-matrix** <!-----the additive genetic variances and covariances between traits -->[@Hansen2008].
+For example, stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].
+**In contrast, disruptive selection for different trait values acts to increase genetic variance in traits, thus increasing the capacity for future adaptation [@Bolnick2008]**.<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection alters the genetic covariance between traits, which may facilitate or hinder future adaptation depending on the pattern of selection on those traits **and the structure of the G-matrix** [@Brodie1992].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the **fitness** landscape **of interacting populations**.
+
+The loss of biodiversity is altering the structure of ecological networks<!--communities-->**[@Landi2018ComplexityStability]**, which may influence **the slope and curvature of the fitness landscape**<!-- evolutionary constraints -->in a number of ways.
+**Consider first the slope of the fitness landscape <!--For example, -->in a <!--multitrophic community or -->food web.
+If different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community <!--may constrain evolution by -->**would** increase the number of traits under selection**, which may constrain the trajectory of evolution toward a specific phenotype**.
+Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities**, which would allow for a greater diversity of phenotypes.
+Now consider the curvature of the fitness landscape.
+If consumers impose selection on different ends of the trait distribution, then a more diverse consumer community may impose stabilizing selection, and thus decrease the evolutionary potential of their resource.
+In contrast, additional consumers may impose disruptive selection if they increase the fitness impact on the mean phenotype of the resource, which would act to increase genetic variance in the trait.**
+
+To examine these different possibilities, we conducted a field experiment that removed a consumer guild that **parasitizes**<!--directly and indirectly impacts fitness of -->an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
 \ref{fig:Conceptual}).
@@
 \ref{fig:Conceptual}).
-The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
+<!-- Omit due to Reviewer #1 comment: The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
 <!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
@@
 \ref{fig:Conceptual}).
-We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's adaptive landscape.
-Taken together, our study gives insight to how the loss of biodiversity may constrain the evolution of interacting populations.
+We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's **fitness** landscape.
+Taken together, our study gives insight to how the loss of biodiversity may **alter both the trajectory and evolutionary potential**<!--constrain the evolution -->of interacting populations.
 
@@
 We setup our food-web manipulation across 128 plants soon after galls began developing on willows in early June of 2013.
-These 128 plants came from eight different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
+These 128 plants came from **8** different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
 For the original food web (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
-Marking galls with flagging tape ensured that all galls had similar phenology when we collected galls later in the season.
+Marking galls with flagging tape ensured that **we compared galls with similar phenology in both treatments** when we collected galls later in the season.
 For the removal food web, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
@@
 In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature.
-We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or were parasitized.
-We did not include other sources of mortality in our analyses, such as early larval death, as they could influence the expression of the gall phenotype and confound estimates of selection.
+We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or **died due to parasitism.
+We further distinguished whether mortality was caused by an egg or larval parasitoid**.
+**Early larval death was another important source of mortality (`r round(mean(full_df$early.larval.death), 2)*100`%), but we excluded these cases from our analysis.
+We did this because early larval death can stunt gall growth, which would confound estimates of selection due to parasitism on chamber diameter (one of the phenotypes we measured; details given below).**
+<!--We did not include other sources of mortality in our analyses, such as early larval death, as they could influence **gall growth, which would confound estimates of selection due to parasitism on chamber diameter (one of the phenotypes we measured; details given below)**.
 <!--Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
@@
 All larvae collected from the same multi-chambered gall were scored with the same clutch size.
-Third, we measured oviposition preference as the density of larvae observed on a plant in an independent survey.
+Third, we measured oviposition preference **for individual plants** as the density of larvae observed on a plant in an independent survey.
 We did this by randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
@@
 Measuring larval densities on plants in the field is a common method for measuring oviposition preference [@Gripenberg2010]; however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference [@Singer1986].
-Fortunately, a couple features of our study system suggest that larval densities may be a good proxy for oviposition preference.
-For example, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
-Also, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
-
-## Quantifying the Adaptive Landscape
-
-Inferring adaptive landscapes assumes that trait distributions are multivariate normal [@Lande1983]. 
+Fortunately, **two** features of our study system suggest that larval densities may be a good proxy for oviposition preference.
+**First**, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
+**Second**, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
+
+## Quantifying the **Fitness** Landscape
+
+Inferring **fitness** landscapes assumes that trait distributions are multivariate normal [@Lande1983]. 
 To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
-We then scaled all phenotypic traits (mean=0 and SD=1) across treatments prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
+**Chamber diameter already had a normal distribution so we did not transform it.** We then scaled all phenotypic traits (mean=0 and SD=1) across treatments prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
 
@@
 First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment.
-Second, we translated selection surfaces into the scale of relative fitness ($w$) in order to calculate standardized selection gradients.
-Third, we used our estimates of directional selection gradients to characterize the slope of the adaptive landscape, which we used to measure selective constraints.
-Finally, we estimated the curvature of the adaptive landscape and used a simulation to explore its effects on the adaptive potential of the gall midge population in the next generation.
+Second, we translated selection surfaces into the scale of relative fitness ($w\boldsymbol{=W/\bar{W}}$) in order to calculate standardized selection gradients.
+Third, we used our estimates of directional selection gradients to characterize the slope of the **fitness** landscape, which we used to measure selective constraints.
+Finally, we estimated the curvature of the **fitness** landscape and used a simulation to explore its effects on the adaptive potential of the gall midge population in the next generation.
 
@@
 To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_i$), quadratic ($\alpha_{ii}$), and linear interactions ($\alpha_{ij}$) between each trait.
-We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.
-Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
-Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the adaptive landscape [@Arnold2003].
-To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall ID nested within plant ID nested within genotype ID as random effects.
+<!--We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.--> Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
+Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the **fitness** landscape [@Arnold2003].
+To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall **identity** nested within plant **identity** nested within genotype **identity** as random effects.
 Although statistical models with random effects are not common in analyses of natural selection, we think that modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
-Since our end goal was to characterize the relationship between mean trait values and mean fitness (adaptive landscape), we assumed the mean value of our random effects (i.e.
+Since our end goal was to characterize the relationship between mean trait values and mean fitness (**fitness** landscape), we assumed the mean value of our random effects (i.e.
 setting them to zero) when calculating selection surfaces.
@@
 **Selection gradients**: Selection gradients cannot be estimated directly from GLMMs of selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the above model measure the change in the logarithm of the odds of surviving (i.e.
+For example, the coefficients in the **previously described binomial** model measure the change in the **log-odds** of surviving (i.e.
 $\text{ln}\{W(z)/[1-W(z)]\}$) associated with 1 SD change in a trait with all other traits held fixed at their mean.
@@
 **Selective constraints**: <!--We measured evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
--->The number of selective constraints is determined by the slope of the adaptive landscape, which in our study corresponds to:
+-->The number of selective constraints is determined by the slope of the **fitness** landscape, which in our study corresponds to:
 
@@
 By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e.
-95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on selective constraints.
-This gives insight as to whether there is a specific combination of phenotypes favored by natural selection (i.e.
+95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on \textbf{the number of} selective constraints.
+<!--This gives insight as to whether there is a specific combination of phenotypes favored by natural selection (i.e.
 more traits under directional selection), or whether multiple trait combinations have comparable fitness (i.e.
-less traits under directional selection).
-
-**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}$) are governed by the curvature of the adaptive landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
+less traits under directional selection).-->
+
+**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\boldsymbol{\text{C}})\text{G}$) are governed by the curvature of the **fitness** landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 
@@
 Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
-Subtracting these two matrices results in the curvature matrix of the adaptive landscape:
+Subtracting these two matrices results in the curvature matrix of the **fitness** landscape:
 
@@
 -->Evolvability measures the ability for a trait to evolve toward a given direction of selection [@Hansen2008].
-In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can compute its average evolvability over random selection gradients [@Hansen2008; @Melo2015].
+In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can compute its average evolvability over random **directional** selection gradients [@Hansen2008; @Melo2015].
 By computing the average evolvability (here, we used `r n_random_gradients` random $\beta$s) for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of the associated traits.
@@
 To estimate this potential bias, we subset our data to only include galls where there was variation in larval survival within the same gall (i.e.
-1 > mean survival > 0).
+1 > **survival** > 0).
 If we assume that larvae within each gall should have similar chamber diameters because they come from the same clutch and experience the same local environment (an assumption our data supports: gall ID explains 54% of the variance in chamber diameter), then the relationship between chamber diameter and larval survival in this data subset represents the effect of parasitism on trait expression (i.e.
@@
 Using the same models as described above, we substituted egg parasitism as our response variable to quantify selection surfaces and selection gradients acting on the egg parasitoid.
-Note that we cannot test the effect of food-web structure on the egg parasitoid's adaptive landscape ---we can only estimate selection imposed by larval parasitoids.
+Note that we cannot test the effect of food-web structure on the egg parasitoid's **fitness** landscape ---we can only estimate selection imposed by larval parasitoids.
 This comparison is still useful though in determining the extent to which the loss of consumers may have indirect evolutionary effects by altering selection on multiple interacting populations.
@@
 Unless otherwise noted, we report mean estimates of selection surfaces and selection gradients with 95% confidence intervals in brackets.
-Note that for visualizing the adaptive landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
-This emphasizes the fact that we can only reliably estimate the shape of the adaptive landscape near the mean phenotype of the population [@Arnold2001].
-We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the adaptive landscape [@Arnold2003].
+Note that for visualizing the **fitness** landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
+This emphasizes the fact that we can only reliably estimate the shape of the **fitness** landscape near the mean phenotype of the population [@Arnold2001].
+We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the **fitness** landscape [@Arnold2003].
 All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
@@
 \hline
-\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} \\
+\textbf{Selection gradient} & \textbf{Original} & \textbf{Removal} & \textbf{Contrast} (\small{Original - Removal}) \\
 \hline
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] }\\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`] }\\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`] }\\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`] \\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`] \\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`] \\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`] }\\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`] \\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`] \\
 
@@
 `r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`,
+`r round(-1*filter(tidy_foodweb_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`] \\ 
 \hline
@@
 `r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` 
-[`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was simply a consequence of the (expected) lower survival of gall midges in the original food web <!--(original $\bar W$=
+[`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`,
+`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`]), but was simply a consequence of the (expected) lower survival of gall midges in the original food web <!--(original $\bar W$=
 `r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$mean,2)` 
@@
 It is worth noting that positive selection on chamber diameter in both treatments was unexpected.
-For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is strongly correlated with an unmeasured trait that is under selection (e.g.
+For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is **either directly related to survival** or strongly correlated with an unmeasured trait that is under selection (e.g.
 immune response).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
@@
 For clarity, we only display 100 bootstraps even though inferences are based on 1,000 replicates.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the \\textbf{fitness} landscape."}
 knitr::include_graphics("../analyses/UV_landscapes.pdf")
@@
 
-To visualize the multivariate effects of these selective constraints, we plotted the adaptive landscape for each trait combination in each treatment (fig.
+To visualize the multivariate effects of these selective constraints, we plotted the **fitness** landscape for each trait combination in each treatment (fig.
 \ref{fig:MV_Landscape}).
 The arrows in fig.
-\ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while contours represent predicted survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
+\ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while **the dotted lines** represent predicted survival of the mean phenotype in each food-web treatment.
+Notice that arrows point more toward a corner of the **fitness** landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
 This indicates that the removal of consumers more strongly favored a specific combination of traits, rather than allowing for multiple trait combinations to have comparable fitness.
 
-```{r MV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of adaptive landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
+```{r MV_Landscape, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:MV_Landscape}Two dimensional view of \\textbf{fitness} landscapes of gall midge phenotypes in the original food web and with the removal of larval parasitoids.
 Each panel corresponds to a different combination of phenotypic traits: clutch size and chamber diameter (A); clutch size and oviposition preference (B); oviposition preference and chamber diameter (C).
-Arrows represent mean estimates of directional selection gradients, while contours represent predicted larval survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the adaptive landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
+Arrows represent mean estimates of directional selection gradients, while \\textbf{dotted lines} represent predicted larval survival of the mean phenotype in each food-web treatment.
+Notice that arrows point more toward a corner of the \\textbf{fitness} landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
 This indicates that the removal of consumers more strongly favored a specific combination of traits.
-Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the adaptive landscape."}
+Note that mean larval survival is plotted on a natural log scale to reflect the mathematical definition of the \\textbf{fitness} landscape."}
 knitr::include_graphics("../analyses/MV_landscapes.pdf")
@@
 
-\indent The curvature of the adaptive landscape indirectly affects genetic constraints and is influenced by directional, quadratic, and correlational selection gradients.
+\indent The curvature of the **fitness** landscape indirectly affects genetic constraints and is influenced by directional, quadratic, and correlational selection gradients.
 There was no clear evidence of correlational selection for any combination of traits in either food-web treatment (table \ref{Table:Gradients}).
@@
 In contrast, our food-web treatment did alter quadratic selection acting on oviposition preference (table \ref{Table:Gradients}).
-The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the removal of larval parasitoids (fig.
+In particular, we observed disruptive selection in the original food web, with selection favoring females that either avoided high densities (<0.5 SD above mean density), or if gall densities were high enough (>0.5 SD above mean), then selection favored females that were attracted to high densities (fig.
 \ref{fig:UV_Landscape}B).
-This dampened relationship was partly due to a trend for nonlinear selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
+This nonlinear
+<!--The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the removal of larval parasitoids (fig.
+\ref{fig:UV_Landscape}B).
+This dampened--> relationship was partly due to a trend for disruptive<!--nonlinear--> selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
@@
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in the original food web.
-This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.
-
-Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the adaptive landscape in each food-web treatment.
+This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), which would act to increase the relative fitness of gall midges.<!--, and thus a less than additive effect on gall midges.-->
+
+Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the **fitness** landscape in each food-web treatment.
 
@@
 \ref{fig:EggPtoid_Selection}).
+**This may indicate that larval parasitoids switch to target galls that have been parasitized by an egg parasitoid once egg parasitoid densities are high enough.
+This prey switching behavior would contribute to the disruptive selection we observed on gall midge preference (fig.
+\ref{fig:UV_Landscape}B).**
 
@@
 We found that the removal of larval parasitoids constrained phenotypic evolution in gall midges in two key ways.
-First, more traits contributed to the slope of the adaptive landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
-Second, removing larval parasitoids altered the curvature of the adaptive landscape in such a way that tended to decrease the evolvability of associated traits.
-Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's adaptive potential in the face of novel selection pressures.
+First, **we observed directional selection on more traits** in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.<!--First, more traits contributed to the slope of the **fitness** landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.--> Second, removing larval parasitoids altered the curvature of the **fitness** landscape in such a way that tended to decrease the evolvability of associated traits.
+Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's **fitness** potential in the face of novel selection pressures.
 Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
-Taken together, our study provides experimental evidence from the field that the loss of consumers may constrain the adaptive potential of remaining populations.
+Taken together, our study provides experimental evidence from the field that the loss of consumers may constrain the **fitness** potential of remaining populations.
 
@@
 When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different consumers impose conflicting selection pressures or select for distinct traits.
-When consumers impose conflicting selection on traits, as in our study and others [@Weis1985; @Abrahamson1997; @Start2016; @Start2018], then consumer diversity acts to neutralize selection and relax selective constraints.<!-- For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
+When consumers impose conflicting selection on traits, as in our study and others [@Weis1985; @Abrahamson1997; @Start2016; @Start2018], then consumer diversity acts to neutralize selection, **which can maintain larger evolvability.**<!--and relax selective constraints.<!-- For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
 Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.--> On the other hand, different consumers may impose selection on different traits; therefore, a more diverse consumer community may favor a particular combination of traits and increase selective constraints.
@@
 <!--Indirect effects of selective constraints-->
-We also found evidence for a general decrease in trait evolvability when we excluded larval parasitoids due to changes in the curvature of the adaptive landscape<!--indirect effects of selection on the population's G-matrix-->.
-This result was driven by nonlinear selection on gall midge oviposition preference in the original food web, which was due to both increases in intraguild predation and the lower mean survival of gall midges.
+We also found evidence for a general decrease in trait evolvability when we excluded larval parasitoids due to changes in the curvature of the **fitness** landscape<!--indirect effects of selection on the population's G-matrix-->.
+This result was driven by **disruptive**<!--nonlinear--> selection on gall midge oviposition preference in the original food web, which was likely due to both increases in intraguild predation **on egg parasitoids (i.e.
+prey switching)** and the lower mean survival of gall midges.
+**This pattern of selection acts to increase genetic variation in oviposition preference, which in turn enhances the ability of the gall midge population to respond to uncertain selection pressures in the next generation (i.e.
+evolvability).
+This pattern of selection also indicates the possibility of evolutionary bistability, where different initial conditions (e.g.
+mean oviposition preference) select for different phenotypes of the same species in similar environments [@Landi2018LifeHistory].
+Thus, this pattern of selection may contribute to genetic and phenotypic diversity both within and among populations.** Current theory, however, often assumes genetic variances and covariances remain constant over time **and space** rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017; **@Medeiros2018**].
+Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that emerge in a network of interacting species.
+
+<!-- 
+Taken together, these results suggest that the loss of larval parasitoids may reduce genetic and phenotypic diversity both within and among gall midge populations.
+
+This would result in a bimodal distribution in average oviposition preference across populations.
+
 While these results are intriguing, they still indicate that the indirect effects of selection are contingent on the structure of a population's G-matrix (e.g.
@@
 Together, this suggests that consumer extinctions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
--->Indeed, current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017].
+Indeed, current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017].
 Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that emerge in a network of interacting species.
@@
 
+Another possible caveat is that our manipulation may represent a perturbation to the shape of the fitness landscape, rather than the effects of losing a consumer guild *per se*.
+This is because the fitness landscape we are only able to infer the shape of the fitness landscape near the mean phenotype of the population, rather than its shape after being exposed to many generations of selection by the removal treatment.
+This is a weakness of virtually all field studies of natural selection, although it may be circumvented through experimental evolution [e.g.
+@Betts2018].
+
 <!--Indirect evolutionary effects-->
@@
 This release occurs more on trees with high larval densities, which could intensify future selection on gall midge oviposition preference.
-A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in ecological communities [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
+**This suggests that the loss of larval parasitoids would likely impose even greater constraints on the trajectory of evolution than what we estimated in our study.
+However, while this may intensify selection toward gall midges to avoid conspecifics, this may actually relax selection imposed by gall midges on the plant, due to plants having lower gall densities.**  A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in ecological communities [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
 If indirect evolutionary effects are common [@Miller1996; @Walsh2013; @Guimaraes2017], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
@@
 <!-- Conclusions -->
-Our study gives insight to how the loss of consumers alters evolutionary constraints on remaining populations.
+Our study gives insight to how the loss of consumers alters **natural selection, and in turn** evolutionary constraints on remaining populations.
 In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
 Our work also highlights some key challenges for predicting phenotypic evolution in rapidly changing communities.
-<!--First, the simplification of ecological communities may increase selective constraints, requiring knowledge of genetic variances and covariances of multiple traits to accurately predict evolutionary change.--><!--actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.-->For example, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait, yet our results highlight that the number of traits under selection may change with the network context.
+<!--First, the simplification of ecological communities may increase selective constraints, requiring knowledge of genetic variances and covariances of multiple traits to accurately predict evolutionary change.--><!--actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.-->For example, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait [but see @Brown2007; @Leimar2009], yet our results highlight that the number of traits under selection may change with the network context.
 Importantly, we found that different species/guilds imposed different selection pressures.
 Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the ecological community.
-We expect that a continued integration of adaptive landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
+We expect that a continued integration of **fitness** landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
 

### 2020-03-11 manuscript/manuscript_clean.Rmd
accepted clean version

--- 2020-01-13 manuscript/manuscript.Rmd
@@
 ---
-# Decided to manually format the title page because I had greater control. Note that you should use put this info in the YAML header for compatability across document formats (e.g. html)
-#title: Phenotypic evolution is more constrained in simpler food webs
-#author: 
-#- Matthew A. Barbour$^{1,2,\ast}$ 
-#- Christopher J. Greyson-Gaito$^{2,3}$ 
-#- Arezoo Sootodeh$^{2}$ 
-#- Brendan Locke$^{4}$ 
-#- Jordi Bascompte$^{1}$ 
-# for compatability across document formats use 'date' for affiliations, as recommended by https://github.com/rstudio/bookdown/issues/348, with | to create new sections.
-#date: | 
-#    | 1. Affiliation
 output:
@@
 ## Reproduce analyses ----
-#knitr::knit("../analysesreproduce_analyses.Rmd") 
 rmarkdown::render("../analyses/reproduce_analyses.Rmd", clean = FALSE)
@@
 
-*Keywords*: **fitness landscape**, adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, <!--complexity, biodiversity,-->community context, extinction.
+*Keywords*: fitness landscape, adaptive landscape, ecological networks, eco-evolutionary dynamics, natural selection, host-parasitoid, community context, extinction.
 
@@
 
-*Abstract Word Count*: 251
+*Abstract Word Count*: 256
 
@@
 
-*Total Word Count*: `r wordcountaddin::word_count("manuscript.Rmd") - 527` <!-- subtract estimate of Abstract, Impact, Acknowledgements, Author Contributions, Data Accessibility, and their associated headers -->
+*Total Word Count*: `r wordcountaddin::word_count("manuscript_clean.Rmd") - 552` <!-- subtract estimate of Abstract, Impact, Acknowledgements, Author Contributions, Data Accessibility, and their associated headers -->
 
@@
 \bigskip
-
-<!-- \footnotesize Prepared using an *Am. Nat.* inspired \LaTeX{} template for Rmarkdown. \normalsize -->
 
@@
 
-The loss of biodiversity<!--Global change--> is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
-Theory on **fitness** landscapes provides a framework for predicting how selection constrains phenotypic evolution, but often treats the network context of evolving populations as a ``black box''.
-Here, we integrate ecological networks and **fitness** landscapes to examine how changes in food-web structure shape evolutionary constraints.
-We conducted a field experiment that removed<!--simulated the extinction of--> a guild of larval parasitoids that imposed direct and indirect selection pressures on an insect herbivore.
+The loss of biodiversity is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
+Theory on fitness landscapes provides a framework for predicting how selection alters the trajectory and evolutionary potential of populations, but often treats the network of interacting populations as a ``black box''.
+Here, we integrate ecological networks and fitness landscapes to examine how changes in food-web structure shape phenotypic evolution.
+We conducted a field experiment that removed a guild of larval parasitoids that imposed direct and indirect selection pressures on an insect herbivore.
 We then measured herbivore survival as a function of three key phenotypic traits to estimate directional, quadratic, and correlational selection gradients in each treatment.
-We used these selection gradients to characterize the slope and curvature of the **fitness** landscape to understand the direct and indirect effects of consumer loss on evolutionary constraints.
-We found that the number of traits under directional selection increased with the removal of larval parasitoids, indicating greater selective constraints on the trajectory of evolutionary change.
-Similarly, we found that the removal of larval parasitoids altered the curvature of the **fitness** landscape in such a way that tended to decrease the evolvability of the traits we measured in the next generation.<!--In contrast, the adaptive landscape was more neutral in the original food web because different parasitoid guilds impose different selection pressures, minimizing relative fitness differences among phenotypes.--> Our results suggest that the loss of trophic interactions <!--due to consumer extinctions -->can impose greater constraints on phenotypic evolution.
+We used these selection gradients to characterize the slope and curvature of the fitness landscape to understand the direct and indirect effects of consumer loss on phenotypic evolution.
+We found that the number of traits under directional selection increased with the removal of larval parasitoids, indicating evolution was more constrained toward a specific combination of traits.
+Similarly, we found that the removal of larval parasitoids altered the curvature of the fitness landscape in such a way that tended to decrease the evolvability of the traits we measured in the next generation.
+Our results suggest that the loss of trophic interactions can impose greater constraints on phenotypic evolution.
 This indicates that the simplification of ecological communities may constrain the adaptive potential of remaining populations to future environmental change.
@@
 
-<!--
-We found that the loss of predators increased the number of prey traits under selection, indicating that the trajectory of evolution was more constrained to a specific combination of traits<!--.
-This suggests that simpler communities may constrain the trajectory of evolution toward a specific combination of traits--><!--.
-In addition, we found that that the loss of predators could make it more difficult for prey to adapt to future environments.
-Taken together, our results suggest that the loss of biodiversity may rewire interactions in such a way that constrains the adaptive potential of remaining populations.
--->
-
 \newpage
-
-<!-- > "What escapes the eye, however, is a much more insidious kind of extinction: the extinction of ecological interactions." @Janzen1974 -->
 
@@
 
-The **fitness** landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
-More than a metaphor, the **fitness** landscape links quantitative genetic and phenotypic variation **in multiple traits** to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory]<!--, giving insight to the direct and indirect effects of selective constraints [@Arnold1992]-->.
-Ecological interactions often play a key role in shaping natural selection<!--selective constraints-->, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006].
-Although there is clear evidence that species interactions can shape the **fitness** landscape, we still have a poor understanding of how the **fitness** landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018; **@Hui2018**].
+The fitness landscape provides a powerful framework for understanding how natural selection has shaped the evolution of biodiversity ---from genes to phenotypes to species [@Wright1931; @Simpson1944; @Arnold2001].
+More than a metaphor, the fitness landscape links quantitative genetic and phenotypic variation in multiple traits to evolution by natural selection [@Lande1979; @Arnold1984applications; @Arnold1984theory].
+Ecological interactions often play a key role in shaping natural selection, as evidenced by the role of antagonistic and mutualistic interactions in driving evolutionary change [@Schluter2000; @Abrams2000; @Bronstein2006].
+Although there is clear evidence that species interactions can shape the fitness landscape, we still have a poor understanding of how the fitness landscape is shaped by a community of interacting species [@McPeek2017; @terHorst2018; @Hui2018].
 Resolution on how change in ecological communities shape phenotypic evolution is urgently needed though, given the rapid losses of biodiversity we are observing in the Anthropocene [@Scheffers2016].
@@
 Ecological networks, such as food webs describing who-eats-whom, provide an explicit representation of the direct and indirect effects that emerge in a community of interacting species [@Bascompte2014; @McCann2012].
-Here, we integrate ecological networks and **fitness** landscapes to understand how ecological communities constrain evolutionary change **[@Hui2018]**.
-The <!--direct and indirect -->effects of natural selection can be inferred by quantifying the slope and curvature of the **fitness** landscape **for multiple phenotypic traits** [@Arnold1992].
-<!--For example, t-->The slope is determined by the **strength of** directional selection <!--gradients -->acting on each trait**,which** influences the trajectory of evolutionary change [@Lande1979;@Arnold1992].
-**This fact is made clear by the 'Lande equation', $\Delta \bar z = \beta\text{G}$, where $\Delta \bar z$ is a column vector of the average change in each trait between generations, $\beta$ is a column vector of directional selection gradients acting on each trait (i.e.
-slope), and $\text{G}$ is the additive genetic (co)variance matrix for these traits (i.e.
-G-matrix).
-@Grant1995 used their knowledge of the slope of the fitness landscape for multiple traits related to body and beak size in Darwin's finches <!--, in addition to the G-matrix of those traits, -->to accurately predict the trajectory of evolution in these traits in response to different episodes of selection imposed by drought.**
-<!--For example, a drought in 1976-1977 on Daphne Major in the Gal\'apagos imposed directional selection for large weight, wing length, and bill depth in medium ground finches, and this equation predicted well the evolutionary response in all three of these traits in the next generation (Grant and Grant 1995).
-This equation has been used to predict short-term evolutionary change in Darwin's finches (Grant and Grant 1995).-->
-<!--Selective constraints on evolution increase with the number of traits under directional selection, as this diminishes the number of optimal solutions [@Arnold2003].-->
-The curvature of the **fitness** landscape is governed by the **strength of stabilizing, disruptive, and correlational selection acting on each trait<!--directional, quadratic, and correlational <!--nonlinear selection gradients-->, which <!--and acts to to indirectly constrain evolution -->can alter the potential for evolutionary change through its effect on <!--genetic constraints [@Arnold1992; @Hansen2008].
-Genetic constraints are largely governed by--><!-- a population's -->the G-matrix** <!-----the additive genetic variances and covariances between traits -->[@Hansen2008].
-For example, stabilizing selection acts to erode genetic variance in traits, which can impose a constraint on the ability of those traits to respond to future selection [@Hansen2008].
-**In contrast, disruptive selection for different trait values acts to increase genetic variance in traits, thus increasing the capacity for future adaptation [@Bolnick2008]**.<!-- In general, genetic constraints will increase with the number of traits under directional or stabilizing selection, as this will decrease the additive genetic variance in those traits [@Hansen2008].--> Correlational selection alters the genetic covariance between traits, which may facilitate or hinder future adaptation depending on the pattern of selection on those traits **and the structure of the G-matrix** [@Brodie1992].<!--Genetic constraints may also increase with the number of trait combinations under correlational selection, as this type of selection decreases the evolutionary independence of traits [@Hansen2008].--> If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the **fitness** landscape **of interacting populations**.
+Here, we integrate ecological networks and fitness landscapes to understand how selection imposed by ecological communities alter the trajectory and evolutionary potential of interacting populations [@Hui2018].
+The effects of natural selection on multiple phenotypic traits can be inferred by quantifying the slope and curvature of the fitness landscape [@Arnold1992].
+The slope is determined by the strength of directional selection acting on each trait, which influences the trajectory of evolution [@Lande1979; @Arnold1992].
+This fact is made clear by the 'Lande equation', $\Delta\bar z = \text{G}\beta$, where $\Delta \bar z$ is a column vector of the average change in each trait between generations, \text{G} is the additive genetic (co)variance matrix for these traits (i.e.
+G-matrix), and $\beta$ is a column vector of directional selection gradients acting on each trait (i.e.
+slope).
+Grant and Grant [-@Grant1995] used the slope of the fitness landscape for multiple traits related to body and beak size in Darwin's finches to accurately predict the effects of drought on the evolutionary trajectory of these traits.
+The curvature of the fitness landscape is governed by the strength of stabilizing, disruptive, and correlational selection acting on each trait, which can alter the evolutionary potential of a population through its effect on the G-matrix [@Hansen2008].
+For example, stabilizing selection acts to erode genetic variance in a trait, which can impose a constraint on the ability of this trait to respond to future selection [@Hansen2008].
+In contrast, disruptive selection toward extreme trait values acts to increase genetic variance in a trait, thus increasing the capacity for future adaptation [@Bolnick2008].
+Correlational selection alters the genetic covariance between traits, which may facilitate or hinder future adaptation depending on the pattern of selection on those traits and the structure of the G-matrix [@Brodie1992].
+If we want to predict how ecological communities shape phenotypic evolution, we must understand how ecological networks shape the fitness landscape of interacting populations.
 
-The loss of biodiversity is altering the structure of ecological networks<!--communities-->**[@Landi2018ComplexityStability]**, which may influence **the slope and curvature of the fitness landscape**<!-- evolutionary constraints -->in a number of ways.
-**Consider first the slope of the fitness landscape <!--For example, -->in a <!--multitrophic community or -->food web.
-If different consumers impose directional selection on different traits of a shared resource, then a more diverse consumer community <!--may constrain evolution by -->**would** increase the number of traits under selection**, which may constrain the trajectory of evolution toward a specific phenotype**.
-Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities**, which would allow for a greater diversity of phenotypes.
-Now consider the curvature of the fitness landscape.
-If consumers impose selection on different ends of the trait distribution, then a more diverse consumer community may impose stabilizing selection, and thus decrease the evolutionary potential of their resource.
-In contrast, additional consumers may impose disruptive selection if they increase the fitness impact on the mean phenotype of the resource, which would act to increase genetic variance in the trait.**
+The loss of biodiversity is altering the structure of ecological networks [@Landi2018ComplexityStability], which may influence the slope and curvature of the fitness landscape in a number of ways.
+For example, consider how changes in consumer diversity in a food web may alter the slope of the fitness landscape for a shared resource.
+If different consumers impose directional selection on different traits of the resource, then a more diverse consumer community would increase the number of traits under selection, which may constrain the trajectory of evolution toward a specific phenotype.
+Alternatively, if consumers impose selection on different values of a trait, then their selective effects would cancel each other out in more diverse communities, which would allow for a greater diversity of phenotypes to persist.
+Now consider the effects of consumer diversity on the curvature of the fitness landscape.
+If consumers impose selection on different ends of a resource's trait distribution, then a more diverse consumer community may impose stabilizing selection, which would decrease genetic variance in this trait.
+In contrast, additional consumers may impose disruptive selection if their cumulative effect decreases the relative fitness of a resource's average trait value, which would increase the genetic variance in this trait.
 
-To examine these different possibilities, we conducted a field experiment that removed a consumer guild that **parasitizes**<!--directly and indirectly impacts fitness of -->an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
+To examine these different possibilities, we conducted a field experiment that removed a consumer guild that parasitizes an abundant insect herbivore (*Iteomyia salicisverruca*, Family Cecidomyiidae; fig.
 \ref{fig:Conceptual}).
@@
 \ref{fig:Conceptual}).
-We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's **fitness** landscape.
-Taken together, our study gives insight to how the loss of biodiversity may **alter both the trajectory and evolutionary potential**<!--constrain the evolution -->of interacting populations.
+We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's fitness landscape.
+Taken together, our study gives insight to how the loss of biodiversity may alter both the trajectory and evolutionary potential of interacting populations.
 
-```{r Conceptual, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (*Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana*.
+```{r Conceptual, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:Conceptual}Experimental manipulation of food-web structure associated with a leaf-galling midge (b, *Iteomyia salicisverruca*) feeding on the willow *Salix hookeriana* (a).
 Black arrows denote the flow of energy in this network of trophic interactions.
 In the original food web, we allowed the full suite of egg and larval parasitoids to impose selection.
-In the removal food web, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (*Platygaster* sp.) to impose selection.
+In the removal food web, we used mesh bags to exclude the guild of larval parasitoids, only allowing the egg parasitoid (c, *Platygaster* sp.) to impose selection.
 Note that larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid.
-Larval parasitoids include the following species (from left to right): *Mesopolobus* sp.
-(Family: Pteromalidae); *Tetrastichus* sp.
-(Family: Eulophidae); and *Torymus* sp.
-(Family: Torymidae)."}
-knitr::include_graphics("../analyses/complex_simple_foodwebs_v4.jpeg")
+Larval parasitoids include the following species: *Mesopolobus* sp.
+(d, Family: Pteromalidae); *Tetrastichus* sp.
+(e, Family: Eulophidae); and *Torymus* sp.
+(f, Family: Torymidae)."}
+knitr::include_graphics("../analyses/complex_simple_foodwebs_v4_5.jpg")
 ```
@@
 We setup our food-web manipulation across 128 plants soon after galls began developing on willows in early June of 2013.
-These 128 plants came from **8** different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
+These 128 plants came from 8 different plant genotypes that spanned the range of trait variation observed in this willow population [@Barbour2015].
 For the original food web (eight replicates per genotype), we used flagging tape to mark 14 galled leaves per plant (~30 larvae), allowing the full suite of egg and larval parasitoids to impose selection.
-Marking galls with flagging tape ensured that **we compared galls with similar phenology in both treatments** when we collected galls later in the season.
+Marking galls with flagging tape ensured that we compared galls with similar phenology in both treatments when we collected galls later in the season.
 For the removal food web, we enclosed 14 galled leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species that attack during larval development.
@@
 In late August, we collected marked and bagged galls from each plant, placed them into 30 mL vials and kept them in the lab for 4 months at room temperature.
-We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or **died due to parasitism.
-We further distinguished whether mortality was caused by an egg or larval parasitoid**.
-**Early larval death was another important source of mortality (`r round(mean(full_df$early.larval.death), 2)*100`%), but we excluded these cases from our analysis.
-We did this because early larval death can stunt gall growth, which would confound estimates of selection due to parasitism on chamber diameter (one of the phenotypes we measured; details given below).**
-<!--We did not include other sources of mortality in our analyses, such as early larval death, as they could influence **gall growth, which would confound estimates of selection due to parasitism on chamber diameter (one of the phenotypes we measured; details given below)**.
-<!--Since we were interested in selection imposed by parasitoids, we excluded other sources of mortality (`r round((mean(full_df$early.larval.death) + mean(full_df$unknown_mortality)), 2)*100`% mortality from other sources).
-Another reason why we excluded other sources of mortality, such as early larval death, is that they can influence the expression of the gall phenotype and confound estimates of selection.--> For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
+We then opened galls under a dissecting scope and determined whether larvae survived to pupation (our measure of fitness) or died due to parasitism.
+We further distinguished whether mortality was caused by an egg or larval parasitoid.
+Early larval death was another important source of mortality (`r round(mean(full_df$early.larval.death), 2)*100`%), but we excluded these cases from our analysis.
+We did this because early larval death can stunt gall growth, which would confound estimates of selection due to parasitism on one of the phenotypes we measured (chamber diameter; details given in next section).
+For the food-web treatment that excluded larval parasitoids, we further restricted our data by removing any incidental instances of parasitism by a larval parasitoid.
 This represented less than 3\% of the observations in this food-web treatment and allowed us to focus our inferences of selection on those imposed by the egg parasitoid.
@@
 All larvae collected from the same multi-chambered gall were scored with the same clutch size.
-Third, we measured oviposition preference **for individual plants** as the density of larvae observed on a plant in an independent survey.
+Third, we measured oviposition preference for individual plants as the density of larvae observed on a plant in an independent survey.
 We did this by randomly sampling five branches per tree and counting the number of individual gall chambers (number of larvae).
@@
 Measuring larval densities on plants in the field is a common method for measuring oviposition preference [@Gripenberg2010]; however, caution must be taken in inferring 'preference' as larval densities can be influenced by processes other than preference [@Singer1986].
-Fortunately, **two** features of our study system suggest that larval densities may be a good proxy for oviposition preference.
-**First**, since our data comes from a randomized placement of plant genotypes in a common garden, there is no consistent bias in which plant genotypes females are exposed to while searching for oviposition sites.
-**Second**, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
+Fortunately, two features of our study system suggest that larval densities may be a good proxy for oviposition preference.
+First, since our data comes from a randomized placement of plant genotypes in a common garden, females midges have equal exposure to many possible plant genotypes when choosing an oviposition site.
+Second, egg predation is a minor source of mortality for galling insects in general [@Hawkins1997]; therefore, we do not expect any prior egg predation to bias our estimates of observed larval densities.
 
-## Quantifying the **Fitness** Landscape
+## Quantifying the Fitness Landscape
 
-Inferring **fitness** landscapes assumes that trait distributions are multivariate normal [@Lande1983]. 
+Inferring the fitness landscape assumes that trait distributions are multivariate normal [@Lande1983]. 
 To approximate this assumption, we log-transformed clutch size and square-root transformed oviposition preference.
-**Chamber diameter already had a normal distribution so we did not transform it.** We then scaled all phenotypic traits (mean=0 and SD=1) across treatments prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
+Chamber diameter already had a normal distribution so we did not transform it.
+We then scaled all phenotypic traits (mean=0 and SD=1) across treatments prior to our analyses (detailed below) to ensure that our estimates of selection were comparable across traits and with other studies.
 
@@
 First, we used generalized linear mixed models (GLMM) to quantify selection surfaces \textemdash linear and nonlinear relationships between absolute fitness ($W$) and standardized phenotypic traits ($i$) of individuals \textemdash in each food-web treatment.
-Second, we translated selection surfaces into the scale of relative fitness ($w\boldsymbol{=W/\bar{W}}$) in order to calculate standardized selection gradients.
-Third, we used our estimates of directional selection gradients to characterize the slope of the **fitness** landscape, which we used to measure selective constraints.
-Finally, we estimated the curvature of the **fitness** landscape and used a simulation to explore its effects on the adaptive potential of the gall midge population in the next generation.
+Second, we scaled selection surfaces relative to mean fitness ($\bar W$) in order to calculate standardized selection gradients.
+Third, we used our estimates of directional selection gradients to characterize the slope of the fitness landscape, which we used to quantify the effects of food-web structure on the trajectory of evolution.
+Finally, we estimated the curvature of the fitness landscape and used a simulation to explore its effects on the adaptive potential of the gall midge population in the next generation.
 
 **Selection surfaces**: Since larval survival was our measure of absolute fitness, we used a GLMM that assumed a binomial error distribution (and logit-link function).
-To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_i$), quadratic ($\alpha_{ii}$), and linear interactions ($\alpha_{ij}$) between each trait.
-<!--We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.--> Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
-Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the **fitness** landscape [@Arnold2003].
-To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall **identity** nested within plant **identity** nested within genotype **identity** as random effects.
+To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_i$), quadratic ($\alpha_{ii}$), and statistical interactions ($\alpha_{ij}$) between each trait.
+<!--Removed at Reviewer #1's suggestion because it is redundant: We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.-->Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
+Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the fitness landscape [@Arnold2003].
+To account for the nonindependence of clutch size (measured at gall level) and oviposition preference (measured at plant level) as well as any independent effects of willow genotype on larval survival, we modelled gall identity nested within plant identity nested within genotype identity as random effects.
 Although statistical models with random effects are not common in analyses of natural selection, we think that modelling random effects can mitigate biased estimates of selection due to environmental covariances between traits and fitness [@Rausher1992].
-Since our end goal was to characterize the relationship between mean trait values and mean fitness (**fitness** landscape), we assumed the mean value of our random effects (i.e.
+Since our end goal was to characterize the relationship between mean trait values and mean fitness (fitness landscape), we assumed the mean value of our random effects (i.e.
 setting them to zero) when calculating selection surfaces.
@@
 **Selection gradients**: Selection gradients cannot be estimated directly from GLMMs of selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the **previously described binomial** model measure the change in the **log-odds** of surviving (i.e.
-$\text{ln}\{W(z)/[1-W(z)]\}$) associated with 1 SD change in a trait with all other traits held fixed at their mean.
+For example, the coefficients in the previously described binomial model measure the change in the log-odds of survival <!--(i.e.
+$\text{ln}\{W(z)/[1-W(z)]\}$)-->associated with 1 SD change in a trait with all other traits held fixed at their mean.
 Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlational ($\gamma_{ij}$) selection gradients.
@@
 $\alpha_i$, $\alpha_{ii}$, or $\alpha_{ij}$).
-We then divided this average gradient by the mean fitness ($\bar W$) to put it on the scale of relative fitness, and thus interpretable as a selection gradient.
+We then divided this average gradient by the mean fitness ($\bar W$) to put it on the scale of relative fitness ($w=W/\bar W$), and thus interpretable as a selection gradient.
 We estimated selection gradients separately for each food-web treatment.
@@
 
-**Selective constraints**: <!--We measured evolutionary constraints by inspecting the slope and curvature of the adaptive landscape.
--->The number of selective constraints is determined by the slope of the **fitness** landscape, which in our study corresponds to:
+**Evolutionary trajectory**: The effect of selection on the trajectory of evolution is determined by the slope of the fitness landscape, which in our study corresponds to:
 
@@
 where each $\beta_i$ corresponds to the directional selection gradient acting on each trait.
-By comparing the number of directional selection gradients that show clear evidence of contributing to the slope (i.e.
-95%  CI does not overlap zero) in our food-web treatments, we can infer the effect of food-web structure on \textbf{the number of} selective constraints.
-<!--This gives insight as to whether there is a specific combination of phenotypes favored by natural selection (i.e.
-more traits under directional selection), or whether multiple trait combinations have comparable fitness (i.e.
-less traits under directional selection).-->
+By comparing which directional selection gradients show clear evidence of contributing to the slope in each food-web treatment (i.e.
+95%  CI does not overlap zero), we can infer the effect of food-web structure on the trajectory of phenotypic evolution.
 
-**Genetic constraints**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\boldsymbol{\text{C}})\text{G}$) are governed by the curvature of the **fitness** landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
+**Evolutionary potential**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\boldsymbol{\text{C}})\text{G}$) are governed by the curvature of the fitness landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 
@@
 Note that we ommitted the upper triangle of each matrix for clarity since it is simply the reflection of the lower triangle.
-Subtracting these two matrices results in the curvature matrix of the **fitness** landscape:
+Subtracting these two matrices results in the curvature matrix of the fitness landscape:
 
@@
 where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
-<!--In other words, the sign of diagonal terms of the curvature matrix dictate whether selection will increase (+), decrease (-), or cause no change (0) in the additive genetic variance of a trait.
-Similarly, any nonzero covariance terms (off-diagonal) indicate the effects of selection on additive genetic covariance between two traits.
--->We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI.
+We used bootstrapped values of each selection gradient to estimate the curvature of each component of the matrix and its associated 95% CI.
 We also used this information to determine whether the curvature of each component differed between our food-web treatments.
 
-Knowledge of the curvature matrix alone gives an incomplete picture of its indirect effect on genetic constraints.
-This is because genetic constraints are ultimately determined by the structure of the G-matrix, and therefore also depend on its structure before selection.
+Knowledge of the curvature matrix alone gives an incomplete picture of its indirect effect on evolutionary potential.
+This is because the evolutionary potential of a population is ultimately determined by the structure of its G-matrix, and therefore also depends on its structure before selection.
 Although we do not know the underlying G-matrix for the traits we measured in this experiment, we can still gain insight to how our food-web treatment would alter genetic constraints more generally.
@@
 
-The G-matrix itself is a complex structure, but has a clear theoretical link to the evolvability of phenotypic traits [@Hansen2008].
-<!--We used evolvability as our measure of genetic constraint, as it has a solid foundation in theory of quantitative genetics and adaptive landscapes [@Hansen2008].
--->Evolvability measures the ability for a trait to evolve toward a given direction of selection [@Hansen2008].
-In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can compute its average evolvability over random **directional** selection gradients [@Hansen2008; @Melo2015].
+The G-matrix itself is a complex structure, but has a clear theoretical link to the evolutionary potential, or evolvability of phenotypic traits [@Hansen2008].
+Evolvability measures the ability for a trait to evolve toward a given direction of selection [@Hansen2008].
+In the absence of knowledge about the direction of selection that a population will actually experience in the next generation, we can compute its average evolvability over random directional selection gradients [@Hansen2008; @Melo2015].
 By computing the average evolvability (here, we used `r n_random_gradients` random $\beta$s) for each of `r n_Gmats` random G-matrices, we can then assess how changes in the curvature matrix alter the evolutionary potential of the associated traits.
 We report the distribution of these effect sizes, rather than conduct a statistical test, because the number of replicates in a simulation can be arbitrarily high, thus making any effect size statistically significant [@White2014].
-
-<!--
-Therefore, we can infer the number of genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-For these analyses, we retained estimates for selection gradients that showed clear evidence of being different from zero (i.e., 95% CI did not overlap zero) and set other gradients to zero, prior to calculating the curvature matrix in each food-web treatment.
-This provides a conservative estimate of the factors contributing to the curvature of the adaptive landscape.
-
-Note that our metrics of selective and genetic constraints do not put much stock in differences in the magnitude of selection between food-web treatments.
-This is because there is a high likelihood that we are underestimating the magnitude of selection in our treatment that excludes larval parasitoids.
-We expect this because larval parasitoids not only impose mortality on gall midges, but egg parasitoids as well (fig.
-\ref{fig:Conceptual}).
-Therefore, our short-term removal of larval parasitoids has not allowed for an increase in egg parasitoid abundance after being released from intraguild predation.
-An increase in the abundance of egg parasitoids would decrease mean survival of gall midges, thus increasing the variance in relative fitness of midges, and consequently the magnitude of selection estimates.
-A recent paper by @Hunter2018 highlights this pervasive effect of survival on the magnitude of selection estimates.<!--Therefore, we expect the magnitude of selection reflects a transient dynamic that would change over time.--><!-- This is why we use more qualitative metrics of evolutionary constraints (i.e., selective constraints = number of traits under directional selection; genetic constraints = number of decreasing variances + nonzero covariances).-->
 
@@
 To estimate this potential bias, we subset our data to only include galls where there was variation in larval survival within the same gall (i.e.
-1 > **survival** > 0).
+1 > survival > 0).
 If we assume that larvae within each gall should have similar chamber diameters because they come from the same clutch and experience the same local environment (an assumption our data supports: gall ID explains 54% of the variance in chamber diameter), then the relationship between chamber diameter and larval survival in this data subset represents the effect of parasitism on trait expression (i.e.
@@
 Using the same models as described above, we substituted egg parasitism as our response variable to quantify selection surfaces and selection gradients acting on the egg parasitoid.
-Note that we cannot test the effect of food-web structure on the egg parasitoid's **fitness** landscape ---we can only estimate selection imposed by larval parasitoids.
+Note that we cannot test the effect of food-web structure on the egg parasitoid's fitness landscape ---we can only estimate selection imposed by larval parasitoids.
 This comparison is still useful though in determining the extent to which the loss of consumers may have indirect evolutionary effects by altering selection on multiple interacting populations.
@@
 Unless otherwise noted, we report mean estimates of selection surfaces and selection gradients with 95% confidence intervals in brackets.
-Note that for visualizing the **fitness** landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
-This emphasizes the fact that we can only reliably estimate the shape of the **fitness** landscape near the mean phenotype of the population [@Arnold2001].
-We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the **fitness** landscape [@Arnold2003].
+Note that for visualizing the fitness landscape we restrict trait axes to $\pm 1$ SD of the mean trait value.
+This emphasizes the fact that we can only reliably estimate the shape of the fitness landscape near the mean phenotype of the population [@Arnold2001].
+We also plot mean larval survival on a natural log scale to accurately reflect the mathematical definition of the fitness landscape [@Arnold2003].
 All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
@@
 
-## Consumer removal increases selective constraints
+## Consumer removal constrains the evolutionary trajectory of gall midges
 
@@
 Still, there was no clear evidence of directional selection on oviposition in the original food web (table \ref{Table:Gradients}).
-<!--This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), and thus a less than additive effect on gall midges.-->Chamber diameter experienced positive directional selection in both food-web treatments (fig.
+Chamber diameter experienced positive directional selection in both food-web treatments (fig.
 \ref{fig:UV_Landscape}C).
-Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival <!--(selection surfaces: original $\alpha_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.high,2)`]; extinction $\alpha_{\text{Diam}}$=
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`])-->
+Although the magnitude of selection on chamber diameter was relatively higher in the original food web (table \ref{Table:Gradients}), this was not due to any difference in the relationship between chamber diameter and survival
 (selection surfaces: contrast $\alpha_{\text{Diam}}$=
@@
 [`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`,
-`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`]), but was simply a consequence of the (expected) lower survival of gall midges in the original food web <!--(original $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="(Intercept)")$conf.high,2)`]; extinction $\bar W$=
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$mean,2)` 
-[`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="(Intercept)")$conf.high,2)`])-->
+`r -1*round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`]), but was simply a consequence of the (expected) lower survival of gall midges in the original food web 
 (contrast $\bar W$=
@@
 It is worth noting that positive selection on chamber diameter in both treatments was unexpected.
-For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is **either directly related to survival** or strongly correlated with an unmeasured trait that is under selection (e.g.
-immune response).<!-- but selection was `r round(((filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean - filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) / filter(tidy_foodweb_grads, type=="Extinction", term=="sc.Diam")$mean) * 100, 0)`% higher in complex food webs (table \ref{Table:Gradients}; fig.
-\ref{fig:UV_Landscape}).
-This was not due to any difference between egg and larval parasitoids ($\beta_{\text{Diam}}$ contrast =
-`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(-1*filter(tidy_egglarval_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`]), but was due to the lower average survival in complex food webs ($\bar W$ contrast `r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$mean, 2)`
-[`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.low, 2)`,
-`r round(-1*filter(tidy_foodweb_alphas, type=="Diff", term=="(Intercept)")$conf.high, 2)`]).-->
+For example, the fact that larger galls provide more of a refuge from larval parasitoids makes sense since they attack after the gall is formed; however, egg parasitoids attack prior to gall formation, which suggests that chamber diameter is either directly related to survival or strongly correlated with an unmeasured trait that is under selection (e.g.
+immune response).
 
@@
 
-To visualize the multivariate effects of these selective constraints, we plotted the **fitness** landscape for each trait combination in each treatment (fig.
+To visualize the multivariate effects of natural selection, we plotted the fitness landscape for each trait combination in each treatment (fig.
 \ref{fig:MV_Landscape}).
 The arrows in fig.
-\ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while **the dotted lines** represent predicted survival of the mean phenotype in each food-web treatment.
-Notice that arrows point more toward a corner of the **fitness** landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
+\ref{fig:MV_Landscape} represent mean estimates of directional selection gradients, while the dotted lines represent predicted survival of the mean phenotype in each food-web treatment.
+Notice that arrows point more toward a corner of the fitness landscape for each combination of traits with the removal of larval parasitoids compared to the original food web.
 This indicates that the removal of consumers more strongly favored a specific combination of traits, rather than allowing for multiple trait combinations to have comparable fitness.
@@
 
-## Consumer removal indirectly increases genetic constraints
+## Consumer removal constrains the evolutionary potential of gall midges
 
-\indent The curvature of the **fitness** landscape indirectly affects genetic constraints and is influenced by directional, quadratic, and correlational selection gradients.
+\indent The curvature of the fitness landscape indirectly affects evolutionary potential and is influenced by directional, quadratic, and correlational selection gradients.
 There was no clear evidence of correlational selection for any combination of traits in either food-web treatment (table \ref{Table:Gradients}).
@@
 \ref{fig:UV_Landscape}B).
-This nonlinear
-<!--The negative relationship between oviposition preference and larval survival dampened at high densities in the original food web, but not with the removal of larval parasitoids (fig.
-\ref{fig:UV_Landscape}B).
-This dampened--> relationship was partly due to a trend for disruptive<!--nonlinear--> selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
+This nonlinear relationship was partly due to a trend for disruptive selection imposed by larval parasitoids ($\gamma_{\text{Pref:Pref}}$=
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` 
@@
 `r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`]), but was also magnified by the lower average survival in the original food web.
-This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), which would act to increase the relative fitness of gall midges.<!--, and thus a less than additive effect on gall midges.-->
+This was likely a result of larval parasitoids imposing greater mortality on egg parasitoids at high gall midge densities (see **Selection on egg parasitoids** section), which would act to increase the relative fitness of gall midges at high densities.
 
-Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the **fitness** landscape in each food-web treatment.
+Using our estimates of directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlation selection ($\gamma_{ij}$), we calculated the curvature ($\text{C}=\gamma - \beta \beta^\text{T}$) of the fitness landscape in each food-web treatment.
 
@@
 
-Interestingly, when we translate the effect of the curvature matrix onto genetic constraints in the next generation, we see that the removal of consumers had a general tendency to decrease evolvability (fig.
+Interestingly, when we translate the effect of the curvature matrix onto evolutionary potential in the next generation, we see that the removal of consumers had a general tendency to decrease evolvability (fig.
 \ref{fig:Evolvability}).
@@
 
-<!--In our study, this corresponds to:
-
-$$\textbf{Curvature} = \begin{pmatrix} \gamma_{\text{Diam:Diam}}&& \\ \gamma_{\text{Clutch:Diam}}&\gamma_{\text{Clutch:Clutch}}& \\ \gamma_{\text{Pref:Diam}} & \gamma_{\text{Pref:Clutch}} &\gamma_{\text{Pref:Pref}} \end{pmatrix} - \begin{pmatrix} \beta_{\text{Diam}}\beta_{\text{Diam}}&& \\ \beta_{\text{Clutch}}\beta_{\text{Diam}}&\beta_{\text{Clutch}}\beta_{\text{Clutch}}& \\ \beta_{\text{Pref}}\beta_{\text{Diam}} & \beta_{\text{Pref}}\beta_{\text{Clutch}} &\beta_{\text{Pref}}\beta_{\text{Pref}} \end{pmatrix}$$
-
-$$\textbf{Curvature} = \begin{pmatrix} \text{C}_{\text{Diam:Diam}}&& \\ \text{C}_{\text{Clutch:Diam}} & \text{C}_{\text{Clutch:Clutch}} & \\ \text{C}_{\text{Pref:Diam}} & \text{C}_{\text{Pref:Clutch}} & \text{C}_{\text{Pref:Pref}} \end{pmatrix}$$
-\bigskip
-
-where each $\text{C}_{ii}$ (diagonal) represents the effect of selection on the additive genetic variance in a trait, and each $\text{C}_{ij}$ (off-diagonal) represents the effect of selection on the additive genetic covariance between a particular trait combination.
-In order to obtain a conservative estimate of the factors contributing to the curvature, we only used estimates of selection that clearly differed from zero (bold values in table \ref{Table:Gradients}), otherwise we set estimates of selection to zero (non-bold values in table \ref{Table:Gradients}) prior to our calculation.
-We found that the curvatures of the adaptive landscape exhibited the following structures:
-
-$$\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
-`r round(original_gammas["Diam","Diam"],2)` &  &  \\  
-`r round(original_gammas["Clutch","Diam"],2)` & `r round(original_gammas["Clutch","Clutch"],2)` &  \\  
-`r round(original_gammas["Pref","Diam"],2)` & `r round(original_gammas["Pref","Clutch"],2)` & `r round(original_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
-`r round(original_betas["Diam",],2)`\cdot`r round(original_betas["Diam",],2)` &  &  \\  
-`r round(original_betas["Clutch",],2)`\cdot`r round(original_betas["Diam",],2)` & `r round(original_betas["Clutch",],2)`\cdot`r round(original_betas["Clutch",],2)` &  \\  
-`r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Diam",],2)` & `r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Clutch",],2)` & `r round(original_betas["Pref",],2)`\cdot`r round(original_betas["Pref",],2)` \end{pmatrix}$$
-
-$$\textbf{Curvature}_{\text{original}} = \begin{pmatrix} 
-`r round(original_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(original_curvature["Clutch","Diam"],2)` & `r round(original_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(original_curvature["Pref","Diam"],2)` & `r round(original_curvature["Pref","Clutch"],2)` & `r round(original_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-$$\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
-`r round(extinction_gammas["Diam","Diam"],2)` &  &  \\  
-`r round(extinction_gammas["Clutch","Diam"],2)` & `r round(extinction_gammas["Clutch","Clutch"],2)` &  \\  
-`r round(extinction_gammas["Pref","Diam"],2)` & `r round(extinction_gammas["Pref","Clutch"],2)` & `r round(extinction_gammas["Pref","Pref"],2)` \end{pmatrix} - \begin{pmatrix} 
-`r round(extinction_betas["Diam",],2)`\cdot`r round(extinction_betas["Diam",],2)` &  &  \\  
-`r round(extinction_betas["Clutch",],2)`\cdot`r round(extinction_betas["Diam",],2)` & `r round(extinction_betas["Clutch",],2)`\cdot`r round(extinction_betas["Clutch",],2)` &  \\  
-`r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Diam",],2)` & `r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Clutch",],2)` & `r round(extinction_betas["Pref",],2)`\cdot`r round(extinction_betas["Pref",],2)` \end{pmatrix}$$
-
-$$\textbf{Curvature}_{\text{extinction}} = \begin{pmatrix} 
-`r round(extinction_curvature["Diam","Diam"],2)` &  &  \\  
-`r round(extinction_curvature["Clutch","Diam"],2)` & `r round(extinction_curvature["Clutch","Clutch"],2)` &  \\  
-`r round(extinction_curvature["Pref","Diam"],2)` & `r round(extinction_curvature["Pref","Clutch"],2)` & `r round(extinction_curvature["Pref","Pref"],2)` \end{pmatrix}$$
-
-Remember that we can infer the indirect effects of selection on genetic constraints by summing the number of negative signs along the diagonal (decrease in additive genetic variance) and the number of nonzero terms along the off-diagonal (trait integration) of the curvature matrix.
-The structure of these matrices indicates that the extinction of larval parasitoids increased the number of genetic constraints on gall midges (6 of 6) relative to the original food web (1 of 6).
-For example, directional selection resulting from the exclusion of larval parasitoids acted to decrease genetic variance for all three phenotypic traits (negative diagonal terms), whereas only one trait (chamber diameter) experienced a decrease in additive genetic variance in the original food web.
-For genetic covariances, the combined effects of directional selection resulting from consumer extinctions favored integration among all three phenotypic traits (nonzero off-diagonal terms), and thus constraints along all three axes of covariance (fig.
-\ref{fig:MV_Landscape}).
-In contrast, the absence of directional selection in clutch size and oviposition preference did not promote trait integration along any axis in the original food web (fig.
-\ref{fig:MV_Landscape}).
--->
 \bigskip
@@
 \ref{fig:EggPtoid_Selection}).
-**This may indicate that larval parasitoids switch to target galls that have been parasitized by an egg parasitoid once egg parasitoid densities are high enough.
-This prey switching behavior would contribute to the disruptive selection we observed on gall midge preference (fig.
-\ref{fig:UV_Landscape}B).**
+This may indicate that larval parasitoids switch to target galls that have been parasitized by an egg parasitoid once egg parasitoid densities are high enough.
+This prey switching behavior would contribute to the disruptive selection we observed on gall midge preference by increasing the relative fitness of gall midges at high densities (fig.
+\ref{fig:UV_Landscape}B).
 
@@
 We found that the removal of larval parasitoids constrained phenotypic evolution in gall midges in two key ways.
-First, **we observed directional selection on more traits** in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.<!--First, more traits contributed to the slope of the **fitness** landscape in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.--> Second, removing larval parasitoids altered the curvature of the **fitness** landscape in such a way that tended to decrease the evolvability of associated traits.
-Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's **fitness** potential in the face of novel selection pressures.
+First, we observed directional selection on more traits in the absence of larval parasitoids, suggesting greater constraints on the trajectory of phenotypic evolution.
+Second, removing larval parasitoids altered the curvature of the fitness landscape in such a way that tended to decrease the evolvability of associated traits.
+Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's fitness potential in the face of novel selection pressures.
 Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
-Taken together, our study provides experimental evidence from the field that the loss of consumers may constrain the **fitness** potential of remaining populations.
+Taken together, our study provides experimental evidence from the field that the loss of consumers may constrain the adaptive potential of remaining populations.
 
-<!--Selective constraints
-All three phenotypic traits we examined experienced directional selection when we excluded larval parasitoids, indicating that there is an optimal phenotype that maximizes larval survival (i.e.
-large chamber diameter, small clutch size, and avoidance of conspecifics).
-In contrast, we did not observe clear evidence of selective constraints on clutch size and oviposition preference in the original food web.
-This suggests that there are many optimal phenotypes (adaptive peaks), or in this case, a flat adaptive landscape where there are no fitness consequences for phenotypic change in these traits.
-<!-- need to see if I can salvage this, because as the editor points out, it is not exactly true.-->
-<!--This also implies that as selective constraints dampen in food webs with more consumers, then the trajectory of evolution becomes more determined by how the genetic architecture of traits (G-matrix) interacts with other evolutionary processes (e.g.
-genetic drift, gene flow, and mutation).<!-- This is made clear if we inspect the 'Lande equation', $\Delta z = \text{G} \beta$, where G corresponds to the population's G-matrix.
-As the components of $\beta$ go to zero, then $\Delta z$ is more influenced by the G-matrix.
-[Removing because this statement is simply not true]-->
-<!--Interestingly, this aligns with @Schluter1996's hypothesis that phenotypic evolution often follows 'genetic lines of least resistance'.
-@Schluter1996 found support for this hypothesis from data on natural populations of several vertebrate species, including threespine sticklebacks, a few species of songbirds, and mice from the genus *Peromyscus*.
-All of these species occupy intermediate trophic levels and are likely embedded in complex food webs, which is consistent with our suggestion that genetic constraints may have a stronger influence in food webs with more consumers.
--->
 <!-- Generality of results -->
@@
 When consumers are functionally different and abundant though, the effect of consumer loss will depend on whether different consumers impose conflicting selection pressures or select for distinct traits.
-When consumers impose conflicting selection on traits, as in our study and others [@Weis1985; @Abrahamson1997; @Start2016; @Start2018], then consumer diversity acts to neutralize selection, **which can maintain larger evolvability.**<!--and relax selective constraints.<!-- For example, parisitoids and birds impose conflicting selection pressures on the size of galls induced by the fly *Eurosta solidaginis* [@Weis1985; @Abrahamson1997].
-Recent studies in this system have shown that decreases in the relative abundance of birds, due to either small patch sizes [@Start2016] or proximity to urban areas [@Start2018] causes a shift from neutral to directional selection on gall size.--> On the other hand, different consumers may impose selection on different traits; therefore, a more diverse consumer community may favor a particular combination of traits and increase selective constraints.
+When consumers impose conflicting selection on traits, as in our study and others [@Weis1985; @Abrahamson1997; @Start2016; @Start2018], then consumer diversity acts to neutralize selection, which can maintain larger evolvability.
+On the other hand, different consumers may impose selection on different traits; therefore, a more diverse consumer community may favor a particular combination of traits and increase selective constraints.
 Examples of this include strong genetic covariances in plant resistance to different insect herbivores [@Maddox1990; @Wise2007; @Wise2013], although there are also examples where these covariances are weak [@Roche1997; @Barbour2015], or vary from year-to-year [@Johnson2007].
 We suggest that gaining predictive insight to the evolutionary consequences of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions [@Bascompte2009].
-<!--We suggest that gaining predictive insight to the effects of food-web disassembly requires an understanding of the mechanisms governing the assembly of trophic interactions.-->
 
 <!--Indirect effects of selective constraints-->
-We also found evidence for a general decrease in trait evolvability when we excluded larval parasitoids due to changes in the curvature of the **fitness** landscape<!--indirect effects of selection on the population's G-matrix-->.
-This result was driven by **disruptive**<!--nonlinear--> selection on gall midge oviposition preference in the original food web, which was likely due to both increases in intraguild predation **on egg parasitoids (i.e.
-prey switching)** and the lower mean survival of gall midges.
-**This pattern of selection acts to increase genetic variation in oviposition preference, which in turn enhances the ability of the gall midge population to respond to uncertain selection pressures in the next generation (i.e.
+We also found evidence for a general decrease in trait evolvability when we excluded larval parasitoids due to changes in the curvature of the fitness landscape.
+This result was driven by disruptive selection on gall midge oviposition preference in the original food web, which was likely due to both increases in intraguild predation on egg parasitoids (i.e.
+prey switching) and the lower mean survival of gall midges.
+This pattern of selection acts to increase genetic variation in oviposition preference, which in turn enhances the ability of the gall midge population to respond to uncertain selection pressures in the next generation (i.e.
 evolvability).
@@
 mean oviposition preference) select for different phenotypes of the same species in similar environments [@Landi2018LifeHistory].
-Thus, this pattern of selection may contribute to genetic and phenotypic diversity both within and among populations.** Current theory, however, often assumes genetic variances and covariances remain constant over time **and space** rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017; **@Medeiros2018**].
-Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that emerge in a network of interacting species.
-
-<!-- 
-Taken together, these results suggest that the loss of larval parasitoids may reduce genetic and phenotypic diversity both within and among gall midge populations.
-
-This would result in a bimodal distribution in average oviposition preference across populations.
-
-While these results are intriguing, they still indicate that the indirect effects of selection are contingent on the structure of a population's G-matrix (e.g.
-consumer removals *increased* evolvability in 29% of the scenarios).
-This highlights the importance of future studies to characterize the G-matrix in order to accurately predict how changes in network context will alter the evolutionary potential of remaining populations.
-<!--The ability of a population to adapt to novel selection pressures (evolvability) is largely governed by the structure of its G-matrix [@Hansen2008].
-When selection favors genetic covariance between traits (positive or negative), this results in less autonomy of evolutionary responses to changing environments.
-Similarly, decreases in genetic variance constrain potential for the trait itself to evolve.
-Together, this suggests that consumer extinctions may decrease the evolutionary potential of populations by indirectly selecting for decreases in genetic variance in multiple traits and favoring trait integration.
-Indeed, current theory often assumes genetic variances and covariances remain constant over time rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017].
+Thus, this pattern of selection may contribute to genetic and phenotypic diversity both within and among populations.
+Current theory, however, often assumes genetic variances and covariances remain constant over time and space rather than dynamically changing with the network context [@McPeek2017; @Guimaraes2017; @Medeiros2018].
 Our empirical results highlight the need to explore the evolutionary consequences of not only direct effects of selection, but indirect effects on genetic constraints that emerge in a network of interacting species.
@@
 For example, we see clear evidence of all three traits being under directional selection (i.e.
-greater selective constraints, table S2) as well as a decrease, albeit smaller, in trait evolvability under different G-matrix scenarios (`r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`%, fig.
+greater constraints on the trajectory of evolution, table S2) as well as a decrease, albeit smaller, in trait evolvability under different G-matrix scenarios (`r round(sum(larvalptoid_random_evolvabilities$Diff < 0) / length(larvalptoid_random_evolvabilities$Diff) * 100,0)`%, fig.
 S1).
@@
 
-Another possible caveat is that our manipulation may represent a perturbation to the shape of the fitness landscape, rather than the effects of losing a consumer guild *per se*.
-This is because the fitness landscape we are only able to infer the shape of the fitness landscape near the mean phenotype of the population, rather than its shape after being exposed to many generations of selection by the removal treatment.
-This is a weakness of virtually all field studies of natural selection, although it may be circumvented through experimental evolution [e.g.
-@Betts2018].
+<!--Second, our manipulation of food-web structure may simply represent a perturbation to the shape of the fitness landscape, rather than the effects of losing a consumer guild *per se*.
+This is because we are only able to infer the shape of the fitness landscape near the mean phenotype of the population, rather than its shape after being exposed to many generations of selection by the removal treatment.
+This is a caveat for virtually all field studies of natural selection, although it may be circumvented through experimental evolution [e.g.
+@Betts2018].-->
 
@@
 This release occurs more on trees with high larval densities, which could intensify future selection on gall midge oviposition preference.
-**This suggests that the loss of larval parasitoids would likely impose even greater constraints on the trajectory of evolution than what we estimated in our study.
-However, while this may intensify selection toward gall midges to avoid conspecifics, this may actually relax selection imposed by gall midges on the plant, due to plants having lower gall densities.**  A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in ecological communities [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
+This suggests that the loss of larval parasitoids would likely impose even greater constraints on the trajectory of evolution than our current estimates indicate.
+Interestingly, this increase in the strength of selection on gall midges may reduce their densities, which would weaken selection imposed on willows by the gall midge through an evolutionary trophic cascade.
+A growing number of experiments over the past two decades have demonstrated the presence and potential importance of indirect evolutionary effects that emerge in ecological communities [@Pilson1996; @Juenger1998; @Stinchcombe2001; @Lankau2007; @Walsh2008; @Walsh2010; @terHorst2010; @Sahli2011; @Lau2012; @terHorst2015; @Schiestl2018; @Start2019].
 If indirect evolutionary effects are common [@Miller1996; @Walsh2013; @Guimaraes2017], then predicting evolutionary trajectories resulting from the loss of consumers will require evolutionary studies to explicitly account for the ecological networks that species are embedded in.
 
-<!-- Community context shaping adaptation to environmental change
-There is a growing number of theoretical studies on adaptation to directional environmental change that incorporate species interactions [e.g.
-@deMazancourt2008; @Johansson2008; @Norberg2012; @Osmond2017PredatorsHelpPrey].
-This work has given insight to the mechanisms by which interactions between species can modify their adaptive potential<!--pairwise interactions modify the adaptive potential of species--><!--.
-Our study hints at a novel mechanism, whereby a more diverse consumer community alters the adaptive landscape in such a way that facilitates future adaptation by allowing genetic and phenotypic variation to persist.
-This mechanism only emerges once we consider selection imposed by multiple species on multiple traits.
-<!--move beyond pairwise interactions to consider selection on multiple traits in a community context.--><!--However, a study on competition has highlighted that we may expect the opposite effect of species diversity in competitive communities [@deMazancourt2008].
-This negative effect of species diversity on adaptation occurs because there is a greater chance that the optimal phenotype is already occupied by a competitor in a more diverse community.
-More work is needed to examine how the distribution of different interaction types affects adaptation to environmental change in species-rich communities.
---> 
-<!-- Caveats 
-Our study has some limitations to consider when relating our findings to the effect of consumer extinctions on evolutionary constraints more generally.
-First, we removed other sources of mortality prior to our analyses.
-While this was necessary to avoid confounding estimates of selection with effects on phenotypic expression, we may be overestimating the effects of selection due to consumers.
-Second, our metrics of evolutionary constraints do not account for variation in the magnitude of selection pressures.
-While metrics that incorporate the magnitude of selection are possible [@Hansen2008], they were not appropriate for our study as our experimental removal of larval parasitoids artificially increased the mean fitness of gall midges (in the short term), which dampens the magnitude of selection gradients in this treatment [@Hunter2018].
-This is why we used more qualitative metrics of evolutionary constraints, which are robust to this artificial effect and simply require sufficient sample sizes to detect evidence of selection.
--->
-<!--Note though that this should have made it more difficult to detect selection in this treatment, yet it was this extinction treatment that increased the number of traits under selection.
-<!--results in a transient dynamic in the strength (but not direction) of selection.
-Such transient dynamics may be common in short-term experimental studies of natural selection, but they can be detected by using natural history information and dissecting the sources of selection (e.g.
-quantifying selection surfaces and treatment effects on mean fitness) as we did here.
--->
-
 <!-- Conclusions -->
-Our study gives insight to how the loss of consumers alters **natural selection, and in turn** evolutionary constraints on remaining populations.
+Our study gives insight to how the loss of consumers alters natural selection, and in turn the trajectory and evolutionary potential of remaining populations.
 In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.
 Our work also highlights some key challenges for predicting phenotypic evolution in rapidly changing communities.
-<!--First, the simplification of ecological communities may increase selective constraints, requiring knowledge of genetic variances and covariances of multiple traits to accurately predict evolutionary change.--><!--actually reduce the predictability of phenotypic evolution, because knowledge is required of both selective and genetic constraints, rather than potentially just genetic constraints in more complex systems.-->For example, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait [but see @Brown2007; @Leimar2009], yet our results highlight that the number of traits under selection may change with the network context.
+For example, many theoretical models of eco-evolutionary dynamics focus on phenotypic change in a single trait [but see @Brown2007; @Leimar2009], yet our results highlight that the number of traits under selection may change with the network context.
 Importantly, we found that different species/guilds imposed different selection pressures.
 Knowing these hidden selection pressures is critical for prediction, because the trajectory of evolution will depend on the nature of change in the ecological community.
-We expect that a continued integration of **fitness** landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
+We expect that a continued integration of fitness landscapes and ecological networks will enhance our ability to predict the evolutionary consequences of changes in ecological communities.
 
@@
 For assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
+This manuscript was improved by incorporating feedback from two anonymous reviewers.
 For funding support, we thank the University of British Columbia (James Robert Thompson Fellowship and Four-Year Fellowship to M.A.
@@
 All data and code to reproduce the reported results are publicly available on GitHub (https://github.com/mabarbour/complexity_selection) and have been archived on Zenodo (https://zenodo.org/badge/latestdoi/108833263).
-
-<!-- TABLE NOT REFERENCED IN RESULTS
-
-\begin{table}[h]
-\caption{Relationship between absolute fitness (larval survival) and phenotypic traits of gall midges in complex vs. simple food webs.}
-\label{Table:Coefs}
-\centering
-\begin{tabular}{lccc}
-\\ 
-\hline
-\textbf{Coefficient} & \textbf{Original} & \textbf{Extinction} & \textbf{Contrast}  \\ 
-\hline
-$\alpha_{\text{Diam}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam")$conf.high,2)`] }& 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
-
-$\alpha_{\text{Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch")$conf.high,2)`] }& 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] }\\
-
-$\alpha_{\text{Pref}}$ &
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.sqrt.Pref")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\alpha_{\text{Diam,Diam}}$ &
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\alpha_{\text{Clutch,Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\alpha_{\text{Pref,Pref}}$ & 
-\textbf{
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\
-
-$\alpha_{\text{Diam,Clutch}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\alpha_{\text{Diam,Pref}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\alpha_{\text{Clutch,Pref}}$ & 
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Extinction", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_foodweb_alphas, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\alpha_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-# Appendix A
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients acting on egg parasitoids (\textit{Platygaster} sp.)}
-\label{Table:ExtendedGradients}
-\centering
-\begin{tabular}{lc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Contrast = Original - Removal}  \\ 
-\hline
-$\beta_{\text{Diam}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam")$conf.high,2)`] \\
-
-$\beta_{\text{Clutch}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch")$conf.high,2)`] \\
-
-$\beta_{\text{Pref}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.Diam^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Clutch}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Pref:Pref}}$ &
-
-\textbf{
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }\\
-
-$\gamma_{\text{Diam:Clutch}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Pref}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] \\
-
-$\gamma_{\text{Clutch:Pref}}$ &
-
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_eggegg_grads, type=="Diff", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-\bigskip
-
-\begin{table}[h]
-\caption{Standardized selection gradients imposed by larval parasitoids on gall midges in the original food web.
-This gives insight to selection acting on gall midges in the absence of the dominant egg parasitoid.}
-\label{Table:LarvalGradients}
-\centering
-\begin{tabular}{lc}
-\\ 
-\hline
-\textbf{Selection gradient} & \textbf{Larval Parasitoids} \\ % & \textbf{Original} 
-\hline
-$\beta_{\text{Diam}}$ & 
-%\textbf{
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } & 
-\textbf{
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam")$conf.high,2)`] } \\
-
-$\beta_{\text{Clutch}}$ & 
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch")$conf.high,2)`] }\\
-
-$\beta_{\text{Pref}}$ &
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] & 
-\textbf{
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.sqrt.Pref")$conf.high,2)`] } \\
-
-$\gamma_{\text{Diam:Diam}}$ &
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.Diam^2)")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.Diam^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.Diam^2)")$conf.high,2)`]  \\
-
-$\gamma_{\text{Clutch:Clutch}}$ & 
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] &
-
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.log.Clutch^2)")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.log.Clutch^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Pref:Pref}}$ & 
-%\textbf{
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] }&
-
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="I(sc.sqrt.Pref^2)")$conf.high,2)`] \\
-
-$\gamma_{\text{Diam:Clutch}}$ & 
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`] &
-
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.log.Clutch")$conf.high,2)`]  \\
-
-$\gamma_{\text{Diam:Pref}}$ & 
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.Diam:sc.sqrt.Pref")$conf.high,2)`]  \\
-
-$\gamma_{\text{Clutch:Pref}}$ & 
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-%`r round(filter(tidy_foodweb_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`] &
-
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$mean,2)` [
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.low,2)`,
-`r round(filter(tidy_egglarval_grads, type=="Original", term=="sc.log.Clutch:sc.sqrt.Pref")$conf.high,2)`]  \\ 
-\hline
-\end{tabular}
-\bigskip{}
-\\
-{\footnotesize Note: Values in brackets represent 95\% confidence intervals. Bold values indicate that the 95\% CI does not overlap zero. $\beta_{\text{Diam}}$ has been adjusted for bias.}
-\end{table}
-
-```{r LarvalPtoid Evolvability, echo=FALSE, fig.pos="h", fig.cap="\\label{fig:LarvalPtoidEvolvability}Change in average evolvability for 10,000 random G-matrices using our best (mean) estimate of the curvature matrix for selection in the absence of egg parasitoids vs.
-the original food web.
-We found that the curvature imposed by the loss of egg parasitoids decreased evolvability in 57% of the G-matrices (i.e.
-the change in evolvability was negative for 57% of the simulations), which is smaller in magnitude, but in the same direction, as the effects of losing larval parasitoids."}
-knitr::include_graphics("../analyses/larvalptoid_delta_evolvability.pdf")
-```
--->

### 2020-03-11 analyses/reproduce_analyses.Rmd
update analyses for accepted version of manuscript.

@@
   scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l")+
-  coord_cartesian(ylim=c(0.07,1))
+  coord_cartesian(ylim=c(0.07,1))  +
+  theme_cowplot()
 
@@
   scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
+  coord_cartesian(ylim=c(0.07,1)) +
+  theme_cowplot()
 
@@
   scale_y_log10(breaks=uni_breaks, labels=uni_breaks) + annotation_logticks(sides = "l") +
-  coord_cartesian(ylim=c(0.07,1))
+  coord_cartesian(ylim=c(0.07,1)) +
+  theme_cowplot()
 ```
@@
   scale_fill_viridis(name = "Mean larval\nsurvival", trans="log", breaks = my_breaks, labels = my_breaks, limits = c(AF_range$min, AF_range$max)) +
+  theme_cowplot() +
   theme(strip.background = element_blank(),
@@
   xlab(expression(paste(Delta," evolvability (removal - original)"))) +
-  ylab("Count")
+  ylab("Count") +
+  theme_cowplot()
 
@@
   xlab(expression(paste(Delta," evolvability (larval parasitoids - original)"))) +
-  ylab("Count")
+  ylab("Count") +
+  theme_cowplot()
 

### 2020-03-11 manuscript/manuscript_clean.Rmd
incorporate final minor edits to accepted version.

@@
 The loss of biodiversity is altering the structure of ecological networks; however, we are currently in a poor position to predict how these altered communities will affect the evolutionary potential of remaining populations.
-Theory on fitness landscapes provides a framework for predicting how selection alters the trajectory and evolutionary potential of populations, but often treats the network of interacting populations as a ``black box''.
+Theory on fitness landscapes provides a framework for predicting how selection alters the evolutionary trajectory and adaptive potential of populations, but often treats the network of interacting populations as a ``black box''.
 Here, we integrate ecological networks and fitness landscapes to examine how changes in food-web structure shape phenotypic evolution.
@@
 The loss of biodiversity is rewiring the web of life; however, it is uncertain how this will affect the ability of remaining populations to evolve and adapt to future environments.
-To gain insight to these effects, we conducted a field experiment that either maintained a natural community of predators or removed all but one of the predators that was able to impose selection on a common prey.
+To gain insight into these effects, we conducted a field experiment that either maintained a natural community of predators or removed all but one of the predators that was able to impose selection on a common prey.
 We found that the loss of predators acted to constrain prey evolution toward a particular combination of traits.
@@
 Ecological networks, such as food webs describing who-eats-whom, provide an explicit representation of the direct and indirect effects that emerge in a community of interacting species [@Bascompte2014; @McCann2012].
-Here, we integrate ecological networks and fitness landscapes to understand how selection imposed by ecological communities alter the trajectory and evolutionary potential of interacting populations [@Hui2018].
+Here, we integrate ecological networks and fitness landscapes to understand how selection imposed by ecological communities alter the evolutionary trajectory and adaptive potential of interacting populations [@Hui2018].
 The effects of natural selection on multiple phenotypic traits can be inferred by quantifying the slope and curvature of the fitness landscape [@Arnold1992].
@@
 \ref{fig:Conceptual}).
-<!-- Omit due to Reviewer #1 comment: The relative abundance of these larval parasitoids is much lower than the egg parasitoid [@Barbour2016], and thus represents a plausible extinction scenario for this system.
-<!--While this manipulation simulates an extreme co-extinction event, the likelihood of such co-extinction events is increasing in the Anthropocene.
--->Larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid (fig.
+Larval parasitoids also impose indirect effects on gall midge fitness through intraguild predation on the egg parasitoid (fig.
 \ref{fig:Conceptual}).
 We applied modern statistical methods to quantify how changes in food-web structure altered the slope and curvature of the gall midge's fitness landscape.
-Taken together, our study gives insight to how the loss of biodiversity may alter both the trajectory and evolutionary potential of interacting populations.
+Taken together, our study gives insight to how the loss of biodiversity may alter both the evolutionary trajectory and adaptive potential of interacting populations.
 
@@
 To approximate the selection surface, we modelled larval survival as a function of food-web treatment as well as linear ($\alpha_i$), quadratic ($\alpha_{ii}$), and statistical interactions ($\alpha_{ij}$) between each trait.
-<!--Removed at Reviewer #1's suggestion because it is redundant: We also allowed these selection surfaces ($\alpha$) to vary between food-web treatments.-->Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
+Note that to obtain valid estimates of linear selection surfaces, we removed nonlinear terms prior to estimating linear relationships [@Lande1983].
 Other approaches have been advocated for approximating selection surfaces [@Schluter1988]; however, our approach enables us to calculate selection gradients, and thus is more appropriate for approximating the fitness landscape [@Arnold2003].
@@
 **Selection gradients**: Selection gradients cannot be estimated directly from GLMMs of selection surfaces because the response is in terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the previously described binomial model measure the change in the log-odds of survival <!--(i.e.
-$\text{ln}\{W(z)/[1-W(z)]\}$)-->associated with 1 SD change in a trait with all other traits held fixed at their mean.
+For example, the coefficients in the previously described binomial model measure the change in the log-odds of survival associated with 1 SD change in a trait with all other traits held fixed at their mean.
 Therefore, we used the method developed by @Janzen1998 to translate selection surfaces from the above model into the scale of relative fitness in order to calculate directional ($\beta_i$), quadratic ($\gamma_{ii}$), and correlational ($\gamma_{ij}$) selection gradients.
@@
 where each $\beta_i$ corresponds to the directional selection gradient acting on each trait.
-By comparing which directional selection gradients show clear evidence of contributing to the slope in each food-web treatment (i.e.
+By comparing selection gradients in each food-web treatment (i.e.
 95%  CI does not overlap zero), we can infer the effect of food-web structure on the trajectory of phenotypic evolution.
 
-**Evolutionary potential**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}(\boldsymbol{\text{C}})\text{G}$) are governed by the curvature of the fitness landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
+**Evolutionary potential**: The indirect effects of selection on the G-matrix ($\Delta\text{G}=\text{G}\text{C}\text{G}$) are governed by the curvature of the fitness landscape ($\text{C}=\gamma - \beta \beta^\text{T}$), which in our study corresponds to:
 
@@
 Specifically, we calculated how our best estimate of the curvature matrix (mean values) in each treatment changed the structure of `r n_Gmats` random G-matrices for the next generation.
-We restricted the range of additive genetic variance (*V~G~*) in these G-matrices to between 0 and 0.5 to reflect typical ranges in narrow-sense heritability values (*h*^2^; note that *h*^2^ = *V~G~* when the phenotypic variance is scaled to 1).
+We restricted the range of additive genetic variance (*V~G~*) for each element in these G-matrices to between 0 and 0.5 to reflect typical ranges in narrow-sense heritability values (*h*^2^; note that *h*^2^ = *V~G~* when the phenotypic variance is scaled to 1).
 Note that this analysis assumes that the effects of recombination and mutation on the G-matrix are much smaller than the effects of selection, which appears to be a reasonable assumption over short time scales [@Arnold2008].
@@
 1 > survival > 0).
-If we assume that larvae within each gall should have similar chamber diameters because they come from the same clutch and experience the same local environment (an assumption our data supports: gall ID explains 54% of the variance in chamber diameter), then the relationship between chamber diameter and larval survival in this data subset represents the effect of parasitism on trait expression (i.e.
+If we assume that larvae within each gall should have similar chamber diameters because they come from the same clutch and experience the same local environment (an assumption our data supports: gall identity explains 54% of the variance in chamber diameter), then the relationship between chamber diameter and larval survival in this data subset represents the effect of parasitism on trait expression (i.e.
 bias).
@@
 Second, removing larval parasitoids altered the curvature of the fitness landscape in such a way that tended to decrease the evolvability of associated traits.
-Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's fitness potential in the face of novel selection pressures.
+Assuming these traits have other ecological functions, then this decrease in evolvability could constrain the gall midge's adaptive potential in the face of novel selection pressures.
 Our experiment also revealed evidence of indirect selection pressures, suggesting that the loss of consumers may have complex effects on the trajectories of phenotypic evolution.
@@
 
-<!--Second, our manipulation of food-web structure may simply represent a perturbation to the shape of the fitness landscape, rather than the effects of losing a consumer guild *per se*.
-This is because we are only able to infer the shape of the fitness landscape near the mean phenotype of the population, rather than its shape after being exposed to many generations of selection by the removal treatment.
-This is a caveat for virtually all field studies of natural selection, although it may be circumvented through experimental evolution [e.g.
-@Betts2018].-->
-
 <!--Indirect evolutionary effects-->
@@
 <!-- Conclusions -->
-Our study gives insight to how the loss of consumers alters natural selection, and in turn the trajectory and evolutionary potential of remaining populations.
+Our study gives insight to how the loss of consumers alters natural selection, and in turn the evolutionary trajectory and adaptive potential of remaining populations.
 In particular, it hints at a potential insidious effect of local extinctions that compromises the robustness of remaining populations to future environmental change.

### 2020-03-11 manuscript/manuscript_clean.tex
incorporate final minor edits to accepted version.

--- 2019-09-18 manuscript/manuscript.tex
@@
 \IfFileExists{microtype.sty}{%
-\usepackage{microtype}
+\usepackage[]{microtype}
 \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
 }{}
-\usepackage{hyperref}
+\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
+\usepackage[unicode=true]{hyperref}
 \PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref
-\hypersetup{unicode=true,
+\hypersetup{
             colorlinks=true,
@@
 
-%%% Use protect on footnotes to avoid problems with footnotes in titles
-\let\rmarkdownfootnote\footnote%
-\def\footnote{\protect\rmarkdownfootnote}
-
-%%% Change title format to be more compact
-\usepackage{titling}
-
-% Create subtitle command for use in maketitle
-\providecommand{\subtitle}[1]{
-  \posttitle{
-    \begin{center}\large#1\end{center}
-    }
-}
-
-\setlength{\droptitle}{-2em}
-
-  \title{}
-    \pretitle{\vspace{\droptitle}}
-  \posttitle{}
-    \author{}
-    \preauthor{}\postauthor{}
-    \date{}
-    \predate{}\postdate{}
+% set default figure placement to htbp
+\makeatletter
+\def\fps@figure{htbp}
+\makeatother
 
@@
 
+\author{}
+\date{\vspace{-2.5em}}
+
 \begin{document}
@@
 
-\emph{Keywords}: adaptive landscape, ecological networks,
-eco-evolutionary dynamics, natural selection, host-parasitoid, community
-context, extinction.
-
-\bigskip
-
-\emph{Abstract Word Count}: 251
-
-\bigskip
-
-\emph{Total Word Count}: 5833
+\emph{Keywords}: fitness landscape, adaptive landscape, ecological
+networks, eco-evolutionary dynamics, natural selection, host-parasitoid,
+community context, extinction.
+
+\bigskip
+
+\emph{Abstract Word Count}: 256
+
+\bigskip
+
+\emph{Total Word Count}: 6119
 
@@
 these altered communities will affect the evolutionary potential of
-remaining populations. Theory on adaptive landscapes provides a
-framework for predicting how selection constrains phenotypic evolution,
-but often treats the network context of evolving populations as a
-``black box''. Here, we integrate ecological networks and adaptive
-landscapes to examine how changes in food-web structure shape
-evolutionary constraints. We conducted a field experiment that removed a
-guild of larval parasitoids that imposed direct and indirect selection
-pressures on an insect herbivore. We then measured herbivore survival as
-a function of three key phenotypic traits to estimate directional,
-quadratic, and correlational selection gradients in each treatment. We
-used these selection gradients to characterize the slope and curvature
-of the adaptive landscape to understand the direct and indirect effects
-of consumer loss on evolutionary constraints. We found that the number
-of traits under directional selection increased with the removal of
-larval parasitoids, indicating greater selective constraints on the
-trajectory of evolutionary change. Similarly, we found that the removal
-of larval parasitoids altered the curvature of the adaptive landscape in
-such a way that tended to decrease the evolvability of the traits we
-measured in the next generation. Our results suggest that the loss of
-trophic interactions can impose greater constraints on phenotypic
-evolution. This indicates that the simplification of ecological
-communities may constrain the adaptive potential of remaining
-populations to future environmental change.
+remaining populations. Theory on fitness landscapes provides a framework
+for predicting how selection alters the evolutionary trajectory and
+adaptive potential of populations, but often treats the network of
+interacting populations as a ``black box''. Here, we integrate
+ecological networks and fitness landscapes to examine how changes in
+food-web structure shape phenotypic evolution. We conducted a field
+experiment that removed a guild of larval parasitoids that imposed
+direct and indirect selection pressures on an insect herbivore. We then
+measured herbivore survival as a function of three key phenotypic traits
+to estimate directional, quadratic, and correlational selection
+gradients in each treatment. We used these selection gradients to
+characterize the slope and curvature of the fitness landscape to
+understand the direct and indirect effects of consumer loss on
+phenotypic evolution. We found that the number of traits under
+directional selection increased with the removal of larval parasitoids,
+indicating evolution was more constrained toward a specific combination
+of traits. Similarly, we found that the removal of larval parasitoids
+altered the curvature of the fitness landscape in such a way that tended
+to decrease the evolvability of the traits we measured in the next
+generation. Our results suggest that the loss of trophic interactions
+can impose greater constraints on phenotypic evolution. This indicates
+that the simplification of ecological communities may constrain the
+adaptive potential of remaining populations to future environmental
+change.
 
@@
 uncertain how this will affect the ability of remaining populations to
-evolve and adapt to future environments. To gain insight to these
+evolve and adapt to future environments. To gain insight into these
 effects, we conducted a field experiment that either maintained a
@@
 
-The adaptive landscape provides a powerful framework for understanding
+The fitness landscape provides a powerful framework for understanding
 how natural selection has shaped the evolution of biodiversity ---from
@@
 \citep{Wright1931, Simpson1944, Arnold2001}. More than a metaphor, the
-adaptive landscape links quantitative genetic and phenotypic variation
-to evolution by natural selection
-\citep{Lande1979, Arnold1984applications, Arnold1984theory}, giving
-insight to the direct and indirect effects of selective constraints
-\citep{Arnold1992}. Ecological interactions often play a key role in
-shaping selective constraints, as evidenced by the role of antagonistic
-and mutualistic interactions in driving evolutionary change
+fitness landscape links quantitative genetic and phenotypic variation in
+multiple traits to evolution by natural selection
+\citep{Lande1979, Arnold1984applications, Arnold1984theory}. Ecological
+interactions often play a key role in shaping natural selection, as
+evidenced by the role of antagonistic and mutualistic interactions in
+driving evolutionary change
 \citep{Schluter2000, Abrams2000, Bronstein2006}. Although there is clear
-evidence that species interactions can shape the adaptive landscape, we
-still have a poor understanding of how the adaptive landscape is shaped
-by a community of interacting species \citep{McPeek2017, terHorst2018}.
-Resolution on how change in ecological communities shape phenotypic
-evolution is urgently needed though, given the rapid losses of
-biodiversity we are observing in the Anthropocene \citep{Scheffers2016}.
+evidence that species interactions can shape the fitness landscape, we
+still have a poor understanding of how the fitness landscape is shaped
+by a community of interacting species
+\citep{McPeek2017, terHorst2018, Hui2018}. Resolution on how change in
+ecological communities shape phenotypic evolution is urgently needed
+though, given the rapid losses of biodiversity we are observing in the
+Anthropocene \citep{Scheffers2016}.
 
@@
 \citep{Bascompte2014, McCann2012}. Here, we integrate ecological
-networks and adaptive landscapes to understand how ecological
-communities constrain evolutionary change. The direct and indirect
-effects of natural selection can be inferred by quantifying the slope
-and curvature of the adaptive landscape \citep{Arnold1992}. For example,
-the slope is determined by directional selection gradients acting on
-each phenotypic trait and influences the trajectory of evolutionary
-change \citep{Lande1979, Arnold1992}. Selective constraints on evolution
-increase with the number of traits under directional selection, as this
-diminishes the number of optimal solutions \citep{Arnold2003}. The
-curvature of the adaptive landscape is governed by nonlinear selection
-gradients and acts to indirectly constrain evolution through its effect
-on genetic constraints \citep{Arnold1992, Hansen2008}. Genetic
-constraints are largely governed by a population's G-matrix ---the
-additive genetic variances and covariances between traits
-\citep{Hansen2008}. Stabilizing selection acts to erode genetic variance
-in traits, which can impose a constraint on the ability of those traits
-to respond to future selection \citep{Hansen2008}. Correlational
-selection may alter the genetic covariance between traits, which may
-facilitate or hinder future adaptation depending on the pattern of
-selection on those traits \citep{Hansen2008}. If we want to predict how
-ecological communities shape phenotypic evolution, we must understand
-how ecological networks shape the adaptive landscape.
+networks and fitness landscapes to understand how selection imposed by
+ecological communities alter the evolutionary trajectory and adaptive
+potential of interacting populations \citep{Hui2018}. The effects of
+natural selection on multiple phenotypic traits can be inferred by
+quantifying the slope and curvature of the fitness landscape
+\citep{Arnold1992}. The slope is determined by the strength of
+directional selection acting on each trait, which influences the
+trajectory of evolution \citep{Lande1979, Arnold1992}. This fact is made
+clear by the `Lande equation', \(\Delta\bar z = \text{G}\beta\), where
+\(\Delta \bar z\) is a column vector of the average change in each trait
+between generations, \text{G} is the additive genetic (co)variance
+matrix for these traits (i.e.~G-matrix), and \(\beta\) is a column
+vector of directional selection gradients acting on each trait
+(i.e.~slope). Grant and Grant \citeyearpar{Grant1995} used the slope of
+the fitness landscape for multiple traits related to body and beak size
+in Darwin's finches to accurately predict the effects of drought on the
+evolutionary trajectory of these traits. The curvature of the fitness
+landscape is governed by the strength of stabilizing, disruptive, and
+correlational selection acting on each trait, which can alter the
+evolutionary potential of a population through its effect on the
+G-matrix \citep{Hansen2008}. For example, stabilizing selection acts to
+erode genetic variance in a trait, which can impose a constraint on the
+ability of this trait to respond to future selection \citep{Hansen2008}.
+In contrast, disruptive selection toward extreme trait values acts to
+increase genetic variance in a trait, thus increasing the capacity for
+future adaptation \citep{Bolnick2008}. Correlational selection alters
+the genetic covariance between traits, which may facilitate or hinder
+future adaptation depending on the pattern of selection on those traits
+and the structure of the G-matrix \citep{Brodie1992}. If we want to
+predict how ecological communities shape phenotypic evolution, we must
+understand how ecological networks shape the fitness landscape of
+interacting populations.
 
 The loss of biodiversity is altering the structure of ecological
-networks, which may influence evolutionary constraints in a number of
-ways. For example, in a food web, if different consumers impose
-directional selection on different traits of a shared resource, then a
-more diverse consumer community may constrain evolution by increasing
-the number of traits under selection. Alternatively, if consumers impose
-selection on different values of a trait, then their selective effects
-would cancel each other out in more diverse communities. To examine
-these different possibilities, we conducted a field experiment that
-removed a consumer guild that directly and indirectly impacts fitness of
-an abundant insect herbivore (\emph{Iteomyia salicisverruca}, Family
-Cecidomyiidae; fig. \ref{fig:Conceptual}). The larvae of this herbivore
-induce tooth-shaped galls when they feed on the developing leaves of
-willow trees \citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect
-larva from attack by generalist predators (e.g.~ants, spiders), but they
+networks \citep{Landi2018ComplexityStability}, which may influence the
+slope and curvature of the fitness landscape in a number of ways. For
+example, consider how changes in consumer diversity in a food web may
+alter the slope of the fitness landscape for a shared resource. If
+different consumers impose directional selection on different traits of
+the resource, then a more diverse consumer community would increase the
+number of traits under selection, which may constrain the trajectory of
+evolution toward a specific phenotype. Alternatively, if consumers
+impose selection on different values of a trait, then their selective
+effects would cancel each other out in more diverse communities, which
+would allow for a greater diversity of phenotypes to persist. Now
+consider the effects of consumer diversity on the curvature of the
+fitness landscape. If consumers impose selection on different ends of a
+resource's trait distribution, then a more diverse consumer community
+may impose stabilizing selection, which would decrease genetic variance
+in this trait. In contrast, additional consumers may impose disruptive
+selection if their cumulative effect decreases the relative fitness of a
+resource's average trait value, which would increase the genetic
+variance in this trait.
+
+To examine these different possibilities, we conducted a field
+experiment that removed a consumer guild that parasitizes an abundant
+insect herbivore (\emph{Iteomyia salicisverruca}, Family Cecidomyiidae;
+fig. \ref{fig:Conceptual}). The larvae of this herbivore induce
+tooth-shaped galls when they feed on the developing leaves of willow
+trees \citep[\emph{Salix} sp.,][]{Russo2006}. These galls protect larva
+from attack by generalist predators (e.g.~ants, spiders), but they
 suffer high mortality from egg and larval parasitoids
@@
 larval parasitoids to impose selection on gall midge traits (original
-food web, fig. \ref{fig:Conceptual}). The relative abundance of these
-larval parasitoids is much lower than the egg parasitoid
-\citep{Barbour2016}, and thus represents a plausible extinction scenario
-for this system. Larval parasitoids also impose indirect effects on gall
-midge fitness through intraguild predation on the egg parasitoid (fig.
-\ref{fig:Conceptual}). We applied modern statistical methods to quantify
-how changes in food-web structure altered the slope and curvature of the
-gall midge's adaptive landscape. Taken together, our study gives insight
-to how the loss of biodiversity may constrain the evolution of
+food web, fig. \ref{fig:Conceptual}). Larval parasitoids also impose
+indirect effects on gall midge fitness through intraguild predation on
+the egg parasitoid (fig. \ref{fig:Conceptual}). We applied modern
+statistical methods to quantify how changes in food-web structure
+altered the slope and curvature of the gall midge's fitness landscape.
+Taken together, our study gives insight to how the loss of biodiversity
+may alter both the evolutionary trajectory and adaptive potential of
 interacting populations.
@@
 \centering
-\includegraphics{../analyses/complex_simple_foodwebs_v4.jpeg}
+\includegraphics{../analyses/complex_simple_foodwebs_v4_5.jpg}
 \caption{\label{fig:Conceptual}Experimental manipulation of food-web
-structure associated with a leaf-galling midge (\emph{Iteomyia
-salicisverruca}) feeding on the willow \emph{Salix hookeriana}. Black
-arrows denote the flow of energy in this network of trophic
+structure associated with a leaf-galling midge (b, \emph{Iteomyia
+salicisverruca}) feeding on the willow \emph{Salix hookeriana} (a).
+Black arrows denote the flow of energy in this network of trophic
 interactions. In the original food web, we allowed the full suite of egg
@@
 used mesh bags to exclude the guild of larval parasitoids, only allowing
-the egg parasitoid (\emph{Platygaster} sp.) to impose selection. Note
+the egg parasitoid (c, \emph{Platygaster} sp.) to impose selection. Note
 that larval parasitoids also impose indirect effects on gall midge
 fitness through intraguild predation on the egg parasitoid. Larval
-parasitoids include the following species (from left to right):
-\emph{Mesopolobus} sp. (Family: Pteromalidae); \emph{Tetrastichus} sp.
-(Family: Eulophidae); and \emph{Torymus} sp. (Family: Torymidae).}
+parasitoids include the following species: \emph{Mesopolobus} sp. (d,
+Family: Pteromalidae); \emph{Tetrastichus} sp. (e, Family: Eulophidae);
+and \emph{Torymus} sp. (f, Family: Torymidae).}
 \end{figure}
@@
 began developing on willows in early June of 2013. These 128 plants came
-from eight different plant genotypes that spanned the range of trait
+from 8 different plant genotypes that spanned the range of trait
 variation observed in this willow population \citep{Barbour2015}. For
@@
 allowing the full suite of egg and larval parasitoids to impose
-selection. Marking galls with flagging tape ensured that all galls had
-similar phenology when we collected galls later in the season. For the
-removal food web, we enclosed 14 galled leaves with 10x15cm organza bags
-(ULINE, Pleasant Prairie, WI, USA) to exclude three parasitoid species
-that attack during larval development. This treatment did not exclude
-the egg parasitoid \emph{Platygaster} sp., which attacks prior to gall
-initiation \citep[larva initiate gall development in Cecidomyiid
-midges:][]{Gagne1989}. It was not possible to reciprocally manipulate
-parasitoid attack (i.e.~exclude egg parasitoid, but allow larval
-parasitoids), because it was not possible to identify midge oviposition
-sites prior to gall formation. In late August, we collected marked and
-bagged galls from each plant, placed them into 30 mL vials and kept them
-in the lab for 4 months at room temperature. We then opened galls under
-a dissecting scope and determined whether larvae survived to pupation
-(our measure of fitness) or were parasitized. We did not include other
-sources of mortality in our analyses, such as early larval death, as
-they could influence the expression of the gall phenotype and confound
-estimates of selection. For the food-web treatment that excluded larval
-parasitoids, we further restricted our data by removing any incidental
-instances of parasitism by a larval parasitoid. This represented less
-than 3\% of the observations in this food-web treatment and allowed us
-to focus our inferences of selection on those imposed by the egg
-parasitoid. Our final dataset contains survival estimates for 1285
-larvae from 613 galls and 111 plants.
+selection. Marking galls with flagging tape ensured that we compared
+galls with similar phenology in both treatments when we collected galls
+later in the season. For the removal food web, we enclosed 14 galled
+leaves with 10x15cm organza bags (ULINE, Pleasant Prairie, WI, USA) to
+exclude three parasitoid species that attack during larval development.
+This treatment did not exclude the egg parasitoid \emph{Platygaster}
+sp., which attacks prior to gall initiation \citep[larva initiate gall
+development in Cecidomyiid midges:][]{Gagne1989}. It was not possible to
+reciprocally manipulate parasitoid attack (i.e.~exclude egg parasitoid,
+but allow larval parasitoids), because it was not possible to identify
+midge oviposition sites prior to gall formation. In late August, we
+collected marked and bagged galls from each plant, placed them into 30
+mL vials and kept them in the lab for 4 months at room temperature. We
+then opened galls under a dissecting scope and determined whether larvae
+survived to pupation (our measure of fitness) or died due to parasitism.
+We further distinguished whether mortality was caused by an egg or
+larval parasitoid. Early larval death was another important source of
+mortality (17\%), but we excluded these cases from our analysis. We did
+this because early larval death can stunt gall growth, which would
+confound estimates of selection due to parasitism on one of the
+phenotypes we measured (chamber diameter; details given in next
+section). For the food-web treatment that excluded larval parasitoids,
+we further restricted our data by removing any incidental instances of
+parasitism by a larval parasitoid. This represented less than 3\% of the
+observations in this food-web treatment and allowed us to focus our
+inferences of selection on those imposed by the egg parasitoid. Our
+final dataset contains survival estimates for 1285 larvae from 613 galls
+and 111 plants.
 
@@
 multi-chambered gall were scored with the same clutch size. Third, we
-measured oviposition preference as the density of larvae observed on a
-plant in an independent survey. We did this by randomly sampling five
-branches per tree and counting the number of individual gall chambers
-(number of larvae). We then converted these counts to a measure of
-larval density per 100 shoots by counting the number of shoots on the
-last branch we sampled. All larvae collected from the same plant were
-scored with the same oviposition preference. Measuring larval densities
-on plants in the field is a common method for measuring oviposition
-preference \citep{Gripenberg2010}; however, caution must be taken in
-inferring `preference' as larval densities can be influenced by
-processes other than preference \citep{Singer1986}. Fortunately, a
-couple features of our study system suggest that larval densities may be
-a good proxy for oviposition preference. For example, since our data
-comes from a randomized placement of plant genotypes in a common garden,
-there is no consistent bias in which plant genotypes females are exposed
-to while searching for oviposition sites. Also, egg predation is a minor
-source of mortality for galling insects in general \citep{Hawkins1997};
-therefore, we do not expect any prior egg predation to bias our
-estimates of observed larval densities.
-
-\subsection{Quantifying the Adaptive
-Landscape}\label{quantifying-the-adaptive-landscape}
-
-Inferring adaptive landscapes assumes that trait distributions are
+measured oviposition preference for individual plants as the density of
+larvae observed on a plant in an independent survey. We did this by
+randomly sampling five branches per tree and counting the number of
+individual gall chambers (number of larvae). We then converted these
+counts to a measure of larval density per 100 shoots by counting the
+number of shoots on the last branch we sampled. All larvae collected
+from the same plant were scored with the same oviposition preference.
+Measuring larval densities on plants in the field is a common method for
+measuring oviposition preference \citep{Gripenberg2010}; however,
+caution must be taken in inferring `preference' as larval densities can
+be influenced by processes other than preference \citep{Singer1986}.
+Fortunately, two features of our study system suggest that larval
+densities may be a good proxy for oviposition preference. First, since
+our data comes from a randomized placement of plant genotypes in a
+common garden, females midges have equal exposure to many possible plant
+genotypes when choosing an oviposition site. Second, egg predation is a
+minor source of mortality for galling insects in general
+\citep{Hawkins1997}; therefore, we do not expect any prior egg predation
+to bias our estimates of observed larval densities.
+
+\subsection{Quantifying the Fitness
+Landscape}\label{quantifying-the-fitness-landscape}
+
+Inferring the fitness landscape assumes that trait distributions are
 multivariate normal \citep{Lande1983}. To approximate this assumption,
 we log-transformed clutch size and square-root transformed oviposition
-preference. We then scaled all phenotypic traits (mean=0 and SD=1)
+preference. Chamber diameter already had a normal distribution so we did
+not transform it. We then scaled all phenotypic traits (mean=0 and SD=1)
 across treatments prior to our analyses (detailed below) to ensure that
@@
 standardized phenotypic traits (\(i\)) of individuals \textemdash in
-each food-web treatment. Second, we translated selection surfaces into
-the scale of relative fitness (\(w\)) in order to calculate standardized
+each food-web treatment. Second, we scaled selection surfaces relative
+to mean fitness (\(\bar W\)) in order to calculate standardized
 selection gradients. Third, we used our estimates of directional
-selection gradients to characterize the slope of the adaptive landscape,
-which we used to measure selective constraints. Finally, we estimated
-the curvature of the adaptive landscape and used a simulation to explore
-its effects on the adaptive potential of the gall midge population in
-the next generation.
+selection gradients to characterize the slope of the fitness landscape,
+which we used to quantify the effects of food-web structure on the
+trajectory of evolution. Finally, we estimated the curvature of the
+fitness landscape and used a simulation to explore its effects on the
+adaptive potential of the gall midge population in the next generation.
 
@@
 as well as linear (\(\alpha_i\)), quadratic (\(\alpha_{ii}\)), and
-linear interactions (\(\alpha_{ij}\)) between each trait. We also
-allowed these selection surfaces (\(\alpha\)) to vary between food-web
-treatments. Note that to obtain valid estimates of linear selection
-surfaces, we removed nonlinear terms prior to estimating linear
-relationships \citep{Lande1983}. Other approaches have been advocated
-for approximating selection surfaces \citep{Schluter1988}; however, our
+statistical interactions (\(\alpha_{ij}\)) between each trait. Note that
+to obtain valid estimates of linear selection surfaces, we removed
+nonlinear terms prior to estimating linear relationships
+\citep{Lande1983}. Other approaches have been advocated for
+approximating selection surfaces \citep{Schluter1988}; however, our
 approach enables us to calculate selection gradients, and thus is more
-appropriate for approximating the adaptive landscape \citep{Arnold2003}.
+appropriate for approximating the fitness landscape \citep{Arnold2003}.
 To account for the nonindependence of clutch size (measured at gall
@@
 any independent effects of willow genotype on larval survival, we
-modelled gall ID nested within plant ID nested within genotype ID as
-random effects. Although statistical models with random effects are not
-common in analyses of natural selection, we think that modelling random
-effects can mitigate biased estimates of selection due to environmental
-covariances between traits and fitness \citep{Rausher1992}. Since our
-end goal was to characterize the relationship between mean trait values
-and mean fitness (adaptive landscape), we assumed the mean value of our
-random effects (i.e.~setting them to zero) when calculating selection
-surfaces. We then used parametric bootstrapping (1,000 replicates) to
-estimate the effect of food-web treatment on larval survival as well as
-selection surfaces in each food-web treatment. To determine whether
-trait-fitness relationships differed between food-web treatments, we
-calculated the difference in bootstrapped replicates between treatments.
+modelled gall identity nested within plant identity nested within
+genotype identity as random effects. Although statistical models with
+random effects are not common in analyses of natural selection, we think
+that modelling random effects can mitigate biased estimates of selection
+due to environmental covariances between traits and fitness
+\citep{Rausher1992}. Since our end goal was to characterize the
+relationship between mean trait values and mean fitness (fitness
+landscape), we assumed the mean value of our random effects
+(i.e.~setting them to zero) when calculating selection surfaces. We then
+used parametric bootstrapping (1,000 replicates) to estimate the effect
+of food-web treatment on larval survival as well as selection surfaces
+in each food-web treatment. To determine whether trait-fitness
+relationships differed between food-web treatments, we calculated the
+difference in bootstrapped replicates between treatments.
 
@@
 terms of absolute fitness and the coefficients are on a nonlinear scale.
-For example, the coefficients in the above model measure the change in
-the logarithm of the odds of surviving (i.e.
-\(\text{ln}\{W(z)/[1-W(z)]\}\)) associated with 1 SD change in a trait
-with all other traits held fixed at their mean. Therefore, we used the
-method developed by \citet{Janzen1998} to translate selection surfaces
-from the above model into the scale of relative fitness in order to
-calculate directional (\(\beta_i\)), quadratic (\(\gamma_{ii}\)), and
-correlational (\(\gamma_{ij}\)) selection gradients. Briefly, this
-method calculates the average gradient of selection surfaces by
-multiplying the average of \(W(z)[1-W(z)]\) by each regression
-coefficient (e.g. \(\alpha_i\), \(\alpha_{ii}\), or \(\alpha_{ij}\)). We
-then divided this average gradient by the mean fitness (\(\bar W\)) to
-put it on the scale of relative fitness, and thus interpretable as a
-selection gradient. We estimated selection gradients separately for each
-food-web treatment. We also determined whether selection gradients
-differed between food-web treatments by calculating the difference in
+For example, the coefficients in the previously described binomial model
+measure the change in the log-odds of survival associated with 1 SD
+change in a trait with all other traits held fixed at their mean.
+Therefore, we used the method developed by \citet{Janzen1998} to
+translate selection surfaces from the above model into the scale of
+relative fitness in order to calculate directional (\(\beta_i\)),
+quadratic (\(\gamma_{ii}\)), and correlational (\(\gamma_{ij}\))
+selection gradients. Briefly, this method calculates the average
+gradient of selection surfaces by multiplying the average of
+\(W(z)[1-W(z)]\) by each regression coefficient (e.g. \(\alpha_i\),
+\(\alpha_{ii}\), or \(\alpha_{ij}\)). We then divided this average
+gradient by the mean fitness (\(\bar W\)) to put it on the scale of
+relative fitness (\(w=W/\bar W\)), and thus interpretable as a selection
+gradient. We estimated selection gradients separately for each food-web
+treatment. We also determined whether selection gradients differed
+between food-web treatments by calculating the difference in
 bootstrapped replicates between treatments. Note that we doubled all
@@
 
-\textbf{Selective constraints}: The number of selective constraints is
-determined by the slope of the adaptive landscape, which in our study
-corresponds to:
+\textbf{Evolutionary trajectory}: The effect of selection on the
+trajectory of evolution is determined by the slope of the fitness
+landscape, which in our study corresponds to:
 
@@
 where each \(\beta_i\) corresponds to the directional selection gradient
-acting on each trait. By comparing the number of directional selection
-gradients that show clear evidence of contributing to the slope
-(i.e.~95\% CI does not overlap zero) in our food-web treatments, we can
-infer the effect of food-web structure on selective constraints. This
-gives insight as to whether there is a specific combination of
-phenotypes favored by natural selection (i.e.~more traits under
-directional selection), or whether multiple trait combinations have
-comparable fitness (i.e.~less traits under directional selection).
-
-\textbf{Genetic constraints}: The indirect effects of selection on the
-G-matrix
-(\(\Delta\text{G}=\text{G}(\gamma - \beta \beta^\text{T})\text{G}\)) are
-governed by the curvature of the adaptive landscape
+acting on each trait. By comparing selection gradients in each food-web
+treatment (i.e.~95\% CI does not overlap zero), we can infer the effect
+of food-web structure on the trajectory of phenotypic evolution.
+
+\textbf{Evolutionary potential}: The indirect effects of selection on
+the G-matrix (\(\Delta\text{G}=\text{G}\text{C}\text{G}\)) are governed
+by the curvature of the fitness landscape
 (\(\text{C}=\gamma - \beta \beta^\text{T}\)), which in our study
@@
 reflection of the lower triangle. Subtracting these two matrices results
-in the curvature matrix of the adaptive landscape:
+in the curvature matrix of the fitness landscape:
 
@@
 Knowledge of the curvature matrix alone gives an incomplete picture of
-its indirect effect on genetic constraints. This is because genetic
-constraints are ultimately determined by the structure of the G-matrix,
-and therefore also depend on its structure before selection. Although we
-do not know the underlying G-matrix for the traits we measured in this
-experiment, we can still gain insight to how our food-web treatment
-would alter genetic constraints more generally. Specifically, we
-calculated how our best estimate of the curvature matrix (mean values)
-in each treatment changed the structure of \ensuremath{10^{4}} random
-G-matrices for the next generation. We restricted the range of additive
-genetic variance (\emph{V\textsubscript{G}}) in these G-matrices to
+its indirect effect on evolutionary potential. This is because the
+evolutionary potential of a population is ultimately determined by the
+structure of its G-matrix, and therefore also depends on its structure
+before selection. Although we do not know the underlying G-matrix for
+the traits we measured in this experiment, we can still gain insight to
+how our food-web treatment would alter genetic constraints more
+generally. Specifically, we calculated how our best estimate of the
+curvature matrix (mean values) in each treatment changed the structure
+of \ensuremath{10^{4}} random G-matrices for the next generation. We
+restricted the range of additive genetic variance
+(\emph{V\textsubscript{G}}) for each element in these G-matrices to
 between 0 and 0.5 to reflect typical ranges in narrow-sense heritability
@@
 The G-matrix itself is a complex structure, but has a clear theoretical
-link to the evolvability of phenotypic traits \citep{Hansen2008}.
-Evolvability measures the ability for a trait to evolve toward a given
-direction of selection \citep{Hansen2008}. In the absence of knowledge
-about the direction of selection that a population will actually
-experience in the next generation, we can compute its average
-evolvability over random selection gradients
+link to the evolutionary potential, or evolvability of phenotypic traits
+\citep{Hansen2008}. Evolvability measures the ability for a trait to
+evolve toward a given direction of selection \citep{Hansen2008}. In the
+absence of knowledge about the direction of selection that a population
+will actually experience in the next generation, we can compute its
+average evolvability over random directional selection gradients
 \citep{Hansen2008, Melo2015}. By computing the average evolvability
@@
 our data to only include galls where there was variation in larval
-survival within the same gall (i.e.~1 \textgreater{} mean survival
+survival within the same gall (i.e.~1 \textgreater{} survival
 \textgreater{} 0). If we assume that larvae within each gall should have
@@
 experience the same local environment (an assumption our data supports:
-gall ID explains 54\% of the variance in chamber diameter), then the
-relationship between chamber diameter and larval survival in this data
-subset represents the effect of parasitism on trait expression
+gall identity explains 54\% of the variance in chamber diameter), then
+the relationship between chamber diameter and larval survival in this
+data subset represents the effect of parasitism on trait expression
 (i.e.~bias). We used a GLMM with the same structure as described
@@
 on the egg parasitoid. Note that we cannot test the effect of food-web
-structure on the egg parasitoid's adaptive landscape ---we can only
+structure on the egg parasitoid's fitness landscape ---we can only
 estimate selection imposed by larval parasitoids. This comparison is
@@
 and selection gradients with 95\% confidence intervals in brackets. Note
-that for visualizing the adaptive landscape we restrict trait axes to
+that for visualizing the fitness landscape we restrict trait axes to
 \(\pm 1\) SD of the mean trait value. This emphasizes the fact that we
-can only reliably estimate the shape of the adaptive landscape near the
+can only reliably estimate the shape of the fitness landscape near the
 mean phenotype of the population \citep{Arnold2001}. We also plot mean
 larval survival on a natural log scale to accurately reflect the
-mathematical definition of the adaptive landscape \citep{Arnold2003}.
-All data and code to reproduce the reported results are publicly
-available on GitHub
-(\url{https://github.com/mabarbour/complexity_selection}) and have been
-archived on Zenodo (\url{https://zenodo.org/badge/latestdoi/108833263}).
+mathematical definition of the fitness landscape \citep{Arnold2003}. All
+data and code to reproduce the reported results are publicly available
+on GitHub (\url{https://github.com/mabarbour/complexity_selection}) and
+have been archived on Zenodo
+(\url{https://zenodo.org/badge/latestdoi/108833263}).
 
@@
 
-\subsection{Consumer removal increases selective
-constraints}\label{consumer-removal-increases-selective-constraints}
+\subsection{Consumer removal constrains the evolutionary trajectory of
+gall
+midges}\label{consumer-removal-constrains-the-evolutionary-trajectory-of-gall-midges}
 
@@
 0.14 [
-0.27,
-0] }\\
+0,
+0.27] }\\
 
@@
 0.15 [
-0.29,
-0.03] }\\
+0.03,
+0.29] }\\
 
@@
 0.03 [
-0.21,
--0.15] \\
+-0.15,
+0.21] \\
 
@@
 0.03 [
-0.27,
--0.2] \\
+-0.2,
+0.27] \\
 
@@
 0.06 [
-0.32,
--0.2] \\
+-0.2,
+0.32] \\
 
@@
 0.32 [
-0.64,
-0.01] }\\
+0.01,
+0.64] }\\
 
@@
 0.02 [
-0.17,
--0.12] \\
+-0.12,
+0.17] \\
 
@@
 -0.12 [
-0.05,
--0.3] \\
+-0.3,
+0.05] \\
 
@@
 0.03 [
-0.18,
--0.12] \\ 
+-0.12,
+0.18] \\ 
 \hline
@@
 relationship between chamber diameter and survival (selection surfaces:
-contrast \(\alpha_{\text{Diam}}\)= 0.04 {[}0.55, -0.5{]}), but was
+contrast \(\alpha_{\text{Diam}}\)= 0.04 {[}-0.5, 0.55{]}), but was
 simply a consequence of the (expected) lower survival of gall midges in
@@
 they attack after the gall is formed; however, egg parasitoids attack
-prior to gall formation, which suggests that chamber diameter is
-strongly correlated with an unmeasured trait that is under selection
-(e.g.~immune response).
+prior to gall formation, which suggests that chamber diameter is either
+directly related to survival or strongly correlated with an unmeasured
+trait that is under selection (e.g.~immune response).
 
@@
 that mean larval survival is plotted on a natural log scale to reflect
-the mathematical definition of the adaptive landscape.}
+the mathematical definition of the \textbf{fitness} landscape.}
 \end{figure}
@@
 
-To visualize the multivariate effects of these selective constraints, we
-plotted the adaptive landscape for each trait combination in each
-treatment (fig. \ref{fig:MV_Landscape}). The arrows in fig.
-\ref{fig:MV_Landscape} represent mean estimates of directional selection
-gradients, while contours represent predicted survival of the mean
-phenotype in each food-web treatment. Notice that arrows point more
-toward a corner of the adaptive landscape for each combination of traits
-with the removal of larval parasitoids compared to the original food
-web. This indicates that the removal of consumers more strongly favored
-a specific combination of traits, rather than allowing for multiple
-trait combinations to have comparable fitness.
+To visualize the multivariate effects of natural selection, we plotted
+the fitness landscape for each trait combination in each treatment (fig.
+\ref{fig:MV_Landscape}). The arrows in fig. \ref{fig:MV_Landscape}
+represent mean estimates of directional selection gradients, while the
+dotted lines represent predicted survival of the mean phenotype in each
+food-web treatment. Notice that arrows point more toward a corner of the
+fitness landscape for each combination of traits with the removal of
+larval parasitoids compared to the original food web. This indicates
+that the removal of consumers more strongly favored a specific
+combination of traits, rather than allowing for multiple trait
+combinations to have comparable fitness.
 
@@
 \includegraphics{../analyses/MV_landscapes.pdf}
-\caption{\label{fig:MV_Landscape}Two dimensional view of adaptive
-landscapes of gall midge phenotypes in the original food web and with
-the removal of larval parasitoids. Each panel corresponds to a different
-combination of phenotypic traits: clutch size and chamber diameter (A);
-clutch size and oviposition preference (B); oviposition preference and
-chamber diameter (C). Arrows represent mean estimates of directional
-selection gradients, while contours represent predicted larval survival
-of the mean phenotype in each food-web treatment. Notice that arrows
-point more toward a corner of the adaptive landscape for each
-combination of traits with the removal of larval parasitoids compared to
-the original food web. This indicates that the removal of consumers more
+\caption{\label{fig:MV_Landscape}Two dimensional view of
+\textbf{fitness} landscapes of gall midge phenotypes in the original
+food web and with the removal of larval parasitoids. Each panel
+corresponds to a different combination of phenotypic traits: clutch size
+and chamber diameter (A); clutch size and oviposition preference (B);
+oviposition preference and chamber diameter (C). Arrows represent mean
+estimates of directional selection gradients, while
+\textbf{dotted lines} represent predicted larval survival of the mean
+phenotype in each food-web treatment. Notice that arrows point more
+toward a corner of the \textbf{fitness} landscape for each combination
+of traits with the removal of larval parasitoids compared to the
+original food web. This indicates that the removal of consumers more
 strongly favored a specific combination of traits. Note that mean larval
 survival is plotted on a natural log scale to reflect the mathematical
-definition of the adaptive landscape.}
+definition of the \textbf{fitness} landscape.}
 \end{figure}
@@
 
-\subsection{Consumer removal indirectly increases genetic
-constraints}\label{consumer-removal-indirectly-increases-genetic-constraints}
-
-\indent The curvature of the adaptive landscape indirectly affects
-genetic constraints and is influenced by directional, quadratic, and
+\subsection{Consumer removal constrains the evolutionary potential of
+gall
+midges}\label{consumer-removal-constrains-the-evolutionary-potential-of-gall-midges}
+
+\indent The curvature of the fitness landscape indirectly affects
+evolutionary potential and is influenced by directional, quadratic, and
 correlational selection gradients. There was no clear evidence of
@@
 our food-web treatment did alter quadratic selection acting on
-oviposition preference (table \ref{Table:Gradients}). The negative
-relationship between oviposition preference and larval survival dampened
-at high densities in the original food web, but not with the removal of
-larval parasitoids (fig. \ref{fig:UV_Landscape}B). This dampened
-relationship was partly due to a trend for nonlinear selection imposed
-by larval parasitoids (\(\gamma_{\text{Pref:Pref}}\)= 0.18 {[}-0.02,
-0.42{]}), but was also magnified by the lower average survival in the
-original food web. This was likely a result of larval parasitoids
-imposing greater mortality on egg parasitoids at high gall midge
-densities (see \textbf{Selection on egg parasitoids} section), and thus
-a less than additive effect on gall midges.
+oviposition preference (table \ref{Table:Gradients}). In particular, we
+observed disruptive selection in the original food web, with selection
+favoring females that either avoided high densities (\textless{}0.5 SD
+above mean density), or if gall densities were high enough
+(\textgreater{}0.5 SD above mean), then selection favored females that
+were attracted to high densities (fig. \ref{fig:UV_Landscape}B). This
+nonlinear relationship was partly due to a trend for disruptive
+selection imposed by larval parasitoids (\(\gamma_{\text{Pref:Pref}}\)=
+0.18 {[}-0.02, 0.42{]}), but was also magnified by the lower average
+survival in the original food web. This was likely a result of larval
+parasitoids imposing greater mortality on egg parasitoids at high gall
+midge densities (see \textbf{Selection on egg parasitoids} section),
+which would act to increase the relative fitness of gall midges at high
+densities.
 
@@
 calculated the curvature (\(\text{C}=\gamma - \beta \beta^\text{T}\)) of
-the adaptive landscape in each food-web treatment.
+the fitness landscape in each food-web treatment.
 
@@
 Interestingly, when we translate the effect of the curvature matrix onto
-genetic constraints in the next generation, we see that the removal of
-consumers had a general tendency to decrease evolvability (fig.
+evolutionary potential in the next generation, we see that the removal
+of consumers had a general tendency to decrease evolvability (fig.
 \ref{fig:Evolvability}). Specifically, the removal food web decreased
@@
 such that the impact of larval parasitoids increased nonlinearly with
-higher gall midge densities (fig. \ref{fig:EggPtoid_Selection}).
+higher gall midge densities (fig. \ref{fig:EggPtoid_Selection}). This
+may indicate that larval parasitoids switch to target galls that have
+been parasitized by an egg parasitoid once egg parasitoid densities are
+high enough. This prey switching behavior would contribute to the
+disruptive selection we observed on gall midge preference by increasing
+the relative fitness of gall midges at high densities (fig.
+\ref{fig:UV_Landscape}B).
 
@@
 We found that the removal of larval parasitoids constrained phenotypic
-evolution in gall midges in two key ways. First, more traits contributed
-to the slope of the adaptive landscape in the absence of larval
-parasitoids, suggesting greater constraints on the trajectory of
-phenotypic evolution. Second, removing larval parasitoids altered the
-curvature of the adaptive landscape in such a way that tended to
-decrease the evolvability of associated traits. Assuming these traits
-have other ecological functions, then this decrease in evolvability
-could constrain the gall midge's adaptive potential in the face of novel
-selection pressures. Our experiment also revealed evidence of indirect
-selection pressures, suggesting that the loss of consumers may have
-complex effects on the trajectories of phenotypic evolution. Taken
-together, our study provides experimental evidence from the field that
-the loss of consumers may constrain the adaptive potential of remaining
-populations.
+evolution in gall midges in two key ways. First, we observed directional
+selection on more traits in the absence of larval parasitoids,
+suggesting greater constraints on the trajectory of phenotypic
+evolution. Second, removing larval parasitoids altered the curvature of
+the fitness landscape in such a way that tended to decrease the
+evolvability of associated traits. Assuming these traits have other
+ecological functions, then this decrease in evolvability could constrain
+the gall midge's adaptive potential in the face of novel selection
+pressures. Our experiment also revealed evidence of indirect selection
+pressures, suggesting that the loss of consumers may have complex
+effects on the trajectories of phenotypic evolution. Taken together, our
+study provides experimental evidence from the field that the loss of
+consumers may constrain the adaptive potential of remaining populations.
 
@@
 others \citep{Weis1985, Abrahamson1997, Start2016, Start2018}, then
-consumer diversity acts to neutralize selection and relax selective
-constraints. On the other hand, different consumers may impose selection
-on different traits; therefore, a more diverse consumer community may
-favor a particular combination of traits and increase selective
-constraints. Examples of this include strong genetic covariances in
-plant resistance to different insect herbivores
+consumer diversity acts to neutralize selection, which can maintain
+larger evolvability. On the other hand, different consumers may impose
+selection on different traits; therefore, a more diverse consumer
+community may favor a particular combination of traits and increase
+selective constraints. Examples of this include strong genetic
+covariances in plant resistance to different insect herbivores
 \citep{Maddox1990, Wise2007, Wise2013}, although there are also examples
@@
 we excluded larval parasitoids due to changes in the curvature of the
-adaptive landscape. This result was driven by nonlinear selection on
+fitness landscape. This result was driven by disruptive selection on
 gall midge oviposition preference in the original food web, which was
-due to both increases in intraguild predation and the lower mean
-survival of gall midges. While these results are intriguing, they still
-indicate that the indirect effects of selection are contingent on the
-structure of a population's G-matrix (e.g.~consumer removals
-\emph{increased} evolvability in 29\% of the scenarios). This highlights
-the importance of future studies to characterize the G-matrix in order
-to accurately predict how changes in network context will alter the
-evolutionary potential of remaining populations. Indeed, current theory
-often assumes genetic variances and covariances remain constant over
-time rather than dynamically changing with the network context
-\citep{McPeek2017, Guimaraes2017}. Our empirical results highlight the
-need to explore the evolutionary consequences of not only direct effects
-of selection, but indirect effects on genetic constraints that emerge in
-a network of interacting species.
+likely due to both increases in intraguild predation on egg parasitoids
+(i.e.~prey switching) and the lower mean survival of gall midges. This
+pattern of selection acts to increase genetic variation in oviposition
+preference, which in turn enhances the ability of the gall midge
+population to respond to uncertain selection pressures in the next
+generation (i.e.~evolvability). This pattern of selection also indicates
+the possibility of evolutionary bistability, where different initial
+conditions (e.g.~mean oviposition preference) select for different
+phenotypes of the same species in similar environments
+\citep{Landi2018LifeHistory}. Thus, this pattern of selection may
+contribute to genetic and phenotypic diversity both within and among
+populations. Current theory, however, often assumes genetic variances
+and covariances remain constant over time and space rather than
+dynamically changing with the network context
+\citep{McPeek2017, Guimaraes2017, Medeiros2018}. Our empirical results
+highlight the need to explore the evolutionary consequences of not only
+direct effects of selection, but indirect effects on genetic constraints
+that emerge in a network of interacting species.
 
@@
 parasitoids. For example, we see clear evidence of all three traits
-being under directional selection (i.e.~greater selective constraints,
-table S2) as well as a decrease, albeit smaller, in trait evolvability
-under different G-matrix scenarios (57\%, fig. S1). This suggests that
-our results could be robust to this caveat, which was simply not
-possible to manipulate given the biology of our system (see
-\textbf{Manipulating Food-web Structure} section for explanation).
+being under directional selection (i.e.~greater constraints on the
+trajectory of evolution, table S2) as well as a decrease, albeit
+smaller, in trait evolvability under different G-matrix scenarios (57\%,
+fig. S1). This suggests that our results could be robust to this caveat,
+which was simply not possible to manipulate given the biology of our
+system (see \textbf{Manipulating Food-web Structure} section for
+explanation).
 
@@
 densities, which could intensify future selection on gall midge
-oviposition preference. A growing number of experiments over the past
-two decades have demonstrated the presence and potential importance of
-indirect evolutionary effects that emerge in ecological communities
+oviposition preference. This suggests that the loss of larval
+parasitoids would likely impose even greater constraints on the
+trajectory of evolution than our current estimates indicate.
+Interestingly, this increase in the strength of selection on gall midges
+may reduce their densities, which would weaken selection imposed on
+willows by the gall midge through an evolutionary trophic cascade. A
+growing number of experiments over the past two decades have
+demonstrated the presence and potential importance of indirect
+evolutionary effects that emerge in ecological communities
 \citep{Pilson1996, Juenger1998, Stinchcombe2001, Lankau2007, Walsh2008, Walsh2010, terHorst2010, Sahli2011, Lau2012, terHorst2015, Schiestl2018, Start2019}.
@@
 
-Our study gives insight to how the loss of consumers alters evolutionary
-constraints on remaining populations. In particular, it hints at a
+Our study gives insight to how the loss of consumers alters natural
+selection, and in turn the evolutionary trajectory and adaptive
+potential of remaining populations. In particular, it hints at a
 potential insidious effect of local extinctions that compromises the
@@
 models of eco-evolutionary dynamics focus on phenotypic change in a
-single trait, yet our results highlight that the number of traits under
-selection may change with the network context. Importantly, we found
-that different species/guilds imposed different selection pressures.
-Knowing these hidden selection pressures is critical for prediction,
-because the trajectory of evolution will depend on the nature of change
-in the ecological community. We expect that a continued integration of
-adaptive landscapes and ecological networks will enhance our ability to
-predict the evolutionary consequences of changes in ecological
-communities.
+single trait \citep[but see][]{Brown2007, Leimar2009}, yet our results
+highlight that the number of traits under selection may change with the
+network context. Importantly, we found that different species/guilds
+imposed different selection pressures. Knowing these hidden selection
+pressures is critical for prediction, because the trajectory of
+evolution will depend on the nature of change in the ecological
+community. We expect that a continued integration of fitness landscapes
+and ecological networks will enhance our ability to predict the
+evolutionary consequences of changes in ecological communities.
 
@@
 assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
-For funding support, we thank the University of British Columbia (James
-Robert Thompson Fellowship and Four-Year Fellowship to M.A.~Barbour),
-NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
-Science Foundation (grant 31003A\_160671 to J. Bascompte). The authors
-declare no conflict of interest.
+This manuscript was improved by incorporating feedback from two
+anonymous reviewers. For funding support, we thank the University of
+British Columbia (James Robert Thompson Fellowship and Four-Year
+Fellowship to M.A.~Barbour), NSERC (Discovery grant to Greg Crutsinger),
+and the Swiss National Science Foundation (grant 31003A\_160671 to J.
+Bascompte). The authors declare no conflict of interest.
 
